### 2017-09-11 palatini.tex
adding frame

\section{The Palatini formulation}
\brian{I first want to recall the palatini action and then formulate it using BV-BRST.}

\subsection{The physical theory}
In this section we construct a perturbative BV theory modeling the first-order Palatini approach to $N=1$ supegravity in four dimensions.

The na\"{i}ve fields in the first-order formalism are the following: 
\begin{align*}
e & \in \Omega^1(\RR^4 ; T \RR^4) \\
\omega & \in \Omega^1(\RR^4 ; \so(4)) \\
\psi & \in \Omega^1(\RR^4 ; \Pi S) .
\end{align*}

The na\"{i}ve action (the one involving only the fields above) splits up into two parts: $S (e, \omega, \psi) = S_{\rm Pal}(e, \omega) + S_{\rm fer}(e, \omega, \psi)$ where $S_{\rm Pal}$ is the ordinary Palatini action from general relativity
\ben
S_{\rm Pal} (e, \omega) = \int \epsilon(F_\omega \wedge e \wedge e)
\een
and
\ben
S_{\rm fer}(e,\omega,\psi) = \int \<\psi, e \cdot \d_\omega \psi\> .
\een
We explain the notation in the functionals above. 
In the top line the $\wedge$ product denotes the usual product on forms together with the exterior tensor product in the respective tensor bundles that the forms take values in. 
The symbol $\epsilon$ denotes the composition $\tensor^4 \RR^4 \to \wedge^4 \RR^4 \cong \RR$. 
In the second line $e \wedge \d_\omega \psi$ denotes wedge product of forms combined with Clifford multiplication $T \RR^n \tensor S \to S$. 
The pairing in the second line is the canonical \brian{finish}.

If we did not have the term $S_{\rm fer}$, the equations of motion for the variation of the field $\omega$ result in the condition that $\omega$ is the spin connection associated to the vielbien $e$. 
Plugging this in to the equation of motion for $e$ result in the usual Einstein field equations.

Suppose now that we turn on the term $S_{\rm fer}$. 
Since $S_{\rm fer}$ involves a dependence on $\omega$, the equations of motion for variation of $\omega$ do not quite say that $\omega$ is the spin connection for $e$. 
Instead, it states that the following equation holds
\ben
\omega = \omega(e) + K(\psi)
\een
where $K(\psi)$ depends quadratically on the field $\psi$ is the spin 
Explicitly, the function $K$ is of the form
\ben
K(\psi) = ?? 
\een 
\brian{I can't seem to find a coordinate independent way of writing this, but the formula I found is
\ben
K(\psi)_{\mu \nu \rho} = -\frac{1}{4} (\Bar{\psi}_\mu \gamma_\rho \psi_\nu - \Bar{\psi}_\nu \gamma_\mu \psi_\rho + \Bar{\psi}_\rho \gamma_\nu \psi_\mu). 
\een
}
\brian{The remaining equations of motion should yield the Eienstein equations with torsion. Not sure of the best way to interpret $K$ as a torsion term.}

\subsection{Symmetries}

There are two types of symmetries present in the theory, bosonic and fermionic. 
The bosonic gauge Lie algebra is of the form
\ben
(f , \varphi) \in \Omega^0(\RR^4 ; \mathfrak{i}\fs\fo(4)) = \Omega^0(\RR^4 ; \fs\fo(4)) \ltimes \Omega^0(\RR^4 ; \RR^4) . 
\een 
Given such an element the action on fields is of the form
\ben
\begin{pmatrix}
e \\ \omega \\ \psi 
\end{pmatrix} 
\mapsto
\begin{pmatrix}
e + L_\varphi e + [f,e] \\
\omega + L_\varphi \omega + \d_\omega f \\
\psi + L_\varphi \psi + [f,\psi] .
\end{pmatrix} .
\een
Here, $L_\varphi (-)$ denotes Lie derivative of the natural tensor and $\d_\omega = \d + \omega$ is the covariant derivative. 
We interpret this action as saying that the vector field $\varphi$ acts by infinitesimal diffeomorphisms, and the Lie algebra valued function $f$ acts by an ordinary gauge symmetry.

There are also fermionic, or {\em super}, symmetries present. 
The fermionic factor of the gauge Lie algebra is of the form 
\ben
\chi \in \Omega^0(\RR^4 ; \Pi S) .
\een
The action of $\chi$ on the fields is of the form
\ben
\begin{pmatrix}
e \\ \omega \\ \psi 
\end{pmatrix} 
\mapsto
\begin{pmatrix}
e + \Gamma(\chi, e) \\
\omega \\
\psi + \d_\omega \chi
\end{pmatrix} .
\een 
Here $\Gamma$ is obtained from $\fs\so(4)$-invariant vector valued map $\Gamma_0 : S \tensor S \to \RR^4$ by tensoring with functions $C^\infty(\RR^4)$. 
It is a classical calculation to show that $S_{\rm Pal} + S_{\rm fer}$ is invariant under this supersymmetry, see Section 9.4 of \cite{freedman} for instance.

\subsection{BV-BRST}

We now proceed to formulate the Palatini action in the BV-BRST formalism. 
We will work perturbatively from this point on, so it will be necessary to fix a solution to the classical equations of motion $(e_0,\omega_0,\psi_0)$.

We will write down a local $L_\infty$ algebra on $\RR^4$ whose Maurer-Cartan elements coincide with the solutions to the classical equation of motion.
Closure of $L_\infty$ brackets under the the generalized Jacobi relations will encode the gauge symmetries in the previous section. 
The final piece of data is that of a (-3)-shifted symplectic structure on this $L_\infty$ algebra. 
This pairing allows us to encode the action functional described above. 
Note that this $L_\infty$ algebra will have two gradings: an internal cohomological grading that we will refer to as the ``degree'', and a $\ZZ/2$ grading that we will refer to as the ``super degree".

The degree zero part of the $L_\infty$ algebra is the $\ZZ/2$ graded space of gauge symmetries $\Omega^0(\RR^4 ; \fs\fo(4)) \oplus \Omega^0(\RR^4 ; \RR^4) \oplus \Omega^0(\RR^4 ; \Pi S)$. 
The degree one part of the $L_\infty$ algebra is simply the physical space of fields $\Omega^1(\RR^4 ; \fs\fo(4)) \oplus \Omega^1(\RR^4 ; \RR^4) \oplus \Omega^1(\RR^4 ; \Pi S)$.

\[\xymatrix{
   \Omega^0(X; \CC^4) \ar[r]^\d & \Omega^1(X; \CC^4) \ar[r]^{e_0 \wedge \d} &\Omega^3(X; \wedge^2 \CC^4) \ar[r]^\d &\Omega^4(X; \wedge^2 \CC^4) \\
   \Omega^0(X; \so(4;\CC)) \ar[r]^\d \ar[ur]^{\cdot  e_0} & \Omega^1(X; \so(4;\CC)) \ar[r]^{e_0 \wedge \d} \ar[ur]^{\cdot(e_0 \wedge e_0)} &\Omega^3(X; \wedge^3 \CC^4) \ar[r]^\d \ar[ur]^{e_0 \wedge} &\Omega^4(X; \wedge^3 \CC^4) \\
   \Pi\Omega^0(X; S) \ar[r]^\d & \Pi\Omega^1(X; S) \ar[r]^{\rho(e_0) \d} &\Pi\Omega^3(X; S) \ar[r]^\d &\Pi\Omega^4(X; S) \\
}\]

The first two rows are bosonic, and the last row is fermionic. 
The operator $\cdot e_0 : \Omega^0(\RR^4 ; \fs \fo(4)) \to \Omega^1(\RR^4 ; \CC^4)$ is given by acting on $e_0$. 
The dual operator $e_0 \wedge : \Omega^3(\RR^4 ; \wedge^3 \CC^4) \to \Omega^4(\RR^4 ; \wedge^2 \CC^4)$ first identifies $\wedge^3 \CC^4 \cong \CC^4$ using the metric and then wedges with $e_0$. 
The map $\cdot (e_0 \wedge e_0)$ is given by acting on $e_0 \wedge e_0$ via the second exterior power of the fundamental representation of $\fs \fo (4)$.

### 2017-12-19 2017 June 6 - chiral supermultiplet.tex
chiral multiplet

\documentclass[10pt]{amsart}

\usepackage{macros,slashed}
\linespread{1.25}

\title{$\cN = 1$ chiral supermultiplet}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\def\SU{{\rm SU}}
\def\Spin{{\rm Spin}}
\def\dvol{{\rm dvol}}
\def\dslash{\slashed{\partial}}
\begin{document}
\maketitle

In this section we describe how the $\cN = 1$ chiral supermultiplet in four dimensions is related to the two dimensional $\beta\gamma$ system.

\subsection{}

\subsubsection{}

We work on the four manifold $\RR^4$ equipped with the flat metric. We will write $\Omega^i$ for the space of smooth $i$-forms on $\RR^4$. The space of sections of the spinor bundles are denoted by $\sS_{\pm} = C^\infty(\RR^4 ; S_{\pm})$ where $S_{\pm}$ are the defining representations of the two copies of $\SU(2)$ in $\Spin(4)$. Write $\dvol = \d x_1 \cdots \d x_4$ and $\star$ for the Hodge star operator.

We fix an even dimensional real vector space $V$ equipped with a complex structure, denoted by $J$, and a Hermitian inner product, denoted by $h$.

\subsubsection{}

\begin{dfn}
The $N=1$ chiral supermultiplet on $\RR^4$ with values in the complex vector space $V$ equipped with a Hermitian pairing $h$ has space of fields
\bestar
\Phi_+ & = & (\varphi_+ , \psi_+, F_+) \in \Omega^0 \tensor V \oplus \cS_+ \tensor V \oplus \Omega^2 \tensor V \\
\Phi_- & = & (\varphi_-,\psi_-,F_-) \in \Omega^0 \tensor V \oplus \cS_- \tensor V \oplus \Omega^2 \tensor V 
\eestar
and action functional given by
\ben
S^{\rm SO}(\varphi,\psi,F) = \int h(\varphi \tensor \Delta \varphi)\dvol + \int h(\<\psi_+ , \dslash \psi_-\>) \dvol +\int F^2
\een
where $\<-,-\>$ denotes the standard symplectic pairing $S_+ \tensor S_+ \to \CC$. 
\end{dfn}

We have written the fields as a pair of superfields, a chiral one $\Phi_+$ and an anti-chiral one $\Phi_-$.

It will be useful for our purposes to write the chiral supermultiplet in the BV-BRST formalism. There are no gauge symmetries, so all that this amounts to is the the introduction of the anti-fields to the fields we have already written.
\bestar
\Phi_+^\vee & = & (\varphi_+^\vee, \psi_+^\vee, F_+^\vee) \in \Omega^4 \tensor V \oplus \cS_-' \tensor V \oplus \Omega^2 \tensor V \\
\Phi_-^\vee & = & (\varphi_-^\vee, \psi_-^\vee, F_-^\vee) \in \Omega^4 \tensor V \oplus \cS_-' \tensor V \oplus \Omega^2 \tensor V .
\eestar
We note that the anti-field to a positive spinor $\psi_+ \in \cS_{\pm}$ is a spinor $\psi_\pm^\vee \in \cS_+$ of the same chirality. The prime simply indicates the same underlying spinor bundle except we are viewing it as an anti-field. Using this notation, we can define the classical theory in the BV formalism in a succinct way.

\begin{dfn} The $N=1$ chiral supermultiplet on $\RR^4$ in the BV formalism is the $\ZZ \times \ZZ/2$ graded theory with complex of fields given by
\end{dfn}

The $R$-charge of an anti-field is opposite to that of the corresponding field. Thus, $\psi_{\pm}^\vee$ has $R$-charge $\mp 1$ and $F^\vee_{\pm}$ has $R$-charge $\mp 2$.

We will perform a twist of the free chiral supermultiplet by a fixed constant spinor $Q \in \cS_-$. This element acts on the fields $\Phi = (\varphi_+, \psi_+, F)$ as above:
\ben
Q \cdot (\varphi_+, \psi_+, F) = (0, Q \cdot (\d \varphi_+), \<Q, \dslash \psi_+\>) .
\een
The action of $Q$ on the anti-fields reads is determined by compatibility with the $(-1)$-shifted symplectic pairing. Explicitly it is
\ben
Q \cdot (\varphi_+^\vee, \psi_+^\vee, F) = (\<Q, \dslash \psi_+^\vee\>, Q \cdot (\star F_+^\vee), 0) .
\een

We have arrived at the following.

\begin{prop} The twist of the $N=1$ free chiral supermultiplet on $\RR^4$ with values in the hermitian vector space $V$ by an element $Q \in \cS_-$ is equivalent to the free $\beta\gamma$ system on $\CC^2$ with values in $V$:
\ben
(\gamma,\beta) \in \Omega^{0,*}(\CC^2 ; V) \oplus \Omega^{1,*}(\CC^2 ; V^\vee)[1] .
\een
The action functional is $S(\gamma,\beta) = \int \<\beta, \dbar \gamma\>$ where $\<-,-\>$ is the evaluation pairing on $V$. 
\end{prop}

\subsubsection{}
We will introduce the following ``first-order" reformulation of the chiral supermultiplet that will be convenient for our description of it as a BV theory. Introduce additional scalar fields of the form
\ben
B \in \Omega^3 \tensor V
\een
and define the action 
\bestar
S^{\rm FO}(\varphi, B , \psi , F) & = &  \int h(B \wedge \d \varphi) - \frac{1}{2} \int h(B \wedge \star B)  \\ & + & \int h(\<\psi_+ , \dslash \psi_-\>) \dvol 
\eestar

\begin{lem} The theories $S^{\rm SO}$ and $S^{\rm FO}$ are classically equivalent. 
\end{lem}
\begin{proof} We show that the spaces of solutions to the classical equations of motion are equivalent. The equations of motion for the chiral supermultiplet read
\bestar
\Delta \varphi & = & 0 \\
\dslash \psi & = & 0 \\
F & = & 0 .
\eestar 
Next, consider $S^{\rm FO}$. The pieces of the action functional involving $\psi, F$ are identical. We use the variation of the scalar field $\varphi \mapsto \varphi + \delta \varphi$ to obtain the equation of motion $\d B = 0$. The variation $B \mapsto B + \delta B$ yields the equation $\d \varphi - h^\vee(\star B)$. This equation is equivalent to $\star \d \varphi = h^\vee (B)$. Applying $\d$ to this equation and using the equation $\d B = 0$ we obtain $\d \star \d \varphi = \Delta \varphi = 0$, as desired.

An explicit equivalence at the level of fields can be written as follows. \brian{Want $\varphi \mapsto \varphi, B \mapsto \star h^\vee(\d \varphi) + h^\vee(F)$.}
\end{proof}

\brian{physics description of susy action}

\subsubsection{}
We describe the theory $S^{\rm FO}$ as a classical theory in the BV formalism. The space of fields
\[
\xymatrix{
& \ul{0} & \ul{1} \\
{\rm Fermion \; degree}\;\; \ul{0} & \Omega^0 \tensor V \ar[r]^-{\d_+} & (\Omega^1 \tensor V)_+ \\
{\rm Fermion \; degree} \; \; \ul{0} & (\Omega^{3} \tensor V)_- \ar[r]^-{\d} & \Omega^4 \tensor V  \\
{\rm Fermion \; degree} \; \; \ul{1} & (\sS_+ \oplus \sS_-) \tensor V \ar[r]^-{\dslash} & (\sS'_-\oplus \sS'_+) \tensor V \\
}
\]

\end{document}

### 2018-06-18 2d_bcov.tex
Create 2d_bcov.tex

\documentclass[10pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

%\usepackage{tikz}
%\usetikzlibrary{arrows,shapes}
%\usetikzlibrary{trees}
%\usetikzlibrary{matrix,arrows}
%\usetikzlibrary{positioning}
%\usetikzlibrary{calc,through}
%\usetikzlibrary{decorations.pathreplacing}
%\usepackage{pgffor}

\def\PV{{\rm PV}}

\title{BCOV theory on a complex surface}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\begin{document}
\maketitle
\tableofcontents

Suppose $X$ is a complex manifold of complex dimension $2$. equipped with a holomorphic symplectic form $\omega \in \Omega^{2,hol}(X)$.
We study BCOV theory on $X$, which should be thought of as the theory of ``divergence-free holomorphic polyvector fields" with respect to the fixed symplectic structure.

Let $\PV^{k, hol}(X)$ be the space of holomorphic $k$-polyvector fields; these are holomorphic sections of the $k$th exterior power of the holomorphic tangent bundle $\wedge^k T^{1,0}X$.
The holomorphic volume form identifies
\ben
\PV^{0,hol}(X) \cong_\omega \Omega^{2,hol}(X) \;\;, \;\; \PV^{1,hol}(X) \cong_\omega \Omega^{1,hol}(X) \;\; , \;\; \PV^{2,hol}(X) \cong_\omega \Omega^{0,hol}(X) = \sO^{hol}(X) .
\een
In particular, the holomorphic de Rham operator $\partial : \Omega^{i,hol}\to \Omega^{i+1,hol}$ defines an operator
\be\label{partial}
\partial : \PV^{k,hol}(X) \to \PV^{k-1,hol}(X) .
\ee
At the crudest level, the fields consist of those holomorphic polyvector fields in the kernel of the operator $\partial$.

The problem with this definition is that it does not fit the usual definition of the space of fields for a classical field theory.
In particular, the space of fields is not equal to the smooth sections of a vector bundle. 
The solution to this problem consists of two steps:
\begin{itemize}
\item Resolve the space of holomorphic polyvector fields via its Dolbeualt resolution. 
This amounts to replacing ${\rm PV}^{k,hol}(X)$ by the complex $\PV^{k,*}(X)$ equipped with its Dolbeualt differential 
\ben
\dbar : \PV^{k,l}(X) \to \PV^{k,l+1}(X) .
\een
As sheaves one has $\PV^{k,*} \simeq \PV^{k,hol}$. 
We equip the double complex $\PV^{*,*}(X)$ with the grading coming from totalization.
Notice that since the operator $\partial$ in (\ref{partial}) is a holomorphic differential operator it extends in a natural way to $\PV^{*,*}(X)$. 
\item The next step is to resolve the kernel
\ben
\ker \partial \subset \PV^{*,hol}(X),
\een
or more accurately its Dolbeualt version
\ben
(\ker \partial, \dbar) \subset \left(\PV^{*,*}(X), \dbar\right)
\een
One introduces the formal parameter $t$ of cohomological degree $2$ ...
\end{itemize}

The non-local form of the action functional is
\ben
S(\alpha) = \frac{1}{2} \int_X \alpha \dbar (\partial^{-1} \alpha) + \frac{1}{3} \int_X \alpha^3 .
\een
Notice that in this form only elements in $\PV^{\geq 1, *}$ appear in the action functional.
There is a change of coordinates that will put this action functional in a more familiar form.

Suppose $\alpha^{1,*}$ is in the kernel of $\partial : \PV^{1,*} (X) \to \PV^{0,*}(X)$.
Then, locally, we can assume that $\alpha^{1,*} = \partial (\alpha^{2,*})$ for some $\alpha^{2,*} \in \PV^{2,*}(X)$.
Under the isomorphisms between polyvector fields and Dolbeualt forms, we redefine our fields via
\begin{align*}
\PV^{2,*}(X) & \cong_\omega \Omega^{0,*}(X)\\
\alpha^{2,*} & \leftrightarrow A^{0,*} 
\end{align*}
and
\begin{align*}
PV^{0,*}(X) & \cong_\omega \Omega^{2,*}(X) = \omega \cdot \Omega^{0,*}(X) \\
\alpha^{0,*} & \leftrightarrow \omega \cdot B^{0,*}
\end{align*}
In particular, the new fields $A,B$ are now Dolbeault forms. 
Keeping track of the cohomological degree, we find that the our new space of fields is
\ben
A + \epsilon B \in \Omega^{0,*}(X)[\epsilon][1]
\een
where $\epsilon$ is a formal parameter of degree $+1$.
In particular, the fields in degree zero are $A^{0,1} \in \Omega^{0,1}(X)$ and $B^0 \in \Omega^0(X)$. 
In terms of these new fields, the action functional takes the form
\be\label{action2}
S(A,B) = \int_X \omega B \dbar A + \frac{1}{2} \int_X B \partial A \partial A .
\ee

There is yet another way we can recast this classical theory that more clearly reflects the dependence of the theory on the symplectic form. 
As above, suppose $X$ is a symplectic surface with holomorphic symplectic form $\omega$. 
We will consider the Lie algebra of holomorphic vector fields $\cX^{hol}(X)$, or more accurately, its Dobleault resolution $\cX^{*} (X) = \Omega^{0,*}(X, T^{1,0}X)$.

There is a sub Lie algebra of $\cX^{hol}(X)$ consisting of holomorphic {\em symplectic} vector fields
\ben
\{X \in \cX^{hol}(X) \; | \; L_X \omega = 0\} \subset \cX^{hol}(X) .
\een
Since the symplectic form is holomorphic, there is a resolution via the Dolbeualt complex.
Indeed, there is a sub dg Lie algebra 
\ben
\cX_{symp}^* (X) = \{\xi \in \Omega^{0,*}(X, T^{1,0}X) \; | \; L_\xi \omega = 0\} \subset \cX^*(X) .
\een
When one equips the left hand side with the $\dbar$ differential, this is a resolution for holomorphic symplectic vector fields.

There is a related Lie algebra of holomorphic {\em Hamiltonian} vector fields. 
This Lie algebra has underlying vector space the space of holomorphic functions $\sO^{hol}(X)$ and is equipped with Lie bracket given by the holomorphic Poisson bracket $\{-,-\}_\omega$. 
As we've done several times already, this Lie algebra admits a Dolbeualt resolution as a dg Lie algebra 
\be\label{hamiltonian}
\left(\Omega^{0,*}(X), \dbar, \{-,-\}_\omega \right).
\ee

Locally, every holomorphic symplectic vector field is Hamiltonian. 
Thus, as sheaves of dg Lie algebras we might as well replace $\cX_{symp}^{*}(X)$ with the dg Lie algebra (\ref{hamiltonian}).

Given any dg Lie algebra, there is a standard construction to define a classical BV theory.

The fields are
\ben
(A, B) \in \Omega^{0,*}(X) [1] \oplus \Omega^{2,*}(X) 
\een
The action functional is
\ben
\int_X B \dbar A + \frac{1}{2} \int_X B \{A, A\} .
\een
6
\end{document}

### 2018-06-19 2d_bcov.tex
2d bcov

@@
 \maketitle
-\tableofcontents
+%\tableofcontents
 
-Suppose $X$ is a complex manifold of complex dimension $2$. equipped with a holomorphic symplectic form $\omega \in \Omega^{2,hol}(X)$.
-We study BCOV theory on $X$, which should be thought of as the theory of ``divergence-free holomorphic polyvector fields" with respect to the fixed symplectic structure.
+Suppose $X$ is a complex manifold of complex dimension $\dim_\CC(X) = 2$ equipped with a holomorphic symplectic form $\omega \in \Omega^{2,hol}(X)$.
+We study BCOV theory on $X$, which should be thought of as the theory of ``divergence-free holomorphic polyvector fields" with respect to the volume form determined by the fixed symplectic structure.
 
@@
 There is a related Lie algebra of holomorphic {\em Hamiltonian} vector fields. 
-This Lie algebra has underlying vector space the space of holomorphic functions $\sO^{hol}(X)$ and is equipped with Lie bracket given by the holomorphic Poisson bracket $\{-,-\}_\omega$. 
+This Lie algebra has underlying vector space the space of holomorphic functions $\sO^{hol}(X)$ and is equipped with Lie bracket given by the holomorphic Poisson bracket $\{-,-\}_\omega$ determined by the symplectic form $\omega$.
 As we've done several times already, this Lie algebra admits a Dolbeualt resolution as a dg Lie algebra 
@@
 
-Given any dg Lie algebra, there is a standard construction to define a classical BV theory.
+Given any dg Lie algebra, there is a standard construction to define a classical BV theory. \brian{cotangent theory}
 
@@
 The action functional is
-\ben
+\be\label{action3}
 \int_X B \dbar A + \frac{1}{2} \int_X B \{A, A\} .
-\een
-6
+\ee
+
+The following lemma is an immediate consequence of our discussion.
+
+\begin{lem} 
+The action functional (\ref{action2}) is equivalent to the action functional (\ref{action3}).
+In other words, BCOV theory on a complex surface is equivalent to the cotangent theory associated to the Lie algebra of holomorphic symplectic vector fields.
+\end{lem}
+
 \end{document}

### 2018-09-18 Twist_Notes_18_9.tex
New notes on twisting in BRST language

\documentclass[10pt, oneside]{article}
\input math_headers.sty

\title{Notes on Twisted SYM and SUGRA}
\author{Chris Elliott}
\date{\today}

\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

\addbibresource{Twist.bib}

\begin{document}

\section{Some BRST Twisting Calculations}

The following is Pavel's suggestion, as I understand it.  I'm going to only consider linear spaces of fields (complexes rather than $Q$-manifolds) for now.

\begin{definition}
A \emph{BRST Theory} on $M$ is a sheaf of super cochain complexes $(\Phi, \dBRST)$ of fields on $M$ along with a (polynomial) Lagrangian density, which is a $\ZZ/2\ZZ$-graded map of sheaves $\LL \colon \sym^\bullet(\Phi) \to \dens_M$ satisfying $\LL \circ \dBRST = 0$ (where the differential is extended as a derivation).

A morphism of BRST theories on $M$ is a sheaf map $f \colon \Phi_1 \to \Phi_2$ that strictly commutes with the differentials, and where the triangle relating the two Lagrangian densities homotopy commutes.  Say that $f$ is an \emph{equivalence} if it is a quasi-isomorphism.  Note: Pavel suggested, in the more general $Q$-manifold context, that we should say $f$ is an equivalence if its homotopy fiber is equivalent to $V_{\mr{dR}}$ for some linear space $V$.
\end{definition}

\begin{remark}
One obtains the BV complex from the BRST complex by taking the twisted shifted cotangent bundle of $(\Phi, \dBRST)$, using the $!$-dual and twisting by the quadratic part of $\LL$.  The higher order terms in the polynomial $\LL$ define the $L_\infty$-structure but I haven't tried to write this down carefully.   Equivalences of BRST theories should induce $L_\infty$ equivalences of BV complexes.
\end{remark}

We can define twists in this language
\vspace{-10pt}
\begin{enumerate}
 \item With respect to a fermionic degree 0 endomorphism $Q$ of the BRST complex so that $Q^2 = 0$ and $\LL \circ Q = 0$.  We add $Q$ to the BRST differential: the resulting theory is now only a sheaf of $\ZZ/2\ZZ$-graded complexes.
 \item With respect to an action $(Q,\alpha)$ of $\CC^\times \ltimes \Pi \CC$ on the BRST complex so that $\LL \circ Q = 0$ and $\LL \circ \alpha = \LL$.  We form the usual total complex construction: the resulting theory is still $\ZZ$-graded.
\end{enumerate}
\vspace{-10pt}

Now, let's try to write down some of the descriptions of twisted theories that we've been discussing.
\begin{example}[10d $\mc N=1$ Super Yang-Mills]
I'm going to try to write this following the calculation in Baulieu \cite{Baulieu}.  We choose a complex structure on $\RR^{10}$ and decompose the (BRST) fields into irreducible components for the action of $\SU(5)$.  The fields one obtains are
\begin{align*}
A = A_{0, 1} + A_{1, 0} \\
\lambda = \chi + \psi_{1, 0} + B_{0, 2},
\end{align*}
where the subscripts indicate the form type of the component fields.  There's also a ghost $c$, which is a scalar in degree $-1$.  Finally we'll introduce an auxiliary scalar field $h$ (bosonic, in degree 0)   The BRST differential is given by $c \mapsto (\dd c, \ol{\dd} c)$.  Denote this complex by $(\Phi^{\mr{YM}}, \dBRST^{\mr{YM}})$.  The holomorphic twist is only $\ZZ/2\ZZ$-graded, and is given by the identity map from $\psi$ to $A_{1,0}$, the identity map from $h$ to $\chi$, along with the map $\ol \dd$ from $A_{0,1}$ to $B$ \footnote{More precisely, if we're doing perturbation theory around a background connection $A'$ we take the covariant derivative with respect to this $A'$.}.

We expect the holomorphically twisted theory to be equivalent to 5d holomorphic Chern-Simons theory.  The BRST fields here are given by $c, A_{0,1}$ and $B_{0,2}$ in even, odd and even degrees respectively (this is only a $\ZZ/2\ZZ$-graded theory).  Denote this complex by $(\Phi^{\mr{hCS}},\dBRST^{\mr{hCS}})$.  It's clear that the projection $\Phi^{\mr{YM}} \to \Phi^{\mr{hCS}}$ is a quasi-isomorphism with respect to the $Q$-twisted BRST differential: its fiber is the contractible complex $h \mapsto \chi, \psi \mapsto A_{1,0}$.  It remains for us to verify that this projection is compatible with the Lagrangian densities of the two theories.  In other words, if we take the Lagrangian density of 10d $\mc N=1$ Yang-Mills theory and subtract the Lagrangian density of holomorphic Chern-Simons theory applied to the fields $c, A_{0,1}$ and $B$ then the result is $Q$-exact.

I can do this calculation with the BV Lagrangian instead (Question: is this sufficient, and if so, why?).  This is what Baulieu does.  The BV Lagrangian density in 10d $\mc N=1$ Yang-Mills theory, where we ignore scaling factors for the individual terms, is given as follows.  Write $J$ for the map from $(1,1)$-forms to functions given by the chosen hermitian structure, and write $\Omega$ for the associated volume form (yes, I know I need to be more careful here).  Then
\begin{align*}
\LL_{\mr{YM}} &= J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
&+ \st{A_{1, 0}}\wedge \partial c + \st{A_{0, 1}}\wedge \overline{\partial} c + \st{c}\wedge [c, c] + \st{A_{0, 1}}\wedge [c, A_{0, 1}] + \st{A_{1, 0}}\wedge [c, A_{1, 0}] + \st{B}\wedge [c, B] + \st{\chi}\wedge [c, \chi] 
+ \st{\psi}\wedge [c, \psi].
\end{align*}
The holomorphic Chern-Simons action, on the other hand, can be written as
\begin{align*}
\LL_{\mr{hCS}} &= B \wedge \ol \dd_{A_{0,1}} B + \st B \wedge F_{0,2} + \st B \wedge [c,B] + \st A_{0,1} \wedge \ol \dd_{A_{0,1}}c + \st c \wedge [c,c]
\end{align*}
so taking the difference we're left with
\begin{align*}
\LL_{\mr{YM}} - \LL_{\mr{hCS}} &= J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega \\
&+ \st{A_{1, 0}}\wedge \partial c    + \st{A_{1, 0}}\wedge [c, A_{1, 0}]  + \st{\chi}\wedge [c, \chi] 
+ \st{\psi}\wedge [c, \psi] - \st B \wedge F_{0,2}.
\end{align*}
Now, $\st \chi, h, \st A_{1,0}$ and $\psi$ are all $Q$-exact (viewed as linear functionals on $\Phi$, so we can immediately simplify this to say that
\[ \LL_{\mr{YM}} - \LL_{\mr{hCS}} = J^2(F_{2, 0}\wedge F_{0,2})\Omega - \st B \wedge F_{0,2}  + Q\text{-exact}.\]
Likewise $F_{0,2}$ is $Q$-exact, which implies that this difference of Lagrangian densities is $Q$-exact, as required.
\end{example}

\begin{example}[4d $\mc N=1$ supergravity]
Warning: this is still very rough.  Caveat lector.

Let's now consider the example of twisted supergravity as in \cite{BaulieuBellonReys}.  We can model the BRST Fields using the first order formalism for supergravity as developed by D'Auria and Fr\'e.  In other words, the fields are modelled as gauge fields for the super Poincar\'e algebra.  Here we'll use the ordinary $\mc N=1$ super Poincar\'e algebra with no extension and no auxiliary fields, so $\Phi_{\mr{SUGRA}} = \Omega^0(\RR^4; \mf{iso}(4) \ltimes (S_+ \oplus S_-))[1] \to \Omega^1(\RR^4; \mf{iso}(4) \ltimes (S_+ \oplus S_-))$.  We obtain our twist by choosing a non-zero background for the ghost of the gravitino. So we choose a complex structure on $\RR^4$ and choose a square-zero supercharge in $S_+$ stabilized by the corresponding action of $\mr U(2)$ (unique up to scale).  We view this as a constant value for the ghost of the gravitino.  There is a compatible $\mr U(1)$-action so that $S_+$ has weight 1, $S_-$ has weight $-1$ and $\iso(4)$ has weight 0.

We can decompose the fields according to the action of this choice of $\mr U(2)$.  We won't fully decompose into irreducible components, but we can split $\Omega^1$ into $\Omega^{0,1} \oplus \Omega^{1,0}$ and then split ghosts and the holomorphic and anti-holomorphic components of the fields into 
\begin{align*}
e^{0,1} &= e^{0,1}_{1,0} + e^{0,1}_{0,1} \text{ and } \xi = \xi_{1,0} + \xi_{0,1} \\
\omega^{0,1} &= \omega^{0,1}_{\mr{hol}} + A^{0,1}_e + A^{0,1}_f + A^{0,1}_h \text{ and } \Omega = \Omega_{\mr{hol}} + \phi_e + \phi_f + \phi_h\\
\lambda^{0,1}_- &= \lambda^{0,1}_- \text{ and } \chi_- = \chi_- \\
\lambda^{0,1}_+ &= \lambda^{0,1}_0 + \lambda^{0,1}_{2,0} \text{ and } \chi_+ = \chi_0 + \chi_{2,0}
\end{align*}
where in each case we write the ordinary anti-holomorphic fields followed by their corresponding ghosts (we haven't written the holomorphic fields but they split identically: we denote them using a superscript $1,0$ in place of $0,1$).  Here for instance $\Omega_{\mr{hol}}$ is $\su(2)$-valued and the $\phi$ fields are scalars.

In this language the bosonic ghost $Q$ we twist by is a constant of type $\chi_0$.  The associated supersymmetries act on these component fields by the identity maps from $\chi_-$ to $\xi_{0,1}$, from $\phi_h$ to $\chi_0$ and from $\phi_f$ to $\chi_{2,0}$, and identically for the corresponding holomorphic and anti-holomorphic fields.

We'd like to show that this theory is equivalent to the cotangent theory to the theory of holomorphic symplectic structures.  The BRST complex here is given by $\Omega^0(\CC^2)[1] \to (\Omega^{0,1}(\CC^2) \oplus \Omega^{2,0}(\CC^2))$ with differential $(\ol \dd,0)$.  There's an obvious cochain map from supergravity into this theory given by the projection onto the BRST fields $(\phi_f, \pi (e^{1,0}_{1,0}), A^{0,1}_f)$ where by $\pi (e^{1,0}_{1,0})$ we mean the projection onto the antisymmetric part.  The natural question to ask here is, how close is this to providing an equivalence of BRST theories?  My first instinct is that it won't be -- maybe we need to use a modified model, perhaps with some auxiliary fields.

In order to investigate this we'll need to describe the BRST or BV action functionals, which will involve choosing a background vielbein.  My hope is that this choice will break the symmetry between the holomorphic and anti-holomorphic fields above.

\end{example}

\pagestyle{bib}
\printbibliography

\textsc{Institut des Hautes \'Etudes Scientifiques}\\
\textsc{35 Route de Chartres, Bures-sur-Yvette, 91440, France}\\
\texttt{celliott@ihes.fr}
\end{document}

### 2018-09-19 Twist_Notes_18_9.tex
small comments

@@
 
+\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
+
 \begin{document}
@@
 
+\brian{Little confused by this. 
+Here are some points to clarify:
+\begin{enumerate}
+\item Here $\d_{BRST}$ is the {\em linear} term in the BRST differential? 
+Maybe it'd be best to write this as $Q$. 
+\item For any examples that we want to discuss quantization we probably want to impose the usual geometric restrictions. 
+So $(\Phi, Q)$ is an elliptic complex (possibly just $\ZZ/2$ graded).
+\item You have in mind $\LL$ that depend more than just jets of fields?
+\item Usually, we mod out by total derivatives. 
+I would say the {\em theory} is really the element $\int \LL \in \mathcal{O}_{loc}(\Phi) = \dens_M \otimes_{D_M} \sym^\bullet(J \Phi)^\vee$.
+\end{enumerate}
+}
+
 \begin{remark}
@@
 \end{remark}
+
+\brian{
+Why is $\Phi \oplus \Phi^![-3]$ $L_\infty$? 
+I don't think just the condition $\LL \d_{BRST} = 0$ implies this...
+It seems like the thing you want to call a BRST theory is just a local $L_\infty$-algebra. 
+Am I missing something really basic?
+}
 
@@
 \begin{align*}
-A = A_{0, 1} + A_{1, 0} \\
-\lambda = \chi + \psi_{1, 0} + B_{0, 2},
+A = A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5, \fg) \oplus \Omega^{1,0}{\CC^5, \fg)
+\lambda = \chi + \psi_{1, 0} + B_{0, 2} \in \Omega^0(\CC^5,
 \end{align*}
+
 where the subscripts indicate the form type of the component fields.

### 2019-01-08 10-9-8d_twists_1_19.tex
added some 10,9,8d notes

\documentclass[10pt, oneside]{article}
\input math_headers.sty

\title{Notes on Twisted SYM}
\author{Chris Elliott}
\date{\today}

\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

\addbibresource{Twist.bib}

\begin{document}

\section{Some BRST Twisting Calculations}

\begin{example}[10d $\mc N=1$ Super Yang-Mills]
I'm going to write this following the calculation in Baulieu \cite{Baulieu}.  We choose a complex structure on $\RR^{10}$ and decompose the (BRST) fields into irreducible components for the action of $\SU(5)$.  The fields one obtains are
\begin{align*}
A &= A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
\lambda &= \chi + \psi_{1, 0} + B_{0, 2} \in \Omega^0(\CC^5; S_+),
\end{align*}

where the subscripts indicate the form type of the component fields.  There's also a ghost $c$, which is a $\gg$-valued scalar in degree $-1$.  Finally we'll introduce an auxiliary scalar field $h$ (bosonic, in degree 0).  The BRST differential is given by $c \mapsto (\dd c, \ol{\dd} c)$.  Denote this complex by $(\Phi^{\mr{YM}}, \dBRST^{\mr{YM}})$.  The dg Lie bracket is given by the action of $c$ on the other component fields.  The holomorphic twist is only $\ZZ/2\ZZ$-graded, and is given by the identity map from $\psi$ to $A_{1,0}$, the identity map from $h$ to $\chi$, along with the map $\ol \dd$ from $A_{0,1}$ to $B$ \footnote{More precisely, if we're doing perturbation theory around a background connection $A'$ we take the covariant derivative with respect to this $A'$.}.

We expect the holomorphically twisted theory to be equivalent to 5d holomorphic Chern-Simons theory.  The BRST fields here are given by $c, A_{0,1}$ and $B_{0,2}$ in even, odd and even degrees respectively (this is only a $\ZZ/2\ZZ$-graded theory).  Denote this complex by $(\Phi^{\mr{hCS}},\dBRST^{\mr{hCS}})$.  It's clear that the projection $\Phi^{\mr{YM}} \to \Phi^{\mr{hCS}}$ is a quasi-isomorphism with respect to the $Q$-twisted BRST differential: its fiber is the contractible complex $h \mapsto \chi, \psi \mapsto A_{1,0}$.  It remains for us to verify that this projection is compatible with the Lagrangian densities of the two theories.  In other words, if we take the Lagrangian density of 10d $\mc N=1$ Yang-Mills theory and subtract the Lagrangian density of holomorphic Chern-Simons theory applied to the fields $c, A_{0,1}$ and $B$ then the result is $Q$-exact.

So, let's describe the Lagrangian density of 10d $\mc N=1$ Yang-Mills theory in terms of our component fields.  We have
\begin{align*}
\LL_{\mr{YM}} &= (B \wedge \ol \dd_{A_{0,1}} B) + J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega \\
&= (B \wedge \ol \dd_{A_{0,1}} B) + \frac\delta{\delta Q}\bigg( 2J^2(F_{2, 0}\wedge B)\Omega + h\chi\Omega + \chi J(F_{1,1}) \Omega + J( \chi \wedge (F_{1,1})) \Omega\bigg).
\end{align*}
Therefore, after twisting the Lagrangian density is equivalent to just $B \wedge \ol \dd_{A_{0,1}} B$, which is the Lagrangian density in 5d holomorphic Chern-Simons theory, as required.
\end{example}

\begin{example}[9d $\mc N=1$ Super Yang-Mills]
Let's decompose our fields further into irreducible summands with respect to the action of $\SU(4)$.  We also restrict to 10d fields which are constant in the $x^{10}$-direction.  The only fields we'll consider are those which survived the 10d holomorphic twist.  These fields are
\begin{align*}
B^{10} &= B + A \wedge \d x^9 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_9) \\
A^{10}_{0,1} &= A' + \phi \d x^9 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_9)
\end{align*}
along with the ghost $c$.

All the square-zero supercharges lie in the same $\spin(9)$-orbit, so choose a square-zero $Q$ which is still square-zero in 10 dimensions.  The twist with respect to $Q$ is then just the dimensional reduction of the 10d twisted theory calculated above.  So, the twisted action functional is just calculated by decomposing the 10d twisted action
\[\LL^Q = B \wedge (\dd_{A'} A + [\phi, B]) \d x^9.\]
\end{example}

\begin{example}[8d $\mc N=1$ Super Yang-Mills]
There are two ways of dimensionally reducing a second time: we can either reduce in the direction $x^9$ to obtain another holomorphic twist, or we can reduce in a non-invariant direction to obtain a partially topological twist.

\begin{enumerate}
\item The latter -- the partially topological twist -- is acted upon by $\SU(3)$.  Again, let's decompose our twisted component fields with respect to the action of $\SU(3)$, and restrict to fields which are constant in the $x^{10}$ and $x^9$ directions.  The result is
\begin{align*}
B^{10} &= B + A_2 + A_3 + \phi_1 \in (\Omega^{0,2}(\CC^3; \gg) \oplus \Omega^{0,1}(\CC^3; \gg)^2\oplus \Omega^0(\CC^3; \gg)) \otimes \Omega^0(\RR_7 \times \RR_8)\\
A^{10}_{0,1} &= A_1 + \phi_2 + \phi_3 \in (\Omega^{0,1}(\CC^3; \gg) \oplus \Omega^0(\CC^3; \gg)^2) \otimes \Omega^0(\RR_7 \times \RR_8)
\end{align*}
again, along with the ghost $c$ (I've skipped writing the $\d x^7$ and $\d x^8$ factors in here).

As in dimension 9 we choose a square-zero $Q$ of rank $(1,1)$ which is still square-zero in 10 dimensions, and decompose the 10d twisted theory calculated above into these component fields.  The twisted action functional looks like
\[\LL^Q = B \wedge (\ol \dd \phi_1 + [A_1,\phi_1] - [A_3,\phi_2] - [A_2,\phi_3]) \d x^7 \wedge \d x^8.\]

\item The former -- the holomorphic twist -- is essentially equivalent to the theory discussed in dimension 9, but without the $\Omega^0(\RR_9)$ factor.  It is still acted upon by $\SU(4)$.  This theory should be a cotangent theory where the base -- in terms of BV fields -- is spanned by $c, A, \st B, \st A', \st \phi$, and the fiber is spanned by $\phi, A', B, \st A, \st c$.  We can see this by thinking about which fields are bosonic and which are fermionic.  This example should, for the first time, be promotable into a $\ZZ$-graded theory.  For this to produce the correct degrees, we need $A'$ to have R-symmetry weight $-1$ and $\phi$ to have R-symmetry weight $-2$.  I don't see right now where this is supposed to come from.
\end{enumerate}

\end{example}

\pagestyle{bib}
\printbibliography

\textsc{Institut des Hautes \'Etudes Scientifiques}\\
\textsc{35 Route de Chartres, Bures-sur-Yvette, 91440, France}\\
\texttt{celliott@ihes.fr}
\end{document}

### 2019-01-08 Twisted Supergravity/Pure_spinors.tex
tidying

\documentclass[10pt, oneside]{article}

\IfFileExists{../math_headers.sty}
  {\input ../math_headers.sty}
  {\IfFileExists{./math_headers.sty}
    {\input ./math_headers.sty}
    {\typeout{Header file not found}
    }
  }

\title{Notes on Pure Spinors}
\author{Chris Elliott}
\date{}

\DeclareMathOperator{\EOM}{EOM}
\newcommand{\EOMs}{\EOM_{\text{sing}}}
\DeclareMathOperator{\PT}{\mathbb{PT}}
\DeclareMathOperator{\PN}{\mathbb{PN}}

\begin{document}
\maketitle

\section{Pure Spinors}
Let $S$ be the Dirac spinor representation of $\so(1,n-1)$, and let $V$ be the complex $n$-dimensional vector representation.  I'll write $(v,w)$ for the inner product on $V$, $\langle Q, Q' \rangle$ for the invariant nondegenerate $\CC$ valued pairing on $S$, and $\Gamma(Q, Q')$ for the equivariant vector valued pairing on $S$.

For a spinor $Q$ we define its \emph{null space} $T_Q$ to be 
\[T_Q = \{v \in V \colon \rho(v)Q = 0\} \sub V.\]
Note that $T_Q$ is totally isotropic, since if $v, w$ are in $T_Q$ then
\[(v,w)Q = (\rho(v)\rho(w) - \rho(w)\rho(v))Q = 0.\]

\begin{definition}
A spinor $Q$ is called \emph{pure} if the space $T_Q$ is \emph{maximal}, i.e. of dimension $\lfloor \frac n2 \rfloor$.  It is called \emph{square zero} if $\Gamma(Q,Q) = 0$
\end{definition}

Now, I'd like to investigate the image 
\[S_Q = \mr{Im}(\Gamma(Q,-)) \sub V\]
of the map induced by pairing with a pure or square zero spinor $Q$.
\begin{prop}
Let $Q$ be a pure spinor.
\vspace{-6pt}
\begin{itemize}
 \item If $n=2m$ is even, then $S_Q = T_Q$.
 \item If $n=2m-1$ is odd, then $T_Q \sub S_Q$ is a codimension 1 subspace.
\end{itemize}
\vspace{-6pt}
\end{prop}

\begin{proof}
First observe that $S_Q^\perp = T_Q$.  Indeed, let $v$ be a vector in $S_Q^\perp$, i.e. $(v, w) = 0$ for all $w \in S_Q$.  That is
\begin{align*}
&\qquad (v, \Gamma(Q,Q')) = 0 \text{ for all } Q' \in S \\
&\Leftrightarrow \langle \rho(v)Q, Q' \rangle  = 0 \text{ for all } Q' \in S \\
&\Leftrightarrow \rho(v)Q = 0 
\end{align*}
So $v \in S_Q^\perp$ if and only if $v \in T^Q$.  Furthermore, taking a second orthogonal complement, this means that $S_Q = T_Q^\perp$, and therefore -- since $T_Q$ is totally isotropic -- $T_Q \sub S_Q$.  Looking at dimensions, since $Q$ is pure, $\dim T_Q = \lfloor \frac n2 \rfloor$, so $\dim  S_Q = \lceil \frac n2 \rceil$.  This completes the proof.
\end{proof}

Now, what's the relationship between pure spinors and square zero spinors?  To answer this question, we'll use an interesting decomposition.  Every spinor $Q$ induces a matrix element $Q \otimes \ol Q \in S \otimes S^* \iso \eend(S)$ via the diagonal embedding and the invariant pairing on $S$.  If $S$ is irreducible (i.e. for Dirac spinors in odd dimensions or Weyl spinors in even dimensions) we can identify endomorphisms with elements of the Clifford algebra, and thus decompose the spinor bilinear as
\[Q \otimes \ol Q = \sum_{p=0}^n F_p\]
where $F_p \in \wedge^p V$.  We can explicitly identify these elements $F_p$ as, in index notation, the Clifford algebra element $Q_i \gamma^{a_1 \cdots a_p}_{ij} Q_j$.  In this language we can characterise pure spinors \cite{Chevalley}.
\begin{theorem}[Chevalley]
A spinor $Q$ is pure if and only if it is Weyl (in even dimensions), and $F_p = 0$ for all $p < n/2$. 
\end{theorem}

In particular, $F_1 = 0$ whenever $n > 2$, so we have
\begin{corollary}
All pure spinors in dimensions $n > 2$ are square zero.
\end{corollary}

Now, let's investigate pure and square zero spinors in various dimensions.
\vspace{-6pt}
\begin{itemize}
 \item 
\end{itemize}

\bibliographystyle{alpha}
\bibliography{Supergravity}

\textsc{Department of Mathematics, Northwestern University}\\
\textsc{2033 Sheridan Road, Evanston, IL 60208, USA} \\
\texttt{celliott@math.northwestern.edu}
\end{document}

### 2019-01-08 Twisted Supergravity/Supergravity.tex
tidying

\documentclass[10pt, oneside]{article}

\IfFileExists{../math_headers.sty}
  {\input ../math_headers.sty}
  {\IfFileExists{./math_headers.sty}
    {\input ./math_headers.sty}
    {\typeout{Header file not found}
    }
  }

\title{Notes on Supergravity}
\author{Chris Elliott}
\date{}

\DeclareMathOperator{\EOM}{EOM}
\newcommand{\EOMs}{\EOM_{\text{sing}}}
\DeclareMathOperator{\PT}{\mathbb{PT}}
\DeclareMathOperator{\PN}{\mathbb{PN}}

\begin{document}
\maketitle
This is a set of notes on supergravity theories that I'm writing while trying to learn the basics.  The formulae come from the indicated references, but there's a good chance I've introduced errors in signs and constant factors.

\section{First Order Gravity and Supergravity Fields}
Let $X$ be a smooth manifold of dimension $n = p+q$.  The first order formalism for gravity gives a description of signature $(p,q)$ pseudo-Riemannian metrics on $X$.  Let $\mf{iso}(p,q)$ denote the Poincar\'e group of signature $(p,q)$, i.e. the semidirect product $\so(p,q) \ltimes \RR^n$.  The \emph{fields} of gravity in the first order formalism are, locally, $\mf{iso}(p,q)$-valued 1-forms on $X$.

Let's be more specific.  Let $F(T_X) \to X$ be the frame bundle of $X$, so pseudo-Riemannian metrics are the same as reductions of structure group of $F(T_X)$ to $O(p,q)$.  Equivalently, such a reduction is a linear bundle isomorphism 
\[e \colon T_X \to V\]
where $V$ is the vector bundle associated to a principal $O(p,q)$-bundle $P$.  Locally at least we can assume that $V$ is trivial, in which case $e$ is just a local section of the frame bundle.  Such an $e$ is called a \emph{vielbein}.  We can produce a pseudo-Riemannian metric from a vielbein by pulling back the canonical metric on $V$ along $e$.  We'll come back to this point of view from a more sophisticated point of view shortly.

Working in the first-order formalism means that we introduce an additional field into the action as well as the metric.  Essentially we think of the metric and its Levi-Civita connection as independent dynamical objects in the action.  Let $\omega$ be a connection on the principal bundle $P$, or yields a connection on $V$ and hence on $T_X$ by pulling back along the isomorphism $e$.  Locally the connection is an $\so(p,q)$-valued 1-form on $X$.  Taking $\omega$ and $e$ together we locally obtain an $\mf{iso}(p,q)$-valued 1-form.

There are various action functionals we might consider, but there's a standard choice called the \emph{Palatini action}, which we'll explain in the case where $V$ is trivial.  Write $\Omega$ for the curvature of $\omega$.  The Palatini Lagrangian density is
\[\mc L(e, \omega) = \langle \Omega \wedge e \wedge \cdots \wedge e\rangle\]
where there are $n-2$ copies of $e$, and where $\langle\,-\,\rangle \in C^\bullet(\mf{iso}(p,q))$ is the invariant polynomial which is totally alternating in the canonical basis.

\subsection{Gravity Fields Without Global Triviality}
Leaving the action aside for a moment, let's rephrase the description of the space of fields in a more explicit way, without the condition of $V$ being globally trivial.  To do so, we follow the formalism in \cite{SSS}.  If $\gg$ is any Lie algebra, $\gg$-valued 1-forms on $X$ are the same as dga morphisms
\[A \colon W^\bullet(\gg) \to \Omega^\bullet(X)\]
where $W^\bullet(\gg)$ is the Weil algebra of $\gg$.  Here the forms themselves are the images of the degree 0 generators, and their curvatures are the images of the degree 1 generators.  We use this to \emph{define} the space $\Omega^\bullet(X; L)$ for any (super) $L_\infty$ algebra $L$ as the complex $\hom_{\dga}(W^\bullet(L), \Omega^\bullet(X))$.  The space of flat $L$-valued 1-forms is the subspace of maps factoring through the Chevalley-Eilenberg complex $C^\bullet(L)$.

Fiorenza-Sati-Schreiber define the notion of a $L$-valued connection, not necessarily flat, in this language.  The definition is as follows.
\begin{definition} \label{connectiondef}
An $L$-bundle with connection $A$ on $X$ is a surjective submersion $\pi \colon Y \to X$, and a commutative diagram of dgas
\[\xymatrix{
C^\bullet(L) \ar[r] &\Omega^\bullet_{\mr{vert}}(Y) \\
W^\bullet(L) \ar[u] \ar[r]^A &\Omega^\bullet(Y) \ar[u] \\
\mr{inv}(L) \ar[u] \ar[r] & \Omega^\bullet(X) \ar[u]_{\pi^*}
}\]
where $\mr{inv}(L)$ denotes the space of \emph{invariant polynomials} for $L$ (the kernel of the map $W^\bullet(L) \to C^\bullet(L)$), and where $\Omega^\bullet_{\mr{vert}}(Y)$ denotes the cokernel of the map $\pi_* \colon \Omega^\bullet(X) \to \Omega^\bullet(Y)$.  Two such objects are equivalent if the maps $A_{\mr{vert}} \colon C^\bullet(L) \to \Omega^\bullet_{\mr{vert}}(Y)$ and  $A'_{\mr{vert}} \colon C^\bullet(L) \to \Omega^\bullet_{\mr{vert}}(Y')$ if their pullbacks to the common refinement $Y \times_X Y'$ are \emph{concordant}, i.e. if there exists a map
\[C^\bullet(L)  \to \Omega^\bullet_{\mr{vert}}(Y \times_X Y') \otimes \Omega^\bullet(I)\]
for $I = [0,1]$ the unit interval, restricting to the two maps via pulling back under the maps induced by the inclusion of the two end points of $I$.
\end{definition}

\begin{remark}
I might, following Schreiber, refer to the images of the shifted generators of $W^\bullet(L)$ as \emph{fields}, and the images of the unshifted generators as \emph{field strengths}.  The interpretation is that the images of the shifted generators are components of the connection, and the images of the unshifted generators are the components of its curvature.
\end{remark}

We should think of these as $L$-valued 1-forms on $Y$ flat along the fibres of $\pi \colon Y \to X$.  The columns of the above diagram are exact, so the bottom row is determined by the other two.

\subsection{Supergravity Fields}
Since the above formalism made sense for any (super) $L_\infty$ algebra, we can immediately describe the spaces of fields in supergravity theories.  As a starting point, we consider \emph{super Poincar\'e algebras}.  These depend on a choice of real spinorial representation $S$ of $\so(p,q)$, and non-degenerate $\Spin(p,q)$-invariant pairing $\Gamma \colon S \otimes S \to \RR^{p,q}$.  The super Poincar\'e algebra is then 
\[\mf{iso}(p,q) \ltimes S\]
with an additional collection of brackets coming from the pairing $\Gamma$.

In general, formulations of supergravity actually use a more general kind of algebras: one is required to adjoin higher degree elements, forming an $L_n$ algebra, not just a Lie algebra.  This is done by taking a super Poincar\'e algebra as above and forming iterated extensions by degree $n$ $L_\infty$ algebra cocycles.  Such extensions are studied in detail in \cite{FSS}, where they are referred to as the ``brane bouquet''.  We'll investigate the case of 11-dimensional $N=1$ supergravity in Lorentzian signature, `maximal' supergravity, where the relevant algebra was first described by D'Auria and Fr\'e in \cite{DF} (and in more detail in the book \cite{CDF}).

\begin{definition}
The 11-dimensional \emph{supergravity $L_\infty$ algebra} $\sugra(10,1)$ is defined as an iterated extension of the super Lie algebra $\mf{iso}(1,10) \ltimes S$, where $S$ is the 32-real-dimensional Majorana spin representation of $\so(10,1)$.  We first form the extension from the Chevalley-Eilenberg 4-cocycle
\[\mu_4 = \frac 12 \ol \psi \wedge \gamma^{ab} \psi \wedge e_a \wedge e_b \]
where $e_a$ are a basis for the translations in $\mf{iso}(10,1)$, and $\psi_\alpha$ are a basis for $S$.  Denote the new degree 3 basis element by $C$.  We then form a second extension via the Chevalley Eilenberg 7-cocycle
\[\mu_7 = \frac 12 \ol \psi \wedge \gamma^{abcde} \psi \wedge e_a \wedge e_b \wedge e_c \wedge e_d \wedge e_e + \frac {13}2 \ol \psi \wedge \gamma^{ab} \psi \wedge e_a \wedge e_b \wedge C.\]
\end{definition}
I've ommitted the calculation that these cochains are closed under the Chevalley-Eilenberg differential, which can be found in any of the above references.  We interpret the extensions as adjoining a \emph{supergravity C-field} and its electro-magnetic dual.  A \emph{field} in supergravity is then a $\sugra(10,1)$-bundle with connection in the sense of definition \ref{connectiondef}.  In particular, locally fields are maps from the Weil algebra of this $L_\infty$ algebra to the algebra of differential forms.

Why this specific $L_\infty$ algebra?  The answer has several parts.
\vspace{-8pt}
\begin{enumerate}
 \item Why the degree 3 generator?  This field component -- called the \emph{supergravity C field} -- was introduced in the original formulation of 11d supergravity by Julia, Cremmer and Scherk \cite{CJS}.  They observed that introducing a C field in addition to the graviton and gravitino fields ensures that the classical moduli space has equal bosonic and fermionic (virtual) dimension (specifically, dimension 128).  This is a necessary condition if we want any non-trivial supersymmetries.
 \item Why the degree 6 generator?  In particular, if it's going to be dual to the C field on-shell it should be possible to eliminate it from the equations of motion, so why include it in the first place?  We'd like the action to include a generalised Maxwell term for the 3-form field, i.e. a term of the form
 \[F_C \wedge \ast F_C\]
 where $F_C$ is the curvature of $C$ and $\ast F_C$ is its Hodge dual with respect to the metric (itself a dynamical field).  However we cannot expect this to arise naturally from the Chern-Simons approach to the equations of notion that we'll discuss in the next section since $\ast F_C$ is not polynomial in the components of the metric (one needs to take a square root).  We get around this by introducing an auxilliary dual 7-form field $C'$, including a term of form $F_C \wedge F_{C'}$ in the action along with additional terms ensuring the fields are dual on-shell.
 \item Why extend the algebra using these specific cocycles?  Consider cocycle for the 3-form field.  What we've done by imposing this particular cocycle extension is enforced the flatness condition
 \[dC- \frac 12 \ol \psi \wedge \gamma_{a_1 b_1} \psi \wedge e^{a_1} \wedge e^{a_2} = 0\]
 among the fields (at least in a vacuum state, where all field strengths -- unshifted generators in the Weil algebra -- vanish).  This is a necessary condition for supersymmetry.  Indeed, the condition of having all field strengths vanish should be supersymmetry invariant, which means the field strengths themselves should be supersymmetry invariant.  Now, the variation of $C$ under linear action of a supercharge $Q$ must be a 3-form depending linearly on $Q$ and the gravitino field $\psi$.  Essentially the only possibility is
 \[\delta C = \ol Q \wedge \gamma_{a_1 a_2} \psi \wedge e^{a_1} \wedge e^{a_2}\]
 up to some constant factor.  If we compute $\delta(F_C) = d(\delta C)$, we find that it is non-zero, so the physical curvature must differ from the na\"ive curvature $F_C$ by some polynomial in the other fields.  One can compute which such polynomials are cocycles using Fierz identities, and this is the only possibility.  The constant $1/2$ arises by computing the variation and comparing to $d(\delta C)$.

\end{enumerate}

\section{Supergravity Action}
Having produced a definition for the fields, how can we define an action functional extending the Palatini-Hilbert-Einstein action for ordinary gravity?  There is a natural general idea that makes sense for any $L_\infty$ algebra $L$: given a \emph{Chern-Simons element} -- an element $\mr{cs}$ of $W^n(L)$ where $n$ is the dimension of space-time -- we can evaluate a field $A$ at this element to get an $n$-form on $Y$.  Now, na\"ively, we might ask for this $n$-form to be \emph{horizontal}, i.e. to canonically descend to a top form on $X$.  However we really only need to ask for something weaker.  We don't need the Lagrangian density to be a canonical top form on $X$ to have well-defined equations of motion, only its first variation.  So it suffices for the differential $d\mr{cs}$ in the Weil algebra to be horizontal, i.e. to actually lie in the subalgebra $\mr{inv}^{n+1}(L) \sub W^{n+1}(L)$ of invariant polynomials.  In \cite{DF} this is called the \emph{cosmo-cocycle condition}, and its significance is explained by Schreiber in \cite{Schreiber}.  Concretely we're asking the Weil differential $d\mr{cs}$ to vanish after setting all the unshifted generators (the field strengths) to zero.

For a reasonable theory we'll just need to choose the element $\mr{cs}$ satisfying some sensible properties.  For supergravity, we might want the following (as in section 4 of \cite{DF}).
\vspace{-12pt}
\begin{enumerate}
 \item The term should be locally $\so(10,1)$-invariant.
 \item The term should be invariant under the action of $\CC^\times$ by R-symmetries, up to a global rescaling which doesn't affect the equations of motion.  This action is diagonal in the basis we've chosen.  The connection form $\omega$ has weight 0, the vielbein $e$ has weight 1, the gravitino $\psi$ has weight $1/2$, the C field has weight $3$ and its dual has weight $6$.  Their field strengths all have the same respective weights (equation (4.3) in \cite{DF}).
\end{enumerate}
These conditions determine an (almost \footnote{unique up to addition of a topological term of form $\int F_C \wedge F_{C'}$.}) unique Palatini like Chern-Simons element, and hence Lagrangian density, for the algebra $\sugra(10,1)$.  To write it out we write $\Omega$ for the field strength of the spin connection, $R$ for the field strength of the vielbein, $\rho$ for the field strength of the gravitino and $F_C$ for the field strength of the C field.  Also, displayed indices refer to a basis of the translation group inside $L$; their position as raised or lowered is not meaningful, and is only included to make the summation convention more explicit \cite{CDF}. 
\begin{align*}
\mr{cs} = &- \frac 19 \; \eps_{a_1 \cdots a_{11}} \Omega^{a_1 a_2} \wedge e^{a_3} \wedge \cdots \wedge e^{a_{11}} \\
&+ \frac 7{30}i \; (R^a \wedge e_a) \wedge (\ol \psi \wedge \gamma_{a_1 \cdots a_5} \psi) \wedge e^{a_1} \wedge e^{a_2} \wedge e^{a_3} \wedge e^{a_4} \wedge e^{a_5} \\
&- 84 i \; F_C \wedge (\ol \psi \wedge \gamma_{a_1 \cdots a_5} \psi) \wedge e^{a_1} \wedge e^{a_2} \wedge e_{a_3} \wedge e_{a_4} \wedge e_{a_5}\\
&- 840 \;C \wedge F_C \wedge (\ol \psi \wedge \gamma_{a_1 a_2} \psi) \wedge e^{a_1} \wedge e^{a_2} \\
&+ 2 \;(\ol \rho \wedge \gamma_{a_1 \cdots a_5} \psi) \wedge e^{a_1} \wedge e^{a_2} \wedge e_{a_3} \wedge e_{a_4} \wedge e_{a_5}\\
&+ \frac 14 \; \eps_{a_1 \cdots a_{11}} (\ol \psi \wedge \gamma_{a_1 a_2} \psi) \wedge (\ol \psi \wedge \gamma_{a_3 a_4} \psi) \wedge e^{a_5} \wedge e^{a_{11}} \\
&+ 210 \; C \wedge (\ol \psi \wedge \gamma^2 \psi) \wedge (\ol \psi \wedge \gamma^2 \psi) \wedge e_a \wedge e_b \wedge e_c \wedge e_d \\
&+ 840 \; C \wedge F_C \wedge F_C 
\end{align*}

This action has several features it's worth remarking upon.  First note that the first line is the Palatini Lagrangian density for ordinary gravity.  Secondly, while we have a Chern-Simons term for the C field, we haven't found the Maxwell type term we wanted.  Indeed, the dual field $C'$ and it's field strength $F_{C'}$ don't appear in the action at all!  D'Auria and Fr\'e show that one can recover something like this term using a trick.  Replace $W^\bullet(\sugra(10,1))$ by $W^\bullet(\sugra(10,1)) \otimes \wedge^4 \RR^{11}$, and denote the generators of the new factor by $G^{a_1 a_2 a_3 a_4}$ (in degree zero). Add to the Chern-Simons form above the term
\[\mr{cs}' = 2\; G^{a_1 a_2 a_3 a_4} F_C \wedge e^{a_5} \wedge \cdots \wedge e^{a^{11}} - \frac 1{330} \; G_{a_1 a_2 a_3 a_4}G^{a_1 a_2 a_3 a_4} \eps_{b_1 \cdots b_{11}} e^{b_1} \wedge \cdots \wedge e^{b_{11}}.\]
Now, when one computes the equations of motion for this modified Lagrangian, one finds no new degrees of freedom.  Indeed, on-shell the $G$ components recover the space-time components of the curvature $F_C$ of the $C$-field.  However, one now has non-trivial dynamics for the C field as required.

\subsection{Questions}
\vspace{-8pt}
\begin{enumerate}
 \item We introduced the 6-form field to give an explicit Maxwell term to the C field, but we failed.  In order to satisfy the cosmo cocycle conditions we had to normalise all the terms involving $C'$ and its derivative in such a way that they collected in a topological term.  In which case, why bother forming the second $L_\infty$ algebra extension at all?  We could've just stuck with the original extension.  All we gained was the topological term.
 \item This ``0-form trick'' was necessary to give the C field any suitable dynamics, but it's a bit clunky.  Can we incorporate it more neatly into the general story of Chern-Simons for $L_\infty$ algebras.  For instance, starting with the $L_\infty$ algebra $\sugra(10,1) \oplus \wedge^4 \RR^{11}$?
 \item There aren't any obvious kinetic terms in the action.  Is that a problem?  If one fixes the fields coming from the metric then one sees a Dirac term and a mass term for the gravitino (the fifth and second lines in $\mr{cs}$), and a Maxwell type term for the C field coming from $\mr{cs}'$.  However, how might one compute a propagator for the graviton?
 \item Is there a natural way to recover the supersymmetry action from this picture?  One can compute them by hand without too much trouble: one finds, for a supercharge $Q$ and the fields that actually appear in the action \cite{FreGrassi}, 
 \begin{align*}
  \delta e^a &= i \ol Q \wedge \gamma^a \psi \\
  \delta \psi &= \nabla(\omega) Q + \frac i3 G_{a_1 a_2 a_3 a_4} (\gamma^{a_1 a_2 a_3} Q \wedge V^{a_4} - \frac 18 \gamma^{a_1 a_2 a_3 a_4} Q) \\
  \delta C &= -\ol Q \wedge \gamma_{a_1 a_2} \psi \wedge e^{a_1} \wedge e^{a_2}
 \end{align*}
 and all field strengths are supersymmetry invariant.  Here $\nabla(\omega)$ denotes the covariant derivative associated to the connection $\omega$.
\end{enumerate}

\section{Pure Spinors, and Spinors in 11 Dimensions}
To investigate twists of this theory it will be necessary to understand the supersymmetry algebra, in particular the vector valued pairing between spinors in signature $(10,1)$.  This pairing is encoded in the Clifford algebra structure, i.e. in the Gamma matrices we've been using above.  We'd like to compute the subspace of \emph{square zero spinors} -- those satisfying $\Gamma(Q,Q) = 0$ -- and the possible cohomologies of the supersymmetry algebra with respect to the diffferential $[Q,-]$ for such a spinor.  Some relevant calculations are included in Cederwall's work on 11d supergravity \cite{Cederwall1} \cite{Cederwall2}.

Before specialising to 11 dimensions, let's investigate those spinors satisfying $\Gamma(Q,Q) = 0$ in arbitrary dimension.  These subspaces of the spaces of spinors are closely related to the \emph{pure spinors} introduced by Cartan and Chevalley.  I referred to chapter III of the book \cite{Chevalley} as a comprehensive reference on pure spinors, and the paper \cite{BudinichTrautman} for a more concise treatment.   Let $S$ be the complex (Dirac) spin representation of $\so(1,n-1)$ (since we're only discussing complex representations the signature won't actually play a role), and let $V$ be the complex $n$-dimensional vector representation.
\begin{definition}
For a spinor $Q \in S$, its \emph{nullspace} $T_Q$ is the space of vectors $v \in V$ that Clifford annihilate $Q$, i.e. $\{v \colon \rho(v)Q = 0\}$.  The spinor is called \emph{pure} if $\dim T_Q = \lfloor \frac n2 \rfloor$.
\end{definition}
Notice that this is the largest possible dimension for $T_Q$ since these nullspaces are always \emph{totally isotropic}.  Indeed, if $v$ and $w$ are in $T_Q$ then
\[(v,w)Q = (\rho(v)\rho(w) - \rho(w)\rho(v))Q = 0.\]
We should also notice that all such maximally isotropic subspaces $T$ arise as the nullspace of some spinor $Q$.  The action of the Clifford algebra $\mr{Cl}(V)$ on $S$ is faithful, so choosing a basis $\{v_1, \ldots, v_{\lfloor \frac n2 \rfloor}\}$ for $T$, we can find a spinor $Q$ so that
\[\rho(v_1) \cdots \rho(v_{\lfloor \frac n2 \rfloor}) Q \ne 0,\]
and then $T \sub T_Q$, and they must be equal by maximality.  In fact, such a $Q$ is uniquely determined up to rescaling.

Now, lets investigate the image of the $\Gamma$ pairing with a pure spinor, i.e. the subspace
\[S_Q = \mr{Im}(\Gamma(Q,-)) \sub V.\]
\begin{prop} \label{purespinorimage}
Let $Q$ be a pure spinor.
\vspace{-6pt}
\begin{itemize}
 \item If $n=2m$ is even, then $S_Q = T_Q$.
 \item If $n=2m-1$ is odd, then $T_Q \sub S_Q$ is a codimension 1 subspace.
\end{itemize}
\vspace{-6pt}
\end{prop}

\begin{proof}
First observe that $S_Q^\perp = T_Q$.  Indeed, let $v$ be a vector in $S_Q^\perp$, i.e. $(v, w) = 0$ for all $w \in S_Q$.  That is
\begin{align*}
&\qquad (v, \Gamma(Q,Q')) = 0 \text{ for all } Q' \in S \\
&\Leftrightarrow \langle \rho(v)Q, Q' \rangle  = 0 \text{ for all } Q' \in S \\
&\Leftrightarrow \rho(v)Q = 0 
\end{align*}
So $v \in S_Q^\perp$ if and only if $v \in T_Q$.  Furthermore, taking a second orthogonal complement, this means that $S_Q = T_Q^\perp$, and therefore -- since $T_Q$ is totally isotropic -- $T_Q \sub S_Q$.  Looking at dimensions, since $Q$ is pure, $\dim T_Q = \lfloor \frac n2 \rfloor$, so $\dim  S_Q = \lceil \frac n2 \rceil$.  This completes the proof.
\end{proof}

Now, what's the relationship between pure spinors and those satisfying $\Gamma(Q,Q)=0$?  To answer this question, we'll use an interesting decomposition.  Every spinor $Q$ induces a matrix element $Q \otimes \ol Q \in S \otimes S^* \iso \eend(S)$ via the diagonal embedding and the invariant pairing on $S$.  If $S$ is irreducible (i.e. for Dirac spinors in odd dimensions or Weyl spinors in even dimensions) we can identify endomorphisms with elements of the Clifford algebra, and thus decompose the spinor bilinear as
\[Q \otimes \ol Q = \sum_{p=0}^n F_p\]
where $F_p \in \wedge^p V$.  We can explicitly identify these elements $F_p$ as, in index notation, the Clifford algebra element $Q_i \gamma^{a_1 \cdots a_p}_{ij} Q_j$.  There's a nice characterisation of pure spinors in this language.
\begin{theorem}[Chevalley] \label{ChevalleyCriterion}
A non-zero spinor $Q$ is pure if and only if it is Weyl (in even dimensions), and $F_p = 0$ for all $p < \lfloor n/2 \rfloor$. 
\end{theorem}

In particular, $F_1 = 0$ whenever $n > 3$, so we have
\begin{corollary}
All pure spinors in dimensions $n > 3$ satisfy $\Gamma(Q,Q) = 0$.
\end{corollary}

Another useful fact is the following (explained for instance in \cite{BudinichTrautman})
\begin{lemma} \label{WeylCriterion}
If $Q$ is a Weyl spinor in dimension $n=2m$, the tensor $F_p$ is zero unless $p \equiv m \mod 4$.
\end{lemma}

\begin{proof}
This is a combination of two symmetries satisfied by $F_p$.  Firstly, $F_p = 0$ whenever $m-p$ is odd, since the spinor pairing $\langle -,- \rangle \colon S \otimes S \to \CC$ pairs $S_\pm$ with itself when $m$ is even, and pairs $S_+$ with $S_-$ with $m$ is odd, and Clifford multiplication always interchanges $S_+$ and $S_-$.

Secondly, we have a general symmetry in spinor bilinears, of form
\[\langle Q_1, \rho(v_1) \cdots \rho(v_p) Q_2 \rangle = (-1)^{\frac{m(m-1)}2 + \frac{p(p-1)}2}\langle Q_2, \rho(v_1) \cdots \rho(v_p) Q_1 \rangle.\]
This is a combination of the symmetry property $\langle Q_1, Q_2 \rangle = (-1)^{\frac{m(m-1)}2} \langle Q_2, Q_1 \rangle$ of the spinor pairing, and the fact that we have to do $\frac {p(p-1)}2$ swaps to restore the $p$ Clifford multiplications to the correct order upon moving them to the other side of the bracket, picking up a factor of $-1$ for each.  Thus, since if $m-p \equiv 2 \mod 4$ then $\frac{m(m-1)}2 + \frac{p(p-1)}2$ is odd, in this case the tensor $F_p$ also vanishes.
\end{proof}

Now, let's use these facts to investigate pure spinors in various dimensions.
\vspace{-6pt}
\begin{itemize}
 \item Let's deal with the special case $n=2$ first.  There is an isomorphism $\so(2;\CC) \iso \CC$, under which the Weyl spin representations are 1-dimensional of weights $\pm 1$, and the vector representation is $V \iso \CC_2 \oplus \CC_{-2}$.  A positive Weyl spinor $Q$ has $T_Q = \CC_{-2}$, and a negative Weyl spinor has $T_Q = \CC_{2}$, so every Weyl spinor is pure.  However, no spinors satisfy $\Gamma(Q,Q) = 0$, since the pairings $S_\pm \otimes S_\pm \to V$ are injective.

 \item Now, even dimensions 4 and 6 are very simple.  Again, every Weyl spinor is pure.  Indeed, by the corollary, we only need to show that $F_p = 0$ when $p = 0$ or 1 in dimension 4, or 0,1 or 2 in dimension 6, and lemma \ref{WeylCriterion} tells us that all of these vanish.  In particular, all Weyl spinors square to zero under the Gamma pairing.  Of course, there are other spinors we might use for twisting that square to zero but are not Weyl spinors, and therefore not pure.

 \item In dimension 8, we have a single constraint for a Weyl spinor to be pure, that $F_0 = 0$, i.e. that the spinor satisfies $\langle Q,Q \rangle = 0$.  All Weyl spinors satisfy $\Gamma(Q,Q) = 0$ however, so in this dimension squaring to zero is strictly weaker than being pure.  This is interesting in particular because of the following fact (\cite{Charlton} 3.3.1).
 \begin{prop}
 If $Q$ is an impure spinor in eight dimensions then the image space $S_Q$ is all of $V$.
 \end{prop}

 \begin{proof}
 We proved in \ref{purespinorimage} that, for any spinor, $S_Q = T_Q^\perp$, so we must show that $T_Q = \{0\}$ for an impure spinor.  To see this, we decompose the space $S_+$ (or $S_-$) into two subspaces consisting only of pure spinors, specifically
 \begin{align*}
 &\mr{span} \{z, \rho(x_1)\rho(x_2)z, \rho(x_1)\rho(x_3)z, \rho(x_1)\rho(x_4)z\} \\
 &\mr{span} \{\rho(x_2)\rho(x_3)z, \rho(x_2)\rho(x_4)z, \rho(x_3)\rho(x_4)z, \rho(x_1)\rho(x_2)\rho(x_3)\rho(x_4)z\}
 \end{align*}
 where $z$ is a volume form for any maximally totally isotropic subspace, and $x_1, x_2,x_3,x_4$ is a basis for a complementary maximally totally isotropic space.  Write $Q = Q_1 + Q_2$ where the $Q_i$ are pure, one in each subspace.  By \cite{Charlton} 2.3.35 the intersection $T_{Q_1} \cap T_{Q_2}$ must be $\{0\}$ since $Q$ is impure.  However, by \cite{Charlton} 3.2.18, $T_{Q_1} \cap T_{Q_2} = T_Q$, as required.
 \end{proof}
 This means $N=1$ supersymmetric field theories in 8 dimensions admit topological twists.

 \item In dimension 10, the constraint for a Weyl spinor to be pure is that $F_1 = 0$, i.e. a Weyl spinor $Q$ in dimension 10 is pure if and only if $\Gamma(Q,Q) = 0$.

 \item Let's move on to odd dimensions.  There's a basic fact that we can use to help ourselves understand these.  Recall that there's a natural isomorphism of $\so(2m-1)$-representations between the spin representation in dimension $2m-1$ and either Weyl spinor representation in dimension $2m$, after choosing any codimension one subspace in $\CC^{2m}$ (\cite{Chevalley} III.8).
 \begin{prop}
 A non-zero $Q$ in $2m-1$ dimensions is pure if and only if it is pure as a Weyl spinor in $2m$ dimensions.
 \end{prop}
 In particular, in dimensions 1, 3 and 5 every spinor is pure, so by Chevalley's criterion \ref{ChevalleyCriterion} all spinors in dimension 5 also square to zero.

 \item In dimension 7, we have a single pure spinor constraint: $\langle Q, Q \rangle_8 = 0$ where $\langle-,-\rangle_8$ denotes the spinor pairing in 8 dimensions.  Thus in 7 dimensions the pure spinors and those satisfying $\Gamma(Q,Q) = 0$ coincide, and are both given by a quadric hypersurface in $S$.  Similarly, in dimension 9 a spinor $Q$ is pure if and only if $\Gamma_{10}(Q,Q) = 0$, where $\Gamma_{10}$ is the vector valued pairing applied to $Q$ as a 10-dimensional Weyl spinor.

 \item Dimension 11 is the case we're most interested in for the purposes of this note, so let's recall for completeness some basic facts about spinors in signature $(10,1)$.  There are $\RR$-algebra isomorphisms
\[\mr{Cl}^+(10,1;\RR) \iso \mr{Cl}(1,9; \RR) \iso \mat_{32}(\RR),\]
and the Majorana spinor representation $S$ is the 32-dimensional representation of this algebra, inheriting an action of $\spin(10,1) \sub \mr{Cl}^+(10,1;\RR)$, and hence of $\so(10,1)$.  As a module for $\so(9,1)$, $S_\RR$ splits into $S_{\RR+} \oplus S_{\RR-}$ where $S_{\RR\pm}$ are the two Majorana-Weyl spinors representations, dual to one another.  Write $S, S_+$ and $S_-$ for the complexifications of these representations.

For a spinor $Q$ to be pure, it has to satisfy the constraint $F_2 = 0$.  The space of pure spinors agrees with the space of pure positive helicity (say) Weyl spinors in dimension 12. In particular it satisfies $\Gamma(Q,Q) = 0$, but there are additional constraints.  Let's try to understand the full space of spinors in 11 dimensions satisfying $\Gamma(Q,Q) = 0$.  To do so, we follow the description in \cite{Cederwall1} and decompose $Q$ into $Q_+ + Q_-$ as an $\so(9,1)$ spinor.  The $\so(9,1)$ gamma pairing acts diagonally on the two factors: one has
\[\Gamma_\pm \colon S_\pm \otimes S_\pm \to \CC^{10}.\]
With respect to this pairing, the condition $\Gamma(Q,Q)=0$ says that
\begin{align*}
&\Gamma_+(Q_+, Q_+) - \Gamma_-(Q_-, Q_-) = 0 \\
\text{and } &\langle Q_+, Q_-\rangle = 0.
\end{align*}
The last condition comes from the vanishing of the last component in $V$, perpendicular to our chosen 10-dimensional subspace.

We can produce spinors satisfying these equations by first fixing $Q_+$, then setting $Q_- = \rho(v)Q_+$, where $v$ is a unit vector orthogonal to the vector $\Gamma_+(Q_+, Q_+)$.  That $v$ must be a unit vector is required by the first condition above, and the orthogonality is required by the second condition.  Note also that any vector $v \in T_{Q_+}$ is orthogonal to $\Gamma_+(Q_+,Q_+)$ because $T_{Q_+} = S_{Q_+}^\perp \sub \langle \Gamma_+(Q_+,Q_+)\rangle^\perp$, so the space of square zero spinors we've defined admits a proper map to the space $S_+$ whose fibre over $Q_+$ is a $k$-sphere, where $k = 8 - \dim(T_{Q_+})$.

\begin{question}
Why does this produce all spinors $Q$ such that $\Gamma(Q,Q) = 0$, as Cederwall claims?
\end{question}

\begin{remark}
In \cite{Cederwall1}, Cederwall \emph{defines} a pure spinor in 11 dimensions to be a spinor satisfying $\Gamma(Q,Q)=0$.  What other sources call a pure spinor (a pure Weyl spinor in dimension 12), he calls a \emph{very pure spinor}.  These are characterised by the 12d condition $F_2 = 0$.
\end{remark}

\end{itemize}

\section{Twisting $N=1$, $d=4$ Supergravity}
Before trying to compute twists of the 11-dimensional theory, let's investigate an easier example: $N=1$ supergravity on $\RR^4$.  The fields in this theory really are just gauge fields for the super Poincar\'e algebra in four dimensions.  We'll write them as
\begin{align*}
\omega &\in \Omega^1(\RR^4; \so(4)) \\
e &\in \Omega^1(\RR^4; \RR^4) \\
\psi &\in \Omega^1(\RR^4; \Pi S)
\end{align*}
where $S \iso S_+ \oplus S_-$ is the four-dimensional Dirac spin representation of $\so(4)$.  The Lagrangian density is a natural extension of the Einstein-Hilbert action.
\[\mc L(\omega, e, \psi) = \eps_{a_1 a_2 a_3 a_4} \Omega^{a_1 a_2} \wedge e^{a_3} \wedge e^{a_4} + 4 \ol \psi \wedge \gamma_a \,D_\omega \psi \wedge e^a.\]
The gauge group $\Omega^0(\RR^4; \mf{iso}(4) \oplus \Pi S) \iso \Omega^0(\RR^4; \so(4)) \oplus \Omega^0(\RR^4; \RR^4) \oplus \Omega^0(\RR^4; \Pi S)$ acts on the fields so as to preserve the action.  We treat the three factors separately.  Elements $f \in \Omega^0(\RR^4; \so(4))$ in the first factor act by simple gauge transformations: $\omega \mapsto \omega + D_\omega f$, $e \mapsto e + [e,f]$ and $\psi \mapsto [\psi,f]$.  Elements $\phi \in \Omega^0(\RR^4; \RR^4)$ in the second factor act by infinitesmial diffeomorphisms.  Specifically $\omega \mapsto \omega + \iota_\phi F_\omega$ and $e \mapsto e + d_\omega \phi  + \iota_\phi (d_\omega e)$, where $\iota_\phi$ is contraction with $\phi$ thought of as a vector field on $\RR^4$.  Elements $\chi \in \Omega^0(\RR^4; S)$ in the final, fermionic factor act by \emph{supersymmetries}: $e \mapsto e + \Gamma(\chi, \psi)$ and $\psi \mapsto \psi + D_\omega \chi$.

We must compute the (complexified) BV complex near a classical solution to the equations of motion $(\omega_0, e_0, \psi_0)$.  The BV complex is fairly easy to write down.  It looks like
\[\xymatrix{
   \Omega^0(X; \CC^4) \ar[r]^d & \Omega^1(X; \CC^4) \ar[r]^{e_0 \wedge d} &\Omega^3(X; \wedge^2 \CC^4) \ar[r]^d &\Omega^4(X; \wedge^2 \CC^4) \\
   \Omega^0(X; \so(4;\CC)) \ar[r]^d \ar[ur]^{e_0} & \Omega^1(X; \so(4;\CC)) \ar[r]^{e_0 \wedge d} \ar[ur]^{[e_0 \wedge e_0]} &\Omega^3(X; \wedge^3 \CC^4) \ar[r]^d \ar[ur]^{e_0} &\Omega^4(X; \wedge^3 \CC^4) \\
   \Pi\Omega^0(X; S) \ar[r]^d & \Pi\Omega^1(X; S) \ar[r]^{\rho(e_0) d} &\Pi\Omega^3(X; S) \ar[r]^d &\Pi\Omega^4(X; S) \\
}\]
so the first two rows are bosonic and the last is fermionic.  The pairing pairs the first two rows with one another, and pairs $S_\pm$ with itself in the last row.  The notation $\rho(e_0)$ denotes Clifford multiplication by the vector component of $e_0$ and wedge with the form component.  The operator $e_0 \colon \Omega^0(X;\so(4;\CC)) \to \Omega^1(X;\CC^4)$ is given by acting on $e_0$, and its dual operator $e_0 \colon \Omega^3(X;\wedge^3\CC^4) \to \Omega^4(X;\wedge^2\CC^4)$ is given by identifying $\wedge^3\CC^4$ with $\CC^4$ using the metric, and wedging with $e_0$.  Finally, the operator $[e_0 \wedge e_0] \colon \Omega^1(X;\so(2;\CC)) \to \Omega^3(X; \so(4;\CC))$ is given by composing $e_0 \wedge e_0 \colon \Omega^1(X;\wedge^2\CC^4) \to \Omega^3(X; \wedge^2(\wedge^2 \CC^4))$ with the Lie bracket on $\so(4;\CC)$, thought of as a map $\wedge^2(\wedge^2 \CC^4) \to \wedge^2\CC^4$.  This complex admits an $L_\infty$ structure with the higher brackets determined by the higher order terms in the action functional and the gauge symmetry.

Let $Q \in \Omega^0(X; S_+)$ be a fixed global section of the Weyl spinor bundle.  The action of this supersymmetry, combined with the $\CC^\times$ action in which $S_\pm$ has weight $\pm 1$, yields \emph{twisting data} for the supergravity theory.  The cokernel of the map $\Gamma(Q,-)$ corresponds to a choice of complex structure on $X$.  We choose the reference vierbein $e_0$ to live in the holomorphic tangent bundle inside the full complexified tangent bundle, $\Omega^1(X; \CC^2) \sub \Omega^1(X;\CC^4)$.  The twisted BV complex is
\[\xymatrix{
   \Omega^0(X; S_-) \ar[r] \ar[rd] & \Omega^1(X; S_-) \ar[r]\ \ar[rd] &\Omega^3(X; S_-) \ar[r] \ar[rdd] &\Omega^4(X; S_-) \ar[rdd] \\
   &\Omega^0(X; \CC^4) \ar[r] & \Omega^1(X; \CC^4) \ar[r]\ &\Omega^3(X; \wedge^2 \CC^4) \ar[r] \ar[rdd] &\Omega^4(X; \wedge^2 \CC^4) \ar[rdd] \\
   &\Omega^0(X; \so(4;\CC)) \ar[r] \ar[rd] \ar[ur] & \Omega^1(X; \so(4;\CC)) \ar[r] \ar[ru] \ar[rd] &\Omega^3(X; \wedge^3 \CC^4) \ar[r] \ar[ur] &\Omega^4(X; \wedge^3 \CC^4) \\ 
   &&\Omega^0(X; S_+) \ar[r] & \Omega^1(X; S_+) \ar[r]\ &\Omega^3(X; S_+) \ar[r] &\Omega^4(X; S_+) \\
}\]
where now all rows are bosonic.  The new, downward diagonal arrows here are given by the action of the supersymmetry $Q$.  This complex is quasi-isomorphic to the complex 
\[\xymatrix{
 \Omega^0(X; \CC^2) \ar[r] & \Omega^1(X; \CC^2) \ar[r] &\Omega^3(X; \gl(2;\CC)) \ar[r] &\Omega^4(X; \gl(2;\CC)) \\
   \Omega^0(X; \gl(2;\CC)) \ar[r] \ar[ur] & \Omega^1(X; \gl(2;\CC)) \ar[r] \ar[ur] &\Omega^3(X; \CC^2) \ar[r] \ar[ur] &\Omega^4(X; \CC^2) \\
}\]
where the map $\Omega^1(X; \gl(2;\CC)) \to \Omega^3(X; \CC^2)$ is given by $d$ followed by applying the two by two matrix component to the vector component of $e_0$ and wedging the form components, and the map $\Omega^1(X; \CC^2) \to \Omega^3(X; \gl(2;\CC))$ is given by $d$ followed by wedging with $e_0$, and noting that this lands in $\sl(2;\CC)_+ \sub \so(4;\CC) \iso \wedge^2 \CC^4$ \chris{or gl}.

Going one step further, this is quasi-isomorphic to the complex
\[\xymatrix{
\Omega^{0,0}(X; \CC^2) \ar[r]^{\ol \dd} &\Omega^{0,1}(X; \CC^2) \ar[r]^{e_0 \wedge \ol \dd} &\Omega^{1,2}(X; \gl(2;\CC)) \ar[r]^(.55){\pi \circ \ol \dd} &\Omega^{2,2}(X;\CC^2)\\
\Omega^{0,0}(X;\CC^2) \ar[r]^(.45){\iota \circ \ol \dd}&\Omega^{1,0}(X; \gl(2;\CC)) \ar[r]^{e_0 \wedge \ol \dd} &\Omega^{2,1}(X; \CC^2) \ar[r]^{\ol \dd} &\Omega^{2,2}(X;\CC^2)
}\]
where the map $\Omega^{0,0}(X;\CC^2) \to \Omega^{1,0}(X; \gl(2;\CC))$ uses the inclusion of the annihilator of $e_0$ in $\CC^2$, and its dual likewise uses the projection onto the annihilator.

Now, let's interpret the fields and the action functional we obtain.  The vierbein $e$ becomes a $(0,1)$ form valued in the holomorphic tangent bundle of $X$, and the spin connection $\omega$ becomes a connection on the holomorphic tangent bundle, compatible with the complex structure.  The holomorphic vierbein yields a Hermitian metric $h$ on the holomorphic tangent bundle by an analogous procedure to the construction of a Riemannian metric from a vierbein on any manifold; we choose a reference anti-Hermitian metric $h_0$ on the anti-holomorphic tangent bundle $T^{0,1}X$, and define
\[h(u, v) = h_0(e(u), e(v)).\]
We naturally expect the equations of motion to impose that $h$ is a Hermite-Einstein metric, and $\omega$ is the associated Chern connection to $h$ (so an auxiliary field).  Let's check that this is indeed the case.  The Lagrangian density in the twisted theory is still of form 
\[\mc L(\omega, e) = \langle \Omega \wedge e \wedge e \rangle\]
where $\langle \; \rangle$ denotes the canonical trivialisation of $\wedge^4 \CC^4$ on the complexified tangent bundle, and where $\Omega$ denotes the holomorphic curvature of $\omega$, lying in $\Omega^{2,0}(X; \gl(2;\CC))$.

Solving the equations of motion, as one would do in ordinary first order gravity, we obtain an Einstein condition
\[R_{ab} = k h_{ab}\]
where $R_{ab}$ is the Ricci tensor, which -- in the holomorphic setting -- a priori is a section of $(T^{1,0}X)^{\otimes 2}$.  We also obtain a torsion-freeness condition for the connection, of form $T_a = 0$, where in the holomorphic setting the torsion $T_a$ is a $\CC^2$-valued $(2,0)$-form.  This implies not only that the connection $\omega$ is the Chern connection associated to $h$, but \emph{also} that the Hermitian metric $h$ in fact defines a K\"ahler structure on $X$ (this is a standard fact in complex geometry, but for my own sake, a textbook reference is \cite{Huybrechts} proposition 4.A.7).  Thus we conclude that the moduli space of solutions to the equations of motion is the moduli space of \emph{K\"ahler-Einstein Structures} on the holomorphic tangent bundle of $X$, with complex structure given by the choice of twist $Q$.  In particular, by the Kobayashi-Hitchin correspondence, it is non-empty if and only if the holomorphic tangent bundle is semistable.

\begin{remark}
The gauge group here has split into two parts, but I suspect they'll glue together to a copy of $\Omega^0(X;\gl(2;\CC))$, acting in the expected way on the fields.  I haven't checked that the brackets work correctly yet.
\end{remark}

\section{Twisting Maximal Supergravity}
Let's now try to mimic this calculation for supergravity in 11 dimensions.  We'll start by describing the linearised BV complex near a fixed elfbein field $e_0$, just as we did above.  The quadratic term of the Lagrangian density after making the perturbation $e \mapsto e + e_0$ has form (ignoring constants)
\[\langle \omega \wedge \omega \wedge e_0^9 \rangle + \langle d\omega \wedge e \wedge e_0^8 \rangle + \langle \ol \psi \wedge (1+d)\rho(e_0)^5 \psi \rangle + \langle dC \wedge dC \wedge e_0^3 \rangle.\]
Thus we expect a complexified BV complex of form
\[\xymatrix{
&\Omega^0(X; \CC^{11}) \ar[r] &\Omega^1(X;\CC^{11}) \ar[r] &\Omega^{10}(X; \wedge^9\CC^{11}) \ar[r] &\Omega^{11}(X;\wedge^9\CC^{11}) &\\
&\Omega^0(X; \so(11;\CC)) \ar[r] \ar[ur] &\Omega^1(X;\so(11;\CC)) \ar[r] \ar[ur] &\Omega^{10}(X; \wedge^{10}\CC^{11}) \ar[r] \ar[ur] &\Omega^{11}(X;\wedge^{10}\CC^{11}) &\\
\cdots\ar[r] &\Omega^2(X;\CC) \ar[r] &\Omega^3(X;\CC) \ar[r] &\Omega^8(X;\CC) \ar[r] &\Omega^9(X;\CC) \ar[r] &\cdots \\
&\Pi\Omega^0(X; S) \ar[r] &\Pi\Omega^1(X;S) \ar[r] &\Pi\Omega^{10}(X; S) \ar[r] &\Pi\Omega^{11}(X;S) &\\
}\]

\begin{landscape}
where, as before, the first and second lines are paired with one another, and the third and fourth lines are paired with themselves, all by a wedge-and-integrate pairing.  The twisted BV complex has a similar form to that in four dimension, but incorporating the supergravity C-field.
\[
\xymatrix{
\hspace*{-30pt}
\Omega^0(X; S_-) \ar[r] \ar[dr] &\Omega^1(X;S_-) \ar[r] \ar[dr] &\Omega^{10}(X; S_-) \ar[r] \ar[ddr] &\Omega^{11}(X;S_-) \ar[ddr] &&\\
&\Omega^0(X; \CC^{11}) \ar[r] &\Omega^1(X;\CC^{11}) \ar[r] &\Omega^{10}(X; \wedge^9\CC^{11}) \ar[r] \ar[ddr] &\Omega^{11}(X;\wedge^9\CC^{11}) \ar[ddr]&\\
&\Omega^0(X; \so(11;\CC)) \ar[r] \ar[ur] \ar[dr] &\Omega^1(X;\so(11;\CC)) \ar[r] \ar[ur] \ar[dr] &\Omega^{10}(X; \wedge^{10}\CC^{11}) \ar[r] \ar[ur] &\Omega^{11}(X;\wedge^{10}\CC^{11}) &\\
&&\Omega^0(X; S_+) \ar[r] \ar[rd] &\Omega^1(X;S_+) \ar[r] \ar[rd] &\Omega^{10}(X; S_+) \ar[r] \ar[rd] &\Omega^{11}(X;S_+) \ar[rd] \\
&&\cdots \ar[r] &\Omega^2(X;\CC) \ar[r] &\Omega^3(X;\CC) \ar[r] &\Omega^8(X;\CC) \ar[r] &\Omega^9(X;\CC) \ar[r] &\cdots \\
}
\]

The first interesting map, $[-,Q] \colon S_- \to \CC^{11}$, is injective and has cokernel $\CC^5$.  The other interesting map, $\mr{act}_Q \colon \so(11;\CC) \to S_+$, has an interesting kernel \emph{and} cokernel.  To analyse these, Igusa \cite{Igusa} computed all the possible (complex) orbits and stabiliser subgroups for spinors in eleven dimensions.  There are five orbits, whose associated stabilisers are
\begin{itemize}
 \item $\SL(5;\CC)$, of dimension 24.
 \item $\SL(5;\CC) \ltimes U_{15}$ of dimension $24+15 = 39$.
 \item $(G_2 \times \SL(2;\CC)) \ltimes U_{15}$ of dimension $(14 + 3) + 15 = 32$.
 \item $\Spin(7;\CC) \ltimes \CC^9$ of dimension $27 + 9 = 36$.
 \item $\Sp(4;\CC) \ltimes U_{14}$ of dimension $10 + 14 = 24$.
\end{itemize}
where $U_{14}$ and $U_{15}$ are connected unipotent groups of complex dimension 14 and 15.  Charlton \cite{Charlton} states that the pure spinors comprise the orbit of smallest dimension.  This smallest dimensional orbit corresponds to the largest dimensional stabiliser, which we see -- from the list -- is $\SL(5;\CC) \ltimes U_{15}$.  Here $U_{15}$ is the group of upper triangular six-by-six matrices with 1 along the diagonal.  To describe the $\SL(5;\CC)$ action, we naturally identify this with $\wedge^2 \CC^6$, then choose a vector $v_0$ in $\CC^6$ to induce an identification with $\wedge^2 \CC^5 \oplus \CC^5 \wedge \{v_0\}$, with its natural $\SL(5;\CC)$ action.  
\end{landscape}

This group embeds in $\SO(12;\CC)$ as block matrices of form
\[\left(\begin{array}{ccc|c|ccc|c}
&&&&&&&\\
&\alpha&&0&&0&&0\\
&&&&&&&\\
\hline
&0&&1&&0&&0\\
\hline
&&&&&&&\\
&\gamma \alpha&&v&&(\alpha^T)^{-1}&&0\\
&&&&&&&\\
\hline
&-v^T\alpha&&0&&0&&1
\end{array}\right)\]
where $\alpha \in \SL(5;\CC)$, $v\in \CC^5$ and $\gamma \in \so(5;\CC)$.  One can check that this is a subgroup, where we use the quadratic form of signature $(6,6)$ on $\CC^{12}$.  What's more, it lies in a copy of $\SO(11;\CC)$ embedded in $\SO(12;\CC)$ as the group of block matrices of form
\[\left(\begin{array}{ccc|c|ccc|c}
&&&&&&&\\
&\alpha&&0&&\beta&&0\\
&&&&&&&\\
\hline
&0&&1&&0&&0\\
\hline
&&&&&&&\\
&\gamma &&v&&\delta&&0\\
&&&&&&&\\
\hline
&w&&a&&x&&1
\end{array}\right)\]
representing isometries.  The double cover map $\spin(11;\CC) \to \SO(11;\CC)$ maps the stabiliser of $Q$ isomorphically onto this group, since the stabiliser in the spin group doesn't include the element $-1$ (the other element of the preimage of the identity under the double covering map). \chris{What's more, some of the other orbits correspond to interesting square zero spinors which we could use to twist.}

Now, the image of the action map is given by the tangent space to the $\Spin(11;\CC)$ orbit at $Q \in S_+$.  If we choose a pure spinor, the orbit has dimension 16, thus so does the image under the infinitesimal action map.  The last interesting map is the one that lands in the space of C-fields, namely the map $\Omega^1(X;S_+) \to \Omega^3(X;\CC)$ sending a positive gravitino $\psi$ to the 3-form $\ol Q \wedge \gamma_{ab} \psi \wedge e_0^a \wedge e_0^b$, or in a more coordinate free notation, $\langle Q, \rho(e_0)^2 \psi \rangle$.  Note that any endomorphism $F$ of the space of spinors is realised by iterated Clifford multiplication \chris{todo.  $\langle Q, \rho(v)Q \rangle = (v, \Gamma(Q,Q)) = 0$, but it's not clear for iterated Clifford multiplication.  Does $\Gamma(Q,\rho(v)Q)$ at least lie in a MTIS with $v$?  Want to show the $S_+$ cohomology group vanishes.}

Finally we need to investigate the image of this map in $\Omega^3(X;\CC)$. \chris{It's probably generated by covectors of form $v \wedge \gamma_{ab} e_0^a \wedge e_0^b$, so isomorphic to $\Omega^1(X;\CC)$?}

\chris{Actually, I should try to phrase this all in the Weil algebra language first.  In parturbation theory we shouldn't need to worry about the difference between connections and 1-forms, and should just consider the shifted cotangent space to $\hom_{\mr{cdga}}(W^\bullet(\gg), \Omega^\bullet(X))$.  This lives inside the degree zero part of $(W^\bullet(\gg))^* \otimes \Omega^\bullet(X)$ (which models cochain complex morphisms), which we should suitably resolve.  Going further we need to take into account gauge transformations, modelled by concordance.  Maybe there's a simplicial description here to which we can apply Dold-Kan to get the BRST complex?  This looks like the usual simplicial $L_\infty$ algebra construction using differential forms on $n$-simplices.}

\bibliographystyle{alpha}
\bibliography{Supergravity}

\textsc{Department of Mathematics, Northwestern University}\\
\textsc{2033 Sheridan Road, Evanston, IL 60208, USA} \\
\texttt{celliott@math.northwestern.edu}
\end{document}

### 2019-01-08 Twisted Supergravity/Twisted_SUGRA.tex
tidying

\documentclass[10pt, oneside]{article}

\IfFileExists{./math_headers.sty}
  {\input ./math_headers.sty}
  {\IfFileExists{../math_headers.sty}
    {\input ../math_headers.sty}
    {\typeout{Header file not found}
    }
  }

\title{Holomorphically Twisted Supergravity}
\author{Chris Elliott}

\usepackage{verbatim}

\DeclareMathOperator{\EOM}{EOM}
\newcommand{\vac}{\mc{V} \text{ac}}
\newcommand{\del}{\partial}
\def\d{{\rm d}}
\newcommand{\Obs}{\mathrm{Obs}}
\newcommand{\map}{\underline{\mathrm{Map}}}
\newcommand{\siso}{\mathfrak{siso}}

\begin{document}

\maketitle

\section{Introduction}

\chris{Later we can write an intro to the BV setup, and to twisting.}

\subsection{Introduction to Supersymmetry}
In this paper we'll mainly discuss the $N=1$ supersymmetry algebra in dimension 4, although we'll sometimes obtain examples of supersymmetric theories by compactification from higher dimensional supersymmetric theories.

\begin{definition}
The complex $N=1$ \emph{super Poincar\'e algebra} in dimension 4 $\siso(4;\CC)$ is the complex super Lie algebra whose bosonic part is the Poincar\'e algebra $\so(4;\CC) \ltimes \CC^4$, and whose fermionic part is the Dirac spin representation $S$ of $\so(4;\CC)$.  Concretely we can decompose $\so(4;\CC)$ as $\sl(2;\CC)_+ \oplus \sl(2;\CC)_-$, and $S$ splits as the sum $S_+ \oplus S_-$ of the fundamental representations of the two factors.  There is a bracket between the fermionic elements given by the unique $\so(4;\CC)$-equivariant map
\[\Gamma \colon S_+ \otimes S_- \to \CC^4\]
where $\so(4;\CC)$ acts on $\CC^4$ by the fundamental representation.
\end{definition}

\section{Supergravity in the First Order Formalism}
In this section we'll explain how 4d $N=1$ supergravity can be modelled perturbatively in the BV formalism using the first order formalism for gravity.  This will allow us to make sense perturbatively of \emph{twisted} supergravity theories.  While the 4d $N=1$ supersymmetry algebra doesn't include any topological supercharges we can consider the twist with respect to holomorphic supercharges, which we'll argue yields a perturbative theory of K\"ahler-Einstein structures.

Our main object of study will be the following classical BV theory.
\begin{definition}
The theory of \emph{$N=1$ supergravity} in the first-order formalism is the BV theory on $\RR^4$ modelled by the following sheaf $L_{N=1}$ of $L_\infty$-algebras.  We fix a reference 1-form $e_0 \in \Omega^1(\RR^4; T_{\RR^4}^\CC)$ valued in the complexified tangent bundle.  The theory $L_{N=1}$ assigns to an open set $U \sub \RR^4$ the following cochain complex.
\[\xymatrix{
& \underline{0} & \underline{1} & \underline{2} & \underline 3 \\
\mbox{Fermion degree }0 & \Omega^0(U; T^\CC_U) \ar[r]^\d & \Omega^1(U; T^\CC_U) \ar[r]^{e_0 \wedge \d} &\Omega^3(U; \wedge^2 T^\CC_U) \ar[r]^\d &\Omega^4(U; \wedge^2 T^\CC_U) \\
\mbox{Fermion degree }0 & \Omega^0(U; \so(4;\CC)) \ar[r]^\d \ar[ur]^{e_0} & \Omega^1(U; \so(4;\CC)) \ar[r]^{e_0 \wedge \d} \ar[ur]^{[e_0 \wedge e_0]} &\Omega^3(U; \wedge^3 T^\CC_U) \ar[r]^\d \ar[ur]^{e_0} &\Omega^4(U; \wedge^3 T^\CC_U) \\
\mbox{Fermion degree }1 & \Omega^0(U; S) \ar[r]^\d & \Omega^1(U; S) \ar[r]^{\sd e_0 \d} &\Omega^3(U; S) \ar[r]^\d &\Omega^4(U; S).
}\]
Here $\sd e_0$ denotes the usual Dirac slash notation $\sd e_0 = \gamma^i (e_0)_i$.  This cochain complex admits a natural degree $-3$ wedge-pairing $L_{N=1} \otimes L_{N=1} \to \mr{Dens}[3]$ valued in densities, where the first two rows are paired with one another and $S_\pm$ is paired with itself in the last row.  The complex is also equipped with degree 2 and degree 3 brackets making it into an $L_\infty$-algebra; it's most straightforward to encode this $L_\infty$-structure in terms of an interaction functional $I$ satisfying the classical master equation.  We can describe this interaction concretely in terms of individual fields in the BV theory.

We'll use the following notation for the fields.  We denote the ghosts (generators of the degree 0 part of the BV complex) by $f \in \Omega^0(\RR^4;T_{\RR^4})$, $\phi \in \Omega^0(\RR^4;\so(4))$ and $\chi \in \Omega^0(\RR^4;\mc S)$.  We denote the classical fields (generators of the degree 1 part of the BV complex) by $e \in \Omega^1(\RR^4;T_{\RR^4})$, $A \in \Omega^1(\RR^4;\so(4))$ and $\psi \in \Omega^1(\RR^4;\mc S)$.  We denote the antighosts and antifields dual to these generators by the symbols $f^\vee, \phi^\vee, \chi^\vee, e^\vee, A^\vee$ and $\psi^\vee$.

Our interaction functional will split as
\[I_{N=1} = I_{\mr{Pal}} + I_{\mr{fer}} + I_{\mr{ghost}}\]
where $I_{\mr{Pal}} = F_A \wedge e \wedge e$ and $I_{\mr{fer}} = \langle \psi, \sd e \d_A \psi \rangle$, where $\langle -,- \rangle$ denotes the scalar-valued pairing between spinors.  Together these make up the ordinary (as opposed to BV) classical interaction for the $N=1$ supergravity theory in the first order formalism.  The third factor $I_{\mr{ghost}}$ encodes the infinitesimal gauge symmetry and take the following form:
\[
I_{\mr{ghost}} = \sum_{\text{BV fields } \alpha}  \left( \langle \alpha^\vee, [\phi, \alpha]\rangle_{\mr{BV}} + \langle \alpha^\vee, [\chi, \alpha]\rangle_{\mr{BV}} + \langle \alpha^\vee, [f, \alpha] + \mc L_f \d_A \alpha \rangle_{\mr{BV}} \right)
\]
where $\langle -,-\rangle_{\mr{BV}}$ denotes the degree $-3$ BV pairing, and the sum is over the twelve summands of the BV complex.
\end{definition}

This theory admits a natural twisting datum -- an action of the supergroup $\aut(\Pi \CC) = \CC^\times \ltimes \Pi \CC$ -- as follows.  Let $Q \in S_+$ be a fixed Weyl spinor.  If we like we can view $Q$ as an element of $\Omega^0(U; \mc S_U)$ for each open set $U \sub \RR^4$.
\begin{definition}
The \emph{holomorphic twisting datum} on $L_{N=1}$ associated to this choice of $Q$ is defined as follows.  We define a $\CC^\times$-action on $L_{N=1}(U)$ by giving $\Omega^\bullet(U; \mc S_{+U})$ weight 1 and $\Omega^\bullet(U; \mc S_{-U})$ weight $-1$, and we define a $\Pi \CC$ action generated by the bracket $[Q,-]$, which has $\CC^\times$-weight 1 since $Q$ has weight 1.
\end{definition}

In order to compute the twist with respect to this action we must compute the total complex of $L_{N=1}(U)$ viewed as a double complex with respect to its internal BV-BRST differential and the new grading and differential given by $[Q,-]$, i.e. the following:
\begin{equation} \xymatrix{
   \Omega^0(U; S_-) \ar[r] \ar[rd] & \Omega^1(U; S_-) \ar[r]\ \ar[rd] &\Omega^3(U; S_-) \ar[r] \ar[rdd] &\Omega^4(U; S_-) \ar[rdd] \\
   &\Omega^0(U; T^\CC_U) \ar[r] & \Omega^1(U; T^\CC_U) \ar[r]\ &\Omega^3(U; \wedge^2 T^\CC_U) \ar[r] \ar[rdd] &\Omega^4(U; \wedge^2 T^\CC_U) \ar[rdd] \\
   &\Omega^0(U; \so(4;\CC)) \ar[r] \ar[rd] \ar[ur] & \Omega^1(U; \so(4;\CC)) \ar[r] \ar[ru] \ar[rd] &\Omega^3(U; \wedge^3 T^\CC_U) \ar[r] \ar[ur] &\Omega^4(U; \wedge^3 T^\CC_U) \\ 
   &&\Omega^0(U; S_+) \ar[r] & \Omega^1(U; S_+) \ar[r]\ &\Omega^3(U; S_+) \ar[r] &\Omega^4(U; S_+). \\
}\label{twisted_complex}\end{equation}
We'll describe a natural subcomplex quasi-isomorphic to this total complex, and investigate the new $L_\infty$-structure.

\begin{remark}
This description of twisted supergravity from the point of view of the first-order formalism is equivalent to the notion of twisted supergravity as introduced by Costello and Li \cite{CostelloLi}.  Indeed, Costello and Li describe twisted supergravity as simply performing calculations in a background where the bosonic ghost takes a non-zero value.  In our language, the bosonic ghosts are the fields $(\chi_+ + \chi_-) \in \Omega^0(\RR^4;S)$.  After modifying the degrees of the BV complex by adding the R-charge, the positive helicity bosonic ghost $\chi_+ \in \Omega^0(\RR^4;S_+)$ lies in degree 0.  We described the differential in the untwisted supergravity theory in terms of perturbations around a non-trivial vielbein field $e_0$.  In Costello and Li's language, one could instead consider perturbations around a non-trivial field $(e_0, (\chi_+)_0) \in \Omega^1(\RR^4; T^\CC_{\RR^4}) \oplus \Omega^0(\RR^4; S_+)$.  Adding the bosonic ghost $(\chi_+)_0$ to the background has the same affect as adding $[(\chi_+)_0, -]$ to the BV differential, which is exactly what we're doing in our description with $(\chi_+)_0 = Q$.
\end{remark}

Note that the choice of a holomorphic supercharge $Q$ above induces a choice of complex structure on $\RR^4$.  Indeed, there is a canonical $\so(4;\CC)$-equivariant isomorphism $\mc S_+ \otimes \mc S_- \to T^\CC_{\RR^4}$ of complex vector bundles on $\RR^4$, and so a choice of element $Q \in S_+$ -- or equivalently of a global section of the spinor bundle $\mc S_+$ induces a choice of complex 2-dimensional subbundle of $T^\CC_{\RR^4}$, i.e. a complex structure on $\RR^4$.  Suppose from now on that our $e_0$ is adapted to this complex structure, i.e. that it lives in $\Omega^1(\RR^4; T^{0,1}_{\RR^4}) \sub \Omega^1(\RR^4; T^\CC_{\RR^4})$.

\begin{prop}
The following subcomplex $L_{\mr{hol}}(U) \sub L_{N=1}^{\mr{tw}}(U)$ of the twisted BV complex \ref{twisted_complex}, corresponding to the complex structure induced by the choice of $Q$ is a quasi-isomorphism:
\begin{equation}\xymatrix{
&&\Omega^{2,1}(U;\CC) \ar[dr]^{\iota_+ \circ \ol \dd} & \\
\Omega^{0,0}(U; T^{0,1}_U) \ar[r]^{\ol \dd} &\Omega^{0,1}(U; T^{0,1}_U) \ar[ur]^{e_0 \wedge \dd} \ar[r]^{e_0 \wedge \ol \dd} &\Omega^{1,2}(U; \CC \oplus \sl(2;\CC)) \ar[r]^(.55){\pi_{\mr{ann}(e_0)} \circ \dd} &\Omega^{2,2}(U;T^{0,1}_U)\\
\Omega^{0,0}(U;T^{0,1}_U) \ar[dr]_{\pi_+ \circ \ol \dd} \ar[r]^(.45){\iota_{\mr{ann}(e_0)} \circ \dd}&\Omega^{1,0}(U; \CC \oplus \sl(2;\CC)) \ar[r]^{e_0 \wedge \ol \dd} &\Omega^{2,1}(U; T^{0,1}_U) \ar[r]^{\ol \dd} &\Omega^{2,2}(U;T^{0,1}_U).\\
&\Omega^{0,1}(U;\CC) \ar[ur]^{e_0 \wedge \dd} &&
}\label{small_model}\end{equation}
Here $\CC \oplus \sl(2;\CC) \sub \so(4;\CC)$ is the centralizer of the supercharge $Q$, $\iota_{\mr{ann}(e_0)}$ indicates the inclusion of the (two-dimensional) annihilator of $e_0$ in $\RR^4$ and $\pi_{\mr{ann}(e_0)}$ is the projection onto the same annihilator (defined using the Iwasawa decomposition), and likewise $\iota_+$ and $\pi_+$ denote the inclusion of and projection onto the one-dimensional summand of this annihilator lying in the first factor of $\sl(2;\CC)_+ \oplus \sl(2;\CC)_-$.  
\end{prop}

\begin{proof}
We'll check this by splitting the inclusion into a composite of two inclusions, each of which is a quasi-isomorphism.  Consider the intermediate subcomplex
\begin{equation}\xymatrix{
 \Omega^0(U; T^{0,1}_U) \ar[r] & \Omega^1(U; T^{0,1}_U) \ar[r] &\Omega^3(U; \CC \oplus \sl(2;\CC)) \ar[r] &\Omega^4(U; \CC \oplus \sl(2;\CC)) \\
   \Omega^0(U; \CC \oplus \sl(2;\CC)) \ar[r] \ar[ur] & \Omega^1(U; \CC \oplus \sl(2;\CC)) \ar[r] \ar[ur] &\Omega^3(U; T^{0,1}_U) \ar[r] \ar[ur] &\Omega^4(U; T^{0,1}_U) 
} \label{intermediate_complex}\end{equation}
where the map $\Omega^1(U; \CC \oplus \sl(2;\CC)) \to \Omega^3(U; T^{0,1}_U)$ is given by sending $\alpha \otimes A$ to $\d \alpha \wedge A(e_0)$, and the map $\Omega^1(U; T^{0,1}_U)) \to \Omega^3(U; \CC \oplus \sl(2;\CC))$ is given by sending $e$ to $\d e \wedge e_0$ and noting that this lands in the subalgebra $\CC \oplus \sl(2;\CC)$ of $\so(4;\CC) \iso \wedge^2 \CC^4$ which centralizes $Q$.  To see that the inclusion of this subcomplex into $L_{N=1}^{\mr{tw}}(U)$ is a quasi-isomorphism we just need to observe that 
\begin{enumerate}
 \item The map $[Q,-] \colon \Omega^i(U; S_-) \to \Omega^i(U; T_U)$ is injective and its image is exactly the subspace of $i$-forms valued in \emph{holomorphic} vector fields for the complex structure coming from $Q$ -- this is the definition of the complex structure.
 \item The map $\mr{act}_Q \colon \Omega^i(U; \so(4;\CC)) \to \Omega^i(U; S_+)$ is surjective and its kernel is the subspace of $i$-forms valued in the centralizer of $Q$.
\end{enumerate}
Having done this calculation we've established that the intermediate complex \ref{intermediate_complex} is equivalent to the $E_2$-page of the spectral sequence whose $\d_0$ is the new differential $[Q,-]$ coming from the twist, with respect to the grading by $\CC^\times$-weight $-1,0$ and $+1$.  Because this $E_2$-page is concentrated in $\CC^\times$-weight 0, it's equivalent to the $E_\infty$-page, which means that our inclusion is a quasi-isomorphism as claimed.

We now need to check that the inclusion of \ref{small_model} into this intermediate complex is also a quasi-isomorphism, which essentially means computing the kernel and cokernel of the three diagonal maps from the bottom row to the top (applying exactly the same argument).  First consider the map $\Omega^0(U; \CC \oplus \sl(2;\CC)) \to \Omega^1(U, T^{0,1}_U)$ defined by $A \mapsto A(e_0)$.  The kernel of this map consists of $A$ that annihilate $e_0$.  This annihilator is 2-dimensional and abelian, and we can naturally identify it with the space of sections of the holomorphic tangent bundle $T^{0,1}_U$.  The image of this map consists of \emph{holomorphic} 1-forms valued in $T^{0,1}_U$, and so the cokernel can canonically be identified with $\Omega^{0,1}(U, T^{0,1}_U)$.  The morphism $\Omega^3(U; T^{0,1}_U) \to \Omega^4(U; \CC \oplus \sl(2;\CC))$ is dual to this map under the non-degenerate BV pairing, so we can identify the kernel and cokernel as $\Omega^{2,1}(U; T^{0,1}_U)$ and $\Omega^{2,2}(U; T^{0,1}_U)$ -- the duals of the kernel and cokernel we just computed.

Finally we consider the map $\Omega^1(U; \CC \oplus \sl(2;\CC)) \to \Omega^3(U; \CC \oplus \sl(2;\CC))$ which sends $\alpha \otimes A$ to $\alpha \otimes [A, [e_0 \wedge e_0]]$ where $[e_0 \wedge e_0]$ is viewed as an element of $\Omega^2(U; \so(4;\CC))$.  In fact by definition it's an element of $\Omega^{2,0}(U; \sl(2;\CC)_+)$.  The assumption that $[e_0 \wedge e_0]$ is non-zero ensures that it's a regular element \chris{need an argument that it can't be a nilpotent}, so the kernel and cokernel of our map are given by $\Omega^{0,1}(U;\CC) \oplus \Omega^{1,0}(U; \CC \oplus \sl(2\CC)$ and$\Omega^{2,1}(U;\CC) \oplus \Omega^{1,2}(U; \CC \oplus \sl(2\CC)$ respectively, as required.
\end{proof}

Now, let's address the Lie bracket on the twisted BV complex.  We'll understand how the Lie bracket changes after twisting by investigating the twisted algebra of observables, i.e. the twist of the Chevalley-Eilenberg cochain complex of our $L_\infty$-algebra.  We can do this using a straightforward spectral sequence argument.  We'll use the following fact \chris{include elsewhere, including the notation I'm calling $\nu$.}

\begin{prop} \label{twisted_observables_prop}
Let $\obs_{N=1}$ be the classical factorization algebra of observables in the untwisted $N=1$ theory, and let $\obs_{N=1}^Q$ be the classical factorization algebra of observables in the $Q$-twisted theory.  Up to regrading, the algebra $\obs_{N=1}^Q$ is equivalent to the algebra obtained from $\obs_{N=1}$ by adding the operator $\{\nu(Q),-\}$ to the differential.  Here $\nu(Q)$ is the conserved current asociated to the symmetry $Q$.
\end{prop}

\begin{prop}
There is an embedding of graded vector spaces $L_{\mr{hol}}^\natural(U) \to L^\natural_{N=1}(U)$ \emph{without} turning on the twist, where the notation $\natural$ here means the graded vector space obtained by forgetting the differential.  This allows us to restrict the BV interaction functional $I_{N=1}$ to a functional on $L_{\mr{hol}}^\natural(U)$.  This interaction satisfies the classical master equation, and therefore defines an $L_\infty$-structure on $L_{\mr{hol}}$.  Furthermore the embedding $L_{\mr{hol}}(U) \to L_{N=1}^{\mr{tw}}(U)$ is an $L_\infty$-map. 
\end{prop}

\begin{proof}
We'll use Proposition \ref{twisted_observables_prop} and the spectral sequence of the double complex for the internal grading and differential $\d_{\mr{cl}}$ on $\obs_{N=1}(U) = C^\bullet(L_{N=1}(U))$ and the R-weight grading and differential $\{\nu(Q),-\}$.  In order to verify our claim, we'll just need to check that this spectral sequence collapses at the $E_2$-page, so that
\[H^\bullet_{\mr{CE}}(H^\bullet(L(U),Q), \d_{\mr{CE}}) \iso H^\bullet_{\mr{CE}}(L(U), \d_{\mr{CE}} + Q)\]
where we've written $Q$ for the operator $\{\nu(Q),-\}$. This degeneration is easy to see because $H^\bullet(L(U),Q) \iso L_{\mr{hol}}(U)$ is concentrated in degree 0 for the R-symmetry weight grading, which means that the higher differentials in the spectral sequence automatically vanish.

Now, we recall that one can extract the classical interaction functional for a classical field theory from the Maurer-Cartan equations for the $L_\infty$ structure, or equivalently from the equation $\d_{\mr{CE}}(\OO) = 0$ in the Chevalley-Eilenberg complex.  This spectral sequence argument tells us in particular that a $Q$-closed field is closed for the classical differential in the untwisted theory (i.e. as an element in $L^\natural_{N=1}(U)$) if and only if it is closed for the classical differential in the twisted theory (i.e. as an element in $L_{\mr{hol}}^\natural(U)$).  Therefore the classical interaction obtained by restriction to $L_{\mr{hol}}^\natural(U)$ (equivalently the degree 2 and 3 brackets obtained by restriction) is equivalent to the classical interaction obtained from the spectral sequence, which means that this restricted classical interaction satisfies the classical master equation (or equivalently the restricted brackets are well-defined on $L_{\mr{hol}}$).
\end{proof}

Having given this description, how should we think about the twisted supergravity theory?  We can read off a nice description of the equations of motion of the twisted theory from the classical BV complex, which suggests that non-perturbatively the twisted supergravity theory should admit K\"ahler-Einstein structures as classical solutions, as we'll now explain.

Firstly, the classical fields in the holomorphically twisted theory on an open set $U$ are given as follows:
\begin{align*}
 e_{\mr{hol}} &\in \Omega^{0,1}(U; T^{0,1}_U) \\ 
 A_{\mr{hol}} &\in \Omega^{1,0}(U; \sl(2;\CC)) \\
 A' &\in \Omega^{1}(U; \CC).
\end{align*}
The holomorphic vielbein $e_{\mr{hol}}$ defines a hermitian metric on the holomorphic tangent bundle of $U$ just as the ordinary vielbein defines a Riemannian metric on the ordinary tangent bundle: we choose a reference

\chris{todo.  If we look at the form of the action this extra field $A'$ is going to end up non-propagating, so we'll get a K\"ahler-Einstein metric and a free abelian gauge field with no coupling between them.  The equations of motion for the gauge field will look like Chern-Simons equations: $\tr(e_0 \wedge A' \wedge \d A') = 0$ (though I need to think a little more about what $\tr$ means here exactly).}

\bibliographystyle{alpha}
\bibliography{Supergravity}

\textsc{Institut des Hautes \'Etudes Scientifiques}\\
\textsc{35 Route de Chartres, Bures-sur-Yvette, 91440, France}\\
\texttt{celliott@ihes.fr}\\
\vspace{5pt}
\end{document}

### 2019-01-08 Twisted Supergravity/gauge_transformation.tex
tidying

\documentclass[10pt, oneside]{article}

\IfFileExists{../math_headers.sty}
  {\input ../math_headers.sty}
  {\IfFileExists{./math_headers.sty}
    {\input ./math_headers.sty}
    {\typeout{Header file not found}
    }
  }

\title{Notes on Supergravity}
\author{Chris Elliott}
\date{}

\fancyhead[R]{}

\begin{document}

The Lagrangian density is, in a local coordinate patch, given by
\[\LL(\omega, e) = \eps_{abcd} \Omega^{ab} \wedge e^c \wedge e^d.\]
Compute its first variation under the gauge transformation $e^a \mapsto e^a + \dd f^a + \omega^{ab} f_b$.  We find
\begin{align*}
\delta\LL(\omega, e) &= \eps_{abcd} \Omega^{ab} \wedge (\dd^c f\wedge  e^d + f \omega^c \wedge e^d + e^c \wedge \dd^d f + f e^c \wedge \omega^d)\\ 
&= (\eps_{abcd} + \eps_{abdc}) \Omega^{ab} \wedge (\dd^c f\wedge  e^d + f \omega^c \wedge e^d) \\
&= 0.
\end{align*}
In the index notation, the order in which we write the forms isn't important, only the order of the indices.

Now, here's what I think this calculation really means.  First, how should we interpret the Palatini action?  I'll explain it in $n$ dimensions.  We can take $e$, which is an $\RR^n$ valued 1-form, and produce a $\wedge^{n-2} \RR^n$ valued $n-2$ form, which I'll write as 
\[e^{a_1} \wedge e^{a_2} \wedge \cdots  \wedge e^{a_{n-2}}.\]
This is totally antisymmetric in the $a_i$ indices.  What's more, the curvature $\Omega$ of the connection $\omega$ is an $\so(n)$ valued 2-form, and $\so(n)$ is canonically isomorphic to $\wedge^2 \RR^n$.  Thus we produce a $\wedge^n \RR^n$ valued $n$ form which I'll write as 
\[\Omega^{a_1 a_2}  \wedge e^{a_3}  \wedge e^{a_4}  \wedge \cdots \wedge  e^{a_n}.\]
Our choice of basis gives us a canonical isomorphism $\wedge^n \RR^n \iso \RR$, thus an $\RR$ valued $n$ form which I could reasonably write as 
\[\frac 1{n!}\eps_{a_1 \cdots a_n} \Omega^{a_1 a_2}  \wedge e^{a_3}  \wedge e^{a_4}  \wedge \cdots  \wedge e^{a_n}.\]

Note that while the wedge product of 1-forms remains antisymmetric, $e^a \wedge e^b$ is still not zero if $a \ne b$, because we're pairing different components of the vielbein.  The symmetry I used to see that the variation vanishes is on the level of components: it was that
\[e^a \wedge (d_\omega f)^b = - e^b \wedge (d \omega f)^a.\]

\end{document}

### 2019-01-08 Twisted Supergravity/sugra_frame.tex
tidying

\documentclass[10pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

\setcounter{tocdepth}{1}

\title{Twisted $N=1$ supergravity}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{red}{OG: }\textcolor{red}}

\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc,through}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{pgffor}
%\usepackage{tikz-feynman}

\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    fermionbar/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw=black},
    gluon/.style={decorate, draw=black,
        decoration={coil,amplitude=4pt, segment length=5pt}},
    scalar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    scalarbar/.style={dashed,draw=black, postaction={decorate},
        dwecoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    scalarnoarrow/.style={dashed,draw=black},
    electron/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
}

\begin{document}
\maketitle

%\input{intro}
\tableofcontents

\input{palatini}

\end{document}

### 2019-01-09 10-9-8d_twists_1_19.tex
some more 8d edits

@@
 \begin{align*}
-B^{10} &= B + A \wedge \d x^9 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_9) \\
-A^{10}_{0,1} &= A' + \phi \d x^9 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_9)
+B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_9) \\
+A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_9)
 \end{align*}
@@
 \end{align*}
-again, along with the ghost $c$ (I've skipped writing the $\d x^7$ and $\d x^8$ factors in here).
+again, along with the ghost $c$ (I've skipped writing the $\d \ol z^4$ and $\d \ol z^5$ factors in here).
 
@@
 It is still acted upon by $\SU(4)$.
-This theory should be a cotangent theory where the base -- in terms of BV fields -- is spanned by $c, A, \st B, \st A', \st \phi$, and the fiber is spanned by $\phi, A', B, \st A, \st c$.
+This theory should be a cotangent theory where the base -- in terms of BV fields -- is spanned by $c, A', B, \st A, \st \phi$, and the fiber is spanned by $\phi, A, \st B, \st A', \st c$.
 We can see this by thinking about which fields are bosonic and which are fermionic.
 This example should, for the first time, be promotable into a $\ZZ$-graded theory.
-For this to produce the correct degrees, we need $A'$ to have R-symmetry weight $-1$ and $\phi$ to have R-symmetry weight $-2$.
-I don't see right now where this is supposed to come from.
+For this to produce the correct degrees, we need the following R-charges under the 8d $\CC^\times$ R-symmetry group:
+\begin{align*}
+B &\text{: charge } +1 \\
+A &\text{: charge } -1 \\
+A' &\text{: charge } 0 \\
+\phi &\text{: charge } -2. \\
+\end{align*}
+In 10-dimensions, $A^{10}$, and hence $A_{0,1}^{10}$, has R-charge 0, and $\lambda$, and hence $B^{10}$, has R-charge $+1$.
+So writing $A_{0,1}^{10} = A' + \phi \d \ol z^5$ and $B^{10} = B + A \wedge \d \ol z^5$ we get the correct R-charges if $\d \ol z^5$ has R-charge 2.
+
 \end{enumerate}

### 2019-01-09 10-9-8d_twists_1_19.tex
some more 8d edits

@@
 
+If we assume these R-symmetry weights are correct then, indeed, the holomorphically twisted theory is equivalent to the cotangent theory to $\bun_G(X^4)$ as predicted.
+Question: I'm not sure how to see this in the BRST language.
+I can verify this using the BV action functional: it gives the twisted BV complex an $L_\infty$ structure which is equivalent to the one on that cotangent theory.
+For instance, the quadratic term $B^{10} \wedge \ol \dd A^{10}_{0,1}$ in the BV action gives us the differentials $\phi \to A$ and $A' \to B$.
+
 \end{enumerate}

### 2019-02-05 6d_new.tex
6d calculation

\documentclass[10pt, oneside]{article}
\input math_headers.sty

\title{6d $\cN = (1,0)}
\author{Brian}
\date{\today}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\def\tensor{{\otimes}}

\begin{document}

\section{The holomorphic twist of $6d$ $\mc N = (1,0)$ SUSY}

The underlying supervector space for the $6d$ $\mc N = (1,0)$ supersymmetry algebra has the following description. 
\begin{enumerate}
\item The bosonic piece of the 6d $\mc N = (1,0)$ supersymmetry algebra is
\[
(\mf {so} (6, \CC) \times \mf {sl}(2, \CC)_R) \ltimes V
\]
where 
\begin{itemize}
\item $V = \CC^6$ is the fundamental representation of $\mf {so}(6,\CC)$.
\item $\mf {sl}(2, \CC)_R$ is the $R$-symmetry algebra.
It acts trivially on $V$. 
\end{itemize}
\item The fermionic piece of the algebra is 
\[
S_+ \otimes_\CC W
\]
where $S_+ = \CC^4$ is the chiral irreducible spin representation of $\so(6, \CC)$ and $W_R = \CC^2$ is the two-dimensional vector space. 
\end{enumerate}

The Lie bracket for the superalgebra is determined by the rules:
\begin{enumerate}
\item
There is a term in the Lie bracket for the fundamental action of $\mf {so}(6, \CC)$ on $V$ and the spinorial action of $\mf {so}(6,\CC)$ on $S_+$. 
\item 
There is a term in the Lie bracket given by the action of $\mf {sl} (2,\CC)$ on $S_+ \otimes_\CC W_R$ by rotating the $W_R = \CC^2$ factor. 
\item
The final term in the Lie bracket is defined by the composition
\[
\Gamma : (S_+ \otimes \CC^2) \otimes (S_+ \otimes \CC^2) = (S_+ \otimes S_+) \otimes (\CC^2 \otimes \CC^2) \xrightarrow{\wedge \otimes \omega_{std}} V 
\]
where we have used the isomorphism $\wedge^2 S_+ \cong V$ and the standard symplectic form on $\CC^2$. 
\end{enumerate}

\subsection{Pure gauge theory}

The field content for $6d$ $\mc N = (1,0)$ pure gauge theory consists of a gauge field
\[
A \in C^\infty(\RR^4, V) \tensor \mf g = \Omega^1(\RR^6, \mf g)
\]
and a spinor
\[
\psi \in C^\infty(\RR^4, S_+ \tensor W_R) \tensor \mf g .
\]
As a convention, we choose a basis for $W_R$ given by symbols $\{+, -\}$ and we accordingly decompose the spinor as $\psi = \psi_+ + \psi_-$ where $\psi_{\pm} \in C^\infty(\RR^4, S_+) \tensor \mf g$.
\brian{yikes, bad notation?}

\subsection{The hypermultiplet}

\subsection{Holomorphic language}

A complex structure on $\RR^6 \cong \CC^3$ determines an embedding $\mf {gl} (3, \CC) \hookrightarrow \mf {so} (6, \CC)$. 
With respect to this inclusion, the $\mf {so}(6,\CC)$ representations split as
\begin{align*}
V & = V^{1,0} \oplus V^{0,1} \\
S_+ & = \CC \oplus \wedge^2(V^{0,1})
\end{align*}
where $V^{1,0}$ is the fundamental representation of $\mf {gl}(3, \CC)$ and $V^{0,1}$ its complex conjugate.

Accordingly, the fields of the pure gauge theory decompose as
\[
A = A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3, \mf g) \oplus \Omega^{0,1}(\CC^3, \mf g)
\]
and 
\[
\psi = \phi + \chi^{0,2} \in C^\infty(\CC^3, W_R) \tensor \mf g \oplus \Omega^{0,2}(\CC^3, W_R) \tensor \mf g .
\]
In our notation above, after we choose a basis $\{+,-\}$ for $W_R$ we can decompose the spinor further into $\phi_{\pm} \in C^\infty(\CC^3) \tensor \mf g$ and $\chi^{0,2}_{\pm} \in \Omega^{0,2}(\CC^3) \tensor \mf g$.

\end{document}

### 2019-02-18 pure spinors.tex
Describing some geometry behind pure spinors

\documentclass[12pt]{amsart}

\usepackage{eucal}
\usepackage{amssymb}
\usepackage{stmaryrd}

\usepackage{color}
\definecolor{e-mail}{rgb}{0,.40,.80}
\definecolor{reference}{rgb}{.20,.60,.22}
\definecolor{citation}{rgb}{0,.40,.80}

\usepackage[colorlinks=true,
            linkcolor=reference,
            citecolor=citation,
            urlcolor=e-mail]{hyperref}
\usepackage{cleveref}
\usepackage[all]{xy}

\textwidth=16.5cm
\oddsidemargin=0cm
\evensidemargin=0cm
\textheight=22cm
\topmargin=0cm

\binoppenalty=10000
\relpenalty=10000

\newcommand{\C}{\mathbf{C}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cO}{\mathcal{O}}
\renewcommand{\P}{\mathrm{P}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\T}{\mathrm{T}}

\newcommand{\End}{\mathrm{End}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\LGr}{\mathrm{LGr}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\SL}{\mathrm{SL}}
\newcommand{\Spin}{\mathrm{Spin}}
\newcommand{\Sym}{\mathrm{Sym}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lm}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{example}[thm]{Example}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\begin{document}
\title{Pure spinor formalism}
\author{Pavel Safronov}
\maketitle

\section{Pure spinors}

Let $V=\C^{10}$ and $S_+, S_-$ be the semi-spin representations of $\Spin(V)$. We have a nondegenerate $\Spin(V)$-equivariant pairing $\Gamma\colon \Sym^2(S_+)\rightarrow V$.

For a vector space $L$ we denote by $\ML(L)$ the metalinear group, i.e. the $2:1$ cover of $\GL(L)$ given by the pullback
\[
\xymatrix{
\ML(L) \ar[r] \ar[d] & \GL(1) \ar^{z\mapsto z^2}[d] \\
\GL(L) \ar^{\det}[r] & \GL(1)
}
\]

\textbf{Fact}: the choice of a spin structure on $V$ endows any Lagrangian subspace $L\subset V$ with a metalinear structure, i.e. a choice of $\det(L)^{1/2}$.

\begin{prop}$ $
\begin{enumerate}
\item The group $\Spin(V)$ acts transitively on the set $\LGr(V)$ of Lagrangian subspaces $L\subset V$.

\item The stabilizer of a Lagrangian subspace $L\subset V$ is a parabolic subgroup $G_L\subset \Spin(V)$ which fits into an exact sequence
\[1\longrightarrow \wedge^2 L\longrightarrow G_L\longrightarrow \ML(L)\longrightarrow 1.\]
The choice of a Lagrangian complement $L^*\subset V$ to $L\subset V$ determines a splitting of this exact sequence, i.e. it gives an identification $G_L\cong \ML(L)\ltimes \wedge^2 L$.

\item Under the restriction $G_L\subset \Spin(V)$ the semi-spin representations split as
\[S_+ = (\C\oplus \wedge^2(L^*)\oplus \wedge^4(L^*))\otimes \det(L)^{1/2},\qquad S_- = (\C\oplus \wedge^2L\oplus \wedge^4 L)\otimes \det(L)^{-1/2}.\]
\end{enumerate}
\end{prop}

The tangent bundle $\T_{\LGr(V)}$ to $\LGr(V)$ is naturally $\Spin(V)$-equivariant. Its fiber at $L\in\LGr(V)$ is isomorphic to
\[\wedge^2(L\oplus L^*) / (\End(L)\oplus \wedge^2 L)\cong \wedge^2 L^*\]
as a $G_L$-representation (here $\wedge^2 L$ acts trivially). In particular, $\dim(\LGr(V)) = 10$.

We have $\det(\wedge^2 L^*) \cong \deg(L)^{-4}$. This representation is not $G_L$-invariant, so $\LGr(V)$ does not have a $\Spin(V)$-invariant Calabi--Yau structure.

\begin{prop}$ $
Let $\P$ be the set of nonzero elements $Q\in S_+$ satisfying $\Gamma(Q, Q) = 0$ and $\tilde{\P} = \P\cup \{0\}$.
\begin{itemize}
\item For $Q\in \P$ the image of $\Gamma(Q, -)\colon S_+\rightarrow V$ is a Lagrangian subspace. In particular, we have a projection $\P\rightarrow \LGr(V)$.

\item The natural action of $\C^\times$ on $\P$ by scaling gives $\P\rightarrow \LGr(V)$ the structure of a $\C^\times$-torsor. The fiber of $\P\rightarrow \LGr(V)$ at $L\subset V$ may be identified with nonzero elements $Q\in\det(L)^{1/2}$.
\end{itemize}
\end{prop}

The tangent bundle $\T_\P$ to $\P$ is naturally $\Spin(V)$-equivariant. Its fiber at $Q\in \P$ is isomorphic to
\[\wedge^2(L\oplus L^*) / (\End_0(L)\oplus \wedge^2 L)\cong \wedge^2 L^* \oplus \C\]
as a $\SL(L)\ltimes \wedge^2 L$-representation ($\wedge^2 L$ acts from the first to the second summand). In particular, $\det(\T_{\P, Q})\cong \det(L)^{-4}$ which is trivial as a $\SL(L)\ltimes \wedge^2 L$-representation. In particular, there is a unique $\Spin(V)$-invariant Calabi--Yau structure on $\P$.

Choose a point $Q\in P$. We can introduce a coordinate chart near $Q$ in the following way. We split
\[S_+ = (\C\oplus \wedge^2(L^*)\oplus \wedge^4(L^*))\otimes \det(L)^{1/2}.\]
Let $(\ell, A, M)\in S_+$ be components of a spinor with respect to this splitting. The pure spinor constraint is
\begin{align*}
\ell M + \Lambda\wedge \Lambda &= 0,\\
\langle \Lambda, M\rangle &= 0,
\end{align*}
where in the last line the pairing is $\wedge^2 L^*\otimes \wedge^4 L^*\rightarrow \det(L)^*\otimes L^*$.

In particular, in a neighborhood of $Q$ (i.e. in a neighborhood of $\Lambda=0$, $M=0$ and $\ell\neq 0$) the pair $(\ell, \Lambda)$ gives a coordinate chart. We may identify
\[\det(\wedge^2(L^*)\otimes \det(L)^{1/2})\cong \det(L),\]
so in this chart the unique $\Spin(V)$-invariant Calabi--Yau structure has the form
\[\Omega = \ell^{-3} \d \ell \d^{10} \Lambda.\]

\section{Pure spinor formulation of 10d SYM}

Let
\[T = \Pi\Sigma_+\oplus V\]
be the supertranslation Lie algebra and $G_T$ the supertranslation group. Then $C^\infty(G_T)$ carries two commuting $T$-actions given by left and right translations. For $\sigma\in S_+$ denote by $Q_\sigma$ and $\cD_\sigma$ the corresponding vector fields.

We assign the ghost number number $1$ and odd fermionic degree to coordinates on $\P$. The fields in our theory are
\[\cF = C^\infty(G_T)\otimes \cO(\P)\otimes \g[1].\]
The differential at $\sigma\in \P$ is given by $\cD_\sigma$. There is a residual supersymmetry action on $\cF$ given by $Q_\sigma$.

The differential $\cD$ can be split as $\cD^0 + \cD^1$, where $\cD^0$ is $\cD$ with $\Gamma=0$. The differential $\cD^0$ does not act on $C^\infty(V)$, so it just becomes an overall factor.

\begin{defn}
The \defterm{zero-mode cohomology} is the cohomology of $C^\infty(\Pi S)\otimes \cO(\P)$ with respect to $\cD^0$.
\end{defn}

\end{document}

### 2019-02-27 10d_SYM_Notes.tex
new 10d file

\documentclass[10pt, oneside]{article}

\input ./math_headers.sty

\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

\addbibresource{Twist.bib}

\title{Notes on 10d Super Yang-Mills}
\author{Chris Elliott, Pavel Safronov and Brian Williams}
\date{\today}

\begin{document}

\maketitle

\section{Minimal Super Yang-Mills}
%BRST Fields, Action Functional, BV Complex

\subsection{On-Shell Supersymmetry Action}
%Failure to commute with the classical BV differential

\section{Baulieu's 10 Model}
%SU(5) BRST and BV Fields, Action Functional, BV Complex

\subsection{Off-Shell Action of a Scalar Supersymmetry}
%Does it do anything interesting to the anti-fields?

\section{Homotopy Data}
%We were going to check in particular that everything was a chain map

\subsection{Homotopy Transfer of the Scalar Supersymmetry}

\pagestyle{bib}
\printbibliography

\end{document}

### 2019-03-01 10d_SYM_Notes.tex
Starting to define minimal 10d SYM

@@
 \section{Minimal Super Yang-Mills}
-%BRST Fields, Action Functional, BV Complex
+Our starting point will be the theory complexifying the usual 10d super Yang-Mills theory.
+Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.
+The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of a boson: a connection $A$ on the trivial $G$-bundle, and a fermion: a $\gg$-valued section $\lambda$ of the Weyl spinor bundle associated to the spinor representation $S_+$ \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.}.
+These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$.
+
+We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
+\[L_{\mr{BRST}} = \Omega^0(\RR^{10}; \gg) \to \Omega^1(\RR^{10}; \gg) \oplus \Omega^0(\RR^{10}; \Pi S_+ \otimes \gg)\]
+with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
+
+The action functional in 10d super Yang-Mills is given by
+\[S(A,\lambda) = \int_{\RR^{10}} \langle F_A \wedge \ast F_A + (\lambda, \sd D_A \lambda)\rangle,\]
+where $\langle - \rangle$ denotes an invariant pairing on $\gg$, and $(,)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).
+
+We can re-encode this data in terms of the classical BV complex.  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
+\[\xymatrix{
+\Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
+&\Omega^0(\RR^{10}; \Pi S_- \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
+}\]
+with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
+\begin{align*}
+\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
+(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
+\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
+(A \otimes \lambda) &\mapsto \ast \sd A \lambda
+\end{align*}
+in degree 2, and the map
+\begin{align*}
+\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
+(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
+\end{align*}
+in degree 3.
 

### 2019-03-01 10d_SYM_Notes.tex
Starting to define minimal 10d SYM

@@
 Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.
-The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of a boson: a connection $A$ on the trivial $G$-bundle, and a fermion: a $\gg$-valued section $\lambda$ of the Weyl spinor bundle associated to the spinor representation $S_+$ \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.}.
+The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of a boson: a connection $A$ on the trivial $G$-bundle, and a fermion: a $\gg$-valued section $\lambda$ of the Weyl spinor bundle associated to the spinor representation $S_+$ \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.
+I think for our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.
+The complexified theory twists to holomorphic Chern-Simons theory with complex gauge group.}.
 These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$.
@@
 
-We can re-encode this data in terms of the classical BV complex.  This is the $L_\infty$-algebra whose underlying cochain complex takes the form
+We can re-encode this data in terms of the classical BV complex (Phil and I wrote this down in \cite[Section 3.1]{ElliottYoo1}).
+This is the $L_\infty$-algebra whose underlying cochain complex takes the form
 \[\xymatrix{

### 2019-03-01 10d_SYM_Notes.tex
Starting SUSY transformations in 10d

@@
 \subsection{On-Shell Supersymmetry Action}
+We can define an action of the 10d $\mc N=1$ supersymmetry algebra on the complex of BRST fields in this minimal super Yang-Mills theory.
+The Poincar\'e action is clear, and the action of the supersymmetry $Q$ is generated -- in the usual Physics notation -- by the transformation \cite{BrinkSchwarzScherk}
+\begin{align*}
+\delta_Q A &= \Gamma(Q,\lambda) \\
+\delta_Q \lambda &= \frac 14 \sd F_A Q,
+\end{align*}
+where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F^{ij} \gamma_i \gamma_j$.
+To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.
+So, we calculate
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] A &= \frac 14 (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
+&= \\
+\text{and } \delta_{Q_1}, \delta_{Q_2}] \lambda &= \frac 14 (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
+&= 
+\end{align*}
+
 %Failure to commute with the classical BV differential

### 2019-03-01 10d_SYM_Notes.tex
Starting SUSY transformations in 10d

@@
 \delta_Q A &= \Gamma(Q,\lambda) \\
-\delta_Q \lambda &= \frac 14 \sd F_A Q,
+\delta_Q \lambda &= \sd F_A Q,
 \end{align*}
-where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F^{ij} \gamma_i \gamma_j$.
+where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
 To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.
@@
 \begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] A &= \frac 14 (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
-&= \\
-\text{and } \delta_{Q_1}, \delta_{Q_2}] \lambda &= \frac 14 (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
+[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
+&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_1 \gamma^k \gamma^i \gamma^j Q_2)\\
+&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_2 \gamma^j \gamma^i \gamma^k Q_1)\\
+&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 - Q_2 \gamma^j \gamma^k \gamma^i Q_1)\\
+&=  F_{ij}\delta^{kj}(Q_2 \gamma^i Q_1) \\
+&= \delta_{[Q_1, Q_2]} A,
+\end{align*}
+where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric, i.e.
+$\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$, three times, and on the fourth and fifth lines we used the Clifford relations.
+Similarly we can calculate
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
 &= 

### 2019-03-01 10d_SYM_Notes.tex
Continuing 10d SUSY action description

@@
 \end{align*}
-where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric, i.e.
-$\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$, three times, and on the fourth and fifth lines we used the Clifford relations.
+where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e.
+that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- three times, and on the fourth and fifth lines we used the Clifford relations.
 Similarly we can calculate
@@
 [\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
+&= (Q_2 \gamma_j \dd_i \lambda + [Q_2\gamma_i \lambda, Q_2 \gamma_j \lambda]) (\gamma^i \gamma^j Q_1) - (1 \leftrightarrow 2) \\
 &= 
 \end{align*}
+
+\begin{remark}
+I'm part way through trying to do these calculations myself, but for reference I found these calculations in the master's thesis \cite{Guillen} we've discussed before.
+For instance for the commutator of two supersymmetries acting on a spinor see equation 2.1.13.
+\end{remark}
 

### 2019-03-04 10d_SYM_Notes.tex
Started notes on Baulieu's theory

@@
 \begin{remark}
-I'm part way through trying to do these calculations myself, but for reference I found these calculations in the master's thesis \cite{Guillen} we've discussed before.
+I'm part way through trying to do these calculations myself, but for reference I found these calculations discussed in the master's thesis \cite{Guillen} we've discussed before.
 For instance for the commutator of two supersymmetries acting on a spinor see equation 2.1.13.
@@
 \section{Baulieu's 10 Model}
+
+Baulieu \cite{Baulieu} considers an extension of 10d Super-Yang Mills including an auxiliary $\gg$-valued scalar field $h$.
+The inclusion of this field breaks the manifest $\SO(10)$ symmetry to the subgroup $\SU(5)$, corresponding to a choice of complex structure on $\RR^{10}$.
+Let's describe this classical theory in an explicitly $\SU(5)$-invariant way.
+With respect to this choice of complex structure $\CC^5$ becomes Calabi-Yau: we'll denote the holomorphic top-form by $\Omega$ and the map $\Omega^{p,q}(\CC^5) \to \Omega^{p-1,q-1}(\CC^5)$ induced from the K\"ahler structure by $J$.
+
+The ordinary fields $A$ and $\lambda$ of super Yang-Mills will decompose according to the decomposition of the vector and Weyl spinor representations of $\SO(10)$ into irreducible $\SU(5)$-representations.
+So, explicitly $A$ splits up into fields
+\[A_{1,0} + A_{0,1} \in \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,1}(\CC^5; \gg),\]
+and $\lambda$ splits up into fields
+\[\chi + \psi + B \in \Pi(\Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg)).\]
+In terms of these fields, and including the auxiliary field $h$, the action functional becomes
+\[S(A_{1,0}, A_{0,1}, \chi, \psi, B, h) = \int \langle (B \wedge \ol \dd_{A_{0,1}} B) + J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega \rangle.\]
+One derives this action functional by decomposing the 10d super Yang-Mills action functional into $\SU(5)$ irreducible component fields, then introducing a Lagrange multiplier $h$ to eliminate the $F_{1,1}^2$ term.
 %SU(5) BRST and BV Fields, Action Functional, BV Complex

### 2019-03-05 10d_SYM_Notes.tex
b edits

@@
 \author{Chris Elliott, Pavel Safronov and Brian Williams}
+
 \date{\today}
+
+\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
 
@@
 
+\brian{I realized I'm still confused with the role of Baulieu's $h$-field. 
+I really suspect it's different than the usual auxiliary field story. 
+It seems like Baulieu doesn't even write down the apparent off-shell SUSY module structure. 
+}
+\brian{I think without ever introducing an auxiliary field we can obtain the following module structure.}
+
+\def\oloc{\mathcal{O}_{loc}}
+
+Let $\oloc^{BRST}$ and $\oloc^{BV}$ be the local functionals for the BRST and BV fields, respectively. 
+The BRST operator endows $\oloc^{BRST}$ with the structure of a cochain complex, and the BV operator together with the BV bracket endow $\oloc^{BV}[-1]$ with the structure of a dg Lie algebra. 
+Note that there is a map of dg Lie algebras
+\[
+\oloc^{BV}[-1] \to {\rm End}(\oloc^{BRST})
+\]
+sending a functional $I$ to the endomorphism $\{I,-\}$.
+
+\def\cN{\mathcal{N}}
+
+The cursory definition of the linear map
+\[
+\mf g_{\cN=1} \to {\rm End}(\oloc^{BRST})
+\]
+is not a map of Lie algebras. 
+It fails to preserve the Lie bracket by a term proportional to the equations of motion in the field $\lambda$. 
+I claim that Baulieu's introduction of the $h$-field does not resolve this issue. (We can see this by counting fermion number. 
+The space where the failure for this to be a Lie map is $S_+$, yet we are only adding a scalar $h$ in the auxiliary, so there's no way.
+
+Instead, what one should try is the following. 
+(This doesn't ever use a holomorphic language, so maybe I'm making a silly mistake.)
+There is an obvious lift of the linear map $\mf g_{\cN=1} \to {\rm End}(\oloc^{BRST})$ to the BV complex
+\[
+\mf g_{\cN=1} \to \oloc^{BV} [-1] .
+\]
+%The prescription for defining this map is simple. 
+This is still, of course, not a map of dg Lie algebras.
+However, I claim that there is an $L_\infty$ correction to this map.
+
+Fix a basis $\{Q_\alpha\}$ of $S_+$ and write a general element of the form $Q_{\alpha} = \epsilon^\alpha Q_\alpha$.
+The putative, linear action, of the element $Q$ on the BV complex is through functionals of the form
+\[
+\int \epsilon \lambda^* \sd F_A 
+\]
+where $\lambda^*$ denotes the anti-field to $\lambda$. 
+I claim that we can correct the action by adding a quadratic term to the action that sends a pair $Q_1 \otimes Q_2$ to the functional
+\[
+\int \epsilon_1 \lambda^* \epsilon_2 \lambda^*  .
+\]
+
+In terms of an $L_\infty$ action, I'm saying that there is the usual linear map
+\[
+I^{(1)} : \mf g_{\cN=1} \to \oloc^{BV} 
+\]
+plus an $L_\infty$ correction of the form:
+\[
+I^{(2)} : \mf g_{\cN=1}^{\otimes 2} \to \oloc^{BV} [-2]  .
+\]
+You may ask why we have to stop there, but I don't have a great conceptual answer besides the computational fact that it seems like it works out. 
+I claim that $I^{(1)} + I^{(2)}$ determines an off-shell action of $\mf g_{\cN=1}$ on the BV complex.
+
+At the level of generators, we are proposing a new transformation law of the form 
+\begin{align*}
+\delta A &= \d c + \Gamma(\epsilon,\lambda) \\
+\delta \lambda &= [c,\lambda] + \epsilon \sd F_A  \pm \# \epsilon (\epsilon \lambda^*)  \\
+\delta \lambda^* &= \sd \partial \lambda + [c, \lambda^*] + \epsilon \sd A^*  .
+\end{align*}
+I've included terms coming from the BV operator (which have no $\epsilon$ dependence). 
+The only new term is the last one in the transformation law for $\lambda$, $\epsilon (\epsilon \lambda^*)$.
+
 \section{Homotopy Data}

### 2019-03-07 10d_SYM_Notes.tex
Response to Brian

@@
 
+\chris{
+I'm a little confused by a few things: can I ask for clarification?
+\begin{enumerate}
+ \item Firstly, while I understand the map $(I \mapsto \{I, -\}) \colon \oloc^{BV}[-1] \to {\rm End}(\oloc^{BV})$, I don't understand how it lifts to ${\rm End}(\oloc^{BRST})$.
+For instance (maybe a little heuristically, but I hope what I'm trying to say makes sense), let $\alpha$ be a scalar field and let $\alpha^*$ be its antifield.
+Let $I = (\alpha^*)^2$ in $\oloc^{BV}$.
+Then $\{(\alpha^*)^2, \alpha\} = 2\alpha^*$ is a non-trivial element of $\oloc^{BV}$ which is not in the image of $\oloc^{BRST}$, which says that my na\"ive guess for how to define your map doesn't work, so I must be supposed to do something more clever?
+ \item I wanted to clarify something about your ``counting fermion number'' argument.
+I thought that this argument only applied to the action of a whole supersymmetry algebra, not a single square zero supercharge.
+That is, if we're trying to construct off-shell BRST supersymmetry then the space of BRST fields should yield a representation of the supersymmetry algebra.
+Representations $V_0 \oplus V_1$ of the supersymmetry algebra have to have the same number of bosonic and fermionic degrees of freedom -- i.e.
+$\dim V_0 = \dim V_1$, because we can choose a supertranslation $Q$ which squares to a translation.
+So if $\alpha$ denotes the supersymmetry algebra action, the composite of $\alpha(Q)|_{V_0} \colon V_0 \to V_1$ and $\alpha(Q)|_{V_1} \colon V_1 \to V_0$ is equal to the action of a translation, which is an isomorphism, and therefore $\alpha(Q)$ must also be an isomorphism, so $\dim V_0 = \dim V_1$.
+However this argument doesn't apply anymore if you just want an action of a single square-zero odd symmetry.
+Maybe you have something else in mind though?
+ \item Could you include some of the calculation that the map you define at the end is an $L_\infty$ map?  This seems like it might be exactly what we're looking for.
+\end{enumerate}
+}
+
 \section{Homotopy Data}

### 2019-03-07 10d_SYM_Notes.tex
addressing Chris' comments

@@
 \newcommand{\sdel}{\slashed{\partial}}
+\newcommand{\cO}{\mathcal{O}}
 \newcommand{\sdelbar}{\overline{\slashed{\partial}}}
@@
 
-\addbibresource{Twist.bib}
+%\addbibresource{Twist.bib}
 
@@
 \date{\today}
-
-\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
 
@@
 sending a functional $I$ to the endomorphism $\{I,-\}$.
+\brian{No there is not.}
 
@@
 \]
-You may ask why we have to stop there, but I don't have a great conceptual answer besides the computational fact that it seems like it works out. 
+You may ask why we have to stop there, but I don't have a great conceptual answer besides the computational fact that it seems like it works out. o
 I claim that $I^{(1)} + I^{(2)}$ determines an off-shell action of $\mf g_{\cN=1}$ on the BV complex.
@@
 
+\brian{
+\begin{enumerate}
+\item I was being sloppy, and you are right. 
+Think of BRST as functions on $B \mf g$ and BV as functions on $T^* B\mf g$.
+Since vector fields include inside poly-vector fields there is a map of dg Lie algebras
+\[
+{\rm Der}(\cO(B \mf g)) = {\rm Vect}(B \mf g) \to \cO(T^* B \mf g) .
+\]
+So, really, the map should go the other way.
+I'll fix the above when I have more time, but basically what I'm saying is that even though we can't write down a Lie map to derivations of BRST, we can map one to the bigger BV complex.
+That's why the action looks like its by poly-vector fields, not just derivations. 
+\item
+I think I was also being sloppy here, and I don't see a way of making my argument precise. 
+I will try to find the reference (I think it may be Berkovits) where he says something to this effect. 
+\item
+OK, I wanted to see if you thought it was reasonable before including the details. 
+I'll work on writing that up now!
+\end{enumerate}
+}
+
 \section{Homotopy Data}
@@
 
-\pagestyle{bib}
-\printbibliography
+%\pagestyle{bib}
+%\printbibliography
 

### 2019-03-20 10d_SYM_Notes.tex
Computations in the abelian case
Added comments on Baulieu's scalar supersymmetry

@@
 
-%\addbibresource{Twist.bib}
+\newcommand{\brian}[1]{\textcolor{blue}{BW: #1}}
+
+\addbibresource{Twist.bib}
 
@@
 
-\section{Baulieu's 10 Model}
-
-Baulieu \cite{Baulieu} considers an extension of 10d Super-Yang Mills including an auxiliary $\gg$-valued scalar field $h$.
-The inclusion of this field breaks the manifest $\SO(10)$ symmetry to the subgroup $\SU(5)$, corresponding to a choice of complex structure on $\RR^{10}$.
-Let's describe this classical theory in an explicitly $\SU(5)$-invariant way.
-With respect to this choice of complex structure $\CC^5$ becomes Calabi-Yau: we'll denote the holomorphic top-form by $\Omega$ and the map $\Omega^{p,q}(\CC^5) \to \Omega^{p-1,q-1}(\CC^5)$ induced from the K\"ahler structure by $J$.
-
-The ordinary fields $A$ and $\lambda$ of super Yang-Mills will decompose according to the decomposition of the vector and Weyl spinor representations of $\SO(10)$ into irreducible $\SU(5)$-representations.
-So, explicitly $A$ splits up into fields
-\[A_{1,0} + A_{0,1} \in \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,1}(\CC^5; \gg),\]
-and $\lambda$ splits up into fields
-\[\chi + \psi + B \in \Pi(\Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg)).\]
-In terms of these fields, and including the auxiliary field $h$, the action functional becomes
-\[S(A_{1,0}, A_{0,1}, \chi, \psi, B, h) = \int \langle (B \wedge \ol \dd_{A_{0,1}} B) + J^2(F_{2, 0}\wedge F_{0,2})\Omega + \|h\|^2\Omega + h J(F_{1,1}) \Omega + J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega + J^2(B \wedge (\dd_{A_{1,0}} \psi)) \Omega \rangle.\]
-One derives this action functional by decomposing the 10d super Yang-Mills action functional into $\SU(5)$ irreducible component fields, then introducing a Lagrange multiplier $h$ to eliminate the $F_{1,1}^2$ term.
-%SU(5) BRST and BV Fields, Action Functional, BV Complex
-
-\subsection{Off-Shell Action of a Scalar Supersymmetry}
-%Does it do anything interesting to the anti-fields?
-
+\subsection{An Off-Shell Supersymmetry Action?}
 \brian{I realized I'm still confused with the role of Baulieu's $h$-field. 
@@
 
+\subsubsection{Abelian case}
+
+The BV differential is
+\begin{align*}
+\delta_{BV} c &= 0 \\
+\delta_{BV} A &= \d c \\
+\delta_{BV} \lambda &= 0 \\
+\delta_{BV} \lambda^* &= \sd D_A \lambda \\
+\delta_{BV} A^* &= \d\ast F \\
+\delta_{BV} c^* &= \d A^*
+\end{align*}
+
+\[I^{(1)} = \int (\lambda^*, \sd F \epsilon) + \int A^* \Gamma(\epsilon, \lambda)\]
+
+\[\delta_{BV} I^{(1)} = \int (\sd D_A\lambda, \sd F\epsilon) + \int (\d\ast F) \Gamma(\epsilon, \lambda).\]
+\section{Baulieu's 10 Model}
+
+Baulieu \cite{Baulieu} considers an extension of 10d Super-Yang Mills including an auxiliary $\gg$-valued scalar field $h$.
+The inclusion of this field breaks the manifest $\SO(10)$ symmetry to the subgroup $\SU(5)$, corresponding to a choice of complex structure on $\RR^{10}$.
+Let's describe this classical theory in an explicitly $\SU(5)$-invariant way.
+With respect to this choice of complex structure $\CC^5$ becomes Calabi-Yau: we'll denote the holomorphic top-form by $\Omega$ and the map $\Omega^{p,q}(\CC^5) \to \Omega^{p-1,q-1}(\CC^5)$ induced from the K\"ahler structure by $J$.
+
+The ordinary fields $A$ and $\lambda$ of super Yang-Mills will decompose according to the decomposition of the vector and Weyl spinor representations of $\SO(10)$ into irreducible $\SU(5)$-representations.
+So, explicitly $A$ splits up into fields
+\[A_{1,0} + A_{0,1} \in \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,1}(\CC^5; \gg),\]
+and $\lambda$ splits up into fields
+\[\chi + \psi + B \in \Pi(\Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg)).\]
+In terms of these fields, and including the auxiliary field $h$, the action functional becomes
+\[S(A_{1,0}, A_{0,1}, \chi, \psi, B, h) = \int \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle.\]
+One derives this action functional by decomposing the 10d super Yang-Mills action functional into $\SU(5)$ irreducible component fields, then introducing a Lagrange multiplier $h$ to eliminate the $F_{1,1}^2$ term.
+%SU(5) BRST and BV Fields, Action Functional, BV Complex
+
+\subsection{Off-Shell Action of a Scalar Supersymmetry}
+
+Consider the following square-zero supersymmetry acting on Baulieu's theory:
+\begin{align*}
+\delta A_{1,0} &= \psi \\
+\delta \chi &= h \\
+\delta B &= F_{0,2} \\
+\end{align*}
+acting trivially on all other (BRST) fields.
+This clearly squares to zero, so defines an action of the supergroup $\Pi \CC$ on the BRST complex.
+We can calculate the variation of the action functional with respect to this symmetry, and see that it vanishes.
+Indeed,
+\begin{align*}
+\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
+&= \int \langle J^2(\dd_{A_{1,0}} B \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge (\dd_{A_{1,0}} \psi) - 0) \Omega \rangle \\
+&= 0.
+\end{align*}
+This should mean that the $\Pi \CC$ action is off-shell, so extends to an action on the full BV complex (the above calculation should be equivalent to showing that $\delta$ commutes with the BV differential).
+
 \section{Homotopy Data}
@@
 
-%\pagestyle{bib}
-%\printbibliography
+\pagestyle{bib}
+\printbibliography
 

### 2019-03-21 10d_SYM_Notes.tex
Added comments on Baulieu's scalar supersymmetry
added a remark on scalar SUSY without h

@@
 \delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega - \frac 12 \|h\|^2\Omega + h J(F_{1,1}) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
-&= \int \langle J^2(\dd_{A_{1,0}} B \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge (\dd_{A_{1,0}} \psi) - 0) \Omega \rangle \\
+&= \int \langle J^2(\dd_{A_{1,0}} \psi \wedge F_{0,2})\Omega - 0 + h J(\ol \dd_{A_{0,1}} \psi) \Omega - J( h (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge \dd_{A_{1,0}} \psi)\Omega - 0\rangle \\
 &= 0.
@@
 This should mean that the $\Pi \CC$ action is off-shell, so extends to an action on the full BV complex (the above calculation should be equivalent to showing that $\delta$ commutes with the BV differential).
+
+Let me also explicitly show that the BV action functional is also invariant for this square-zero supersymmetry.  So we also include the dual action
+\begin{align*}
+\delta \psi^* &= A_{1,0}^* \\
+\delta h^* &= \chi^* \\
+\delta A_{0,1}^* &= \ol \dd_{A_{0,1}} B^*.
+\end{align*}
+The variation of the part of the BV action functional involving the anti-fields is then calculated to vanish as follows.
+\begin{align*}
+&\!\!\! \delta S_{\mr{anti}} = \\
+&= \int \delta \left(c^* \wedge [c, c] + {A^*_{1, 0}}\wedge (\partial c + [c,A_{1,0}]) + {A^*_{0, 1}}\wedge (\ol \dd c + [c, A_{0, 1}]) - B^*\wedge [c, B] - \chi^*\wedge [c, \chi] - \psi^*\wedge [c, \psi] \right) + h^* \wedge [c,h] \\
+&= \int 0 +A^*_{1,0} \wedge [c,\psi] + \ol \dd_{A_{0,1}} B^* \wedge [c,A_{0,1}] - B^* \wedge [c,F_{0,2}] - \chi^* \wedge [c,h] - A_{1,0}^* \wedge [c,\psi] + \chi^* \wedge [c,h] \\
+&= 0.
+\end{align*}
+
+\begin{remark}
+If we don't adjoin the auxiliary field $h$, but do break the $\spin(10)$ symmetry down to $\SU(5)$ and consider the scalar supersymmetry with respect to the on-shell action from the previous section, then the BRST action is still preserved.
+The supersymmetries are as above, except that now $\delta \chi = JF_{1,1)}$.
+We have, very similarly to the calculation above,
+\begin{align*}
+\delta S &= \int \delta \langle J^2(F_{2, 0}\wedge F_{0,2})\Omega + J^2(F_{1,1}^2) \Omega - J( \chi \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(B \wedge (\dd_{A_{1,0}} \psi) - (B \wedge \ol \dd_{A_{0,1}} B)) \Omega \rangle \\
+&= \int \langle J^2(\dd_{A_{1,0}} \psi \wedge F_{0,2})\Omega - 0 + J^2(F_{1,1} \wedge \ol \dd_{A_{0,1}} \psi) \Omega - J^2( F_{1,1} \wedge (\ol \dd_{A_{0,1}} \psi)) \Omega - J^2(F_{0,2} \wedge \dd_{A_{1,0}} \psi)\Omega - 0 \rangle \\
+&= 0.
+\end{align*}
+\chris{Actually maybe this doesn't quite work, because of a factor of two.
+We had $\delta(hJF_{1,1}) = hJ(\ol \dd \psi)$, whereas $\delta(J^2F_{1,1}^2) = 2 J^2(F_{1,1} \wedge \ol \dd \psi)$, and that extra 2 seems to break the cancellation.}
+
+On the other hand, if try to extend this to the BV fields, we must have $\delta A^*_{1,0} = 0$ so that $\delta^2 = 0$, so we would need to modify $\delta A^*_{0,1}$ to include some term cancelling the term $\delta(\chi^*\wedge [c, \chi]) = \chi^* \wedge [c, JF_{1,1}]$, but without introducing a new term $\delta(A_{0,1}^* \wedge \ol \dd c)$.
+This na\"ively doesn't look like it's possible.
+
+\end{remark}
 

### 2019-03-22 10d_SYM_Notes.tex
U(5)-invariant SUSY

@@
 
-\newcommand{\map}{\ul{\mr{Map}}}
+\newcommand{\C}{\mathbf{C}}
 \newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
@@
 \newcommand{\sdel}{\slashed{\partial}}
+\newcommand{\map}{\ul{\mr{Map}}}
 \newcommand{\cO}{\mathcal{O}}
@@
 \end{remark}
+
+\subsection{$U(5)$-invariant splitting}
+
+Pick a reduction of the structure group to $U(5)\subset SO(10)$.
+This splits the defining representation as $\C^{10} = L\oplus L^*$ giving a decomposition $A = A_{0, 1} + A_{1, 0}$.
+Therefore, $\wedge^2 \C^{10} \cong \wedge^2 L \oplus \End(L) \oplus \wedge^2 L^*$ which gives a decomposition $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$.
+We denote by $J\colon \End(L)\rightarrow \C$ the trace.
+The semi-spin representation splits as $S_+ = (\C\oplus \wedge^2 L\oplus \wedge^4 L)\otimes \det(L)^{-1/2}$ giving a decomposition $\lambda = \chi + B + \psi$.
+
+If $Q\in S_+$ is the scalar supercharge, the supersymmetry transformations become
+\begin{align*}
+\delta_Q A_{1, 0} &= Q\psi \\
+\delta_Q B &= Q F_{0, 2} \\
+\delta_Q \chi &= -\frac{1}{2}Q J(F_{1, 1}).
+\end{align*}
+Note that $\delta_Q^2 \chi = -\frac{1}{2} J(\overline{\partial}_{A_{0, 1}} \psi)$ and zero on other fields.
 

### 2019-03-24 10d_SYM_Notes.tex
SUSY invariance of 10d SYM

--- 2019-03-21 10d_SYM_Notes.tex
@@
 \newcommand{\sdel}{\slashed{\partial}}
+\newcommand{\map}{\ul{\mr{Map}}}
 \newcommand{\cO}{\mathcal{O}}
+\newcommand{\R}{\mathbf{R}}
 \newcommand{\sdelbar}{\overline{\slashed{\partial}}}
@@
 The action functional in 10d super Yang-Mills is given by
-\[S(A,\lambda) = \int_{\RR^{10}} \langle F_A \wedge \ast F_A + (\lambda, \sd D_A \lambda)\rangle,\]
+\[S(A,\lambda) = \int_{\RR^{10}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
 where $\langle - \rangle$ denotes an invariant pairing on $\gg$, and $(,)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).
@@
 
-%Failure to commute with the classical BV differential
+\subsection{$SU(5)$-invariant splitting}
+
+We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
+
+\begin{prop}
+Let $M$ be a K\"{a}hler $d$-fold and decompose
+\[\Omega^2(M; \C) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\C\omega\oplus \Omega^{1, 1}_\perp(M)).\]
+Then
+\begin{enumerate}
+\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\C\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.
+
+\item For $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
+\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
+\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in\C\omega$ we have
+\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
+\end{enumerate}
+\end{prop}
+
+\begin{corollary}
+Let $M$ be a K\"{a}hler $d$-fold. Then
+\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
+\end{corollary}
+
+Pick a reduction of the structure group to $SU(5)\subset SO(10)$.
+This gives rise to a K\"{a}hler structure $\omega$ on $\R^{10}$ and a nonvanishing holomorphic 5-form $\Omega$.
+We denote by $\Lambda\colon \Omega^k(M)\rightarrow \Omega^{k-2}(M)$ the dual Lefschetz operator defined by $(\Lambda \alpha, \beta) = (\alpha, \beta\wedge \omega)$.
+
+The connection splits as $A = A_{0, 1} + A_{1, 0}$. The semi-spin representation decomposes as
+\[S_+ \cong \C\oplus \Omega^{0, 2} \oplus \Omega^{1, 0},\]
+which gives rise to a decomposition $\lambda = \chi + B + \psi$.
+
+If $Q\in S_+$ is the scalar supercharge, the supersymmetry transformations become
+\begin{align*}
+\delta_Q A_{1, 0} &= \psi \\
+\delta_Q B &= F_{0, 2} \\
+\delta_Q \chi &= \frac{1}{2} \Lambda F_{1, 1}.
+\end{align*}
+Note that $\delta_Q^2 \chi = \frac{1}{2} \Lambda(\overline{\partial} \psi)$ and zero on other fields.
+
+Let
+\[S_{top} = \frac{1}{12}\int F\wedge F\wedge \omega^3\]
+be the instanton number. Then we get
+\[
+S + S_{top} = \int \frac{\omega^5}{5!}\left(2(F_{2, 0}, F_{0, 2}) + \frac{1}{2} (\Lambda F_{1, 1})^2 - 2\Lambda(\overline{\partial}\psi) \chi - 2(B, \partial \psi)\right) - B\wedge \overline{\partial} B\wedge \Omega
+\]
+
+We then have
+\[\delta_Q(S+S_{top}) = \int \frac{\omega^5}{5!}\left(2(F_{0, 2}, \partial \psi) + \Lambda F_{1, 1} \Lambda(\overline{\partial}\psi) - \Lambda F_{1, 1} \Lambda(\overline{\partial}\psi) - 2(F_{0, 2}, \partial \psi)\right) = 0.
+\]
+
+Note that $\delta_Q S_{top} = 0$ (it is a topological invariant).
+Therefore, $\delta_Q S = 0$.
+We have checked it for a pure spinor supercharge.
+The span of pure spinors in $S_+$ is an $SO(10)$-subrepresentation which by irreducibility has to be everything.
+Thus, any spinor is a linear combination of pure spinors and so $\delta_Q S = 0$ for any supercharge $Q$.
 

### 2019-03-29 10d_SYM_Notes.tex
On-shell Lie action calculation

@@
 where the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
-To check that this defines a supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra.
+To check that this defines an on-shell supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra, up to terms in the ideal generated by the equations of motion.
 So, we calculate
@@
 that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- three times, and on the fourth and fifth lines we used the Clifford relations.
-Similarly we can calculate
+Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.
+Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
 \begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 - \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
-&= (Q_2 \gamma_j \dd_i \lambda + [Q_2\gamma_i \lambda, Q_2 \gamma_j \lambda]) (\gamma^i \gamma^j Q_1) - (1 \leftrightarrow 2) \\
-&= 
+[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
+&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
+&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
+&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
+&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
+&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
 \end{align*}
+using the fact that 
+\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
+as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
+&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
+\end{align*}
+In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
 
 \begin{remark}
-I'm part way through trying to do these calculations myself, but for reference I found these calculations discussed in the master's thesis \cite{Guillen} we've discussed before.
-For instance for the commutator of two supersymmetries acting on a spinor see equation 2.1.13.
+This suggests a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.
+Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
+\begin{align*}
+\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
+Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
+\end{align*}
 \end{remark}

### 2019-03-30 10d_SYM_Notes.tex

@@
 \begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) - \Gamma(Q_1,\sd F_A Q_2)) \\
-&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_1 \gamma^k \gamma^i \gamma^j Q_2)\\
-&=  F_{ij}(Q_2 \gamma^k \gamma^i \gamma^j Q_1 - Q_2 \gamma^j \gamma^i \gamma^k Q_1)\\
-&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 - Q_2 \gamma^j \gamma^k \gamma^i Q_1)\\
-&=  F_{ij}\delta^{kj}(Q_2 \gamma^i Q_1) \\
+[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
+&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
+&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
+&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
+&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
 &= \delta_{[Q_1, Q_2]} A,
@@
 where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e.
-that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- three times, and on the fourth and fifth lines we used the Clifford relations.
+that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.
 Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.

### 2019-04-08 10d_SYM_Notes.tex
small edits

@@
 \newcommand{\st}[1]{{}^*{#1}}
-
-\newcommand{\brian}[1]{\textcolor{blue}{BW: #1}}
+\newcommand{\clie}{{\rm C}_{\rm Lie}}
+\def\cN{\mathcal{N}}
 
@@
 \Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
-&\Omega^0(\RR^{10}; \Pi S_- \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
+&\Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S_- \otimes \gg), &
 }\]
+\brian{I've changed the spinor component in degree zero to $S_+$, check if that's OK.}
 with degree $-3$ invariant pairing induced by the invariant pairing on $\gg$ and the pairing $(,)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
@@
 \end{remark}
+
+\subsection{Off-shell supersymmetry action}
+
+The goal is to show that the maps
+\begin{align*}
+\delta^{(1)}_+ \colon S_+ \otimes \left( \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \right) &\to \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \\
+Q \otimes (A + \lambda) &\mapsto  \Gamma(Q,\lambda) + \sd F_A Q .
+\end{align*}
+\begin{align*}
+\delta^{(2)}_+ \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_+) &\to \Gamma(\RR^{10}; \Pi S_-' [-1]) \\
+Q_1 \otimes Q_2 \otimes \lambda &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
+\end{align*}
+define an $L_\infty$-action of the supersymmetry algebra on the BV complex.
+
+The BV action involving the component $\Pi S_+$ of the supersymmetry algebra reads
+\begin{align*}
+I_+^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = A^* \wedge \Gamma(Q, \lambda) + (\lambda^*, \sd F_A Q) \\
+I_+^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left(\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right) .
+\end{align*}
+
+\brian{Part of BV action involving the bosonic translations}
+
+It suffices to show that the Maurer-Cartan equation for the functional $I^{(1)}_+ + I^{(2)}_+$ holds:
+\[
+(\d_{CE} + \d_{BV}) \left(I_+^{(1)} + I_+^{(2)}\right) + \frac{1}{2} \left\{I_+^{(1)} + I_+^{(2)}, I_+^{(1)} + I_+^{(2)} \right\} = 0 .
+\]
+The space of equivariant BV functionals $\clie^*(\mf g_{\cN=1}) \otimes \cO_{BV}$ is filtered by the number of anti-field components. 
+With respect to this filtration,  this Maurer-Cartan equation splits into four equations:
+\begin{enumerate}
+\item[(1)] $\d_{BV} I^{(1)} = 0$ ;
+\item[(2)] $\d_{CE} I^{(1)}_+ + \d_{BV} I^{(2)}_+ + \frac{1}{2}  \left\{I_+^{(1)} , I_+^{(1)} \right\} = 0$ ;
+\item[(3)] $\d_{CE} I^{(2)}_+ + \{I^{(1)}_+, I^{(2)}_+\} = 0$ ;
+\item[(4)] $\{I^{(2)}_+ , I^{(2)}_+ \} = 0$.
+\end{enumerate}
+
+Equation (1) follows from \brian{p. 14 in \cite{BaezHuerta}}.
+
+Equation (2). \brian{this will entail adding a few sentences after Chris' calculation above.}
+
+Equation (3).
+Note that $\d_{CE} I^{(2)}_+ = 0$ since the term $I^{(2)}_+$ is quadratic in the term $\Pi S_+ \subset \mf g_{\cN =1}$ and there are no brackets that land in the odd component of supersymmetry algebra.
+The second term $\{I^{(1)}_+, I^{(2)}_+\}$ splits into two terms.
+The first is a functional of the form \brian{keeping with Pavel's notation from the email, the $\Gamma_{\pm}$ and $\rho_{\pm}$ tell you which spinor your acting on}
+\[
+(Q_1, Q_2, Q_3 ; A^*, \lambda^*) \mapsto A^* \wedge \Gamma_+(Q_1, \rho_- (\Gamma_+(Q_2, Q_3)) \lambda^*) + (123)
+\] 
+and the second is
+\[
+(Q_1, Q_2, Q_3 ; A^*, \lambda^*) \mapsto (\lambda^*, Q_1) (A^* \wedge \Gamma_+(Q_2, Q_3)) + (123) .
+\]
+
+\begin{lemma}
+For any $\psi_+ \in S_+$, $\psi_- \in S_-$, and $v \in V$, the following relation holds
+\[
+\Gamma_+(\psi_+, \rho_-(v) \psi_-) + \Gamma_-(\psi_-, \rho_+(v) \psi_+) = (\psi_-, \psi_+) v
+\]
+\end{lemma}
+\begin{proof}
+We will prove that for any $w \in V$ the following relation holds
+\[
+g\left(w, \Gamma_+(\psi_+, \rho_-(v) \psi_-) + \Gamma_-(\psi_-, \rho_+(v) \psi_+) \right) = (\psi_-, \psi_+) g(w,v)
+\]
+where $g$ is the fixed metric on $V$. 
+Since \brian{Something about adjointness of $\Gamma$ and $\rho$} the left hand side is equal to
+\[
+\left(\rho(w) (\psi_+ + \psi_-), \rho(v) (\psi_+ + \psi_-) \right) .
+\]
+Now the pairing $(-,-) : S_{\pm} \otimes S_{\mp} \to \CC$ is equivariant with respect Clifford multiplication, so this is expression is equal to $g(w,v) (\psi_-, \psi_+)$ as desired.
+Since this is true for all $w \in V$, the claim follows. 
+\end{proof}
 
@@
 \brian{No there is not.}
-
-\def\cN{\mathcal{N}}
 

### 2019-04-14 supermultiplets.tex
Classification of supermultiplets

\documentclass[12pt]{amsart}

\usepackage{eucal}
\usepackage{amssymb}
\usepackage{stmaryrd}

\usepackage{color}
\definecolor{e-mail}{rgb}{0,.40,.80}
\definecolor{reference}{rgb}{.20,.60,.22}
\definecolor{citation}{rgb}{0,.40,.80}

\usepackage[colorlinks=true,
            linkcolor=reference,
            citecolor=citation,
            urlcolor=e-mail]{hyperref}
\usepackage{cleveref}
\usepackage[all]{xy}

\textwidth=16.5cm
\oddsidemargin=0cm
\evensidemargin=0cm
\textheight=22cm
\topmargin=0cm

\binoppenalty=10000
\relpenalty=10000

\newcommand{\C}{\mathbf{C}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\Z}{\mathbf{Z}}

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Spin}{\mathrm{Spin}}
\newcommand{\Sym}{\mathrm{Sym}}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lm}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{example}[thm]{Example}

\begin{document}
\title{Classification of massless supermultiplets}
\maketitle

\section{}

Let $V$ be a complex vector space with a chosen spin structure. Let $\Sigma$ be a spinorial representation of $\Spin(V)$, $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ the associated vector-valued pairing and $T_\Sigma$ the supertranslation group with Lie algebra $\Pi\Sigma\oplus V$. The superPoincar\'{e} group is $\Spin(V)\ltimes T_\Sigma$.

Recall that massless representations of the Poincar\'{e} group are parametrized in the following way. Split $V = V_0\oplus \C e_+\oplus \C e_-$, where $e_+$ and $e_-$ are null vectors with $(e_+, e_-) = 1$. Then massless representations correspond to finite-dimensional representations of $\Spin(V_0)$.

\begin{remark}
We ignore the continuous-spin representations. Alternatively, we only consider finite-dimensional representations of the little group.
\end{remark}

We label irreducible representations of $\Spin(2)$ by \defterm{helicity} which is a half-integer number.

\begin{defn}
Suppose $\dim(V_0)\geq 2$. A representation $\rho$ of $\Spin(V_0)$ is \defterm{admissible} if for some (equivalently, any) nondegenerate subspace $\C^2\subset V_0$ the helicities appearing in $\rho$ are at most $1$ by absolute value.
\end{defn}

In a similar way, massless representations of the superPoincar\'{e} group are parametrized as follows (see \cite[Lecture 6]{Freed} for details). Consider a quadratic form on $\Sigma$ defined by $q(Q, Q) = (e_+, \Gamma(Q, Q))$ for $Q\in \Sigma$. Let $\Sigma_0$ be the radical of $q$ and $\overline{\Sigma} = \Sigma / \Sigma_0$. Let $\Cl(\overline{\Sigma}, q)$ be the associated Clifford algebra. Then massless representations correspond to finite-dimensional representations of $\Cl(\overline{\Sigma}, q)$ with a compatible action of $\Spin(V_0)$.

\subsection{$d=3$}

We have $\Spin(1)\cong \Z/2$. We denote its irreducible representations by $\C$ and $S$ which correspond to the massless scalar and massless spinor.

The spinorial representation is
\[\Sigma = (S\oplus S)\otimes W,\]
where $W$ carries a nondegenerate symmetric bilinear form. We have
\[\overline{\Sigma} = S\otimes W.\]

There is a unique supermultiplet which contains $\dim(W)$ scalars and $\dim(W)$ spinors.

\subsection{$d=4$}

The admissible irreducible representations of $\Spin(2)$ are the trivial one-dimensional representation $\C$, the semi-spin representations $S_{\pm}$ of helicity $\pm\frac{1}{2}$ and the half-vector representations $V_{\pm}$ of helicity $\pm 1$.

The spinorial representation is
\[\Sigma = (S_+\oplus S_-)\otimes W\oplus (S_+\oplus S_-)\otimes W^*\]
for a complex vector space $W$.

The radical is $\Sigma_0 = S_+\otimes W\oplus S_-\otimes W^*$, so
\[\overline{\Sigma} = S_-\otimes W\oplus S_+\otimes W^*\]
with $q$ the obvious quadratic form. In particular, it contains a Lagrangian subspace $S_+\otimes W^*$, so irreducible massless representations of the superPoincar\'{e} group are parametrized by irreducible $\Spin(2)$-representations $\C_h$ labeled by a half-integer $h$, so that the corresponding representation of the little group is
\[\C_h\otimes \wedge^\bullet(S_+\otimes W^*).\]

This representation is admissible if $-1\leq h\leq 1$ and $h+\cN/2\leq 1$. In particular, we must have $\cN\leq 4$.

In this dimension we have to make sure our representations are CPT invariant. We will only deal with PT invariance. This corresponds to extending $\Spin(2)$ to $\Z/2\ltimes \Spin(2)$, where $\Z/2$ acts on $\Spin(2)$ by inversion.

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=1$. Chiral multiplet $\C^{\oplus 2}\oplus S_+\oplus S_-$ and the $\cN=1$ vector multiplet $S_+\oplus S_-\oplus V_+\oplus V_-$.

\item $\cN=2$. Half-hypermultiplet (aka $\cN=1$ chiral multiplet) and an $\cN=2$ vector multiplet $\C^{\oplus 2}\oplus (S_+\oplus S_-)^{\oplus 2}\oplus V_+\oplus V_-$.

\item $\cN=4, \cN=3$. $\cN=4$ vector multiplet $\C^{\oplus 6}\oplus (S_+\oplus S_-)^{\oplus 4}\oplus V_+\oplus V_-$.
\end{itemize}

\subsection{$d=5$}

The admissible irreducible representations of $\Spin(3)$ are the trivial one-dimensional representation $\C$, the spin representation $S$ and the vector representation $V_3$.

The spinorial representation is
\[\Sigma = (S\oplus S)\otimes W,\]
where $W$ is a complex symplectic vector space. The radical is
\[\Sigma_0 = S\otimes W\]
(say, the first summand), so
\[\overline{\Sigma} = S\otimes W.\]

The quadratic form is given by the product of the symplectic structure on $W$ and the symplectic structure on $S$. Choose a Lagrangian subspace $L\subset W$. Then the masless irreducible representations of the superPoincar\'{e} group are parametrized by irreducible representations $M$ of $\Spin(3)$ so that the corresponding representation of the little group is
\[M\otimes \wedge^\bullet(S\otimes L).\]

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=1$. The chiral multiplet (aka half-hypermultiplet) $\C^{\oplus 2}\oplus S$ and the $\cN=1$ vector multiplet $\C\oplus S^{\oplus 2}\oplus V_3$.

\item $\cN=2$. $\cN=2$ vector multiplet $\C^{\oplus 5}\oplus S^{\oplus 4}\oplus V_3$.
\end{itemize}

\subsection{$d=6$}

The admissible irreducible representations of $\Spin(4)$ are the trivial one-dimensional representation $\C$, the semi-spin representations $S_{\pm}$, the vector representation $V_4$ and the (anti) self-dual form representations $\Sym^2(S_{\pm})$. Note that we have a decomposition
\[\wedge^2 V_4\cong \Sym^2(S_+)\oplus \Sym^2(S_-).\]

The spinorial representation is
\[\Sigma = (S_+\oplus S_-)\otimes W_+\oplus (S_+\oplus S_-)\otimes W_-,\]
where $W_\pm$ are symplectic vector spaces.

We have
\[\overline{\Sigma} = S_-\otimes W_+\oplus S_+\otimes W_-\]
with the quadratic form being the product of the symplectic form on $S_-$, $S_+$ and $W_{\pm}$. Pick Lagrangians $L_{\pm}\subset W_{\pm}$. Then the massless irreducile reprsentations of the superPoincar\'{e} group are parametrized by an irreducible $\Spin(4)$-representation $M$, so that the corresponding representation of the little group is
\[M\otimes \wedge^\bullet(S_-\otimes L_+\oplus S_+\otimes L_-).\]

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=(1, 0)$. The chiral multiplet (aka half-hypermultiplet) $\C^2\oplus S_-$, the tensor multiplet $\C\oplus S_-^{\oplus 2}\oplus \Sym^2(S_-)$ and the $\cN=(1, 0)$ vector multiplet $S_+^{\oplus 2}\oplus V_4$.

\item $\cN=(1, 1)$. The $\cN=(1, 1)$ vector multiplet $\C^{\oplus 4}\oplus (S_+\oplus S_-)^{\oplus 2}\oplus V_4$.

\item $\cN=(2, 0)$. The $\cN=(2, 0)$ tensor multiplet $\C^{\oplus 5}\oplus S_-^{\oplus 4}\oplus \Sym^2(S_-)$.
\end{itemize}

\subsection{$d=7$}

The only irreducible admissible representations of $\Spin(5)$ are the trivial one-dimensional representation $\C$, the 4d spin representation $S$ and the 5d vector representation $V_5$.

The spinorial representation is
\[\Sigma = (S\oplus S)\otimes W,\]
where $W$ is a symplectic vector space. We have
\[\overline{\Sigma} = S\otimes W\]
with the quadratic form the product of the symplectic structure on $S$ and the symplectic structure on $W$. Pick a Lagrangian subspace $L\subset W$. Then the irreducible representation of the little group is
\[M\otimes \wedge^\bullet(S\otimes L),\]
where $M$ is an irreducible representation of $\Spin(5)$.

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=1$. The vector multiplet $\C^{\oplus 3}\oplus S^{\oplus 2}\oplus V_5$.
\end{itemize}

\subsection{$d=8$}

The only irreducible admissible representations of $\Spin(6)$ are the trivial one-dmensional representation $\C$, the 4d semi-spin representations $S_{\pm}$ and the 6d vector representation $V_6$. The spinorial representation is
\[\Sigma=(S_+\oplus S_-)\otimes (W\oplus W^*)\]
for a complex vector space $W$. We have
\[\overline{\Sigma} = S_+\otimes W\oplus S_-\otimes W^*\]
with the quadratic form given by a pairing $S_+\otimes S_-\rightarrow \C$. Then the irreducible representation of the little group is
\[M\otimes \wedge^\bullet(S_+\otimes W),\]
where $M$ is an irreducible representation of $\Spin(6)$.

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=1$. The vector multiplet $\C^{\oplus 2}\oplus S_+\oplus S_-\oplus V_6$.
\end{itemize}

\subsection{$d=9$}

The only admissible irreducible representations of $\Spin(7)$ are the trivial one-dimensional representation $\C$, the 8d spin representation $S$ and the 7d vector representation $V_7$. The spinorial representation is
\[\Sigma = (S\oplus S)\otimes W,\]
where $W$ carries a nondegenerate symmetric bilinear form. We have
\[\overline{\Sigma} = S\otimes W.\]

Note that in the case $\dim(W)$ odd there is no $\Spin(7)$-invariant Lagrangian subspace in $\overline{\Sigma}$.

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=1$. The vector multiplet $\C\oplus S\oplus V$.
\end{itemize}

\subsection{$d=10$}

The only admissible irreducible representations of $\Spin(8)$ are the trivial one-dimensional representation $\C$, the semi-spin representations $S_{\pm}$ and the 8d vector representation $V_8$. The spinorial representation is
\[\Sigma = (S_+\oplus S_-)\otimes W_+\oplus (S_+\oplus S_-)\otimes W_-,\]
where $W_{\pm}$ carry nondegenerate symmetric bilinear forms. We have
\[\overline{\Sigma} = S_-\otimes W_+\oplus S_+\otimes W_-.\]

The list of admissible supermultiplets:
\begin{itemize}
\item $\cN=(1, 0)$. The vector multiplet $S_-\oplus V$.
\end{itemize}

\begin{thebibliography}{Freed}
\bibitem[Freed]{Freed} D. Freed, Classical field theory and supersymmetry, \url{https://web.ma.utexas.edu/users/dafr/pcmi.pdf}.
\end{thebibliography}

\end{document}

### 2019-04-14 paper.tex
Outline of the paper

\documentclass[10pt, oneside]{article}

\input ./math_headers.sty

\addbibresource{Twist.bib}

\title{Twists of supersymmetric gauge theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\section{Introduction}

\section{Preliminaries}

\subsection{Shifted symplectic manifolds}

% Define QP manifolds (Z x Z/2-graded, Q doesn't have to be Hamiltonian)
% Tangent complex of a QP manifold at a classical solution forms a cyclic L_infinity algebra
% equivalence of QP manifolds

\subsection{Models of field theories}

% field theories defined in terms of vector bundles on spacetime
% explain how to obtain a QP manifold
% explain how to obtain a factorization algebra given a classical solution

\subsection{Supersymmetry}

% spinorial representations, supertranslation groups, superPoincar\'{e} groups
% list possible massless supermultiplets in dimensions [4, 10] with <= 16 supercharges
% explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)

\subsection{Supersymmetric twisting}

% twisting of field theories
% twisting homomorphisms
% list all possible twists in dimensions [2, 10] with <= 16 supercharges

\section{Twists}

\subsection{Dimension 10}

% \cN=(1, 0) SYM
% Construct the L_infinity action of supersymmetry

\subsection{Dimension 9}

% \cN=1 SYM

\subsection{Dimension 8}

% \cN=1 SYM

\subsection{Dimension 7}

% \cN=1 SYM

\subsection{Dimension 6}

% \cN=(1, 1) SYM

% \cN=(1, 0) SYM with matter in a pseudo-real representation. Construct the L_infinity action of supersymmetry

\subsection{Dimension 5}

% \cN=2 SYM
% \cN=1 SYM with matter in a pseudo-real representation.

\subsection{Dimension 4}

% \cN=4 SYM
% \cN=2 SYM with matter in a pseudo-real representation
% \cN=1 SYM with matter in a complex representation

\subsection{Dimension 3}

% \cN=8 SYM
% \cN=4 SYM with matter in a pseudo-real representation
% \cN=2 SYM with matter in a complex representation

\subsection{Dimension 2}

% \cN=(8, 8) SYM
% \cN=(4, 4) SYM with matter in a pseudo-real representation
% \cN=(2, 2) SYM with matter in a complex representation

\pagestyle{bib}
\printbibliography

\end{document}

### 2019-04-15 paper.tex
10d redux

@@
 \input ./math_headers.sty
+
+\def\cA{\mathcal A}\def\cB{\mathcal B}\def\cC{\mathcal C}\def\cD{\mathcal D}
+\def\cE{\mathcal E}\def\cF{\mathcal F}\def\cG{\mathcal G}\def\cH{\mathcal H}
+\def\cI{\mathcal I}\def\cJ{\mathcal J}\def\cK{\mathcal K}\def\cL{\mathcal L}
+\def\cM{\mathcal M}\def\cN{\mathcal N}\def\cO{\mathcal O}\def\cP{\mathcal P}
+\def\cQ{\mathcal Q}\def\cR{\mathcal R}\def\cS{\mathcal S}\def\cT{\mathcal T}
+\def\cU{\mathcal U}\def\cV{\mathcal V}\def\cW{\mathcal W}\def\cX{\mathcal X}
+\def\cY{\mathcal Y}\def\cZ{\mathcal Z}
+
+\def\AA{\mathbb A}\def\BB{\mathbb B}\def\CC{\mathbb C}\def\DD{\mathbb D}
+\def\EE{\mathbb E}\def\FF{\mathbb F}\def\GG{\mathbb G}\def\HH{\mathbb H}
+\def\II{\mathbb I}\def\JJ{\mathbb J}\def\KK{\mathbb K}\def\LL{\mathbb L}
+\def\MM{\mathbb M}\def\NN{\mathbb N}\def\OO{\mathbb O}\def\PP{\mathbb P}
+\def\QQ{\mathbb Q}\def\RR{\mathbb R}\def\SS{\mathbb S}\def\TT{\mathbb T}
+\def\UU{\mathbb U}\def\VV{\mathbb V}\def\WW{\mathbb W}\def\XX{\mathbb X}
+\def\YY{\mathbb Y}\def\ZZ{\mathbb Z}
+
+\def\fA{\mathfrak A}\def\fB{\mathfrak B}\def\fC{\mathfrak C}\def\fD{\mathfrak D}
+\def\fE{\mathfrak E} \def\fF{\mathfrak F}\def\fG{\mathfrak G}\def\fH{\mathfrak H}
+\def\fI{\mathfrak I}\def\fJ{\mathfrak J}\def\fK{\mathfrak K}\def\fL{\mathfrak L}
+\def\fM{\mathfrak M}\def\fN{\mathfrak N}\def\fO{\mathfrak O}\def\fP{\mathfrak P}
+\def\fQ{\mathfrak Q}\def\fR{\mathfrak R}\def\fS{\mathfrak S}\def\fT{\mathfrak T}
+\def\fU{\mathfrak U}\def\fV{\mathfrak V}\def\fW{\mathfrak W}\def\fX{\mathfrak X}
+\def\fY{\mathfrak Y}\def\fZ{\mathfrak Z}
+
+\def\fa{\mathfrak a}\def\fb{\mathfrak b}\def\fc{\mathfrak c}\def\fd{\mathfrak d}
+\def\fe{\mathfrak e}\def\ff{\mathfrak f}\def\fg{\mathfrak g}\def\fh{\mathfrak h} \def\fj{\mathfrak j}\def\fk{\mathfrak k}\def\fl{\mathfrak l} \def\fm{\mathfrak m}\def\fn{\mathfrak n}\def\fo{\mathfrak o}\def\fp{\mathfrak p} \def\fq{\mathfrak q}\def\fr{\mathfrak r}\def\fs{\mathfrak s}\def\ft{\mathfrak t}
+\def\fu{\mathfrak u}\def\fv{\mathfrak v}\def\fw{\mathfrak w}\def\fx{\mathfrak x}
+\def\fy{\mathfrak y}\def\fz{\mathfrak z}
+
+\def\<{\langle}
+\def\>{\rangle}
+\def\cloc{{\rm C}_{\rm loc}}
+\def\bu{\bullet}
+\def\clie{{\rm C}_{\rm Lie}}
 
@@
 
-\subsection{Supersymmetry}
+\subsection{Supersymmetry} \label{sec: susy}
 
@@
 % explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)
+
+\brian{How we we feel about using $L$ for the local Lie algebra of BRST fields and $\fL$ for the BV fields?}
 
@@
 \subsection{Dimension 10}
+
+Our starting point will be (complexified) 10d super Yang-Mills theory.  
+Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  
+The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of:
+\begin{itemize}
+\item a single boson: a connection $A \in \Omega^1(\RR^{10} ; \fg)$ on the trivial $G$-bundle;
+\item a single fermion: a $\gg$-valued section $\lambda \in \Omega^0(\RR^{10}) \otimes \Pi S_+ \otimes \fg$ of the Weyl spinor bundle associated to the spinor representation $S_+$. 
+\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.
+I think for our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.
+The complexified theory twists to holomorphic Chern-Simons theory with complex gauge group.}.
+\end{itemize}
+These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$. 
+Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{10} ; \fg)$.
+
+We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
+\[
+L \;\;\; = \begin{array}{ccccc}
+& \ul{0} & & \ul{1} & \\ 
+& & & & \\
+& \Omega^0(\RR^{10}; \gg) & \to & \Omega^1(\RR^{10}; \gg) \oplus \Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) & 
+\end{array}
+\]
+with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
+
+The action functional in 10d super Yang-Mills is given by
+\[S(A,\lambda) = \int_{\RR^{10}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
+where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and $(-,-)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).
+\brian{I think we should set up this notation in Section \ref{sec: susy} above, and recount it briefly here.}
+
+We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
+This is the local $L_\infty$-algebra $\fL$ on $\RR^{10}$ whose underlying cochain complex takes the form
+\[
+\xymatrix{
+& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
+\fL & = & \Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
+& & &\Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S'_- \otimes \gg), &
+}\]
+\brian{I've changed the spinor component in degree zero to $S_+$, check if that's OK.}
+with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the pairing $(-,-)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
+\begin{align*}
+\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
+(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
+\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
+(A \otimes \lambda) &\mapsto \ast \sd A \lambda
+\end{align*}
+in degree 2, and the map
+\begin{align*}
+\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
+(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
+\end{align*}
+in degree 3.
+
+We obtain the BV action by the formula
+\[
+S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
+\]
+where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
+The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.
+
+\subsubsection{The naive supersymmetry action}
+
+The naive supersymmetry action is defined by saying that bosonic piece of the supersymmetry algebra acts by isometries on $\CC^{10}$, and on the fields via pullback. 
+The fermionic piece of the supersymmetry algebra is defined by saying that $Q \in S_+$ acts infinitesimally by
+\[
+\begin{pmatrix}
+A \\ \lambda
+\end{pmatrix}
+\mapsto
+\begin{pmatrix} A + \delta_Q A \\
+\lambda + \delta_Q \lambda
+\end{pmatrix}
+\]
+where 
+\begin{align*}
+\delta_Q A &= \Gamma(Q,\lambda) \\
+\delta_Q \lambda &= \sd F_A Q .
+\end{align*}
+Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  
+%To check that this defines an on-shell supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra, up to terms in the ideal generated by the equations of motion.
+
+\begin{lemma}
+Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
+The following relations hold:
+\begin{itemize}
+\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
+\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
+\end{itemize}
+Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
+\end{lemma}
+\begin{proof}
+Both are direct calculations using standard Clifford relations which cite below.
+So, we calculate
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
+&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
+&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
+&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
+&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
+&= \delta_{[Q_1, Q_2]} A,
+\end{align*}
+where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e.
+that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.
+Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.
+Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
+&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
+&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
+&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
+&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
+&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
+\end{align*}
+using the fact that 
+\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
+as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
+&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
+\end{align*}
+\end{proof}
+
+In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
+In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".
+
+\subsubsection{Off-shell formulation}
+
+Based off the calculations in the previous subsection, we are motivated to write down the following $L_\infty$ action of the supersymmetry algebra on the space of BV fields.
+
+The linear part of the action is simply the naive action we have already written down:
+\begin{align*}
+\delta^{(1)} \colon S_+ \otimes \left( \Omega^1(\RR^{10} ; \mf g) \oplus \Omega^0(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \right) &\to \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \\
+Q \otimes (A + \lambda) &\mapsto  \Gamma(Q,\lambda) + \sd F_A Q .
+\end{align*}
+In other words, $\delta^{(1)}(Q \otimes (A + \lambda)) = \delta_Q A + \delta_Q\lambda $ in the notation of the previous subsection.
+We define the following quadratic action as
+\begin{align*}
+\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Omega^0(\RR^{10}; \Pi S_+) &\to \Omega^0(\RR^{10}; \Pi S_-' [-1]) \\
+Q_1 \otimes Q_2 \otimes \lambda &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right) .
+\end{align*}
+
+The BV action involving the component $\Pi S_+$ of the supersymmetry algebra reads
+\begin{align*}
+I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+\end{align*}
+
+\begin{prop}
+The functional
+\[
+\fS = S_{BV} + I^{\rm Bos} + I^{(1)} + I^{(2)} \in \clie^\bu(\fg_{\cN=1}) \otimes \cloc^\bu(\fL) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\d_{\rm Lie}  \left( \fS \right) + \{S_{BV}, \fS\} + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
+\]
+\end{prop}
+
+To state the above proposition differently, the functional $\fS$ prescribes an $L_\infty$ map
+\[
+\fS : \fg_{\cN=1} \rightsquigarrow \cloc^\bu(\fL) [-1]
+\]
+\brian{add more}
 
@@
 
+\subsubsection{$\cN=1$ SYM with matter}
+
+Let $R$ be a complex representation of $\mf g$.
+
+The matter sector of the theory is labeled by the BRST fields:
+\begin{itemize}
+\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
+\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
+\end{itemize} 
+which together define the (abelian) local Lie algebra
+\[
+L_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
+\]
 \subsection{Dimension 3}

### 2019-05-06 paper.tex
merge
the definition of a classical theory

@@
 
+\subsection{The definition of a field theory}
 % field theories defined in terms of vector bundles on spacetime
+
+\begin{dfn}
+A {\bf free classical field theory} on a manifold $M$ is the data:
+\begin{itemize}
+\item a finite rank $\ZZ$-graded vector bundle $E \to M$ equipped with a differential operator of cohomological degree $+1$
+\[
+Q : \cE \to \cE [1] 
+\]
+such that (1) $Q^2 = 0$ and (2) $(\cE , Q)$ is an elliptic complex;
+\item a map of bundles
+\[
+\omega : E \otimes E \to {\rm Dens}_M [-1]
+\]
+that is (1) fiberwise nondegenerate, (2) graded skew symmetric, and (3) satisfies $\int_M \omega\<e_0, Qe_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\end{itemize}
+\end{dfn}
+
+\begin{dfn}
+A {\bf classical field theory} is a free classical field theory $(E, Q, \omega)$ equipped with a functional
+\[
+I \in \oloc^+(E)
+\]
+satisfying the classical master equation 
+\[
+Q I + \frac{1}{2} \{I,I\} = 0 .
+\]
+\end{dfn}
+
+A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
+It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
+The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
+\[
+\left(\cO(E), Q + \{I,-\}\right) .
+\]
+We will refer to this as the classical BV complex of the theory.
+
+\begin{dfn}
+A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
+\[
+F : E \to E'
+\]
+that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
+\end{dfn}
+
+Note that a map of classical field theories induces a map of BV complexes
+\[
+F^* : \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
+\]
+This allows us to make the following definition of an equivalence between classical theories.
+
+\begin{dfn}
+A map of classical field theories $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
+\[
+F^* :  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
+\]
+\end{dfn}
+
 % explain how to obtain a QP manifold
+
 % explain how to obtain a factorization algebra given a classical solution
@@
 
+\subsubsection{The minimal twist}
+
 % \cN=(1, 0) SYM

### 2019-05-06 paper.tex
merge

@@
 
+\brian{recall dfn of $\oloc$ of a gr vb.}
+
 \begin{dfn}
@@
 \]
-satisfying the classical master equation 
+of cohomological degree zero satisfying the classical master equation 
 \[
@@
 \end{dfn}
+
+\begin{remark}
+There is a super variant of the above two definitions. 
+A $\ZZ/2$ graded field theory is a $\ZZ \times \ZZ/2$ graded vector bundle $E$ equipped with the same additional data as above.
+We require that $Q, \omega, I$ all have even parity with respect to the additional $\ZZ/2$ grading. 
+\end{remark}
 
@@
 % list possible massless supermultiplets in dimensions [4, 10] with <= 16 supercharges
+
+\subsubsection{Supersymmetric field theory}
+
 % explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)
 
-\brian{How we we feel about using $L$ for the local Lie algebra of BRST fields and $\fL$ for the BV fields?}
+\begin{dfn}
+Let $(E,Q,\omega, I)$ be a $\ZZ/2$-graded classical field theory on $\RR^n$. 
+A {\em strict action} of a super Lie algebra $\fg$ on $(E,Q,\omega, I)$ is a map of super dg Lie algebras
+\[
+\rho : \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
+\]
+More generally, an $L_\infty$ {\em action} is an $L_\infty$ map of super dg Lie algebras
+\[
+\rho : \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
+\]
+\end{dfn}
 
+\begin{rmk}
+More generally, one can speak of what it means for a 
 \subsection{Supersymmetric twisting}
@@
 \[
-L_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
+\sE_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
 \]

### 2019-05-31 paper.tex
Editing section 10

@@
 
-\input ./math_headers.sty
-
-\def\cA{\mathcal A}\def\cB{\mathcal B}\def\cC{\mathcal C}\def\cD{\mathcal D}
-\def\cE{\mathcal E}\def\cF{\mathcal F}\def\cG{\mathcal G}\def\cH{\mathcal H}
-\def\cI{\mathcal I}\def\cJ{\mathcal J}\def\cK{\mathcal K}\def\cL{\mathcal L}
-\def\cM{\mathcal M}\def\cN{\mathcal N}\def\cO{\mathcal O}\def\cP{\mathcal P}
-\def\cQ{\mathcal Q}\def\cR{\mathcal R}\def\cS{\mathcal S}\def\cT{\mathcal T}
-\def\cU{\mathcal U}\def\cV{\mathcal V}\def\cW{\mathcal W}\def\cX{\mathcal X}
-\def\cY{\mathcal Y}\def\cZ{\mathcal Z}
-
-\def\AA{\mathbb A}\def\BB{\mathbb B}\def\CC{\mathbb C}\def\DD{\mathbb D}
-\def\EE{\mathbb E}\def\FF{\mathbb F}\def\GG{\mathbb G}\def\HH{\mathbb H}
-\def\II{\mathbb I}\def\JJ{\mathbb J}\def\KK{\mathbb K}\def\LL{\mathbb L}
-\def\MM{\mathbb M}\def\NN{\mathbb N}\def\OO{\mathbb O}\def\PP{\mathbb P}
-\def\QQ{\mathbb Q}\def\RR{\mathbb R}\def\SS{\mathbb S}\def\TT{\mathbb T}
-\def\UU{\mathbb U}\def\VV{\mathbb V}\def\WW{\mathbb W}\def\XX{\mathbb X}
-\def\YY{\mathbb Y}\def\ZZ{\mathbb Z}
-
-\def\fA{\mathfrak A}\def\fB{\mathfrak B}\def\fC{\mathfrak C}\def\fD{\mathfrak D}
-\def\fE{\mathfrak E} \def\fF{\mathfrak F}\def\fG{\mathfrak G}\def\fH{\mathfrak H}
-\def\fI{\mathfrak I}\def\fJ{\mathfrak J}\def\fK{\mathfrak K}\def\fL{\mathfrak L}
-\def\fM{\mathfrak M}\def\fN{\mathfrak N}\def\fO{\mathfrak O}\def\fP{\mathfrak P}
-\def\fQ{\mathfrak Q}\def\fR{\mathfrak R}\def\fS{\mathfrak S}\def\fT{\mathfrak T}
-\def\fU{\mathfrak U}\def\fV{\mathfrak V}\def\fW{\mathfrak W}\def\fX{\mathfrak X}
-\def\fY{\mathfrak Y}\def\fZ{\mathfrak Z}
-
-\def\fa{\mathfrak a}\def\fb{\mathfrak b}\def\fc{\mathfrak c}\def\fd{\mathfrak d}
-\def\fe{\mathfrak e}\def\ff{\mathfrak f}\def\fg{\mathfrak g}\def\fh{\mathfrak h} \def\fj{\mathfrak j}\def\fk{\mathfrak k}\def\fl{\mathfrak l} \def\fm{\mathfrak m}\def\fn{\mathfrak n}\def\fo{\mathfrak o}\def\fp{\mathfrak p} \def\fq{\mathfrak q}\def\fr{\mathfrak r}\def\fs{\mathfrak s}\def\ft{\mathfrak t}
-\def\fu{\mathfrak u}\def\fv{\mathfrak v}\def\fw{\mathfrak w}\def\fx{\mathfrak x}
-\def\fy{\mathfrak y}\def\fz{\mathfrak z}
-
-\def\<{\langle}
-\def\>{\rangle}
-\def\cloc{{\rm C}_{\rm loc}}
-\def\bu{\bullet}
-\def\clie{{\rm C}_{\rm Lie}}
+\input ./combined_macros.sty
 
@@
 
-\begin{dfn}
+\begin{dfn} \label{equivalence_def}
 A map of classical field theories $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
 \[
-F^* :  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
+F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
 \]
@@
 More generally, one can speak of what it means for a 
+\end{rmk}
 \subsection{Supersymmetric twisting}
@@
 
-Our starting point will be (complexified) 10d super Yang-Mills theory.  
-Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  
+Our starting point will be (complexified) 10d super Yang-Mills theory. Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  
 The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of:
 \begin{itemize}
-\item a single boson: a connection $A \in \Omega^1(\RR^{10} ; \fg)$ on the trivial $G$-bundle;
-\item a single fermion: a $\gg$-valued section $\lambda \in \Omega^0(\RR^{10}) \otimes \Pi S_+ \otimes \fg$ of the Weyl spinor bundle associated to the spinor representation $S_+$. 
+\item A connection $A \in \Omega^1(\RR^{10} ; \fg)$ on the trivial $G$-bundle;
+\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{10}) \otimes \Pi S_+ \otimes \fg$ of the Weyl spinor bundle associated to the spinor representation $S_+$. 
 \footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.
-I think for our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.
+For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.
 The complexified theory twists to holomorphic Chern-Simons theory with complex gauge group.}.
@@
 }\]
-\brian{I've changed the spinor component in degree zero to $S_+$, check if that's OK.}
 with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the pairing $(-,-)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
@@
 
-\subsubsection{The naive supersymmetry action}
+\subsubsection{The Supersymmetry Action}
+In order to construct an action of the $\mc N=(1,0)$ supersymmetry algebra $\mf A$ on the 10d supersymmetric gauge theory $\fL$, we proceed in two steps.
+\begin{enumerate}
+ \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the Poincar\'e algebra by isometries of $\RR^{10}$ \chris{define this above}, which is only well-defined on-shell.
+In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
+ \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
+\end{enumerate}
 
-The naive supersymmetry action is defined by saying that bosonic piece of the supersymmetry algebra acts by isometries on $\CC^{10}$, and on the fields via pullback. 
+Since this is our first example, we will work through it in some detail, in order to motivate the formul\ae{} that will recur in later examples.
 The fermionic piece of the supersymmetry algebra is defined by saying that $Q \in S_+$ acts infinitesimally by
@@
 Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
-%To check that this defines an on-shell supersymmetry action we need to check it's compatible with the brackets in the supersymmetry algebra, up to terms in the ideal generated by the equations of motion.
 
-\begin{lemma}
+\begin{lemma} \label{10d_onshell_lemma}
 Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
@@
 \end{lemma}
+
 \begin{proof}
@@
 In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".
-
-\subsubsection{Off-shell formulation}
-
-Based off the calculations in the previous subsection, we are motivated to write down the following $L_\infty$ action of the supersymmetry algebra on the space of BV fields.
-
-The linear part of the action is simply the naive action we have already written down:
+This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.
+Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
 \begin{align*}
-\delta^{(1)} \colon S_+ \otimes \left( \Omega^1(\RR^{10} ; \mf g) \oplus \Omega^0(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \right) &\to \Omega^1(\RR^{10} ; \mf g) \oplus \Gamma(\RR^{10}; \Pi S_+[-1] \otimes \mf g) \\
-Q \otimes (A + \lambda) &\mapsto  \Gamma(Q,\lambda) + \sd F_A Q .
-\end{align*}
-In other words, $\delta^{(1)}(Q \otimes (A + \lambda)) = \delta_Q A + \delta_Q\lambda $ in the notation of the previous subsection.
-We define the following quadratic action as
-\begin{align*}
-\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Omega^0(\RR^{10}; \Pi S_+) &\to \Omega^0(\RR^{10}; \Pi S_-' [-1]) \\
-Q_1 \otimes Q_2 \otimes \lambda &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right) .
+\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
+Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
 \end{align*}
 
-The BV action involving the component $\Pi S_+$ of the supersymmetry algebra reads
+We'll rewrite this as a local functional in the theory $\fL$ coupled to the $\mc N=(1,0)$ super Lie algebra $\mf A$.
+
+\begin{definition}
+The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{10}$ is defined to be the cochain
+\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
+where 
 \begin{align*}
@@
 \end{align*}
+\end{definition}
 
 \begin{prop}
+Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here}.
 The functional
-\[
-\fS = S_{BV} + I^{\rm Bos} + I^{(1)} + I^{(2)} \in \clie^\bu(\fg_{\cN=1}) \otimes \cloc^\bu(\fL) [-1]
-\]
+\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
 satisfies the Maurer-Cartan equation
-\[
-\d_{\rm Lie}  \left( \fS \right) + \{S_{BV}, \fS\} + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
-\]
+\begin{equation} 
+\label{10d_MC}
+(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
+\end{equation}
 \end{prop}
 
-To state the above proposition differently, the functional $\fS$ prescribes an $L_\infty$ map
-\[
-\fS : \fg_{\cN=1} \rightsquigarrow \cloc^\bu(\fL) [-1]
-\]
-\brian{add more}
+\begin{proof}
+We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
+\begin{align}
+\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
+&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
+&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
+&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
+&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
+\end{align}
+Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.
+The remaining terms are those involving the action of supersymmetries.
 
-\subsubsection{The minimal twist}
+First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.
+First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.
+Then \ref{10d_MC_1} is zero by Baez--Huerta.
+Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}.
+Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.
+Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
+\end{proof}
 
-% \cN=(1, 0) SYM
-% Construct the L_infinity action of supersymmetry
+\subsubsection{The Holomorphic Twist}
+
+\newcommand{\hCS}{\mathrm{hCS}}
+\chris{this definition should go elsewhere.  We also need to include a description of the holomorphic supercharge, and something about the trivial $\SU(5)$ twisting homomorphism.}
+
+\begin{definition}
+Let $X$ be a Calabi-Yau variety of odd complex dimension $d$, and let $G$ be a complex reductive group.
+\emph{Holomorphic Chern-Simons theory} is the $\ZZ/2\ZZ$-graded classical field theory $(E_\hCS, Q_\hCS, \omega_\hCS, I_\hCS)$, where $E_\hCS$ is the graded vector bundle $\Omega^{0,\bullet}(X;\gg)$, $Q_{\hCS}$ is the Dolbeault differential, $\omega_\hCS$ is the density-valued pairing associated to the Calabi-Yau structure on $X$ and a choice of invariant pairing on $\gg$, and $I_\hCS$ is the cubic interactional functional
+\[I_{\hCS}(\alpha) = \frac 16 [\alpha \wedge \alpha \wedge \alpha].\]
+\end{definition}
+
+\begin{theorem}
+The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
+\end{theorem}
+
+\begin{proof}
+We will first construct a morphism $\iota$ from holomorphic Chern-Simons theory to the twisted theory $\fL^Q$.
+\chris{We split the fields of 10d super Yang-Mills into $\SU(5)$ irreducible representations, so the ghost $c$, then fields $A_{0,1}, A_{1,0}, B, \psi, \chi$ and their antifields, and include $c, A_{0,1}, B, B^\vee, A_{0,1}^\vee, c^\vee$.
+Easy to check that it defines a morphism to the twisted theory.}
+
+Now, to verify that this morphism is an equivalence as in Definition \ref{equivalence_def}, we must check that the induced morphism 
+\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q,-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
+is a quasi-isomorphism. \chris{...}
+
+\end{proof}
 
@@
 \[
-\sE_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
+\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
 \]

### 2019-05-31 paper.tex
Editing section 10

@@
 \[
-Q : \cE \to \cE [1] 
+Q \colon \cE \to \cE [1] 
 \]
@@
 Now, to verify that this morphism is an equivalence as in Definition \ref{equivalence_def}, we must check that the induced morphism 
-\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q,-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
-is a quasi-isomorphism. \chris{...}
+\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q + I^{(2)}_{Q\otimes Q},-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
+is a quasi-isomorphism.
+\chris{maybe try filtering the left-hand side by the number of $\chi$ and $\chi^\vee$ fields occuring.
+The 0th filtered piece should coincide with the right-hand side exactly, and maybe we'd like to see that everything else is killed off by some differential in the spectral sequence?}
 

### 2019-07-04 paper.tex
SUSY background

@@
 \addbibresource{Twist.bib}
+
+\usepackage{pdflscape}
+\usetikzlibrary{shapes.geometric, arrows, positioning}
+
+\tikzstyle{s16} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=red!30]
+\tikzstyle{s16chiral} = [s16, dashed]
+\tikzstyle{s8} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s4} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
+\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=green!30]
+\tikzstyle{dimension} = [ellipse, text centered, text width=1cm, minimum height=1cm, draw=black]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 
-\subsection{Shifted symplectic manifolds}
-
-% Define QP manifolds (Z x Z/2-graded, Q doesn't have to be Hamiltonian)
-% Tangent complex of a QP manifold at a classical solution forms a cyclic L_infinity algebra
-% equivalence of QP manifolds
-
-\subsection{Models of field theories}
+Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
 
 \subsection{The definition of a field theory}
-% field theories defined in terms of vector bundles on spacetime
 
@@
 \begin{itemize}
-\item a finite rank $\ZZ$-graded vector bundle $E \to M$ equipped with a differential operator of cohomological degree $+1$
+\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
 \[
-Q \colon \cE \to \cE [1] 
+\d \colon \cE \to \cE [1] 
 \]
-such that (1) $Q^2 = 0$ and (2) $(\cE , Q)$ is an elliptic complex;
+such that (1) $\d^2 = 0$ and (2) $(\cE , \d)$ is an elliptic complex;
 \item a map of bundles
 \[
-\omega : E \otimes E \to {\rm Dens}_M [-1]
+\omega\colon E \otimes E \to {\rm Dens}_M [-1]
 \]
-that is (1) fiberwise nondegenerate, (2) graded skew symmetric, and (3) satisfies $\int_M \omega\<e_0, Qe_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+that is
+\begin{enumerate}
+\item fiberwise nondegenerate,
+\item graded skew symmetric, and
+\item satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\end{enumerate}
 \end{itemize}
@@
 \begin{dfn}
-A {\bf classical field theory} is a free classical field theory $(E, Q, \omega)$ equipped with a functional
+A {\bf classical field theory} is a free classical field theory $(E, \d, \omega)$ equipped with an even functional
 \[
@@
 \[
-Q I + \frac{1}{2} \{I,I\} = 0 .
+\d I + \frac{1}{2} \{I,I\} = 0 .
 \]
@@
 
+Given a classical field theory $(E, \d, \omega, I)$ we denote by
+\[S_{BV} = \frac{1}{2} \int_M \omega(e, \d e) + I\in \oloc(E)\]
+the BV action of the theory.
+
 \begin{remark}
-There is a super variant of the above two definitions. 
-A $\ZZ/2$ graded field theory is a $\ZZ \times \ZZ/2$ graded vector bundle $E$ equipped with the same additional data as above.
-We require that $Q, \omega, I$ all have even parity with respect to the additional $\ZZ/2$ grading. 
+We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $\d$ is simply an odd operator.
 \end{remark}
@@
 It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
-The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
+The classical master equation implies that the operator $\d + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
 \[
-\left(\cO(E), Q + \{I,-\}\right) .
+\left(\cO(E), \d + \{I,-\}\right) .
 \]
-We will refer to this as the classical BV complex of the theory.
+We will refer to this as the {\bf classical BV complex} of the theory.
 
 \begin{dfn}
-A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
+A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is a linear map of vector bundles
 \[
-F : E \to E'
+F\colon E \to E'
 \]
-that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
+that intertwines the differentials $\d, \d'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
 \end{dfn}
@@
 \[
-F^* : \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
+F^*\colon \left(\cO (\cE)[-1], \d + \{I,-\} \right) \to \left(\cO (\cE')[-1], \d' + \{I',-\} \right) .
 \]
@@
 \begin{dfn} \label{equivalence_def}
-A map of classical field theories $F : (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
+A morphism of classical field theories $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
 \[
-F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
+F^* \colon  \left(\cO(\cE')[-1], \d' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], \d + \{I,-\} \right) .
 \]
@@
 
-% explain how to obtain a QP manifold
+\begin{dfn}
+Let $(E, \d,\omega, I)$ be a classical field theory 
+A {\bf strict action} of a super Lie algebra $\fg$ on $(E, \d,\omega, I)$ is a map of super dg Lie algebras
+\[
+\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
+\]
+More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
+\[
+\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
+\]
+\end{dfn}
 
-% explain how to obtain a factorization algebra given a classical solution
+We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes.
+
+\pavel{explain how to obtain a factorization algebra from a classical field theory.}
+
+\pavel{explain how to get a BV theory from a BRST theory}
+
+\subsection{Examples}
+
+\pavel{(partially) topological BF theories and Chern-Simons theories in different dimensions.}
 
@@
 
-% spinorial representations, supertranslation groups, superPoincar\'{e} groups
-% list possible massless supermultiplets in dimensions [4, 10] with <= 16 supercharges
+In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
 
-\subsubsection{Supersymmetric field theory}
+Let $V_\RR = \RR^n$ endowed with its nondegenerate bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+\begin{itemize}
+\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the {\bf spin} representation $S$.
 
-% explain what a supersymmetric field theory is (in terms of the L_infinity action of the supertranslation algebra)
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the {\bf semi-spin} representations $S_+, S_-$.
+\end{itemize}
 
 \begin{dfn}
-Let $(E,Q,\omega, I)$ be a $\ZZ/2$-graded classical field theory on $\RR^n$. 
-A {\em strict action} of a super Lie algebra $\fg$ on $(E,Q,\omega, I)$ is a map of super dg Lie algebras
-\[
-\rho : \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
-\]
-More generally, an $L_\infty$ {\em action} is an $L_\infty$ map of super dg Lie algebras
-\[
-\rho : \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
-\]
+A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
 \end{dfn}
 
-\begin{rmk}
-More generally, one can speak of what it means for a 
-\end{rmk}
+So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
+
+\begin{dfn}
+Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
+\end{dfn}
+
+For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
+In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
+\begin{itemize}
+\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
+
+\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
+
+\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
+
+\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
+\end{itemize}
+
+Fix the following data:
+\begin{itemize}
+\item A spinorial representation $\Sigma$ of $\so(V)$.
+
+\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+
+\item A complex Lie group $G_R$, the {\bf group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
+\end{itemize}
+
+Note that the supertranslation Lie algebra $T$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
+
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the Poincar\'{e} group which acts in the obvious way on $M$.
+
+\begin{dfn}
+A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
+\end{dfn}
+
 \subsection{Supersymmetric twisting}
 
-% twisting of field theories
-% twisting homomorphisms
-% list all possible twists in dimensions [2, 10] with <= 16 supercharges
+\begin{dfn}
+A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+\end{dfn}
+
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+\begin{itemize}
+\item A supercharge $Q$ is {\bf topological} if $d = n$.
+
+\item A supercharge $Q$ is {\bf holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a {\bf holomorphic-topological} (alternatively, partially topological) supercharge.
+The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+\begin{dfn}
+A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{dfn}
+
+We will call $\alpha$ in a twisting datum a {\bf twisting homomorphism}.
+
+\begin{dfn}
+Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
+for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+\end{dfn}
+
+\begin{prop}
+The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
+\end{prop}
+\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{remark}
+Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
+\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
+where the $\ZZ/2$-grading on $E$ is the total grading.
+\end{remark}
 
@@
 
+\begin{landscape}
+\begin{figure}
+\begin{tikzpicture}[node distance=0.5cm and 0.5cm, text width=2cm]
+\node (101) [s16chiral] {Rank $(1, 0)$. $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$. $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$. $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$. $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$. $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$. $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$. $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$. $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$. $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$. $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$. $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$. $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$. $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$. $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$. $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$. $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$. $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$. $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$. $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$. $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$. $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$. $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$. $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$. $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$. $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$. $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
+\end{landscape}
+
 \end{document}

### 2019-07-11 paper.tex
merge error
modest edits

@@
 \]
-such that (1) $\d^2 = 0$ and (2) $(\cE , \d)$ is an elliptic complex;
+such that $(1)$: $\d^2 = 0$ and $(2)$: the pair $(\cE , \d)$ is an elliptic complex;
 \item a map of bundles
@@
 \begin{enumerate}
-\item fiberwise nondegenerate,
-\item graded skew symmetric, and
-\item satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(1)$] fiberwise nondegenerate,
+\item[$(2)$] graded skew symmetric, and
+\item[$(3)$] satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 \]
+\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
 \end{dfn}
@@
 % \cN=(2, 2) SYM with matter in a complex representation
+%BRIAN FIND REFERENCE OF BELOW
+% \cN=(0,2) SYM with matter 
+% \cN=(0,4) SYM with matter
+% \cN=(0,8) SYM with matter
 
@@
 
+\appendix
+
+\section{Functional analysis}
+
+\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{CG1}, here. }
+
+\section{$\infty$ algebra}
+
+\brian{Not sure if this deserves a whole appendix, but it may be good to spell out what $L_\infty$ modules are, etc..}
+
 \end{document}

### 2019-07-16 paper.tex
adding technical lemmas

@@
 \begin{dfn}
-A {\bf free classical field theory} on a manifold $M$ is the data:
+A {\bf free BV theory} on a manifold $M$ is the data:
 \begin{itemize}
@@
 \[
-\d \colon \cE \to \cE [1] 
+Q \colon \cE \to \cE [1] 
 \]
-such that $(1)$: $\d^2 = 0$ and $(2)$: the pair $(\cE , \d)$ is an elliptic complex;
+such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
 \item a map of bundles
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega\<e_0, \d e_1\> = (-1)^{|e_0|} \int_M \omega(\d e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 \begin{dfn}
-A {\bf classical field theory} is a free classical field theory $(E, \d, \omega)$ equipped with an even functional
+A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
 \[
@@
 \[
-\d I + \frac{1}{2} \{I,I\} = 0 .
+Q I + \frac{1}{2} \{I,I\} = 0 .
 \]
@@
 
-Given a classical field theory $(E, \d, \omega, I)$ we denote by
-\[S_{BV} = \frac{1}{2} \int_M \omega(e, \d e) + I\in \oloc(E)\]
+Given a classical field theory $(E, Q, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
 the BV action of the theory.
@@
 \begin{remark}
-We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $\d$ is simply an odd operator.
+We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
 \end{remark}
@@
 It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
-The classical master equation implies that the operator $\d + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
+The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
 \[
-\left(\cO(E), \d + \{I,-\}\right) .
+\left(\cO(E), Q + \{I,-\}\right) .
 \]
@@
 \begin{dfn}
-A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is a linear map of vector bundles
+A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
 \[
@@
 \]
-that intertwines the differentials $\d, \d'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
+that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
 \end{dfn}
@@
 \[
-F^*\colon \left(\cO (\cE)[-1], \d + \{I,-\} \right) \to \left(\cO (\cE')[-1], \d' + \{I',-\} \right) .
+F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
 \]
@@
 \begin{dfn} \label{equivalence_def}
-A morphism of classical field theories $F\colon (E, \d, \omega, I) \to (E', \d', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
+A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
 \[
-F^* \colon  \left(\cO(\cE')[-1], \d' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], \d + \{I,-\} \right) .
+F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
 \]
@@
 \begin{dfn}
-Let $(E, \d,\omega, I)$ be a classical field theory 
-A {\bf strict action} of a super Lie algebra $\fg$ on $(E, \d,\omega, I)$ is a map of super dg Lie algebras
+Let $(E, Q,\omega, I)$ be a classical field theory 
+A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras
 \[
-\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
+\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
 \]
@@
 \[
-\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, \d + \{I,-\}_\omega\right) .
+\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
 \]
@@
 
+\subsection{The classical factorization algebra}
+
 \pavel{explain how to obtain a factorization algebra from a classical field theory.}
 
+Let $(E, Q, \omega, I)$ be a classical field theory and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
+Then, we recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime that should be thought of as  functions on the formal neighborhood of the derived critical locus of the action $S$ near $\psi_0$.
+
+\begin{dfn}
+Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
+The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra
+\[
+\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
+\]
+\end{dfn}
+
+\subsection{From BRST to BV}
+
 \pavel{explain how to get a BV theory from a BRST theory}
+
+%\begin{dfn}
+%A {\bf classical BRST theory} is a finite rank $\ZZ \times \ZZ / 2$-graded vector bundle $F \to M$ equipped with an even differential operator of cohomological degree $+1$
+%\[
+%Q : \cF \to \cF[1]
+%\]
+%such that $Q
 
@@
 
+\def\CVS{{\rm CVS}}
+\def\DVS{{\rm DVS}}
+
 \brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{CG1}, here. }
+
+\subsection{Notations and conventions}
+
+\begin{dfn}
+Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
+For any open set $U \subset M$, define the following notations:
+\begin{itemize}
+\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
+\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
+\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
+\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
+\end{itemize}
+\end{dfn}
+
+If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
+For an open set $U \subset M$ let 
+\[
+\cE(U)^\vee = \Bar{\cE}^!_c(U)
+\]
+be the continuous, or distributional dual, to $\sE(U)$.
+
+\begin{prop}
+Let $E,F$ be vector bundles on $M,N$ respectively.
+Then
+\[
+\cE(M) \Hat{\otimes}_\beta \cF(N) \cong \Gamma(M \times N, E \boxtimes F)
+\]
+\end{prop}
+
+\begin{dfn}
+Let $E$ be a vector bundle on $M$ and $U \subset M$.
+The completed algebra of functions on $\cE(U)$ is
+\[
+\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
+\]
+\end{dfn}
+
+\subsection{Homological algebra}
+
+There is a functor
+\[
+dif_c : \CVS \to \DVS .
+\]
+
+\begin{dfn}
+Suppose $V,W$ are cochain complexes in convenient vector spaces. 
+A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
+\[
+dif_c (f) : dif_c(V) \to dif_c(W)
+\]
+is a quasi-isomorphism of differentiable vector spaces.
+\end{dfn}
+
+\begin{dfn}
+A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
+\[
+\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
+\]
+where each map is a monomorphism in each cohomological degree. 
+A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
+\end{dfn}
+
+\begin{thm}[Eilenberg-Moore Comparison]
+Let $f : V \to W$ be a map of filtered cochain complexes in an AB4 abelian category.
+Suppose, for each integer $n$ there exists an integer $p$ such that $F_p V^n = 0 = F_p W^n$.
+If there is an integer $r \geq 0$ such that the induced map on the $r$th page of the corresponding spectral sequences 
+\[
+f_r^{pq} :  E_r^{pq} V \to E_r^{pq} W
+\]
+is an isomorphism for all $p,q$, then $f : V \to W$ is a quasi-isomorphism. 
+\end{thm}
+
+The category of differentiable vector space is an AB4 category, in fact, it is actually a Grothendieck abelian category.
+
+\begin{thm}[Theorem 2.2.1 of \cite{CG1}]
+The category $\DVS$ is a Grothendieck abelian category.
+\end{thm}
+
+In particular, we can freely apply the Eilenberg-Moore comparison result to the types of topological cochain complexes we come across in the BV formalism.
+
+\begin{dfn}
+A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
+\[
+\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
+\]
+where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
+\end{dfn}
 

### 2019-07-16 10d_section_draft.tex
Draft of 10d section, material to be incorporated later

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty
\newcommand{\hCS}{\mathrm{hCS}}

\addbibresource{Twist.bib}

\title{Twists of supersymmetric gauge theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\section{Background Structure}
\chris{This section consists of material common to our twisting calculations, to be edited and perhaps inserted before the 10d section}

\chris{As you pointed out, these lemmas should go with other discussion of functional analysis issues.}
\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.  There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
\end{lemma}

\begin{lemma} \label{invert_quis_lemma}
Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
\end{lemma}

\subsection{Dimensional Reduction} \label{dim_red_section}
\chris{I'm including this with the aim to not have to prove supersymmetry invariance of non-maximal theories.  It's a pretty rough draft, so apologies there}
The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.

\begin{definition}
Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection. Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.  The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.  The symplectic pairing is defined as the composite
\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.  The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
\[\phi \mapsto i^*(Q(p^*(\phi))).\]
Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}.
\end{definition}

Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.

\begin{prop} \label{dim_red_SUSY_prop}
The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
\end{prop}

\begin{proof}
 \chris{I think this will be straightforward.}
\end{proof}

\chris{we could alternatively write this in terms of BRST fields.}

\chris{By the way, I see no obstruction to proving the following.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

\subsection{Supersymmetric Yang-Mills Theory}
We'll begin with a detailed description of the maximal (complexified) supersymmetric Yang-Mills theories, which exist in dimensions 3,4, 6 and 10.  Using the methods described in Section \ref{dim_red_section}, the construction of these theory, with the supersymmetry actions, will descend to supersymmetric theories in all lower dimensions.

Let us begin with a general description of supersymmetric Yang-Mills theory on $\RR^n$, with spinorial matter.  Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.  The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
\begin{itemize}
\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.  For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.  
\end{itemize}
These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.

We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
\[
L \;\;\; = \begin{array}{ccccc}
& \ul{0} & & \ul{1} & \\ 
& & & & \\
& \Omega^0(\RR^{n}; \gg) & \to & \Omega^1(\RR^{n}; \gg) \oplus \Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) & 
\end{array}
\]
with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.

The action functional in 10d super Yang-Mills is given by
\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$. \chris{Brian suggested defining this notation in the section on supersymmety more broadly.  I agree.}

We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
This is the local $L_\infty$-algebra $\fL$ on $\RR^{n}$ whose underlying cochain complex takes the form
\[
\xymatrix{
& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
\fL & = & \Omega^0(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{n}; \gg) \ar[r]^{\d \ast \d} &\Omega^{n-1}(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^{n}(\RR^{n}; \gg) \\
& & &\Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{n}(\RR^{n}; \Pi \Sigma^* \otimes \gg), &
}\]
with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the evaluation pairing $(-,-)$ between $\Sigma$ and $\Sigma^*$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{n}; \gg)$ on everything along with
\begin{align*}
\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^0(\RR^{n}; \Sigma \otimes \gg) &\to \Omega^{n}(\RR^{10}; \Sigma* \otimes \gg) \\
(A \otimes \lambda) &\mapsto \ast \sd A \lambda
\end{align*}
in degree 2, and the map
\begin{align*}
\ell_3 \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
\end{align*}
in degree 3.

We obtain the BV action by the formula
\[
S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
\]
where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.

\subsubsection{Supersymmetry Actions}
For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10, so $\Sigma$ is the 2-dimensional Dirac representation $S$, the 4-dimensional Dirac representation $S_+ \oplus S_-$, the 8-dimensional symplectic Weyl representation $S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, and the 16-dimensional Weyl representation $S_+$ respectively.  We will now proceed to construct this supersymmetry algebra action. \chris{can we do it all in one go, using the fact that the 3 $\psi$ rule \cite[Theorem 11]{BaezHuerta} works exactly in these dimensions?  If not we can just write the calculation out four times.  We've already started to write it in the 10-dimensional case, though it's incomplete.  How would you suggest proceeding?}

\subsection{Standard Equivalences Between Classical Field Theories}
In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.

\begin{lemma} \label{symplectomorphism_lemma}
A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
\end{lemma}

\begin{lemma} \label{inclusion_and_projection_lemma}
Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
\begin{enumerate}
 \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.  Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
 \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.  Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
\end{enumerate}
\end{lemma}

\begin{lemma} \label{symplectic_composite_lemma}
Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.  Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.  Then the cochain map 
\begin{equation}
\label{symp_composite_eqn}\mc E^\bullet (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
\end{equation}
obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
\end{lemma}

\begin{lemma} \label{interaction_pullback_lemma}
In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.  If $\mc C_2^\bullet = 0$, or if $\mc C_1^\bullet$ and $\mc C_2^\bullet$ are both isotropic subspaces of $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
\end{lemma}

\section{Twists}
\subsection{Dimension 10}

\pagestyle{bib}
\printbibliography

\end{document}

### 2019-07-16 10d_section_draft.tex
Sketching in the content in the 10d argument

@@
 \subsection{Dimension 10}
+\chris{background, recall there is only one class of twists, by a pure spinor.
+There's a trivial twisting homomorphism from $\SU(5)$, and so it's defined on CY5s.
+Give names to the BV component fields as irreducible $\SU(5)$ representations: this is important for the argument below.}
+
+\begin{theorem}
+The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
+\end{theorem}
+
+\begin{proof}
+\chris{recall the steps.
+1) Modify $\chi^\vee$ by a linear change of variables $\chi^\vee \mapsto \chi^vee + \Lambda F_{1,1}$.
+2) Integrate out the contractible doublet $\chi, \chi^\vee$.
+3) Note that the pairs $A_{1,0}, \psi$ and $\psi^\vee, A_{1,0}^\vee$ can be killed in pairs, and the composite of these operations defines a symplectomorphism.
+4) These steps each preserve the action, so that we have a map of interacting theories.
+5) Using the spectral sequence, this map is an equivalence.}
+\end{proof}
 

### 2019-07-16 paper.tex

@@
 A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
-It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
-The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
+It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
+The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
 \[
-\left(\cO(E), Q + \{I,-\}\right) .
+\left(\cO(\cE), Q + \{I,-\}\right) .
 \]
+In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
 We will refer to this as the {\bf classical BV complex} of the theory.
@@
 
-Note that a map of classical field theories induces a map of BV complexes
+Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
 \[
@@
 \begin{dfn} \label{equivalence_def}
-A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
+A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
 \[
@@
 
+For a short background on homological algebra with differentiable pro-cochain complexes, including the notion of quasi-isomorphism, we refer to Appendix \ref{appx: top}.
+For a more thorough introduction, and for which our conventions are based on, we refer to \cite{CG1}.
+
 \begin{dfn}
 Let $(E, Q,\omega, I)$ be a classical field theory 
-A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras
+A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
 \[
@@
 Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
-The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra
+The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
 \[
@@
 \end{dfn}
+
+Notice that the BV complex we defined in the previous section is simply the global sections of the factorization algebra along $M$.
 
@@
 
-\section{Functional analysis}
+\section{Functional analysis} \label{appx: top}
 
@@
 \]
-be the continuous, or distributional dual, to $\sE(U)$.
+be the continuous, or distributional, dual to $\cE(U)$.
+
+\brian{recall definition of CVS. all our familiar spaces above are in $\CVS$. talk about tensor products.}
 
@@
 
-\begin{dfn}
+\begin{dfn}\label{dfn: fnl}
 Let $E$ be a vector bundle on $M$ and $U \subset M$.
-The completed algebra of functions on $\cE(U)$ is
+The {\bf completed algebra of functions} on $\cE(U)$ is
 \[
@@
 \]
+On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
 \end{dfn}
@@
 \subsection{Homological algebra}
+
+\brian{can't do cokernels in CVS, blah blah}
 
@@
 
-\begin{dfn}
+\begin{dfn}\label{dfn: pro}
 A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
@@
 
+\begin{lem}
+If $(E, \omega, Q, I)$ is the data of a classical theory on $M$, then the BV complex
+\[
+\left(\cO(\cE) , Q + \{I,-\}\right)
+\]
+is a differentiable pro-cochain complex.
+More generally, the classical factorization algebra of observables $\Obs$ is a factorization algebra in differentiable pro-cochain complexes. 
+\end{lem}
+
 \section{$\infty$ algebra}

### 2019-07-17 10d_section_draft.tex
Starting 10d setup

@@
 \subsection{Dimension 10}
+We'll begin by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Theorem \chris{ref}.
+In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
+These square-zero supercharges are holomorphic.
+
+Fix a non-trivial pure spinor $Q$.
+The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
+Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
+The BRST fields split as
+\begin{align*}
+c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
+A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
+\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
+\end{align*}
+
 \chris{background, recall there is only one class of twists, by a pure spinor.
@@
 
+We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
+
 \begin{theorem}
@@
 \end{theorem}
+
+\begin{remark}
+This twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $-1$-symplectic pairing.
+\end{remark}
 

### 2019-07-17 10d_section_draft.tex
Starting 10d argument

@@
 
-\subsubsection{Supersymmetry Actions}
+\subsubsection{Supersymmetry Actions} \label{SUSY_action_section}
 For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10, so $\Sigma$ is the 2-dimensional Dirac representation $S$, the 4-dimensional Dirac representation $S_+ \oplus S_-$, the 8-dimensional symplectic Weyl representation $S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, and the 16-dimensional Weyl representation $S_+$ respectively.
@@
 \subsection{Dimension 10}
-We'll begin by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Theorem \chris{ref}.
+We'll begin by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
 In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
@@
 
-Fix a non-trivial pure spinor $Q$.
+Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
 The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
 Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
-The BRST fields split as
+The BRST fields split as follows:
 \begin{align*}
@@
 
-\chris{background, recall there is only one class of twists, by a pure spinor.
-There's a trivial twisting homomorphism from $\SU(5)$, and so it's defined on CY5s.
-Give names to the BV component fields as irreducible $\SU(5)$ representations: this is important for the argument below.}
+In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
+\begin{align*}
+S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
+S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
+\end{align*}
+where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
+Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
+It has a quadratic and a cubic component given by
+\begin{align*}
+I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
+I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
+\end{align*}
+The twisted action functional is obtained by adding these terms to the original BV action functional.
 
@@
 \begin{proof}
-\chris{recall the steps.
-1) Modify $\chi^\vee$ by a linear change of variables $\chi^\vee \mapsto \chi^vee + \Lambda F_{1,1}$.
-2) Integrate out the contractible doublet $\chi, \chi^\vee$.
-3) Note that the pairs $A_{1,0}, \psi$ and $\psi^\vee, A_{1,0}^\vee$ can be killed in pairs, and the composite of these operations defines a symplectomorphism.
-4) These steps each preserve the action, so that we have a map of interacting theories.
-5) Using the spectral sequence, this map is an equivalence.}
+We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
+
+\begin{enumerate}
+ \item The first part of our equivalence of classical field theories will be a simple change of variables.
+Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$.
+In terms of $\chi'^\vee$, the quadratic part of the twisted action functional becomes
+ \begin{align*}
+  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi \wedge (\ol \dd \psi))  + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
+  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
+ \end{align*}
+ The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
+However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
+Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
+We think of this as ``integrating out'' the field $\chi$ and its antifield.
+
+ \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
+We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
+ \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
+ Observe that the classical BV complex associated to this action functional takes the form \chris{I'm confused here: there are actually both maps into the $\psi \to A_{1,0}$ two step complex ($c \mapsto \dd c$) and maps out ($A_{1,0} \to A_{0,1}^\vee$ and $\psi \to B^\vee$).
+So the argument we'd been thinking of doesn't work?
+I don't remember, did we discuss this?}
+
+ \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories. \chris{...}
+
+ \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
+The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
+Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
+an equivalence of classical field theories.
+\end{enumerate}
 \end{proof}

### 2019-07-17 10d_section_draft.tex
Continuing draft of 10d argument

@@
  \item The first part of our equivalence of classical field theories will be a simple change of variables.
-Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$.
-In terms of $\chi'^\vee$, the quadratic part of the twisted action functional becomes
+Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
+In terms of $\chi'$, the quadratic part of the twisted action functional becomes
  \begin{align*}
-  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi \wedge (\ol \dd \psi))  + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
+  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
   &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
@@
  The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
-However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
+However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
 Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
-We think of this as ``integrating out'' the field $\chi$ and its antifield.
+We think of this as ``integrating out'' the field $\chi'$ and its antifield.
 
@@
  \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- Observe that the classical BV complex associated to this action functional takes the form \chris{I'm confused here: there are actually both maps into the $\psi \to A_{1,0}$ two step complex ($c \mapsto \dd c$) and maps out ($A_{1,0} \to A_{0,1}^\vee$ and $\psi \to B^\vee$).
+ Observe that the classical BV complex associated to this action functional can be written in the following form:
+ \[\xymatrix{
+ &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{A_{1,0}} \ar[dr]\\
+ \Omega^0(\CC^5;\gg)_c \ar[r] \ar[urrr] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
+ \Omega^{4,0}(\CC^5;\gg)_{A_{1,0}^\vee} \ar[r] \ar[urrrrr]  &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee}. 
+ }\]
+ \chris{I'm confused here: there are actually both maps into the $\psi \to A_{1,0}$ two step complex ($c \mapsto \dd c$) and maps out ($A_{1,0} \to A_{0,1}^\vee$ and $\psi \to B^\vee$).
 So the argument we'd been thinking of doesn't work?
-I don't remember, did we discuss this?}
+I don't remember, did we discuss this?
+I want to eliminate those ugly arrows involving $c$ and $c^\vee$ (also obviously they make the diagram above unreadable).}
 
- \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories. \chris{...}
+ \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
+We'll use Lemma \ref{interaction_pullback_lemma}.
+Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
+The resulting interaction is
+ \[
+  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
+ \]
+ which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
+The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
 

### 2019-07-17 10d_section_draft.tex
Completed first draft of 10d argument, with a gap.

@@
  \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- Observe that the classical BV complex associated to this action functional can be written in the following form:
+ We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
+This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
+\chris{This isn't quite right I think.
+We need to kill that term, however, for the below argument to work.
+Can we fix it?}
+
+ Observe that the classical BV complex associated to this action functional can now be written in the following form:
  \[\xymatrix{
- &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{A_{1,0}} \ar[dr]\\
- \Omega^0(\CC^5;\gg)_c \ar[r] \ar[urrr] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
- \Omega^{4,0}(\CC^5;\gg)_{A_{1,0}^\vee} \ar[r] \ar[urrrrr]  &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee}. 
+ &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
+ \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
+ \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
  }\]
- \chris{I'm confused here: there are actually both maps into the $\psi \to A_{1,0}$ two step complex ($c \mapsto \dd c$) and maps out ($A_{1,0} \to A_{0,1}^\vee$ and $\psi \to B^\vee$).
-So the argument we'd been thinking of doesn't work?
-I don't remember, did we discuss this?
-I want to eliminate those ugly arrows involving $c$ and $c^\vee$ (also obviously they make the diagram above unreadable).}
+ where the first and third rows are dual under the symplectic pairing.
+This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
+the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
 
@@
 
+The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+
 \pagestyle{bib}

### 2019-07-17 10d_section_draft.tex
Clarified the behaviour of interactions

@@
 \begin{lemma} \label{interaction_pullback_lemma}
-In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
-If $\mc C_2^\bullet = 0$, or if $\mc C_1^\bullet$ and $\mc C_2^\bullet$ are both isotropic subspaces of $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
+In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
+Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
+Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
 \end{lemma}
+
+\begin{proof}
+We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
+Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
+\end{proof}
 
@@
  \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-We'll use Lemma \ref{interaction_pullback_lemma}.
+The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
+In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
 Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).

### 2019-07-17 paper.tex
hcs

@@
 \pavel{(partially) topological BF theories and Chern-Simons theories in different dimensions.}
+
+\subsubsection{Holomorphic Chern-Simons}
+
+Fix a Calabi-Yau manifold $X$ of complex dimension $n$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n$. 
+In particular, for odd $n$ we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
+When $n$ is even must work with a graded Lie algebra with an odd pairing.
+In any case, we denote the pairing by $\<-,-\>$.
+
+\begin{dfn}
+Let $X, \fg$ be as above.
+{\bf Holomorphic Chern-Simons theory} on $X$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\hCS, Q_\hCS, \omega_\hCS, I_\hCS)$, where the space of fields is given by the Dolbeault complex with coefficients in $\gg$
+\[
+\cE_\hCS = \Omega^{0,\bullet}(X;\gg)[1],
+\]
+$Q_{\hCS} = \dbar$ is the Dolbeault differential, $\omega_\hCS$ is the density-valued pairing
+\[
+\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X,
+\]
+where $\Omega_X$ is the Calabi-Yau structure on $X$, and $I_\hCS$ is the cubic interactional functional
+\[
+I_{\hCS}(\alpha) = \frac 16 \<\alpha \wedge [\alpha, \alpha]\> \wedge \Omega_X .
+\]
+\end{dfn}
+
+\begin{eg} 
+Let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$, and let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
+Define the $\ZZ/2$-graded Lie algebra
+\[
+\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3] 
+\]
+where $\epsilon_i$ are odd formal variables.
+
+There is an odd pairing on $\fg$ defined using the pairing on $\fh$ and the Berezin integral along the odd coordinates:
+\[
+\<X , Y\> = \int_{\CC^{0|3}} \d \epsilon_1 \d \epsilon_2 \d \epsilon_3 \<X, Y\>_\fh 
+\] 
+where $X,Y \in \fg = \fh[\epsilon_i]$.
+
+With this data, holomorphic Chern-Simons on the $2$-fold $X$ with values in $\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3]$ is defined. 
+\brian{check this} In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.
+
+On $X = \CC^2$ with its standard Calabi-Yau form $\Omega_X = \d z_1 \d z_2$ this theory is equivalent to the holomorphic twist of $\cN=4$ super Yang-Mills on $\RR^4$ for the Lie algebra $\fh$.
+
+\end{eg}
 
@@
 
-\newcommand{\hCS}{\mathrm{hCS}}
 \chris{this definition should go elsewhere.  We also need to include a description of the holomorphic supercharge, and something about the trivial $\SU(5)$ twisting homomorphism.}

### 2019-07-17 10d_section_draft.tex
cleaning up and comments

@@
 \input ./combined_macros.sty
-\newcommand{\hCS}{\mathrm{hCS}}
 
@@
 \begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
-Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
+Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
 There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
 \end{lemma}
+\begin{proof}
+The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
+We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
+natural decreasing filtration 
+\[
+F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
+\]
+which is compatible with both $Q$ and $\{I,-\}$ separately.
+The associated graded of this filtration is the differentiable cochain complex given by
+\[
+\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
+\]
+This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
+Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
+\brian{shall we say a word about convergence? This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.}
+\end{proof}
 
@@
 \end{lemma}
+\brian{I think Pavel had something to say for this lemma.}
 
@@
 
-The action functional in 10d super Yang-Mills is given by
+The action functional for super Yang-Mills theory is given by
 \[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
@@
 \end{lemma}
+
+\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
+In any case, I do like that we've stated them clearly.}
 
@@
 \begin{remark}
-This twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $-1$-symplectic pairing.
+From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
 \end{remark}
@@
 The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+\brian{How do we place 10d YM on an arbitrary 5-fold? 
+Are you using something about sugra?
+}
 

### 2019-07-18 10d_section_draft.tex
Replying to Brian's comments

@@
 Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
-\brian{shall we say a word about convergence? This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.}
+\brian{shall we say a word about convergence?
+This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.} \chris{Does convergence require that the interaction is polynomial, or alternatively does this bound the number of differentials appearing in the spectral sequence?}
 \end{proof}
@@
 \brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
-In any case, I do like that we've stated them clearly.}
+In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
 
@@
 Are you using something about sugra?
-}
+} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
+I'm not thinking of using sugra.
+Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
+Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
 

### 2019-07-18 10d_section_draft.tex
Minor comments on dimensional reduction

@@
 
-\chris{By the way, I see no obstruction to proving the following.}
+\chris{By the way, I see no obstruction to proving the following.
+One just needs to check that the action of an infinitesimal symmetry $X$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.}
 \begin{lemma}

### 2019-07-19 paper.tex
Merged 10d material into the main file, and restructured

@@
 
-\section{Preliminaries}
+\section{The BV-BRST Formalism}
 
@@
 
-\subsection{The definition of a field theory}
+\subsection{Classical BV Theories}
 
@@
 
-\subsection{The classical factorization algebra}
+\subsection{The Classical Factorization Algebra}
 
@@
 
-\subsection{Examples}
-
-\pavel{(partially) topological BF theories and Chern-Simons theories in different dimensions.}
-
-\subsubsection{Holomorphic Chern-Simons}
+\subsection{Examples of BV-BRST Theories}
+\subsubsection{Partially Holomorphic Examples}
 
@@
 
-\subsection{Supersymmetry} \label{sec: susy}
+\subsubsection{Yang-Mills Theory}
+Let us now give an example of a theory which is not partially holomorphic.
+We will give a general description of Yang-Mills theory on $\RR^n$, with spinorial matter.
+Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.
+The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
+\begin{itemize}
+\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
+\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
+\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.
+For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.
+\end{itemize}
+These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
+Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.
+
+We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
+\[
+L \;\;\; = \begin{array}{ccccc}
+& \ul{0} & & \ul{1} & \\ 
+& & & & \\
+& \Omega^0(\RR^{n}; \gg) & \to & \Omega^1(\RR^{n}; \gg) \oplus \Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) & 
+\end{array}
+\]
+with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
+
+The action functional for super Yang-Mills theory is given by
+\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
+where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$.
+\chris{Brian suggested defining this notation in the section on supersymmety more broadly.
+I agree.}
+
+We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
+This is the local $L_\infty$-algebra $\fL$ on $\RR^{n}$ whose underlying cochain complex takes the form
+\[
+\xymatrix{
+& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
+\fL & = & \Omega^0(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{n}; \gg) \ar[r]^{\d \ast \d} &\Omega^{n-1}(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^{n}(\RR^{n}; \gg) \\
+& & &\Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{n}(\RR^{n}; \Pi \Sigma^* \otimes \gg), &
+}\]
+with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the evaluation pairing $(-,-)$ between $\Sigma$ and $\Sigma^*$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{n}; \gg)$ on everything along with
+\begin{align*}
+\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
+(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
+\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^0(\RR^{n}; \Sigma \otimes \gg) &\to \Omega^{n}(\RR^{10}; \Sigma* \otimes \gg) \\
+(A \otimes \lambda) &\mapsto \ast \sd A \lambda
+\end{align*}
+in degree 2, and the map
+\begin{align*}
+\ell_3 \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
+(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
+\end{align*}
+in degree 3.
+
+We obtain the BV action by the formula
+\[
+S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
+\]
+where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
+The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.
+
+\subsection{Dimensional Reduction} \label{dim_red_section}
+The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.
+
+\begin{definition}
+Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection.
+Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.
+The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.
+The symplectic pairing is defined as the composite
+\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
+with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.
+The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
+\[\phi \mapsto i^*(Q(p^*(\phi))).\]
+Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}: there is a canonical map defined on an open set $U \sub \RR^m$ by
+\[\sym^k \mc E^\vee(U\times (\RR^m)^\perp) \to \sym^k p^*i^*\mc E^\vee(U\times (\RR^m)^\perp) \iso \sym^k i^*\mc E(U).\]
+\end{definition}
+
+Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.
+
+\begin{prop} \label{dim_red_SUSY_prop}
+The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
+\end{prop}
+
+\begin{proof}
+ \chris{I think this will be straightforward.}
+\end{proof}
+
+\chris{we could alternatively write this in terms of BRST fields.}
+
+\chris{By the way, I see no obstruction to proving the following.
+One just needs to check that the action of an infinitesimal symmetry $X$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.}
+\begin{lemma}
+If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
+\end{lemma}
+
+\section{Supersymmetry} \label{sec: susy}
 
@@
 
-\subsection{Supersymmetric twisting}
+\subsection{Supersymmetric Yang-Mills Theory} \label{SUSY_action_section}
+For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10, so $\Sigma$ is the 2-dimensional Dirac representation $S$, the 4-dimensional Dirac representation $S_+ \oplus S_-$, the 8-dimensional symplectic Weyl representation $S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, and the 16-dimensional Weyl representation $S_+$ respectively.
+We will now proceed to construct this supersymmetry algebra action.
+\chris{can we do it all in one go, using the fact that the 3 $\psi$ rule \cite[Theorem 11]{BaezHuerta} works exactly in these dimensions?
+If not we can just write the calculation out four times.
+We've already started to write it in the 10-dimensional case, though it's incomplete.
+How would you suggest proceeding?}
 
-\begin{dfn}
-A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{dfn}
-
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
-\begin{itemize}
-\item A supercharge $Q$ is {\bf topological} if $d = n$.
-
-\item A supercharge $Q$ is {\bf holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a {\bf holomorphic-topological} (alternatively, partially topological) supercharge.
-The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
-
-\begin{dfn}
-A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{dfn}
-
-We will call $\alpha$ in a twisting datum a {\bf twisting homomorphism}.
-
-\begin{dfn}
-Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{dfn}
-
-\begin{prop}
-The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
-\end{prop}
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
-\end{remark}
-
-\section{Twists}
-
-\subsection{Dimension 10}
-
-Our starting point will be (complexified) 10d super Yang-Mills theory. Fix a complex reductive gauge group $G$ with Lie algebra $\gg$.  
-The ordinary fields of super Yang-Mills theory on $\RR^{10}$ consist of:
-\begin{itemize}
-\item A connection $A \in \Omega^1(\RR^{10} ; \fg)$ on the trivial $G$-bundle;
-\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{10}) \otimes \Pi S_+ \otimes \fg$ of the Weyl spinor bundle associated to the spinor representation $S_+$. 
-\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of the Majorana-Weyl spinor bundle, which necessitates working in Lorentzian signature.
-For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.
-The complexified theory twists to holomorphic Chern-Simons theory with complex gauge group.}.
-\end{itemize}
-These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{10}$. 
-Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{10} ; \fg)$.
-
-We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
-\[
-L \;\;\; = \begin{array}{ccccc}
-& \ul{0} & & \ul{1} & \\ 
-& & & & \\
-& \Omega^0(\RR^{10}; \gg) & \to & \Omega^1(\RR^{10}; \gg) \oplus \Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) & 
-\end{array}
-\]
-with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
-
-The action functional in 10d super Yang-Mills is given by
-\[S(A,\lambda) = \int_{\RR^{10}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
-where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and $(-,-)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).
-\brian{I think we should set up this notation in Section \ref{sec: susy} above, and recount it briefly here.}
-
-We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
-This is the local $L_\infty$-algebra $\fL$ on $\RR^{10}$ whose underlying cochain complex takes the form
-\[
-\xymatrix{
-& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-\fL & = & \Omega^0(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{10}; \gg) \ar[r]^{\d \ast \d} &\Omega^9(\RR^{10}; \gg) \ar[r]^{\d} &\Omega^{10}(\RR^{10}; \gg) \\
-& & &\Omega^0(\RR^{10}; \Pi S_+ \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{10}(\RR^{10}; \Pi S'_- \otimes \gg), &
-}\]
-with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the pairing $(-,-)$ between $S_+$ and $S_-$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{10}; \gg)$ on everything along with
-\begin{align*}
-\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
-(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
-\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^0(\RR^{10}; S_{+} \otimes \gg) &\to \Omega^{10}(\RR^{10}; S_{-} \otimes \gg) \\
-(A \otimes \lambda) &\mapsto \ast \sd A \lambda
-\end{align*}
-in degree 2, and the map
-\begin{align*}
-\ell_3 \colon \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) \otimes \Omega^1(\RR^{10};\gg) &\to \Omega^{9}(\RR^{10};\gg) \\
-(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
-\end{align*}
-in degree 3.
-
-We obtain the BV action by the formula
-\[
-S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
-\]
-where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
-The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.
-
-\subsubsection{The Supersymmetry Action}
-In order to construct an action of the $\mc N=(1,0)$ supersymmetry algebra $\mf A$ on the 10d supersymmetric gauge theory $\fL$, we proceed in two steps.
+We'll start by constructing an action of the $\mc N=(1,0)$ supersymmetry algebra $\mf A$ on the 10d supersymmetric gauge theory $\fL$.  We proceed in two steps.
 \begin{enumerate}
@@
 
-\subsubsection{The Holomorphic Twist}
+\subsection{Supersymmetric twisting}
 
-\chris{this definition should go elsewhere.  We also need to include a description of the holomorphic supercharge, and something about the trivial $\SU(5)$ twisting homomorphism.}
+\begin{dfn}
+A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+\end{dfn}
 
-\begin{definition}
-Let $X$ be a Calabi-Yau variety of odd complex dimension $d$, and let $G$ be a complex reductive group.
-\emph{Holomorphic Chern-Simons theory} is the $\ZZ/2\ZZ$-graded classical field theory $(E_\hCS, Q_\hCS, \omega_\hCS, I_\hCS)$, where $E_\hCS$ is the graded vector bundle $\Omega^{0,\bullet}(X;\gg)$, $Q_{\hCS}$ is the Dolbeault differential, $\omega_\hCS$ is the density-valued pairing associated to the Calabi-Yau structure on $X$ and a choice of invariant pairing on $\gg$, and $I_\hCS$ is the cubic interactional functional
-\[I_{\hCS}(\alpha) = \frac 16 [\alpha \wedge \alpha \wedge \alpha].\]
-\end{definition}
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+\begin{itemize}
+\item A supercharge $Q$ is {\bf topological} if $d = n$.
+
+\item A supercharge $Q$ is {\bf holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a {\bf holomorphic-topological} (alternatively, partially topological) supercharge.
+The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+\begin{dfn}
+A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{dfn}
+
+We will call $\alpha$ in a twisting datum a {\bf twisting homomorphism}.
+
+\begin{dfn}
+Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
+for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+\end{dfn}
+
+\begin{prop}
+The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
+\end{prop}
+\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{remark}
+Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
+\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
+where the $\ZZ/2$-grading on $E$ is the total grading.
+\end{remark}
+
+\section{Twists}
+
+\subsection{Standard Equivalences Between Classical Field Theories}
+In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
+
+\begin{lemma} \label{symplectomorphism_lemma}
+A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
+\end{lemma}
+
+\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
+In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
+
+\begin{lemma} \label{inclusion_and_projection_lemma}
+Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
+\begin{enumerate}
+ \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
+Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
+ \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
+Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
+\end{enumerate}
+\end{lemma}
+
+\begin{lemma} \label{symplectic_composite_lemma}
+Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
+Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
+Then the cochain map
+\begin{equation}
+\label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
+\end{equation}
+obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
+\end{lemma}
+
+\begin{lemma} \label{interaction_pullback_lemma}
+In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
+Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
+Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
+\end{lemma}
+
+\begin{proof}
+We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
+Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
+\end{proof}
+
+\subsection{Dimension 10}
+We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
+In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
+These square-zero supercharges are holomorphic.
+
+Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
+The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
+Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
+The BRST fields split as follows:
+\begin{align*}
+c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
+A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
+\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
+\end{align*}
+
+In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
+\begin{align*}
+S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
+S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
+\end{align*}
+where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
+Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
+It has a quadratic and a cubic component given by
+\begin{align*}
+I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
+I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
+\end{align*}
+The twisted action functional is obtained by adding these terms to the original BV action functional.
+
+We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
 
@@
 
+\begin{remark}
+From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
+\end{remark}
+
 \begin{proof}
-We will first construct a morphism $\iota$ from holomorphic Chern-Simons theory to the twisted theory $\fL^Q$.
-\chris{We split the fields of 10d super Yang-Mills into $\SU(5)$ irreducible representations, so the ghost $c$, then fields $A_{0,1}, A_{1,0}, B, \psi, \chi$ and their antifields, and include $c, A_{0,1}, B, B^\vee, A_{0,1}^\vee, c^\vee$.
-Easy to check that it defines a morphism to the twisted theory.}
+We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
 
-Now, to verify that this morphism is an equivalence as in Definition \ref{equivalence_def}, we must check that the induced morphism 
-\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q + I^{(2)}_{Q\otimes Q},-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
-is a quasi-isomorphism.
-\chris{maybe try filtering the left-hand side by the number of $\chi$ and $\chi^\vee$ fields occuring.
-The 0th filtered piece should coincide with the right-hand side exactly, and maybe we'd like to see that everything else is killed off by some differential in the spectral sequence?}
+\begin{enumerate}
+ \item The first part of our equivalence of classical field theories will be a simple change of variables.
+Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
+In terms of $\chi'$, the quadratic part of the twisted action functional becomes
+ \begin{align*}
+  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
+  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
+ \end{align*}
+ The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
+However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
+Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
+We think of this as ``integrating out'' the field $\chi'$ and its antifield.
 
+ \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
+We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
+ \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
+ We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
+This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
+\chris{This isn't quite right I think.
+We need to kill that term, however, for the below argument to work.
+Can we fix it?}
+
+ Observe that the classical BV complex associated to this action functional can now be written in the following form:
+ \[\xymatrix{
+ &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
+ \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
+ \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
+ }\]
+ where the first and third rows are dual under the symplectic pairing.
+This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
+the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
+
+ \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
+The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
+In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
+Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
+The resulting interaction is
+ \[
+  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
+ \]
+ which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
+The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
+
+ \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
+The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
+Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
+an equivalence of classical field theories.
+\end{enumerate}
 \end{proof}
+
+The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+\brian{How do we place 10d YM on an arbitrary 5-fold? 
+Are you using something about sugra?
+} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
+I'm not thinking of using sugra.
+Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
+Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
 
@@
 
+\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
+Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
+There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
+\end{lemma}
+\begin{proof}
+The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
+We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
+natural decreasing filtration 
+\[
+F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
+\]
+which is compatible with both $Q$ and $\{I,-\}$ separately.
+The associated graded of this filtration is the differentiable cochain complex given by
+\[
+\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
+\]
+This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
+Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
+\brian{shall we say a word about convergence?
+This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.} \chris{Does convergence require that the interaction is polynomial, or alternatively does this bound the number of differentials appearing in the spectral sequence?}
+\end{proof}
+
+\begin{lemma} \label{invert_quis_lemma}
+Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
+\end{lemma}
+\brian{I think Pavel had something to say for this lemma.}
+
 \section{$\infty$ algebra}

### 2019-07-19 paper.tex
BRST

@@
 \subsection{From BRST to BV}
+
+\begin{dfn}
+A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
+\begin{itemize}
+\item a $\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item a differential operator
+\[
+Q_{BRST} : \cF \to \cF^!  ;
+\]
+\item a local functional $I_{BRST} \in \oloc^+(\cF)$ of polynomial degree $\geq 3$.
+\end{itemize}
+Together, this data must satisfy the master equation
+\[
+[\d_{CE}, Q_{BRST}] + \d_{CE} I_{BRST} = 0 .
+\]
+\brian{even separately, I suppose?}
+\end{dfn}
+
+One can think of the space of field $\cF$ as a (linear) graded manifold.
+In doing so, the $L_\infty$ structure on $\cF[-1]$ determines a vector field $X$ of cohomological degree $+1$ on this graded manifold. 
+The operator $Q$ determines a one-form on $\cF$, and the master equation says that this one-form vanish along the vector field $X$. 
+Similarly, the condition $\d_{CE} I = 0$ means the function $I$ on $\cF$ vanish along $X$.
+
+From a classical BRST theory $(\cF, Q_{BRST}, I_{BRST})$, one can construct a classical BV theory as follows. 
+Let $\{\ell_k\}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
+
+First, we define the free BV theory. 
+This will only use the linear operation on the $L_\infty$ algebra $\cF$, and the operator $Q_{BRST}$. 
+The underlying bundle of the BV theory is
+\[
+E = F \oplus F^! [-1] = F \oplus F^* \otimes {\rm Dens}_M .
+\]
+The differential of the free BV theory is
+\[
+Q = \ell_1 + Q_{BRST} .
+\]
+The BV pairing is defined by the composition
+\[
+E \otimes E = (F \oplus F^![-1]) \otimes (F \oplus F^![-1]) \to F \otimes F^! [-1] \oplus F^![-1] \otimes F \to {\rm Dens}_M [-1] .
+\]
+In the first arrow, we have used the obvious projection. 
+The second arrow is given by the evaluation pairing between $F$ and $F^*$. 
+The data $(\cE, Q, \omega)$ defines a free BV theory.
+
+The interacting theory is constructed as follows.
+First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p : \cE = \cF \oplus \cF^![-1] \to \cF$.
+These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
+\[
+I_{F} (e) = \sum_{k \geq 2} \int_M \frac{1}{(k+1)!} \omega(e, (p^*\ell_k) (e, \ldots, e)) . 
+\] 
+Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
+\[
+I_{BV} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
+\]
+
+\begin{lemma}
+Given a classical BRST theory $(F, Q_{BRST}, I_{BRST})$, the data $(E, Q, \omega, I) = (F \oplus F^![-1] , \ell_1 + Q_{BRST} , I_{BV})$ defines a classical BV theory.
+That is, the BV classical master equation
+\[
+Q I + \frac{1}{2} \{I, I\} = 0 \iff (Q + \ell_1) (I_F + p^*I_{BRST}) + \frac{1}{2} \{I_F + p^*I_{BRST}, I_F + p^*I_{BRST}\} = 0
+\]
+holds.
+We refer to this classical BV theory as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+\end{lemma}
 

### 2019-07-19 paper.tex
BF

@@
 \]
+where $\d_{CE}$ is the Chevalley-Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
 \brian{even separately, I suppose?}
@@
 
+We can unwrap this definition as follows. 
 One can think of the space of field $\cF$ as a (linear) graded manifold.
@@
 \]
-The BV pairing is defined by the composition
+The BV pairing $\omega_{F}$ is defined by the composition
 \[
@@
 \]
-In the first arrow, we have used the obvious projection. 
+The first arrow is the obvious projection. 
 The second arrow is given by the evaluation pairing between $F$ and $F^*$. 
-The data $(\cE, Q, \omega)$ defines a free BV theory.
+It's immediate to check that the data $(\cE, Q, \omega)$ defines a free BV theory.
 
@@
 \[
-I_{F} (e) = \sum_{k \geq 2} \int_M \frac{1}{(k+1)!} \omega(e, (p^*\ell_k) (e, \ldots, e)) . 
+I_{F} (e) = \sum_{k \geq 2} \int_M \frac{1}{(k+1)!} \omega_F(e, (p^*\ell_k) (e, \ldots, e)) . 
 \] 
@@
 \begin{lemma}
-Given a classical BRST theory $(F, Q_{BRST}, I_{BRST})$, the data $(E, Q, \omega, I) = (F \oplus F^![-1] , \ell_1 + Q_{BRST} , I_{BV})$ defines a classical BV theory.
+Given a classical BRST theory $(F, Q_{BRST}, I_{BRST})$, the data $(E, Q, \omega, I) = (F \oplus F^![-1] , \ell_1 + Q_{BRST} , \omega_F, I_{BV})$ defines a classical BV theory.
 That is, the BV classical master equation
@@
 
-\pavel{explain how to get a BV theory from a BRST theory}
+\begin{proof}
+\brian{shouldn't be hard...}
+\end{proof}
 
@@
 \subsection{Examples of BV-BRST Theories}
-\subsubsection{Partially Holomorphic Examples}
+
+\brian{should we make these definitions, recollections, or just conventions?}
+
+If $M$ is a smooth manifold, its {\em de Rham stack}, as a dg ringed space, is 
+\[
+M_{\rm dR} = \left(M , (\Omega^*_M, \d_{\rm dR})\right) .
+\]
+
+If $X$ is a complex manifold, there are two naturally associated dg ringed spaces that will be important for us. 
+The first is the $\dbar$-{\em stack}, defined by
+\[
+X_{\dbar} = \left(M , (\Omega^{0,*}_X, \dbar) \right) .
+\]
+The next is the {\em Dolbeault stack}, defined by
+\[
+X_{\rm Dol} = \left(M, (\Omega^{*,*}_X, \dbar)\right) .
+\] 
+Note that as sheaves of dg modules, there is a quasi-isomorphism $(\Omega^{p,*}_M, \dbar) = \Omega^{p, hol}_M$.
+Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.
+
+\subsubsection{Mixed holomorphic/topological BF theory}
+
+\begin{dfn}
+Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
+Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
+The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
+\[
+\cF[-1] = \Omega^{0,*}_X \Hat{\otimes} \Omega^{*,*}_Y \Hat{\otimes} \Omega^*_M \otimes \fg .
+\] 
+The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative products on differential forms. 
+This is a classical BRST theory by choosing $Q_{BRST} = 0, I_{BRST} = 0$. 
+In other words, $\cF$ is defined by the mapping stack
+\[
+{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
+\]
+
+The {\bf mixed holomorphic-Dolbeault-topological BF theory} is the BV theory given by the $(-1)$-shifted cotangent bundle to $\cF$.
+
+\end{dfn}
+
+\subsubsection{Mixed holomorphic/topological Chern-Simons theory}
+
+The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. 
+Unlike the examples of mixed BF theory above, these BV theories do not arise, in general, as shifted cotangent bundles.
 

### 2019-07-21 paper.tex
small changes

@@
 The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
-\[
+\begin{equation}\label{bvcplx}
 \left(\cO(\cE), Q + \{I,-\}\right) .
-\]
+\end{equation}
 In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
@@
 
-Let $(E, Q, \omega, I)$ be a classical field theory and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
-Then, we recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime that should be thought of as  functions on the formal neighborhood of the derived critical locus of the action $S$ near $\psi_0$.
+Let $(E, Q, \omega, I)$ be a classical BV theory. 
+%and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
+We recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime.
 
@@
 
-Notice that the BV complex we defined in the previous section is simply the global sections of the factorization algebra along $M$.
+Notice that the BV complex we defined in the previous section, Equation (\ref{bvplx}), is the global sections of the factorization algebra along $M$.
+The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
+It makes sense to restrict fields to any open set $U \subset M$. 
+Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.
+
+The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in Proposition ?? of \cite{CG2}.
 
@@
 \[
-M_{\rm dR} = \left(M , (\Omega^*_M, \d_{\rm dR})\right) .
+M_{\rm dR} = \left(M , (\Omega^\bu_M, \d_{\rm dR})\right) .
 \]
@@
 \[
-X_{\dbar} = \left(M , (\Omega^{0,*}_X, \dbar) \right) .
+X_{\dbar} = \left(M , (\Omega^{0,\bu}_X, \dbar) \right) .
 \]
@@
 \[
-X_{\rm Dol} = \left(M, (\Omega^{*,*}_X, \dbar)\right) .
+X_{\rm Dol} = \left(M, (\Omega^{\bu,\bu}_X, \dbar)\right) .
 \] 
@@
 \[
-\cF[-1] = \Omega^{0,*}_X \Hat{\otimes} \Omega^{*,*}_Y \Hat{\otimes} \Omega^*_M \otimes \fg .
-\] 
-The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative products on differential forms. 
-This is a classical BRST theory by choosing $Q_{BRST} = 0, I_{BRST} = 0$. 
+\cF[-1] = \Omega^{0,\bu}_X \Hat{\otimes} \Omega^{\bu,\bu}_Y \Hat{\otimes} \Omega^\bu_M \otimes \fg .
+\] 
+The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative product on differential forms. 
+This is a classical BRST theory by choosing $Q_{BRST} = 0$ and $I_{BRST} = 0$. 
 In other words, $\cF$ is defined by the mapping stack
@@
 The {\bf mixed holomorphic-Dolbeault-topological BF theory} is the BV theory given by the $(-1)$-shifted cotangent bundle to $\cF$.
-
-\end{dfn}
+\end{dfn}
+
+Unpacking the definition \brian{unpack and write out action explicitly?}
 
@@
 
-Fix a Calabi-Yau manifold $X$ of complex dimension $n$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n$. 
-In particular, for odd $n$ we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
-When $n$ is even must work with a graded Lie algebra with an odd pairing.
-In any case, we denote the pairing by $\<-,-\>$.
-
-\begin{dfn}
-Let $X, \fg$ be as above.
-{\bf Holomorphic Chern-Simons theory} on $X$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\hCS, Q_\hCS, \omega_\hCS, I_\hCS)$, where the space of fields is given by the Dolbeault complex with coefficients in $\gg$
-\[
-\cE_\hCS = \Omega^{0,\bullet}(X;\gg)[1],
-\]
-$Q_{\hCS} = \dbar$ is the Dolbeault differential, $\omega_\hCS$ is the density-valued pairing
-\[
-\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X,
-\]
-where $\Omega_X$ is the Calabi-Yau structure on $X$, and $I_\hCS$ is the cubic interactional functional
+Fix a Calabi-Yau manifold $X$ of {\em complex} dimension $n$, a smooth manifold of {\em real} dimension $m$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n+m$.
+In particular, if $n+m$ is odd, we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
+When $n+m$ is even, we must work with a graded Lie algebra with an odd pairing.
+In any case, we denote the pairing on $\fg$ by $\<-,-\>$.
+
+\begin{dfn}
+Let $X, M$, and $\fg$ be as above.
+{\bf Mixed Chern-Simons theory} on $X \times M$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\mCS, Q_\mCS, \omega_\mCS, I_\mCS)$, where the space of fields is given by
+\[
+\cE_\mCS = \Omega^{0,\bullet}(X) \Hat{\otimes} \Omega^\bu(M) \otimes \fg [1] .
+\]
+The linear part of the BV differential is
+\[
+Q_{\mCS} = \dbar \otimes 1 \otimes 1 + 1 \otimes \otimes 1 \otimes \d_{\dR}
+\]
+where $\dbar$ is the Dolbeault differential on $X$, and $\d_{\dR}$ is the de Rham differential on $M$.
+The pairing $\omega_\hCS$ is
+\[
+\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X ,
+\]
+where $\Omega_X$ is the Calabi-Yau structure on $X$.
+Finally, the interaction $I_\hCS$ is
 \[
@@
 \]
-\end{dfn}
+As a mapping stack, mixed Chern-Simons is given by
+\[
+{\rm Map} (X_{\dbar} \times M_{\dR} , B \fg) .
+\]
+
+\end{dfn}
+
+By convention, when $X$ is the trivial complex manifold we take $\Omega_X = 1$.
 
 \begin{eg}
-Let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$, and let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
+The most basic  example is to take $X$ trivial and $\dim_{\RR} (M) = 3$.
+Then we obtain ordinary Chern-Simons theory on $M$. 
+Of course, this theory admits an obvious lift to a $\ZZ$-graded BV theory. 
+\end{eg}
+
+\begin{eg} 
+Now, take $M$ to be trivial and let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$.
+Since $n + m = 2$ is even, we must take a graded Lie algebra with odd pairing. 
+First, let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
 Define the $\ZZ/2$-graded Lie algebra
@@
 With this data, holomorphic Chern-Simons on the $2$-fold $X$ with values in $\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3]$ is defined.
-\brian{check this} In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.
+In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.
 

### 2019-07-24 paper.tex
appendix

@@
 
+\subsection{Differentiable vector spaces}
+\def\Mfld{{\rm Mfld}}
+
+Let $\Mfld$ denote the site of smooth manifolds (of arbitrary dimension) where the morphisms are smooth maps, and a cover $f : X \to Y$ is a surjective local diffeomorphism.
+
+\begin{dfn} 
+We use the following notations and naming conventions for sheaves on $\Mfld$:
+\begin{itemize}
+\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
+\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
+\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
+If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
+\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
+\[
+\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
+\]
+for every smooth manifold $X$, which is required to be natural under pullbacks:
+\[
+f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
+\]
+for every smooth map $f : X \to Y$. 
+A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
+\end{itemize}
+\end{dfn}
+
 \subsection{Homological algebra}
 
-\brian{can't do cokernels in CVS, blah blah}
-
 There is a functor
 \[
-dif_c : \CVS \to \DVS .
-\]
+dif_c : \CVS \to \DVS 
+\]
+from the category of convenient vector spaces to the category of differentiable vector spaces. 
+This functor does not preserve cokernels, so $dif_c$ does not preserve cohomology. 
+In particular, with a naive definition of quasi-isomorphism internal to $\CVS$, the functor $dif_c$ does not preserve quasi-isomorphisms. 
+To avoid this issue, we make the following definition.
 
@@
 
-\begin{dfn}
-A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
-\[
-\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
-\]
-where each map is a monomorphism in each cohomological degree. 
-A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
-\end{dfn}
+The cochain complexes arising in classical field theory are naturally convenient vector spaces. 
+The above definition is used in what we mean by quasi-isomorphism between classical field theories, as in Definition \brian{??}.
+
+Throughout the paper we make use of familiar manipulations with spectral sequences arising from filtrations of cochain complexes internal to differentiable vector spaces. 
+A main tool is the classical Eilenberg-Moore comparison theorem, which is stated as follows.
 
@@
 
+The following is the natural definition of a filtered differentiable cochain complex.
+
+\begin{dfn}
+A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
+\[
+\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
+\]
+where each map is a monomorphism in each cohomological degree. 
+A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
+\end{dfn}
+
 The category of differentiable vector space is an AB4 category, in fact, it is actually a Grothendieck abelian category.
@@
 
+\subsubsection{The classical BV complex}
+
 \begin{lem}
@@
 \end{lem}
+
+The above lemma used the natural filtration on the classical BV complex given by polynomial degree of observables. 
+Since the free part of the differential $Q$ always preserves this filtration, the first term of the resulting spectral sequence simply computes the cohomology of the underlying free theory. 
+The differential on the higher pages depend on the interacting part of of the action.
 
@@
 \begin{lemma} \label{invert_quis_lemma}
-Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
+Any quasi-isomorphism of differentiable cochain complexes admits a quasi-inverse.
 \end{lemma}

### 2019-08-06 paper.tex
Started some notes on 9d, also some minor rearrangements and comments

@@
 
-\tikzstyle{s16} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=red!30]
+\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
-\tikzstyle{s4} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
-\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=green!30]
-\tikzstyle{dimension} = [ellipse, text centered, text width=1cm, minimum height=1cm, draw=black]
+\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
+\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
+\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
 \tikzstyle{arrow} = [thick,->,>=stealth]
@@
 Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
-The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
+The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} \chris{I don't really understand why this thing needs a name, since it's only a theory in a trivial way, with zero action.
+Why not just call this thing $\cF$, call its shifted cotangent something like ``generalized BF theory'', then if $\fg$ has a pairing call the theory built out of $\cF$ with its AKSZ structure something like ``generalized Chern-Simons theory'' (I'm brainstorming other names too: e.g.
+``Hodge-Chern-Simons theory'')?
+Or do you want to reserve the name Chern-Simons for the case where $\fg$ is a Lie algebra, not an $L_\infty$ algebra?} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
 \[
@@
 
-\subsection{Standard Equivalences Between Classical Field Theories}
-In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
-
-\begin{lemma} \label{symplectomorphism_lemma}
-A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
-\end{lemma}
-
-\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
-In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
-
-\begin{lemma} \label{inclusion_and_projection_lemma}
-Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
-\begin{enumerate}
- \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
-Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
- \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
-Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
-\end{enumerate}
-\end{lemma}
-
-\begin{lemma} \label{symplectic_composite_lemma}
-Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
-Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
-Then the cochain map
-\begin{equation}
-\label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
-\end{equation}
-obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
-\end{lemma}
-
-\begin{lemma} \label{interaction_pullback_lemma}
-In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
-Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
-Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
-\end{lemma}
-
-\begin{proof}
-We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
-Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
-\end{proof}
-
-\subsection{Dimension 10}
-We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
-In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
-These square-zero supercharges are holomorphic.
-
-Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
-The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
-Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
-The BRST fields split as follows:
-\begin{align*}
-c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
-A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
-\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
-\end{align*}
-
-In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
-\begin{align*}
-S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
-S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
-\end{align*}
-where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
-Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
-It has a quadratic and a cubic component given by
-\begin{align*}
-I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
-I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
-\end{align*}
-The twisted action functional is obtained by adding these terms to the original BV action functional.
-
-We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
-
-\begin{theorem}
-The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
-\end{theorem}
-
-\begin{remark}
-From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
-\end{remark}
-
-\begin{proof}
-We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
-
-\begin{enumerate}
- \item The first part of our equivalence of classical field theories will be a simple change of variables.
-Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
-In terms of $\chi'$, the quadratic part of the twisted action functional becomes
- \begin{align*}
-  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
-  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
- \end{align*}
- The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
-However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
-Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
-We think of this as ``integrating out'' the field $\chi'$ and its antifield.
-
- \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
-We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
- \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
-This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
-\chris{This isn't quite right I think.
-We need to kill that term, however, for the below argument to work.
-Can we fix it?}
-
- Observe that the classical BV complex associated to this action functional can now be written in the following form:
- \[\xymatrix{
- &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
- \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
- \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
- }\]
- where the first and third rows are dual under the symplectic pairing.
-This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
-the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
-
- \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
-In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
-Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
-The resulting interaction is
- \[
-  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
- \]
- which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
-The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
-
- \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
-The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
-Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
-an equivalence of classical field theories.
-\end{enumerate}
-\end{proof}
-
-The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-\brian{How do we place 10d YM on an arbitrary 5-fold? 
-Are you using something about sugra?
-} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
-I'm not thinking of using sugra.
-Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
-Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
-
-\subsection{Dimension 9}
-
-% \cN=1 SYM
-
-\subsection{Dimension 8}
-
-% \cN=1 SYM
-
-\subsection{Dimension 7}
-
-% \cN=1 SYM
-
-\subsection{Dimension 6}
-
-% \cN=(1, 1) SYM
-
-% \cN=(1, 0) SYM with matter in a pseudo-real representation. Construct the L_infinity action of supersymmetry
-
-\subsection{Dimension 5}
-
-% \cN=2 SYM
-% \cN=1 SYM with matter in a pseudo-real representation.
-
-\subsection{Dimension 4}
-
-% \cN=4 SYM
-% \cN=2 SYM with matter in a pseudo-real representation
-% \cN=1 SYM with matter in a complex representation
-
-\subsubsection{$\cN=1$ SYM with matter}
-
-Let $R$ be a complex representation of $\mf g$.
-
-The matter sector of the theory is labeled by the BRST fields:
-\begin{itemize}
-\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
-\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
-\end{itemize} 
-which together define the (abelian) local Lie algebra
-\[
-\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
-\]
-\subsection{Dimension 3}
-
-% \cN=8 SYM
-% \cN=4 SYM with matter in a pseudo-real representation
-% \cN=2 SYM with matter in a complex representation
-
-\subsection{Dimension 2}
-
-% \cN=(8, 8) SYM
-% \cN=(4, 4) SYM with matter in a pseudo-real representation
-% \cN=(2, 2) SYM with matter in a complex representation
-%BRIAN FIND REFERENCE OF BELOW
-% \cN=(0,2) SYM with matter 
-% \cN=(0,4) SYM with matter
-% \cN=(0,8) SYM with matter
-
-\pagestyle{bib}
-\printbibliography
-
-\begin{landscape}
+%\begin{landscape}
 \begin{figure}
-\begin{tikzpicture}[node distance=0.5cm and 0.5cm, text width=2cm]
-\node (101) [s16chiral] {Rank $(1, 0)$. $d=5$};
-\node (91) [s16, below=of 101] {Rank $1$. $d=5$};
-\node (82) [s16, below=of 91] {Rank $(1, 1)$. $d=5$};
-\node (81) [s16, left=of 82] {Rank $(1, 0)$. $d=4$};
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
 \node (825) [right=of 82] {};
-\node (83) [s16, right=of 825] {Rank $(1, 0)$. $d=8$};
-\node (71) [s16, below=of 81] {Rank $1$. $d=4$};
-\node (72) [s16, below=of 82] {Rank $2$. $d=5$};
-\node (73) [s16, below=of 83] {Rank $1$. $d=7$};
-\node (62) [s16, below=of 71] {Rank $(1, 1)$. $d=4$};
-\node (61) [s8, left=of 62] {Rank $(1, 0)$. $d=3$};
-\node (63) [s16, below=of 72] {Rank $(2, 2)$. $d=5$};
-\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$. $d=5$};
-\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$. $d=6$};
-\node (51) [s8, below=of 61] {Rank $1$. $d=3$};
-\node (52) [s16, below=of 62] {Rank $2$. $d=4$};
-\node (53) [s16, below=of 63] {Rank $4$. $d=5$};
-\node (54) [s16, below=of 64] {Rank $2$. $d=5$};
-\node (42) [s8, below=of 51] {Rank $(1, 1)$. $d=3$};
-\node (41) [s4, left=of 42] {Rank $(1, 0)$. $d=2$};
-\node (43) [s16, right=of 42] {Rank $(2, 2)$. $d=4$};
-\node (44) [s16, right=of 43] {Rank $(2, 1)$. $d=4$};
-\node (45) [s8, right=of 44] {Rank $(2, 0)$. $d=4$};
-\node (31) [s4, below=of 41] {Rank $1$. $d=2$};
-\node (32) [s8, below=of 42] {Rank $2$. $d=3$};
-\node (22) [s4, below=of 31] {Rank $(1, 1)$. $d=2$};
-\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$. $d=1$};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
 
@@
 \end{figure}
-\end{landscape}
+%\end{landscape}
+
+\subsection{Standard Equivalences Between Classical Field Theories}
+In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
+
+\begin{lemma} \label{symplectomorphism_lemma}
+A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
+\end{lemma}
+
+\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
+In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
+
+\begin{lemma} \label{inclusion_and_projection_lemma}
+Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
+\begin{enumerate}
+ \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
+Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
+ \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
+Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
+\end{enumerate}
+\end{lemma}
+
+\begin{lemma} \label{symplectic_composite_lemma}
+Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
+Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
+Then the cochain map
+\begin{equation}
+\label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
+\end{equation}
+obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
+\end{lemma}
+
+\begin{lemma} \label{interaction_pullback_lemma}
+In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
+Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
+Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
+\end{lemma}
+
+\begin{proof}
+We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
+Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
+\end{proof}
+
+\subsection{Dimension 10}
+We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
+In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
+These square-zero supercharges are holomorphic.
+
+Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
+The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
+Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
+The BRST fields split as follows:
+\begin{align*}
+c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
+A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
+\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
+\end{align*}
+
+In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
+\begin{align*}
+S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
+S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
+\end{align*}
+where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
+Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
+It has a quadratic and a cubic component given by
+\begin{align*}
+I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
+I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
+\end{align*}
+The twisted action functional is obtained by adding these terms to the original BV action functional.
+
+We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
+
+\begin{theorem}\label{10d_twist_thm}
+The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
+\end{theorem}
+
+\begin{remark}
+From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
+\end{remark}
+
+\begin{proof}
+We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
+
+\begin{enumerate}
+ \item The first part of our equivalence of classical field theories will be a simple change of variables.
+Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
+In terms of $\chi'$, the quadratic part of the twisted action functional becomes
+ \begin{align*}
+  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
+  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
+ \end{align*}
+ The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
+However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
+Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
+We think of this as ``integrating out'' the field $\chi'$ and its antifield.
+
+ \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
+We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
+ \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
+ We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
+This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
+\chris{This isn't quite right I think.
+We need to kill that term, however, for the below argument to work.
+Can we fix it?}
+
+ Observe that the classical BV complex associated to this action functional can now be written in the following form:
+ \[\xymatrix{
+ &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
+ \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
+ \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
+ }\]
+ where the first and third rows are dual under the symplectic pairing.
+This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
+the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
+
+ \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
+The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
+In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
+Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
+The resulting interaction is
+ \[
+  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
+ \]
+ which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
+The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
+
+ \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
+The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
+Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
+an equivalence of classical field theories.
+\end{enumerate}
+\end{proof}
+
+The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+\brian{How do we place 10d YM on an arbitrary 5-fold? 
+Are you using something about sugra?
+} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
+I'm not thinking of using sugra.
+Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
+Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
+
+\subsection{Dimension 9}
+The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
+It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.
+
+\chris{There is a single non-zero class of square zero supercharges in 9d, which are minimal (i.e. have 5d image).  They are stabilized by $\SU(4)$.  The twisted theory is only $\ZZ/2\ZZ$-graded.}
+
+\begin{theorem}
+The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
+\end{theorem}
+
+The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.  These fields, in the BRST formalism, decompose as
+\begin{align*}
+B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
+A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
+\end{align*}
+along with the ghost $c$. \chris{can prove the theorem by the same argument as in 10d, or using dimensional reduction.}
+
+\subsection{Dimension 8}
+
+% \cN=1 SYM, three twists
+
+\subsection{Dimension 7}
+
+% \cN=1 SYM, three twists identical to dimension 8
+
+\subsection{Dimension 6}
+
+% \cN=(1, 1) SYM, three twists identical to dimension 8
+
+% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.
+
+\subsection{Dimension 5}
+
+% \cN=2 SYM, three twists
+% \cN=1 SYM with matter in a pseudo-real representation, one twist.
+
+\subsection{Dimension 4}
+
+% \cN=4 SYM
+% \cN=2 SYM with matter in a pseudo-real representation
+% \cN=1 SYM with matter in a complex representation
+
+\subsubsection{$\cN=1$ SYM with matter}
+
+Let $R$ be a complex representation of $\mf g$.
+
+The matter sector of the theory is labeled by the BRST fields:
+\begin{itemize}
+\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
+\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
+\end{itemize} 
+which together define the (abelian) local Lie algebra
+\[
+\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
+\]
+\subsection{Dimension 3}
+
+% \cN=8 SYM
+% \cN=4 SYM with matter in a pseudo-real representation
+% \cN=2 SYM with matter in a complex representation
+
+\subsection{Dimension 2}
+
+% \cN=(8, 8) SYM
+% \cN=(4, 4) SYM with matter in a pseudo-real representation
+% \cN=(2, 2) SYM with matter in a complex representation
+%BRIAN FIND REFERENCE OF BELOW
+% \cN=(0,2) SYM with matter 
+% \cN=(0,4) SYM with matter
+% \cN=(0,8) SYM with matter
 
@@
 
+\pagestyle{bib}
+\printbibliography
+
 \end{document}

### 2019-08-06 paper.tex
Started some notes on 9d, also some minor rearrangements and comments
Added some comments on proving supersymmetry for SYM

@@
 \begin{prop}
-Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here}.
+Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
+On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
+To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}.
 The functional
@@
 Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
+
+\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.
+Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
 \end{proof}
@@
 \end{remark}
+
+\subsection{Twisting Homomorphisms and Curved Backgrounds}
 

### 2019-08-07 paper.tex
Editing SYM section

@@
 \subsection{Supersymmetric Yang-Mills Theory} \label{SUSY_action_section}
-For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10, so $\Sigma$ is the 2-dimensional Dirac representation $S$, the 4-dimensional Dirac representation $S_+ \oplus S_-$, the 8-dimensional symplectic Weyl representation $S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, and the 16-dimensional Weyl representation $S_+$ respectively.
-We will now proceed to construct this supersymmetry algebra action.
-\chris{can we do it all in one go, using the fact that the 3 $\psi$ rule \cite[Theorem 11]{BaezHuerta} works exactly in these dimensions?
-If not we can just write the calculation out four times.
-We've already started to write it in the 10-dimensional case, though it's incomplete.
-How would you suggest proceeding?}
-
-We'll start by constructing an action of the $\mc N=(1,0)$ supersymmetry algebra $\mf A$ on the 10d supersymmetric gauge theory $\fL$.  We proceed in two steps.
+For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10.
+In this subsection we will construct these supersymmetry algebra actions.
+
+In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
+\begin{itemize}
+ \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
+ \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
+ \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
+ \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
+\end{itemize}
+We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
 \begin{enumerate}
- \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the Poincar\'e algebra by isometries of $\RR^{10}$ \chris{define this above}, which is only well-defined on-shell.
+ \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.
 In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
@@
 \end{enumerate}
-
-Since this is our first example, we will work through it in some detail, in order to motivate the formul\ae{} that will recur in later examples.
-The fermionic piece of the supersymmetry algebra is defined by saying that $Q \in S_+$ acts infinitesimally by
+This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.
+In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.
+Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
+%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
+
+\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
+The multilinear map 
+\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
+obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
+\end{theorem}
+
+We'll begin with a discussion of the on-shell supersymmetry action, discuss its failure to close off-shell, and then derive the $L_\infty$-correction to this failure.
+Then we'll state and prove the main theorem of this section: the fact that our super Yang-Mills theories are supersymmetric.
+
+So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
 \[
@@
 Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
-
+We can check that this supersymmetry action does not close off-shell.
+Indeed \chris{...}
+
+\chris{heavily edit the below.}
 \begin{lemma} \label{10d_onshell_lemma}
@@
 \begin{definition}
-The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{10}$ is defined to be the cochain
+The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
 \[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
@@
 \begin{prop}
-Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra \chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
-On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
-To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}.
-The functional
+Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
 \[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
@@
 \end{prop}
+
+\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
+On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
+To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}
 

### 2019-08-13 paper.tex
Continuing edits to SYM section

@@
 
-\brian{recall dfn of $\oloc$ of a gr vb.}
+\brian{recall dfn of $\oloc$ of a gr vb.} \chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}
 
@@
 
-\begin{dfn}
+\begin{dfn} \label{infinitesimal_action_def}
 Let $(E, Q,\omega, I)$ be a classical field theory 
@@
 \]
-\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
+\brian{maybe point to appendix where we can fix conventions for $\infty$-maps} \chris{Can we also give the definition here of an equivariant classical field theory in terms of the Maurer-Cartan / equivariant classical master equation?}
 \end{dfn}
@@
 We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes.
+\chris{below we define it in terms of an interaction with components $I^{(1)}, I^{(2)}$ etc, so we should give that point of view here as well.}
 
@@
 
+We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.
+
+\begin{definition}
+The $n$-dimensional \emph{Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.
+The $n$-dimensional \emph{Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
+\end{definition}
+
+The $n$-dimensional Poincar\'e algebra acts, in the sense of definition \ref{infinitesimal_action_def}, on Yang-Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
+\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}
+
+\begin{prop} \label{YM_Poincare_invariant_prop}
+Yang-Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
+\[\d_{\mr{Lie}}I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\}.\]
+\end{prop}
+
+\begin{proof}
+\chris{...}
+\end{proof}
+
 \subsection{Dimensional Reduction} \label{dim_red_section}
@@
 \end{itemize}
+
+\begin{definition}
+In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
+\end{definition}
+
 We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
@@
 Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
-%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
-
-\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
+
+\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
 The multilinear map 
@@
 \end{align*}
-Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
-We can check that this supersymmetry action does not close off-shell.
-Indeed \chris{...}
-
-\chris{heavily edit the below.}
-\begin{lemma} \label{10d_onshell_lemma}
-Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
+Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.
+
+\begin{lemma} \label{onshell_action_lemma}
+Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
 The following relations hold:
@@
 \begin{proof}
+\chris{todo:rewrite}
 Both are direct calculations using standard Clifford relations which cite below.
@@
 \begin{align*}
-\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
+\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
 Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
@@
 
-We'll rewrite this as a local functional in the theory $\fL$ coupled to the $\mc N=(1,0)$ super Lie algebra $\mf A$.
+We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.
 
@@
 
-\begin{prop}
+We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
+\begin{lemma} \label{onshell_interaction_lemma}
+The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
+\[\{I^{(1)},I^{(1)}\} = - 2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\end{lemma}
+
+\begin{proof}
+This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed \chris{...}
+\end{proof}
+
+The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
+\begin{lemma} \label{SUSY_rotation_invariance_lemma}
+Let $I_{\mr{rot}}$ be the interaction associated to the action of $\so(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
+The functionals $I^{(1)}$ and $I^{(2)}$ are rotation invariant, meaning that
+\[\d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},\]
+for $i=1,2$.
+\end{lemma}
+
+\begin{proof}
+\chris{...}
+\end{proof}
+
+Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.
+
+\begin{theorem} \label{SUSY_YM_theorem}
 Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
-\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
+\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
 satisfies the Maurer-Cartan equation
 \begin{equation} 
-\label{10d_MC}
-(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
+\label{nd_MC}
+(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
 \end{equation}
-\end{prop}
-
-\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
-On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
-To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}
+\end{theorem}
 
 \begin{proof}
-We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
+We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
 \begin{align}
-\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
-&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
-&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
-&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
-&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
+\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
+&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
+&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
+&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
+&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
 \end{align}
-Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.
+Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
 The remaining terms are those involving the action of supersymmetries.
 
-First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.
-First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.
-Then \ref{10d_MC_1} is zero by Baez--Huerta.
-Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}.
-Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.
-Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
-
-\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.
-Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
+First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.  Baez and Huerta prove that in our four critical dimensions \chris{argue why this is the same}.
+
+In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.
+Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.
+Indeed \chris{...}.
+
+Finally, term \ref{MC_4} vanishes because the interaction $I^{(2)}$ only involves antifields: the BV antibracket of two expressions involving only antifields is always zero.
 \end{proof}
+
+\chris{Discuss dimensional reduction, and then the inclusion of the action of R-symmetries.}
 

### 2019-08-13 paper.tex
Continuing edits to SYM section

@@
 Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.
-Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
+Similarly we can calculate, (as in \cite{Guillen}):
 \begin{align*}
@@
 \[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
-as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
+as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
 \begin{align*}
@@
 \[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
-where 
+where \chris{sign}
 \begin{align*}
@@
 \begin{lemma} \label{SUSY_rotation_invariance_lemma}
-Let $I_{\mr{rot}}$ be the interaction associated to the action of $\so(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
-The functionals $I^{(1)}$ and $I^{(2)}$ are rotation invariant, meaning that
-\[\d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},\]
+Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
+The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
+\begin{equation}\label{rot_invariance_eqn}
+ \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
+\end{equation}
 for $i=1,2$.
@@
 \begin{proof}
+First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since 
 \chris{...}
@@
 Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.
-Indeed \chris{...}.
+Indeed, we expand
+\begin{align*}
+ \{I^{(1)}, I^{(2)}\}  &= \left\{\<A^* , \Gamma(Q, \lambda)\>, \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>\right\}\\
+ &= \left\< A^*\;,\; \Gamma\left(Q, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\> + \\
+ &\quad + .
+\end{align*}
+\chris{include the terms from the other $\lambda^*$ on the third line.} We can rewrite
+\chris{...}.
 

### 2019-08-14 paper.tex
Continuing edits to SYM section, and to dimensional reduction section

@@
 
-\subsubsection{Yang-Mills Theory}
+\subsubsection{Yang-Mills Theory} \label{YM_section}
 Let us now give an example of a theory which is not partially holomorphic.
@@
 \begin{prop} \label{dim_red_SUSY_prop}
-The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
+The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
 \end{prop}
@@
 \begin{proof}
- \chris{I think this will be straightforward.}
+ \chris{Proof idea: start with an equivariant action functional $\mf S$ in $n$-dimensions.
+There is a cochain map $C^\bullet_{\mr{loc}}(\mf L) \to C^\bullet_{\mr{loc}}(\mf L')$ by restriction.
+There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
+However these two maps do, together, define a cochain map
+ \[F \colon (C^\bullet_{\mr{Lie}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
+ on the subcomplex consisting of those functionals where, upon restriction
+
+ We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S) = \mf S'$ in $m$-dimensions, i.e a supersymmetric action functional.
+ }
 \end{proof}
@@
 \begin{enumerate}
- \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.
-In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
+ \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.
+In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
  \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
@@
 This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.
-In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.
+In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .
 Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
@@
 \begin{proof}
-\chris{todo:rewrite}
+\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
 Both are direct calculations using standard Clifford relations which cite below.
@@
 \[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
-where \chris{sign}
+where \chris{correct sign?}
 \begin{align*}
 I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & = - \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
 \end{align*}
@@
 \begin{proof}
-This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed \chris{...}
+This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ is exactly  \chris{...}
 \end{proof}
@@
 \begin{proof}
-First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since 
+First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.
+If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module,
 \chris{...}
@@
 
-First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.  Baez and Huerta prove that in our four critical dimensions \chris{argue why this is the same}.
+First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.
+Baez and Huerta prove that in our four critical dimensions, the variation $\delta^{(1)}S_{\mr{BRST}}$ of the ordinary BRST action functional vanishes.
+In particular, this implies that $\delta^{(1)}S_{\mr{BV}} = \{I^{(1)}, S_{\mr{BV}}\}$ also vanishes, since \chris{why?}.
 
@@
 
-\chris{Discuss dimensional reduction, and then the inclusion of the action of R-symmetries.}
+We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
+\begin{corollary}
+Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
+Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
+Then the super Poincar\'e algebra
+\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
+obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
+\end{corollary}
+
+\begin{proof}
+This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
+\end{proof}
+
+\begin{remark}
+We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
+\end{remark}
 

### 2019-08-14 paper.tex
Continuing edits to SYM section, and to dimensional reduction section

@@
 \begin{proof}
- \chris{Proof idea: start with an equivariant action functional $\mf S$ in $n$-dimensions.
-There is a cochain map $C^\bullet_{\mr{loc}}(\mf L) \to C^\bullet_{\mr{loc}}(\mf L')$ by restriction.
+ \chris{Proof idea: start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map
+ \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}(\iso(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\iso(m)) \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
+ given by the inclusion of $\iso(m) \inj \iso(n)$, and the restriction of fields from $n$ to $m$-dimensions.
+We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
+
+ Now include supertranslations.
 There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
@@
 
- We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S) = \mf S'$ in $m$-dimensions, i.e a supersymmetric action functional.
  }

### 2019-08-14 paper.tex
Adding some more comments on dimensional reduction

@@
 \begin{proof}
- \chris{Proof idea: start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map
- \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}(\iso(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\iso(m)) \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
- given by the inclusion of $\iso(m) \inj \iso(n)$, and the restriction of fields from $n$ to $m$-dimensions.
+ \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
+There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(\mf L')),\]
+ given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
 We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
 
- Now include supertranslations.
-There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
-However these two maps do, together, define a cochain map
- \[F \colon (C^\bullet_{\mr{Lie}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
- on the subcomplex consisting of those functionals where, upon restriction
-
- }
+ Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
+There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
+Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))\] to $\mf S$ anyway.
+We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
+We can then use the same argument as above.
 \end{proof}

### 2019-08-15 paper.tex
Editing a Lemma about {I^1, I^1}
Screwing around with gamma matrices but it's a mess

@@
 \[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
-where \chris{correct sign?}
+where 
 \begin{align*}
 I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & = - \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
 \end{align*}
@@
 The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
-\[\{I^{(1)},I^{(1)}\} = - 2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
 \end{lemma}
@@
 \begin{proof}
-This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ is exactly  \chris{...}
+This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
+\begin{align*}
+\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\>, \<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\> \} \\
+&= 2(\langle A^*, [\delta_{Q}, \delta_{Q}] A \rangle + \langle \lambda^*, [\delta_{Q}, \delta_{Q}] \lambda \rangle) \\
+ &= 2(\langle A^*, \delta_{[Q,Q]} A \rangle + \langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle  - \rho(\Gamma(Q,Q)) \sd \dd \lambda - \frac 12(Q, \sd \dd \lambda)Q - \frac 12(Q, \sd \dd \lambda)Q) \\
+ &= 2\langle A^*, \delta_{[Q,Q]} A \rangle + 2\langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
+ &=
+\end{align*}
+Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
+\chris{What about that $[Q,Q]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q,Q]$.}
 \end{proof}
@@
 \begin{align*}
- \{I^{(1)}, I^{(2)}\}  &= \left\{\<A^* , \Gamma(Q, \lambda)\>, \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>\right\}\\
- &= \left\< A^*\;,\; \Gamma\left(Q, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\> + \\
- &\quad + .
-\end{align*}
-\chris{include the terms from the other $\lambda^*$ on the third line.} We can rewrite
-\chris{...}.
+ \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
+ &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
+ &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
+ &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
+ &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
+\end{align*}
+where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
+\begin{align*}
+\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
+&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
+\end{align*}
+since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}
+\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
+\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
+I don't see that here -- is that true?
+Maybe I'm missing a simplification?
+If anything I'm seeing only the second term (which the 3-$\psi$ rule doesn't apply to).
+Maybe it's the difference of two expressions to which the rule does apply?}.
 

### 2019-08-15 paper.tex
Screwing around with gamma matrices but it's a mess

@@
 \begin{align*}
-\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\>, \<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\> \} \\
-&= 2(\langle A^*, [\delta_{Q}, \delta_{Q}] A \rangle + \langle \lambda^*, [\delta_{Q}, \delta_{Q}] \lambda \rangle) \\
- &= 2(\langle A^*, \delta_{[Q,Q]} A \rangle + \langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle  - \rho(\Gamma(Q,Q)) \sd \dd \lambda - \frac 12(Q, \sd \dd \lambda)Q - \frac 12(Q, \sd \dd \lambda)Q) \\
- &= 2\langle A^*, \delta_{[Q,Q]} A \rangle + 2\langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
+\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
+&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
+ &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
+ &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
  &=
@@
 Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
-\chris{What about that $[Q,Q]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q,Q]$.}
+\chris{What about that $[Q_1,Q_2]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q_1,Q_2]$.}
 \end{proof}
@@
 \end{align*}
-since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}
+since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
+We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
+\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
+which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
 \chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
 \[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
-I don't see that here -- is that true?
-Maybe I'm missing a simplification?
-If anything I'm seeing only the second term (which the 3-$\psi$ rule doesn't apply to).
-Maybe it's the difference of two expressions to which the rule does apply?}.
+I don't see that here -- is that true?  I might be missing something.}.
 

### 2019-08-15 paper.tex
Some minor edits to dimensional reduction section

@@
  \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
-There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(\mf L')),\]
+There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\]
  given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
@@
 There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
-Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))\] to $\mf S$ anyway.
+Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.
 We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
@@
 \chris{By the way, I see no obstruction to proving the following.
-One just needs to check that the action of an infinitesimal symmetry $X$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.}
+One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.
+This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
 \begin{lemma}

### 2019-08-16 paper.tex
Polishing of Section 1

--- 2019-08-15 paper.tex
@@
 \input ./combined_macros.sty
+
+\newcommand{\Dens}{\mathrm{Dens}}
 
@@
 
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the space of smooth sections of $E$.
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}).
+We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
+
 \subsection{Classical BV Theories}
@@
 \[
-\omega\colon E \otimes E \to {\rm Dens}_M [-1]
+\omega\colon E \otimes E \to \Dens_M [-1]
 \]
@@
 
-\brian{recall dfn of $\oloc$ of a gr vb.} \chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}
+We call $\cE$ the {\bf space of BV fields}.
 
@@
 \[
-I \in \oloc^+(E)
+I \in \oloc^+(\cE)
 \]
@@
 \begin{remark}
-We will also consider $\ZZ/2$-graded classical field theories which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
+We will also consider {\bf $\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
+\end{remark}
+
+\begin{remark}
+The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a symplectic isomorphism $L\cong L^![-3]$.
 \end{remark}
@@
 \begin{dfn}
-A {\bf morphism} of classical field theories (defined on the same manifold $M$) $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is a linear map of vector bundles
+A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
 \[
@@
 For a short background on homological algebra with differentiable pro-cochain complexes, including the notion of quasi-isomorphism, we refer to Appendix \ref{appx: top}.
-For a more thorough introduction, and for which our conventions are based on, we refer to \cite{CG1}.
-
-\begin{dfn} \label{infinitesimal_action_def}
+For a more thorough introduction, and for which our conventions are based on, we refer to \cite{Book1}.
+
+\begin{dfn}
 Let $(E, Q,\omega, I)$ be a classical field theory 
@@
 \]
-\brian{maybe point to appendix where we can fix conventions for $\infty$-maps} \chris{Can we also give the definition here of an equivariant classical field theory in terms of the Maurer-Cartan / equivariant classical master equation?}
-\end{dfn}
-
-We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes.
-\chris{below we define it in terms of an interaction with components $I^{(1)}, I^{(2)}$ etc, so we should give that point of view here as well.}
+\end{dfn}
+
+We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
 
@@
 
-\pavel{explain how to obtain a factorization algebra from a classical field theory.}
-
-Let $(E, Q, \omega, I)$ be a classical BV theory. 
-%and suppose $\psi_0 \in \sE$ is a fixed solution to the equations of motion. 
-We recall the formalism of \cite{CG1,CG2} which extracts a factorization algebra on spacetime.
+Let $(E, Q, \omega, I)$ be a classical BV theory. We recall the formalism of \cite{Book1,Book2} which extracts a factorization algebra on spacetime.
 
@@
 
-Notice that the BV complex we defined in the previous section, Equation (\ref{bvplx}), is the global sections of the factorization algebra along $M$.
+Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
 The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
@@
 
-The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in Proposition ?? of \cite{CG2}.
+The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in \cite[Section 3]{Book2}.
 
@@
 \begin{itemize}
-\item a $\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item a differential operator
-\[
-Q_{BRST} : \cF \to \cF^!  ;
-\]
-\item a local functional $I_{BRST} \in \oloc^+(\cF)$ of polynomial degree $\geq 3$.
-\end{itemize}
-Together, this data must satisfy the master equation
-\[
-[\d_{CE}, Q_{BRST}] + \d_{CE} I_{BRST} = 0 .
-\]
-where $\d_{CE}$ is the Chevalley-Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
-\brian{even separately, I suppose?}
-\end{dfn}
-
-We can unwrap this definition as follows. 
-One can think of the space of field $\cF$ as a (linear) graded manifold.
-In doing so, the $L_\infty$ structure on $\cF[-1]$ determines a vector field $X$ of cohomological degree $+1$ on this graded manifold. 
-The operator $Q$ determines a one-form on $\cF$, and the master equation says that this one-form vanish along the vector field $X$. 
-Similarly, the condition $\d_{CE} I = 0$ means the function $I$ on $\cF$ vanish along $X$.
-
-From a classical BRST theory $(\cF, Q_{BRST}, I_{BRST})$, one can construct a classical BV theory as follows. 
-Let $\{\ell_k\}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
+\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\end{itemize}
+Together, these data must satisfy the equation
+\[Q_{BRST} S_{BRST} = 0,\]
+where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+\end{dfn}
+
+We call $\cF$ the {\bf space of BRST fields}.
+
+From a classical BRST theory $(\cF, S_{BRST})$, one can construct a classical BV theory as follows.
+Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
 
 First, we define the free BV theory.
-This will only use the linear operation on the $L_\infty$ algebra $\cF$, and the operator $Q_{BRST}$. 
+Split $S_{BRST} = S^{free}_{BRST} + I_{BRST}$, where $I_{BRST}\in\oloc^+(\cF)$ and $S^{free}_{BRST}$ is a quadratic local functional which we may view as defining a map
+\[S^{free}_{BRST}\colon F\rightarrow F^!.\]
 The underlying bundle of the BV theory is
 \[
-E = F \oplus F^! [-1] = F \oplus F^* \otimes {\rm Dens}_M .
+E = F \oplus F^! [-1].
 \]
@@
 \[
-Q = \ell_1 + Q_{BRST} .
-\]
-The BV pairing $\omega_{F}$ is defined by the composition
-\[
-E \otimes E = (F \oplus F^![-1]) \otimes (F \oplus F^![-1]) \to F \otimes F^! [-1] \oplus F^![-1] \otimes F \to {\rm Dens}_M [-1] .
-\]
-The first arrow is the obvious projection. 
-The second arrow is given by the evaluation pairing between $F$ and $F^*$. 
-It's immediate to check that the data $(\cE, Q, \omega)$ defines a free BV theory.
+Q = \ell_1 + S^{free}_{BRST}.
+\]
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
 
 The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p : \cE = \cF \oplus \cF^![-1] \to \cF$.
+First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
 These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
 \[
-I_{F} (e) = \sum_{k \geq 2} \int_M \frac{1}{(k+1)!} \omega_F(e, (p^*\ell_k) (e, \ldots, e)) . 
-\] 
-Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
+I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
+\] 
+which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
 \[
@@
 \begin{lemma}
-Given a classical BRST theory $(F, Q_{BRST}, I_{BRST})$, the data $(E, Q, \omega, I) = (F \oplus F^![-1] , \ell_1 + Q_{BRST} , \omega_F, I_{BV})$ defines a classical BV theory.
-That is, the BV classical master equation
-\[
-Q I + \frac{1}{2} \{I, I\} = 0 \iff (Q + \ell_1) (I_F + p^*I_{BRST}) + \frac{1}{2} \{I_F + p^*I_{BRST}, I_F + p^*I_{BRST}\} = 0
-\]
-holds.
-We refer to this classical BV theory as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q, \omega, I)$ is a classical BV theory.
 \end{lemma}
 
-\begin{proof}
-\brian{shouldn't be hard...}
-\end{proof}
-
-%\begin{dfn}
-%A {\bf classical BRST theory} is a finite rank $\ZZ \times \ZZ / 2$-graded vector bundle $F \to M$ equipped with an even differential operator of cohomological degree $+1$
-%\[
-%Q : \cF \to \cF[1]
-%\]
-%such that $Q
+We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of {\bf cotangent type}.
 
@@
 
+\begin{comment}
 \brian{should we make these definitions, recollections, or just conventions?}
@@
 Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.
-
-\subsubsection{Mixed holomorphic/topological BF theory}
-
-\begin{dfn}
-Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
-Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
-The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} \chris{I don't really understand why this thing needs a name, since it's only a theory in a trivial way, with zero action.
-Why not just call this thing $\cF$, call its shifted cotangent something like ``generalized BF theory'', then if $\fg$ has a pairing call the theory built out of $\cF$ with its AKSZ structure something like ``generalized Chern-Simons theory'' (I'm brainstorming other names too: e.g.
-``Hodge-Chern-Simons theory'')?
-Or do you want to reserve the name Chern-Simons for the case where $\fg$ is a Lie algebra, not an $L_\infty$ algebra?} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
-\[
-\cF[-1] = \Omega^{0,\bu}_X \Hat{\otimes} \Omega^{\bu,\bu}_Y \Hat{\otimes} \Omega^\bu_M \otimes \fg .
-\] 
-The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative product on differential forms. 
-This is a classical BRST theory by choosing $Q_{BRST} = 0$ and $I_{BRST} = 0$. 
-In other words, $\cF$ is defined by the mapping stack
-\[
-{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
-\]
-
-The {\bf mixed holomorphic-Dolbeault-topological BF theory} is the BV theory given by the $(-1)$-shifted cotangent bundle to $\cF$.
-\end{dfn}
-
-Unpacking the definition \brian{unpack and write out action explicitly?}
-
-\subsubsection{Mixed holomorphic/topological Chern-Simons theory}
-
-The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. 
-Unlike the examples of mixed BF theory above, these BV theories do not arise, in general, as shifted cotangent bundles.
-
-Fix a Calabi-Yau manifold $X$ of {\em complex} dimension $n$, a smooth manifold of {\em real} dimension $m$, and let $\fg$ be a $\ZZ/2$-graded Lie algebra with a non-degenerate graded symmetric pairing of parity opposite to $n+m$.
-In particular, if $n+m$ is odd, we can take an ordinary complex semi-simple Lie algebra $\fg$ with its Killing form. 
-When $n+m$ is even, we must work with a graded Lie algebra with an odd pairing.
-In any case, we denote the pairing on $\fg$ by $\<-,-\>$.
-
-\begin{dfn}
-Let $X, M$, and $\fg$ be as above.
-{\bf Mixed Chern-Simons theory} on $X \times M$ with values in $\fg$ is the $\ZZ/2$-graded classical field theory $(E_\mCS, Q_\mCS, \omega_\mCS, I_\mCS)$, where the space of fields is given by
-\[
-\cE_\mCS = \Omega^{0,\bullet}(X) \Hat{\otimes} \Omega^\bu(M) \otimes \fg [1] .
-\]
-The linear part of the BV differential is
-\[
-Q_{\mCS} = \dbar \otimes 1 \otimes 1 + 1 \otimes \otimes 1 \otimes \d_{\dR}
-\]
-where $\dbar$ is the Dolbeault differential on $X$, and $\d_{\dR}$ is the de Rham differential on $M$.
-The pairing $\omega_\hCS$ is
-\[
-\omega_{\hCS} (\alpha,\beta) = \<\alpha \wedge \beta\> \wedge \Omega_X ,
-\]
-where $\Omega_X$ is the Calabi-Yau structure on $X$.
-Finally, the interaction $I_\hCS$ is
-\[
-I_{\hCS}(\alpha) = \frac 16 \<\alpha \wedge [\alpha, \alpha]\> \wedge \Omega_X .
-\]
-As a mapping stack, mixed Chern-Simons is given by
-\[
-{\rm Map} (X_{\dbar} \times M_{\dR} , B \fg) .
-\]
-
-\end{dfn}
-
-By convention, when $X$ is the trivial complex manifold we take $\Omega_X = 1$.
-
-\begin{eg}
-The most basic  example is to take $X$ trivial and $\dim_{\RR} (M) = 3$.
-Then we obtain ordinary Chern-Simons theory on $M$. 
-Of course, this theory admits an obvious lift to a $\ZZ$-graded BV theory. 
-\end{eg}
-
-\begin{eg} 
-Now, take $M$ to be trivial and let $X$ be a Calabi-Yau $2$-fold, like $\CC^2$.
-Since $n + m = 2$ is even, we must take a graded Lie algebra with odd pairing. 
-First, let $\fh$ be an ordinary Lie algebra equipped with an invariant non-degenerate symmetric pairing $\<-,-\>_\fh$. 
-Define the $\ZZ/2$-graded Lie algebra
-\[
-\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3] 
-\]
-where $\epsilon_i$ are odd formal variables.
-
-There is an odd pairing on $\fg$ defined using the pairing on $\fh$ and the Berezin integral along the odd coordinates:
-\[
-\<X , Y\> = \int_{\CC^{0|3}} \d \epsilon_1 \d \epsilon_2 \d \epsilon_3 \<X, Y\>_\fh 
-\] 
-where $X,Y \in \fg = \fh[\epsilon_i]$.
-
-With this data, holomorphic Chern-Simons on the $2$-fold $X$ with values in $\fg = \fh[\epsilon_1,\epsilon_2, \epsilon_3]$ is defined.
-In fact, in this example, there is a natural lift to a $\ZZ$-graded theory whereby the coordinates $\epsilon_i$ are given cohomological degree $-1$.
-
-On $X = \CC^2$ with its standard Calabi-Yau form $\Omega_X = \d z_1 \d z_2$ this theory is equivalent to the holomorphic twist of $\cN=4$ super Yang-Mills on $\RR^4$ for the Lie algebra $\fh$.
-
-\end{eg}
-
-\subsubsection{Yang-Mills Theory} \label{YM_section}
+\end{comment}
+
+\subsubsection{Generalized BF theory}
+
+\begin{dfn}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix an $L_\infty$ algebra $\fg$.
+The {\bf generalized BF theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading.
+$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
+
+\item The BRST action is $S_{BRST} = 0$.
+\end{itemize}
+\end{dfn}
+
+Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
+\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
+where we denote the two fields by $A$ and $B$. The BV action is
+\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
+where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
+
+\begin{example}
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with the BV action
+\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
+\end{example}
+
+\subsubsection{Generalized Chern--Simons theory}
+
+The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
+
+\begin{dfn}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix an $L_\infty$ algebra $\fg$.
+We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+The {\bf generalized Chern--Simons theory} is the following classical BV theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading.
+
+\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
+
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
+
+\item The interaction term is
+\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
+\end{itemize}
+\label{def:generalizedBF}
+\end{dfn}
+
+We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
+
+\begin{example}
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
+\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
+\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
+The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
+Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
+\end{example}
+
+\subsubsection{Super Yang--Mills Theory}
+
 Let us now give an example of a theory which is not partially holomorphic.
-We will give a general description of Yang-Mills theory on $\RR^n$, with spinorial matter.
-Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.
-The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
-\begin{itemize}
-\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
-\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
-\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.
-For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.
-\end{itemize}
-These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
-Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.
-
-We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
+We will give a general description of the Yang--Mills theory on $M=\RR^n$ with adjoint spinorial matter.
+Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(n; \CC)$ with an $\so(n)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to \CC^n$ (see Section \ref{sec: susy} for more details on supersymmetry).
+The fields of super Yang--Mills theory are the following:
+\begin{itemize}
+\item A connection $A \in \Omega^1(\RR^n; \fg)$ on the trivial bundle.
+
+\item A section $\lambda \in \Omega^0(\RR^n; \Pi \Sigma \otimes \fg)$.
+
+\item The ghost field $c\in\Omega^0(\RR^n; \fg)[1]$.
+\end{itemize}
+
+Thus, the bundle of BRST fields is
+\[F = (\Omega^1(M)\oplus \Omega^0(M; \Pi\Sigma)\oplus \Omega^0(M)[1])\otimes \fg.\]
+The corresponding local super dg Lie algebra $L=F[-1]$ is
 \[
@@
 & & & & \\
-& \Omega^0(\RR^{n}; \gg) & \to & \Omega^1(\RR^{n}; \gg) \oplus \Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) & 
+& \Omega^0(M; \gg) & \to & \Omega^1(M; \gg) \oplus \Omega^0(M; \Pi \Sigma \otimes \gg) & 
 \end{array}
 \]
-with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
-
-The action functional for super Yang-Mills theory is given by
-\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
-where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$.
-\chris{Brian suggested defining this notation in the section on supersymmety more broadly.
-I agree.}
-
-We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
-This is the local $L_\infty$-algebra $\fL$ on $\RR^{n}$ whose underlying cochain complex takes the form
-\[
-\xymatrix{
-& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-\fL & = & \Omega^0(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{n}; \gg) \ar[r]^{\d \ast \d} &\Omega^{n-1}(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^{n}(\RR^{n}; \gg) \\
-& & &\Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{n}(\RR^{n}; \Pi \Sigma^* \otimes \gg), &
-}\]
-with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the evaluation pairing $(-,-)$ between $\Sigma$ and $\Sigma^*$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{n}; \gg)$ on everything along with
-\begin{align*}
-\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
-(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
-\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^0(\RR^{n}; \Sigma \otimes \gg) &\to \Omega^{n}(\RR^{10}; \Sigma* \otimes \gg) \\
-(A \otimes \lambda) &\mapsto \ast \sd A \lambda
-\end{align*}
-in degree 2, and the map
-\begin{align*}
-\ell_3 \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
-(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
-\end{align*}
-in degree 3.
-
-We obtain the BV action by the formula
-\[
-S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
-\]
-where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
-The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.
-
-We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.
-
-\begin{definition}
-The $n$-dimensional \emph{Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.
-The $n$-dimensional \emph{Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
-\end{definition}
-
-The $n$-dimensional Poincar\'e algebra acts, in the sense of definition \ref{infinitesimal_action_def}, on Yang-Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
-\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}
-
-\begin{prop} \label{YM_Poincare_invariant_prop}
-Yang-Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
-\[\d_{\mr{Lie}}I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\}.\]
-\end{prop}
-
-\begin{proof}
-\chris{...}
-\end{proof}
+whose differential is the de Rham differential $\Omega^0(M; \gg)\rightarrow \Omega^1(M; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.
+
+Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).
+We denote by $\sd\d$ the Dirac operator for the zero connection.
+
+The BRST action is given by
+\[S(A, \lambda) = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]
+
+The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}).
+Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively.
+The bundle of BV fields is
+\[E = \Omega^1(M; \fg)\oplus \Omega^0(M; \Pi\Sigma\otimes \fg)\oplus \Omega^0(M; \fg)[1] \oplus \Omega^{n-1}(M; \fg^*)[-1]\oplus \Omega^n(M; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(M; \fg^*)[-2].\]
+The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
+\[S_{BV} = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]
 
@@
 \begin{prop} \label{dim_red_SUSY_prop}
-The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
+The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
 \end{prop}
@@
 \begin{proof}
- \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
-There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(\mf L')),\]
- given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
-We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
-
- Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
-There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
-Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))\] to $\mf S$ anyway.
-We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
-We can then use the same argument as above.
+ \chris{I think this will be straightforward.}
 \end{proof}
@@
 \end{itemize}
-
-\begin{definition}
-In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
-\end{definition}
-
 We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
 \begin{enumerate}
- \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.
-In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
+ \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.
+In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
  \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
@@
 This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.
-In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .
+In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.
 Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
-
-\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
+%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
+
+\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
 The multilinear map 
@@
 \end{align*}
-Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.
-
-\begin{lemma} \label{onshell_action_lemma}
-Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
+Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.
+We can check that this supersymmetry action does not close off-shell.
+Indeed \chris{...}
+
+\chris{heavily edit the below.}
+\begin{lemma} \label{10d_onshell_lemma}
+Suppose $Q_1, Q_2 \in S_+$ and $(A, \lambda)$ are fields.
 The following relations hold:
@@
 \begin{proof}
-\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
 Both are direct calculations using standard Clifford relations which cite below.
@@
 Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.
-Similarly we can calculate, (as in \cite{Guillen}):
+Similarly we can calculate, following the calculation in Guillen \cite{Guillen}:
 \begin{align*}
@@
 \[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
-as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
+as in \cite[Theorem 11]{BaezHuerta}.  Making one more simplification using the Clifford relations, we have
 \begin{align*}
@@
 \begin{align*}
-\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
+\delta^{(2)} \colon S_+ \otimes S_+ \otimes \Gamma(\RR^{10}; \Pi S_-[-1]) &\to \Gamma(\RR^{10}; \Pi S_+) \\
 Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
@@
 
-We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.
+We'll rewrite this as a local functional in the theory $\fL$ coupled to the $\mc N=(1,0)$ super Lie algebra $\mf A$.
 
@@
 I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
 \end{align*}
@@
 
-We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
-\begin{lemma} \label{onshell_interaction_lemma}
-The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
-\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
-\end{lemma}
-
-\begin{proof}
-This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
-\begin{align*}
-\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\>, \<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\> \} \\
-&= 2(\langle A^*, [\delta_{Q}, \delta_{Q}] A \rangle + \langle \lambda^*, [\delta_{Q}, \delta_{Q}] \lambda \rangle) \\
- &= 2(\langle A^*, \delta_{[Q,Q]} A \rangle + \langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle  - \rho(\Gamma(Q,Q)) \sd \dd \lambda - \frac 12(Q, \sd \dd \lambda)Q - \frac 12(Q, \sd \dd \lambda)Q) \\
- &= 2\langle A^*, \delta_{[Q,Q]} A \rangle + 2\langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
- &=
-\end{align*}
-Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
-\chris{What about that $[Q,Q]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q,Q]$.}
-\end{proof}
-
-The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
-\begin{lemma} \label{SUSY_rotation_invariance_lemma}
-Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
-The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
-\begin{equation}\label{rot_invariance_eqn}
- \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
-\end{equation}
-for $i=1,2$.
-\end{lemma}
-
-\begin{proof}
-First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.
-If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module,
-\chris{...}
-\end{proof}
-
-Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.
-
-\begin{theorem} \label{SUSY_YM_theorem}
+\begin{prop}
 Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
-\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
+\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
 satisfies the Maurer-Cartan equation
 \begin{equation} 
-\label{nd_MC}
-(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
+\label{10d_MC}
+(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
 \end{equation}
-\end{theorem}
+\end{prop}
+
+\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
+On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
+To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}
 
 \begin{proof}
-We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
+We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
 \begin{align}
-\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
-&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
-&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
-&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
-&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
+\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
+&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
+&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
+&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
+&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
 \end{align}
-Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
+Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.
 The remaining terms are those involving the action of supersymmetries.
 
-First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.
-Baez and Huerta prove that in our four critical dimensions, the variation $\delta^{(1)}S_{\mr{BRST}}$ of the ordinary BRST action functional vanishes.
-In particular, this implies that $\delta^{(1)}S_{\mr{BV}} = \{I^{(1)}, S_{\mr{BV}}\}$ also vanishes, since \chris{why?}.
-
-In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.
-Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.
-Indeed, we expand
-\begin{align*}
- \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
- &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
- &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
- &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
- &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
-\end{align*}
-where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
-\begin{align*}
-\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
-&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
-\end{align*}
-since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}
-\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
-\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
-I don't see that here -- is that true?
-Maybe I'm missing a simplification?
-If anything I'm seeing only the second term (which the 3-$\psi$ rule doesn't apply to).
-Maybe it's the difference of two expressions to which the rule does apply?}.
-
-Finally, term \ref{MC_4} vanishes because the interaction $I^{(2)}$ only involves antifields: the BV antibracket of two expressions involving only antifields is always zero.
+First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.
+First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.
+Then \ref{10d_MC_1} is zero by Baez--Huerta.
+Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}.
+Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.
+Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
+
+\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.
+Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
 \end{proof}
-
-We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
-\begin{corollary}
-Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
-Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
-Then the super Poincar\'e algebra
-\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
-obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
-\end{corollary}
-
-\begin{proof}
-This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
-\end{proof}
-
-\begin{remark}
-We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
-\end{remark}
 
@@
 
-\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{CG1}, here. }
+\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{Book1}, here. }
 
@@
 
-\begin{thm}[Theorem 2.2.1 of \cite{CG1}]
+\begin{thm}[{\cite[Theorem 2.2.1]{Book1}}]
 The category $\DVS$ is a Grothendieck abelian category.
@@
 \section{$\infty$ algebra}
+\label{appx:infinity}
 

### 2019-08-16 paper.tex

@@
 We call $\cE$ the {\bf space of BV fields}.
+\chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}
 
@@
 Given a classical field theory $(E, Q, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
+\[S_{BV} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
 the BV action of the theory.
@@
 \]
-More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
+More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
 \[
@@
 We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
+
+Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
+\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
+which satisfies the Maurer--Cartan equation
+\[\{S_{BV}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
+for every $k\geq 0$.
 
@@
 
-\subsubsection{Super Yang--Mills Theory}
+\subsubsection{Super Yang--Mills Theory} \label{YM_section}
 
@@
 \[S_{BV} = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]
+
+We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.
+
+\begin{definition}
+The $n$-dimensional {\bf Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.
+The $n$-dimensional {\bf Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
+\end{definition}
+
+The $n$-dimensional Poincar\'e algebra acts, in the sense of Definition \ref{infinitesimal_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
+\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}
+
+\begin{prop} \label{YM_Poincare_invariant_prop}
+Yang--Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
+\[\{S_{BV}, I_{\mr{Poin}}\} + \d_{CE} I_{\mr{Poin}} + \frac 12 \{I_{\mr{Poin}}, I_{\mr{Poin}}\} = 0.\]
+\end{prop}
+\begin{proof}
+\chris{...}
+\end{proof}
 
@@
 \begin{proof}
- \chris{I think this will be straightforward.}
+ \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
+There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\]
+ given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
+We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
+
+ Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
+There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
+Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.
+We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
+We can then use the same argument as above.
 \end{proof}
@@
 \end{itemize}
+
+\begin{definition}
+In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
+\end{definition}
+
 We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
 \begin{enumerate}
- \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ \chris{define this above}, which is only well-defined on-shell.
-In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion \chris{induces a Lie homomorphism on cohomology?}.
+ \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.
+In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
  \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
@@
 This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.
-In particular, we will use the following ``3-$\psi$'s rule'' \chris{see citations in Baez Huerta for more references, which we might include}.
+In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .
 Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
-%We will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
-
-\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}]
+
+\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
 The multilinear map 
@@
 \begin{proof}
+\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
 Both are direct calculations using standard Clifford relations which cite below.
@@
 I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & = \pm \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
 \end{align*}
@@
 
-\begin{prop}
+We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
+\begin{lemma} \label{onshell_interaction_lemma}
+The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
+\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\end{lemma}
+
+\begin{proof}
+This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
+\begin{align*}
+\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
+&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
+ &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
+ &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
+ &=
+\end{align*}
+Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
+\chris{What about that $[Q_1,Q_2]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q_1,Q_2]$.}
+\end{proof}
+
+The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
+\begin{lemma} \label{SUSY_rotation_invariance_lemma}
+Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
+The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
+\begin{equation}\label{rot_invariance_eqn}
+ \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
+\end{equation}
+for $i=1,2$.
+\end{lemma}
+
+\begin{proof}
+First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.
+If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module,
+\chris{...}
+\end{proof}
+
+Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.
+
+\begin{theorem} \label{SUSY_YM_theorem}
 Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
-\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL) [-1]\]
+\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
 satisfies the Maurer-Cartan equation
 \begin{equation} 
-\label{10d_MC}
-(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\} = 0 .
+\label{nd_MC}
+(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
 \end{equation}
-\end{prop}
-
-\chris{we'll have to see whether we want Poincar\'e or just translation here, probably translation, because then there are no $\d_{\mr{Lie}}I^{(i)}$ terms to worry about.
-On the other hand we would like to know that the theories are supersymmetric, not just super-translation invariant.
-To include rotations and R-symmetries we need to additionally check that some terms like $\d_{\mr{Lie}}+ \{I_{\mr{rotation}} + I_{\text{R-symmetry}}, I^{(i)}\}$ vanish.}
+\end{theorem}
 
 \begin{proof}
-We can filter the complex $\clie^\bu(\mc A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{10d_MC} splits up as
+We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
 \begin{align}
-\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{10d_MC_BV}\\
-&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{10d_MC_1}\\
-&\quad + \d_{\mr{Lie}} I^{(1)} + \{S_{\mr{BV}}, I^{(2)}\} + \{I_{\mr{Poin}}, I^{(1)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{10d_MC_2}\\
-&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{10d_MC_3}\\
-&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{10d_MC_4}
+\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
+&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
+&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
+&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
+&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
 \end{align}
-Taking these terms one at a time, we first note that the vanishing of \ref{10d_MC_BV} is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, along with the fact that this theory is Poincar\'e invariant \chris{ref some earlier discussion}.
+Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
 The remaining terms are those involving the action of supersymmetries.
 
-First, the term \ref{10d_MC_1} vanishes by \chris{We've discussed this.
-First the $\{I_{\mr{Poin}}, I^{(i)}\}$ terms vanish by Poincar\'e invariance of the interaction terms.
-Then \ref{10d_MC_1} is zero by Baez--Huerta.
-Term \ref{10d_MC_2} is Lemma \ref{10d_onshell_lemma}.
-Term \ref{10d_MC_3} vanishes because, first $\d_{\mr{Lie}}I^{(2)} = 0$ since ...not sure right now..., then the remaining term vanishes by the trick where we symmetrize in three spinors.
-Finally \ref{10d_MC_4} vanishes because $I^{(2)}$ only involves antifields.}
-
-\chris{apart from the Lemma \ref{10d_onshell_lemma}, this is all completely identical for dimensions 3,4,6,10.
-Even that lemma only uses abstract gamma matrix manipulations that work in any dimension along with the Baez Huerta rule that applies in those dimensions, so I think we should just state a single result valid for those four theories simultaneously.}
+First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.
+Baez and Huerta prove that in our four critical dimensions, the variation $\delta^{(1)}S_{\mr{BRST}}$ of the ordinary BRST action functional vanishes.
+In particular, this implies that $\delta^{(1)}S_{\mr{BV}} = \{I^{(1)}, S_{\mr{BV}}\}$ also vanishes, since \chris{why?}.
+
+In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.
+Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.
+Indeed, we expand
+\begin{align*}
+ \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
+ &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
+ &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
+ &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
+ &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
+\end{align*}
+where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
+\begin{align*}
+\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
+&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
+\end{align*}
+since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
+We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
+\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
+which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
+\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
+\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
+I don't see that here -- is that true?  I might be missing something.}.
+
+Finally, term \ref{MC_4} vanishes because the interaction $I^{(2)}$ only involves antifields: the BV antibracket of two expressions involving only antifields is always zero.
 \end{proof}
+
+We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
+\begin{corollary}
+Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
+Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
+Then the super Poincar\'e algebra
+\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
+obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
+\end{corollary}
+
+\begin{proof}
+This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
+\end{proof}
+
+\begin{remark}
+We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
+\end{remark}
 

### 2019-08-16 paper.tex
Started editing the 8d twists section

--- 2019-08-15 paper.tex
@@
 \end{align*}
-since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
+since \chris{The equality of the first terms looks right when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
 We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
@@
 
-\chris{There is a single non-zero class of square zero supercharges in 9d, which are minimal (i.e. have 5d image).  They are stabilized by $\SU(4)$.  The twisted theory is only $\ZZ/2\ZZ$-graded.}
+There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
+Such supercharges are minimal (i.e.
+have 5d image).
+They are stabilized by $\SU(4)$.
+Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.
 
@@
 \subsection{Dimension 8}
+The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
+It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\phi_2$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.
+
+In 8 dimensions, there are 3 classes of non-equivalent non-zero supercharges by which we can twist.
+\begin{enumerate}
+ \item Pure spinors, with $\lambda_+ = 0$ or $\lambda_- = 0$.
+These supercharges are holomorphic.
+They are stabilized by $\SU(4)$.
+Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
+ \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.
+These supercharges are topological.
+They are stabilized by $\Spin(7) \sub \SO(8)$.
+Again, twists by such supercharges can be made $\ZZ$-graded.
+ \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction.
+\chris{I should say this more clearly, maybe including some general discussion at the beginning of the section, and referring to the figure.}
+
+\subsubsection{The Holomorphic Twist}
+
+\subsubsection{The Topological Twist}
+
+\subsubsection{The Rank 2 Twist}
 

### 2019-08-17 paper.tex
Minor wording changes
Definition of dimensional reduction

@@
 \end{proof}
+
+\subsection{Dimensional Reduction, take 2}
+
+\begin{definition}
+A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if we are given the following data:
+\begin{itemize}
+\item A submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.
+
+\item An isomorphism $p^* E_N\cong E_M$.
+\end{itemize}
+These data are required to satisfy the following conditions:
+\begin{itemize}
+\item The diagram
+\[
+\xymatrix{
+p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
+E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
+}
+\]
+is commutative.
+
+\item The diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+is commutative.
+
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
+\end{itemize}
+\end{definition}
 

### 2019-08-18 paper.tex
Comments based on conversations with Pavel earlier

@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf free BV theory} on a manifold $M$ is the data:
@@
 \end{itemize}
-\end{dfn}
-
-We call $\cE$ the {\bf space of BV fields}.
-\chris{before the definition below we should probably define the antibracket $\{,\}$ (in terms of the shifted symplectic structure).}
-
-\begin{dfn}
+\end{definition}
+
+We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
+\begin{definition}
+The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
+\end{definition}
+
+\begin{definition}
 A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
-\[
-I \in \oloc^+(\cE)
-\]
+\[I \in \oloc^+(\cE)\]
 of cohomological degree zero satisfying the classical master equation 
-\[
-Q I + \frac{1}{2} \{I,I\} = 0 .
-\]
-\end{dfn}
+\[Q I + \frac{1}{2} \{I,I\} = 0 .\]
+\end{definition}
 
 Given a classical field theory $(E, Q, \omega, I)$ we denote by
-\[S_{BV} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
+\[S_{\mr{BV}} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
 the BV action of the theory.
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
@@
 that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn} \label{equivalence_def}
+\begin{definition} \label{equivalence_def}
 A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
@@
 \]
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn} \label{infinitesimal_action_def}
+\subsection{Symmetries in the Classical BV Formalism}
+
+\chris{The idea, and a description of the kind of infinitesimal symmetries we're talking about (maybe just by a super Lie algebra in this paper, although we allow $L_\infty$ actions).
+More generally we might consider the action of general local $L_\infty$ algebras.}
+
+\begin{definition} \label{infinitesimal_action_def}
 Let $(E, Q,\omega, I)$ be a classical field theory 
@@
 which satisfies the Maurer--Cartan equation
-\[\{S_{BV}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
+\[\{S_{\mr{BV}}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
 for every $k\geq 0$.
 
+\begin{definition}
+\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.}
+\end{definition}
+
+\begin{definition}
+\chris{The definition of the equivariant observables in a classical BV theory with a symmetry as the relative Chevalley Eilenberg complex with coefficients in local functionals, with its anti-bracket.}
+\end{definition}
+
+\begin{remark}
+\chris{Remark on the d\'ecalage isomorphism with a reference, then give an interpretation of the relative Chevalley-Eilenberg complex after applying this isomorphism as the inclusion of background fields valued in the constant sheaf with value $\gg$.}
+\end{remark}
+
+\chris{mention smooth group actions, with a reference.}
+
 \subsection{The Classical Factorization Algebra}
@@
 
-\begin{dfn}
+\begin{definition}
 Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
@@
 where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
-\end{dfn}
+\end{definition}
 
@@
 \[
-I_{BV} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
+I_{\mr{BV}} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
 \]
@@
 
-\begin{dfn}
+\begin{definition}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
@@
 \end{itemize}
-\end{dfn}
+\end{definition}
 
@@
 \label{def:generalizedBF}
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
 The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
-\end{dfn}
+\end{definition}
 
@@
 
+\chris{todo: replace the argument here with an argument that only works in terms of the $I^{(i)}$.}
+
 \begin{proof}
@@
 We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
+Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.
+We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.
+
 \begin{lemma} \label{onshell_interaction_lemma}
 The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
-\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
 \end{lemma}
@@
 \begin{proof}
+\chris{fix to take care with signs, also we're removing that earlier lemma so this all needs changing.}
 This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
@@
  &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
- &=
-\end{align*}
-Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
-\chris{What about that $[Q_1,Q_2]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q_1,Q_2]$.}
+ &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\}.
+\end{align*}
+Here we applied Lemma \ref{onshell_action_lemma} on the third line.
 \end{proof}
@@
  \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
- &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
- &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
- &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
- &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
-\end{align*}
-where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
-\begin{align*}
-\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
-&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
-\end{align*}
-since \chris{The equality of the first terms looks right when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
-We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
-\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
-which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
-\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
-\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
-I don't see that here -- is that true?  I might be missing something.}.
+ &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + (123) \\
+ &= \left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1)\right\rangle + (123),
+\end{align*}
+where $(123)$ indicates symmetrization in $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
+\begin{align*}
+\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= 
+\end{align*}
+\chris{...}
 
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
@@
 for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{dfn}
+\end{definition}
 
@@
 
-In 8 dimensions, there are 3 classes of non-equivalent non-zero supercharges by which we can twist.
+In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
 \begin{enumerate}
- \item Pure spinors, with $\lambda_+ = 0$ or $\lambda_- = 0$.
+ \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.
 These supercharges are holomorphic.
@@
 
-\begin{dfn}
+\begin{definition}
 Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
@@
 
-\begin{dfn}\label{dfn: fnl}
+\begin{definition}\label{dfn: fnl}
 Let $E$ be a vector bundle on $M$ and $U \subset M$.
@@
 On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn} 
+\begin{definition} 
 We use the following notations and naming conventions for sheaves on $\Mfld$:
@@
 
-\begin{dfn}
+\begin{definition}
 Suppose $V,W$ are cochain complexes in convenient vector spaces. 
@@
 is a quasi-isomorphism of differentiable vector spaces.
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}
+\begin{definition}
 A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
@@
 A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
-\end{dfn}
+\end{definition}
 
@@
 
-\begin{dfn}\label{dfn: pro}
+\begin{definition}\label{dfn: pro}
 A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
@@
 where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
-\end{dfn}
+\end{definition}
 
@@
 
-\section{$\infty$ algebra}
+\section{$\infty$-Algebra}
 \label{appx:infinity}

### 2019-08-18 paper.tex
Making edits and corrections based on my conversation with Pavel.

@@
 
-\subsection{Symmetries in the Classical BV Formalism}
+\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
 
@@
 
-\chris{todo: replace the argument here with an argument that only works in terms of the $I^{(i)}$.}
-
-\begin{proof}
-\chris{I'm leaving this for now, but Pavel wanted to rewrite this coordinate freely.}
-Both are direct calculations using standard Clifford relations which cite below.
+We'll prove this lemma after first translating it into more convenient language: the terminology of the equivariant action functional, as introduced in Section \ref{symmetry_section}.
+Our Lemma \ref{onshell_action_lemma} tells us that the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
+In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".
+This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.
+Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
+\begin{align*}
+\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
+Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
+\end{align*}
+
+We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.
+
+\begin{definition}
+The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
+\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
+where 
+\begin{align*}
+I^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
+I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
+\end{align*}
+\end{definition}
+
+We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals, using the interpretation where 
+\begin{align*}
+I^{(1)}(Q) &= \<A^* , \delta_{Q} A\> + \<\lambda^*, \delta_{Q_1} \lambda\> \\
+\text{and } I^{(2)}(Q_1,Q_2) &= \<\lambda^*, \delta^{(2)}_{Q_1,Q_2}\lambda\>.
+\end{align*}
+Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.
+We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.
+
+\begin{lemma} \label{onshell_interaction_lemma}
+The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
+\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\end{lemma}
+
+\chris{Pavel wants to replace these two proofs: first of Lemma \ref{onshell_action_lemma}, then of Lemma \ref{onshell_interaction_lemma}, with a single coordinate free argument.}
+\begin{proof}[Proof of Lemma \ref{onshell_action_lemma}]
+Both of the two statements are direct calculations using standard Clifford relations which cite below.
 So, we calculate
@@
 
-In particular the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
-In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".
-This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.
-Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
-\begin{align*}
-\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
-Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
-\end{align*}
-
-We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.
-
-\begin{definition}
-The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
-\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
-where 
-\begin{align*}
-I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
-\end{align*}
-\end{definition}
-
-We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
-Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.
-We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.
-
-\begin{lemma} \label{onshell_interaction_lemma}
-The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
-\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
-\end{lemma}
-
-\begin{proof}
-\chris{fix to take care with signs, also we're removing that earlier lemma so this all needs changing.}
-This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
+\begin{proof}[Proof of Lemma \ref{onshell_interaction_lemma}]
+The functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
 \begin{align*}
@@
  &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
- &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\}.
-\end{align*}
-Here we applied Lemma \ref{onshell_action_lemma} on the third line.
+ &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\},
+\end{align*}
+where we applied Lemma \ref{onshell_action_lemma} on the third line. \chris{note, we should be careful to make sure that the sign in the $\d_{\mr{CE}}^\Gamma I^{(1)}$ term is correct.}
 \end{proof}
@@
 The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
+Let $\d^{\mr{rot}}_{\mr{CE}}$ denote the Chevalley Eilenberg differential in the super Lie algebra $\so(n) \ltimes \Pi \Sigma$.
+The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
+\[\d_{\mr{CE}}(Q) = \d^\Gamma_{\mr{CE}}(Q) + \d^{\mr{rot}}_{\mr{CE}}(Q).\]
+
 \begin{lemma} \label{SUSY_rotation_invariance_lemma}
-Let $I_{\mr{Poin}}$ be the interaction associated to the action of $\mf{iso}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
+Let $I_{\mr{rot}}$ be the interaction associated to the action of the Lie algebra $\mf{so}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
 The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
 \begin{equation}\label{rot_invariance_eqn}
- \d_{\mr{Lie}} I^{(i)} = - \{I_{\mr{Poin}}, I^{(i)}\},
+ \d^{\mr{rot}}_{\mr{CE}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},
 \end{equation}
@@
 \begin{proof}
-First, note that only the action of $\so(n)$ contributes to the two terms in the expression \ref{rot_invariance_eqn}, since the Lie bracket between a supertranslation and an ordinary translation is always zero.
-If we then consider the space $\Sigma$ of supertranslations as an $\so(n)$-module,
+If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
 \chris{...}
@@
 \begin{align}
-\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{Lie}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
+\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{CE}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
 &\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
-&\quad + \d_{\mr{Lie}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
-&\quad + \d_{\mr{Lie}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
+&\quad + \d_{\mr{CE}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
+&\quad + \d_{\mr{CE}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
 &\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
@@
 \end{align*}
-where $(123)$ indicates symmetrization in $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
-\begin{align*}
-\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= 
-\end{align*}
-\chris{...}
+where $(123)$ indicates symmetrization in the supercharges $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
+\begin{align*}
+\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle - (\lambda^*, Q_3) g(A^*, \Gamma(Q_1,Q_2)).
+\end{align*}
+\chris{needs an argument, and care with signs.
+Probably with the coordinate free argument above we'll have to include some lemmas on spinor manipulation that we can reference here.}  Thus, after symmetrization, we have shown that
+\[\{I^{(1)}, I^{(2)}\}= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle + (123),\]
+which vanishes by Theorem \ref{3_psi_thm}.
 
@@
 \end{remark}
+
+\chris{Pavel points out that we would like to know more, namely supersymmetry for theories with supersymmetric matter.  In order to prove this, we have to check :
+\begin{enumerate}
+ \item That the 4d chiral and 6d hyper multiplet are supersymmetric.
+ \item That the coupling terms $I_{\mr{coupling}}$ between these multiplets and the vector multiplet satisfy $\{I_{\mr{coupling}}, I^{(i)}\} = 0$ for $i=1,2$ (the $I^{(i)}$ split into a term describing the action on the vector as above, plus a term describing the action on the matter, and in the bracket these must cancel.)
+\end{enumerate}
+This implies the same after dimensional reduction, which tells us supersymmetry for the remaining examples: 5d, 3d, and 2d with matter.}
 

### 2019-08-18 paper.tex
Added a reference

@@
 \begin{definition}
-\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.}
+\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.
+Pavel suggested saying that $C^\bullet(\gg; V) = \hom(\sym^\bullet(\gg[1]), V)$, and following the sign rule he used in \cite[Section 2.1]{SafronovCoisoInt}.}
 \end{definition}

### 2019-08-18 paper.tex
Added a proof of rotation invariance of the supertranslation action

@@
 The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
-\[\d_{\mr{CE}}(Q) = \d^\Gamma_{\mr{CE}}(Q) + \d^{\mr{rot}}_{\mr{CE}}(Q).\]
+\[\d_{\mr{CE}}(F) = \d^\Gamma_{\mr{CE}}(F) + \d^{\mr{rot}}_{\mr{CE}}(F).\]
 
@@
 \begin{proof}
-If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
-\chris{...}
+Let $X$ be an element of $\so(n)$, and write $X \cdot A$ and $X \cdot \lambda$ for the image of the fields $A$ and $\lambda$ under the action of the symmetry $X$.  In particular, we can write
+\[I_{\mr{rot}}(A,\lambda, A^\vee, \lambda^\vee, X) = \langle A^\vee, X \cdot A \rangle + \langle \lambda^\vee, X \cdot \lambda \rangle.
+\]
+Therefore, the operator $\{I_{\mr{rot}}(X), -\}$ on the space of local functionals is freely generated by the operator on linear functionals in the Yang-Mills BV fields given by the action of the rotation $X$.
+On the other hand, the Chevalley-Eilenberg differential $\d^{\mr{rot}}_{\mr{CE}}$ is freely generated by the operator on \emph{supertranslations} in $\Sigma$, sending $Q$ to $X \cdot Q$.
+
+So, for the functionals at hand, we compute
+\begin{align*}
+\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
+&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
+&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
+&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)},
+\end{align*}
+and
+\begin{align*}
+\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2 X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
+&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
+&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
+&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
+&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
+&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}.
+\end{align*}
+\chris{I should take care that the signs I introduce when I move $X$ around are all correct here, and probably include more explanation.}
 \end{proof}

### 2019-08-18 paper.tex
Added a comment on the proof of rotation invariance of the supertranslation action

--- 2019-08-18 paper.tex
@@
 \begin{proof}
-If we consider the space $\Sigma$ of supertranslations as an $\so(n)$-module, 
-\chris{...}
+Let $X$ be an element of $\so(n)$, and write $X \cdot A$ and $X \cdot \lambda$ for the image of the fields $A$ and $\lambda$ under the action of the symmetry $X$.  In particular, we can write
+\[I_{\mr{rot}}(A,\lambda, A^\vee, \lambda^\vee, X) = \langle A^\vee, X \cdot A \rangle + \langle \lambda^\vee, X \cdot \lambda \rangle.
+\]
+Therefore, the operator $\{I_{\mr{rot}}(X), -\}$ on the space of local functionals is freely generated by the operator on linear functionals in the Yang-Mills BV fields given by the action of the rotation $X$.
+On the other hand, the Chevalley-Eilenberg differential $\d^{\mr{rot}}_{\mr{CE}}$ is freely generated by the operator on \emph{supertranslations} in $\Sigma$, sending $Q$ to $X \cdot Q$.
+
+So, for the functionals at hand, we compute
+\begin{align*}
+\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
+&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
+&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
+&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)}(A,\lambda, A^\vee, \lambda^\vee, Q, X),
+\end{align*}
+and
+\begin{align*}
+\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2, X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
+&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
+&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
+&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
+&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
+&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}(\lambda^\vee, Q_1, Q_2, X).
+\end{align*}
+\chris{I should take care that the signs I introduce when I move $X$ around are all correct here, and include more explanation.
+This argument assumes that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$, that $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$, which I think should follow from $\so(n)$ equivariance of $\Gamma$ and $\rho$, but I should check and verify the signs.}
 \end{proof}

### 2019-08-18 paper.tex
Improved proof of rotation invariance of the supertranslation action

@@
 
-So, for the functionals at hand, we compute
+So, for the functionals at hand.
+We'll use three properties of the action of $\so(n)$: that -- for spinovs $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.
+These identities all follow from the equivariance of the pairing $\Gamma$, the scalar pairing $(,)$, and the Clifford multiplication $\rho$.
+Using these facts, we compute
 \begin{align*}
@@
 \end{align*}
-\chris{I should take care that the signs I introduce when I move $X$ around are all correct here, and include more explanation.
-This argument assumes that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$, that $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$, which I think should follow from $\so(n)$ equivariance of $\Gamma$ and $\rho$, but I should check and verify the signs.}
 \end{proof}

### 2019-08-19 paper.tex
Twisting arguments in dimensions 9 and 8

@@
 
-\subsubsection{Generalized BF theory}
+\subsubsection{Generalized BF theory} \label{gen_BF_section}
 
@@
 
-\subsubsection{Generalized Chern--Simons theory}
+\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
 
@@
 \end{definition}
+
+\chris{A question: are dimensional reductions, per this definition, unique?
+I'd really like the answer to be yes (at least for dimensional reduction along a vector space), so that I can say the twist of a dimensional reduction is equivalent to \emph{the} (unique) dimensional reduction of the twist -- assuming the dimensional reductions before and after twisting exist (which, again, I'd like them to, at least for dimensional reduction along a vector space).}
 
@@
 This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
-\begin{lemma}
+\begin{lemma} \label{commuting_twist_and_reduction_lemma}
 If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
 \end{lemma}
+
+We'll conclude this section by discussing some examples of dimensional reduction in the context of generalized BF and Chern-Simons theories.
+First we'll describe what happens when we dimensionally reduce generalized Chern-Simons theory along $\RR$ in a holomorphic direction.
+
+\begin{lemma} \label{CS_diml_red_lemma}
+Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
+Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.
+The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
+\end{lemma}
+
+\chris{I haven't made the notation here match the notation in Section \ref{gen_CS_section} yet.}
+
+\begin{proof}
+\chris{sketchy}
+Let us denote the complex of BV fields in our generalized Chern-Simons theory on $X \times C$ by $(E_X \boxtimes \bigwedge^\bullet (T^{0,1}_C)^\vee) \otimes \gg[1]$, with differential on the sheaf of sections given by $Q_X + \ol \dd_C + \ell_1$ and pairing on the sheaf of sections by $\omega_X \boxtimes \omega_C$.
+Write $p$ for the projection $C \to L$.
+It's enough to observe that there is a canonical graded isomorphism $p^*\Omega^\bullet(L) \iso \Omega^{0,\bullet}(C)$ intertwining on the one hand the de Rham and Dolbeault differentials, and on the other hand the two integration maps against the orientation on $L$ and the Calabi-Yau structure on $C$.
+\end{proof}
+
+What about if we, instead, reduce generalized Chern-Simons theory in a de Rham direction?
+
+\begin{lemma} \label{CS_to_BF_diml_red_lemma}
+Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
+The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
+\end{lemma}
+
+\begin{proof}
+\chris{...}
+\end{proof}
 
@@
 So, for the functionals at hand.
-We'll use three properties of the action of $\so(n)$: that -- for spinovs $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.
+We'll use three properties of the action of $\so(n)$: that -- for spinors $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.
 These identities all follow from the equivariance of the pairing $\Gamma$, the scalar pairing $(,)$, and the Clifford multiplication $\rho$.
@@
 
-\begin{theorem}
+Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
+The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.
+These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
+\begin{align*}
+B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
+A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
+\end{align*}
+along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
+
+\begin{theorem} \label{9d_twist_thm}
 The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
@@
 
-The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.  These fields, in the BRST formalism, decompose as
-\begin{align*}
-B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
-A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
-\end{align*}
-along with the ghost $c$. \chris{can prove the theorem by the same argument as in 10d, or using dimensional reduction.}
+\begin{proof}
+Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
+Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.
+According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.
+
+As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_lemma}.
+\end{proof}
+
+\begin{remark}
+One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
+\end{remark}
 
@@
 \subsubsection{The Holomorphic Twist}
+Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
+As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
+This theory can, however, be made canonically $\ZZ$-graded.
+
+\begin{theorem} \label{8d_holo_twist_thm}
+The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
+\end{theorem}
+
+\begin{proof}
+We can demonstrate this by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory, as calculated in Theorem \ref{9d_twist_thm}.  Indeed, \chris{...}
+\end{proof}
+
+\subsubsection{The Rank 2 Twist}
+We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
+We can understand this twist by a second application of Lemma \ref{CS_diml_red_lemma} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
+This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.
+
+\begin{theorem} \label{8d_rank2_twist_thm}
+The twist by a rank 2 supercharge of 8d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with a pair $L_1 \times L_2$ of oriented 1-manifolds is equivalent to mixed Chern-Simons theory on $X_3 \times (L_1 \times L_2)_{\mr{dR}}$.
+\end{theorem}
+
+\begin{proof}
+The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_lemma} twice.
+\end{proof}
+
+\chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}
 
@@
 
-\subsubsection{The Rank 2 Twist}
-
-% \cN=1 SYM, three twists
+\chris{Here we're going to decompose the Yang-Mills fields under $\spin(7)$.
+The vector of $\so(8)$ becomes the 8d Dirac spinor representation, and the two Weyl spinor representations both split as $7+1$, so the fields look like $\psi$, $A_+, A_-, \phi_+, \phi_-$.}
 

### 2019-08-19 paper.tex
Twisting arguments in dimensions 9 and 8

@@
 
+\subsection{A-Type Twists} \label{A_twist_section}
+\chris{...}
+
 \subsection{Dimension 10}
@@
 \begin{align*}
-B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
-A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
+B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
+A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
 \end{align*}
@@
 
-\subsubsection{The Holomorphic Twist}
+\subsubsection{The Holomorphic and Topological Twists}
 Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
@@
 
+On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
+This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a family of degenerations of the holomorphic twist -- the twist by a pure Weyl spinor.
+
+The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.
+If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.
+The BRST fields decompose as
+\begin{align*}
+A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
+\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
+\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
+\end{align*}
+along with the ghost and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
+In terms of these component fields we can write the BV action functional -- split into its BRST and antifield parts -- as
+\begin{align*}
+S_{\mr{BRST}} &= \\ 
+S_{\mr{anti}} &= .
+\end{align*}
+
+\chris{There might be a clever trick to avoid these calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-_1$.) -- I need to think about it.}
+
 \begin{theorem} \label{8d_holo_twist_thm}
 The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
+If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$
 \end{theorem}
@@
 \begin{proof}
-We can demonstrate this by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory, as calculated in Theorem \ref{9d_twist_thm}.  Indeed, \chris{...}
+
 \end{proof}
+
+\begin{remark}
+Alternatively, we can calculate the holomorphic twist by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.
+\end{remark}
 
@@
 \chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}
-
-\subsubsection{The Topological Twist}
-
-\chris{Here we're going to decompose the Yang-Mills fields under $\spin(7)$.
-The vector of $\so(8)$ becomes the 8d Dirac spinor representation, and the two Weyl spinor representations both split as $7+1$, so the fields look like $\psi$, $A_+, A_-, \phi_+, \phi_-$.}
 

### 2019-08-26 paper.tex
merge

@@
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
 \tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
@@
 
-We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
-\begin{definition}
-The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
-\end{definition}
+We call $\cE$ the {\em space of BV fields}.  
+The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
+In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
+Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
+
+\begin{definition}
+The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
+\[
+\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
+\]
+defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
+\chris{Also cite \cite{WittenAntibracket}.}
+\end{definition}
+
+This pairing is graded symmetric and satisfies the graded Jacobi identity.
+Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
 

### 2019-08-26 paper.tex
paper edits

@@
 
-A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
-It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
+A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
+It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$\footnote{Although, for two arbitrary functionals $F, G \in \cO(\cE)$, the bracket $\{F,G\}$ is not defined.}, see Definition \ref{dfn: fnl} in the appendix.
 The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
@@
 In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
-We will refer to this as the {\bf classical BV complex} of the theory.
+We will refer to this as the {\em classical BV complex} of the theory.
 
@@
 \[
-F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
+F^*\colon \left(\cO (\cE')[-1], Q' + \{I',-\} \right) \to \left(\cO (\cE)[-1], Q + \{I,-\} \right).
 \]
@@
 We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
-
-Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
-\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
+\brian{Is there a reason $\rho_2$ is the linear map. I'd thought $\rho_1$...}
+
+Concretely, an action $\rho$ of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
+\[I_{\rho} = \sum_{k\geq 1} I_{\rho}^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
 which satisfies the Maurer--Cartan equation
-\[\{S_{\mr{BV}}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
+\[\{S_{\mr{BV}}, I_\rho^{(k+1)}\} + \d_{CE} I_{\rho}^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I_{\rho}^{(a)}, I_{\rho}^{(b)}\} = 0\]
 for every $k\geq 0$.
@@
 
-%\begin{landscape}
-\begin{figure}
-\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-\node (825) [right=of 82] {};
-\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-
-\draw[arrow] (101) -- (91);
-\draw[arrow] (91) -- (81);
-\draw[arrow] (91) -- (82);
-\draw[arrow] (81) -- (71);
-\draw[arrow] (82) -- (71);
-\draw[arrow] (82) -- (72);
-\draw[arrow] (83) -- (73);
-\draw[arrow] (71) -- (61);
-\draw[arrow] (71) -- (62);
-\draw[arrow] (72) -- (62);
-\draw[arrow] (72) -- (63);
-\draw[arrow] (73) -- (65);
-\draw[arrow] (61) -- (51);
-\draw[arrow] (62) -- (51);
-\draw[arrow] (62) -- (52);
-\draw[arrow] (63) -- (53);
-\draw[arrow] (64) -- (52);
-\draw[arrow] (64) -- (54);
-\draw[arrow] (65) -- (54);
-\draw[arrow] (51) -- (41);
-\draw[arrow] (51) -- (42);
-\draw[arrow] (52) -- (42);
-\draw[arrow] (52) -- (43);
-\draw[arrow] (53) -- (43);
-\draw[arrow] (54) -- (43);
-\draw[arrow] (54) -- (44);
-\draw[arrow] (54) -- (45);
-\draw[arrow] (41) -- (31);
-\draw[arrow] (42) -- (31);
-\draw[arrow] (42) -- (32);
-\draw[arrow] (43) -- (32);
-\draw[arrow] (44) -- (32);
-\draw[arrow] (45) -- (32);
-\draw[arrow] (31) -- (21);
-\draw[arrow] (31) -- (22);
-\draw[arrow] (32) -- (22);
-
-\node (2d) [dimension, left=of 21] {2d};
-\node (3d) [dimension, above=of 2d] {3d};
-\node (4d) [dimension, above=of 3d] {4d};
-\node (5d) [dimension, above=of 4d] {5d};
-\node (6d) [dimension, above=of 5d] {6d};
-\node (7d) [dimension, above=of 6d] {7d};
-\node (8d) [dimension, above=of 7d] {8d};
-\node (9d) [dimension, above=of 8d] {9d};
-\node (10d) [dimension, above=of 9d] {10d};
-\end{tikzpicture}
-\caption{Orbits of square-zero supercharges.}
-\label{fig:superchargeorbits}
-\end{figure}
-%\end{landscape}
+%%\begin{landscape}
+%\begin{figure}
+%\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+%\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+%\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+%\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+%\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+%\node (825) [right=of 82] {};
+%\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+%\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+%\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+%\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+%\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+%\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+%\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+%\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+%\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+%\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+%\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+%\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+%\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+%\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+%\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+%\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+%\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+%\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+%\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+%\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+%\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+%\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+%
+%\draw[arrow] (101) -- (91);
+%\draw[arrow] (91) -- (81);
+%\draw[arrow] (91) -- (82);
+%\draw[arrow] (81) -- (71);
+%\draw[arrow] (82) -- (71);
+%\draw[arrow] (82) -- (72);
+%\draw[arrow] (83) -- (73);
+%\draw[arrow] (71) -- (61);
+%\draw[arrow] (71) -- (62);
+%\draw[arrow] (72) -- (62);
+%\draw[arrow] (72) -- (63);
+%\draw[arrow] (73) -- (65);
+%\draw[arrow] (61) -- (51);
+%\draw[arrow] (62) -- (51);
+%\draw[arrow] (62) -- (52);
+%\draw[arrow] (63) -- (53);
+%\draw[arrow] (64) -- (52);
+%\draw[arrow] (64) -- (54);
+%\draw[arrow] (65) -- (54);
+%\draw[arrow] (51) -- (41);
+%\draw[arrow] (51) -- (42);
+%\draw[arrow] (52) -- (42);
+%\draw[arrow] (52) -- (43);
+%\draw[arrow] (53) -- (43);
+%\draw[arrow] (54) -- (43);
+%\draw[arrow] (54) -- (44);
+%\draw[arrow] (54) -- (45);
+%\draw[arrow] (41) -- (31);
+%\draw[arrow] (42) -- (31);
+%\draw[arrow] (42) -- (32);
+%\draw[arrow] (43) -- (32);
+%\draw[arrow] (44) -- (32);
+%\draw[arrow] (45) -- (32);
+%\draw[arrow] (31) -- (21);
+%\draw[arrow] (31) -- (22);
+%\draw[arrow] (32) -- (22);
+%
+%\node (2d) [dimension, left=of 21] {2d};
+%\node (3d) [dimension, above=of 2d] {3d};
+%\node (4d) [dimension, above=of 3d] {4d};
+%\node (5d) [dimension, above=of 4d] {5d};
+%\node (6d) [dimension, above=of 5d] {6d};
+%\node (7d) [dimension, above=of 6d] {7d};
+%\node (8d) [dimension, above=of 7d] {8d};
+%\node (9d) [dimension, above=of 8d] {9d};
+%\node (10d) [dimension, above=of 9d] {10d};
+%\end{tikzpicture}
+%\caption{Orbits of square-zero supercharges.}
+%\label{fig:superchargeorbits}
+%\end{figure}
+%%\end{landscape}
 

### 2019-08-28 paper.tex
4d n=1

@@
 
+\brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
+
 \begin{theorem} \label{9d_twist_thm}
@@
 
-Let $R$ be a complex representation of $\mf g$.
-
-The matter sector of the theory is labeled by the BRST fields:
-\begin{itemize}
-\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
-\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
-\end{itemize} 
-which together define the (abelian) local Lie algebra
-\[
-\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
-\]
-\subsection{Dimension 3}
+The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
+In addition, $4$-dimensional supersymmetry supports a chiral (anti-chiral matter) multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
+
+The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
+This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
+We have written down the action for supersymmetric Yang-Mills numerous times. 
+The kinetic action for $4$-dimensional $\mc N = 1$ matter is of the form
+\[
+S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
+\]
+Here $\<-,-\>_R$ denotes the obvious pairing between $R$ and $R^*$. 
+Super Yang-Mills couples to the matter via the action 
+\[
+S_{\rm couple} = \int \d^4 x \;
+\]
+
+The action by supersymmetry for the $4$-dimensional matter theory is encoded by a linear and quadratic functional
+\begin{align*}
+I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
+I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R
+\end{align*}
+
+There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from hereon. 
+Such supercharges are minimal (i.e. have 2d image).  
+They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think}.  
+The R-symmetry group is $U(1)$, and so the twisted theory by such a supercharge is always $\ZZ$-graded.
+
+We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the $\SU(2)$ stabilizer.
+The fields of the pure Yang-Mills part decomposes as:
+\begin{align*}
+c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
+A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
+\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
+\end{align*}
+
+The matter fields decompose as
+\begin{align*}
+\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
+\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
+\psi_- & \mapsto \beta_0 + \beta_{2,0} \in \Omega^{0,0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) .
+\end{align*}
+
+%
+%The matter sector of the theory is labeled by the BRST fields:
+%\begin{itemize}
+%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
+%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
+%\end{itemize} 
+%which together define the (abelian) local Lie algebra
+%\[
+%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
+%\]
+%\subsection{Dimension 3}
 

### 2019-08-29 paper.tex
Fixing clashes

--- 2019-08-26 paper.tex
@@
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
 \tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
@@
 
-We call $\cE$ the {\em space of BV fields}.  
-The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
-In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
-Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
-
-\begin{definition}
-The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
-\[
-\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
-\]
-defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
-\chris{Also cite \cite{WittenAntibracket}.}
-\end{definition}
-
-This pairing is graded symmetric and satisfies the graded Jacobi identity.
-Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
+We call $\cE$ the {\bf space of BV fields}.  The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted Poisson bracket, in the following way.
+\begin{definition}
+The \emph{BV antibracket} $\{-,-\}$ is the \chris{give at least an informal definition and a reference to a formal definition in the book \cite{Book2}.  Also cite \cite{WittenAntibracket}.}
+\end{definition}
 
@@
 
-When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction.
-\chris{I should say this more clearly, maybe including some general discussion at the beginning of the section, and referring to the figure.}
+When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.
+The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.
 
@@
 As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
-This theory can, however, be made canonically $\ZZ$-graded.
+This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.
 
 On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a family of degenerations of the holomorphic twist -- the twist by a pure Weyl spinor.
+This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
 
@@
 \end{align*}
-along with the ghost and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
-In terms of these component fields we can write the BV action functional -- split into its BRST and antifield parts -- as
+along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
+In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.
+We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.
+The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
+\begin{align*}
+I^{(1)}_t &= \\
+I^{(2)}_t &= .
+\end{align*}
+
+We can also write the BV action functional -- split into its BRST and antifield parts -- as
 \begin{align*}
@@
 
-\chris{There might be a clever trick to avoid these calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-_1$.) -- I need to think about it.}
+\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{1,0}$ and $\chi^-_1$.) -- I need to think about it.}
 

### 2019-09-04 paper.tex
8d interaction sketch calculation

@@
 \begin{align*}
-I^{(1)}_t &= \\
-I^{(2)}_t &= .
-\end{align*}
+I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi_1^+ + t\chi_1^- \rangle + \langle \phi_2^\vee, \chi_2^- + t\chi_2^+ \rangle + \langle (\chi_1^-)\vee + t(\chi_1^+)^\vee, \Lambda F_{1,1} \rangle + \\
+&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \chi_1^0) \rangle \\
+I^{(2)}_t &= \int \langle (\chi_1^+)^\vee + t(\chi_1^-)^\vee, (\chi_1^+)^\vee \rangle.
+\end{align*}
+\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}
 
@@
 \begin{proof}
-
+\chris{Strategy: compute the holomorphic twist, as in 10d, and see which fields survive.
+Then consider the perturbation of the twisted action.
+Show that it doesn't change the fields that survive, maybe using a spectral sequence associated to the perturbation, and compute how the BV differential deforms.}
 \end{proof}

### 2019-09-04 paper.tex
Minor edits to 4d section

@@
 The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
-In addition, $4$-dimensional supersymmetry supports a chiral (anti-chiral matter) multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
+In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
 
@@
 This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
-We have written down the action for supersymmetric Yang-Mills numerous times. 
-The kinetic action for $4$-dimensional $\mc N = 1$ matter is of the form
+We have written down the action for supersymmetric Yang-Mills theory numerous times. 
+The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
 \[
@@
 \]
-Here $\<-,-\>_R$ denotes the obvious pairing between $R$ and $R^*$. 
+Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
 Super Yang-Mills couples to the matter via the action 
@@
 
-The action by supersymmetry for the $4$-dimensional matter theory is encoded by a linear and quadratic functional
+The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
 \begin{align*}
 I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
-I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R
-\end{align*}
-
-There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from hereon. 
+I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.
+\end{align*}
+
+There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on. 
 Such supercharges are minimal (i.e. have 2d image).  
-They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think}.  
-The R-symmetry group is $U(1)$, and so the twisted theory by such a supercharge is always $\ZZ$-graded.
+They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think} \chris{Agreed: a minimal square zero spinor of positive helicity is stabilized by $\SU(2)_-$, but also by a torus in $\SU(2)_+$.}.  
+The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
 

### 2019-09-04 paper.tex
hyper

@@
 Fix an $L_\infty$ algebra $\fg$.
-The {\bf generalized BF theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+The {\bf generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
 \begin{itemize}
@@
 \begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with the BV action
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
 \[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
 \end{example}
+
+Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
+In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$-system.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix a complex vector space $V$.
+The {\bf generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$, where every field is considered even with respect to the $\ZZ/2$-grading.
+$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
+
+\item The BRST action is $S_{BRST} = 0$.
+\end{itemize}
+\end{definition}
+
+The generalized $\beta\gamma$ system is a special case of generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
+
+\brian{Should we say something about coupling here?}
 
@@
 
+\subsubsection{$\cN=(1,0)$ with matter}
+
+The $6$-dimensional $\mc N = (1,0)$ super Yang-Mills theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
+\[
+\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
+\]
+where $W$ is a (complex) $2$-dimensional symplectic vector space. 
+The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation.
+
+A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
+Let $S_-^{6d}$ be the negative $\so(6)$ irreducible spin representation and suppose $R$ is a (complex) symplectic $\fg$-representation, with symplectic pairing labeled by $\<-,-\>_R$. 
+The BRST fields of the $(1,0)$ hypermultiplet consist of a $W \otimes R$-valued scalar
+\[
+\phi \in \Omega^0(\RR^6) \otimes W \otimes R
+\]
+and an $R$ valued negative Weyl spinor
+\[
+\psi_- \in \Omega^0(\RR^6) \otimes S_-^{6d} \otimes R .
+\]
+Denote the induced symplectic pairing on $W \otimes R$ by $\<-,-\>_{W \otimes R}$. 
+The action of the free hypermultiplet is given by
+\[
+S_{\rm matter} (\phi, \psi_-) = \frac{1}{2} \int_{\RR^6} \d^6 x \; \<\partial_{x_i} \phi , \partial_{x_i} \phi\>_{W \otimes R} + \frac{1}{2} \int_{\RR^6} \d^6 x \;\<\psi_-, \sd \dd \psi_-\>_R .
+\]
+
+The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int \<\phi^*, (Q, \psi_-)\>_{W \otimes R} + \int \<\psi^*_-, \rho(\d \phi) Q\>_R \\
+I^{(2)} (Q_1 \otimes Q_2) & = \int \<\psi^*_- , \rho(\Gamma(Q_1, Q_2)) \psi_-\>_R 
+\end{align*}
+where we recall that the pairing is of the form $\Gamma : \Sigma^{\otimes 2} = (S_+ \otimes W)^{\otimes 2} \to V$. \brian{I'm also using $(S_+)^* = S_-$.}
+
 \subsection{Dimension 5}
@@
 \begin{align*}
-I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
+I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_+ \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_-\>_R \\
 I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.

### 2019-09-06 paper.tex
merge error

--- 2019-09-04 paper.tex
@@
 \begin{document}
+
+\tableofcontents
 
@@
 
-When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.
-The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.
+When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction.
+\chris{I should say this more clearly, maybe including some general discussion at the beginning of the section, and referring to the figure.}
 
@@
 As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
-This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.
+This theory can, however, be made canonically $\ZZ$-graded.
 
 On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
+This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a family of degenerations of the holomorphic twist -- the twist by a pure Weyl spinor.
 
@@
 \end{align*}
-along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
-In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.
-We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.
-The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
-\begin{align*}
-I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi_1^+ + t\chi_1^- \rangle + \langle \phi_2^\vee, \chi_2^- + t\chi_2^+ \rangle + \langle (\chi_1^-)\vee + t(\chi_1^+)^\vee, \Lambda F_{1,1} \rangle + \\
-&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \chi_1^0) \rangle \\
-I^{(2)}_t &= \int \langle (\chi_1^+)^\vee + t(\chi_1^-)^\vee, (\chi_1^+)^\vee \rangle.
-\end{align*}
-\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}
-
-We can also write the BV action functional -- split into its BRST and antifield parts -- as
+along with the ghost and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
+In terms of these component fields we can write the BV action functional -- split into its BRST and antifield parts -- as
 \begin{align*}
@@
 
-\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{1,0}$ and $\chi^-_1$.) -- I need to think about it.}
+\chris{There might be a clever trick to avoid these calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-_1$.) -- I need to think about it.}
 
@@
 \begin{proof}
-\chris{Strategy: compute the holomorphic twist, as in 10d, and see which fields survive.
-Then consider the perturbation of the twisted action.
-Show that it doesn't change the fields that survive, maybe using a spectral sequence associated to the perturbation, and compute how the BV differential deforms.}
+
 \end{proof}
@@
 
-The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
+The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
 In addition, $4$-dimensional supersymmetry supports a chiral (anti-chiral matter) multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
@@
 Here $\<-,-\>_R$ denotes the obvious pairing between $R$ and $R^*$. 
-Super Yang-Mills couples to the matter via the action 
+The coupling to Super Yang-Mills couples to the matter via the action \brian{what to say}
 \[
@@
 \]
-
-The action by supersymmetry for the $4$-dimensional matter theory is encoded by a linear and quadratic functional
-\begin{align*}
-I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
-I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R
-\end{align*}
-
+Let $S_{\rm BV}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
+
+The BV action is clearly Poincar\'{e} invariant, so there is an interaction $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
+
+As in Section \ref{symmetry_section}, we encode the action by supersymmetry for the $4$-dimensional matter theory by the functionals
+\begin{align*}
+I^{(1)}_{\rm matter} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, Q_+ \d \phi\>_R + \int \<\psi_-^*, Q_- \d \Bar{\phi}\>_R \\
+I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R 
+\end{align*}
+where $Q_\pm \in S_{\pm}$.
+
+Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$. \brian{this is so similar to the 10d case. How do you suggest we do this?}
+
+\begin{prop} 
+Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
+Then, the functional
+\[
+\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
+\]
+\end{prop}
+
+Note that $I^{(1)}$ is linear in the supersymmetry algebra, and $I^{(2)}$ is quadratic.
+Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.
+
+We proceed to describe the twist of this general $4$-dimensional $\mc N=1$ gauge theory. 
 There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from hereon. 

### 2019-09-06 paper.tex

--- 2019-09-04 paper.tex
@@
 \]
+
 Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
@@
 \]
+Let $S_{\rm BV}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
+
+The BV action is clearly Poincar\'{e} invariant, so there is an interaction $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
 
@@
 \end{align*}
+where $Q_\pm \in S_{\pm}$.
+
+Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$. \brian{this is so similar to the 10d case. How do you suggest we do this?}
+
+\begin{prop} 
+Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
+Then, the functional
+\[
+\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
+\]
+\end{prop}
+
+Note that $I^{(1)}$ is linear in the supersymmetry algebra, and $I^{(2)}$ is quadratic.
+Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.
 

### 2019-09-10 paper.tex
Actions of Lie algebras on field theories

@@
 
-Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
+Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading.
+\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
+For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
 
@@
 The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
-In Section 3 of \cite{CosRenorm}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$. 
+In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$.
 Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
@@
 \begin{definition}
-The {\bf BV antibracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
-\[
-\{-,-\} : \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
+The {\bf BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
+\[
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
 \]
 defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
-\chris{Also cite \cite{WittenAntibracket}.}
-\end{definition}
-
-This pairing is graded symmetric and satisfies the graded Jacobi identity.
-Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
+\end{definition}
+
+The BV bracket satisfies the symmetry property
+\[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
+and the graded Jacobi identity. Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
 
@@
 
-\chris{The idea, and a description of the kind of infinitesimal symmetries we're talking about (maybe just by a super Lie algebra in this paper, although we allow $L_\infty$ actions).
-More generally we might consider the action of general local $L_\infty$ algebras.}
-
-\begin{definition} \label{infinitesimal_action_def}
-Let $(E, Q,\omega, I)$ be a classical field theory 
-A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
-\[
-\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
-\]
-More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super Lie algebras
-\[
-\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
-\]
-\end{definition}
-
-We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
-\brian{Is there a reason $\rho_2$ is the linear map. I'd thought $\rho_1$...}
-
-Concretely, an action $\rho$ of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
-\[I_{\rho} = \sum_{k\geq 1} I_{\rho}^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
-which satisfies the Maurer--Cartan equation
-\[\{S_{\mr{BV}}, I_\rho^{(k+1)}\} + \d_{CE} I_{\rho}^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I_{\rho}^{(a)}, I_{\rho}^{(b)}\} = 0\]
-for every $k\geq 0$.
-
-\begin{definition}
-\chris{The definition of the Chevalley-Eilenberg complex with coefficients, in particular the cup product / bracket, with its correct sign.
-Pavel suggested saying that $C^\bullet(\gg; V) = \hom(\sym^\bullet(\gg[1]), V)$, and following the sign rule he used in \cite[Section 2.1]{SafronovCoisoInt}.}
-\end{definition}
-
-\begin{definition}
-\chris{The definition of the equivariant observables in a classical BV theory with a symmetry as the relative Chevalley Eilenberg complex with coefficients in local functionals, with its anti-bracket.}
+In this section we define what it means for a Lie algebra to act on a classical field theory.
+Let $(E, Q,\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Consider the graded vector space
+\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
+parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n).\]
+We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
+\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
+and the BV bracket by the formula
+\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
+where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
+\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
+
+\begin{definition}
+\label{infinitesimal_action_def}
+Let $(E, Q,\omega, I)$ be a classical field theory. An {\bf action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
+\[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
+where $I^{(0)} = I$ and $I^{(k)}\colon \fg^{\otimes k}\rightarrow \oloc(\cE)$, which satisfies the Maurer--Cartan equation
+\[(Q + \d_{CE}) I_\rho + \frac{1}{2} \{I_\rho, I_\rho\} = 0.\]
+\end{definition}
+
+We may also define actions of supergroups on classical field theories.
+
+\begin{definition}
+\label{group_action_def}
+Let $(E, Q, \omega, I)$ be a classical field theory.
+An {\bf action} of a supergroup $G$ on $(E, Q, \omega, I)$ is an action of $G$ on $\cE$ preserving the symplectic pairing $\omega$, differential $Q$ and $I$ together with an action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$ such that for every $x\in\fg$ the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{definition}
@@
 \begin{remark}
-\chris{Remark on the d\'ecalage isomorphism with a reference, then give an interpretation of the relative Chevalley-Eilenberg complex after applying this isomorphism as the inclusion of background fields valued in the constant sheaf with value $\gg$.}
+While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
 \end{remark}
-
-\chris{mention smooth group actions, with a reference.}
 
@@
 
+If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
+\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
+
 \subsection{Examples of BV-BRST Theories}
 
-\begin{comment}
-\brian{should we make these definitions, recollections, or just conventions?}
-
-If $M$ is a smooth manifold, its {\em de Rham stack}, as a dg ringed space, is 
-\[
-M_{\rm dR} = \left(M , (\Omega^\bu_M, \d_{\rm dR})\right) .
-\]
-
-If $X$ is a complex manifold, there are two naturally associated dg ringed spaces that will be important for us. 
-The first is the $\dbar$-{\em stack}, defined by
-\[
-X_{\dbar} = \left(M , (\Omega^{0,\bu}_X, \dbar) \right) .
-\]
-The next is the {\em Dolbeault stack}, defined by
-\[
-X_{\rm Dol} = \left(M, (\Omega^{\bu,\bu}_X, \dbar)\right) .
-\] 
-Note that as sheaves of dg modules, there is a quasi-isomorphism $(\Omega^{p,*}_M, \dbar) = \Omega^{p, hol}_M$.
-Thus, one can think of the underlying ring of the Dolbeault stack as functions on the shifted holomorphic tangent bundle $T^{1,0} [1] M$ of $M$.
-\end{comment}
+In this section we give some examples of classical field theories we will use.
+All theories we consider in this section except for the Yang--Mills theory are $\ZZ$-graded, i.e.
+all fields are considered even with respect to the $\ZZ/2$-grading.
 
@@
 
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading.
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
 $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
@@
 Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
-In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$-system.
+In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
 
@@
 
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$, where every field is considered even with respect to the $\ZZ/2$-grading.
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
 $F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
@@
 
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$, where every field is considered even with respect to the $\ZZ/2$-grading.
+\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
 
@@
 Let us now give an example of a theory which is not partially holomorphic.
-We will give a general description of the Yang--Mills theory on $M=\RR^n$ with adjoint spinorial matter.
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(n; \CC)$ with an $\so(n)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to \CC^n$ (see Section \ref{sec: susy} for more details on supersymmetry).
+We will give a general description of the Yang--Mills theory on a vector space $V_\RR = \RR^n$ with adjoint spinorial matter.
+Denote by $V=V_\RR\otimes_\RR \CC$ its complexification.
+
+Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$ (see Section \ref{sec: susy} for more details on supersymmetry).
 The fields of super Yang--Mills theory are the following:
 \begin{itemize}
-\item A connection $A \in \Omega^1(\RR^n; \fg)$ on the trivial bundle.
-
-\item A section $\lambda \in \Omega^0(\RR^n; \Pi \Sigma \otimes \fg)$.
-
-\item The ghost field $c\in\Omega^0(\RR^n; \fg)[1]$.
+\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
+
+\item A section $\lambda \in \Omega^0(V_\RR; \Pi \Sigma \otimes \fg)$.
+
+\item The ghost field $c\in\Omega^0(V_\RR; \fg)[1]$.
 \end{itemize}
@@
 Thus, the bundle of BRST fields is
-\[F = (\Omega^1(M)\oplus \Omega^0(M; \Pi\Sigma)\oplus \Omega^0(M)[1])\otimes \fg.\]
+\[F = (\Omega^1(V_\RR)\oplus \Omega^0(V_\RR; \Pi\Sigma)\oplus \Omega^0(V_\RR)[1])\otimes \fg.\]
 The corresponding local super dg Lie algebra $L=F[-1]$ is
@@
 & & & & \\
-& \Omega^0(M; \gg) & \to & \Omega^1(M; \gg) \oplus \Omega^0(M; \Pi \Sigma \otimes \gg) & 
+& \Omega^0(V_\RR; \gg) & \to & \Omega^1(V_\RR; \gg) \oplus \Omega^0(V_\RR; \Pi \Sigma \otimes \gg) & 
 \end{array}
 \]
-whose differential is the de Rham differential $\Omega^0(M; \gg)\rightarrow \Omega^1(M; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.
+whose differential is the de Rham differential $\Omega^0(V_\RR; \gg)\rightarrow \Omega^1(V_\RR; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.
 
@@
 The BRST action is given by
-\[S(A, \lambda) = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]
+\[S(A, \lambda) = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]
 
@@
 The bundle of BV fields is
-\[E = \Omega^1(M; \fg)\oplus \Omega^0(M; \Pi\Sigma\otimes \fg)\oplus \Omega^0(M; \fg)[1] \oplus \Omega^{n-1}(M; \fg^*)[-1]\oplus \Omega^n(M; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(M; \fg^*)[-2].\]
+\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
 The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\[S_{BV} = \int_M \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]
-
-We'll conclude this section with a discussion of the Poincar\'e invariance of classical Yang-Mills theory.
-
-\begin{definition}
-The $n$-dimensional {\bf Poincar\'e group} is the group $\mr{ISO}(n) = \SO(n) \ltimes \RR^n$ of isometries of $\RR^n$ with its flat Riemannian metric.
-The $n$-dimensional {\bf Poincar\'e algebra} $\mf{iso}(n)$ is the Lie algebra of the Poincar\'e group.
-\end{definition}
-
-The $n$-dimensional Poincar\'e algebra acts, in the sense of Definition \ref{infinitesimal_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
-\chris{define the interaction functional $I_\mr{Poin}$ associated to the Poincar\'e action on Yang-Mills theory.}
-
-\begin{prop} \label{YM_Poincare_invariant_prop}
-Yang--Mills theory is \emph{Poincar\'e invariant}.  That is, the classical BV action functional satisfies the Maurer-Cartan equation
-\[\{S_{BV}, I_{\mr{Poin}}\} + \d_{CE} I_{\mr{Poin}} + \frac 12 \{I_{\mr{Poin}}, I_{\mr{Poin}}\} = 0.\]
-\end{prop}
-\begin{proof}
-\chris{...}
-\end{proof}
+\[S_{BV} = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]
+
+We conclude this section with a discussion of the Poincar\'e invariance of classical Yang--Mills theory.
+
+\begin{definition}
+The {\bf Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The {\bf Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
+\end{definition}
+
+The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
+Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
+The corresponding Hamiltonian is given by
+\[
+I_{\mr{Poin}}(v) = \int_{V_\RR} (v.A) \wedge A^* + (v.\lambda) \lambda^* + (v.c)c^*,
+\]
+where $v\in\mf{iso}(V)$.
 
@@
 In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
+
+\subsection{Supersymmetry algebras}
 

### 2019-09-11 paper.tex
Merging changes

@@
 
+\maketitle
+
 \tableofcontents
-
-\maketitle
 
@@
 The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
-It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\phi_2$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.
+It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.
 
@@
 \begin{align*}
-A &\mapsto A_{0,1} + A_{1,0} + \chi^0_1 + \chi^0_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
-\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+_1 + \chi^+_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
-\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^-_1 + \chi^-_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
-\end{align*}
-along with the ghost $c$ and the two scalar fields $\phi_1$ and $\phi_2$, which remain unchanged.
+A &\mapsto A_{0,1} + A_{1,0} + \phi_2 + \wt \phi_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
+\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+ + \wt \chi^+ \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
+\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^- + \wt \chi^- \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
+\end{align*}
+along with the ghost $c$ and the two scalar fields $\phi_1$ and $\wt \phi_1$, which remain unchanged.
 In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.
@@
 \begin{align*}
-I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi_1^+ + t\chi_1^- \rangle + \langle \phi_2^\vee, \chi_2^- + t\chi_2^+ \rangle + \langle (\chi_1^-)\vee + t(\chi_1^+)^\vee, \Lambda F_{1,1} \rangle + \\
-&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \chi_1^0) \rangle \\
-I^{(2)}_t &= \int \langle (\chi_1^+)^\vee + t(\chi_1^-)^\vee, (\chi_1^+)^\vee \rangle.
+I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi^+ + t\chi^- \rangle + \langle \phi_2^\vee, \wt \chi^- + t\wt \chi^+ \rangle + \langle (\chi^-)\vee + t(\chi^+)^\vee, \Lambda F_{1,1} \rangle + \\
+&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \phi_2) \rangle \\
+I^{(2)}_t &= \int \langle (\chi^+)^\vee + t(\chi^-)^\vee, (\chi^+)^\vee \rangle.
 \end{align*}
@@
 
-\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $A_{0,1}, \chi^0_1, \phi_1, \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{1,0}$ and $\chi^-_1$.) -- I need to think about it.}
+\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $c, A_{0,1}, \phi_1, \phi_2 \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-$, and their antifields.) -- I need to think about it.}
 

### 2019-09-11 Rough_8d_notes.tex
Adding a version of the rough 8d notes file to the repo

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\Dens}{\mathrm{Dens}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{Twists of supersymmetric gauge theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

As we break 10d SYM from $\spin(10)$ to further subgroups of the spin group, the super Yang-Mills fields decompose as follows:
\[
\xymatrix{
&\lambda \ar[dl]_{\to \Spin(8)} \ar[dr]^{\to \SU(5)} &\\
\lambda_+, \lambda_- \ar[dr]_{\to \SU(4)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to \SU(4)} \\
&(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi), \chi \ar[d]_{\to \SU(3)} &\\
&((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+ &
}\]
for the fermions and
\[\xymatrix{
&A \ar[dl]_{\to \Spin(8)} \ar[dr]^{\to \SU(5)} & \\
A,\phi, \wt \phi \ar[dr]_{\to \SU(4)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to \SU(4)} \\
&A_{0,1},A_{1,0},\phi, \wt \phi \ar[d]_{\to \SU(3)} & \\
&A_{0,1},A_{1,0},(\phi_1,  \phi_1),(\wt \phi_2, \wt \phi_2)&
}
\]
for the bosons.  Here, for the fermions, the $+,-$ superscripts indicate whether we came from $\lambda_+$ or $\lambda_-$ (and the way the fields decompose otherwise is indicated by the brackets in a way I hope is more-or-less clear).

If we reduce the holomorphically twisted 10d theory to 8d, so restrict from $\SU(5)$ to $\SU(4)$, we can pick up a $\ZZ$-grading, where the fields coming from $\lambda_{\pm}$ have weight $\pm 1$, and where the surviving bosonic scalar $\phi$ has weight $-2$.  The components in the BV complex look like
\[\xymatrix{
&c \ar[r] &A_{0,1} \ar[r] &B_{0,2} \ar[r] &\psi_{0,1}^\vee \ar[r] &\phi^\vee \\
\phi \ar[r] &\psi_{0,1} \ar[r] &B_{0,2}^\vee \ar[r] &A_{0,1}^\vee \ar[r] &c^\vee &
}\]
in degrees $-2, \ldots, 3$.  Now, if we reduce further to $\SU(3)$ representations, this can be rewritten as 
\[\xymatrix{
&c \ar[r] \ar[dr] &A_{0,1} \ar[r] \ar[dr] &\psi^+_{1,0} \ar[r] \ar[dr] &\chi^{-\vee} \ar[dr] & \\
&&\phi_2 \ar[r]  &\psi^+_{0,1} \ar[r]  &\psi^{-\vee}_{0,1} \ar[r] &\phi_1^\vee \\
\phi_1 \ar[r] \ar[dr] &\psi_{0,1}^- \ar[r] \ar[dr] &\psi^{+\vee}_{0,1} \ar[r] \ar[dr] &\phi_2^\vee \ar[dr] && \\
&\chi^- \ar[r]  &\psi^{+\vee}_{1,0} \ar[r]  &A_{0,1}^\vee \ar[r] &c^\vee&
}\]
Note that this looks like the shifted cotangent to the complex $(\Omega^{0,\bullet}(\CC^3) \otimes \Omega^\bullet(\RR^2))[1]$.

If we want to turn on the isomorphism between the two shifted copies of the complex, it looks like we need a pair of functionals that look something like
\begin{align*}
I^{(1)}_t &= t \int \langle c^\vee, \phi_1 \rangle + \langle A_{0,1}^\vee, \psi_{0,1}^- \rangle + \langle \phi_2^\vee, \chi^- \rangle \\
I^{(2)}_t &= t \int \dvol \Lambda (\psi_{1,0}^{+\vee} \wedge \psi_{0,1}^{+\vee}).
\end{align*}
I'm a bit concerned about this, because it's unclear how $c^\vee$ could appear from our description of the supersymmetry action.
\end{document}

### 2019-09-11 paper.tex
Added a remark on a suggestion Brian made

@@
 This implies the same after dimensional reduction, which tells us supersymmetry for the remaining examples: 5d, 3d, and 2d with matter.}
+
+\chris{Brian's suggestion to avoid this second calculation is as follows.
+By assumption, the holomorphically twisted theory will be equivariant for $\SU(n) \ltimes \CC^n$.
+It is also expected to be a cotangent theory, so equivariant for the $\CC^\times$ action that scales the cotangent fiber.
+Brian says that he knows how to calculate the cohomology group corresponding to interactions equivariant for this group, and that it will be one-dimensional.
+As a consequence, the holomorphic twist will have an action which is automatically cohomologous to the expected answer.
+It remains to show that the twisted theory is $\CC^\times$-equivariant.
+The $\CC^\times$ action we should consider is the one where BRST fields have weight 0 and their antifields have weight 1.}
 

### 2019-09-13 paper.tex
merge

@@
 
-\brian{Should we say something about coupling here?}
+\brian{Should we say something about how the holomorphic theories couple here?}
 
@@
 
-The $6$-dimensional $\mc N = (1,0)$ super Yang-Mills theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
-\[
-\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
-\]
-where $W$ is a (complex) $2$-dimensional symplectic vector space. 
-The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation.
-
 A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
@@
 where we recall that the pairing is of the form $\Gamma : \Sigma^{\otimes 2} = (S_+ \otimes W)^{\otimes 2} \to V$. \brian{I'm also using $(S_+)^* = S_-$.}
+These functionals provide an off-shell action of $\cN = (1,0)$ supersymmetry on the free hypermultiplet, as the following proposition shows.
+Below, $\fL_{\rm matter}$ is the abelian local Lie algebra describing the free hypermultiplet, and $\mf A$ is the $(0,1)$ supertranslation algebra.  
+As always, $I_{\rm Poin}$ is the action functional encoding ordinary Poincar\'{e} invariance.
+
+\begin{prop}[\cite{SWchar}]
+The functional
+\[
+\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm matter}) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS_{\rm matter} + \frac{1}{2} \{\fS_{\rm matter}, \fS_{\rm matter}\} \right) = 0 .
+\]
+\end{prop}
+\begin{proof}
+\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
+\end{proof}
+
+Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
+The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
+\[
+\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
+\]
+where $W$ is a (complex) $2$-dimensional symplectic vector space. 
+The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
+The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
+I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
+\end{align*}
+These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, as the following proposition states. 
+Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.
+
+\begin{prop}[\cite{SWchar}]
+The functional
+\[
+\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
+\]
+\end{prop}
+\begin{proof}
+\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
+\end{proof}
+
+\brian{now on to couplings...}
 
@@
 In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$). 
+We note that the results in the section have appeared in \cite{SW4d}.
 
@@
 
-Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$. \brian{this is so similar to the 10d case. How do you suggest we do this?}
-
-\begin{prop} 
+Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$ by:
+\begin{align*}
+I^{(1)}_{\rm gauge} (Q_+, Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda)\> + \<\lambda^*, \sd F_A (Q_+ + Q_-)\> \\
+I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda^*) Q_- + (Q_-, \lambda^*)Q_+)\right\> .
+\end{align*}
+
+\begin{prop}[\cite{SWchar}]
 Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
@@
 
+\begin{prop}[\cite{SWchar}]
+The minimal twist of 4d $\cN=1$ super Yang-Mills coupled to the $\cN=1$ chiral multiplet on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system.
+\end{prop}
 %

### 2019-09-20 paper.tex
couplings

@@
 \end{align}
-Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
+Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory \brian{here is a statement about 10d, but the theorem is about dimensions 3,4, 6, 10} satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
 The remaining terms are those involving the action of supersymmetries.
@@
 \end{align*}
-These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, as the following proposition states. 
+These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, which we proved above in Theorem \label{SUSY_YM_theorem}, and state below as a proposition. 
 Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.
 
-\begin{prop}[\cite{SWchar}]
+ implies the following proposition for $6d$
+\begin{prop}[special case of Theorem \ref{SUSY_YM_theorem}]
 The functional
@@
 \end{prop}
-\begin{proof}
-\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
-\end{proof}
-
-\brian{now on to couplings...}
 
@@
 In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
-We note that the results in the section have appeared in \cite{SW4d}.
 
@@
 This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
-We have written down the action for supersymmetric Yang-Mills theory numerous times. 
+We have written down the action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm gauge}$ here. 
 The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
@@
 Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
-Super Yang-Mills couples to the matter via the action 
-\[
-S_{\rm couple} = \int \d^4 x \;
-\]
-Let $S_{\rm BV}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
+There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields. 
+Since we will not need the explicit form of the coupling in the untwisted theory, we do not give the formula here. 
+Let $S_{\rm BV} = S_{\rm gauge} + S_{\rm matter} + S_{\rm couple}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
 
@@
 \end{align*}
+
+These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we state in the following proposition.
+The result appears in \cite{SWchar}, and we do not repeat the proof here.
 
@@
 Such supercharges are minimal (i.e. have 2d image).  
-They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think} \chris{Agreed: a minimal square zero spinor of positive helicity is stabilized by $\SU(2)_-$, but also by a torus in $\SU(2)_+$.}.  
+They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
 The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
 
-We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the $\SU(2)$ stabilizer.
+We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
 The fields of the pure Yang-Mills part decomposes as:
@@
 
+There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
+\begin{itemize}
+\item The twisted theory is a shifted cotangent theory in the BV formalism. 
+This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
+\item The action functional is invariant with respect to the group $\U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
+\item The action functional is translation invariant, this follows from the fact that the untwisted theory has an 
+\end{itemize}
+
+Let $\fg$ and $R$ be a Lie algebra together with a representation.
+Define the following graded Lie algebra
+\[
+\sG_{\cN=1} = \fg[z_1,z_2] \ltimes \left(\d^2 z \; \fg^* [z_1,z_2] [-1] \oplus R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
+\]
+Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.
+
+\begin{prop}
+The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
+\[
+\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
+\]
+\end{prop}
+
 \begin{prop}[\cite{SWchar}]
-The minimal twist of 4d $\cN=1$ super Yang-Mills coupled to the $\cN=1$ chiral multiplet on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
 \end{prop}

### 2019-10-23 paper.tex
4d calc

@@
 that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.
-Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.
-Similarly we can calculate, (as in \cite{Guillen}):
+
+\brian{Here's the coordinate free argument. 
+\begin{align*}
+[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\ 
+& = i_{[Q_1,Q_2]} (F_A) \\ & = L_{[Q_1,Q_2]} (A) + \d_A(i_X A) .
+\end{align*}
+In the second line we have used the identity 
+\[
+\Gamma(Q_1, \rho(\omega) Q_2) + \Gamma(Q_2, \rho(\omega) Q_1) = i_{[Q_1,Q_2]} (\omega)
+\]
+which holds for every two-form $\omega$. 
+}
+Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
 \begin{align*}
@@
 \begin{align*}
-I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_+ \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_-\>_R \\
-I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.
+I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
+I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R +.
 \end{align*}
 where $Q_\pm \in S_{\pm}$. 
+As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
+\[
+I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
+\]
 
@@
 \begin{align*}
-I^{(1)}_{\rm gauge} (Q_+, Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda)\> + \<\lambda^*, \sd F_A (Q_+ + Q_-)\> \\
+I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda)\> + \<\lambda^*, \sd F_A (Q_+ + Q_-)\> \\
 I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda^*) Q_- + (Q_-, \lambda^*)Q_+)\right\> .
@@
 Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.
+
+\begin{proof}
+First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
+We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
+It is clear that
+\[
+\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 ,
+\]
+so we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
+
+\brian{should I say something about why the term $\{S_{\rm matter}, I^{(1)}\} = 0$.}
+
+The BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$ reads:
+\[
+\{I^{(1)}, I^{(1)}\}(Q_+ + Q_-, Q_+' + Q_-') = \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi}^* + \psi_+ + \psi_-\right) \right\>  .
+\]
+Now
+\begin{align*} 
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
+\end{align*}
+In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
+The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative. 
+Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
+This calculation implies
+\[
+\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
+\]
+for all $Q_\pm, Q_\pm'$.
+
+Next, we prove the following lemma involving the pieces of $I^{(1)}_{\rm matter}$, $I^{(2)}_{\rm matter}$ involving $\psi_\pm$.
+This will finish the proof that the pure matter sector $\fS_{\rm matter}$ satisfies the classical master equation. 
+\begin{lem}
+\[
+\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\} = 0.
+\]
+\end{lem}
+\begin{proof}
+
+\begin{align*}
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = Fierz / 3 \psi \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
+\end{align*}
+\end{proof}
+
+Next, we move on to the gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
+\end{proof}
 
@@
 \item The action functional is invariant with respect to the group $\U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is translation invariant, this follows from the fact that the untwisted theory has an 
-\end{itemize}
-
+\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
+\end{itemize}
+
+The first symmetry we exploit is translation invariance. 
+There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
 Let $\fg$ and $R$ be a Lie algebra together with a representation.
@@
 \[
-\sG_{\cN=1} = \fg[z_1,z_2] \ltimes \left(\d^2 z \; \fg^* [z_1,z_2] [-1] \oplus R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
-\]
+\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
+\]
+One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
 Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.

### 2019-10-23 Rough_8d_notes.tex

@@
 &\lambda \ar[dl]_{\to \Spin(8)} \ar[dr]^{\to \SU(5)} &\\
-\lambda_+, \lambda_- \ar[dr]_{\to \SU(4)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to \SU(4)} \\
-&(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi), \chi \ar[d]_{\to \SU(3)} &\\
+\lambda_+, \lambda_- \ar[dr]_{\to \SU(4)} \ar[d]_{\to \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to \SU(4)} \\
+(A_7^+, \wt \chi^+), (A_7^-, \wt \chi^-) \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi), \chi \ar[d]_{\to \SU(3)} &\\
  &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+ &
@@
 &A \ar[dl]_{\to \Spin(8)} \ar[dr]^{\to \SU(5)} & \\
-A,\phi, \wt \phi \ar[dr]_{\to \SU(4)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to \SU(4)} \\
-&A_{0,1},A_{1,0},\phi, \wt \phi \ar[d]_{\to \SU(3)} & \\
-&A_{0,1},A_{1,0},(\phi_1,  \phi_1),(\wt \phi_2, \wt \phi_2)&
+A,\phi, \wt \phi \ar[dr]_{\to \SU(4)} \ar[d]_{\to \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to \SU(4)} \\
+\lambda_7, \phi, \wt \phi \ar[dr] &A_{0,1},A_{1,0},\phi, \wt \phi \ar[d]_{\to \SU(3)} & \\
+&A_{0,1},A_{1,0},(\phi_1,  \phi_2),(\wt \phi_1, \wt \phi_2)&
 }
@@
 \begin{align*}
-I^{(1)}_t &= t \int \langle c^\vee, \phi_1 \rangle + \langle A_{0,1}^\vee, \psi_{0,1}^- \rangle + \langle \phi_2^\vee, \chi^- \rangle \\
-I^{(2)}_t &= t \int \dvol \Lambda (\psi_{1,0}^{+\vee} \wedge \psi_{0,1}^{+\vee}).
+I^{(1)}_t &= t \int \langle A_{0,1}^\vee, \psi_{0,1}^- \rangle + \langle \phi_2^\vee, \chi^- \rangle \\
+I^{(2)}_t &= t \int \langle c^\vee, \phi_1 \rangle + \dvol \Lambda (\psi_{1,0}^{+\vee} \wedge \psi_{0,1}^{+\vee}).
 \end{align*}
-I'm a bit concerned about this, because it's unclear how $c^\vee$ could appear from our description of the supersymmetry action.
+
+%Let's now restrict the fields in the untwisted classical BV theory now, not to $\SU(4)$ but to $\Spin(7)$, and try to determine the action %of the impure twist using the fact that it is supposed to be compatible with $\Spin(7)$.
+This theory should also be $\ZZ$-graded.
+The %components in the BV complex look like
+%\[\xymatrix{
+%. 
+%}\]
+%again in degrees
+
 \end{document}

### 2019-10-24 paper.tex
small changes

@@
 
+Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
+Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
+
 \brian{should I say something about why the term $\{S_{\rm matter}, I^{(1)}\} = 0$.}
+The equality $\{S_{\rm matter}, I^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
+The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for concreteness. 
+The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
+\begin{align*}
+\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
+& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
+\end{align*}
+The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
+\begin{align*}
+\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
+\end{align*}
+\brian{Get the signs right and these terms should cancel.}
 
@@
 This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
-\item The action functional is invariant with respect to the group $\U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
+\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
 \item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 

### 2019-10-28 paper.tex
merge error
Minor changes

@@
 \[
-\{I^{(1)}, I^{(1)}\}(Q_+ + Q_-, Q_+' + Q_-') = \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi}^* + \psi_+ + \psi_-\right) \right\>  .
+\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
 \]
@@
 \begin{align*} 
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
 \end{align*}
@@
 Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
-This calculation implies
+The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
+Thus, this calculation implies
 \[
@@
 This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively.
+
+\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
 \item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.

### 2019-10-28 paper.tex
edits

@@
 
-The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
-In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
-
-The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
-This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
-We have written down the action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm gauge}$ here. 
-The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
-\[
-S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
-\]
-
-Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
-There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields. 
-Since we will not need the explicit form of the coupling in the untwisted theory, we do not give the formula here. 
-Let $S_{\rm BV} = S_{\rm gauge} + S_{\rm matter} + S_{\rm couple}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
-
-The BV action is clearly Poincar\'{e} invariant, so there is an interaction $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
+The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
+In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$):
+\[
+(\phi, \Bar{\phi}, \psi_\pm) \in 
+\]
+The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
+The field content for the BRST fields in the gauge sector is:
+\[
+(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
+\]
+
+For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
+\[
+(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
+\]
+We have written down the full BV action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm BV, gauge}$.
+
+The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
+\[
+S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
+\]
+Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.
+
+There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
+\begin{align*}
+S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
+& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
+& \pm g^2 \int (\phi \Bar{\phi}) * (\phi \Bar{\phi}) 
+\end{align*}
+\brian{add terms involving antifields}
+
+The action
+\[
+S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's})
+\]
+is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
+
+The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
 
@@
 I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
-I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R +.
+I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
 \end{align*}
@@
 
-Note that $I^{(1)}$ is linear in the supersymmetry algebra, and $I^{(2)}$ is quadratic.
-Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.
+Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.
 
@@
 
-\brian{should I say something about why the term $\{S_{\rm matter}, I^{(1)}\} = 0$.}
-The equality $\{S_{\rm matter}, I^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
-The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for concreteness. 
+The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
+The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
 The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
 \begin{align*}
-\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
+\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
 & = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
@@
 \begin{align*}
-\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
+\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
 \end{align*}
@@
 
-The BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$ reads:
+The computation of the remaining terms in the matter sector are summarized in the following lemma. 
+\begin{lem}
+\[
+\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
+\]
+\end{lem}
+\begin{proof}
+
+First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
 \[
@@
 \]
-Now
+We first focus on terms involving variations of $\phi, \Bar{\phi}$:
 \begin{align*} 
@@
 The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.
+
 Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
@@
 
-Next, we prove the following lemma involving the pieces of $I^{(1)}_{\rm matter}$, $I^{(2)}_{\rm matter}$ involving $\psi_\pm$.
-This will finish the proof that the pure matter sector $\fS_{\rm matter}$ satisfies the classical master equation. 
-\begin{lem}
-\[
-\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\} = 0.
-\]
-\end{lem}
-\begin{proof}
-
+Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$.
+We must show
+\[
+\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
+\]
+for all $Q_\pm, Q_\pm'$.
+
+We start by computing the variation of $\psi_+ + \psi_-$:
 \begin{align*}
@@
 This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
-
-\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
 \item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.

### 2019-10-29 paper.tex
paper

@@
 The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
-In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$):
-\[
-(\phi, \Bar{\phi}, \psi_\pm) \in 
-\]
+In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
+
 The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
@@
 \]
-We have written down the full BV action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm BV, gauge}$.
+
+Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.
 
@@
 & \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
-& \pm g^2 \int (\phi \Bar{\phi}) * (\phi \Bar{\phi}) 
+&\brian{where does this term come from \pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R}
 \end{align*}
@@
 
-Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$ by:
-\begin{align*}
-I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda)\> + \<\lambda^*, \sd F_A (Q_+ + Q_-)\> \\
-I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda^*) Q_- + (Q_-, \lambda^*)Q_+)\right\> .
-\end{align*}
-
-These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we state in the following proposition.
-The result appears in \cite{SWchar}, and we do not repeat the proof here.
+The action of supersymmetry on the gauge sector is encoded by the functionals:
+\begin{align*}
+I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
+I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
+\end{align*}
+
+These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.
+
+%The result appears in \cite{SWchar}, and we do not repeat the proof here.
 
@@
 \begin{proof}
+Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
+Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
+
 First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
 We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
-It is clear that
-\[
-\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 ,
-\]
-so we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
-
-Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
-Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
+From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
+\[
+\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
+\]
+So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
 
@@
 \begin{align*}
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = Fierz / 3 \psi \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
 \end{align*}
@@
 
-Next, we move on to the gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
+Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
 \end{proof}
@@
 There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
-Such supercharges are minimal (i.e. have 2d image).  
+For concreteness, we will fix a nonzero supercharge of negative chirality $$Q = Q_- \in S_-$$ to twist by. 
+Such supercharges are minimal (i.e. have two dimensional image).  
 They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
@@
 
+\begin{itemize}
+\item[(1)] 
 We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
@@
 \begin{align*}
-c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
+c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
 A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
+\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
+\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
+\end{align*}
+and their antifields:
+\begin{align*}
+c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
+A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
+\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
+\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
 \end{align*}
@@
 \phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
+\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
 \psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
-\psi_- & \mapsto \beta_0 + \beta_{2,0} \in \Omega^{0,0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) .
-\end{align*}
-
-There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
-\begin{itemize}
-\item The twisted theory is a shifted cotangent theory in the BV formalism. 
-This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
-\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
+\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
+\end{align*}
+and their antifields:
+\begin{align*}
+\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
+\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
+\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
+\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
+\end{align*}
+
+\item[(2)] Next, we study the linear differential in the twisted theory. 
+At the linear level, the matter and gauge sectors completely decouple. 
+For the matter sector, the linear differential is:
+\[
+\xymatrix{
+\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
+& \Omega^0(\CC^2; R)_{\gamma_0} \ar[r] & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
+\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
+\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
+}
+\]
+For the gauge sector, the linear differential is:
+\[
+\xymatrix{
+\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
+\Omega^0(\CC^2; \fg)_{A_0} \ar[r] & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
+& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
+\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
+& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
+}
+\]
 \end{itemize}
 
-The first symmetry we exploit is translation invariance. 
-There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
-Let $\fg$ and $R$ be a Lie algebra together with a representation.
-Define the following graded Lie algebra
-\[
-\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
-\]
-One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
-Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.
-
-\begin{prop}
-The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
-\[
-\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
-\]
-\end{prop}
+%There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
+%\begin{itemize}
+%\item The twisted theory is a shifted cotangent theory in the BV formalism. 
+%This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
+%\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
+%\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
+%\end{itemize}
+%
+%The first symmetry we exploit is translation invariance. 
+%There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
+%Let $\fg$ and $R$ be a Lie algebra together with a representation.
+%Define the following graded Lie algebra
+%\[
+%\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
+%\]
+%One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
+%Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.
+%
+%
+%\begin{prop}
+%The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
+%\[
+%\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
+%\]
+%\end{prop}
 

### 2019-10-30 paper.tex

@@
 
+There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
+\begin{itemize}
+\item The twisted theory is a shifted cotangent theory in the BV formalism. 
+This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively.
+
+\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
+\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
+\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
+\end{itemize}
+
+The first symmetry we exploit is translation invariance. 
+There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
+Let $\fg$ and $R$ be a Lie algebra together with a representation.
+Define the following graded Lie algebra
 \item[(2)] Next, we study the linear differential in the twisted theory. 

### 2019-10-30 paper.tex
New draft of 8d section

@@
 The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.
-If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$.
-The BRST fields decompose as
-\begin{align*}
-A &\mapsto A_{0,1} + A_{1,0} + \phi_2 + \wt \phi_2 \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
-\lambda_+ &\mapsto \psi^+_{0,1} + \psi^+_{1,0} + \chi^+ + \wt \chi^+ \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg\\
-\lambda_- &\mapsto \psi^-_{0,1} + \psi^-_{1,0} + \chi^- + \wt \chi^- \in (\Omega^{0,1}(\CC^3) \oplus \Omega^{1,0}(\CC^3) \oplus \Omega^0(\CC^3)^2) \otimes \Omega^0(\RR^2_{x^7,x^8}) \otimes \gg
-\end{align*}
-along with the ghost $c$ and the two scalar fields $\phi_1$ and $\wt \phi_1$, which remain unchanged.
-In terms of these component fields we can write the action of our 1-parameter family of supercharges, which we'll denote by $Q_{\mr{hol}} + tQ'$.
-We choose the two supercharge $Q_{\mr{hol}}$ and $Q'$ to each be pure individually, but to have impure sum.
-The action of such a supercharge can be written in terms of a quadratic and a cubic interaction as
-\begin{align*}
-I^{(1)}_t &= \int \langle A_{1,0}^\vee, \psi_{1,0}^- + t\psi_{1,0}^+\rangle + \langle \phi_1^\vee, \chi^+ + t\chi^- \rangle + \langle \phi_2^\vee, \wt \chi^- + t\wt \chi^+ \rangle + \langle (\chi^-)\vee + t(\chi^+)^\vee, \Lambda F_{1,1} \rangle + \\
-&\quad + \langle (\psi^-_{1,0})^\vee + t(\psi^+_{1,0})^\vee, F_{0,2} \rangle + \langle (\psi^-_{0,1})^\vee + t(\psi^+_{0,1})^\vee, \ol \dd_{A_{0,1}} (\phi_1 + \phi_2) \rangle \\
-I^{(2)}_t &= \int \langle (\chi^+)^\vee + t(\chi^-)^\vee, (\chi^+)^\vee \rangle.
-\end{align*}
-\chris{This is a bit of a mess, but it's a first pass guess, and I think it's correct for $t=0$.  I want to identify $F_{0,2}$ on a CY3 with a $(1,0)$ form.}
-
-We can also write the BV action functional -- split into its BRST and antifield parts -- as
-\begin{align*}
-S_{\mr{BRST}} &= \\ 
-S_{\mr{anti}} &= .
-\end{align*}
-
-\chris{There might be a clever trick to avoid these action functional calculations, involving the 10d calculation we already did to argue that certain fields definitely don't contribute (the ones that died in the 10d holomorphic twist, so we're left with only $c, A_{0,1}, \phi_1, \phi_2 \psi^+_{0,1}, \psi^+_{1,0}, \psi^-_{0,1}$ and $\chi^-$, and their antifields.) -- I need to think about it.}
+If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
+So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
+We can write this schematically in the following way.
+
+First, let us consider the reduction of the 10d spinor $\lambda$.
+We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
+We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
+Let us continue to decompose these fields into smaller subgroups.
+We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
+\begin{figure}[!h]
+\[
+\xymatrix{
+&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
+\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
+(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
+ &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
+}\]
+\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
+\label{fig:8dfermiondecomp}
+\end{figure}
+In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
+The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
+Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
+
+We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
+\begin{figure}[!h]
+\[\xymatrix{
+&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
+A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
+\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
+&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
+}
+\]
+\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
+\label{fig:8dbosondecomp}
+\end{figure}
+Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
+
+Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
+We begin by considering $\mr O(8)$ itself.
+\begin{prop} \label{O8_decomposition_of_susy_prop}
+
+After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\begin{align*}
+I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
+I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
+\end{align*}
+if $Q^+$ is an element of $S_+$, and
+\begin{align*}
+I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
+I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
+\end{align*}
+if $Q^-$ is an element of $S_-$.
+\end{prop}
+
+\begin{proof}
+There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
+\chris{Pavel gave this argument, in terms of light-cone coordinates.}
+\end{proof}
+
+\begin{remark}
+A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
+comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
+\end{remark}
+
+Let us now consider the further reductions to $\SU(4)$, to $\spin(7)$, and to their intersection $\SU(3)$.  We will use the form of the supersymmetric interaction term above to prove the following.
 
@@
 The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
-If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$
+If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$.
 \end{theorem}
@@
 \begin{proof}
-\chris{Strategy: compute the holomorphic twist, as in 10d, and see which fields survive.
-Then consider the perturbation of the twisted action.
-Show that it doesn't change the fields that survive, maybe using a spectral sequence associated to the perturbation, and compute how the BV differential deforms.}
+We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
+We can do this by by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.
+More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
+Lemma \ref{CS_to_BF_diml_red_lemma} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
+
+Note that, unlike in 9d, this theory can be made $\ZZ$-graded, rather than just $\ZZ/2\ZZ$-graded.
+To do so, we consider the action of the 8d R-symmetry group $\CC^\times$, where $S_+$ has weight $+1$ and $S_-$ has weight $-1$, so in particular the holomorphic supercharge $Q_+$ has weight 1.
+We've chosen notation for our component fields that makes it easy to read off the R-symmetry weight of each field: fermions with superscript $+$ have weight $+1$, fermions with superscript $-$ have weight $-1$, the bosonic scalars $\phi_1$ and $\wt \phi_1$ have weight -$2$, and the other bosons have weight 0.
+With respect to this $\ZZ$-grading, the classical BV complex, as an $\SU(4)$-module, has the form
+\[\xymatrix{&\Omega^0(X_4; \gg)_c \ar[r] &\Omega^{0,1}(X_4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^+_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{\psi_{0,1}^{-\vee}} \ar[r] &\Omega^{0,4}(X_4; \gg)_{\phi_1^\vee} \\
+\Omega^0(X_4; \gg)_{\phi_1} \ar[r] &\Omega^{0,1}(X_4; \gg)_{\psi_{0,1}^{-}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^{+\vee}_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,4}(X_4; \gg)_{c^\vee}&
+}\]
+placed in cohomological degrees $-2, \ldots, 3$.
+
+Now, suppose $X_4$ splits into a product of the form $X_3 \times S$.  If we restrict to $\SU(3)$ representations, our classical BV complex becomes
+
+\resizebox{1.05\textwidth}{!}{$\xymatrix@C-20pt{&\Omega^0(X_3 \times S; \gg)_c \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{A_{0,1}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^+_{1,0}} \ar[r]  &\Omega^{0,3}(X_3 \times S; \gg)_{\chi^{-\vee}} \ar[rd] & \\
+&&\Omega^0(X_3 \times S; \gg\omega)_{\phi_2} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi^{+}_{0,1}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{\psi^{-\vee}_{0,1}} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{\phi_{1}^{\vee}} \\
+\Omega^0(X_3 \times S; \gg)_{\phi_1} \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{\psi_{0,1}^{-}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^{+\vee}_{0,1}} \ar[r] \ar[rd] &\Omega^{0,3}(X_3 \times S; \gg)_{\phi_{2}^\vee} \ar[rd]&& \\
+&\Omega^0(X_3 \times S; \gg\omega)_{\phi_1} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi_{1,0}^{+\vee}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{c^\vee}&}
+$}
+where Dolbeault forms here refer to forms on $X_3$, and $\omega$ denotes the volume form on $S$.
+
+Let $Q = Q^+ + tQ'$ be a generically topological 1-parameter family of supercharges in $S_+$, where $Q'$ is an impure spinor stabilized by $\spin(7)$.
+The supercharges $Q_+$ and $Q'$ automatically commute, so to complete the proof it remains for us to compute the action of the further supercharge $Q'$ on the classical BV complex above.
+To do so we will use the description of the supersymmetry action from Proposition \ref{O8_decomposition_of_susy_prop}.
+So, we'll first observe that several summands of $I^{(1)}(Q')$ and $I^{(2)}(Q')$ are forced to vanish.
+In $I^{(1)}(Q')$, the term pairing $\lambda_+^\vee$ and $A$ cannot be $\spin(7)$-invariant, so must vanish.
+The same applies to the term pairing $\lambda_-^\vee$ and $\phi_1$.
+We are left with, in terms of $\Spin(7)$-fields,
+\begin{align*}
+I^{(1)}(tQ') &= t\langle\lambda_7^\vee, \lambda^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
+I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 (A_7^{+\vee} , A_7^{+\vee}),
+\end{align*}
+where we pair $A_7^{+\vee}$ with itself using the restriction of the scalar pairing on $S_+$ to the 7d vector representation \chris{can probably be phrased in terms of the $\spin(7)$-structure somehow}.
+Restricting to representations of $\SU(3)$, this takes the form
+\begin{align*}
+I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
+I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 \Lambda(\psi_{0,1}^{+\vee} \wedge \psi_{1,0}^{-\vee}),
+\end{align*}
+plus terms that vanish in the $Q_+$-twist.
+We can then read off the deformation of the $Q_+$-twist by $Q'$: the further differential associated to the $Q'$ supersymmetry turns on an isomorphism between the two copies of $\Omega^{0,\bullet}(X_3, \Omega^\bullet(S;\gg))$ in the $Q_+$-twisted classical BV complex.
+This is exactly the classical field theory described by $\map(X_3 \times S, B\gg)_{\mr{Hod}}$, as required.
 \end{proof}
-
-\begin{remark}
-Alternatively, we can calculate the holomorphic twist by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.
-\end{remark}
 

### 2019-11-04 paper.tex
typo fix
Vector multiplet SUSY

@@
 
+\newcommand{\Cl}{\mathrm{Cl}}
 \newcommand{\Dens}{\mathrm{Dens}}
@@
 
-\subsubsection{Super Yang--Mills Theory} \label{YM_section}
+\subsubsection{Yang--Mills Theory with Spinorial Matter} \label{YM_section}
 
@@
 
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$ (see Section \ref{sec: susy} for more details on supersymmetry).
-The fields of super Yang--Mills theory are the following:
+Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$.
+We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
+\begin{equation}
+(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
+\label{eq:Gammaspinorpairing}
+\end{equation}
+for any $Q_1, Q_2\in\Sigma$ and $v\in V$.
+
+The fields of Yang--Mills theory are as follows:
 \begin{itemize}
@@
 Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).
-We denote by $\sd\d$ the Dirac operator for the zero connection.
 
 The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle.\]
+\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]
 
@@
 The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\[S_{BV} = \int_{V_\RR} \left\langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\right\rangle + (A^*, \d_A c) + (\lambda^*, [\lambda, c]).\]
+\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]
 
@@
 
-The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$ for any choice $\Sigma$ of matter representation.
+The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
 Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
 The corresponding Hamiltonian is given by
-\[
-I_{\mr{Poin}}(v) = \int_{V_\RR} (v.A) \wedge A^* + (v.\lambda) \lambda^* + (v.c)c^*,
-\]
-where $v\in\mf{iso}(V)$.
+\begin{equation}
+I^{(1)}(v) = \int_{V_\RR} -(L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*,
+\label{eq:Poincareaction}
+\end{equation}
+for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
 
@@
 
-\subsection{Supersymmetric Yang-Mills Theory} \label{SUSY_action_section}
-For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10.
-In this subsection we will construct these supersymmetry algebra actions.
-
-In this section, we will consider pairs $(\mf A, \fL)$ consisting of a supersymmetry algebra and an instance of Yang-Mills theory with matter, in one of the following four situations.
+\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
+
+For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
+In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
 \begin{itemize}
@@
 \end{itemize}
-
-\begin{definition}
-In each case we will write $\wt \Sigma$ for the spin representation obtained from $\Sigma$ by parity reversal, so in dimensions 3 and 4 $\wt \Sigma = \Sigma$, in dimension 6 $\wt \Sigma = S_- \otimes W$, and in dimension 10 $\wt \Sigma = S_-$.
-\end{definition}
-
-We'll construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf A$ on the theory $\fL$.  This construction will proceed in two steps.
+These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.
+
+We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
+
+Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
+\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
+by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
+\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
+This gives rise to an action map
+\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
+of two-forms on spinors.
+Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
+\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
+on $\Sigma$ and $\Sigma^*$.
+
+\begin{thm}
+The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
+\begin{align*}
+I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
+I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
+\end{align*}
+satisfies the classical master equation
+\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
+\label{thm:vectormultipletSUSY}
+\end{thm}
+
+The rest of the section will be devoted to the proof of the above theorem.
+
+Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
+\begin{equation}
+q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
+\label{eq:quantizationtwoforms}
+\end{equation}
+
+The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.
+
+The following properties of the Clifford action will be useful.
+Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
+
+\begin{prop}
+One has the following:
 \begin{enumerate}
- \item There is an ordinary Lie action of the super Lie algebra $\mf A$ on the theory $\fL$, extending the standard action of the $n$-dimensional Poincar\'e algebra by isometries of $\RR^{n}$ as discussed in Section \ref{YM_section}, which is only well-defined on-shell.
-In other words, there is a linear map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ which is a Lie action modulo the ideal generated by the equations of motion.
- \item We can promote this on-shell action to an $L_\infty$ map $\delta^{(1)} \colon \mf A \to \cloc^\bu(\fL)[-1]$ by including a quadratic term $\delta^{(2)}$ which ``corrects'' for the failure of the map $\delta^{(1)}$ to be a Lie map on-the-nose.
+\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
+\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
+
+\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
+\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]
+
+\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
+\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
 \end{enumerate}
-This construction only works in the four special dimensions $3,4,6$ and 10: our argument will use results of Baez and Huerta \cite{BaezHuerta} proven using the structure of the four normed division algebras $\RR, \CC, \bb H$ and $\bb O$.
-In particular, we will use the following ``3-$\psi$'s rule'', discussed in the 10-dimensional case by Schray \cite{Schray} .
-Let $g(v,w)$ denote the Riemannian metric on $\RR^n$.
-
-\begin{theorem}[{\cite[Theorem 11]{BaezHuerta}}] \label{3_psi_thm}
-The multilinear map 
-\[T \colon \Sigma \otimes \Sigma \otimes \Sigma \otimes \Sigma \to \CC,\]
-obtained by symmetrizing the expression $g(\Gamma(\psi_1,\psi_2), \Gamma(\psi_3, \psi_4))$ in the first three variables, is zero.
-\end{theorem}
-
-We'll begin with a discussion of the on-shell supersymmetry action, discuss its failure to close off-shell, and then derive the $L_\infty$-correction to this failure.
-Then we'll state and prove the main theorem of this section: the fact that our super Yang-Mills theories are supersymmetric.
-
-So, we start by discussing the on-shell supersymmetry.  The fermionic part of the supersymmetry algebra is defined by saying that $Q \in \Sigma$ acts infinitesimally by
-\[
-\begin{pmatrix}
-A \\ \lambda
-\end{pmatrix}
-\mapsto
-\begin{pmatrix} A + \delta_Q A \\
-\lambda + \delta_Q \lambda
-\end{pmatrix}
-\]
-where 
-\begin{align*}
-\delta_Q A &= \Gamma(Q,\lambda) \\
-\delta_Q \lambda &= \sd F_A Q .
-\end{align*}
-Here, the notation $\sd F_A$ stands for the iterated Clifford multiplication $\sd F_A = F_{ij} \gamma^i \gamma^j$.  We can check that this supersymmetry action does not close off-shell.
-
-\begin{lemma} \label{onshell_action_lemma}
-Suppose $Q_1, Q_2 \in \Sigma$ and $(A, \lambda)$ are super Yang-Mills fields.
-The following relations hold:
-\begin{itemize}
-\item[(1)] \label{10dsusyA} $ [\delta_{Q_1}, \delta_{Q_2}] A = \delta_{[Q_1, Q_2]} A$.
-\item[(2)] \label{10dsusyL} $ [\delta_{Q_1}, \delta_{Q_2}] \lambda = \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2$ .
-\end{itemize}
-Here, the commutator on the left hand side of the equations takes place in the algebra of endomorphisms of the space of fields.
+\label{prop:cliffordactionproperties}
+\end{prop}
+
+In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases.
+This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.
+
+\begin{prop}
+Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
+\label{prop:3psi}
+\end{prop}
+
+We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
+\begin{align*}
+\{S_{BV}, I^{(1)}\} &= 0 \\
+\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
+\{I^{(2)}, I^{(2)}\} &= 0.
+\end{align*}
+
+Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$.
+The rest of the claims will be proved in a sequence of Lemmas.
+To simplify the expressions, we drop the integrals and omit the natural pairings.
+
+\begin{lemma}
+One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
 \end{lemma}
-
-We'll prove this lemma after first translating it into more convenient language: the terminology of the equivariant action functional, as introduced in Section \ref{symmetry_section}.
-Our Lemma \ref{onshell_action_lemma} tells us that the supersymmetry action is a Lie algebra homomorphism only modulo the ideal generated by the equation of motion $\sd \dd \lambda = 0$.
-In other words, this supersymmetry action only defined an action of the Lie algebra of supertranslations ``on-shell".
-This calculation suggests introducing a second order correction to the supersymmetry action on the BV theory, which has the chance of closing off-shell.
-Define a second order action depending on the antifield $\lambda^*$ to the gluino $\lambda$ by
-\begin{align*}
-\delta^{(2)} \colon \Sigma \otimes \Sigma \otimes \Gamma(\RR^{n}; \Pi \wt \Sigma[-1]) &\to \Gamma(\RR^{n}; \Pi \Sigma) \\
-Q_1 \otimes Q_2 \otimes \lambda^* &\mapsto - \left(\rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right).
-\end{align*}
-
-We'll rewrite this as a local functional in the theory $\fL$ coupled to the supersymmetry Lie algebra $\mf A$.
-
-\begin{definition}
-The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
-\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
-where 
-\begin{align*}
-I^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
-I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
-\end{align*}
-\end{definition}
-
-We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals, using the interpretation where 
-\begin{align*}
-I^{(1)}(Q) &= \<A^* , \delta_{Q} A\> + \<\lambda^*, \delta_{Q_1} \lambda\> \\
-\text{and } I^{(2)}(Q_1,Q_2) &= \<\lambda^*, \delta^{(2)}_{Q_1,Q_2}\lambda\>.
-\end{align*}
-Let us write $\d_{\mr{CE}}^\Gamma$ for the Chevalley-Eilenberg differential associated to the \emph{supertranslation algebra} $\CC^m \oplus \Pi \Sigma$, with bracket given by the pairing $\Gamma$.
-We include the superscript $\Gamma$ here to distinguish this differential from the Chevalley-Eilenberg differential in the full super Poincar\'e algebra, which we will use below.
-
-\begin{lemma} \label{onshell_interaction_lemma}
-The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
-\[\{I^{(1)},I^{(1)}\} + \d_{\mr{CE}}^\Gamma I^{(1)} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
+\begin{proof}
+Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.
+
+The first term gives
+\begin{align*}
+\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
+&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
+&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
+&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
+\end{align*}
+
+The second term gives
+\begin{align*}
+\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
+\end{align*}
+where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.
+
+By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
+
+The third term gives
+\begin{align*}
+\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
+&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
+\end{align*}
+
+The fourth term gives
+\begin{align*}
+\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
+\end{align*}
+
+Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
+\end{proof}
+
+\begin{remark}
+The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
+\end{remark}
+
+\begin{lemma}
+One has
+\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
 \end{lemma}
-
-\chris{Pavel wants to replace these two proofs: first of Lemma \ref{onshell_action_lemma}, then of Lemma \ref{onshell_interaction_lemma}, with a single coordinate free argument.}
-\begin{proof}[Proof of Lemma \ref{onshell_action_lemma}]
-Both of the two statements are direct calculations using standard Clifford relations which cite below.
-So, we calculate
-\begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\
-&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_1 \gamma^k \gamma^j \gamma^i Q_2) \\
-&=  F_{ij}(Q_2 \gamma^k \gamma^j \gamma^i Q_1 + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
-&= F_{ij}(\delta^{jk}(Q_2\gamma^i Q_i) - Q_2 \gamma^i \gamma^j \gamma^k + Q_2 \gamma^i \gamma^j \gamma^k Q_1)\\
-&=  F_{ij}\delta^{jk}(Q_2 \gamma^i Q_1) \\
-&= \delta_{[Q_1, Q_2]} A,
-\end{align*}
-where on the third line we used the fact that the pairing $\Gamma(-,-)$ is symmetric -- i.e.
-that $\lambda_1 \gamma^i \lambda_2 = \lambda_2 \gamma^i \lambda_1$ -- and on the fourth line we used the Clifford relation $\gamma^j\gamma^j+\gamma^j\gamma^j = \delta^{jk}$.
-
-\brian{Here's the coordinate free argument. 
-\begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] A &= (\Gamma(Q_2,\sd F_A Q_1) + \Gamma(Q_1,\sd F_A Q_2)) \\ 
-& = i_{[Q_1,Q_2]} (F_A) \\ & = L_{[Q_1,Q_2]} (A) + \d_A(i_X A) .
-\end{align*}
-In the second line we have used the identity 
-\[
-\Gamma(Q_1, \rho(\omega) Q_2) + \Gamma(Q_2, \rho(\omega) Q_1) = i_{[Q_1,Q_2]} (\omega)
-\]
-which holds for every two-form $\omega$. 
-}
-Note that, on the gauge fields, the action is a Lie action on the nose, not only on-shell.  Similarly we can calculate, (as in \cite{Guillen}):
-\begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] \lambda &= (\sd F_{\Gamma(Q_2, \lambda)} Q_1 + \sd F_{\Gamma(Q_1,\lambda)} Q_2) \\
-&= \frac 12((Q_2 (\gamma_j \dd_i - \gamma_i \dd_j) \lambda) (\gamma^i \gamma^j Q_1) + (1 \leftrightarrow 2)) \\
-&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) - \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^i \gamma^j Q_2) \\
-&= \frac 12((Q_2 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_1 + (Q_1 \gamma_j \dd_i \lambda) \gamma^i \gamma^j Q_2) + \frac 12((Q_2 \gamma_i \dd_j \lambda) \gamma^j \gamma^j Q_1 + (Q_1 \gamma_i \dd_j \lambda) \gamma^j \gamma^i Q_2) + \\
-&\quad - \frac 12((Q_2 \gamma_i \dd_j \lambda) \delta_{ij} Q_1 + \frac 12(Q_1 \gamma_i \dd_j \lambda) \delta^{ij} Q_2) \\
-&= ((Q_1 \gamma_j Q_2) (\gamma^i \gamma^j \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2
-\end{align*}
-using the fact that 
-\[(\psi_1 \gamma_j \psi_2)(\gamma^j \psi_3) + (\psi_2 \gamma_j \psi_3)(\gamma^j \psi_1) + (\psi_3 \gamma_j \psi_1)(\gamma^j \psi_2) = 0,\]
-as in Theorem \ref{3_psi_thm}.  Making one more simplification using the Clifford relations, we have
-\begin{align*}
-[\delta_{Q_1}, \delta_{Q_2}] \lambda &= ((Q_1 \gamma_j Q_2) (\delta^{ij} \dd_i \lambda) - ((Q_1 \gamma_j Q_2) (\gamma^j \gamma^i \dd_i \lambda) - \frac 12(Q_2 \gamma_i \dd_i \lambda)Q_1 - \frac 12(Q_1 \gamma_i \dd_i \lambda)Q_2 \\
-&= \delta_{[Q_1,Q_2]} \lambda - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_2, \sd \dd \lambda)Q_1 - \frac 12(Q_2, \sd \dd \lambda)Q_2.
-\end{align*}
+\begin{proof}
+Evaluating the equation
+\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
+on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
+So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
+
+The individual terms are
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
+= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
+&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
+\end{align*}
+\begin{align*}
+(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
+&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
+\end{align*}
+and
+\begin{align*}
+\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
+&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
+\end{align*}
+The total coefficient in front of $A^*$ is
+\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
+Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
+
+The total coefficient in front of $c^*$ is
+\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
+
+The total coefficient in front of $\lambda^*$ is
+\begin{align*}
+&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
+&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
+\end{align*}
+Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
+\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
+which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
 \end{proof}
 
-\begin{proof}[Proof of Lemma \ref{onshell_interaction_lemma}]
-The functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
-\begin{align*}
-\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_{Q_1} A\> + \<\lambda^*, \delta_{Q_1} \lambda\>, \<A^* , \delta_{Q_2} A\> + \<\lambda^*, \delta_{Q_2} \lambda\> \} \\
-&= 2(\langle A^*, [\delta_{Q_1}, \delta_{Q_2}] A \rangle + \langle \lambda^*, [\delta_{Q_1}, \delta_{Q_2}] \lambda \rangle) \\
- &= 2(\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + \langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle  - \rho(\Gamma(Q_1,Q_2)) \sd \dd \lambda - \frac 12(Q_1, \sd \dd \lambda)Q_2 - \frac 12(Q_2, \sd \dd \lambda)Q_1) \\
- &= 2\langle A^*, \delta_{[Q_1,Q_2]} A \rangle + 2\langle \lambda^*, \delta_{[Q_1,Q_2]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
- &= - \d_{\mr{CE}}^\Gamma I^{(1)} -2\{S_{\mr{BV}} , I^{(2)}\},
-\end{align*}
-where we applied Lemma \ref{onshell_action_lemma} on the third line. \chris{note, we should be careful to make sure that the sign in the $\d_{\mr{CE}}^\Gamma I^{(1)}$ term is correct.}
-\end{proof}
-
-The functionals $I^{(1)}$ and $I^{(2)}$ are also rotation invariant, in the following sense.
-Let $\d^{\mr{rot}}_{\mr{CE}}$ denote the Chevalley Eilenberg differential in the super Lie algebra $\so(n) \ltimes \Pi \Sigma$.
-The total Chevalley-Eilenberg differential, applied to a functional $F$ on the purely fermionic part of the super Poincar\'e algebra, is therefore the sum
-\[\d_{\mr{CE}}(F) = \d^\Gamma_{\mr{CE}}(F) + \d^{\mr{rot}}_{\mr{CE}}(F).\]
-
-\begin{lemma} \label{SUSY_rotation_invariance_lemma}
-Let $I_{\mr{rot}}$ be the interaction associated to the action of the Lie algebra $\mf{so}(n)$ on super Yang-Mills theory from Theorem \ref{YM_Poincare_invariant_prop}.
-The functionals $I^{(1)}$ and $I^{(2)}$ are Poincar\'e invariant, meaning that
-\begin{equation}\label{rot_invariance_eqn}
- \d^{\mr{rot}}_{\mr{CE}} I^{(i)} = - \{I_{\mr{rot}}, I^{(i)}\},
-\end{equation}
-for $i=1,2$.
+Evaluating the equation
+\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
+on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in\Sigma$.
 \end{lemma}
-
 \begin{proof}
-Let $X$ be an element of $\so(n)$, and write $X \cdot A$ and $X \cdot \lambda$ for the image of the fields $A$ and $\lambda$ under the action of the symmetry $X$.  In particular, we can write
-\[I_{\mr{rot}}(A,\lambda, A^\vee, \lambda^\vee, X) = \langle A^\vee, X \cdot A \rangle + \langle \lambda^\vee, X \cdot \lambda \rangle.
-\]
-Therefore, the operator $\{I_{\mr{rot}}(X), -\}$ on the space of local functionals is freely generated by the operator on linear functionals in the Yang-Mills BV fields given by the action of the rotation $X$.
-On the other hand, the Chevalley-Eilenberg differential $\d^{\mr{rot}}_{\mr{CE}}$ is freely generated by the operator on \emph{supertranslations} in $\Sigma$, sending $Q$ to $X \cdot Q$.
-
-So, for the functionals at hand.
-We'll use three properties of the action of $\so(n)$: that -- for spinors $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.
-These identities all follow from the equivariance of the pairing $\Gamma$, the scalar pairing $(,)$, and the Clifford multiplication $\rho$.
-Using these facts, we compute
-\begin{align*}
-\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
-&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
-&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
-&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)}(A,\lambda, A^\vee, \lambda^\vee, Q, X),
-\end{align*}
-and
-\begin{align*}
-\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2, X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
-&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
-&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
-&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
-&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
-&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}(\lambda^\vee, Q_1, Q_2, X).
-\end{align*}
-\end{proof}
-
-Now that we've defined the supersymmetry action, we can prove the main theorem of this section: that minimal super Yang-Mills theory in dimensions $n=3,4,6$ and 10 is, indeed, a supersymmetric classical field theory.
-
-\begin{theorem} \label{SUSY_YM_theorem}
-Let $S_{\mr{BV}}$ be the BV action functional in the theory $\fL$, and write $I_{\mr{Poin}}$ for the interaction generating the Lie action of the Poincar\'e algebra. The functional
-\[\fS = S_{\mr{BV}} + I_{\mr{Poin}} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]\]
-satisfies the Maurer-Cartan equation
-\begin{equation} 
-\label{nd_MC}
-(\d_{\rm Lie} \fS + \frac{1}{2} \left\{\fS , \fS \right\}) = 0 .
-\end{equation}
-\end{theorem}
-
-\begin{proof}
-We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
-\begin{align}
-\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{CE}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
-&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
-&\quad + \d_{\mr{CE}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
-&\quad + \d_{\mr{CE}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
-&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
-\end{align}
-Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory \brian{here is a statement about 10d, but the theorem is about dimensions 3,4, 6, 10} satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}.
-The remaining terms are those involving the action of supersymmetries.
-
-First, the term \ref{MC_1} vanishes by \cite[Proposition 14]{BaezHuerta}.
-Baez and Huerta prove that in our four critical dimensions, the variation $\delta^{(1)}S_{\mr{BRST}}$ of the ordinary BRST action functional vanishes.
-In particular, this implies that $\delta^{(1)}S_{\mr{BV}} = \{I^{(1)}, S_{\mr{BV}}\}$ also vanishes, since \chris{why?}.
-
-In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.
-Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.
-Indeed, we expand
-\begin{align*}
- \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
- &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + (123) \\
- &= \left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1)\right\rangle + (123),
-\end{align*}
-where $(123)$ indicates symmetrization in the supercharges $Q_1, Q_2, Q_3$.  We can simplify this expression by manipulating the first summand.  Indeed,
-\begin{align*}
-\left\langle A^*\;,\; \Gamma(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*)\right\rangle &= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle - (\lambda^*, Q_3) g(A^*, \Gamma(Q_1,Q_2)).
-\end{align*}
-\chris{needs an argument, and care with signs.
-Probably with the coordinate free argument above we'll have to include some lemmas on spinor manipulation that we can reference here.}  Thus, after symmetrization, we have shown that
-\[\{I^{(1)}, I^{(2)}\}= - \left\langle A^*\;,\; \Gamma(\lambda^*, \rho(\Gamma(Q_1,Q_2)) Q_3)\right\rangle + (123),\]
-which vanishes by Theorem \ref{3_psi_thm}.
-
-Finally, term \ref{MC_4} vanishes because the interaction $I^{(2)}$ only involves antifields: the BV antibracket of two expressions involving only antifields is always zero.
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
+\end{align*}
+
+$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
+By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+The Clifford relation implies that
+\begin{align*}
+\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
+&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
+\end{align*}
+Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
 \end{proof}
@@
 
-\chris{Pavel points out that we would like to know more, namely supersymmetry for theories with supersymmetric matter.  In order to prove this, we have to check :
-\begin{enumerate}
- \item That the 4d chiral and 6d hyper multiplet are supersymmetric.
- \item That the coupling terms $I_{\mr{coupling}}$ between these multiplets and the vector multiplet satisfy $\{I_{\mr{coupling}}, I^{(i)}\} = 0$ for $i=1,2$ (the $I^{(i)}$ split into a term describing the action on the vector as above, plus a term describing the action on the matter, and in the bracket these must cancel.)
-\end{enumerate}
-This implies the same after dimensional reduction, which tells us supersymmetry for the remaining examples: 5d, 3d, and 2d with matter.}
-
-\chris{Brian's suggestion to avoid this second calculation is as follows.
-By assumption, the holomorphically twisted theory will be equivariant for $\SU(n) \ltimes \CC^n$.
-It is also expected to be a cotangent theory, so equivariant for the $\CC^\times$ action that scales the cotangent fiber.
-Brian says that he knows how to calculate the cohomology group corresponding to interactions equivariant for this group, and that it will be one-dimensional.
-As a consequence, the holomorphic twist will have an action which is automatically cohomologous to the expected answer.
-It remains to show that the twisted theory is $\CC^\times$-equivariant.
-The $\CC^\times$ action we should consider is the one where BRST fields have weight 0 and their antifields have weight 1.}
+\subsection{Chiral multiplet}
+
+\pavel{6d $\cN=(1, 0)$ and 4d $\cN=1$.}
 
@@
 \subsection{Dimension 10}
-We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
+We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:vectormultipletSUSY}.
 In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
@@
 \begin{align*}
-I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
+I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi_{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
 I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 \Lambda(\psi_{0,1}^{+\vee} \wedge \psi_{1,0}^{-\vee}),
@@
 
-\section{$\infty$-Algebra}
-\label{appx:infinity}
-
-\brian{Not sure if this deserves a whole appendix, but it may be good to spell out what $L_\infty$ modules are, etc..}
-
 \pagestyle{bib}

### 2019-11-04 paper.tex
7d additions

@@
 \subsection{Dimension 7}
-
-% \cN=1 SYM, three twists identical to dimension 8
+The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
+It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
+
+In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
+\begin{enumerate}
+ \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
+ \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
+ \item Rank 2 square-zero spinors, i.e.
+square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
+Such supercharges have a 5-dimensional image in $\CC^7$.
+Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
+
+\begin{theorem} \label{7d_holo_twist_thm}
+The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
+This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem} \label{7d_rank2_twist_thm}
+The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with an oriented 1-manifold $L$ is equivalent to mixed Chern-Simons theory on $X_3 \times (L)_{\mr{dR}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
 

### 2019-11-06 paper.tex
Dimensional reduction update

--- 2019-11-04 paper.tex
@@
 \label{group_action_def}
-Let $(E, Q, \omega, I)$ be a classical field theory.
-An {\bf action} of a supergroup $G$ on $(E, Q, \omega, I)$ is an action of $G$ on $\cE$ preserving the symplectic pairing $\omega$, differential $Q$ and $I$ together with an action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$ such that for every $x\in\fg$ the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An {\bf action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
+\begin{itemize}
+\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
+
+\item An action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$.
+\end{itemize}
+These are required to satisfy the following conditions:
+\begin{itemize}
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
+
+\item For every $x\in\fg$, the vctor field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\end{itemize}
 \end{definition}
@@
 
-\subsection{Examples of BV-BRST Theories}
+\subsection{Examples of Classical Field Theories}
 
@@
 \end{itemize}
-\end{definition}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+\label{def:generalizedBF}
+\end{definition}
+
+\begin{remark}
+We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
+\end{remark}
 
@@
 \end{itemize}
-\label{def:generalizedBF}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+\label{def:generalizedCS}
 \end{definition}
@@
 
-\begin{definition}
-A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if we are given the following data:
-\begin{itemize}
-\item A submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.
-
-\item An isomorphism $p^* E_N\cong E_M$.
-\end{itemize}
-These data are required to satisfy the following conditions:
+In this section we formulate the procedure of dimensional reduction of a classical field theory.
+Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
+an isomorphism $p^*\Dens_N\cong \Dens_M$.
+
+\begin{definition}
+A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 
-\chris{A question: are dimensional reductions, per this definition, unique?
-I'd really like the answer to be yes (at least for dimensional reduction along a vector space), so that I can say the twist of a dimensional reduction is equivalent to \emph{the} (unique) dimensional reduction of the twist -- assuming the dimensional reductions before and after twisting exist (which, again, I'd like them to, at least for dimensional reduction along a vector space).}
+We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
+Thus, dimensional reductions of a given classical field theory on $M$ form a groupoid.
+
+\begin{prop}
+Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
+Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
+
+Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
+If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
+\label{prop:dimensionalreductionunique}
+\end{prop}
+\begin{proof} \textbf{Uniqueness}.
+We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
+Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
+In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
+
+Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
+
+\textbf{Existence}.
+Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
+Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
+Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
+The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
+\end{proof}
+
+By the previous Proposition we may simply talk about \emph{the} dimensional reduction of a given classical field theory when the fibers of $p$ are contractible.
+We will now describe dimensional reductions of the classical Chern--Simons theory.
+
+\begin{prop}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
+\end{prop}
+\begin{proof}
+To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+\[\map(\pt, T^*[-1] B \fg)\]
+has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
+
+We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
+Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
+The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
+Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
+\end{proof}
+
+\begin{prop}
+Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
+\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+\end{prop}
+\begin{proof}
+We may assume $X,Y,M=\pt$ as in the previous proof.
+
+We have
+\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
+and
+\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
+Under the pullback map
+\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
+the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
+\end{proof}
 
@@
 
+\pavel{$Q$ denotes both the differential on fields and the supercharge.}
+
 \begin{definition}
@@
 \end{remark}
+
+\subsection{Compactification of supersymmetric theories}
+
+Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
+
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$. We have a natural embedding
+\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
+so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
+\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
+where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
+\[G_W = G_V\times \Spin(W^\perp_\RR).\]
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
+We have the following generalization of this statement to supersymmetric theories.
+
+\begin{prop}
+Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
+\end{prop}
+
+\begin{prop}
+Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
+Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
+\end{prop}
 

### 2019-11-08 paper.tex
Current 7d status

--- 2019-11-04 paper.tex
@@
 \begin{theorem} \label{7d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with an oriented 1-manifold $L$ is equivalent to mixed Chern-Simons theory on $X_3 \times (L)_{\mr{dR}}$.
+The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
+\chris{actually I need to think about the twisting homomorphism here.}
 \end{theorem}

### 2019-11-08 paper.tex

--- 2019-11-06 paper.tex
@@
 \subsection{Dimension 7}
-
-% \cN=1 SYM, three twists identical to dimension 8
+The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
+It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
+
+In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
+\begin{enumerate}
+ \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
+ \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
+ \item Rank 2 square-zero spinors, i.e.
+square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
+Such supercharges have a 5-dimensional image in $\CC^7$.
+Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
+
+\begin{theorem} \label{7d_holo_twist_thm}
+The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
+This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem} \label{7d_rank2_twist_thm}
+The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
+\chris{actually I need to think about the twisting homomorphism here.}
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
 

### 2019-11-11 paper.tex
merge

--- 2019-11-08 paper.tex
@@
 \subsection{Dimension 7}
-The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
-It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
-
-In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
- \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
- \item Rank 2 square-zero spinors, i.e.
-square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
-Such supercharges have a 5-dimensional image in $\CC^7$.
-Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
-
-\begin{theorem} \label{7d_holo_twist_thm}
-The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-
-\end{proof}
-
-\begin{theorem} \label{7d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
-\chris{actually I need to think about the twisting homomorphism here.}
-\end{theorem}
-
-\begin{proof}
-
-\end{proof}
+
+% \cN=1 SYM, three twists identical to dimension 8
 
@@
 S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
-& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
-&\brian{where does this term come from \pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R}
+& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
 \end{align*}
 \brian{add terms involving antifields}
+\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
+This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter.
+My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
+}
 
@@
 \end{align*}
+\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
+If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
+The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
+Such terms would turn this acyclic.
+Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
+}
 
@@
 \end{lem}
+\brian{extra terms in $I^{(2)}$?}
 \begin{proof}

### 2019-11-11 6dsusy.tex
4d 6d

--- 2019-11-11 paper.tex
@@
-\documentclass[10pt, oneside]{article}
-
-\input ./combined_macros.sty
-
-\newcommand{\Cl}{\mathrm{Cl}}
-\newcommand{\Dens}{\mathrm{Dens}}
-
-\addbibresource{Twist.bib}
-
-\usepackage{pdflscape}
-\usetikzlibrary{shapes.geometric, arrows, positioning}
-
-\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
-\tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
-\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
-\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
-\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
-\tikzstyle{arrow} = [thick,->,>=stealth]
-
-\title{Twists of supersymmetric gauge theories}
-\author{Chris Elliott\and Pavel Safronov \and Brian Williams}
-
-\date{\today}
-
-\begin{document}
-
-\maketitle
-
-\tableofcontents
-
-\section*{Introduction}
-
-\section{The BV-BRST Formalism}
-
-Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading.
-\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
-For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
-
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the space of smooth sections of $E$.
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}).
-We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
-
-\subsection{Classical BV Theories}
-
-\begin{definition}
-A {\bf free BV theory} on a manifold $M$ is the data:
-\begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
-\[
-Q \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
-\item a map of bundles
-\[
-\omega\colon E \otimes E \to \Dens_M [-1]
-\]
-that is
-\begin{enumerate}
-\item[$(1)$] fiberwise nondegenerate,
-\item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
-\end{enumerate}
-\end{itemize}
-\end{definition}
-
-We call $\cE$ the {\em space of BV fields}.  
-The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
-In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$.
-Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
-
-\begin{definition}
-The {\bf BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
-\]
-defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
-\end{definition}
-
-The BV bracket satisfies the symmetry property
-\[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
-and the graded Jacobi identity. Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
-
-\begin{definition}
-A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
-\[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the classical master equation 
-\[Q I + \frac{1}{2} \{I,I\} = 0 .\]
-\end{definition}
-
-Given a classical field theory $(E, Q, \omega, I)$ we denote by
-\[S_{\mr{BV}} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
-the BV action of the theory.
-
-\begin{remark}
-We will also consider {\bf $\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
-\end{remark}
-
-\begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a symplectic isomorphism $L\cong L^![-3]$.
-\end{remark}
-
-A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
-It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$\footnote{Although, for two arbitrary functionals $F, G \in \cO(\cE)$, the bracket $\{F,G\}$ is not defined.}, see Definition \ref{dfn: fnl} in the appendix.
-The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
-\begin{equation}\label{bvcplx}
-\left(\cO(\cE), Q + \{I,-\}\right) .
-\end{equation}
-In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
-We will refer to this as the {\em classical BV complex} of the theory.
-
-\begin{definition}
-A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
-\[
-F\colon E \to E'
-\]
-that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
-\end{definition}
-
-Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
-\[
-F^*\colon \left(\cO (\cE')[-1], Q' + \{I',-\} \right) \to \left(\cO (\cE)[-1], Q + \{I,-\} \right).
-\]
-This allows us to make the following definition of an equivalence between classical theories.
-
-\begin{definition} \label{equivalence_def}
-A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
-\[
-F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
-\]
-\end{definition}
-
-For a short background on homological algebra with differentiable pro-cochain complexes, including the notion of quasi-isomorphism, we refer to Appendix \ref{appx: top}.
-For a more thorough introduction, and for which our conventions are based on, we refer to \cite{Book1}.
-
-\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
-
-In this section we define what it means for a Lie algebra to act on a classical field theory.
-Let $(E, Q,\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-Consider the graded vector space
-\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n).\]
-We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
-\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the BV bracket by the formula
-\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
-where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
-\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-
-\begin{definition}
-\label{infinitesimal_action_def}
-Let $(E, Q,\omega, I)$ be a classical field theory. An {\bf action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
-\[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
-where $I^{(0)} = I$ and $I^{(k)}\colon \fg^{\otimes k}\rightarrow \oloc(\cE)$, which satisfies the Maurer--Cartan equation
-\[(Q + \d_{CE}) I_\rho + \frac{1}{2} \{I_\rho, I_\rho\} = 0.\]
-\end{definition}
-
-We may also define actions of supergroups on classical field theories.
-
-\begin{definition}
-\label{group_action_def}
-Let $(E, Q, \omega, I)$ be a classical field theory.
-An {\bf action} of a supergroup $G$ on $(E, Q, \omega, I)$ is an action of $G$ on $\cE$ preserving the symplectic pairing $\omega$, differential $Q$ and $I$ together with an action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$ such that for every $x\in\fg$ the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
-\end{definition}
-
-\begin{remark}
-While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
-\end{remark}
-
-\subsection{The Classical Factorization Algebra}
-
-Let $(E, Q, \omega, I)$ be a classical BV theory. We recall the formalism of \cite{Book1,Book2} which extracts a factorization algebra on spacetime.
-
-\begin{definition}
-Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
-The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
-\[
-\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
-\]
-\end{definition}
-
-Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
-The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
-It makes sense to restrict fields to any open set $U \subset M$. 
-Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.
-
-The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in \cite[Section 3]{Book2}.
-
-\subsection{From BRST to BV}
-
-\begin{definition}
-A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
-\begin{itemize}
-\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
-\end{itemize}
-Together, these data must satisfy the equation
-\[Q_{BRST} S_{BRST} = 0,\]
-where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
-\end{definition}
-
-We call $\cF$ the {\bf space of BRST fields}.
-
-From a classical BRST theory $(\cF, S_{BRST})$, one can construct a classical BV theory as follows.
-Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
-
-First, we define the free BV theory.
-Split $S_{BRST} = S^{free}_{BRST} + I_{BRST}$, where $I_{BRST}\in\oloc^+(\cF)$ and $S^{free}_{BRST}$ is a quadratic local functional which we may view as defining a map
-\[S^{free}_{BRST}\colon F\rightarrow F^!.\]
-The underlying bundle of the BV theory is
-\[
-E = F \oplus F^! [-1].
-\]
-The differential of the free BV theory is
-\[
-Q = \ell_1 + S^{free}_{BRST}.
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
-
-The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
-These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
-\[
-I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
-\] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
-\]
-
-\begin{lemma}
-Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q, \omega, I)$ is a classical BV theory.
-\end{lemma}
-
-We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of {\bf cotangent type}.
-
-If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
-\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-
-\subsection{Examples of BV-BRST Theories}
-
-In this section we give some examples of classical field theories we will use.
-All theories we consider in this section except for the Yang--Mills theory are $\ZZ$-graded, i.e.
-all fields are considered even with respect to the $\ZZ/2$-grading.
-
-\subsubsection{Generalized BF theory} \label{gen_BF_section}
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix an $L_\infty$ algebra $\fg$.
-The {\bf generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
-
-\item The BRST action is $S_{BRST} = 0$.
-\end{itemize}
-\end{definition}
-
-Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
-\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
-where we denote the two fields by $A$ and $B$. The BV action is
-\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
-where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
-
-\begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
-\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
-\end{example}
-
-Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
-In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix a complex vector space $V$.
-The {\bf generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
-$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-
-\item The BRST action is $S_{BRST} = 0$.
-\end{itemize}
-\end{definition}
-
-The generalized $\beta\gamma$ system is a special case of generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
-
-\brian{Should we say something about how the holomorphic theories couple here?}
-
-\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
-
-The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix an $L_\infty$ algebra $\fg$.
-We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The {\bf generalized Chern--Simons theory} is the following classical BV theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-
-\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
-
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
-
-\item The interaction term is
-\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
-\end{itemize}
-\label{def:generalizedBF}
-\end{definition}
-
-We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
-
-\begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
-\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
-\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
-The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
-Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
-\end{example}
-
-\subsubsection{Yang--Mills Theory with Spinorial Matter} \label{YM_section}
-
-Let us now give an example of a theory which is not partially holomorphic.
-We will give a general description of the Yang--Mills theory on a vector space $V_\RR = \RR^n$ with adjoint spinorial matter.
-Denote by $V=V_\RR\otimes_\RR \CC$ its complexification.
-
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$.
-We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
-\begin{equation}
-(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
-\label{eq:Gammaspinorpairing}
-\end{equation}
-for any $Q_1, Q_2\in\Sigma$ and $v\in V$.
-
-The fields of Yang--Mills theory are as follows:
-\begin{itemize}
-\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
-
-\item A section $\lambda \in \Omega^0(V_\RR; \Pi \Sigma \otimes \fg)$.
-
-\item The ghost field $c\in\Omega^0(V_\RR; \fg)[1]$.
-\end{itemize}
-
-Thus, the bundle of BRST fields is
-\[F = (\Omega^1(V_\RR)\oplus \Omega^0(V_\RR; \Pi\Sigma)\oplus \Omega^0(V_\RR)[1])\otimes \fg.\]
-The corresponding local super dg Lie algebra $L=F[-1]$ is
-\[
-L \;\;\; = \begin{array}{ccccc}
-& \ul{0} & & \ul{1} & \\ 
-& & & & \\
-& \Omega^0(V_\RR; \gg) & \to & \Omega^1(V_\RR; \gg) \oplus \Omega^0(V_\RR; \Pi \Sigma \otimes \gg) & 
-\end{array}
-\]
-whose differential is the de Rham differential $\Omega^0(V_\RR; \gg)\rightarrow \Omega^1(V_\RR; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.
-
-Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).
-
-The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]
-
-The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}).
-Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively.
-The bundle of BV fields is
-\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
-The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]
-
-We conclude this section with a discussion of the Poincar\'e invariance of classical Yang--Mills theory.
-
-\begin{definition}
-The {\bf Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The {\bf Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
-\end{definition}
-
-The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
-Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
-The corresponding Hamiltonian is given by
-\begin{equation}
-I^{(1)}(v) = \int_{V_\RR} -(L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*,
-\label{eq:Poincareaction}
-\end{equation}
-for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
-
-\subsection{Dimensional Reduction, take 2}
-
-\begin{definition}
-A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if we are given the following data:
-\begin{itemize}
-\item A submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.
-
-\item An isomorphism $p^* E_N\cong E_M$.
-\end{itemize}
-These data are required to satisfy the following conditions:
-\begin{itemize}
-\item The diagram
-\[
-\xymatrix{
-p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
-E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
-}
-\]
-is commutative.
-
-\item The diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-is commutative.
-
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
-\end{itemize}
-\end{definition}
-
-\chris{A question: are dimensional reductions, per this definition, unique?
-I'd really like the answer to be yes (at least for dimensional reduction along a vector space), so that I can say the twist of a dimensional reduction is equivalent to \emph{the} (unique) dimensional reduction of the twist -- assuming the dimensional reductions before and after twisting exist (which, again, I'd like them to, at least for dimensional reduction along a vector space).}
-
-\subsection{Dimensional Reduction} \label{dim_red_section}
-The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.
-
-\begin{definition}
-Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection.
-Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.
-The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.
-The symplectic pairing is defined as the composite
-\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
-with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.
-The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
-\[\phi \mapsto i^*(Q(p^*(\phi))).\]
-Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}: there is a canonical map defined on an open set $U \sub \RR^m$ by
-\[\sym^k \mc E^\vee(U\times (\RR^m)^\perp) \to \sym^k p^*i^*\mc E^\vee(U\times (\RR^m)^\perp) \iso \sym^k i^*\mc E(U).\]
-\end{definition}
-
-Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.
-
-\begin{prop} \label{dim_red_SUSY_prop}
-The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
-\end{prop}
-
-\begin{proof}
- \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
-There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\]
- given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
-We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
-
- Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
-There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
-Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.
-We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
-We can then use the same argument as above.
-\end{proof}
-
-\chris{we could alternatively write this in terms of BRST fields.}
-
-\chris{By the way, I see no obstruction to proving the following.
-One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.
-This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
-\begin{lemma} \label{commuting_twist_and_reduction_lemma}
-If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
-\end{lemma}
-
-We'll conclude this section by discussing some examples of dimensional reduction in the context of generalized BF and Chern-Simons theories.
-First we'll describe what happens when we dimensionally reduce generalized Chern-Simons theory along $\RR$ in a holomorphic direction.
-
-\begin{lemma} \label{CS_diml_red_lemma}
-Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
-Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.
-The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
-\end{lemma}
-
-\chris{I haven't made the notation here match the notation in Section \ref{gen_CS_section} yet.}
-
-\begin{proof}
-\chris{sketchy}
-Let us denote the complex of BV fields in our generalized Chern-Simons theory on $X \times C$ by $(E_X \boxtimes \bigwedge^\bullet (T^{0,1}_C)^\vee) \otimes \gg[1]$, with differential on the sheaf of sections given by $Q_X + \ol \dd_C + \ell_1$ and pairing on the sheaf of sections by $\omega_X \boxtimes \omega_C$.
-Write $p$ for the projection $C \to L$.
-It's enough to observe that there is a canonical graded isomorphism $p^*\Omega^\bullet(L) \iso \Omega^{0,\bullet}(C)$ intertwining on the one hand the de Rham and Dolbeault differentials, and on the other hand the two integration maps against the orientation on $L$ and the Calabi-Yau structure on $C$.
-\end{proof}
-
-What about if we, instead, reduce generalized Chern-Simons theory in a de Rham direction?
-
-\begin{lemma} \label{CS_to_BF_diml_red_lemma}
-Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
-The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
-\end{lemma}
-
-\begin{proof}
-\chris{...}
-\end{proof}
-
-\section{Supersymmetry} \label{sec: susy}
-
-In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
-
-\subsection{Supersymmetry algebras}
-
-Let $V_\RR = \RR^n$ endowed with its nondegenerate bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
-\begin{itemize}
-\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the {\bf spin} representation $S$.
-
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the {\bf semi-spin} representations $S_+, S_-$.
-\end{itemize}
-
-\begin{definition}
-A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
-\end{definition}
-
-So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
-
-\begin{definition}
-Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
-\end{definition}
-
-For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
-In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
-\begin{itemize}
-\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
-
-\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
-
-\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
-
-\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
-\end{itemize}
-
-Fix the following data:
-\begin{itemize}
-\item A spinorial representation $\Sigma$ of $\so(V)$.
-
-\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-
-\item A complex Lie group $G_R$, the {\bf group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
-\end{itemize}
-
-Note that the supertranslation Lie algebra $T$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
-
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the Poincar\'{e} group which acts in the obvious way on $M$.
-
-\begin{definition}
-A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
-\end{definition}
-
-\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
-
-For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
-In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
-\begin{itemize}
- \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
- \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
- \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
- \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
-\end{itemize}
-These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.
-
-We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
-
-Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
-\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
-by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
-This gives rise to an action map
-\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
-of two-forms on spinors.
-Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
-\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
-on $\Sigma$ and $\Sigma^*$.
-
-\begin{thm}
-The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
-\begin{align*}
-I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
-I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
-\end{align*}
-satisfies the classical master equation
-\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
-\label{thm:vectormultipletSUSY}
-\end{thm}
-
-The rest of the section will be devoted to the proof of the above theorem.
-
-Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
-\begin{equation}
-q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
-\label{eq:quantizationtwoforms}
-\end{equation}
-
-The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.
-
-The following properties of the Clifford action will be useful.
-Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
-
-\begin{prop}
-One has the following:
-\begin{enumerate}
-\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
-\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
-
-\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
-\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]
-
-\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
-\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
-\end{enumerate}
-\label{prop:cliffordactionproperties}
-\end{prop}
-
-In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases.
-This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.
-
-\begin{prop}
-Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
-\label{prop:3psi}
-\end{prop}
-
-We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
-\begin{align*}
-\{S_{BV}, I^{(1)}\} &= 0 \\
-\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
-\{I^{(2)}, I^{(2)}\} &= 0.
-\end{align*}
-
-Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$.
-The rest of the claims will be proved in a sequence of Lemmas.
-To simplify the expressions, we drop the integrals and omit the natural pairings.
-
-\begin{lemma}
-One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
-\end{lemma}
-\begin{proof}
-Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.
-
-The first term gives
-\begin{align*}
-\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
-&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
-&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
-&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
-\end{align*}
-
-The second term gives
-\begin{align*}
-\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
-\end{align*}
-where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.
-
-By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
-
-The third term gives
-\begin{align*}
-\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
-&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
-\end{align*}
-
-The fourth term gives
-\begin{align*}
-\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
-\end{align*}
-
-Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
-\end{proof}
-
-\begin{remark}
-The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
-\end{remark}
-
-\begin{lemma}
-One has
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
-\end{lemma}
-\begin{proof}
-Evaluating the equation
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
-on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
-So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
-
-The individual terms are
-\begin{align*}
-\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
-= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
-&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
-\end{align*}
-\begin{align*}
-(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
-&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
-\end{align*}
-and
-\begin{align*}
-\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
-&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
-\end{align*}
-The total coefficient in front of $A^*$ is
-\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
-Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
-
-The total coefficient in front of $c^*$ is
-\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
-
-The total coefficient in front of $\lambda^*$ is
-\begin{align*}
-&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
-&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
-\end{align*}
-Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
-\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
-\end{proof}
-
-Evaluating the equation
-\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
-on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.
-
-\begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in\Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
-&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
-\end{align*}
-
-$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
-By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
-The Clifford relation implies that
-\begin{align*}
-\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
-&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
-\end{align*}
-Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
-\end{proof}
-
-We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
-\begin{corollary}
-Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
-Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
-Then the super Poincar\'e algebra
-\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
-obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
-\end{corollary}
-
-\begin{proof}
-This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
-\end{proof}
-
-\begin{remark}
-We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
-\end{remark}
-
-\subsection{Chiral multiplet}
-
-\pavel{6d $\cN=(1, 0)$ and 4d $\cN=1$.}
-
-\subsection{Supersymmetric twisting}
-
-\begin{definition}
-A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{definition}
-
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
-\begin{itemize}
-\item A supercharge $Q$ is {\bf topological} if $d = n$.
-
-\item A supercharge $Q$ is {\bf holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a {\bf holomorphic-topological} (alternatively, partially topological) supercharge.
-The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
-
-\begin{definition}
-A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-We will call $\alpha$ in a twisting datum a {\bf twisting homomorphism}.
-
-\begin{definition}
-Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{definition}
-
-\begin{prop}
-The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
-\end{prop}
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
-\end{remark}
-
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
-
-\section{Twists}
-
-%%\begin{landscape}
-%\begin{figure}
-%\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-%\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-%\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-%\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-%\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-%\node (825) [right=of 82] {};
-%\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-%\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-%\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-%\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-%\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-%\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-%\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-%\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-%\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-%\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-%\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-%\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-%\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-%\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-%\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-%\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-%\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-%\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-%\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-%\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-%\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-%\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-%
-%\draw[arrow] (101) -- (91);
-%\draw[arrow] (91) -- (81);
-%\draw[arrow] (91) -- (82);
-%\draw[arrow] (81) -- (71);
-%\draw[arrow] (82) -- (71);
-%\draw[arrow] (82) -- (72);
-%\draw[arrow] (83) -- (73);
-%\draw[arrow] (71) -- (61);
-%\draw[arrow] (71) -- (62);
-%\draw[arrow] (72) -- (62);
-%\draw[arrow] (72) -- (63);
-%\draw[arrow] (73) -- (65);
-%\draw[arrow] (61) -- (51);
-%\draw[arrow] (62) -- (51);
-%\draw[arrow] (62) -- (52);
-%\draw[arrow] (63) -- (53);
-%\draw[arrow] (64) -- (52);
-%\draw[arrow] (64) -- (54);
-%\draw[arrow] (65) -- (54);
-%\draw[arrow] (51) -- (41);
-%\draw[arrow] (51) -- (42);
-%\draw[arrow] (52) -- (42);
-%\draw[arrow] (52) -- (43);
-%\draw[arrow] (53) -- (43);
-%\draw[arrow] (54) -- (43);
-%\draw[arrow] (54) -- (44);
-%\draw[arrow] (54) -- (45);
-%\draw[arrow] (41) -- (31);
-%\draw[arrow] (42) -- (31);
-%\draw[arrow] (42) -- (32);
-%\draw[arrow] (43) -- (32);
-%\draw[arrow] (44) -- (32);
-%\draw[arrow] (45) -- (32);
-%\draw[arrow] (31) -- (21);
-%\draw[arrow] (31) -- (22);
-%\draw[arrow] (32) -- (22);
-%
-%\node (2d) [dimension, left=of 21] {2d};
-%\node (3d) [dimension, above=of 2d] {3d};
-%\node (4d) [dimension, above=of 3d] {4d};
-%\node (5d) [dimension, above=of 4d] {5d};
-%\node (6d) [dimension, above=of 5d] {6d};
-%\node (7d) [dimension, above=of 6d] {7d};
-%\node (8d) [dimension, above=of 7d] {8d};
-%\node (9d) [dimension, above=of 8d] {9d};
-%\node (10d) [dimension, above=of 9d] {10d};
-%\end{tikzpicture}
-%\caption{Orbits of square-zero supercharges.}
-%\label{fig:superchargeorbits}
-%\end{figure}
-%%\end{landscape}
-
-\subsection{Standard Equivalences Between Classical Field Theories}
-In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
-
-\begin{lemma} \label{symplectomorphism_lemma}
-A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
-\end{lemma}
-
-\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
-In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
-
-\begin{lemma} \label{inclusion_and_projection_lemma}
-Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
-\begin{enumerate}
- \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
-Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
- \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
-Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
-\end{enumerate}
-\end{lemma}
-
-\begin{lemma} \label{symplectic_composite_lemma}
-Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
-Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
-Then the cochain map
-\begin{equation}
-\label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
-\end{equation}
-obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
-\end{lemma}
-
-\begin{lemma} \label{interaction_pullback_lemma}
-In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
-Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
-Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
-\end{lemma}
-
-\begin{proof}
-We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
-Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
-\end{proof}
-
-\subsection{A-Type Twists} \label{A_twist_section}
-\chris{...}
-
-\subsection{Dimension 10}
-We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:vectormultipletSUSY}.
-In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
-These square-zero supercharges are holomorphic.
-
-Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
-The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
-Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
-The BRST fields split as follows:
-\begin{align*}
-c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
-A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
-\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
-\end{align*}
-
-In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
-\begin{align*}
-S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
-S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
-\end{align*}
-where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
-Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
-It has a quadratic and a cubic component given by
-\begin{align*}
-I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
-I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
-\end{align*}
-The twisted action functional is obtained by adding these terms to the original BV action functional.
-
-We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
-
-\begin{theorem}\label{10d_twist_thm}
-The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
-\end{theorem}
-
-\begin{remark}
-From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
-\end{remark}
-
-\begin{proof}
-We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
-
-\begin{enumerate}
- \item The first part of our equivalence of classical field theories will be a simple change of variables.
-Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
-In terms of $\chi'$, the quadratic part of the twisted action functional becomes
- \begin{align*}
-  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
-  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
- \end{align*}
- The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
-However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
-Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
-We think of this as ``integrating out'' the field $\chi'$ and its antifield.
-
- \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
-We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
- \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
-This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
-\chris{This isn't quite right I think.
-We need to kill that term, however, for the below argument to work.
-Can we fix it?}
-
- Observe that the classical BV complex associated to this action functional can now be written in the following form:
- \[\xymatrix{
- &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
- \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
- \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
- }\]
- where the first and third rows are dual under the symplectic pairing.
-This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
-the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
-
- \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
-In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
-Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
-The resulting interaction is
- \[
-  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
- \]
- which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
-The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
-
- \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
-The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
-Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
-an equivalence of classical field theories.
-\end{enumerate}
-\end{proof}
-
-The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-\brian{How do we place 10d YM on an arbitrary 5-fold? 
-Are you using something about sugra?
-} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
-I'm not thinking of using sugra.
-Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
-Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
-
-\subsection{Dimension 9}
-The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
-It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.
-
-There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
-Such supercharges are minimal (i.e.
-have 5d image).
-They are stabilized by $\SU(4)$.
-Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.
-
-Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
-The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.
-These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
-\begin{align*}
-B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
-A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
-\end{align*}
-along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
-
-\brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
-
-\begin{theorem} \label{9d_twist_thm}
-The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-\end{theorem}
-
-\begin{proof}
-Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
-Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.
-According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.
-
-As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_lemma}.
-\end{proof}
-
-\begin{remark}
-One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
-\end{remark}
-
-\subsection{Dimension 8}
-The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
-It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.
-
-In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are holomorphic.
-They are stabilized by $\SU(4)$.
-Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
- \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are topological.
-They are stabilized by $\Spin(7) \sub \SO(8)$.
-Again, twists by such supercharges can be made $\ZZ$-graded.
- \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.
-The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.
-
-\subsubsection{The Holomorphic and Topological Twists}
-Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
-As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
-This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.
-
-On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
-
-The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.
-If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
-So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
-We can write this schematically in the following way.
-
-First, let us consider the reduction of the 10d spinor $\lambda$.
-We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
-We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
-Let us continue to decompose these fields into smaller subgroups.
-We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
-\begin{figure}[!h]
-\[
-\xymatrix{
-&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
-\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
-(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
- &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
-}\]
-\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dfermiondecomp}
-\end{figure}
-In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
-The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
-Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
-
-We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
-\begin{figure}[!h]
-\[\xymatrix{
-&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
-A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
-\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
-&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
-}
-\]
-\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dbosondecomp}
-\end{figure}
-Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
-
-Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
-We begin by considering $\mr O(8)$ itself.
-\begin{prop} \label{O8_decomposition_of_susy_prop}
-
-After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
-I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
-\end{align*}
-if $Q^+$ is an element of $S_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
-I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
-\end{align*}
-if $Q^-$ is an element of $S_-$.
-\end{prop}
-
-\begin{proof}
-There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
-\chris{Pavel gave this argument, in terms of light-cone coordinates.}
-\end{proof}
-
-\begin{remark}
-A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
-comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
-\end{remark}
-
-Let us now consider the further reductions to $\SU(4)$, to $\spin(7)$, and to their intersection $\SU(3)$.  We will use the form of the supersymmetric interaction term above to prove the following.
-
-\begin{theorem} \label{8d_holo_twist_thm}
-The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
-If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.
-More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Lemma \ref{CS_to_BF_diml_red_lemma} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
-
-Note that, unlike in 9d, this theory can be made $\ZZ$-graded, rather than just $\ZZ/2\ZZ$-graded.
-To do so, we consider the action of the 8d R-symmetry group $\CC^\times$, where $S_+$ has weight $+1$ and $S_-$ has weight $-1$, so in particular the holomorphic supercharge $Q_+$ has weight 1.
-We've chosen notation for our component fields that makes it easy to read off the R-symmetry weight of each field: fermions with superscript $+$ have weight $+1$, fermions with superscript $-$ have weight $-1$, the bosonic scalars $\phi_1$ and $\wt \phi_1$ have weight -$2$, and the other bosons have weight 0.
-With respect to this $\ZZ$-grading, the classical BV complex, as an $\SU(4)$-module, has the form
-\[\xymatrix{&\Omega^0(X_4; \gg)_c \ar[r] &\Omega^{0,1}(X_4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^+_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{\psi_{0,1}^{-\vee}} \ar[r] &\Omega^{0,4}(X_4; \gg)_{\phi_1^\vee} \\
-\Omega^0(X_4; \gg)_{\phi_1} \ar[r] &\Omega^{0,1}(X_4; \gg)_{\psi_{0,1}^{-}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^{+\vee}_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,4}(X_4; \gg)_{c^\vee}&
-}\]
-placed in cohomological degrees $-2, \ldots, 3$.
-
-Now, suppose $X_4$ splits into a product of the form $X_3 \times S$.  If we restrict to $\SU(3)$ representations, our classical BV complex becomes
-
-\resizebox{1.05\textwidth}{!}{$\xymatrix@C-20pt{&\Omega^0(X_3 \times S; \gg)_c \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{A_{0,1}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^+_{1,0}} \ar[r]  &\Omega^{0,3}(X_3 \times S; \gg)_{\chi^{-\vee}} \ar[rd] & \\
-&&\Omega^0(X_3 \times S; \gg\omega)_{\phi_2} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi^{+}_{0,1}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{\psi^{-\vee}_{0,1}} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{\phi_{1}^{\vee}} \\
-\Omega^0(X_3 \times S; \gg)_{\phi_1} \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{\psi_{0,1}^{-}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^{+\vee}_{0,1}} \ar[r] \ar[rd] &\Omega^{0,3}(X_3 \times S; \gg)_{\phi_{2}^\vee} \ar[rd]&& \\
-&\Omega^0(X_3 \times S; \gg\omega)_{\phi_1} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi_{1,0}^{+\vee}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{c^\vee}&}
-$}
-where Dolbeault forms here refer to forms on $X_3$, and $\omega$ denotes the volume form on $S$.
-
-Let $Q = Q^+ + tQ'$ be a generically topological 1-parameter family of supercharges in $S_+$, where $Q'$ is an impure spinor stabilized by $\spin(7)$.
-The supercharges $Q_+$ and $Q'$ automatically commute, so to complete the proof it remains for us to compute the action of the further supercharge $Q'$ on the classical BV complex above.
-To do so we will use the description of the supersymmetry action from Proposition \ref{O8_decomposition_of_susy_prop}.
-So, we'll first observe that several summands of $I^{(1)}(Q')$ and $I^{(2)}(Q')$ are forced to vanish.
-In $I^{(1)}(Q')$, the term pairing $\lambda_+^\vee$ and $A$ cannot be $\spin(7)$-invariant, so must vanish.
-The same applies to the term pairing $\lambda_-^\vee$ and $\phi_1$.
-We are left with, in terms of $\Spin(7)$-fields,
-\begin{align*}
-I^{(1)}(tQ') &= t\langle\lambda_7^\vee, \lambda^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 (A_7^{+\vee} , A_7^{+\vee}),
-\end{align*}
-where we pair $A_7^{+\vee}$ with itself using the restriction of the scalar pairing on $S_+$ to the 7d vector representation \chris{can probably be phrased in terms of the $\spin(7)$-structure somehow}.
-Restricting to representations of $\SU(3)$, this takes the form
-\begin{align*}
-I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi_{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 \Lambda(\psi_{0,1}^{+\vee} \wedge \psi_{1,0}^{-\vee}),
-\end{align*}
-plus terms that vanish in the $Q_+$-twist.
-We can then read off the deformation of the $Q_+$-twist by $Q'$: the further differential associated to the $Q'$ supersymmetry turns on an isomorphism between the two copies of $\Omega^{0,\bullet}(X_3, \Omega^\bullet(S;\gg))$ in the $Q_+$-twisted classical BV complex.
-This is exactly the classical field theory described by $\map(X_3 \times S, B\gg)_{\mr{Hod}}$, as required.
-\end{proof}
-
-\subsubsection{The Rank 2 Twist}
-We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
-We can understand this twist by a second application of Lemma \ref{CS_diml_red_lemma} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
-This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.
-
-\begin{theorem} \label{8d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 8d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with a pair $L_1 \times L_2$ of oriented 1-manifolds is equivalent to mixed Chern-Simons theory on $X_3 \times (L_1 \times L_2)_{\mr{dR}}$.
-\end{theorem}
-
-\begin{proof}
-The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_lemma} twice.
-\end{proof}
-
-\chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}
-
-\subsection{Dimension 7}
-
-% \cN=1 SYM, three twists identical to dimension 8
-
-\subsection{Dimension 6}
-
-% \cN=(1, 1) SYM, three twists identical to dimension 8
-
-% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.
-
-\subsubsection{$\cN=(1,0)$ with matter}
-
 A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
@@
 \end{prop}
-
-\subsection{Dimension 5}
-
-% \cN=2 SYM, three twists
-% \cN=1 SYM with matter in a pseudo-real representation, one twist.
-
-\subsection{Dimension 4}
-
-% \cN=4 SYM
-% \cN=2 SYM with matter in a pseudo-real representation
-% \cN=1 SYM with matter in a complex representation
-
-\subsubsection{$\cN=1$ SYM with matter}
-
-The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
-In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
-
-The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
-The field content for the BRST fields in the gauge sector is:
-\[
-(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
-\]
-
-For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
-\[
-(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
-\]
-
-Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.
-
-The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
-\[
-S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
-\]
-Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.
-
-There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
-\begin{align*}
-S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
-& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
-\end{align*}
-\brian{add terms involving antifields}
-\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
-This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter.
-My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
-}
-
-The action
-\[
-S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's})
-\]
-is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
-
-The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
-
-The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
-\begin{align*}
-I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
-I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
-\end{align*}
-where $Q_\pm \in S_{\pm}$. 
-As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
-\[
-I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
-\]
-
-The action of supersymmetry on the gauge sector is encoded by the functionals:
-\begin{align*}
-I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
-I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
-\end{align*}
-\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
-If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
-The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
-Such terms would turn this acyclic.
-Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
-}
-
-These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.
-
-%The result appears in \cite{SWchar}, and we do not repeat the proof here.
-
-\begin{prop}[\cite{SWchar}]
-Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
-Then, the functional
-\[
-\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
-\]
-satisfies the Maurer-Cartan equation
-\[
-\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
-\]
-\end{prop}
-
-Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.
-
-\begin{proof}
-Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
-Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
-
-First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
-We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
-From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
-\[
-\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
-\]
-So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
-
-The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
-The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
-The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
-\begin{align*}
-\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
-& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
-\end{align*}
-The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
-\begin{align*}
-\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
-\end{align*}
-\brian{Get the signs right and these terms should cancel.}
-
-The computation of the remaining terms in the matter sector are summarized in the following lemma. 
-\begin{lem}
-\[
-\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
-\]
-\end{lem}
-\brian{extra terms in $I^{(2)}$?}
-\begin{proof}
-
-First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
-\[
-\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
-\]
-We first focus on terms involving variations of $\phi, \Bar{\phi}$:
-\begin{align*} 
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
-\end{align*}
-In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
-The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.
-
-Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
-The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
-Thus, this calculation implies
-\[
-\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
-\]
-for all $Q_\pm, Q_\pm'$.
-
-Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$.
-We must show
-\[
-\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
-\]
-for all $Q_\pm, Q_\pm'$.
-
-We start by computing the variation of $\psi_+ + \psi_-$:
-\begin{align*}
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
-\end{align*}
-\end{proof}
-
-Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
-\end{proof}
-
-There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
-For concreteness, we will fix a nonzero supercharge of negative chirality $$Q = Q_- \in S_-$$ to twist by. 
-Such supercharges are minimal (i.e. have two dimensional image).  
-They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
-The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
-
-\begin{itemize}
-\item[(1)] 
-We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
-The fields of the pure Yang-Mills part decomposes as:
-\begin{align*}
-c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
-A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
-\end{align*}
-and their antifields:
-\begin{align*}
-c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
-A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
-\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
-\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
-\end{align*}
-
-The matter fields decompose as
-\begin{align*}
-\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
-\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
-\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
-\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
-\end{align*}
-and their antifields:
-\begin{align*}
-\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
-\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
-\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
-\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
-\end{align*}
-
-There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
-\begin{itemize}
-\item The twisted theory is a shifted cotangent theory in the BV formalism. 
-This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively.
-
-\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
-\end{itemize}
-
-The first symmetry we exploit is translation invariance. 
-There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
-Let $\fg$ and $R$ be a Lie algebra together with a representation.
-Define the following graded Lie algebra
-\item[(2)] Next, we study the linear differential in the twisted theory. 
-At the linear level, the matter and gauge sectors completely decouple. 
-For the matter sector, the linear differential is:
-\[
-\xymatrix{
-\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-& \Omega^0(\CC^2; R)_{\gamma_0} \ar[r] & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
-\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
-\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
-}
-\]
-For the gauge sector, the linear differential is:
-\[
-\xymatrix{
-\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-\Omega^0(\CC^2; \fg)_{A_0} \ar[r] & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
-& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
-\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
-& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
-}
-\]
-\end{itemize}
-
-%There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
-%\begin{itemize}
-%\item The twisted theory is a shifted cotangent theory in the BV formalism. 
-%This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
-%\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-%\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
-%\end{itemize}
-%
-%The first symmetry we exploit is translation invariance. 
-%There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
-%Let $\fg$ and $R$ be a Lie algebra together with a representation.
-%Define the following graded Lie algebra
-%\[
-%\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
-%\]
-%One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
-%Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.
-%
-%
-%\begin{prop}
-%The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
-%\[
-%\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
-%\]
-%\end{prop}
-
-\begin{prop}[\cite{SWchar}]
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
-\end{prop}
-%
-%The matter sector of the theory is labeled by the BRST fields:
-%\begin{itemize}
-%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
-%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
-%\end{itemize} 
-%which together define the (abelian) local Lie algebra
-%\[
-%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
-%\]
-%\subsection{Dimension 3}
-
-% \cN=8 SYM
-% \cN=4 SYM with matter in a pseudo-real representation
-% \cN=2 SYM with matter in a complex representation
-
-\subsection{Dimension 2}
-
-% \cN=(8, 8) SYM
-% \cN=(4, 4) SYM with matter in a pseudo-real representation
-% \cN=(2, 2) SYM with matter in a complex representation
-%BRIAN FIND REFERENCE OF BELOW
-% \cN=(0,2) SYM with matter 
-% \cN=(0,4) SYM with matter
-% \cN=(0,8) SYM with matter
-
-\appendix
-
-\section{Functional analysis} \label{appx: top}
-
-\def\CVS{{\rm CVS}}
-\def\DVS{{\rm DVS}}
-
-\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{Book1}, here. }
-
-\subsection{Notations and conventions}
-
-\begin{definition}
-Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
-For any open set $U \subset M$, define the following notations:
-\begin{itemize}
-\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
-\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
-\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
-\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
-\end{itemize}
-\end{definition}
-
-If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
-For an open set $U \subset M$ let 
-\[
-\cE(U)^\vee = \Bar{\cE}^!_c(U)
-\]
-be the continuous, or distributional, dual to $\cE(U)$.
-
-\brian{recall definition of CVS. all our familiar spaces above are in $\CVS$. talk about tensor products.}
-
-\begin{prop}
-Let $E,F$ be vector bundles on $M,N$ respectively.
-Then
-\[
-\cE(M) \Hat{\otimes}_\beta \cF(N) \cong \Gamma(M \times N, E \boxtimes F)
-\]
-\end{prop}
-
-\begin{definition}\label{dfn: fnl}
-Let $E$ be a vector bundle on $M$ and $U \subset M$.
-The {\bf completed algebra of functions} on $\cE(U)$ is
-\[
-\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
-\]
-On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
-\end{definition}
-
-\subsection{Differentiable vector spaces}
-\def\Mfld{{\rm Mfld}}
-
-Let $\Mfld$ denote the site of smooth manifolds (of arbitrary dimension) where the morphisms are smooth maps, and a cover $f : X \to Y$ is a surjective local diffeomorphism.
-
-\begin{definition} 
-We use the following notations and naming conventions for sheaves on $\Mfld$:
-\begin{itemize}
-\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
-\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
-\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
-If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
-\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
-\[
-\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
-\]
-for every smooth manifold $X$, which is required to be natural under pullbacks:
-\[
-f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
-\]
-for every smooth map $f : X \to Y$. 
-A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
-\end{itemize}
-\end{definition}
-
-\subsection{Homological algebra}
-
-There is a functor
-\[
-dif_c : \CVS \to \DVS 
-\]
-from the category of convenient vector spaces to the category of differentiable vector spaces. 
-This functor does not preserve cokernels, so $dif_c$ does not preserve cohomology. 
-In particular, with a naive definition of quasi-isomorphism internal to $\CVS$, the functor $dif_c$ does not preserve quasi-isomorphisms. 
-To avoid this issue, we make the following definition.
-
-\begin{definition}
-Suppose $V,W$ are cochain complexes in convenient vector spaces. 
-A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
-\[
-dif_c (f) : dif_c(V) \to dif_c(W)
-\]
-is a quasi-isomorphism of differentiable vector spaces.
-\end{definition}
-
-The cochain complexes arising in classical field theory are naturally convenient vector spaces. 
-The above definition is used in what we mean by quasi-isomorphism between classical field theories, as in Definition \brian{??}.
-
-Throughout the paper we make use of familiar manipulations with spectral sequences arising from filtrations of cochain complexes internal to differentiable vector spaces. 
-A main tool is the classical Eilenberg-Moore comparison theorem, which is stated as follows.
-
-\begin{thm}[Eilenberg-Moore Comparison]
-Let $f : V \to W$ be a map of filtered cochain complexes in an AB4 abelian category.
-Suppose, for each integer $n$ there exists an integer $p$ such that $F_p V^n = 0 = F_p W^n$.
-If there is an integer $r \geq 0$ such that the induced map on the $r$th page of the corresponding spectral sequences 
-\[
-f_r^{pq} :  E_r^{pq} V \to E_r^{pq} W
-\]
-is an isomorphism for all $p,q$, then $f : V \to W$ is a quasi-isomorphism. 
-\end{thm}
-
-The following is the natural definition of a filtered differentiable cochain complex.
-
-\begin{definition}
-A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
-\[
-\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
-\]
-where each map is a monomorphism in each cohomological degree. 
-A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
-\end{definition}
-
-The category of differentiable vector space is an AB4 category, in fact, it is actually a Grothendieck abelian category.
-
-\begin{thm}[{\cite[Theorem 2.2.1]{Book1}}]
-The category $\DVS$ is a Grothendieck abelian category.
-\end{thm}
-
-In particular, we can freely apply the Eilenberg-Moore comparison result to the types of topological cochain complexes we come across in the BV formalism.
-
-\begin{definition}\label{dfn: pro}
-A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
-\[
-\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
-\]
-where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
-\end{definition}
-
-\subsubsection{The classical BV complex}
-
-\begin{lem}
-If $(E, \omega, Q, I)$ is the data of a classical theory on $M$, then the BV complex
-\[
-\left(\cO(\cE) , Q + \{I,-\}\right)
-\]
-is a differentiable pro-cochain complex.
-More generally, the classical factorization algebra of observables $\Obs$ is a factorization algebra in differentiable pro-cochain complexes. 
-\end{lem}
-
-The above lemma used the natural filtration on the classical BV complex given by polynomial degree of observables. 
-Since the free part of the differential $Q$ always preserves this filtration, the first term of the resulting spectral sequence simply computes the cohomology of the underlying free theory. 
-The differential on the higher pages depend on the interacting part of of the action.
-
-\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
-Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.  
-There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
-\end{lemma}
-\begin{proof}
-The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
-We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
-natural decreasing filtration 
-\[
-F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
-\]
-which is compatible with both $Q$ and $\{I,-\}$ separately.
-The associated graded of this filtration is the differentiable cochain complex given by
-\[
-\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
-\]
-This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
-Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
-\brian{shall we say a word about convergence?
-This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.} \chris{Does convergence require that the interaction is polynomial, or alternatively does this bound the number of differentials appearing in the spectral sequence?}
-\end{proof}
-
-\begin{lemma} \label{invert_quis_lemma}
-Any quasi-isomorphism of differentiable cochain complexes admits a quasi-inverse.
-\end{lemma}
-\brian{I think Pavel had something to say for this lemma.}
-
-\pagestyle{bib}
-\printbibliography
-
-\end{document}

### 2019-11-11 paper.tex
4d 6d

@@
 
-The generalized $\beta\gamma$ system is a special case of generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
-
-\brian{Should we say something about how the holomorphic theories couple here?}
+\begin{rmk}
+This is a special case of generalized BF theory:
+the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
+\end{rmk}
 
@@
 for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
+
+\subsubsection{The free scalar and free fermion}
+
+\brian{does this warrant it's own definition?}
 
@@
 The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
+\brian{Where is the Poincare part?}
 \begin{align*}
@@
 \label{thm:vectormultipletSUSY}
+\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
+\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
 \end{thm}
@@
 
-A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
-Let $S_-^{6d}$ be the negative $\so(6)$ irreducible spin representation and suppose $R$ is a (complex) symplectic $\fg$-representation, with symplectic pairing labeled by $\<-,-\>_R$. 
-The BRST fields of the $(1,0)$ hypermultiplet consist of a $W \otimes R$-valued scalar
-\[
-\phi \in \Omega^0(\RR^6) \otimes W \otimes R
-\]
-and an $R$ valued negative Weyl spinor
-\[
-\psi_- \in \Omega^0(\RR^6) \otimes S_-^{6d} \otimes R .
-\]
-Denote the induced symplectic pairing on $W \otimes R$ by $\<-,-\>_{W \otimes R}$. 
-The action of the free hypermultiplet is given by
-\[
-S_{\rm matter} (\phi, \psi_-) = \frac{1}{2} \int_{\RR^6} \d^6 x \; \<\partial_{x_i} \phi , \partial_{x_i} \phi\>_{W \otimes R} + \frac{1}{2} \int_{\RR^6} \d^6 x \;\<\psi_-, \sd \dd \psi_-\>_R .
-\]
-
-The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
-\begin{align*}
-I^{(1)} (Q) & = \int \<\phi^*, (Q, \psi_-)\>_{W \otimes R} + \int \<\psi^*_-, \rho(\d \phi) Q\>_R \\
-I^{(2)} (Q_1 \otimes Q_2) & = \int \<\psi^*_- , \rho(\Gamma(Q_1, Q_2)) \psi_-\>_R 
-\end{align*}
-where we recall that the pairing is of the form $\Gamma : \Sigma^{\otimes 2} = (S_+ \otimes W)^{\otimes 2} \to V$. \brian{I'm also using $(S_+)^* = S_-$.}
-These functionals provide an off-shell action of $\cN = (1,0)$ supersymmetry on the free hypermultiplet, as the following proposition shows.
-Below, $\fL_{\rm matter}$ is the abelian local Lie algebra describing the free hypermultiplet, and $\mf A$ is the $(0,1)$ supertranslation algebra.  
-As always, $I_{\rm Poin}$ is the action functional encoding ordinary Poincar\'{e} invariance.
-
-\begin{prop}[\cite{SWchar}]
-The functional
-\[
-\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm matter}) [-1]
-\]
-satisfies the Maurer-Cartan equation
-\[
-\left(\d_{\rm Lie} \fS_{\rm matter} + \frac{1}{2} \{\fS_{\rm matter}, \fS_{\rm matter}\} \right) = 0 .
-\]
-\end{prop}
-\begin{proof}
-\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
-\end{proof}
-
-Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
-The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
-\[
-\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
-\]
-where $W$ is a (complex) $2$-dimensional symplectic vector space. 
-The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
-The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
-\begin{align*}
-I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
-I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
-\end{align*}
-These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, which we proved above in Theorem \label{SUSY_YM_theorem}, and state below as a proposition. 
-Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.
-
- implies the following proposition for $6d$
-\begin{prop}[special case of Theorem \ref{SUSY_YM_theorem}]
-The functional
-\[
-\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
-\]
-satisfies the Maurer-Cartan equation
-\[
-\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
-\]
-\end{prop}
-
 \subsection{Dimension 5}
@@
 % \cN=1 SYM with matter in a complex representation
-
-\subsubsection{$\cN=1$ SYM with matter}
-
-The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
-In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
-
-The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
-The field content for the BRST fields in the gauge sector is:
-\[
-(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
-\]
-
-For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
-\[
-(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
-\]
-
-Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.
-
-The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
-\[
-S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
-\]
-Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.
-
-There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
-\begin{align*}
-S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
-& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
-\end{align*}
-\brian{add terms involving antifields}
-\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
-This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter.
-My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
-}
-
-The action
-\[
-S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's})
-\]
-is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
-
-The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
-
-The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
-\begin{align*}
-I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
-I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
-\end{align*}
-where $Q_\pm \in S_{\pm}$. 
-As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
-\[
-I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
-\]
-
-The action of supersymmetry on the gauge sector is encoded by the functionals:
-\begin{align*}
-I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
-I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
-\end{align*}
-\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
-If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
-The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
-Such terms would turn this acyclic.
-Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
-}
-
-These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.
-
-%The result appears in \cite{SWchar}, and we do not repeat the proof here.
-
-\begin{prop}[\cite{SWchar}]
-Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
-Then, the functional
-\[
-\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
-\]
-satisfies the Maurer-Cartan equation
-\[
-\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
-\]
-\end{prop}
-
-Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.
-
-\begin{proof}
-Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
-Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
-
-First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
-We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
-From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
-\[
-\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
-\]
-So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
-
-The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
-The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
-The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
-\begin{align*}
-\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
-& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
-\end{align*}
-The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
-\begin{align*}
-\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
-\end{align*}
-\brian{Get the signs right and these terms should cancel.}
-
-The computation of the remaining terms in the matter sector are summarized in the following lemma. 
-\begin{lem}
-\[
-\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
-\]
-\end{lem}
-\brian{extra terms in $I^{(2)}$?}
-\begin{proof}
-
-First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
-\[
-\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
-\]
-We first focus on terms involving variations of $\phi, \Bar{\phi}$:
-\begin{align*} 
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
-\end{align*}
-In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
-The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.
-
-Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
-The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
-Thus, this calculation implies
-\[
-\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
-\]
-for all $Q_\pm, Q_\pm'$.
-
-Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$.
-We must show
-\[
-\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
-\]
-for all $Q_\pm, Q_\pm'$.
-
-We start by computing the variation of $\psi_+ + \psi_-$:
-\begin{align*}
-[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
-\end{align*}
-\end{proof}
-
-Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
-\end{proof}
 

### 2019-11-11 4dsusy.tex

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{4d $\cN=1$}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\subsection{Theories of matter}
To define the chiral multiplet we fix a complex vector space $R$, and denote the natural pairing between $R$ and $R^*$ by $\<-,-\>_R$. 
The spinorial pairing $\<-,-\> : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $\<-,-\>_R$.

The field content for the 4-dimensional chiral multiplet with values in a complex vector space $R$ is:
\begin{itemize}
\item a pair of scalars $\phi \in C^\infty(\RR^4 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^4 ; R^*)$.
\item a left Weyl spinor $\psi_+ \in C^\infty(\RR^4 ; R \otimes S_+)$ and a right Weyl spinor $\psi_- \in C^\infty(\RR^4 ; R^* \otimes S_-)$.
\end{itemize}

The space of BRST fields is 
\[
F = C^\infty(\RR^4 ; R \oplus R^* \oplus R \otimes S_+ \oplus R^* \otimes S_-) .
\]

The BRST action is
\[
S (\phi, \Bar{\phi}, \psi_\pm) = \int_{\RR^4} \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

\subsection{Matter multiplets}

In some dimensions $n \leq 6$ there exists {\em matter} representations of supersymmetry.

\begin{itemize}
\item Dimension $n=4$, the chiral multiplet.
\item Dimension $n=6$, hyper multiplet. 
\end{itemize}

\subsubsection{The chiral multiplet}

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^* + \Bar{\phi}^*, (Q, \psi_+ + \psi_-)\>_R + \<\psi_+^* + \psi_-^*, \rho(\d \phi + \d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^* + \psi_-^*, \psi_+^*+\psi_-^*)) - \frac{1}{2}(Q_1, \psi_+^* + \psi_-^*)(Q_2, \psi_+^*+\psi_-^*)
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

\begin{thm}
The functional $\fS = S + I_{\rm Poin}^{(1)} + I^{(1)} + I^{(2)}$ with $I_{\rm Poin}$ as in Section \ref{??} satisfies the classical master equation
\[
\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
\]
\end{thm}

\section{scrap}

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
The field content for the BRST fields in the gauge sector is:
\[
(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
\]

For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
\[
(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
\]

Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.

The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi
\end{align*}
\brian{add terms involving antifields}
\brian{There is a term of the form $\pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R$ that is usually written down.
This indeed changes the EOM, and is needed to compensate an extra term in the definition of $I_{\rm gauge}^{(1)}$ when we couple to matter. My claim is that if we disregard both of these terms we will get a consistent supersymmetric system still.
}

The action
\[
S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) 
\]
is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
\end{align*}
where $Q_\pm \in S_{\pm}$. 
As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
\[
I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
\]

The action of supersymmetry on the gauge sector is encoded by the functionals:
\begin{align*}
I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
\end{align*}
\brian{C and P claim there should be some extra terms in $I^{(2)}_{\rm gauge}$ coming from reduction. 
If a few of those terms are of the form $\<\lambda_-^*, \lambda_-^*\>\<Q_-,Q_-\>$ and $\<\lambda_+^*, \lambda_+^*\>\<Q_+,Q_+\>$ we'd be in business. 
The issue is that in the twist calculation below has an extra copy of a complex involving components of $\lambda_-^*$ in degree zero and $\lambda_-$ in degree $+1$.
Such terms would turn this acyclic.
Can we see why such terms are {\em necessary} to preserve off-shell SUSY?
}

These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.

%The result appears in \cite{SWchar}, and we do not repeat the proof here.

\begin{prop}[\cite{SWchar}]
Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
Then, the functional
\[
\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
\]
\end{prop}

Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.

\begin{proof}
Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.

First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
\[
\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
\]
So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.

The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
\end{align*}
The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
\begin{align*}
\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+)) 
\end{align*}
\brian{Get the signs right and these terms should cancel.}

The computation of the remaining terms in the matter sector are summarized in the following lemma. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
\]
\end{lem}
\brian{extra terms in $I^{(2)}$?}
\begin{proof}

First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
\[
\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
\]
We first focus on terms involving variations of $\phi, \Bar{\phi}$:
\begin{align*} 
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
\end{align*}
In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.

Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
Thus, this calculation implies
\[
\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
\]
for all $Q_\pm, Q_\pm'$.

Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$. 
We must show
\[
\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
\]
for all $Q_\pm, Q_\pm'$.

We start by computing the variation of $\psi_+ + \psi_-$:
\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}

\end{document}

### 2019-11-12 4dsusy.tex

@@
 \subsection{Theories of matter}
-To define the chiral multiplet we fix a complex vector space $R$, and denote the natural pairing between $R$ and $R^*$ by $\<-,-\>_R$. 
-The spinorial pairing $\<-,-\> : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $\<-,-\>_R$.
+In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(4; \CC)$. 
+To define the chiral multiplet we fix a complex vector space $R$.
+The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.
 
@@
 \item a pair of scalars $\phi \in C^\infty(\RR^4 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^4 ; R^*)$.
-\item a left Weyl spinor $\psi_+ \in C^\infty(\RR^4 ; R \otimes S_+)$ and a right Weyl spinor $\psi_- \in C^\infty(\RR^4 ; R^* \otimes S_-)$.
+\item a positive Weyl spinor $\psi_+ \in C^\infty(\RR^4 ; R \otimes S_+)$ and a negative Weyl spinor $\psi_- \in C^\infty(\RR^4 ; R^* \otimes S_-)$.
 \end{itemize}
@@
 \[
-S (\phi, \Bar{\phi}, \psi_\pm) = \int_{\RR^4} \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
+S (\phi, \Bar{\phi}, \psi_\pm) = - \int_{\RR^4} (\d \phi \wedge * \d \Bar{\phi})_R + \int (\psi_+ , \sd \dd \psi_-)_R .
 \]
@@
 
-In some dimensions $n \leq 6$ there exists {\em matter} representations of supersymmetry.
+In some dimensions $n \leq 6$ there exists the following {\em matter} representations of supersymmetry.
 
 \begin{itemize}
-\item Dimension $n=4$, the chiral multiplet.
-\item Dimension $n=6$, hyper multiplet. 
+\item Dimension $n=4$, with $\Sigma = S_+ \otimes R \oplus S_- \otimes R^*$, with $R$ a complex vector space.
+This is called the $\cN=1$ chiral multiplet.
+\item Dimension $n=6$, with $\Sigma = S_+ \oplus W_+$ (or $\Sigma = S_- \otimes W_-$), with $W_+$ (or $W_-$) a complex, symplectic representation.
+This is called the $\cN=(1,0)$ (or $\cN=(0,1)$) hyper multiplet.
 \end{itemize}
@@
 
+In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(4; \CC)$.
+
 The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
 \begin{align*}
-I^{(1)}(Q) & = \int \<\phi^* + \Bar{\phi}^*, (Q, \psi_+ + \psi_-)\>_R + \<\psi_+^* + \psi_-^*, \rho(\d \phi + \d \Bar{\phi})Q \>_R \\
-I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^* + \psi_-^*, \psi_+^*+\psi_-^*)) - \frac{1}{2}(Q_1, \psi_+^* + \psi_-^*)(Q_2, \psi_+^*+\psi_-^*)
+I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
+I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - \int (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
 \end{align*}
@@
 \begin{thm}
-The functional $\fS = S + I_{\rm Poin}^{(1)} + I^{(1)} + I^{(2)}$ with $I_{\rm Poin}$ as in Section \ref{??} satisfies the classical master equation
+The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
+\begin{equation}\label{CMEchiral}
+\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
+\end{thm}
+
+Before proving the theorem, we decompose the classical master equation (\ref{CMEchiral}) into the following equations:
+\begin{equation}\label{CMEchiral2}
+\begin{array}{rrrrrr}
+\{S , I^{(1)}\} & = & 0 \\ 
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
+\{I^{(2)}, I^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi, \Bar{\phi}$, and $\psi_{\pm}$.
+
+The first equation in (\ref{CMEchiral2}) states that the classical action for the chiral multiplet is supersymmetric.
+
+\begin{lemma} 
+One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
+\end{lemma}
+\begin{proof}
+The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
+\begin{align*}
+- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) \\
+& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
+\end{align*}
+The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
+\begin{align*}
+\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
+\end{align*}
+Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$, as desired. 
+\end{proof}
+
+Next, we move on to the second equation in (\ref{CMEchiral2}).
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEchiral3}
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating the equation (\ref{CMEchiral3}) on $v_1,v_2 \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in S_+ \oplus S_-$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in S_+ \oplus S_-$.
+
+The individual terms are:
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ & - \Bar{\phi}^* (Q_1, \rho(\d \Bar{\phi}) Q_2) - \Bar{\phi}^* (Q_2, \rho(\d \Bar{\phi})Q_1) \\ &  -  (\psi_+^*, \rho(\d(Q_1,\psi_+))Q_2) - (\psi_+^*, \rho(\d(Q_2, \psi_+)) Q_1) \\ & - (\psi_-^*, \rho(\d(Q_1, \psi_-)) Q_2) - (\psi_-^*, \rho(\d(Q_2, \psi_-))Q_1)
+\end{align*}
+
+\begin{align*}
+(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - \Bar{\phi}^* L_{\Gamma(Q_1,Q_2)} \Bar{\phi} \\ &  - (\psi_+^* , \Gamma(Q_1,Q_2) . \psi_+) - (\psi_-^*, \Gamma(Q_1,Q_2) . \psi_-)
+\end{align*}
+
+and
+\begin{align*}
+\{S, I^{(2)}(Q_1,Q_2)\} = & 
+\end{align*}
+
+We first collect all terms in Equation (\ref{CMEchiral3}) proportional to $\phi^*$:
 \[
-\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
 \]
-\end{thm}
+By Proposition \ref{??}
+\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term. 
+Similarly, all terms proportional to $\Bar{\phi}^*$ also vanish.
+
+Next, we collect all terms in Equation (\ref{CMEchiral3}) proportional to $\psi_+^*$:
+\begin{align*}
+& - \frac{1}{2} \rho(\d(Q_1,\psi_+))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi_+)) Q_1 - \Gamma(Q_1,Q_2) . \psi_+
+\\ 
+& \pm \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+ \mp \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 \mp \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2
+\end{align*}
+
+\end{proof}
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in S_+ \oplus S_-$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = 
+\end{align*}
+
+$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
+By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+The Clifford relation implies that
+%\begin{align*}
+%\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
+%&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
+%\end{align*}
+%Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
+\end{proof}
 

### 2019-11-12 4dsusy.tex
merge

@@
 \[
-S (\phi, \Bar{\phi}, \psi_\pm) = - \int_{\RR^4} (\d \phi \wedge * \d \Bar{\phi})_R + \int (\psi_+ , \sd \dd \psi_-)_R .
+S (\phi, \Bar{\phi}, \psi_\pm) = \int_{\RR^4}  - (\d \phi \wedge * \d \Bar{\phi})_R + (\psi_+ , \sd \dd \psi_-)_R .
 \]
@@
 
+\begin{lem}
+\label{lem: oneform}
+Let $\alpha$ be any $1$-form on $V$, $\psi \in C^\infty(V, \Sigma)$,  and $Q \in \Sigma$. 
+Then
+\[
+\d (Q, \psi) \wedge * \alpha = * (\rho(\alpha)Q, \sd \dd \psi) .
+\]
+\end{lem}
+\begin{proof}
+Let $V_\alpha$ denote the vector field corresponding to $\alpha$. 
+Note that $\d(Q,\psi) \wedge * \alpha = * (Q, V_\alpha . \psi)$. 
+The result then follows from invariance of $(-,-)$ and the formula $\sd \dd \psi = \rho(\d x_i) (\partial_i \psi)$. 
+\end{proof}
+
 \subsubsection{The chiral multiplet}
@@
 I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
-I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - \int (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
+I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
 \end{align*}
@@
 \begin{align*}
-- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) \\
-& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
+- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) 
+%\\
+%& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
 \end{align*}
@@
 \end{align*}
-Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$, as desired. 
+Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$ by Lemma \ref{lem: oneform} as desired. 
 \end{proof}

### 2019-11-12 paper.tex
edited on dim red explanation

@@
 
-\subsection{Dimensional Reduction, take 2}
+\subsection{Dimensional Reduction} \label{dim_red_section}
 
@@
 an isomorphism $p^*\Dens_N\cong \Dens_M$.
-
-\begin{definition}
-A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
+We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
+
+\begin{definition}
+We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a {\bf dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
-Thus, dimensional reductions of a given classical field theory on $M$ form a groupoid.
+Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
+In fact, when dimensional reduction makes sense, this groupoid is always contractible.
 
@@
 \end{prop}
+
+Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to canonical isomorphism.
+
 \begin{proof} \textbf{Uniqueness}.
@@
 
-By the previous Proposition we may simply talk about \emph{the} dimensional reduction of a given classical field theory when the fibers of $p$ are contractible.
 We will now describe dimensional reductions of the classical Chern--Simons theory.
 
-\begin{prop}
+\begin{prop} \label{CS_diml_red_prop}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
@@
 \end{prop}
+
 \begin{proof}
@@
 
-\subsection{Dimensional Reduction} \label{dim_red_section}
-The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.
-
-\begin{definition}
-Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection.
-Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.
-The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.
-The symplectic pairing is defined as the composite
-\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
-with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.
-The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
-\[\phi \mapsto i^*(Q(p^*(\phi))).\]
-Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}: there is a canonical map defined on an open set $U \sub \RR^m$ by
-\[\sym^k \mc E^\vee(U\times (\RR^m)^\perp) \to \sym^k p^*i^*\mc E^\vee(U\times (\RR^m)^\perp) \iso \sym^k i^*\mc E(U).\]
-\end{definition}
-
-Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.
-
-\begin{prop} \label{dim_red_SUSY_prop}
-The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
-\end{prop}
-
-\begin{proof}
- \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
-There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\]
- given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
-We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
-
- Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
-There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
-Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.
-We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
-We can then use the same argument as above.
-\end{proof}
-
-\chris{we could alternatively write this in terms of BRST fields.}
-
-\chris{By the way, I see no obstruction to proving the following.
-One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.
-This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
-\begin{lemma} \label{commuting_twist_and_reduction_lemma}
-If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
-\end{lemma}
-
-We'll conclude this section by discussing some examples of dimensional reduction in the context of generalized BF and Chern-Simons theories.
-First we'll describe what happens when we dimensionally reduce generalized Chern-Simons theory along $\RR$ in a holomorphic direction.
-
-\begin{lemma} \label{CS_diml_red_lemma}
-Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
+%\begin{lemma} \label{CS_diml_red_lemma}
+%Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
 Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.
 The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
-\end{lemma}
-
-\chris{I haven't made the notation here match the notation in Section \ref{gen_CS_section} yet.}
-
-\begin{proof}
-\chris{sketchy}
-Let us denote the complex of BV fields in our generalized Chern-Simons theory on $X \times C$ by $(E_X \boxtimes \bigwedge^\bullet (T^{0,1}_C)^\vee) \otimes \gg[1]$, with differential on the sheaf of sections given by $Q_X + \ol \dd_C + \ell_1$ and pairing on the sheaf of sections by $\omega_X \boxtimes \omega_C$.
-Write $p$ for the projection $C \to L$.
-It's enough to observe that there is a canonical graded isomorphism $p^*\Omega^\bullet(L) \iso \Omega^{0,\bullet}(C)$ intertwining on the one hand the de Rham and Dolbeault differentials, and on the other hand the two integration maps against the orientation on $L$ and the Calabi-Yau structure on $C$.
-\end{proof}
-
-What about if we, instead, reduce generalized Chern-Simons theory in a de Rham direction?
-
-\begin{lemma} \label{CS_to_BF_diml_red_lemma}
-Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
+%\end{lemma}
+
+%\begin{lemma} \label{CS_to_BF_diml_red_lemma}
+%Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
 The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
-\end{lemma}
-
-\begin{proof}
-\chris{...}
-\end{proof}
+%\end{lemma}
 
@@
 
-\subsection{Compactification of supersymmetric theories}
+\subsection{Dimensional Reduction of Supersymmetric Theories}
 
@@
 
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$. We have a natural embedding
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
+This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
+We have a natural embedding
 \[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
 We have the following generalization of this statement to supersymmetric theories.
@@
 \begin{prop}
-Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible $\mf A'$-supersymmetric structure.
 \end{prop}

### 2019-11-13 paper.tex
minor edits to dimensional reduction

@@
 
-\begin{definition}
+\begin{definition} \label{def:twisting}
 Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
@@
 
-\begin{prop}
+\begin{prop} \label{prop:susydimlred}
 Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible $\mf A'$-supersymmetric structure.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
 \end{prop}
+
+\begin{proof}
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+\end{proof}
+
+The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
 
@@
 
-%%\begin{landscape}
-%\begin{figure}
-%\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-%\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-%\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-%\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-%\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-%\node (825) [right=of 82] {};
-%\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-%\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-%\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-%\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-%\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-%\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-%\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-%\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-%\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-%\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-%\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-%\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-%\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-%\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-%\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-%\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-%\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-%\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-%\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-%\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-%\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-%\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-%
-%\draw[arrow] (101) -- (91);
-%\draw[arrow] (91) -- (81);
-%\draw[arrow] (91) -- (82);
-%\draw[arrow] (81) -- (71);
-%\draw[arrow] (82) -- (71);
-%\draw[arrow] (82) -- (72);
-%\draw[arrow] (83) -- (73);
-%\draw[arrow] (71) -- (61);
-%\draw[arrow] (71) -- (62);
-%\draw[arrow] (72) -- (62);
-%\draw[arrow] (72) -- (63);
-%\draw[arrow] (73) -- (65);
-%\draw[arrow] (61) -- (51);
-%\draw[arrow] (62) -- (51);
-%\draw[arrow] (62) -- (52);
-%\draw[arrow] (63) -- (53);
-%\draw[arrow] (64) -- (52);
-%\draw[arrow] (64) -- (54);
-%\draw[arrow] (65) -- (54);
-%\draw[arrow] (51) -- (41);
-%\draw[arrow] (51) -- (42);
-%\draw[arrow] (52) -- (42);
-%\draw[arrow] (52) -- (43);
-%\draw[arrow] (53) -- (43);
-%\draw[arrow] (54) -- (43);
-%\draw[arrow] (54) -- (44);
-%\draw[arrow] (54) -- (45);
-%\draw[arrow] (41) -- (31);
-%\draw[arrow] (42) -- (31);
-%\draw[arrow] (42) -- (32);
-%\draw[arrow] (43) -- (32);
-%\draw[arrow] (44) -- (32);
-%\draw[arrow] (45) -- (32);
-%\draw[arrow] (31) -- (21);
-%\draw[arrow] (31) -- (22);
-%\draw[arrow] (32) -- (22);
-%
-%\node (2d) [dimension, left=of 21] {2d};
-%\node (3d) [dimension, above=of 2d] {3d};
-%\node (4d) [dimension, above=of 3d] {4d};
-%\node (5d) [dimension, above=of 4d] {5d};
-%\node (6d) [dimension, above=of 5d] {6d};
-%\node (7d) [dimension, above=of 6d] {7d};
-%\node (8d) [dimension, above=of 7d] {8d};
-%\node (9d) [dimension, above=of 8d] {9d};
-%\node (10d) [dimension, above=of 9d] {10d};
-%\end{tikzpicture}
-%\caption{Orbits of square-zero supercharges.}
-%\label{fig:superchargeorbits}
-%\end{figure}
-%%\end{landscape}
+%\begin{landscape}
+\begin{figure}
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
+%\end{landscape}
 

### 2019-11-14 paper.tex
merge

--- 2019-11-11 paper.tex
@@
 \label{group_action_def}
-Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An {\bf action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
-\begin{itemize}
-\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
-
-\item An action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$.
-\end{itemize}
-These are required to satisfy the following conditions:
-\begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vctor field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
-\end{itemize}
+Let $(E, Q, \omega, I)$ be a classical field theory.
+An {\bf action} of a supergroup $G$ on $(E, Q, \omega, I)$ is an action of $G$ on $\cE$ preserving the symplectic pairing $\omega$, differential $Q$ and $I$ together with an action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$ such that for every $x\in\fg$ the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{definition}
@@
 
-\subsection{Examples of Classical Field Theories}
+\subsection{Examples of BV-BRST Theories}
 
@@
 \end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\label{def:generalizedBF}
-\end{definition}
-
-\begin{remark}
-We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
-\end{remark}
+\end{definition}
 
@@
 
-\begin{rmk}
-This is a special case of generalized BF theory:
-the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
-\end{rmk}
+The generalized $\beta\gamma$ system is a special case of generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
+
+\brian{Should we say something about how the holomorphic theories couple here?}
+
+\brian{Symplectic, non-polarized version.}
 
@@
 \end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
-\label{def:generalizedCS}
+\label{def:generalizedBF}
 \end{definition}
@@
 
-\subsubsection{The free scalar and free fermion}
-
-\brian{does this warrant it's own definition?}
-
 \subsection{Dimensional Reduction, take 2}
 
-In this section we formulate the procedure of dimensional reduction of a classical field theory.
-Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
-an isomorphism $p^*\Dens_N\cong \Dens_M$.
-
-\begin{definition}
-A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+\begin{definition}
+A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if we are given the following data:
+\begin{itemize}
+\item A submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.
+
+\item An isomorphism $p^* E_N\cong E_M$.
+\end{itemize}
+These data are required to satisfy the following conditions:
 \begin{itemize}
@@
 
-We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
-Thus, dimensional reductions of a given classical field theory on $M$ form a groupoid.
-
-\begin{prop}
-Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
-Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
-
-Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
-If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
-\label{prop:dimensionalreductionunique}
-\end{prop}
-\begin{proof} \textbf{Uniqueness}.
-We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
-Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
-In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
-
-Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
-
-\textbf{Existence}.
-Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
-Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
-Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
-The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
-\end{proof}
-
-By the previous Proposition we may simply talk about \emph{the} dimensional reduction of a given classical field theory when the fibers of $p$ are contractible.
-We will now describe dimensional reductions of the classical Chern--Simons theory.
-
-\begin{prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
-\end{prop}
-\begin{proof}
-To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
-\[\map(\pt, T^*[-1] B \fg)\]
-has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
-
-We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
-Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
-Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
-\end{proof}
-
-\begin{prop}
-Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
-\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-\end{prop}
-\begin{proof}
-We may assume $X,Y,M=\pt$ as in the previous proof.
-
-We have
-\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
-and
-\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
-Under the pullback map
-\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
-the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\end{proof}
+\chris{A question: are dimensional reductions, per this definition, unique?
+I'd really like the answer to be yes (at least for dimensional reduction along a vector space), so that I can say the twist of a dimensional reduction is equivalent to \emph{the} (unique) dimensional reduction of the twist -- assuming the dimensional reductions before and after twisting exist (which, again, I'd like them to, at least for dimensional reduction along a vector space).}
 
@@
 The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
-\brian{Where is the Poincare part?}
 \begin{align*}
@@
 \label{thm:vectormultipletSUSY}
-\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
-\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
 \end{thm}
@@
 
-\pavel{$Q$ denotes both the differential on fields and the supercharge.}
-
 \begin{definition}
@@
 \end{remark}
-
-\subsection{Compactification of supersymmetric theories}
-
-Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
-
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$. We have a natural embedding
-\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
-so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
-\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
-where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
-\[G_W = G_V\times \Spin(W^\perp_\RR).\]
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
-We have the following generalization of this statement to supersymmetric theories.
-
-\begin{prop}
-Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
-\end{prop}
-
-\begin{prop}
-Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
-Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
-\end{prop}
 
@@
 \subsection{Dimension 7}
-The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
-It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
-
-In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
- \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
- \item Rank 2 square-zero spinors, i.e.
-square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
-Such supercharges have a 5-dimensional image in $\CC^7$.
-Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
-
-\begin{theorem} \label{7d_holo_twist_thm}
-The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
+
+% \cN=1 SYM, three twists identical to dimension 8
+
+\subsection{Dimension 6}
+
+% \cN=(1, 1) SYM, three twists identical to dimension 8
+
+% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.
+
+\subsubsection{$\cN=(1,0)$ with matter}
+
+A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
+Let $S_-^{6d}$ be the negative $\so(6)$ irreducible spin representation and suppose $R$ is a (complex) symplectic $\fg$-representation, with symplectic pairing labeled by $\<-,-\>_R$. 
+The BRST fields of the $(1,0)$ hypermultiplet consist of a $W \otimes R$-valued scalar
+\[
+\phi \in \Omega^0(\RR^6) \otimes W \otimes R
+\]
+and an $R$ valued negative Weyl spinor
+\[
+\psi_- \in \Omega^0(\RR^6) \otimes S_-^{6d} \otimes R .
+\]
+Denote the induced symplectic pairing on $W \otimes R$ by $\<-,-\>_{W \otimes R}$. 
+The action of the free hypermultiplet is given by
+\[
+S_{\rm matter} (\phi, \psi_-) = \frac{1}{2} \int_{\RR^6} \d^6 x \; \<\partial_{x_i} \phi , \partial_{x_i} \phi\>_{W \otimes R} + \frac{1}{2} \int_{\RR^6} \d^6 x \;\<\psi_-, \sd \dd \psi_-\>_R .
+\]
+
+The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int \<\phi^*, (Q, \psi_-)\>_{W \otimes R} + \int \<\psi^*_-, \rho(\d \phi) Q\>_R \\
+I^{(2)} (Q_1 \otimes Q_2) & = \int \<\psi^*_- , \rho(\Gamma(Q_1, Q_2)) \psi_-\>_R 
+\end{align*}
+where we recall that the pairing is of the form $\Gamma : \Sigma^{\otimes 2} = (S_+ \otimes W)^{\otimes 2} \to V$. \brian{I'm also using $(S_+)^* = S_-$.}
+These functionals provide an off-shell action of $\cN = (1,0)$ supersymmetry on the free hypermultiplet, as the following proposition shows.
+Below, $\fL_{\rm matter}$ is the abelian local Lie algebra describing the free hypermultiplet, and $\mf A$ is the $(0,1)$ supertranslation algebra.  
+As always, $I_{\rm Poin}$ is the action functional encoding ordinary Poincar\'{e} invariance.
+
+\begin{prop}[\cite{SWchar}]
+The functional
+\[
+\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm matter}) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS_{\rm matter} + \frac{1}{2} \{\fS_{\rm matter}, \fS_{\rm matter}\} \right) = 0 .
+\]
+\end{prop}
 \begin{proof}
-
+\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
 \end{proof}
 
-\begin{theorem} \label{7d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
-\chris{actually I need to think about the twisting homomorphism here.}
-\end{theorem}
-
-\begin{proof}
-
-\end{proof}
-
-\subsection{Dimension 6}
-
-% \cN=(1, 1) SYM, three twists identical to dimension 8
-
-% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.
-
-\subsubsection{$\cN=(1,0)$ with matter}
+Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
+The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
+\[
+\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
+\]
+where $W$ is a (complex) $2$-dimensional symplectic vector space. 
+The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
+The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
+I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
+\end{align*}
+These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, which we proved above in Theorem \label{SUSY_YM_theorem}, and state below as a proposition. 
+Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.
+
+ implies the following proposition for $6d$
+\begin{prop}[special case of Theorem \ref{SUSY_YM_theorem}]
+The functional
+\[
+\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
+\]
+\end{prop}
 
@@
 % \cN=1 SYM with matter in a complex representation
+
+\subsubsection{$\cN=1$ SYM with matter}
+
+The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
+In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).
+
+The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$.
+The field content for the BRST fields in the gauge sector is:
+\[
+(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
+\]
+
+For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
+\[
+(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
+\]
+
+Th full BV action for $\cN=1$ supersymmetric pure Yang-Mills theory on $\RR^4$ was defined in Section \ref{YM_section}, which we call $S_{\rm BV, gauge}$ in this section.
+
+The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
+\[
+S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
+\]
+Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.
+
+There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
+\begin{align*}
+S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
+& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
+&\brian{where does this term come from \pm g^2 \int \<(\phi \Bar{\phi}), * (\phi \Bar{\phi})\>_R}
+\end{align*}
+\brian{add terms involving antifields}
+
+The action
+\[
+S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's})
+\]
+is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.
+
+The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.
+
+The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
+\begin{align*}
+I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
+I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
+\end{align*}
+where $Q_\pm \in S_{\pm}$. 
+As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
+\[
+I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
+\]
+
+The action of supersymmetry on the gauge sector is encoded by the functionals:
+\begin{align*}
+I^{(1)}_{\rm gauge} (Q_+ + Q_-) & = \int \<A^* , \Gamma(Q_+ + Q_-, \lambda_+ + \lambda_-)\> + \<\lambda_+^*+\lambda_-^*, \sd F_A (Q_+ + Q_-)\> \\
+I^{(2)}_{\rm gauge} (Q_+ \otimes Q_-) & = \int \left\<\lambda^*, \rho(\Gamma(Q_+, Q_-)) \lambda^* + \frac{1}{2} ((Q_+, \lambda_+^*+\lambda_-^*) Q_- + (Q_-, \lambda^*_+ + \lambda_-^*)Q_+)\right\> .
+\end{align*}
+
+These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we summarize in the following proposition.
+
+%The result appears in \cite{SWchar}, and we do not repeat the proof here.
+
+\begin{prop}[\cite{SWchar}]
+Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
+Then, the functional
+\[
+\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
+\]
+satisfies the Maurer-Cartan equation
+\[
+\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
+\]
+\end{prop}
+
+Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.
+
+\begin{proof}
+Throughout this proof we drop the pairing $\<-,-\>_R$ from the notation.
+Also, we continue to denote the spinorial pairing by $\<-,-\>$ and the standard inner product by $(-,-)$.
+
+First, consider the pure matter sector $\fS_{\rm matter} = S_{\rm matter} + I_{\rm Poin} + I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}$. 
+We will show that $\fS_{\rm matter}$ satisfies the classical master equation. 
+From the form of $S_{\rm matter}$ and by Poincar\'{e} invariance of the matter action, it is clear that
+\[
+\d_{\rm Lie} S_{\rm matter} + \d_{\rm Lie} (I^{(1)}_{\rm matter} + I^{(2)}_{\rm matter}) + \frac{1}{2} \{S_{\rm matter} + I_{\rm Poin}, S_{\rm matter} + I_{\rm Poin}\} = 0 .
+\]
+So, we only need to consider the terms involving $\{S_{\rm matter}, I_{\rm matter}^{(1)}\}$, $\{S_{\rm matter}, I^{(2)}_{\rm matter}\}$, $\d_{\rm Lie} I_{\rm Poin}$, and $\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}$.
+
+The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
+The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
+The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
+\begin{align*}
+\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
+& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
+\end{align*}
+The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
+\begin{align*}
+\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+))
+\end{align*}
+\brian{Get the signs right and these terms should cancel.}
+
+The computation of the remaining terms in the matter sector are summarized in the following lemma. 
+\begin{lem}
+\[
+\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
+\]
+\end{lem}
+\begin{proof}
+
+First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
+\[
+\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
+\]
+We first focus on terms involving variations of $\phi, \Bar{\phi}$:
+\begin{align*} 
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
+\end{align*}
+In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
+The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.
+
+Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
+The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
+Thus, this calculation implies
+\[
+\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
+\]
+for all $Q_\pm, Q_\pm'$.
+
+Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$.
+We must show
+\[
+\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
+\]
+for all $Q_\pm, Q_\pm'$.
+
+We start by computing the variation of $\psi_+ + \psi_-$:
+\begin{align*}
+[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = \brian{Fierz / 3 \psi} \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
+\end{align*}
+\end{proof}
+
+Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
+\end{proof}
 

### 2019-11-14 6dsusy.tex

@@
+\documentclass[10pt, oneside]{article}
+
+\input ./combined_macros.sty
+
+\newcommand{\Cl}{\mathrm{Cl}}
+\newcommand{\Dens}{\mathrm{Dens}}
+
+\addbibresource{Twist.bib}
+
+\usepackage{pdflscape}
+\usetikzlibrary{shapes.geometric, arrows, positioning}
+
+\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
+\tikzstyle{s16chiral} = [s16, dashed]
+\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
+\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
+\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
+\tikzstyle{arrow} = [thick,->,>=stealth]
+
+\title{4d $\cN=1$}
+\author{Chris Elliott\and Pavel Safronov \and Brian Williams}
+
+\date{\today}
+
+\begin{document}
+
+\maketitle
+
+\subsection{The (half) hyper multiplet}
+
+In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(6; \CC)$. 
+The spinorial representation we will be interested in is $\Sigma = S_+ \otimes W_+$, where $\dim_{\CC}(W_+) = 2$ is a two-dimensional multiplicity space. 
+To define the half hyper multiplet we fix a complex, symplectic vector space $U$ whose symplectic form we call $\omega_U$.
+We combine the symplectic forms $\omega_U, \omega_{W_+}$ to define a pairing 
+\[
+(-,-)_{W_+ \otimes U}  := \omega_{W_+} \otimes \omega_U : (W_+ \otimes U)^{\otimes 2} \to \CC .
+\]
+The spinorial pairing $(-,-) : S_+ \otimes S_- \to \CC$ together with the obvious symplectic form $\omega_{W_+}$ on $W_+$, and the symplectic form $\omega_U$ on $U$ induces a pairing (that we denote by the same symbol)
+\[
+(-,-)_U : (S_\pm \otimes U) \otimes (S_\mp \otimes U) \to \CC .
+%(-,-)_U : (S_\pm \otimes W_+ \otimes U)^{\otimes 2} \to \CC  
+\]
+
+\begin{remark}
+The terminology ``half" hyper multiplet is to be consistent with the terminology in the physics literature. 
+The (full) hyper multiplet refers to a multiplet which depends on the choice of a (not necessarily symplectic) vector space $R$. 
+The relationship between the two is obtained by looking at the cotangent space $U = T^*R$.
+That is, the half hyper multiplet with values in the symplectic vector space $U = T^* R$ (with its obvious symplectic structure) is the (full) hyper multiplet for $R$. 
+\end{remark}
+
+The field content for the 6-dimensional half hyper multiplet with values in $U$ is:
+\begin{itemize}
+\item a scalar valued in $W_+ \otimes U$; $\phi \in C^\infty(\RR^4 ; W_+ \otimes U)$;
+\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
+\end{itemize}
+
+The space of BRST fields is thus
+\[
+F = C^\infty(\RR^4 ; W_+ \otimes U \oplus S_- \otimes U) .
+\]
+
+The BRST action is
+\[
+S (\phi, \psi) = \int_{\RR^4} - \frac{1}{2}  (\d \phi \wedge * \d \phi)_{W_+ \otimes U} + \frac{1}{2} (\psi , \sd \dd \psi)_U .
+\]
+As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
+
+The action of supersymmetry is given by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) - \frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  .
+\end{align*}
+where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
+We point out some conventions in the definition of $I^{(2)}$. 
+First, we define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
+\[
+\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
+\]
+Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
+\[
+(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
+\]
+The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
+Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
+
+The following result states that these functionals encode an off-shell action of six-dimensional $\cN=(1,0)$ supersymmetry on the half hypermultiplet valued in $U$. 
+The proof is very similar to the case of the four-dimensional $\cN=1$ chiral multiplet.
+
+\begin{thm}
+The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
+\begin{equation}\label{CMEhyper}
+\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
+\end{thm}
+
+We decompose the classical master equation (\ref{CMEhyper}) into the following equations:
+\begin{equation}\label{CMEhyper2}
+\begin{array}{rrrrrr}
+\{S , I^{(1)}\} & = & 0 \\ 
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
+\{I^{(2)}, I^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
+
+The first equation in (\ref{CMEhyper2}) states that the classical action for the chiral multiplet is supersymmetric.
+
+\begin{lemma} 
+One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+\end{lemma}
+\begin{proof}
+Observe
+\[
+- \{\d \phi \wedge * \d \phi, \phi^*  (Q, \psi) \} = - 2 \d (Q, \psi) \wedge * \d \phi .
+\]
+and
+\[
+\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) \d^4 x .
+\]
+The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
+\end{proof}
+
+Next, we move on to the second equation in (\ref{CMEhyper2}).
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEhyper3}
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating the equation (\ref{CMEhyper3}) on $v_1,v_2 \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
+
+The individual terms are:
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  -  (\psi^*, \rho(\d(Q_1,\psi))Q_2) - (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
+\end{align*}
+
+\begin{align*}
+(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
+\end{align*}
+
+and
+\begin{align*}
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) - \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) .
+\end{align*}
+
+We first collect all terms in Equation (\ref{CMEhyper3}) proportional to $\phi^*$:
+\[
+- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
+\]
+By the Clifford identity
+\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term.
+
+Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
+\begin{align*}
+& - \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
+\\ 
+& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2
+\end{align*}
+By \label{prop:cliffordactionproperties} item (2), the first, second, fifth, and sixth terms combine to give
+\[
+- \frac{1}{2} \left( \sd \dd \rho(\Gamma(Q,\psi)) Q_2 + \sd \dd \rho(\Gamma(Q_2, \psi))Q_1 \right)  .
+\]
+This term is equal to $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2)) \psi$ by \ref{prop:3psi}. 
+The Clifford relation implies this term cancels with the remaining terms.
+
+\end{proof}
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in S_+ \oplus S_-$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(\d
+\end{align*}
+
+$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
+By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+The Clifford relation implies that
+
+\end{proof}
+\newpage
+
+\section{SCRAP}
+
 A general theory of matter for $\cN = (1,0)$ supersymmetry arranges into a hypermultiplet which has the following BRST description.
@@
 \end{prop}
+
+\end{document}

### 2019-11-14 paper.tex

--- 2019-11-12 paper.tex
@@
 
+\brian{Symplectic, non-polarized version.}
+
 \subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
@@
 
-\subsection{Dimensional Reduction} \label{dim_red_section}
+\subsection{Dimensional Reduction, take 2}
 
@@
 an isomorphism $p^*\Dens_N\cong \Dens_M$.
-The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
-We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
-
-\begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a {\bf dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+
+\begin{definition}
+A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
-Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
-In fact, when dimensional reduction makes sense, this groupoid is always contractible.
+Thus, dimensional reductions of a given classical field theory on $M$ form a groupoid.
 
@@
 \end{prop}
-
-Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to canonical isomorphism.
-
 \begin{proof} \textbf{Uniqueness}.
@@
 
+By the previous Proposition we may simply talk about \emph{the} dimensional reduction of a given classical field theory when the fibers of $p$ are contractible.
 We will now describe dimensional reductions of the classical Chern--Simons theory.
 
-\begin{prop} \label{CS_diml_red_prop}
+\begin{prop}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
@@
 \end{prop}
-
 \begin{proof}
@@
 
-%\begin{lemma} \label{CS_diml_red_lemma}
-%Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
+\subsection{Dimensional Reduction} \label{dim_red_section}
+The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.
+
+\begin{definition}
+Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection.
+Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.
+The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.
+The symplectic pairing is defined as the composite
+\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
+with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.
+The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
+\[\phi \mapsto i^*(Q(p^*(\phi))).\]
+Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}: there is a canonical map defined on an open set $U \sub \RR^m$ by
+\[\sym^k \mc E^\vee(U\times (\RR^m)^\perp) \to \sym^k p^*i^*\mc E^\vee(U\times (\RR^m)^\perp) \iso \sym^k i^*\mc E(U).\]
+\end{definition}
+
+Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.
+
+\begin{prop} \label{dim_red_SUSY_prop}
+The dimensional reduction of a supersymmetric classical field theory $\mf L$ on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory $\mf L'$ on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
+\end{prop}
+
+\begin{proof}
+ \chris{Here's a proof sketch/outline/idea.} Start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.
+There is a cochain map \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}}(\mf{iso}(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf{iso}(m)) \otimes C^\bullet_{\mr{loc}}(p^* \mf L')),\]
+ given by the inclusion of $\mf{iso}(m) \inj \mf{iso}(n)$, and the restriction of a functional to act only those fields which are constant on $(\RR^m)^\perp$.
+We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.
+
+ Now include supertranslations, so start with an $\mf A$-invariant action functional $\mf S$ in $n$-dimensions.
+There is a graded linear map $C^\bullet_{\mr{Lie}}(\mf A) \to C^\bullet_{\mr{Lie}}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.
+Let's apply the graded linear map \[F \colon (C^\bullet_{\mr{Lie}}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))\to (C^\bullet_{\mr{Lie}}(\mf A') \otimes C^\bullet_{\mr{loc}}(p^*\mf L'))\] to $\mf S$ anyway.
+We'll find that $\d F(\mf S) - F \d(\mf S)$ vanishes, because the failure of $F$ and $\d$ to commute involves the action of the translations perpendicular to $\RR^m$, which act trivially on the Poincar\'e invariant theory $\mf L'$.
+We can then use the same argument as above.
+\end{proof}
+
+\chris{we could alternatively write this in terms of BRST fields.}
+
+\chris{By the way, I see no obstruction to proving the following.
+One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.
+This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
+\begin{lemma} \label{commuting_twist_and_reduction_lemma}
+If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
+\end{lemma}
+
+We'll conclude this section by discussing some examples of dimensional reduction in the context of generalized BF and Chern-Simons theories.
+First we'll describe what happens when we dimensionally reduce generalized Chern-Simons theory along $\RR$ in a holomorphic direction.
+
+\begin{lemma} \label{CS_diml_red_lemma}
+Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
 Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.
 The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
-%\end{lemma}
-
-%\begin{lemma} \label{CS_to_BF_diml_red_lemma}
-%Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
+\end{lemma}
+
+\chris{I haven't made the notation here match the notation in Section \ref{gen_CS_section} yet.}
+
+\begin{proof}
+\chris{sketchy}
+Let us denote the complex of BV fields in our generalized Chern-Simons theory on $X \times C$ by $(E_X \boxtimes \bigwedge^\bullet (T^{0,1}_C)^\vee) \otimes \gg[1]$, with differential on the sheaf of sections given by $Q_X + \ol \dd_C + \ell_1$ and pairing on the sheaf of sections by $\omega_X \boxtimes \omega_C$.
+Write $p$ for the projection $C \to L$.
+It's enough to observe that there is a canonical graded isomorphism $p^*\Omega^\bullet(L) \iso \Omega^{0,\bullet}(C)$ intertwining on the one hand the de Rham and Dolbeault differentials, and on the other hand the two integration maps against the orientation on $L$ and the Calabi-Yau structure on $C$.
+\end{proof}
+
+What about if we, instead, reduce generalized Chern-Simons theory in a de Rham direction?
+
+\begin{lemma} \label{CS_to_BF_diml_red_lemma}
+Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
 The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
-%\end{lemma}
+\end{lemma}
+
+\begin{proof}
+\chris{...}
+\end{proof}
 
@@
 
-\subsection{Dimensional Reduction of Supersymmetric Theories}
+\subsection{Compactification of supersymmetric theories}
 
@@
 
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
-We have a natural embedding
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$. We have a natural embedding
 \[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
 We have the following generalization of this statement to supersymmetric theories.
@@
 \begin{prop}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible $\mf A'$-supersymmetric structure.
+Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
 \end{prop}

### 2019-11-14 6dsusy.tex
6d

@@
 I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) - \frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  .
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
 \end{align*}
@@
 We point out some conventions in the definition of $I^{(2)}$. 
-First, we define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
+Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
 \[
@@
 \]
-Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
-\[
-(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
-\]
-The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
-Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
+%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
+%\[
+%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
+%\]
+%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
+%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
 
@@
 \begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) - \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) .
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
 \end{align*}
+Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.
 
@@
 \\ 
-& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2
+& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
 \end{align*}
-By \label{prop:cliffordactionproperties} item (2), the first, second, fifth, and sixth terms combine to give
+By Proposition \ref{prop:cliffordactionproperties} item (2), the first, second, and fourth terms combine to give
 \[

### 2019-11-14 6dsusy.tex
6d

@@
 \maketitle
+
+\brian{This holds for $\Sigma = S_+ \otimes W_+$.}
+
+\begin{prop}\label{prop: new3psi}
+Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
+Then
+\[
+(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
+\]
+\end{prop}
 
@@
 Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
-\begin{align*}
-& - \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
+\begin{equation}\label{psistar}
+\begin{array}{cccc}
+& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
 \\ 
-& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
-\end{align*}
-By Proposition \ref{prop:cliffordactionproperties} item (2), the first, second, and fourth terms combine to give
+& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
+\end{array}
+\end{equation}
+By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
 \[
-- \frac{1}{2} \left( \sd \dd \rho(\Gamma(Q,\psi)) Q_2 + \sd \dd \rho(\Gamma(Q_2, \psi))Q_1 \right)  .
+- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
 \]
-This term is equal to $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2)) \psi$ by \ref{prop:3psi}. 
-The Clifford relation implies this term cancels with the remaining terms.
-
+Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
+So the expression (\ref{psistar}) is identically zero. 
 \end{proof}

### 2019-11-15 paper.tex
merge error

@@
 
-\brian{Symplectic, non-polarized version.}
-
 \subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
@@
 
-\subsection{Chiral multiplet}
+\subsection{Supersymmetric matter}
 
 \pavel{6d $\cN=(1, 0)$ and 4d $\cN=1$.}
+
+\subsection{Supersymmetric couplings}
 
@@
 
-\subsubsection{$\cN=(1,0)$ with matter}
+\subsubsection{$\cN=(1,0)$ with hypermultiplet matter}
 
@@
 
+\subsubsection{$\cN=1$ with chiral multiplet matter}
 There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
@@
 
+\begin{prop}[See also \cite{SWchar}]
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
+\end{prop}
+
 \begin{itemize}
@@
 \begin{align*}
-\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R) \\
+\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
 \Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
@@
 
-There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
-\begin{itemize}
-\item The twisted theory is a shifted cotangent theory in the BV formalism. 
-This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively.
-
-\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
-\end{itemize}
-
-The first symmetry we exploit is translation invariance. 
-There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
-Let $\fg$ and $R$ be a Lie algebra together with a representation.
-Define the following graded Lie algebra
 \item[(2)] Next, we study the linear differential in the twisted theory. 
 At the linear level, the matter and gauge sectors completely decouple.
-For the matter sector, the linear differential is:
+
+For the gauge sector, the linear differential on the twisted BV complex is the following:
 \[
@@
 \ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-& \Omega^0(\CC^2; R)_{\gamma_0} \ar[r] & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
-\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
-\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
+\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
+& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
+\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
+& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
 }
 \]
-For the gauge sector, the linear differential is:
+The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
+The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
+This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$.
+
+For the matter sector, the linear differential is:
 \[
@@
 \ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-\Omega^0(\CC^2; \fg)_{A_0} \ar[r] & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar[r] & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
-& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar[r] & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
-\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
-& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
+& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
+\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
+\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
 }
 \]
+This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$.
+
+\item[(3)] 
+We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
 \end{itemize}
@@
 
-\begin{prop}[\cite{SWchar}]
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
-\end{prop}
+\subsubsection{$\cN=2$ SYM with hypermultiplet matter}
+%quaternionic is hyperkahler
+%pseudo-real is quaternionic
+
+\subsubsection{$\cN=4$ SYM}
+
 %

### 2019-11-15 paper.tex

@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
 We have the following generalization of this statement to supersymmetric theories.
 
-\begin{prop}
-Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
+\begin{prop} \label{prop:susydimlred}
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
 \end{prop}
+
+\begin{proof}
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+\end{proof}
+
+The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
 

### 2019-11-15 paper.tex
some susy action calculation in 6d

@@
 We begin by considering $\mr O(8)$ itself.
+
 \begin{prop} \label{O8_decomposition_of_susy_prop}
-
 After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
@@
 \subsection{Dimension 6}
-
-% \cN=(1, 1) SYM, three twists identical to dimension 8
-
-% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.
-
-\subsubsection{$\cN=(1,0)$ with hypermultiplet matter}
+In dimension 6 there are two possible supersymmetry groups by which we can act.
+There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry, consisting of a pure gauge theory coupled to matter living in a symplectic representation $V$.
+If $V \iso T^*\gg$, then the $(1,0)$ supersymmetry can be enhanced to $\mc N=(1,1)$ supersymmetry.
+This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills down to $\RR^6$.
+
+\subsubsection{$\mc N = (1,0)$ with hypermultiplet matter}
+
+\subsubsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
+
+Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills on $\RR^6$ as $c$, the ghost, along with:
+\begin{itemize}
+ \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.
+These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e.
+the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.
+We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
+ \item Fermions: spinor fields $\psi^+ \otimes u^+$ and $\psi^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
+\end{itemize}
+
+\begin{prop} \label{O6_decomposition_of_susy_prop}
+After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\begin{align*}
+I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
+I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
+\end{align*}
+if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
+\begin{align*}
+I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
+I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
+\end{align*}
+if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.
+In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.
+There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
+\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle, u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
+\end{prop}
+
+\begin{remark}
+If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.
+If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
+\end{remark}
 

### 2019-11-15 paper.tex
some initial drafts in 6 and 5d

@@
 We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
- \item Fermions: spinor fields $\psi^+ \otimes u^+$ and $\psi^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
+ \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
 \end{itemize}
@@
 There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
-\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle, u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
+\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
 \end{prop}
@@
 
+In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
+\begin{enumerate}
+ \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic, like in the $\mc N=(1,0)$ supersymmetry algebra.
+ \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
+ \begin{enumerate}
+ \item \chris{4 invariant directions}
+ \item \chris{topological (this twist is a degeneration of the previous type)}
+ \end{enumerate}
+ \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+We already considered the holomorphic twist in the previous subsection.
+The remaining three classes are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
+
+\chris{types 2a and 2b fit into a family of the form $\mr{Map}(S_2 \times \Sigma_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}(\Sigma \times (M_4)_{\mr{dR}}, BG)$.}
+
 \subsection{Dimension 5}
 
-% \cN=2 SYM, three twists
-% \cN=1 SYM with matter in a pseudo-real representation, one twist.
+\subsubsection{$\mc N = 1$ Super Yang-Mills with a Hypermultiplet}
+
+\subsubsection{$\mc N = 2$ Super Yang-Mills Theory}
+
+Exactly as in the case of 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
+\begin{enumerate}
+ \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
+ \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
+ \begin{enumerate}
+ \item \chris{4 invariant directions}
+ \item \chris{topological (this twist is a degeneration of the previous type)}
+ \end{enumerate}
+ \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+\chris{types 2a and 2b fit into a family of the form $\mr{Map}(\Sigma \times (M_3)_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}((M_5)_{\mr{dR}}, BG)$.}
 

### 2019-11-15 paper.tex
6d done in paper

--- 2019-11-15 paper.tex
@@
 
-\pavel{6d $\cN=(1, 0)$ and 4d $\cN=1$.}
+\subsubsection{The 4d $\cN=1$ chiral multiplet}
+
+\subsubsection{The 6d $\cN=(1, 0)$ hypermultiplet}
+
+In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(6; \CC)$. 
+The spinorial representation we will be interested in is $\Sigma = S_+ \otimes W_+$, where $\dim_{\CC}(W_+) = 2$ is a two-dimensional multiplicity space. 
+To define the half hyper multiplet we fix a complex, symplectic vector space $U$ whose symplectic form we call $\omega_U$.
+We combine the symplectic forms $\omega_U, \omega_{W_+}$ to define a pairing 
+\[
+(-,-)_{W_+ \otimes U}  := \omega_{W_+} \otimes \omega_U : (W_+ \otimes U)^{\otimes 2} \to \CC .
+\]
+The spinorial pairing $(-,-) : S_+ \otimes S_- \to \CC$ together with the obvious symplectic form $\omega_{W_+}$ on $W_+$, and the symplectic form $\omega_U$ on $U$ induces a pairing (that we denote by the same symbol)
+\[
+(-,-)_U : (S_\pm \otimes U) \otimes (S_\mp \otimes U) \to \CC .
+%(-,-)_U : (S_\pm \otimes W_+ \otimes U)^{\otimes 2} \to \CC  
+\]
+
+\begin{remark}
+The terminology ``half" hyper multiplet is to be consistent with the terminology in the physics literature. 
+The (full) hyper multiplet refers to a multiplet which depends on the choice of a (not necessarily symplectic) vector space $R$. 
+The relationship between the two is obtained by looking at the cotangent space $U = T^*R$.
+That is, the half hyper multiplet with values in the symplectic vector space $U = T^* R$ (with its obvious symplectic structure) is the (full) hyper multiplet for $R$. 
+\end{remark}
+
+The field content for the 6-dimensional half hyper multiplet with values in $U$ is:
+\begin{itemize}
+\item a scalar valued in $W_+ \otimes U$; $\phi \in C^\infty(\RR^4 ; W_+ \otimes U)$;
+\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
+\end{itemize}
+
+The space of BRST fields is thus
+\[
+F = C^\infty(\RR^4 ; W_+ \otimes U \oplus S_- \otimes U) .
+\]
+
+The BRST action is
+\[
+S (\phi, \psi) = \int_{\RR^4} - \frac{1}{2}  (\d \phi \wedge * \d \phi)_{W_+ \otimes U} + \frac{1}{2} (\psi , \sd \dd \psi)_U .
+\]
+As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
+
+The action of supersymmetry is given by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) 
+%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
+\end{align*}
+where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
+We point out some conventions in the definition of $I^{(2)}$. 
+Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
+\[
+\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
+\]
+
+In order to prove the hypermultiplet is supersymmetric, we will need to following proposition about $6$-dimensional spinor representations.
+
+\begin{prop}\label{prop: new3psi}
+Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
+Then
+\[
+(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
+\]
+\end{prop}
+
+%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
+%\[
+%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
+%\]
+%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
+%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
+
+The following result states that these functionals encode an off-shell action of six-dimensional $\cN=(1,0)$ supersymmetry on the half hypermultiplet valued in $U$. 
+The proof is very similar to the case of the four-dimensional $\cN=1$ chiral multiplet.
+
+\begin{thm}
+The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
+\begin{equation}\label{CMEhyper}
+\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
+\end{thm}
+
+We decompose the classical master equation (\ref{CMEhyper}) into the following equations:
+\begin{equation}\label{CMEhyper2}
+\begin{array}{rrrrrr}
+\{S , I^{(1)}\} & = & 0 \\ 
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
+\{I^{(2)}, I^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
+
+The first equation in (\ref{CMEhyper2}) states that the classical action for the chiral multiplet is supersymmetric.
+
+\begin{lemma} 
+One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+\end{lemma}
+\begin{proof}
+Observe
+\[
+- \{\d \phi \wedge * \d \phi, \phi^*  (Q, \psi) \} = - 2 \d (Q, \psi) \wedge * \d \phi .
+\]
+and
+\[
+\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) \d^4 x .
+\]
+The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
+\end{proof}
+
+Next, we move on to the second equation in (\ref{CMEhyper2}).
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEhyper3}
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating expression (\ref{CMEhyper3}) on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
+
+The individual terms are:
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  -  (\psi^*, \rho(\d(Q_1,\psi))Q_2) - (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
+\end{align*}
+
+\begin{align*}
+(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
+\end{align*}
+
+and
+\begin{align*}
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) 
+% \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
+\end{align*}
+Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.
+
+We first collect all terms in Equation (\ref{CMEhyper3}) proportional to $\phi^*$:
+\[
+- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
+\]
+By the Clifford identity
+\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term.
+
+Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
+\begin{equation}\label{psistar}
+\begin{array}{cccc}
+& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
+\\ 
+& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
+%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
+\end{array}
+\end{equation}
+By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
+\[
+- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
+\]
+Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
+So the expression (\ref{psistar}) is identically zero. 
+\end{proof}
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in \Sigma$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\end{align*}
+The expression
+$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
 
@@
 
-\begin{definition} \label{def:twisting}
+\begin{definition}
 Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that dimensional reduction of theories along the projection $p\colon V_\RR\rightarrow W_\RR$ exist and are unique.
 We have the following generalization of this statement to supersymmetric theories.
 
-\begin{prop} \label{prop:susydimlred}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
+\begin{prop}
+Suppose $(E, Q, \omega, I)$ is a supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along $p\colon V_\RR\rightarrow W_\RR$ has a unique compatible supersymmetric structure.
 \end{prop}
-
-\begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
-\end{proof}
-
-The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
 

### 2019-11-18 coupling.tex
coupling

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{4d $\cN=1$}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\subsection{Supersymmetric coupling}
\subsubsection{The 6d vector multiplet coupled to the hypermultiplet}

Let $S_{\rm gauge}$ and $S_{\rm matter}$ be the BV actions for the $6d$ $\cN=(1,0)$ vector and hyper multiplets, respectively. 
The coupled theory has action $S_{\rm gauge} + S_{\rm matter} + I_{\rm couple}$ where
\[
I_{\rm couple} = g (\psi, [A, \psi])_U + g (\d_{A} \phi, [A,\phi])_U + g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + g (\psi^*, [c, \psi])_U + g (\phi^*, [c, \phi])_U + g^2 \left((\phi, \phi)_U\right)^2 .
\]
\brian{
The notation $(\lambda, \psi) \in C^\infty(\RR^6 ; U)$ means we act by the representation and then use the scalar pairing.}

The action of supersymmetry on the pure vector multiplet was constructed in Section \ref{sec: vector} and was encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$. 
The action of supersymmetry on the pure hyper multiplet was constructed in Section \ref{sec: hyper} and was encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm matter}$ and $I^{(2)}_{\rm matter}$. 
Additionally, in the coupled theory, there are the following new terms in the action of supersymmetry:
\begin{align*}
I^{(1)}_{\rm couple} (Q) & = \int g (\psi^*, \rho([A, \phi]) Q)_U + \frac{1}{2} g (\lambda^*, Q \mu(\phi))_\fg \\
I^{(2)} (Q_1 , Q_2) & =  \brian{are any terms necessary here?}
\end{align*}
\brian{
It looks like we need to choose a moment map $\mu : U^{\otimes 2} \to \fg^*$. }

\begin{thm}
Let $S_{\rm BV} = S_{\rm gauge} + S_{\rm matter} + I_{\rm couple}$ be the full BV action for the coupled vector to hyper multiplet and let
\begin{align*}
I^{(1)} & = I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter} + I^{(1)}_{\rm couple} \\
I^{(2)} & = I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter} .
\end{align*}
Then, $\fS = S_{\rm BV} + I^{(1)} + I^{(2)}$ satisfies the classical master equation
\begin{equation}\label{CMEcouple}
\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
\end{equation}
\end{thm}

We have already seen that $S_{\rm BV}$ is consistent, so satisifies the ordinary classical master equation $\{S_{\rm BV}, S_{\rm BV}\}$. 
We decompose the remaining terms in the classical master equation \ref{CMEcouple} into components based on the cardinality of the number of odd supersymmetry inputs, many of which have already been studied in Sections \ref{sec: vector} and \ref{sec: hyper}. 
The new equations we must verify are the following:
\begin{equation}\label{CMEhyper2}
\begin{array}{rrrrrr}
\{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\} & = & 0 \\ 
\d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
\{I_{\rm couple}^{(1)}, I^{(2)}\} & =& 0 \\
%\{I^{(2)}, I^{(2)}\} & =& 0
\end{array}
\end{equation}

\begin{lem} One has
\[
\{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\}  =  0 
\]
\end{lem}
\begin{proof}
First, we compute
\begin{align*}
\{S_{\rm BV} , I^{(1)}_{\rm couple}\} = & g (\rho([A, \phi]) Q, \sd \dd \psi) + g (\psi^*, \rho([\d_A c, \phi]) Q) + g (\sd \dd_A \lambda, \mu(\phi) Q) + g (\lambda^*, [c, \mu(\phi) Q]) 
\end{align*}
Next,
\begin{align*}
\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & g (\psi, \rho(\Gamma(Q, \lambda)) \psi] + g (\d_A \phi, [\Gamma(Q, \lambda), \phi]) + g (\psi, [\rho(F_A) Q, \phi]) \\ + & g (\d_A \phi, [A, (Q, \psi)]) + g (\psi, [\lambda, (Q, \psi)]) + g (\phi^*, [c, (Q,\psi)]) + g^2 (\phi, \phi) (\phi, (Q, \psi)) \\ + & g ([A, \psi] , \rho(\d \phi)Q) + g ([\lambda, \phi] , \rho (\d \phi) Q) + g (\psi^*, [c , \rho(\d(\phi)) Q]) . 
\end{align*}
Finally,
\begin{align*}
\{I_{\rm couple}, I^{(1)}_{\rm couple}\} = & g^2 (\rho([A,\phi]) Q, [Q,\psi]) + g^2 (\rho([A,\phi]) Q, [\lambda, \phi]) + g^2 (\psi^*, \rho([A, [c,\phi]]) Q) \\ + & g^2 (\psi, [\mu(\phi) Q, \phi]) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q)
\end{align*}

Now, we collect all terms depending on the fields $A, \phi, \psi$:
\begin{align*}
\end{align*}

Here, we collect all terms depending only on $\psi$ and $\lambda$:
\[
- (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\psi, [\lambda, (Q, \psi)]) + (\psi, Q) (\lambda, \psi)
\]
This expression vanishes by Proposition \ref{prop: new3psi}.
\end{proof}

\end{document}

### 2019-11-18 6dsusy.tex
merge error

@@
 
-\title{4d $\cN=1$}
+\title{6d $\cN=(1,0)$}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) 
+%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
 \end{align*}
@@
 \begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) 
+% \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
 \end{align*}
@@
 \\ 
-& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
+& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
+%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
 \end{array}
@@
 \begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(\d
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
 \end{align*}
-
-$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
-By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
-The Clifford relation implies that
-
+The expression
+$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization is identically zero.
 \end{proof}

### 2019-11-19 coupling.tex
small change
edits

@@
 The coupled theory has action $S_{\rm gauge} + S_{\rm matter} + I_{\rm couple}$ where
-\[
-I_{\rm couple} = g (\psi, [A, \psi])_U + g (\d_{A} \phi, [A,\phi])_U + g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + g (\psi^*, [c, \psi])_U + g (\phi^*, [c, \phi])_U + g^2 \left((\phi, \phi)_U\right)^2 .
-\]
+\begin{align*}
+I_{\rm couple} = & - g (\psi, [A, \psi])_U - g (\d_{A} \phi, [A,\phi])_U \\ + & g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + g (\lambda, \mu(\phi, \psi))_\fg \\ + & g (\psi^*, [c, \psi])_U + g (\phi^*, [c, \phi])_U \\ + & g^2 \left(\mu(\phi, \phi), \mu(\phi, \phi) \right)_\fg .
+\end{align*}
+ \brian{I need to nail down this Yukawa}
 \brian{
-The notation $(\lambda, \psi) \in C^\infty(\RR^6 ; U)$ means we act by the representation and then use the scalar pairing.}
+It looks like we need to choose a moment map $\mu : U^{\otimes 2} \to \fg^*$. }
 
@@
 I^{(1)}_{\rm couple} (Q) & = \int g (\psi^*, \rho([A, \phi]) Q)_U + \frac{1}{2} g (\lambda^*, Q \mu(\phi))_\fg \\
-I^{(2)} (Q_1 , Q_2) & =  \brian{are any terms necessary here?}
+I^{(2)} (Q_1 , Q_2) & = 0 
 \end{align*}
-\brian{
-It looks like we need to choose a moment map $\mu : U^{\otimes 2} \to \fg^*$. }
+\brian{It appears there are no additional $L_\infty$ corrections}
 
@@
 \begin{align*}
-\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & g (\psi, \rho(\Gamma(Q, \lambda)) \psi] + g (\d_A \phi, [\Gamma(Q, \lambda), \phi]) + g (\psi, [\rho(F_A) Q, \phi]) \\ + & g (\d_A \phi, [A, (Q, \psi)]) + g (\psi, [\lambda, (Q, \psi)]) + g (\phi^*, [c, (Q,\psi)]) + g^2 (\phi, \phi) (\phi, (Q, \psi)) \\ + & g ([A, \psi] , \rho(\d \phi)Q) + g ([\lambda, \phi] , \rho (\d \phi) Q) + g (\psi^*, [c , \rho(\d(\phi)) Q]) .
+\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & - g (\psi, \rho(\Gamma(Q, \lambda)) \psi] - g (\d_A \phi, [\Gamma(Q, \lambda), \phi]) + g (\psi, [\rho(F_A) Q, \phi]) \\ + & g (\d_A \phi, [A, (Q, \psi)]) + g (\psi, [\lambda, (Q, \psi)]) + g (\phi^*, [c, (Q,\psi)]) +  g (\psi, (Q  , \psi) \lambda) \\ + & g^2 (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) + g ([A, \psi] , \rho(\d \phi)Q) + g ([\lambda, \phi] , \rho (\d \phi) Q) + g (\psi^*, [c , \rho(\d(\phi)) Q]) .
 \end{align*}
@@
 \begin{align*}
-\{I_{\rm couple}, I^{(1)}_{\rm couple}\} = & g^2 (\rho([A,\phi]) Q, [Q,\psi]) + g^2 (\rho([A,\phi]) Q, [\lambda, \phi]) + g^2 (\psi^*, \rho([A, [c,\phi]]) Q) \\ + & g^2 (\psi, [\mu(\phi) Q, \phi]) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q)
+\{I_{\rm couple}, I^{(1)}_{\rm couple}\} = & g^2 (\rho([A,\phi]) Q, [Q,\psi]) + g^2 (\rho([A,\phi]) Q, [\lambda, \phi]) + g^2 (\psi^*, \rho([A, [c,\phi]]) Q) \\ + & g^2 (\psi, [\mu(\phi, \phi) Q, \phi]) + g^2  (\phi, (\mu(\phi, \phi)Q, \psi) ) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q) \\ + & g^2 (\mu(\phi, \psi), \mu(\phi,\phi) Q)
 \end{align*}
 
-Now, we collect all terms depending on the fields $A, \phi, \psi$:
+Here, we collect all terms depending on the fields $A, \phi, \psi$:
 \begin{align*}
@@
 This expression vanishes by Proposition \ref{prop: new3psi}.
+
+Here, we collect all terms involving only $\phi$ and $\psi$:
+\begin{align*}
+& \pm  (\psi, [\mu(\phi, \phi) Q, \phi]) +  (\phi, (\mu(\phi, \phi)Q, \psi) ) \\
+\pm & (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) \pm (\mu(\phi, \psi), \mu(\phi,\phi)Q)
+\end{align*}
+\brian{I want to say each line is zero.}
+
+Here, we collect all terms depending only on $\lambda^*, \phi$ and $c$:
+\[
+- (\lambda^*, \mu([c, \phi], \phi) Q) + (\lambda^*, [c, Q \mu(\phi,\phi)]) .
+\]
+Since $\mu : U^{\otimes 2} \to \fg^*$ is $\fg$-invariant, this expression vanishes. 
 \end{proof}

### 2019-11-19 paper.tex
more tidying in 6 and 5d

@@
 
-\subsubsection{$\mc N = (1,0)$ with hypermultiplet matter}
+\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter}
 
@@
 \begin{enumerate}
- \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic, like in the $\mc N=(1,0)$ supersymmetry algebra.
+ \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
  \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
  \begin{enumerate}
- \item \chris{4 invariant directions}
- \item \chris{topological (this twist is a degeneration of the previous type)}
+ \item Generically, $Q$ is topological.
+ \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
  \end{enumerate}
@@
 
-\chris{types 2a and 2b fit into a family of the form $\mr{Map}(S_2 \times \Sigma_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}(\Sigma \times (M_4)_{\mr{dR}}, BG)$.}
+\begin{theorem} \label{6d_rk11_twist_thm}
+The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$.
+This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem} \label{6d_rk22_twist_thm}
+The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
 
@@
 
-\subsubsection{$\mc N = 1$ Super Yang-Mills with a Hypermultiplet}
+\subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
 
@@
 
-Exactly as in the case of 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
+Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
 \begin{enumerate}
@@
  \begin{enumerate}
- \item \chris{4 invariant directions}
- \item \chris{topological (this twist is a degeneration of the previous type)}
+ \item Generically, $Q$ is topological.
+ \item There is a special locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
  \end{enumerate}
@@
 
-\chris{types 2a and 2b fit into a family of the form $\mr{Map}(\Sigma \times (M_3)_{\mr{dR}}, BG)_{\mr{Hod}}$.  Type 3 gives $\mr{Map}((M_5)_{\mr{dR}}, BG)$.}
+\begin{theorem} \label{5d_rk2_twist_thm}
+The twist of 5d $\mc N=2$ super Yang-Mills theory by a rank $2$ supercharge with 4 invariant directions on the product of a Calabi-Yau curve $C$ and an oriented 3-manifold $M_3$ is equivalent to mixed BF theory on the product $C \times (M_3)_{\mr{dR}}$.
+This twist degenerates to a one-parameter family of topological twists of the form $\map(C \times (M_3)_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem} \label{5d_rk4_twist_thm}
+The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on ah an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
 

### 2019-11-22 paper.tex
organizing 5d section

@@
 
-\begin{prop} \label{CS_diml_red_prop}
+\begin{prop} \label{CS_to_BF_diml_red_prop}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
@@
 
-\begin{prop}
+\begin{prop} \label{CS_diml_red_prop}
 Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
@@
 \end{proof}
-
-%\begin{lemma} \label{CS_diml_red_lemma}
-%Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.
-Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.
-The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
-%\end{lemma}
-
-%\begin{lemma} \label{CS_to_BF_diml_red_lemma}
-%Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.
-The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
-%\end{lemma}
 
@@
 
-As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_lemma}.
+As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
 \end{proof}
@@
 We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory.
+We can do this by by applying Lemma \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
 More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Lemma \ref{CS_to_BF_diml_red_lemma} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
+Lemma \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
 
@@
 We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
-We can understand this twist by a second application of Lemma \ref{CS_diml_red_lemma} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
+We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
 This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.
@@
 \begin{proof}
-The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_lemma} twice.
+The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_prop} twice.
 \end{proof}
@@
 
-\subsection{Dimension 7}
+\subsection{Dimension 7} \label{7d_section}
 The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
@@
 
-\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter}
+\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
 
@@
 \subsection{Dimension 5}
+The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.
+The maximal supersymmetric gauge theory has $\mc N=2$.
+However, there are $\mc N=1$ super Yang-Mills theory for every choice $U$ of symplectic representation of the gauge group.
 
 \subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
+We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
+This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
+ \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
+ \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
+ \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes W \otimes U)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=1$ supercharges.  We can describe the supersymmetry action as follows.
+\begin{prop}
+The supersymmetry action $I^{(1)} = I^{(1)}_{\mr{gauge}} + I^{(1)}_{\mr{matter}} + I^{(1)}_{\mr{couple}}$ and $I^{(2)} = I^{(2)}_{\mr{gauge}} + I^{(2)}_{\mr{matter}}$ from Section \ref{6d_10_section} restricts to 5-dimensional $\mc N=1$ fields as follows:
+\begin{align*}
+I^{(1)}_{\mr{gauge}}(Q) &= \int \\
+I^{(1)}_{\mr{matter}}(Q) &= \int \\I^{(1)}_{\mr{gauge}}(Q) &= \int \\
+I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
+I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \\
+I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int 
+\end{align*}
+\end{prop}
+
+\begin{proof}
+\chris{...}
+\end{proof}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+There is a unique class of square-zero supercharges in the 5d $\mc N=1$ supersymmetry algebra.
+Twists by such supercharges are minimal: they are invariant in three directions.
+The stabilizer of a minimal supercharge is isomorphic to $\SU(2) \sub \Spin(5)$.
+
+\begin{theorem} \label{5d_holo_twist_theorem}
+The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory $\mr{Map}(S \times L_{\mr{dR}}, U//G)$.
+\end{theorem}
+
+\begin{proof}
+This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in \chris{ref} above, by applying Proposition \ref{CS_diml_red_prop}.
+\end{proof}
 
@@
 
-Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from section \ref{7d_section}, to representations of the group $\mr O(5)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
+ \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
+\end{itemize}
+We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.
+
+\vspace{-10pt}
+\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=2$ supercharges.  We can describe the supersymmetry action as follows.
+\begin{prop}
+The supersymmetry action $I^{(1)}$ and $I^{(2)}$ from \chris{ref} restricts to 5-dimensional $\mc N=1$ fields as
+\begin{align*}
+I^{(1)}(Q) &= \int \\
+I^{(2)}(Q_1,Q_2) &= \int 
+\end{align*}
+\end{prop}
+
+\begin{proof}
+This follows by restricting the 6d $\mc N=(1,1)$ supersymmetry action further to $\mr O(5)$.  Indeed \chris{...}
+\end{proof}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).
+These supercharges all occur as square zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
 \begin{enumerate}
@@
  \begin{enumerate}
- \item Generically, $Q$ is topological.
- \item There is a special locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
+ \item The open locus, consisting of topological supercharges.
+ \item There is a special locus consisting of supercharges with 4 invariant directions.  The former class can be realised as a degeneration of this case.
  \end{enumerate}
@@
 This twist degenerates to a one-parameter family of topological twists of the form $\map(C \times (M_3)_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+Let us describe the partition function of the A-type topological twist appearing at generic points of this family.  
+\begin{theorem}
+\chris{Something about the Haydys-Witten equations...}
 \end{theorem}

### 2019-12-04 paper.tex
Some 4d and 8d edits

@@
 \subsection{Dimension 8}
+\vspace{-10pt}
+\paragraph{Fields:} 
 The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
-It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.
-
+It has BRST fields given by a ghost $c$ along with the following.
+\begin{itemize}
+ \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
+ \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
+\end{itemize}
+
+We will see shortly that in the 8d $\mc N=1$ supersymmetry algebra there are holomorphic square-zero supercharges stabilized by the group $\SU(4)$, and topological square-zero supercharges stabilized by $\spin(7)$.
+If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
+So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
+We can write this schematically in the following way.
+
+First, let us consider the reduction of the 10d spinor $\lambda$.
+We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
+We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
+Let us continue to decompose these fields into smaller subgroups.
+We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
+\begin{figure}[!h]
+\[
+\xymatrix{
+&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
+\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
+(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
+ &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
+}\]
+\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
+\label{fig:8dfermiondecomp}
+\end{figure}
+In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
+The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
+Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
+
+We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
+\begin{figure}[!h]
+\[\xymatrix{
+&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
+A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
+\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
+&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
+}
+\]
+\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
+\label{fig:8dbosondecomp}
+\end{figure}
+Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
+
+\vspace{-10pt}
+\paragraph{Supersymmetry action:} 
+Using the decomposition of the fields described above, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
+We begin by considering $\mr O(8)$ itself.
+
+\begin{prop} \label{O8_decomposition_of_susy_prop}
+After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\begin{align*}
+I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
+I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
+\end{align*}
+if $Q^+$ is an element of $S_+$, and
+\begin{align*}
+I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
+I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
+\end{align*}
+if $Q^-$ is an element of $S_-$.
+\end{prop}
+
+\begin{proof}
+There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
+\chris{Pavel gave this argument, in terms of light-cone coordinates.}
+\end{proof}
+
+\begin{remark}
+A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
+comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
+\end{remark}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
 In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
@@
 
-\subsubsection{The Holomorphic and Topological Twists}
 Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
@@
 This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
-
-The holomorphic supercharge is stabilized by the group $\SU(4)$, and the topological supercharge is stabilized by $\spin(7)$.
-If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
-So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
-We can write this schematically in the following way.
-
-First, let us consider the reduction of the 10d spinor $\lambda$.
-We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
-We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
-Let us continue to decompose these fields into smaller subgroups.
-We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
-\begin{figure}[!h]
-\[
-\xymatrix{
-&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
-\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
-(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
- &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
-}\]
-\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dfermiondecomp}
-\end{figure}
-In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
-The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
-Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
-
-We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
-\begin{figure}[!h]
-\[\xymatrix{
-&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
-A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
-\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
-&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
-}
-\]
-\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dbosondecomp}
-\end{figure}
-Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
-
-Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
-We begin by considering $\mr O(8)$ itself.
-
-\begin{prop} \label{O8_decomposition_of_susy_prop}
-After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
-I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
-\end{align*}
-if $Q^+$ is an element of $S_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
-I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
-\end{align*}
-if $Q^-$ is an element of $S_-$.
-\end{prop}
-
-\begin{proof}
-There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
-\chris{Pavel gave this argument, in terms of light-cone coordinates.}
-\end{proof}
-
-\begin{remark}
-A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
-comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
-\end{remark}
 
@@
 
-\subsubsection{The Rank 2 Twist}
 We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
@@
 I^{(1)}_{\mr{gauge}}(Q) &= \int \\
-I^{(1)}_{\mr{matter}}(Q) &= \int \\I^{(1)}_{\mr{gauge}}(Q) &= \int \\
+I^{(1)}_{\mr{matter}}(Q) &= \int \\
 I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
@@
 \end{prop}
-
-\begin{proof}
-\chris{...}
-\end{proof}
 
@@
 
-\subsubsection{$\mc N = 2$ Super Yang-Mills Theory}
+\subsubsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}
 
@@
 
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
+ \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Supersymmetry action:} 
+\begin{prop}
+Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\begin{align*}
+I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
+&\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
+&\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
+\end{align*}
+and
+\begin{align*}
+I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
+&\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
+&\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
+\end{align*}
+where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
+\end{prop}
 %

### 2019-12-06 coupling.tex
coupling

@@
 
-\title{4d $\cN=1$}
+\title{Coupling}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 
+We choose a quadratic moment map $\mu : U^{\otimes 2} \to \fg^*$ which satisfying
+\[
+(x, \mu(a, b))_{\fg} = ([x, a], b)_U
+\]
+for all $x \in \fg$, and $a,b \in U$.
+
 Let $S_{\rm gauge}$ and $S_{\rm matter}$ be the BV actions for the $6d$ $\cN=(1,0)$ vector and hyper multiplets, respectively. 
@@
 \begin{align*}
-I_{\rm couple} = & - g (\psi, [A, \psi])_U - g (\d_{A} \phi, [A,\phi])_U \\ + & g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + g (\lambda, \mu(\phi, \psi))_\fg \\ + & g (\psi^*, [c, \psi])_U + g (\phi^*, [c, \phi])_U \\ + & g^2 \left(\mu(\phi, \phi), \mu(\phi, \phi) \right)_\fg .
+I_{\rm couple} = &- g (A, \mu \otimes \Gamma (\psi, \psi)_\fg - g (A, \mu(\d \phi, \phi)) - g (A, \mu(\phi, [A, \phi]))_\fg \\ + & 
+%g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + 
+g (\lambda, \mu(\phi, \psi))_\fg \\ + & g (\psi^*, [c, \psi])_U + g (\phi^*, [c, \phi])_U \\ + & g^2 \left(\mu(\phi, \phi), \mu(\phi, \phi) \right)_\fg .
 \end{align*}
- \brian{I need to nail down this Yukawa}
-\brian{
-It looks like we need to choose a moment map $\mu : U^{\otimes 2} \to \fg^*$. }
 
-The action of supersymmetry on the pure vector multiplet was constructed in Section \ref{sec: vector} and was encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$.
-The action of supersymmetry on the pure hyper multiplet was constructed in Section \ref{sec: hyper} and was encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm matter}$ and $I^{(2)}_{\rm matter}$.
+%\begin{align*}
+%I_{\rm couple} = & - g (A, \mu \otimes \Gamma (\psi, \psi)_\fg - g (A, \mu(\d \phi, \phi)) - g (A, \mu(\phi, [A, \phi]))_\fg \\ + & 
+%%g (\psi, [\lambda, \phi])_U + g (\phi, (\lambda, \psi))_U + 
+%g (\lambda, \mu(\phi, \psi))_\fg \\ + & g (c, \mu(\psi^*, \psi])_\fg + g (c, \mu(\phi^*, \phi))_\fg \\ + & g^2 \left(\mu(\phi, \phi), \mu(\phi, \phi) \right)_\fg .
+%\end{align*}
+
+The action of supersymmetry on the pure vector multiplet was constructed in Section \ref{sec: vector} and was shown to be encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$.
+The action of supersymmetry on the pure hyper multiplet was constructed in Section \ref{sec: hyper} and was shown to be encoded by linear and quadratic functionals that we denote $I^{(1)}_{\rm matter}$ and $I^{(2)}_{\rm matter}$.
 Additionally, in the coupled theory, there are the following new terms in the action of supersymmetry:
@@
 \begin{align*}
-\{S_{\rm BV} , I^{(1)}_{\rm couple}\} = & g (\rho([A, \phi]) Q, \sd \dd \psi) + g (\psi^*, \rho([\d_A c, \phi]) Q) + g (\sd \dd_A \lambda, \mu(\phi) Q) + g (\lambda^*, [c, \mu(\phi) Q]) 
+\{S_{\rm BV} , I^{(1)}_{\rm couple}\} = & g (\rho([A, \phi]) Q, \sd \dd \psi) + g (\psi^*, \rho([\d_A c, \phi]) Q) + \frac{1}{2} g (\sd \dd_A \lambda, \mu(\phi, \phi) Q) + g (\lambda^*, [c, \mu(\phi) Q])
 \end{align*}
@@
 \begin{align*}
-\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & - g (\psi, \rho(\Gamma(Q, \lambda)) \psi] - g (\d_A \phi, [\Gamma(Q, \lambda), \phi]) + g (\psi, [\rho(F_A) Q, \phi]) \\ + & g (\d_A \phi, [A, (Q, \psi)]) + g (\psi, [\lambda, (Q, \psi)]) + g (\phi^*, [c, (Q,\psi)]) +  g (\psi, (Q  , \psi) \lambda) \\ + & g^2 (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) + g ([A, \psi] , \rho(\d \phi)Q) + g ([\lambda, \phi] , \rho (\d \phi) Q) + g (\psi^*, [c , \rho(\d(\phi)) Q]) .
+\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & - g (\Gamma(Q, \lambda), (\mu \otimes \Gamma)(\psi,\psi)) - g (\Gamma(Q, \lambda), \mu(\phi, \d_A \phi)) + g (\rho(F_A)Q , \mu(\phi, \psi)) \\ + & g (A, \mu((Q, \psi), \d_A \phi)) + g (A, (\mu \otimes \Gamma)(\psi, \rho(\d \phi) Q)) + g (\lambda, \mu((Q, \psi), \psi)) + g (\lambda, \mu(\phi, \rho(\d \phi)  Q)) \\ + & g (\phi^*, [c, (Q,\psi)])  + g (\psi^*, \rho(\d [c , \phi ]) Q) + g^2 (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) .
 \end{align*}
@@
 \begin{align*}
-\{I_{\rm couple}, I^{(1)}_{\rm couple}\} = & g^2 (\rho([A,\phi]) Q, [Q,\psi]) + g^2 (\rho([A,\phi]) Q, [\lambda, \phi]) + g^2 (\psi^*, \rho([A, [c,\phi]]) Q) \\ + & g^2 (\psi, [\mu(\phi, \phi) Q, \phi]) + g^2  (\phi, (\mu(\phi, \phi)Q, \psi) ) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q) \\ + & g^2 (\mu(\phi, \psi), \mu(\phi,\phi) Q)
+\{I_{\rm couple}, I^{(1)}_{\rm couple}\} = & g^2 (A, (\mu \otimes \Gamma)(\psi, \rho([A, \phi]) Q)) + g^2 (\lambda, \mu(\phi, \rho([A, \phi]) Q)) + g^2 (\mu(\phi, \phi)Q , \mu(\phi, \psi)) \\
++ &g^2 (\psi^*, \rho([A, [c,\phi]]) Q) + g^2 (\psi^*, [c, \rho([A,\phi])Q]) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q)  
+\end{align*}
+%& g^2 (\rho([A,\phi]) Q, [Q,\psi]) + g^2 (\rho([A,\phi]) Q, [\lambda, \phi]) + g^2 (\psi^*, \rho([A, [c,\phi]]) Q) \\ + & g^2 (\mu(\phi,\phi)Q , \mu(\phi,\psi)) + g^2 (\lambda^*, \mu([c,\phi], \phi) Q) \\ + & g^2 (\mu(\phi, \psi), \mu(\phi,\phi) Q)
+
+Here, we collect all terms involving only $A, \phi, \psi$:
+\begin{align*}
+& 
 \end{align*}
 
-Here, we collect all terms depending on the fields $A, \phi, \psi$:
-\begin{align*}
-\end{align*}
-
-Here, we collect all terms depending only on $\psi$ and $\lambda$:
+Here, we collect all terms involving only $\psi$ and $\lambda$:
 \[
-- (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\psi, [\lambda, (Q, \psi)]) + (\psi, Q) (\lambda, \psi)
+- (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\lambda, \mu((Q,\psi), \psi)) = - (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\psi, [\lambda, (Q, \psi)]) + (\psi, Q) (\lambda, \psi)
 \]
@@
 
+Here, we collect all terms involving only $A, \phi$ and $\psi$:
+
+Here, we collect all terms involving only $A, \lambda$ and $\phi$:
+
 Here, we collect all terms involving only $\phi$ and $\psi$:
 \begin{align*}
-& \pm  (\psi, [\mu(\phi, \phi) Q, \phi]) +  (\phi, (\mu(\phi, \phi)Q, \psi) ) \\
 \pm & (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) \pm (\mu(\phi, \psi), \mu(\phi,\phi)Q)
 \end{align*}
-\brian{I want to say each line is zero.}
+Since $(\mu(\phi, \psi), \mu(\phi,\phi)Q) = (\mu(\phi, \phi) , \mu(\phi, (Q, \psi))$ this expression is identically zero.
+
+Here, we collect all terms involving only $\phi^*, c$ and $\psi$:
+
+Here, we collect all terms involving only $\psi^*$, $c$, $A$, and $\phi$:
+\[
+\pm (\psi^*, \rho([\d_A c, \phi]) Q) + (\psi^*, [c, \rho(\d \phi) Q]) + (\psi^*, \rho([A,[c,\phi]]) Q) .
+\]
+By the Jacobi identity, this simplifies to $\pm(\psi^*, [c, \d_A \phi] Q)$. \brian{stuck here}.
+%Thus, the sum of the last two terms cancels with the first term.
 
@@
 
+\begin{lem} 
+We have $\{I_{\rm couple}^{(1)}, I^{(2)}\} = 0$. 
+\end{lem}
+\begin{proof}
+This follows from the simple observation that $I^{(2)}$ only involves the antifields $\lambda^*$, $\psi^*$ whereas $I^{(1)}_{\rm couple}$ only involves the fields $A$ and $\phi$.
+So by type reasons, all terms in the bracket are zero.
+\end{proof}
+
+\section{The holomorphic twist}
+
+The holomorphic twist of the 6d $\cN=(1,0)$ vector multiplet coupled to the hyper multiplet can be described in the BV formalism as a ($\ZZ/2$-graded) generalized Chern-Simons theory on any Calabi-Yau $3$-fold $X$.
+
+Suppose the vector multiplet takes values in a Lie algebra $\fg$ and the hyper multiplet is valued in a symplectic $\fg$-representation $(U,\omega_U)$. 
+Define the following graded Lie algebra
+\[
+\begin{array}{ccccccccc}
+&&& \ul{0}  & & \ul{1} & & \ul{2} \\
+\fg_U & = && \fg & & U & & \fg^*
+\end{array}
+\]
+where the Lie brackets are given by:
+\begin{itemize}
+\item the usual Lie bracket $\fg \otimes \fg \to \fg$;
+\item the representation $\fg \otimes U[-1] \to U[-1]$;
+\item the coadjoint action $\fg \otimes \fg^*[-2] \to \fg^*[-2]$;
+\item the moment map $\mu_k : (U[-1])^{\otimes k} \to \fg^*[-2]$ \brian{could be $L_\infty$-maps, $k=2$ is the ordinary situation.}
+\end{itemize}
+
+The Lie algebra has a natural nondegenerate invariant pairing $\omega$ of degree $(+2)$ defined by combining the symplectic pairing $\omega_U$ on $U$ together with the natural dual pairing between $\fg$ and its dual.
+
+Given $\fg_U$ we can consider generalized Chern-Simons theory on $(X, \Omega^{0,\bu})$ with values in $\fg_U$.
+Note that this is only a $\ZZ/2$-graded theory in the BV formalism, since $\fg_U$ has a pairing of degree $+2$ and $\dim_\CC (X) = 3$. 
+The underlying space of BV fields is 
+\[
+\Omega^{0,\bu}_X \otimes \fg_U [1]
+\]
+and the action functional is of Chern-Simons type $S(\alpha) = \int_X (\alpha, \dbar \alpha) + \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X} \Omega_X\wedge \langle \alpha \wedge \ell_k(\alpha, \dots, \alpha)\rangle.$
+
+For the specific graded Lie algebra $\fg_U$ we can decompose $\alpha = A + \varphi + B$ where $A$ is $\fg$-valued, $\varphi$ is $U$-valued, and $B$ is $\fg^*$-valued.
+The action then takes the form
+\[
+S(A + \varphi + B) = \int_X \left(B, \dbar A + \frac{1}{2} [A,A] \right)_\fg + \omega_U \left(\varphi, \dbar \varphi + [A, \varphi] \right) + \sum_{k\geq 2} (A, \mu(\varphi, \ldots, \varphi))_\fg .
+\]
+
 \end{document}

### 2019-12-06 coupling.tex
coupling

@@
 \subsubsection{The 6d vector multiplet coupled to the hypermultiplet}
+
+\brian{Some conventions
+\begin{itemize}
+\item For $x \in \fg$ and $a \in U$ I will write $[x, a]$ for the action of $x$ on $a$. 
+\end{itemize}
+}
 
@@
 \begin{align*}
-\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & - g (\Gamma(Q, \lambda), (\mu \otimes \Gamma)(\psi,\psi)) - g (\Gamma(Q, \lambda), \mu(\phi, \d_A \phi)) + g (\rho(F_A)Q , \mu(\phi, \psi)) \\ + & g (A, \mu((Q, \psi), \d_A \phi)) + g (A, (\mu \otimes \Gamma)(\psi, \rho(\d \phi) Q)) + g (\lambda, \mu((Q, \psi), \psi)) + g (\lambda, \mu(\phi, \rho(\d \phi)  Q)) \\ + & g (\phi^*, [c, (Q,\psi)])  + g (\psi^*, \rho(\d [c , \phi ]) Q) + g^2 (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) .
+\{I_{\rm couple} , I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} = & - g (\Gamma(Q, \lambda), (\mu \otimes \Gamma)(\psi,\psi)) - g (\Gamma(Q, \lambda), \mu(\phi, \d_A \phi)) + g (\rho(F_A)Q , \mu(\phi, \psi)) \\ + & g (A, \mu((Q, \psi), \d_A \phi)) + g (A, (\mu \otimes \Gamma)(\psi, \rho(\d \phi) Q)) + g (\lambda, \mu((Q, \psi), \psi)) + g (\lambda, \mu(\phi, \rho(\d \phi)  Q)) \\ + & g (\phi^*, [c, (Q,\psi)])  + g (\psi^*, \rho( [c ,\d \phi ]) Q) + g^2 (\mu(\phi, \phi) , \mu(\phi, (Q, \psi)) .
 \end{align*}
@@
 \[
-- (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\lambda, \mu((Q,\psi), \psi)) = - (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\psi, [\lambda, (Q, \psi)]) + (\psi, Q) (\lambda, \psi)
+- (\psi, \rho(\Gamma(Q, \lambda)) \psi) + (\lambda, \mu((Q,\psi), \psi))
 \]
-This expression vanishes by Proposition \ref{prop: new3psi}.
+By Proposition \ref{prop: new3psi} we have
+\[
+(\psi, \rho(\Gamma(Q, \lambda)) \psi) = (\psi, [\lambda, (Q, \psi)] ) .
+\]
+So, by the moment map condition the total expression involving $\psi, \lambda$ vanishes.
+
+Here, we collect all terms involving only $\lambda$ and $\phi$:
+\[
+(\lambda, \mu( \phi, \rho(\d \phi)Q)) - ([\Gamma(\lambda, Q), \phi], \d \phi). 
+\]
+By the moment map condition the first term is $([\lambda, \phi], \rho(\d \phi) Q)$. 
+So, by the Clifford relation, these terms cancel.
 
@@
 Since $(\mu(\phi, \psi), \mu(\phi,\phi)Q) = (\mu(\phi, \phi) , \mu(\phi, (Q, \psi))$ this expression is identically zero. 
+\brian{fix signs}
 
 Here, we collect all terms involving only $\phi^*, c$ and $\psi$:
+\[
+(\phi^*, [c, (Q, \psi)]) \pm (\phi^*, (Q, [c,\psi])) 
+\]
+which clearly vanishes.
+
+Here, we collect all terms involving only $\psi^*$, $c$, and $\phi$:
+\[
+(\psi^*, [c, \rho(\d \phi) Q]) \pm (\psi^*, \rho( [c ,\d \phi ]) Q) 
+\]
+which clearly vanishes.
 
@@
 \[
-\pm (\psi^*, \rho([\d_A c, \phi]) Q) + (\psi^*, [c, \rho(\d \phi) Q]) + (\psi^*, \rho([A,[c,\phi]]) Q) .
+\pm (\psi^*, [c, \rho([A,\phi]) Q]) \pm (\psi^*, \rho([A,[c,\phi]]) Q) 
 \]
-By the Jacobi identity, this simplifies to $\pm(\psi^*, [c, \d_A \phi] Q)$. \brian{stuck here}.
+which clearly vanishes. 
 %Thus, the sum of the last two terms cancels with the first term.

### 2019-12-07 coupling.tex
pavel discuss

@@
 The new equations we must verify are the following:
-\begin{equation}\label{CMEhyper2}
+\begin{equation}\label{CMEcouple}
 \begin{array}{rrrrrr}
 \{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\} & = & 0 \\ 
-\d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
+\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} + \d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
 \{I_{\rm couple}^{(1)}, I^{(2)}\} & =& 0 \\
@@
 \end{equation}
+
+The third equation is zero by type reasons.
+\begin{lem} 
+We have $\{I_{\rm couple}^{(1)}, I^{(2)}\} = 0$. 
+\end{lem}
+\begin{proof}
+This follows from the simple observation that $I^{(2)}$ only involves the antifields $\lambda^*$, $\psi^*$ whereas $I^{(1)}_{\rm couple}$ only involves the fields $A$ and $\phi$.
+So by type reasons, all terms in the bracket are zero.
+\end{proof}
+
+This leaves us to verify the first two equations of (\ref{CMEcouple}). 
+We begin with the first equation.
 
@@
 
+Finally, we verify the second equation in (\ref{CMEcouple}).
+
 \begin{lem}
-We have $\{I_{\rm couple}^{(1)}, I^{(2)}\} = 0$. 
+One has
+\[
+\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} + \d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} =  0.
+\]
 \end{lem}
 \begin{proof}
-This follows from the simple observation that $I^{(2)}$ only involves the antifields $\lambda^*$, $\psi^*$ whereas $I^{(1)}_{\rm couple}$ only involves the fields $A$ and $\phi$.
-So by type reasons, all terms in the bracket are zero.
+The second and fourth terms are zero by type reasons.
+Thus, we must show
+\begin{equation}\label{CMEcouple2}
+\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} +  \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} = 0
+\end{equation}
+
+We begin by expanding $\{I_{\rm couple}, I^{(2)}_{\rm gauge}\}$:
+\begin{align*}
+\{I_{\rm couple}, I^{(2)}_{\rm gauge}\} (Q_1,Q_2) = & (\rho(\Gamma(Q_1,Q_2)) \lambda^*, \mu(\phi,\psi)) + (Q_1, \mu(\phi, \psi)) (Q_2, \lambda^*) + (Q_1, \lambda^*)(Q_2 \mu(\phi,\psi)) \\ + & (\psi^*, [i_{\Gamma(Q_1,Q_2)} A , \psi]) + (\phi^*, [i_{\Gamma(Q_1,Q_2)} A , \phi])
+\end{align*}
+
+Next, we expand $\{I_{\rm couple}, I^{(2)}_{\rm matter}\}$:
+\begin{align*}
+\{I_{\rm couple}, I^{(2)}_{\rm matter}\} = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) +  (\psi^*, [c, \rho(\Gamma(Q_1,Q_2)) \psi^*])
+\end{align*}
+
+Expanding $\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}$:
+\begin{align*}
+\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\} = (\phi^* Q_1 , \rho([A,\phi]) Q_2) + \brian{finish}
+\end{align*}
+
 \end{proof}

### 2019-12-08 coupling.tex
coupling roughly done

@@
 
-Here, we collect all terms involving only $A, \phi, \psi$:
-\begin{align*}
-& 
-\end{align*}
+First, we collect all terms involving only $A, \phi$ and $\psi$.
+This is obtained by extracting the $A$-dependent terms in the expression
+\[
+\pm (\d_A(Q, \psi), \d_A \psi) \pm (\rho(\d_A\phi)Q, \sd \dd_A \psi) .
+\]
+The proof that this expression vanishes is identical to the proof of Lemma \ref{lem: hyper1}.
 
@@
 So, by the Clifford relation, these terms cancel.
-
-Here, we collect all terms involving only $A, \phi$ and $\psi$:
 
@@
 \]
-Since $\mu : U^{\otimes 2} \to \fg^*$ is $\fg$-invariant, this expression vanishes. 
+Since the moment map $\mu$ is $\fg$-invariant, this expression vanishes. 
 \end{proof}
@@
 \begin{align*}
-\{I_{\rm couple}, I^{(2)}_{\rm matter}\} = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) +  (\psi^*, [c, \rho(\Gamma(Q_1,Q_2)) \psi^*])
+\{I_{\rm couple}, I^{(2)}_{\rm matter}\} (Q_1,Q_2) = & (\rho(\Gamma(Q_1,Q_2)) \psi^*, [A, \psi]) + (\lambda, \mu(\phi, \rho(\Gamma(Q_1,Q_2)) \psi^*)) \\ & + (\Gamma(Q_1, Q_2), \Gamma([c, \psi^*], \psi^*)) + (\Gamma(Q_1, Q_2), \Gamma(\psi^*, [c, \psi^*])).
 \end{align*} 
+The last line vanishes by the $\fg$-invariance of the symplectic pairing for $U$.
 
@@
 \begin{align*}
-\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\} = (\phi^* Q_1 , \rho([A,\phi]) Q_2) + \brian{finish}
+\{I^{(1)}_{\rm gauge}, I^{(1)}_{\rm couple}\}(Q_1,Q_2) = & (\psi^*, \rho([\Gamma(Q_1, \lambda), \phi]) Q_2) + (\psi^*, \rho([\Gamma(Q_2, \lambda), \phi]) Q_1) \\ + & (A^*, \Gamma(Q_1, \mu(\phi, \phi) Q_2)) - (A^*, \Gamma(Q_2, \mu(\phi, \phi) Q_1)) .
 \end{align*}
+Notice the term proportional to $A^*$ vanishes.
+
+\begin{align*}
+\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\}  (Q_1,Q_2) = & (\phi^* Q_1 , \rho([A,\phi]) Q_2) + (\phi^* Q_2 , \rho([A,\phi]) Q_1) \\ + &  (\psi^*, \rho([A, (Q_1, \psi)]) Q_2) +  (\psi^*, \rho([A, (Q_2, \psi)]) Q_1) \\ + & (\lambda^*, \mu((Q_1, \psi), \phi) Q_2) +  (\lambda^*, \mu((Q_2, \psi), \phi) Q_1)
+\end{align*}
+
+We collect terms involving $\phi, A$ and $\phi^*$:
+\[
+\pm [i_{\Gamma(Q_1, Q_2)} A, \phi] + (Q_1, \rho([A,\phi])Q_2) + (Q_2, \rho([A,\phi])Q_1)
+\]
+By Proposition \ref{prop:cliffordactionproperties} the last two terms cancel with the first term.
+
+Next, we collect terms involving $\phi, \psi$ and $\lambda^*$. 
+This term is obtained by taking the $\fg$-pairing of $\mu(\phi, \psi)$ with
+\[
+\pm \rho(\Gamma(Q_1,Q_2)) \lambda^* + (Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*) Q_2
+\]
+which vanishes by Proposition \ref{prop: new3psi}.
+
+Next, we collect terms involving $\lambda, \phi, \psi^*$.
+This term can be written as pairing the antifield $\psi^*$ with the field
+\[
+\rho(\Gamma(Q_1,Q_2)) [\lambda, \phi] + \rho([\Gamma(Q_1,\lambda), \phi]) Q_2  + \rho([\Gamma(Q_2,\lambda), \phi]) Q_1. 
+\]
+This whole expression is equal to applying the $\fg$-valued field 
+\[
+\rho(\Gamma(Q_1,Q_2)) \lambda + \rho(\Gamma(Q_1,\lambda)) Q_2  + \rho(\Gamma(Q_2,\lambda)) Q_1
+\]
+to the field $\phi$ by the representation. 
+This expression vanished by Proposition \ref{prop:3psi}.
+
+Finally, we collect terms involving $\psi^*,A$ and $\psi$.
+This can be written as the pairing of the antifield $\psi^*$ with the field
+\[
+\pm [A, \rho(\Gamma(Q_1,Q_2)) \psi] + \rho([A, (Q_1, \psi)]) Q_2 + \rho([A, (Q_2, \psi)]) Q_1 .
+\] 
+This expression is equal to applying the $\fg$-valued field $A$ to the field
+\[
+\pm \rho(\Gamma(Q_1,Q_2)) \psi + (Q_1, \psi) Q_2 + (Q_2, \psi) Q_1
+\]
+which vanishes by Proposition \ref{prop: new3psi}.
 

### 2019-12-10 paper.tex
merge
Fixed equivalences of classical field theories

@@
 
+\newcommand{\defterm}[1]{\textbf{\emph{#1}}}
+
 \addbibresource{Twist.bib}
@@
 \begin{definition}
-A {\bf free BV theory} on a manifold $M$ is the data:
+A \defterm{free BV theory} on a manifold $M$ is the data:
 \begin{itemize}
@@
 
-We call $\cE$ the {\em space of BV fields}.  
+We call $\cE$ the \defterm{space of BV fields}.  
 The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
-In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every {\em local} functional $f \in \cO(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$.
+In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every functional $f \in \oloc(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$.
 Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
@@
 \begin{definition}
-The {\bf BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
+The \defterm{BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
 \[
@@
 \end{definition}
+
+\begin{remark}
+Note that the BV bracket in fact defines a bilinear map $\{-, -\}\colon \oloc(\cE)\times\cO(\cE)\rightarrow \cO(\cE)$. However, it does \emph{not} define a bracket on $\cO(\cE)$ itself.
+\end{remark}
 
@@
 \begin{definition}
-A {\bf classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
+A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
 \[I \in \oloc^+(\cE)\]
@@
 \begin{remark}
-We will also consider {\bf $\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
 \end{remark}
@@
 \begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a symplectic isomorphism $L\cong L^![-3]$.
+The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e. a symplectic isomorphism $L\cong L^![-3]$.
 \end{remark}
 
-A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
-It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$\footnote{Although, for two arbitrary functionals $F, G \in \cO(\cE)$, the bracket $\{F,G\}$ is not defined.}, see Definition \ref{dfn: fnl} in the appendix.
+A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all functionals $\cO(E)$.
 The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
@@
 \begin{definition}
-A {\bf morphism} $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a linear map of vector bundles
-\[
-F\colon E \to E'
-\]
-that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. 
-\end{definition}
-
-Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
-\[
-F^*\colon \left(\cO (\cE')[-1], Q' + \{I',-\} \right) \to \left(\cO (\cE)[-1], Q + \{I,-\} \right).
-\]
-This allows us to make the following definition of an equivalence between classical theories.
-
-\begin{definition} \label{equivalence_def}
-A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
-\[
-F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
-\]
+A \defterm{morphism} $F\colon (E, Q, \omega, I) \rightsquigarrow (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is an \defterm{equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
 \end{definition}
@@
 \label{infinitesimal_action_def}
-Let $(E, Q,\omega, I)$ be a classical field theory. An {\bf action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
+Let $(E, Q,\omega, I)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
 \[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
@@
 \label{group_action_def}
-Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An {\bf action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
+Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
 \begin{itemize}
@@
 Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
-The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
+The \defterm{classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
 \[
@@
 \begin{definition}
-A {\bf classical BRST theory} on a manifold $M$ consists of the following data:
+A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
 \begin{itemize}
@@
 
-We call $\cF$ the {\bf space of BRST fields}.
+We call $\cF$ the \defterm{space of BRST fields}.
 
@@
 
-We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the {\bf $(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of {\bf cotangent type}.
+We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
 
@@
 Fix an $L_\infty$ algebra $\fg$.
-The {\bf generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
 \begin{itemize}
@@
 Fix a complex vector space $V$.
-The {\bf generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
 \begin{itemize}
@@
 We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The {\bf generalized Chern--Simons theory} is the following classical BV theory:
+The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
 \begin{itemize}
@@
 \begin{definition}
-The {\bf Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The {\bf Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
+The \defterm{Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The \defterm{Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
 \end{definition}
@@
 \begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a {\bf dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 \begin{itemize}
-\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the {\bf spin} representation $S$.
-
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the {\bf semi-spin} representations $S_+, S_-$.
-\end{itemize}
-
-\begin{definition}
-A {\bf spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
+\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.
+
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
+\end{itemize}
+
+\begin{definition}
+A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
 \end{definition}
@@
 Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-The {\bf supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
+The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
 \end{definition}
@@
 
-\item A complex Lie group $G_R$, the {\bf group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
+\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
 \end{itemize}
@@
 \begin{definition}
-A classical field theory $(E, Q, \omega, I)$ is {\bf supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
 \end{definition}
@@
 \begin{definition}
-A {\bf square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
 \end{definition}
@@
 \begin{itemize}
-\item A supercharge $Q$ is {\bf topological} if $d = n$.
-
-\item A supercharge $Q$ is {\bf holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a {\bf holomorphic-topological} (alternatively, partially topological) supercharge.
+\item A supercharge $Q$ is \defterm{topological} if $d = n$.
+
+\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
 The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
@@
 \begin{definition}
-A {\bf twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-We will call $\alpha$ in a twisting datum a {\bf twisting homomorphism}.
+A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{definition}
+
+We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
 
@@
 Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The {\bf $Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 Let $E$ be a vector bundle on $M$ and $U \subset M$.
-The {\bf completed algebra of functions} on $\cE(U)$ is
+The \defterm{completed algebra of functions} on $\cE(U)$ is
 \[
@@
 \begin{itemize}
-\item a {\bf smooth vector space} is a sheaf of vector spaces on $\Mfld$.
+\item a \defterm{smooth vector space} is a sheaf of vector spaces on $\Mfld$.
 \item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
-\item a $C^\infty$-{\bf module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
+\item a \defterm{$C^\infty$-module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
 If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
-\item a {\bf differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
+\item a \defterm{differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
 \[
@@
 Suppose $V,W$ are cochain complexes in convenient vector spaces. 
-A cochain map $f : V \to W$ is a {\bf quasi-isomorphism} if the map
+A cochain map $f\colon V \to W$ is a \defterm{quasi-isomorphism} if the map
 \[
@@
 \begin{definition}
-A {\bf filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
+A \defterm{filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
 \[
@@
 where each map is a monomorphism in each cohomological degree. 
-A filtered differentiable cochain complex is {\bf complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
+A filtered differentiable cochain complex is \defterm{complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
 \end{definition}
@@
 \begin{definition}\label{dfn: pro}
-A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
+A \defterm{differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
 \[

### 2019-12-10 matter.tex
matter

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{Matter, uniformly}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\begin{definition}
Let $\fg$ be a Lie algebra.
An even (resp. odd) {\bf supersymmetric matter pair} is a pair $(\SS, U)$ where 
\begin{itemize}
\item[(1)] $\SS$ is a $\ZZ/2$-graded spinorial representation equipped with an even (resp. odd) nondegenerate $V$-valued pairing
\[
\Gamma : \wedge^2(\SS)^0 \xto{\cong} V
\]
(resp. $\Gamma : \wedge^2(\SS)^1 \xto{\cong} V$), and

\item[(2)] $U$ is an even (resp. odd) symplectic $\fg$-representation.
\end{itemize}
\end{definition}

\begin{lem}
For a fixed Lie algebra $\fg$, a complete classification of the supersymmetric matter pairs \brian{Should we say minimal here? What about dimension 3 and 2?} (for dimensions $n \geq 2$) are:
\begin{itemize}
\item[(1)] Dimension $n = 4$. 
There is an odd supersymmetric matter pair $(\SS = S_+ \oplus S_-, U = R \oplus R^*)$ where the odd pairing $\Gamma : S_+ \otimes S_- \xto{\cong} V$ is the usual $\Gamma$ pairing. Here, $R$ is a $\fg$-representation, and in the odd symplectic representation $U = R \oplus R^*$ we view $R$ as even and $R^*$ as odd. 
\item[(2)] Dimension $n=6$.
There are two even supersymmetric matter pairs: $(\SS = S_+ \otimes W_+, U)$ and $(\SS = S_- \otimes W_-, U)$ where $W_\pm$ is a $2$-dimension symplectic vector space and $U$ is a symplectic $\fg$-representation. 
The even nondegenerate pairings are the usual $\Gamma$ pairings $\Gamma : \wedge^2 (S_\pm) \xto{\cong} V$ 
\end{itemize}
\end{lem}

\begin{prop}
\brian{how to state $3 \psi$-rule}

\begin{itemize}
\item[(1)] Dimension $n = 4$.
Suppose $Q_+ \oplus Q_- \in S_+ \oplus S_-$.
Then, the following diagram commutes
\[
\xymatrix{
S_+ \otimes S_- \ar[dr]_-{(Q_+ + Q_-,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
& S_+ \oplus S_- &  
}
\]
\item[(2)] Dimension $n = 6$. 
Suppose $Q \in S_\mp$.
Then, the following diagram commutes
\[
\xymatrix{
\wedge^2 S_\pm \ar[dr]_-{(Q,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
& S_\pm & 
}
\]
\end{itemize}
\end{prop}

To a supersymmetric matter pair we will associate a free BV theory whose underlying BRST fields consist of:
\begin{itemize}
\item a scalar $\phi \in C^\infty(\RR^n ; \SS^*)$;
\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
\begin{dfn}
The BRST theory associated to a supersymmetric matter pair (even or odd) $(\SS, U)$ has underlying bundle of BRST fields:
\[

\end{document}

### 2019-12-13 coupling_2.tex
New file on standardizing notation

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8 } = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{Coupling}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}
\begin{document}

Fields and supercharges live in the following places.

\begin{table}[!h]
\centering
\begin{tabular}[!h]{c|c|c|c}
&6d&4d&3d \\
\hline
$A \in V_n \otimes \gg$& $V_6 \otimes \gg$ &$V_4 \otimes \gg$ & $V_3 \otimes \gg$ \\
$\lambda \in \Sigma \otimes \gg$ &$S_+ \otimes W_+ \otimes \gg$ & $(S_+ \oplus S_-) \otimes \gg$ & $S \otimes \gg$ \\
$\psi \in \Psi$ & $S_- \otimes U$ & $(S_+ \otimes R) \oplus (S_- \otimes R^*)$ & $S \otimes R$ \\
$\phi \in \Phi$ & $W_+ \otimes U$ & $R \oplus R^*$ & $R$ \\
$Q \in \Sigma$ & $S_+ \otimes W_+$ & $S_+ \oplus S_-$ & $S$ \\
$Q^* \in S^*$ & $S_-$ & $S_+ \oplus S_-$ & $S$
\end{tabular}
\end{table}

Here $\Phi$ is a representation of $\gg$ and $\Psi$ is a representation of $\so(n) \oplus \gg$.  To define the action, including the background field $Q$, we need the following structures, all $\gg$-equivariant. 
\begin{enumerate}
 \item A first-order differential operator $\sd \dd \colon \Psi \to \Psi^*$.
 \item An operator $\rho_\Psi \colon V_n \otimes \Psi^* \to \Psi$.
 \item A gamma pairing $\Gamma \colon \sym^2 \Psi \to V_n$.
 \item A moment map pairing $\mu \colon \sym^2 \Phi \to \gg$.
 \item An additional $\gg$-equivariant map $Y \colon \Sigma \otimes \Psi \to \Phi$, or equivalently, using $\mu$, either a map $Y_\mu\colon \Sigma \otimes \Psi \otimes \Phi \to \gg$ or $Y_\mu^* \colon \Sigma \otimes \Phi \to \gg \otimes \Psi^*$.
\end{enumerate}

With this data in mind, we define the action, and the coupling to supercharges $Q$, as follows.  I'll write $\eta$ for the pairing on $V_n \otimes \gg$ induced from the metric and the Killing form, and $\kappa$ for the Killing form alone.
\begin{align*}
S_{\mr{gauge}} &= \int \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*)\\
S_{\mr{matter}} &= \int - \frac{1}{2}  (\d \phi \wedge * \d \phi) + \frac{1}{2} (\psi , \sd \dd \psi)\\
I_{\mr{couple}} &= \int g\big( \eta(A, \Gamma (\psi, \psi)) - \frac 12 \eta(A, \d_A \mu( \phi, \phi)) - 
\kappa \circ Y_\mu(\lambda,\psi,\phi)  +  (\psi^*, [c, \psi])_U + \\
&\qquad\qquad\qquad\qquad\qquad\qquad +  (\phi^*, [c, \phi])\big)  +  g^2 \left(\mu(\phi, \phi), \mu(\phi, \phi) \right) \\
I^{(1)}_{\mr{gauge}}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
I^{(1)}_{\mr{matter}}(Q) &= \int (\phi^*, Y(Q, \psi)) + (\psi^*, \rho(\d \phi) Q)\\
I^{(1)}_{\mr{couple}}(Q) &= \int g (\psi^*, \kappa \circ \rho_\Psi \circ (1 \otimes Y_\mu^*)(A, Q, \phi)) + \frac{1}{2} g (\lambda^*, Q \otimes \mu(\phi,\phi)) \\
I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - (\iota_{\Gamma(Q_1, Q_2)} A, c^*) \\
I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)).
\end{align*}

With all of this, along with an appropriate version of the ``$3\psi$-rule'' -- which should say something about the compatibility of these structures, along with the claim that the map from either $\wedge^2S_+$, $S_+ \otimes S_-$ or $\sym^2 S$ to $V_n$ is an isomorphism -- I speculate the supersymmetry calculation should work symmetrically.  The $3\psi$ rule should just be the following.

\begin{prop}\label{prop: new3psi}
Suppose $Q_1,Q_2 \in \Sigma$ and $Q^* \in S$. 
Then
\[
(Q_1, Q^*) Q_2 + (Q_2, Q^*)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q^*
\]
\end{prop}

%\section{Supersymmetric coupling}

%We'll explain how to prove the following.
%\begin{prop}
%The following equations hold, for the supersymmetry action of the 6d $\mc N=(1,0)$ super Yang-Mills theory coupled to a hypermultiplet valued in a symplectic representation $U$.
%\begin{equation}\label{CMEcouple}
%\begin{array}{rrrrrr}
%\{S_{\rm BV} , I^{(1)}_{\rm couple}\} + \{I_{\rm couple}, I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}\} + \{I_{\rm couple}, I^{(1)}_{\rm couple}\} & = & 0 \\ 
%\{I_{\rm couple}, I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter}\} + \d_{CE} I^{(1)}_{\rm couple} + \{I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter}, I^{(1)}_{\rm couple}\} + \frac{1}{2} \{I_{\rm couple}^{(1)}, I_{\rm couple}^{(1)}\} & = & 0 \\
%\{I_{\rm couple}^{(1)}, I^{(2)}\} & =& 0 \\
%\{I^{(2)}, I^{(2)}\} & =& 0
%\end{array}
%\end{equation}
%\end{prop}

\end{document}

### 2019-12-27 paper.tex
merge
Matter SUSY in all dimensions, 10d SYM update

@@
 \newcommand{\Dens}{\mathrm{Dens}}
+\renewcommand{\Re}{\mathrm{Re}}
 
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q e_1) = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is an \defterm{equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
+A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory.
 \end{definition}
@@
 For a more thorough introduction, and for which our conventions are based on, we refer to \cite{Book1}.
+
+We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
+First, we consider the process of integrating out an auxiliary field.
+
+\begin{prop}
+Fix a volume form $\dvol_M$ on $M$.
+Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
+Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
+Suppose the BV action is
+\[S_{BV} = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
+where $S_0$ and $S_1$ are independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
+\label{prop:integrateoutfield}
+\end{prop}
+\begin{proof}
+\pavel{The map $E_0\rightarrow E$ is obviously compatible with all the structures.}
+\end{proof}
+
+We may also remove a trivial BRST doublet.
+
+\begin{prop}
+Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus F\oplus F^![-1]\oplus F^!\oplus F[-1]$.
+Denote by $\phi, \phi^*$ sections of $F,F^![-1]$ and by $\psi, \psi^*$ sections of $F^!, F[-1]$.
+Suppose
+\[Q\phi + \{I, \phi\} = \psi - F_\psi,\qquad Q\psi^* + \{I, \psi^*\} = \phi^* - F_{\phi^*},\]
+where $F_\psi$ is independent of $\psi$ and $F_{\phi^*}$ is independent of $\phi^*$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = 0, \phi^* = F_{\phi^*}, \psi = F_\psi, \psi^* = 0$ in the original BV action.
+\label{prop:BRSTdoublet}
+\end{prop}
+\begin{proof}
+\end{proof}
 
@@
 Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
-The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
+The BV complex can be thought of as the complex of functions on the derived critical locus of the BRST action.
 It makes sense to restrict fields to any open set $U \subset M$. 
-Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.
+Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the BRST action where we restrict the theory to $U$.
 
@@
 
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$.
-We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
-\begin{equation}
-(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
-\label{eq:Gammaspinorpairing}
-\end{equation}
-for any $Q_1, Q_2\in\Sigma$ and $v\in V$.
-
-The fields of Yang--Mills theory are as follows:
+Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a Clifford module $\Sigma\oplus \Sigma^*$ as in Section \ref{sect:spinors}.
+The fields of the Yang--Mills theory are as follows:
 \begin{itemize}
@@
 The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]
+\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd \dd_A \lambda)\right\rangle.\]
 
@@
 The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]
+\begin{equation}
+S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd\dd_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).
+\label{eq:YMBVaction}
+\end{equation}
 
@@
 \end{proof}
+
+\begin{remark}
+Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
+\end{remark}
 
@@
 
-Let $V_\RR = \RR^n$ endowed with its nondegenerate bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
 \begin{itemize}
@@
 
+\subsection{Division algebras and supersymmetry}
+\label{sect:divisionalgebras}
+
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and division algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+
+Let $A_\RR$ be a (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+\begin{enumerate}
+\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\end{enumerate}
+
+For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
+We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
+$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
+
+We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
+So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
+
+Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
+
+\begin{lemma}
+Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
+Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
+\label{lm:extendpairing}
+\end{lemma}
+
+Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
+\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
+given, respectively, by
+\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
+
+The following is proved in \cite[Proposition 6]{BaezHuerta}.
+
+\begin{prop}
+The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
+\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
+\end{prop}
+
+We have a nondegenerate scalar spinorial pairing
+\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
+given by
+\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
+It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
+\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
+
+By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
+\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
+
+We will now state two important properties of $\Gamma$ and the spinorial pairing.
+The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
+
+\begin{thm}
+Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
+\label{thm:3psi}
+\end{thm}
+
+If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
+
+\begin{thm}
+Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
+\label{thm:matter3psi}
+\end{thm}
+\begin{proof}
+The right-hand side is
+\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
+which by associativity can be rewritten as
+\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
+which is the left-hand side.
+\end{proof}
+
+We will be interested in the following four examples:
+\begin{enumerate}
+\item $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$ (3d $\mc N=1$ supersymmetry).
+
+\item $A_\RR = \CC$. We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations (4d $\mc N=1$ supersymmetry).
+
+\item $A_\RR = \mathbb{H}$.
+We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$ (6d $\mc N=(1, 0)$ supersymmetry).
+
+\item $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation (10d $\mc N=(1, 0)$ supersymmetry).
+\end{enumerate}
+
+All four examples are alternative, while the first three examples are moreover associative.
+
+\subsection{Supersymmetric twisting}
+
+\pavel{$Q$ denotes both the differential on fields and the supercharge.}
+
+\begin{definition}
+A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+\end{definition}
+
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+\begin{itemize}
+\item A supercharge $Q$ is \defterm{topological} if $d = n$.
+
+\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
+The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+\begin{definition}
+A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{definition}
+
+We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
+
+\begin{definition} \label{def:twisting}
+Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
+for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+\end{definition}
+
+\begin{prop}
+The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
+\end{prop}
+\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{remark}
+Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
+\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
+where the $\ZZ/2$-grading on $E$ is the total grading.
+\end{remark}
+
+\subsection{Dimensional Reduction of Supersymmetric Theories}
+
+Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
+
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
+This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
+We have a natural embedding
+\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
+so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
+\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
+where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
+\[G_W = G_V\times \Spin(W^\perp_\RR).\]
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
+We have the following generalization of this statement to supersymmetric theories.
+
+\begin{prop} \label{prop:susydimlred}
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
+\end{prop}
+
+\begin{proof}
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+\end{proof}
+
+The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
+
+\begin{prop}
+Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
+Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
+\label{prop:twistdimensionalreduction}
+\end{prop}
+
+\subsection{Twisting Homomorphisms and Curved Backgrounds}
+
+\section{Supersymmetric Yang--Mills theories}
+
+In this section we construct supersymmetry action on all super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
+\begin{itemize}
+\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.
+
+\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$. \pavel{Moment maps?}
+
+\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
+
+\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
+\end{itemize}
+
+In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills.
+So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.
+
 \subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
 
-For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
-In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
-\begin{itemize}
- \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
- \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
- \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
- \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
-\end{itemize}
-These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.
-
-We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Fix an \emph{alternative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
+We will show that in this case the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
+
+We will construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
 Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
-
-Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
-\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
-by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
-This gives rise to an action map
-\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
-of two-forms on spinors.
-Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
-\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
-on $\Sigma$ and $\Sigma^*$.
 
@@
 
-Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
-\begin{equation}
-q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
-\label{eq:quantizationtwoforms}
-\end{equation}
-
-The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.
-
 The following properties of the Clifford action will be useful.
 Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
-
-\begin{prop}
-One has the following:
-\begin{enumerate}
-\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
-\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
-
-\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
-\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]
-
-\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
-\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
-\end{enumerate}
-\label{prop:cliffordactionproperties}
-\end{prop}
-
-In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases.
-This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.
-
-\begin{prop}
-Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
-\label{prop:3psi}
-\end{prop}
 
@@
 \begin{align*}
-\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
+\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\dd}_A\lambda) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\dd}_A(\rho(F_A) Q)) \\
 &= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
 \end{align*}
-where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.
-
-By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
+where we have used Proposition \ref{prop:cliffordactionproperty3} and the Bianchi identity in the last line.
+
+By \eqref{eq:Gammaspinorpairing} and Theorem \ref{thm:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
 
@@
 \begin{align*}
-\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
+\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\dd}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\dd}_A \lambda + [c, \lambda^*]) \\
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\dd}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
 &+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
@@
 \[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
-Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
+Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
 
@@
 &-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
-&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
-\end{align*}
-Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
-\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
+&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\dd}_A\lambda - \frac{1}{2}(Q_2, \sd{\dd}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\dd}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
+\end{align*}
+Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
+\[-\frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
+which is equal to $\frac{1}{2} \sd{\dd}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Theorem \ref{thm:3psi}. Using the Clifford relation this term cancels the rest of the terms.
 \end{proof}
@@
 
-$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
-By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+$\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
+By Theorem \ref{thm:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
 The Clifford relation implies that
@@
 \end{align*}
-Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
-\end{proof}
-
+Therefore, again using Theorem \ref{thm:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
+\end{proof}
+
+\begin{comment}
+\pavel{This might go in the coupling section.}
 We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
@@
 \end{remark}
-
+\end{comment}
+
+\subsection{Matter multiplet}
+
+Fix an \emph{associative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
+Note that $\Sigma$ and $\Sigma^*$ are naturally right $A$-modules; the Clifford multiplication $V\otimes \Sigma\rightarrow \Sigma^*$ and the spinorial pairing $\Sigma\otimes \Sigma^*\rightarrow A$ are maps of right $A$-modules.
+We will use the antiinvolution $\sigma\colon A\rightarrow A$ to turn left $A$-modules into right $A$-modules.
+
+Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
+\[(av, w) = (v, \sigma(a)w).\]
+Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
+\begin{itemize}
+\item $A_\RR=\RR$, so $A=\CC$. We are looking for a complex vector space $P$ equipped with a nondegenerate symmetric bilinear pairing.
+
+\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$.
+A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$.
+Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$.
+So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$.
+In other words, the data boils down to a complex vector space $R$, so that $P = R\oplus R^*$.
+
+\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
+A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
+Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
+So, the data boils down a complex symplectic vector space $U$.
+\end{itemize}
+
+We are going to construct a theory on $V_\RR$ describing a matter multiplet valued in $P$. The BRST fields are given as follows:
+\begin{itemize}
+\item a scalar $\phi\in\Gamma(V_\RR; P)$;
+\item a spinor $\psi\in\Gamma(V_\RR; \Pi \Sigma^*\otimes_A P)$.
+\end{itemize}
+As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
+
+We extend the pairings on $P$ and between $\Sigma$ and $\Sigma^*$ to a pairing between $\Sigma\otimes_A P$ and $\Sigma^*\otimes_A P$ in the following way.
+Given $\sum_i \tilde{s}_i\otimes v_i\in \Sigma^*\otimes_A P$ and $\sum_j s_j\otimes w_j\in\Sigma\otimes_A P$, their pairing is
+\begin{equation}
+\sum_{i, j} \Re((v_i, w_j)^A (s_j, \tilde{s}_i)^A),
+\label{eq:spinorialmatterpairing}
+\end{equation}
+where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
+\[\Gamma_P\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
+defined by the property
+\[(v, \Gamma_P(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
+
+The action for the matter multiplet is
+\[
+S = \int_{V_\RR} -\frac{1}{2}  (\d \phi \wedge * \d \phi) + \frac{1}{2} (\psi , \sd \dd \psi)\dvol,
+\]
+where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
+
+The action of supersymmetry is given by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int (\phi^*, (Q, \psi)) - (\psi^*, \rho(\d \phi) Q) \\
+I^{(2)} (Q_1 , Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)_P) \end{align*}
+where $Q, Q_1,Q_2 \in \Sigma$.
+
+The following result states that these functionals encode an off-shell action of the supersymmetry on the matter multiplet.
+
+\begin{thm}
+The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
+\begin{equation}\label{CMEmatter}
+\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
+\end{thm}
+
+We decompose the classical master equation \eqref{CMEmatter} into the following equations:
+\begin{equation}\label{CMEmatter2}
+\begin{array}{rrrrrr}
+\{S , I^{(1)}\} & = & 0 \\ 
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
+\{I^{(2)}, I^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
+
+The first equation in \eqref{CMEmatter2} states that the classical action for the matter multiplet is supersymmetric.
+
+\begin{lemma} \label{lem: matter1}
+One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+\end{lemma}
+\begin{proof}
+Observe
+\[
+\{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = 2 (\d (Q, \psi) , \d \phi ) .
+\]
+and
+\[
+\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2(\psi, \sd \dd \rho(\d \phi) Q).
+\]
+
+By Proposition \ref{prop:cliffordactionproperty3} $\sd \dd\rho(\d\phi) Q = (\d^* \d\phi) Q$. Therefore,
+\[2(\psi, \sd \dd \rho(\d \phi) Q) = 2(\d^*\d\phi)(\psi, Q) = -2(\d\phi, \d(\psi, Q))\]
+which cancels the first term.
+\end{proof}
+
+Next, we move on to the second equation in \eqref{CMEmatter2}.
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEmatter3}
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating expression \eqref{CMEmatter3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
+
+The individual terms are:
+\begin{align*}
+\frac{1}{2}\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &\phi^* (Q_1, \rho(\d \phi) Q_2) + \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  + (\psi^*, \rho(\d(Q_1,\psi))Q_2) + (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
+\end{align*}
+
+\begin{align*}
+(\d_{CE}I^{(1)})(Q_1,Q_2) = &-\phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
+\end{align*}
+
+and
+\begin{align*}
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi)_P
+\end{align*}
+Note that we can rewrite this as $\frac{1}{2} (\rho(\Gamma(Q_1, Q_2)) \sd \dd \psi, \psi^*)$.
+
+We first collect all terms in equation \eqref{CMEmatter3} proportional to $\phi^*$:
+\[
+\frac{1}{2} (Q_1, \rho(\d\phi) Q_2) + \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
+\]
+
+By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the third term.
+
+Next, we collect all terms in equation \eqref{CMEmatter3} proportional to $\psi^*$:
+\begin{equation}\label{psistar}
+\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1,\partial_i \psi)^A + \frac{1}{2} \sum_i (\rho(e^i) Q_1)(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi.
+\end{equation}
+The first and second terms can be written as:
+\[
+\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1, \partial_i \psi)^A + \frac{1}{2} \sum_i(\rho(e^i)Q_1)(Q_2, \partial_i \psi)^A = \frac{1}{2} \sd \dd \left(Q_2(Q_1, \psi)^A + Q_1(Q_2, \psi)^A\right).
+\]
+Applying Theorem \ref{thm:matter3psi} to $Q_3 = \psi$, this becomes $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\Gamma(Q_1,Q_2) . \psi$ which cancels the third term.
+\end{proof}
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in \Sigma$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)_P) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\end{align*}
+The expression
+$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
+
+\begin{comment}
 \subsection{Supersymmetric matter}
@@
 I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) 
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) %
 %\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
@@
 
-\begin{lemma} 
+\begin{lemma} \label{lem: hyper1}
 One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
@@
 \[
-- \{\d \phi \wedge * \d \phi, \phi^*  (Q, \psi) \} = - 2 \d (Q, \psi) \wedge * \d \phi .
+- \{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = - 2 (\d (Q, \psi) , \d \phi ) .
 \]
@@
 \[
-\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) \d^4 x .
+\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) .
 \]
@@
 \end{equation}
-By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
+By Proposition \ref{prop:cliffordactionproperty3}, the first and second terms can be written as:
 \[
@@
 The expression
-$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
+$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
+\end{comment}
 
@@
 
-\subsection{Supersymmetric twisting}
-
-\pavel{$Q$ denotes both the differential on fields and the supercharge.}
-
-\begin{definition}
-A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{definition}
-
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
-\begin{itemize}
-\item A supercharge $Q$ is \defterm{topological} if $d = n$.
-
-\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
-The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
-
-\begin{definition}
-A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
-
-\begin{definition} \label{def:twisting}
-Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{definition}
+\section{Dimension 10}
+
+The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with a nondegenerate symmetric bilinear pairing.
+There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
+We concentrate on the first case, the second case being identical.
+So, we fix $W_+=\CC$ and $W_- = 0$.
+
+\subsection{$\cN=(1, 0)$ super Yang--Mills theory}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
+Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
+Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
+The vector representation decomposes as
+\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5)\]
+the semi-spin representation $S_+$ decomposes as
+\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
+and the semi-spin representation $S_-$ decomposes as
+\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
+Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
+Under the above decomposition the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
+\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
+
+\vspace{-10pt}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
+\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
+\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
+\end{itemize}
+We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
+
+The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields.
+We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
 
 \begin{prop}
-The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
+Let $(M, \omega)$ be a K\"{a}hler $d$-fold and decompose
+\[\Omega^2(M) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\CC\omega\oplus \Omega^{1, 1}_\perp(M)).\]
+Then
+\begin{enumerate}
+\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\CC\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.
+
+\item For a form $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
+\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
+\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in\CC\omega$ we have
+\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
+\end{enumerate}
 \end{prop}
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{corollary}
+Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
+\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
+\end{corollary}
+
+Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
+The BV action of the twisted theory $S_{BV}$ is then the sum of the following terms:
+\begin{align*}
+S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{anti} &= \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
+I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
+\end{align*}
+
+\begin{thm}
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
+\label{thm:10dholomorphictwist}
+\end{thm}
+\begin{proof}
+First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
+\begin{align*}
+S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+&+ \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
+\end{align*}
+
+Next, we have a term $\int \psi\wedge A_{1, 0}^*$ in the action, i.e.
+$(\psi, A_{1, 0})$ is a BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
+\[
+S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
+\]
+
+The holomorphic Chern--Simons theory has fields $c, A_{0, 1}, B, \tilde{B}, \tilde{A}_{0, 1}, \tilde{c}$ with the BV action
+\[
+S_{CS} = \int \left(c\wedge \ol\dd_{A_{0, 1}} \tilde{A}_{0, 1} + \tilde{B}\wedge F_{0, 2} + \frac{1}{2} B\wedge \ol\dd_{A_{0, 1}} B + \frac{1}{2}[c, c]\tilde{c} + [B, c]\wedge \tilde{B}\right)\Omega
+\]
+Up to a rescaling of the antifields, it coincides with the BV action $S_0$.
+\end{proof}
 
 \begin{remark}
-Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
+A similar claim was previously proved by Baulieu \cite{Baulieu} by adding an auxiliary field to 10d $\mc N=(1, 0)$ super Yang--Mills.
 \end{remark}
 
-\subsection{Dimensional Reduction of Supersymmetric Theories}
-
-Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
-
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
-We have a natural embedding
-\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
-so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
-\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
-where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
-\[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
-We have the following generalization of this statement to supersymmetric theories.
-
-\begin{prop} \label{prop:susydimlred}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
-\end{prop}
-
-\begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
-\end{proof}
-
-The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
-
-\begin{prop}
-Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
-Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
-\end{prop}
-
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
+\section{Dimension 9}
+
+The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
+So, we fix $W = \CC$.
+
+\subsection{$\cN=1$ super Yang--Mills theory}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
+Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
+
+Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+
+\begin{thm}
+The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
+\end{thm}
+\begin{proof}
+By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
+In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
+
+From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
+By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
+\end{proof}
 
@@
 
-In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
+In terms of these component fields, the BV action can be written in the following way.  We will split the BV action up into the BRST action and the antifield action.
 \begin{align*}
@@
 
+\section{Spinors}
+\label{sect:spinors}
+
+\pavel{A bit out of place.}
+
+In this paper we will extensively use the theory of spinors.
+Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
+\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
+Consider a $\ZZ/2$-graded Clifford module $M=M^+\oplus M^-$.
+Denote the Clifford action by $\rho(v)\in\eend(M)$.
+We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
+\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
+for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
+\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
+by
+\begin{equation}
+(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
+\label{eq:Gammaspinorpairing}
+\end{equation}
+
+We have a subset $\Spin(V)\subset \Cl(V)$, so $\Sigma$ and $\Sigma^*$ are representations of the spin group. Moreover, the Clifford action and the maps $\Gamma$ are $\Spin(V)$-equivariant.
+
+We may identify $\wedge^2(V)\rightarrow \so(V)$ via
+\[\omega\mapsto (w\mapsto -2\iota_{(w, -\rangle)} \omega).\]
+This gives rise to an action map
+\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
+of two-forms on spinors.
+
+Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
+\begin{equation}
+q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
+\label{eq:quantizationtwoforms}
+\end{equation}
+
+The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$, so that $\so(V)$-equivariance of $\Gamma$ gives the following.
+
+\begin{prop}
+For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
+\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
+\label{prop:cliffordactionproperty1}
+\end{prop}
+
+We may extend the discussion to the case of Riemannian manifolds $M$, where we replace $V$ by the vector bundle $TM$.
+Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
+\[\sd{\dd}\colon \Gamma(M, \Sigma)\rightarrow \Gamma(M, \Sigma^*).\]
+
+From \eqref{eq:quantizationtwoforms} we get the following property.
+
+\begin{prop}
+Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma)$. Then
+\[\sd{\dd}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\dd} \lambda) Q_2.\]
+\label{prop:cliffordactionproperty2}
+\end{prop}
+
+Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
+
+\begin{prop}
+Suppose $Q\in\Sigma$ and $X\in\Omega^p(M)$. Then
+\[\sd{\dd}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
+\label{prop:cliffordactionproperty3}
+\end{prop}
+
+Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\dd}$ is the corresponding twisted Dirac operator.
+
 \pagestyle{bib}

### 2019-12-29 paper.tex
Added coupling calculation

@@
 
+\newcommand{\BV}{\mathrm{BV}}
 \newcommand{\Cl}{\mathrm{Cl}}
 \newcommand{\Dens}{\mathrm{Dens}}
+\newcommand{\gauge}{\mathrm{gauge}}
+\newcommand{\matter}{\mathrm{matter}}
 \renewcommand{\Re}{\mathrm{Re}}
@@
 We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}).
+An element of $\oloc(\cE)$ will be denoted by
+\[\int_M \omega(\phi, \phi', \dots),\]
+where $\omega$ is a density on $M$ depending on infinite jets of sections of $E$.
+Note, however, that the integral here is a formal symbol.
 We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
@@
 
-We call $\cE$ the \defterm{space of BV fields}.  
-The pairing $\omega$ equips the algebra of local functionals on $E$ with a shifted bracket, in the following way.
-In \cite[Chapter 5, Section 3]{CostelloBook}, it is shown that to every functional $f \in \oloc(\cE)$ there exists a symplectic vector field $X_f$ on $\cE$ whose Hamiltonian function is $f$.
-Note that if $f$ is degree $n$, then $X_f$ is of degree $n+1$ due to the degree of $\omega$.
-
-\begin{definition}
-The \defterm{BV bracket} $\{-,-\}$ is the bilinear map of cohomological degree $+1$
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE)
-\]
-defined by sending a pair $(f,g)$ to the local functional $X_f (g)$.
-\end{definition}
-
-\begin{remark}
-Note that the BV bracket in fact defines a bilinear map $\{-, -\}\colon \oloc(\cE)\times\cO(\cE)\rightarrow \cO(\cE)$. However, it does \emph{not} define a bracket on $\cO(\cE)$ itself.
-\end{remark}
+We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook})
+\[
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE).
+\]
 
@@
 \[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
-and the graded Jacobi identity. Note that since local functionals do not form an algebra, it is not a (shifted) Poisson bracket.
+and the Leibniz rule
 
@@
 
-A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all functionals $\cO(E)$.
-The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
-\begin{equation}\label{bvcplx}
-\left(\cO(\cE), Q + \{I,-\}\right) .
-\end{equation}
-In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
-We will refer to this as the {\em classical BV complex} of the theory.
-
 \begin{definition}
@@
 \end{definition}
-
-For a short background on homological algebra with differentiable pro-cochain complexes, including the notion of quasi-isomorphism, we refer to Appendix \ref{appx: top}.
-For a more thorough introduction, and for which our conventions are based on, we refer to \cite{Book1}.
 
@@
 
-\item For every $x\in\fg$, the vctor field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\item For every $x\in\fg$, the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{itemize}
@@
 \subsection{The Classical Factorization Algebra}
+
+\pavel{Is this section needed?}
 
@@
 In this section we give some examples of classical field theories we will use.
-All theories we consider in this section except for the Yang--Mills theory are $\ZZ$-graded, i.e.
+All theories we consider in this section are $\ZZ$-graded, i.e.
 all fields are considered even with respect to the $\ZZ/2$-grading.
@@
 \end{example}
-
-\subsubsection{Yang--Mills Theory with Spinorial Matter} \label{YM_section}
-
-Let us now give an example of a theory which is not partially holomorphic.
-We will give a general description of the Yang--Mills theory on a vector space $V_\RR = \RR^n$ with adjoint spinorial matter.
-Denote by $V=V_\RR\otimes_\RR \CC$ its complexification.
-
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a Clifford module $\Sigma\oplus \Sigma^*$ as in Section \ref{sect:spinors}.
-The fields of the Yang--Mills theory are as follows:
-\begin{itemize}
-\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
-
-\item A section $\lambda \in \Omega^0(V_\RR; \Pi \Sigma \otimes \fg)$.
-
-\item The ghost field $c\in\Omega^0(V_\RR; \fg)[1]$.
-\end{itemize}
-
-Thus, the bundle of BRST fields is
-\[F = (\Omega^1(V_\RR)\oplus \Omega^0(V_\RR; \Pi\Sigma)\oplus \Omega^0(V_\RR)[1])\otimes \fg.\]
-The corresponding local super dg Lie algebra $L=F[-1]$ is
-\[
-L \;\;\; = \begin{array}{ccccc}
-& \ul{0} & & \ul{1} & \\ 
-& & & & \\
-& \Omega^0(V_\RR; \gg) & \to & \Omega^1(V_\RR; \gg) \oplus \Omega^0(V_\RR; \Pi \Sigma \otimes \gg) & 
-\end{array}
-\]
-whose differential is the de Rham differential $\Omega^0(V_\RR; \gg)\rightarrow \Omega^1(V_\RR; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.
-
-Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).
-
-The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd \dd_A \lambda)\right\rangle.\]
-
-The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}).
-Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively.
-The bundle of BV fields is
-\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
-The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\begin{equation}
-S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd\dd_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).
-\label{eq:YMBVaction}
-\end{equation}
-
-We conclude this section with a discussion of the Poincar\'e invariance of classical Yang--Mills theory.
-
-\begin{definition}
-The \defterm{Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The \defterm{Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
-\end{definition}
-
-The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
-Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
-The corresponding Hamiltonian is given by
-\begin{equation}
-I^{(1)}(v) = \int_{V_\RR} -(L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*,
-\label{eq:Poincareaction}
-\end{equation}
-for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
-
-\subsubsection{The free scalar and free fermion}
-
-\brian{does this warrant it's own definition?}
 
@@
 
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the Poincar\'{e} group which acts in the obvious way on $M$.
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
 
@@
 
-\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$. \pavel{Moment maps?}
+\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
 
@@
 
-\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
+\subsection{Pure super Yang--Mills theory}
+\label{sect:gaugemultipletSUSY}
+
+We begin with a description of the pure minimally supersymmetric Yang--Mills theories in dimensions 3, 4, 6 and 10.
 
 Fix an \emph{alternative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
-We will show that in this case the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
-
-We will construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
+Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing.
+The fields of the Yang--Mills theory are as follows:
+\begin{itemize}
+\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
+
+\item A spinor $\lambda \in \Gamma(V_\RR; \Pi \Sigma \otimes \fg)$.
+
+\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
+\end{itemize}
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
+
+Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Section \ref{sect:spinors}).
+
+The BRST action is given by
+\[S(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+
+We introduce the gauge transformations
+\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\]
+so that the BV action is given by
+\begin{equation}
+S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
+\label{eq:YMBVaction}
+\end{equation}
+
+To simplify the notation, the pairing on $\fg$ from now on will be implicit.
+
+The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
+Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
+The corresponding Hamiltonian is given by
+\begin{equation}
+I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
+\label{eq:YMPoincareaction}
+\end{equation}
+for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
+
+We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
+The action of supersymmetry is given by a linear and quadratic functionals
+\begin{align*}
+I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
+I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
+\end{align*}
 
 \begin{thm}
-The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
-\brian{Where is the Poincare part?}
-\begin{align*}
-I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
-I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
-\end{align*}
-satisfies the classical master equation
-\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
-\label{thm:vectormultipletSUSY}
-\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
-\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)}$ satisfies the classical master equation
+\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
+\label{thm:gaugemultipletSUSY}
 \end{thm}
 
-The rest of the section will be devoted to the proof of the above theorem.
-
-The following properties of the Clifford action will be useful.
-Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
-
-We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
-\begin{align*}
-\{S_{BV}, I^{(1)}\} &= 0 \\
-\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
-\{I^{(2)}, I^{(2)}\} &= 0.
-\end{align*}
-
-Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$.
+The rest of the section will be devoted to the proof of the above theorem. The classical master equation decomposes into the following equations:
+\begin{align*}
+\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
+\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
+\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
+\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
+\end{align*}
+
+Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
 The rest of the claims will be proved in a sequence of Lemmas.
-To simplify the expressions, we drop the integrals and omit the natural pairings.
+To simplify the expressions, we drop the integrals.
 
 \begin{lemma}
-One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
+One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
+\label{lm:gaugemultiplet1}
 \end{lemma}
 \begin{proof}
-Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.
+Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.
 
@@
 \begin{align*}
-\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
-&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
-&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
-&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
+\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
+&= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
 \end{align*}
@@
 \begin{align*}
-\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\dd}_A\lambda) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\dd}_A(\rho(F_A) Q)) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
+\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast \d_A\ast F_A) Q),
 \end{align*}
@@
 
-By \eqref{eq:Gammaspinorpairing} and Theorem \ref{thm:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
-
-The third term gives
-\begin{align*}
-\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
-&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
-\end{align*}
-
-The fourth term gives
-\begin{align*}
-\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
-\end{align*}
-
-Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
+By \eqref{eq:Gammaspinorpairing} and Theorem \ref{thm:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
+
+Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
 \end{proof}
@@
 \begin{remark}
-The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
+The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; our proof essentially follows \cite{BaezHuerta}.
 \end{remark}
@@
 One has
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
+\label{lm:gaugemultiplet2}
 \end{lemma}
@@
 Evaluating the equation
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
-on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
+on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
@@
 \begin{align*}
-\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
-= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
-&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
-\end{align*}
-\begin{align*}
-(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
-&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
+\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
+= &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
+&-\frac{1}{2}(\rho(\d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) + \frac{1}{2}(\Gamma(Q_1, \rho(F_A)Q_2), A^*),
+\end{align*}
+\begin{align*}
+(\d_{CE} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
 \end{align*}
@@
 \begin{align*}
-\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\dd}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\dd}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\dd}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
+\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
 &+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
@@
 The total coefficient in front of $A^*$ is
-\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
-Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
+\[\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) + \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) + L_{\Gamma(Q_1, Q_2)} A - \d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
+Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $-\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
 
 The total coefficient in front of $c^*$ is
-\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
+\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
 
@@
 \begin{align*}
-&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
-&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\dd}_A\lambda - \frac{1}{2}(Q_2, \sd{\dd}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\dd}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
+&-\frac{1}{2}\rho(\d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(\d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
+&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\d}_A\lambda - \frac{1}{2}(Q_2, \sd{\d}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\d}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
 \end{align*}
 Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
-\[-\frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{\dd}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Theorem \ref{thm:3psi}. Using the Clifford relation this term cancels the rest of the terms.
+\[-\frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
+which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Theorem \ref{thm:3psi}. Using the Clifford relation this term cancels the rest of the terms.
 \end{proof}
@@
 Evaluating the equation
-\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
+\[\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
 on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
 
 \begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in\Sigma$.
+\label{lm:gaugemultiplet3}
 \end{lemma}
@@
 \begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
-&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
-\end{align*}
-
-$\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
+\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+&+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
+\end{align*}
+
+$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
 By Theorem \ref{thm:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
@@
 \subsection{Matter multiplet}
+\label{sect:mattermultipletSUSY}
 
@@
 \[(av, w) = (v, \sigma(a)w).\]
-Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
-\begin{itemize}
-\item $A_\RR=\RR$, so $A=\CC$. We are looking for a complex vector space $P$ equipped with a nondegenerate symmetric bilinear pairing.
+Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
+\begin{itemize}
+\item $A_\RR=\RR$, so $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.
 
@@
 So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$.
-In other words, the data boils down to a complex vector space $R$, so that $P = R\oplus R^*$.
+In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.
 
@@
 Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
-So, the data boils down a complex symplectic vector space $U$.
+So, the data boils down a symplectic $\fg$-representation $U$.
 \end{itemize}
@@
 \end{itemize}
-As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
+As usual, we denote the antifields by $\phi^*\in\Gamma(V_\RR; \Pi P)$ and $\psi^*\in\Gamma(V_\RR; \Sigma\otimes_A P)$.
 
@@
 where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
-\[\Gamma_P\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
+\[\Gamma\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
 defined by the property
-\[(v, \Gamma_P(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
-
-The action for the matter multiplet is
-\[
-S = \int_{V_\RR} -\frac{1}{2}  (\d \phi \wedge * \d \phi) + \frac{1}{2} (\psi , \sd \dd \psi)\dvol,
+\[(v, \Gamma(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
+
+The BV action for the matter multiplet is
+\[
+S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
 \]
@@
 
+It is Poincar\'{e}-invariant with the corresponding Hamiltonian
+\begin{equation}
+I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
+\label{eq:matterPoincareaction}
+\end{equation}
+for $v\in\mf{iso}(V)$.
+
 The action of supersymmetry is given by a linear and quadratic functional:
 \begin{align*}
-I^{(1)} (Q) & = \int (\phi^*, (Q, \psi)) - (\psi^*, \rho(\d \phi) Q) \\
-I^{(2)} (Q_1 , Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)_P) \end{align*}
+I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \\
+I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*))
+\end{align*}
 where $Q, Q_1,Q_2 \in \Sigma$.
 
-The following result states that these functionals encode an off-shell action of the supersymmetry on the matter multiplet.
+We consider the full action of the super Yang--Mills theory
+\[S_{\BV} = S_{\gauge} + S_{\matter}\]
+together with a supersymmetry action functionals
+\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]
+
+The following result states that these functionals encode an off-shell action of the supersymmetry algebra.
 
 \begin{thm}
-The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
-\begin{equation}\label{CMEmatter}
-\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
+\begin{equation}
+\label{CMEYM}
+\d_{CE} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
 \end{equation}
+\label{thm:YMSUSY}
 \end{thm}
 
-We decompose the classical master equation \eqref{CMEmatter} into the following equations:
-\begin{equation}\label{CMEmatter2}
+The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
+\begin{equation}
+\label{CMEYM2}
 \begin{array}{rrrrrr}
-\{S , I^{(1)}\} & = & 0 \\ 
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
-\{I^{(2)}, I^{(2)}\} & =& 0
+\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
+\d_{CE} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
+\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
 \end{array}
@@
 
-The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
-
-The first equation in \eqref{CMEmatter2} states that the classical action for the matter multiplet is supersymmetric.
-
-\begin{lemma} \label{lem: matter1}
-One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
+
+The first equation in \eqref{CMEYM2} states that the classical action is supersymmetric.
+
+\begin{lemma} \label{lem:YM1}
+One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
 \end{lemma}
 \begin{proof}
-Observe
-\[
-\{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = 2 (\d (Q, \psi) , \d \phi ) .
-\]
-and
-\[
-\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2(\psi, \sd \dd \rho(\d \phi) Q).
-\]
-
-By Proposition \ref{prop:cliffordactionproperty3} $\sd \dd\rho(\d\phi) Q = (\d^* \d\phi) Q$. Therefore,
-\[2(\psi, \sd \dd \rho(\d \phi) Q) = 2(\d^*\d\phi)(\psi, Q) = -2(\d\phi, \d(\psi, Q))\]
-which cancels the first term.
-\end{proof}
-
-Next, we move on to the second equation in \eqref{CMEmatter2}.
+Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.
+
+The first term gives
+\begin{align*}
+\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
+&= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
+\end{align*}
+
+The second term gives
+\begin{align*}
+\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
+&= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
+\end{align*}
+where we have used Proposition \ref{prop:cliffordactionproperty3} in the second line.
+
+The third term gives
+\begin{align*}
+\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
+&= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
+\end{align*}
+where we have used Theorem \ref{thm:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
+\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
+
+Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
+\end{proof}
+
+Next, we move on to the second equation in \eqref{CMEYM2}.
 
@@
 One has
-\begin{equation}\label{CMEmatter3}
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\begin{equation}\label{CMEYM3}
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
 \end{equation}
@@
 \begin{proof}
-Evaluating expression \eqref{CMEmatter3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action.
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
@@
 \begin{align*}
-\frac{1}{2}\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &\phi^* (Q_1, \rho(\d \phi) Q_2) + \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  + (\psi^*, \rho(\d(Q_1,\psi))Q_2) + (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
-\end{align*}
-
-\begin{align*}
-(\d_{CE}I^{(1)})(Q_1,Q_2) = &-\phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
-\end{align*}
+\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
+=&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
+\end{align*}
+
+\begin{align*}
+\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
+=& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
+\end{align*}
+
+\[
+(\d_{CE}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+\]
 
 and
-\begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi)_P
-\end{align*}
-Note that we can rewrite this as $\frac{1}{2} (\rho(\Gamma(Q_1, Q_2)) \sd \dd \psi, \psi^*)$.
-
-We first collect all terms in equation \eqref{CMEmatter3} proportional to $\phi^*$:
-\[
-\frac{1}{2} (Q_1, \rho(\d\phi) Q_2) + \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
-\]
-
-By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the third term.
-
-Next, we collect all terms in equation \eqref{CMEmatter3} proportional to $\psi^*$:
+\[
+\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
+\]
+
+We first collect all terms in equation \eqref{CMEYM3} proportional to $\phi^*$:
+\[
+-\frac{1}{2} (Q_1, \rho(\d_A\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d_A \phi) Q_1) + L_{\Gamma(Q_1,Q_2)} \phi + (\iota_{\Gamma(Q_1, Q_2)} A)\phi.
+\]
+
+By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the last two terms.
+
+Next, we collect all terms in equation \eqref{CMEYM3} containing $\psi^*$ and $\psi$:
 \begin{equation}\label{psistar}
-\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1,\partial_i \psi)^A + \frac{1}{2} \sum_i (\rho(e^i) Q_1)(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi.
+\frac{1}{2} \sd \d_A Q_2(Q_1 \psi)^A + \frac{1}{2} \sd \d_A Q_1(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \d_A \psi - (\iota_{\Gamma(Q_1, Q_2)} A)\psi.
 \end{equation}
-The first and second terms can be written as:
-\[
-\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1, \partial_i \psi)^A + \frac{1}{2} \sum_i(\rho(e^i)Q_1)(Q_2, \partial_i \psi)^A = \frac{1}{2} \sd \dd \left(Q_2(Q_1, \psi)^A + Q_1(Q_2, \psi)^A\right).
-\]
-Applying Theorem \ref{thm:matter3psi} to $Q_3 = \psi$, this becomes $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
-Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\Gamma(Q_1,Q_2) . \psi$ which cancels the third term.
+Applying Theorem \ref{thm:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\iota_{\Gamma(Q_1,Q_2)}\d_A \psi$ which cancels the remaining terms.
 \end{proof}
@@
 \begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in \Sigma$.
@@
 \begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)_P) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
 \end{align*}
 The expression
-$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
-
-\begin{comment}
-\subsection{Supersymmetric matter}
-
-\subsubsection{The 4d $\cN=1$ chiral multiplet}
-
-\subsubsection{The 6d $\cN=(1, 0)$ hypermultiplet}
-
-In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(6; \CC)$. 
-The spinorial representation we will be interested in is $\Sigma = S_+ \otimes W_+$, where $\dim_{\CC}(W_+) = 2$ is a two-dimensional multiplicity space. 
-To define the half hyper multiplet we fix a complex, symplectic vector space $U$ whose symplectic form we call $\omega_U$.
-We combine the symplectic forms $\omega_U, \omega_{W_+}$ to define a pairing 
-\[
-(-,-)_{W_+ \otimes U}  := \omega_{W_+} \otimes \omega_U : (W_+ \otimes U)^{\otimes 2} \to \CC .
-\]
-The spinorial pairing $(-,-) : S_+ \otimes S_- \to \CC$ together with the obvious symplectic form $\omega_{W_+}$ on $W_+$, and the symplectic form $\omega_U$ on $U$ induces a pairing (that we denote by the same symbol)
-\[
-(-,-)_U : (S_\pm \otimes U) \otimes (S_\mp \otimes U) \to \CC .
-%(-,-)_U : (S_\pm \otimes W_+ \otimes U)^{\otimes 2} \to \CC  
-\]
-
-\begin{remark}
-The terminology ``half" hyper multiplet is to be consistent with the terminology in the physics literature. 
-The (full) hyper multiplet refers to a multiplet which depends on the choice of a (not necessarily symplectic) vector space $R$. 
-The relationship between the two is obtained by looking at the cotangent space $U = T^*R$.
-That is, the half hyper multiplet with values in the symplectic vector space $U = T^* R$ (with its obvious symplectic structure) is the (full) hyper multiplet for $R$. 
-\end{remark}
-
-The field content for the 6-dimensional half hyper multiplet with values in $U$ is:
-\begin{itemize}
-\item a scalar valued in $W_+ \otimes U$; $\phi \in C^\infty(\RR^4 ; W_+ \otimes U)$;
-\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
-\end{itemize}
-
-The space of BRST fields is thus
-\[
-F = C^\infty(\RR^4 ; W_+ \otimes U \oplus S_- \otimes U) .
-\]
-
-The BRST action is
-\[
-S (\phi, \psi) = \int_{\RR^4} - \frac{1}{2}  (\d \phi \wedge * \d \phi)_{W_+ \otimes U} + \frac{1}{2} (\psi , \sd \dd \psi)_U .
-\]
-As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
-
-The action of supersymmetry is given by a linear and quadratic functional:
-\begin{align*}
-I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) %
-%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
-\end{align*}
-where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
-We point out some conventions in the definition of $I^{(2)}$. 
-Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
-\[
-\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
-\]
-
-In order to prove the hypermultiplet is supersymmetric, we will need to following proposition about $6$-dimensional spinor representations.
-
-\begin{prop}\label{prop: new3psi}
-Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
-Then
-\[
-(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
-\]
-\end{prop}
-
-%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
-%\[
-%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
-%\]
-%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
-%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
-
-The following result states that these functionals encode an off-shell action of six-dimensional $\cN=(1,0)$ supersymmetry on the half hypermultiplet valued in $U$. 
-The proof is very similar to the case of the four-dimensional $\cN=1$ chiral multiplet.
-
-\begin{thm}
-The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
-\begin{equation}\label{CMEhyper}
-\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
-\end{equation}
-\end{thm}
-
-We decompose the classical master equation (\ref{CMEhyper}) into the following equations:
-\begin{equation}\label{CMEhyper2}
-\begin{array}{rrrrrr}
-\{S , I^{(1)}\} & = & 0 \\ 
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
-\{I^{(2)}, I^{(2)}\} & =& 0
-\end{array}
-\end{equation}
-
-The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
-
-The first equation in (\ref{CMEhyper2}) states that the classical action for the chiral multiplet is supersymmetric.
-
-\begin{lemma} \label{lem: hyper1}
-One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
-\end{lemma}
-\begin{proof}
-Observe
-\[
-- \{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = - 2 (\d (Q, \psi) , \d \phi ) .
-\]
-and
-\[
-\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) .
-\]
-The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
-\end{proof}
-
-Next, we move on to the second equation in (\ref{CMEhyper2}).
-
-\begin{lemma} 
-One has
-\begin{equation}\label{CMEhyper3}
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
-\end{equation}
-\end{lemma}
-\begin{proof}
-Evaluating expression (\ref{CMEhyper3}) on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
-So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
-
-The individual terms are:
-\begin{align*}
-\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  -  (\psi^*, \rho(\d(Q_1,\psi))Q_2) - (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
-\end{align*}
-
-\begin{align*}
-(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
-\end{align*}
-
-and
-\begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) 
-% \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
-\end{align*}
-Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.
-
-We first collect all terms in Equation (\ref{CMEhyper3}) proportional to $\phi^*$:
-\[
-- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
-\]
-By the Clifford identity
-\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term.
-
-Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
-\begin{equation}\label{psistar}
-\begin{array}{cccc}
-& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
-\\ 
-& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
-%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
-\end{array}
-\end{equation}
-By Proposition \ref{prop:cliffordactionproperty3}, the first and second terms can be written as:
-\[
-- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
-\]
-Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
-Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
-So the expression (\ref{psistar}) is identically zero. 
-\end{proof}
-
-\begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in \Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
-\end{align*}
-The expression
-$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
-\end{comment}
-
-\subsection{Supersymmetric couplings}
+$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
 
@@
 The vector representation decomposes as
-\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5)\]
+\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5),\]
 the semi-spin representation $S_+$ decomposes as
@@
 S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{anti} &= \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+S_{anti} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
 I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
@@
 S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
 &+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
@@
 \[
-S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
-\]
-
-The holomorphic Chern--Simons theory has fields $c, A_{0, 1}, B, \tilde{B}, \tilde{A}_{0, 1}, \tilde{c}$ with the BV action
-\[
-S_{CS} = \int \left(c\wedge \ol\dd_{A_{0, 1}} \tilde{A}_{0, 1} + \tilde{B}\wedge F_{0, 2} + \frac{1}{2} B\wedge \ol\dd_{A_{0, 1}} B + \frac{1}{2}[c, c]\tilde{c} + [B, c]\wedge \tilde{B}\right)\Omega
-\]
-Up to a rescaling of the antifields, it coincides with the BV action $S_0$.
+S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
+\]
+Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
 \end{proof}
@@
 \subsection{Dimension 10}
-We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:vectormultipletSUSY}.
+We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:gaugemultipletSUSY}.
 In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
@@
 
-\pavel{A bit out of place.}
-
 In this paper we will extensively use the theory of spinors.
@@
 Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
-\[\sd{\dd}\colon \Gamma(M, \Sigma)\rightarrow \Gamma(M, \Sigma^*).\]
+\[\sd{\d}\colon \Gamma(M, \Sigma)\rightarrow \Gamma(M, \Sigma^*).\]
 
@@
 Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma)$. Then
-\[\sd{\dd}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\dd} \lambda) Q_2.\]
+\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
 \label{prop:cliffordactionproperty2}
@@
 Suppose $Q\in\Sigma$ and $X\in\Omega^p(M)$. Then
-\[\sd{\dd}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
+\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
 \label{prop:cliffordactionproperty3}
@@
 
-Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\dd}$ is the corresponding twisted Dirac operator.
+Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\d}$ is the corresponding twisted Dirac operator.
 

### 2020-01-02 paper.tex
Responding to Pavel's edits

@@
 
+\part{Supersymmetric Gauge Theory}
+
 \section{The BV-BRST Formalism}
@@
 where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
 \label{prop:integrateoutfield}
 \end{prop}
-\begin{proof}
-\pavel{The map $E_0\rightarrow E$ is obviously compatible with all the structures.}
+
+\begin{proof}
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
+Then we define the required perturbative equivalence as follows.
+First $F_1(e) = (e, Q_1(e), 0) \in E$.
+Then, for $n > 1$, define
+\begin{align*}
+F_n \colon \sym^n(E_0) &\to E \\
+e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
+\end{align*}
+These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
+\begin{align*}
+S(F(e)) &= S(e, S_1(e), 0) \\
+&= S_0(e) + \frac 12 \dvol_M \int S_1(e)^2 - 2 S_1(e)^2) \\
+&= S_0(e) - \frac 12 S_1(e)^2 \\
+&= S'(e).
+\end{align*}
+Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
 \end{proof}
@@
 \begin{prop}
-Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus F\oplus F^![-1]\oplus F^!\oplus F[-1]$.
-Denote by $\phi, \phi^*$ sections of $F,F^![-1]$ and by $\psi, \psi^*$ sections of $F^!, F[-1]$.
+Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q\phi + \{I, \phi\} = \psi - F_\psi,\qquad Q\psi^* + \{I, \psi^*\} = \phi^* - F_{\phi^*},\]
-where $F_\psi$ is independent of $\psi$ and $F_{\phi^*}$ is independent of $\phi^*$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = 0, \phi^* = F_{\phi^*}, \psi = F_\psi, \psi^* = 0$ in the original BV action.
+\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
 \label{prop:BRSTdoublet}
 \end{prop}
-\begin{proof}
+
+\begin{proof}
+Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
+We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
+\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
+Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
+Also, by construction, the $F_n$ intertwine the action functionals, since
+\begin{align*}
+S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
+&= S_0(e).
+\end{align*}
+Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
 \end{proof}
@@
 
-\pavel{Is this section needed?}
+\pavel{Is this section needed?} \chris{something is needed if we want to connect to the story from our previous paper: we'd like to say that all of these twisted SUSY field theories (or rather, the topological ones) produce $\bb E_n$ algebras, no?
+Certainly not all of them are interesting.
+I don't know whether we need the section here, but we would like to say something somewhere.}
 
@@
 \subsection{Twisting Homomorphisms and Curved Backgrounds}
+
+\subsection{A-Type Twists} \label{A_twist_section}
+\chris{...}
 
@@
 
+\part{A Catalogue of Twists}
+
 \section{Dimension 10}
@@
 \end{itemize}
-
-\subsubsection{Holomorphic twist}
 
@@
 
-\subsubsection{Holomorphic twist}
-
 We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
@@
 \end{proof}
-
-\section{Twists}
 
@@
 
-\subsection{Standard Equivalences Between Classical Field Theories}
-In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
-
-\begin{lemma} \label{symplectomorphism_lemma}
-A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
-\end{lemma}
-
-\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
+% \subsection{Standard Equivalences Between Classical Field Theories}
+% In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
+% 
+% \begin{lemma} \label{symplectomorphism_lemma}
+% A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
+% \end{lemma}
+% 
+% \brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
 In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
-
-\begin{lemma} \label{inclusion_and_projection_lemma}
-Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
-\begin{enumerate}
- \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
+% 
+% \begin{lemma} \label{inclusion_and_projection_lemma}
+% Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
+% \begin{enumerate}
+%  \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
 Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
- \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
+%  \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
 Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
-\end{enumerate}
-\end{lemma}
-
-\begin{lemma} \label{symplectic_composite_lemma}
-Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
+% \end{enumerate}
+% \end{lemma}
+% 
+% \begin{lemma} \label{symplectic_composite_lemma}
+% Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
 Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
 Then the cochain map
-\begin{equation}
-\label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
-\end{equation}
-obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
-\end{lemma}
-
-\begin{lemma} \label{interaction_pullback_lemma}
-In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
+% \begin{equation}
+% \label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
+% \end{equation}
+% obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
+% \end{lemma}
+% 
+% \begin{lemma} \label{interaction_pullback_lemma}
+% In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
 Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
 Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
-\end{lemma}
-
-\begin{proof}
-We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
+% \end{lemma}
+% 
+% \begin{proof}
+% We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
 Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
-\end{proof}
-
-\subsection{A-Type Twists} \label{A_twist_section}
-\chris{...}
-
-\subsection{Dimension 10}
-We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:gaugemultipletSUSY}.
+% \end{proof}
+% 
+% \subsection{A-Type Twists} \label{A_twist_section}
+% \chris{...}
+% 
+% \subsection{Dimension 10}
+% We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:gaugemultipletSUSY}.
 In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
 These square-zero supercharges are holomorphic.
-
-Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
+% 
+% Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
 The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
@@
 The BRST fields split as follows:
-\begin{align*}
-c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
-A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
-\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
-\end{align*}
-
-In terms of these component fields, the BV action can be written in the following way.  We will split the BV action up into the BRST action and the antifield action.
-\begin{align*}
-S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
-S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
-\end{align*}
-where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
+% \begin{align*}
+% c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
+% A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
+% \lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
+% \end{align*}
+% 
+% In terms of these component fields, the BV action can be written in the following way.  We will split the BV action up into the BRST action and the antifield action.
+% \begin{align*}
+% S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
+% S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
+% \end{align*}
+% where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
 Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
 It has a quadratic and a cubic component given by
-\begin{align*}
-I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
-I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
-\end{align*}
-The twisted action functional is obtained by adding these terms to the original BV action functional.
-
-We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
-
-\begin{theorem}\label{10d_twist_thm}
-The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
-\end{theorem}
-
-\begin{remark}
-From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
-\end{remark}
-
-\begin{proof}
-We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
-
-\begin{enumerate}
- \item The first part of our equivalence of classical field theories will be a simple change of variables.
+% \begin{align*}
+% I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
+% I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
+% \end{align*}
+% The twisted action functional is obtained by adding these terms to the original BV action functional.
+% 
+% We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
+% 
+% \begin{theorem}\label{10d_twist_thm}
+% The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
+% \end{theorem}
+% 
+% \begin{remark}
+% From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+% As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
+% \end{remark}
+% 
+% \begin{proof}
+% We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
+% 
+% \begin{enumerate}
+%  \item The first part of our equivalence of classical field theories will be a simple change of variables.
 Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
 In terms of $\chi'$, the quadratic part of the twisted action functional becomes
- \begin{align*}
-  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
-  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
- \end{align*}
- The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
+%  \begin{align*}
+%   S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
+%   &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
+%  \end{align*}
+%  The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
 However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
@@
 We think of this as ``integrating out'' the field $\chi'$ and its antifield.
-
- \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
+%  
+%  \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
 We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
- \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
+%  \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
+%  We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
 This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
@@
 Can we fix it?}
-
- Observe that the classical BV complex associated to this action functional can now be written in the following form:
- \[\xymatrix{
- &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
- \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
- \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
- }\]
- where the first and third rows are dual under the symplectic pairing.
+%  
+%  Observe that the classical BV complex associated to this action functional can now be written in the following form:
+%  \[\xymatrix{
+%  &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
+%  \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
+%  \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
+%  }\]
+%  where the first and third rows are dual under the symplectic pairing.
 This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
 the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
-
- \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
+%  
+%  \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
 The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
@@
 The resulting interaction is
- \[
-  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
- \]
- which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
+%  \[
+%   I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
+%  \]
+%  which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
 The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
-
- \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
+%  
+%  \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
 The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
@@
 an equivalence of classical field theories.
-\end{enumerate}
-\end{proof}
-
-The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-\brian{How do we place 10d YM on an arbitrary 5-fold? 
-Are you using something about sugra?
-} \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
+% \end{enumerate}
+% \end{proof}
+% 
+% The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+% \brian{How do we place 10d YM on an arbitrary 5-fold? 
+% Are you using something about sugra?
+% } \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
 I'm not thinking of using sugra.
@@
 Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
-
-\subsection{Dimension 9}
-The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
+% 
+% 
+% \subsection{Dimension 9}
+% The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
 It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.
-
-There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
+% 
+% There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
 Such supercharges are minimal (i.e.
@@
 Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.
-
-Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
+% 
+% Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
 The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.
 These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
-\begin{align*}
-B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
-A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
-\end{align*}
-along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
-
-\brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
-
-\begin{theorem} \label{9d_twist_thm}
-The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-\end{theorem}
-
-\begin{proof}
-Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
+% \begin{align*}
+% B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
+% A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
+% \end{align*}
+% along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
+% 
+% \brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
+% 
+% \begin{theorem} \label{9d_twist_thm}
+% The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
+% \end{theorem}
+% 
+% \begin{proof}
+% Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
 Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.
 According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.
-
-As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
-\end{proof}
-
-\begin{remark}
-One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
-\end{remark}
-
-\subsection{Dimension 8}
+% 
+% As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
+% \end{proof}
+% 
+% \begin{remark}
+% One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
+% \end{remark}
+
+\section{Dimension 8}
 \vspace{-10pt}
@@
 
-\subsection{Dimension 7} \label{7d_section}
+\section{Dimension 7} \label{7d_section}
 The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
@@
 
-\subsection{Dimension 6}
+\section{Dimension 6}
 In dimension 6 there are two possible supersymmetry groups by which we can act.
@@
 
-\subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
-
-\subsubsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
+\subsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
+
+\subsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
 
@@
 
-We already considered the holomorphic twist in the previous subsection.
+We already considered the holomorphic twist in the previous section.
 The remaining three classes are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
@@
 
-\subsection{Dimension 5}
+\section{Dimension 5}
 The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.
@@
 
-\subsubsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
+\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
 We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
@@
 
-\subsubsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}
+\subsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}
 
@@
 \begin{enumerate}
- \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous subsection.
+ \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous section.
  \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
@@
 
-\subsection{Dimension 4}
+\section{Dimension 4}
 
@@
 
-\subsubsection{$\cN=1$ with chiral multiplet matter}
+\subsection{$\cN=1$ with chiral multiplet matter}
 There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
@@
 
-\subsubsection{$\cN=2$ SYM with hypermultiplet matter}
+\subsection{$\cN=2$ SYM with hypermultiplet matter}
 %quaternionic is hyperkahler
@@
 
-\subsubsection{$\cN=4$ SYM}
+\subsection{$\cN=4$ SYM}
 
@@
 %\]
-%\subsection{Dimension 3}
+%\section{Dimension 3}
 
@@
 
-\subsection{Dimension 2}
+\section{Dimension 2}
 

### 2020-01-02 paper.tex
merge

--- 2019-12-27 paper.tex
@@
 \newcommand{\Dens}{\mathrm{Dens}}
-\renewcommand{\Re}{\mathrm{Re}}
 
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q e_1) = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
-A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory.
+A morphism is an \defterm{equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
 \end{definition}
@@
 For a more thorough introduction, and for which our conventions are based on, we refer to \cite{Book1}.
-
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
-First, we consider the process of integrating out an auxiliary field.
-
-\begin{prop}
-Fix a volume form $\dvol_M$ on $M$.
-Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
-Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
-Suppose the BV action is
-\[S_{BV} = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
-where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
-\label{prop:integrateoutfield}
-\end{prop}
-\begin{proof}
-\pavel{The map $E_0\rightarrow E$ is obviously compatible with all the structures.}
-\end{proof}
-
-We may also remove a trivial BRST doublet.
-
-\begin{prop}
-Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus F\oplus F^![-1]\oplus F^!\oplus F[-1]$.
-Denote by $\phi, \phi^*$ sections of $F,F^![-1]$ and by $\psi, \psi^*$ sections of $F^!, F[-1]$.
-Suppose
-\[Q\phi + \{I, \phi\} = \psi - F_\psi,\qquad Q\psi^* + \{I, \psi^*\} = \phi^* - F_{\phi^*},\]
-where $F_\psi$ is independent of $\psi$ and $F_{\phi^*}$ is independent of $\phi^*$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = 0, \phi^* = F_{\phi^*}, \psi = F_\psi, \psi^* = 0$ in the original BV action.
-\label{prop:BRSTdoublet}
-\end{prop}
-\begin{proof}
-\end{proof}
 
@@
 Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
-The BV complex can be thought of as the complex of functions on the derived critical locus of the BRST action.
+The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
 It makes sense to restrict fields to any open set $U \subset M$. 
-Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the BRST action where we restrict the theory to $U$.
+Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.
 
@@
 
-Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a Clifford module $\Sigma\oplus \Sigma^*$ as in Section \ref{sect:spinors}.
-The fields of the Yang--Mills theory are as follows:
+Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$.
+We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
+\begin{equation}
+(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
+\label{eq:Gammaspinorpairing}
+\end{equation}
+for any $Q_1, Q_2\in\Sigma$ and $v\in V$.
+
+The fields of Yang--Mills theory are as follows:
 \begin{itemize}
@@
 The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd \dd_A \lambda)\right\rangle.\]
+\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]
 
@@
 The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
-\begin{equation}
-S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd\dd_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).
-\label{eq:YMBVaction}
-\end{equation}
+\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]
 
@@
 \end{proof}
-
-\begin{remark}
-Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
-\end{remark}
 
@@
 
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+Let $V_\RR = \RR^n$ endowed with its nondegenerate bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
 \begin{itemize}
@@
 
-\subsection{Division algebras and supersymmetry}
-\label{sect:divisionalgebras}
-
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and division algebras. Our treatment will essentially follow \cite{BaezHuerta}.
-
-Let $A_\RR$ be a (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
+
+For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
+In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
+\begin{itemize}
+ \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
+ \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
+ \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
+ \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
+\end{itemize}
+These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.
+
+We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
+
+Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
+\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
+by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
+\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
+This gives rise to an action map
+\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
+of two-forms on spinors.
+Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
+\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
+on $\Sigma$ and $\Sigma^*$.
+
+\begin{thm}
+The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
+\brian{Where is the Poincare part?}
+\begin{align*}
+I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
+I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
+\end{align*}
+satisfies the classical master equation
+\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
+\label{thm:vectormultipletSUSY}
+\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
+\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
+\end{thm}
+
+The rest of the section will be devoted to the proof of the above theorem.
+
+Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
+\begin{equation}
+q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
+\label{eq:quantizationtwoforms}
+\end{equation}
+
+The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.
+
+The following properties of the Clifford action will be useful.
+Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
+
+\begin{prop}
+One has the following:
 \begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
+\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
+\brian{is there a similar expression for one-forms?}
+
+\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
+\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]
+
+\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
+\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
 \end{enumerate}
-
-For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
-$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
-Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-
-We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
-So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
-
-Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
+\label{prop:cliffordactionproperties}
+\end{prop}
+
+In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases.
+This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.
+
+\begin{prop}
+Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
+\label{prop:3psi}
+\end{prop}
+
+We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
+\begin{align*}
+\{S_{BV}, I^{(1)}\} &= 0 \\
+\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
+\{I^{(2)}, I^{(2)}\} &= 0.
+\end{align*}
+
+Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$.
+The rest of the claims will be proved in a sequence of Lemmas.
+To simplify the expressions, we drop the integrals and omit the natural pairings.
 
 \begin{lemma}
-Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
-Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
-\label{lm:extendpairing}
+One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
 \end{lemma}
-
-Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
-\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
-given, respectively, by
-\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
-
-The following is proved in \cite[Proposition 6]{BaezHuerta}.
-
-\begin{prop}
-The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
-\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
+\begin{proof}
+Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.
+
+The first term gives
+\begin{align*}
+\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
+&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
+&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
+&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
+\end{align*}
+
+The second term gives
+\begin{align*}
+\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
+\end{align*}
+where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.
+
+By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
+
+The third term gives
+\begin{align*}
+\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
+&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
+\end{align*}
+
+The fourth term gives
+\begin{align*}
+\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
+\end{align*}
+
+Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
+\end{proof}
+
+\begin{remark}
+The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
+\end{remark}
+
+\begin{lemma}
+One has
+\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
+\end{lemma}
+\begin{proof}
+Evaluating the equation
+\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
+on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
+So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
+
+The individual terms are
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
+= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
+&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
+\end{align*}
+\begin{align*}
+(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
+&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
+\end{align*}
+and
+\begin{align*}
+\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
+&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
+\end{align*}
+The total coefficient in front of $A^*$ is
+\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
+Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
+
+The total coefficient in front of $c^*$ is
+\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
+
+The total coefficient in front of $\lambda^*$ is
+\begin{align*}
+&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
+&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
+\end{align*}
+Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
+\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
+which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
+\end{proof}
+
+Evaluating the equation
+\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
+on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in\Sigma$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
+\end{align*}
+
+$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression.
+By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+The Clifford relation implies that
+\begin{align*}
+\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
+&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
+\end{align*}
+Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
+\end{proof}
+
+We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
+\begin{corollary}
+Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
+Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
+Then the super Poincar\'e algebra
+\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
+obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
+\end{corollary}
+
+\begin{proof}
+This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
+\end{proof}
+
+\begin{remark}
+We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
+\end{remark}
+
+\subsection{Supersymmetric matter}
+
+\subsubsection{The 4d $\cN=1$ chiral multiplet}
+
+\subsubsection{The 6d $\cN=(1, 0)$ hypermultiplet}
+
+In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(6; \CC)$. 
+The spinorial representation we will be interested in is $\Sigma = S_+ \otimes W_+$, where $\dim_{\CC}(W_+) = 2$ is a two-dimensional multiplicity space. 
+To define the half hyper multiplet we fix a complex, symplectic vector space $U$ whose symplectic form we call $\omega_U$.
+We combine the symplectic forms $\omega_U, \omega_{W_+}$ to define a pairing 
+\[
+(-,-)_{W_+ \otimes U}  := \omega_{W_+} \otimes \omega_U : (W_+ \otimes U)^{\otimes 2} \to \CC .
+\]
+The spinorial pairing $(-,-) : S_+ \otimes S_- \to \CC$ together with the obvious symplectic form $\omega_{W_+}$ on $W_+$, and the symplectic form $\omega_U$ on $U$ induces a pairing (that we denote by the same symbol)
+\[
+(-,-)_U : (S_\pm \otimes U) \otimes (S_\mp \otimes U) \to \CC .
+%(-,-)_U : (S_\pm \otimes W_+ \otimes U)^{\otimes 2} \to \CC  
+\]
+
+\begin{remark}
+The terminology ``half" hyper multiplet is to be consistent with the terminology in the physics literature. 
+The (full) hyper multiplet refers to a multiplet which depends on the choice of a (not necessarily symplectic) vector space $R$. 
+The relationship between the two is obtained by looking at the cotangent space $U = T^*R$.
+That is, the half hyper multiplet with values in the symplectic vector space $U = T^* R$ (with its obvious symplectic structure) is the (full) hyper multiplet for $R$. 
+\end{remark}
+
+The field content for the 6-dimensional half hyper multiplet with values in $U$ is:
+\begin{itemize}
+\item a scalar valued in $W_+ \otimes U$; $\phi \in C^\infty(\RR^4 ; W_+ \otimes U)$;
+\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
+\end{itemize}
+
+The space of BRST fields is thus
+\[
+F = C^\infty(\RR^4 ; W_+ \otimes U \oplus S_- \otimes U) .
+\]
+
+The BRST action is
+\[
+S (\phi, \psi) = \int_{\RR^4} - \frac{1}{2}  (\d \phi \wedge * \d \phi)_{W_+ \otimes U} + \frac{1}{2} (\psi , \sd \dd \psi)_U .
+\]
+As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
+
+The action of supersymmetry is given by a linear and quadratic functional:
+\begin{align*}
+I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
+I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) %
+%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
+\end{align*}
+where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
+We point out some conventions in the definition of $I^{(2)}$. 
+Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
+\[
+\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
+\]
+
+In order to prove the hypermultiplet is supersymmetric, we will need to following proposition about $6$-dimensional spinor representations.
+
+\begin{prop}\label{prop: new3psi}
+Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
+Then
+\[
+(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
+\]
 \end{prop}
 
-We have a nondegenerate scalar spinorial pairing
-\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
-given by
-\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
-It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
-\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
-
-By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
-\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
-
-We will now state two important properties of $\Gamma$ and the spinorial pairing.
-The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
+%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
+%\[
+%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
+%\]
+%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
+%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
+
+The following result states that these functionals encode an off-shell action of six-dimensional $\cN=(1,0)$ supersymmetry on the half hypermultiplet valued in $U$. 
+The proof is very similar to the case of the four-dimensional $\cN=1$ chiral multiplet.
 
 \begin{thm}
-Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
-\label{thm:3psi}
+The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
+\begin{equation}\label{CMEhyper}
+\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
 \end{thm}
 
-If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
-
-\begin{thm}
-Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
-\label{thm:matter3psi}
-\end{thm}
-\begin{proof}
-The right-hand side is
-\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
-which by associativity can be rewritten as
-\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
-which is the left-hand side.
-\end{proof}
-
-We will be interested in the following four examples:
-\begin{enumerate}
-\item $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$ (3d $\mc N=1$ supersymmetry).
-
-\item $A_\RR = \CC$. We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations (4d $\mc N=1$ supersymmetry).
-
-\item $A_\RR = \mathbb{H}$.
-We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$ (6d $\mc N=(1, 0)$ supersymmetry).
-
-\item $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation (10d $\mc N=(1, 0)$ supersymmetry).
-\end{enumerate}
-
-All four examples are alternative, while the first three examples are moreover associative.
+We decompose the classical master equation (\ref{CMEhyper}) into the following equations:
+\begin{equation}\label{CMEhyper2}
+\begin{array}{rrrrrr}
+\{S , I^{(1)}\} & = & 0 \\ 
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
+\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
+\{I^{(2)}, I^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
+
+The first equation in (\ref{CMEhyper2}) states that the classical action for the chiral multiplet is supersymmetric.
+
+\begin{lemma} \label{lem: hyper1}
+One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+\end{lemma}
+\begin{proof}
+Observe
+\[
+- \{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = - 2 (\d (Q, \psi) , \d \phi ) .
+\]
+and
+\[
+\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) .
+\]
+The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
+\end{proof}
+
+Next, we move on to the second equation in (\ref{CMEhyper2}).
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEhyper3}
+\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating expression (\ref{CMEhyper3}) on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
+
+The individual terms are:
+\begin{align*}
+\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  -  (\psi^*, \rho(\d(Q_1,\psi))Q_2) - (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
+\end{align*}
+
+\begin{align*}
+(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
+\end{align*}
+
+and
+\begin{align*}
+\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) 
+% \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
+\end{align*}
+Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.
+
+We first collect all terms in Equation (\ref{CMEhyper3}) proportional to $\phi^*$:
+\[
+- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
+\]
+By the Clifford identity
+\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term.
+
+Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
+\begin{equation}\label{psistar}
+\begin{array}{cccc}
+& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
+\\ 
+& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
+%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
+\end{array}
+\end{equation}
+By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
+\[
+- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
+\]
+Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
+So the expression (\ref{psistar}) is identically zero. 
+\end{proof}
+
+\begin{lemma}
+\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in \Sigma$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\end{align*}
+The expression
+$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
+
+\subsection{Supersymmetric couplings}
 
@@
 Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
-\label{prop:twistdimensionalreduction}
 \end{prop}
@@
 \subsection{Twisting Homomorphisms and Curved Backgrounds}
-
-\section{Supersymmetric Yang--Mills theories}
-
-In this section we construct supersymmetry action on all super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
-\begin{itemize}
-\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.
-
-\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$. \pavel{Moment maps?}
-
-\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
-
-\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
-\end{itemize}
-
-In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills.
-So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.
-
-\subsection{Vector multiplet} \label{sect:vectormultipletSUSY}
-
-Fix an \emph{alternative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
-We will show that in this case the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.
-
-We will construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
-
-\begin{thm}
-The functional $I_\rho = I_{BV} + I^{(1)} + I^{(2)}$ with
-\brian{Where is the Poincare part?}
-\begin{align*}
-I^{(1)}(Q) &= \int (\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A), \lambda^*) \\
-I^{(2)}(Q_1, Q_2) &= \int \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*
-\end{align*}
-satisfies the classical master equation
-\[(Q+\d_{CE}) I_{\rho} + \frac{1}{2}\{I_\rho, I_\rho\} = 0.\]
-\label{thm:vectormultipletSUSY}
-\brian{confused by the notation here. Is $Q$ a supercharge or a linear BRST operator?}
-\brian{Also, we should be consistent and either use $S_{BV}$ or $I_{BV}$.}
-\end{thm}
-
-The rest of the section will be devoted to the proof of the above theorem.
-
-The following properties of the Clifford action will be useful.
-Here the first property expresses $\so(V)$-invariance of the pairing $\Gamma\colon\Sigma\otimes \Sigma\rightarrow V$, the second property follows from \eqref{eq:quantizationtwoforms} and the third property was proved in \cite[equation 7.6]{Snygg}.
-
-We are now ready to prove Theorem \ref{thm:vectormultipletSUSY}. The classical master equation decomposes into the following equations:
-\begin{align*}
-\{S_{BV}, I^{(1)}\} &= 0 \\
-\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} &= 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} &= 0 \\
-\{I^{(2)}, I^{(2)}\} &= 0.
-\end{align*}
-
-Note that the last equation is automatically satisfied since $I^{(2)}$ is independent of $\lambda$ and $c$.
-The rest of the claims will be proved in a sequence of Lemmas.
-To simplify the expressions, we drop the integrals and omit the natural pairings.
-
-\begin{lemma}
-One has $\{S_{BV}, I^{(1)}(Q)\} = 0$.
-\end{lemma}
-\begin{proof}
-Let us decompose $S_{BV} = \sum_{i=1}^5 S_{BV}^i$ into individual summands.
-
-The first term gives
-\begin{align*}
-\{S_{BV}^1, I^{(1)}(Q)\} &= -\frac{1}{2} d_A \Gamma(Q, \lambda)\wedge \ast F_A\\
-&= -\frac{1}{2} \Gamma(Q, \lambda)\wedge d_A \ast F_A \\
-&= -\frac{1}{2}(-1)^{n-1} d_A\ast F_A\wedge \Gamma(Q, \lambda) \\
-&= -\frac{1}{2}(-1)^{n-1} (\ast d_A \ast F_A, \Gamma(Q, \lambda)).
-\end{align*}
-
-The second term gives
-\begin{align*}
-\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\dd}_A\lambda) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\dd}_A(\rho(F_A) Q)) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
-\end{align*}
-where we have used Proposition \ref{prop:cliffordactionproperty3} and the Bianchi identity in the last line.
-
-By \eqref{eq:Gammaspinorpairing} and Theorem \ref{thm:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.
-
-The third term gives
-\begin{align*}
-\{S_{BV}^3, I^{(1)}(Q)\} &= -[\Gamma(Q, \lambda), c]\wedge A^* - \frac{1}{2}\langle\rho(d_A d_A c)Q, \lambda^*\rangle \\
-&= -\Gamma(Q, [\lambda, c])\wedge A^* - \frac{1}{2}(\rho([F_A, c]) Q, \lambda^*).
-\end{align*}
-
-The fourth term gives
-\begin{align*}
-\{S_{BV}^4, I^{(1)}(Q)\} &= \frac{1}{2}([\rho(F_A) Q, c], \lambda^*) + \Gamma(Q, [\lambda, c])\wedge A^*.
-\end{align*}
-
-Again, we get $\{S_{BV}^3 + S_{BV}^4, I^{(1)}(Q)\}$ = 0. The fifth term gives $\{S_{BV}^5, I^{(1)}(Q)\} = 0$.
-\end{proof}
-
-\begin{remark}
-The previous Lemma expresses the fact that the super Yang--Mills action is supersymmetric which is one of the main results of \cite{BaezHuerta}.
-\end{remark}
-
-\begin{lemma}
-One has
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0.\]
-\end{lemma}
-\begin{proof}
-Evaluating the equation
-\[\{S_{BV}, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2}\{I^{(1)}, I^{(1)}\} = 0\]
-on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:Poincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
-So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
-
-The individual terms are
-\begin{align*}
-\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
-= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
-&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
-\end{align*}
-\begin{align*}
-(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
-&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
-\end{align*}
-and
-\begin{align*}
-\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\dd}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\dd}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\dd}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
-&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
-\end{align*}
-The total coefficient in front of $A^*$ is
-\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
-Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
-
-The total coefficient in front of $c^*$ is
-\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
-
-The total coefficient in front of $\lambda^*$ is
-\begin{align*}
-&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
-&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\dd}_A\lambda - \frac{1}{2}(Q_2, \sd{\dd}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\dd}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
-\end{align*}
-Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
-\[-\frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\dd}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{\dd}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Theorem \ref{thm:3psi}. Using the Clifford relation this term cancels the rest of the terms.
-\end{proof}
-
-Evaluating the equation
-\[\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} = 0\]
-on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I^{(2)}$.
-
-\begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in\Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* + \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
-&- \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) - \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
-\end{align*}
-
-$\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
-By Theorem \ref{thm:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
-The Clifford relation implies that
-\begin{align*}
-\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
-&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
-\end{align*}
-Therefore, again using Theorem \ref{thm:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
-\end{proof}
-
-\begin{comment}
-\pavel{This might go in the coupling section.}
-We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
-\begin{corollary}
-Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
-Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
-Then the super Poincar\'e algebra
-\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
-obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
-\end{corollary}
-
-\begin{proof}
-This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
-\end{proof}
-
-\begin{remark}
-We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
-\end{remark}
-\end{comment}
-
-\subsection{Matter multiplet}
-
-Fix an \emph{associative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
-Note that $\Sigma$ and $\Sigma^*$ are naturally right $A$-modules; the Clifford multiplication $V\otimes \Sigma\rightarrow \Sigma^*$ and the spinorial pairing $\Sigma\otimes \Sigma^*\rightarrow A$ are maps of right $A$-modules.
-We will use the antiinvolution $\sigma\colon A\rightarrow A$ to turn left $A$-modules into right $A$-modules.
-
-Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
-\[(av, w) = (v, \sigma(a)w).\]
-Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
-\begin{itemize}
-\item $A_\RR=\RR$, so $A=\CC$. We are looking for a complex vector space $P$ equipped with a nondegenerate symmetric bilinear pairing.
-
-\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$.
-A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$.
-Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$.
-So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$.
-In other words, the data boils down to a complex vector space $R$, so that $P = R\oplus R^*$.
-
-\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
-Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
-So, the data boils down a complex symplectic vector space $U$.
-\end{itemize}
-
-We are going to construct a theory on $V_\RR$ describing a matter multiplet valued in $P$. The BRST fields are given as follows:
-\begin{itemize}
-\item a scalar $\phi\in\Gamma(V_\RR; P)$;
-\item a spinor $\psi\in\Gamma(V_\RR; \Pi \Sigma^*\otimes_A P)$.
-\end{itemize}
-As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
-
-We extend the pairings on $P$ and between $\Sigma$ and $\Sigma^*$ to a pairing between $\Sigma\otimes_A P$ and $\Sigma^*\otimes_A P$ in the following way.
-Given $\sum_i \tilde{s}_i\otimes v_i\in \Sigma^*\otimes_A P$ and $\sum_j s_j\otimes w_j\in\Sigma\otimes_A P$, their pairing is
-\begin{equation}
-\sum_{i, j} \Re((v_i, w_j)^A (s_j, \tilde{s}_i)^A),
-\label{eq:spinorialmatterpairing}
-\end{equation}
-where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
-\[\Gamma_P\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
-defined by the property
-\[(v, \Gamma_P(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
-
-The action for the matter multiplet is
-\[
-S = \int_{V_\RR} -\frac{1}{2}  (\d \phi \wedge * \d \phi) + \frac{1}{2} (\psi , \sd \dd \psi)\dvol,
-\]
-where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
-
-The action of supersymmetry is given by a linear and quadratic functional:
-\begin{align*}
-I^{(1)} (Q) & = \int (\phi^*, (Q, \psi)) - (\psi^*, \rho(\d \phi) Q) \\
-I^{(2)} (Q_1 , Q_2) & = \int \frac{1}{4}(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)_P) \end{align*}
-where $Q, Q_1,Q_2 \in \Sigma$.
-
-The following result states that these functionals encode an off-shell action of the supersymmetry on the matter multiplet.
-
-\begin{thm}
-The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
-\begin{equation}\label{CMEmatter}
-\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
-\end{equation}
-\end{thm}
-
-We decompose the classical master equation \eqref{CMEmatter} into the following equations:
-\begin{equation}\label{CMEmatter2}
-\begin{array}{rrrrrr}
-\{S , I^{(1)}\} & = & 0 \\ 
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
-\{I^{(2)}, I^{(2)}\} & =& 0
-\end{array}
-\end{equation}
-
-The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
-
-The first equation in \eqref{CMEmatter2} states that the classical action for the matter multiplet is supersymmetric.
-
-\begin{lemma} \label{lem: matter1}
-One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
-\end{lemma}
-\begin{proof}
-Observe
-\[
-\{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = 2 (\d (Q, \psi) , \d \phi ) .
-\]
-and
-\[
-\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2(\psi, \sd \dd \rho(\d \phi) Q).
-\]
-
-By Proposition \ref{prop:cliffordactionproperty3} $\sd \dd\rho(\d\phi) Q = (\d^* \d\phi) Q$. Therefore,
-\[2(\psi, \sd \dd \rho(\d \phi) Q) = 2(\d^*\d\phi)(\psi, Q) = -2(\d\phi, \d(\psi, Q))\]
-which cancels the first term.
-\end{proof}
-
-Next, we move on to the second equation in \eqref{CMEmatter2}.
-
-\begin{lemma} 
-One has
-\begin{equation}\label{CMEmatter3}
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
-\end{equation}
-\end{lemma}
-\begin{proof}
-Evaluating expression \eqref{CMEmatter3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
-So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
-
-The individual terms are:
-\begin{align*}
-\frac{1}{2}\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &\phi^* (Q_1, \rho(\d \phi) Q_2) + \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  + (\psi^*, \rho(\d(Q_1,\psi))Q_2) + (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
-\end{align*}
-
-\begin{align*}
-(\d_{CE}I^{(1)})(Q_1,Q_2) = &-\phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
-\end{align*}
-
-and
-\begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi)_P
-\end{align*}
-Note that we can rewrite this as $\frac{1}{2} (\rho(\Gamma(Q_1, Q_2)) \sd \dd \psi, \psi^*)$.
-
-We first collect all terms in equation \eqref{CMEmatter3} proportional to $\phi^*$:
-\[
-\frac{1}{2} (Q_1, \rho(\d\phi) Q_2) + \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
-\]
-
-By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the third term.
-
-Next, we collect all terms in equation \eqref{CMEmatter3} proportional to $\psi^*$:
-\begin{equation}\label{psistar}
-\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1,\partial_i \psi)^A + \frac{1}{2} \sum_i (\rho(e^i) Q_1)(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi.
-\end{equation}
-The first and second terms can be written as:
-\[
-\frac{1}{2} \sum_i (\rho(e^i)Q_2)(Q_1, \partial_i \psi)^A + \frac{1}{2} \sum_i(\rho(e^i)Q_1)(Q_2, \partial_i \psi)^A = \frac{1}{2} \sd \dd \left(Q_2(Q_1, \psi)^A + Q_1(Q_2, \psi)^A\right).
-\]
-Applying Theorem \ref{thm:matter3psi} to $Q_3 = \psi$, this becomes $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
-Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\Gamma(Q_1,Q_2) . \psi$ which cancels the third term.
-\end{proof}
-
-\begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in \Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)_P) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
-\end{align*}
-The expression
-$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
-
-\begin{comment}
-\subsection{Supersymmetric matter}
-
-\subsubsection{The 4d $\cN=1$ chiral multiplet}
-
-\subsubsection{The 6d $\cN=(1, 0)$ hypermultiplet}
-
-In this subsection, $S_+ / S_-$ denote the positive/negative irreducible spin representations of $\mf{so}(6; \CC)$. 
-The spinorial representation we will be interested in is $\Sigma = S_+ \otimes W_+$, where $\dim_{\CC}(W_+) = 2$ is a two-dimensional multiplicity space. 
-To define the half hyper multiplet we fix a complex, symplectic vector space $U$ whose symplectic form we call $\omega_U$.
-We combine the symplectic forms $\omega_U, \omega_{W_+}$ to define a pairing 
-\[
-(-,-)_{W_+ \otimes U}  := \omega_{W_+} \otimes \omega_U : (W_+ \otimes U)^{\otimes 2} \to \CC .
-\]
-The spinorial pairing $(-,-) : S_+ \otimes S_- \to \CC$ together with the obvious symplectic form $\omega_{W_+}$ on $W_+$, and the symplectic form $\omega_U$ on $U$ induces a pairing (that we denote by the same symbol)
-\[
-(-,-)_U : (S_\pm \otimes U) \otimes (S_\mp \otimes U) \to \CC .
-%(-,-)_U : (S_\pm \otimes W_+ \otimes U)^{\otimes 2} \to \CC  
-\]
-
-\begin{remark}
-The terminology ``half" hyper multiplet is to be consistent with the terminology in the physics literature. 
-The (full) hyper multiplet refers to a multiplet which depends on the choice of a (not necessarily symplectic) vector space $R$. 
-The relationship between the two is obtained by looking at the cotangent space $U = T^*R$.
-That is, the half hyper multiplet with values in the symplectic vector space $U = T^* R$ (with its obvious symplectic structure) is the (full) hyper multiplet for $R$. 
-\end{remark}
-
-The field content for the 6-dimensional half hyper multiplet with values in $U$ is:
-\begin{itemize}
-\item a scalar valued in $W_+ \otimes U$; $\phi \in C^\infty(\RR^4 ; W_+ \otimes U)$;
-\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
-\end{itemize}
-
-The space of BRST fields is thus
-\[
-F = C^\infty(\RR^4 ; W_+ \otimes U \oplus S_- \otimes U) .
-\]
-
-The BRST action is
-\[
-S (\phi, \psi) = \int_{\RR^4} - \frac{1}{2}  (\d \phi \wedge * \d \phi)_{W_+ \otimes U} + \frac{1}{2} (\psi , \sd \dd \psi)_U .
-\]
-As usual, we denote the antifields by $\phi^*$ and $\psi^*$.
-
-The action of supersymmetry is given by a linear and quadratic functional:
-\begin{align*}
-I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) %
-%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
-\end{align*}
-where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
-We point out some conventions in the definition of $I^{(2)}$. 
-Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
-\[
-\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
-\]
-
-In order to prove the hypermultiplet is supersymmetric, we will need to following proposition about $6$-dimensional spinor representations.
-
-\begin{prop}\label{prop: new3psi}
-Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
-Then
-\[
-(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
-\]
-\end{prop}
-
-%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
-%\[
-%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
-%\]
-%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
-%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}
-
-The following result states that these functionals encode an off-shell action of six-dimensional $\cN=(1,0)$ supersymmetry on the half hypermultiplet valued in $U$. 
-The proof is very similar to the case of the four-dimensional $\cN=1$ chiral multiplet.
-
-\begin{thm}
-The functional $\fS = S + I^{(1)} + I^{(2)}$ satisfies the classical master equation
-\begin{equation}\label{CMEhyper}
-\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
-\end{equation}
-\end{thm}
-
-We decompose the classical master equation (\ref{CMEhyper}) into the following equations:
-\begin{equation}\label{CMEhyper2}
-\begin{array}{rrrrrr}
-\{S , I^{(1)}\} & = & 0 \\ 
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} & = & 0 \\
-\d_{CE} I^{(2)} + \{I^{(1)}, I^{(2)}\} & =& 0 \\
-\{I^{(2)}, I^{(2)}\} & =& 0
-\end{array}
-\end{equation}
-
-The last equation is automatically satisfied since $I^{(2)}$ is independent of $\phi$ and $\psi$.
-
-The first equation in (\ref{CMEhyper2}) states that the classical action for the chiral multiplet is supersymmetric.
-
-\begin{lemma} \label{lem: hyper1}
-One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
-\end{lemma}
-\begin{proof}
-Observe
-\[
-- \{(\d \phi , \d \phi), (\phi^* , (Q, \psi)) \} = - 2 (\d (Q, \psi) , \d \phi ) .
-\]
-and
-\[
-\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) .
-\]
-The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
-\end{proof}
-
-Next, we move on to the second equation in (\ref{CMEhyper2}).
-
-\begin{lemma} 
-One has
-\begin{equation}\label{CMEhyper3}
-\{S, I^{(2)}\} + \d_{CE} I^{(1)} + \frac{1}{2} \{I^{(1)}, I^{(1)}\} = 0 .
-\end{equation}
-\end{lemma}
-\begin{proof}
-Evaluating expression (\ref{CMEhyper3}) on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that (??) defines a strict Lie action. 
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e} invariant.
-So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
-
-The individual terms are:
-\begin{align*}
-\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = & - \phi^* (Q_1, \rho(\d \phi) Q_2) - \phi^* (Q_2, \rho(\d \phi)Q_1) \\ &  -  (\psi^*, \rho(\d(Q_1,\psi))Q_2) - (\psi^*, \rho(\d(Q_2, \psi)) Q_1) 
-\end{align*}
-
-\begin{align*}
-(\d_{CE}I^{(1)})(Q_1,Q_2) = & - \phi^* L_{\Gamma(Q_1,Q_2)} (\phi) - (\psi^*, \Gamma(Q_1,Q_2) . \psi)
-\end{align*}
-
-and
-\begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) 
-% \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
-\end{align*}
-Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.
-
-We first collect all terms in Equation (\ref{CMEhyper3}) proportional to $\phi^*$:
-\[
-- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
-\]
-By the Clifford identity
-\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term.
-
-Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
-\begin{equation}\label{psistar}
-\begin{array}{cccc}
-& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
-\\ 
-& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
-%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
-\end{array}
-\end{equation}
-By Proposition \ref{prop:cliffordactionproperty3}, the first and second terms can be written as:
-\[
-- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
-\]
-Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
-Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
-So the expression (\ref{psistar}) is identically zero. 
-\end{proof}
-
-\begin{lemma}
-\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in \Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
-\end{align*}
-The expression
-$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
-\end{comment}
-
-\subsection{Supersymmetric couplings}
-
-\section{Dimension 10}
-
-The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with a nondegenerate symmetric bilinear pairing.
-There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
-We concentrate on the first case, the second case being identical.
-So, we fix $W_+=\CC$ and $W_- = 0$.
-
-\subsection{$\cN=(1, 0)$ super Yang--Mills theory}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
-Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
-\end{itemize}
-
-\subsubsection{Holomorphic twist}
-
-We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
-Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
-The vector representation decomposes as
-\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5)\]
-the semi-spin representation $S_+$ decomposes as
-\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
-and the semi-spin representation $S_-$ decomposes as
-\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
-Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
-Under the above decomposition the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
-\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
-
-\vspace{-10pt}
-\paragraph{Fields:} The BRST fields are given by:
-\begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
-\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
-\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
-\end{itemize}
-We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
-
-The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields.
-We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
-
-\begin{prop}
-Let $(M, \omega)$ be a K\"{a}hler $d$-fold and decompose
-\[\Omega^2(M) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\CC\omega\oplus \Omega^{1, 1}_\perp(M)).\]
-Then
-\begin{enumerate}
-\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\CC\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.
-
-\item For a form $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
-\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
-
-\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
-\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
-
-\item For $\alpha\in\CC\omega$ we have
-\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
-\end{enumerate}
-\end{prop}
-
-\begin{corollary}
-Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
-\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
-\end{corollary}
-
-Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{BV}$ is then the sum of the following terms:
-\begin{align*}
-S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{anti} &= \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
-I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
-\end{align*}
-
-\begin{thm}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
-\label{thm:10dholomorphictwist}
-\end{thm}
-\begin{proof}
-First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
-\begin{align*}
-S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int -\dd_{A_{1, 0}} c\wedge A_{1, 0}^* - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
-\end{align*}
-
-Next, we have a term $\int \psi\wedge A_{1, 0}^*$ in the action, i.e.
-$(\psi, A_{1, 0})$ is a BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
-The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
-\[
-S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega - \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
-\]
-
-The holomorphic Chern--Simons theory has fields $c, A_{0, 1}, B, \tilde{B}, \tilde{A}_{0, 1}, \tilde{c}$ with the BV action
-\[
-S_{CS} = \int \left(c\wedge \ol\dd_{A_{0, 1}} \tilde{A}_{0, 1} + \tilde{B}\wedge F_{0, 2} + \frac{1}{2} B\wedge \ol\dd_{A_{0, 1}} B + \frac{1}{2}[c, c]\tilde{c} + [B, c]\wedge \tilde{B}\right)\Omega
-\]
-Up to a rescaling of the antifields, it coincides with the BV action $S_0$.
-\end{proof}
-
-\begin{remark}
-A similar claim was previously proved by Baulieu \cite{Baulieu} by adding an auxiliary field to 10d $\mc N=(1, 0)$ super Yang--Mills.
-\end{remark}
-
-\section{Dimension 9}
-
-The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
-So, we fix $W = \CC$.
-
-\subsection{$\cN=1$ super Yang--Mills theory}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
-\end{itemize}
-
-\subsubsection{Holomorphic twist}
-
-We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
-Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
-
-Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-
-\begin{thm}
-The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
-\end{thm}
-\begin{proof}
-By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
-In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
-
-From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
-By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
-\end{proof}
 
@@
 
-In terms of these component fields, the BV action can be written in the following way.  We will split the BV action up into the BRST action and the antifield action.
+In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
 \begin{align*}
@@
 \subsection{Dimension 6}
+
 In dimension 6 there are two possible supersymmetry groups by which we can act.
@@
 \subsubsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
+
+The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sec: couple}. 
+The fields are:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^6;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^6 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item $U$-valued scalars: $\phi \in C^\infty(\RR^6 ; W_+ \otimes U)$;
+\item $U$-valued fermions: $\psi \in C^\infty(\RR^6 ; S_- \otimes U)$ .
+\end{itemize}
+
+The interaction terms encoding $\mc N = (1,0)$ supersymmetry $I^{(1)}$ and $I^{(2)}$ are:
+\begin{align*}
+I^{(1)} & = I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter} + I^{(1)}_{\rm couple} \\
+I^{(2)} & = I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter} 
+\end{align*}
+where
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q) &= (\Gamma(Q, \lambda), A^*)_\fg + \frac{1}{2}(\rho(F_A), \lambda^*)_\fg \\
+I_{\rm gauge}^{(2)}(Q_1, Q_2) &= \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)_\fg) - \frac{1}{2}((Q_1, \lambda^*),(Q_2, \lambda^*))_\fg - \iota_{\Gamma(Q_1, Q_2)} A c^*\\
+I^{(1)}_{\rm matter} (Q) & = (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
+I^{(2)}_{\rm matter} (Q_1 , Q_2) & =  \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \\
+I^{(1)}_{\rm couple} (Q) & = g (\psi^*, \rho([A, \phi]) Q)_U + \frac{1}{2} g (\lambda^*, Q \mu(\phi,\phi))_\fg 
+%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
+\end{align*}
+
+Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
+Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
+
+We decompose the fields with respect to $\U(5) \hookrightarrow \SO(6)$:
+\begin{align*}
+c & \mapsto A^0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+A & \mapsto A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3 ; \fg) \oplus \Omega^{0,1}(\CC^3) \\
+\lambda & \mapsto \lambda^0_1 w_1 + \lambda_2^0 w_2 + A^{0,2} w_1 +  \Tilde{\lambda}^{0,2} w_2\in \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \\
+\phi & \mapsto A 
+\end{align*} 
+where the $A^{\bu, \bu}, \lambda^{\bu,\bu}, \Tilde{\lambda}^{\bu,\bu}$ are all $\fg$-valued forms.
 
@@
 
-\section{Spinors}
-\label{sect:spinors}
-
-\pavel{A bit out of place.}
-
-In this paper we will extensively use the theory of spinors.
-Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
-\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
-Consider a $\ZZ/2$-graded Clifford module $M=M^+\oplus M^-$.
-Denote the Clifford action by $\rho(v)\in\eend(M)$.
-We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
-\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
-for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
-\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
-by
-\begin{equation}
-(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
-\label{eq:Gammaspinorpairing}
-\end{equation}
-
-We have a subset $\Spin(V)\subset \Cl(V)$, so $\Sigma$ and $\Sigma^*$ are representations of the spin group. Moreover, the Clifford action and the maps $\Gamma$ are $\Spin(V)$-equivariant.
-
-We may identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -\rangle)} \omega).\]
-This gives rise to an action map
-\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
-of two-forms on spinors.
-
-Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
-\begin{equation}
-q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
-\label{eq:quantizationtwoforms}
-\end{equation}
-
-The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$, so that $\so(V)$-equivariance of $\Gamma$ gives the following.
-
-\begin{prop}
-For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
-\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
-\label{prop:cliffordactionproperty1}
-\end{prop}
-
-We may extend the discussion to the case of Riemannian manifolds $M$, where we replace $V$ by the vector bundle $TM$.
-Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
-\[\sd{\dd}\colon \Gamma(M, \Sigma)\rightarrow \Gamma(M, \Sigma^*).\]
-
-From \eqref{eq:quantizationtwoforms} we get the following property.
-
-\begin{prop}
-Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma)$. Then
-\[\sd{\dd}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\dd} \lambda) Q_2.\]
-\label{prop:cliffordactionproperty2}
-\end{prop}
-
-Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
-
-\begin{prop}
-Suppose $Q\in\Sigma$ and $X\in\Omega^p(M)$. Then
-\[\sd{\dd}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
-\label{prop:cliffordactionproperty3}
-\end{prop}
-
-Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\dd}$ is the corresponding twisted Dirac operator.
-
 \pagestyle{bib}

### 2020-01-02 paper.tex

--- 2020-01-02 paper.tex
@@
 
-\subsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
+The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sec: couple}. 
+The fields are:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^6;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^6 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item $U$-valued scalars: $\phi \in C^\infty(\RR^6 ; W_+ \otimes U)$;
+\item $U$-valued fermions: $\psi \in C^\infty(\RR^6 ; S_- \otimes U)$ .
+\end{itemize}
+
+The interaction terms encoding $\mc N = (1,0)$ supersymmetry $I^{(1)}$ and $I^{(2)}$ are:
+\begin{align*}
+I^{(1)} & = I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter} + I^{(1)}_{\rm couple} \\
+I^{(2)} & = I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter} 
+\end{align*}
+where
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q) &= (\Gamma(Q, \lambda), A^*)_\fg + \frac{1}{2}(\rho(F_A), \lambda^*)_\fg \\
+I_{\rm gauge}^{(2)}(Q_1, Q_2) &= \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)_\fg) - \frac{1}{2}((Q_1, \lambda^*),(Q_2, \lambda^*))_\fg - \iota_{\Gamma(Q_1, Q_2)} A c^*\\
+I^{(1)}_{\rm matter} (Q) & = (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
+I^{(2)}_{\rm matter} (Q_1 , Q_2) & =  \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \\
+I^{(1)}_{\rm couple} (Q) & = g (\psi^*, \rho([A, \phi]) Q)_U + \frac{1}{2} g (\lambda^*, Q \mu(\phi,\phi))_\fg 
+%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
+\end{align*}
+
+Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
+Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
+
+We decompose the fields with respect to $\U(5) \hookrightarrow \SO(6)$:
+\begin{align*}
+c & \mapsto A^0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+A & \mapsto A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3 ; \fg) \oplus \Omega^{0,1}(\CC^3) \\
+\lambda & \mapsto \lambda^0_1 w_1 + \lambda_2^0 w_2 + A^{0,2} w_1 +  \Tilde{\lambda}^{0,2} w_2\in \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \\
+\phi & \mapsto A 
+\end{align*} 
+where the $A^{\bu, \bu}, \lambda^{\bu,\bu}, \Tilde{\lambda}^{\bu,\bu}$ are all $\fg$-valued forms.
+
+\subsubsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
 

### 2020-01-05 paper.tex
Small comments added
2d chiral supersymmetry

@@
 \renewcommand{\Re}{\mathrm{Re}}
+\newcommand{\U}{\mathrm{U}}
 
@@
 
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?}
+
 \begin{prop}
@@
 
-\subsection{The Classical Factorization Algebra}
-
-\pavel{Is this section needed?} \chris{something is needed if we want to connect to the story from our previous paper: we'd like to say that all of these twisted SUSY field theories (or rather, the topological ones) produce $\bb E_n$ algebras, no?
-Certainly not all of them are interesting.
-I don't know whether we need the section here, but we would like to say something somewhere.}
-
-Let $(E, Q, \omega, I)$ be a classical BV theory. We recall the formalism of \cite{Book1,Book2} which extracts a factorization algebra on spacetime.
-
-\begin{definition}
-Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
-The \defterm{classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
-\[
-\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
-\]
-\end{definition}
-
-Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
-The BV complex can be thought of as the complex of functions on the derived critical locus of the BRST action.
-It makes sense to restrict fields to any open set $U \subset M$. 
-Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the BRST action where we restrict the theory to $U$.
-
-The fact that the assignment $U \mapsto \Obs(U)$ defines a factorization algebra can be found in \cite[Section 3]{Book2}.
-
 \subsection{From BRST to BV}
@@
 
-\subsection{Division algebras and supersymmetry}
+\subsection{Division algebras and minimal supersymmetry}
 \label{sect:divisionalgebras}
@@
 \end{prop}
+
+So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
 
@@
 \begin{enumerate}
-\item $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$ (3d $\mc N=1$ supersymmetry).
-
-\item $A_\RR = \CC$. We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations (4d $\mc N=1$ supersymmetry).
-
-\item $A_\RR = \mathbb{H}$.
+\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
+
+\item (\textbf{4d $\mc N=1$ supersymmetry}) $A_\RR = \CC$.
+We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
+
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$.
 We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$ (6d $\mc N=(1, 0)$ supersymmetry).
-
-\item $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation (10d $\mc N=(1, 0)$ supersymmetry).
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
 \end{enumerate}
@@
 All four examples are alternative, while the first three examples are moreover associative.
+
+\subsection{Two-dimensional chiral supersymmetry}
+
+In the previous section we have related division algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
+In this section we explain a different relationship between division algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
+
+Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
+\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
+and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
+\begin{equation}
+(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
+\label{eq:2dvectorpairing}
+\end{equation}
+
+Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
+\[\Sigma = S_+\otimes W\]
+and its dual
+\[\Sigma^* = S_-\otimes W.\]
+The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
+\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
+and similarly for $V\otimes S_-\rightarrow S_+$.
+
+\begin{prop}
+For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
+\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
+\begin{align*}
+\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
+&= 4(s, f)^2 s.
+\end{align*}
+But by \eqref{eq:2dvectorpairing} we have
+\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
+which proves the claim.
+\end{proof}
+
+The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
+Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
+
+The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
+\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
+and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.
+
+\begin{prop}
+For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
+\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
+\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
+The right-hand side is
+\begin{align*}
+(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
+&= 2(s, f)^2 (q_1, q_2).
+\end{align*}
+\end{proof}
+
+An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.
+
+\begin{thm}
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
+\label{thm:2d3psi}
+\end{thm}
+\begin{proof}
+Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
+\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
+\end{proof}
+
+We will now fix an associative algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and set $W = A$.
+The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
+Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
+
+Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
+\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
+
+\begin{thm}
+For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
+\label{thm:2dmatter3psi}
+\end{thm}
+\begin{proof}
+Pick basis elements $s\in S_+$ and $f\in S_-$, so that
+\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
+The right-hand side is
+\begin{align*}
+(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
+&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
+\end{align*}
+We have
+\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
+so the left-hand side is
+\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
+By associativity of $A$ the two expressions are equal.
+\end{proof}
 
@@
 
+\begin{landscape}
+\begin{figure}
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
+\end{landscape}
+
 \section{Supersymmetric Yang--Mills theories}
 
-In this section we construct supersymmetry action on all super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
+In this section we construct supersymmetry action on super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
 \begin{itemize}
@@
 \item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
+
+\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.
+
+\item (4 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
+
+\item (2 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
+
+\item (1 supercharge, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
 \end{itemize}
@@
 
-We begin with a description of the pure minimally supersymmetric Yang--Mills theories in dimensions 3, 4, 6 and 10.
-
-Fix an \emph{alternative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
-Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing.
-The fields of the Yang--Mills theory are as follows:
+We begin with a description of certain pure supersymmetric Yang--Mills theories.
+Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
+Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
+\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
+defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.
+
+\begin{assumption}
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
+\label{assumption:3psi}
+\end{assumption}
+
+Explicitly, we consider the following cases:
+\begin{itemize}
+\item (\textbf{2d $\cN=(\cN_+, 0)$ supersymmetry}) We have $\dim(V) = 2$ and $\Sigma = S_+\otimes W$ for some complex vector space $W$ equipped with a nondegenerate symmetric bilinear pairing.
+Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:2d3psi}.
+
+\item (\textbf{3d $\cN=1$ supersymmetry}) We have $\dim(V) = 3$ and $\Sigma = S$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{4d $\cN=1$ supersymmetry}) We have $\dim(V) = 4$ and $\Sigma = S_+\oplus S_-$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ for a two-dimensional complex symplectic vector space $W_+$.
+Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{10d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+\end{itemize}
+
+Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The fields of the Yang--Mills theory are as follows:
 \begin{itemize}
@@
 
-Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Section \ref{sect:spinors}).
+Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).
 
 The BRST action is given by
-\[S(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
-
-We introduce the gauge transformations
-\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\]
+\[S_{BRST}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+
+We introduce gauge transformations
+\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
 so that the BV action is given by
@@
 
-By \eqref{eq:Gammaspinorpairing} and Theorem \ref{thm:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
+By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
 
@@
 \[-\frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Theorem \ref{thm:3psi}. Using the Clifford relation this term cancels the rest of the terms.
+which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Assumption \ref{assumption:3psi}. Using the Clifford relation this term cancels the rest of the terms.
 \end{proof}
@@
 $\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
-By Theorem \ref{thm:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
 The Clifford relation implies that
@@
 \end{align*}
-Therefore, again using Theorem \ref{thm:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
+Therefore, again using Assumption \ref{assumption:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
 \end{proof}
@@
 
-Fix an \emph{associative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$.
-Note that $\Sigma$ and $\Sigma^*$ are naturally right $A$-modules; the Clifford multiplication $V\otimes \Sigma\rightarrow \Sigma^*$ and the spinorial pairing $\Sigma\otimes \Sigma^*\rightarrow A$ are maps of right $A$-modules.
-We will use the antiinvolution $\sigma\colon A\rightarrow A$ to turn left $A$-modules into right $A$-modules.
+In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e.
+the supersymmetric gauged linear $\sigma$-models.
+Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models in \cite[Chapter 3]{DeligneFreed}.
+
+Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
+In addition, fix a real associative algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and denote its complexification by $A$.
+Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
+Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
+We make the following additional assumption.
+
+\begin{assumption}
+For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
+\label{assumption:matter3psi}
+\end{assumption}
+
+Explicitly, we consider the following cases:
+\begin{itemize}
+\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{3d $\cN=1$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{4d $\cN=1$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+\end{itemize}
 
@@
 \end{align*}
-where we have used Theorem \ref{thm:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
+where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
 \[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
@@
 \end{equation}
-Applying Theorem \ref{thm:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Applying Assumption \ref{assumption:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
 Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\iota_{\Gamma(Q_1,Q_2)}\d_A \psi$ which cancels the remaining terms.
@@
 The expression
-$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Theorem \ref{thm:3psi} the cyclic symmetrization is identically zero.
+$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
 \end{proof}
@@
 \end{proof}
-
-%%\begin{landscape}
-%\begin{figure}
-%\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-%\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-%\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-%\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-%\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-%\node (825) [right=of 82] {};
-%\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-%\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-%\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-%\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-%\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-%\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-%\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-%\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-%\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-%\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-%\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-%\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-%\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-%\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-%\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-%\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-%\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-%\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-%\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-%\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-%\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-%\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-%
-%\draw[arrow] (101) -- (91);
-%\draw[arrow] (91) -- (81);
-%\draw[arrow] (91) -- (82);
-%\draw[arrow] (81) -- (71);
-%\draw[arrow] (82) -- (71);
-%\draw[arrow] (82) -- (72);
-%\draw[arrow] (83) -- (73);
-%\draw[arrow] (71) -- (61);
-%\draw[arrow] (71) -- (62);
-%\draw[arrow] (72) -- (62);
-%\draw[arrow] (72) -- (63);
-%\draw[arrow] (73) -- (65);
-%\draw[arrow] (61) -- (51);
-%\draw[arrow] (62) -- (51);
-%\draw[arrow] (62) -- (52);
-%\draw[arrow] (63) -- (53);
-%\draw[arrow] (64) -- (52);
-%\draw[arrow] (64) -- (54);
-%\draw[arrow] (65) -- (54);
-%\draw[arrow] (51) -- (41);
-%\draw[arrow] (51) -- (42);
-%\draw[arrow] (52) -- (42);
-%\draw[arrow] (52) -- (43);
-%\draw[arrow] (53) -- (43);
-%\draw[arrow] (54) -- (43);
-%\draw[arrow] (54) -- (44);
-%\draw[arrow] (54) -- (45);
-%\draw[arrow] (41) -- (31);
-%\draw[arrow] (42) -- (31);
-%\draw[arrow] (42) -- (32);
-%\draw[arrow] (43) -- (32);
-%\draw[arrow] (44) -- (32);
-%\draw[arrow] (45) -- (32);
-%\draw[arrow] (31) -- (21);
-%\draw[arrow] (31) -- (22);
-%\draw[arrow] (32) -- (22);
-%
-%\node (2d) [dimension, left=of 21] {2d};
-%\node (3d) [dimension, above=of 2d] {3d};
-%\node (4d) [dimension, above=of 3d] {4d};
-%\node (5d) [dimension, above=of 4d] {5d};
-%\node (6d) [dimension, above=of 5d] {6d};
-%\node (7d) [dimension, above=of 6d] {7d};
-%\node (8d) [dimension, above=of 7d] {8d};
-%\node (9d) [dimension, above=of 8d] {9d};
-%\node (10d) [dimension, above=of 9d] {10d};
-%\end{tikzpicture}
-%\caption{Orbits of square-zero supercharges.}
-%\label{fig:superchargeorbits}
-%\end{figure}
-%%\end{landscape}
 
@@
 %\]
-%\section{Dimension 3}
+
+\section{Dimension 3}
 
@@
 \appendix
-
-\section{Functional analysis} \label{appx: top}
-
-\def\CVS{{\rm CVS}}
-\def\DVS{{\rm DVS}}
-
-\brian{We can put all our conventions for topological vector spaces, largely borrowed from \cite{Book1}, here. }
-
-\subsection{Notations and conventions}
-
-\begin{definition}
-Let $M$ be a manifold and $E$ a (graded) vector bundle on $M$.  
-For any open set $U \subset M$, define the following notations:
-\begin{itemize}
-\item $\cE(U)$ denotes the graded vector space of smooth sections supported on $U$;
-\item $\cE_c(U)$ denotes the graded vector space of compactly supported smooth sections on $U$;
-\item $\Bar{\cE}(U)$ denotes the graded vector space of distributional smooth sections on $U$;
-\item $\Bar{\cE}_c(U)$ denotes the graded vector space of compactly supported distributional smooth sections on $U$.
-\end{itemize}
-\end{definition}
-
-If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
-For an open set $U \subset M$ let 
-\[
-\cE(U)^\vee = \Bar{\cE}^!_c(U)
-\]
-be the continuous, or distributional, dual to $\cE(U)$.
-
-\brian{recall definition of CVS. all our familiar spaces above are in $\CVS$. talk about tensor products.}
-
-\begin{prop}
-Let $E,F$ be vector bundles on $M,N$ respectively.
-Then
-\[
-\cE(M) \Hat{\otimes}_\beta \cF(N) \cong \Gamma(M \times N, E \boxtimes F)
-\]
-\end{prop}
-
-\begin{definition}\label{dfn: fnl}
-Let $E$ be a vector bundle on $M$ and $U \subset M$.
-The \defterm{completed algebra of functions} on $\cE(U)$ is
-\[
-\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
-\]
-On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
-\end{definition}
-
-\subsection{Differentiable vector spaces}
-\def\Mfld{{\rm Mfld}}
-
-Let $\Mfld$ denote the site of smooth manifolds (of arbitrary dimension) where the morphisms are smooth maps, and a cover $f : X \to Y$ is a surjective local diffeomorphism.
-
-\begin{definition} 
-We use the following notations and naming conventions for sheaves on $\Mfld$:
-\begin{itemize}
-\item a \defterm{smooth vector space} is a sheaf of vector spaces on $\Mfld$.
-\item Let $C^\infty$ denote the smooth vector space which assigns the space of smooth functions $C^\infty(X)$ to a smooth manifold $X$.
-\item a \defterm{$C^\infty$-module} is a smooth vector space $V$ equipped with a structure of a module over $C^\infty$. 
-If $V$ is a $C^\infty$-module, we denote $C^\infty(X, V) := V(X)$, the valued of $V$ on the smooth manifold $X$.
-\item a \defterm{differentiable vector space} is a $C^\infty$-module $V$ equipped with a flat connection
-\[
-\nabla_{X,V} : C^\infty(X, V) \to \Omega^1(X, V)
-\]
-for every smooth manifold $X$, which is required to be natural under pullbacks:
-\[
-f^* \circ \nabla_{Y,V} = \nabla_{X,V} \circ f^*
-\]
-for every smooth map $f : X \to Y$. 
-A map of differentiable vector spaces is a map of $C^\infty$-modules which intertwines the flat connections. 
-\end{itemize}
-\end{definition}
-
-\subsection{Homological algebra}
-
-There is a functor
-\[
-dif_c : \CVS \to \DVS 
-\]
-from the category of convenient vector spaces to the category of differentiable vector spaces. 
-This functor does not preserve cokernels, so $dif_c$ does not preserve cohomology. 
-In particular, with a naive definition of quasi-isomorphism internal to $\CVS$, the functor $dif_c$ does not preserve quasi-isomorphisms. 
-To avoid this issue, we make the following definition.
-
-\begin{definition}
-Suppose $V,W$ are cochain complexes in convenient vector spaces. 
-A cochain map $f\colon V \to W$ is a \defterm{quasi-isomorphism} if the map
-\[
-dif_c (f) : dif_c(V) \to dif_c(W)
-\]
-is a quasi-isomorphism of differentiable vector spaces.
-\end{definition}
-
-The cochain complexes arising in classical field theory are naturally convenient vector spaces. 
-The above definition is used in what we mean by quasi-isomorphism between classical field theories, as in Definition \brian{??}.
-
-Throughout the paper we make use of familiar manipulations with spectral sequences arising from filtrations of cochain complexes internal to differentiable vector spaces. 
-A main tool is the classical Eilenberg-Moore comparison theorem, which is stated as follows.
-
-\begin{thm}[Eilenberg-Moore Comparison]
-Let $f : V \to W$ be a map of filtered cochain complexes in an AB4 abelian category.
-Suppose, for each integer $n$ there exists an integer $p$ such that $F_p V^n = 0 = F_p W^n$.
-If there is an integer $r \geq 0$ such that the induced map on the $r$th page of the corresponding spectral sequences 
-\[
-f_r^{pq} :  E_r^{pq} V \to E_r^{pq} W
-\]
-is an isomorphism for all $p,q$, then $f : V \to W$ is a quasi-isomorphism. 
-\end{thm}
-
-The following is the natural definition of a filtered differentiable cochain complex.
-
-\begin{definition}
-A \defterm{filtered differentiable cochain complex} is a sequence of differentiable cochain complexes
-\[
-\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
-\]
-where each map is a monomorphism in each cohomological degree. 
-A filtered differentiable cochain complex is \defterm{complete} if the canonical maps $V \to V / F_n V$ induce an isomorphism $V \cong \lim V / F_n V$. 
-\end{definition}
-
-The category of differentiable vector space is an AB4 category, in fact, it is actually a Grothendieck abelian category.
-
-\begin{thm}[{\cite[Theorem 2.2.1]{Book1}}]
-The category $\DVS$ is a Grothendieck abelian category.
-\end{thm}
-
-In particular, we can freely apply the Eilenberg-Moore comparison result to the types of topological cochain complexes we come across in the BV formalism.
-
-\begin{definition}\label{dfn: pro}
-A \defterm{differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
-\[
-\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
-\]
-where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
-\end{definition}
-
-\subsubsection{The classical BV complex}
-
-\begin{lem}
-If $(E, \omega, Q, I)$ is the data of a classical theory on $M$, then the BV complex
-\[
-\left(\cO(\cE) , Q + \{I,-\}\right)
-\]
-is a differentiable pro-cochain complex.
-More generally, the classical factorization algebra of observables $\Obs$ is a factorization algebra in differentiable pro-cochain complexes. 
-\end{lem}
-
-The above lemma used the natural filtration on the classical BV complex given by polynomial degree of observables. 
-Since the free part of the differential $Q$ always preserves this filtration, the first term of the resulting spectral sequence simply computes the cohomology of the underlying free theory. 
-The differential on the higher pages depend on the interacting part of of the action.
-
-\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
-Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.  
-There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
-\end{lemma}
-\begin{proof}
-The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
-We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
-natural decreasing filtration 
-\[
-F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
-\]
-which is compatible with both $Q$ and $\{I,-\}$ separately.
-The associated graded of this filtration is the differentiable cochain complex given by
-\[
-\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
-\]
-This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
-Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
-\brian{shall we say a word about convergence?
-This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.} \chris{Does convergence require that the interaction is polynomial, or alternatively does this bound the number of differentials appearing in the spectral sequence?}
-\end{proof}
-
-\begin{lemma} \label{invert_quis_lemma}
-Any quasi-isomorphism of differentiable cochain complexes admits a quasi-inverse.
-\end{lemma}
-\brian{I think Pavel had something to say for this lemma.}
 
@@
 
-We may extend the discussion to the case of Riemannian manifolds $M$, where we replace $V$ by the vector bundle $TM$.
+We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
 Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
-\[\sd{\d}\colon \Gamma(M, \Sigma)\rightarrow \Gamma(M, \Sigma^*).\]
+\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]
 
@@
 \begin{prop}
-Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma)$. Then
+Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
 \[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
@@
 \begin{prop}
-Suppose $Q\in\Sigma$ and $X\in\Omega^p(M)$. Then
+Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
 \[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]

### 2020-01-05 paper.tex
sec2and3

--- 2020-01-02 paper.tex
@@
 
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the space of smooth sections of $E$.
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}).
-An element of $\oloc(\cE)$ will be denoted by
-\[\int_M \omega(\phi, \phi', \dots),\]
-where $\omega$ is a density on $M$ depending on infinite jets of sections of $E$.
-Note, however, that the integral here is a formal symbol.
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
+We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
+For conventions on functions on topological vector spaces we refer to Appendix \ref{appx: top}. 
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
+\[\int_M f (\phi, \phi', \dots),\]
+where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
+The space of local functionals can be viewed as a subspace
+\[
+\oloc(\cE) \subset \cO(\cE_c)
+\]
+where we the integral symbol makes sense in earnest on sections which are compactly supported.
 We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
+
+Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
+By definition, this is 
+\[
+{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
+\]
+where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
+When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
+There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
 
@@
 \[
-Q \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
+Q_{BV} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{BV}^2 = 0$ and $(2)$: the pair $(\cE , Q_{BV})$ is an elliptic complex;
 \item a map of bundles
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q e_1) = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{BV} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{BV} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 \[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE).
-\]
-
-The BV bracket satisfies the symmetry property
-\[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
-and the Leibniz rule
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
+\]
+This bracket is of cohomological degree $+1$. 
+To define the bracket, first note that there is a linear map
+\[
+\d_{dR} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+\]
+defined as follows. 
+A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
+\[
+D_1(-) \cdots D_n(-) \Omega
+\]
+where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
+Without loss of generality, suppose $F$ is of this form. 
+Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
+\[
+\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
+\]
+where $\phi$ denotes a compactly supported section. 
+Define the symmetric multilinear map
+\[
+\begin{array}{ccccl}
+\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
+& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\end{array}
+\]
+Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
+
+The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega : E \cong E^! [-1]$ and hence an isomorphism of local functions
+\[
+\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+\]
+We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
+In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
+\[
+X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
+\]
+This is the Hamiltonian vector field corresponding to $F$. 
+Finally, the BV bracket between local functionals $F, G$ is defined by
+\[
+\{F, G\} = X_F (G) .
+\]
+
+The BV bracket enjoys the graded skew symmetry property
+\[
+\{F, G\} = (-1)^{|F| |G|} \{G, F\}
+\]
+as well as the graded Jacobi identity.
+This bracket together wtih $Q_{BV}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
+Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
 
@@
 \[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the classical master equation 
-\[Q I + \frac{1}{2} \{I,I\} = 0 .\]
+of cohomological degree zero satisfying the Maurer-Cartan equation
+\[Q_{BV} I + \frac{1}{2} \{I,I\} = 0 .\]
 \end{definition}
 
-Given a classical field theory $(E, Q, \omega, I)$ we denote by
-\[S_{\mr{BV}} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
+Given a classical field theory $(E, Q_{BV}, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q_{BV} e) + I\in \oloc(E)\]
 the BV action of the theory.
+
+\begin{remark}
+The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
+The operator $Q_{BV}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
+\end{remark}
 
@@
 \begin{definition}
-A \defterm{morphism} $F\colon (E, Q, \omega, I) \rightsquigarrow (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
-A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory.
+A \defterm{morphism} $F\colon (E, Q_{BV}, \omega, I) \rightsquigarrow (E', Q_{BV}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{BV}, Q_{BV}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q_{BV}')$ is a quasi-isomorphism.
+A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
 \end{definition}
@@
 Suppose the BV action is
-\[S_{BV} = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
+\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
 where $S_0$ and $S_1$ are independent of $\phi$.
@@
 S(F(e)) &= S(e, S_1(e), 0) \\
-&= S_0(e) + \frac 12 \dvol_M \int S_1(e)^2 - 2 S_1(e)^2) \\
+&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
 &= S_0(e) - \frac 12 S_1(e)^2 \\
@@
 
-In this section we define what it means for a Lie algebra to act on a classical field theory.
-Let $(E, Q,\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
+Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
 Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
+\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
 parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n).\]
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
+where $x_j \in \fg$. 
 We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
 \[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the BV bracket by the formula
+and the degree $+1$ BV bracket by the formula
 \[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
+The operator $Q_{BV}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{BV} f)(x_1,\ldots, x_n) = Q_{BV} f(x_1,\ldots, x_n) 
+\]
+where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
+The differentials $\d_{CE}$ and $Q_{BV}$ are compatible in the sense that $(\d_{CE} + Q_{BV})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{BV}$. 
+Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
 
@@
 \label{infinitesimal_action_def}
-Let $(E, Q,\omega, I)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
-\[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
-where $I^{(0)} = I$ and $I^{(k)}\colon \fg^{\otimes k}\rightarrow \oloc(\cE)$, which satisfies the Maurer--Cartan equation
-\[(Q + \d_{CE}) I_\rho + \frac{1}{2} \{I_\rho, I_\rho\} = 0.\]
+Let $(E, Q_{BV},\omega, I)$ be a classical field theory. 
+\begin{itemize}
+\item[(1)]
+An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{BV}, \omega, I)$ is an element of cohomological degree zero 
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
+where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $I_\fg^{(0)} = I$;
+\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
+\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
+\[(\d_{CE} + Q_{BV}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\end{itemize}
+\item[(2)]
+For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
+An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
+\[
+Q_{BV} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+\]
+is elliptic as a $C^\bu(\fg)$-linear differential operator.
+\end{itemize}
 \end{definition}
+
+\begin{rmk}
+\brian{Explain $C^\bu(\fg)$-linear elliptic}
+\end{rmk}
+
+\begin{rmk}
+We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
+One can also formulate actions of a Lie algebra on a classical theory in these terms. 
+The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
+\[
+\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
+\]
+is satisfied.
+\end{rmk}
+
+\begin{rmk}
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
+Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{BV} + \{I_\fg, -\}$ 
+defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
+By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
+\[
+\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
+\]
+combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
+\end{rmk}
 
@@
 \label{group_action_def}
-Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
+Let $(E, Q_{BV}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{BV}, \omega, I)$ is given by the following data:
 \begin{itemize}
@@
 
-\item An action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$.
+\item An action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$.
 \end{itemize}
@@
 
-\item For every $x\in\fg$, the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{itemize}
@@
 \[
-Q = \ell_1 + S^{free}_{BRST}.
+Q_{BV} = \ell_1 + S^{free}_{BRST}.
 \]
@@
 \[
-I_{\mr{BV}} = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
+I = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
 \]
@@
 \begin{lemma}
-Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q, \omega, I)$ is a classical BV theory.
+Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{BV}, \omega, I)$ is a classical BV theory.
 \end{lemma}
 
-We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+We refer to the classical BV theory $(E, Q_{BV}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
 In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
@@
 \begin{definition}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
+\label{dfn: super}
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
 \end{definition}
@@
 \begin{definition} \label{def:twisting}
-Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+Suppose $(E, Q_{BV}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{BV} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 \end{prop}
+
+\begin{proof}
+The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
+Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
+Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
+
+Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
+The operator 
+\end{proof}
+
 \pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
@@
 We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
+Let $\cE_{\rm SYM}$ denote the space of BV fields.
 
@@
 
-We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
@@
 
-\begin{thm}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)}$ satisfies the classical master equation
+The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
+
+\begin{thm}\label{thm:gaugemultipletSUSY}
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ defines satisfies the classical master equation
 \[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-\label{thm:gaugemultipletSUSY}
+Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
 \end{thm}

### 2020-01-05 paper.tex

--- 2020-01-05 paper.tex
@@
 \end{proof}
+
+%\begin{landscape}
+\begin{figure}
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
+%\end{landscape}
 

### 2020-01-06 paper.tex
merging

--- 2020-01-05 paper.tex
@@
 
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
-We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
-For conventions on functions on topological vector spaces we refer to Appendix \ref{appx: top}. 
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
-\[\int_M f (\phi, \phi', \dots),\]
-where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
-The space of local functionals can be viewed as a subspace
-\[
-\oloc(\cE) \subset \cO(\cE_c)
-\]
-where we the integral symbol makes sense in earnest on sections which are compactly supported.
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the space of smooth sections of $E$.
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}).
+An element of $\oloc(\cE)$ will be denoted by
+\[\int_M \omega(\phi, \phi', \dots),\]
+where $\omega$ is a density on $M$ depending on infinite jets of sections of $E$.
+Note, however, that the integral here is a formal symbol.
 We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
-
-Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
-By definition, this is 
-\[
-{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
-\]
-where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
-When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
-There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
 
@@
 \[
-Q_{BV} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{BV}^2 = 0$ and $(2)$: the pair $(\cE , Q_{BV})$ is an elliptic complex;
+Q \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
 \item a map of bundles
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{BV} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{BV} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q e_1) = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 \[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
-\]
-This bracket is of cohomological degree $+1$. 
-To define the bracket, first note that there is a linear map
-\[
-\d_{dR} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
-\]
-defined as follows. 
-A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
-\[
-D_1(-) \cdots D_n(-) \Omega
-\]
-where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
-Without loss of generality, suppose $F$ is of this form. 
-Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
-\[
-\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
-\]
-where $\phi$ denotes a compactly supported section. 
-Define the symmetric multilinear map
-\[
-\begin{array}{ccccl}
-\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
-& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
-\end{array}
-\]
-Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
-This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
-
-The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega : E \cong E^! [-1]$ and hence an isomorphism of local functions
-\[
-\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
-\]
-We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
-In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
-\[
-X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
-\]
-This is the Hamiltonian vector field corresponding to $F$. 
-Finally, the BV bracket between local functionals $F, G$ is defined by
-\[
-\{F, G\} = X_F (G) .
-\]
-
-The BV bracket enjoys the graded skew symmetry property
-\[
-\{F, G\} = (-1)^{|F| |G|} \{G, F\}
-\]
-as well as the graded Jacobi identity.
-This bracket together wtih $Q_{BV}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
-Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE).
+\]
+
+The BV bracket satisfies the symmetry property
+\[\{f, g\} = (-1)^{|f| |g|} \{g, f\}\]
+and the Leibniz rule
 
@@
 \[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{BV} I + \frac{1}{2} \{I,I\} = 0 .\]
+of cohomological degree zero satisfying the classical master equation 
+\[Q I + \frac{1}{2} \{I,I\} = 0 .\]
 \end{definition}
 
-Given a classical field theory $(E, Q_{BV}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{BV} e) + I\in \oloc(E)\]
+Given a classical field theory $(E, Q, \omega, I)$ we denote by
+\[S_{\mr{BV}} = \frac{1}{2} \int_M \omega(e, Q e) + I\in \oloc(E)\]
 the BV action of the theory.
@@
 \begin{remark}
-The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
-The operator $Q_{BV}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
-Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
-\end{remark}
-
-\begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondingly, $Q$ is simply an odd operator.
 \end{remark}
@@
 \begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{BV}, \omega, I) \rightsquigarrow (E', Q_{BV}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{BV}, Q_{BV}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q_{BV}')$ is a quasi-isomorphism.
-A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
+A \defterm{morphism} $F\colon (E, Q, \omega, I) \rightsquigarrow (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
+A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory.
 \end{definition}
@@
 Suppose the BV action is
-\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
+\[S_{BV} = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
 where $S_0$ and $S_1$ are independent of $\phi$.
@@
 S(F(e)) &= S(e, S_1(e), 0) \\
-&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
+&= S_0(e) + \frac 12 \dvol_M \int S_1(e)^2 - 2 S_1(e)^2) \\
 &= S_0(e) - \frac 12 S_1(e)^2 \\
@@
 
-In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
-Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+In this section we define what it means for a Lie algebra to act on a classical field theory.
+Let $(E, Q,\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
 Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
 parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
-where $x_j \in \fg$. 
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n).\]
 We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
 \[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the degree $+1$ BV bracket by the formula
+and the BV bracket by the formula
 \[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-The operator $Q_{BV}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{BV} f)(x_1,\ldots, x_n) = Q_{BV} f(x_1,\ldots, x_n) 
-\]
-where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{BV}$ are compatible in the sense that $(\d_{CE} + Q_{BV})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{BV}$. 
-Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
 
@@
 \label{infinitesimal_action_def}
-Let $(E, Q_{BV},\omega, I)$ be a classical field theory. 
-\begin{itemize}
-\item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{BV}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$;
-\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
-\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{BV}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
-\end{itemize}
-\item[(2)]
-For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
-\[
-Q_{BV} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
-\]
-is elliptic as a $C^\bu(\fg)$-linear differential operator.
-\end{itemize}
+Let $(E, Q,\omega, I)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q, \omega, I)$ is an element
+\[I_{\rho} = \sum_{k\geq 0} I^{(k)}\in C^\bullet(\fg, \oloc(\cE)),\]
+where $I^{(0)} = I$ and $I^{(k)}\colon \fg^{\otimes k}\rightarrow \oloc(\cE)$, which satisfies the Maurer--Cartan equation
+\[(Q + \d_{CE}) I_\rho + \frac{1}{2} \{I_\rho, I_\rho\} = 0.\]
 \end{definition}
-
-\begin{rmk}
-\brian{Explain $C^\bu(\fg)$-linear elliptic}
-\end{rmk}
-
-\begin{rmk}
-We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
-One can also formulate actions of a Lie algebra on a classical theory in these terms. 
-The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
-\[
-\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
-\]
-is satisfied.
-\end{rmk}
-
-\begin{rmk}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
-Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{BV} + \{I_\fg, -\}$ 
-defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
-By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
-\[
-\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
-\]
-combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
-\end{rmk}
 
@@
 \label{group_action_def}
-Let $(E, Q_{BV}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{BV}, \omega, I)$ is given by the following data:
+Let $(E, Q, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q, \omega, I)$ is given by the following data:
 \begin{itemize}
@@
 
-\item An action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$.
+\item An action $I_\rho$ of its super Lie algebra $\fg$ with $I^{(k)} = 0$ for $k\geq 2$.
 \end{itemize}
@@
 
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\item For every $x\in\fg$, the vector field $X_{I^{(1)}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{itemize}
@@
 \item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
 \end{itemize}
 Together, these data must satisfy the equation
-\[Q_{BRST} S_{BRST} = 0,\]
-where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
+where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
 \end{definition}
@@
 
-From a classical BRST theory $(\cF, S_{BRST})$, one can construct a classical BV theory as follows.
+From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
 Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
@@
 First, we define the free BV theory.
-Split $S_{BRST} = S^{free}_{BRST} + I_{BRST}$, where $I_{BRST}\in\oloc^+(\cF)$ and $S^{free}_{BRST}$ is a quadratic local functional which we may view as defining a map
-\[S^{free}_{BRST}\colon F\rightarrow F^!.\]
+Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
+\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
 The underlying bundle of the BV theory is
@@
 \[
-Q_{BV} = \ell_1 + S^{free}_{BRST}.
+Q = \ell_1 + S^{\mr{free}}_{\mr{BRST}}.
 \]
@@
 \] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
+which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
+\[
+I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
 \]
@@
 \begin{lemma}
-Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{BV}, \omega, I)$ is a classical BV theory.
+Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q, \omega, I)$ is a classical BV theory.
 \end{lemma}
 
-We refer to the classical BV theory $(E, Q_{BV}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
+We refer to the classical BV theory $(E, Q, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+In the case $S_{\mr{BRST}} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
 
@@
 
-\item The BRST action is $S_{BRST} = 0$.
+\item The BRST action is $S_{\mr{BRST}} = 0$.
 \end{itemize}
@@
 \begin{definition}
-\label{dfn: super}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
 \end{definition}
@@
 
-Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
+Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$ \chris{it's a bit unclear here why they're notated differently}. We have action maps
 \[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
@@
 \begin{definition} \label{def:twisting}
-Suppose $(E, Q_{BV}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{BV} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+Suppose $(E, \d, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 \end{prop}
-
-\begin{proof}
-The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
-Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
-Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
-
-Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
-The operator 
-\end{proof}
-
 \pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
@@
 \subsection{A-Type Twists} \label{A_twist_section}
-\chris{...}
+\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
 
@@
 We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
-Let $\cE_{\rm SYM}$ denote the space of BV fields.
 
@@
 
-We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
@@
 
-The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
-
-\begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ defines satisfies the classical master equation
+\begin{thm}
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)}$ satisfies the classical master equation
 \[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
+\label{thm:gaugemultipletSUSY}
 \end{thm}
@@
 \begin{align*}
-S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
 S_{anti} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
@@
 
-We decompose the fields with respect to $\U(5) \hookrightarrow \SO(6)$:
+We decompose the fields with respect to $\mr U(5) \hookrightarrow \SO(6)$:
 \begin{align*}

### 2020-01-07 paper.tex

--- 2020-01-05 paper.tex
@@
 \[
-Q_{BV} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{BV}^2 = 0$ and $(2)$: the pair $(\cE , Q_{BV})$ is an elliptic complex;
+Q_{\mr{BV}} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
 \item a map of bundles
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{BV} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{BV} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 as well as the graded Jacobi identity.
-This bracket together wtih $Q_{BV}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
+This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
 Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
@@
 of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{BV} I + \frac{1}{2} \{I,I\} = 0 .\]
+\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
 \end{definition}
 
-Given a classical field theory $(E, Q_{BV}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{BV} e) + I\in \oloc(E)\]
+Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
 the BV action of the theory.
 
-\begin{remark}
 The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
 In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
-The operator $Q_{BV}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
 Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
-\end{remark}
 
 \begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
 \end{remark}
@@
 \begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{BV}, \omega, I) \rightsquigarrow (E', Q_{BV}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{BV}, Q_{BV}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q_{BV}')$ is a quasi-isomorphism.
+A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 
-\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?}
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
 
@@
 In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
-Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
 Consider the graded vector space
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-The operator $Q_{BV}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{BV} f)(x_1,\ldots, x_n) = Q_{BV} f(x_1,\ldots, x_n) 
+The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
 \]
 where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{BV}$ are compatible in the sense that $(\d_{CE} + Q_{BV})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{BV}$. 
+The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
 Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
@@
 \label{infinitesimal_action_def}
-Let $(E, Q_{BV},\omega, I)$ be a classical field theory. 
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
 \begin{itemize}
 \item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{BV}, \omega, I)$ is an element of cohomological degree zero 
+An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
 \[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
@@
 \item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{BV}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
 \end{itemize}
@@
 \[
-Q_{BV} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
 \]
@@
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{BV} + \{I_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 \label{group_action_def}
-Let $(E, Q_{BV}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{BV}, \omega, I)$ is given by the following data:
+Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
+An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
 \begin{itemize}
@@
 The differential of the free BV theory is
-\[
-Q_{BV} = \ell_1 + S^{free}_{BRST}.
+\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
 \]
@@
 \begin{lemma}
-Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{BV}, \omega, I)$ is a classical BV theory.
+Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
 \end{lemma}
 
-We refer to the classical BV theory $(E, Q_{BV}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
 In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
@@
 \begin{definition} \label{def:twisting}
-Suppose $(E, Q_{BV}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{BV} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 \item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
-
+\end{itemize}
+
+There are a few additional possibilities that occur in dimension 2.
+
+\begin{itemize}
 \item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.
@@
 Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{BV}$ is then the sum of the following terms:
-\begin{align*}
-S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{anti} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
+\begin{align*}
+S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
 I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
@@
 \end{thm}
+
 \begin{proof}

### 2020-01-07 paper.tex
Added 6d (1,0) calculation

@@
 
-\begin{corollary}
+\begin{corollary} \label{Kahler_YM_term_cor}
 Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
@@
 In dimension 6 there are two possible supersymmetry groups by which we can act.  
-There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry, consisting of a pure gauge theory coupled to matter living in a symplectic representation $V$.  
-If $V \iso T^*\gg$, then the $(1,0)$ supersymmetry can be enhanced to $\mc N=(1,1)$ supersymmetry.  
-This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills down to $\RR^6$.
+There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry, consisting of a pure gauge theory coupled to matter living in a symplectic representation $U$.  
+If $U \iso T^*\gg$, then the $(1,0)$ supersymmetry algebra action can be enhanced to an $\mc N=(1,1)$ supersymmetry algebra action.  
+This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills from $\RR^{10}$ down to $\RR^6$.
 
@@
 
-The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sec: couple}. 
-The fields are:
+The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sect:mattermultipletSUSY}. 
+The untwisted fields are given by:
 \begin{itemize}
@@
 
-The interaction terms encoding $\mc N = (1,0)$ supersymmetry $I^{(1)}$ and $I^{(2)}$ are:
-\begin{align*}
-I^{(1)} & = I^{(1)}_{\rm gauge} + I^{(1)}_{\rm matter} + I^{(1)}_{\rm couple} \\
-I^{(2)} & = I^{(2)}_{\rm gauge} + I^{(2)}_{\rm matter} 
-\end{align*}
-where
-\begin{align*}
-I_{\rm gauge}^{(1)}(Q) &= (\Gamma(Q, \lambda), A^*)_\fg + \frac{1}{2}(\rho(F_A), \lambda^*)_\fg \\
-I_{\rm gauge}^{(2)}(Q_1, Q_2) &= \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)_\fg) - \frac{1}{2}((Q_1, \lambda^*),(Q_2, \lambda^*))_\fg - \iota_{\Gamma(Q_1, Q_2)} A c^*\\
-I^{(1)}_{\rm matter} (Q) & = (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
-I^{(2)}_{\rm matter} (Q_1 , Q_2) & =  \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \\
-I^{(1)}_{\rm couple} (Q) & = g (\psi^*, \rho([A, \phi]) Q)_U + \frac{1}{2} g (\lambda^*, Q \mu(\phi,\phi))_\fg 
-%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
-\end{align*}
-
 Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
+The only square zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
 Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
 
-We decompose the fields with respect to $\mr U(5) \hookrightarrow \SO(6)$:
-\begin{align*}
-c & \mapsto A^0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
-A & \mapsto A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3 ; \fg) \oplus \Omega^{0,1}(\CC^3) \\
-\lambda & \mapsto \lambda^0_1 w_1 + \lambda_2^0 w_2 + A^{0,2} w_1 +  \Tilde{\lambda}^{0,2} w_2\in \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \\
-\phi & \mapsto A 
-\end{align*} 
-where the $A^{\bu, \bu}, \lambda^{\bu,\bu}, \Tilde{\lambda}^{\bu,\bu}$ are all $\fg$-valued forms.
-
-\subsubsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
+We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
+\begin{align*}
+c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
+\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
+\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
+\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
+\end{align*} 
+and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
+In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
+&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
+S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
+&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
+I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+\end{align*}
+Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.
+
+\begin{thm}
+The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
+That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with 2-shifted symplectic structure induced from the symplectic pairing on $U$.
+\label{thm:6dholomorphictwist}
+\end{thm}
+
+\begin{proof}
+The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.
+First, we integrate out the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+We then observe that the action includes the terms $\int \dvol  (B_{1,0}, A_{1,0}^*)$ and  $\int \dvol (\nu', \nu^*)$.
+In other words, the pairs $(B_{1,0}, A_{1,0})$ and $(\nu, \nu')$ form BRST doublets, which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+The twisted theory is therefore perturbatively equivalent to the theory with BV action
+\begin{align*}
+ S_{\mr{BV}} &= \int \dvol \bigg( \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})  + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) +  \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* \\
+  &\qquad  + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* + [\lambda_{0}, A_0]\wedge \lambda_{0}^* + \frac{1}{2}[A_0, A_0]A_0^* +  [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^*  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
+\end{proof}
+
+\subsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
 

### 2020-01-07 paper.tex
merge

--- 2020-01-07 paper.tex
@@
 \renewcommand{\Re}{\mathrm{Re}}
-\newcommand{\U}{\mathrm{U}}
+%\newcommand{\U}{\mathrm{U}}
 
@@
 \[
-Q_{\mr{BV}} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
+Q_{BV} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{BV}^2 = 0$ and $(2)$: the pair $(\cE , Q_{BV})$ is an elliptic complex;
 \item a map of bundles
@@
 \item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{BV} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{BV} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
 \end{enumerate}
@@
 as well as the graded Jacobi identity.
-This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
+This bracket together wtih $Q_{BV}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
 Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
@@
 of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+\[Q_{BV} I + \frac{1}{2} \{I,I\} = 0 .\]
 \end{definition}
 
-Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
+Given a classical field theory $(E, Q_{BV}, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q_{BV} e) + I\in \oloc(E)\]
 the BV action of the theory.
 
+\begin{remark}
 The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
-The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$, which is at least quadratic in the fields, satisfying the classical master equation.
+The operator $Q_{BV}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
 Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
+\end{remark}
 
 \begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
 \end{remark}
@@
 
+Next, we formulate the notion of an equivalence of classical BV theories.
+
 \begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+A \defterm{morphism} $F\colon (E, Q_{BV}, \omega, I) \rightsquigarrow (E', Q_{BV}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{BV}, Q_{BV}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q_{BV}')$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 
-\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?}
 
@@
 In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
 Consider the graded vector space
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
+The operator $Q_{BV}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{BV} f)(x_1,\ldots, x_n) = Q_{BV} f(x_1,\ldots, x_n) 
 \]
 where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
+The differentials $\d_{CE}$ and $Q_{BV}$ are compatible in the sense that $(\d_{CE} + Q_{BV})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{BV}$. 
 Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
@@
 \label{infinitesimal_action_def}
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
+Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra. 
 \begin{itemize}
 \item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
+An $L_\infty$ \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{BV}, \omega, I)$ is an element of cohomological degree zero 
 \[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
@@
 \item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\[(\d_{CE} + Q_{BV}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
 \end{itemize}
@@
 \[
-Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+Q_{BV} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
 \]
@@
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{BV} + \{I_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 \label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
-An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
+Let $(E, Q_{BV}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
+An (elliptic) \defterm{action} of $G$ on $(E, Q_{BV}, \omega, I)$ is given by the following data:
 \begin{itemize}
@@
 
-\item An action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$.
+\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
 \end{itemize}
@@
 \item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\item A local functional $S_{BRST} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
 \end{itemize}
 Together, these data must satisfy the equation
-\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
-where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+\[Q_{BRST} S_{BRST} = 0,\]
+where $Q_{BRST}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
 \end{definition}
@@
 
-From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
+From a classical BRST theory $(\cF, S_{BRST})$, one can construct a classical BV theory as follows.
 Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
@@
 First, we define the free BV theory.
-Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
-\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
+Split $S_{BRST} = S^{free}_{BRST} + I_{BRST}$, where $I_{BRST}\in\oloc^+(\cF)$ and $S^{free}_{BRST}$ is a quadratic local functional which we may view as defining a map
+\[S^{free}_{BRST}\colon F\rightarrow F^!.\]
 The underlying bundle of the BV theory is
@@
 \]
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
 The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
+\[
+Q_{BV} = \ell_1 + \{S^{free}_{BRST},-\} .
+\]
 
@@
 \] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
+which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
+\[
+I = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
 \]
@@
 \begin{lemma}
-Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
+Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{BV}, \omega, I)$ is a classical BV theory.
 \end{lemma}
 
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+We refer to the classical BV theory $(E, Q_{BV}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
 In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
@@
 \[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-
+\brian{Looks like you're using a bracket we haven't defined. 
+We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
 \subsection{Examples of Classical Field Theories}
@@
 
-\item The BRST action is $S_{\mr{BRST}} = 0$.
+\item The BRST action is $S_{BRST} = 0$.
 \end{itemize}
@@
 
-\brian{Symplectic, non-polarized version.}
+\brian{Symplectic, non-polarized version needed for 6d N=(1,0).}
 
@@
 Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $T=\Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
+The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
 \end{definition}
@@
 
-Note that the supertranslation Lie algebra $T$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
+Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
 
@@
 \label{dfn: super}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $T$ on the classical theory.
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
 \end{definition}
@@
 
-Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$ \chris{it's a bit unclear here why they're notated differently}. We have action maps
+Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
 \[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
@@
 We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
+\brian{Is this quite right? I think $\alpha$ is something different.
+Physics usually calls the twisting homomorphism the one from the Lorentz group to $G_R$. 
+Also, I think $Q$ is required to be a scalar under the twisting homomorphism.}
+
+Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
+Recall, this means we have a Maurer-Cartan element 
+\[
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
+Define
+\[
+I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
+\]
+Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
 
 \begin{definition} \label{def:twisting}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+Suppose $(E, Q_{BV}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The \defterm{$Q$-twisted classical field theory} is the classical field theory 
+\[
+\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)
+\]
+where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 \begin{prop}
-The collection $(E^Q, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$ is a classical field theory.
+The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
 \end{prop}
@@
 \subsection{A-Type Twists} \label{A_twist_section}
-\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
+\chris{...}
 
@@
 \item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
-\end{itemize}
-
-There are a few additional possibilities that occur in dimension 2.
-
-\begin{itemize}
+
 \item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.
@@
 \begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ defines satisfies the classical master equation
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ satisfies the classical master equation
 \[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
@@
 Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
-\begin{align*}
-S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+The BV action of the twisted theory $S_{BV}$ is then the sum of the following terms:
+\begin{align*}
+S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{anti} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
 I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
@@
 \end{thm}
-
 \begin{proof}
@@
 
-We decompose the fields with respect to $\mr U(5) \hookrightarrow \SO(6)$:
+We decompose the fields with respect to $\U(5) \hookrightarrow \SO(6)$:
 \begin{align*}

### 2020-01-07 paper.tex

--- 2020-01-07 paper.tex
@@
 The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
+
 In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
 The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+
 Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
@@
 \end{remark}
+
+Next, we formulate the notion of an equivalence of classical BV theories.
 
@@
 \]
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
 The differential of the free BV theory is
@@
 \]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
 
@@
 We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
+\brian{Is this quite right? I think $\alpha$ is something different.
+Physics usually calls the twisting homomorphism the one from the Lorentz group to $G_R$. 
+Also, I think $Q$ is required to be a scalar under the twisting homomorphism.}
+
+Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
+Recall, this means we have a Maurer-Cartan element 
+\[
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
+Define
+\[
+I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
+\]
+Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
 

### 2020-01-07 paper.tex
typo fix

--- 2020-01-07 paper.tex
@@
 The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
-That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with 2-shifted symplectic structure induced from the symplectic pairing on $U$.
+That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
 \label{thm:6dholomorphictwist}
@@
 \begin{align*}
- S_{\mr{BV}} &= \int \dvol \bigg( \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})  + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) +  \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* \\
+ S_{\mr{BV}} &= \int \Omega \bigg( (\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})  + (\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \frac 12 (F_{0,2} \wedge \lambda_{0,2}^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0 \wedge \psi_{0,1}^*) +  \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* \\
   &\qquad  + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* + [\lambda_{0}, A_0]\wedge \lambda_{0}^* + \frac{1}{2}[A_0, A_0]A_0^* +  [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^*  \bigg).
@@
 \end{proof}
+
+\begin{remark}
+This theory is in general only $\ZZ/2\ZZ$-graded.
+If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to saythis more carefully}.
+\end{remark}
 

### 2020-01-07 paper.tex
Edited 6d (1,1) section

@@
 
-\begin{remark}
+\begin{remark} \label{6d_BF_remark}
 This theory is in general only $\ZZ/2\ZZ$-graded.
-If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to saythis more carefully}.
+If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to complete this and say it more carefully}.
 \end{remark}
@@
 
-Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills on $\RR^6$ as $c$, the ghost, along with:
+There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$.
+This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.
+Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
 \begin{itemize}
@@
 \end{itemize}
+
+We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}
 
@@
 
-We already considered the holomorphic twist in the previous section.
-The remaining three classes are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
+We already considered the holomorphic twist in the previous section: it admits the following description.
+
+\begin{theorem} \label{6d_holo_twist_thm}
+The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e.
+the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
+\end{theorem}
+
+\begin{proof}
+Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.
+One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
+\end{proof}
+
+The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
 
 \begin{theorem} \label{6d_rk11_twist_thm}
-The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$.
+The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$.
 This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
@@
 \begin{proof}
-
+We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
+That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 7-dimensions.
 \end{proof}
@@
 \begin{theorem} \label{6d_rk22_twist_thm}
-The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
+The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
 \end{theorem}
@@
 \begin{proof}
-
+We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.
+That is, we apply Proposition \ref{CS_diml_red_prop}.
 \end{proof}

### 2020-01-07 paper.tex
typos and 5d edits

@@
 The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sect:mattermultipletSUSY}.
+
+\vspace{-10pt}
+\paragraph{Fields:}
 The untwisted fields are given by:
@@
 
+\vspace{-10pt}
+\paragraph{Twisting data:}
 Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
@@
 &\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
-S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
+S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu' \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
 &\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
@@
 This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.
-Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
+
+\vspace{-10pt}
+\paragraph{Fields:} Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
 \begin{itemize}
@@
 
+\vspace{-10pt}
+\paragraph{Twisting data:}
 In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
@@
 \vspace{-10pt}
-\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=1$ supercharges.  We can describe the supersymmetry action as follows.
-\begin{prop}
-The supersymmetry action $I^{(1)} = I^{(1)}_{\mr{gauge}} + I^{(1)}_{\mr{matter}} + I^{(1)}_{\mr{couple}}$ and $I^{(2)} = I^{(2)}_{\mr{gauge}} + I^{(2)}_{\mr{matter}}$ from Section \ref{6d_10_section} restricts to 5-dimensional $\mc N=1$ fields as follows:
-\begin{align*}
-I^{(1)}_{\mr{gauge}}(Q) &= \int \\
-I^{(1)}_{\mr{matter}}(Q) &= \int \\
-I^{(2)}_{\mr{couple}}(Q_1,Q_2) &= \int  \\
-I^{(2)}_{\mr{gauge}}(Q_1,Q_2) &= \int \\
-I^{(2)}_{\mr{matter}}(Q_1,Q_2) &= \int 
-\end{align*}
-\end{prop}
-
-\vspace{-10pt}
 \paragraph{Twisting data:}
@@
 \begin{theorem} \label{5d_holo_twist_theorem}
-The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory $\mr{Map}(S \times L_{\mr{dR}}, U//G)$.
+The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U/\!/G)$.
 \end{theorem}
@@
 \begin{proof}
-This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in \chris{ref} above, by applying Proposition \ref{CS_diml_red_prop}.
+This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in Theorem \ref{thm:6dholomorphictwist} above, by applying Proposition \ref{CS_diml_red_prop} to dimensionally reduce along one of the non-invariant Calabi-Yau directions.
 \end{proof}
@@
 We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} Let $Q, Q_1$ and $Q_2$ be $\mc N=2$ supercharges.  We can describe the supersymmetry action as follows.
-\begin{prop}
-The supersymmetry action $I^{(1)}$ and $I^{(2)}$ from \chris{ref} restricts to 5-dimensional $\mc N=1$ fields as
-\begin{align*}
-I^{(1)}(Q) &= \int \\
-I^{(2)}(Q_1,Q_2) &= \int 
-\end{align*}
-\end{prop}
-
-\begin{proof}
-This follows by restricting the 6d $\mc N=(1,1)$ supersymmetry action further to $\mr O(5)$.  Indeed \chris{...}
-\end{proof}
 
@@
 \begin{proof}
-
+As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 6-dimensions.
 \end{proof}
@@
 \begin{theorem} \label{5d_rk4_twist_thm}
-The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on ah an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$.
+The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}(M_5, B\gg)$.
 \end{theorem}
@@
 \begin{proof}
-
+We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.
+That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
 \end{proof}

### 2020-01-08 paper.tex
4d

--- 2020-01-07 paper.tex
@@
 
-We will call $\alpha$ in a twisting datum a \defterm{twisting homomorphism}.
-\brian{Is this quite right? I think $\alpha$ is something different.
-Physics usually calls the twisting homomorphism the one from the Lorentz group to $G_R$. 
-Also, I think $Q$ is required to be a scalar under the twisting homomorphism.}
-
 Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
@@
 \begin{remark}
-Without a twisting homomorphism $\alpha$, we obtain a $\ZZ/2$-graded classical field theory
+Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
 \[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
@@
 \end{align*} 
+\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
 and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
@@
 \subsection{$\cN=1$ with chiral multiplet matter} 
+There is a minimal supersymmetric field theory with $\cN=1$ supersymmetry consisting of a pure gauge theory coupled to supersymmetric matter depending on a complex representation $R$.
+
+%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.
+
+The field content for the 4-dimensional $\cN=1$ super Yang-Mills theory coupled to chiral matter is given by:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
+\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^1(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
+\item scalars: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
+\item fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
+\end{itemize}
+
 There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
-For concreteness, we will fix a nonzero supercharge of negative chirality $$Q = Q_- \in S_-$$ to twist by. 
+Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
 Such supercharges are minimal (i.e. have two dimensional image).  
@@
 
+We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
+The fields of the pure Yang-Mills part decomposes as:
+\begin{align*}
+c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
+A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
+\lambda_- & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
+\lambda_+ & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) \\
+\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R^*) \\
+\Bar{\phi} & \mapsto \gamma_0 \in \Omega^{2,2}(\CC^2 ; R) \\
+\psi_+ & \mapsto \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) \\
+\psi_- & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R)
+\end{align*}
+and their antifields:
+\begin{align*}
+c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
+A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
+\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
+\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
+\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
+\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
+\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
+\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
+\end{align*}
+
+The untwisted action functionals decompose as follows.
+
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
+S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
+&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
+I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
+I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\lambda_0^*)^2.
+\end{align*}
+Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}4$.
+
 \begin{prop}[See also \cite{SWchar}]
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
 \end{prop}
+
+\begin{proof}
+The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
+First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int \dvol  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int \dvol (\phi, \psi_0^*)$.  
+Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+ S_{\mr{BV}} &= \int \bigg( (B_{2,1} \ol \dd_{A_{0,1}} A_{0})  + B_{2,0} F_{0,2} + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} + \beta_{2,1} \dbar_{A_{0,1}} \gamma_0 \\ 
+  &\qquad  + [A_{0,2}, A_0]\wedge B_{2,0} + \frac{1}{2}[A_0, A_0]B_{2,2} +  [\gamma_0, A_0]\wedge \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1}  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
+ \end{proof}
 

### 2020-01-08 paper.tex
merging

--- 2020-01-07 paper.tex
@@
 
-\brian{Symplectic, non-polarized version needed for 6d N=(1,0).}
+\brian{Symplectic, non-polarized version needed for 6d N=(1,0).} \chris{following Brian's suggestion I've used the term: holomorphic BF theory coupled to a higher holomorphic symplectic boson, valued in a representation $U$.
+If we continue to use that term, we should explain it here.}
 
@@
 
-\begin{landscape}
+%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
+
+% \begin{landscape}
+% \begin{figure}
+% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+% \node (825) [right=of 82] {};
+% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+% 
+% \draw[arrow] (101) -- (91);
+% \draw[arrow] (91) -- (81);
+% \draw[arrow] (91) -- (82);
+% \draw[arrow] (81) -- (71);
+% \draw[arrow] (82) -- (71);
+% \draw[arrow] (82) -- (72);
+% \draw[arrow] (83) -- (73);
+% \draw[arrow] (71) -- (61);
+% \draw[arrow] (71) -- (62);
+% \draw[arrow] (72) -- (62);
+% \draw[arrow] (72) -- (63);
+% \draw[arrow] (73) -- (65);
+% \draw[arrow] (61) -- (51);
+% \draw[arrow] (62) -- (51);
+% \draw[arrow] (62) -- (52);
+% \draw[arrow] (63) -- (53);
+% \draw[arrow] (64) -- (52);
+% \draw[arrow] (64) -- (54);
+% \draw[arrow] (65) -- (54);
+% \draw[arrow] (51) -- (41);
+% \draw[arrow] (51) -- (42);
+% \draw[arrow] (52) -- (42);
+% \draw[arrow] (52) -- (43);
+% \draw[arrow] (53) -- (43);
+% \draw[arrow] (54) -- (43);
+% \draw[arrow] (54) -- (44);
+% \draw[arrow] (54) -- (45);
+% \draw[arrow] (41) -- (31);
+% \draw[arrow] (42) -- (31);
+% \draw[arrow] (42) -- (32);
+% \draw[arrow] (43) -- (32);
+% \draw[arrow] (44) -- (32);
+% \draw[arrow] (45) -- (32);
+% \draw[arrow] (31) -- (21);
+% \draw[arrow] (31) -- (22);
+% \draw[arrow] (32) -- (22);
+% 
+% \node (2d) [dimension, left=of 21] {2d};
+% \node (3d) [dimension, above=of 2d] {3d};
+% \node (4d) [dimension, above=of 3d] {4d};
+% \node (5d) [dimension, above=of 4d] {5d};
+% \node (6d) [dimension, above=of 5d] {6d};
+% \node (7d) [dimension, above=of 6d] {7d};
+% \node (8d) [dimension, above=of 7d] {8d};
+% \node (9d) [dimension, above=of 8d] {9d};
+% \node (10d) [dimension, above=of 9d] {10d};
+% \end{tikzpicture}
+% \caption{Orbits of square-zero supercharges.}
+% \label{fig:superchargeorbits}
+% \end{figure}
+% \end{landscape}
+
+\section{Supersymmetric Yang--Mills theories}
+
+In this section we construct supersymmetry action on super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
+\begin{itemize}
+\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.
+
+\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
+
+\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
+
+\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
+\end{itemize}
+
+There are a few additional possibilities that occur in dimension 2.
+
+\begin{itemize}
+\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.
+
+\item (4 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
+
+\item (2 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
+
+\item (1 supercharge, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
+\end{itemize}
+
+In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills.
+So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.
+
+\subsection{Pure super Yang--Mills theory}
+\label{sect:gaugemultipletSUSY}
+
+We begin with a description of certain pure supersymmetric Yang--Mills theories.
+Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
+Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
+\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
+defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.
+
+\begin{assumption}
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
+\label{assumption:3psi}
+\end{assumption}
+
+Explicitly, we consider the following cases:
+\begin{itemize}
+\item (\textbf{2d $\cN=(\cN_+, 0)$ supersymmetry}) We have $\dim(V) = 2$ and $\Sigma = S_+\otimes W$ for some complex vector space $W$ equipped with a nondegenerate symmetric bilinear pairing.
+Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:2d3psi}.
+
+\item (\textbf{3d $\cN=1$ supersymmetry}) We have $\dim(V) = 3$ and $\Sigma = S$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{4d $\cN=1$ supersymmetry}) We have $\dim(V) = 4$ and $\Sigma = S_+\oplus S_-$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ for a two-dimensional complex symplectic vector space $W_+$.
+Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+
+\item (\textbf{10d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
+\end{itemize}
+
+Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The fields of the Yang--Mills theory are as follows:
+\begin{itemize}
+\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
+
+\item A spinor $\lambda \in \Gamma(V_\RR; \Pi \Sigma \otimes \fg)$.
+
+\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
+\end{itemize}
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
+Let $\cE_{\rm SYM}$ denote the space of BV fields.
+
+Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).
+
+The BRST action is given by
+\[S_{BRST}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+
+We introduce gauge transformations
+\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
+so that the BV action is given by
+\begin{equation}
+S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
+\label{eq:YMBVaction}
+\end{equation}
+
+To simplify the notation, the pairing on $\fg$ from now on will be implicit.
+
+The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
+Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
+The corresponding Hamiltonian is given by
+\begin{equation}
+I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
+\label{eq:YMPoincareaction}
+\end{equation}
+for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
+
+We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
+The action of supersymmetry is given by a linear and quadratic functionals
+\begin{align*}
+I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
+I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
+\end{align*}
+
+The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
+
+\begin{thm}\label{thm:gaugemultipletSUSY}
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ satisfies the classical master equation
+\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
+Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
+\end{thm}
+
+The rest of the section will be devoted to the proof of the above theorem. The classical master equation decomposes into the following equations:
+\begin{align*}
+\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
+\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
+\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
+\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
+\end{align*}
+
+Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
+The rest of the claims will be proved in a sequence of Lemmas.
+To simplify the expressions, we drop the integrals.
+
+\begin{lemma}
+One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
+\label{lm:gaugemultiplet1}
+\end{lemma}
+\begin{proof}
+Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.
+
+The first term gives
+\begin{align*}
+\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
+&= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
+\end{align*}
+
+The second term gives
+\begin{align*}
+\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
+&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast \d_A\ast F_A) Q),
+\end{align*}
+where we have used Proposition \ref{prop:cliffordactionproperty3} and the Bianchi identity in the last line.
+
+By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
+
+Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
+\end{proof}
+
+\begin{remark}
+The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; our proof essentially follows \cite{BaezHuerta}.
+\end{remark}
+
+\begin{lemma}
+One has
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
+\label{lm:gaugemultiplet2}
+\end{lemma}
+\begin{proof}
+Evaluating the equation
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
+on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
+So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
+
+The individual terms are
+\begin{align*}
+\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
+= &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
+&-\frac{1}{2}(\rho(\d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) + \frac{1}{2}(\Gamma(Q_1, \rho(F_A)Q_2), A^*),
+\end{align*}
+\begin{align*}
+(\d_{CE} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
+\end{align*}
+and
+\begin{align*}
+\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
+&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
+\end{align*}
+The total coefficient in front of $A^*$ is
+\[\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) + \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) + L_{\Gamma(Q_1, Q_2)} A - \d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
+Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $-\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
+
+The total coefficient in front of $c^*$ is
+\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
+
+The total coefficient in front of $\lambda^*$ is
+\begin{align*}
+&-\frac{1}{2}\rho(\d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(\d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
+&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\d}_A\lambda - \frac{1}{2}(Q_2, \sd{\d}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\d}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
+\end{align*}
+Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
+\[-\frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
+which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Assumption \ref{assumption:3psi}. Using the Clifford relation this term cancels the rest of the terms.
+\end{proof}
+
+Evaluating the equation
+\[\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
+on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
+
+\begin{lemma}
+\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in\Sigma$.
+\label{lm:gaugemultiplet3}
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+&+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
+\end{align*}
+
+$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
+By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
+The Clifford relation implies that
+\begin{align*}
+\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
+&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
+\end{align*}
+Therefore, again using Assumption \ref{assumption:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
+\end{proof}
+
+\begin{comment}
+\pavel{This might go in the coupling section.}
+We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
+\begin{corollary}
+Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
+Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
+Then the super Poincar\'e algebra
+\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
+obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
+\end{corollary}
+
+\begin{proof}
+This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
+\end{proof}
+
+\begin{remark}
+We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
+\end{remark}
+\end{comment}
+
+\subsection{Matter multiplet}
+\label{sect:mattermultipletSUSY}
+
+In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e.
+the supersymmetric gauged linear $\sigma$-models.
+Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models in \cite[Chapter 3]{DeligneFreed}.
+
+Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
+In addition, fix a real associative algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and denote its complexification by $A$.
+Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
+Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
+We make the following additional assumption.
+
+\begin{assumption}
+For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
+\label{assumption:matter3psi}
+\end{assumption}
+
+Explicitly, we consider the following cases:
+\begin{itemize}
+\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{3d $\cN=1$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{4d $\cN=1$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+\end{itemize}
+
+Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
+\[(av, w) = (v, \sigma(a)w).\]
+Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
+\begin{itemize}
+\item $A_\RR=\RR$, so $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.
+
+\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$.
+A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$.
+Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$.
+So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$.
+In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.
+
+\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
+A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
+Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
+So, the data boils down a symplectic $\fg$-representation $U$.
+\end{itemize}
+
+We are going to construct a theory on $V_\RR$ describing a matter multiplet valued in $P$. The BRST fields are given as follows:
+\begin{itemize}
+\item a scalar $\phi\in\Gamma(V_\RR; P)$;
+\item a spinor $\psi\in\Gamma(V_\RR; \Pi \Sigma^*\otimes_A P)$.
+\end{itemize}
+As usual, we denote the antifields by $\phi^*\in\Gamma(V_\RR; \Pi P)$ and $\psi^*\in\Gamma(V_\RR; \Sigma\otimes_A P)$.
+
+We extend the pairings on $P$ and between $\Sigma$ and $\Sigma^*$ to a pairing between $\Sigma\otimes_A P$ and $\Sigma^*\otimes_A P$ in the following way.
+Given $\sum_i \tilde{s}_i\otimes v_i\in \Sigma^*\otimes_A P$ and $\sum_j s_j\otimes w_j\in\Sigma\otimes_A P$, their pairing is
+\begin{equation}
+\sum_{i, j} \Re((v_i, w_j)^A (s_j, \tilde{s}_i)^A),
+\label{eq:spinorialmatterpairing}
+\end{equation}
+where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
+\[\Gamma\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
+defined by the property
+\[(v, \Gamma(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
+
+The BV action for the matter multiplet is
+\[
+S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
+\]
+where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
+
+It is Poincar\'{e}-invariant with the corresponding Hamiltonian
+\begin{equation}
+I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
+\label{eq:matterPoincareaction}
+\end{equation}
+for $v\in\mf{iso}(V)$.
+
+The action of supersymmetry is given by a linear and quadratic functional:
+\begin{align*}
+I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \\
+I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*))
+\end{align*}
+where $Q, Q_1,Q_2 \in \Sigma$.
+
+We consider the full action of the super Yang--Mills theory
+\[S_{\BV} = S_{\gauge} + S_{\matter}\]
+together with a supersymmetry action functionals
+\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]
+
+The following result states that these functionals encode an off-shell action of the supersymmetry algebra.
+
+\begin{thm}
+The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
+\begin{equation}
+\label{CMEYM}
+\d_{CE} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\end{equation}
+\label{thm:YMSUSY}
+\end{thm}
+
+The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
+\begin{equation}
+\label{CMEYM2}
+\begin{array}{rrrrrr}
+\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
+\d_{CE} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
+\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
+\end{array}
+\end{equation}
+
+The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
+
+The first equation in \eqref{CMEYM2} states that the classical action is supersymmetric.
+
+\begin{lemma} \label{lem:YM1}
+One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+\end{lemma}
+\begin{proof}
+Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.
+
+The first term gives
+\begin{align*}
+\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
+&= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
+\end{align*}
+
+The second term gives
+\begin{align*}
+\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
+&= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
+\end{align*}
+where we have used Proposition \ref{prop:cliffordactionproperty3} in the second line.
+
+The third term gives
+\begin{align*}
+\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
+&= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
+\end{align*}
+where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
+\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
+
+Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
+\end{proof}
+
+Next, we move on to the second equation in \eqref{CMEYM2}.
+
+\begin{lemma} 
+One has
+\begin{equation}\label{CMEYM3}
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
+\end{equation}
+\end{lemma}
+\begin{proof}
+Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action.
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
+So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
+
+The individual terms are:
+\begin{align*}
+\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
+=&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
+\end{align*}
+
+\begin{align*}
+\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
+=& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
+\end{align*}
+
+\[
+(\d_{CE}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+\]
+
+and
+\[
+\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
+\]
+
+We first collect all terms in equation \eqref{CMEYM3} proportional to $\phi^*$:
+\[
+-\frac{1}{2} (Q_1, \rho(\d_A\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d_A \phi) Q_1) + L_{\Gamma(Q_1,Q_2)} \phi + (\iota_{\Gamma(Q_1, Q_2)} A)\phi.
+\]
+
+By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the last two terms.
+
+Next, we collect all terms in equation \eqref{CMEYM3} containing $\psi^*$ and $\psi$:
+\begin{equation}\label{psistar}
+\frac{1}{2} \sd \d_A Q_2(Q_1 \psi)^A + \frac{1}{2} \sd \d_A Q_1(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \d_A \psi - (\iota_{\Gamma(Q_1, Q_2)} A)\psi.
+\end{equation}
+Applying Assumption \ref{assumption:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
+Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\iota_{\Gamma(Q_1,Q_2)}\d_A \psi$ which cancels the remaining terms.
+\end{proof}
+
+\begin{lemma}
+\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+for every $Q_1, Q_2, Q_3\in \Sigma$.
+\end{lemma}
+\begin{proof}
+We have
+\begin{align*}
+\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\end{align*}
+The expression
+$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
+\end{proof}
+
+\part{A Catalogue of Twists}
+
+\section{Dimension 10}
+
+The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with a nondegenerate symmetric bilinear pairing.
+There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
+We concentrate on the first case, the second case being identical.
+So, we fix $W_+=\CC$ and $W_- = 0$.
+
+\subsection{$\cN=(1, 0)$ super Yang--Mills theory}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
+Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
+\end{itemize}
+
+We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
+Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
+The vector representation decomposes as
+\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5),\]
+the semi-spin representation $S_+$ decomposes as
+\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
+and the semi-spin representation $S_-$ decomposes as
+\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
+Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
+Under the above decomposition the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
+\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
+
+\vspace{-10pt}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
+\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
+\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
+\end{itemize}
+We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
+
+The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields.
+We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
+
+\begin{prop}
+Let $(M, \omega)$ be a K\"{a}hler $d$-fold and decompose
+\[\Omega^2(M) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\CC\omega\oplus \Omega^{1, 1}_\perp(M)).\]
+Then
+\begin{enumerate}
+\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\CC\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.
+
+\item For a form $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
+\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
+\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
+
+\item For $\alpha\in\CC\omega$ we have
+\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
+\end{enumerate}
+\end{prop}
+
+\begin{corollary} \label{Kahler_YM_term_cor}
+Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
+\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
+\end{corollary}
+
+Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
+The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
+\begin{align*}
+S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
+I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
+\end{align*}
+
+\begin{thm}
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
+\label{thm:10dholomorphictwist}
+\end{thm}
+
+\begin{proof}
+First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
+\begin{align*}
+S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
+&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
+\end{align*}
+
+Next, we have a term $\int \psi\wedge A_{1, 0}^*$ in the action, i.e.
+$(\psi, A_{1, 0})$ is a BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
+\[
+S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
+\]
+Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
+\end{proof}
+
+\begin{remark}
+A similar claim was previously proved by Baulieu \cite{Baulieu} by adding an auxiliary field to 10d $\mc N=(1, 0)$ super Yang--Mills.
+\end{remark}
+
+\section{Dimension 9}
+
+The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
+So, we fix $W = \CC$.
+
+\subsection{$\cN=1$ super Yang--Mills theory}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
+\end{itemize}
+
+We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
+Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
+
+Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+
+\begin{thm}
+The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
+\end{thm}
+\begin{proof}
+By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
+In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
+
+From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
+By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
+\end{proof}
+
+%\begin{landscape}
 \begin{figure}
@@
 \end{figure}
-\end{landscape}
-
-\section{Supersymmetric Yang--Mills theories}
-
-In this section we construct supersymmetry action on super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
-\begin{itemize}
-\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.
-
-\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
-
-\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
-
-\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
-\end{itemize}
-
-There are a few additional possibilities that occur in dimension 2.
-
-\begin{itemize}
-\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.
-
-\item (4 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
-
-\item (2 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
-
-\item (1 supercharge, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
-\end{itemize}
-
-In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills.
-So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.
-
-\subsection{Pure super Yang--Mills theory}
-\label{sect:gaugemultipletSUSY}
-
-We begin with a description of certain pure supersymmetric Yang--Mills theories.
-Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
-Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
-\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
-defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.
-
-\begin{assumption}
-For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
-\label{assumption:3psi}
-\end{assumption}
-
-Explicitly, we consider the following cases:
-\begin{itemize}
-\item (\textbf{2d $\cN=(\cN_+, 0)$ supersymmetry}) We have $\dim(V) = 2$ and $\Sigma = S_+\otimes W$ for some complex vector space $W$ equipped with a nondegenerate symmetric bilinear pairing.
-Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:2d3psi}.
-
-\item (\textbf{3d $\cN=1$ supersymmetry}) We have $\dim(V) = 3$ and $\Sigma = S$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
-
-\item (\textbf{4d $\cN=1$ supersymmetry}) We have $\dim(V) = 4$ and $\Sigma = S_+\oplus S_-$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
-
-\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ for a two-dimensional complex symplectic vector space $W_+$.
-Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
-
-\item (\textbf{10d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
-\end{itemize}
-
-Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The fields of the Yang--Mills theory are as follows:
-\begin{itemize}
-\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.
-
-\item A spinor $\lambda \in \Gamma(V_\RR; \Pi \Sigma \otimes \fg)$.
-
-\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
-\end{itemize}
-We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
-Let $\cE_{\rm SYM}$ denote the space of BV fields.
-
-Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).
-
-The BRST action is given by
-\[S_{BRST}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
-
-We introduce gauge transformations
-\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
-so that the BV action is given by
-\begin{equation}
-S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
-\label{eq:YMBVaction}
-\end{equation}
-
-To simplify the notation, the pairing on $\fg$ from now on will be implicit.
-
-The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$.
-Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$.
-The corresponding Hamiltonian is given by
-\begin{equation}
-I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
-\label{eq:YMPoincareaction}
-\end{equation}
-for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.
-
-We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
-The action of supersymmetry is given by a linear and quadratic functionals
-\begin{align*}
-I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
-I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
-\end{align*}
-
-The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
-
-\begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ satisfies the classical master equation
-\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
-\end{thm}
-
-The rest of the section will be devoted to the proof of the above theorem. The classical master equation decomposes into the following equations:
-\begin{align*}
-\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
-\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
-\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
-\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
-\end{align*}
-
-Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
-The rest of the claims will be proved in a sequence of Lemmas.
-To simplify the expressions, we drop the integrals.
-
-\begin{lemma}
-One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
-\label{lm:gaugemultiplet1}
-\end{lemma}
-\begin{proof}
-Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.
-
-The first term gives
-\begin{align*}
-\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
-&= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
-\end{align*}
-
-The second term gives
-\begin{align*}
-\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
-&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast \d_A\ast F_A) Q),
-\end{align*}
-where we have used Proposition \ref{prop:cliffordactionproperty3} and the Bianchi identity in the last line.
-
-By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
-
-Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
-\end{proof}
-
-\begin{remark}
-The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; our proof essentially follows \cite{BaezHuerta}.
-\end{remark}
-
-\begin{lemma}
-One has
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
-\label{lm:gaugemultiplet2}
-\end{lemma}
-\begin{proof}
-Evaluating the equation
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
-on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
-So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
-
-The individual terms are
-\begin{align*}
-\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
-= &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
-&-\frac{1}{2}(\rho(\d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) + \frac{1}{2}(\Gamma(Q_1, \rho(F_A)Q_2), A^*),
-\end{align*}
-\begin{align*}
-(\d_{CE} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
-&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
-\end{align*}
-and
-\begin{align*}
-\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
-&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
-\end{align*}
-The total coefficient in front of $A^*$ is
-\[\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) + \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) + L_{\Gamma(Q_1, Q_2)} A - \d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
-Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $-\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.
-
-The total coefficient in front of $c^*$ is
-\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]
-
-The total coefficient in front of $\lambda^*$ is
-\begin{align*}
-&-\frac{1}{2}\rho(\d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(\d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
-&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\d}_A\lambda - \frac{1}{2}(Q_2, \sd{\d}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\d}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
-\end{align*}
-Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
-\[-\frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
-which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Assumption \ref{assumption:3psi}. Using the Clifford relation this term cancels the rest of the terms.
-\end{proof}
-
-Evaluating the equation
-\[\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
-on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
-
-\begin{lemma}
-\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in\Sigma$.
-\label{lm:gaugemultiplet3}
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
-&+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
-\end{align*}
-
-$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
-By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
-The Clifford relation implies that
-\begin{align*}
-\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
-&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
-\end{align*}
-Therefore, again using Assumption \ref{assumption:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
-\end{proof}
-
-\begin{comment}
-\pavel{This might go in the coupling section.}
-We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
-\begin{corollary}
-Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
-Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
-Then the super Poincar\'e algebra
-\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
-obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
-\end{corollary}
-
-\begin{proof}
-This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
-\end{proof}
-
-\begin{remark}
-We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
-\end{remark}
-\end{comment}
-
-\subsection{Matter multiplet}
-\label{sect:mattermultipletSUSY}
-
-In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e.
-the supersymmetric gauged linear $\sigma$-models.
-Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models in \cite[Chapter 3]{DeligneFreed}.
-
-Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a real associative algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and denote its complexification by $A$.
-Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
-Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
-We make the following additional assumption.
-
-\begin{assumption}
-For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
-\label{assumption:matter3psi}
-\end{assumption}
-
-Explicitly, we consider the following cases:
-\begin{itemize}
-\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{3d $\cN=1$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
-
-\item (\textbf{4d $\cN=1$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
-
-\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
-\end{itemize}
-
-Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
-\[(av, w) = (v, \sigma(a)w).\]
-Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
-\begin{itemize}
-\item $A_\RR=\RR$, so $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.
-
-\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$.
-A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$.
-Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$.
-So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$.
-In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.
-
-\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
-Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
-So, the data boils down a symplectic $\fg$-representation $U$.
-\end{itemize}
-
-We are going to construct a theory on $V_\RR$ describing a matter multiplet valued in $P$. The BRST fields are given as follows:
-\begin{itemize}
-\item a scalar $\phi\in\Gamma(V_\RR; P)$;
-\item a spinor $\psi\in\Gamma(V_\RR; \Pi \Sigma^*\otimes_A P)$.
-\end{itemize}
-As usual, we denote the antifields by $\phi^*\in\Gamma(V_\RR; \Pi P)$ and $\psi^*\in\Gamma(V_\RR; \Sigma\otimes_A P)$.
-
-We extend the pairings on $P$ and between $\Sigma$ and $\Sigma^*$ to a pairing between $\Sigma\otimes_A P$ and $\Sigma^*\otimes_A P$ in the following way.
-Given $\sum_i \tilde{s}_i\otimes v_i\in \Sigma^*\otimes_A P$ and $\sum_j s_j\otimes w_j\in\Sigma\otimes_A P$, their pairing is
-\begin{equation}
-\sum_{i, j} \Re((v_i, w_j)^A (s_j, \tilde{s}_i)^A),
-\label{eq:spinorialmatterpairing}
-\end{equation}
-where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
-\[\Gamma\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
-defined by the property
-\[(v, \Gamma(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]
-
-The BV action for the matter multiplet is
-\[
-S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
-\]
-where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
-
-It is Poincar\'{e}-invariant with the corresponding Hamiltonian
-\begin{equation}
-I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
-\label{eq:matterPoincareaction}
-\end{equation}
-for $v\in\mf{iso}(V)$.
-
-The action of supersymmetry is given by a linear and quadratic functional:
-\begin{align*}
-I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \\
-I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*))
-\end{align*}
-where $Q, Q_1,Q_2 \in \Sigma$.
-
-We consider the full action of the super Yang--Mills theory
-\[S_{\BV} = S_{\gauge} + S_{\matter}\]
-together with a supersymmetry action functionals
-\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]
-
-The following result states that these functionals encode an off-shell action of the supersymmetry algebra.
-
-\begin{thm}
-The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
-\begin{equation}
-\label{CMEYM}
-\d_{CE} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
-\end{equation}
-\label{thm:YMSUSY}
-\end{thm}
-
-The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
-\begin{equation}
-\label{CMEYM2}
-\begin{array}{rrrrrr}
-\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
-\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
-\d_{CE} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
-\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
-\end{array}
-\end{equation}
-
-The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
-
-The first equation in \eqref{CMEYM2} states that the classical action is supersymmetric.
-
-\begin{lemma} \label{lem:YM1}
-One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
-\end{lemma}
-\begin{proof}
-Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.
-
-The first term gives
-\begin{align*}
-\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
-&= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
-\end{align*}
-
-The second term gives
-\begin{align*}
-\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
-&= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
-\end{align*}
-where we have used Proposition \ref{prop:cliffordactionproperty3} in the second line.
-
-The third term gives
-\begin{align*}
-\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
-&= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
-\end{align*}
-where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
-\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
-
-Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
-\end{proof}
-
-Next, we move on to the second equation in \eqref{CMEYM2}.
-
-\begin{lemma} 
-One has
-\begin{equation}\label{CMEYM3}
-\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
-\end{equation}
-\end{lemma}
-\begin{proof}
-Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action.
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
-So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
-
-The individual terms are:
-\begin{align*}
-\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
-=&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
-\end{align*}
-
-\begin{align*}
-\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
-=& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
-\end{align*}
-
-\[
-(\d_{CE}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
-\]
-
-and
-\[
-\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
-\]
-
-We first collect all terms in equation \eqref{CMEYM3} proportional to $\phi^*$:
-\[
--\frac{1}{2} (Q_1, \rho(\d_A\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d_A \phi) Q_1) + L_{\Gamma(Q_1,Q_2)} \phi + (\iota_{\Gamma(Q_1, Q_2)} A)\phi.
-\]
-
-By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the last two terms.
-
-Next, we collect all terms in equation \eqref{CMEYM3} containing $\psi^*$ and $\psi$:
-\begin{equation}\label{psistar}
-\frac{1}{2} \sd \d_A Q_2(Q_1 \psi)^A + \frac{1}{2} \sd \d_A Q_1(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \d_A \psi - (\iota_{\Gamma(Q_1, Q_2)} A)\psi.
-\end{equation}
-Applying Assumption \ref{assumption:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
-Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\iota_{\Gamma(Q_1,Q_2)}\d_A \psi$ which cancels the remaining terms.
-\end{proof}
-
-\begin{lemma}
-\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
-for every $Q_1, Q_2, Q_3\in \Sigma$.
-\end{lemma}
-\begin{proof}
-We have
-\begin{align*}
-\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
-\end{align*}
-The expression
-$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
-\end{proof}
-
-\part{A Catalogue of Twists}
-
-\section{Dimension 10}
-
-The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with a nondegenerate symmetric bilinear pairing.
-There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
-We concentrate on the first case, the second case being identical.
-So, we fix $W_+=\CC$ and $W_- = 0$.
-
-\subsection{$\cN=(1, 0)$ super Yang--Mills theory}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
-Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
-\end{itemize}
-
-We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
-Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
-The vector representation decomposes as
-\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5),\]
-the semi-spin representation $S_+$ decomposes as
-\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
-and the semi-spin representation $S_-$ decomposes as
-\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
-Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
-Under the above decomposition the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
-\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
-
-\vspace{-10pt}
-\paragraph{Fields:} The BRST fields are given by:
-\begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
-\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
-\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
-\end{itemize}
-We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
-
-The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields.
-We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
-
-\begin{prop}
-Let $(M, \omega)$ be a K\"{a}hler $d$-fold and decompose
-\[\Omega^2(M) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\CC\omega\oplus \Omega^{1, 1}_\perp(M)).\]
-Then
-\begin{enumerate}
-\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\CC\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.
-
-\item For a form $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
-\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
-
-\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
-\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]
-
-\item For $\alpha\in\CC\omega$ we have
-\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
-\end{enumerate}
-\end{prop}
-
-\begin{corollary} \label{Kahler_YM_term_cor}
-Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
-\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
-\end{corollary}
-
-Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
-\begin{align*}
-S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
-I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
-\end{align*}
-
-\begin{thm}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
-\label{thm:10dholomorphictwist}
-\end{thm}
-
-\begin{proof}
-First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
-\begin{align*}
-S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
-\end{align*}
-
-Next, we have a term $\int \psi\wedge A_{1, 0}^*$ in the action, i.e.
-$(\psi, A_{1, 0})$ is a BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
-The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
-\[
-S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
-\]
-Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
-\end{proof}
-
-\begin{remark}
-A similar claim was previously proved by Baulieu \cite{Baulieu} by adding an auxiliary field to 10d $\mc N=(1, 0)$ super Yang--Mills.
-\end{remark}
-
-\section{Dimension 9}
-
-The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
-So, we fix $W = \CC$.
-
-\subsection{$\cN=1$ super Yang--Mills theory}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
-\end{itemize}
-
-We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
-Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
-
-Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-
-\begin{thm}
-The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
-\end{thm}
-\begin{proof}
-By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
-In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
-
-From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
-By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
-\end{proof}
-
-%\begin{landscape}
-\begin{figure}
-\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-\node (825) [right=of 82] {};
-\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-
-\draw[arrow] (101) -- (91);
-\draw[arrow] (91) -- (81);
-\draw[arrow] (91) -- (82);
-\draw[arrow] (81) -- (71);
-\draw[arrow] (82) -- (71);
-\draw[arrow] (82) -- (72);
-\draw[arrow] (83) -- (73);
-\draw[arrow] (71) -- (61);
-\draw[arrow] (71) -- (62);
-\draw[arrow] (72) -- (62);
-\draw[arrow] (72) -- (63);
-\draw[arrow] (73) -- (65);
-\draw[arrow] (61) -- (51);
-\draw[arrow] (62) -- (51);
-\draw[arrow] (62) -- (52);
-\draw[arrow] (63) -- (53);
-\draw[arrow] (64) -- (52);
-\draw[arrow] (64) -- (54);
-\draw[arrow] (65) -- (54);
-\draw[arrow] (51) -- (41);
-\draw[arrow] (51) -- (42);
-\draw[arrow] (52) -- (42);
-\draw[arrow] (52) -- (43);
-\draw[arrow] (53) -- (43);
-\draw[arrow] (54) -- (43);
-\draw[arrow] (54) -- (44);
-\draw[arrow] (54) -- (45);
-\draw[arrow] (41) -- (31);
-\draw[arrow] (42) -- (31);
-\draw[arrow] (42) -- (32);
-\draw[arrow] (43) -- (32);
-\draw[arrow] (44) -- (32);
-\draw[arrow] (45) -- (32);
-\draw[arrow] (31) -- (21);
-\draw[arrow] (31) -- (22);
-\draw[arrow] (32) -- (22);
-
-\node (2d) [dimension, left=of 21] {2d};
-\node (3d) [dimension, above=of 2d] {3d};
-\node (4d) [dimension, above=of 3d] {4d};
-\node (5d) [dimension, above=of 4d] {5d};
-\node (6d) [dimension, above=of 5d] {6d};
-\node (7d) [dimension, above=of 6d] {7d};
-\node (8d) [dimension, above=of 7d] {8d};
-\node (9d) [dimension, above=of 8d] {9d};
-\node (10d) [dimension, above=of 9d] {10d};
-\end{tikzpicture}
-\caption{Orbits of square-zero supercharges.}
-\label{fig:superchargeorbits}
-\end{figure}
 %\end{landscape}

### 2020-01-08 paper.tex
Minor changes

@@
 We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
-For conventions on functions on topological vector spaces we refer to Appendix \ref{appx: top}. 
 We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
@@
 We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
-Let $\cE_{\rm SYM}$ denote the space of BV fields.
+Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.
 
@@
 \begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ satisfies the classical master equation
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
 \[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
@@
 \begin{thm}
+\label{9d_twist_thm}
 The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
@@
 \begin{proof}
-
+This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.
+That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
 \end{proof}
@@
 \begin{proof}
-
+Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_to_BF_diml_red_prop}.
 \end{proof}
@@
 \begin{theorem} \label{5d_rk4_twist_thm}
-The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}(M_5, B\gg)$.
+The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}((M_5)_{\mr{dR}}, B\gg)$.
 \end{theorem}
@@
 \section{Dimension 4}
-
-% \cN=4 SYM
-% \cN=2 SYM with matter in a pseudo-real representation
-% \cN=1 SYM with matter in a complex representation
 
@@
 
-\subsection{$\cN=2$ SYM with hypermultiplet matter}
+\subsection{$\cN=2$ Super Yang-Mills with hypermultiplet matter}
 %quaternionic is hyperkahler
@@
 
-\subsection{$\cN=4$ SYM}
+\subsection{$\cN=4$ Super Yang-Mills}
 
@@
 
-% \cN=8 SYM
-% \cN=4 SYM with matter in a pseudo-real representation
-% \cN=2 SYM with matter in a complex representation
+% \cN=8 Super Yang-Mills
+% \cN=4 Super Yang-Mills with matter in a pseudo-real representation
+% \cN=2 Super Yang-Mills with matter in a complex representation
 
@@
 
-% \cN=(8, 8) SYM
-% \cN=(4, 4) SYM with matter in a pseudo-real representation
-% \cN=(2, 2) SYM with matter in a complex representation
+% \cN=(8, 8) Super Yang-Mills
+% \cN=(4, 4) Super Yang-Mills with matter in a pseudo-real representation
+% \cN=(2, 2) Super Yang-Mills with matter in a complex representation
 %BRIAN FIND REFERENCE OF BELOW
-% \cN=(0,2) SYM with matter 
-% \cN=(0,4) SYM with matter
-% \cN=(0,8) SYM with matter
+% \cN=(0,2) Super Yang-Mills with matter 
+% \cN=(0,4) Super Yang-Mills with matter
+% \cN=(0,8) Super Yang-Mills with matter
 

### 2020-01-08 paper.tex
Some 4d edits

@@
 
-\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}
+\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}  \label{5d_1_section}
 We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
@@
  \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
- \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes W \otimes U)$.
+ \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes U)$.
 \end{itemize}
@@
 
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from section \ref{7d_section}, to representations of the group $\mr O(5)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from Section \ref{7d_section}, to representations of the group $\mr O(5)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsection{$\cN=2$ Super Yang-Mills with hypermultiplet matter}
-%quaternionic is hyperkahler
-%pseudo-real is quaternionic
+\subsection{$\cN=2$ Super Yang-Mills with Matter}
+
+We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.
+In these terms we can describe the BRST fields.
+
+\vspace{-10pt}
+\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg)^2$.
+ \item $U$-valued bosons: a $W$-valued scalar field $\phi \in \Omega^0(\RR^4; W \otimes U)$.
+ \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+ \item $U$-valued fermions: a Dirac spinor $\psi \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
+\end{itemize}
 

### 2020-01-08 paper.tex
finished 4d n=1

@@
 \end{align*}
-This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
- \end{proof}
-
-\begin{itemize}
-\item[(1)] 
-We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
-The fields of the pure Yang-Mills part decomposes as:
-\begin{align*}
-c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
-A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
-\end{align*}
-and their antifields:
-\begin{align*}
-c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
-A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
-\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
-\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
-\end{align*}
-
-The matter fields decompose as
-\begin{align*}
-\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
-\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
-\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
-\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
-\end{align*}
-and their antifields:
-\begin{align*}
-\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
-\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
-\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
-\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
-\end{align*}
-
-\item[(2)] Next, we study the linear differential in the twisted theory. 
-At the linear level, the matter and gauge sectors completely decouple.
-
-For the gauge sector, the linear differential on the twisted BV complex is the following:
-\[
-\xymatrix{
-\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
-& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
-\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
-& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
-}
-\]
-The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
-The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
-This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$.
-
-For the matter sector, the linear differential is:
-\[
-\xymatrix{
-\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
-\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
-\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
-}
-\]
-This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$.
-
-\item[(3)] 
-We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
-\end{itemize}
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{2,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{2,\bu}$ comprise the fields of the $\beta\gamma$ system.
+\end{proof}
+
+%\begin{itemize}
+%\item[(1)] 
+%We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
+%The fields of the pure Yang-Mills part decomposes as:
+%\begin{align*}
+%c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
+%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
+%\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
+%\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
+%\end{align*}
+%and their antifields:
+%\begin{align*}
+%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
+%A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
+%\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
+%\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
+%\end{align*}
+%
+%The matter fields decompose as
+%\begin{align*}
+%\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
+%\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
+%\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
+%\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
+%\end{align*}
+%and their antifields:
+%\begin{align*}
+%\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
+%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
+%\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
+%\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
+%\end{align*}
+%
+%\item[(2)] Next, we study the linear differential in the twisted theory. 
+%At the linear level, the matter and gauge sectors completely decouple. 
+%
+%For the gauge sector, the linear differential on the twisted BV complex is the following:
+%\[
+%\xymatrix{
+%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
+%\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
+%& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
+%\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
+%& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
+%}
+%\]
+%The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
+%The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
+%This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$. 
+%
+%For the matter sector, the linear differential is:
+%\[
+%\xymatrix{
+%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
+%& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
+%\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
+%\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
+%}
+%\]
+%This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$. 
+%
+%\item[(3)] 
+%We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
+%\end{itemize}
 

### 2020-01-08 paper.tex
started 4d N=2

@@
 We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Lemma \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
+We can do this by by applying Proposition \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
 More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Lemma \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
+Proposition \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
 
@@
 This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.
-That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
+That is, by applying Proposition \ref{CS_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
 \end{proof}
@@
 \begin{proof}
-Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_to_BF_diml_red_prop}.
+Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_diml_red_prop}.
 \end{proof}
@@
 We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 7-dimensions.
+That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
 \end{proof}
@@
 We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.
-That is, we apply Proposition \ref{CS_diml_red_prop}.
+That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
 \end{proof}
@@
 \begin{proof}
-As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 6-dimensions.
+As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 6-dimensions.
 \end{proof}
@@
 We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
+That is, we apply Proposition \ref{CS_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
 \end{proof}
@@
 
-\begin{prop}[See also \cite{SWchar}]
+\begin{thm}[See also \cite{SWchar}]
 The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
-\end{prop}
+\end{thm}
 
@@
 
+\vspace{-10pt}
+\paragraph{Twisting data:}
+There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
+\begin{itemize}
+ \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
+ \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
+ \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
+\end{itemize}
+
+We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.
+
+\begin{theorem} \label{4d_2_holo_twist_thm}
+The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
+\end{theorem}
+
+\begin{proof}
+To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.
+That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
+\end{proof}
+
 \subsection{$\cN=4$ Super Yang-Mills}

### 2020-01-08 paper.tex
continuing 4d N=2

@@
 \end{align*}
-Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}4$.
-
-\begin{thm}[See also \cite{SWchar}]
+Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.
+
+\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
 The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
@@
 \begin{itemize}
- \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg)^2$.
+ \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
  \item $U$-valued bosons: a $W$-valued scalar field $\phi \in \Omega^0(\RR^4; W \otimes U)$.
- \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
- \item $U$-valued fermions: a Dirac spinor $\psi \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
-\end{itemize}
+ \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+ \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Supersymmetry action:} 
+\begin{prop} \label{4d_2_susy_action_prop}
+After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\begin{align*}
+I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
+&\qquad  + \frac 12 ((\rho(F_A)Q, \lambda_+^*)(u_+^*,  w_+) + \rho(\d_A \phi_2(w_+ \wedge u_-^*))Q, \lambda_-^*) \bigg)\\
+I^{(1)}_{\mr{matter}}(Q) &= \\
+I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
+I^{(2)}_{\mr{matter}}(Q,Q) &= 
+\end{align*}
+if $Q=Q^+ \otimes w^+$ is an element of $S_+ \otimes W$, and
+\begin{align*}
+I^{(1)}_{\mr{gauge}}(Q) &= \\
+I^{(1)}_{\mr{matter}}(Q) &= \\
+I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
+I^{(2)}_{\mr{matter}}(Q,Q) &= 
+\end{align*}
+if $Q=Q^- \otimes W_-$ is an element of $S_- \otimes W^*$.
+\end{prop}
 
@@
 That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
+\end{proof}
+
+We'll first consider the deformation of the holomorphic twist to the topological twist corresponding to a rank $(2,0)$ supercharge.
+
+\begin{theorem} \label{4d_Donaldson_twist_thm}
+The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U/\!/\gg)_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{proof}
+Suppose the family of generically rank $(2,0)$ supercharge splits as a sum of two rank 1 supercharges as $Q_{\mr{hol}} + tQ$, where $t \in \CC$.
+It is enough to understand the deformation of the holomorphically twisted action functional, which we wrote down in the proof of Theorem \ref{4d_minimal_twist_thm}, by $I^{(1)}(tQ) + I^{(2)}(tQ,tQ)$ using Proposition \ref{4d_2_susy_action_prop}.
+
+\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.}
+\end{proof}
+
+We now address the rank $(1,1)$ twist.
+
+\begin{theorem} \label{4d_11_twist_thm}
+The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U/\!/\gg)$.
+This theory is generally only $\ZZ/2\ZZ$-graded.
+\end{theorem}
+
+\begin{proof}
+
 \end{proof}

### 2020-01-08 paper.tex
continuing 4d N=2

@@
 
-We now address the rank $(1,1)$ twist.
+We now address the rank $(1,1)$ twist.  This is more straightforward: we can understand it by dimensional reduction from the 5d holomorphic twist, this time in a non-invariant direction.
 
@@
 \begin{proof}
-
+We start with the 5d $\mc N=1$ holomorphic twist, as in Theorem \ref{5d_holo_twist_theorem}, and dimensionally reduce in one of the two non-invariant directions.
+That is, we apply Proposition \ref{CS_diml_red_prop}.
 \end{proof}

### 2020-01-09 paper.tex
merge

--- 2020-01-08 paper.tex
@@
 We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Proposition \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
+We can do this by by applying Lemma \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
 More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Proposition \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
+Lemma \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
 
@@
 This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.
-That is, by applying Proposition \ref{CS_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
+That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
 \end{proof}
@@
 \begin{proof}
-Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_diml_red_prop}.
+Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_to_BF_diml_red_prop}.
 \end{proof}
@@
 We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
+That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 7-dimensions.
 \end{proof}
@@
 We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
+That is, we apply Proposition \ref{CS_diml_red_prop}.
 \end{proof}
@@
 \begin{proof}
-As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 6-dimensions.
+As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family of twists in 6-dimensions.
 \end{proof}
@@
 We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.
-That is, we apply Proposition \ref{CS_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
+That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
 \end{proof}
@@
 
-\begin{thm}[See also \cite{SWchar}]
+\begin{prop}[See also \cite{SWchar}]
 The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
-\end{thm}
+\end{prop}
 
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
-\begin{itemize}
- \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
- \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
- \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
-\end{itemize}
-
-We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.
-
-\begin{theorem} \label{4d_2_holo_twist_thm}
-The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
-\end{theorem}
-
-\begin{proof}
-To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
-\end{proof}
-
 \subsection{$\cN=4$ Super Yang-Mills}
@@
 % \cN=(0,2) Super Yang-Mills with matter
+
+\subsection{$\cN=(0,2)$ Super Yang-Mills with matter}
+
+The untwisted fields are given by:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W \otimes \fg)$. 
+\item $R$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes R)$;
+\item $R$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_- \otimes R)$ .
+\end{itemize}
+
 % \cN=(0,4) Super Yang-Mills with matter

### 2020-01-09 paper.tex
continuing 4d N=2 slowly

--- 2020-01-08 paper.tex
@@
  \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
- \item $U$-valued bosons: a $W$-valued scalar field $\phi \in \Omega^0(\RR^4; W \otimes U)$.
+ \item $U$-valued bosons: a $W \oplus W^*$-valued scalar field $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^4; (W \oplus W^*) \otimes U)$.
  \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
@@
 \paragraph{Supersymmetry action:} 
+It will be enough for our purposes to describe only the action of a chiral supercharge.
 \begin{prop} \label{4d_2_susy_action_prop}
@@
 I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
-&\qquad  + \frac 12 ((\rho(F_A)Q, \lambda_+^*)(u_+^*,  w_+) + \rho(\d_A \phi_2(w_+ \wedge u_-^*))Q, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q) &= \\
-I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
-I^{(2)}_{\mr{matter}}(Q,Q) &= 
-\end{align*}
-if $Q=Q^+ \otimes w^+$ is an element of $S_+ \otimes W$, and
-\begin{align*}
-I^{(1)}_{\mr{gauge}}(Q) &= \\
-I^{(1)}_{\mr{matter}}(Q) &= \\
-I^{(2)}_{\mr{gauge}}(Q,Q) &= \\
-I^{(2)}_{\mr{matter}}(Q,Q) &= 
-\end{align*}
-if $Q=Q^- \otimes W_-$ is an element of $S_- \otimes W^*$.
+&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
+I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi')Q_+, \psi_+^*)(v',w_+)) \\
+I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
+I^{(2)}_{\mr{matter}}(Q,Q) &= 0 %\frac 14 \dvol (Q_+,Q_+)(\psi_+,\psi_+)(w_+ \wedge w_+)
+\end{align*}
+if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
 \end{prop}

### 2020-01-10 paper.tex
starting edits to section 1

@@
 
+\begin{figure}
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
+
 \part{Supersymmetric Gauge Theory}
@@
 
-Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading.
+In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.
+Most of the material in this section is not original.
+We refer the reader to \chris{refs} for more details.
+We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
+We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.
+We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.
+
+\subsection{Conventions}
+Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
@@
 Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
-We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
+We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
 \[\int_M f (\phi, \phi', \dots),\]
@@
 \]
-where we the integral symbol makes sense in earnest on sections which are compactly supported.
+where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
 We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
@@
 
+The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
+
 \begin{definition}
-A \defterm{free BV theory} on a manifold $M$ is the data:
+A \defterm{free BV theory} on a manifold $M$ is the data of:
 \begin{itemize}
@@
 This bracket is of cohomological degree $+1$. 
-To define the bracket, first note that there is a linear map
-\[
-\d_{dR} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+We will now explain how to define the BV bracket.  First note that there is a linear map
+\[
+\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
 \]
@@
 
-The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega : E \cong E^! [-1]$ and hence an isomorphism of local functions
+The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
 \[
@@
 Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
+
+Now, we will include interactions in the BV picture.
 
@@
 
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
 The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
 
-Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
+Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}, I, \omega)$ as the data of a classical field theory.
 
@@
 \begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e. a symplectic isomorphism $L\cong L^![-3]$.
+The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
+a symplectic isomorphism $L\cong L^![-3]$.
+\chris{todo: add references}
 \end{remark}
@@
 %\begin{landscape}
-\begin{figure}
-\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-\node (825) [right=of 82] {};
-\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-
-\draw[arrow] (101) -- (91);
-\draw[arrow] (91) -- (81);
-\draw[arrow] (91) -- (82);
-\draw[arrow] (81) -- (71);
-\draw[arrow] (82) -- (71);
-\draw[arrow] (82) -- (72);
-\draw[arrow] (83) -- (73);
-\draw[arrow] (71) -- (61);
-\draw[arrow] (71) -- (62);
-\draw[arrow] (72) -- (62);
-\draw[arrow] (72) -- (63);
-\draw[arrow] (73) -- (65);
-\draw[arrow] (61) -- (51);
-\draw[arrow] (62) -- (51);
-\draw[arrow] (62) -- (52);
-\draw[arrow] (63) -- (53);
-\draw[arrow] (64) -- (52);
-\draw[arrow] (64) -- (54);
-\draw[arrow] (65) -- (54);
-\draw[arrow] (51) -- (41);
-\draw[arrow] (51) -- (42);
-\draw[arrow] (52) -- (42);
-\draw[arrow] (52) -- (43);
-\draw[arrow] (53) -- (43);
-\draw[arrow] (54) -- (43);
-\draw[arrow] (54) -- (44);
-\draw[arrow] (54) -- (45);
-\draw[arrow] (41) -- (31);
-\draw[arrow] (42) -- (31);
-\draw[arrow] (42) -- (32);
-\draw[arrow] (43) -- (32);
-\draw[arrow] (44) -- (32);
-\draw[arrow] (45) -- (32);
-\draw[arrow] (31) -- (21);
-\draw[arrow] (31) -- (22);
-\draw[arrow] (32) -- (22);
-
-\node (2d) [dimension, left=of 21] {2d};
-\node (3d) [dimension, above=of 2d] {3d};
-\node (4d) [dimension, above=of 3d] {4d};
-\node (5d) [dimension, above=of 4d] {5d};
-\node (6d) [dimension, above=of 5d] {6d};
-\node (7d) [dimension, above=of 6d] {7d};
-\node (8d) [dimension, above=of 7d] {8d};
-\node (9d) [dimension, above=of 8d] {9d};
-\node (10d) [dimension, above=of 9d] {10d};
-\end{tikzpicture}
-\caption{Orbits of square-zero supercharges.}
-\label{fig:superchargeorbits}
-\end{figure}
+
 %\end{landscape}

### 2020-01-13 paper.tex
Started a table of twists

@@
 
+\begin{abstract}
+
+\end{abstract}
+
 \tableofcontents
@@
 \section*{Introduction}
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|c|c|c|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ &&&$\bun_G(\CC^5)$ &\\ \hline
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
+ \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
+ &&& $T^*_{\mr{odd}}\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
+ &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
+ &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
+ &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
+ \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
+ &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
+ &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
+ \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
+ &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
+ &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
+ \multirow{10}*{4} & \multirow{10}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
+ &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
+ &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
+ &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \hline
+  \multirow{6}*{3} & \multirow{6}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
+ %&&& {} & \\ \cline{3-5}
+ %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
+ %&&& {} & \\ \cline{3-5}
+ %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
+ %&&& {} & \\ \hline
+ \end{tabular}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
 
@@
 
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}, I, \omega)$ as the data of a classical field theory.
+Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
 

### 2020-01-13 paper.tex
added three tables of twists

@@
 
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|c|c|c|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
+ &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
+ \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
+ &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
+ \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
+ \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
+  \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
+
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
+ \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
+ &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
+  \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
+
 \begin{figure}

### 2020-01-13 paper.tex
Rotation actions on BF and Chern-Simons

--- 2020-01-10 paper.tex
@@
 \newcommand{\matter}{\mathrm{matter}}
+\newcommand{\MU}{\mathrm{MU}}
 \renewcommand{\Re}{\mathrm{Re}}
-%\newcommand{\U}{\mathrm{U}}
+\newcommand{\U}{\mathrm{U}}
+
+\newcommand{\ham}{/\!\!/}
 
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
 Fix an $L_\infty$ algebra $\fg$.
@@
 \begin{rmk}
-This is a special case of generalized BF theory:
-the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
+This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
 \end{rmk}
 
-\brian{Symplectic, non-polarized version needed for 6d N=(1,0).} \chris{following Brian's suggestion I've used the term: holomorphic BF theory coupled to a higher holomorphic symplectic boson, valued in a representation $U$.
-If we continue to use that term, we should explain it here.}
+We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
+
+\begin{example}
+Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
+\[\cL = \fg\oplus V[-1]\]
+with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
+The space of fields in the corresponding generalized BF theory will be denoted by
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
+where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+\end{example}
+
+The following is obvious from the definition.
+
+\begin{prop}
+Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
+Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\label{prop:BFrotationaction}
+\end{prop}
+
+\begin{remark}
+In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
+\end{remark}
 
@@
 \end{example}
+
+\begin{example}
+Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
+Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
+Consider the dg Lie algebra
+\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
+with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
+The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
+The space of fields in the corresponding Chern--Simons theory will be denoted by
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
+
+Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
+\begin{align*}
+E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
+\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
+\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
+\end{align*}
+and the action functional as before.
+\label{ex:CSHamiltonianreduction}
+\end{example}
+
+As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.
+
+\begin{prop}
+Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
+Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
+Then it carries an action of $\SU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\end{prop}
+
+We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
+Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$.
+We define the unitary metalinear group to be
+\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
+where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
+
+\begin{prop}
+Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure.
+Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
+Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\end{prop}
 
@@
 
-\subsection{Division algebras and minimal supersymmetry}
-\label{sect:divisionalgebras}
-
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and division algebras. Our treatment will essentially follow \cite{BaezHuerta}.
-
-Let $A_\RR$ be a (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+\subsection{Composition algebras and minimal supersymmetry}
+\label{sect:compositionalgebras}
+
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+
+Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
 \begin{enumerate}
@@
 \end{enumerate}
+
+It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
+$A_\RR$ is a real composition algebra.
 
@@
 
-Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$ \chris{it's a bit unclear here why they're notated differently}. We have action maps
+Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
 \[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
@@
 
-We will be interested in the following four examples:
+We will be interested in the following examples:
 \begin{enumerate}
@@
 
-\item (\textbf{4d $\mc N=1$ supersymmetry}) $A_\RR = \CC$.
-We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
 Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
-
-\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$.
-We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).
+
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
 Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
-
-\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
+We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
+We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
 \end{enumerate}
@@
 
-In the previous section we have related division algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
-In this section we explain a different relationship between division algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
+In the previous section we have related composition algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
+In this section we explain a different relationship between composition algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
 
@@
 
-We will now fix an associative algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and set $W = A$.
+We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
 The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
@@
 Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a real associative algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and denote its complexification by $A$.
+In addition, fix a real associative composition algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and denote its complexification by $A$.
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.

### 2020-01-13 paper.tex

@@
 \section*{Introduction}
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|c|c|c|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ &&&$\bun_G(\CC^5)$ &\\ \hline
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
+ \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
+ &&& $T^*_{\mr{odd}}\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
+ &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
+ &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
+ &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
+ \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
+ &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
+ &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
+ \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
+ &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
+ &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
+ \multirow{10}*{4} & \multirow{10}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
+ &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
+ &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
+ &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \hline
+  \multirow{6}*{3} & \multirow{6}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
+ %&&& {} & \\ \cline{3-5}
+ %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
+ %&&& {} & \\ \cline{3-5}
+ %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
+ %&&& {} & \\ \hline
+ \end{tabular}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
+
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|c|c|c|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
+ &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
+ \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
+ &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
+ \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{2 (holomorphic)} \\
+ &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
+ \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
+  \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
+
+\begin{table}[!h]
+ \centering
+ \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
+ $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
+ \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
+ &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
+  \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
+ \label{table_of_twists_16}
+\end{table}
 

### 2020-01-13 paper.tex
Some corrections to table
Different version of figure

@@
 \usepackage{pdflscape}
-\usetikzlibrary{shapes.geometric, arrows, positioning}
-
-\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
+\usetikzlibrary{shapes.geometric, arrows, positioning, matrix}
+
+\tikzstyle{s16} = [rectangle, rounded corners, text centered, innersep=0pt, draw=black,fill=red!30]
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
-\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
-\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
+\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
+\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
+\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
 \tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
@@
 \section*{Introduction} 
-\begin{table}[!h]
+\begin{table}[htbp]
  \centering
@@
  \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
- &&& $T^*_{\mr{odd}}\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
@@
  &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{10}*{4} & \multirow{10}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
@@
  && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
- &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \hline
-  \multirow{6}*{3} & \multirow{6}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+ &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
+ &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
@@
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $2$ (generic)} & {Perturbatively trivial (generic)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
@@
  &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (holomorphic)} \\
+ && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
  &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{2 (holomorphic)} \\
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
  &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
@@
 
-\begin{table}[!h]
+\begin{table}[htbp]
  \centering
@@
 
-\begin{figure}
-\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-\node (825) [right=of 82] {};
-\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-
-\draw[arrow] (101) -- (91);
-\draw[arrow] (91) -- (81);
-\draw[arrow] (91) -- (82);
-\draw[arrow] (81) -- (71);
-\draw[arrow] (82) -- (71);
-\draw[arrow] (82) -- (72);
-\draw[arrow] (83) -- (73);
-\draw[arrow] (71) -- (61);
-\draw[arrow] (71) -- (62);
-\draw[arrow] (72) -- (62);
-\draw[arrow] (72) -- (63);
-\draw[arrow] (73) -- (65);
-\draw[arrow] (61) -- (51);
-\draw[arrow] (62) -- (51);
-\draw[arrow] (62) -- (52);
+\begin{figure}[hbp]
+\begin{tikzpicture}
+  \matrix (mat) [nodes in empty cells, minimum width=3.5ex, minimum height=3.5ex, column sep=1.8ex,row sep=6ex]{
+   \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
+  \node {8}; &    &   & \node[s16] (88) {$(1,0)_i$};  &   &   &   &&   &&&&   &&&   \\
+  \node {7}; &    &   &   & \node[s16] (77) {$1_i$};  &   &   &&   &&&&   &&&   \\
+  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_g$};  &   &&   &&&&   &&&   \\
+  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_g$};  &   &&&&   &&&   \\
+  \node {4}; &    &   & \node[s16] (84) {$(1,0)_p$};  & \node[s16] (74) {$1_p$};  & \node[s16] (64) {$(1,1)_s$};  & \node[s16] (54) {$2_s$};  && \node[s16] (44B) {$(2,2)_s$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_g$};  &   &&&   \\
+  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &\node[s16] (33g) {$2_g$};  &   \\
+  \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
+  \node (i1) {1}; &   &  &  &  &  &   & &   &&& &   && &   \\};
+
+  \draw[thick] (corner.south west) -- (d2.south west);
+  \draw[thick] (corner.north east) -- (i1.south east);
+
+  \draw[dotted] (0.4,-7) -- (0.4,7);
+  \draw[dotted] (6.35,-7) -- (6.35,7);
+  \draw[dotted] (-2,-7) -- (-2,7);
+  \draw[dotted] (-3.8,-7) -- (-3.8,7);
+  \draw[dotted] (-4.75,-7) -- (-4.75,7);
+  \draw[dotted] (-6.25,-7) -- (-6.25,7);
+  \draw[dotted] (-7.1,-7) -- (-7.1,7);
+
+  \draw[arrow] (105) -- (95);
+  \draw[arrow] (95) -- (85);
+  \draw[arrow] (88) -- (77);
+  \draw[arrow] (95) -- (84);
+  \draw[arrow] (85) -- (75);
+  \draw[arrow] (85) -- (74);
+  \draw[arrow] (84) -- (74);
+  \draw[arrow] (77) -- (66);
+  \draw[arrow] (75) -- (65);
+  \draw[arrow] (75) -- (64);
+  \draw[arrow] (74) -- (64);
+  \draw[arrow] (74) -- (63);
+  \draw[arrow] (66) -- (55A);
+  \draw[arrow] (65) -- (55B);
+  \draw[arrow] (65) -- (54);
+  \draw[arrow] (64) -- (54);
+  \draw[arrow] (64) -- (53);
   \draw[arrow] (63) -- (53);
-\draw[arrow] (64) -- (52);
-\draw[arrow] (64) -- (54);
-\draw[arrow] (65) -- (54);
-\draw[arrow] (51) -- (41);
-\draw[arrow] (51) -- (42);
-\draw[arrow] (52) -- (42);
-\draw[arrow] (52) -- (43);
+  \draw[arrow] (55A) -- (44g);
+  \draw[arrow] (55B) -- (44B);
+  \draw[arrow] (54) -- (44B);
+  \draw[arrow] (54) -- (43);
   \draw[arrow] (53) -- (43);
-\draw[arrow] (54) -- (43);
-\draw[arrow] (54) -- (44);
-\draw[arrow] (54) -- (45);
-\draw[arrow] (41) -- (31);
-\draw[arrow] (42) -- (31);
+  \draw[arrow] (53) -- (42);
+  \draw[arrow] (44B) -- (33B);
+  \draw[arrow] (44A) -- (33A);
+  \draw[arrow] (44K) -- (33A);
+  \draw[arrow] (44g) -- (33g);
+  \draw[arrow] (43) -- (33B);
+  \draw[arrow] (43) -- (32);
   \draw[arrow] (42) -- (32);
-\draw[arrow] (43) -- (32);
-\draw[arrow] (44) -- (32);
-\draw[arrow] (45) -- (32);
-\draw[arrow] (31) -- (21);
-\draw[arrow] (31) -- (22);
-\draw[arrow] (32) -- (22);
-
-\node (2d) [dimension, left=of 21] {2d};
-\node (3d) [dimension, above=of 2d] {3d};
-\node (4d) [dimension, above=of 3d] {4d};
-\node (5d) [dimension, above=of 4d] {5d};
-\node (6d) [dimension, above=of 5d] {6d};
-\node (7d) [dimension, above=of 6d] {7d};
-\node (8d) [dimension, above=of 7d] {8d};
-\node (9d) [dimension, above=of 8d] {9d};
-\node (10d) [dimension, above=of 9d] {10d};
+
 \end{tikzpicture}
@@
 
-\part{Supersymmetric Gauge Theory}
-
-\section{The BV-BRST Formalism}
-
-In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.
-Most of the material in this section is not original.
-We refer the reader to \chris{refs} for more details.
-We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
-We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.
-We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.
-
-\subsection{Conventions}
-Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
-\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
-For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
-
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
-We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
-\[\int_M f (\phi, \phi', \dots),\]
-where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
-The space of local functionals can be viewed as a subspace
-\[
-\oloc(\cE) \subset \cO(\cE_c)
-\]
-where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
-We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
-
-Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
-By definition, this is 
-\[
-{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
-\]
-where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
-When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
-There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
-
-\subsection{Classical BV Theories}
-
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
-
-\begin{definition}
-A \defterm{free BV theory} on a manifold $M$ is the data of:
-\begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
-\[
-Q_{\mr{BV}} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
-\item a map of bundles
-\[
-\omega\colon E \otimes E \to \Dens_M [-1]
-\]
-that is
-\begin{enumerate}
-\item[$(1)$] fiberwise nondegenerate,
-\item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
-\end{enumerate}
-\end{itemize}
-\end{definition}
-
-We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
-\]
-This bracket is of cohomological degree $+1$. 
-We will now explain how to define the BV bracket.  First note that there is a linear map
-\[
-\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
-\]
-defined as follows. 
-A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
-\[
-D_1(-) \cdots D_n(-) \Omega
-\]
-where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
-Without loss of generality, suppose $F$ is of this form. 
-Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
-\[
-\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
-\]
-where $\phi$ denotes a compactly supported section. 
-Define the symmetric multilinear map
-\[
-\begin{array}{ccccl}
-\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
-& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
-\end{array}
-\]
-Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
-This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
-
-The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
-\[
-\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
-\]
-We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
-In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
-\[
-X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
-\]
-This is the Hamiltonian vector field corresponding to $F$. 
-Finally, the BV bracket between local functionals $F, G$ is defined by
-\[
-\{F, G\} = X_F (G) .
-\]
-
-The BV bracket enjoys the graded skew symmetry property
-\[
-\{F, G\} = (-1)^{|F| |G|} \{G, F\}
-\]
-as well as the graded Jacobi identity.
-This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
-Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
-
-Now, we will include interactions in the BV picture.
-
-\begin{definition}
-A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
-\[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
-\end{definition}
-
-Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
-the BV action of the theory.
-
-The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
-
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
-The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
-
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
-
-\begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
-\end{remark}
-
-\begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$.
-\chris{todo: add references}
-\end{remark}
-
-Next, we formulate the notion of an equivalence of classical BV theories.
-
-\begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
-A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
-\end{definition}
-
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
-First, we consider the process of integrating out an auxiliary field.
-
-\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
-
-\begin{prop}
-Fix a volume form $\dvol_M$ on $M$.
-Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
-Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
-Suppose the BV action is
-\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
-where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
-\label{prop:integrateoutfield}
-\end{prop}
-
-\begin{proof}
-Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
-Then we define the required perturbative equivalence as follows.
-First $F_1(e) = (e, Q_1(e), 0) \in E$.
-Then, for $n > 1$, define
-\begin{align*}
-F_n \colon \sym^n(E_0) &\to E \\
-e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
-\end{align*}
-These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
-\begin{align*}
-S(F(e)) &= S(e, S_1(e), 0) \\
-&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
-&= S_0(e) - \frac 12 S_1(e)^2 \\
-&= S'(e).
-\end{align*}
-Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
-\end{proof}
-
-We may also remove a trivial BRST doublet.
-
-\begin{prop}
-Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
-Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
-Suppose
-\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-\label{prop:BRSTdoublet}
-\end{prop}
-
-\begin{proof}
-Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
-We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
-\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
-Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
-Also, by construction, the $F_n$ intertwine the action functionals, since
-\begin{align*}
-S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
-&= S_0(e).
-\end{align*}
-Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
-\end{proof}
-
-\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
-
-In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-Consider the graded vector space
-\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
-parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
-where $x_j \in \fg$. 
-We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
-\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the degree $+1$ BV bracket by the formula
-\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
-where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
-\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
-\]
-where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
-Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
-
-\begin{definition}
-\label{infinitesimal_action_def}
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
-\begin{itemize}
-\item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$;
-\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
-\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
-\end{itemize}
-\item[(2)]
-For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
-\[
-Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
-\]
-is elliptic as a $C^\bu(\fg)$-linear differential operator.
-\end{itemize}
-\end{definition}
-
-\begin{rmk}
-\brian{Explain $C^\bu(\fg)$-linear elliptic}
-\end{rmk}
-
-\begin{rmk}
-We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
-One can also formulate actions of a Lie algebra on a classical theory in these terms. 
-The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
-\[
-\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
-\]
-is satisfied.
-\end{rmk}
-
-\begin{rmk}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
-Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
-defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
-By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
-\[
-\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
-\]
-combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
-\end{rmk}
-
-We may also define actions of supergroups on classical field theories.
-
-\begin{definition}
-\label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
-An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
-\begin{itemize}
-\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
-
-\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
-\end{itemize}
-These are required to satisfy the following conditions:
-\begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
-\end{itemize}
-\end{definition}
-
-\begin{remark}
-While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
-\end{remark}
-
-\subsection{From BRST to BV}
-
-\begin{definition}
-A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
-\begin{itemize}
-\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
-\end{itemize}
-Together, these data must satisfy the equation
-\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
-where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
-\end{definition}
-
-We call $\cF$ the \defterm{space of BRST fields}.
-
-From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
-Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
-
-First, we define the free BV theory.
-Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
-\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
-The underlying bundle of the BV theory is
-\[
-E = F \oplus F^! [-1].
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
-The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
-\]
-
-The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
-These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
-\[
-I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
-\] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
-\]
-
-\begin{lemma}
-Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
-\end{lemma}
-
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
-
-If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
-\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-\brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
-\subsection{Examples of Classical Field Theories}
-
-In this section we give some examples of classical field theories we will use.
-All theories we consider in this section are $\ZZ$-graded, i.e.
-all fields are considered even with respect to the $\ZZ/2$-grading.
-
-\subsubsection{Generalized BF theory} \label{gen_BF_section}
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
-The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\label{def:generalizedBF}
-\end{definition}
-
-\begin{remark}
-We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
-\end{remark}
-
-Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
-\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
-where we denote the two fields by $A$ and $B$. The BV action is
-\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
-where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
-
-\begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
-\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
-\end{example}
-
-Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
-In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix a complex vector space $V$.
-The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
-$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-\end{definition}
-
-\begin{rmk}
-This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
-\end{rmk}
-
-We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
-
-\begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\]
-with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
-where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}
-
-The following is obvious from the definition.
-
-\begin{prop}
-Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
-Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\label{prop:BFrotationaction}
-\end{prop}
-
-\begin{remark}
-In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
-\end{remark}
-
-\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
-
-The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
-We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-
-\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
-
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
-
-\item The interaction term is
-\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
-\label{def:generalizedCS}
-\end{definition}
-
-We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
-
-\begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
-\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
-\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
-The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
-Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
-\end{example}
-
-\begin{example}
-Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
-Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
-Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
-with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
-The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
-The space of fields in the corresponding Chern--Simons theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
-
-Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
-\begin{align*}
-E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
-\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
-\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
-\end{align*}
-and the action functional as before.
-\label{ex:CSHamiltonianreduction}
-\end{example}
-
-As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.
-
-\begin{prop}
-Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
-Then it carries an action of $\SU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\end{prop}
-
-We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
-Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$.
-We define the unitary metalinear group to be
-\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
-where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
-
-\begin{prop}
-Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
-Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\end{prop}
-
-\subsection{Dimensional Reduction} \label{dim_red_section}
-
-In this section we formulate the procedure of dimensional reduction of a classical field theory.
-Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
-an isomorphism $p^*\Dens_N\cong \Dens_M$.
-The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
-We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
-
-\begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
-\begin{itemize}
-\item The diagram
-\[
-\xymatrix{
-p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
-E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
-}
-\]
-is commutative.
-
-\item The diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-is commutative.
-
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
-\end{itemize}
-\end{definition}
-
-We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
-Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
-In fact, when dimensional reduction makes sense, this groupoid is always contractible.
-
-\begin{prop}
-Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
-Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
-
-Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
-If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
-\label{prop:dimensionalreductionunique}
-\end{prop}
-\begin{proof} \textbf{Uniqueness}.
-We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
-Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
-In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
-
-Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
-
-\textbf{Existence}.
-Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
-Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
-Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
-The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
-\end{proof}
-
-\begin{remark}
-Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
-\end{remark}
-
-We will now describe dimensional reductions of the classical Chern--Simons theory.
-
-\begin{prop} \label{CS_to_BF_diml_red_prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
-\end{prop}
-
-\begin{proof}
-To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
-\[\map(\pt, T^*[-1] B \fg)\]
-has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
-
-We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
-Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
-Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
-\end{proof}
-
-\begin{prop} \label{CS_diml_red_prop}
-Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
-\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-\end{prop}
-
-\begin{proof}
-We may assume $X,Y,M=\pt$ as in the previous proof.
-
-We have
-\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
-and
-\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
-Under the pullback map
-\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
-the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\end{proof}
-
-\section{Supersymmetry} \label{sec: susy}
-
-In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
-
-\subsection{Supersymmetry algebras}
-
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
-\begin{itemize}
-\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.
-
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
-\end{itemize}
-
-\begin{definition}
-A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
-\end{definition}
-
-So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
-
-\begin{definition}
-Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
-\end{definition}
-
-For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
-In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
-\begin{itemize}
-\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
-
-\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
-
-\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
-
-\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
-\end{itemize}
-
-Fix the following data:
-\begin{itemize}
-\item A spinorial representation $\Sigma$ of $\so(V)$.
-
-\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-
-\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
-\end{itemize}
-
-Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
-
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
-
-\begin{definition}
-\label{dfn: super}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
-\end{definition}
-
-\subsection{Composition algebras and minimal supersymmetry}
-\label{sect:compositionalgebras}
-
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
-
-Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
-\begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
-\end{enumerate}
-
-It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
-$A_\RR$ is a real composition algebra.
-
-For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
-$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
-Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-
-We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
-So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
-
-Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
-
-\begin{lemma}
-Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
-Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
-\label{lm:extendpairing}
-\end{lemma}
-
-Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
-\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
-given, respectively, by
-\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
-
-The following is proved in \cite[Proposition 6]{BaezHuerta}.
-
-\begin{prop}
-The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
-\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
-\end{prop}
-
-So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
-
-We have a nondegenerate scalar spinorial pairing
-\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
-given by
-\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
-It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
-\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
-
-By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
-\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
-
-We will now state two important properties of $\Gamma$ and the spinorial pairing.
-The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
-
-\begin{thm}
-Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
-\label{thm:3psi}
-\end{thm}
-
-If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
-
-\begin{thm}
-Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
-\label{thm:matter3psi}
-\end{thm}
-\begin{proof}
-The right-hand side is
-\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
-which by associativity can be rewritten as
-\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
-which is the left-hand side.
-\end{proof}
-
-We will be interested in the following examples:
-\begin{enumerate}
-\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
-
-\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
-Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
-We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).
-
-\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
-We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).
-
-\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
-We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
-\end{enumerate}
-
-All four examples are alternative, while the first three examples are moreover associative.
-
-\subsection{Two-dimensional chiral supersymmetry}
-
-In the previous section we have related composition algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
-In this section we explain a different relationship between composition algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
-
-Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
-\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
-and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
-\begin{equation}
-(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
-\label{eq:2dvectorpairing}
-\end{equation}
-
-Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
-\[\Sigma = S_+\otimes W\]
-and its dual
-\[\Sigma^* = S_-\otimes W.\]
-The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
-\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
-and similarly for $V\otimes S_-\rightarrow S_+$.
-
-\begin{prop}
-For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
-\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
-\end{prop}
-\begin{proof}
-It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
-\begin{align*}
-\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
-&= 4(s, f)^2 s.
-\end{align*}
-But by \eqref{eq:2dvectorpairing} we have
-\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
-which proves the claim.
-\end{proof}
-
-The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
-Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
-
-The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
-\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
-and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.
-
-\begin{prop}
-For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
-\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
-\end{prop}
-\begin{proof}
-It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
-\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
-The right-hand side is
-\begin{align*}
-(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
-&= 2(s, f)^2 (q_1, q_2).
-\end{align*}
-\end{proof}
-
-An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.
-
-\begin{thm}
-For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
-\label{thm:2d3psi}
-\end{thm}
-\begin{proof}
-Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
-\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
-\end{proof}
-
-We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
-The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
-Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
-
-Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
-\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
-
-\begin{thm}
-For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
-\label{thm:2dmatter3psi}
-\end{thm}
-\begin{proof}
-Pick basis elements $s\in S_+$ and $f\in S_-$, so that
-\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
-The right-hand side is
-\begin{align*}
-(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
-&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
-\end{align*}
-We have
-\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
-so the left-hand side is
-\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
-By associativity of $A$ the two expressions are equal.
-\end{proof}
-
-\subsection{Supersymmetric twisting}
-
-\begin{definition}
-A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{definition}
-
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
-\begin{itemize}
-\item A supercharge $Q$ is \defterm{topological} if $d = n$.
-
-\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
-The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
-
-\begin{definition}
-A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
-Recall, this means we have a Maurer-Cartan element 
-\[
-I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
-\]
-where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
-For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
-Define
-\[
-I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
-\]
-Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
-
-\begin{definition} \label{def:twisting}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{definition}
-
-\begin{prop}
-The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
-\end{prop}
-
-\begin{proof}
-The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
-Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
-Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
-
-Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
-The operator 
-\end{proof}
-
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
-\end{remark}
-
-\subsection{Dimensional Reduction of Supersymmetric Theories}
-
-Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
-
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
-We have a natural embedding
-\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
-so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
-\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
-where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
-\[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
-We have the following generalization of this statement to supersymmetric theories.
-
-\begin{prop} \label{prop:susydimlred}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
-\end{prop}
-
-\begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
-\end{proof}
-
-The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
-
-\begin{prop}
-Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
-Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
-\label{prop:twistdimensionalreduction}
-\end{prop}
-
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
-
-\subsection{A-Type Twists} \label{A_twist_section}
-\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
-
-%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
-
-% \begin{landscape}
 % \begin{figure}
@@
 % \end{figure}
+
+\part{Supersymmetric Gauge Theory}
+
+\section{The BV-BRST Formalism}
+
+In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.
+Most of the material in this section is not original.
+We refer the reader to \chris{refs} for more details.
+We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
+We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.
+We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.
+
+\subsection{Conventions}
+Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
+\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
+For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
+
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
+We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
+\[\int_M f (\phi, \phi', \dots),\]
+where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
+The space of local functionals can be viewed as a subspace
+\[
+\oloc(\cE) \subset \cO(\cE_c)
+\]
+where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
+We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
+
+Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
+By definition, this is 
+\[
+{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
+\]
+where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
+When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
+There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
+
+\subsection{Classical BV Theories}
+
+The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
+
+\begin{definition}
+A \defterm{free BV theory} on a manifold $M$ is the data of:
+\begin{itemize}
+\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
+\[
+Q_{\mr{BV}} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
+\item a map of bundles
+\[
+\omega\colon E \otimes E \to \Dens_M [-1]
+\]
+that is
+\begin{enumerate}
+\item[$(1)$] fiberwise nondegenerate,
+\item[$(2)$] graded skew symmetric, and
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\end{enumerate}
+\end{itemize}
+\end{definition}
+
+We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
+\[
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
+\]
+This bracket is of cohomological degree $+1$. 
+We will now explain how to define the BV bracket.  First note that there is a linear map
+\[
+\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+\]
+defined as follows. 
+A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
+\[
+D_1(-) \cdots D_n(-) \Omega
+\]
+where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
+Without loss of generality, suppose $F$ is of this form. 
+Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
+\[
+\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
+\]
+where $\phi$ denotes a compactly supported section. 
+Define the symmetric multilinear map
+\[
+\begin{array}{ccccl}
+\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
+& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\end{array}
+\]
+Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
+
+The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
+\[
+\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+\]
+We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
+In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
+\[
+X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
+\]
+This is the Hamiltonian vector field corresponding to $F$. 
+Finally, the BV bracket between local functionals $F, G$ is defined by
+\[
+\{F, G\} = X_F (G) .
+\]
+
+The BV bracket enjoys the graded skew symmetry property
+\[
+\{F, G\} = (-1)^{|F| |G|} \{G, F\}
+\]
+as well as the graded Jacobi identity.
+This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
+Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
+
+Now, we will include interactions in the BV picture.
+
+\begin{definition}
+A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
+\[I \in \oloc^+(\cE)\]
+of cohomological degree zero satisfying the Maurer-Cartan equation
+\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+\end{definition}
+
+Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
+the BV action of the theory.
+
+The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
+
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
+The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+
+Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
+
+\begin{remark}
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
+\end{remark}
+
+\begin{remark}
+The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
+a symplectic isomorphism $L\cong L^![-3]$.
+\chris{todo: add references}
+\end{remark}
+
+Next, we formulate the notion of an equivalence of classical BV theories.
+
+\begin{definition}
+A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
+\end{definition}
+
+We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
+First, we consider the process of integrating out an auxiliary field.
+
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
+
+\begin{prop}
+Fix a volume form $\dvol_M$ on $M$.
+Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
+Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
+Suppose the BV action is
+\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
+where $S_0$ and $S_1$ are independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
+\label{prop:integrateoutfield}
+\end{prop}
+
+\begin{proof}
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
+Then we define the required perturbative equivalence as follows.
+First $F_1(e) = (e, Q_1(e), 0) \in E$.
+Then, for $n > 1$, define
+\begin{align*}
+F_n \colon \sym^n(E_0) &\to E \\
+e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
+\end{align*}
+These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
+\begin{align*}
+S(F(e)) &= S(e, S_1(e), 0) \\
+&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
+&= S_0(e) - \frac 12 S_1(e)^2 \\
+&= S'(e).
+\end{align*}
+Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
+\end{proof}
+
+We may also remove a trivial BRST doublet.
+
+\begin{prop}
+Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
+Suppose
+\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
+\label{prop:BRSTdoublet}
+\end{prop}
+
+\begin{proof}
+Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
+We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
+\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
+Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
+Also, by construction, the $F_n$ intertwine the action functionals, since
+\begin{align*}
+S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
+&= S_0(e).
+\end{align*}
+Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
+\end{proof}
+
+\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
+
+In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Consider the graded vector space
+\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
+\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
+parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
+where $x_j \in \fg$. 
+We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
+\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
+and the degree $+1$ BV bracket by the formula
+\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
+where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
+\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
+The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
+\]
+where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
+The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
+Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
+
+\begin{definition}
+\label{infinitesimal_action_def}
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
+\begin{itemize}
+\item[(1)]
+An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
+where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $I_\fg^{(0)} = I$;
+\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
+\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
+\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\end{itemize}
+\item[(2)]
+For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
+An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
+\[
+Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+\]
+is elliptic as a $C^\bu(\fg)$-linear differential operator.
+\end{itemize}
+\end{definition}
+
+\begin{rmk}
+\brian{Explain $C^\bu(\fg)$-linear elliptic}
+\end{rmk}
+
+\begin{rmk}
+We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
+One can also formulate actions of a Lie algebra on a classical theory in these terms. 
+The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
+\[
+\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
+\]
+is satisfied.
+\end{rmk}
+
+\begin{rmk}
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
+Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
+By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
+\[
+\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
+\]
+combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
+\end{rmk}
+
+We may also define actions of supergroups on classical field theories.
+
+\begin{definition}
+\label{group_action_def}
+Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
+An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
+\begin{itemize}
+\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
+
+\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
+\end{itemize}
+These are required to satisfy the following conditions:
+\begin{itemize}
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
+
+\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\end{itemize}
+\end{definition}
+
+\begin{remark}
+While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
+\end{remark}
+
+\subsection{From BRST to BV}
+
+\begin{definition}
+A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
+\begin{itemize}
+\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\end{itemize}
+Together, these data must satisfy the equation
+\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
+where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+\end{definition}
+
+We call $\cF$ the \defterm{space of BRST fields}.
+
+From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
+Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
+
+First, we define the free BV theory.
+Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
+\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
+The underlying bundle of the BV theory is
+\[
+E = F \oplus F^! [-1].
+\]
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
+The differential of the free BV theory is
+\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
+\]
+
+The interacting theory is constructed as follows.
+First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
+These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
+\[
+I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
+\] 
+which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
+\[
+I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
+\]
+
+\begin{lemma}
+Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
+\end{lemma}
+
+We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
+
+If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
+\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
+\brian{Looks like you're using a bracket we haven't defined. 
+We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
+\subsection{Examples of Classical Field Theories}
+
+In this section we give some examples of classical field theories we will use.
+All theories we consider in this section are $\ZZ$-graded, i.e.
+all fields are considered even with respect to the $\ZZ/2$-grading.
+
+\subsubsection{Generalized BF theory} \label{gen_BF_section}
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Fix an $L_\infty$ algebra $\fg$.
+The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
+$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
+
+\item The BRST action is $S_{\mr{BRST}} = 0$.
+\end{itemize}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+\label{def:generalizedBF}
+\end{definition}
+
+\begin{remark}
+We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
+\end{remark}
+
+Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
+\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
+where we denote the two fields by $A$ and $B$. The BV action is
+\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
+where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
+
+\begin{example}
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
+\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
+\end{example}
+
+Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
+In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix a complex vector space $V$.
+The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
+$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
+
+\item The BRST action is $S_{\mr{BRST}} = 0$.
+\end{itemize}
+\end{definition}
+
+\begin{rmk}
+This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
+\end{rmk}
+
+We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
+
+\begin{example}
+Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
+\[\cL = \fg\oplus V[-1]\]
+with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
+The space of fields in the corresponding generalized BF theory will be denoted by
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
+where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+\end{example}
+
+The following is obvious from the definition.
+
+\begin{prop}
+Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
+Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\label{prop:BFrotationaction}
+\end{prop}
+
+\begin{remark}
+In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
+\end{remark}
+
+\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
+
+The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Fix an $L_\infty$ algebra $\fg$.
+We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
+
+\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
+
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
+
+\item The interaction term is
+\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
+\end{itemize}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+\label{def:generalizedCS}
+\end{definition}
+
+We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
+
+\begin{example}
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
+\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
+\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
+The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
+Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
+\end{example}
+
+\begin{example}
+Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
+Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
+Consider the dg Lie algebra
+\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
+with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
+The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
+The space of fields in the corresponding Chern--Simons theory will be denoted by
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
+
+Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
+\begin{align*}
+E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
+\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
+\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
+\end{align*}
+and the action functional as before.
+\label{ex:CSHamiltonianreduction}
+\end{example}
+
+As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.
+
+\begin{prop}
+Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
+Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
+Then it carries an action of $\SU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\end{prop}
+
+We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
+Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$.
+We define the unitary metalinear group to be
+\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
+where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
+
+\begin{prop}
+Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure.
+Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
+Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\end{prop}
+
+\subsection{Dimensional Reduction} \label{dim_red_section}
+
+In this section we formulate the procedure of dimensional reduction of a classical field theory.
+Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
+an isomorphism $p^*\Dens_N\cong \Dens_M$.
+The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
+We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
+
+\begin{definition}
+We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+\begin{itemize}
+\item The diagram
+\[
+\xymatrix{
+p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
+E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
+}
+\]
+is commutative.
+
+\item The diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+is commutative.
+
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
+\end{itemize}
+\end{definition}
+
+We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
+Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
+In fact, when dimensional reduction makes sense, this groupoid is always contractible.
+
+\begin{prop}
+Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
+Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
+
+Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
+If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
+\label{prop:dimensionalreductionunique}
+\end{prop}
+\begin{proof} \textbf{Uniqueness}.
+We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
+Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
+In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
+
+Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
+
+\textbf{Existence}.
+Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
+Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
+Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
+The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
+\end{proof}
+
+\begin{remark}
+Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
+\end{remark}
+
+We will now describe dimensional reductions of the classical Chern--Simons theory.
+
+\begin{prop} \label{CS_to_BF_diml_red_prop}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
+\end{prop}
+
+\begin{proof}
+To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+\[\map(\pt, T^*[-1] B \fg)\]
+has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
+
+We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
+Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
+The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
+Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
+\end{proof}
+
+\begin{prop} \label{CS_diml_red_prop}
+Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
+\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+\end{prop}
+
+\begin{proof}
+We may assume $X,Y,M=\pt$ as in the previous proof.
+
+We have
+\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
+and
+\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
+Under the pullback map
+\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
+the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
+\end{proof}
+
+\section{Supersymmetry} \label{sec: susy}
+
+In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
+
+\subsection{Supersymmetry algebras}
+
+Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+\begin{itemize}
+\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.
+
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
+\end{itemize}
+
+\begin{definition}
+A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
+\end{definition}
+
+So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
+
+\begin{definition}
+Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
+\end{definition}
+
+For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
+In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
+\begin{itemize}
+\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
+
+\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
+
+\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
+
+\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
+\end{itemize}
+
+Fix the following data:
+\begin{itemize}
+\item A spinorial representation $\Sigma$ of $\so(V)$.
+
+\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+
+\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
+\end{itemize}
+
+Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
+
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
+
+\begin{definition}
+\label{dfn: super}
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
+\end{definition}
+
+\subsection{Composition algebras and minimal supersymmetry}
+\label{sect:compositionalgebras}
+
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+
+Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+\begin{enumerate}
+\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\end{enumerate}
+
+It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
+$A_\RR$ is a real composition algebra.
+
+For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
+We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
+$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
+
+We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
+So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
+
+Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
+
+\begin{lemma}
+Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
+Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
+\label{lm:extendpairing}
+\end{lemma}
+
+Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
+\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
+given, respectively, by
+\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
+
+The following is proved in \cite[Proposition 6]{BaezHuerta}.
+
+\begin{prop}
+The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
+\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
+\end{prop}
+
+So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
+
+We have a nondegenerate scalar spinorial pairing
+\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
+given by
+\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
+It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
+\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
+
+By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
+\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
+
+We will now state two important properties of $\Gamma$ and the spinorial pairing.
+The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
+
+\begin{thm}
+Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
+\label{thm:3psi}
+\end{thm}
+
+If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
+
+\begin{thm}
+Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
+\label{thm:matter3psi}
+\end{thm}
+\begin{proof}
+The right-hand side is
+\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
+which by associativity can be rewritten as
+\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
+which is the left-hand side.
+\end{proof}
+
+We will be interested in the following examples:
+\begin{enumerate}
+\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
+
+\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
+We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).
+
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
+We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
+We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
+\end{enumerate}
+
+All four examples are alternative, while the first three examples are moreover associative.
+
+\subsection{Two-dimensional chiral supersymmetry}
+
+In the previous section we have related composition algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
+In this section we explain a different relationship between composition algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
+
+Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
+\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
+and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
+\begin{equation}
+(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
+\label{eq:2dvectorpairing}
+\end{equation}
+
+Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
+\[\Sigma = S_+\otimes W\]
+and its dual
+\[\Sigma^* = S_-\otimes W.\]
+The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
+\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
+and similarly for $V\otimes S_-\rightarrow S_+$.
+
+\begin{prop}
+For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
+\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
+\begin{align*}
+\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
+&= 4(s, f)^2 s.
+\end{align*}
+But by \eqref{eq:2dvectorpairing} we have
+\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
+which proves the claim.
+\end{proof}
+
+The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
+Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
+
+The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
+\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
+and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.
+
+\begin{prop}
+For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
+\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
+\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
+The right-hand side is
+\begin{align*}
+(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
+&= 2(s, f)^2 (q_1, q_2).
+\end{align*}
+\end{proof}
+
+An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.
+
+\begin{thm}
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
+\label{thm:2d3psi}
+\end{thm}
+\begin{proof}
+Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
+\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
+\end{proof}
+
+We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
+The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
+Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
+
+Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
+\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
+
+\begin{thm}
+For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
+\label{thm:2dmatter3psi}
+\end{thm}
+\begin{proof}
+Pick basis elements $s\in S_+$ and $f\in S_-$, so that
+\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
+The right-hand side is
+\begin{align*}
+(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
+&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
+\end{align*}
+We have
+\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
+so the left-hand side is
+\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
+By associativity of $A$ the two expressions are equal.
+\end{proof}
+
+\subsection{Supersymmetric twisting}
+
+\begin{definition}
+A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+\end{definition}
+
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+\begin{itemize}
+\item A supercharge $Q$ is \defterm{topological} if $d = n$.
+
+\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
+The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+\begin{definition}
+A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{definition}
+
+Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
+Recall, this means we have a Maurer-Cartan element 
+\[
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
+Define
+\[
+I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
+\]
+Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
+
+\begin{definition} \label{def:twisting}
+Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
+for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+\end{definition}
+
+\begin{prop}
+The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
+\end{prop}
+
+\begin{proof}
+The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
+Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
+Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
+
+Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
+The operator 
+\end{proof}
+
+\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{remark}
+Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
+\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
+where the $\ZZ/2$-grading on $E$ is the total grading.
+\end{remark}
+
+\subsection{Dimensional Reduction of Supersymmetric Theories}
+
+Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
+
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
+This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
+We have a natural embedding
+\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
+so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
+\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
+where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
+\[G_W = G_V\times \Spin(W^\perp_\RR).\]
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
+We have the following generalization of this statement to supersymmetric theories.
+
+\begin{prop} \label{prop:susydimlred}
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
+\end{prop}
+
+\begin{proof}
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+\end{proof}
+
+The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
+
+\begin{prop}
+Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
+Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
+\label{prop:twistdimensionalreduction}
+\end{prop}
+
+\subsection{Twisting Homomorphisms and Curved Backgrounds}
+
+\subsection{A-Type Twists} \label{A_twist_section}
+\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
+
+%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
+
+% \begin{landscape}
+% \begin{figure}
+% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+% \node (825) [right=of 82] {};
+% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+% 
+% \draw[arrow] (101) -- (91);
+% \draw[arrow] (91) -- (81);
+% \draw[arrow] (91) -- (82);
+% \draw[arrow] (81) -- (71);
+% \draw[arrow] (82) -- (71);
+% \draw[arrow] (82) -- (72);
+% \draw[arrow] (83) -- (73);
+% \draw[arrow] (71) -- (61);
+% \draw[arrow] (71) -- (62);
+% \draw[arrow] (72) -- (62);
+% \draw[arrow] (72) -- (63);
+% \draw[arrow] (73) -- (65);
+% \draw[arrow] (61) -- (51);
+% \draw[arrow] (62) -- (51);
+% \draw[arrow] (62) -- (52);
+% \draw[arrow] (63) -- (53);
+% \draw[arrow] (64) -- (52);
+% \draw[arrow] (64) -- (54);
+% \draw[arrow] (65) -- (54);
+% \draw[arrow] (51) -- (41);
+% \draw[arrow] (51) -- (42);
+% \draw[arrow] (52) -- (42);
+% \draw[arrow] (52) -- (43);
+% \draw[arrow] (53) -- (43);
+% \draw[arrow] (54) -- (43);
+% \draw[arrow] (54) -- (44);
+% \draw[arrow] (54) -- (45);
+% \draw[arrow] (41) -- (31);
+% \draw[arrow] (42) -- (31);
+% \draw[arrow] (42) -- (32);
+% \draw[arrow] (43) -- (32);
+% \draw[arrow] (44) -- (32);
+% \draw[arrow] (45) -- (32);
+% \draw[arrow] (31) -- (21);
+% \draw[arrow] (31) -- (22);
+% \draw[arrow] (32) -- (22);
+% 
+% \node (2d) [dimension, left=of 21] {2d};
+% \node (3d) [dimension, above=of 2d] {3d};
+% \node (4d) [dimension, above=of 3d] {4d};
+% \node (5d) [dimension, above=of 4d] {5d};
+% \node (6d) [dimension, above=of 5d] {6d};
+% \node (7d) [dimension, above=of 6d] {7d};
+% \node (8d) [dimension, above=of 7d] {8d};
+% \node (9d) [dimension, above=of 8d] {9d};
+% \node (10d) [dimension, above=of 9d] {10d};
+% \end{tikzpicture}
+% \caption{Orbits of square-zero supercharges.}
+% \label{fig:superchargeorbits}
+% \end{figure}
 % \end{landscape}

### 2020-01-13 paper.tex
caption for figure

@@
 \end{tikzpicture}
-\caption{Orbits of square-zero supercharges.}
+\caption{This figure shows the orbits of square-zero supercharges in each dimension.
+The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiplet orbits.
+Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.
+Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.}
 \label{fig:superchargeorbits}

### 2020-01-13 paper.tex
compiler error
note on changes to make

@@
 
-\tikzstyle{s16} = [rectangle, rounded corners, text centered, innersep=0pt, draw=black,fill=red!30]
+\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=red!30]
 \tikzstyle{s16chiral} = [s16, dashed]
@@
 
+\chris{Todo: would be more correct to remove the generic rank 2 twist in 3d, same as the 3d A twist (dual RW).
+I should do this in the tables and the diagrams.
+Also todo: change the labels of orbits to A and B.}
+
 \begin{table}[!h]

### 2020-01-13 paper.tex
2d

--- 2020-01-13 paper.tex
@@
 \newcommand{\matter}{\mathrm{matter}}
-\newcommand{\MU}{\mathrm{MU}}
 \renewcommand{\Re}{\mathrm{Re}}
-\newcommand{\U}{\mathrm{U}}
-
-\newcommand{\ham}{/\!\!/}
+%\newcommand{\U}{\mathrm{U}}
 
@@
 \usepackage{pdflscape}
-\usetikzlibrary{shapes.geometric, arrows, positioning, matrix}
-
-\tikzstyle{s16} = [rectangle, rounded corners, text centered, innersep=0pt, draw=black,fill=red!30]
+\usetikzlibrary{shapes.geometric, arrows, positioning}
+
+\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
-\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
-\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
+\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
+\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
+\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
 \tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
@@
 
-\begin{abstract}
-
-\end{abstract}
-
 \tableofcontents
@@
 \section*{Introduction}
-\begin{table}[htbp]
- \centering
- \begin{tabular}{c|c|c|c|c}
- $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
- \hline
- \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
- &&&$\bun_G(\CC^5)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
- &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
- \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
- &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
- &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
- &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
-  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
- &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
- &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
- &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
- \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
- &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
- &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
- &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
- &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
- &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
- &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
- &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
- &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
- &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
- &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
- &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $2$ (generic)} & {Perturbatively trivial (generic)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
- %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
- %&&& {} & \\ \cline{3-5}
- %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
- %&&& {} & \\ \cline{3-5}
- %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
- %&&& {} & \\ \hline
- \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
- \label{table_of_twists_16}
-\end{table}
-
-\begin{table}[!h]
- \centering
- \begin{tabular}{c|c|c|c|c}
- $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
- \hline
- \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
- &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
- \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
- &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
- \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
- &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
- \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
-  \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
- \label{table_of_twists_16}
-\end{table}
-
-\begin{table}[htbp]
- \centering
- \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
- $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
- \hline
- \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
- \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
- &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
-  \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
- \label{table_of_twists_16}
-\end{table}
-
-\begin{figure}[hbp]
-\begin{tikzpicture}
-  \matrix (mat) [nodes in empty cells, minimum width=3.5ex, minimum height=3.5ex, column sep=1.8ex,row sep=6ex]{
-   \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
-  \node {8}; &    &   & \node[s16] (88) {$(1,0)_i$};  &   &   &   &&   &&&&   &&&   \\
-  \node {7}; &    &   &   & \node[s16] (77) {$1_i$};  &   &   &&   &&&&   &&&   \\
-  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_g$};  &   &&   &&&&   &&&   \\
-  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_g$};  &   &&&&   &&&   \\
-  \node {4}; &    &   & \node[s16] (84) {$(1,0)_p$};  & \node[s16] (74) {$1_p$};  & \node[s16] (64) {$(1,1)_s$};  & \node[s16] (54) {$2_s$};  && \node[s16] (44B) {$(2,2)_s$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_g$};  &   &&&   \\
-  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &\node[s16] (33g) {$2_g$};  &   \\
-  \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
-  \node (i1) {1}; &   &  &  &  &  &   & &   &&& &   && &   \\};
-
-  \draw[thick] (corner.south west) -- (d2.south west);
-  \draw[thick] (corner.north east) -- (i1.south east);
-
-  \draw[dotted] (0.4,-7) -- (0.4,7);
-  \draw[dotted] (6.35,-7) -- (6.35,7);
-  \draw[dotted] (-2,-7) -- (-2,7);
-  \draw[dotted] (-3.8,-7) -- (-3.8,7);
-  \draw[dotted] (-4.75,-7) -- (-4.75,7);
-  \draw[dotted] (-6.25,-7) -- (-6.25,7);
-  \draw[dotted] (-7.1,-7) -- (-7.1,7);
-
-  \draw[arrow] (105) -- (95);
-  \draw[arrow] (95) -- (85);
-  \draw[arrow] (88) -- (77);
-  \draw[arrow] (95) -- (84);
-  \draw[arrow] (85) -- (75);
-  \draw[arrow] (85) -- (74);
-  \draw[arrow] (84) -- (74);
-  \draw[arrow] (77) -- (66);
-  \draw[arrow] (75) -- (65);
-  \draw[arrow] (75) -- (64);
-  \draw[arrow] (74) -- (64);
-  \draw[arrow] (74) -- (63);
-  \draw[arrow] (66) -- (55A);
-  \draw[arrow] (65) -- (55B);
-  \draw[arrow] (65) -- (54);
-  \draw[arrow] (64) -- (54);
-  \draw[arrow] (64) -- (53);
-  \draw[arrow] (63) -- (53);
-  \draw[arrow] (55A) -- (44g);
-  \draw[arrow] (55B) -- (44B);
-  \draw[arrow] (54) -- (44B);
-  \draw[arrow] (54) -- (43);
-  \draw[arrow] (53) -- (43);
-  \draw[arrow] (53) -- (42);
-  \draw[arrow] (44B) -- (33B);
-  \draw[arrow] (44A) -- (33A);
-  \draw[arrow] (44K) -- (33A);
-  \draw[arrow] (44g) -- (33g);
-  \draw[arrow] (43) -- (33B);
-  \draw[arrow] (43) -- (32);
-  \draw[arrow] (42) -- (32);
-
-\end{tikzpicture}
-\caption{Orbits of square-zero supercharges.}
-\label{fig:superchargeorbits}
-\end{figure}
-
+
+\part{Supersymmetric Gauge Theory}
+
+\section{The BV-BRST Formalism}
+
+Throughout the paper we will mostly work with a $\ZZ\times\ZZ/2$-grading.
+\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
+For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
+
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
+We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
+We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
+\[\int_M f (\phi, \phi', \dots),\]
+where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
+The space of local functionals can be viewed as a subspace
+\[
+\oloc(\cE) \subset \cO(\cE_c)
+\]
+where we the integral symbol makes sense in earnest on sections which are compactly supported.
+We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
+
+Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
+By definition, this is 
+\[
+{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
+\]
+where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
+When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
+There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
+
+\subsection{Classical BV Theories}
+
+\begin{definition}
+A \defterm{free BV theory} on a manifold $M$ is the data:
+\begin{itemize}
+\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
+\[
+Q_{\mr{BV}} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
+\item a map of bundles
+\[
+\omega\colon E \otimes E \to \Dens_M [-1]
+\]
+that is
+\begin{enumerate}
+\item[$(1)$] fiberwise nondegenerate,
+\item[$(2)$] graded skew symmetric, and
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\end{enumerate}
+\end{itemize}
+\end{definition}
+
+We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
+\[
+\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
+\]
+This bracket is of cohomological degree $+1$. 
+To define the bracket, first note that there is a linear map
+\[
+\d_{dR} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+\]
+defined as follows. 
+A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
+\[
+D_1(-) \cdots D_n(-) \Omega
+\]
+where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
+Without loss of generality, suppose $F$ is of this form. 
+Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
+\[
+\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
+\]
+where $\phi$ denotes a compactly supported section. 
+Define the symmetric multilinear map
+\[
+\begin{array}{ccccl}
+\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
+& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\end{array}
+\]
+Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
+
+The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega : E \cong E^! [-1]$ and hence an isomorphism of local functions
+\[
+\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+\]
+We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
+In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
+\[
+X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
+\]
+This is the Hamiltonian vector field corresponding to $F$. 
+Finally, the BV bracket between local functionals $F, G$ is defined by
+\[
+\{F, G\} = X_F (G) .
+\]
+
+The BV bracket enjoys the graded skew symmetry property
+\[
+\{F, G\} = (-1)^{|F| |G|} \{G, F\}
+\]
+as well as the graded Jacobi identity.
+This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
+Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
+
+\begin{definition}
+A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
+\[I \in \oloc^+(\cE)\]
+of cohomological degree zero satisfying the Maurer-Cartan equation
+\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+\end{definition}
+
+Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
+\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
+the BV action of the theory.
+
+The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
+
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
+The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
+
+Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
+
+\begin{remark}
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
+\end{remark}
+
+\begin{remark}
+The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e. a symplectic isomorphism $L\cong L^![-3]$.
+\end{remark}
+
+Next, we formulate the notion of an equivalence of classical BV theories.
+
+\begin{definition}
+A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
+a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
+\end{definition}
+
+We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
+First, we consider the process of integrating out an auxiliary field.
+
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
+
+\begin{prop}
+Fix a volume form $\dvol_M$ on $M$.
+Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
+Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
+Suppose the BV action is
+\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
+where $S_0$ and $S_1$ are independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
+\label{prop:integrateoutfield}
+\end{prop}
+
+\begin{proof}
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
+Then we define the required perturbative equivalence as follows.
+First $F_1(e) = (e, Q_1(e), 0) \in E$.
+Then, for $n > 1$, define
+\begin{align*}
+F_n \colon \sym^n(E_0) &\to E \\
+e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
+\end{align*}
+These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
+\begin{align*}
+S(F(e)) &= S(e, S_1(e), 0) \\
+&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
+&= S_0(e) - \frac 12 S_1(e)^2 \\
+&= S'(e).
+\end{align*}
+Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
+\end{proof}
+
+We may also remove a trivial BRST doublet.
+
+\begin{prop}
+Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
+Suppose
+\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
+\label{prop:BRSTdoublet}
+\end{prop}
+
+\begin{proof}
+Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
+We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
+\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
+Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
+Also, by construction, the $F_n$ intertwine the action functionals, since
+\begin{align*}
+S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
+&= S_0(e).
+\end{align*}
+Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
+\end{proof}
+
+\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
+
+In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Consider the graded vector space
+\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
+\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
+parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
+where $x_j \in \fg$. 
+We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
+\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
+and the degree $+1$ BV bracket by the formula
+\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
+where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
+\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
+The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
+\]
+where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
+The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
+Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
+
+\begin{definition}
+\label{infinitesimal_action_def}
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
+\begin{itemize}
+\item[(1)]
+An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
+where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $I_\fg^{(0)} = I$;
+\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
+\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
+\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\end{itemize}
+\item[(2)]
+For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
+An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
+\[
+Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+\]
+is elliptic as a $C^\bu(\fg)$-linear differential operator.
+\end{itemize}
+\end{definition}
+
+\begin{rmk}
+\brian{Explain $C^\bu(\fg)$-linear elliptic}
+\end{rmk}
+
+\begin{rmk}
+We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
+One can also formulate actions of a Lie algebra on a classical theory in these terms. 
+The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
+\[
+\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
+\]
+is satisfied.
+\end{rmk}
+
+\begin{rmk}
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
+Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
+By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
+\[
+\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
+\]
+combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
+\end{rmk}
+
+We may also define actions of supergroups on classical field theories.
+
+\begin{definition}
+\label{group_action_def}
+Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
+An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
+\begin{itemize}
+\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
+
+\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
+\end{itemize}
+These are required to satisfy the following conditions:
+\begin{itemize}
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
+
+\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\end{itemize}
+\end{definition}
+
+\begin{remark}
+While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
+\end{remark}
+
+\subsection{From BRST to BV}
+
+\begin{definition}
+A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
+\begin{itemize}
+\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\end{itemize}
+Together, these data must satisfy the equation
+\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
+where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+\end{definition}
+
+We call $\cF$ the \defterm{space of BRST fields}.
+
+From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
+Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
+
+First, we define the free BV theory.
+Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
+\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
+The underlying bundle of the BV theory is
+\[
+E = F \oplus F^! [-1].
+\]
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
+The differential of the free BV theory is
+\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
+\]
+
+The interacting theory is constructed as follows.
+First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
+These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
+\[
+I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
+\] 
+which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
+\[
+I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
+\]
+
+\begin{lemma}
+Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
+\end{lemma}
+
+We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
+In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
+
+If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
+\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
+\brian{Looks like you're using a bracket we haven't defined. 
+We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
+\subsection{Examples of Classical Field Theories}
+
+In this section we give some examples of classical field theories we will use.
+All theories we consider in this section are $\ZZ$-graded, i.e.
+all fields are considered even with respect to the $\ZZ/2$-grading.
+
+\subsubsection{Generalized BF theory} \label{gen_BF_section}
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix an $L_\infty$ algebra $\fg$.
+The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
+$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
+
+\item The BRST action is $S_{\mr{BRST}} = 0$.
+\end{itemize}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+\label{def:generalizedBF}
+\end{definition}
+
+\begin{remark}
+We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
+\end{remark}
+
+Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
+\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
+where we denote the two fields by $A$ and $B$. The BV action is
+\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
+where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
+
+\begin{example}
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
+\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
+\end{example}
+
+Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
+In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix a complex vector space $V$.
+The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
+$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
+
+\item The BRST action is $S_{\mr{BRST}} = 0$.
+\end{itemize}
+\end{definition}
+
+\begin{rmk}
+This is a special case of generalized BF theory:
+the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure. 
+\end{rmk}
+
+\brian{Symplectic, non-polarized version needed for 6d N=(1,0).} \chris{following Brian's suggestion I've used the term: holomorphic BF theory coupled to a higher holomorphic symplectic boson, valued in a representation $U$.
+If we continue to use that term, we should explain it here.}
+
+\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
+
+The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix an $L_\infty$ algebra $\fg$.
+We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
+\begin{itemize}
+\item The spacetime is the smooth manifold $X\times Y\times M$.
+
+\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
+
+\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
+
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
+
+\item The interaction term is
+\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
+\end{itemize}
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+\label{def:generalizedCS}
+\end{definition}
+
+We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
+
+\begin{example}
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
+\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
+\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+\end{example}
+
+\begin{example}
+If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
+The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
+Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
+\end{example}
+
+\subsection{Dimensional Reduction} \label{dim_red_section}
+
+In this section we formulate the procedure of dimensional reduction of a classical field theory.
+Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
+an isomorphism $p^*\Dens_N\cong \Dens_M$.
+The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
+We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
+
+\begin{definition}
+We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+\begin{itemize}
+\item The diagram
+\[
+\xymatrix{
+p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
+E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
+}
+\]
+is commutative.
+
+\item The diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+is commutative.
+
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
+\end{itemize}
+\end{definition}
+
+We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
+Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
+In fact, when dimensional reduction makes sense, this groupoid is always contractible.
+
+\begin{prop}
+Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
+Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
+
+Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
+If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
+\label{prop:dimensionalreductionunique}
+\end{prop}
+\begin{proof} \textbf{Uniqueness}.
+We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
+Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
+In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
+
+Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
+\[
+\xymatrix{
+\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
+\cE_M \ar^{Q_M}[r] & \cE_M[1]
+}
+\]
+uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
+
+\textbf{Existence}.
+Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
+Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
+Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
+The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
+\end{proof}
+
+\begin{remark}
+Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
+\end{remark}
+
+We will now describe dimensional reductions of the classical Chern--Simons theory.
+
+\begin{prop} \label{CS_to_BF_diml_red_prop}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
+\end{prop}
+
+\begin{proof}
+To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+\[\map(\pt, T^*[-1] B \fg)\]
+has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
+
+We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
+Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
+The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
+Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
+\end{proof}
+
+\begin{prop} \label{CS_diml_red_prop}
+Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
+\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+\end{prop}
+
+\begin{proof}
+We may assume $X,Y,M=\pt$ as in the previous proof.
+
+We have
+\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
+and
+\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
+Under the pullback map
+\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
+the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
+\end{proof}
+
+\section{Supersymmetry} \label{sec: susy}
+
+In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
+
+\subsection{Supersymmetry algebras}
+
+Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+\begin{itemize}
+\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.
+
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
+\end{itemize}
+
+\begin{definition}
+A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
+\end{definition}
+
+So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
+
+\begin{definition}
+Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
+\end{definition}
+
+For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
+In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
+\begin{itemize}
+\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
+
+\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
+
+\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
+
+\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
+\end{itemize}
+
+Fix the following data:
+\begin{itemize}
+\item A spinorial representation $\Sigma$ of $\so(V)$.
+
+\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
+
+\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
+\end{itemize}
+
+Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
+
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
+
+\begin{definition}
+\label{dfn: super}
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
+\end{definition}
+
+\subsection{Division algebras and minimal supersymmetry}
+\label{sect:divisionalgebras}
+
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and division algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+
+Let $A_\RR$ be a (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+\begin{enumerate}
+\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\end{enumerate}
+
+For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
+We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
+$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
+
+We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
+So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
+
+Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
+
+\begin{lemma}
+Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
+Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
+\label{lm:extendpairing}
+\end{lemma}
+
+Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$ \chris{it's a bit unclear here why they're notated differently}. We have action maps
+\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
+given, respectively, by
+\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
+
+The following is proved in \cite[Proposition 6]{BaezHuerta}.
+
+\begin{prop}
+The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
+\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
+\end{prop}
+
+So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
+
+We have a nondegenerate scalar spinorial pairing
+\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
+given by
+\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
+It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
+\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
+
+By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
+\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
+
+We will now state two important properties of $\Gamma$ and the spinorial pairing.
+The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
+
+\begin{thm}
+Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
+\label{thm:3psi}
+\end{thm}
+
+If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
+
+\begin{thm}
+Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
+\label{thm:matter3psi}
+\end{thm}
+\begin{proof}
+The right-hand side is
+\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
+which by associativity can be rewritten as
+\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
+which is the left-hand side.
+\end{proof}
+
+We will be interested in the following four examples:
+\begin{enumerate}
+\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
+
+\item (\textbf{4d $\mc N=1$ supersymmetry}) $A_\RR = \CC$.
+We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
+
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$.
+We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
+\end{enumerate}
+
+All four examples are alternative, while the first three examples are moreover associative.
+
+\subsection{Two-dimensional chiral supersymmetry}
+
+In the previous section we have related division algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
+In this section we explain a different relationship between division algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
+
+Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
+\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
+and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
+\begin{equation}
+(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
+\label{eq:2dvectorpairing}
+\end{equation}
+
+Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
+\[\Sigma = S_+\otimes W\]
+and its dual
+\[\Sigma^* = S_-\otimes W.\]
+The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
+\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
+and similarly for $V\otimes S_-\rightarrow S_+$.
+
+\begin{prop}
+For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
+\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
+\begin{align*}
+\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
+&= 4(s, f)^2 s.
+\end{align*}
+But by \eqref{eq:2dvectorpairing} we have
+\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
+which proves the claim.
+\end{proof}
+
+The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
+Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
+
+The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
+\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
+and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.
+
+\begin{prop}
+For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
+\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
+\end{prop}
+\begin{proof}
+It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
+\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
+The right-hand side is
+\begin{align*}
+(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
+&= 2(s, f)^2 (q_1, q_2).
+\end{align*}
+\end{proof}
+
+An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.
+
+\begin{thm}
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
+\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
+\label{thm:2d3psi}
+\end{thm}
+\begin{proof}
+Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
+\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
+\end{proof}
+
+We will now fix an associative algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and set $W = A$.
+The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
+Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
+
+Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
+\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
+
+\begin{thm}
+For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
+\label{thm:2dmatter3psi}
+\end{thm}
+\begin{proof}
+Pick basis elements $s\in S_+$ and $f\in S_-$, so that
+\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
+The right-hand side is
+\begin{align*}
+(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
+&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
+\end{align*}
+We have
+\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
+so the left-hand side is
+\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
+By associativity of $A$ the two expressions are equal.
+\end{proof}
+
+\subsection{Supersymmetric twisting}
+
+\begin{definition}
+A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+\end{definition}
+
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+\begin{itemize}
+\item A supercharge $Q$ is \defterm{topological} if $d = n$.
+
+\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
+\end{itemize}
+
+In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
+The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+\begin{definition}
+A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+\end{definition}
+
+Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
+Recall, this means we have a Maurer-Cartan element 
+\[
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
+Define
+\[
+I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
+\]
+Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
+
+\begin{definition} \label{def:twisting}
+Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
+The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
+for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+\end{definition}
+
+\begin{prop}
+The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
+\end{prop}
+
+\begin{proof}
+The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
+Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
+Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
+
+Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
+The operator 
+\end{proof}
+
+\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
+
+\begin{remark}
+Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
+\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
+where the $\ZZ/2$-grading on $E$ is the total grading.
+\end{remark}
+
+\subsection{Dimensional Reduction of Supersymmetric Theories}
+
+Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
+
+Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
+This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
+We have a natural embedding
+\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
+so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
+\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
+where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
+\[G_W = G_V\times \Spin(W^\perp_\RR).\]
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+
+Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
+We have the following generalization of this statement to supersymmetric theories.
+
+\begin{prop} \label{prop:susydimlred}
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
+\end{prop}
+
+\begin{proof}
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+\end{proof}
+
+The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
+
+\begin{prop}
+Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
+Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
+\label{prop:twistdimensionalreduction}
+\end{prop}
+
+\subsection{Twisting Homomorphisms and Curved Backgrounds}
+
+\subsection{A-Type Twists} \label{A_twist_section}
+\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
+
+%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
+
+% \begin{landscape}
 % \begin{figure}
@@
 % \end{figure}
-
-\part{Supersymmetric Gauge Theory}
-
-\section{The BV-BRST Formalism}
-
-In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.
-Most of the material in this section is not original.
-We refer the reader to \chris{refs} for more details.
-We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
-We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.
-We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.
-
-\subsection{Conventions}
-Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
-\emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
-For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
-
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
-We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
-We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
-\[\int_M f (\phi, \phi', \dots),\]
-where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
-The space of local functionals can be viewed as a subspace
-\[
-\oloc(\cE) \subset \cO(\cE_c)
-\]
-where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
-We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.
-
-Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
-By definition, this is 
-\[
-{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
-\]
-where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
-When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
-There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.
-
-\subsection{Classical BV Theories}
-
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
-
-\begin{definition}
-A \defterm{free BV theory} on a manifold $M$ is the data of:
-\begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
-\[
-Q_{\mr{BV}} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
-\item a map of bundles
-\[
-\omega\colon E \otimes E \to \Dens_M [-1]
-\]
-that is
-\begin{enumerate}
-\item[$(1)$] fiberwise nondegenerate,
-\item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
-\end{enumerate}
-\end{itemize}
-\end{definition}
-
-We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
-\]
-This bracket is of cohomological degree $+1$. 
-We will now explain how to define the BV bracket.  First note that there is a linear map
-\[
-\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
-\]
-defined as follows. 
-A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
-\[
-D_1(-) \cdots D_n(-) \Omega
-\]
-where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
-Without loss of generality, suppose $F$ is of this form. 
-Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
-\[
-\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
-\]
-where $\phi$ denotes a compactly supported section. 
-Define the symmetric multilinear map
-\[
-\begin{array}{ccccl}
-\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
-& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
-\end{array}
-\]
-Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
-This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
-
-The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
-\[
-\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
-\]
-We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
-In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
-\[
-X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
-\]
-This is the Hamiltonian vector field corresponding to $F$. 
-Finally, the BV bracket between local functionals $F, G$ is defined by
-\[
-\{F, G\} = X_F (G) .
-\]
-
-The BV bracket enjoys the graded skew symmetry property
-\[
-\{F, G\} = (-1)^{|F| |G|} \{G, F\}
-\]
-as well as the graded Jacobi identity.
-This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
-Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
-
-Now, we will include interactions in the BV picture.
-
-\begin{definition}
-A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
-\[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
-\end{definition}
-
-Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
-the BV action of the theory.
-
-The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
-
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
-The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
-
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
-
-\begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
-\end{remark}
-
-\begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$.
-\chris{todo: add references}
-\end{remark}
-
-Next, we formulate the notion of an equivalence of classical BV theories.
-
-\begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
-A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
-\end{definition}
-
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories.
-First, we consider the process of integrating out an auxiliary field.
-
-\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
-
-\begin{prop}
-Fix a volume form $\dvol_M$ on $M$.
-Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
-Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
-Suppose the BV action is
-\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
-where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
-\label{prop:integrateoutfield}
-\end{prop}
-
-\begin{proof}
-Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
-Then we define the required perturbative equivalence as follows.
-First $F_1(e) = (e, Q_1(e), 0) \in E$.
-Then, for $n > 1$, define
-\begin{align*}
-F_n \colon \sym^n(E_0) &\to E \\
-e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
-\end{align*}
-These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
-\begin{align*}
-S(F(e)) &= S(e, S_1(e), 0) \\
-&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
-&= S_0(e) - \frac 12 S_1(e)^2 \\
-&= S'(e).
-\end{align*}
-Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
-\end{proof}
-
-We may also remove a trivial BRST doublet.
-
-\begin{prop}
-Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
-Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
-Suppose
-\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-\label{prop:BRSTdoublet}
-\end{prop}
-
-\begin{proof}
-Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
-We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
-\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
-Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
-Also, by construction, the $F_n$ intertwine the action functionals, since
-\begin{align*}
-S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
-&= S_0(e).
-\end{align*}
-Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
-\end{proof}
-
-\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
-
-In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-Consider the graded vector space
-\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
-parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
-where $x_j \in \fg$. 
-We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
-\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the degree $+1$ BV bracket by the formula
-\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
-where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
-\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
-\]
-where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
-Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
-
-\begin{definition}
-\label{infinitesimal_action_def}
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
-\begin{itemize}
-\item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$;
-\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
-\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
-\end{itemize}
-\item[(2)]
-For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
-\[
-Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
-\]
-is elliptic as a $C^\bu(\fg)$-linear differential operator.
-\end{itemize}
-\end{definition}
-
-\begin{rmk}
-\brian{Explain $C^\bu(\fg)$-linear elliptic}
-\end{rmk}
-
-\begin{rmk}
-We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
-One can also formulate actions of a Lie algebra on a classical theory in these terms. 
-The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
-\[
-\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
-\]
-is satisfied.
-\end{rmk}
-
-\begin{rmk}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
-Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
-defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
-By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
-\[
-\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
-\]
-combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
-\end{rmk}
-
-We may also define actions of supergroups on classical field theories.
-
-\begin{definition}
-\label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
-An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
-\begin{itemize}
-\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.
-
-\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
-\end{itemize}
-These are required to satisfy the following conditions:
-\begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
-\end{itemize}
-\end{definition}
-
-\begin{remark}
-While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
-\end{remark}
-
-\subsection{From BRST to BV}
-
-\begin{definition}
-A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
-\begin{itemize}
-\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
-\end{itemize}
-Together, these data must satisfy the equation
-\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
-where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
-\end{definition}
-
-We call $\cF$ the \defterm{space of BRST fields}.
-
-From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
-Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
-
-First, we define the free BV theory.
-Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
-\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
-The underlying bundle of the BV theory is
-\[
-E = F \oplus F^! [-1].
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
-The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
-\]
-
-The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
-These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
-\[
-I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
-\] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
-\]
-
-\begin{lemma}
-Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
-\end{lemma}
-
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
-
-If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
-\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-\brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
-\subsection{Examples of Classical Field Theories}
-
-In this section we give some examples of classical field theories we will use.
-All theories we consider in this section are $\ZZ$-graded, i.e.
-all fields are considered even with respect to the $\ZZ/2$-grading.
-
-\subsubsection{Generalized BF theory} \label{gen_BF_section}
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
-The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\label{def:generalizedBF}
-\end{definition}
-
-\begin{remark}
-We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
-\end{remark}
-
-Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
-\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
-where we denote the two fields by $A$ and $B$. The BV action is
-\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
-where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
-
-\begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
-\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
-\end{example}
-
-Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
-In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix a complex vector space $V$.
-The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
-$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-\end{definition}
-
-\begin{rmk}
-This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
-\end{rmk}
-
-We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
-
-\begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\]
-with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
-where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}
-
-The following is obvious from the definition.
-
-\begin{prop}
-Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
-Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\label{prop:BFrotationaction}
-\end{prop}
-
-\begin{remark}
-In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
-\end{remark}
-
-\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
-
-The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
-
-\begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
-We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-
-\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
-
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
-
-\item The interaction term is
-\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
-\label{def:generalizedCS}
-\end{definition}
-
-We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
-
-\begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
-\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
-\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-\end{example}
-
-\begin{example}
-If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
-The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
-Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
-\end{example}
-
-\begin{example}
-Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
-Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
-Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
-with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
-The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
-The space of fields in the corresponding Chern--Simons theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
-
-Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
-\begin{align*}
-E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
-\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
-\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
-\end{align*}
-and the action functional as before.
-\label{ex:CSHamiltonianreduction}
-\end{example}
-
-As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.
-
-\begin{prop}
-Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
-Then it carries an action of $\SU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\end{prop}
-
-We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
-Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$.
-We define the unitary metalinear group to be
-\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
-where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
-
-\begin{prop}
-Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
-Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
-\end{prop}
-
-\subsection{Dimensional Reduction} \label{dim_red_section}
-
-In this section we formulate the procedure of dimensional reduction of a classical field theory.
-Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
-an isomorphism $p^*\Dens_N\cong \Dens_M$.
-The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.
-We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.
-
-\begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
-\begin{itemize}
-\item The diagram
-\[
-\xymatrix{
-p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
-E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
-}
-\]
-is commutative.
-
-\item The diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-is commutative.
-
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
-\end{itemize}
-\end{definition}
-
-We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
-Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
-In fact, when dimensional reduction makes sense, this groupoid is always contractible.
-
-\begin{prop}
-Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
-Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
-
-Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
-If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
-\label{prop:dimensionalreductionunique}
-\end{prop}
-\begin{proof} \textbf{Uniqueness}.
-We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
-Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
-In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
-
-Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
-
-\textbf{Existence}.
-Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
-Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
-Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
-The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
-\end{proof}
-
-\begin{remark}
-Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
-\end{remark}
-
-We will now describe dimensional reductions of the classical Chern--Simons theory.
-
-\begin{prop} \label{CS_to_BF_diml_red_prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
-\end{prop}
-
-\begin{proof}
-To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
-\[\map(\pt, T^*[-1] B \fg)\]
-has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
-
-We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
-Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
-Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
-\end{proof}
-
-\begin{prop} \label{CS_diml_red_prop}
-Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
-\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-\end{prop}
-
-\begin{proof}
-We may assume $X,Y,M=\pt$ as in the previous proof.
-
-We have
-\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
-and
-\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
-Under the pullback map
-\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
-the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\end{proof}
-
-\section{Supersymmetry} \label{sec: susy}
-
-In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
-
-\subsection{Supersymmetry algebras}
-
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
-\begin{itemize}
-\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.
-
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
-\end{itemize}
-
-\begin{definition}
-A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
-\end{definition}
-
-So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
-
-\begin{definition}
-Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
-\end{definition}
-
-For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
-In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
-\begin{itemize}
-\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.
-
-\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.
-
-\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.
-
-\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
-\end{itemize}
-
-Fix the following data:
-\begin{itemize}
-\item A spinorial representation $\Sigma$ of $\so(V)$.
-
-\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.
-
-\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
-\end{itemize}
-
-Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
-
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
-
-\begin{definition}
-\label{dfn: super}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
-\end{definition}
-
-\subsection{Composition algebras and minimal supersymmetry}
-\label{sect:compositionalgebras}
-
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
-
-Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
-\begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
-\end{enumerate}
-
-It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
-$A_\RR$ is a real composition algebra.
-
-For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
-$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
-Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-
-We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
-So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
-
-Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
-
-\begin{lemma}
-Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
-Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
-\label{lm:extendpairing}
-\end{lemma}
-
-Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
-\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
-given, respectively, by
-\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
-
-The following is proved in \cite[Proposition 6]{BaezHuerta}.
-
-\begin{prop}
-The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
-\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
-\end{prop}
-
-So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
-
-We have a nondegenerate scalar spinorial pairing
-\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
-given by
-\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
-It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
-\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
-
-By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
-\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]
-
-We will now state two important properties of $\Gamma$ and the spinorial pairing.
-The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
-
-\begin{thm}
-Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
-\label{thm:3psi}
-\end{thm}
-
-If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.
-
-\begin{thm}
-Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
-\label{thm:matter3psi}
-\end{thm}
-\begin{proof}
-The right-hand side is
-\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
-which by associativity can be rewritten as
-\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
-which is the left-hand side.
-\end{proof}
-
-We will be interested in the following examples:
-\begin{enumerate}
-\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
-
-\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
-Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
-We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).
-
-\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
-We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).
-
-\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
-We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
-\end{enumerate}
-
-All four examples are alternative, while the first three examples are moreover associative.
-
-\subsection{Two-dimensional chiral supersymmetry}
-
-In the previous section we have related composition algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10.
-In this section we explain a different relationship between composition algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.
-
-Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
-\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
-and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
-\begin{equation}
-(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
-\label{eq:2dvectorpairing}
-\end{equation}
-
-Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
-\[\Sigma = S_+\otimes W\]
-and its dual
-\[\Sigma^* = S_-\otimes W.\]
-The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
-\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
-and similarly for $V\otimes S_-\rightarrow S_+$.
-
-\begin{prop}
-For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
-\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
-\end{prop}
-\begin{proof}
-It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
-\begin{align*}
-\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
-&= 4(s, f)^2 s.
-\end{align*}
-But by \eqref{eq:2dvectorpairing} we have
-\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
-which proves the claim.
-\end{proof}
-
-The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
-Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
-
-The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
-\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
-and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.
-
-\begin{prop}
-For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
-\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
-\end{prop}
-\begin{proof}
-It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
-\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
-The right-hand side is
-\begin{align*}
-(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
-&= 2(s, f)^2 (q_1, q_2).
-\end{align*}
-\end{proof}
-
-An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.
-
-\begin{thm}
-For $Q_1, Q_2, Q_3\in\Sigma$ we have
-\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
-\label{thm:2d3psi}
-\end{thm}
-\begin{proof}
-Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
-\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
-\end{proof}
-
-We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
-The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
-Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
-
-Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
-\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
-
-\begin{thm}
-For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
-\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
-\label{thm:2dmatter3psi}
-\end{thm}
-\begin{proof}
-Pick basis elements $s\in S_+$ and $f\in S_-$, so that
-\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
-The right-hand side is
-\begin{align*}
-(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
-&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
-\end{align*}
-We have
-\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
-so the left-hand side is
-\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
-By associativity of $A$ the two expressions are equal.
-\end{proof}
-
-\subsection{Supersymmetric twisting}
-
-\begin{definition}
-A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
-\end{definition}
-
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
-\begin{itemize}
-\item A supercharge $Q$ is \defterm{topological} if $d = n$.
-
-\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
-\end{itemize}
-
-In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge.
-The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
-
-\begin{definition}
-A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
-Recall, this means we have a Maurer-Cartan element 
-\[
-I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
-\]
-where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
-For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
-Define
-\[
-I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
-\]
-Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
-
-\begin{definition} \label{def:twisting}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
-\end{definition}
-
-\begin{prop}
-The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
-\end{prop}
-
-\begin{proof}
-The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
-Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
-Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
-
-Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
-The operator 
-\end{proof}
-
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
-\end{remark}
-
-\subsection{Dimensional Reduction of Supersymmetric Theories}
-
-Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.
-
-Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
-We have a natural embedding
-\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
-so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
-\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
-where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
-\[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
-
-Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique.
-We have the following generalization of this statement to supersymmetric theories.
-
-\begin{prop} \label{prop:susydimlred}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
-\end{prop}
-
-\begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
-\end{proof}
-
-The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.
-
-\begin{prop}
-Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
-Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
-\label{prop:twistdimensionalreduction}
-\end{prop}
-
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
-
-\subsection{A-Type Twists} \label{A_twist_section}
-\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
-
-%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
-
-% \begin{landscape}
-% \begin{figure}
-% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-% \node (825) [right=of 82] {};
-% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-% 
-% \draw[arrow] (101) -- (91);
-% \draw[arrow] (91) -- (81);
-% \draw[arrow] (91) -- (82);
-% \draw[arrow] (81) -- (71);
-% \draw[arrow] (82) -- (71);
-% \draw[arrow] (82) -- (72);
-% \draw[arrow] (83) -- (73);
-% \draw[arrow] (71) -- (61);
-% \draw[arrow] (71) -- (62);
-% \draw[arrow] (72) -- (62);
-% \draw[arrow] (72) -- (63);
-% \draw[arrow] (73) -- (65);
-% \draw[arrow] (61) -- (51);
-% \draw[arrow] (62) -- (51);
-% \draw[arrow] (62) -- (52);
-% \draw[arrow] (63) -- (53);
-% \draw[arrow] (64) -- (52);
-% \draw[arrow] (64) -- (54);
-% \draw[arrow] (65) -- (54);
-% \draw[arrow] (51) -- (41);
-% \draw[arrow] (51) -- (42);
-% \draw[arrow] (52) -- (42);
-% \draw[arrow] (52) -- (43);
-% \draw[arrow] (53) -- (43);
-% \draw[arrow] (54) -- (43);
-% \draw[arrow] (54) -- (44);
-% \draw[arrow] (54) -- (45);
-% \draw[arrow] (41) -- (31);
-% \draw[arrow] (42) -- (31);
-% \draw[arrow] (42) -- (32);
-% \draw[arrow] (43) -- (32);
-% \draw[arrow] (44) -- (32);
-% \draw[arrow] (45) -- (32);
-% \draw[arrow] (31) -- (21);
-% \draw[arrow] (31) -- (22);
-% \draw[arrow] (32) -- (22);
-% 
-% \node (2d) [dimension, left=of 21] {2d};
-% \node (3d) [dimension, above=of 2d] {3d};
-% \node (4d) [dimension, above=of 3d] {4d};
-% \node (5d) [dimension, above=of 4d] {5d};
-% \node (6d) [dimension, above=of 5d] {6d};
-% \node (7d) [dimension, above=of 6d] {7d};
-% \node (8d) [dimension, above=of 7d] {8d};
-% \node (9d) [dimension, above=of 8d] {9d};
-% \node (10d) [dimension, above=of 9d] {10d};
-% \end{tikzpicture}
-% \caption{Orbits of square-zero supercharges.}
-% \label{fig:superchargeorbits}
-% \end{figure}
 % \end{landscape}
@@
 Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a real associative composition algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and denote its complexification by $A$.
+In addition, fix a real associative algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:divisionalgebras} and denote its complexification by $A$.
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
@@
 %\begin{landscape}
-
+\begin{figure}
+\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+\node (825) [right=of 82] {};
+\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+
+\draw[arrow] (101) -- (91);
+\draw[arrow] (91) -- (81);
+\draw[arrow] (91) -- (82);
+\draw[arrow] (81) -- (71);
+\draw[arrow] (82) -- (71);
+\draw[arrow] (82) -- (72);
+\draw[arrow] (83) -- (73);
+\draw[arrow] (71) -- (61);
+\draw[arrow] (71) -- (62);
+\draw[arrow] (72) -- (62);
+\draw[arrow] (72) -- (63);
+\draw[arrow] (73) -- (65);
+\draw[arrow] (61) -- (51);
+\draw[arrow] (62) -- (51);
+\draw[arrow] (62) -- (52);
+\draw[arrow] (63) -- (53);
+\draw[arrow] (64) -- (52);
+\draw[arrow] (64) -- (54);
+\draw[arrow] (65) -- (54);
+\draw[arrow] (51) -- (41);
+\draw[arrow] (51) -- (42);
+\draw[arrow] (52) -- (42);
+\draw[arrow] (52) -- (43);
+\draw[arrow] (53) -- (43);
+\draw[arrow] (54) -- (43);
+\draw[arrow] (54) -- (44);
+\draw[arrow] (54) -- (45);
+\draw[arrow] (41) -- (31);
+\draw[arrow] (42) -- (31);
+\draw[arrow] (42) -- (32);
+\draw[arrow] (43) -- (32);
+\draw[arrow] (44) -- (32);
+\draw[arrow] (45) -- (32);
+\draw[arrow] (31) -- (21);
+\draw[arrow] (31) -- (22);
+\draw[arrow] (32) -- (22);
+
+\node (2d) [dimension, left=of 21] {2d};
+\node (3d) [dimension, above=of 2d] {3d};
+\node (4d) [dimension, above=of 3d] {4d};
+\node (5d) [dimension, above=of 4d] {5d};
+\node (6d) [dimension, above=of 5d] {6d};
+\node (7d) [dimension, above=of 6d] {7d};
+\node (8d) [dimension, above=of 7d] {8d};
+\node (9d) [dimension, above=of 8d] {9d};
+\node (10d) [dimension, above=of 9d] {10d};
+\end{tikzpicture}
+\caption{Orbits of square-zero supercharges.}
+\label{fig:superchargeorbits}
+\end{figure}
 %\end{landscape}
@@
 &\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
-I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
+I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
 I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
@@
 First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int \dvol  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int \dvol (\phi, \psi_0^*)$.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_{1,1}^*)$.  
 Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
@@
 \item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W \otimes \fg)$. 
-\item $R$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes R)$;
-\item $R$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_- \otimes R)$ .
-\end{itemize}
-
-% \cN=(0,4) Super Yang-Mills with matter
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
+\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R^*)$.
+\end{itemize}
+Here, $W$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+Choose the basis $\{u,v\}$ for $W_-$ with pairing given by $\<u, v\> = 1$.
+
+We will twist by an element $Q = q \otimes w_1 \in S_- \otimes W_-$.
+
+The fields decompose as
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} &  {\rm Fermion} & R & {\rm Twisted}  \\
+c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & 0 & -1 \\
+A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) & (0,0) \\
+\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,1) & (1,-1) & (1,-1) \\
+\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 & 0 \\
+\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 & 0 \\
+\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & 1 & -1 & -1 \\
+\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 & 1 
+\end{array}
+\]
+The anti-fields decompose as
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} &  {\rm Fermion} & R & {\rm Twisted}  \\
+c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 0 & 2 \\
+A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (0,0) & (1,1) \\
+\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (1,1) & (-1,1) & (0,2) \\
+\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 0 & 1 \\
+\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 0 & 1 \\
+\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 1 & 2 \\
+\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & 1 & -1 & 0 
+\end{array}
+\]
+
+%\begin{align*}
+%c^* & \mapsto B_{1,1} \in \Omega^0(\CC ; \fg) \\
+%A^* & \mapsto A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \\
+%\lambda^* & \mapsto \lambda^*_{1,1} w_1 + \lambda^*_{0,1} w_2 \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \\
+%\phi^* & \mapsto \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) \\
+%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{1,1}(\CC ; R) \\
+%\psi^* & \mapsto \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) \\
+%\Bar{\psi}^* & \mapsto \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)  
+%\end{align*}
+
+The action functionals decompose as:
+\begin{align*}
+S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0})  \right)  \\
+S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi})) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} \wedge \partial_{A_{1,0}} \psi_{0})  + \\
+&\qquad + (([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1}) )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \beta_{1,1} + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \beta_{1,0} + [\psi_0, A_0] \psi_{1,1}^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
+I^{(1)}_{\mr{matter}} &=  \int \left( (\psi_{1,1}^*, \Bar{\phi}) + \frac 12(\beta_{1,0} \wedge \dbar \gamma_0) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
+\end{align*}
+%Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.
+
+\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
+The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
+\end{thm}
+\begin{proof}
+The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
+First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
+Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+ S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + \beta_{1,0} \dbar_{A_{0,1}} \gamma_{0} \\ 
+  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [\gamma_0, A_0]\wedge \beta_{1,1} + [\gamma_{0,1}, A_0]\wedge \beta_{1,0}  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{1,\bu}$ comprise the fields of the $\beta\gamma$ system.
+\end{proof}
+
+\subsection{$\cN=(0,4)$ Super Yang-Mills with matter}
+
+The untwisted fields are given by:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
+\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R^*)$.
+\end{itemize}
+Here, $W_-$ is a complex four-dimensional vector space equipped with a symmetric pairing. 
+Choose the basis $\{w_1,w_2,w_3,w_4\}$ for $W_-$ with pairing given by $\<w_1, w_2\> = 1$.
+
 % \cN=(0,8) Super Yang-Mills with matter

### 2020-01-13 paper.tex
0,N

@@
 \renewcommand{\Re}{\mathrm{Re}}
-\newcommand{\U}{\mathrm{U}}
+%\newcommand{\U}{\mathrm{U}}
+\def\U{\mathrm{U}}
 
@@
 \item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R^*)$.
+\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
 \end{itemize}
@@
 
-We will twist by an element $Q = q \otimes w_1 \in S_- \otimes W_-$.
+We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.
 
@@
 \begin{array} {lllcccccc}
-& &  & {\rm Untwisted} &  {\rm Fermion} & R & {\rm Twisted}  \\
-c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & 0 & -1 \\
-A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) & (0,0) \\
-\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,1) & (1,-1) & (1,-1) \\
-\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 & 0 \\
-\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 & 0 \\
-\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & 1 & -1 & -1 \\
-\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 & 1 
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
+A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
+\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
+\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
+\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
+\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
 \end{array}
@@
 \begin{array} {lllcccccc}
-& &  & {\rm Untwisted} &  {\rm Fermion} & R & {\rm Twisted}  \\
-c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 0 & 2 \\
-A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (0,0) & (1,1) \\
-\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (1,1) & (-1,1) & (0,2) \\
-\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 0 & 1 \\
-\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 0 & 1 \\
-\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 1 & 2 \\
-\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & 1 & -1 & 0 
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
+A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
+\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
+\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
+\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
+\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
+\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
 \end{array}
@@
 Here, $W_-$ is a complex four-dimensional vector space equipped with a symmetric pairing. 
-Choose the basis $\{w_1,w_2,w_3,w_4\}$ for $W_-$ with pairing given by $\<w_1, w_2\> = 1$.
+Choose the basis $\{u_1,u_2,v_1,v_2\}$ for $W_-$ with pairing given by $\<u_i, v_j\> = \delta_{ij}$.
 
 % \cN=(0,8) Super Yang-Mills with matter
+
+\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills with matter}
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\end{itemize}
+Choose a splitting $W_- = \CC\{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
+
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
+A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v + \chi \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_- \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
+\end{array}
+\]
+
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
+A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
+\end{array}
+\]
+
+\begin{align*}
+S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
+\end{align*}
 

### 2020-01-13 paper.tex
merging
(0,4)
(0,N)

@@
 the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
+\brian{This is not defined}
 \end{proof}
@@
 
+We consider $\cN=(0,2)$ super Yang-Mills coupled to the $\cN=(0,2)$ chiral multiplet with values in a representation $R$. 
+\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
+
 The untwisted fields are given by:
@@
 \item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R^*)$.
+\item $W_- \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W_- \otimes U)$;
+\item $U$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes U)$ .
 \end{itemize}
@@
 
-\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills with matter}
+\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills}
+
 \begin{itemize}
@@
 \end{itemize}
-Choose a splitting $W_- = \CC\{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
+Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
 
@@
 S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* \\
+&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
 I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
@@
 \end{align*}
+
+\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
+The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts on the left by the adjoint action.
+\end{thm}
+\begin{proof}
+First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
+Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+ S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
+  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
+\end{proof}
 

### 2020-01-13 paper.tex
(0,N)

@@
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts on the left by the adjoint action.
+The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
 \end{thm}
@@
 First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
-Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
+Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
 which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

### 2020-01-14 paper.tex
minor edits

@@
 
-\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
+\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$ 
 \end{itemize}
@@
 
+\brian{How do we see the various flavors of matter multiplets? For instance, in $2d (0,2)$ there is the Fermi multiplet and the chiral multiplet. 
+Your description only sees the chiral.
+In $2d (0,4)$ there are even more: the hypermultiplet (two $(0,2)$ chirals), the twisted hypermultiplet (the same as the hyper, different $R$-symmetry), the fermi multiplet (two $(0,2)$ fermi multiplets).
+I'm not sure which your description sees, but I have a hunch it's the $(0,4)$ hypermultiplet. 
+What is the reason for only seeing certain multiplets via this general setup?
+}
+
 In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e.
@@
 \subsection{$\cN=1$ with chiral multiplet matter} 
-There is a minimal supersymmetric field theory with $\cN=1$ supersymmetry consisting of a pure gauge theory coupled to supersymmetric matter depending on a complex representation $R$.
+We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
+The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.
 
@@
 
-We consider $\cN=(0,2)$ super Yang-Mills coupled to the $\cN=(0,2)$ chiral multiplet with values in a representation $R$. 
+We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
+The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.
+
 \brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
@@
 \subsection{$\cN=(0,4)$ Super Yang-Mills with matter}
+
+\brian{Confused.}
 

### 2020-01-14 paper.tex
merge

--- 2020-01-13 paper.tex
@@
 \renewcommand{\Re}{\mathrm{Re}}
-%\newcommand{\U}{\mathrm{U}}
-\def\U{\mathrm{U}}
+\renewcommand{\U}{\mathrm{U}}
 
@@
 
+\clearpage
 \begin{figure}[hbp]
@@
 the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\brian{This is not defined}
 \end{proof}
@@
 
-We consider $\cN=(0,2)$ super Yang-Mills coupled to the $\cN=(0,2)$ chiral multiplet with values in a representation $R$. 
-\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
-
 The untwisted fields are given by:
@@
 \item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W_- \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W_- \otimes U)$;
-\item $U$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes U)$ .
+\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
+\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R^*)$.
 \end{itemize}
@@
 
-\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills}
-
+\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills with matter}
 \begin{itemize}
@@
 \end{itemize}
-Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
+Choose a splitting $W_- = \CC\{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
 
@@
 S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* \\
 I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
@@
 \end{align*}
-
-\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts on the left by the adjoint action.
-\end{thm}
-\begin{proof}
-First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
-Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
-
-The twisted theory is therefore perturbatively equivalent to the theory with BV action 
-\begin{align*}
- S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
-  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
-\end{align*}
-This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
-\end{proof}
 

### 2020-01-14 paper.tex
Continued editing

--- 2020-01-14 paper.tex
@@
 \begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
 \end{remark}
@@
 First, we consider the process of integrating out an auxiliary field.
-
-\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
 
@@
 
+\begin{remark}
+In terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
+\[\xymatrix{
+\cdots \ar[r] &\mc E_0^0 \ar[r]^{Q_0} \ar[dr] &\mc E_0^1 \ar[r] &\cdots \\
+&\cO_M \ar^{i}[r] \ar[ur] &\dens_M &
+}\]
+where $i$ is the canonical inclusion, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify the differential $Q_0$ and the Lie structure.
+\end{remark}
+
 We may also remove a trivial BRST doublet.
@@
 \begin{prop}
-Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
 where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
+Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
 \label{prop:BRSTdoublet}
@@
 
+\begin{remark}
+Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
+\[\xymatrix{
+\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
+&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
+&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
+}\]
+with the differentials $E_1 \to E_1$ and $E_1^!
+\to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
+\chris{Pavel, is this, and the other remark above, what you wanted me to add?}
+\end{remark}
+
 \subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
@@
 Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-Consider the graded vector space
+We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
+We begin by defining an appropriate version of the Chevalley-Eilenberg cochain complex.
+
+\begin{definition}
+The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
@@
 parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
-where $x_j \in \fg$. 
-We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
-\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
-and the degree $+1$ BV bracket by the formula
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
+where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
+\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
+The complex is additionally equipped with a degree $+1$ BV bracket via the formula
 \[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
+\end{definition}
+
 The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
@@
 \]
-where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
+where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
 The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
 Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
+This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.
+This is defined as follows.
 
@@
 An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$;
-\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
+where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $I_\fg^{(0)} = I$.
+\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
 \item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
@@
 For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
+An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
 \[
@@
 We may also define actions of supergroups on classical field theories.
+The action of a supergroup $G$ is more data than the action of a super Lie algebra $\gg$: it includes the infinitesimal action of the Lie algebra $\gg$, along with an action of $G$ on the fields exponentiating this infinitesimal action.
+That is, we make the following definition (see also \cite[]{Book1} \chris{section}).
 
@@
 \label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
+Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory, and let $G$ be a supergroup acting on spacetime $M$.
 An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
@@
 \begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, the differential $Q$ and the interaction term $I$.
+
+\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
 \end{itemize}
@@
 \begin{remark}
-While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
+While we allow for $L_\infty$ actions of Lie algebras, we will only consider strict actions of Lie groups in the present work.
 \end{remark}
@@
 \subsection{From BRST to BV}
+We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.
+These data can be packaged into what's known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
 
@@
 
+\begin{remark}
+In the most typical examples, the bundle $F$ is concentrated in $\ZZ$-degrees $-1$ and 0.
+In this case, sections in degree 0 are thought of as physical fields, and ghosts -- sections in degree $-1$ -- are thought of as generators of the infinitesimal gauge symmetry.
+The action of gauge transformations on fields is then encoded by the Lie structure.
+\end{remark}
+
 From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
@@
 
+\begin{remark}
+In general, multiple BRST theories can give rise to the same BV theory.
+A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
+Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
+\end{remark}
+
 If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
@@
 \brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
+We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.} \chris{I don't think we need to say this so precisely.
+I think it's enough to say that a homogeneous splitting $F = \bigoplus_i \Phi_i$ induces a splitting $F^!
+= \bigoplus_i \Phi_i^!$, and if we denote a general element of the summand $\Phi_i$ by $\phi$ then we will denote a general element of the summand $\Phi_i^!$ by $\phi^*$.}
+
 \subsection{Examples of Classical Field Theories}
 
-In this section we give some examples of classical field theories we will use.
+In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories.
 All theories we consider in this section are $\ZZ$-graded, i.e.
-all fields are considered even with respect to the $\ZZ/2$-grading.
+the space $E$ of fields will be completely even with respect to the $\ZZ/2$-grading.
 
 \subsubsection{Generalized BF theory} \label{gen_BF_section}
+
+Our first example will generalize the fundamental example of \emph{BF} theory to a not entirely topological context.
+Ordinarily, BF theory describes the classical BRST theory with fields \chris{...
+todo, include references.}
 
@@
 the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\brian{This is not defined}
+\brian{This is not defined} \chris{is compactly supported enough?
+We want to compare pairings.}
 \end{proof}
@@
 
-\subsection{Composition algebras and minimal supersymmetry}
+\subsection{Composition algebras and Minimal Supersymmetry}
 \label{sect:compositionalgebras}
@@
 What is the reason for only seeing certain multiplets via this general setup?
-}
+} \chris{Presumably pure $\mc N = (0,N)$ means a $(0,2)$ vector coupled to $N-2$ Fermi multiplets, so some of these are already covered by the classification?
+Perhaps your concern is that you want a formalism that allows Fermis that are not adjoint valued?
+I don't think the difference between this hyper and twisted hyper is germane here: the proof of supersymmetry is that there is an action of super Poincar\'e, it doesn't involve the action of R-symmetry.}
 
@@
 
-%\begin{landscape}
-
-%\end{landscape}
-
+%%%%%%%%%%%%%%%%%%
 % \subsection{Standard Equivalences Between Classical Field Theories}
@@
 % 
-% \brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
-In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
 % 
@@
 % \end{proof}
-% 
-% The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-% \brian{How do we place 10d YM on an arbitrary 5-fold? 
-% Are you using something about sugra?
-% } \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
-I'm not thinking of using sugra.
-Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
-Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
-% 
-% 
-% \subsection{Dimension 9}
-% The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
-It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.
-% 
-% There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
-Such supercharges are minimal (i.e.
-have 5d image).
-They are stabilized by $\SU(4)$.
-Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.
-% 
-% Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
-The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.
-These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
-% \begin{align*}
-% B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
-% A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
-% \end{align*}
-% along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
-% 
-% \brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
-% 
-% \begin{theorem} \label{9d_twist_thm}
-% The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-% \end{theorem}
-% 
-% \begin{proof}
-% Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
-Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.
-According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.
-% 
-% As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
-% \end{proof}
-% 
-% \begin{remark}
-% One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
-% \end{remark}
+
+%%%%%%%%%%%%%%%%%
 

### 2020-01-14 paper.tex
paper

--- 2020-01-14 paper.tex
@@
 
-\subsection{$\cN=(0,2)$ Super Yang-Mills with matter}
+\subsection{$\cN=(0,2)$ Super Yang-Mills with matter} \label{sec:2d(0,2)}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
+\begin{thm}[See also \cite{SWchar}] \label{2d(0,2)}
 The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
@@
 
-\brian{Confused.}
-
-The untwisted fields are given by:
+We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
+The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
+The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
+Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
+
+The field content is:
 \begin{itemize}
@@
 \item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W_- \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W_- \otimes U)$;
-\item $U$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes U)$ .
-\end{itemize}
-Here, $W_-$ is a complex four-dimensional vector space equipped with a symmetric pairing. 
-Choose the basis $\{u_1,u_2,v_1,v_2\}$ for $W_-$ with pairing given by $\<u_i, v_j\> = \delta_{ij}$.
+\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+\end{itemize}
+
+We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+
+\begin{thm}\label{2d(0,4)}
+The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+\end{thm}
+
+\begin{proof}
+The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
+On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+\[
+S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
+\]
+given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
+Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
+The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
+The claim now follows from Theorem \ref{2d(0,2)}. 
+\end{proof}
+
+\begin{rmk}
+The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+\end{rmk}
 
@@
 \subsection{$\cN=(0,\cN_-)$ Super Yang-Mills}
+
+We consider pure $\cN=(0,\cN_-)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_- \geq 2$.
+The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_-$ is the $\cN_-$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.
 
@@
 \end{itemize}
-Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
-
+Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$ such that the pairing restricted to $ {\rm span}_{\CC} \{u, v\}$ is $\<u,v\> = 1$.
+
+The field content is:
 \[
@@
 
-\[
-\begin{array} {lllcccccc}
-& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
-A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
-\end{array}
-\]
-
-\begin{align*}
-S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
-I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
-\end{align*}
+We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+
+%\[
+%\begin{array} {lllcccccc}
+%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+%c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
+%A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+%\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
+%\end{array}
+%\]
+
+%\begin{align*}
+%S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
+%S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
+%&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
+%I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
+%I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
+%\end{align*}
 
@@
 \begin{proof}
-First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
-Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
-
-The twisted theory is therefore perturbatively equivalent to the theory with BV action 
-\begin{align*}
- S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
-  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
-\end{align*}
-This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
+The proof is similar to the proof of Theorem \ref{2d(0,4)}.
+The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
+On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+\[
+S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
+\]
+given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
+Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
+Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
+The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+The claim now follows from a special case of Theorem \ref{2d(0,2)} where we take $R = 0$. 
+%First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
+%We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
+%Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
+%which can be integrated out using Proposition \ref{prop:BRSTdoublet}.  
+%
+%The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+%\begin{align*}
+% S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
+%  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
+%\end{align*}
+%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
 \end{proof}

### 2020-01-14 paper.tex
Continued editing

--- 2020-01-14 paper.tex
@@
 The maximal supersymmetric gauge theory has $\mc N=2$.
-However, there are $\mc N=1$ super Yang-Mills theory for every choice $U$ of symplectic representation of the gauge group.
+However, there are $\mc N=1$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group.
 
@@
 \begin{itemize}
- \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
+ \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^0(\RR^5; \gg)$.
  \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
@@
 
-\subsection{$\cN=1$ with chiral multiplet matter} 
+\subsection{$\cN=1$ with chiral multiplet matter} \label{4d_1_section}
 We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
@@
 \item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
-\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^1(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
-\item scalars: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
-\item fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
+\item $R$-valued bosons: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
+\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^0(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
+\item $R$-valued fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
 \end{itemize}
@@
 \section{Dimension 3}
-
-% \cN=8 Super Yang-Mills
-% \cN=4 Super Yang-Mills with matter in a pseudo-real representation
-% \cN=2 Super Yang-Mills with matter in a complex representation
+The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.
+The maximal supersymmetric gauge theory has $\mc N=8$.
+However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.
+
+\subsection{$\cN = 2$ Super Yang-Mills with Chiral Matter}
+We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
+So, fix a gauge group $G$, and a representation $R$.
+The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
+ \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
+ \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
+ \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one.
+
+\subsection{$\cN = 4$ Super Yang-Mills with Hypermultiplet Matter}
+
+\subsection{$\cN = 8$ Super Yang-Mills Theory}
 

### 2020-01-15 paper.tex
continuing with 3d

@@
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
 \end{thm}
@@
 However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.
+In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
 
@@
 \paragraph{Twisting data:}
-In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one.
+In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
+
+\begin{thm} \label{3d_minimal_twist_thm}
+The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+\end{thm}
+
+\begin{proof}
+This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.
+That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
+\end{proof}
 
 \subsection{$\cN = 4$ Super Yang-Mills with Hypermultiplet Matter}
+We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
+ \item $U$-valued bosons: a pair of $W$-valued scalar fields $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^3; (W \oplus W) \otimes U)$.
+ \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
+ \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
+In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.
+The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.
+Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.
+
+\begin{theorem} \label{3d_4_holo_A_twist_thm}
+The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U/\!/\gg))$.
+The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U/\!/\gg)_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{proof}
+To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
+\end{proof}
+
+\begin{theorem} \label{3d_2_B_twist_thm}
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U/\!/\gg)$.
+This theory is generally only $\ZZ/2\ZZ$-graded.
+\end{theorem}
+
+\begin{proof}
+Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
+\end{proof}
 

### 2020-01-15 paper.tex
first run through 3d

@@
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $2$ (generic)} & {Perturbatively trivial (generic)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from Section \ref{6d_10_section} to representations of the group $\mr O(5)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsection{$\cN=2$ Super Yang-Mills with Matter}
+\subsection{$\cN=2$ Super Yang-Mills with Matter} \label{4d_2_section}
 
@@
 
-\subsection{$\cN=4$ Super Yang-Mills}
+\subsection{$\cN=4$ Super Yang-Mills} \label{4d_4_section}
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \subsection{$\cN = 8$ Super Yang-Mills Theory}
+Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
+This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
+ \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.
+There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).
+The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.
+
+\begin{theorem} 
+The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
+The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{theorem} 
+The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
+\end{theorem}
 

### 2020-01-15 paper.tex
Editing through S1

@@
  \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
- &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
  \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
- &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
- &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
@@
 \subsection{Conventions}
-Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
+Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
-For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
+For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.
 
@@
 \begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
+\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
 \[
@@
 \begin{remark}
-We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
 \end{remark}
@@
 \begin{itemize}
-\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
 \item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
@@
 All theories we consider in this section are $\ZZ$-graded, i.e.
-the space $E$ of fields will be completely even with respect to the $\ZZ/2$-grading.
+the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.
 
@@
 
-\begin{remark}
-We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
+\begin{remark} \label{mapping_stack_remark}
+The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.
+I can add this later.
+I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
+The language of the mapping stack will simply be used as a compact way of referring to the theory above.
 \end{remark}
@@
 
-Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
-In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
+We will see many $BF$ theories as the output when we twists a supersymmetric gauge theories.
+In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as a generalized $\beta\gamma$ system, extending the usual 2d $\beta \gamma$ system.
 
@@
 \begin{rmk}
-This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
+This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure.
 \end{rmk}
 
-We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
+We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.
 
 \begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
+Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
 \[\cL = \fg\oplus V[-1]\]
 with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted by
+The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
 \[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
@@
 \subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
-
 The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
@@
 
-We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
+We may also consider a $\ZZ/2\ZZ$-graded version of the above theory where $\fg$ is merely $\ZZ/2\ZZ$-graded.
 
 \begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
 \[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.
+This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.
+If $d$ is not 3 this theory is only $\ZZ/2\ZZ$-graded.
 \end{example}
@@
 \[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
+As in the previous example, this still makes sense if $X$ is a Calabi-Yau $d$-fold with $d$ odd, as a $\ZZ/2\ZZ$-graded theory.
 \end{example}
@@
 Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
+The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$.
 Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
@@
 
-So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
+So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.
 
@@
 The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
-Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
+Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2\ZZ$-graded Clifford module.
 
@@
 \begin{remark}
-Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2$-graded classical field theory
+Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2\ZZ$-graded classical field theory
 \[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2$-grading on $E$ is the total grading.
+where the $\ZZ/2\ZZ$-grading on $E$ is the total grading.
 \end{remark}
@@
 Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
-Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
+Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
 \[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
 A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
 A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
@@
 % From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2\ZZ$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
 % As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
@@
 The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
-That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
+That is, the theory with the space of fields $\mr{Map}(\CC^3, U\ham \gg)$, where $U\ham \gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
 \label{thm:6dholomorphictwist}
@@
 We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
+That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
 \end{proof}
@@
 \begin{theorem} \label{5d_holo_twist_theorem}
-The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U/\!/G)$.
+The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
 \end{theorem}
@@
 \begin{theorem} \label{4d_2_holo_twist_thm}
-The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
+The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
 \end{theorem}
@@
 \begin{theorem} \label{4d_Donaldson_twist_thm}
-The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U/\!/\gg)_{\mr{Hod}})$.
+The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.
 \end{theorem}
@@
 \begin{theorem} \label{4d_11_twist_thm}
-The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U/\!/\gg)$.
+The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.
 This theory is generally only $\ZZ/2\ZZ$-graded.
@@
 \begin{theorem} \label{3d_4_holo_A_twist_thm}
-The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U/\!/\gg))$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U/\!/\gg)_{\mr{Hod}})$.
+The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
+The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
 \end{theorem}
@@
 \begin{theorem} \label{3d_2_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U/\!/\gg)$.
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
 This theory is generally only $\ZZ/2\ZZ$-graded.
@@
 \[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
-Consider a $\ZZ/2$-graded Clifford module $M=M^+\oplus M^-$.
+Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$.
 Denote the Clifford action by $\rho(v)\in\eend(M)$.

### 2020-01-15 paper.tex
Editing through S2

@@
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
- \label{table_of_twists_16}
+ \label{table_of_twists_8}
 \end{table}
@@
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
- \label{table_of_twists_16}
+ \label{table_of_twists_4}
 \end{table}
@@
 
-\subsubsection{Generalized BF theory} \label{gen_BF_section}
+\subsubsection{Generalized BF Theory} \label{gen_BF_section}
 
@@
 Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
-\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
-where we denote the two fields by $A$ and $B$. The BV action is
+\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*,\]
+\chris{I changed a shift here which I don't think was correct, but someone should double check.} where we denote the two fields by $A$ and $B$. The BV action is
 \[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
@@
 
-\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
+Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
+These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
+In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.
+So at $t=0$ we will recover generalized BF theory.
+
+We will refer to these families as Hodge deformations of generalized BF theory.
+The terminology here comes from Simpson's Hodge stack \chris{ref}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
+
+\begin{definition} \label{Hodge_family_def}
+Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.
+The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so
+\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
+but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
+\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
+\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
+induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
+\end{definition}
+
+Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
+\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]
+
+\subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
 The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
@@
 \section{Supersymmetry} \label{sec: susy}
-
-In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
-
-\subsection{Supersymmetry algebras}
-
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.
+So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
+We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.
+
+\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
+In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.
+
+Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and let $V=V_\RR\otimes_\RR\CC$ be its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
 \begin{itemize}
@@
 
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+$ and $S_-$.
 \end{itemize}
@@
 \begin{definition}
-A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
+A \defterm{spinorial representation} $\Sigma$ is a finite sum of spin or semi-spin representations of $\so(V)$.
 \end{definition}
@@
 
-For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
-In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
+For a given spinorial representation, the pairing $\Gamma$ is typically unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
+In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows.
 \begin{itemize}
@@
 
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
+We will now define the fundamental notion of a supersymmetric field theory.
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$.
+Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
 
@@
 
-\subsection{Composition algebras and Minimal Supersymmetry}
+\subsection{Composition Algebras and Minimal Supersymmetry}
 \label{sect:compositionalgebras}
 
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow that of Baez and Huerta \cite{BaezHuerta}.
 
@@
 
-It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
-$A_\RR$ is a real composition algebra.
+In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
+$A_\RR$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.
 
@@
 
-Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
-\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
+Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.
+The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.
+We define action maps
+\[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
 given, respectively, by
@@
 
-\subsection{Two-dimensional chiral supersymmetry}
+\subsection{Two-dimensional Chiral Supersymmetry}
 
@@
 
-\subsection{Supersymmetric twisting}
+\subsection{Supersymmetric Twisting}
+The idea of twisting, originally developed by Witten \chris{refs}, is \chris{todo: brief contextual remarks, not much detail, as we'll say more in the intro.}
 
@@
 \item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.
+
+\item A supercharge $Q$ is \defterm{minimal} if $n$ is odd and $d=(n+1)/2$.
 \end{itemize}
@@
 The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
-\begin{itemize}
-\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
-Dashed border denotes chiral supersymmetry (i.e.
-$(\cN_+, 0)$ in even dimensions).
-
-\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
-
-\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
-
-\item Arrows denote compactifications from higher to lower dimensions.
-\end{itemize}
+In particular, the orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}.
+
+We will now define the twist of a supersymmetric field theory by a square-zero supercharge.
+In order to obtain a $\ZZ$-graded theory, we will need to also include an additional piece of data as follows.
 
@@
 Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
-Recall, this means we have a Maurer-Cartan element 
+Recall from Section \ref{symmetry_section} that this means we have a Maurer-Cartan element 
 \[
@@
 \]
-where $I_{\fA}^{(k)} : \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+where $I_{\fA}^{(k)} \colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
 For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
@@
 Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
+The {$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{I_{\fA}^2(Q), -\}, \omega, I + I_{\fA}^{\ge 3}(Q))$, where
 \[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
@@
 \begin{prop}
-The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
+The collection $\left(E^Q, Q_{\mr{BV}} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
 \end{prop}
@@
 
-Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
+Ellipticity of $(E^Q, \d + \{I_\fA^2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
 The operator 
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ \chris{we never actually defined supersymmetry algebras or R-symmetry: need to go back and add this to Section \ref{sec:susyalgebras}.}.
 
@@
 
-\subsection{A-Type Twists} \label{A_twist_section}
-\chris{I think we should discuss these Hodge families somewhere, maybe not here though.}
-
-%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
-
-% \begin{landscape}
-% \begin{figure}
-% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-% \node (825) [right=of 82] {};
-% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-% 
-% \draw[arrow] (101) -- (91);
-% \draw[arrow] (91) -- (81);
-% \draw[arrow] (91) -- (82);
-% \draw[arrow] (81) -- (71);
-% \draw[arrow] (82) -- (71);
-% \draw[arrow] (82) -- (72);
-% \draw[arrow] (83) -- (73);
-% \draw[arrow] (71) -- (61);
-% \draw[arrow] (71) -- (62);
-% \draw[arrow] (72) -- (62);
-% \draw[arrow] (72) -- (63);
-% \draw[arrow] (73) -- (65);
-% \draw[arrow] (61) -- (51);
-% \draw[arrow] (62) -- (51);
-% \draw[arrow] (62) -- (52);
-% \draw[arrow] (63) -- (53);
-% \draw[arrow] (64) -- (52);
-% \draw[arrow] (64) -- (54);
-% \draw[arrow] (65) -- (54);
-% \draw[arrow] (51) -- (41);
-% \draw[arrow] (51) -- (42);
-% \draw[arrow] (52) -- (42);
-% \draw[arrow] (52) -- (43);
-% \draw[arrow] (53) -- (43);
-% \draw[arrow] (54) -- (43);
-% \draw[arrow] (54) -- (44);
-% \draw[arrow] (54) -- (45);
-% \draw[arrow] (41) -- (31);
-% \draw[arrow] (42) -- (31);
-% \draw[arrow] (42) -- (32);
-% \draw[arrow] (43) -- (32);
-% \draw[arrow] (44) -- (32);
-% \draw[arrow] (45) -- (32);
-% \draw[arrow] (31) -- (21);
-% \draw[arrow] (31) -- (22);
-% \draw[arrow] (32) -- (22);
-% 
-% \node (2d) [dimension, left=of 21] {2d};
-% \node (3d) [dimension, above=of 2d] {3d};
-% \node (4d) [dimension, above=of 3d] {4d};
-% \node (5d) [dimension, above=of 4d] {5d};
-% \node (6d) [dimension, above=of 5d] {6d};
-% \node (7d) [dimension, above=of 6d] {7d};
-% \node (8d) [dimension, above=of 7d] {8d};
-% \node (9d) [dimension, above=of 8d] {9d};
-% \node (10d) [dimension, above=of 9d] {10d};
-% \end{tikzpicture}
-% \caption{Orbits of square-zero supercharges.}
-% \label{fig:superchargeorbits}
-% \end{figure}
-% \end{landscape}
-
-\section{Supersymmetric Yang--Mills theories}
+\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}
 
@@
 
-\subsection{Pure super Yang--Mills theory}
+\subsection{Pure Super Yang--Mills Theory}
 \label{sect:gaugemultipletSUSY}
@@
 
-\subsection{Matter multiplet}
+\subsection{Coupling to Matter Multiplets}
 \label{sect:mattermultipletSUSY}
@@
 A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
-comes from a 10d square zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
+comes from a 10d square-zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
 \end{remark}
@@
 On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an A-type twist, as we discussed in Section \ref{A_twist_section} \chris{to add}: we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
+This will be our first example of an twist which is perturbatively trivial on its own, but non-trivial as a one-parameter family, as we discussed at the end of Section \ref{gen_BF_section}.
+That is, we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
 
@@
 Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
-The only square zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
+The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
 Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
@@
 Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).
-These supercharges all occur as square zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
+These supercharges all occur as square-zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
 \begin{enumerate}
@@
 
-There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
+There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
 Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
 Such supercharges are minimal (i.e. have two dimensional image).  
-They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
+They are stabilized by ${\rm U}(2)$; indeed a minimal square-zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
 The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
@@
 \paragraph{Twisting data:}
-In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
+In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
+\begin{thm}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
 The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
 \end{thm}
+
 \begin{proof}

### 2020-01-15 paper.tex
More edits for formatting and clarity

@@
 
-\begin{table}[!h]
+\begin{table}[!ht]
  \centering
@@
 
-\begin{table}[htbp]
+\begin{table}[hbp]
  \centering
@@
 where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
-\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
+\[(\d_{\mr{CE}} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
 The complex is additionally equipped with a degree $+1$ BV bracket via the formula
@@
 where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
+The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
 Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
@@
 \item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
 \end{itemize}
@@
 \[
-\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
+\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
 \]
@@
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
+\[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
 \]
@@
 We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
+In the case $S_{\mr{BRST}} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
 
@@
 
-\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
-\end{itemize}
-We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
+\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
+\end{itemize}
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
 Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.
@@
 The BRST action is given by
-\[S_{BRST}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
 
@@
 We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, with $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
-The action of supersymmetry is given by a linear and quadratic functionals
+The action of supersymmetry is given by a linear and a quadratic functional
 \begin{align*}
@@
 The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
-\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
+\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
 Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
@@
 \{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
-\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
-\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
+\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
+\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
 \{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
@@
 \begin{remark}
-The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; our proof essentially follows \cite{BaezHuerta}.
+The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; this was proven by Baez and Huerta in \cite{BaezHuerta}, and our proof essentially follows the proof in loc.
+cit.
 \end{remark}
@@
 One has
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
 \label{lm:gaugemultiplet2}
@@
 Evaluating the equation
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
 on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
@@
 \begin{align*}
-(\d_{CE} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+(\d_{\mr{CE}} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
 &= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
@@
 Evaluating the equation
-\[\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
+\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
 on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
@@
 the supersymmetric gauged linear $\sigma$-models.
-Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models in \cite[Chapter 3]{DeligneFreed}.
+Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models by Deligne and Freed in \cite[Chapter 3]{DeligneFreed}.
 
@@
 \label{CMEYM}
-\d_{CE} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\d_{\mr{CE}} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
 \end{equation}
@@
 \{S_{\BV} , I^{(1)}\} & = & 0 \\ 
-\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
-\d_{CE} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
+\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
+\d_{\mr{CE}} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
 \{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
@@
 \begin{equation}\label{CMEYM3}
-\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
+\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
 \end{equation}
@@
 \[
-(\d_{CE}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+(\d_{\mr{CE}}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
 \]
@@
 
-\subsection{$\cN=(1, 0)$ super Yang--Mills theory}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills theory}
 
@@
 
-\subsection{$\cN=1$ super Yang--Mills theory}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
 
@@
 We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
-\begin{figure}[!h]
+\begin{figure}[!htb]
 \[
@@
 
-\subsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
+\subsection{\texorpdfstring{$\mc N = (1,0)$}{N=(1,0)} Super Yang-Mills Theory with Matter} \label{6d_10_section}
 
@@
 
-\subsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
+\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}
 
@@
 
-\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}  \label{5d_1_section}
+\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang-Mills Theory with Matter}  \label{5d_1_section}
 We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
@@
 
-\subsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}
+\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang-Mills Theory} \label{5d_2_section}
 
@@
 
-\subsection{$\cN=1$ with chiral multiplet matter} \label{4d_1_section}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} with chiral multiplet matter} \label{4d_1_section}
 We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
@@
 
-\subsection{$\cN=2$ Super Yang-Mills with Matter} \label{4d_2_section}
+\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills with Matter} \label{4d_2_section}
 
@@
 
-\subsection{$\cN=4$ Super Yang-Mills} \label{4d_4_section}
+\subsection{\texorpdfstring{$\cN=4$}{N=4} Super Yang-Mills} \label{4d_4_section}
 
@@
 
-\subsection{$\cN = 2$ Super Yang-Mills with Chiral Matter}
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter}
 We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
@@
 
-\subsection{$\cN = 4$ Super Yang-Mills with Hypermultiplet Matter}
+\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter}
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
@@
 
-\subsection{$\cN = 8$ Super Yang-Mills Theory}
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory}
 Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
@@
 
-\subsection{$\cN=(0,2)$ Super Yang-Mills with matter} \label{sec:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}
 
@@
 
-\subsection{$\cN=(0,4)$ Super Yang-Mills with matter}
+\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with matter}
 
@@
 
-\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills}
+\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang-Mills}
 

### 2020-01-15 paper.tex
Minor edit
Section headers

@@
 
-\title{Twists of supersymmetric gauge theories}
+\title{Twists of Supersymmetric Gauge Theories}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 \part{A Catalogue of Twists}
+\chris{We actually used this heading in our previous paper, so maybe a different name?}
 
@@
 
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
+\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(8,8)}
+
 \subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}

### 2020-01-15 paper.tex
Started 2d non-chiral

@@
 
-\subsection{Two-dimensional Chiral Supersymmetry}
+\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}
 
@@
 
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter}
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
 We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
@@
 
-\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter}
+\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
@@
 
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory}
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
 Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
@@
 
-% \cN=(8, 8) Super Yang-Mills
-% \cN=(4, 4) Super Yang-Mills with matter in a pseudo-real representation
-% \cN=(2, 2) Super Yang-Mills with matter in a complex representation
-%BRIAN FIND REFERENCE OF BELOW
-% \cN=(0,2) Super Yang-Mills with matter
+There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
+First we have theories with $\(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+We additionally have gauge theories with chiral, i.e.
+$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.
+We'll address twists for these two classes of theory in turn.
 
 \subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
+First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
+This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
+ \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus \otimes (S_+ \oplus S_-) \otimes R^*)$.
+\end{itemize}
+
+\vspace{-10pt}
+\paragraph{Twisting data:}
+In the $\mc N=(2,2)$ supersymmetry algebra there is are two classes of non-trivial orbits of square-zero supercharges.
+We have both square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic, and square-zero supercharges of rank $(1,1)$, which are topological.
+\chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
+
+\begin{thm} \label{2d_minimal_twist_thm}
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to topological $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$.
+\end{thm}
+
+\begin{proof}
+This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.
+That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex directions into a real de Rham direction.
+\end{proof}
+
 \subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
+We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
+
 \subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(8,8)}

### 2020-01-16 paper.tex
continuing with 2d section

@@
  && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
@@
 There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $\(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+First we have theories with $(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
 We additionally have gauge theories with chiral, i.e.
@@
 \vspace{-10pt}
+\paragraph{Supersymmetry action:} 
+\chris{todo}
+
+\vspace{-10pt}
 \paragraph{Twisting data:}
-In the $\mc N=(2,2)$ supersymmetry algebra there is are two classes of non-trivial orbits of square-zero supercharges.
-We have both square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic, and square-zero supercharges of rank $(1,1)$, which are topological.
+In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
+\begin{itemize}
+ \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic
+ \item Square-zero supecharges of rank $(1,1)$ are topological, and split into two classes: the B-supercharge arises by dimensional reduction from 3 dimensions, and the A-supercharge does not.
+\end{itemize}
 \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
 
-\begin{thm} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to topological $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$.
-\end{thm}
+The calculation of the twists here is similar to what we saw in 4d $\mc N=2$.
+The holomorphic twist and the B-twist arise by dimensional reduction from 3d, but the A-twist as a deformation of the holomorphic twist is not, and must be calculated directly.
+
+\begin{theorem} \label{2d_minimal_twist_thm}
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+\end{theorem}
 
@@
 This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex directions into a real de Rham direction.
-\end{proof}
-
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
-
-\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(8,8)}
+That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_to_BF_diml_red_prop} to dimensionally reduce in the real de Rham direction.
+\end{proof}
+
+\begin{theorem} \label{2d_2_A_twist_thm}
+The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{proof}
+
+\end{proof}
+
+Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
+\begin{theorem} \label{2d_2_B_twist_thm}
+The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2, (R/\gg))$.
+\end{theorem}
+
+\begin{proof}
+We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.
+That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
+\end{proof}
+
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
+We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
+We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.
+
+The following equivalences follow from the results in the previous section by substituting $R = $ \chris{what is it exactly?}.
+
+\begin{theorem}
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.
+Together they are perturbatively equivalent to a holomorphic BF theory and its Hodge deformation, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
+
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{theorem}
+The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
+\end{theorem}
 

### 2020-01-16 paper.tex
More edits to section 1

@@
 
-\chris{Todo: would be more correct to remove the generic rank 2 twist in 3d, same as the 3d A twist (dual RW).
-I should do this in the tables and the diagrams.
-Also todo: change the labels of orbits to A and B.}
-
 \begin{table}[!ht]
@@
    \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
-  \node {8}; &    &   & \node[s16] (88) {$(1,0)_i$};  &   &   &   &&   &&&&   &&&   \\
-  \node {7}; &    &   &   & \node[s16] (77) {$1_i$};  &   &   &&   &&&&   &&&   \\
-  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_g$};  &   &&   &&&&   &&&   \\
-  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_g$};  &   &&&&   &&&   \\
-  \node {4}; &    &   & \node[s16] (84) {$(1,0)_p$};  & \node[s16] (74) {$1_p$};  & \node[s16] (64) {$(1,1)_s$};  & \node[s16] (54) {$2_s$};  && \node[s16] (44B) {$(2,2)_s$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_g$};  &   &&&   \\
-  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &\node[s16] (33g) {$2_g$};  &   \\
+  \node {8}; &    &   & \node[s16] (88) {$(1,0)_A$};  &   &   &   &&   &&&&   &&&   \\
+  \node {7}; &    &   &   & \node[s16] (77) {$1_A$};  &   &   &&   &&&&   &&&   \\
+  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_A$};  &   &&   &&&&   &&&   \\
+  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_A$};  &   &&&&   &&&   \\
+  \node {4}; &    &   & \node[s16] (84) {$(1,0)_B$};  & \node[s16] (74) {$1_B$};  & \node[s16] (64) {$(1,1)_B$};  & \node[s16] (54) {$2_B$};  && \node[s16] (44B) {$(2,2)_B$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_A$};  &   &&&   \\
+  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &  &   \\
   \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
@@
 
-  \draw[dotted] (0.4,-7) -- (0.4,7);
-  \draw[dotted] (6.35,-7) -- (6.35,7);
+  \draw[dotted] (0.5,-7) -- (0.5,7);
+  \draw[dotted] (6.4,-7) -- (6.4,7);
   \draw[dotted] (-2,-7) -- (-2,7);
   \draw[dotted] (-3.8,-7) -- (-3.8,7);
-  \draw[dotted] (-4.75,-7) -- (-4.75,7);
-  \draw[dotted] (-6.25,-7) -- (-6.25,7);
-  \draw[dotted] (-7.1,-7) -- (-7.1,7);
+  \draw[dotted] (-4.8,-7) -- (-4.8,7);
+  \draw[dotted] (-6.3,-7) -- (-6.3,7);
+  \draw[dotted] (-7.3,-7) -- (-7.3,7);
 
@@
   \draw[arrow] (44K) -- (33A);
-  \draw[arrow] (44g) -- (33g);
   \draw[arrow] (43) -- (33B);
@@
   \draw[arrow] (42) -- (32);
+  \draw[arrow] (44g) -- (33A);
 
@@
 Most of the material in this section is not original.
-We refer the reader to \chris{refs} for more details.
+We refer the reader to \cite{CostelloBook, Book2} for more details on this perspective.
 We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
@@
 
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
+The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
+In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
+That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
+The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
 
@@
 The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$.
-\chris{todo: add references}
+a symplectic isomorphism $L\cong L^![-3]$ \cite[Chapter 5.4]{Book2}.
 \end{remark}
@@
 \subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
-
-In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
+In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion).
 Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
@@
 The action of a supergroup $G$ is more data than the action of a super Lie algebra $\gg$: it includes the infinitesimal action of the Lie algebra $\gg$, along with an action of $G$ on the fields exponentiating this infinitesimal action.
-That is, we make the following definition (see also \cite[]{Book1} \chris{section}).
+That is, we make the following definition.
 
@@
 
-Our first example will generalize the fundamental example of \emph{BF} theory to a not entirely topological context.
-Ordinarily, BF theory describes the classical BRST theory with fields \chris{...
-todo, include references.}
+Our first example will generalize the fundamental example of \emph{BF theory} to a not entirely topological context.
+Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
+\[S(A,B) = \int_M \langle F_A \wedge B \rangle.\]
+This theory is, in fact, of cotangent type, where the base of the cotangent includes $A$ and its antifield, and the fiber includes $B$ and its antifield.
+This basic setup can be generalized to a setting where $M$ need not be entirely topological, and where $\gg$ may be a more general $L_\infty$ algebra, in the following way.
 
@@
 We will refer to these families as Hodge deformations of generalized BF theory.
-The terminology here comes from Simpson's Hodge stack \chris{ref}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
+The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
 

### 2020-01-16 paper.tex
correction to 4d N=2
merge

--- 2020-01-15 paper.tex
@@
 
-\title{Twists of Supersymmetric Gauge Theories}
+\title{Twists of supersymmetric gauge theories}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 
-\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}
+\subsection{Two-dimensional Chiral Supersymmetry}
 
@@
 
-\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
-Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
+\item $A_\RR=\mathbb{H}$, so $A=\eend(Z)$.
+A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $Z$.
+Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$.
 So, the data boils down a symplectic $\fg$-representation $U$.
@@
 \part{A Catalogue of Twists}
-\chris{We actually used this heading in our previous paper, so maybe a different name?}
 
@@
 
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter}
 We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
@@
 
-\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
+\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter}
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
@@
 
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory}
 Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
@@
 
-There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $\(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
-We additionally have gauge theories with chiral, i.e.
-$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.
-We'll address twists for these two classes of theory in turn.
-
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
-First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
-This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
- \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus \otimes (S_+ \oplus S_-) \otimes R^*)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=(2,2)$ supersymmetry algebra there is are two classes of non-trivial orbits of square-zero supercharges.
-We have both square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic, and square-zero supercharges of rank $(1,1)$, which are topological.
-\chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
-
-\begin{thm} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to topological $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$.
-\end{thm}
-
-\begin{proof}
-This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex directions into a real de Rham direction.
-\end{proof}
-
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
-
-\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(8,8)}
+% \cN=(8, 8) Super Yang-Mills
+% \cN=(4, 4) Super Yang-Mills with matter in a pseudo-real representation
+% \cN=(2, 2) Super Yang-Mills with matter in a complex representation
+%BRIAN FIND REFERENCE OF BELOW
+% \cN=(0,2) Super Yang-Mills with matter
 

### 2020-01-16 paper.tex

--- 2020-01-16 paper.tex
@@
  \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
- \item $U$-valued bosons: a $W \oplus W^*$-valued scalar field $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^4; (W \oplus W^*) \otimes U)$.
+ \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
  \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
@@
 &\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi')Q_+, \psi_+^*)(v',w_+)) \\
+I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
 I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
@@
  \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item $U$-valued bosons: a pair of $W$-valued scalar fields $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^3; (W \oplus W) \otimes U)$.
+ \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
  \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.

### 2020-01-16 paper.tex
added an abstract, more small additions

@@
 
-\title{Twists of Supersymmetric Gauge Theories}
+\title{A Catalogue of Twists of Supersymmetric Gauge Theories}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 \begin{abstract}
-
+We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.
+Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory.
 \end{abstract}
@@
 
-Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.
+Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.  We will sometimes want to refer to the infinitesimal version of this action.
+\begin{definition}
+Let $\fA$ be a supertranslation algebra.  The corresponding \emph{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
+\end{definition}
 
@@
 \subsection{Supersymmetric Twisting}
-The idea of twisting, originally developed by Witten \chris{refs}, is \chris{todo: brief contextual remarks, not much detail, as we'll say more in the intro.}
+The idea of twisting, originally developed by Witten \cite{WittenTQFT}, is to modify a classical BV theory by deforming the differential $Q_{\mr{BV}}$ by the action of a square-zero fermionic symmetry.
 
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ \chris{we never actually defined supersymmetry algebras or R-symmetry: need to go back and add this to Section \ref{sec:susyalgebras}.}.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sec:susyalgebras}.
 
@@
 
-\begin{comment}
-\pavel{This might go in the coupling section.}
-We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
-\begin{corollary}
-Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.
-Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.
-Then the super Poincar\'e algebra
-\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
-obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
-\end{corollary}
-
-\begin{proof}
-This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
-\end{proof}
-
-\begin{remark}
-We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
-\end{remark}
-\end{comment}
-
 \subsection{Coupling to Matter Multiplets}
@@
 
-\item $A_\RR=\mathbb{H}$, so $A=\eend(Z)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $Z$.
-Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$.
+\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$.
+A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
+Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
 So, the data boils down a symplectic $\fg$-representation $U$.
@@
 \section{Dimension 8}
+
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+
 \vspace{-10pt}
@@
 \section{Dimension 7} \label{7d_section}
+
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
 The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
@@
 
-The following equivalences follow from the results in the previous section by substituting $R = $ \chris{what is it exactly?}.
+The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.
 

### 2020-01-17 paper.tex
8d twists

--- 2020-01-16 paper.tex
@@
 \newcommand{\gauge}{\mathrm{gauge}}
+\newcommand{\Hod}{\mathrm{Hod}}
 \newcommand{\matter}{\mathrm{matter}}
@@
 \renewcommand{\Re}{\mathrm{Re}}
-\renewcommand{\U}{\mathrm{U}}
+%\newcommand{\U}{\mathrm{U}}
+\def\U{\mathrm{U}}
 
@@
  && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, T^*[2](\gg/\gg))$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \cline{3-5}
+  && \multirow{2}*{Rank $2$ (generic)} & {Perturbatively trivial (generic)} & \multirow{2}*{3 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
@@
 
-\begin{table}[!ht]
+\chris{Todo: would be more correct to remove the generic rank 2 twist in 3d, same as the 3d A twist (dual RW).
+I should do this in the tables and the diagrams.
+Also todo: change the labels of orbits to A and B.}
+
+\begin{table}[!h]
  \centering
@@
  \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
- &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^3, U /\!/G)$ & \\ \hline
  \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
- &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U /\!/G)$ & \\ \hline
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^2, U /\!/G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
- &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
+ &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC^2, U /\!/G)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)$  & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U /\!/G)$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U /\!/G)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
- \label{table_of_twists_8}
+ \label{table_of_twists_16}
 \end{table}
 
-\begin{table}[hbp]
+\begin{table}[htbp]
  \centering
@@
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
- \label{table_of_twists_4}
+ \label{table_of_twists_16}
 \end{table}
 
-\clearpage
 \begin{figure}[hbp]
@@
    \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
-  \node {8}; &    &   & \node[s16] (88) {$(1,0)_A$};  &   &   &   &&   &&&&   &&&   \\
-  \node {7}; &    &   &   & \node[s16] (77) {$1_A$};  &   &   &&   &&&&   &&&   \\
-  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_A$};  &   &&   &&&&   &&&   \\
-  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_A$};  &   &&&&   &&&   \\
-  \node {4}; &    &   & \node[s16] (84) {$(1,0)_B$};  & \node[s16] (74) {$1_B$};  & \node[s16] (64) {$(1,1)_B$};  & \node[s16] (54) {$2_B$};  && \node[s16] (44B) {$(2,2)_B$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_A$};  &   &&&   \\
-  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &  &   \\
+  \node {8}; &    &   & \node[s16] (88) {$(1,0)_i$};  &   &   &   &&   &&&&   &&&   \\
+  \node {7}; &    &   &   & \node[s16] (77) {$1_i$};  &   &   &&   &&&&   &&&   \\
+  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_g$};  &   &&   &&&&   &&&   \\
+  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_g$};  &   &&&&   &&&   \\
+  \node {4}; &    &   & \node[s16] (84) {$(1,0)_p$};  & \node[s16] (74) {$1_p$};  & \node[s16] (64) {$(1,1)_s$};  & \node[s16] (54) {$2_s$};  && \node[s16] (44B) {$(2,2)_s$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_g$};  &   &&&   \\
+  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &\node[s16] (33g) {$2_g$};  &   \\
   \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
@@
 
-  \draw[dotted] (0.5,-7) -- (0.5,7);
-  \draw[dotted] (6.4,-7) -- (6.4,7);
+  \draw[dotted] (0.4,-7) -- (0.4,7);
+  \draw[dotted] (6.35,-7) -- (6.35,7);
   \draw[dotted] (-2,-7) -- (-2,7);
   \draw[dotted] (-3.8,-7) -- (-3.8,7);
-  \draw[dotted] (-4.8,-7) -- (-4.8,7);
-  \draw[dotted] (-6.3,-7) -- (-6.3,7);
-  \draw[dotted] (-7.3,-7) -- (-7.3,7);
+  \draw[dotted] (-4.75,-7) -- (-4.75,7);
+  \draw[dotted] (-6.25,-7) -- (-6.25,7);
+  \draw[dotted] (-7.1,-7) -- (-7.1,7);
 
@@
   \draw[arrow] (44K) -- (33A);
+  \draw[arrow] (44g) -- (33g);
   \draw[arrow] (43) -- (33B);
@@
   \draw[arrow] (42) -- (32);
-  \draw[arrow] (44g) -- (33A);
 
@@
 Most of the material in this section is not original.
-We refer the reader to \cite{CostelloBook, Book2} for more details on this perspective.
+We refer the reader to \chris{refs} for more details.
 We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
@@
 \subsection{Conventions}
-Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
+Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2$-grading.
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
-For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.
+For an element $x$ we denote by $|x|\in\ZZ/2$ the total degree.
 
@@
 
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
-In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
-That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
-The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
+\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}
+
+The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief \chris{...}
 
@@
 \begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
+\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
 \[
@@
 \begin{remark}
-We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
+We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
 \end{remark}
@@
 The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$ \cite[Chapter 5.4]{Book2}.
+a symplectic isomorphism $L\cong L^![-3]$.
+\chris{todo: add references}
 \end{remark}
@@
 First, we consider the process of integrating out an auxiliary field.
+
+\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}
 
@@
 
-\begin{remark}
-In terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
-\[\xymatrix{
-\cdots \ar[r] &\mc E_0^0 \ar[r]^{Q_0} \ar[dr] &\mc E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^{i}[r] \ar[ur] &\dens_M &
-}\]
-where $i$ is the canonical inclusion, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify the differential $Q_0$ and the Lie structure.
-\end{remark}
-
 We may also remove a trivial BRST doublet.
@@
 \begin{prop}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+\[Q\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
 where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
-Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
 \label{prop:BRSTdoublet}
@@
 
-\begin{remark}
-Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
-\[\xymatrix{
-\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
-&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
-}\]
-with the differentials $E_1 \to E_1$ and $E_1^!
-\to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
-\chris{Pavel, is this, and the other remark above, what you wanted me to add?}
-\end{remark}
-
 \subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
-In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion).
+
+In this section we define what it means for a (super) Lie algebra to act on a classical field theory.
 Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
-We begin by defining an appropriate version of the Chevalley-Eilenberg cochain complex.
-
-\begin{definition}
-The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
+Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
@@
 parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
-\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
-where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
-\[(\d_{\mr{CE}} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
-The complex is additionally equipped with a degree $+1$ BV bracket via the formula
+\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
+where $x_j \in \fg$. 
+We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
+\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
+and the degree $+1$ BV bracket by the formula
 \[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
@@
 \[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
-\end{definition}
-
 The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
@@
 \]
-where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
+where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
+The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$.
 Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
-This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.
-This is defined as follows.
 
@@
 An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$.
-\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
+where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $I_\fg^{(0)} = I$;
+\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
 \item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
 \end{itemize}
@@
 For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
+An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
 \[
@@
 \[
-\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
+\d_{CE} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
 \]
@@
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 We may also define actions of supergroups on classical field theories.
-The action of a supergroup $G$ is more data than the action of a super Lie algebra $\gg$: it includes the infinitesimal action of the Lie algebra $\gg$, along with an action of $G$ on the fields exponentiating this infinitesimal action.
-That is, we make the following definition.
 
@@
 \label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory, and let $G$ be a supergroup acting on spacetime $M$.
+Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$.
 An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
@@
 \begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, the differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.
+
+\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action on $\cE$.
 \end{itemize}
@@
 \begin{remark}
-While we allow for $L_\infty$ actions of Lie algebras, we will only consider strict actions of Lie groups in the present work.
+While we allow for $L_\infty$ actions of Lie algebras, we only consider strict actions of Lie groups.
 \end{remark}
@@
 \subsection{From BRST to BV}
-We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.
-These data can be packaged into what's known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
 
@@
 \begin{itemize}
-\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item a $\ZZ\times\ZZ/2$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
 \item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
@@
 
-\begin{remark}
-In the most typical examples, the bundle $F$ is concentrated in $\ZZ$-degrees $-1$ and 0.
-In this case, sections in degree 0 are thought of as physical fields, and ghosts -- sections in degree $-1$ -- are thought of as generators of the infinitesimal gauge symmetry.
-The action of gauge transformations on fields is then encoded by the Lie structure.
-\end{remark}
-
 From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
@@
 The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
+\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
 \]
@@
 We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{\mr{BRST}} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
-
-\begin{remark}
-In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
-Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
-\end{remark}
+In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
 
@@
 \brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.} \chris{I don't think we need to say this so precisely.
-I think it's enough to say that a homogeneous splitting $F = \bigoplus_i \Phi_i$ induces a splitting $F^!
-= \bigoplus_i \Phi_i^!$, and if we denote a general element of the summand $\Phi_i$ by $\phi$ then we will denote a general element of the summand $\Phi_i^!$ by $\phi^*$.}
-
+We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.}
 \subsection{Examples of Classical Field Theories}
 
-In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories.
+In this section we give some examples of classical field theories we will use.
 All theories we consider in this section are $\ZZ$-graded, i.e.
-the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.
-
-\subsubsection{Generalized BF Theory} \label{gen_BF_section}
-
-Our first example will generalize the fundamental example of \emph{BF theory} to a not entirely topological context.
-Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
-\[S(A,B) = \int_M \langle F_A \wedge B \rangle.\]
-This theory is, in fact, of cotangent type, where the base of the cotangent includes $A$ and its antifield, and the fiber includes $B$ and its antifield.
-This basic setup can be generalized to a setting where $M$ need not be entirely topological, and where $\gg$ may be a more general $L_\infty$ algebra, in the following way.
+all fields are considered even with respect to the $\ZZ/2$-grading.
+
+\subsubsection{Generalized BF theory} \label{gen_BF_section}
 
@@
 
-\begin{remark} \label{mapping_stack_remark}
-The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.
-I can add this later.
-I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
-The language of the mapping stack will simply be used as a compact way of referring to the theory above.
+\begin{remark}
+We do not provide any interpretation for the above mapping space and simply view it as a compact way of referring to the theory above.
 \end{remark}
@@
 Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
-\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*,\]
-\chris{I changed a shift here which I don't think was correct, but someone should double check.} where we denote the two fields by $A$ and $B$. The BV action is
+\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*[d-2],\]
+where we denote the two fields by $A$ and $B$. The BV action is
 \[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
@@
 
-We will see many $BF$ theories as the output when we twists a supersymmetric gauge theories.
-In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as a generalized $\beta\gamma$ system, extending the usual 2d $\beta \gamma$ system.
+Generally speaking, $BF$ theories will be the output of twisting a supersymmetric gauge theory. 
+In fact, a special case also applies to twisting theories of matter, which we will refer to as a $\beta\gamma$ system.
 
@@
 \begin{rmk}
-This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure.
+This is a special case of generalized BF theory: the generalized $\beta\gamma$ system is generalized $BF$ theory in the case that the $L_\infty$ aglebra is $\fg = V[-1]$, with trivial $L_\infty$ structure.
 \end{rmk}
 
-We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.
+We may also couple a $\beta\gamma$ system to a generalized $BF$ theory as follows.
 
 \begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
+Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ a dg representation of $\fg$. Consider the dg Lie algebra
 \[\cL = \fg\oplus V[-1]\]
 with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
+The space of fields in the corresponding generalized BF theory will be denoted by
 \[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
@@
 
-Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
-These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
-In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.
-So at $t=0$ we will recover generalized BF theory.
-
-We will refer to these families as Hodge deformations of generalized BF theory.
-The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
-
-\begin{definition} \label{Hodge_family_def}
-Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.
-The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so
-\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
-but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
-\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
-\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
-induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
-\end{definition}
-
-Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
-\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]
-
-\subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
+\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}
+
 The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
@@
 
-We may also consider a $\ZZ/2\ZZ$-graded version of the above theory where $\fg$ is merely $\ZZ/2\ZZ$-graded.
+We may also consider a $\ZZ/2$-graded version of the above theory where $\fg$ is merely $\ZZ/2$-graded.
 
 \begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
 \[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.
-This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.
-If $d$ is not 3 this theory is only $\ZZ/2\ZZ$-graded.
 \end{example}
@@
 \[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-As in the previous example, this still makes sense if $X$ is a Calabi-Yau $d$-fold with $d$ odd, as a $\ZZ/2\ZZ$-graded theory.
 \end{example}
@@
 Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
+\label{ex:CSBF}
 \end{example}
@@
 We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
-Consider the determinant map $\det\colon \U(n)\rightarrow \U(1)$.
 We define the unitary metalinear group to be
 \[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
-where $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
+where $\U(n)\rightarrow \U(1)$ is the determinant map and $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$.
+The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
 
@@
 \end{prop}
+
+\subsubsection{Generalized Hodge theory}
+
+We will also consider deformations of the generalized BF theory to a perturbatively trivial theory.
+By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.
+
+Given an $L_\infty$ algebra $\fg$ we denote by $\fg_{\Hod}$ the $\CC[t]$-linear $L_\infty$ algebra
+\[\fg_{\Hod} = \CC[t]\otimes (\fg\oplus \fg[1])\]
+with the $L_\infty$ brackets coming from the $L_\infty$ brackets on $\fg$ in the first term, where we consider $\fg[1]$ as the adjoint representation of $\fg$.
+The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.
+
+If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.
+
+\begin{definition}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Fix an $L_\infty$ algebra $\fg$.
+We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
+\end{definition}
+
+\begin{prop}
+The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+
+The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
+\label{prop:Hodgetheoryspecialization}
+\end{prop}
+\begin{proof}
+At $t=0$ we get
+\[\left.\fg_\Hod\right|_{t=0}\cong \fg\oplus \fg[1]\cong \fg\oplus \fg^*[d-1],\]
+where we use the symmetric bilinear pairing on $\fg$ in the second isomorphism. The first claim then follows from Example \ref{ex:CSBF}.
+
+At $t\neq 0$ the $L_\infty$ algebra $\fg_\Hod$ becomes acyclic which proves the second claim.
+\end{proof}
 
@@
 Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$.
+The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q$.
 Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
@@
 
+Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation.
+Recall that the symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e.
+a real volume form.
+We denote by $V=V_\RR\otimes_{\RR}\CC$ its complexification.
+$V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$.
+Moreover, $V$ carries a complex volume form $\Omega_V$:
+\[\det(V)\cong \det(V_\RR)\otimes_{\RR}\CC\]
+and we use the real volume form on $V_\RR$.
+
+Functoriality of this construction gives a group homomorphism
+\begin{equation}
+\SO(V_\RR)\longrightarrow \SU(V)
+\label{eq:SOtoSU}
+\end{equation}
+such that the real projection $\Re\colon V\rightarrow V_\RR$ is $\SO(V_\RR)$-equivariant.
+
 \begin{prop} \label{CS_diml_red_prop}
-Let $X,Y,M,\fg$ be as before. Equip $\CC$ with a holomorphic volume form $\d z$ and consider the generalized Chern--Simons theory
-\[\map((X\times \CC)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon (X\times \CC)\times Y\times M\rightarrow X\times Y\times (M\times \RR)$ induced by the projection $\CC\rightarrow \RR$ given by $(x, y)\mapsto x$ is isomorphic to the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above. Consider the generalized Chern--Simons theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
 \end{prop}
-
 \begin{proof}
@@
 We have
-\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
+\[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
 and
-\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
+\[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]
+
 Under the pullback map
-\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
-the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
-\brian{This is not defined} \chris{is compactly supported enough?
-We want to compare pairings.}
+\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
+the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$.
+\brian{This is not defined}
 \end{proof}
@@
 \section{Supersymmetry} \label{sec: susy}
-Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.
-So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
-We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.
-
-\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
-In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.
-
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and let $V=V_\RR\otimes_\RR\CC$ be its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+
+In this section we recall the framework for supersymmetry following \cite{ElliottSafronov} and \cite{DeligneSpinors}, we refer there for more details.
+
+\subsection{Supersymmetry algebras}
+
+Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form.
+Denote by $V=V_\RR\otimes_\RR\CC$ its complexification.
+Consider the Lie algebra $\so(V)$.
+Let us recall the following facts:
 \begin{itemize}
@@
 
-\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+$ and $S_-$.
+\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+, S_-$.
 \end{itemize}
@@
 \begin{definition}
-A \defterm{spinorial representation} $\Sigma$ is a finite sum of spin or semi-spin representations of $\so(V)$.
+A \defterm{spinorial representation} $\Sigma$ is a sum of spin or semi-spin representations of $\so(V)$.
 \end{definition}
@@
 
-For a given spinorial representation, the pairing $\Gamma$ is typically unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
-In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows.
+For a given spinorial representation, the pairing $\Gamma$ is unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation.
+In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows:
 \begin{itemize}
@@
 
-\item A complex Lie group $G_R$, the \defterm{group of $R$-symmetries}, which is a subgroup of $\so(V)$-equivariant automorphisms of $(\Sigma, \Gamma)$.
+\item A Lie group $G_R$, the \defterm{group of $R$-symmetries}, which acts on $\Sigma$ by $\so(V)$-equivariant automorphisms preserving $\Gamma$.
 \end{itemize}
@@
 
-We will now define the fundamental notion of a supersymmetric field theory.
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$.
-Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
 
@@
 
-\subsection{Composition Algebras and Minimal Supersymmetry}
+\subsection{Composition algebras and minimal supersymmetry}
 \label{sect:compositionalgebras}
 
-We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow that of Baez and Huerta \cite{BaezHuerta}.
-
-Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow \cite{BaezHuerta}.
+
+Let $A$ be a unital (possibly non-associative) complex algebra equipped with an antiinvolution $\sigma\colon A\rightarrow A$. We make the following assumptions:
 \begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A\rightarrow \CC$. We assume that it is nondegenerate.
 \end{enumerate}
 
-In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
-$A_\RR$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.
-
-For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
-$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+It is known \cite[Chapter 1.3]{SpringerVeldkamp} that the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
+$A$ is a complex composition algebra.
+
+For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
+We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$.
+$V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
 Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-
-We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
-So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
 
@@
 
-Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.
-The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.
-We define action maps
-\[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
+Consider two spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
+\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
 given, respectively, by
@@
 
-So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.
+So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2$-graded Clifford module.
 
@@
 \begin{enumerate}
-\item (\textbf{3d $\mc N=1$ supersymmetry}) $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$.
-
-\item (\textbf{4d $\mc N=1$ supersymmetry}) We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+\item (\textbf{3d $\mc N=1$ supersymmetry}) $A = \CC$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3, \CC)$.
+
+\item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
 Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
-We have two choices: $A_\RR=\CC$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR=\RR[x]/(x^2-1)$ is the algebra of split-complex numbers (which equips $V_\RR$ with a metric of split signature (2, 2)).
-
-\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
 Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
-We have two choices: $A_\RR = \mathbb{H}$ (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-quaternions (which equips $V_\RR$ with a metric of split signature $(3, 3)$).
-
-\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
-We have two choices: $A_|RR$ is the algebra of octonions (which equips $V_\RR$ with a metric of Minkowski signature) and $A_\RR$ is the algebra of split-octonions (which equips $V_\RR$ with a metric of split signature $(5, 5)$).
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{O}\otimes_{\RR}\CC$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
 \end{enumerate}
@@
 
-\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}
+\subsection{Two-dimensional chiral supersymmetry}
 
@@
 The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component.
-Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2\ZZ$-graded Clifford module.
+Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2$-graded Clifford module.
 
@@
 
-\subsection{Supersymmetric Twisting}
-The idea of twisting, originally developed by Witten \chris{refs}, is \chris{todo: brief contextual remarks, not much detail, as we'll say more in the intro.}
+\subsection{Supersymmetric twisting}
 
@@
 A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$.
+Its \defterm{number of invariant directions} is the dimension of the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$.
 \end{definition}
 
-It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ has dimension at least $n/2$.
-We will use the following adjectives for square-zero supercharges depending on $d=\dim(\mathrm{im}\Gamma(Q, -))$:
+It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the number $d$ of invariant directions is at least $n/2$.
+We will use the following adjectives for square-zero supercharges depending on $d$:
 \begin{itemize}
@@
 
-\item A supercharge $Q$ is \defterm{minimal} if $n$ is odd and $d=(n+1)/2$.
+\item A supercharge $Q$ is \defterm{minimal} if $n$ is odd and $d = (n+1)/2$.
 \end{itemize}
@@
 The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}.
-In particular, the orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}.
-
-We will now define the twist of a supersymmetric field theory by a square-zero supercharge.
-In order to obtain a $\ZZ$-graded theory, we will need to also include an additional piece of data as follows.
-
-\begin{definition}
-A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
-\end{definition}
-
-Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
-Recall from Section \ref{symmetry_section} that this means we have a Maurer-Cartan element 
+In particular, orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V_\RR)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}:
+\begin{itemize}
+\item The color denotes the amount of supersymmetries: red denotes 16 supercharges, orange 8 supercharges, yellow 4 supercharges and green 2 supercharges.
+Dashed border denotes chiral supersymmetry (i.e.
+$(\cN_+, 0)$ in even dimensions).
+
+\item $d$ denotes the dimension of the image of $\Gamma(Q, -)$.
+
+\item Rank denotes the rank of the tensor $Q\in S\otimes W$ in odd dimensions or $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ in even dimensions.
+
+\item Arrows denote compactifications from higher to lower dimensions.
+\end{itemize}
+
+Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
 \[
@@
 \]
-where $I_{\fA}^{(k)} \colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
+where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
+
+\begin{comment}
 For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
@@
 Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$. 
+\end{comment}
 
 \begin{definition} \label{def:twisting}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The {$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{I_{\fA}^2(Q), -\}, \omega, I + I_{\fA}^{\ge 3}(Q))$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge.
+The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
+\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
 \end{definition}
 
+Given additional data, we may enhance the classical field theory.
+
+\begin{definition}
+Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1.
+\end{definition}
+
+Given a homomorphism $\alpha$, we consider the new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
+The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$.
+But it also has cohomological degree $-k$.
+In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
+
+\begin{definition}
+Let $Q\in\Sigma$ be a square-zero supercharge and suppose $G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism.
+A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the composite $G\rightarrow \Spin(V_\RR)\times G_R$.
+\end{definition}
+
+The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action.
+However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
+However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
+
+\begin{comment}
 \begin{prop}
-The collection $\left(E^Q, Q_{\mr{BV}} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
+The collection $\left(E^Q, Q_{BV} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
 \end{prop}
@@
 
-Ellipticity of $(E^Q, \d + \{I_\fA^2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
+Ellipticity of $(E^Q, \d + \{\rho_2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
 The operator 
 \end{proof}
-
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2\ZZ$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2\ZZ$-grading on $E$ is the total grading.
-\end{remark}
+\end{comment}
 
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ \chris{we never actually defined supersymmetry algebras or R-symmetry: need to go back and add this to Section \ref{sec:susyalgebras}.}.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$.
 
@@
 
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
-
-\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}
+%  This figure was included twice: once in landscape and once in portait.  I'm commenting out the landscape version here - CE
+
+% \begin{landscape}
+% \begin{figure}
+% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
+% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
+% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
+% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
+% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
+% \node (825) [right=of 82] {};
+% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
+% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
+% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
+% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
+% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
+% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
+% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
+% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
+% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
+% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
+% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
+% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
+% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
+% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
+% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
+% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
+% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
+% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
+% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
+% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
+% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
+% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
+% 
+% \draw[arrow] (101) -- (91);
+% \draw[arrow] (91) -- (81);
+% \draw[arrow] (91) -- (82);
+% \draw[arrow] (81) -- (71);
+% \draw[arrow] (82) -- (71);
+% \draw[arrow] (82) -- (72);
+% \draw[arrow] (83) -- (73);
+% \draw[arrow] (71) -- (61);
+% \draw[arrow] (71) -- (62);
+% \draw[arrow] (72) -- (62);
+% \draw[arrow] (72) -- (63);
+% \draw[arrow] (73) -- (65);
+% \draw[arrow] (61) -- (51);
+% \draw[arrow] (62) -- (51);
+% \draw[arrow] (62) -- (52);
+% \draw[arrow] (63) -- (53);
+% \draw[arrow] (64) -- (52);
+% \draw[arrow] (64) -- (54);
+% \draw[arrow] (65) -- (54);
+% \draw[arrow] (51) -- (41);
+% \draw[arrow] (51) -- (42);
+% \draw[arrow] (52) -- (42);
+% \draw[arrow] (52) -- (43);
+% \draw[arrow] (53) -- (43);
+% \draw[arrow] (54) -- (43);
+% \draw[arrow] (54) -- (44);
+% \draw[arrow] (54) -- (45);
+% \draw[arrow] (41) -- (31);
+% \draw[arrow] (42) -- (31);
+% \draw[arrow] (42) -- (32);
+% \draw[arrow] (43) -- (32);
+% \draw[arrow] (44) -- (32);
+% \draw[arrow] (45) -- (32);
+% \draw[arrow] (31) -- (21);
+% \draw[arrow] (31) -- (22);
+% \draw[arrow] (32) -- (22);
+% 
+% \node (2d) [dimension, left=of 21] {2d};
+% \node (3d) [dimension, above=of 2d] {3d};
+% \node (4d) [dimension, above=of 3d] {4d};
+% \node (5d) [dimension, above=of 4d] {5d};
+% \node (6d) [dimension, above=of 5d] {6d};
+% \node (7d) [dimension, above=of 6d] {7d};
+% \node (8d) [dimension, above=of 7d] {8d};
+% \node (9d) [dimension, above=of 8d] {9d};
+% \node (10d) [dimension, above=of 9d] {10d};
+% \end{tikzpicture}
+% \caption{Orbits of square-zero supercharges.}
+% \label{fig:superchargeorbits}
+% \end{figure}
+% \end{landscape}
+
+\section{Supersymmetric Yang--Mills theories}
 
@@
 
-\subsection{Pure Super Yang--Mills Theory}
+\subsection{Pure super Yang--Mills theory}
 \label{sect:gaugemultipletSUSY}
@@
 Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
-Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
+Fix a $\ZZ/2$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
 \[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
@@
 
-\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
-\end{itemize}
-We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
-Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.
+\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
+\end{itemize}
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$. Let $\cE_{\gauge}$ denote the space of BV fields.
 
@@
 The BRST action is given by
-\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+\[S_{BRST}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
 
@@
 We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. 
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, with $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
-The action of supersymmetry is given by a linear and a quadratic functional
-\begin{align*}
-I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
+The action of supersymmetry is given by a linear and quadratic functionals
+\begin{align}
+I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
 I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
-\end{align*}
-
-The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
+\label{eq:gaugeI2}
+\end{align}
+
+The following theorem summarizes the fact that super Yang--Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
 
 \begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
-\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
+\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
+Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
 \end{thm}
@@
 \{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
-\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
-\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
+\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
+\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
 \{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
@@
 \begin{remark}
-The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; this was proven by Baez and Huerta in \cite{BaezHuerta}, and our proof essentially follows the proof in loc.
-cit.
+The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; our proof essentially follows \cite{BaezHuerta}.
 \end{remark}
@@
 One has
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
 \label{lm:gaugemultiplet2}
@@
 Evaluating the equation
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{CE} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
 on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
@@
 \begin{align*}
-(\d_{\mr{CE}} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+(\d_{CE} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
 &= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
@@
 Evaluating the equation
-\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
+\[\d_{CE} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
 on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
@@
 
-\subsection{Coupling to Matter Multiplets}
+\subsection{Matter multiplet}
 \label{sect:mattermultipletSUSY}
@@
 What is the reason for only seeing certain multiplets via this general setup?
-} \chris{Presumably pure $\mc N = (0,N)$ means a $(0,2)$ vector coupled to $N-2$ Fermi multiplets, so some of these are already covered by the classification?
-Perhaps your concern is that you want a formalism that allows Fermis that are not adjoint valued?
-I don't think the difference between this hyper and twisted hyper is germane here: the proof of supersymmetry is that there is an action of super Poincar\'e, it doesn't involve the action of R-symmetry.}
+}
 
@@
 the supersymmetric gauged linear $\sigma$-models.
-Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models by Deligne and Freed in \cite[Chapter 3]{DeligneFreed}.
+Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models in \cite[Chapter 3]{DeligneFreed}.
 
 Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a real associative composition algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and denote its complexification by $A$.
+In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras}.
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
@@
 \begin{itemize}
-\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
-
-\item (\textbf{3d $\cN=1$ supersymmetry}) $A_\RR = \RR$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
-
-\item (\textbf{4d $\cN=1$ supersymmetry}) $A_\RR = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
-
-\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A_\RR = \mathbb{H}$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+
+\item (\textbf{3d $\cN=1$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{4d $\cN=1$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
 \end{itemize}
@@
 \[(av, w) = (v, \sigma(a)w).\]
-Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A_\RR=\RR, \CC, \mathbb{H}$ we get the following data:
-\begin{itemize}
-\item $A_\RR=\RR$, so $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.
-
-\item $A_\RR=\CC$, so $A=\CC[x]/(x^2+1)$.
+Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing.
+Explicitly, for $A=\CC, \CC\otimes_\RR\CC, \mathbb{H}\otimes_\RR\CC$ we get the following data:
+\begin{itemize}
+\item $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.
+
+\item $A=\CC[x]/(x^2+1)$.
 A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$.
@@
 
-\item $A_\RR=\mathbb{H}$, so $A=\eend(Z)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $Z$.
-Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$.
+\item $A=\eend(W_+)$.
+A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$.
+Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$.
 So, the data boils down a symplectic $\fg$-representation $U$.
@@
 The action of supersymmetry is given by a linear and quadratic functional:
-\begin{align*}
-I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \\
-I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*))
-\end{align*}
+\begin{align}
+I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
+I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
+\end{align}
 where $Q, Q_1,Q_2 \in \Sigma$.
@@
 \label{CMEYM}
-\d_{\mr{CE}} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\d_{CE} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
 \end{equation}
@@
 \{S_{\BV} , I^{(1)}\} & = & 0 \\ 
-\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
-\d_{\mr{CE}} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
+\d_{CE} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
 \{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
@@
 \begin{equation}\label{CMEYM3}
-\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
+\{S_{\matter}, I^{(2)}\} + \d_{CE} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
 \end{equation}
@@
 \[
-(\d_{\mr{CE}}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+(\d_{CE}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
 \]
@@
 
-The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with a nondegenerate symmetric bilinear pairing.
+The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10, \CC)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with nondegenerate symmetric bilinear pairings.
 There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills theory}
+\subsection{$\cN=(1, 0)$ super Yang--Mills}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 \begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
-Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
-\end{itemize}
-
-We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible twisting datum $\alpha$.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with a nonvanishing complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
+Such a supercharge is stabilized by $G=\SU(5)\subset \Spin(10, \CC)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+\label{sect:10dholomorphictwist}
+
+We will now fix a Calabi--Yau structure giving rise to a square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
 Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
+We denote the real volume form on $\RR^{10}$ by
+\[\dvol = \frac{\omega^5}{5!}.\]
+
 The vector representation decomposes as
@@
 Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
-Under the above decomposition the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
+Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
 \[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
@@
 The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields.
-We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
+To write it out we will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.
 
@@
 The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
-\begin{align*}
-S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
-I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
-\end{align*}
+\begin{align}
+S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
+S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
+I^{(1)} &= \int \dvol\left(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
+I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+\end{align}
 
 \begin{thm}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ with the space of fields $\map(\CC^5, B\gg)$.
+Moreover, the equivalence is $\SU(5)$-equivariant.
 \label{thm:10dholomorphictwist}
 \end{thm}
-
-\begin{proof}
-First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+\begin{proof}
+First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
 So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
 \begin{align*}
-S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
-&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
-\end{align*}
-
-Next, we have a term $\int \psi\wedge A_{1, 0}^*$ in the action, i.e.
-$(\psi, A_{1, 0})$ is a BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
+&+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
+\end{align*}
+
+Next, we have a term $\int \dvol \psi\wedge A_{1, 0}^*$ in the action, i.e.
+$(\psi, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
 The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
-S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* + F_{0, 2}\wedge B^*
+S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \dvol\left((\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^* + (F_{0, 2}, B^*)\right)
 \]
@@
 
-The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
-So, we fix $W = \CC$.
-
-\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9, \CC)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
+
+\subsection{$\cN=1$ super Yang--Mills}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$.
-So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
+So, it gives rise to a $\ZZ/2$-graded holomorphic theory.
 A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
+Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(9, \CC)$.
 \end{itemize}
@@
 Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
+
+\subsubsection{Minimal twist}
 
@@
 The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
+Moreover, the equivalence is $\SU(4)$-equivariant.
 \end{thm}
@@
 
-%%%%%%%%%%%%%%%%%%
+%\begin{landscape}
+
+%\end{landscape}
+
 % \subsection{Standard Equivalences Between Classical Field Theories}
@@
 % 
+% \brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
+In any case, I do like that we've stated them clearly.} \chris{I'm not sure what you have in mind (for instance I'm not sure why you would need the Grothendieck condition there), but I think the lemmas below should be formally immediate in this dg category of differentiable cochain complexes setting (like the first one follows in any context where you have an exact sequence $0 \to A \to B \to C \to 0$ and the fact that if $C$ is equivalent to 0 then $A \to B$ is an equivalence, or the same with $A$ and $B \to C$.)}
 % 
@@
 % From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2\ZZ$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
+% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
 % As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
@@
 % \end{proof}
-
-%%%%%%%%%%%%%%%%%
+% 
+% The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
+% \brian{How do we place 10d YM on an arbitrary 5-fold? 
+% Are you using something about sugra?
+% } \chris{Not an arbitrary 5-fold, but just Calabi-Yau.
+I'm not thinking of using sugra.
+Instead I want to say that a Calabi-Yau 5-fold has a principal $\SU(5)$ frame bundle.
+Take the fields to be sections of the associated vector bundles under the appropriate representations, then use the same action functional: the Lagrangian density is $\SU(5)$ invariant and so will define a density on the 5-fold.}
+% 
+% 
+% \subsection{Dimension 9}
+% The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.
+It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.
+% 
+% There is a single non-zero equivalence class of square zero supercharges in 9 dimensions.
+Such supercharges are minimal (i.e.
+have 5d image).
+They are stabilized by $\SU(4)$.
+Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.
+% 
+% Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.
+The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.
+These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
+% \begin{align*}
+% B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9}) \\
+% A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR_{x^9})
+% \end{align*}
+% along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.
+% 
+% \brian{Where is the one-form in the $\RR$-direction? Are we identifying that with $\phi$?}
+% 
+% \begin{theorem} \label{9d_twist_thm}
+% The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
+% \end{theorem}
+% 
+% \begin{proof}
+% Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.
+Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.
+According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.
+% 
+% As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_prop}.
+% \end{proof}
+% 
+% \begin{remark}
+% One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
+% \end{remark}
 
 \section{Dimension 8}
+
+The 8-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 8-dimensional semi-spin representations of $\Spin(8, \CC)$ and $W$ is a complex vector space.
+The semi-spin representations carry nondegenerate symmetric bilinear pairings $S_{\pm}\otimes S_{\pm}\rightarrow \CC$.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
+
+\subsection{$\cN=1$ super Yang--Mills}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+
+The 8d $\cN=1$ supersymmetry algebra admits three twists:
+\begin{itemize}
+\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm} = 0$.
+These are holomorphic.
+Moreover, we may choose a homomorphism $\alpha\colon \U(1)\rightarrow \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
+Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$.
+We have a twisting homomorphism $\phi\colon \U(4)\xrightarrow{\det} \U(1)\rightarrow G_R=\Spin(2, \RR)$, so the twisted theory carries an action of $\U(4)$.
+
+\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm}\neq 0$.
+These are topological.
+As before, we may choose a compatible homomorphism $\alpha$, so they give rise to a $\ZZ$-graded topological theory.
+Such a supercharge is stabilized by $\Spin(7, \RR)\subset \Spin(8, \CC)$.
+
+\item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero.
+These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2$-graded theory.
+We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$.
+The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$.
+The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$.
+We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+\label{sect:8dholomorphictwist}
+
+Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$. In this case the theory carries a $\U(4)$-action and a $\ZZ$-grading. Choose a K\"ahler structure on $\RR^8\cong \CC^4$.
+
 \vspace{-10pt}
-\paragraph{Fields:} 
-The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
-It has BRST fields given by a ghost $c$ along with the following.
-\begin{itemize}
- \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
- \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
-\end{itemize}
-
-We will see shortly that in the 8d $\mc N=1$ supersymmetry algebra there are holomorphic square-zero supercharges stabilized by the group $\SU(4)$, and topological square-zero supercharges stabilized by $\spin(7)$.
-If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
-So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
-We can write this schematically in the following way.
-
-First, let us consider the reduction of the 10d spinor $\lambda$.
-We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
-We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
-Let us continue to decompose these fields into smaller subgroups.
-We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
-\begin{figure}[!htb]
-\[
-\xymatrix{
-&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
-\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
-(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
- &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
-}\]
-\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dfermiondecomp}
-\end{figure}
-In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
-The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
-Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
-
-We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
-\begin{figure}[!h]
-\[\xymatrix{
-&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
-A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
-\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
-&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^4; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(\CC^4; \gg)$.
+\item Scalar fields $\phi\in\Omega^{4,0}(\CC^4; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(\CC^4; \gg)[-2]$.
+\item Fermions $\chi\in\Omega^0(\CC^4; \gg)[-1]$, $B\in\Omega^{0, 2}(\CC^4; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(\CC^4; \gg)[-1]$, $\psi\in\Omega^{1, 0}(\CC^4; \gg)[1]$ and $C\in\Omega^{3, 0}(\CC^4; \gg)[1]$.
+
+\item A ghost field $c\in \Omega^0(\CC^4; \gg)[1]$.
+\end{itemize}
+
+\begin{thm}
+The holomorphic twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory on $\CC^4$ with the space of fields $\map(\CC^4, T^*[3] B\fg)$.
+Moreover, the equivalence is $\U(4)$-equivariant.
+\label{thm:8dholomorphictwist}
+\end{thm}
+\begin{proof}
+8d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 10d $\cN=1$ super Yang--Mills theory.
+Under dimensional reduction the 10d fields from Section \ref{sect:10dholomorphictwist} decompose as follows:
+\begin{align*}
+A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
+\psi&\rightsquigarrow \psi, \wt\chi \\
+B&\rightsquigarrow B, C.
+\end{align*}
+
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{9d_twist_thm}).
+We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
+Indeed, the equivalence given by Theorem \ref{9d_twist_thm} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
+&&\ar@{}^{\bigoplus}[r] &&& \\
+\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
 }
 \]
-\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dbosondecomp}
-\end{figure}
-Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-Using the decomposition of the fields described above, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
-We begin by considering $\mr O(8)$ itself.
-
-\begin{prop} \label{O8_decomposition_of_susy_prop}
-After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
-I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
-\end{align*}
-if $Q^+$ is an element of $S_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
-I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
-\end{align*}
-if $Q^-$ is an element of $S_-$.
+concentrated in cohomological degrees $-2, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory.
+\end{proof}
+
+\subsubsection{Partially topological twist}
+
+Next we discuss the case of the partially topological twist with 5 invariant directions.
+Recall that it is merely $\ZZ/2$-graded.
+Decompose $M=\RR^8\cong\CC^3\times \RR^2$ and choose a Calabi--Yau structure on $\CC^3$.
+Using the twisting homomorphism $\SU(3)\times \Spin(2, \RR)\rightarrow G_R$ the twisted theory carries an action of $\SU(3)\times \Spin(2, \RR)$ acting on the individual factors of $\CC^3\times \RR^2$.
+
+\begin{thm}
+The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
+\label{thm:8dpartiallytopologicaltwist}
+\end{thm}
+\begin{proof}
+Denote $V_\RR=\RR^2$, so that we consider 8d $\cN=1$ super Yang--Mills on $\CC^3\times V_\RR$.
+By definition it is obtained as a dimensional reduction of the 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ along the projection $\Re\colon V\rightarrow V_\RR$, where $V=V_\RR\otimes_\RR \CC$.
+
+Let $Q = (Q_+, Q_-)$ be the square-zero supercharge corresponding to the partially topological twist.
+Since we have $(Q_\pm, Q_\pm)_{S_\pm} = 0$, the element $Q_+ + Q_-$ is a square-zero supercharge in the 10-dimensional supersymmetry algebra.
+By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
+Moreover, the equivalence is $\SU(3)\times \SU(V)$-equivariant.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $\CC^3\times V$ along $V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times V_\RR, B\fg)$ and this isomorphism is $\SU(3)\times \SO(V_\RR)$-equivariant, where $\SO(V_\RR)$ acts on $V$ via the homomorphism \eqref{eq:SOtoSU}.
+
+Therefore, we just need to establish that the $\Spin(V_\RR)$-action on the twisted 8d $\cN=1$ super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(V_\RR)$-action on the generalized Chern--Simons theory.
+The $\Spin(V_\RR)$-action on the fields on 8d $\cN=1$ super Yang--Mills is obtained via the homomorphism
+\[\Spin(V_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(V_\RR)\times \Spin(V_\RR)\hookrightarrow \Spin(V_\RR\oplus V_\RR),\]
+where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(V_\RR)$ and the twisting homomorphism, i.e.
+the identity map, to the $R$-symmetry group $G_R=\Spin(V_\RR)$.
+The $\SO(V_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
+\[\SO(V_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(V)\longrightarrow \SO(V_\RR\oplus V_\RR)\]
+
+The claim then follows from the commutativity of the diagram
+\[
+\xymatrix@C=2cm{
+\SO(V_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(V_\RR)\times \SO(V_\RR) \ar[d] \\
+\SU(V) \ar[r] & \SO(V_\RR\oplus V_\RR).
+}
+\]
+\end{proof}
+
+\subsubsection{Topological twist}
+
+Finally we discuss the case of the topological twist.
+We are going to prove that it is perturbatively trivial.
+In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and decribe the corresponding family of twisted theories.
+
+Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$.
+Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure.
+Moreover, fix a complex volume form on $L$.
+Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
+\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
+The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$.
+Consider a family of square-zero supercharges
+\[Q_t = \alpha + t\beta\in\Sigma_+\]
+for $t\in\CC$. We have
+\[(Q_t, Q_t) = t,\]
+so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.
+
+We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}.
+Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$.
+First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.
+
+\begin{prop}
+The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the 8d $\cN=1$ super Yang--Mills fields are
+\begin{align*}
+I^{(1)}(Q_t) &= \int \dvol\left(-(\psi, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \psi^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
+\end{align*}
 \end{prop}
 
-\begin{proof}
-There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
-\chris{Pavel gave this argument, in terms of light-cone coordinates.}
-\end{proof}
-
-\begin{remark}
-A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
-comes from a 10d square-zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
-\end{remark}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are holomorphic.
-They are stabilized by $\SU(4)$.
-Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
- \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are topological.
-They are stabilized by $\Spin(7) \sub \SO(8)$.
-Again, twists by such supercharges can be made $\ZZ$-graded.
- \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.
-The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.
-
-Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
-As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
-This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.
-
-On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an twist which is perturbatively trivial on its own, but non-trivial as a one-parameter family, as we discussed at the end of Section \ref{gen_BF_section}.
-That is, we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
-
-Let us now consider the further reductions to $\SU(4)$, to $\spin(7)$, and to their intersection $\SU(3)$.  We will use the form of the supersymmetric interaction term above to prove the following.
-
-\begin{theorem} \label{8d_holo_twist_thm}
-The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
-If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Proposition \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
-More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Proposition \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
-
-Note that, unlike in 9d, this theory can be made $\ZZ$-graded, rather than just $\ZZ/2\ZZ$-graded.
-To do so, we consider the action of the 8d R-symmetry group $\CC^\times$, where $S_+$ has weight $+1$ and $S_-$ has weight $-1$, so in particular the holomorphic supercharge $Q_+$ has weight 1.
-We've chosen notation for our component fields that makes it easy to read off the R-symmetry weight of each field: fermions with superscript $+$ have weight $+1$, fermions with superscript $-$ have weight $-1$, the bosonic scalars $\phi_1$ and $\wt \phi_1$ have weight -$2$, and the other bosons have weight 0.
-With respect to this $\ZZ$-grading, the classical BV complex, as an $\SU(4)$-module, has the form
-\[\xymatrix{&\Omega^0(X_4; \gg)_c \ar[r] &\Omega^{0,1}(X_4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^+_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{\psi_{0,1}^{-\vee}} \ar[r] &\Omega^{0,4}(X_4; \gg)_{\phi_1^\vee} \\
-\Omega^0(X_4; \gg)_{\phi_1} \ar[r] &\Omega^{0,1}(X_4; \gg)_{\psi_{0,1}^{-}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^{+\vee}_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,4}(X_4; \gg)_{c^\vee}&
-}\]
-placed in cohomological degrees $-2, \ldots, 3$.
-
-Now, suppose $X_4$ splits into a product of the form $X_3 \times S$.  If we restrict to $\SU(3)$ representations, our classical BV complex becomes
-
-\resizebox{1.05\textwidth}{!}{$\xymatrix@C-20pt{&\Omega^0(X_3 \times S; \gg)_c \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{A_{0,1}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^+_{1,0}} \ar[r]  &\Omega^{0,3}(X_3 \times S; \gg)_{\chi^{-\vee}} \ar[rd] & \\
-&&\Omega^0(X_3 \times S; \gg\omega)_{\phi_2} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi^{+}_{0,1}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{\psi^{-\vee}_{0,1}} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{\phi_{1}^{\vee}} \\
-\Omega^0(X_3 \times S; \gg)_{\phi_1} \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{\psi_{0,1}^{-}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^{+\vee}_{0,1}} \ar[r] \ar[rd] &\Omega^{0,3}(X_3 \times S; \gg)_{\phi_{2}^\vee} \ar[rd]&& \\
-&\Omega^0(X_3 \times S; \gg\omega)_{\phi_1} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi_{1,0}^{+\vee}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{c^\vee}&}
-$}
-where Dolbeault forms here refer to forms on $X_3$, and $\omega$ denotes the volume form on $S$.
-
-Let $Q = Q^+ + tQ'$ be a generically topological 1-parameter family of supercharges in $S_+$, where $Q'$ is an impure spinor stabilized by $\spin(7)$.
-The supercharges $Q_+$ and $Q'$ automatically commute, so to complete the proof it remains for us to compute the action of the further supercharge $Q'$ on the classical BV complex above.
-To do so we will use the description of the supersymmetry action from Proposition \ref{O8_decomposition_of_susy_prop}.
-So, we'll first observe that several summands of $I^{(1)}(Q')$ and $I^{(2)}(Q')$ are forced to vanish.
-In $I^{(1)}(Q')$, the term pairing $\lambda_+^\vee$ and $A$ cannot be $\spin(7)$-invariant, so must vanish.
-The same applies to the term pairing $\lambda_-^\vee$ and $\phi_1$.
-We are left with, in terms of $\Spin(7)$-fields,
-\begin{align*}
-I^{(1)}(tQ') &= t\langle\lambda_7^\vee, \lambda^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 (A_7^{+\vee} , A_7^{+\vee}),
-\end{align*}
-where we pair $A_7^{+\vee}$ with itself using the restriction of the scalar pairing on $S_+$ to the 7d vector representation \chris{can probably be phrased in terms of the $\spin(7)$-structure somehow}.
-Restricting to representations of $\SU(3)$, this takes the form
-\begin{align*}
-I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi_{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 \Lambda(\psi_{0,1}^{+\vee} \wedge \psi_{1,0}^{-\vee}),
-\end{align*}
-plus terms that vanish in the $Q_+$-twist.
-We can then read off the deformation of the $Q_+$-twist by $Q'$: the further differential associated to the $Q'$ supersymmetry turns on an isomorphism between the two copies of $\Omega^{0,\bullet}(X_3, \Omega^\bullet(S;\gg))$ in the $Q_+$-twisted classical BV complex.
-This is exactly the classical field theory described by $\map(X_3 \times S, B\gg)_{\mr{Hod}}$, as required.
-\end{proof}
-
-We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
-We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
-This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.
-
-\begin{theorem} \label{8d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 8d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with a pair $L_1 \times L_2$ of oriented 1-manifolds is equivalent to mixed Chern-Simons theory on $X_3 \times (L_1 \times L_2)_{\mr{dR}}$.
-\end{theorem}
-
-\begin{proof}
-The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_prop} twice.
-\end{proof}
-
-\chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}
+The action of the twisted 8d super Yang--Mills theory is given by
+\[S_{Q_t} = S_{\mathrm{BRST}} + S_{\mathrm{anti}} + I^{(1)}(Q_t) + I^{(2)}(Q_t),\]
+where $S_{\mathrm{BRST}}$ and $S_{\mathrm{anti}}$ are given by \eqref{eq:10dBRST} and \eqref{eq:10danti} respectively.
+
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(2, \RR)$ with respect to which $Q_t$ has weight $1$, so the $Q_t$-twisted theory will have a $\ZZ$-grading.
+
+\begin{thm}
+The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, (B\fg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\SU(4)$-equivariant.
+\label{thm:8dHodgetwist}
+\end{thm}
+\begin{proof}
+The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.
+
+Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$.
+Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\psi, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We are left with the action
+\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + t\phi c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
+where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
+Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
+The former is given by (cf.
+the proof of Theorem \ref{thm:8dholomorphictwist})
+\[
+\xymatrix@C=0.5cm{
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
+\Omega^0(\CC^4; \gg)_{\phi} \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
+}
+\]
+which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+\end{proof}
+
+\begin{cor}
+The topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively trivial.
+\label{cor:8dtopologicaltwist}
+\end{cor}
+\begin{proof}
+The topological twist of 8d $\cN=1$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$.
+From Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
+\end{proof}
 
@@
 
-\subsection{\texorpdfstring{$\mc N = (1,0)$}{N=(1,0)} Super Yang-Mills Theory with Matter} \label{6d_10_section}
+\subsection{$\mc N = (1,0)$ Super Yang-Mills Theory with Matter} \label{6d_10_section}
 
@@
 Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
-The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
+The only square zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
 Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
@@
 The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
-That is, the theory with the space of fields $\mr{Map}(\CC^3, U\ham \gg)$, where $U\ham \gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
+That is, the theory with the space of fields $\mr{Map}(\CC^3, U/\!/\gg)$, where $U/\!/\gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
 \label{thm:6dholomorphictwist}
@@
 
-\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}
+\subsection{$\mc N = (1,1)$ Super Yang-Mills Theory}
 
@@
 We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
+That is, by applying Proposition \ref{CS__diml_red_prop} to the family of twists in 7-dimensions.
 \end{proof}
@@
 The maximal supersymmetric gauge theory has $\mc N=2$.
-However, there are $\mc N=1$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group.
-
-\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang-Mills Theory with Matter}  \label{5d_1_section}
+However, there are $\mc N=1$ super Yang-Mills theory for every choice $U$ of symplectic representation of the gauge group.
+
+\subsection{$\mc N = 1$ Super Yang-Mills Theory with Matter}  \label{5d_1_section}
 We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from Section \ref{6d_10_section} to representations of the group $\mr O(5)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from section \ref{6d_10_section} to representations of the group $\mr O(5)$.
 In addition to the ghost $c$, the fields we obtain are
 \begin{itemize}
- \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^0(\RR^5; \gg)$.
+ \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^1(\RR^5; \gg)$.
  \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
@@
 \begin{theorem} \label{5d_holo_twist_theorem}
-The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
+The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U/\!/G)$.
 \end{theorem}
@@
 
-\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang-Mills Theory} \label{5d_2_section}
+\subsection{$\mc N = 2$ Super Yang-Mills Theory} \label{5d_2_section}
 
@@
 Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).
-These supercharges all occur as square-zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
+These supercharges all occur as square zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
 \begin{enumerate}
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} with chiral multiplet matter} \label{4d_1_section}
+\subsection{$\cN=1$ with chiral multiplet matter} 
 We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
@@
 \item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
-\item $R$-valued bosons: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
-\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^0(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
-\item $R$-valued fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
-\end{itemize}
-
-There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
+\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^1(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
+\item scalars: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
+\item fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
+\end{itemize}
+
+There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
 Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
 Such supercharges are minimal (i.e. have two dimensional image).  
-They are stabilized by ${\rm U}(2)$; indeed a minimal square-zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
+They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
 The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
@@
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$.
 \end{thm}
@@
 
-\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills with Matter} \label{4d_2_section}
+\subsection{$\cN=2$ Super Yang-Mills with Matter}
 
@@
  \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
- \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
+ \item $U$-valued bosons: a $W \oplus W^*$-valued scalar field $(\phi \otimes v,\phi' \otimes v') \in \Omega^0(\RR^4; (W \oplus W^*) \otimes U)$.
  \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
@@
 &\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
+I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi')Q_+, \psi_+^*)(v',w_+)) \\
 I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
@@
 \begin{theorem} \label{4d_2_holo_twist_thm}
-The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
+The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U/\!/\gg))$.
 \end{theorem}
@@
 \begin{theorem} \label{4d_Donaldson_twist_thm}
-The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.
+The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U/\!/\gg)_{\mr{Hod}})$.
 \end{theorem}
@@
 \begin{theorem} \label{4d_11_twist_thm}
-The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.
+The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U/\!/\gg)$.
 This theory is generally only $\ZZ/2\ZZ$-graded.
@@
 
-\subsection{\texorpdfstring{$\cN=4$}{N=4} Super Yang-Mills} \label{4d_4_section}
+\subsection{$\cN=4$ Super Yang-Mills}
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from section \ref{5d_2_section} to representations of the group $\mr O(4)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \section{Dimension 3}
-The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.
-The maximal supersymmetric gauge theory has $\mc N=8$.
-However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.
-In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
-
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
-We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
-So, fix a gauge group $G$, and a representation $R$.
-The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
- \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
- \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
-
-\begin{thm} \label{3d_minimal_twist_thm}
-The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
-\end{thm}
-
-\begin{proof}
-This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
-\end{proof}
-
-\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
-We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
- \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
- \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.
-The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.
-Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.
-
-\begin{theorem} \label{3d_4_holo_A_twist_thm}
-The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
-\end{theorem}
-
-\begin{proof}
-To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
-\end{proof}
-
-\begin{theorem} \label{3d_2_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-This theory is generally only $\ZZ/2\ZZ$-graded.
-\end{theorem}
-
-\begin{proof}
-Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
-\end{proof}
-
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
-Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
-This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
- \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.
-There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).
-The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.
-
-\begin{theorem} 
-The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
-\end{theorem}
-
-\begin{theorem} 
-The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
-\end{theorem}
+
+% \cN=8 Super Yang-Mills
+% \cN=4 Super Yang-Mills with matter in a pseudo-real representation
+% \cN=2 Super Yang-Mills with matter in a complex representation
 
@@
 
-There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
-We additionally have gauge theories with chiral, i.e.
-$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.
-We'll address twists for these two classes of theory in turn.
-
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
-First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
-This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
- \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus \otimes (S_+ \oplus S_-) \otimes R^*)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-\chris{todo}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
-\begin{itemize}
- \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic
- \item Square-zero supecharges of rank $(1,1)$ are topological, and split into two classes: the B-supercharge arises by dimensional reduction from 3 dimensions, and the A-supercharge does not.
-\end{itemize}
-\chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
-
-The calculation of the twists here is similar to what we saw in 4d $\mc N=2$.
-The holomorphic twist and the B-twist arise by dimensional reduction from 3d, but the A-twist as a deformation of the holomorphic twist is not, and must be calculated directly.
-
-\begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
-\end{theorem}
-
-\begin{proof}
-This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_to_BF_diml_red_prop} to dimensionally reduce in the real de Rham direction.
-\end{proof}
-
-\begin{theorem} \label{2d_2_A_twist_thm}
-The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
-\end{theorem}
-
-\begin{proof}
-
-\end{proof}
-
-Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
-\begin{theorem} \label{2d_2_B_twist_thm}
-The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2, (R/\gg))$.
-\end{theorem}
-
-\begin{proof}
-We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
-\end{proof}
-
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
-We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.
-
-The following equivalences follow from the results in the previous section by substituting $R = $ \chris{what is it exactly?}.
-
-\begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.
-Together they are perturbatively equivalent to a holomorphic BF theory and its Hodge deformation, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
-
-If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
-\end{theorem}
-
-\begin{theorem}
-The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
-If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
-\end{theorem}
-
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}
+% \cN=(8, 8) Super Yang-Mills
+% \cN=(4, 4) Super Yang-Mills with matter in a pseudo-real representation
+% \cN=(2, 2) Super Yang-Mills with matter in a complex representation
+%BRIAN FIND REFERENCE OF BELOW
+% \cN=(0,2) Super Yang-Mills with matter
+
+\subsection{$\cN=(0,2)$ Super Yang-Mills with matter}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{2d(0,2)}
+\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
 The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
@@
 
-\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with matter}
-
-We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
-The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
-Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
-
-The field content is:
+\subsection{$\cN=(0,4)$ Super Yang-Mills with matter}
+
+\brian{Confused.}
+
+The untwisted fields are given by:
 \begin{itemize}
@@
 \item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-\end{itemize}
-
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
-
-\begin{thm}\label{2d(0,4)}
-The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-\end{thm}
-
-\begin{proof}
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
-Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
-The claim now follows from Theorem \ref{2d(0,2)}. 
-\end{proof}
-
-\begin{rmk}
-The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-\end{rmk}
+\item $W_- \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W_- \otimes U)$;
+\item $U$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes U)$ .
+\end{itemize}
+Here, $W_-$ is a complex four-dimensional vector space equipped with a symmetric pairing. 
+Choose the basis $\{u_1,u_2,v_1,v_2\}$ for $W_-$ with pairing given by $\<u_i, v_j\> = \delta_{ij}$.
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang-Mills}
-
-We consider pure $\cN=(0,\cN_-)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_- \geq 2$.
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_-$ is the $\cN_-$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.
+\subsection{$\cN=(0,\cN_-)$ Super Yang-Mills}
 
@@
 \end{itemize}
-Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$ such that the pairing restricted to $ {\rm span}_{\CC} \{u, v\}$ is $\<u,v\> = 1$.
-
-The field content is:
+Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$.
+
 \[
@@
 
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
-
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
-%A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-%\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
-%\end{array}
-%\]
-
-%\begin{align*}
-%S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
-%S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-%&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
-%I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
-%I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
-%\end{align*}
-
-\begin{thm}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
+A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
+\end{array}
+\]
+
+\begin{align*}
+S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
+&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
+\end{align*}
+
+\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
 The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
 \end{thm}
-
-\begin{proof}
-The proof is similar to the proof of Theorem \ref{2d(0,4)}.
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
-Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
-Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The claim now follows from a special case of Theorem \ref{2d(0,2)} where we take $R = 0$. 
-%First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-%We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
-%Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
-%which can be integrated out using Proposition \ref{prop:BRSTdoublet}.  
-%
-%The twisted theory is therefore perturbatively equivalent to the theory with BV action 
-%\begin{align*}
-% S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
-%  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
-%\end{align*}
-%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
+\begin{proof}
+First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
+Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+ S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
+  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
 \end{proof}
@@
 \[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
-Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$.
+Consider a $\ZZ/2$-graded Clifford module $M=M^+\oplus M^-$.
 Denote the Clifford action by $\rho(v)\in\eend(M)$.

### 2020-01-17 paper.tex

--- 2020-01-16 paper.tex
@@
 
+\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}
+
 The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
@@
 We have
-\[\Omega^{0, \bullet}_{\CC}\cong \underline{\CC}\oplus \underline{\CC}\d \overline{z}[-1]\]
+\[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
 and
-\[\Omega^\bullet_{\RR}\cong \underline{\CC}\oplus \underline{\CC} \d x[-1].\]
+\[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]
+
 Under the pullback map
-\[\Omega^\bullet(\RR; \CC)\rightarrow \Omega^\bullet(\CC)\rightarrow \Omega^{0, \bullet}(\CC)\]
-the integration map $\int_\CC \d z\wedge (-)\colon \Omega^{0, \bullet}(\CC)\rightarrow \CC$ reduces to the integration map $\int_\RR (-)\colon \Omega^{\bullet}(\RR;\CC)\rightarrow \CC$.
+\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
+the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$.
 \brian{This is not defined} \chris{is compactly supported enough?
@@
 
-Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and let $V=V_\RR\otimes_\RR\CC$ be its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
+Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form.
+Denote by $V=V_\RR\otimes_\RR\CC$ its complexification.
+Consider the Lie algebra $\so(V)$.
+Let us recall the following facts:
 \begin{itemize}
@@
 
-Let $A_\RR$ be a unital (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
+Let $A$ be a unital (possibly non-associative) complex algebra equipped with an antiinvolution $\sigma\colon A\rightarrow A$. We make the following assumptions:
 \begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
+\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A\rightarrow \CC$. We assume that it is nondegenerate.
 \end{enumerate}
@@
 In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
-$A_\RR$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.
-
-For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$.
-$V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+$A$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.
+
+For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
+We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$.
+$V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
 Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-
-We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$.
-So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.
 
@@
 
-We will now define the twist of a supersymmetric field theory by a square-zero supercharge.
-In order to obtain a $\ZZ$-graded theory, we will need to also include an additional piece of data as follows.
+Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
+\[
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
+
+\begin{definition} \label{def:twisting}
+Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge.
+The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
+\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
+\end{definition}
+
+Given additional data, we may enhance the classical field theory.
 
 \begin{definition}
-A \defterm{twisting datum} is a pair $(Q, \alpha)$, where $Q\in\Sigma$ is a square-zero supercharge and $\alpha\colon U(1)\rightarrow G_R$ is a homomorphism under which $Q$ has weight $1$.
+Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1.
 \end{definition}
 
-Let $(E, Q_{BV}, \omega, I)$ be a supersymmetric classical field theory.
-Recall from Section \ref{symmetry_section} that this means we have a Maurer-Cartan element 
-\[
-I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
-\]
-where $I_{\fA}^{(k)} \colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def}. 
-For each $k \geq 1$, the functional $I_{\fA}^{(k)}$ further decomposes as a sum $I_{\fA}^{(k)} = \sum_{\ell \geq 0} I_\fA^{(k),\ell}$ where $I_\fA^{(k),\ell}$ is $\ell$-linear in the fields $\cE$. 
-Define
-\[
-I_{\fA}^2 (Q) = \sum_{k \geq 1} I^{(k),2} (Q, \ldots, Q) \;\;\; , \;\;\; I_{\fA}^{\geq 3} (Q) =  \sum_{k \geq 1, \ell \geq 3} I^{(k),\ell} (Q, \ldots, Q) .
-\]
-Note that $I_{\fA}^2 (Q)$ is quadratic as a function of the fields and $I_{\fA}^{\geq 3}(Q) \in \cO_{\rm loc}^+(\cE)$.
-
-\begin{definition} \label{def:twisting}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum.
-The {$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{I_{\fA}^2(Q), -\}, \omega, I + I_{\fA}^{\ge 3}(Q))$, where
-\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
-for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
+Given a homomorphism $\alpha$, we consider the new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
+The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$.
+But it also has cohomological degree $-k$.
+In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
+
+\begin{definition}
+Let $Q\in\Sigma$ be a square-zero supercharge and suppose $G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism.
+A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the composite $G\rightarrow \Spin(V_\RR)\times G_R$.
 \end{definition}
 
-\begin{prop}
-The collection $\left(E^Q, Q_{\mr{BV}} + \{I^2_{\fA} (Q), -\}, \omega, I + I^{\geq 3}_\fA (Q)\right)$ is a classical field theory.
-\end{prop}
-
-\begin{proof}
-The original BV differential $\d$ has $\alpha$-weight zero, and hence descends to an operator of cohomological degree $+1$ on $E^Q$. 
-Now, $Q$ has $\alpha$-weight $+1$ and the BV bracket has $\alpha$-weight zero. 
-Hence, $\{\rho_{2}(Q), -\}$ also defines an operator of cohomological degree $+1$ on $E^Q$.
-
-Ellipticity of $(E^Q, \d + \{I_\fA^2 (Q), -\})$ follows from ellipticity of the original complex $(E, \d)$.
-The operator 
-\end{proof}
-
-\pavel{Need to explain that the degrees work out and check that you still have an elliptic complex.}
-
-\begin{remark}
-Without the homomorphism $\alpha : U(1) \to G_R$, we obtain a $\ZZ/2\ZZ$-graded classical field theory
-\[(E, \d + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots),\]
-where the $\ZZ/2\ZZ$-grading on $E$ is the total grading.
-\end{remark}
+The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action.
+However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
+However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
 
@@
 
-\subsection{Twisting Homomorphisms and Curved Backgrounds}
-
 \section{Supersymmetric Yang--Mills theories} \label{sec:SYM}
@@
 \end{itemize}
-We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
-Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.
+
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
+Let $\cE_{\gauge}$ denote the space of BV fields.
 
@@
 We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, with $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
 The action of supersymmetry is given by a linear and a quadratic functional
-\begin{align*}
-I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \\
+\begin{align}
+I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
 I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
-\end{align*}
-
-The following theorem summarizes the fact that super Yang-Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
+\label{eq:gaugeI2}
+\end{align}
+
+The following theorem summarizes the fact that super Yang--Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.
 
 \begin{thm}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
 \[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
+Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
 \end{thm}
@@
 Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a real associative composition algebra $A_\RR$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and denote its complexification by $A$.
+In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras}.
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
@@
 
-\item $A_\RR=\mathbb{H}$, so $A=\eend(Z)$.
-A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $Z$.
+\item $A=\eend(Z)$.
+A left $A$-module is necessarily of the form $P\cong Z\otimes U$, where $A$ just acts on $Z$.
 Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$.
@@
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
-Such a supercharge is stabilized by $\SU(5)\subset \Spin(10)$.
-\end{itemize}
-
-We will now fix a nonzero square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
+A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with a nonvanishing complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
+Such a supercharge is stabilized by $G=\SU(5)\subset \Spin(10, \CC)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+\label{sect:10dholomorphictwist}
+
+We will now fix a Calabi--Yau structure giving rise to a square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
 Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
+We denote the real volume form on $\RR^{10}$ by
+\[\dvol = \frac{\omega^5}{5!}.\]
+
 The vector representation decomposes as
@@
 
-The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry.
-So, we fix $W = \CC$.
+The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9, \CC)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
 
@@
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $\RR^9$, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
-Such a supercharge is stabilized by $\SU(4)\subset \Spin(9)$.
+A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with a complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(9, \CC)$.
 \end{itemize}
@@
 
-%%%%%%%%%%%%%%%%%%
-% \subsection{Standard Equivalences Between Classical Field Theories}
-% In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
-% 
-% \begin{lemma} \label{symplectomorphism_lemma}
-% A linear symplectomorphism $F \colon \mc E^\bullet \to \mc E^\bullet$ induces an equivalence of theories between $(\mc E^\bullet, Q, \omega, I)$ and $(\mc E^\bullet, F^*Q, \omega, F^*I)$.
-% \end{lemma}
-% 
-% 
-% \begin{lemma} \label{inclusion_and_projection_lemma}
-% Let $(\mc E^\bullet, Q)$ be a cochain complex, and let $(\mc C^\bullet, Q')$ be a contractible cochain complex.
-% \begin{enumerate}
-%  \item Let $F \colon \mc C^\bullet \to \mc E^\bullet$ be a degree 1 map making $(\mc C^\bullet \overset F\to \mc E^\bullet)$ into a cochain complex.
-Then the canonical inclusion $\mc E^\bullet \to (\mc C^\bullet \overset F\to \mc E^\bullet)$ is a quasi-isomorphism.
-%  \item Let $F' \colon \mc E^\bullet \to \mc C^\bullet$ be a degree 1 map making $(\mc E^\bullet \overset {F'}\to \mc C^\bullet)$ into a cochain complex.
-Then the canonical projection $(\mc E^\bullet \overset {F'}\to \mc C^\bullet) \to \mc E^\bullet$ is a quasi-isomorphism.
-% \end{enumerate}
-% \end{lemma}
-% 
-% \begin{lemma} \label{symplectic_composite_lemma}
-% Let $(\mc E^\bullet,Q)$ be a cochain complex, let $(\mc C_1^\bullet, Q_1)$ and $(\mc C_2^\bullet, Q_2)$ be contractible cochain complexes, and let $\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet$ be a pair of degree 1 maps so that the differential $Q + Q_1 + Q_2 + F_1 + F_2$ on the total complex squares to 0.
-Suppose the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$ is equipped with a $-1$-shifted symplectic structure so that $\mc C_1^\bullet \oplus \mc C_2^\bullet$ is a symplectic subspace.
-Then the cochain map
-% \begin{equation}
-% \label{symp_composite_eqn}\mc E^\bullet \to (\mc C_1^\bullet \overset{F_1}\to \mc E^\bullet \overset{F_2}\to \mc C_2^\bullet)
-% \end{equation}
-% obtained as the composite of the projection from Lemma \ref{inclusion_and_projection_lemma} (2) with a quasi-inverse to the inclusion from Lemma \ref{inclusion_and_projection_lemma} (1) is a symplectomorphism.
-% \end{lemma}
-% 
-% \begin{lemma} \label{interaction_pullback_lemma}
-% In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
-Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
-Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
-% \end{lemma}
-% 
-% \begin{proof}
-% We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
-Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
-% \end{proof}
-% 
-% \subsection{A-Type Twists} \label{A_twist_section}
-% \chris{...}
-% 
-% \subsection{Dimension 10}
-% We'll begin our discussing of twists of super Yang-Mills theory by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{sect:gaugemultipletSUSY}.
-In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
-These square-zero supercharges are holomorphic.
-% 
-% Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
-The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
-Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
-The BRST fields split as follows:
-% \begin{align*}
-% c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
-% A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
-% \lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
-% \end{align*}
-% 
-% In terms of these component fields, the BV action can be written in the following way.  We will split the BV action up into the BRST action and the antifield action.
-% \begin{align*}
-% S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
-% S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
-% \end{align*}
-% where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
-Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
-It has a quadratic and a cubic component given by
-% \begin{align*}
-% I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
-% I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
-% \end{align*}
-% The twisted action functional is obtained by adding these terms to the original BV action functional.
-% 
-% We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
-% 
-% \begin{theorem}\label{10d_twist_thm}
-% The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
-% \end{theorem}
-% 
-% \begin{remark}
-% From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-% This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2\ZZ$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
-% As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
-% \end{remark}
-% 
-% \begin{proof}
-% We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
-% 
-% \begin{enumerate}
-%  \item The first part of our equivalence of classical field theories will be a simple change of variables.
-Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
-In terms of $\chi'$, the quadratic part of the twisted action functional becomes
-%  \begin{align*}
-%   S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
-%   &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
-%  \end{align*}
-%  The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
-However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
-Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
-We think of this as ``integrating out'' the field $\chi'$ and its antifield.
-%  
-%  \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
-We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
-%  \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
-%  We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
-This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
-\chris{This isn't quite right I think.
-We need to kill that term, however, for the below argument to work.
-Can we fix it?}
-%  
-%  Observe that the classical BV complex associated to this action functional can now be written in the following form:
-%  \[\xymatrix{
-%  &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
-%  \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
-%  \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
-%  }\]
-%  where the first and third rows are dual under the symplectic pairing.
-This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
-the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
-%  
-%  \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
-In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
-Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
-The resulting interaction is
-%  \[
-%   I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
-%  \]
-%  which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
-The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
-%  
-%  \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
-The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
-Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
-an equivalence of classical field theories.
-% \end{enumerate}
-% \end{proof}
-
-%%%%%%%%%%%%%%%%%
-
 \section{Dimension 8}
 
+The 8-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 8-dimensional semi-spin representations of $\Spin(8, \CC)$ and $W$ is a complex vector space.
+The semi-spin representations carry nondegenerate symmetric bilinear pairings $S_{\pm}\otimes S_{\pm}\rightarrow \CC$.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
+
 \subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
 
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+
+The 8d $\cN=1$ supersymmetry algebra admits three twists:
+\begin{itemize}
+\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm} = 0$.
+These are holomorphic.
+Moreover, we may choose a homomorphism $\alpha\colon \U(1)\rightarrow \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
+Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$.
+We have a twisting homomorphism $\phi\colon \U(4)\xrightarrow{\det} \U(1)\rightarrow G_R=\Spin(2, \RR)$, so the twisted theory carries an action of $\U(4)$.
+
+\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm}\neq 0$.
+These are topological.
+As before, we may choose a compatible homomorphism $\alpha$, so they give rise to a $\ZZ$-graded topological theory.
+Such a supercharge is stabilized by $\Spin(7, \RR)\subset \Spin(8, \CC)$.
+
+\item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero.
+These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2$-graded theory.
+We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$.
+The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$.
+The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$.
+We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+\label{sect:8dholomorphictwist}
+
+Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$. In this case the theory carries a $\U(4)$-action and a $\ZZ$-grading. Choose a K\"ahler structure on $\RR^8\cong \CC^4$.
+
 \vspace{-10pt}
-\paragraph{Fields:} 
-The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.
-It has BRST fields given by a ghost $c$ along with the following.
-\begin{itemize}
- \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
- \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
-\end{itemize}
-
-We will see shortly that in the 8d $\mc N=1$ supersymmetry algebra there are holomorphic square-zero supercharges stabilized by the group $\SU(4)$, and topological square-zero supercharges stabilized by $\spin(7)$.
-If we want to stabilize the full one-parameter family describing the degeneration, we have to decompose our fields according to the action of the intersection $\SU(4) \cap \spin(7) \iso \SU(3)$ \chris{check this claim: can we see it in terms of the Dynkin diagrams?}.
-So, let's begin by establishing notation for the BRST fields of maximal super Yang-Mills after reduction to representations of various subgroups of $\SO(10)$.
-We can write this schematically in the following way.
-
-First, let us consider the reduction of the 10d spinor $\lambda$.
-We have already described the decomposition of the spinor representation into irreducible summands for the group $\SU(5)$: it decomposes into a sum $B_{0,2} + \psi_{1,0} + \chi$ of a $(0,2)$-form, a $(1,0)$-form, and a scalar (all valued in the Lie algebra $\gg$).
-We have also already described its decomposition into irreducible summands for the group $\mr O(8)$: it splits into a positive and a negative Weyl spinor, $\lambda^+ + \lambda^-$.
-Let us continue to decompose these fields into smaller subgroups.
-We indicate this schematically as follows (Figure \ref{fig:8dfermiondecomp}).
-\begin{figure}[!htb]
-\[
-\xymatrix{
-&\lambda \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} &\\
-\lambda^+, \lambda^- \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&B_{0,2}, \psi_{1,0}, \chi \ar[dl]^{\to\,  \SU(4)} \\
-(A_7^+, \wt \chi^+), \lambda^- \ar[dr] &(B_{0,2}^+, \psi_{0,1}^-), (\psi_{1,0}^+, \wt \chi^-), \chi^- \ar[d]_{\to\,  \SU(3)} &\\
- &((\psi_{1,0}^+, \psi_{0,1}^+), (\psi_{0,1}^-, \chi^-)), ((\psi_{1,0}^-, \wt \chi^-), \wt \chi^+), \chi^+. &
-}\]
-\caption{Decomposition of the 10d fermionic field $\lambda$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dfermiondecomp}
-\end{figure}
-In this diagram, the superscript $\pm$ indicates whether each component field arose as a summand of $\lambda^+$ or $\lambda^-$.
-The $\chi^\pm$ and $\wt \chi^\pm$ are $\gg$-valued scalars, and the fields $A_7^\pm$ are $\gg$-valued elements of the vector representation of $\spin(7)$.
-Finally, we have used parentheses to indicate how the fields decompose under the restriction from $\SU(n)$ to $\SU(n-1)$.
-
-We can do the same for the decomposition of the 10d gauge field $A$.  Again, we indicate this schematically as follows (Figure \ref{fig:8dbosondecomp}).
-\begin{figure}[!h]
-\[\xymatrix{
-&A \ar[dl]_{\to\,  \mr{O}(8)} \ar[dr]^{\to\,  \SU(5)} & \\
-A,\phi_1, \wt \phi_1 \ar[dr]_{\to\,  \SU(4)} \ar[d]_{\to\,  \Spin(7)} &&A_{0,1}, A_{1,0} \ar[dl]^{\to\,  \SU(4)} \\
-\lambda_7, \phi_1, \wt \phi_1 \ar[dr] &A_{0,1},A_{1,0},\phi_1, \wt \phi_1 \ar[d]_{\to\,  \SU(3)} & \\
-&(A_{0,1}, \phi_2) ,(A_{1,0}, \wt \phi_2) \phi_1, \wt \phi_1.&
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^4; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(\CC^4; \gg)$.
+\item Scalar fields $\phi\in\Omega^{4,0}(\CC^4; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(\CC^4; \gg)[-2]$.
+\item Fermions $\chi\in\Omega^0(\CC^4; \gg)[-1]$, $B\in\Omega^{0, 2}(\CC^4; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(\CC^4; \gg)[-1]$, $\psi\in\Omega^{1, 0}(\CC^4; \gg)[1]$ and $C\in\Omega^{3, 0}(\CC^4; \gg)[1]$.
+
+\item A ghost field $c\in \Omega^0(\CC^4; \gg)[1]$.
+\end{itemize}
+
+\begin{thm}
+The holomorphic twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory on $\CC^4$ with the space of fields $\map(\CC^4, T^*[3] B\fg)$.
+Moreover, the equivalence is $\U(4)$-equivariant.
+\label{thm:8dholomorphictwist}
+\end{thm}
+\begin{proof}
+8d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 10d $\cN=1$ super Yang--Mills theory.
+Under dimensional reduction the 10d fields from Section \ref{sect:10dholomorphictwist} decompose as follows:
+\begin{align*}
+A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
+\psi&\rightsquigarrow \psi, \wt\chi \\
+B&\rightsquigarrow B, C.
+\end{align*}
+
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{9d_twist_thm}).
+We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
+Indeed, the equivalence given by Theorem \ref{9d_twist_thm} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
+&&\ar@{}^{\bigoplus}[r] &&& \\
+\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
 }
 \]
-\caption{Decomposition of the 10d bosonic field $A$ upon restriction to subgroups of $\mr O(10)$.}
-\label{fig:8dbosondecomp}
-\end{figure}
-Now $\phi_i$ and $\wt \phi_i$ denote $\gg$-valued scalar fields, and $\lambda_7$ denotes a field valued in the spinor representation of $\Spin(7)$.
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-Using the decomposition of the fields described above, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.
-We begin by considering $\mr O(8)$ itself.
-
-\begin{prop} \label{O8_decomposition_of_susy_prop}
-After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
-I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
-\end{align*}
-if $Q^+$ is an element of $S_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
-I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
-\end{align*}
-if $Q^-$ is an element of $S_-$.
+concentrated in cohomological degrees $-2, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory.
+\end{proof}
+
+\subsubsection{Partially topological twist}
+
+Next we discuss the case of the partially topological twist with 5 invariant directions.
+Recall that it is merely $\ZZ/2$-graded.
+Decompose $M=\RR^8\cong\CC^3\times \RR^2$ and choose a Calabi--Yau structure on $\CC^3$.
+Using the twisting homomorphism $\SU(3)\times \Spin(2, \RR)\rightarrow G_R$ the twisted theory carries an action of $\SU(3)\times \Spin(2, \RR)$ acting on the individual factors of $\CC^3\times \RR^2$.
+
+\begin{thm}
+The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
+\label{thm:8dpartiallytopologicaltwist}
+\end{thm}
+\begin{proof}
+Denote $V_\RR=\RR^2$, so that we consider 8d $\cN=1$ super Yang--Mills on $\CC^3\times V_\RR$.
+By definition it is obtained as a dimensional reduction of the 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ along the projection $\Re\colon V\rightarrow V_\RR$, where $V=V_\RR\otimes_\RR \CC$.
+
+Let $Q = (Q_+, Q_-)$ be the square-zero supercharge corresponding to the partially topological twist.
+Since we have $(Q_\pm, Q_\pm)_{S_\pm} = 0$, the element $Q_+ + Q_-$ is a square-zero supercharge in the 10-dimensional supersymmetry algebra.
+By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
+Moreover, the equivalence is $\SU(3)\times \SU(V)$-equivariant.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $\CC^3\times V$ along $V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times V_\RR, B\fg)$ and this isomorphism is $\SU(3)\times \SO(V_\RR)$-equivariant, where $\SO(V_\RR)$ acts on $V$ via the homomorphism \eqref{eq:SOtoSU}.
+
+Therefore, we just need to establish that the $\Spin(V_\RR)$-action on the twisted 8d $\cN=1$ super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(V_\RR)$-action on the generalized Chern--Simons theory.
+The $\Spin(V_\RR)$-action on the fields on 8d $\cN=1$ super Yang--Mills is obtained via the homomorphism
+\[\Spin(V_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(V_\RR)\times \Spin(V_\RR)\hookrightarrow \Spin(V_\RR\oplus V_\RR),\]
+where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(V_\RR)$ and the twisting homomorphism, i.e.
+the identity map, to the $R$-symmetry group $G_R=\Spin(V_\RR)$.
+The $\SO(V_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
+\[\SO(V_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(V)\longrightarrow \SO(V_\RR\oplus V_\RR)\]
+
+The claim then follows from the commutativity of the diagram
+\[
+\xymatrix@C=2cm{
+\SO(V_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(V_\RR)\times \SO(V_\RR) \ar[d] \\
+\SU(V) \ar[r] & \SO(V_\RR\oplus V_\RR).
+}
+\]
+\end{proof}
+
+\subsubsection{Topological twist}
+
+Finally we discuss the case of the topological twist.
+We are going to prove that it is perturbatively trivial.
+In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and decribe the corresponding family of twisted theories.
+
+Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$.
+Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure.
+Moreover, fix a complex volume form on $L$.
+Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
+\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
+The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$.
+Consider a family of square-zero supercharges
+\[Q_t = \alpha + t\beta\in\Sigma_+\]
+for $t\in\CC$. We have
+\[(Q_t, Q_t) = t,\]
+so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.
+
+We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}.
+Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$.
+First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.
+
+\begin{prop}
+The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the 8d $\cN=1$ super Yang--Mills fields are
+\begin{align*}
+I^{(1)}(Q_t) &= \int \dvol\left(-(\psi, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \psi^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
+\end{align*}
 \end{prop}
 
-\begin{proof}
-There are two ingredients in this calculation: we have to decompose our fields as representations of $\mr O(8)$, and simultaneously we have to write the 10d $\Gamma(-,-)$ pairing in terms of the corresponding pairing for 8d spinors, upon dimensional reduction.
-\chris{Pavel gave this argument, in terms of light-cone coordinates.}
-\end{proof}
-
-\begin{remark}
-A Weyl spinor $Q_\pm$ corresponds to a holomorphic twist (i.e.
-comes from a 10d square-zero supercharge) exactly when $(Q_\pm,Q_\pm)=0$ -- in that case many of the terms in the interaction above will vanish.
-\end{remark}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In 8 dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Pure spinors, for which either $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are holomorphic.
-They are stabilized by $\SU(4)$.
-Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
- \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.
-These supercharges are topological.
-They are stabilized by $\Spin(7) \sub \SO(8)$.
-Again, twists by such supercharges can be made $\ZZ$-graded.
- \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction, as indicated on the ``8d'' row of Figure \ref{fig:superchargeorbits}.
-The topological twist (type 2 in the list above) appears in the right-most column of the figure, and is not obtained by dimensional reduction from higher dimensions.
-
-Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.
-As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.
-This theory can, unlike its 10- and 9-dimensional analogues, be made canonically $\ZZ$-graded.
-
-On the other hand, the topological twist -- the twist by an impure Weyl spinor -- of 8d $\mc N=1$ super Yang-Mills theory does not arise by dimensionally reducing a twisted theory in 9 dimensions.
-This will be our first example of an twist which is perturbatively trivial on its own, but non-trivial as a one-parameter family, as we discussed at the end of Section \ref{gen_BF_section}.
-That is, we will understand it as a one parameter family of supercharges, degenerating at zero to the holomorphic twist -- the twist by a pure Weyl spinor.
-
-Let us now consider the further reductions to $\SU(4)$, to $\spin(7)$, and to their intersection $\SU(3)$.  We will use the form of the supersymmetric interaction term above to prove the following.
-
-\begin{theorem} \label{8d_holo_twist_thm}
-The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
-If $X_4$ splits into a product $X_3 \times S$ of a Calabi-Yau 3-fold and a flat surface, then this twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times S, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-We begin by describing the twist by a holomorphic supercharge $Q_+$, on a Calabi-Yau 4-fold $X_4$.
-We can do this by by applying Proposition \ref{CS_to_BF_diml_red_prop} to the minimal twist of 9d super Yang-Mills theory.
-More explicitly, the minimal twist of 9d super Yang-Mills theory on $X_4 \times L$ is modelled by mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
-Proposition \ref{CS_to_BF_diml_red_prop} says that if we reduce this mixed Chern-Simons theory in the $L$-direction, we obtain a holomorphic BF theory described by $\map(X_4, T[1]B\gg)$
-
-Note that, unlike in 9d, this theory can be made $\ZZ$-graded, rather than just $\ZZ/2\ZZ$-graded.
-To do so, we consider the action of the 8d R-symmetry group $\CC^\times$, where $S_+$ has weight $+1$ and $S_-$ has weight $-1$, so in particular the holomorphic supercharge $Q_+$ has weight 1.
-We've chosen notation for our component fields that makes it easy to read off the R-symmetry weight of each field: fermions with superscript $+$ have weight $+1$, fermions with superscript $-$ have weight $-1$, the bosonic scalars $\phi_1$ and $\wt \phi_1$ have weight -$2$, and the other bosons have weight 0.
-With respect to this $\ZZ$-grading, the classical BV complex, as an $\SU(4)$-module, has the form
-\[\xymatrix{&\Omega^0(X_4; \gg)_c \ar[r] &\Omega^{0,1}(X_4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^+_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{\psi_{0,1}^{-\vee}} \ar[r] &\Omega^{0,4}(X_4; \gg)_{\phi_1^\vee} \\
-\Omega^0(X_4; \gg)_{\phi_1} \ar[r] &\Omega^{0,1}(X_4; \gg)_{\psi_{0,1}^{-}} \ar[r] &\Omega^{0,2}(X_4; \gg)_{B^{+\vee}_{0,2}} \ar[r] &\Omega^{0,3}(X_4; \gg)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,4}(X_4; \gg)_{c^\vee}&
-}\]
-placed in cohomological degrees $-2, \ldots, 3$.
-
-Now, suppose $X_4$ splits into a product of the form $X_3 \times S$.  If we restrict to $\SU(3)$ representations, our classical BV complex becomes
-
-\resizebox{1.05\textwidth}{!}{$\xymatrix@C-20pt{&\Omega^0(X_3 \times S; \gg)_c \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{A_{0,1}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^+_{1,0}} \ar[r]  &\Omega^{0,3}(X_3 \times S; \gg)_{\chi^{-\vee}} \ar[rd] & \\
-&&\Omega^0(X_3 \times S; \gg\omega)_{\phi_2} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi^{+}_{0,1}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{\psi^{-\vee}_{0,1}} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{\phi_{1}^{\vee}} \\
-\Omega^0(X_3 \times S; \gg)_{\phi_1} \ar[r] \ar[rd] &\Omega^{0,1}(X_3 \times S; \gg)_{\psi_{0,1}^{-}} \ar[r] \ar[rd] &\Omega^{0,2}(X_3 \times S; \gg)_{\psi^{+\vee}_{0,1}} \ar[r] \ar[rd] &\Omega^{0,3}(X_3 \times S; \gg)_{\phi_{2}^\vee} \ar[rd]&& \\
-&\Omega^0(X_3 \times S; \gg\omega)_{\phi_1} \ar[r] &\Omega^{0,1}(X_3 \times S; \gg\omega)_{\psi_{1,0}^{+\vee}} \ar[r] &\Omega^{0,2}(X_3 \times S; \gg\omega)_{A_{0,1}^\vee} \ar[r] &\Omega^{0,3}(X_3 \times S; \gg\omega)_{c^\vee}&}
-$}
-where Dolbeault forms here refer to forms on $X_3$, and $\omega$ denotes the volume form on $S$.
-
-Let $Q = Q^+ + tQ'$ be a generically topological 1-parameter family of supercharges in $S_+$, where $Q'$ is an impure spinor stabilized by $\spin(7)$.
-The supercharges $Q_+$ and $Q'$ automatically commute, so to complete the proof it remains for us to compute the action of the further supercharge $Q'$ on the classical BV complex above.
-To do so we will use the description of the supersymmetry action from Proposition \ref{O8_decomposition_of_susy_prop}.
-So, we'll first observe that several summands of $I^{(1)}(Q')$ and $I^{(2)}(Q')$ are forced to vanish.
-In $I^{(1)}(Q')$, the term pairing $\lambda_+^\vee$ and $A$ cannot be $\spin(7)$-invariant, so must vanish.
-The same applies to the term pairing $\lambda_-^\vee$ and $\phi_1$.
-We are left with, in terms of $\Spin(7)$-fields,
-\begin{align*}
-I^{(1)}(tQ') &= t\langle\lambda_7^\vee, \lambda^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 (A_7^{+\vee} , A_7^{+\vee}),
-\end{align*}
-where we pair $A_7^{+\vee}$ with itself using the restriction of the scalar pairing on $S_+$ to the 7d vector representation \chris{can probably be phrased in terms of the $\spin(7)$-structure somehow}.
-Restricting to representations of $\SU(3)$, this takes the form
-\begin{align*}
-I^{(1)}(tQ') &= t\langle A_{0,1}^\vee, \psi_{0,1}^-\rangle + t\langle \phi_1^\vee, \chi^+\rangle \\
-I^{(2)}(tQ', tQ') &= t^2\langle c^\vee, \phi_1\rangle + t^2 \Lambda(\psi_{0,1}^{+\vee} \wedge \psi_{1,0}^{-\vee}),
-\end{align*}
-plus terms that vanish in the $Q_+$-twist.
-We can then read off the deformation of the $Q_+$-twist by $Q'$: the further differential associated to the $Q'$ supersymmetry turns on an isomorphism between the two copies of $\Omega^{0,\bullet}(X_3, \Omega^\bullet(S;\gg))$ in the $Q_+$-twisted classical BV complex.
-This is exactly the classical field theory described by $\map(X_3 \times S, B\gg)_{\mr{Hod}}$, as required.
-\end{proof}
-
-We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.
-We can understand this twist by a second application of Lemma \ref{CS_diml_red_prop} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.
-This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.
-
-\begin{theorem} \label{8d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 8d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with a pair $L_1 \times L_2$ of oriented 1-manifolds is equivalent to mixed Chern-Simons theory on $X_3 \times (L_1 \times L_2)_{\mr{dR}}$.
-\end{theorem}
-
-\begin{proof}
-The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_prop} twice.
-\end{proof}
-
-\chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}
+The action of the twisted 8d super Yang--Mills theory is given by
+\[S_{Q_t} = S_{\mathrm{BRST}} + S_{\mathrm{anti}} + I^{(1)}(Q_t) + I^{(2)}(Q_t),\]
+where $S_{\mathrm{BRST}}$ and $S_{\mathrm{anti}}$ are given by \eqref{eq:10dBRST} and \eqref{eq:10danti} respectively.
+
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(2, \RR)$ with respect to which $Q_t$ has weight $1$, so the $Q_t$-twisted theory will have a $\ZZ$-grading.
+
+\begin{thm}
+The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, (B\fg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\SU(4)$-equivariant.
+\label{thm:8dHodgetwist}
+\end{thm}
+\begin{proof}
+The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.
+
+Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$.
+Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\psi, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We are left with the action
+\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + t\phi c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
+where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
+Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
+The former is given by (cf.
+the proof of Theorem \ref{thm:8dholomorphictwist})
+\[
+\xymatrix@C=0.5cm{
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
+\Omega^0(\CC^4; \gg)_{\phi} \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
+}
+\]
+which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+\end{proof}
+
+\begin{cor}
+The topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively trivial.
+\label{cor:8dtopologicaltwist}
+\end{cor}
+\begin{proof}
+The topological twist of 8d $\cN=1$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$.
+From Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
+\end{proof}
 

### 2020-01-17 paper.tex
Some corrections to 4d N=2 SUSY
Comment on 4d N=2

--- 2020-01-16 paper.tex
@@
 
-\part{A Catalogue of Twists}
-\chris{We actually used this heading in our previous paper, so maybe a different name?}
+\part{Classification of Twists}
 
@@
 \begin{align*}
-I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
+I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
 &\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
@@
 I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
-I^{(2)}_{\mr{matter}}(Q,Q) &= 0 %\frac 14 \dvol (Q_+,Q_+)(\psi_+,\psi_+)(w_+ \wedge w_+)
+I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
 \end{align*}
@@
 
-\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.}
+\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.
+Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.
+The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
 \end{proof}

### 2020-01-17 paper.tex
N=1 table

@@
 The fields of the pure Yang-Mills part decomposes as:
-\begin{align*}
-c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
-A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_- & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
-\lambda_+ & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) \\
-\phi & \mapsto \phi \in \Omega^0 (\CC^2 ; R^*) \\
-\Bar{\phi} & \mapsto \gamma_0 \in \Omega^{2,2}(\CC^2 ; R) \\
-\psi_+ & \mapsto \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) \\
-\psi_- & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R)
-\end{align*}
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
+A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
+\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
+\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
+\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
+\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
+\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
+\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
+\end{array}
+\]
+\brian{Is it necessary to put in the antifields?} 
 and their antifields:
@@
 \begin{align*}
-S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
-S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
-&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
+S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
+S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
+&\qquad + 2 (([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
 S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
 &\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
-I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
-I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\lambda_0^*)^2.
+I^{(1)}_{\mr{gauge}} &=  \int  \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
+I^{(1)}_{\mr{matter}} &=  \int  \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int  (\lambda_0^*)^2.
 \end{align*}

### 2020-01-17 paper.tex
Added some comments

@@
 \begin{array}{ccccl}
-\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
+\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
 & & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
@@
 \]
-Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
-This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
+Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
 
@@
 We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
-In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
-\[
-X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
+In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
+\[
+X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
 \]
@@
 Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.
-The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
+The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.
+
+I'll try to write this as Pavel did in 8d, so write as a proposition the action of $Q_{\mr{hol}} + tQ'$, and observe that it induces this deformation.}
 \end{proof}
@@
 \end{prop}
-%
-%The matter sector of the theory is labeled by the BRST fields:
-%\begin{itemize}
-%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
-%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
-%\end{itemize} 
-%which together define the (abelian) local Lie algebra
-%\[
-%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
-%\]
+
+\chris{todo: $(1,0)$, $(2,0)$, $(1,1)$ as above, with $U = T^*\gg$.
+Then $(2,1)$ and generic $(2,2)$ arise as deformations of $(1,1)$ by dimensional reduction from 5d.
+Finally the special $(2,2)$ arises by dimensional reduction from the 5d B-twist.}
 

### 2020-01-17 paper.tex
finall N=1

--- 2020-01-17 paper.tex
@@
 
+%\[
+%\{F(A, B), G(A, B)\} = \frac{\partial}{\partial A} F(A, B) \frac{\partial}{\partial B}  G(A,B) + \frac{\partial}{\partial B} F(A, B) \frac{\partial}{\partial A}  G(A,B)
+%\]
+
 Now, we will include interactions in the BV picture.
@@
 
-\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(Z)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
 
@@
 
-\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A = \eend(W_+)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A = \eend(Z)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
 \end{itemize}
@@
 
+The R-symmetry group is $U(1)$ which acts by $\pm 1$ on $\lambda_{\pm}$ and $\mp 1$ on $\psi_{\pm}$.
+
+\subsubsection{Holomorphic twist}
+
 There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
@@
 Such supercharges are minimal (i.e. have two dimensional image).  
-They are stabilized by ${\rm U}(2)$; indeed a minimal square-zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
-The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.
-
-We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
-The fields of the pure Yang-Mills part decomposes as:
+The twisted theory by such a supercharge can always be made $\ZZ$-graded where the twisting datum is given by the identity map $\alpha = {\rm id} : U(1) \to U(1)$. 
+Such a $Q$ is preserved under a twisting homomorphism
+\[
+\MU(2) \to {\rm Spin}(4) \times U(1) 
+\]
+where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant.
+
+We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
+The fields decompose as:
 \[
@@
 S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
-&\qquad + 2 (([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
+&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )   \bigg) \\
 S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
@@
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\MU(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
 \end{thm}

### 2020-01-17 paper.tex
Added some comments

--- 2020-01-17 paper.tex
@@
 Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.
-The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.
-
-I'll try to write this as Pavel did in 8d, so write as a proposition the action of $Q_{\mr{hol}} + tQ'$, and observe that it induces this deformation.}
+The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
 \end{proof}
@@
 \vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-\begin{prop}
-Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
-&\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
-&\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
-\end{align*}
-and
-\begin{align*}
-I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
-&\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
-&\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
-\end{align*}
-where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
-\end{prop}
+\paragraph{Twisting data:}
+The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.
+We have the following classes.
+\chris{some comments claiming we'll discuss things above, to be added.
+Also this is to revisit after writing the below.}
+\begin{itemize}
+ \item Rank $(1,0)$ (and $(0,1)$) supercharges.
+Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.
+They are compatible with $\SU(2)_- \sub \Spin(4;\RR)$, which can be promoted to a twisting homomorphism from the group $\mr U(2)$ as we say in the 4d $\mc N=1$ section above.
+ \item Rank $(2,0)$ (and $(0,2)$) supercharges.
+Such supercharges automatically square to zero, and are topological: indeed they sit inside an $\mc N=2$ subalgebra.
+They are compatible with any of three possible twisting homomorphisms:
+ \begin{enumerate}
+  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
+  \item The Kapustin-Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
+  \item The Vafa-Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
+ \end{enumerate}
+ \item Rank $(1,1)$ supercharges.
+Such supercharges have three invariant directions, and also sit inside an $\mc N=2$ subalgebra.
+Twists by such supercharges are compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$, but are only $\ZZ/2\ZZ$-graded, as we discussed in the $\mc N=2$ section above.
+ \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, and compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$.
+ \item Rank $(2,2)$ square-zero supercharges are topological, and split into two classes.
+Generically, such supercharges correspond to perturbatively trivial twisted theories, and are only compatible with $\Spin(2;\RR) \times \Spin(2;\RR)$.
+There is a special point of this type which is compatible with Kapustin-Witten twisting homomorphism.
+ \item There is also a special rank $(2,2)$ point (the \emph{B-twisting supercharge}) arising by dimensional reduction from the 5d $\mc N=2$ rank 4 supercharge, which is also compatible with the Kapustin-Witten twisting homomorphism.
+\end{itemize}
+
+We can study all the possible twists using what we say in the $\mc N=2$ subsection, as well as by dimensional reduction from 5d $\mc N=2$ super Yang-Mills theory.
+
+\begin{theorem}
+\chris{holomorphic deforming to rank $(2,0)$, proven above} $\mr{Map}(\CC^2_{\mr{Dol}}, B\gg_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{theorem}
+\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
+\end{theorem}
+
+\begin{theorem}
+\chris{Special rank $(2,2)$ deforming to generic rank $(2,2)$, by dimensional reduction from 5d $2_A$ deforming to $2_B$} $\mr{Map}(\RR^4_{\mr{dR}}, B\gg_{\mr{Hod}})$.
+\end{theorem}
+
+% \vspace{-10pt}
+% \paragraph{Supersymmetry action:} 
+% \begin{prop}
+% Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
+% \begin{align*}
+% I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
+% &\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
+% &\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
+% \end{align*}
+% and
+% \begin{align*}
+% I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
+% &\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
+% &\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
+% \end{align*}
+% where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
+% \end{prop}
 

### 2020-01-18 paper.tex
10d - 7d updates

@@
 \newcommand{\matter}{\mathrm{matter}}
+\newcommand{\ML}{\mathrm{ML}}
 \newcommand{\MU}{\mathrm{MU}}
@@
 where $\U(n)\rightarrow \U(1)$ is the determinant map and $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$.
+We denote by $\det^{1/2}\colon \MU(n)\rightarrow \U(1)$ the projection on the second factor; this may be thought of as a square root of the determinant representation of $\U(n)$.
 The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
@@
 
+\begin{cor}
+Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg).\]
+
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, T^*[d] B\fg).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
+\label{cor:BFholomorphicreduction}
+\end{cor}
+
+\begin{cor}
+Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
+
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
+\label{cor:Hodgeholomorphicreduction}
+\end{cor}
+
 \section{Supersymmetry} \label{sec: susy}
@@
 
+We have an embedding $\U(n)\subset \SO(2n, \RR)$ which lifts to an embedding $\MU(n)\subset \Spin(2n, \RR)$.
+If we denote by $L$ the standard $n$-dimensional representation of $\U(n)$, then the semi-spin representations of $\Spin(2n, \RR)$ restrict to $\MU(n)$ as
+\[S_+\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{even}} L,\qquad S_-\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{odd}} L.\]
+
 \begin{definition}
@@
 We will now define the fundamental notion of a supersymmetric field theory.
-Consider a spacetime manifold $M$ which is an affine space over $V_\RR$.
-Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
+Consider a spacetime manifold $M=V_\RR$.
+Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts by affine transformations on $M$.
 
@@
 \label{dfn: super}
-A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
+A classical field theory $(E, S, \omega)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
 \end{definition}
@@
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with a nonvanishing complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
 Such a supercharge is stabilized by $G=\SU(5)\subset \Spin(10, \CC)$.
@@
 \subsubsection{Holomorphic twist}
-
 \label{sect:10dholomorphictwist}
 
-We will now fix a Calabi--Yau structure giving rise to a square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
-Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
-We denote the real volume form on $\RR^{10}$ by
+Let $Q\in\Sigma$ be a square-zero supercharge.
+The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$.
+Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$.
+Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$.
+In other words, $L$ defines a (linear) complex structure on $V_\RR$.
+Moreover, we may canonically identify $\sigma(L)\cong L^*$.
+
+Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
+\[\Sigma = \det(L)^{1/2} \oplus \wedge^2 L^*\otimes \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2}.\]
+$Q\in\Sigma$ lies in the first summand, so the choice of $Q$ is equivalent to the choice of a (linear) K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
+The square of this half-density defines a Calabi--Yau structure on $M$.
+
+We will now rewrite the fields and the action in terms of the Calabi--Yau structure.
+Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(M)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(M)\rightarrow \Omega^{p, q}(M)$ the dual Lefschetz operator.
+We denote the real volume form on $M$ by
 \[\dvol = \frac{\omega^5}{5!}.\]
@@
 The vector representation decomposes as
-\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5),\]
+\[\Omega^1(M)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 1}(M),\]
 the semi-spin representation $S_+$ decomposes as
-\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
+\[\Omega^0(M; S_+)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 2}(M)\oplus \Omega^0(M)\]
 and the semi-spin representation $S_-$ decomposes as
-\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
+\[\Omega^0(M; S_-)\cong \Omega^{0, 1}(M)\oplus \Omega^{2, 0}(M)\oplus \Omega^0(M).\]
 Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
@@
 \begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
-\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
-\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
+\item Fermions $\psi\in\Omega^{1, 0}(M; \Pi\gg)$, $B\in\Omega^{0, 2}(M; \Pi\gg)$, $\chi\in\Omega^0(M; \Pi\gg)$.
+\item A ghost field $c\in\Omega^0(M; \Pi\gg)$.
 \end{itemize}
@@
 \begin{thm}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ with the space of fields $\map(\CC^5, B\gg)$.
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$.
 Moreover, the equivalence is $\SU(5)$-equivariant.
@@
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
-A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with a complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
 Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(9, \CC)$.
@@
 \subsubsection{Minimal twist}
-
-Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
+\label{sect:9dminimaltwist}
+
+Let $Q\in\Sigma$ be a square-zero supercharge.
+Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp\subset V$.
+Its orthogonal complement $L$ is maximal isotropic and $L^{\perp}/L$ is one-dimensional.
+Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$.
+Moreover, $N = L^{\perp}\cap \sigma(L^{\perp})\subset V$ is a $\sigma$-stable one-dimensional subspace, we let $N_\RR$ be the $\sigma$-invariants of $N$.
+Therefore, we get a decomposition
+\[V = L\oplus \sigma(L)\oplus N,\]
+where $L^{\perp} = L\oplus N$.
+
+Under the embedding $\ML(L)\subset \Spin(V)$ the spin representation $\Sigma=S$ decomposes as
+\[\Sigma = \wedge^\bullet L\otimes \det(L)^{-1/2}\]
+and the supercharge $Q$ lies in the one-dimensional subspace $\det(L)^{1/2}\subset \Sigma$.
+Therefore, the choice of $Q$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
+
+It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations.
+
+Suppose $L$ is a complex vector space equipped with a K\"ahler structure and a complex half-density.
+Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
+Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
+Let $V_\RR = L\times N$ (a 10-dimensional real vector space).
+By the results of Section \ref{sect:10dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density.
+
+The dimensional reduction of 10d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(N_\RR)$.
+We consider a twisting homomorphism $\phi\colon \SU(L)\times \Spin(N_\RR)\rightarrow G_R=\Spin(N_\RR)$ given by the projection onto the second factor under which $Q$ is preserved.
 
 \begin{thm}
-\label{9d_twist_thm}
-The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
+The twist of $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(L)\times \Spin(N_\RR)$-equivariant.
+\label{thm:10dCSreduction}
+\end{thm}
+\begin{proof}
+By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
+Moreover, the equivalence is $\SU(L)\times \SU(N)$-equivariant.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, B\fg)$ and this isomorphism is $\SU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+
+Therefore, we just need to establish that the $\Spin(N_\RR)$-action on the twisted $(5+\dim(L))$-dimensional super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(N_\RR)$-action on the generalized Chern--Simons theory.
+The $\Spin(N_\RR)$-action on the fields of $(5+\dim(L))$-dimensional super Yang--Mills is obtained via the homomorphism
+\[\Spin(N_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(N_\RR)\times \Spin(N_\RR)\hookrightarrow \Spin(N_\RR\oplus N_\RR),\]
+where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(N_\RR)$ and the twisting homomorphism, i.e.
+the identity map, to the $R$-symmetry group $G_R=\Spin(N_\RR)$.
+The $\SO(N_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
+\[\SO(N_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(N)\longrightarrow \SO(N_\RR\oplus N_\RR)\]
+
+The claim then follows from the commutativity of the diagram
+\[
+\xymatrix@C=2cm{
+\SO(N_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(N_\RR)\times \SO(N_\RR) \ar[d] \\
+\SU(N) \ar[r] & \SO(N_\RR\oplus N_\RR).
+}
+\]
+\end{proof}
+
+We will now concentrate on the 9-dimensional case.
+
+\begin{thm}
+The minimal twist of 9d $\mc N=1$ super Yang--Mills on $M=\CC^4\times \RR$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
 Moreover, the equivalence is $\SU(4)$-equivariant.
+\label{thm:9dminimaltwist}
 \end{thm}
 \begin{proof}
-By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
-In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
-
-From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
-By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
+The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^4$.
 \end{proof}
@@
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
@@
 These are holomorphic.
-Moreover, we may choose a homomorphism $\alpha\colon \U(1)\rightarrow \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
+Moreover, we have an isomorphism $\alpha\colon \U(1)\xrightarrow{\sim} \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
 Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$.
-We have a twisting homomorphism $\phi\colon \U(4)\xrightarrow{\det} \U(1)\rightarrow G_R=\Spin(2, \RR)$, so the twisted theory carries an action of $\U(4)$.
+We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\cong G_R$, so the twisted theory carries an action of $\MU(4)$.
 
@@
 \item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero.
-These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2$-graded theory.
+These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
 We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$.
@@
 
-Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$. In this case the theory carries a $\U(4)$-action and a $\ZZ$-grading. Choose a K\"ahler structure on $\RR^8\cong \CC^4$.
+Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$.
+As in Section \ref{sect:10dholomorphictwist}, the data of such $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
+
+We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \RR)$ under which $Q$ becomes scalar.
+Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action.
+In fact, this action will factor through $\U(4)$ by a direct observation.
 
@@
 \begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^4; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(\CC^4; \gg)$.
-\item Scalar fields $\phi\in\Omega^{4,0}(\CC^4; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(\CC^4; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(\CC^4; \gg)[-1]$, $B\in\Omega^{0, 2}(\CC^4; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(\CC^4; \gg)[-1]$, $\psi\in\Omega^{1, 0}(\CC^4; \gg)[1]$ and $C\in\Omega^{3, 0}(\CC^4; \gg)[1]$.
-
-\item A ghost field $c\in \Omega^0(\CC^4; \gg)[1]$.
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
+\item Scalar fields $\phi\in\Omega^{4,0}(M; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(M; \gg)[-2]$.
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\psi\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
+
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
 \end{itemize}
@@
 \begin{thm}
-The holomorphic twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory on $\CC^4$ with the space of fields $\map(\CC^4, T^*[3] B\fg)$.
+The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$.
 Moreover, the equivalence is $\U(4)$-equivariant.
@@
 
-The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{9d_twist_thm}).
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
-Indeed, the equivalence given by Theorem \ref{9d_twist_thm} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
 \[
@@
 
-\subsubsection{Partially topological twist}
-
-Next we discuss the case of the partially topological twist with 5 invariant directions.
-Recall that it is merely $\ZZ/2$-graded.
-Decompose $M=\RR^8\cong\CC^3\times \RR^2$ and choose a Calabi--Yau structure on $\CC^3$.
-Using the twisting homomorphism $\SU(3)\times \Spin(2, \RR)\rightarrow G_R$ the twisted theory carries an action of $\SU(3)\times \Spin(2, \RR)$ acting on the individual factors of $\CC^3\times \RR^2$.
-
-\begin{thm}
-The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
-Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
-\label{thm:8dpartiallytopologicaltwist}
-\end{thm}
-\begin{proof}
-Denote $V_\RR=\RR^2$, so that we consider 8d $\cN=1$ super Yang--Mills on $\CC^3\times V_\RR$.
-By definition it is obtained as a dimensional reduction of the 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ along the projection $\Re\colon V\rightarrow V_\RR$, where $V=V_\RR\otimes_\RR \CC$.
-
-Let $Q = (Q_+, Q_-)$ be the square-zero supercharge corresponding to the partially topological twist.
-Since we have $(Q_\pm, Q_\pm)_{S_\pm} = 0$, the element $Q_+ + Q_-$ is a square-zero supercharge in the 10-dimensional supersymmetry algebra.
-By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
-Moreover, the equivalence is $\SU(3)\times \SU(V)$-equivariant.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $\CC^3\times V$ along $V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times V_\RR, B\fg)$ and this isomorphism is $\SU(3)\times \SO(V_\RR)$-equivariant, where $\SO(V_\RR)$ acts on $V$ via the homomorphism \eqref{eq:SOtoSU}.
-
-Therefore, we just need to establish that the $\Spin(V_\RR)$-action on the twisted 8d $\cN=1$ super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(V_\RR)$-action on the generalized Chern--Simons theory.
-The $\Spin(V_\RR)$-action on the fields on 8d $\cN=1$ super Yang--Mills is obtained via the homomorphism
-\[\Spin(V_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(V_\RR)\times \Spin(V_\RR)\hookrightarrow \Spin(V_\RR\oplus V_\RR),\]
-where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(V_\RR)$ and the twisting homomorphism, i.e.
-the identity map, to the $R$-symmetry group $G_R=\Spin(V_\RR)$.
-The $\SO(V_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
-\[\SO(V_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(V)\longrightarrow \SO(V_\RR\oplus V_\RR)\]
-
-The claim then follows from the commutativity of the diagram
-\[
-\xymatrix@C=2cm{
-\SO(V_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(V_\RR)\times \SO(V_\RR) \ar[d] \\
-\SU(V) \ar[r] & \SO(V_\RR\oplus V_\RR).
-}
-\]
-\end{proof}
-
 \subsubsection{Topological twist}
 
-Finally we discuss the case of the topological twist.
+Next we discuss the case of the topological twist.
 We are going to prove that it is perturbatively trivial.
@@
 Consider a family of square-zero supercharges
-\[Q_t = \alpha + t\beta\in\Sigma_+\]
+\begin{equation}
+Q_t = \alpha + t\beta\in\Sigma_+
+\label{eq:8dHodgefamily}
+\end{equation}
 for $t\in\CC$. We have
@@
 \begin{prop}
-The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the 8d $\cN=1$ super Yang--Mills fields are
+The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
 \begin{align*}
@@
 \begin{thm}
-The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, (B\fg)_{\mr{Hod}})$.
+The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, B\fg_{\mr{Hod}})$.
 Moreover, this equivalence is $\SU(4)$-equivariant.
@@
 The topological twist of 8d $\cN=1$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$.
-From Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
+By Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
+\end{proof}
+
+\subsubsection{Partially topological twist}
+
+Finally we discuss the case of the partially topological supercharge $Q\in\Sigma$.
+We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.
+
+\begin{thm}
+The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
+\label{thm:8dpartiallytopologicaltwist}
+\end{thm}
+\begin{proof}
+The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^3$.
 \end{proof}
@@
 
+The 7-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 8-dimensional spin representation of $\Spin(7, \CC)$ and $W$ is a complex symplectic vector space.
+The spin representation carries a nondegenerate symmetric bilinear pairing $S\otimes S\rightarrow \CC$.
+There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC^2$.
+
 \subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
-The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
-It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
-
-In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
- \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
- \item Rank 2 square-zero spinors, i.e.
-square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
-Such supercharges have a 5-dimensional image in $\CC^7$.
-Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
-
-\begin{theorem} \label{7d_holo_twist_thm}
-The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.
-That is, by applying Proposition \ref{CS_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
-\end{proof}
-
-\begin{theorem} \label{7d_rank2_twist_thm}
-The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
-\chris{actually I need to think about the twisting homomorphism here.}
-\end{theorem}
-
-\begin{proof}
-Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_diml_red_prop}.
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
+
+The 7d $\cN=1$ supersymmetry algebra admits three twists:
+\begin{itemize}
+\item Rank 1 supercharges $Q=\alpha\otimes w\in S\otimes W$, where $(\alpha, \alpha)_S = 0$.
+These are minimal, i.e.
+the number of invariant directions is 4.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
+We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \RR)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.
+
+\item Rank 1 supercharges $Q = \alpha \otimes w \in S \otimes W$, where $(\alpha, \alpha)_S\neq 0$.
+These are topological and stabilized by $G_2\subset \Spin(7, \CC)$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
+
+\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
+\end{itemize}
+
+\subsubsection{Minimal twist}
+
+Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp$, so that its orthogonal complement $L\subset V$ is a 3-dimensional isotropic subspace.
+As in Section \ref{sect:9dminimaltwist}, the data of a partially topological supercharge is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a half-density.
+
+We have $Q=\alpha\otimes w\in S\otimes W$ and denote by $\alpha\colon \U(1)\hookrightarrow G_R=\Spin(3, \RR)$ the subgroup under which $w$ has weight $1$.
+We consider the twisting homomorphism given by the composite
+\[\phi\colon \MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
+As before, the $\MU(3)$-action on the theory factors through a $\U(3)$-action.
+
+\begin{thm}
+The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\RR^7$ is perturbatively equivalent to the generalized BF theory on $\CC^3\times \RR$ with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
+Moreover, the equivalence is $\U(3)$-equivariant.
+\label{thm:7dminimaltwist}
+\end{thm}
+\begin{proof}
+The minimal supercharge $Q=\alpha\otimes w$ may be obtained by dimensional reduction of the holomorphic supercharge in the 8-dimensional supersymmetry algebra.
+Therefore, the minimal twist of 7d $\cN=1$ super Yang--Mills on $\CC^3\times \RR$ is obtained by dimensional reduction from the holomorphic twist of 8d $\cN=1$ super Yang--Mills on $\CC^4$.
+The claim then follows from Theorem \ref{thm:8dholomorphictwist} and Corollary \ref{cor:BFholomorphicreduction}.
+\end{proof}
+
+\subsubsection{Topological twist}
+
+Next we study the topological twist.
+Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L\times \RR$.
+Under $\SU(L)\subset \Spin(V_\RR)$ the spin representation decomposes as
+\[S\cong \wedge^\bullet L.\]
+In particular, it contains two trivial summands: $\CC\alpha$ in the lowest degree and $\CC\beta$ in the top degree.
+
+Consider a family of square-zero supercharges
+\begin{equation}
+Q_t = (\alpha + t\beta)\otimes w
+\label{eq:7dHodgefamily}
+\end{equation}
+for some nonzero $w\in W$. We have $(\alpha + t\beta, \alpha + t\beta)=t$, so at $t=0$ we have a minimal supercharge and at $t\neq 0$ we have a topological supercharge.
+
+\begin{thm}
+The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$.
+Moreover, this equivalence is $\SU(3)$-equivariant.
+\end{thm}
+\begin{proof}
+The family of square-zero supercharges \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ \eqref{eq:8dHodgefamily} in 8 dimensions.
+The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$.
+The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
+\end{proof}
+
+\begin{cor}
+The topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively trivial.
+\end{cor}
+
+\subsubsection{Partially topological twist}
+
+Finally, we discuss the case of a partially topological twist.
+We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor.
+
+\begin{thm}
+The partially topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR^3_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(2)\times \Spin(3, \RR)$-equivariant.
+\label{thm:7dpartiallytopologicaltwist}
+\end{thm}
+\begin{proof}
+The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^2$.
 \end{proof}

### 2020-01-20 paper.tex
6d N=(1, 0)

@@
 \begin{definition}
-Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1.
+Let $Q\in\Sigma$ be a square-zero supercharge.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-grading on mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
 
-Given a homomorphism $\alpha$, we consider the new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
+Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
 The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$.
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills theory}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills}
 
@@
 
-The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
+This theory admits a unique twist:
 \begin{itemize}
@@
 Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
-Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
-\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
+Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \rho + B + \chi\in S_+$ is given by
+\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \rho + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \rho))\in S_-.\]
 
@@
 \item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Fermions $\psi\in\Omega^{1, 0}(M; \Pi\gg)$, $B\in\Omega^{0, 2}(M; \Pi\gg)$, $\chi\in\Omega^0(M; \Pi\gg)$.
-\item A ghost field $c\in\Omega^0(M; \Pi\gg)$.
-\end{itemize}
-We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
+\item Fermions $\rho\in\Omega^{1, 0}(M; \Pi\gg)$, $B\in\Omega^{0, 2}(M; \Pi\gg)$, $\chi\in\Omega^0(M; \Pi\gg)$.
+\item A ghost field $c\in\Omega^0(M; \gg)[1]$.
+\end{itemize}
+We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \rho^*, B^*, \chi^*, c^*$.
 
@@
 \begin{align}
-S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
-S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
-I^{(1)} &= \int \dvol\left(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
+S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\rho) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
+S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
+I^{(1)} &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
 I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
@@
 S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
+&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
 &+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
@@
 
-Next, we have a term $\int \dvol \psi\wedge A_{1, 0}^*$ in the action, i.e.
-$(\psi, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
-The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
+Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e.
+$(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+The above theory then becomes perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.
+
+This theory admits a unique twist:
 \begin{itemize}
@@
 \begin{proof}
+Any square-zero supercharge in the 9-dimensional supersymmetry algebra is square-zero in the 10-dimensional supersymmetry algebra.
 The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^4$.
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric.
 It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
-The 8d $\cN=1$ supersymmetry algebra admits three twists:
+This theory admits three twists:
 \begin{itemize}
@@
 \item Scalar fields $\phi\in\Omega^{4,0}(M; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\psi\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
-
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
-\psi&\rightsquigarrow \psi, \wt\chi \\
+\rho&\rightsquigarrow \rho, \wt\chi \\
 B&\rightsquigarrow B, C.
@@
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
-Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
 \[
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\psi, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \psi^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
 I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
@@
 Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
-We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\psi, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
 We are left with the action
@@
 
-Finally we discuss the case of the partially topological supercharge $Q\in\Sigma$.
+Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$.
 We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.
@@
 \begin{proof}
+Since $Q_+$ and $Q_-$ satisfy $(Q_\pm, Q_\pm)_{S_\pm} = 0$, they lift to a square-zero supercharge in the 10-dimensional supersymmetry algebra.
 The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^3$.
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric.
 It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
 
-The 7d $\cN=1$ supersymmetry algebra admits three twists:
+This theory admits three twists:
 \begin{itemize}
@@
 \begin{proof}
-The family of square-zero supercharges \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ \eqref{eq:8dHodgefamily} in 8 dimensions.
+The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions.
 The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$.
@@
 \begin{proof}
+Any partially topological supercharge in the 7-dimensional supersymmetry algebra lifts to a square-zero supercharge in the 10-dimensional supersymmetry algebra.
 The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^2$.
@@
 \section{Dimension 6}
-In dimension 6 there are two possible supersymmetry groups by which we can act.  
-There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry, consisting of a pure gauge theory coupled to matter living in a symplectic representation $U$.  
-If $U \iso T^*\gg$, then the $(1,0)$ supersymmetry algebra action can be enhanced to an $\mc N=(1,1)$ supersymmetry algebra action.  
-This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills from $\RR^{10}$ down to $\RR^6$.
-
-\subsection{\texorpdfstring{$\mc N = (1,0)$}{N=(1,0)} Super Yang-Mills Theory with Matter} \label{6d_10_section}
-
-The general theory of $\mc N = (1,0)$ coupled to matter has been exhibited in Section \ref{sect:mattermultipletSUSY}.
+
+The 6-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 4-dimensional semi-spin representations of $\Spin(6, \CC)\cong \SL(4, \CC)$ and $W_+, W_-$ are complex symplectic vector spaces.
+We have isomorphisms $S_+\cong S_-^*$.
+
+There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(1, 1)$ supersymmetry, which we consider separately.
+
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}
+
+The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $U$ a complex symplectic $\fg$-representation.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric.
+We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure.
+The $R$-symmetry group depends on the type of the representation $U$:
+\begin{itemize}
+\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.
+
+\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
+\end{itemize}
+
+This theory admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory.
+If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading.
+Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$.
+We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(3)$-action.
+\end{itemize}
 
 \vspace{-10pt}
-\paragraph{Fields:}
-The untwisted fields are given by:
-\begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^6;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^6 ; S_+ \otimes W_+ \otimes \fg)$. 
-\item $U$-valued scalars: $\phi \in C^\infty(\RR^6 ; W_+ \otimes U)$;
-\item $U$-valued fermions: $\psi \in C^\infty(\RR^6 ; S_- \otimes U)$ .
-\end{itemize}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item A gauge field $A \in \Omega^1(M;\fg)$.
+\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
+\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
+\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+Consider a nonzero $Q\in S_+\otimes W_+$.
+Since $\wedge^2(S_+)\cong V$, the square-zero condition is equivalent to the condition that $Q$ has rank 1, i.e.
+$Q=q_+\otimes w_1\in S_+\otimes W_+$.
+We will also fix $w_2\in W_+$ such that $(w_1, w_2) = 1$.
+
+As in Section \ref{sect:10dholomorphictwist}, the data of $q_+$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
+
+Under the embedding $\MU(L)\subset \Spin(V_\RR)$, the semi-spin representations $S_+, S_-$ decompose as
+\[S_+ = \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2},\qquad S_- = \det(L)^{-1/2} \oplus L^*\otimes \det(L)^{1/2},\]
+where $q_+\in S_+$ lies in the first summand.
+
+We fix an embedding $\U(1)\subset \SU(2)$ under which $w_1\in W_+$ has weight $1$. Under the composite
+\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
+we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.
+
+We will now rewrite the fields using the twisting homomorphism $\phi$ from $\MU(3)$, where we denote by $K$ the canonical bundle of $L=\CC^3$.
 
 \vspace{-10pt}
-\paragraph{Twisting data:}
-Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
-The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.
-Without loss of generality we will twist with respect to a supercharge of the form $Q = q_+ \otimes w_1 \in S_+ \otimes W_+$.
-
-We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
+\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
+\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
+\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{3, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 3}(M)$ the antiholomorphic volume form.
+We denote the real volume form on $M$ by
+\[\dvol = \frac{\omega^3}{6} = \Omega\wedge \ol{\Omega}.\]
+
+Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
 \begin{align*}
-c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
-A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
-\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
-\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
-\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
+S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
+&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
+S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
+&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
+&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
+I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
+I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
+I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
 \end{align*}
-\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
-and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
-In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
-\begin{align*}
-S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
-&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
-S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu' \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
-&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
-I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
-I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
-\end{align*}
-Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.
 
 \begin{thm}
-The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
-That is, the theory with the space of fields $\mr{Map}(\CC^3, U\ham \gg)$, where $U\ham \gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
+Moreover, the equivalence is $\MU(3)$-equivariant.
 \label{thm:6dholomorphictwist}
 \end{thm}
-
 \begin{proof}
 The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.
-First, we integrate out the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-We then observe that the action includes the terms $\int \dvol  (B_{1,0}, A_{1,0}^*)$ and  $\int \dvol (\nu', \nu^*)$.
-In other words, the pairs $(B_{1,0}, A_{1,0})$ and $(\nu, \nu')$ form BRST doublets, which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
-The twisted theory is therefore perturbatively equivalent to the theory with BV action
+First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.
+In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
+The twisted theory is therefore perturbatively equivalent to the theory with the BV action
 \begin{align*}
- S_{\mr{BV}} &= \int \Omega \bigg( (\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})  + (\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \frac 12 (F_{0,2} \wedge \lambda_{0,2}^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0 \wedge \psi_{0,1}^*) +  \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* \\
-  &\qquad  + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* + [\lambda_{0}, A_0]\wedge \lambda_{0}^* + \frac{1}{2}[A_0, A_0]A_0^* +  [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^*  \bigg).
+ S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
+ &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
 \end{align*}
-This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
-\end{proof}
-
-\begin{remark} \label{6d_BF_remark}
-This theory is in general only $\ZZ/2\ZZ$-graded.
-If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to complete this and say it more carefully}.
-\end{remark}
+Up to rescaling of the antifields, this is the action functional of the required theory.
+\end{proof}
+
+If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$.
+We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
+We may also use a different twisting homomorphism
+\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
+
+With these modifications the BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
+\item Gauge fermions $\chi\in\Omega^0(M; \fg)[-1]$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)[1]$, $B\in\Omega^{0, 2}(M; \fg)[-1]$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)[1]$.
+\item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
+\item Matter fermions $\psi\in \Omega^{1, 0}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+Note that the $\MU(3)$-action on the fields factors through $\U(3)$ since the square roots of $K$ have canceled out.
+By comparing the degrees and the transformation rules of the fields in Theorem \ref{thm:6dholomorphictwist} we obtain the following statement.
+
+\begin{thm}
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (R/\fg))$.
+Moreover, the equivalence is $\U(3)$-equivariant.
+\label{thm:6dholomorphictwistgraded}
+\end{thm}
+
+\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}
 

### 2020-01-20 paper.tex
Removed my Hodge family definition, and merged into Pavel's

@@
 \end{remark}
-
-Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
-These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
-In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.
-So at $t=0$ we will recover generalized BF theory.
-
-We will refer to these families as Hodge deformations of generalized BF theory.
-The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
-
-\begin{definition} \label{Hodge_family_def}
-Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.
-The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so
-\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
-but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
-\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
-\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
-induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
-\end{definition}
-
-Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
-\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]
 
@@
 \subsubsection{Generalized Hodge theory}
-
-We will also consider deformations of the generalized BF theory to a perturbatively trivial theory.
+Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
+These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
 By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.
@@
 The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.
+The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
 
@@
 
-\begin{definition}
+\begin{definition} \label{Hodge_family_def}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.

### 2020-01-20 paper.tex
Intro brainstorm

@@
 \section*{Introduction}
+
+\chris{Possible topics for the introduction
+\begin{enumerate}
+ \item  Context and literature on twists, including in the BV formalism.
+There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
+Also at least a remark on the perspective in terms of coupling to twisted sugra.
+ \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
+ \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
+ \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
+ \item  Table of the twists, and commentary on where each has appeared before in the literature.
+ \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
+ \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
+ \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
+ \item  Summary of the sections of the paper.
+\end{enumerate}}
+
 \begin{table}[htbp]
@@
 \end{figure}
+
+\subsection*{Acknowledgements}
 
@@
 
-If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.
+If $\fg$ carries a nondegenerate invariant symmetric pairing of degree $d$, so does $\fg_{\Hod}$.
 
@@
 \begin{theorem}
-\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
+\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
+However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
 \end{theorem}

### 2020-01-20 paper.tex
merge

--- 2020-01-20 paper.tex
@@
 \newcommand{\matter}{\mathrm{matter}}
-\newcommand{\ML}{\mathrm{ML}}
 \newcommand{\MU}{\mathrm{MU}}
@@
 where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}
+\end{example}=
 
@@
 where $\U(n)\rightarrow \U(1)$ is the determinant map and $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$.
-We denote by $\det^{1/2}\colon \MU(n)\rightarrow \U(1)$ the projection on the second factor; this may be thought of as a square root of the determinant representation of $\U(n)$.
 The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.
@@
 
+\begin{eg}
+There is a special case of this  of the ``holomorphic symplectic boson". 
+\brian{include this?}
+\end{eg}
 \subsubsection{Generalized Hodge theory}
@@
 
-\begin{cor}
-Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
-\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg).\]
-
-Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, T^*[d] B\fg).\]
-The isomorphism is moreover $\SO(V_\RR)$-equivariant.
-\label{cor:BFholomorphicreduction}
-\end{cor}
-
-\begin{cor}
-Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
-\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
-
-Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Hodge theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
-The isomorphism is moreover $\SO(V_\RR)$-equivariant.
-\label{cor:Hodgeholomorphicreduction}
-\end{cor}
-
 \section{Supersymmetry} \label{sec: susy}
@@
 
-We have an embedding $\U(n)\subset \SO(2n, \RR)$ which lifts to an embedding $\MU(n)\subset \Spin(2n, \RR)$.
-If we denote by $L$ the standard $n$-dimensional representation of $\U(n)$, then the semi-spin representations of $\Spin(2n, \RR)$ restrict to $\MU(n)$ as
-\[S_+\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{even}} L,\qquad S_-\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{odd}} L.\]
-
 \begin{definition}
@@
 We will now define the fundamental notion of a supersymmetric field theory.
-Consider a spacetime manifold $M=V_\RR$.
-Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts by affine transformations on $M$.
+Consider a spacetime manifold $M$ which is an affine space over $V_\RR$.
+Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts in the obvious way on $M$.
 
@@
 \label{dfn: super}
-A classical field theory $(E, S, \omega)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
+A classical field theory $(E, Q, \omega, I)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant elliptic $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
 \end{definition}
@@
 \begin{definition}
-Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-grading on mod 2 on $E$ coincides with the fermionic grading.
+Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1.
 \end{definition}
 
-Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
+Given a homomorphism $\alpha$, we consider the new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
 The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$.
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills theory}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
-
-This theory admits a unique twist:
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 10d $\cN=(1, 0)$ supersymmetry algebra admits a unique twist:
 \begin{itemize}
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a complex structure on $\RR^{10}$ together with a nonvanishing complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{5, 0}(\CC^5)$.
 Such a supercharge is stabilized by $G=\SU(5)\subset \Spin(10, \CC)$.
@@
 \subsubsection{Holomorphic twist}
+
 \label{sect:10dholomorphictwist}
 
-Let $Q\in\Sigma$ be a square-zero supercharge.
-The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$.
-Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$.
-Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$.
-In other words, $L$ defines a (linear) complex structure on $V_\RR$.
-Moreover, we may canonically identify $\sigma(L)\cong L^*$.
-
-Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
-\[\Sigma = \det(L)^{1/2} \oplus \wedge^2 L^*\otimes \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2}.\]
-$Q\in\Sigma$ lies in the first summand, so the choice of $Q$ is equivalent to the choice of a (linear) K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
-The square of this half-density defines a Calabi--Yau structure on $M$.
-
-We will now rewrite the fields and the action in terms of the Calabi--Yau structure.
-Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(M)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(M)\rightarrow \Omega^{p, q}(M)$ the dual Lefschetz operator.
-We denote the real volume form on $M$ by
+We will now fix a Calabi--Yau structure giving rise to a square-zero supercharge $Q$ and rewrite the fields and the action in terms of the Calabi--Yau structure.
+Let $\omega\in\Omega^{1, 1}(\CC^5)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(\CC^5)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(\CC^5)\rightarrow \Omega^{p, q}(\CC^5)$ the dual Lefschetz operator.
+We denote the real volume form on $\RR^{10}$ by
 \[\dvol = \frac{\omega^5}{5!}.\]
@@
 The vector representation decomposes as
-\[\Omega^1(M)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 1}(M),\]
+\[\Omega^1(\CC^5)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 1}(\CC^5),\]
 the semi-spin representation $S_+$ decomposes as
-\[\Omega^0(M; S_+)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 2}(M)\oplus \Omega^0(M)\]
+\[\Omega^0(\CC^5; S_+)\cong \Omega^{1, 0}(\CC^5)\oplus \Omega^{0, 2}(\CC^5)\oplus \Omega^0(\CC^5)\]
 and the semi-spin representation $S_-$ decomposes as
-\[\Omega^0(M; S_-)\cong \Omega^{0, 1}(M)\oplus \Omega^{2, 0}(M)\oplus \Omega^0(M).\]
+\[\Omega^0(\CC^5; S_-)\cong \Omega^{0, 1}(\CC^5)\oplus \Omega^{2, 0}(\CC^5)\oplus \Omega^0(\CC^5).\]
 Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$.
-Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \rho + B + \chi\in S_+$ is given by
-\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \rho + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \rho))\in S_-.\]
+Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \psi + B + \chi\in S_+$ is given by
+\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \psi + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \psi))\in S_-.\]
 
@@
 \begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Fermions $\rho\in\Omega^{1, 0}(M; \Pi\gg)$, $B\in\Omega^{0, 2}(M; \Pi\gg)$, $\chi\in\Omega^0(M; \Pi\gg)$.
-\item A ghost field $c\in\Omega^0(M; \gg)[1]$.
-\end{itemize}
-We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \rho^*, B^*, \chi^*, c^*$.
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^5; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(\CC^5; \gg)$.
+\item Fermions $\psi\in\Omega^{1, 0}(\CC^5; \Pi\gg)$, $B\in\Omega^{0, 2}(\CC^5; \Pi\gg)$, $\chi\in\Omega^0(\CC^5; \Pi\gg)$.
+\item A ghost field $c\in\Omega^0(\CC^5; \Pi\gg)$.
+\end{itemize}
+We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \psi^*, B^*, \chi^*, c^*$.
 
@@
 \begin{align}
-S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\rho) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
-S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
-I^{(1)} &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
+S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
+S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
+I^{(1)} &= \int \dvol\left(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
 I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
@@
 \begin{thm}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$.
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ with the space of fields $\map(\CC^5, B\gg)$.
 Moreover, the equivalence is $\SU(5)$-equivariant.
@@
 S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
-&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
+&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\psi, c], \psi^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
 &+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
@@
 
-Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e.
-$(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
-The above theory then becomes perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
+Next, we have a term $\int \dvol \psi\wedge A_{1, 0}^*$ in the action, i.e.
+$(\psi, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+The above theory then becomes perturbatively equivalent to the theory without fields $\psi,\psi^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.
-
-This theory admits a unique twist:
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
+We consider $\cN=1$ super Yang--Mills theory on $\RR^9$ equipped with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+
+The 9d $\cN=1$ supersymmetry algebra admits a unique twist:
 \begin{itemize}
@@
 So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory.
+A way to construct such a supercharge is to choose a splitting $\RR^9\cong \RR^8\times \RR$ with a complex structure on $\RR^8$ together with a complex half-density whose square is a holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
 Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(9, \CC)$.
@@
 \subsubsection{Minimal twist}
-\label{sect:9dminimaltwist}
-
-Let $Q\in\Sigma$ be a square-zero supercharge.
-Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp\subset V$.
-Its orthogonal complement $L$ is maximal isotropic and $L^{\perp}/L$ is one-dimensional.
-Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$.
-Moreover, $N = L^{\perp}\cap \sigma(L^{\perp})\subset V$ is a $\sigma$-stable one-dimensional subspace, we let $N_\RR$ be the $\sigma$-invariants of $N$.
-Therefore, we get a decomposition
-\[V = L\oplus \sigma(L)\oplus N,\]
-where $L^{\perp} = L\oplus N$.
-
-Under the embedding $\ML(L)\subset \Spin(V)$ the spin representation $\Sigma=S$ decomposes as
-\[\Sigma = \wedge^\bullet L\otimes \det(L)^{-1/2}\]
-and the supercharge $Q$ lies in the one-dimensional subspace $\det(L)^{1/2}\subset \Sigma$.
-Therefore, the choice of $Q$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
-
-It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations.
-
-Suppose $L$ is a complex vector space equipped with a K\"ahler structure and a complex half-density.
-Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
-Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
-Let $V_\RR = L\times N$ (a 10-dimensional real vector space).
-By the results of Section \ref{sect:10dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density.
-
-The dimensional reduction of 10d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$.
-Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(N_\RR)$.
-We consider a twisting homomorphism $\phi\colon \SU(L)\times \Spin(N_\RR)\rightarrow G_R=\Spin(N_\RR)$ given by the projection onto the second factor under which $Q$ is preserved.
+
+Choose a splitting $\RR^9\cong\CC^4\times \RR$ together with a constant holomorphic volume form $\Omega\in\Omega^{4, 0}(\CC^4)$.
 
 \begin{thm}
-The twist of $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
-Moreover, the equivalence is $\SU(L)\times \Spin(N_\RR)$-equivariant.
-\label{thm:10dCSreduction}
+\label{9d_twist_thm}
+The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
+Moreover, the equivalence is $\SU(4)$-equivariant.
 \end{thm}
 \begin{proof}
-By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
-Moreover, the equivalence is $\SU(L)\times \SU(N)$-equivariant.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, B\fg)$ and this isomorphism is $\SU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
-
-Therefore, we just need to establish that the $\Spin(N_\RR)$-action on the twisted $(5+\dim(L))$-dimensional super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(N_\RR)$-action on the generalized Chern--Simons theory.
-The $\Spin(N_\RR)$-action on the fields of $(5+\dim(L))$-dimensional super Yang--Mills is obtained via the homomorphism
-\[\Spin(N_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(N_\RR)\times \Spin(N_\RR)\hookrightarrow \Spin(N_\RR\oplus N_\RR),\]
-where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(N_\RR)$ and the twisting homomorphism, i.e.
-the identity map, to the $R$-symmetry group $G_R=\Spin(N_\RR)$.
-The $\SO(N_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
-\[\SO(N_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(N)\longrightarrow \SO(N_\RR\oplus N_\RR)\]
-
-The claim then follows from the commutativity of the diagram
-\[
-\xymatrix@C=2cm{
-\SO(N_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(N_\RR)\times \SO(N_\RR) \ar[d] \\
-\SU(N) \ar[r] & \SO(N_\RR\oplus N_\RR).
-}
-\]
-\end{proof}
-
-We will now concentrate on the 9-dimensional case.
-
-\begin{thm}
-The minimal twist of 9d $\mc N=1$ super Yang--Mills on $M=\CC^4\times \RR$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
-Moreover, the equivalence is $\SU(4)$-equivariant.
-\label{thm:9dminimaltwist}
-\end{thm}
-\begin{proof}
-Any square-zero supercharge in the 9-dimensional supersymmetry algebra is square-zero in the 10-dimensional supersymmetry algebra.
-The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^4$.
+By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$.
+In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.
+
+From Proposition \ref{prop:twistdimensionalreduction} we get that the holomorphic twist of 9d $\mc N=1$ super Yang--Mills is equivalent to a dimensional reduction of the holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills.
+By Theorem \ref{thm:10dholomorphictwist} the latter theory is equivalent to holomorphic Chern--Simons theory on $\CC^5$, so by Proposition \ref{CS_diml_red_prop} its dimensional reduction is equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$.
 \end{proof}
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
 
 Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $\RR^8$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
 It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
-This theory admits three twists:
+The 8d $\cN=1$ supersymmetry algebra admits three twists:
 \begin{itemize}
@@
 These are holomorphic.
-Moreover, we have an isomorphism $\alpha\colon \U(1)\xrightarrow{\sim} \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
+Moreover, we may choose a homomorphism $\alpha\colon \U(1)\rightarrow \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
 Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$.
-We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\cong G_R$, so the twisted theory carries an action of $\MU(4)$.
+We have a twisting homomorphism $\phi\colon \U(4)\xrightarrow{\det} \U(1)\rightarrow G_R=\Spin(2, \RR)$, so the twisted theory carries an action of $\U(4)$.
 
@@
 \item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero.
-These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
+These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2$-graded theory.
 We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$.
@@
 
-Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$.
-As in Section \ref{sect:10dholomorphictwist}, the data of such $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
-
-We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \RR)$ under which $Q$ becomes scalar.
-Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action.
-In fact, this action will factor through $\U(4)$ by a direct observation.
+Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$. In this case the theory carries a $\U(4)$-action and a $\ZZ$-grading. Choose a K\"ahler structure on $\RR^8\cong \CC^4$.
 
@@
 \begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Scalar fields $\phi\in\Omega^{4,0}(M; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(\CC^4; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(\CC^4; \gg)$.
+\item Scalar fields $\phi\in\Omega^{4,0}(\CC^4; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(\CC^4; \gg)[-2]$.
+\item Fermions $\chi\in\Omega^0(\CC^4; \gg)[-1]$, $B\in\Omega^{0, 2}(\CC^4; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(\CC^4; \gg)[-1]$, $\psi\in\Omega^{1, 0}(\CC^4; \gg)[1]$ and $C\in\Omega^{3, 0}(\CC^4; \gg)[1]$.
+
+\item A ghost field $c\in \Omega^0(\CC^4; \gg)[1]$.
 \end{itemize}
@@
 \begin{thm}
-The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$.
+The holomorphic twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory on $\CC^4$ with the space of fields $\map(\CC^4, T^*[3] B\fg)$.
 Moreover, the equivalence is $\U(4)$-equivariant.
@@
 A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
-\rho&\rightsquigarrow \rho, \wt\chi \\
+\psi&\rightsquigarrow \psi, \wt\chi \\
 B&\rightsquigarrow B, C.
@@
 
-The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{9d_twist_thm}).
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
-Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+Indeed, the equivalence given by Theorem \ref{9d_twist_thm} eliminates fields $A_{1, 0}, \wt\phi, \psi, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
 \[
@@
 
+\subsubsection{Partially topological twist}
+
+Next we discuss the case of the partially topological twist with 5 invariant directions.
+Recall that it is merely $\ZZ/2$-graded.
+Decompose $M=\RR^8\cong\CC^3\times \RR^2$ and choose a Calabi--Yau structure on $\CC^3$.
+Using the twisting homomorphism $\SU(3)\times \Spin(2, \RR)\rightarrow G_R$ the twisted theory carries an action of $\SU(3)\times \Spin(2, \RR)$ acting on the individual factors of $\CC^3\times \RR^2$.
+
+\begin{thm}
+The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
+\label{thm:8dpartiallytopologicaltwist}
+\end{thm}
+\begin{proof}
+Denote $V_\RR=\RR^2$, so that we consider 8d $\cN=1$ super Yang--Mills on $\CC^3\times V_\RR$.
+By definition it is obtained as a dimensional reduction of the 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ along the projection $\Re\colon V\rightarrow V_\RR$, where $V=V_\RR\otimes_\RR \CC$.
+
+Let $Q = (Q_+, Q_-)$ be the square-zero supercharge corresponding to the partially topological twist.
+Since we have $(Q_\pm, Q_\pm)_{S_\pm} = 0$, the element $Q_+ + Q_-$ is a square-zero supercharge in the 10-dimensional supersymmetry algebra.
+By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $\CC^3\times V$ is perturbatively equivalent to the holomorphic Chern--Simons theory.
+Moreover, the equivalence is $\SU(3)\times \SU(V)$-equivariant.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $\CC^3\times V$ along $V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times V_\RR, B\fg)$ and this isomorphism is $\SU(3)\times \SO(V_\RR)$-equivariant, where $\SO(V_\RR)$ acts on $V$ via the homomorphism \eqref{eq:SOtoSU}.
+
+Therefore, we just need to establish that the $\Spin(V_\RR)$-action on the twisted 8d $\cN=1$ super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(V_\RR)$-action on the generalized Chern--Simons theory.
+The $\Spin(V_\RR)$-action on the fields on 8d $\cN=1$ super Yang--Mills is obtained via the homomorphism
+\[\Spin(V_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(V_\RR)\times \Spin(V_\RR)\hookrightarrow \Spin(V_\RR\oplus V_\RR),\]
+where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(V_\RR)$ and the twisting homomorphism, i.e.
+the identity map, to the $R$-symmetry group $G_R=\Spin(V_\RR)$.
+The $\SO(V_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
+\[\SO(V_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(V)\longrightarrow \SO(V_\RR\oplus V_\RR)\]
+
+The claim then follows from the commutativity of the diagram
+\[
+\xymatrix@C=2cm{
+\SO(V_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(V_\RR)\times \SO(V_\RR) \ar[d] \\
+\SU(V) \ar[r] & \SO(V_\RR\oplus V_\RR).
+}
+\]
+\end{proof}
+
 \subsubsection{Topological twist}
 
-Next we discuss the case of the topological twist.
+Finally we discuss the case of the topological twist.
 We are going to prove that it is perturbatively trivial.
@@
 Consider a family of square-zero supercharges
-\begin{equation}
-Q_t = \alpha + t\beta\in\Sigma_+
-\label{eq:8dHodgefamily}
-\end{equation}
+\[Q_t = \alpha + t\beta\in\Sigma_+\]
 for $t\in\CC$. We have
@@
 \begin{prop}
-The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
-\begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the 8d $\cN=1$ super Yang--Mills fields are
+\begin{align*}
+I^{(1)}(Q_t) &= \int \dvol\left(-(\psi, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \psi^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
 I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
@@
 \begin{thm}
-The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, B\fg_{\mr{Hod}})$.
+The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, (B\fg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\SU(4)$-equivariant.
@@
 Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
-We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\psi, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
 We are left with the action
@@
 The topological twist of 8d $\cN=1$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$.
-By Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
-\end{proof}
-
-\subsubsection{Partially topological twist}
-
-Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$.
-We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.
+From Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
+\end{proof}
+
+\section{Dimension 7} \label{7d_section}
+
+\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
+The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.
+It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.
+
+In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
+\begin{enumerate}
+ \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
+ \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
+ \item Rank 2 square-zero spinors, i.e.
+square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.
+Such supercharges have a 5-dimensional image in $\CC^7$.
+Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
+\end{enumerate}
+
+The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.
+
+\begin{theorem} \label{7d_holo_twist_thm}
+The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$.
+This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
+\end{theorem}
+
+\begin{proof}
+This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.
+That is, by applying Proposition \ref{CS_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
+\end{proof}
+
+\begin{theorem} \label{7d_rank2_twist_thm}
+The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$.
+\chris{actually I need to think about the twisting homomorphism here.}
+\end{theorem}
+
+\begin{proof}
+Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_diml_red_prop}.
+\end{proof}
+
+\section{Dimension 6}
+In dimension 6 the odd part of the supersymmetry algebra is $\Sigma = S_+ \otimes W_+$.
+There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry. 
+Here, $W_+$ is a two-dimensional complex vector space equipped with a symplectic form. 
+%This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills from $\RR^{10}$ down to $\RR^6$.
+
+\subsection{\texorpdfstring{$\mc N = (1,0)$}{N=(1,0)} Super Yang-Mills Theory with Matter} \label{6d_10_section}
+
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. 
+The general theory with $\mc N = (1,0)$ supersymmetry consists of pure super Yang-Mills with Lie algebra $\fg$ coupled to $(1,0)$ matter valued in a symplectic vector space $U$, as in Section \ref{sect:mattermultipletSUSY}.
+In physics terminology, the matter here is referred to as the $6d$ $\mc N = (1,0)$ hypermultiplet.
+
+The $R$-symmetry group is $G_R = \SU(2)$. \brian{Or do we want it's noncompact form ${\rm Sp}(W_+) = {\rm Sp}(2, \CC)$. }
+
+\vspace{-10pt}
+\paragraph{Fields:}
+The fields of the theory are given by:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^6;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^6 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item $U$-valued scalars: $\phi \in C^\infty(\RR^6 ; W_+ \otimes U)$;
+\item $U$-valued fermions: $\psi \in C^\infty(\RR^6 ; S_- \otimes U)$ .
+\end{itemize}
+
+Under the $R$-symmetry $\lambda, \phi$ transform as the fundamental representations. \brian{Does this sound right?}
+
+\subsubsection{Holomorphic twist}
+
+Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
+The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  
+Without loss of generality we will twist with respect to a supercharge of the form 
+\[
+Q = q_+ \otimes w_1 \in S_+ \otimes W_+ .
+\]
+Such a $Q$ is preserved under the twisting homomorphism
+\[
+\MU(3) \to {\rm Spin}(6) \times \SU(2) .
+\]
+In the first component this is the homomorphism $\MU(3) \to {\rm Spin}(6)$ lifting $\U(3) \to {\rm SO}(6)$. 
+In the second component, this is the composition $\MU(3) \to \U(1) \to \SU(2)$ where the first map is $\det^{-1/2}$ and the second map is $z \mapsto \begin{pmatrix} z & 0 \\ 0 & \Bar{z} \end{pmatrix}$.
+
+There is no twisting datum homomorphism $\alpha : U(1) \to \SU(2)$ compatible with this twisting homomorphism.
+Thus, the resulting twisted theory is only $\ZZ/2$-graded.
+
+Under the action of $\MU(3)$, the fields decompose as:
+\begin{align*}
+c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3 ; \fg) \\
+\lambda & \mapsto \lambda_{0} + {B}_{1,0} + \chi + \lambda_0 \in \Omega^0(\CC^3 ; \fg) \oplus \Omega^{0,2}(\CC^3 ; \fg) \oplus \Omega^{3,0}(\CC^3 ; \fg) \oplus \Omega^{3,2}(\CC^3 ; \fg) \\
+\phi & \mapsto \nu + \psi_0 \in \Omega^0(\CC^3; K^{-1/2} \otimes U) \oplus \Omega^0(\CC^3 ; K^{1/2} \otimes U) \\
+\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; K^{1/2} \otimes U) \oplus \Omega^{0,3} (\CC^3; K^{1/2} \otimes U ),
+\end{align*}
+
+%\begin{align*}
+%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
+%\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
+%\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
+%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
+%\end{align*}
+
+\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
+and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
+In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
+&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
+S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu' \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
+&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
+I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+\end{align*}
+Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.
 
 \begin{thm}
-The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
-Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
-\label{thm:8dpartiallytopologicaltwist}
-\end{thm}
-\begin{proof}
-Since $Q_+$ and $Q_-$ satisfy $(Q_\pm, Q_\pm)_{S_\pm} = 0$, they lift to a square-zero supercharge in the 10-dimensional supersymmetry algebra.
-The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^3$.
-\end{proof}
-
-\section{Dimension 7} \label{7d_section}
-
-The 7-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 8-dimensional spin representation of $\Spin(7, \CC)$ and $W$ is a complex symplectic vector space.
-The spin representation carries a nondegenerate symmetric bilinear pairing $S\otimes S\rightarrow \CC$.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC^2$.
-
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
-
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric.
-It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
-
-This theory admits three twists:
-\begin{itemize}
-\item Rank 1 supercharges $Q=\alpha\otimes w\in S\otimes W$, where $(\alpha, \alpha)_S = 0$.
-These are minimal, i.e.
-the number of invariant directions is 4.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
-We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \RR)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.
-
-\item Rank 1 supercharges $Q = \alpha \otimes w \in S \otimes W$, where $(\alpha, \alpha)_S\neq 0$.
-These are topological and stabilized by $G_2\subset \Spin(7, \CC)$.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
-
-\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
-\end{itemize}
-
-\subsubsection{Minimal twist}
-
-Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp$, so that its orthogonal complement $L\subset V$ is a 3-dimensional isotropic subspace.
-As in Section \ref{sect:9dminimaltwist}, the data of a partially topological supercharge is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a half-density.
-
-We have $Q=\alpha\otimes w\in S\otimes W$ and denote by $\alpha\colon \U(1)\hookrightarrow G_R=\Spin(3, \RR)$ the subgroup under which $w$ has weight $1$.
-We consider the twisting homomorphism given by the composite
-\[\phi\colon \MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
-As before, the $\MU(3)$-action on the theory factors through a $\U(3)$-action.
-
-\begin{thm}
-The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\RR^7$ is perturbatively equivalent to the generalized BF theory on $\CC^3\times \RR$ with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
-Moreover, the equivalence is $\U(3)$-equivariant.
-\label{thm:7dminimaltwist}
-\end{thm}
-\begin{proof}
-The minimal supercharge $Q=\alpha\otimes w$ may be obtained by dimensional reduction of the holomorphic supercharge in the 8-dimensional supersymmetry algebra.
-Therefore, the minimal twist of 7d $\cN=1$ super Yang--Mills on $\CC^3\times \RR$ is obtained by dimensional reduction from the holomorphic twist of 8d $\cN=1$ super Yang--Mills on $\CC^4$.
-The claim then follows from Theorem \ref{thm:8dholomorphictwist} and Corollary \ref{cor:BFholomorphicreduction}.
-\end{proof}
-
-\subsubsection{Topological twist}
-
-Next we study the topological twist.
-Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L\times \RR$.
-Under $\SU(L)\subset \Spin(V_\RR)$ the spin representation decomposes as
-\[S\cong \wedge^\bullet L.\]
-In particular, it contains two trivial summands: $\CC\alpha$ in the lowest degree and $\CC\beta$ in the top degree.
-
-Consider a family of square-zero supercharges
-\begin{equation}
-Q_t = (\alpha + t\beta)\otimes w
-\label{eq:7dHodgefamily}
-\end{equation}
-for some nonzero $w\in W$. We have $(\alpha + t\beta, \alpha + t\beta)=t$, so at $t=0$ we have a minimal supercharge and at $t\neq 0$ we have a topological supercharge.
-
-\begin{thm}
-The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$.
-Moreover, this equivalence is $\SU(3)$-equivariant.
-\end{thm}
-\begin{proof}
-The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions.
-The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$.
-The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
-\end{proof}
-
-\begin{cor}
-The topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively trivial.
-\end{cor}
-
-\subsubsection{Partially topological twist}
-
-Finally, we discuss the case of a partially topological twist.
-We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor.
-
-\begin{thm}
-The partially topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR^3_{\mr{dR}}, B\fg)$.
-Moreover, the equivalence is $\SU(2)\times \Spin(3, \RR)$-equivariant.
-\label{thm:7dpartiallytopologicaltwist}
-\end{thm}
-\begin{proof}
-Any partially topological supercharge in the 7-dimensional supersymmetry algebra lifts to a square-zero supercharge in the 10-dimensional supersymmetry algebra.
-The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^2$.
-\end{proof}
-
-\section{Dimension 6}
-
-The 6-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 4-dimensional semi-spin representations of $\Spin(6, \CC)\cong \SL(4, \CC)$ and $W_+, W_-$ are complex symplectic vector spaces.
-We have isomorphisms $S_+\cong S_-^*$.
-
-There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(1, 1)$ supersymmetry, which we consider separately.
-
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}
-
-The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $U$ a complex symplectic $\fg$-representation.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric.
-We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure.
-The $R$-symmetry group depends on the type of the representation $U$:
-\begin{itemize}
-\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.
-
-\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
-\end{itemize}
-
-This theory admits a unique twist:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory.
-If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading.
-Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$.
-We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(3)$-action.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Fields:} The BRST fields are given by:
-\begin{itemize}
-\item A gauge field $A \in \Omega^1(M;\fg)$.
-\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
-\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
-\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
-\end{itemize}
-
-\subsubsection{Holomorphic twist}
-
-Consider a nonzero $Q\in S_+\otimes W_+$.
-Since $\wedge^2(S_+)\cong V$, the square-zero condition is equivalent to the condition that $Q$ has rank 1, i.e.
-$Q=q_+\otimes w_1\in S_+\otimes W_+$.
-We will also fix $w_2\in W_+$ such that $(w_1, w_2) = 1$.
-
-As in Section \ref{sect:10dholomorphictwist}, the data of $q_+$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
-
-Under the embedding $\MU(L)\subset \Spin(V_\RR)$, the semi-spin representations $S_+, S_-$ decompose as
-\[S_+ = \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2},\qquad S_- = \det(L)^{-1/2} \oplus L^*\otimes \det(L)^{1/2},\]
-where $q_+\in S_+$ lies in the first summand.
-
-We fix an embedding $\U(1)\subset \SU(2)$ under which $w_1\in W_+$ has weight $1$. Under the composite
-\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
-we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.
-
-We will now rewrite the fields using the twisting homomorphism $\phi$ from $\MU(3)$, where we denote by $K$ the canonical bundle of $L=\CC^3$.
-
-\vspace{-10pt}
-\paragraph{Fields:} The BRST fields are given by:
-\begin{itemize}
-\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
-\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
-\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
-\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
-\end{itemize}
-
-Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{3, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 3}(M)$ the antiholomorphic volume form.
-We denote the real volume form on $M$ by
-\[\dvol = \frac{\omega^3}{6} = \Omega\wedge \ol{\Omega}.\]
-
-Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
-\begin{align*}
-S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
-&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
-S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
-&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
-&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
-I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
-I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
-I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
-\end{align*}
-
-\begin{thm}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
-Moreover, the equivalence is $\MU(3)$-equivariant.
+The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with Lie algebra $\fg$ and matter valued in the symplectic representation $U$ is $\MU(3)$-equivariantly equivalent to holomorphic Chern-Simons on $\CC^3$ with values in $U \ham g$, with classical moduli space $\mr{Map}(\CC^3, U\ham \gg)$.
 \label{thm:6dholomorphictwist}
 \end{thm}
+
+%\begin{thm}
+%The holomorphic twist of 6d $\mc N=(1, 0)$ super Yang--Mills with gauge group $G$, and with a hypermultiplet valued in the symplectic representation $U$, is perturbatively equivalent to holomorphic BF theory on $\CC^3$ equipped with a Calabi--Yau structure $\Omega$, coupled to a holomorphic symplectic boson valued in $U$.
+That is, the theory with the space of fields $\mr{Map}(\CC^3, U\ham \gg)$, where $U\ham \gg$ is the classifying space of the dg Lie algebra $\gg \oplus \gg[-1] \oplus U[-1]$ with even shifted symplectic structure induced from the symplectic pairing on $U$.
+%\label{thm:6dholomorphictwist}
+%\end{thm}
+
 \begin{proof}
 The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.
-First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.
-In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
-The twisted theory is therefore perturbatively equivalent to the theory with the BV action
-\begin{align*}
- S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
- &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
-\end{align*}
-Up to rescaling of the antifields, this is the action functional of the required theory.
-\end{proof}
-
-If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$.
-We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
-We may also use a different twisting homomorphism
-\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
-
-With these modifications the BRST fields are given by:
-\begin{itemize}
-\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
-\item Gauge fermions $\chi\in\Omega^0(M; \fg)[-1]$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)[1]$, $B\in\Omega^{0, 2}(M; \fg)[-1]$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)[1]$.
-\item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
-\item Matter fermions $\psi\in \Omega^{1, 0}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
-\end{itemize}
-
-Note that the $\MU(3)$-action on the fields factors through $\U(3)$ since the square roots of $K$ have canceled out.
-By comparing the degrees and the transformation rules of the fields in Theorem \ref{thm:6dholomorphictwist} we obtain the following statement.
-
-\begin{thm}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (R/\fg))$.
-Moreover, the equivalence is $\U(3)$-equivariant.
-\label{thm:6dholomorphictwistgraded}
-\end{thm}
-
-\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}
+First, we integrate out the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
+We then observe that the action includes the terms $\int \dvol  (B_{1,0}, A_{1,0}^*)$ and  $\int \dvol (\nu', \nu^*)$.
+In other words, the pairs $(B_{1,0}, A_{1,0})$ and $(\nu, \nu')$ form BRST doublets, which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+The twisted theory is therefore perturbatively equivalent to the theory with BV action
+\begin{align*}
+ S_{\mr{BV}} &= \int \Omega \bigg( (\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})  + (\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \frac 12 (F_{0,2} \wedge \lambda_{0,2}^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0 \wedge \psi_{0,1}^*) +  \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* \\
+  &\qquad  + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* + [\lambda_{0}, A_0]\wedge \lambda_{0}^* + \frac{1}{2}[A_0, A_0]A_0^* +  [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^*  \bigg).
+\end{align*}
+This is indeed the action functional of the required theory, where $\lambda_{0,2}$ is identified as the antifield to $A_{0,1}$.
+\end{proof}
+
+\begin{remark} \label{6d_BF_remark}
+This theory is in general only $\ZZ/2\ZZ$-graded.
+If the symplectic representation $U = T^*W$ is of cotangent type, then it is possible to promote to the $\ZZ$-graded generalized BF theory $T^*[-1]\mr{Map}(\CC^3, W/\gg)$ \chris{up to modifying by an even degree shift -- need to complete this and say it more carefully}.
+\end{remark}
 

### 2020-01-21 paper.tex

--- 2020-01-20 paper.tex
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}
+%Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. 
+%The general theory with $\mc N = (1,0)$ supersymmetry consists of pure super Yang-Mills with Lie algebra $\fg$ coupled to $(1,0)$ matter valued in a symplectic vector space $U$, as in Section \ref{sect:mattermultipletSUSY}.
+%In physics terminology, the matter here is referred to as the $6d$ $\mc N = (1,0)$ hypermultiplet.
+%
+%The $R$-symmetry group is $G_R = \SU(2)$. \brian{Or do we want it's noncompact form ${\rm Sp}(W_+) = {\rm Sp}(2, \CC)$. }
+
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills Theory}
 
@@
 
-\vspace{-10pt}
-\paragraph{Fields:} The BRST fields are given by:
-\begin{itemize}
-\item A gauge field $A \in \Omega^1(M;\fg)$.
-\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
-\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
-\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
-\end{itemize}
-
+%\vspace{-10pt}
+%\paragraph{Fields:} The BRST fields are given by:
+%>>>>>>> 016a15254e190191104552713b6e9bc2dba88afb
+%\begin{itemize}
+%\item A gauge field $A \in \Omega^1(M;\fg)$.
+%\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
+%\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
+%\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
+%\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+%\end{itemize}
+%
+%<<<<<<< HEAD
+%Under the $R$-symmetry $\lambda, \phi$ transform as the fundamental representations. \brian{Does this sound right?}
+
+%\subsubsection{Holomorphic twist}
+%
+%Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
+%The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  
+%Without loss of generality we will twist with respect to a supercharge of the form 
+%\[
+%Q = q_+ \otimes w_1 \in S_+ \otimes W_+ .
+%\]
+%Such a $Q$ is preserved under the twisting homomorphism
+%\[
+%\MU(3) \to {\rm Spin}(6) \times \SU(2) .
+%\]
+%In the first component this is the homomorphism $\MU(3) \to {\rm Spin}(6)$ lifting $\U(3) \to {\rm SO}(6)$. 
+%In the second component, this is the composition $\MU(3) \to \U(1) \to \SU(2)$ where the first map is $\det^{-1/2}$ and the second map is $z \mapsto \begin{pmatrix} z & 0 \\ 0 & \Bar{z} \end{pmatrix}$.
+%
+%There is no twisting datum homomorphism $\alpha : U(1) \to \SU(2)$ compatible with this twisting homomorphism.
+%Thus, the resulting twisted theory is only $\ZZ/2$-graded.
+%
+%Under the action of $\MU(3)$, the fields decompose as:
+%\begin{align*}
+%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3 ; \fg) \\
+%\lambda & \mapsto \lambda_{0} + {B}_{1,0} + \chi + \lambda_0 \in \Omega^0(\CC^3 ; \fg) \oplus \Omega^{0,2}(\CC^3 ; \fg) \oplus \Omega^{3,0}(\CC^3 ; \fg) \oplus \Omega^{3,2}(\CC^3 ; \fg) \\
+%\phi & \mapsto \nu + \psi_0 \in \Omega^0(\CC^3; K^{-1/2} \otimes U) \oplus \Omega^0(\CC^3 ; K^{1/2} \otimes U) \\
+%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; K^{1/2} \otimes U) \oplus \Omega^{0,3} (\CC^3; K^{1/2} \otimes U ),
+%\end{align*} 
+%
+%%\begin{align*}
+%%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
+%%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
+%%\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
+%%\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
+%%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
+%%\end{align*} 
+%
+%\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
+%and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
+In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
+%=======
 \subsubsection{Holomorphic twist}
+\label{sec:6dholomorphictwist}
 
@@
 \item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
-\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
+\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
+\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$\brian{Should this be $\psi \in \Omega^{0,1}(M; \Pi U\otimes K^{1/2})$?}.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
+
 \begin{align*}
@@
 \end{thm}
+\brian{What's our convention for ``twisted maps?}
+
 \begin{proof}
@@
 Up to rescaling of the antifields, this is the action functional of the required theory.
+%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
 \end{proof}
@@
 We may also use a different twisting homomorphism
-\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
+\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
 
@@
 \end{thm}
-
-\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}
 
@@
 
-\begin{theorem} \label{5d_holo_twist_theorem}
+\begin{theorem} \label{thm: 5dholtwist}
 The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} with chiral multiplet matter} \label{4d_1_section}
+The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional spin representations of $\Spin(4, \CC)\cong \SU(2) \times \SU(2)$ and $W$ is a complex vector space.
+We have isomorphisms $S_\pm \cong S_\pm^*$ which equivalently determine equivariant pairings $S_\pm \otimes S_\pm \to \CC$.
+
+There are Yang--Mills theories with $\cN=1,2,4$ supersymmetry, which we consider separately.
+
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang-Mills theory} \label{4d_1_section}
 We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
@@
 
-%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.
+The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. 
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $R$ a complex $\fg$-representation. 
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. 
+We fix $W=\CC$. 
+The theory admits an $R$-symmetry group $G_R=\U(1)$.
 
@@
 
-The R-symmetry group is $U(1)$ which acts by $\pm 1$ on $\lambda_{\pm}$ and $\mp 1$ on $\psi_{\pm}$.
+This theory admits a unique twist, which is necessarily of rank $1$:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
+The identity homomorphism $\alpha = {\rm id} \colon \U(1)\rightarrow \U(1)$ given by the identity, makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading. 
+Such a supercharge is stabilized by $G=\SU(2)$. 
+Also, we have a compatible twisting homomorphism 
+\[
+\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
+\]
+where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant. 
+\end{itemize}
+
+%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.
 
@@
 
-There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
-Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
-Such supercharges are minimal (i.e. have two dimensional image).  
-The twisted theory by such a supercharge can always be made $\ZZ$-graded where the twisting datum is given by the identity map $\alpha = {\rm id} : U(1) \to U(1)$. 
-Such a $Q$ is preserved under a twisting homomorphism
-\[
-\MU(2) \to {\rm Spin}(4) \times U(1) 
-\]
-where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant.
+For concreteness, we will fix a square-zero supercharge of positive chirality
+\[
+Q = Q_+ \in S_+ \otimes W
+\]
+to twist by. 
+The data of such a $Q_+$ is equivalent to the data of a K\"{a}hler structure $L$ on $V_\RR$.
+
+Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
+\[
+S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
+\]
+Moreover, under the twisting homomorphism
+\[
+\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
+\]
+we have an identification $W = \det(L)^{1/2}$. 
+By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.
 
@@
 \]
-\brian{Is it necessary to put in the antifields?} 
-and their antifields:
-\begin{align*}
-c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
-A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
-\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
-\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
-\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
-\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
-\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
-\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
-\end{align*}
-
-The untwisted action functionals decompose as follows.
+The anti-fields decompose similarly. 
+%\brian{Is it necessary to put in the antifields?} 
+%and their antifields:
+%\begin{align*}
+%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
+%A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
+%\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
+%\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
+%\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
+%\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
+%\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
+%\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
+%\end{align*}
+
+Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{2, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 2}(M)$ the antiholomorphic volume form.
+We denote the real volume form on $M$ by
+\[\dvol = \frac{\omega^2}{2} = \Omega\wedge \ol{\Omega}.\]
+
+Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
 
@@
 
+Notice that a priori the theory is only $\MU(2)$-equivariant, but manifestly descends to a $\U(2)$-equivariant theory.
+
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\MU(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
+The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\U(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
 \end{thm}
@@
 
-\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills with Matter} \label{4d_2_section}
-
-We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.
-In these terms we can describe the BRST fields.
+\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills Theory} \label{4d_2_section}
+
+The general setup for $\cN=2$ super Yang-Mills is described in Section \ref{sec:SYM} which we now recal.
+Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear nondegenerate invariant pairing and $U$ a complex symplectic $\fg$-representation. 
+We consider $\cN=2$ super Yang-Mills theory on $M = \RR^4$ with the Euclidean metric. 
+We fix $W=\CC^2$. The $R$-symmetry group depends on the type of the representation $U$:
+\begin{itemize}
+\item The theory admits an $R$-symmetry group $G_R=\U(2)$ with $W$ the two-dimensional defining representation.
+%\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\U(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
+\end{itemize}
+
+\paragraph{Twisting data:}
+There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
+\begin{itemize}
+ \item[1.] Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  
+ The corresponding twists are holomorphic.
+ Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra.
+ \item[2.] Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. 
+ The corresponding twists are topological (the \emph{Donaldson twist}).
+ \item[3.] Rank $(1,1)$ square-zero supercharges have three invariant directions.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+\label{sect:4d_2_holomorphictwist}
+
+Take a nonzero square-zero rank $(1,0)$ supercharge $Q\in S_+ \otimes W$.
+We choose a basis for $W$ given by $\{w_1,w_2\}$, and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$. 
+Such a $Q$ is automatically holomorphic and the choice of $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
+
+Under the embedding $\MU(L) \subset \Spin(V_\RR)$, the $S_+$ splits as
+\[
+S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
+\]
+
+We consider the twisting homomorphism 
+\[
+\phi \colon \MU(2) \xto{\det^{1/2}} U(1) \hookrightarrow \U(2)
+\]
+under which $Q$ becomes scalar.
+
+%Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(2)$-action. 
+%In fact, this action will factor through $\U(4)$ by a direct observation.
 
 \vspace{-10pt}
-\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
- \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
- \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
- \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-It will be enough for our purposes to describe only the action of a chiral supercharge.
-\begin{prop} \label{4d_2_susy_action_prop}
-After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
+\item Gauge scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
+\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
+%\item Matter bosons $\nu \in \Omega^0(M ; U \otimes K^{-1/2})$, $\phi \in \Omega^0(M ; U \otimes K^{1/2})$.
+\item Matter bosons $\nu\in\Omega^{2,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
+%\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U \otimes K^{1/2})$, $\varphi \in \Omega^{0} (M ; U \otimes K^{1/2})$, $\Tilde{\nu} \in \Omega^0(M ; U \otimes K^{-1/2})$.
+\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U)$, $\varphi \in \Omega^{2,0} (M ; U)$, $\Tilde{\nu} \in \Omega^{0}(M ; U \otimes K^{-1})$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+\brian{Check that I applied the twisting homomorphism correctly. I'm not seeing square roots anymore.}
+
+\begin{thm}
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, U \ham g)$. 
+Moreover, the equivalence is $\U(2)$-equivariant.
+\label{thm:8dholomorphictwist}
+\end{thm}
+\begin{proof}
+4d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory.
+Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
 \begin{align*}
-I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
-&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
-I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
-I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
+A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
+B&\rightsquigarrow B, b \\
+\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
+\psi & \rightsquigarrow \psi, \varphi . \\
 \end{align*}
-if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
-\end{prop}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
-\begin{itemize}
- \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
- \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
- \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
-\end{itemize}
-
-We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.
-
-\begin{theorem} \label{4d_2_holo_twist_thm}
-The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
-\end{theorem}
-
-\begin{proof}
-To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
-\end{proof}
-
-We'll first consider the deformation of the holomorphic twist to the topological twist corresponding to a rank $(2,0)$ supercharge.
-
-\begin{theorem} \label{4d_Donaldson_twist_thm}
-The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.
-\end{theorem}
-
-\begin{proof}
-Suppose the family of generically rank $(2,0)$ supercharge splits as a sum of two rank 1 supercharges as $Q_{\mr{hol}} + tQ$, where $t \in \CC$.
-It is enough to understand the deformation of the holomorphically twisted action functional, which we wrote down in the proof of Theorem \ref{4d_minimal_twist_thm}, by $I^{(1)}(tQ) + I^{(2)}(tQ,tQ)$ using Proposition \ref{4d_2_susy_action_prop}.
-
-\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.
-Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.
-The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
-\end{proof}
-
-We now address the rank $(1,1)$ twist.  This is more straightforward: we can understand it by dimensional reduction from the 5d holomorphic twist, this time in a non-invariant direction.
-
-\begin{theorem} \label{4d_11_twist_thm}
-The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.
-This theory is generally only $\ZZ/2\ZZ$-graded.
-\end{theorem}
-
-\begin{proof}
-We start with the 5d $\mc N=1$ holomorphic twist, as in Theorem \ref{5d_holo_twist_theorem}, and dimensionally reduce in one of the two non-invariant directions.
-That is, we apply Proposition \ref{CS_diml_red_prop}.
-\end{proof}
+
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm: 5dholtwist}).
+
+We are left to check that the equivalence respects  the gradings and the $\MU(2)$-action.
+Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
+\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
+ & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
+& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
+\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*} \\
+ & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
+ \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*} 
+}
+\]
+concentrated in cohomological degrees $0, \dots, 3$.
+These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
+\end{proof}
+
+\begin{rmk}
+The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+\end{rmk}
+
+\subsubsection{Rank $(2,0)$ topological twist}
+\label{sect:4d_2_donaldson}
+
+\brian{I've copied over Chris' work to another file and am working on it there.}
+
+\subsubsection{Rank $(1,1)$ twist}
+\label{sect:4d_2_11}
 

### 2020-01-21 paper.tex
6d N=(1, 1)

--- 2020-01-20 paper.tex
@@
 \section*{Introduction} 
-
-\chris{Possible topics for the introduction
-\begin{enumerate}
- \item  Context and literature on twists, including in the BV formalism.
-There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
-Also at least a remark on the perspective in terms of coupling to twisted sugra.
- \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
- \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
- \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
- \item  Table of the twists, and commentary on where each has appeared before in the literature.
- \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
- \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
- \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
- \item  Summary of the sections of the paper.
-\end{enumerate}}
-
 \begin{table}[htbp]
@@
 \end{figure}
-
-\subsection*{Acknowledgements}
 
@@
 \end{remark}
+
+Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
+These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
+In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.
+So at $t=0$ we will recover generalized BF theory.
+
+We will refer to these families as Hodge deformations of generalized BF theory.
+The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
+
+\begin{definition} \label{Hodge_family_def}
+Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.
+The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so
+\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
+but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
+\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
+\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
+induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
+\end{definition}
+
+Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
+\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]
 
@@
 \subsubsection{Generalized Hodge theory}
-Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
-These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
+
+We will also consider deformations of the generalized BF theory to a perturbatively trivial theory.
 By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.
@@
 The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.
-The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
-
-If $\fg$ carries a nondegenerate invariant symmetric pairing of degree $d$, so does $\fg_{\Hod}$.
-
-\begin{definition} \label{Hodge_family_def}
+
+If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.
+
+\begin{definition}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
@@
 
+\begin{cor}
+Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
+\label{cor:Hodgetopologicalreduction}
+\end{cor}
+
 Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation.
@@
 \item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$.
 
@@
 \begin{equation}
-Q_t = \alpha + t\beta\in\Sigma_+
+Q_t = \alpha + t\beta\in S_+
 \label{eq:8dHodgefamily}
@@
 
-\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
+\item Square-zero supercharges $Q$ of rank 2.
+These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
+We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor, so tht theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
 \end{itemize}
@@
 Moreover, this equivalence is $\SU(3)$-equivariant.
+\label{thm:7dHodgetwist}
 \end{thm}
@@
 
-Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{3, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 3}(M)$ the antiholomorphic volume form.
-We denote the real volume form on $M$ by
-\[\dvol = \frac{\omega^3}{6} = \Omega\wedge \ol{\Omega}.\]
+Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
+\[\dvol = \frac{\omega^3}{6}.\]
 
@@
 We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
-We may also use a different twisting homomorphism
+We may also use a new twisting homomorphism
 \[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
@@
 
-\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}
-
-There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$.
-This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.
-
-\vspace{-10pt}
-\paragraph{Fields:} Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
-\begin{itemize}
- \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.
-These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e.
-the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.
-We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
- \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
-\end{itemize}
-
-We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}
-
-\begin{prop} \label{O6_decomposition_of_susy_prop}
-After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
-I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
-\end{align*}
-if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
-I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
-\end{align*}
-if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.
-In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.
-There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
-\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
-\end{prop}
-
-\begin{remark}
-If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.
-If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
-\end{remark}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
- \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
- \begin{enumerate}
- \item Generically, $Q$ is topological.
- \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
- \end{enumerate}
- \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-We already considered the holomorphic twist in the previous section: it admits the following description.
-
-\begin{theorem} \label{6d_holo_twist_thm}
-The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e.
-the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
-\end{theorem}
-
-\begin{proof}
-Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.
-One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
-\end{proof}
-
-The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
-
-\begin{theorem} \label{6d_rk11_twist_thm}
-The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
-\end{proof}
-
-\begin{theorem} \label{6d_rk22_twist_thm}
-The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
-\end{theorem}
-
-\begin{proof}
-We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
+The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
+It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.
+
+Given an element $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ we denote by $W^*_{Q_\pm}\subset S_\pm$ the images of $Q$. We classify square-zero supercharges according to the ranks of these spaces:
+\begin{itemize}
+\item Rank $(1, 0)$ and $(0, 1)$.
+These automatically square to zero and are holomorphic.
+Such supercharges factor through a copy of the $\mc N=(1,0)$ (respectively, $\cN=(0, 1)$) supersymmetry algebra.
+They admit a twisting homomorphism from $\MU(3)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.
+
+\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle = 0$.
+These automatically square to zero and have 4 invariant directions.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
+
+\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle \neq 0$.
+These automatically square to zero and are topological.
+Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.
+
+\item Rank $(2, 2)$.
+The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory.
+There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$.
+Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills.
+In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.
+
+\begin{thm}
+The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$.
+Moreover, the equivalence is $\U(3)$-equivariant.
+\label{thm:6d11holomorphictwist}
+\end{thm}
+
+\subsubsection{Rank $(1, 1)$ partially topological twist}
+
+We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
+\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]
+
+Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$.
+Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.
+
+\begin{thm}
+The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$.
+Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
+\end{thm}
+\begin{proof}
+The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.
+
+To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$.
+In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}.
+The claim then follows from a direct comparison.
+\end{proof}
+
+\subsubsection{Topological twist}
+
+Next we study the rank $(1, 1)$ topological twist.
+Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$.
+Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
+\[
+S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
+\]
+Consider a family of square-zero supercharges
+\begin{equation}
+Q_t = \alpha + t\beta\in \Sigma.
+\label{eq:6dHodgefamily}
+\end{equation}
+At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.
+
+\begin{thm}
+The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$.
+Moreover, this equivalence is $\SU(3)$-equivariant.
+\label{thm:6dHodgetwist}
+\end{thm}
+\begin{proof}
+The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}.
+So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills.
+Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
+\end{proof}
+
+\begin{cor}
+The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
+\end{cor}
+
+\subsubsection{Rank $(2, 2)$ twist}
+
+We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.
+
+\begin{thm}
+The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
+\label{thm:6drank22}
+\end{thm}
+\begin{proof}
+Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
+\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
+where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
+\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
+where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
+\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
+where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.
+
+Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e.
+$s_+^\pm, s_-^\pm$ are all nonzero.
+The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.
+
+$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$.
+But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.
+
+So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$.
+The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
 \end{proof}
@@
 \begin{theorem}
-\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
-However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
+\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
 \end{theorem}

### 2020-01-21 paper.tex

--- 2020-01-21 paper.tex
@@
 
-%\vspace{-10pt}
-%\paragraph{Fields:} The BRST fields are given by:
-%>>>>>>> 016a15254e190191104552713b6e9bc2dba88afb
-%\begin{itemize}
-%\item A gauge field $A \in \Omega^1(M;\fg)$.
-%\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
-%\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
-%\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
-%\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
-%\end{itemize}
-%
-%<<<<<<< HEAD
-%Under the $R$-symmetry $\lambda, \phi$ transform as the fundamental representations. \brian{Does this sound right?}
-
-%\subsubsection{Holomorphic twist}
-%
-%Choose a polarized basis $W_+ = {\rm span}_{\CC}\{w_1, w_2\}$.
-%The only square-zero supercharges in the $\mc N=(1,0)$ supersymmetry algebra have rank one.  
-%Without loss of generality we will twist with respect to a supercharge of the form 
-%\[
-%Q = q_+ \otimes w_1 \in S_+ \otimes W_+ .
-%\]
-%Such a $Q$ is preserved under the twisting homomorphism
-%\[
-%\MU(3) \to {\rm Spin}(6) \times \SU(2) .
-%\]
-%In the first component this is the homomorphism $\MU(3) \to {\rm Spin}(6)$ lifting $\U(3) \to {\rm SO}(6)$. 
-%In the second component, this is the composition $\MU(3) \to \U(1) \to \SU(2)$ where the first map is $\det^{-1/2}$ and the second map is $z \mapsto \begin{pmatrix} z & 0 \\ 0 & \Bar{z} \end{pmatrix}$.
-%
-%There is no twisting datum homomorphism $\alpha : U(1) \to \SU(2)$ compatible with this twisting homomorphism.
-%Thus, the resulting twisted theory is only $\ZZ/2$-graded.
-%
-%Under the action of $\MU(3)$, the fields decompose as:
-%\begin{align*}
-%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
-%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3 ; \fg) \\
-%\lambda & \mapsto \lambda_{0} + {B}_{1,0} + \chi + \lambda_0 \in \Omega^0(\CC^3 ; \fg) \oplus \Omega^{0,2}(\CC^3 ; \fg) \oplus \Omega^{3,0}(\CC^3 ; \fg) \oplus \Omega^{3,2}(\CC^3 ; \fg) \\
-%\phi & \mapsto \nu + \psi_0 \in \Omega^0(\CC^3; K^{-1/2} \otimes U) \oplus \Omega^0(\CC^3 ; K^{1/2} \otimes U) \\
-%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; K^{1/2} \otimes U) \oplus \Omega^{0,3} (\CC^3; K^{1/2} \otimes U ),
-%\end{align*} 
-%
-%%\begin{align*}
-%%c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
-%%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
-%%\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
-%%\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
-%%\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
-%%\end{align*} 
-%
-%\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
-%and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.
-In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
-%=======
 \subsubsection{Holomorphic twist}
@@
 \item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
-\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$\brian{Should this be $\psi \in \Omega^{0,1}(M; \Pi U\otimes K^{1/2})$?}.
+\item Matter fermions $\psi\in \Omega^{0, 1}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 \end{thm}
-\brian{What's our convention for ``twisted maps?}
-
 \begin{proof}
@@
 We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
-We may also use a different twisting homomorphism
+We may also use a new twisting homomorphism
 \[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
@@
 \item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
-\item Matter fermions $\psi\in \Omega^{1, 0}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
+\item Matter fermions $\psi\in \Omega^{0, 1}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 
-\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}
-
-There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$.
-This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.
-
-\vspace{-10pt}
-\paragraph{Fields:} Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
-\begin{itemize}
- \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.
-These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e.
-the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.
-We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
- \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
-\end{itemize}
-
-We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}
-
-\begin{prop} \label{O6_decomposition_of_susy_prop}
-After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-\begin{align*}
-I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
-I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
-\end{align*}
-if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
-\begin{align*}
-I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
-I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
-\end{align*}
-if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.
-In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.
-There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
-\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
-\end{prop}
-
-\begin{remark}
-If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.
-If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
-\end{remark}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
-\begin{enumerate}
- \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
- \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
- \begin{enumerate}
- \item Generically, $Q$ is topological.
- \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
- \end{enumerate}
- \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-We already considered the holomorphic twist in the previous section: it admits the following description.
-
-\begin{theorem} \label{6d_holo_twist_thm}
-The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e.
-the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
-\end{theorem}
-
-\begin{proof}
-Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.
-One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
-\end{proof}
-
-The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.
-
-\begin{theorem} \label{6d_rk11_twist_thm}
-The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.
-That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
-\end{proof}
-
-\begin{theorem} \label{6d_rk22_twist_thm}
-The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
-\end{theorem}
-
-\begin{proof}
-We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.
-That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
+\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}
+
+The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
+It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.
+
+Given an element $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ we denote by $W^*_{Q_\pm}\subset S_\pm$ the images of $Q$. We classify square-zero supercharges according to the ranks of these spaces:
+\begin{itemize}
+\item Rank $(1, 0)$ and $(0, 1)$.
+These automatically square to zero and are holomorphic.
+Such supercharges factor through a copy of the $\mc N=(1,0)$ (respectively, $\cN=(0, 1)$) supersymmetry algebra.
+They admit a twisting homomorphism from $\MU(3)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.
+
+\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle = 0$.
+These automatically square to zero and have 4 invariant directions.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
+
+\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle \neq 0$.
+These automatically square to zero and are topological.
+Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.
+
+\item Rank $(2, 2)$.
+The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory.
+There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
+\end{itemize}
+
+\subsubsection{Holomorphic twist}
+
+The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$.
+Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills.
+In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.
+
+\begin{thm}
+The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$.
+Moreover, the equivalence is $\U(3)$-equivariant.
+\label{thm:6d11holomorphictwist}
+\end{thm}
+
+\subsubsection{Rank $(1, 1)$ partially topological twist}
+
+We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
+\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]
+
+Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$.
+Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.
+
+\begin{thm}
+The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$.
+Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
+\end{thm}
+\begin{proof}
+The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.
+
+To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$.
+In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}.
+The claim then follows from a direct comparison.
+\end{proof}
+
+\subsubsection{Topological twist}
+
+Next we study the rank $(1, 1)$ topological twist.
+Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$.
+Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
+\[
+S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
+\]
+Consider a family of square-zero supercharges
+\begin{equation}
+Q_t = \alpha + t\beta\in \Sigma.
+\label{eq:6dHodgefamily}
+\end{equation}
+At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.
+
+\begin{thm}
+The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$.
+Moreover, this equivalence is $\SU(3)$-equivariant.
+\label{thm:6dHodgetwist}
+\end{thm}
+\begin{proof}
+The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}.
+So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills.
+Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
+\end{proof}
+
+\begin{cor}
+The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
+\end{cor}
+
+\subsubsection{Rank $(2, 2)$ twist}
+
+We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.
+
+\begin{thm}
+The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
+\label{thm:6drank22}
+\end{thm}
+\begin{proof}
+Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
+\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
+where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
+\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
+where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
+\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
+where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.
+
+Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e.
+$s_+^\pm, s_-^\pm$ are all nonzero.
+The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.
+
+$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$.
+But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.
+
+So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$.
+The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
 \end{proof}
@@
 Moreover, the equivalence is $\U(2)$-equivariant.
-\label{thm:8dholomorphictwist}
+\label{thm:4dholomorphictwist}
 \end{thm}

### 2020-01-22 paper.tex
N=2

@@
 \item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
-\item Matter bosons $\nu\in\Omega^{3,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
 \item Matter fermions $\psi\in \Omega^{0, 1}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
-The identity homomorphism $\alpha = {\rm id} \colon \U(1)\rightarrow \U(1)$ given by the identity, makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading. 
-Such a supercharge is stabilized by $G=\SU(2)$. 
+The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory. 
+Such a supercharge is stabilized by $\SU(2)$. 
 Also, we have a compatible twisting homomorphism 
@@
 \]
-where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant. 
+where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\det^{1/2} : \MU(2) \to U(1)$ is the square root of determinant. 
 \end{itemize}
@@
 \]
-Moreover, under the twisting homomorphism
+
+We consider the twisting homomorphism
 \[
@@
 \]
-we have an identification $W = \det(L)^{1/2}$. 
+for which $Q_+$ becomes a scalar.
+Under this twisting homomorphism, we have an $\MU(2)$-identification $W = \det(L)^{1/2}$. 
 By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.
+
+Since we have an isomorphism $\alpha : U(1) \cong G_R$ the twisted theory is $\ZZ$-graded.
 
@@
 \]
-under which $Q$ becomes scalar.
+for which $Q$ becomes scalar. 
+\brian{I think we want that second map to be $1 \mapsto (1, -1)$, actually.}
+Under this twisting homomorphism we have an $\MU(2)$-identification $W = \det(L)^{1/2} \oplus \det(L)^{1/2}$ and hence $S_+ \otimes W = (\CC \oplus \det(L))^{\oplus 2}$.
+By construction, $Q_+$ lies in the first scalar factor.
+
+The last piece of the twisting data is the homomorphism $\alpha : \U(1) \hookrightarrow \U(2)$ which embeds diagonally into the Cartan of $\U(2)$. 
+This homomorphism is compatible with the twisting homomorphism $\phi$, so the twisted theory is $\ZZ$-graded.
+\brian{check that $\phi$ and $\alpha$ commute.}
 
@@
 \item Gauge scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
-\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
+\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\rho \in \Omega^{1,0}(M ; \gg)$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
 %\item Matter bosons $\nu \in \Omega^0(M ; U \otimes K^{-1/2})$, $\phi \in \Omega^0(M ; U \otimes K^{1/2})$.
-\item Matter bosons $\nu\in\Omega^{2,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
+\item Matter bosons $\nu\in\Omega^{0,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
 %\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U \otimes K^{1/2})$, $\varphi \in \Omega^{0} (M ; U \otimes K^{1/2})$, $\Tilde{\nu} \in \Omega^0(M ; U \otimes K^{-1/2})$.
@@
 
-We are left to check that the equivalence respects  the gradings and the $\MU(2)$-action.
+Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
 Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
@@
 These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
+Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
 \end{proof}
@@
 
-\brian{I've copied over Chris' work to another file and am working on it there.}
+Next we discuss the case of the topological twist. 
+We are going to prove that it is perturbatively trivial. 
+In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and describe the corresponding family of twisted theories.
+
+Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
+Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. %Moreover, fix a complex volume form on $L$.
+
+We will use the notation for fields of 4d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. 
+First, we are going to write the functionals \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2} in terms of these fields.
+
+\begin{prop}
+Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
+The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right).
+\end{align*}
+\end{prop}
+\begin{proof}
+We first write down the functionals in $\Spin(4)$-notation.
+The fields of $4d \cN=2$ decompose as:
+\begin{itemize}
+ \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a ,\Tilde{a}) \in \Omega^0(\RR^4; \gg \oplus \gg)$.
+ \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
+ \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+ \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
+ \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
+\end{itemize}
+
+\brian{If we split $V^{6d}$ as $V^{4d} \oplus N \oplus N^*$ where $N, N^*$ are trivial one-dimensional $\Spin(4)$-representations, then $W^{4d} = W_+^{6d} \otimes N$ and $W^{4d*} = W_+^{6d} \otimes N^*$.
+Moreover, the isomorphism $\wedge^2 S_+^{6d} \cong V^{6d}$ gives rise to three maps
+\begin{itemize}
+\item $S^{4d}_+ \otimes S^{4d}_- \otimes N \otimes N^* \to V^{4d}$. This is $\Gamma^{4d} \otimes {\rm ev}_N$. 
+\item $\wedge^2(S_+^{4d} \otimes N) \to N^*$. 
+\item $\wedge^2(S_-^{4d} \otimes N^*) \to N$. 
+\end{itemize}
+The bosons in the gauge part live in $a \in N^*$ and $\Tilde{a} \in N$. 
+For $Q_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$ and $\lambda_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$. 
+I want to make sense of $(\<Q_+, \lambda_+\> , \Tilde{a}^*)$ as a scalar via the composition
+\[
+\wedge^2 (S_+^{4d} \otimes W^{6d}_+ \otimes N) \otimes N  \xto{\omega_{W_+}} \wedge^2(S^{4d}_+ \otimes N) \otimes N \to N^* \otimes N \to \CC .
+\]
+The first map is the symplectic pairing on $W_+$. 
+The second map is the second bullet above. 
+The last map is evaluation.
+Do you see an easier way to canonically write this using only 4d objects?
+}
+
+For a general supercharge $Q_+ \in S_+ \otimes W$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
+\begin{align*}
+I^{(1)}_{\mr{gauge}}(Q_+) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
+&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
+I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
+I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
+I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
+\end{align*}
+if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
+
+\end{proof}
 

### 2020-01-22 paper.tex
woops
5d

@@
 
+In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing which should be thought of as the complexified Lie algebra of the gauge group.
+
 \section{Dimension 10}
@@
 
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.
+We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric.
 
@@
 
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.
 
@@
 
-Suppose $L$ is a complex vector space equipped with a K\"ahler structure and a complex half-density.
+Suppose $L$ is a complex vector space equipped with a Hermitian structure and a complex half-density.
 Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
@@
 
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric.
-It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
@@
 \subsubsection{Topological twist}
+\label{sect:8dtopologicaltwist}
 
@@
 
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing.
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric.
-It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
 
@@
 
-We have $Q=\alpha\otimes w\in S\otimes W$ and denote by $\alpha\colon \U(1)\hookrightarrow G_R=\Spin(3, \RR)$ the subgroup under which $w$ has weight $1$.
-We consider the twisting homomorphism given by the composite
-\[\phi\colon \MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
-As before, the $\MU(3)$-action on the theory factors through a $\U(3)$-action.
+It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations.
+
+Suppose $L$ is a complex vector space equipped with a Hermitian structure.
+Suppose $N_\RR=\RR^{4-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
+Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
+Let $V_\RR = L\times N$ (an 8-dimensional real vector space).
+We set $W^8=\det(L)^{-1/2}$ as a representation of $\MU(L)$.
+By the results of Section \ref{sect:8dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
+
+The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$.
+We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
+\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]
 
 \begin{thm}
-The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\RR^7$ is perturbatively equivalent to the generalized BF theory on $\CC^3\times \RR$ with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
+The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
+\label{thm:8dBFreduction}
+\end{thm}
+\begin{proof}
+By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory.
+Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant.
+By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+\end{proof}
+
+We will now concentrate on the 7-dimensional case.
+
+\begin{thm}
+The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
 Moreover, the equivalence is $\U(3)$-equivariant.
@@
 \end{thm}
-\begin{proof}
-The minimal supercharge $Q=\alpha\otimes w$ may be obtained by dimensional reduction of the holomorphic supercharge in the 8-dimensional supersymmetry algebra.
-Therefore, the minimal twist of 7d $\cN=1$ super Yang--Mills on $\CC^3\times \RR$ is obtained by dimensional reduction from the holomorphic twist of 8d $\cN=1$ super Yang--Mills on $\CC^4$.
-The claim then follows from Theorem \ref{thm:8dholomorphictwist} and Corollary \ref{cor:BFholomorphicreduction}.
-\end{proof}
 
@@
 
-Next we study the topological twist.
-Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L\times \RR$.
-Under $\SU(L)\subset \Spin(V_\RR)$ the spin representation decomposes as
-\[S\cong \wedge^\bullet L.\]
-In particular, it contains two trivial summands: $\CC\alpha$ in the lowest degree and $\CC\beta$ in the top degree.
-
-Consider a family of square-zero supercharges
-\begin{equation}
-Q_t = (\alpha + t\beta)\otimes w
-\label{eq:7dHodgefamily}
-\end{equation}
-for some nonzero $w\in W$. We have $(\alpha + t\beta, \alpha + t\beta)=t$, so at $t=0$ we have a minimal supercharge and at $t\neq 0$ we have a topological supercharge.
+Next we study the topological twist. As in the case of the minimal twist, we will perform a computation applicable in lower dimensions as well.
+
+Let $L$ be a complex vector space equipped with a Hermitian structure and a complex half-density.
+Suppose $N_\RR = \RR^{4-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
+Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
+Let $V_\RR=L\times N$, a real 8-dimensional vector space equipped with a complex structure and a complex half-density.
+Using results of Section \ref{sect:8dtopologicaltwist} we obtain a family $Q_t$ of 8d square-zero supercharges.
+
+The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ gives $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
+The $R$-symmetry group is $G_R=\Spin(N_\RR\oplus \RR^2)$ and we consider the grading given by the homomorphism $\alpha\colon\U(1)\hookrightarrow \Spin(2, \RR)\times \Spin(N_\RR)\subset G_R$ given by embedding into the first factor.
+We consider the twisting homomorphism given by $\Spin(N_\RR)\hookrightarrow \Spin(2, \RR)\times \Spin(N_\RR)\subset G_R$ given by embedding into the second factor.
+
+\begin{thm}
+The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q_t$ is perturbatively equivalent to the generalized Hodge theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg_\Hod)$.
+Moreover, the equivalence is $\SU(L)\times \Spin(N_\RR)$-equivariant.
+\label{thm:8dHodgereduction}
+\end{thm}
+\begin{proof}
+By Theorem \ref{thm:8dHodgetwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q_t$ is perturbatively equivalent to the holomorphic Hodge theory.
+Moreover, the equivalence is $\SU(L)\times \SU(N)$-equivariant.
+The claim then follows from Corollary \ref{cor:Hodgeholomorphicreduction}.
+\end{proof}
+
+Now let $L=\CC^3$ and $N_\RR=\RR$.
+Dimensionally reducing the family $Q_t$ along $L\times N\rightarrow L\times N_\RR$ we obtain a family of supercharges which are topological for $t\neq 0$ and has 4 invariant directions for $t=0$.
+In other words, at $t=0$ we get the minimal twist and at $t\neq 0$ the topological twist.
 
@@
 \end{thm}
-\begin{proof}
-The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions.
-The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$.
-The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
-\end{proof}
 
@@
 
-%Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. 
-%The general theory with $\mc N = (1,0)$ supersymmetry consists of pure super Yang-Mills with Lie algebra $\fg$ coupled to $(1,0)$ matter valued in a symplectic vector space $U$, as in Section \ref{sect:mattermultipletSUSY}.
-%In physics terminology, the matter here is referred to as the $6d$ $\mc N = (1,0)$ hypermultiplet.
-%
-%The $R$-symmetry group is $G_R = \SU(2)$. \brian{Or do we want it's noncompact form ${\rm Sp}(W_+) = {\rm Sp}(2, \CC)$. }
-
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}
 
 The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $U$ a complex symplectic $\fg$-representation.
+Let $U$ be a complex symplectic $\fg$-representation.
 We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric.
@@
 \begin{thm}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
 Moreover, the equivalence is $\MU(3)$-equivariant.
@@
 
-We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
-\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]
-
-Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$.
-Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.
+Let $L=\CC^2$ equipped with a Hermitian structure, $N_\RR=\RR^2$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 8-dimensional spacetime $V^8_\RR=L\times N$ and the 6-dimensional spacetime $V^6_\RR=L\times N_\RR$.
+Under the projection $V^8_\RR\rightarrow V^6_\RR$ a holomorphic square-zero supercharge $Q$ in 8 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.
+Therefore, from Theorem \ref{thm:8dBFreduction} we obtain the following statement.
 
@@
 \end{thm}
-\begin{proof}
-The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.
-
-To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$.
-In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}.
-The claim then follows from a direct comparison.
-\end{proof}
 
@@
 
-Next we study the rank $(1, 1)$ topological twist.
-Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$.
-Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
-\[
-S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
-\]
-Consider a family of square-zero supercharges
-\begin{equation}
-Q_t = \alpha + t\beta\in \Sigma.
-\label{eq:6dHodgefamily}
-\end{equation}
-At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.
+Let $L=\CC^2$ equipped with a Hermitian structure and a complex half-density, $N_\RR=\RR^2$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 8-dimensional spacetime $V^8_\RR=L\times N$ and the 6-dimensional spacetime $V^6_\RR=L\times N_\RR$.
+Under the projection $V^8_\RR\rightarrow V^6_\RR$ the family $Q_t$ of 8-dimensional square-zero supercharges given by equation \eqref{eq:8dHodgefamily} dimensionally reduces to a family of square-zero supercharges which are topological for $t\neq 0$ and have 4 invariant directions at $t=0$.
+So, we get a rank $(1, 1)$ partially topological twist at $t=0$ and a rank $(1, 1)$ topological twist at $t\neq 0$.
+Therefore, from Theorem \ref{thm:8dHodgereduction} we obtain the following statement.
 
 \begin{thm}
-The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$.
-Moreover, this equivalence is $\SU(3)$-equivariant.
+The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^2\times \RR^2_{\mathrm{dR}}, B\fg_{\Hod})$.
+Moreover, this equivalence is $\SU(2)\times \Spin(2, \RR)$-equivariant.
 \label{thm:6dHodgetwist}
 \end{thm}
-\begin{proof}
-The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}.
-So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills.
-Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
-\end{proof}
 
@@
 
-We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.
+We consider $L=\CC$ equipped with a Hermitian structure and a complex half-density. From Theorem \ref{thm:10dCSreduction} we obtain the following statement.
 
@@
 \end{thm}
-\begin{proof}
-Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
-\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
-where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
-\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
-where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
-\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
-where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.
-
-Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e.
-$s_+^\pm, s_-^\pm$ are all nonzero.
-The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.
-
-$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$.
-But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.
-
-So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$.
-The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
-\end{proof}
 
 \section{Dimension 5}
-The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.
-The maximal supersymmetric gauge theory has $\mc N=2$.
-However, there are $\mc N=1$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group.
-
-\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang-Mills Theory with Matter}  \label{5d_1_section}
-We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.
-This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from Section \ref{6d_10_section} to representations of the group $\mr O(5)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^0(\RR^5; \gg)$.
- \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
- \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
- \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes U)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-There is a unique class of square-zero supercharges in the 5d $\mc N=1$ supersymmetry algebra.
-Twists by such supercharges are minimal: they are invariant in three directions.
-The stabilizer of a minimal supercharge is isomorphic to $\SU(2) \sub \Spin(5)$.
-
-\begin{theorem} \label{thm: 5dholtwist}
-The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
-\end{theorem}
-
-\begin{proof}
-This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in Theorem \ref{thm:6dholomorphictwist} above, by applying Proposition \ref{CS_diml_red_prop} to dimensionally reduce along one of the non-invariant Calabi-Yau directions.
-\end{proof}
-
-\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang-Mills Theory} \label{5d_2_section}
-
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from Section \ref{7d_section}, to representations of the group $\mr O(5)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
- \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
-\end{itemize}
-We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).
-These supercharges all occur as square-zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
-\begin{enumerate}
- \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous section.
- \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
- \begin{enumerate}
- \item The open locus, consisting of topological supercharges.
- \item There is a special locus consisting of supercharges with 4 invariant directions.  The former class can be realised as a degeneration of this case.
- \end{enumerate}
- \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
-\end{enumerate}
-
-\begin{theorem} \label{5d_rk2_twist_thm}
-The twist of 5d $\mc N=2$ super Yang-Mills theory by a rank $2$ supercharge with 4 invariant directions on the product of a Calabi-Yau curve $C$ and an oriented 3-manifold $M_3$ is equivalent to mixed BF theory on the product $C \times (M_3)_{\mr{dR}}$.
-This twist degenerates to a one-parameter family of topological twists of the form $\map(C \times (M_3)_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
-\end{theorem}
-
-\begin{proof}
-As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 6-dimensions.
-\end{proof}
-
-Let us describe the partition function of the A-type topological twist appearing at generic points of this family.  
-\begin{theorem}
-\chris{Something about the Haydys-Witten equations...}
-\end{theorem}
-
-\begin{proof}
-
-\end{proof}
-
-\begin{theorem} \label{5d_rk4_twist_thm}
-The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}((M_5)_{\mr{dR}}, B\gg)$.
-\end{theorem}
-
-\begin{proof}
-We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.
-That is, we apply Proposition \ref{CS_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
-\end{proof}
+
+The 5-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 4-dimensional spin representation of $\Spin(5, \CC)\cong \Sp(4, \CC)$ and $W$ is a complex symplectic vector space.
+The spin representation carries a symplectic paring $S\otimes S\rightarrow \CC$.
+
+There are Yang--Mills theories with $\cN=1$ or $\cN=2$ supersymmetry, which we consider separately.
+
+\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang--Mills}
+\label{5d_1_section}
+
+We fix $W = \CC^2$ equipped with a symplectic structure.
+Let $U$ be a symplectic $\fg$-representation.
+The 5d $\cN=1$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory.
+
+The $R$-symmetry group coincides with the $R$-symmetry group in 6 dimensions:
+\begin{itemize}
+\item For a general $U$ the $R$-symmetry group is $G_R=\SU(2)$ with $W$ the two-dimensional defining representation.
+
+\item For $U=T^* R$ the $R$-symmetry group is $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
+\end{itemize}
+
+The theory admits a unique twist:
+\begin{itemize}
+\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions.
+There is a twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(2)$-action.
+\end{itemize}
+
+\subsubsection{Minimal twist}
+
+A square-zero supercharge $Q$ has rank 1, i.e. $Q=q_+\otimes w_1$ for some $w_1\in W$. We also choose $w_2\in W$ such that $(w_1, w_2) = 1$. We have a twisting homomorphism
+\[\phi\colon\MU(2)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
+such that $W\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.
+
+As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
+
+We will perform a computation of the twist in a more general setting which will be useful for lower-dimensional computations.
+
+Suppose $L$ is a complex vector space equipped with a Hermitian structure.
+Suppose $N_\RR=\RR^{3-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
+Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
+Let $V_\RR=L\times N$ (a 6-dimensional real vector space).
+We set $W^6_+=\det(L)^{-1/2}w_1\oplus \det(L)^{1/2} w_2$ as a representation of $\MU(L)$.
+By the results of Section \ref{sec:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
+
+The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU2W)\times \Spin(N_\RR)$.
+We consider a twisting homomorphism
+\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SU(2)\times \Spin(N_\RR)\]
+whose first component is $\MU(L)\rightarrow \SU(2)$ as before and the second component is the identity.
+
+\begin{thm}
+The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, U\ham \fg)$.
+Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
+\label{thm:6dCSreduction}
+\end{thm}
+\begin{proof}
+By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\map(L\times N, U\ham \fg)$.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, U\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+\end{proof}
+
+If $U$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \Spin(N_\RR)$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow \SU(2)\times \U(1)\times \Spin(N_\RR)$ given by the diagonal embedding into the first two components.
+We also use a new twisting homomorphism
+\[\wt\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\times \Spin(N_\RR)\xrightarrow{\alpha\times\id}G_R.\]
+
+We will now concentrate on the 5-dimensional case.
+
+\begin{thm}
+The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, U\ham \fg)$.
+Moreover, the equivalence is $\MU(2)$-equivariant.
+\label{thm:5dminimaltwist}
+\end{thm}
+
+\begin{thm}
+The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2] (R/\fg))$.
+Moreover, the equivalence is $\U(2)$-equivariant.
+\label{thm:5dminimaltwistgraded}
+\end{thm}
+
+\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang--Mills} \label{5d_2_section}
+
+The 5d $\cN=2$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
+It admits $R$-symmetry group $G_R=\Spin(5, \RR)$ under which $W$ is the 4-dimensional spin representation which carries a symplectic pairing.
+
+An element $Q\in S\otimes W$ gives rise to maps $S^*\rightarrow W$ and $W^*\rightarrow S$.
+Both $S$ and $W$ are 4-dimensional symplectic vector spaces and the classification of supercharges will use their relative position.
+
+This theory admits four twists:
+\begin{itemize}
+\item Rank 1.
+These automatically square to zero and have 3 invariant directions.
+Such supercharges come from the $\cN=1$ supersymmetry algebra.
+They admit a twisting homomorphism from $\MU(2)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.
+
+\item Rank 2, where the image of $W^*\rightarrow S$ is Lagrangian.
+These automatically square to zero and have 4 invariant directions.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(2, \RR)\times \Spin(3, \RR)\hookrightarrow G_R=\Spin(5, \RR)$.
+
+\item Rank 2, where the image of $W^*\rightarrow S$ is symplectic.
+These automatically square to zero and are topological.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(4, \RR)\hookrightarrow G_R=\Spin(5, \RR)$.
+
+\item Rank 4. These are topological and do not admit a compatible homomorphism $\alpha$. There is the identity twisting homomorphism $\phi\colon \Spin(5, \RR)\rightarrow \Spin(5, \RR)$.
+\end{itemize}
+
+\subsubsection{Minimal twist}
+
+The 5d $\cN=2$ super Yang--Mills viewed as a $\cN=1$ supersymmetry theory coincides with the 5d $\cN=1$ super Yang--Mills with matter valued in the representation $U=T^*\fg=\fg\oplus \fg^*$.
+From Theorem \ref{thm:5dminimaltwistgraded} we obtain the following statement.
+
+\begin{thm}
+The minimal twist of 5d $\cN=2$ super Yang--Mills on $M=\CC^2\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2](\fg/\fg))$.
+Moreover, the equivalence is $\U(2)$-equivariant.
+\end{thm}
+
+\subsubsection{Rank 2 partially topological twist}
+
+Let $L = \CC$ equipped with a Hermitian structure, $N_\RR=\RR^3$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 8-dimensional spacetime $V^8_\RR=L\times N$ and the 5-dimensional spacetime $V^5_\RR=L\times N_\RR$.
+Under the projection $V^8_\RR\rightarrow V^5_\RR$ a holomorphic square-zero supercharge $Q$ in 8 dimensions dimensionally reduces to a rank $2$ partially topological square-zero supercharge in 5 dimensions.
+Therefore, from Theorem \ref{thm:8dBFreduction} we obtain the following statement.
+
+\begin{thm}
+The rank $2$ partially topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC\times \RR^3_{\mathrm{dR}}, T^*[4] B\fg)$.
+Moreover, the equivalence is $\Spin(2, \RR)\times\Spin(3, \RR)$-equivariant.
+\end{thm}
+
+\subsubsection{Rank 2 topological twist}
+
+Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR^3$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 8-dimensional spacetime $V_\RR=L\times N$.
+Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 8-dimensional square-zero supercharges given by \eqref{eq:8dHodgefamily} dimensionally reduces to a family of 5-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 4 invariant directions.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the rank 2 partially topological twist and at $t\neq 0$ we obtain the rank 2 topological twist.
+Therefore, from Theorem \ref{thm:8dHodgereduction} we obtain the following statement.
+
+\begin{thm}
+The twist of 5d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC\times \RR^3_{\mathrm{dR}}, B\fg_{\Hod})$.
+Moreover, this equivalence is $\Spin(3)$-equivariant.
+\label{thm:5dHodgetwist}
+\end{thm}
+
+\begin{cor}
+The rank 2 topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively trivial.
+\label{cor:5drank2topologicaltwist}
+\end{cor}
+
+\subsubsection{Rank 4 twist}
+
+We consider $V_\RR=\RR^5$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
+$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sect:10dholomorphictwist} we obtain a square-zero supercharge $Q$.
+Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to a rank 4 supercharge in 5 dimensions.
+Therefore, from Theorem \ref{thm:10dCSreduction} we obtain the following statement.
+
+\begin{thm}
+The rank $4$ twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the topological Chern--Simons theory with the space of fields $\map(\RR^5_{\mr{dR}}, B\fg)$.
+Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
+\end{thm}
 
@@
 
-\brian{Check that I applied the twisting homomorphism correctly. I'm not seeing square roots anymore.}
-
 \begin{thm}
@@
 
-We will use the notation for fields of 4d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. 
+We will use the notation for fields from Section \ref{sect:4d_2_holomorphictwist}. 
 First, we are going to write the functionals \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2} in terms of these fields.

### 2020-01-22 paper.tex
Responding to some comments

@@
 
-\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}
-
 The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
@@
 \end{remark}
+
+We will also sometimes consider $\CC[t]$-families of classical field theories.  These will be defined as follows.
+\begin{definition} \label{family_of_BV_theories_def}
+A $\CC[t]$-family of classical BV theories is a quadruple $(E,Q_{\mr{BV}}, \omega, I)$ as before, but where now the classical BV differential is $t$-dependent.  In other words, it is given as a map
+\[Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1],\]
+where, for each $t_0 \in \CC$, the quadruple $(E,Q^{t_0}_{\mr{BV}}, \omega, I)$
+\[Q^{t_0}_{\mr{BV}} = \mr{ev}_{t_0} \circ Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1] \to \cE[1]\]
+defines a classical field theory.
+\end{definition}
 
@@
 \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
-\chris{Pavel, is this, and the other remark above, what you wanted me to add?}
 \end{remark}
@@
 \begin{remark} \label{mapping_stack_remark}
-The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.
-I can add this later.
-I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
+The mapping stack above has a precise meaning in the language of derived algebraic geometry -- see for instance \cite{PTVV}, where, if $X, Y$ and $M$ are compact, such a mapping stack is shown to carry a $-1$-shifted symplectic structure.
+For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
 The language of the mapping stack will simply be used as a compact way of referring to the theory above.
@@
 \begin{eg}
-There is a special case of this  of the ``holomorphic symplectic boson". 
-\brian{include this?}
+There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
+This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.
+If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
 \end{eg}
+
 \subsubsection{Generalized Hodge theory}
@@
 We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
+The \defterm{generalized Hodge theory} is the $\CC[t]$-family of classical BV theories, as in Definition \ref{family_of_BV_theories_def}, given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
 \end{definition}

### 2020-01-22 paper.tex
adding structure to flesh out in the intro

@@
 \end{enumerate}}
+
+\subsection*{Summary of Twisted Super Yang-Mills Theories}
+In this section we'll summarize the results of Part \ref{classification_part} of the paper, in which we classify all twists of super Yang-Mills theories in dimensions 2 to 10.
+We'll give this summary in two forms.
+In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we will display all the possible twists with a short name, and a precise description in terms of the moduli space of solutions to the twisted equations of motion.
+We will also, in this subsection, give a short description of each twisted theory in more physical language, with references to where in the literature it was previously considered.
+
+\textbf{Dimension 10}
+\begin{itemize}
+ \item \emph{$\mc N=(1,0)$ holomorphic twist.} The unique twisted super Yang-Mills theory in 10 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to 5d holomorphic Chern-Simons theory.
+It is $\SU(5)$ invariant, and can be defined on a Calabi-Yau 5-fold.
+This twist was first studied by Baulieu \cite{Baulieu}.
+\end{itemize}
+
+\textbf{Dimension 9}
+\begin{itemize}
+ \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang-Mills theory in 9 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory with one topological direction and four holomorphic directions.
+It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold.
+\chris{Maybe no reference here?
+Baulieu, Nekrasov, Losev define a kind of 9d twisted theory but it seems to be truly topological, not partially holomorphic?
+It reduces to the 8d A-twist.}
+\end{itemize}
+
+\textbf{Dimension 8}
+\begin{itemize}
+ \item \emph{$\mc N=1$ holomorphic twist.} 
+ \item \emph{$\mc N=1$ intermediate twist.}
+ \item \emph{$\mc N=1$ topological twist.} \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}
+\end{itemize}
+
+\textbf{Dimension 7}
+\begin{itemize}
+ \item \emph{$\mc N=1$ minimal twist.} 
+ \item \emph{$\mc N=1$ intermediate twist.}
+ \item \emph{$\mc N=1$ topological twist.} 
+\end{itemize}
+
+\textbf{Dimension 6}
+\begin{itemize}
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} 
+ \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}
+ \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.}
+ \item \emph{$\mc N=(1,1)$ topological twist.} 
+\end{itemize}
+
+\textbf{Dimension 5}
+\begin{itemize}
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} 
+ \item \emph{$\mc N=2$ intermediate twist.}
+ \item \emph{$\mc N=2$ topological A twist.}
+ \item \emph{$\mc N=2$ topological B twist.} 
+\end{itemize}
+
+\textbf{Dimension 4}
+\begin{itemize}
+ \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} 
+ \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}
+ \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.}
+ \item \emph{$\mc N=4$ topological B twist.}
+ \item \emph{More general $\mc N=4$ topological twists}
+\end{itemize}
+
+\textbf{Dimension 3}
+\begin{itemize}
+ \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.}
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.}
+\end{itemize}
+
+\textbf{Dimension 2}
+\begin{itemize}
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
+ \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
+ \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
+ \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.}
+\end{itemize}
 
@@
  && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
- &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ &&& $\bun_G(\CC \times \RR^4_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
@@
 
+\subsection*{Outline of the Paper}
+
 \subsection*{Acknowledgements}
 
-% \begin{figure}
-% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
-% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
-% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
-% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
-% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
-% \node (825) [right=of 82] {};
-% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
-% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
-% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
-% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
-% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
-% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
-% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
-% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
-% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
-% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
-% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
-% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
-% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
-% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
-% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
-% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
-% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
-% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
-% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
-% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
-% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
-% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
-% 
-% \draw[arrow] (101) -- (91);
-% \draw[arrow] (91) -- (81);
-% \draw[arrow] (91) -- (82);
-% \draw[arrow] (81) -- (71);
-% \draw[arrow] (82) -- (71);
-% \draw[arrow] (82) -- (72);
-% \draw[arrow] (83) -- (73);
-% \draw[arrow] (71) -- (61);
-% \draw[arrow] (71) -- (62);
-% \draw[arrow] (72) -- (62);
-% \draw[arrow] (72) -- (63);
-% \draw[arrow] (73) -- (65);
-% \draw[arrow] (61) -- (51);
-% \draw[arrow] (62) -- (51);
-% \draw[arrow] (62) -- (52);
-% \draw[arrow] (63) -- (53);
-% \draw[arrow] (64) -- (52);
-% \draw[arrow] (64) -- (54);
-% \draw[arrow] (65) -- (54);
-% \draw[arrow] (51) -- (41);
-% \draw[arrow] (51) -- (42);
-% \draw[arrow] (52) -- (42);
-% \draw[arrow] (52) -- (43);
-% \draw[arrow] (53) -- (43);
-% \draw[arrow] (54) -- (43);
-% \draw[arrow] (54) -- (44);
-% \draw[arrow] (54) -- (45);
-% \draw[arrow] (41) -- (31);
-% \draw[arrow] (42) -- (31);
-% \draw[arrow] (42) -- (32);
-% \draw[arrow] (43) -- (32);
-% \draw[arrow] (44) -- (32);
-% \draw[arrow] (45) -- (32);
-% \draw[arrow] (31) -- (21);
-% \draw[arrow] (31) -- (22);
-% \draw[arrow] (32) -- (22);
-% 
-% \node (2d) [dimension, left=of 21] {2d};
-% \node (3d) [dimension, above=of 2d] {3d};
-% \node (4d) [dimension, above=of 3d] {4d};
-% \node (5d) [dimension, above=of 4d] {5d};
-% \node (6d) [dimension, above=of 5d] {6d};
-% \node (7d) [dimension, above=of 6d] {7d};
-% \node (8d) [dimension, above=of 7d] {8d};
-% \node (9d) [dimension, above=of 8d] {9d};
-% \node (10d) [dimension, above=of 9d] {10d};
-% \end{tikzpicture}
-% \caption{Orbits of square-zero supercharges.}
-% \label{fig:superchargeorbits}
-% \end{figure}
-
-\part{Supersymmetric Gauge Theory}
+\part{Supersymmetric Gauge Theory} \label{formalism_part}
 
@@
 
-\part{Classification of Twists}
+\part{Classification of Twists} \label{classification_part}
 
@@
 
-The dimensional reduction of 10d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$.
+The dimensional reduction of 10d super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$.
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(N_\RR)$.
@@
 
-\chris{todo: $(1,0)$, $(2,0)$, $(1,1)$ as above, with $U = T^*\gg$.
-Then $(2,1)$ and generic $(2,2)$ arise as deformations of $(1,1)$ by dimensional reduction from 5d.
-Finally the special $(2,2)$ arises by dimensional reduction from the 5d B-twist.}
-
 \section{Dimension 3}

### 2020-01-22 paper.tex
Added intro to toc

@@
 \section*{Introduction} 
+\label{sec:intro}
+\addcontentsline{toc}{section}{Introduction}
 
@@
 \subsection*{Summary of Twisted Super Yang-Mills Theories}
+\addcontentsline{toc}{subsection}{Summary of Twisted Super Yang-Mills Theories}
 In this section we'll summarize the results of Part \ref{classification_part} of the paper, in which we classify all twists of super Yang-Mills theories in dimensions 2 to 10.
@@
 \subsection*{Outline of the Paper}
+\addcontentsline{toc}{subsection}{Outline of the Paper}
 
@@
 
-\subsubsection{Rank $(1, 1)$ partially topological twist}
+\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
 
@@
 
-\subsubsection{Rank $(2, 2)$ twist}
+\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Twist}
 
@@
 
-\subsubsection{Rank $(2,0)$ topological twist}
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
 \label{sect:4d_2_donaldson}
@@
 
-\subsubsection{Rank $(1,1)$ twist}
+\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} twist}
 \label{sect:4d_2_11}

### 2020-01-22 paper.tex
s2

--- 2020-01-22 paper.tex
@@
 \end{remark}
-
-We will also sometimes consider $\CC[t]$-families of classical field theories.  These will be defined as follows.
-\begin{definition} \label{family_of_BV_theories_def}
-A $\CC[t]$-family of classical BV theories is a quadruple $(E,Q_{\mr{BV}}, \omega, I)$ as before, but where now the classical BV differential is $t$-dependent.  In other words, it is given as a map
-\[Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1],\]
-where, for each $t_0 \in \CC$, the quadruple $(E,Q^{t_0}_{\mr{BV}}, \omega, I)$
-\[Q^{t_0}_{\mr{BV}} = \mr{ev}_{t_0} \circ Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1] \to \cE[1]\]
-defines a classical field theory.
-\end{definition}
 
@@
 \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
+\chris{Pavel, is this, and the other remark above, what you wanted me to add?}
 \end{remark}
@@
 \begin{remark} \label{mapping_stack_remark}
-The mapping stack above has a precise meaning in the language of derived algebraic geometry -- see for instance \cite{PTVV}, where, if $X, Y$ and $M$ are compact, such a mapping stack is shown to carry a $-1$-shifted symplectic structure.
-For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
+The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.
+I can add this later.
+I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
 The language of the mapping stack will simply be used as a compact way of referring to the theory above.
@@
 \begin{eg}
-There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
-This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.
-If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
+There is a special case of this  of the ``holomorphic symplectic boson". 
+\brian{include this?}
 \end{eg}
-
 \subsubsection{Generalized Hodge theory}
@@
 We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Hodge theory} is the $\CC[t]$-family of classical BV theories, as in Definition \ref{family_of_BV_theories_def}, given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
+The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
 \end{definition}
@@
 \begin{proof}
-We first write down the functionals in $\Spin(4)$-notation.
+We first write down the fields and the functionals in $\Spin(4)$-notation.
+Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
+The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
+\[
+S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
+\]
+The odd part of the $\cN=2$ supersymmetry algebra is 
+\[
+\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
+\]
+where $W_+$ is a complex two-dimensional symplectic vector space. 
+From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
+Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
+A general supercharge $Q \in S_+^4 \otimes W$ is of the form
+\[
+Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
+\]
+where $s_+, s_+' \in S_+^{4d}$.
+
 The fields of $4d \cN=2$ decompose as:
 \begin{itemize}
- \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a ,\Tilde{a}) \in \Omega^0(\RR^4; \gg \oplus \gg)$.
+ \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
  \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
- \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+ \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
  \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
@@
 
-For a general supercharge $Q_+ \in S_+ \otimes W$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
+For a general supercharge $Q_+ \otimes \alpha_+ \in S_+^4 \otimes W = S^4_+ \otimes W_+ \otimes S_+^2$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
 \begin{align*}
-I^{(1)}_{\mr{gauge}}(Q_+) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
+I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
 &\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\

### 2020-01-23 paper.tex
small
donaldson

@@
  & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
+  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
+ \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
 & \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
-\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*} \\
- & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
- \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*} 
+\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
 }
@@
 Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
-Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. %Moreover, fix a complex volume form on $L$.
+Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure.
+We utilize the same notation for the fields of super Yang-Mills theory as in the previous section. 
+\brian{discuss twisting homomorphism}
+%Moreover, fix a complex volume form on $L$.
 
@@
 &+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right).
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
 \end{align*}
@@
 \]
-where $s_+, s_+' \in S_+^{4d}$.
+where $s_+, s_+' \in S_+^{4}$.
 
@@
 \begin{itemize}
- \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
- \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
- \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
- \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
+ \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
+  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
+ \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
+ \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
  \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
 \end{itemize}
-
-\brian{If we split $V^{6d}$ as $V^{4d} \oplus N \oplus N^*$ where $N, N^*$ are trivial one-dimensional $\Spin(4)$-representations, then $W^{4d} = W_+^{6d} \otimes N$ and $W^{4d*} = W_+^{6d} \otimes N^*$.
-Moreover, the isomorphism $\wedge^2 S_+^{6d} \cong V^{6d}$ gives rise to three maps
-\begin{itemize}
-\item $S^{4d}_+ \otimes S^{4d}_- \otimes N \otimes N^* \to V^{4d}$. This is $\Gamma^{4d} \otimes {\rm ev}_N$. 
-\item $\wedge^2(S_+^{4d} \otimes N) \to N^*$. 
-\item $\wedge^2(S_-^{4d} \otimes N^*) \to N$. 
-\end{itemize}
-The bosons in the gauge part live in $a \in N^*$ and $\Tilde{a} \in N$. 
-For $Q_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$ and $\lambda_+ \in S^{4d}_+ \otimes W^{4d} = S^{4d}_+ \otimes W^{6d}_+ \otimes N$. 
-I want to make sense of $(\<Q_+, \lambda_+\> , \Tilde{a}^*)$ as a scalar via the composition
-\[
-\wedge^2 (S_+^{4d} \otimes W^{6d}_+ \otimes N) \otimes N  \xto{\omega_{W_+}} \wedge^2(S^{4d}_+ \otimes N) \otimes N \to N^* \otimes N \to \CC .
-\]
-The first map is the symplectic pairing on $W_+$. 
-The second map is the second bullet above. 
-The last map is evaluation.
-Do you see an easier way to canonically write this using only 4d objects?
-}
+The anti-fields decompose in an analogous way.
 
@@
 I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
-&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
-I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
-I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
+&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*) + (\rho(\d_A a)Q_+, \lambda_-^*) \bigg)\\
+I^{(1)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \dvol (((Q_+,\psi_+), \phi^*) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)) \\
+I^{(2)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_+^*,\lambda_+^*) - \frac 12  (Q_+, \lambda_+^*)^2 - (Q_+,Q_+) a c^* \big) \\
+I^{(2)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*) .
 \end{align*}
-if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
-
+
+The result follows from further decomposing the fields under the action of $\MU(2)$. 
+\end{proof}
+
+\begin{thm}
+The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U//g)_{\mr{Hod}})$. 
+Moreover, this equivalence is $\U(2)$-equivariant.
+\label{thm:4dDonaldsontwist}
+\end{thm}
+\begin{proof}
+The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.
+
+Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$.
+Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We are left with the action
+\[S_{BF} + \int\dvol\left(-t(b, A_{0, 1}^*) + t a c^* + \frac{t}{2} \xi^*\wedge B^* + t (\varphi, \phi^*) + \frac t4 (\psi^*, \psi^*) \right),\]
+where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
+Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
+The former is given by (cf.
+the proof of Theorem \ref{thm:4dholomorphictwist})
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
+& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
+\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
+& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
+& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
+& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
+\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}  \ar@{-->}^{t\id}[ur]
+}
+\]
+which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+\end{proof}
+
+\begin{cor}
+The rank $(2,0)$ topological twist of 4d $\cN=2$ super Yang--Mills is perturbatively trivial.
+\label{cor:4dDonaldsontwist}
+\end{cor}
+\begin{proof}
+The topological twist of 4d $\cN=2$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$.
+By Theorem \ref{thm:4dDonaldsontwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
 \end{proof}

### 2020-01-23 paper.tex
merge

--- 2020-01-22 paper.tex
@@
 
+Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
+The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
+\[
+S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
+\]
+The odd part of the $\cN=2$ supersymmetry algebra is 
+\[
+\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
+\]
+where $W_+$ is a complex two-dimensional symplectic vector space. 
+From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
+Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
+%A general supercharge $Q \in S_+^4 \otimes W$ is of the form
+%\[
+%Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
+%\]
+%where $s_+, s_+' \in S_+^{4}$.
+
+Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
+We twist by a supercharge of the form
+\[
+Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
+\]
+where $t \in \CC$. 
+When $t \ne 0$, this supercharge is of rank $(2,0)$. 
+At $t = 0$ it reduces to the holomorphic supercharge from the previous section.
+
 Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
-Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. %Moreover, fix a complex volume form on $L$.
+Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure determined by the holomorphic supercharge $Q_0$. %Moreover, fix a complex volume form on $L$.
 
@@
 We first write down the fields and the functionals in $\Spin(4)$-notation.
-Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
-The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
-\[
-S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
-\]
-The odd part of the $\cN=2$ supersymmetry algebra is 
-\[
-\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
-\]
-where $W_+$ is a complex two-dimensional symplectic vector space. 
-From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
-Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
-A general supercharge $Q \in S_+^4 \otimes W$ is of the form
-\[
-Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
-\]
-where $s_+, s_+' \in S_+^{4d}$.
-
 The fields of $4d \cN=2$ decompose as:
@@
  \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
- \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
- \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+ \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
+ \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
  \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.

### 2020-01-23 paper.tex

--- 2020-01-23 paper.tex
@@
 \begin{thm}
-The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
+The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(L\times (N_\RR)_{\mr{dR}}, B\fg)$ \brian{the $B$-direction was missing}.
 Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
@@
 The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
-Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU2W)\times \Spin(N_\RR)$.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$.
 We consider a twisting homomorphism
@@
 
-If $U$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \Spin(N_\RR)$.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow \SU(2)\times \U(1)\times \Spin(N_\RR)$ given by the diagonal embedding into the first two components.
-We also use a new twisting homomorphism
-\[\wt\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\times \Spin(N_\RR)\xrightarrow{\alpha\times\id}G_R.\]
-
 We will now concentrate on the 5-dimensional case.
@@
 \end{thm}
+
+If $U$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \Spin(N_\RR)$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow \SU(2)\times \U(1)\times \Spin(N_\RR)$ given by the diagonal embedding into the first two components.
+We also use a new twisting homomorphism
+\[\wt\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\times \Spin(N_\RR)\xrightarrow{\alpha\times\id}G_R.\]
 
@@
 
+Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
+The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
+\[
+S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
+\]
+The odd part of the $\cN=2$ supersymmetry algebra is 
+\[
+\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
+\]
+where $W_+$ is a complex two-dimensional symplectic vector space. 
+From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
+Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
+%A general supercharge $Q \in S_+^4 \otimes W$ is of the form
+%\[
+%Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
+%\]
+%where $s_+, s_+' \in S_+^{4}$.
+
+Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
+We twist by a supercharge of the form
+\[
+Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
+\]
+where $t \in \CC$. 
+When $t \ne 0$, this supercharge is of rank $(2,0)$. 
+At $t = 0$ it reduces to the holomorphic supercharge from the previous section.
+
 Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
-Fix a K\"ahler structure on $\RR^4$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure.
+Denote by $L\subset V$ the $i$-eigenspace of the complex structure determined by the holomorphic supercharge $Q_0$. 
 We utilize the same notation for the fields of super Yang-Mills theory as in the previous section. 
 \brian{discuss twisting homomorphism}
-%Moreover, fix a complex volume form on $L$.
 
@@
 We first write down the fields and the functionals in $\Spin(4)$-notation.
-Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
-The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
-\[
-S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
-\]
-The odd part of the $\cN=2$ supersymmetry algebra is 
-\[
-\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
-\]
-where $W_+$ is a complex two-dimensional symplectic vector space. 
-From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
-Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
-A general supercharge $Q \in S_+^4 \otimes W$ is of the form
-\[
-Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
-\]
-where $s_+, s_+' \in S_+^{4}$.
-
 The fields of $4d \cN=2$ decompose as:
@@
 & & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
-& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
-\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}  \ar@{-->}^{t\id}[ur]
+& & \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
+& \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}  \ar@{-->}^{t\id}[ur]
 }
@@
 \label{sect:4d_2_11}
+
+We finally consider the twist with respect to a rank $(1,1)$ supercharge. 
+We have a twisting homomorphism
+\[
+\phi = (1,1) : \U(1) \times \U(1) \to \U(2) .
+\]
+\brian{Just like holomorphic, I may want $(1,-1)$.}
+
+\begin{theorem} \label{thm:4d_11_twist}
+The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U\ham \gg)$.
+Moreover, this identification is $\U(1) \times \U(1)$-equivariant.
+This theory is generally only $\ZZ/2\ZZ$-graded.
+\end{theorem}
+
+\begin{proof}
+A supercharge of rank $(1,1)$ automatically lifts to a rank $1$ supercharge in the $5d$ $\cN=1$ supersymmetry algebra.
+The result then follows from Theorem \ref{thm:6dCSreduction} applied to $L = \CC$. 
+\end{proof}
+
+If $U = T^* R$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\U(2)\times \U(1)$. 
+The extra $\U(1)$ acts trivially on $W$, by weight $+1$ on $R$ and weight $-1$ on $R^*$. 
+We have a homomorphism $\alpha\colon \U(1)\rightarrow  \U(2) \times \U(1)$ given by the diagonal embedding into the first two components \brian{Again like holomorphic, I may want the skew-diagonal $(1,-1)$ into $\U(2)$ and identity on $\U(1)$.}.
+We also use a new twisting homomorphism
+\[\wt\phi\colon \U(1)\times \U(1) \xrightarrow{\alpha\times\id} \U(2) \times \U(1) = G_R.\]
+
+\begin{thm}\label{thm:4d_11_twistgraded}
+The minimal twist of 4d $\cN=2$ super Yang--Mills on $M=\CC \times \RR^2$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC \times \RR^2_{\mathrm{dR}}, T^*[2] (R/\fg))$.
+Moreover, the equivalence is $\U(1)\times \U(1)$-equivariant.
+\end{thm}
 

### 2020-01-23 paper.tex
List of twists in intro

@@
 \begin{itemize}
- \item \emph{$\mc N=1$ holomorphic twist.} 
- \item \emph{$\mc N=1$ intermediate twist.}
- \item \emph{$\mc N=1$ topological twist.} \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}
+ \item \emph{$\mc N=1$ holomorphic twist.} Super Yang-Mills theory in 8 dimensions admits three classes of twist.
+The minimal twist, by a holomorphic supercharge, is equivalent to a holomorphic version of BF theory.
+This theory is $\mr U(4)$-invariant, and can be defined on arbitrary complex 4-folds.
+ \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in two directions and holomorphic in the remaining three complex directions.
+This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.
+It is $\SU(3) \times \Spin(2;\RR)$-invariant, and can be defined on the product of a Calabi-Yau 3-fold and a Riemann surface.
+ \item \emph{$\mc N=1$ topological twist.}  There is, finally, a novel topological twist in 8-dimensions, which does not arise via dimensional reduction from the theories above.
+This theory is perturbatively trivial, in the sense that the classical BV complex is contractible.
+It can, however, be realised as the generic point in a 1-parameter degeneration of the holomorphic twist.
+This theory is $\spin(7;\RR)$-invariant, although the full one-parameter family is only $\SU(4)$-invariant.
+This theory was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}; its equations of motion include the $\spin(7)$-instanton equation.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ minimal twist.} 
- \item \emph{$\mc N=1$ intermediate twist.}
- \item \emph{$\mc N=1$ topological twist.} 
+ \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
+The minimal twist is equivalent to a mixed version of BF theory with one topological direction and three complex holomorphic directions.
+This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
+ \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.
+This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.
+It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
+ \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.
+This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.
+This theory is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
+This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} 
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.
+This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.
+It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.
+It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and $\mr U(3)$ in the cotangent case, and can be defined on arbitrary complex 3-folds.
+When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter \chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
  \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}

### 2020-01-23 paper.tex
More intro boilerplate stuff

@@
 This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.
-This theory is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
+It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
 This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
@@
 It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.
-It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and $\mr U(3)$ in the cotangent case, and can be defined on arbitrary complex 3-folds.
+It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
 When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter \chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
- \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}
- \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.}
- \item \emph{$\mc N=(1,1)$ topological twist.} 
+ \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
+The one by a supercharge of rank $(1,1)$ is equivalent to a mixed form of BF theory, with two topological directions and two complex holomorphic directions.
+This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
+ \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a mixed form of Chern-Simons theory with four real directions and one complex holomorphic direction.
+This theory is only $\ZZ/2\ZZ$-graded.
+It is invariant for the action of $\spin(4;\RR)$, and can be defined on the product of a flat Riemann surface and a spin 4-manifold.
+ \item \emph{$\mc N=(1,1)$ topological twist.} Finally, there is a topological twist in 6 dimensions obtained by dimensionally reducing the 7-dimensional topological twist.
+This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the holomorphic twist.
+It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
+This theory was also studied in \cite{AcharyaOLoughlinSpence} (\chris{I'm struggling to understand whether we should cite \cite{BaulieuKannoSinger, BaulieuLosevNekrasov} here or elsewhere.}; its equations of motion include the Donaldson-Thomas equations.
 \end{itemize}
@@
 \addcontentsline{toc}{subsection}{Outline of the Paper}
+The remainder of the paper is divided into two parts.
+In Part \ref{formalism_part} we set up the formalism that we will use when we study supersymmetric gauge theories and their twists.
+The first main ingredient is the Batalin-Vilkovisky formalism \cite{BatalinVilkovisky} for classical field theory (Section \ref{BV_section}), as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.
+The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sec:susy}), following Baez and Huerta \cite{BaezHuerta}.
+We use this formalism to prove in Section \ref{sec:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
+We introduce the idea of dimensional reduction (Section \ref{dim_red_section}) for classical field theories to show that supersymmetry action are well-defined in lower dimensions.
+
+In Part \ref{classification_part} of the paper, we produce the classification of supersymmetric Yang-Mills theories in dimensions 2 to 10 systematically.
+We start with dimension 10 and work down by dimensional reduction.
+Each subsection is divided by the number of supersymmetries, and the orbits of square-zero supercharges by which we can twist.
+Twisted theories are characterized up to perturbative equivalence, including the residual Lorentz symmetry acting on each twisted theory.
 
 \subsection*{Acknowledgements}
+We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.
+The research of CE on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
 
@@
 
-\section{The BV-BRST Formalism}
+\section{The BV-BRST Formalism} \label{BV_section}
 
@@
 
-\section{Supersymmetry} \label{sec: susy}
+\section{Supersymmetry} \label{sec:susy}
 Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.
@@
 \begin{thm}
-The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U//g)_{\mr{Hod}})$. 
+The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U\ham g)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(2)$-equivariant.

### 2020-01-23 paper.tex
4d N=1 update

--- 2020-01-23 paper.tex
@@
 \begin{thm}
-The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(L\times (N_\RR)_{\mr{dR}}, B\fg)$ \brian{the $B$-direction was missing}.
+The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, T^*[3] B\fg)$.
 Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
@@
 \begin{align*}
-S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
+S_{\gauge} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
 &\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
@@
 
-The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional spin representations of $\Spin(4, \CC)\cong \SU(2) \times \SU(2)$ and $W$ is a complex vector space.
-We have isomorphisms $S_\pm \cong S_\pm^*$ which equivalently determine equivariant pairings $S_\pm \otimes S_\pm \to \CC$.
+The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional semi-spin representations of $\Spin(4, \CC)\cong \SL(2, \CC) \times \SL(2, \CC)$ and $W$ is a complex vector space.
+The semi-spin representations carry symplectic pairings $S_\pm\otimes S_\pm\rightarrow \CC$.
 
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang-Mills theory} \label{4d_1_section}
-We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
-The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.
-
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{4d_1_section}
 The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $R$ a complex $\fg$-representation. 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. 
-We fix $W=\CC$. 
-The theory admits an $R$-symmetry group $G_R=\U(1)$.
-
-The field content for the 4-dimensional $\cN=1$ super Yang-Mills theory coupled to chiral matter is given by:
-\begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
-\item $R$-valued bosons: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
-\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^0(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
-\item $R$-valued fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
-\end{itemize}
-
-This theory admits a unique twist, which is necessarily of rank $1$:
-\begin{itemize}
-\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
+Let $R$ be a complex $\fg$-representation.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^4$ with the Euclidean metric.
+The theory admits an $R$-symmetry group $G_R=\U(1)$ which acts on $W=\CC$ with weight $1$.
+
+\vspace{-10pt}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge field $A \in \Omega^1(M; \fg)$.
+\item Gauge fermions $(\lambda_+, \lambda_-) \in \Omega^0(M; \Pi S_+ \otimes \fg \oplus \Pi S_- \otimes \fg)$.
+\item Matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(M; R \oplus R^*)$.
+\item Matter fermions $(\psi_-,\psi_+) \in \Omega^0(M; \Pi S_+ \otimes R^* \oplus \Pi S_- \otimes R)$.
+\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+The $R$-symmetry acts with weight $\pm 1$ on $\lambda_\pm, \psi_\pm$.
+
+The theory admits a unique twist:
+\begin{itemize}
+\item Elements $Q\in S_+\oplus S_-$ of rank $(1, 0)$ or rank $(0, 1)$.
+Such supercharges are automatically square-zero and are holomorphic.
 The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory.
-Such a supercharge is stabilized by $\SU(2)$. 
-Also, we have a compatible twisting homomorphism 
-\[
-\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
-\]
-where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\det^{1/2} : \MU(2) \to U(1)$ is the square root of determinant. 
-\end{itemize}
-
-%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.
+Also, we have a compatible twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)$.
+\end{itemize}
 
@@
 
-For concreteness, we will fix a square-zero supercharge of positive chirality
-\[
-Q = Q_+ \in S_+ \otimes W
-\]
-to twist by. 
-The data of such a $Q_+$ is equivalent to the data of a K\"{a}hler structure $L$ on $V_\RR$.
-
-Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
-\[
-S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
-\]
-
-We consider the twisting homomorphism
-\[
-\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
-\]
-for which $Q_+$ becomes a scalar.
-Under this twisting homomorphism, we have an $\MU(2)$-identification $W = \det(L)^{1/2}$. 
-By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.
-
-Since we have an isomorphism $\alpha : U(1) \cong G_R$ the twisted theory is $\ZZ$-graded.
+Choose a complex structure $L$ on $V_\RR$. Under the embedding $\MU(L) = \MU(2) \subset \Spin(V_\RR)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2},\qquad S_- = L \otimes \det(L)^{-1/2} .
+\]
+Consider the twisting homomorphism $\phi\colon\MU(2)\rightarrow G_R$ under which $W = \det(L)^{-1/2}$. Then the spinorial representation becomes
+\[\Sigma = (\CC Q\oplus \det(L)^{-1})\oplus L.\]
+
+The identity map $\alpha\colon \U(1)\cong G_R$ makes $Q$ weight $1$.
 
 We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
-The fields decompose as:
-\[
-\begin{array} {lllcccccc}
-& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
-A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
-\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
-\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
-\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
-\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
-\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
-\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
-\end{array}
-\]
-The anti-fields decompose similarly. 
-%\brian{Is it necessary to put in the antifields?} 
-%and their antifields:
-%\begin{align*}
-%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
-%A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
-%\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
-%\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
-%\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
-%\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
-%\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
-%\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
-%\end{align*}
-
-Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{2, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 2}(M)$ the antiholomorphic volume form.
-We denote the real volume form on $M$ by
-\[\dvol = \frac{\omega^2}{2} = \Omega\wedge \ol{\Omega}.\]
+\vspace{-10pt}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
+\item Gauge fermions $\lambda_{1, 0}\in\Omega^{1, 0}(M; \fg)[1]$, $\lambda_0\in\Omega^0(M; \fg)[-1]$, $A_{0, 2}\in\Omega^{0, 2}(M; \fg)[-1]$.
+\item Matter bosons $\phi\in\Omega^0(M; R^*)$, $\gamma_0\in\Omega^0(M; R)$.
+\item Matter fermions $\psi_0\in\Omega^0(M; R^*)[1]$, $\beta_{2, 0}\in\Omega^{2, 0}(M; R^*)[1]$, $\gamma_{0, 1}\in\Omega^{0, 1}(M; R)[-1]$.
+\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+The corresponding antifields are given by:
+\begin{itemize}
+\item $A_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-1]$, $B_{2, 1}\in\Omega^{2, 1}(M; \fg)[-1]$.
+\item $\lambda_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-2]$, $\lambda_0^*\in\Omega^0(M; \fg)$, $B_{2, 0}\in\Omega^{2, 0}(M; \fg)$.
+\item $\phi^*\in\Omega^{2, 2}(M; R)$, $\gamma_0^*\in\Omega^0(M; R^*)$.
+\item $\psi_0^*\in\Omega^{2, 2}(M; R)[-2]$, $\gamma_{0, 2}\in\Omega^{0, 2}(M; R)[-2]$, $\beta_{2, 1}\in\Omega^{2, 1}(M; R^*)$.
+\item $B_{2, 2}\in\Omega^{2, 2}(M; \gg)[-2]$.
+\end{itemize}
+
+Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
+\[\dvol = \frac{\omega^2}{2}.\]
 
@@
 \begin{align*}
-S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
-S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
-&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )   \bigg) \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
-I^{(1)}_{\mr{gauge}} &=  \int  \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
-I^{(1)}_{\mr{matter}} &=  \int  \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int  (\lambda_0^*)^2.
+S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
+S_{\mr{matter}} &= \int \dvol \left((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)\right) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
+&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )  \\
+S_{\mr{anti}} &= \int \bigg(\dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0 \wedge B_{2, 1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* + \dvol ([\lambda_{0}, A_0], \lambda_{0}^*) + [A_0, A_{0,1}]\wedge B_{2, 1} + [A_{0}, A_{1,0}]\wedge A_{1, 0}^* \\
+&\qquad + \frac{1}{2}[A_0, A_0]B_{2, 2} + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \bigg) \\
+I^{(1)}_{\mr{gauge}} &=  \int  \left( - \lambda_{1,0}\wedge A_{1,0}^* + \frac 12 F_{0,2}\wedge B_{2,0} + \frac 12 \omega\wedge F_{1,1} \lambda_0^*  \right) \\
+I^{(1)}_{\mr{matter}} &=  \int  \left( \psi_0 \phi^* + \frac 12 \ol \dd_{A_{0,1}} \gamma_{0}\wedge \beta_{2,1} \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
 \end{align*}
-Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.
 
@@
 \begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\U(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+Moreover, the equivalence is $\U(2)$-equivariant.
 \end{thm}
@@
 The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_{1,1}^*)$.  
-Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+First, we eliminate the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int \lambda_{1,0} \wedge A_{1,0}^*$ and  $\int \psi_0\phi^*$.
+Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
 
@@
 
-%\begin{itemize}
-%\item[(1)] 
-%We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
-%The fields of the pure Yang-Mills part decomposes as:
-%\begin{align*}
-%c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
-%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
-%\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
-%\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
-%\end{align*}
-%and their antifields:
-%\begin{align*}
-%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
-%A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
-%\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
-%\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
-%\end{align*}
-%
-%The matter fields decompose as
-%\begin{align*}
-%\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
-%\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
-%\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
-%\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
-%\end{align*}
-%and their antifields:
-%\begin{align*}
-%\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
-%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
-%\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
-%\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
-%\end{align*}
-%
-%\item[(2)] Next, we study the linear differential in the twisted theory. 
-%At the linear level, the matter and gauge sectors completely decouple. 
-%
-%For the gauge sector, the linear differential on the twisted BV complex is the following:
-%\[
-%\xymatrix{
-%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-%\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
-%& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
-%\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
-%& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
-%}
-%\]
-%The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
-%The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
-%This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$. 
-%
-%For the matter sector, the linear differential is:
-%\[
-%\xymatrix{
-%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
-%& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
-%\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
-%\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
-%}
-%\]
-%This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$. 
-%
-%\item[(3)] 
-%We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
-%\end{itemize}
-
-%There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
-%\begin{itemize}
-%\item The twisted theory is a shifted cotangent theory in the BV formalism. 
-%This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
-%\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
-%\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
-%\end{itemize}
-%
-%The first symmetry we exploit is translation invariance. 
-%There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
-%Let $\fg$ and $R$ be a Lie algebra together with a representation.
-%Define the following graded Lie algebra
-%\[
-%\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
-%\]
-%One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
-%Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.
-%
-%
-%\begin{prop}
-%The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
-%\[
-%\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
-%\]
-%\end{prop}
-
-\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills Theory} \label{4d_2_section}
-
-The general setup for $\cN=2$ super Yang-Mills is described in Section \ref{sec:SYM} which we now recal.
-Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear nondegenerate invariant pairing and $U$ a complex symplectic $\fg$-representation. 
-We consider $\cN=2$ super Yang-Mills theory on $M = \RR^4$ with the Euclidean metric. 
-We fix $W=\CC^2$. The $R$-symmetry group depends on the type of the representation $U$:
-\begin{itemize}
-\item The theory admits an $R$-symmetry group $G_R=\U(2)$ with $W$ the two-dimensional defining representation.
-%\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\U(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
-\end{itemize}
-
-\paragraph{Twisting data:}
-There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
-\begin{itemize}
- \item[1.] Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  
+\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang--Mills} \label{4d_2_section}
+
+The 4d $\cN=2$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$.
+It admits the $R$-symmetry group $G_R=\SU(W)\times \U(1)$ with $W$ the two-dimensional representation on which $\U(1)$ acts with weight $1$.
+
+\vspace{-10pt}
+\paragraph{Fields:} The BRST fields are given by:
+\begin{itemize}
+\item Gauge field $A \in \Omega^1(M; \fg)$.
+\item Scalar fields $a, \wt a\in\Omega^0(M;\fg)$.
+\item Gauge fermions $(\lambda_+, \lambda_-) \in \Omega^0(M; \Pi S_+ \otimes W\otimes \fg \oplus \Pi S_- \otimes W^*\otimes \fg)$.
+\item Matter boson $\phi\in\Omega^0(M; U\otimes W)$.
+\item Matter fermions $(\psi_-, \psi_+)\in\Omega^0(M; \Pi S_+\otimes U\oplus \Pi S_-\otimes U)$.
+\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+$\U(1)\subset G_R$ has the following action: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.
+
+There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$:
+\begin{itemize}
+ \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  
  The corresponding twists are holomorphic.
- Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra.
- \item[2.] Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. 
+ Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra. As before, they admit a $\ZZ$-grading and a twisting homomorphism from $\MU(2)$.
+ \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. 
  The corresponding twists are topological (the \emph{Donaldson twist}). 
- \item[3.] Rank $(1,1)$ square-zero supercharges have three invariant directions.
+ \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
 \end{itemize}
@@
 
-Take a nonzero square-zero rank $(1,0)$ supercharge $Q\in S_+ \otimes W$.
-We choose a basis for $W$ given by $\{w_1,w_2\}$, and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$. 
-Such a $Q$ is automatically holomorphic and the choice of $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.
-
-Under the embedding $\MU(L) \subset \Spin(V_\RR)$, the $S_+$ splits as
-\[
-S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
-\]
+Choose a basis for $W$ given by $\{w_1, w_2\}$ and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$.
+Denote by $L\subset V$ the image of $\Gamma(Q, -)\colon S_-\rightarrow V$.
+Under the embedding $\MU(L) \subset \Spin(V_\RR)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2},\qquad S_- = L \otimes \det(L)^{-1/2} .
+\]
+
+For an integer $n\in\ZZ$ consider the homomorphism $\alpha_n\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ under which $w_1$ has weight $1$ and $w_2$ has weight $-1$ and the projection on the second factor is given by $z\mapsto z^n$.
 
@@
 \[
-\phi \colon \MU(2) \xto{\det^{1/2}} U(1) \hookrightarrow \U(2)
-\]
-for which $Q$ becomes scalar. 
-\brian{I think we want that second map to be $1 \mapsto (1, -1)$, actually.}
-Under this twisting homomorphism we have an $\MU(2)$-identification $W = \det(L)^{1/2} \oplus \det(L)^{1/2}$ and hence $S_+ \otimes W = (\CC \oplus \det(L))^{\oplus 2}$.
-By construction, $Q_+$ lies in the first scalar factor.
-
-The last piece of the twisting data is the homomorphism $\alpha : \U(1) \hookrightarrow \U(2)$ which embeds diagonally into the Cartan of $\U(2)$. 
-This homomorphism is compatible with the twisting homomorphism $\phi$, so the twisted theory is $\ZZ$-graded.
-\brian{check that $\phi$ and $\alpha$ commute.}
-
-%Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(2)$-action. 
-%In fact, this action will factor through $\U(4)$ by a direct observation.
+\phi \colon \MU(2) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R
+\]
+under which we have an $\MU(2)$-identification $W=\det(L)^{-1/2}w_1 \oplus \det(L)^{1/2}w_2$, so that
+\[S_+\otimes W\cong \CC Q\oplus \det(L)^{-1}\oplus \CC\oplus \det(L).\]
 
@@
 \item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Gauge scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
-\item Gauge fermions $\chi \in \Omega^0(M ; \Pi \gg)$, $\xi \in \Omega^{2,0}(M ; \Pi \gg)$, $B \in \Omega^{0,2}(M ; \gg)$, $b \in \Omega^{0,1}(M ; \gg)$, $\rho \in \Omega^{1,0}(M ; \gg)$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)$.
-%\item Matter bosons $\nu \in \Omega^0(M ; U \otimes K^{-1/2})$, $\phi \in \Omega^0(M ; U \otimes K^{1/2})$.
+\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
+\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
 \item Matter bosons $\nu\in\Omega^{0,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
-%\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U \otimes K^{1/2})$, $\varphi \in \Omega^{0} (M ; U \otimes K^{1/2})$, $\Tilde{\nu} \in \Omega^0(M ; U \otimes K^{-1/2})$.
-\item Matter fermions $\psi \in \Omega^{0,1} (M ; \Pi U)$, $\varphi \in \Omega^{2,0} (M ; U)$, $\Tilde{\nu} \in \Omega^{0}(M ; U \otimes K^{-1})$.
+\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[-1]$, $\varphi \in \Omega^{2,0} (M ; U)[1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 \begin{thm}
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, U \ham g)$. 
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 \begin{proof}
-4d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory.
+4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory.
 Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
@@
 
-The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm: 5dholtwist}).
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
 
@@
 Next we discuss the case of the topological twist.
-We are going to prove that it is perturbatively trivial. 
-In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and describe the corresponding family of twisted theories.
+As in Section \ref{sect:8dtopologicaltwist} it will be useful to consider a family of topological supercharges degenerating to a rank $(1, 0)$ holomorphic supercharge.
 
@@
 From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
-Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $s_+$ is a basis element for $S_+^2$. 
+Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $\alpha_+$ is a basis element for $S_+^2$. 
 %A general supercharge $Q \in S_+^4 \otimes W$ is of the form

### 2020-01-23 paper.tex

@@
 \begin{itemize}
- \item \emph{$\mc N=1$ minimal twist.} 
- \item \emph{$\mc N=1$ intermediate twist.}
- \item \emph{$\mc N=1$ topological twist.} 
+ \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
+The minimal twist is equivalent to a mixed version of BF theory with one topological direction and three complex holomorphic directions.
+This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
+ \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.
+This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.
+It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
+ \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.
+This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.
+It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
+This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} 
- \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.}
- \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.}
- \item \emph{$\mc N=(1,1)$ topological twist.} 
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.
+This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.
+It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.
+It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
+When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter \chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
+ \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
+The one by a supercharge of rank $(1,1)$ is equivalent to a mixed form of BF theory, with two topological directions and two complex holomorphic directions.
+This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
+ \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a mixed form of Chern-Simons theory with four real directions and one complex holomorphic direction.
+This theory is only $\ZZ/2\ZZ$-graded.
+It is invariant for the action of $\spin(4;\RR)$, and can be defined on the product of a flat Riemann surface and a spin 4-manifold.
+ \item \emph{$\mc N=(1,1)$ topological twist.} Finally, there is a topological twist in 6 dimensions obtained by dimensionally reducing the 7-dimensional topological twist.
+This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the holomorphic twist.
+It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
+This theory was also studied in \cite{AcharyaOLoughlinSpence} (\chris{I'm struggling to understand whether we should cite \cite{BaulieuKannoSinger, BaulieuLosevNekrasov} here or elsewhere.}; its equations of motion include the Donaldson-Thomas equations.
 \end{itemize}

### 2020-01-23 paper.tex
3d edits

--- 2020-01-23 paper.tex
@@
 
-The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
+The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$.
@@
 
-The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
+The dimensional reduction of 6d super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$.
@@
 \[
-\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
+\phi \colon \MU(2) \to {\rm Spin}(4) \times U(1) 
 \]
@@
 The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+We fix $W = \CC^2$ equipped with a nondegenerate symmetric bililear pairing.
+
+The R-symmetry group is $\mr O(2)$, acting on $W$ by its defining representation.
+
+This theory admits a unique twist:
+\begin{itemize}
+ \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
+There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
+\end{itemize}
+
+We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
+\subsubsection{Minimal Twist}
+A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.
+
+As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
+Note that in one dimension the choice of a complex half-density is equivalent to a choice of spin structure.
 
@@
 The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+Moreover this equivalence is $\mr U(1)$-equivariant.
 \end{thm}
@@
 \begin{proof}
-This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
+By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\MU(1) = \mr U(1)$-equivariant.
 \end{proof}
@@
 
+\subsubsection{Minimal Twist}
+
+\subsubsection{Topological A Twist}
 \begin{theorem} \label{3d_4_holo_A_twist_thm}
@@
 \end{proof}
+
+\subsubsection{Topological B Twist}
 
@@
 
+\subsubsection{Minimal Twist}
+
+\subsubsection{Topological A Twist}
+
 \begin{theorem} 
@@
 \end{theorem}
+
+\subsubsection{Topological B Twist}
 

### 2020-01-23 paper.tex
transfer to desktop

--- 2020-01-23 paper.tex
@@
 
-For an integer $n\in\ZZ$ consider the homomorphism $\alpha_n\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ under which $w_1$ has weight $1$ and $w_2$ has weight $-1$ and the projection on the second factor is given by $z\mapsto z^n$.
+Recall, the $R$-symmetry group is $G_R = \SU(2) \times \U(1)$.
+For any integer $n\in\ZZ$ consider the homomorphism 
+\[
+\begin{array}{cccccc}
+\alpha_n & \colon & \U(1) & \rightarrow & \SU(2)\times \U(1)\\
+& & z & \mapsto & \left({\rm diag}(z^{2n}, z^{-2n}) , z^{-2n+1} \right)
+\end{array}
+\]
+under which $w_1$ has weight $1$ and $w_2$ has weight $-4n+1$.
 
@@
 \begin{thm}
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.

### 2020-01-23 paper.tex
3d section

--- 2020-01-23 paper.tex
@@
 We twist by a supercharge of the form
-\[
+\begin{equation} 
+\label{eq:4dHodgefamily}
 Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
-\]
+\end{equation}
 where $t \in \CC$. 
@@
 \begin{prop}
-Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
+Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
 The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
+The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation.
+\chris{or should it be $\spin(3;\RR)$?}
+
+In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
+An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
+The classification of orbits includes the rank of this map.
+\begin{itemize}
+ \item Rank 1.
+In this case $Q$ is minimal, with 2 invariant directions.
+Such supercharges come from the $\mc N=2$ supersymmetry algebra.
+They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $A$-twist.
+Rank 2 supercharges are topological.
+A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore a volume form.
+There are two orbits for the $G_R = \SO(4)$ action on the space of volume forms, which we refer to as the $A$-twist and the $B$-twist.
+The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
+It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $B$-twist.
+The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
+It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$.
+\end{itemize}
+
+We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.
-The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.
-Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.
-
 \subsubsection{Minimal Twist}
+The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
+From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.
+
+\begin{theorem} \label{3d_4_minimal_twist_thm}
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
+Moreover, the equivalence is $\U(1)$-equivariant.
+\end{theorem}
 
 \subsubsection{Topological A Twist}
-\begin{theorem} \label{3d_4_holo_A_twist_thm}
-The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
+Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 4-dimensional spacetime $V_\RR=L\times N$.
+Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist.
+Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
+
+\begin{thm}
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\U(1)$-equivariant.
+\label{3d_4_A_twist_thm}
+\end{thm}
+
+\begin{cor}
+The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
+\end{cor}
+
+\subsubsection{Topological B Twist}
+We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
+$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
+Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
+Therefore, from Theorem \ref{thm:6dCSreduction} we obtain the following statement.
+
+\begin{theorem} \label{3d_4_B_twist_thm}
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
-\end{proof}
-
-\subsubsection{Topological B Twist}
-
-\begin{theorem} \label{3d_2_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-This theory is generally only $\ZZ/2\ZZ$-graded.
-\end{theorem}
-
-\begin{proof}
-Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
-\end{proof}
 
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+The $R$-symmetry group is $G_R = \Spin(7;
+RR)$, acting on $W$ by its (Dirac) spin representation.
+
+In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three classes: 
+\begin{itemize}
+ \item Rank 1.
+In this case $Q$ is minimal, with 2 invariant directions.
+Such supercharges come from the $\mc N=2$ supersymmetry algebra.
+They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $A$-twist.
+These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
+The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
+It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $B$-twist.
+These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
+The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
+It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso G_R$.
+\end{itemize}
+
+ We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.
-There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).
-The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.
-
 \subsubsection{Minimal Twist}
+The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
+From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
+
+\begin{theorem} 
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
+Moreover, the equivalence is $\U(1)$-equivariant.
+\end{theorem}
 
 \subsubsection{Topological A Twist}
+From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
 
 \begin{theorem} 
-The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\U(1)$-equivariant.
 \end{theorem}
@@
 \subsubsection{Topological B Twist}
+From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
 
@@
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
+Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
 \end{theorem}

### 2020-01-23 paper.tex

--- 2020-01-23 paper.tex
@@
 The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
-\end{thm}
-
-\begin{proof}
-This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
+Moreover this equivalence is $\mr U(1)$-equivariant.
+\end{thm}
+
+\begin{proof}
+By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\MU(1) = \mr U(1)$-equivariant.
 \end{proof}
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.
-The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.
-Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.
-
-\begin{theorem} \label{3d_4_holo_A_twist_thm}
-The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
+\subsubsection{Minimal Twist}
+The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
+From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.
+
+\begin{theorem} \label{3d_4_minimal_twist_thm}
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
+Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
 
-\begin{proof}
-To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
-\end{proof}
-
-\begin{theorem} \label{3d_2_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-This theory is generally only $\ZZ/2\ZZ$-graded.
+\subsubsection{Topological A Twist}
+Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+Consider the 4-dimensional spacetime $V_\RR=L\times N$.
+Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist.
+Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
+
+\begin{thm}
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\U(1)$-equivariant.
+\label{3d_4_A_twist_thm}
+\end{thm}
+
+\begin{cor}
+The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
+\end{cor}
+
+\subsubsection{Topological B Twist}
+We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
+$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
+Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
+Therefore, from Theorem \ref{thm:6dCSreduction} we obtain the following statement.
+
+\begin{theorem} \label{3d_4_B_twist_thm}
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
-\end{proof}
 
@@
 
-\vspace{-10pt}
-\paragraph{Twisting data:}
-The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.
-There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).
-The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.
+\subsubsection{Minimal Twist}
+The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
+From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
 
 \begin{theorem} 
-The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
-The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
+Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
+
+\subsubsection{Topological A Twist}
+From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
+
+\begin{theorem} 
+The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+\subsubsection{Topological B Twist}
+From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
 

### 2020-01-23 paper.tex
fixing referencing errors

@@
 
-\begin{rmk}
+\begin{remark}
 \brian{Explain $C^\bu(\fg)$-linear elliptic}
-\end{rmk}
-
-\begin{rmk}
+\end{remark}
+
+\begin{remark}
 We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
@@
 is satisfied.
-\end{rmk}
-
-\begin{rmk}
+\end{remark}
+
+\begin{remark}
 We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
@@
 combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
-\end{rmk}
+\end{remark}
 
@@
 
-\begin{rmk}
+\begin{remark}
 This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure.
-\end{rmk}
+\end{remark}
 
@@
 
-\begin{eg}
+\begin{example}
 There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
@@
 If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
-\end{eg}
+\end{example}
 
@@
 
-\begin{cor}
+\begin{corollary}
 Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
@@
 \label{cor:Hodgetopologicalreduction}
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{cor}
+\begin{corollary}
 Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
@@
 \label{cor:BFholomorphicreduction}
-\end{cor}
-
-\begin{cor}
+\end{corollary}
+
+\begin{corollary}
 Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
@@
 \label{cor:Hodgeholomorphicreduction}
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{thm}
+\begin{theorem}
 Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
@@
 \label{thm:3psi}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
@@
 \label{thm:matter3psi}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 For $Q_1, Q_2, Q_3\in\Sigma$ we have
@@
 \label{thm:2d3psi}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
@@
 \label{thm:2dmatter3psi}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}\label{thm:gaugemultipletSUSY}
+\begin{theorem}\label{thm:gaugemultipletSUSY}
 The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
@@
 Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
@@
 \label{thm:YMSUSY}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$.
@@
 \label{thm:10dholomorphictwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
@@
 \label{thm:10dCSreduction}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The minimal twist of 9d $\mc N=1$ super Yang--Mills on $M=\CC^4\times \RR$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
@@
 \label{thm:9dminimaltwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$.
@@
 \label{thm:8dholomorphictwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, B\fg_{\mr{Hod}})$.
@@
 \label{thm:8dHodgetwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{cor}
+\begin{corollary}
 The topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively trivial.
 \label{cor:8dtopologicaltwist}
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$.
@@
 \label{thm:8dpartiallytopologicaltwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, T^*[3] B\fg)$.
@@
 \label{thm:8dBFreduction}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
@@
 \label{thm:7dminimaltwist}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q_t$ is perturbatively equivalent to the generalized Hodge theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg_\Hod)$.
@@
 \label{thm:8dHodgereduction}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$.
@@
 \label{thm:7dHodgetwist}
-\end{thm}
-
-\begin{cor}
+\end{theorem}
+
+\begin{corollary}
 The topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively trivial.
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The partially topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR^3_{\mr{dR}}, B\fg)$.
@@
 \label{thm:7dpartiallytopologicaltwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
@@
 \label{thm:6dholomorphictwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (R/\fg))$.
@@
 \label{thm:6dholomorphictwistgraded}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$.
@@
 \label{thm:6d11holomorphictwist}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$.
 Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^2\times \RR^2_{\mathrm{dR}}, B\fg_{\Hod})$.
@@
 \label{thm:6dHodgetwist}
-\end{thm}
-
-\begin{cor}
+\end{theorem}
+
+\begin{corollary}
 The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$.
@@
 \label{thm:6drank22}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, U\ham \fg)$.
@@
 \label{thm:6dCSreduction}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}
+\begin{theorem}
 The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, U\ham \fg)$.
@@
 \label{thm:5dminimaltwist}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2] (R/\fg))$.
@@
 \label{thm:5dminimaltwistgraded}
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The minimal twist of 5d $\cN=2$ super Yang--Mills on $M=\CC^2\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2](\fg/\fg))$.
 Moreover, the equivalence is $\U(2)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The rank $2$ partially topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC\times \RR^3_{\mathrm{dR}}, T^*[4] B\fg)$.
 Moreover, the equivalence is $\Spin(2, \RR)\times\Spin(3, \RR)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 5d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC\times \RR^3_{\mathrm{dR}}, B\fg_{\Hod})$.
@@
 \label{thm:5dHodgetwist}
-\end{thm}
-
-\begin{cor}
+\end{theorem}
+
+\begin{corollary}
 The rank 2 topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively trivial.
 \label{cor:5drank2topologicaltwist}
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The rank $4$ twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the topological Chern--Simons theory with the space of fields $\map(\RR^5_{\mr{dR}}, B\fg)$.
 Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
+\begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
 The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
@@
 \label{thm:4dholomorphictwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{rmk}
+\begin{remark}
 The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
 The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-\end{rmk}
+\end{remark}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U\ham g)_{\mr{Hod}})$.
@@
 \label{thm:4dDonaldsontwist}
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{cor}
+\begin{corollary}
 The rank $(2,0)$ topological twist of 4d $\cN=2$ super Yang--Mills is perturbatively trivial.
 \label{cor:4dDonaldsontwist}
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 
-\begin{thm}\label{thm:4d_11_twistgraded}
+\begin{theorem}\label{thm:4d_11_twistgraded}
 The minimal twist of 4d $\cN=2$ super Yang--Mills on $M=\CC \times \RR^2$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC \times \RR^2_{\mathrm{dR}}, T^*[2] (R/\fg))$.
 Moreover, the equivalence is $\U(1)\times \U(1)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm} \label{3d_minimal_twist_thm}
+\begin{theorem} \label{3d_minimal_twist_thm}
 The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
 Moreover this equivalence is $\mr U(1)$-equivariant.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}
+\begin{theorem}
 The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
@@
 \label{3d_4_A_twist_thm}
-\end{thm}
-
-\begin{cor}
+\end{theorem}
+
+\begin{corollary}
 The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
-\end{cor}
+\end{corollary}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{2d(0,2)}
+\begin{theorem}[See also \cite{SWchar}] \label{2d(0,2)}
 The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
-\end{thm}
+\end{theorem}
 \begin{proof}
@@
 
-\begin{thm}\label{2d(0,4)}
+\begin{theorem}\label{2d(0,4)}
 The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-\end{thm}
+\end{theorem}
 
@@
 
-\begin{thm}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
+\begin{theorem}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
 The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
-\end{thm}
+\end{theorem}
 

### 2020-01-23 paper.tex
general n

--- 2020-01-23 paper.tex
@@
 
-The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
+The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$.
@@
 
-The dimensional reduction of 6d super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
+The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$.
@@
 \begin{thm}
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
- & \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
   & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
+  }
+\]
+
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{-4n+2} & \ul{-4n+3} & \ul{-4n+4} & \cdots & \ul{4n-1} & \ul{4n} & \ul{4n+1} \\ 
+ &&&& \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
  \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
-& \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
-\Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
 }
 \]
-concentrated in cohomological degrees $0, \dots, 3$.
+
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
+\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
+& & & & \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
+}
+\]
 These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
@@
 We twist by a supercharge of the form
-\begin{equation} 
-\label{eq:4dHodgefamily}
+\[
 Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
-\end{equation}
+\]
 where $t \in \CC$. 
@@
 \begin{prop}
-Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
+Suppose $Q_t$ is the rank $(2,0)$ supercharge as above.
 The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
@@
 The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-We fix $W = \CC^2$ equipped with a nondegenerate symmetric bililear pairing.
-
-The R-symmetry group is $\mr O(2)$, acting on $W$ by its defining representation.
-
-This theory admits a unique twist:
-\begin{itemize}
- \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
-\end{itemize}
-
-We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsubsection{Minimal Twist}
-A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.
-
-As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
-Note that in one dimension the choice of a complex half-density is equivalent to a choice of spin structure.
+\vspace{-10pt}
+\paragraph{Twisting data:}
+In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
 
@@
 The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
-Moreover this equivalence is $\mr U(1)$-equivariant.
-\end{thm}
-
-\begin{proof}
-By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\MU(1) = \mr U(1)$-equivariant.
+\end{thm}
+
+\begin{proof}
+This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.
+That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
 \end{proof}
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation.
-\chris{or should it be $\spin(3;\RR)$?}
-
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
-The classification of orbits includes the rank of this map.
-\begin{itemize}
- \item Rank 1.
-In this case $Q$ is minimal, with 2 invariant directions.
-Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-Rank 2 supercharges are topological.
-A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore a volume form.
-There are two orbits for the $G_R = \SO(4)$ action on the space of volume forms, which we refer to as the $A$-twist and the $B$-twist.
-The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
-It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.
-The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$.
-\end{itemize}
-
-We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsubsection{Minimal Twist}
-The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
-From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.
-
-\begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
-Moreover, the equivalence is $\U(1)$-equivariant.
+\vspace{-10pt}
+\paragraph{Twisting data:}
+In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
+In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.
+The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.
+Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.
+
+\begin{theorem} \label{3d_4_holo_A_twist_thm}
+The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
+The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
 \end{theorem}
 
-\subsubsection{Topological A Twist}
-Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
-Consider the 4-dimensional spacetime $V_\RR=L\times N$.
-Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
-Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist.
-Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
-
-\begin{thm}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
-Moreover, this equivalence is $\U(1)$-equivariant.
-\label{3d_4_A_twist_thm}
-\end{thm}
-
-\begin{cor}
-The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
-\end{cor}
-
-\subsubsection{Topological B Twist}
-We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
-$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
-Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
-Therefore, from Theorem \ref{thm:6dCSreduction} we obtain the following statement.
-
-\begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
+\begin{proof}
+To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
+\end{proof}
+
+\begin{theorem} \label{3d_2_B_twist_thm}
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+This theory is generally only $\ZZ/2\ZZ$-graded.
 \end{theorem}
+
+\begin{proof}
+Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
+\end{proof}
 
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;
-RR)$, acting on $W$ by its (Dirac) spin representation.
-
-In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three classes: 
-\begin{itemize}
- \item Rank 1.
-In this case $Q$ is minimal, with 2 invariant directions.
-Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
-The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
-It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.
-These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
-The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso G_R$.
-\end{itemize}
-
- We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsubsection{Minimal Twist}
-The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
-From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
+\vspace{-10pt}
+\paragraph{Twisting data:}
+The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.
+There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).
+The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.
 
 \begin{theorem} 
-The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
-Moreover, the equivalence is $\U(1)$-equivariant.
+The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
+The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
 \end{theorem}
-
-\subsubsection{Topological A Twist}
-From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
-
-\begin{theorem} 
-The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
-Moreover, this equivalence is $\U(1)$-equivariant.
-\end{theorem}
-
-\subsubsection{Topological B Twist}
-From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
 
@@
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
-Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
 \end{theorem}

### 2020-01-23 paper.tex

--- 2020-01-23 paper.tex
@@
 
-\begin{theorem}
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U\oplus \fg)/\fg)$.
+\begin{thm}
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
 \label{thm:4dholomorphictwist}
-\end{theorem}
+\end{thm}
 \begin{proof}

### 2020-01-23 paper.tex
5d refs
BRST

@@
 \item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)$ and $a \in\Omega^{0}(M; \gg)$;
-\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
-\item Matter bosons $\nu\in\Omega^{0,0}(M; U)$, $\phi\in\Omega^0(M; U)$.
-\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[-1]$, $\varphi \in \Omega^{2,0} (M ; U)[1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[1]$.
+\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[4n-2]$ and $a \in\Omega^{0}(M; \gg)[-4n+2]$;
+\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
+\item Matter bosons $\nu\in\Omega^{0,0}(M; U)[-2n]$, $\phi\in\Omega^0(M; U)[2n]$.
+\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[2n-1]$, $\varphi \in \Omega^{2,0} (M ; U)[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[-2n+1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 
-\begin{thm}
+\begin{theorem}
 The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$.

### 2020-01-23 paper.tex
Added links

--- 2020-01-23 paper.tex
@@
 \section*{Introduction} 
-\label{sec:intro}
+\label{sect:intro}
 \addcontentsline{toc}{section}{Introduction}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} 
- \item \emph{$\mc N=2$ intermediate twist.}
- \item \emph{$\mc N=2$ topological A twist.}
- \item \emph{$\mc N=2$ topological B twist.} 
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} \cite{KallenZabzine}
+ \item \emph{$\mc N=2$ intermediate twist.} \cite{ElliottPestun}
+ \item \emph{$\mc N=2$ topological A twist.} \cite{Anderson, QiuZabzine}
+ \item \emph{$\mc N=2$ topological B twist.} \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}
 \end{itemize}
@@
  \hline
- \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
  &&&$\bun_G(\CC^5)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
  &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
- \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
+ \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ Pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
  &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
+  && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ Impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
  &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
-  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
  &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
+  && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ Impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
  &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
- \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
+ \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{\hyperref[sect:6d11holomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ && \multirow{2}*{\hyperref[sect:6d11partialtwist]{Rank $(1,1)$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
  &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
  &&& $\bun_G(\CC \times \RR^4_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:6d11topologicaltwist]{Rank $(1,1)$ generic}} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
  &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
+ \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{\hyperref[sect:5dminimaltwist]{Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ && \multirow{2}*{\hyperref[sect:5dpartialtwist]{Rank $2$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
  &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
  &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:5drank2topologicaltwist] {Rank $2$ generic}} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
  &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{\hyperref[sect:4d4holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
+ && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(1,1)$}} & Mixed BF Theory & \multirow{2}*{3} \\
  &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4dBtwist] {Rank $(2,2)$ special}} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
  &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4dKapustintwist] {Rank $(2,1)$}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
  &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4dAtwist] {Rank $(2,0)$}} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
  &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
+  && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ generic}} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
  &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d_8_minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_8_B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_8_A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
  \hline
- \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
+ \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
  &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
- \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
+ \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
  &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
- \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
+ && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
  &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4d_2_donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
  &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
- \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
+ \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
@@
  \hline
- \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{\hyperref[sect:4d1holomorphictwist] {Rank $(1,0)$}} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
- \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
+ \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{\hyperref[sect:3dminimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
  &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
@@
 The first main ingredient is the Batalin-Vilkovisky formalism \cite{BatalinVilkovisky} for classical field theory (Section \ref{BV_section}), as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.
-The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sec:susy}), following Baez and Huerta \cite{BaezHuerta}.
-We use this formalism to prove in Section \ref{sec:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
+The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}), following Baez and Huerta \cite{BaezHuerta}.
+We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
 We introduce the idea of dimensional reduction (Section \ref{dim_red_section}) for classical field theories to show that supersymmetry action are well-defined in lower dimensions.
@@
 
-\section{Supersymmetry} \label{sec:susy}
+\section{Supersymmetry} \label{sect:susy}
 Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.
 So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
-We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.
-
-\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
+We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sect:SYM} below.
+
+\subsection{Supersymmetry Algebras} \label{sect:susyalgebras}
 In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.
@@
 
-\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}
+\subsection{Two-dimensional Chiral Supersymmetry} \label{sect:2dchiral}
 
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sec:susyalgebras}.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sect:susyalgebras}.
 
@@
 
-\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}
+\section{Supersymmetric Yang--Mills theories} \label{sect:SYM}
 
@@
 \subsubsection{Partially topological twist}
+\label{sect:8dpartiallytopologicaltwist}
 
@@
 \subsubsection{Minimal twist}
+\label{sect:7dminimaltwist}
 
@@
 \subsubsection{Topological twist}
+\label{sect:7dtopologicaltwist}
 
@@
 \subsubsection{Partially topological twist}
+\label{sect:7dpartialtwist}
 
@@
 
-The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
+The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
 Let $U$ be a complex symplectic $\fg$-representation.
@@
 \subsubsection{Holomorphic twist}
-\label{sec:6dholomorphictwist}
+\label{sect:6dholomorphictwist}
 
@@
 \subsubsection{Holomorphic twist}
+\label{sect:6d11holomorphictwist}
 
@@
 \subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
+\label{sect:6d11partialtwist}
 
@@
 \subsubsection{Topological twist}
+\label{sect:6d11topologicaltwist}
 
@@
 \subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Twist}
+\label{sect:6drank22twist}
 
@@
 \subsubsection{Minimal twist}
+\label{sect:5d1minimaltwist}
 
@@
 We set $W^6_+=\det(L)^{-1/2}w_1\oplus \det(L)^{1/2} w_2$ as a representation of $\MU(L)$.
-By the results of Section \ref{sec:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
+By the results of Section \ref{sect:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
 
@@
 \subsubsection{Minimal twist}
+\label{sect:5dminimaltwist}
 
@@
 \subsubsection{Rank 2 partially topological twist}
+\label{sect:5dpartialtwist}
 
@@
 \subsubsection{Rank 2 topological twist}
+\label{sect:5drank2topologicaltwist}
 
@@
 \subsubsection{Rank 4 twist}
+\label{sect:5drank4twist}
 
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{4d_1_section}
-The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{sect:4d_1_section}
+The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
 Let $R$ be a complex $\fg$-representation.
@@
 \subsubsection{Holomorphic twist}
+\label{sect:4d1holomorphictwist}
 
@@
 \[
-\begin{array}{cccccc}
-\alpha_n & \colon & \U(1) & \rightarrow & \SU(2)\times \U(1)\\
-& & z & \mapsto & \left({\rm diag}(z^{2n}, z^{-2n}) , z^{-2n+1} \right)
+\begin{array}{ccccc}
+\alpha_n \colon & \U(1) & \rightarrow & \SU(2)\times \U(1)\\
+&  z & \mapsto & \left({\rm diag}(z^{2n}, z^{-2n}) , z^{-2n+1} \right)
 \end{array}
@@
 4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory.
-Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
+Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
 \begin{align*}
@@
 
+\subsubsection{Holomorphic Twist}
+\label{sect:4d4holomorphictwist}
+
+\subsubsection{Topological A Twist}
+\label{sect:4dAtwist}
+
 \begin{theorem}
@@
 \end{theorem}
+
+\subsubsection{Partially Topological Twist}
+\label{sect:4d4partialtwist}
+
+\subsubsection{Kapustin Twist}
+\label{sect:4dKapustintwist}
 
@@
 \end{theorem}
+
+\subsubsection{Topological B Twist}
+\label{sect:4dBtwist}
+
+\subsubsection{Topological qGL Twist}
+\label{sect:4dqgltwist}
 
@@
 
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} 
+\label{sect:3d_2_section}
 We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
@@
 
-We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
+We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \subsubsection{Minimal Twist}
+\label{sect:3dminimaltwist}
 A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.
@@
 \subsubsection{Minimal Twist}
+\label{sect:3d_4_minimal_twist}
 The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
@@
 \subsubsection{Topological A Twist}
+\label{sect:3d_4_A_twist}
 Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
@@
 \subsubsection{Topological B Twist}
+\label{sect:3d_4_B_twist}
 We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
-$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
+$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sect:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
 Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
@@
 \subsubsection{Minimal Twist}
+\label{sect:3d_8_minimal_twist}
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
@@
 \subsubsection{Topological A Twist}
+\label{sect:3d_8_A_Twist}
 From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
@@
 \subsubsection{Topological B Twist}
+\label{sect:3d_8_B_Twist}
 From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
@@
 We additionally have gauge theories with chiral, i.e.
-$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.
+$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sect:2dchiral}.
 We'll address twists for these two classes of theory in turn.
 
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
 First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sect:2d(4,4)}
 We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sect:2d(0,2)}
 
@@
 given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
 Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
@@
 Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
 Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 

### 2020-01-23 paper.tex
woops
credited Dylan's work

@@
 It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
-When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter \chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
+When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter.
+This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}.
+\chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
  \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
  &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
- \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ Pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
+ \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
  &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
@@
  &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ Impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
+  && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
  &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
@@
 We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.
+We are also grateful to Dylan Butson for kind discussion of his related forthcoming work.
 The research of CE on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).

### 2020-01-23 paper.tex
still confused about 3d N=4

@@
 \item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[4n-2]$ and $a \in\Omega^{0}(M; \gg)[-4n+2]$;
-\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[1]$.
+\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[4n-1]$.
 \item Matter bosons $\nu\in\Omega^{0,0}(M; U)[-2n]$, $\phi\in\Omega^0(M; U)[2n]$.
@@
 The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation.
-\chris{or should it be $\spin(3;\RR)$?}
 
@@
 Rank 2 supercharges are topological.
-A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore a volume form.
-There are two orbits for the $G_R = \SO(4)$ action on the space of volume forms, which we refer to as the $A$-twist and the $B$-twist.
-The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
+A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
+The $G_R = \SO(4)$-action also corresponds to a choice of orientation, so there are two $G_R$ orbits: those determining the same orientation, and those determining the opposite orientation.
+We refer to as the $A$-twist and the $B$-twist respectively.
+When we dimensionally reduce the rank $(2,0)$ twist from 4d we obtain the A-twist.
 It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.

### 2020-01-23 paper.tex
4d N=2

--- 2020-01-23 paper.tex
@@
 \section*{Introduction} 
-\label{sect:intro}
+\label{sec:intro}
 \addcontentsline{toc}{section}{Introduction}
@@
  \hline
- \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
  &&&$\bun_G(\CC^5)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
  &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
- \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ Pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
+ \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
  &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ Impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
+  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
  &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
-  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
  &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ Impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
+  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
  &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
- \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{\hyperref[sect:6d11holomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
+ \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6d11partialtwist]{Rank $(1,1)$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
  &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
+ && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
  &&& $\bun_G(\CC \times \RR^4_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6d11topologicaltwist]{Rank $(1,1)$ generic}} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
+ && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
  &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{\hyperref[sect:5dminimaltwist]{Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
+ \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5dpartialtwist]{Rank $2$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
+ && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
  &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
  &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5drank2topologicaltwist] {Rank $2$ generic}} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
  &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{\hyperref[sect:4d4holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(1,1)$}} & Mixed BF Theory & \multirow{2}*{3} \\
+ && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
  &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dBtwist] {Rank $(2,2)$ special}} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
  &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dKapustintwist] {Rank $(2,1)$}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
  &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dAtwist] {Rank $(2,0)$}} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
  &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ generic}} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
+  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
  &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d_8_minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_8_B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_8_A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
  \hline
- \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
+ \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
  &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
- \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
+ \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
  &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
- \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
+ && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
  &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d_2_donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
  &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
- \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
+ \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
@@
  \hline
- \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{\hyperref[sect:4d1holomorphictwist] {Rank $(1,0)$}} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
+ \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
- \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{\hyperref[sect:3dminimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
+ \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
  &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
@@
 The first main ingredient is the Batalin-Vilkovisky formalism \cite{BatalinVilkovisky} for classical field theory (Section \ref{BV_section}), as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.
-The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}), following Baez and Huerta \cite{BaezHuerta}.
-We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
+The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sec:susy}), following Baez and Huerta \cite{BaezHuerta}.
+We use this formalism to prove in Section \ref{sec:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
 We introduce the idea of dimensional reduction (Section \ref{dim_red_section}) for classical field theories to show that supersymmetry action are well-defined in lower dimensions.
@@
 
-\section{Supersymmetry} \label{sect:susy}
+\section{Supersymmetry} \label{sec:susy}
 Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.
 So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
-We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sect:SYM} below.
-
-\subsection{Supersymmetry Algebras} \label{sect:susyalgebras}
+We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.
+
+\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
 In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.
@@
 
-\subsection{Two-dimensional Chiral Supersymmetry} \label{sect:2dchiral}
+\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}
 
@@
 \[G_W = G_V\times \Spin(W^\perp_\RR).\]
-This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sect:susyalgebras}.
+This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sec:susyalgebras}.
 
@@
 
-\section{Supersymmetric Yang--Mills theories} \label{sect:SYM}
+\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}
 
@@
 \subsubsection{Partially topological twist}
-\label{sect:8dpartiallytopologicaltwist}
 
@@
 \subsubsection{Minimal twist}
-\label{sect:7dminimaltwist}
 
@@
 \subsubsection{Topological twist}
-\label{sect:7dtopologicaltwist}
 
@@
 \subsubsection{Partially topological twist}
-\label{sect:7dpartialtwist}
 
@@
 
-The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
+The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
 Let $U$ be a complex symplectic $\fg$-representation.
@@
 \subsubsection{Holomorphic twist}
-\label{sect:6dholomorphictwist}
+\label{sec:6dholomorphictwist}
 
@@
 \subsubsection{Holomorphic twist}
-\label{sect:6d11holomorphictwist}
 
@@
 \subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
-\label{sect:6d11partialtwist}
 
@@
 \subsubsection{Topological twist}
-\label{sect:6d11topologicaltwist}
 
@@
 \subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Twist}
-\label{sect:6drank22twist}
 
@@
 \subsubsection{Minimal twist}
-\label{sect:5d1minimaltwist}
 
@@
 We set $W^6_+=\det(L)^{-1/2}w_1\oplus \det(L)^{1/2} w_2$ as a representation of $\MU(L)$.
-By the results of Section \ref{sect:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
+By the results of Section \ref{sec:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.
 
@@
 \subsubsection{Minimal twist}
-\label{sect:5dminimaltwist}
 
@@
 \subsubsection{Rank 2 partially topological twist}
-\label{sect:5dpartialtwist}
 
@@
 \subsubsection{Rank 2 topological twist}
-\label{sect:5drank2topologicaltwist}
 
@@
 \subsubsection{Rank 4 twist}
-\label{sect:5drank4twist}
 
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{sect:4d_1_section}
-The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{4d_1_section}
+The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.
 Let $R$ be a complex $\fg$-representation.
@@
 \subsubsection{Holomorphic twist}
-\label{sect:4d1holomorphictwist}
 
@@
 
+If the representation $U$ is $T^*R = R\oplus R^*$, the $R$-symmetry group is enhanced to $G_R=\SU(W)\times \U(1)\times \U(1)$, where the last $\U(1)$ acts with weight $1$ on $R$ and weight $-1$ on $R^*$.
+
 There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$:
@@
 The corresponding twists are topological (the \emph{Donaldson twist}).
+There is a twisting homomorphism from $\MU(2$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
  \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
+There is a twisting homomorphism $\U(1)\times \U(1)\rightarrow \Spin(4, \RR)$.
+For a general $U$ there is no compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
 \end{itemize}
@@
 
+Note that the $\MU(2)$-action on the fields factors through a $\U(2)$-action since the square roots $\det(L)^{1/2}$ have canceled out.
+
 \begin{theorem}
@@
 4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory.
-Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
+Under dimensional reduction the 6d fields from Section \ref{sec:6dholomorphictwist} decompose as follows:
 \begin{align*}
@@
 These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
-Finally, we observe that the twisted theory manifestly descends to a $\U(2)$-equivariant theory along the natural homomorphism $\MU(2) \to \U(2)$, and all identifications are $\U(2)$-equivariant. 
 \end{proof}
@@
 
-Let $S^{2n}_\pm$ be the semi-spin representations of $\Spin(2n , \CC)$.
-The decomposition of $S^{6}_+$ under the subgroup $\Spin(4 , \CC) \times \Spin(2, \CC) \subset \Spin(6,\CC)$ is
-\[
-S_+^6 = S_+^4 \otimes S_+^2 \oplus S_-^4 \otimes S_-^2 .
-\]
-The odd part of the $\cN=2$ supersymmetry algebra is 
-\[
-\Sigma = S_+^6 \otimes W_+ \cong S_+^4 \otimes W \oplus S_-^4 \otimes W^* .
-\]
-where $W_+$ is a complex two-dimensional symplectic vector space. 
-From this, we have identifications $W = W_+ \otimes S_+^2$ and $W^* = W_+ \otimes S_-^2$. 
-Let $\{u \otimes \alpha_+, v \otimes \alpha_+\}$ be a basis for $W = W_+ \otimes S_+^2$ where $\{u,v\}$ is a symplectic basis for $W_+$ and $\alpha_+$ is a basis element for $S_+^2$. 
-%A general supercharge $Q \in S_+^4 \otimes W$ is of the form
-%\[
-%Q = s_+ \otimes u \otimes \alpha_+ + s_+' \otimes v \otimes \alpha_+ 
-%\]
-%where $s_+, s_+' \in S_+^{4}$.
-
-Let $\{s^1_+, s_+^2\}$ be a basis for $S_+^4$. 
-We twist by a supercharge of the form
+Consider the same twisting homomorphism $\phi\colon \MU(2)\rightarrow G_R$ as in Section \ref{sect:4d_2_holomorphictwist} and $\alpha=\alpha_0\colon \U(1)\rightarrow G_R$.
+With respect to the $\MU(2)$-action we have a decomposition
+\[S_+\otimes W\cong \CC Q_0 \oplus \det(L)^{-1}\oplus \CC \Bar{Q}_0\oplus \det(L).\]
+
+Consider a family of supercharges
 \begin{equation} 
 \label{eq:4dHodgefamily}
-Q_t = s_+^1 \otimes u \otimes \alpha_+ + t s_+^2 \otimes v \otimes \alpha_+
+Q_t = Q_0 + t \Bar{Q}_0
 \end{equation}
-where $t \in \CC$. 
-When $t \ne 0$, this supercharge is of rank $(2,0)$. 
-At $t = 0$ it reduces to the holomorphic supercharge from the previous section.
-
-Let $V_\RR = \RR^4$ and $V=V_\RR\otimes_\RR\CC$. 
-Denote by $L\subset V$ the $i$-eigenspace of the complex structure determined by the holomorphic supercharge $Q_0$. 
-We utilize the same notation for the fields of super Yang-Mills theory as in the previous section. 
-\brian{discuss twisting homomorphism}
+where $t \in \CC$. When $t \ne 0$, this supercharge is of rank $(2,0)$, while at $t = 0$ it reduces to the holomorphic supercharge from the previous section.
+
+\begin{remark}
+With respect to $\alpha_n\colon \U(1)\rightarrow G_R$ the supercharge $Q_0$ has weight $1$, while $\Bar{Q}_0$ has weight $-4n+1$. So, requiring $Q_t$ to have weight $1$ forces us to choose $n=0$.
+\end{remark}
 
@@
 \end{prop}
-\begin{proof}
-We first write down the fields and the functionals in $\Spin(4)$-notation.
-The fields of $4d \cN=2$ decompose as:
-\begin{itemize}
- \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(a \otimes \alpha_-^{\otimes 2} ,\Tilde{a} \otimes \alpha_+^{\otimes 2}) \in \Omega^0(\RR^4; (S^2_-)^{\otimes 2} \otimes \gg \oplus  (S^2_-)^{\otimes 2} \otimes \gg)$.
-  \item $\gg$-valued fermions: a $W = W_+ \otimes S_+^2$-valued Dirac spinor $\lambda = (\lambda_+ \otimes \alpha_+, \lambda_-\otimes \alpha_-) \in \Omega^0(\RR^4; (S^4_+ \otimes W \oplus S^4_- \otimes W^*) \otimes \gg)$.
- \item $U$-valued bosons: a $W = W_+ \otimes S_+^2$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W_+ \otimes S_+^2 \otimes U)$.
- \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+ \otimes \alpha_- ,\psi_- \otimes \alpha_+) \in \Omega^0(\RR^4; (S^4_+ \otimes S_-^2 \oplus S^4_- \otimes S_+^2) \otimes U)$.
- \item a ghost $c \in \Omega^0(\RR^4 ; \gg)$.
-\end{itemize}
-The anti-fields decompose in an analogous way.
-
-For a general supercharge $Q_+ \otimes \alpha_+ \in S_+^4 \otimes W = S^4_+ \otimes W_+ \otimes S_+^2$, the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ decompose as:
-\begin{align*}
-I^{(1)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \bigg(-( \Gamma(Q_+,\lambda_-), A^*) + (\langle Q_+,\lambda_+\rangle , \Tilde{a}^* ) + \\
-&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*) + (\rho(\d_A a)Q_+, \lambda_-^*) \bigg)\\
-I^{(1)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \dvol (((Q_+,\psi_+), \phi^*) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)) \\
-I^{(2)}_{\mr{gauge}}(Q_+ \otimes \alpha_+) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_+^*,\lambda_+^*) - \frac 12  (Q_+, \lambda_+^*)^2 - (Q_+,Q_+) a c^* \big) \\
-I^{(2)}_{\mr{matter}}(Q_+ \otimes \alpha_+) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*) .
-\end{align*}
-
-The result follows from further decomposing the fields under the action of $\MU(2)$. 
-\end{proof}
-
-\begin{theorem}
-The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, (U\ham g)_{\mr{Hod}})$.
+
+\begin{theorem}
+The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, ((U\oplus \fg[2]) / \fg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(2)$-equivariant.
@@
 
-We finally consider the twist with respect to a rank $(1,1)$ supercharge. 
-We have a twisting homomorphism
-\[
-\phi = (1,1) : \U(1) \times \U(1) \to \U(2) .
-\]
-\brian{Just like holomorphic, I may want $(1,-1)$.}
+We finally consider the twist with respect to a rank $(1,1)$ supercharge. We have a twisting homomorphism
+\[
+\phi \colon \Spin(2, \RR) \times \Spin(2, \RR) \to G_R=\SU(2)\times \U(1),
+\]
+where on the first factor $\Spin(2, \RR)\cong \U(1)\hookrightarrow \SU(2)$ is given by the diagonal embedding and on the second factor $\Spin(2, \RR)\cong\U(1)$ is the obvious isomorphism.
+If we denote by $S_\pm^1, S_\pm^2$ the semi-spin representations of the two $\Spin(2, \RR)$, we have
+\[W \cong S_+^2\otimes (S_+^1\oplus S_-^1).\]
+The semi-spin representations of $\Spin(4, \RR)$ decompose with respect to $\Spin(2, \RR)\times \Spin(2, \RR)\subset \Spin(4, \RR)$ as
+\[S_+\cong S_+^1\otimes S_+^2\oplus S_-^1\otimes S_-^2,\qquad S_-\cong S_+^1\otimes S_-^2\oplus S_-^1\otimes S_+^2.\]
+
+So, both $S_+\otimes W$ and $S_-\otimes W^*$ contain a trivial one-dimensional subspace and hence we obtain a rank $(1, 1)$ square-zero supercharge.
 
@@
 The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U\ham \gg)$.
-Moreover, this identification is $\U(1) \times \U(1)$-equivariant.
-This theory is generally only $\ZZ/2\ZZ$-graded.
-\end{theorem}
-
-\begin{proof}
-A supercharge of rank $(1,1)$ automatically lifts to a rank $1$ supercharge in the $5d$ $\cN=1$ supersymmetry algebra.
+Moreover, this equivalence is $\U(1) \times \Spin(2, \RR)$-equivariant.
+\end{theorem}
+\begin{proof}
+Any square-zero supercharge of rank $(1, 1)$ lifts to a rank $1$ supercharge in the 5d $\cN=1$ supersymmetry algebra.
 The result then follows from Theorem \ref{thm:6dCSreduction} applied to $L = \CC$. 
@@
 
-If $U = T^* R$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\U(2)\times \U(1)$. 
+If $U = T^* R$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \U(1)$.
 The extra $\U(1)$ acts trivially on $W$, by weight $+1$ on $R$ and weight $-1$ on $R^*$.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow  \U(2) \times \U(1)$ given by the diagonal embedding into the first two components \brian{Again like holomorphic, I may want the skew-diagonal $(1,-1)$ into $\U(2)$ and identity on $\U(1)$.}.
-We also use a new twisting homomorphism
-\[\wt\phi\colon \U(1)\times \U(1) \xrightarrow{\alpha\times\id} \U(2) \times \U(1) = G_R.\]
+
+We have a homomorphism $\alpha\colon \U(1)\rightarrow  \SU(2)\times \U(1) \times \U(1)$ given by the diagonal embedding into the first and the third components.
+We also use a new twisting homomorphism $\wt\phi\colon \Spin(2, \RR)\times \Spin(2, \RR)\rightarrow G_R$ given by multiplying $\phi$ with the identity homomorphism from the first $\Spin(2, \RR)$ factor to the last $\U(1)$ factor in $G_R$ (cf.
+the definition of $\alpha$ and $\wt\phi$ in Section \ref{sec:6dholomorphictwist}).
 
 \begin{theorem}\label{thm:4d_11_twistgraded}
-The minimal twist of 4d $\cN=2$ super Yang--Mills on $M=\CC \times \RR^2$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC \times \RR^2_{\mathrm{dR}}, T^*[2] (R/\fg))$.
-Moreover, the equivalence is $\U(1)\times \U(1)$-equivariant.
+The minimal twist of 4d $\cN=2$ super Yang--Mills on $M=\CC \times \RR^2$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC \times \RR^2_{\mathrm{dR}}, R/\fg)$.
+Moreover, the equivalence is $\U(1)\times \Spin(2, \RR)$-equivariant.
 \end{theorem}
@@
 
-\subsubsection{Holomorphic Twist}
-\label{sect:4d4holomorphictwist}
-
-\subsubsection{Topological A Twist}
-\label{sect:4dAtwist}
-
 \begin{theorem}
@@
 \end{theorem}
-
-\subsubsection{Partially Topological Twist}
-\label{sect:4d4partialtwist}
-
-\subsubsection{Kapustin Twist}
-\label{sect:4dKapustintwist}
 
@@
 \end{theorem}
-
-\subsubsection{Topological B Twist}
-\label{sect:4dBtwist}
-
-\subsubsection{Topological qGL Twist}
-\label{sect:4dqgltwist}
 
@@
 
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} 
-\label{sect:3d_2_section}
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
 We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
@@
 
-We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
+We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 \subsubsection{Minimal Twist}
-\label{sect:3dminimaltwist}
 A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.
@@
 \subsubsection{Minimal Twist}
-\label{sect:3d_4_minimal_twist}
 The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
@@
 \subsubsection{Topological A Twist}
-\label{sect:3d_4_A_twist}
 Let $L=\CC$ equipped with a Hermitian structure and a complex half density, $N_\RR=\RR$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
@@
 \subsubsection{Topological B Twist}
-\label{sect:3d_4_B_twist}
 We consider $V_\RR=\RR^3$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
-$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sect:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
+$V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sec:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
 Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
@@
 \subsubsection{Minimal Twist}
-\label{sect:3d_8_minimal_twist}
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
@@
 \subsubsection{Topological A Twist}
-\label{sect:3d_8_A_Twist}
 From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
@@
 \subsubsection{Topological B Twist}
-\label{sect:3d_8_B_Twist}
 From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
@@
 We additionally have gauge theories with chiral, i.e.
-$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sect:2dchiral}.
+$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.
 We'll address twists for these two classes of theory in turn.
 
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
 First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.
 In addition to the ghost $c$, the fields we obtain are
@@
 
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sect:2d(4,4)}
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
 We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sect:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}
 
@@
 given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
 Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
@@
 Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
 Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 

### 2020-01-23 paper.tex

--- 2020-01-23 paper.tex
@@
 \end{itemize}
+
+Note that the $\MU(2)$-action on the fields factors through a $\U(2)$-action since the square roots $\det(L)^{1/2}$ have canceled out.
 

### 2020-01-24 paper.tex
beginning N=4

@@
 
+\brian{We have not defined the notation $\Omega^{0,\bu}, \Omega^{\bu,\bu}, \Omega^\bu$.}
+\brian{Also, define the notation $T^*[-1] {\rm Map}$. }
+
 \begin{remark} \label{mapping_stack_remark}
@@
 
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
- \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
+The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. 
+It admits $R$-symmetry group $G_R=\Spin(6; \RR)$ under which $W \cong S_+^6$ is the positive semi-spin representation and $W^* \cong S_-^6$.
+
 The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.  
 We have the following classes. 
-\chris{some comments claiming we'll discuss things above, to be added.
-Also this is to revisit after writing the below.}
-\begin{itemize}
- \item Rank $(1,0)$ (and $(0,1)$) supercharges.
+\chris{some comments claiming we'll discuss things above, to be added.  Also this is to revisit after writing the below.}
+\begin{itemize}
+\item Rank $(1,0)$ and $(0,1)$ supercharges.  
 Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.  
-They are compatible with $\SU(2)_- \sub \Spin(4;\RR)$, which can be promoted to a twisting homomorphism from the group $\mr U(2)$ as we say in the 4d $\mc N=1$ section above.
+They are compatible with the subgroup $\U(2) \sub \Spin(6;\RR) = \SU(4)$.
  \item Rank $(2,0)$ (and $(0,2)$) supercharges.
@@
 
+We consider a rank $1$ supercharge $Q$ which factors through a $\cN=2$ subalgebra (in fact $\cN=1$ subalgebra).
+
+\begin{theorem}
+The holomorphic twist of 4d $\cN=4$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the holomorphic BF theory on $\CC^2_{\rm Dol}$ with the space of fields $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg) = T^*[-1] \higgs_G(\CC^2)$.
+Moreover, the equivalence is $\U(2)$-equivariant.
+\label{thm:4d4holomorphictwist}
+\end{theorem}
+\begin{proof}
+The $4d \cN=4$ super Yang-Mills theory viewed as a $\cN=2$ theory is $\cN=2$ Yang-Mills theory with matter in the adjoint representation. 
+It follows that the twist is given by $T^*[-1] \map(\CC^2 , (\fg \oplus \fg) / \fg)$. 
+\brian{Need to be careful about $\U(2)$ action to get Dolbeault stack.}
+\end{proof}
+
 \subsubsection{Topological A Twist}
 \label{sect:4dAtwist}
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
+ \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+\end{itemize}
 

### 2020-01-24 paper.tex

--- 2020-01-23 paper.tex
@@
 \newcommand{\gauge}{\mathrm{gauge}}
+\newcommand{\Gm}{\mathbb{G}_m}
 \newcommand{\Hod}{\mathrm{Hod}}
@@
 \renewcommand{\Re}{\mathrm{Re}}
+\newcommand{\Sect}{\mathrm{Sect}}
 \renewcommand{\U}{\mathrm{U}}
@@
 
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
 
@@
 \[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
-
-Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
-\begin{align*}
-E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
-\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
-\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
-\end{align*}
-and the action functional as before.
 \label{ex:CSHamiltonianreduction}
+\end{example}
+
+We will also sometimes use the following variant of the generalized Chern--Simons theory (see also \cite{GinzburgRozenblyum}).
+
+\begin{definition}
+Let $m$ be a positive integer.
+Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$.
+We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
+\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(m)\otimes K_X^{n/m} [1]\]
+and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
+\end{definition}
+
+We denote the space of fields $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.
+
+\begin{example}
+Consider the setting of Example \ref{ex:CSHamiltonianreduction}.
+The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$.
+With respec to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
+\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
 \end{example}
@@
 Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
+\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, (V\otimes K_{\CC^{n_1}}^{1/2})\ham\fg).\]
 Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
@@
 These are holomorphic.
-Moreover, we have an isomorphism $\alpha\colon \U(1)\xrightarrow{\sim} \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
+Moreover, we have an embedding $\alpha\colon \U(1)\hookrightarrow \Spin(2, \CC)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory.
 Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$.
-We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\cong G_R$, so the twisted theory carries an action of $\MU(4)$.
+We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\xrightarrow{\alpha} G_R$, so the twisted theory carries an action of $\MU(4)$.
 
@@
 The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$.
-We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
+We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \CC)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
 \end{itemize}
@@
 
-We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \RR)$ under which $Q$ becomes scalar.
-Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action.
+We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \CC)$ under which $Q$ becomes scalar.
+Moreover, we have an embedding $\alpha\colon \U(1)\subset\Spin(2, \CC)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action.
 In fact, this action will factor through $\U(4)$ by a direct observation.
@@
 \begin{theorem}
-The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$.
+The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $T^*[-1]\map(M, B\fg)$.
 Moreover, the equivalence is $\U(4)$-equivariant.
@@
 \]
-concentrated in cohomological degrees $-2, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory.
+concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
 \end{proof}
@@
 Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$.
-We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.
+We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \CC)$ given by projection on the second factor.
 
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \CC)$ with $W$ the two-dimensional spin representation.
 
@@
 the number of invariant directions is 4.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
-We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \RR)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \CC)$ under which they have weight $1$.
+We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \CC)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.
 
@@
 These are topological and stabilized by $G_2\subset \Spin(7, \CC)$.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which they have weight $1$.
 
@@
 These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
-We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor, so tht theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
+We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection on the second factor, so the theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
 \end{itemize}
@@
 The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges.
-Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$.
-We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
-\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]
-
-\begin{theorem}
-The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, T^*[3] B\fg)$.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(2, \CC)\times \Spin(N_\RR)$.
+We consider the grading $\alpha\colon \U(1)\rightarrow G_R$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
+\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\Spin(2, \RR)\times \Spin(N_\RR).\]
+
+\begin{theorem}
+The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(L\times (N_\RR)_{\mr{dR}}, B\fg)$.
 Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
@@
 Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant.
-By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
 \end{proof}
@@
 \begin{theorem}
-The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$.
+The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC^3\times \RR_{\mr{dR}}, B\fg)$.
 Moreover, the equivalence is $\U(3)$-equivariant.
@@
 Finally, we discuss the case of a partially topological twist.
-We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor.
+We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection on the second factor.
 
@@
 \begin{itemize}
-\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.
-
-\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
+\item In general, the theory admits an $R$-symmetry group $G_R=\SL(2, \CC)$ with $W_+$ the two-dimensional defining representation.
+
+\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SL(2, \CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
 \end{itemize}
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory.
-If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading.
+If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SL(2, \CC)\times \GL(1, \CC)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading.
 Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$.
-We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(3)$-action.
+We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SL(2, \CC)$, so the twisted theory carries an $\MU(3)$-action.
 \end{itemize}
@@
 
-We fix an embedding $\U(1)\subset \SU(2)$ under which $w_1\in W_+$ has weight $1$. Under the composite
-\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
+We fix an embedding $\U(1)\subset \SL(2, \CC)$ under which $w_1\in W_+$ has weight $1$. Under the composite
+\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SL(2, \CC)\]
 we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.
@@
 \begin{theorem}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$.
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\Sect(M, (U\otimes K_M^{1/2})\ham \fg)$.
 Moreover, the equivalence is $\MU(3)$-equivariant.
@@
 
-If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$.
-We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
+If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SL(2, \CC)\times \GL(1, \CC)$.
+We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SL(2, \CC)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge.
 We may also use a new twisting homomorphism
@@
 \begin{theorem}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (R/\fg))$.
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $T^*[-1]\map(M, R/\fg)$.
 Moreover, the equivalence is $\U(3)$-equivariant.
@@
 The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
-It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.
+It admits $R$-symmetry group $G_R=\Spin(4, \CC)$ under which $W_+, W_-$ are the two semi-spin representations.
 
@@
 These automatically square to zero and have 4 invariant directions.
-There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SL(2, CC)\times \SL(2, \CC)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
 
@@
 These automatically square to zero and are topological.
-Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.
+Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SL(2, \CC)\times \SL(2, \CC)$ given by the diagonal embedding.
 
@@
 The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory.
-There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
+The twisting homomorphism is given by the obvious embedding $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \CC)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
 \end{itemize}
@@
 The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$.
-Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills.
+Under this isomorphism the R-symmetry group $\SL(2, \CC)\times \GL(1, \CC)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SL(2, \CC)\times \SL(2, \CC)$ of 6d $\cN=(1, 1)$ super Yang--Mills.
 In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.
@@
 \begin{theorem}
-The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$.
+The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $T^*[-1]\map(M, \fg/\fg)$.
 Moreover, the equivalence is $\U(3)$-equivariant.
@@
 \begin{theorem}
-The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$.
+The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC^2\times \RR^2_{\mathrm{dR}}, B\fg)$.
 Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
@@
 \begin{itemize}
-\item For a general $U$ the $R$-symmetry group is $G_R=\SU(2)$ with $W$ the two-dimensional defining representation.
-
-\item For $U=T^* R$ the $R$-symmetry group is $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
+\item For a general $U$ the $R$-symmetry group is $G_R=\SL(2, \CC)$ with $W$ the two-dimensional defining representation.
+
+\item For $U=T^* R$ the $R$-symmetry group is $G_R=\SL(2, \CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
 \end{itemize}
@@
 \item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions.
-There is a twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(2)$-action.
+There is a twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SL(2, \CC)$, so the twisted theory carries an $\MU(2)$-action.
 \end{itemize}
@@
 A square-zero supercharge $Q$ has rank 1, i.e. $Q=q_+\otimes w_1$ for some $w_1\in W$. We also choose $w_2\in W$ such that $(w_1, w_2) = 1$. We have a twisting homomorphism
-\[\phi\colon\MU(2)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
+\[\phi\colon\MU(2)\xrightarrow{\det^{1/2}}\U(1)\subset \SL(2, \CC)\]
 such that $W\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.
@@
 The dimensional reduction of 6d super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges.
-Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU(2)\times \Spin(N_\RR)$.
+Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SL(2, \CC)\times \Spin(N_\RR)$.
 We consider a twisting homomorphism
-\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SU(2)\times \Spin(N_\RR)\]
+\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SL(2, \CC)\times \Spin(N_\RR)\]
 whose first component is $\MU(L)\rightarrow \SU(2)$ as before and the second component is the identity.
@@
 \begin{theorem}
-The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, U\ham \fg)$.
+The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\Sect(L\times (N_\RR)_{\mr{dR}}, (U\otimes K_L^{1/2})\ham \fg)$.
 Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
@@
 \begin{proof}
-By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\map(L\times N, U\ham \fg)$.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, U\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\Sect(L\times N, (U\otimes K_L^{1/2})\ham \fg)$.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\Sect(L\times N_\RR, (U\otimes K_L^{1/2})\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
 \end{proof}
@@
 \begin{theorem}
-The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, U\ham \fg)$.
+The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\Sect(\CC^2\times \RR_{\mathrm{dR}}, (U\otimes K_{\CC^2}^{1/2})\ham \fg)$.
 Moreover, the equivalence is $\MU(2)$-equivariant.
@@
 
-If $U$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \Spin(N_\RR)$.
-We have a homomorphism $\alpha\colon \U(1)\rightarrow \SU(2)\times \U(1)\times \Spin(N_\RR)$ given by the diagonal embedding into the first two components.
+If $U$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SL(2, \CC)\times \GL(1, \CC)\times \Spin(N_\RR)$.
+We have a homomorphism $\alpha\colon \U(1)\rightarrow \SL(2, \CC)\times \GL(1, \CC)\times \Spin(N_\RR)$ given by the diagonal embedding into the first two components.
 We also use a new twisting homomorphism
@@
 \begin{theorem}
-The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2] (R/\fg))$.
+The minimal twist of 5d $\cN=1$ super Yang--Mills on $M=\CC^2\times \RR$ with matter valued in the $\fg$-representation $U=T^* R=R\oplus R^*$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC^2\times \RR_{\mathrm{dR}}, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 The 5d $\cN=2$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
-It admits $R$-symmetry group $G_R=\Spin(5, \RR)$ under which $W$ is the 4-dimensional spin representation which carries a symplectic pairing.
+It admits $R$-symmetry group $G_R=\Spin(5, \CC)$ under which $W$ is the 4-dimensional spin representation which carries a symplectic pairing.
 
@@
 These automatically square to zero and have 4 invariant directions.
-There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(2, \RR)\times \Spin(3, \RR)\hookrightarrow G_R=\Spin(5, \RR)$.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(2, \RR)\times \Spin(3, \RR)\hookrightarrow G_R=\Spin(5, \CC)$.
 
@@
 These automatically square to zero and are topological.
-There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(4, \RR)\hookrightarrow G_R=\Spin(5, \RR)$.
-
-\item Rank 4. These are topological and do not admit a compatible homomorphism $\alpha$. There is the identity twisting homomorphism $\phi\colon \Spin(5, \RR)\rightarrow \Spin(5, \RR)$.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ and a twisting homomorphism $\phi\colon \Spin(4, \RR)\hookrightarrow G_R=\Spin(5, \CC)$.
+
+\item Rank 4. These are topological and do not admit a compatible homomorphism $\alpha$. There is the obvious twisting homomorphism $\phi\colon \Spin(5, \RR)\rightarrow \Spin(5, \CC)$.
 \end{itemize}
@@
 \begin{theorem}
-The minimal twist of 5d $\cN=2$ super Yang--Mills on $M=\CC^2\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR_{\mathrm{dR}}, T^*[2](\fg/\fg))$.
+The minimal twist of 5d $\cN=2$ super Yang--Mills on $M=\CC^2\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC^2\times \RR_{\mathrm{dR}}, \fg/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 \begin{theorem}
-The rank $2$ partially topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC\times \RR^3_{\mathrm{dR}}, T^*[4] B\fg)$.
+The rank $2$ partially topological twist of 5d $\cN=2$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC\times \RR^3_{\mathrm{dR}}, B\fg)$.
 Moreover, the equivalence is $\Spin(2, \RR)\times\Spin(3, \RR)$-equivariant.
@@
 We consider $\cN=1$ super Yang--Mills theory on $M=\RR^4$ with the Euclidean metric.
-The theory admits an $R$-symmetry group $G_R=\U(1)$ which acts on $W=\CC$ with weight $1$.
+The theory admits an $R$-symmetry group $G_R=\GL(1, \CC)$ which acts on $W=\CC$ with weight $1$.
 
@@
 Such supercharges are automatically square-zero and are holomorphic.
-The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory.
-Also, we have a compatible twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)$.
+The embedding $\alpha \colon \U(1) \hookrightarrow G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory.
+Also, we have a compatible twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow G_R$.
 \end{itemize}
@@
 
-The identity map $\alpha\colon \U(1)\cong G_R$ makes $Q$ weight $1$.
+The embedding $\alpha\colon \U(1)\hookrightarrow G_R$ makes $Q$ weight $1$.
 
@@
 The 4d $\cN=2$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$.
-It admits the $R$-symmetry group $G_R=\SU(W)\times \U(1)$ with $W$ the two-dimensional representation on which $\U(1)$ acts with weight $1$.
+Let $W$ be a two-dimensional complex symplectic vector space.
+The theory admits the $R$-symmetry group $G_R=\SL(W)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
 
@@
 \item Matter fermions $(\psi_-, \psi_+)\in\Omega^0(M; \Pi S_+\otimes U\oplus \Pi S_-\otimes U)$.
-\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
-\end{itemize}
-
-$\U(1)\subset G_R$ has the following action: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.
-
-If the representation $U$ is $T^*R = R\oplus R^*$, the $R$-symmetry group is enhanced to $G_R=\SU(W)\times \U(1)\times \U(1)$, where the last $\U(1)$ acts with weight $1$ on $R$ and weight $-1$ on $R^*$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+$\GL(1, \CC)\subset G_R$ has the following action: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.
+
+If the representation $U$ is $T^*R = R\oplus R^*$, the $R$-symmetry group is enhanced to $G_R=\SL(W)\times \GL(1, \CC)\times \GL(1, \CC)$, where the last $\GL(1, \CC)$ acts with weight $1$ on $R$ and weight $-1$ on $R^*$.
 
@@
 The corresponding twists are topological (the \emph{Donaldson twist}).
-There is a twisting homomorphism from $\MU(2$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
+There is a twisting homomorphism from $\MU(2)$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
  \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
-There is a twisting homomorphism $\U(1)\times \U(1)\rightarrow \Spin(4, \RR)$.
+There is a twisting homomorphism from $\Spin(2, \RR)\times \Spin(2, \RR)\subset \Spin(4, \RR)$.
 For a general $U$ there is no compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
@@
 
-Choose a basis for $W$ given by $\{w_1, w_2\}$ and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$.
+Choose a basis for $W$ given by $\{w_1, w_2\}$, where $(w_1, w_2) = 1$, and for concreteness we take $Q=q_+ \otimes w_1$ for some nonzero vector $q_+ \in S_+$.
 Denote by $L\subset V$ the image of $\Gamma(Q, -)\colon S_-\rightarrow V$.
@@
 
-Recall, the $R$-symmetry group is $G_R = \SU(2) \times \U(1)$.
-For any integer $n\in\ZZ$ consider the homomorphism 
+Recall that the $R$-symmetry group is $G_R = \SL(2, \CC) \times \GL(1, \CC)$. For any integer $n\in\ZZ$ consider the homomorphism 
 \[
 \begin{array}{ccccc}
-\alpha_n \colon & \U(1) & \rightarrow & \SU(2)\times \U(1)\\
+\alpha_n \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC)\\
 &  z & \mapsto & \left({\rm diag}(z^{2n}, z^{-2n}) , z^{-2n+1} \right)
@@
 \[
-\phi \colon \MU(2) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R
+\phi \colon \MU(2) \xto{\det^{1/2}} \U(1) \rightarrow G_R
 \]
@@
 \item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[4n-1]$.
-\item Matter bosons $\nu\in\Omega^{0,0}(M; U)[-2n]$, $\phi\in\Omega^0(M; U)[2n]$.
-\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U)[2n-1]$, $\varphi \in \Omega^{2,0} (M ; U)[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U)[-2n+1]$.
+\item Matter bosons $\nu\in\Omega^0(M; U\otimes K_M^{-1/2})[-2n]$, $\phi\in\Omega^0(M; U\otimes K_M^{1/2})[2n]$.
+\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U\otimes K_M^{1/2})[2n-1]$, $\varphi \in \Omega^{2,0} (M ; U\otimes K_M^{-1/2})[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U\otimes K_M^{-1/2})[-2n+1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 
-Note that the $\MU(2)$-action on the fields factors through a $\U(2)$-action since the square roots $\det(L)^{1/2}$ have canceled out.
-
-\begin{theorem}
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills on $M=\RR^4$ is perturbatively (with respect to the choice of twisting data $\alpha = \alpha_n$) is equivalent to the holomorphic BF theory on $M\cong\CC^2$ with the space of fields $T^*[-1] \map(M, (U[2n] \oplus \fg[-4n+2])/\fg)$.
-Moreover, the equivalence is $\U(2)$-equivariant.
+\begin{theorem}
+Fix the twisting datum $\alpha = \alpha_n$.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
+Moreover, the equivalence is $\MU(2)$-equivariant.
 \label{thm:4dholomorphictwist}
@@
 These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
+\pavel{Brian}
 \end{proof}
@@
 The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist. \pavel{Brian}
 \end{remark}
@@
 \begin{theorem}
-The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2, ((U\oplus \fg[2]) / \fg)_{\mr{Hod}})$.
-Moreover, this equivalence is $\U(2)$-equivariant.
+The twist of 4d $\cN=2$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\Sect\left(\CC^2, \left((U\otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$.
+Moreover, this equivalence is $\MU(2)$-equivariant.
 \label{thm:4dDonaldsontwist}
@@
 \]
-which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory. \pavel{Brian}
 \end{proof}
@@
 \[
-\phi \colon \Spin(2, \RR) \times \Spin(2, \RR) \to G_R=\SU(2)\times \U(1),
-\]
-where on the first factor $\Spin(2, \RR)\cong \U(1)\hookrightarrow \SU(2)$ is given by the diagonal embedding and on the second factor $\Spin(2, \RR)\cong\U(1)$ is the obvious isomorphism.
+\phi \colon \Spin(2, \RR) \times \Spin(2, \RR) \to G_R=\SL(W)\times \GL(1, \CC),
+\]
+where on the first factor $\Spin(2, \RR)\cong \U(1)\hookrightarrow \SL(2, \CC)$ is given by the diagonal embedding and on the second factor $\Spin(2, \RR)\hookrightarrow \GL(1, |CC)$ is the obvious inclusion.
 If we denote by $S_\pm^1, S_\pm^2$ the semi-spin representations of the two $\Spin(2, \RR)$, we have
@@
 
-If $U = T^* R$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SU(2)\times \U(1)\times \U(1)$.
-The extra $\U(1)$ acts trivially on $W$, by weight $+1$ on $R$ and weight $-1$ on $R^*$.
-
-We have a homomorphism $\alpha\colon \U(1)\rightarrow  \SU(2)\times \U(1) \times \U(1)$ given by the diagonal embedding into the first and the third components.
-We also use a new twisting homomorphism $\wt\phi\colon \Spin(2, \RR)\times \Spin(2, \RR)\rightarrow G_R$ given by multiplying $\phi$ with the identity homomorphism from the first $\Spin(2, \RR)$ factor to the last $\U(1)$ factor in $G_R$ (cf.
-the definition of $\alpha$ and $\wt\phi$ in Section \ref{sec:6dholomorphictwist}).
+If $U = T^* R$ is of cotangent type, we may enhance the $R$-symmetry group to $G_R=\SL(W)\times \GL(1, \CC)\times \GL(1, \CC)$.
+The last $\GL(1, \CC)$ acts trivially on $W$, by weight $+1$ on $R$ and weight $-1$ on $R^*$.
+
+We have a homomorphism $\alpha\colon \U(1)\rightarrow  \SL(W)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the first and the third components.
+We also use a new twisting homomorphism $\wt\phi\colon \Spin(2, \RR)\times \Spin(2, \RR)\rightarrow G_R$ given by multiplying $\phi$ with the obvious homomorphism from the first $\Spin(2, \RR)$ factor to the last $\GL(1, \CC)$ factor in $G_R$ (cf.
+the definition of $\alpha$ and $\wt\phi$ in Section \ref{sect:6dholomorphictwist}).
 
@@
 
+The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
+It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive semi-spin representation and $W^* \cong S_-^6$.
+
+Let us decompose the rotation group as $\Spin(4, \RR)\cong \SU(2)_+\times \SU(2)_-$.
+The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.
+We have the following classes.
+\begin{itemize}
+\item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.
+The corresponding twists are holomorphic.
+Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra.
+As before, they admit a $\ZZ$-grading and a twisting homomorphism from $\MU(2)$.
+
+\item Rank $(2, 0)$ and $(0, 2)$ supercharges automatically square to zero.
+The corresponding twists are topological.
+Such twists factor through a copy of the $\cN = 2$ supersymmetry algebra.
+They admit the following twisting homomorphisms:
+ \begin{enumerate}
+  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \times \SU(2)_- \to \SL(4,\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
+This is the twisting homomorphism that comes from the $\cN=2$ supersymmetry algebra.
+  \item The Kapustin--Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \times \SU(2)_- \to \SL(4,\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
+  \item The Vafa--Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \times \SU(2)_- \to \SL(4, \CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
+ \end{enumerate}
+
+ \item Rank $(1,1)$ supercharges.
+Such supercharges have three invariant directions.
+They factor through a copy of the $\cN=2$ supersymmetry algebra.
+As before, they admit a twisting homomorphism from $\Spin(2, \RR)\times \Spin(2, \RR)$ and admit a $\ZZ$-grading.
+
+ \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, compatible with a twisting homomorphism from $\MU(2)$ and admit a $\ZZ$-grading.
+
+ \item Rank $(2,2)$ square-zero supercharges are topological. They correspond to a choice of an exact sequence
+ \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
+\end{itemize}
+
+\subsubsection{Holomorphic Twist}
+\label{sect:4d4holomorphictwist}
+
+Let $L$ be a complex structure on $V_\RR$. Consider a twisting homomorphism $\MU(L)\rightarrow G_R=\Spin(6, \CC)$ under which $W$ decomposes as
+\[W = L\otimes \det(L)^{-1/2}\oplus \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2.\]
+In particular,
+\[S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \oplus \CC\oplus \det(L)^{-1}\]
+and we consider the supercharge $Q\in S_+\otimes W$ of rank $(1, 0)$ contained in the scalar summand which spans the subspace $\CC w_1\subset W$.
+
+We consider a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which $L\otimes \det(L)^{-1/2}\subset W$ has weight $-1$ and $w_1,w_2$ have weight $1$. In particular, $Q$ has $\alpha$-weight $1$.
+
+The BRST fields are given by:
+\begin{itemize}
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
+\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
+\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
+\item Matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
+\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varphi \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\end{itemize}
+
+\begin{theorem}
+The holomorphic twist of 4d $\cN=4$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the BF theory with the space of fields $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg)$.
+Moreover, the equivalence is $\MU(2)$-equivariant.
+\label{thm:4d4holomorphictwist}
+\end{theorem}
+\begin{proof}
+The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$.
+Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}.
+From Theorem \ref{thm:4dholomorphictwist} we obtain that the twist is given by $T^*[-1] \map(\CC^2 , (T^*\fg\otimes K_{\CC^2}^{1/2})\ham \fg)$ as a $\ZZ$-graded theory.
+
+Note, however, that the twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above.
+In particular, this equivalence is not $\MU(2)$-equivariant.
+\pavel{Brian}
+\end{proof}
+
+\subsubsection{Topological A Twist}
+\label{sect:4dAtwist}
+
 \vspace{-10pt}
@@
 \end{itemize}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
-The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.
-We have the following classes.
-\chris{some comments claiming we'll discuss things above, to be added.
-Also this is to revisit after writing the below.}
-\begin{itemize}
- \item Rank $(1,0)$ (and $(0,1)$) supercharges.
-Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.
-They are compatible with $\SU(2)_- \sub \Spin(4;\RR)$, which can be promoted to a twisting homomorphism from the group $\mr U(2)$ as we say in the 4d $\mc N=1$ section above.
- \item Rank $(2,0)$ (and $(0,2)$) supercharges.
-Such supercharges automatically square to zero, and are topological: indeed they sit inside an $\mc N=2$ subalgebra.
-They are compatible with any of three possible twisting homomorphisms:
- \begin{enumerate}
-  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
-  \item The Kapustin-Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
-  \item The Vafa-Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
- \end{enumerate}
- \item Rank $(1,1)$ supercharges.
-Such supercharges have three invariant directions, and also sit inside an $\mc N=2$ subalgebra.
-Twists by such supercharges are compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$, but are only $\ZZ/2\ZZ$-graded, as we discussed in the $\mc N=2$ section above.
- \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, and compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$.
- \item Rank $(2,2)$ square-zero supercharges are topological, and split into two classes.
-Generically, such supercharges correspond to perturbatively trivial twisted theories, and are only compatible with $\Spin(2;\RR) \times \Spin(2;\RR)$.
-There is a special point of this type which is compatible with Kapustin-Witten twisting homomorphism.
- \item There is also a special rank $(2,2)$ point (the \emph{B-twisting supercharge}) arising by dimensional reduction from the 5d $\mc N=2$ rank 4 supercharge, which is also compatible with the Kapustin-Witten twisting homomorphism.
-\end{itemize}
-
-We can study all the possible twists using what we say in the $\mc N=2$ subsection, as well as by dimensional reduction from 5d $\mc N=2$ super Yang-Mills theory.
-
-\subsubsection{Holomorphic Twist}
-\label{sect:4d4holomorphictwist}
-
-\subsubsection{Topological A Twist}
-\label{sect:4dAtwist}
 

### 2020-01-24 paper.tex
small

@@
 
-\begin{remark}
-The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist. \pavel{Brian}
-\end{remark}
+%\begin{remark}
+%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+\pavel{Brian} \brian{not quite true, I just meant to say that the shifted symplectic structure no longer explicitly depends on the symplectic structure of $U$, but that's not very precise.
+I'm deleting this comment.}
+%\end{remark}
 
@@
 I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
-I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac 14 t (\psi^*, \psi^*)
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
 \end{align*}
@@
 
-We finally consider the twist with respect to a rank $(1,1)$ supercharge. We have a twisting homomorphism
-\[
-\phi \colon \Spin(2, \RR) \times \Spin(2, \RR) \to G_R=\SL(W)\times \GL(1, \CC),
-\]
-where on the first factor $\Spin(2, \RR)\cong \U(1)\hookrightarrow \SL(2, \CC)$ is given by the diagonal embedding and on the second factor $\Spin(2, \RR)\hookrightarrow \GL(1, |CC)$ is the obvious inclusion.
-If we denote by $S_\pm^1, S_\pm^2$ the semi-spin representations of the two $\Spin(2, \RR)$, we have
-\[W \cong S_+^2\otimes (S_+^1\oplus S_-^1).\]
-The semi-spin representations of $\Spin(4, \RR)$ decompose with respect to $\Spin(2, \RR)\times \Spin(2, \RR)\subset \Spin(4, \RR)$ as
-\[S_+\cong S_+^1\otimes S_+^2\oplus S_-^1\otimes S_-^2,\qquad S_-\cong S_+^1\otimes S_-^2\oplus S_-^1\otimes S_+^2.\]
+We finally consider the twist with respect to a rank $(1,1)$ supercharge.
+In this case, the twist is compatible with the group $G = \Spin(2, \RR) \times \Spin(2, \RR)$. 
+We denote each factor by $\Spin(2, \RR)_i$, $i=1,2$.  
+The twisting homomorphism is
+\[
+\phi \colon \Spin(2, \RR)_1 \times \Spin(2, \RR)_2 \to G_R=\SL(W)\times \GL(1, \CC),
+\]
+where on the first factor $\Spin(2, \RR)_1 \cong \U(1)\hookrightarrow \SL(2, \CC)$ is given by the diagonal embedding and on the second factor $\Spin(2, \RR)_2 \hookrightarrow \GL(1, \CC)$ is the obvious inclusion.
+If we denote by $S_{\pm, i}$, $i=1,2$ the semi-spin representations of the factor $\Spin(2, \RR)_i$, we have
+\[W \cong S_{+,2}\otimes (S_{+,1}\oplus S_{-,1}).\]
+The semi-spin representations of $\Spin(4, \RR)$ decompose with respect to $\Spin(2, \RR)_1 \times \Spin(2, \RR)_2\subset \Spin(4, \RR)$ as
+\[S_+\cong S_{+,1} \otimes S_{+,2} \oplus S_{-,1} \otimes S_{-,2},\qquad S_-\cong S_{+,1} \otimes S_{-,2} \oplus S_{-,1} \otimes S_{+,2}.\]
 
@@
 We have a homomorphism $\alpha\colon \U(1)\rightarrow  \SL(W)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the first and the third components.
-We also use a new twisting homomorphism $\wt\phi\colon \Spin(2, \RR)\times \Spin(2, \RR)\rightarrow G_R$ given by multiplying $\phi$ with the obvious homomorphism from the first $\Spin(2, \RR)$ factor to the last $\GL(1, \CC)$ factor in $G_R$ (cf.
+We also use a new twisting homomorphism $\wt\phi\colon \Spin(2, \RR)_1 \times \Spin(2, \RR)_2\rightarrow G_R$ given by composing $\phi$ with the obvious homomorphism from the first factor $\Spin(2, \RR)_1$ to the last $\GL(1, \CC)$ factor in $G_R$ (cf.
 the definition of $\alpha$ and $\wt\phi$ in Section \ref{sect:6dholomorphictwist}).
@@
 The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
-It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive semi-spin representation and $W^* \cong S_-^6$.
+It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive six-dimensional semi-spin representation and $W^* \cong S_-^6$.
 
@@
 
-Let $L$ be a complex structure on $V_\RR$. Consider a twisting homomorphism $\MU(L)\rightarrow G_R=\Spin(6, \CC)$ under which $W$ decomposes as
+Let $L$ be a complex structure on $V_\RR$. Consider a twisting homomorphism $\MU(L)\rightarrow G_R=\Spin(6; \CC)$ under which $W$ decomposes as
 \[W = L\otimes \det(L)^{-1/2}\oplus \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2.\]

### 2020-01-24 paper.tex
4d N=2

@@
 
-\title{A Catalogue of Twists of Supersymmetric Gauge Theories}
+\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theories}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 
-The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
-
-Next, we check that the equivalence respects  the gradings and the $\MU(2)$-action. 
-Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+The claim about the underlying $\ZZ/2$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
+
+Next, we check that the equivalence respects  the gradings.
+Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$.
+The rest of the fields organize into the following collections:
+\begin{align*}
+c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
+B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg) \\
+a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2-4n] \\
+\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[4n-1] \\
+\phi + \psi + \varphi^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
+\varphi + \psi^* + \phi^* &\in\Omega^{2, \bullet}(M; U\otimes K_M^{-1/2})[1-2n]
+\end{align*}
+
+These fields have the same degrees as in the holomorphic BF theory.
+
+\begin{comment}
+and hence the underlying local $L_\infty$ algebra after the twist becomes
+
 \[
@@
 \]
-These fields have the same degrees as in the holomorphic BF theory and the $L_\infty$ structure is obtained by the natural square zero extension of the dg Lie algebra in the first line by the remaining part of the diagram.
-\pavel{Brian}
-\end{proof}
-
-%\begin{remark}
-%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-\pavel{Brian} \brian{not quite true, I just meant to say that the shifted symplectic structure no longer explicitly depends on the symplectic structure of $U$, but that's not very precise.
-I'm deleting this comment.}
-%\end{remark}
+\end{comment}
+\end{proof}
 
@@
 \[
-\xymatrix@R=0.5cm@C=0.5cm{
+\xymatrix@R=0.5cm@C=0cm{
 \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
@@
 & & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
-& & \Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
-& \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}  \ar@{-->}^{t\id}[ur]
+& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
+& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
 }
 \]
-which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory. \pavel{Brian}
+which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
 \end{proof}
@@
 
-The BRST fields are given by:
+\vspace{-10pt}
+\paragraph{Fields:} In the notation of Section \ref{sect:4d_2_holomorphictwist}, the BRST fields are given by:
 \begin{itemize}
@@
 
+Note that the $\MU(2)$-action on fields factors through a $\U(2)$-action.
+
 \begin{theorem}
 The holomorphic twist of 4d $\cN=4$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the BF theory with the space of fields $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg)$.
-Moreover, the equivalence is $\MU(2)$-equivariant.
+Moreover, the equivalence is $\U(2)$-equivariant.
 \label{thm:4d4holomorphictwist}
@@
 Note, however, that the twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above.
-In particular, this equivalence is not $\MU(2)$-equivariant.
-\pavel{Brian}
-\end{proof}
-
-\subsubsection{Topological A Twist}
+In particular, this equivalence is not $\U(2)$-equivariant.
+In the present case the fields organize in the following collections:
+\begin{align*}
+c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
+\phi + \psi + \varphi^*&\in\Omega^{1, \bullet}(M; \fg) \\
+\xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[-1] \\
+\\
+a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2] \\
+\varphi + \psi^* + \phi^* &\in\Omega^{1, \bullet}(M; \fg)[1] \\
+B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg)
+\end{align*}
+These are exactly the fields in $T^*[-1] \map(\CC^2_{\rm Dol} , B \fg)$.
+\end{proof}
+
+\subsubsection{Rank (2, 0) twist}
 \label{sect:4dAtwist}
@@
 
-\subsubsection{Partially Topological Twist}
+\subsubsection{Rank (1, 1) twist}
 \label{sect:4d4partialtwist}
 
-\subsubsection{Kapustin Twist}
+\subsubsection{Rank (2, 1) twist}
 \label{sect:4dKapustintwist}
@@
 
-\subsubsection{Topological B Twist}
-\label{sect:4dBtwist}
-
-\subsubsection{Topological qGL Twist}
+\subsubsection{Rank (2, 2) twist}
 \label{sect:4dqgltwist}

### 2020-01-24 paper.tex
(2,0)

--- 2020-01-24 paper.tex
@@
 \subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
-\label{sect:4d_2_donaldson}
+\label{sec:4d2Donaldson}
 
@@
 
-\subsubsection{Topological A Twist}
-\label{sect:4dAtwist}
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
+\label{sect:4d4Atwist}
+
+Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
+As in Section \ref{sec:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
+
+We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ as in the previous section.
+Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
+\[
+S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
+\]
+
+Consider the family of supercharges $Q_t = Q_0 + t \Bar{Q}_0 \in S_+\otimes W$ of rank $(1, 0)$ contained in the scalar summands above.
+
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$.
+Moreover, this equivalence is $\MU(2)$-equivariant.
+\label{thm:4d4Atwist}
+\end{theorem}
+\begin{proof}
+The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$. 
+Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
+From Theorem \ref{thm:4dDonaldsontwist} we obtain the desired result.
+\end{proof}
+%\vspace{-10pt}
+%\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
 In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
- \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
-\end{itemize}
-
-\begin{theorem}
-\chris{holomorphic deforming to rank $(2,0)$, proven above} $\mr{Map}(\CC^2_{\mr{Dol}}, B\gg_{\mr{Hod}})$.
-\end{theorem}
+%\begin{itemize}
+% \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
+% \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+%\end{itemize}
 

### 2020-01-24 paper.tex

--- 2020-01-24 paper.tex
@@
 
-\subsubsection{Rank (2, 0) twist}
-\label{sect:4dAtwist}
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
+\label{sect:4d4Atwist}
+
+Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
+As in Section \ref{sec:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
+
+We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ as in the previous section.
+Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
+\[
+S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
+\]
+
+Consider the family of supercharges $Q_t = Q_0 + t \Bar{Q}_0 \in S_+\otimes W$ of rank $(1, 0)$ contained in the scalar summands above.
+
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$.
+Moreover, this equivalence is $\MU(2)$-equivariant.
+\label{thm:4d4Atwist}
+\end{theorem}
+\begin{proof}
+The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$. 
+Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
+From Theorem \ref{thm:4dDonaldsontwist} we obtain the desired result.
+\end{proof}
+%\vspace{-10pt}
+%\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
 In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
- \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
-\end{itemize}
-
-\begin{theorem}
-\chris{holomorphic deforming to rank $(2,0)$, proven above} $\mr{Map}(\CC^2_{\mr{Dol}}, B\gg_{\mr{Hod}})$.
-\end{theorem}
+%\begin{itemize}
+% \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
+% \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
+%\end{itemize}
 

### 2020-01-24 paper.tex

@@
 
-We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ as in the previous section.
+We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
 Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
@@
 \begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$.
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$.
 Moreover, this equivalence is $\MU(2)$-equivariant.
@@
 Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
-From Theorem \ref{thm:4dDonaldsontwist} we obtain the desired result.
+From Theorem \ref{thm:4dDonaldsontwist} we obtain that the twist is $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$ as a $\ZZ$-graded theory.
+
+The twisting homomorphism used in Section \ref{sect:4d_2_holomorphictwist} differs from the twisting homomorphism defined above. 
+In particular, this equivalence is not $\U(2)$-equivariant.
+In the present case the fields decompose in the same fashion as in the proof of Theorem \ref{thm:4d4holomorphictwist} which are precisely the fields of $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$.
 \end{proof}

### 2020-01-24 paper.tex

@@
 \end{proof}
-%\vspace{-10pt}
-%\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.
-In addition to the ghost $c$, the fields we obtain are
-%\begin{itemize}
-% \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
-% \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
-%\end{itemize}
 
@@
 
+Next we consider the twist with respect to a rank $(1,1)$ supercharge.
+As in Section \ref{sect:4d_2_11} the twist is compatible with the group $G = \Spin(2, \RR) \times \Spin(2, \RR)$.
+However, we will use a different twisting homomorphism.
+We denote each factor by $\Spin(2, \RR)_i$, $i=1,2$, and by $S_{\pm, i}$ the semi-spin representations of the factor $\Spin(2, \RR)_i$.
+
+The twisting homomorphism is
+\[
+\phi \colon \Spin(2, \RR)_1 \times \Spin(2, \RR)_2 \to G_R=\SL(W),
+\]
+under which $W$ splits as
+\begin{equation}
+W\cong (S_{+, 1}\otimes S_{+, 2}\oplus S_{-, 1}\otimes S_{-, 2})\oplus (S_{+, 1}\otimes S_{-, 2}\oplus S_{-, 1}\otimes S_{+, 2}).
+\label{eq:4d411decomposition}
+\end{equation}
+
+In this case $S_+\otimes W$ and $S_-\otimes W$ have two-dimensional trivial $G$-subrepresentations.
+Any scalar rank $(1, 1)$ supercharge is square-zero.
+We choose a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which the first two summands in \eqref{eq:4d411decomposition} have weight $1$ and the last two summands have weight $-1$.
+This makes the chosen rank $(1, 1)$ supercharge have weight $1$.
+
+\begin{theorem}
+The rank (1, 1) twist of 4d $\cN=4$ super Yang--Mills on $M=\RR^4$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(\CC_{\rm Dol}\times \RR^2_{\mathrm{dR}}, B \fg)$.
+Moreover, the equivalence is $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant.
+\label{thm:4d4partialtwist}
+\end{theorem}
+\begin{proof}
+The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$.
+By Theorem \ref{thm:4d_11_twist} we obtain that the twist is equivalent to $T^*[-1]\map(\CC\times \RR^2_{\mathrm{dR}}, \fg/\fg)$ as a $\ZZ$-graded theory.
+Let us now analyze the $\Spin(2, \RR)\times \Spin(2, \RR)$-action.
+
+By construction the twisting homomorphism $\Spin(2,\RR)\times \Spin(2, \RR)\rightarrow G_R$ defined by \eqref{eq:4d411decomposition} factors as $\Spin(2, \RR)\times \Spin(2, \RR)\subset \MU(2)\rightarrow G_R$, where the latter map is the twisting homomorphism used in Section \ref{sect:4d4holomorphictwist}.
+Therefore, we have to restrict the fields used in that section to $\Spin(2, \RR)\times \Spin(2, \RR)$.
+But by Theorem \ref{thm:4d4holomorphictwist} the fields belong to $T^*[-1]\map(\CC_{\mr Dol}\times \CC_{\mr Dol}, B\fg)$ whose underlying graded $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant bundle coincides with that of $T^*[-1]\map(\CC_{\mr Dol}\times \RR^2_{\mathrm{dR}}, B\fg)$.
+\end{proof}
+
 \subsubsection{Rank (2, 1) twist}
-\label{sect:4dKapustintwist}
 

### 2020-01-26 paper.tex
4d N=4 (2, 2)

@@
 Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
-\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
+\[S_+\cong \CC Q_0\oplus \wedge^2 L\oplus \CC \Bar{Q}_0.\]
 The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$.
@@
 \begin{equation}
-Q_t = \alpha + t\beta\in S_+
+Q_t = Q_0 + t\Bar{Q}_0\in S_+
 \label{eq:8dHodgefamily}
@@
 B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg) \\
+\\
 a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2-4n] \\
 \xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[4n-1] \\
+\\
 \phi + \psi + \varphi^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
@@
 In particular, this equivalence is not $\U(2)$-equivariant.
-In the present case the fields organize in the following collections:
+In the present case the fields organize into the following collections:
 \begin{align*}
@@
 
-\begin{theorem}
-\chris{Special rank $(2,2)$ deforming to generic rank $(2,2)$, by dimensional reduction from 5d $2_A$ deforming to $2_B$} $\mr{Map}(\RR^4_{\mr{dR}}, B\gg_{\mr{Hod}})$.
-\end{theorem}
-
-% \vspace{-10pt}
-% \paragraph{Supersymmetry action:} 
-% \begin{prop}
-% Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
-% \begin{align*}
-% I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
-% &\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
-% &\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
-% \end{align*}
-% and
-% \begin{align*}
-% I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
-% &\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
-% &\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
-% \end{align*}
-% where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
-% \end{prop}
+Consider a rank $(2, 2)$ supercharge $Q\in S_+\otimes W\oplus S_-\otimes W^*$.
+It defines embeddings $S_+^*\hookrightarrow W$ and $S_-^*\hookrightarrow W^*$ and the square-zero condition is that their images pair to zero.
+In other words, we have a short exact sequence
+\[0\longrightarrow S_+^*\longrightarrow W\longrightarrow S_-\longrightarrow 0.\]
+The semi-spin representations $S_\pm$ carry volume forms induced by scalar spinorial pairings.
+Moreover, $W$ has a canonical volume form since it is the semi-spin representation of $\Spin(6, \CC)\cong \SL(4, \CC)$.
+Comparing these volume forms under the above exact sequence gives an invariant $s\in\CC^\times$ of a rank $(2, 2)$ square-zero supercharge.
+Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parametrized by this invariant.
+
+Let $N_\RR=\RR^4$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification.
+We consider the 8-dimensional Euclidean vector space $N$ which carries a complex half-density.
+By the results of Section \ref{sect:8dtopologicaltwist} we obtain a family $Q_t$ of 8d square-zero supercharges.
+Its dimensional reduction to 4 dimensions also gives a family of 4d square-zero supercharges.
+Then from Theorem \ref{thm:8dHodgereduction} we obtain the following statement.
+
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the topological Hodge theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$.
+\label{thm:4d422Hodgetwist}
+\end{theorem}
+
+Let us now rewrite the family $Q_t$ in 4-dimensional terms.
+Consider the Kapustin--Witten twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\subset \Spin(4, \RR)\times \Spin(2, \RR)\subset \Spin(6, \CC)$ under which $W$ decomposes as
+\[W\cong S_+\oplus S_-.\]
+In this case the spinorial representation becomes
+\[\Sigma\cong S_+\otimes S_+\oplus S_+\otimes S_-\oplus S_-\otimes S_+\oplus S_-\otimes S_-.\]
+In particular, there are two scalar supercharges $Q_+$ and $Q_-$ given by the volume forms on $S_+$ and $S_-$ respectively. We may then consider a family of supercharges
+\[Q = u Q_+ + i v Q_-\]
+for $u, v\in\CC$.
+If $u,v\neq 0$ we obtain a rank $(2, 2)$ supercharge.
+In this case the map $Q\colon S_+^*\cong S_+\rightarrow W$ is given by multiplication by $u$ and the map $Q\colon W\rightarrow S_-$ is given by multiplication by $iv$.
+Therefore, its $s$-invariant is
+\[s = -\frac{u^2}{v^2}.\]
+
+\begin{remark}
+The family $uQ_+ + iv Q_-$ of square-zero supercharges is the same family as studied by Kapustin and Witten, see \cite[Section 3.1]{KapustinWitten}.
+\end{remark}
+
+These supercharges are related to $Q_t$ as follows.
+Let $S_+^8$ be the semi-spin representation of $\Spin(8, \CC)$ and $S_\pm$ the semi-spin representations of $\Spin(4, \CC)$ as before.
+Under the embedding
+\[\Spin(4, \CC)\subset \Spin(4, CC)\times \Spin(4, \CC)\subset \Spin(8, \CC)\]
+$S_+^8$ splits as
+\[S_+^8\cong S_+\otimes S_+\oplus S_-\otimes S_-,\]
+so $Q_+, Q_-\in S_+^8$. We then obtain
+\[Q_0 = Q_+ + Q_-,\qquad \Bar{Q}_0 = Q_+ - Q_-.\]
+Therefore, the $s$-invariant of the family $Q_t$ is
+\begin{equation}
+s = \frac{(1+t)^2}{(1-t)^2}.
+\label{eq:4d4sinvariant}
+\end{equation}
+
+\begin{cor}
+The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s=1$ is perturbatively equivalent to the topological BF theory $T^*[-1]\map(\RR^4_{\mathrm{dR}}, B\fg)$.
+\end{cor}
+\begin{proof}
+The supercharge $Q_0$ has $s$-invariant $s=1$.
+By Theorem \ref{thm:4d422Hodgetwist} the twist by $Q_0$ is perturbatively equivalent to the specialization of the theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$ at $t=0$.
+By Proposition \ref{prop:Hodgetheoryspecialization} the latter is isomorphic to the topological BF theory $T^*[-1]\map(\RR^4_{\mathrm{dR}}, B\fg)$.
+\end{proof}
+
+\begin{cor}
+The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s\neq 1$ is perturbatively trivial.
+\end{cor}
+\begin{proof}
+For any $s\neq 1$ we may find $t\neq 0$ solving \eqref{eq:4d4sinvariant}.
+But by Proposition \ref{prop:Hodgetheoryspecialization} the specialization of the topological Hodge theory $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$ at $t\neq 0$ is perturbatively trivial.
+\end{proof}
 

### 2020-01-27 paper.tex
in the middle
starting (1,2)

@@
 
-\subsubsection{Rank (2, 1) twist}
-
-\begin{theorem}
-\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
+\subsubsection{Rank $(1, 2)$ twist}
+
+Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
+As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.
+
+We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
+\[
+S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
+\]
+Notice the two scalar supercharges $Q_0, \Bar{Q}_0$, both of which are rank $(1,0)$.
+
+Further, the representation $S_- \otimes W$ decomposes under $\MU(2)$ as
+\[
+S_- \otimes W^* = L \otimes L^*  \oplus L \oplus L \otimes \det(L)^{-1} .
+\]
+Within the first summand of $S_- \otimes W^*$ there is the trivial representation $\CC \cdot Q' \subset L \otimes L^*$ consisting of multiples of the identity endomorphism. 
+The corresponding supercharge $Q'$ is of rank $(0,2)$.
+
+The family of supercharges we consider is 
+\begin{equation}\label{4d12hodge}
+Q_t = Q_0 + t Q' .
+\end{equation}
+Since $Q_0, (Q')^*$ arise from different summands of $W$, the supercharges $Q_0, Q'$ commute. 
+Hence $Q_t$ automatically squares to zero.
+
+Notice that for $t \ne 0$ this family specializes to a rank $(1,2)$ supercharge.
+When $t = 0$ the family specializes to the rank $(1,0)$ supercharge $Q_0$.
+
+In the statement of the next proposition, we refer to the decomposition of fields of $4d \cN=4$ super Yang-Mills theory given in the proof of Theorem \ref{thm:4d4holomorphictwist}.
+
+\begin{prop}
+Suppose $Q_t$ is the rank $(1,2)$ supercharge of Equation \ref{4d12hodge}.
+The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
+\brian{these formulas need to be fixed}
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
+%I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
+%I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
+\end{align*}
+\end{prop}
+
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
+\brian{Pavel claims this is equivalent to $\map\left(\CC \times \RR^2_{\rm dR}, B\fg_{\Hod}\right)$}
+Moreover, this equivalence is $\U(2)$-equivariant. \brian{Similarly, $\U(1) \times \U(1)$}
+\label{thm:4d12hodge}
+\end{theorem}
+%
+%\begin{theorem}
+%\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
 However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
-\end{theorem}
+%\end{theorem}
 

### 2020-01-27 paper.tex
small update for 4d N=4 (1, 2)

--- 2020-01-26 paper.tex
@@
 
- \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, compatible with a twisting homomorphism from $\MU(2)$ and admit a $\ZZ$-grading.
+ \item Rank $(2,1)$ and $(1,2)$ supercharges.  Such supercharges are topological, compatible with a twisting homomorphism from $\MU(2)$ and admit a $\ZZ$-grading.
 
@@
  \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
- Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
 These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
@@
 
-\subsubsection{Rank (2, 1) twist}
-
-\begin{theorem}
-\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
-However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
-\end{theorem}
+\subsubsection{Rank $(1, 2)$ twist}
+
+Next we look at the case of the twist by a rank $(1,2)$ supercharge. As in many cases so far, it will be useful to consider a family of topological supercharges which are generically of rank $(1,2)$.
+
+We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
+\[
+S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
+\]
+Further, the representation $S_- \otimes W^*$ decomposes as
+\[
+S_+ \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
+\]
+where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
+The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$.
+Moreover, both are square-zero and commute with each other.
+Therefore, we may consider a family of square-zero supercharges
+\begin{equation}
+Q_t = Q_0 + tQ'
+\label{eq:4d412Hodgefamily}
+\end{equation}
+which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
+
+We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
+
+\begin{prop}
+Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
+The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
+\begin{align*}
+I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* + (\Tilde{\nu}, \nu^*)+ t(\phi, A_{1, 0}^*) + t(\wt\nu, A_{0, 1}^*) + t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda F_{1, 1}\chi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+I^{(2)}_{\gauge} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
+\end{align*}
+\end{prop}
 

### 2020-01-27 paper.tex

@@
 
-Next we look at the case of the twist by a rank $(1,2)$ supercharge. As in many cases so far, it will be useful to consider a family of topological supercharges which are generically of rank $(1,2)$.
+Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
+As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.
 
@@
 \end{prop}
+
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
+Moreover, this equivalence is $\U(2)$-equivariant.
+\label{thm:4d12hodge}
+\end{theorem}
 

### 2020-01-27 paper.tex
5d in intro, and minor fixes

@@
 
-\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theories}
+\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} \cite{KallenZabzine}
- \item \emph{$\mc N=2$ intermediate twist.} \cite{ElliottPestun}
- \item \emph{$\mc N=2$ topological A twist.} \cite{Anderson, QiuZabzine}
- \item \emph{$\mc N=2$ topological B twist.} \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.
+This twist is equivalent to a mixed form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.
+It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).
+This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.
+If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a mixed form of BF theory valued in the adjoint quotient $\gg/\gg$.
+ \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist, with four invariant directions.
+This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.
+It is invariant for the group $\spin(2;\RR) \times \spin(3;\RR)$ and can be defined on the product of a 2-manifold and a 3-manifold, each equipped with a spin structure.
+This twist was considered in \cite{ElliottPestun} on manifolds of the form $\Sigma \times C \times S^1$, where $\Sigma$ and $C$ are Riemann surfaces, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
+ \item \emph{$\mc N=2$ topological A twist.} There are two topological twists in 5d $\mc N=2$.
+One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1,1)$ super Yang-Mills theory.
+It is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the intermediate twist.
+The full family is invariant for the group $\Spin(3;\RR)$.
+This theory was studied by Qiu and Zabzine, \cite{QiuZabzine}, where the equations of motion were shown to include the Haydys-Witten equations.
+Twisting homomorphisms in this situation were previously studied by Anderson \cite{Anderson}.
+ \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with 5d Chern-Simons theory.
+This theory is only $\ZZ/2\ZZ$-graded, and it is invariant for the group $\spin(3;\RR)$.
+This twist was identified in work of Geyer-M\"ulsch and of Bak-Gustavsson\cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
 \end{itemize}
@@
 
-\subsubsection{Rank $(1, 2)$ twist}
+\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} twist}
 
@@
 \begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
 Moreover, this equivalence is $\U(2)$-equivariant.
@@
 
-\subsubsection{Rank (2, 2) twist}
+\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
 \label{sect:4dqgltwist}

### 2020-01-28 paper.tex
merge

--- 2020-01-27 paper.tex
@@
 
- \item Rank $(2,1)$ and $(1,2)$ supercharges.  Such supercharges are topological, compatible with a twisting homomorphism from $\MU(2)$ and admit a $\ZZ$-grading.
+ \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, compatible with a twisting homomorphism from $\MU(2)$ and admit a $\ZZ$-grading.
 
@@
  \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
- Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
 These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
@@
 \begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$.
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^2_{\rm Dol}, B \fg_{\rm Hod})$.
 Moreover, this equivalence is $\MU(2)$-equivariant.
@@
 In particular, this equivalence is not $\U(2)$-equivariant.
-In the present case the fields decompose in the same fashion as in the proof of Theorem \ref{thm:4d4holomorphictwist} which are precisely the fields of $\map(\CC_{\rm Dol}, B \fg_{\rm Hod})$.
+In the present case the fields decompose in the same fashion as in the proof of Theorem \ref{thm:4d4holomorphictwist} which are precisely the fields of $\map(\CC^2_{\rm Dol}, B \fg_{\rm Hod})$.
 \end{proof}
@@
 Therefore, we have to restrict the fields used in that section to $\Spin(2, \RR)\times \Spin(2, \RR)$.
-But by Theorem \ref{thm:4d4holomorphictwist} the fields belong to $T^*[-1]\map(\CC_{\mr Dol}\times \CC_{\mr Dol}, B\fg)$ whose underlying graded $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant bundle coincides with that of $T^*[-1]\map(\CC_{\mr Dol}\times \RR^2_{\mathrm{dR}}, B\fg)$.
-\end{proof}
-
-\subsubsection{Rank $(1, 2)$ twist}
-
-Next we look at the case of the twist by a rank $(1,2)$ supercharge. As in many cases so far, it will be useful to consider a family of topological supercharges which are generically of rank $(1,2)$.
-
-We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
-\[
-S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
-\]
-Further, the representation $S_- \otimes W^*$ decomposes as
-\[
-S_+ \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
-\]
-where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
-The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$.
-Moreover, both are square-zero and commute with each other.
-Therefore, we may consider a family of square-zero supercharges
-\begin{equation}
-Q_t = Q_0 + tQ'
-\label{eq:4d412Hodgefamily}
-\end{equation}
-which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
-
-We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
-
-\begin{prop}
-Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
-The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
-\begin{align*}
-I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* + (\Tilde{\nu}, \nu^*)+ t(\phi, A_{1, 0}^*) + t(\wt\nu, A_{0, 1}^*) + t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda F_{1, 1}\chi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-I^{(2)}_{\gauge} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
-\end{align*}
-\end{prop}
+But by Theorem \ref{thm:4d4holomorphictwist} the fields belong to $T^*[-1]\map(\CC_{\rm Dol}\times \CC_{\rm Dol}, B\fg)$ whose underlying graded $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant bundle coincides with that of $T^*[-1]\map(\CC_{\rm Dol}\times \RR^2_{\mathrm{dR}}, B\fg)$.
+\end{proof}
+
+\subsubsection{Rank (2, 1) twist}
+
+\begin{theorem}
+\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.
+However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
+\end{theorem}
 

### 2020-01-28 paper.tex

--- 2020-01-27 paper.tex
@@
 Therefore, we have to restrict the fields used in that section to $\Spin(2, \RR)\times \Spin(2, \RR)$.
-But by Theorem \ref{thm:4d4holomorphictwist} the fields belong to $T^*[-1]\map(\CC_{\mr Dol}\times \CC_{\mr Dol}, B\fg)$ whose underlying graded $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant bundle coincides with that of $T^*[-1]\map(\CC_{\mr Dol}\times \RR^2_{\mathrm{dR}}, B\fg)$.
+But by Theorem \ref{thm:4d4holomorphictwist} the fields belong to $T^*[-1]\map(\CC_{\rm Dol}\times \CC_{\rm Dol}, B\fg)$ whose underlying graded $\Spin(2, \RR)\times \Spin(2, \RR)$-equivariant bundle coincides with that of $T^*[-1]\map(\CC_{\rm Dol}\times \RR^2_{\mathrm{dR}}, B\fg)$.
 \end{proof}

### 2020-01-28 paper.tex
merging

--- 2020-01-27 paper.tex
@@
 Under the embedding
-\[\Spin(4, \CC)\subset \Spin(4, CC)\times \Spin(4, \CC)\subset \Spin(8, \CC)\]
+\[\Spin(4, \CC)\subset \Spin(4, \CC)\times \Spin(4, \CC)\subset \Spin(8, \CC)\]
 $S_+^8$ splits as

### 2020-01-28 paper.tex
4d intro list

@@
 \begin{itemize}
- \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} 
- \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}
- \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.}
- \item \emph{$\mc N=4$ topological B twist.}
- \item \emph{More general $\mc N=4$ topological twists}
+ \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.
+This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.
+It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.
+In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.
+In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.
+Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.
+This twist was studied \chris{in the pure case?
+check} by Johansen \cite{Johansen}.
+Including the chiral multiplet, this twist was considered in \cite{ACMV}.
+ \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
+This twist is equivalent to a mixed version of BF theory with two real directions and one complex holomorphic direction, coupled to a mixed version of a $U$-valued symplectic boson.
+This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.
+This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
+ \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.
+This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.
+Its equations of motion include the Donaldson-Witten equations.
+If the supersymmetry is promoted to $\mc N=4$, then  \cite{Lozano, VafaWitten}
+ \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
+ \item \emph{More general $\mc N=4$ topological twists} \cite{KapustinWitten, ElliottYoo1}
 \end{itemize}
@@
  &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dBtwist] {Rank $(2,2)$ special}} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ special}} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
  &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dKapustintwist] {Rank $(2,1)$}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(2,1)$}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
  &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dAtwist] {Rank $(2,0)$}} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4d4Atwist] {Rank $(2,0)$}} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
  &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
@@
  &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d_2_donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
  &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline

### 2020-01-28 paper.tex
8d correction
merge
small update for 4d N=4 (1, 2)

@@
 \item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Scalar fields $\phi\in\Omega^{4,0}(M; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(M; \gg)[-2]$.
+\item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
 \item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
@@
 \begin{align*}
-A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
-A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
+A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt a \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
 \rho&\rightsquigarrow \rho, \wt\chi \\
@@
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
-Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt a, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
 \[
 \xymatrix@R=0.5cm@C=0.5cm{
-&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
 &&\ar@{}^{\bigoplus}[r] &&& \\
-\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
+\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
 }
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
-I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) \\
+I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right).
 \end{align*}
@@
 Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
-We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
 We are left with the action
-\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + t\phi c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
+\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
@@
 \xymatrix@C=0.5cm{
-&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
-\Omega^0(\CC^4; \gg)_{\phi} \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
+&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
+\Omega^0(\CC^4; \gg)_a \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
 }
@@
 \begin{align*}
-I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* + (\Tilde{\nu}, \nu^*)+ t(\phi, A_{1, 0}^*) + t(\wt\nu, A_{0, 1}^*) + t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda F_{1, 1}\chi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+\int\dvol\left(\frac{t}{2} (F_{1, 1} + [\phi, \nu], \psi^*) + t\Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + t\Lambda \dd_{A_{1, 0}}\nu \chi^* + \right) \\
 I^{(2)}_{\gauge} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\

### 2020-01-28 paper.tex
merge

--- 2020-01-28 paper.tex
@@
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
 parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
@@
 Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
-\begin{itemize}
-\item[(1)]
+%\begin{itemize}
+%\item[(1)]
 An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
@@
 \end{itemize}
-\item[(2)]
-For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
-\[
-Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
-\]
-is elliptic as a $C^\bu(\fg)$-linear differential operator.
-\end{itemize}
+%\item[(2)]
+%For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
+%An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
+%\[
+%Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
+%\]
+%is elliptic as a $C^\bu(\fg)$-linear differential operator.
+%\end{itemize}
 \end{definition}
-
-\begin{remark}
-\brian{Explain $C^\bu(\fg)$-linear elliptic}
-\end{remark}
 
@@
 I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[\phi, \wt\phi](\chi^*+t\wt\chi^*)\right) \\
 I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
@@
 \[
-S_+ \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
+S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
 \]

### 2020-01-28 paper.tex
4d N=4 (1,2)

--- 2020-01-28 paper.tex
@@
 Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
-The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(2)}_{\rm gauge}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
+The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
 \begin{align*}
-I_{\gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+\int\dvol\left(\frac{t}{2} (F_{1, 1} + [\phi, \nu], \psi^*) + t\Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + t\Lambda \dd_{A_{1, 0}}\nu \chi^* + \right) \\
-I^{(2)}_{\gauge} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+I^{(2)} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
 \end{align*}

### 2020-01-29 paper.tex
reference fixes and minor additions

@@
 Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.
-This twist was studied \chris{in the pure case?
-check} by Johansen \cite{Johansen}.
-Including the chiral multiplet, this twist was considered in \cite{ACMV}.
+This twist was studied by Johansen \cite{Johansen}.
  \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
@@
  \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
- \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.}
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.}
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} \cite{BlauThompson1, KapustinVyas}
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} \cite{BlauThompson2, RozanskyWitten} 
 \end{itemize}
@@
 \subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
-\label{sec:4d2Donaldson}
+\label{sect:4d2Donaldson}
 
@@
 Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
-As in Section \ref{sec:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
+As in Section \ref{sect:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
 

### 2020-01-29 paper.tex
reference fixes and minor additions
4d N=4 (1, 2)
(2,1)
merging

@@
 Its equations of motion include the Donaldson-Witten equations.
-If the supersymmetry is promoted to $\mc N=4$, then  \cite{Lozano, VafaWitten}
+If the supersymmetry is promoted to $\mc N=4$, then \chris{...twisting homomorphisms} \cite{Lozano, VafaWitten}
  \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
+\end{table}
+
+\begin{table}[!ht]
+ \centering
+ \begin{tabular}{c|c|c|c}
+ $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{2}*{6}
+
+ \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
+When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
+When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
+ \label{table_of_twists_2d}
 \end{table}
@@
 &+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-I^{(2)} (Q_t, Q_t) &= \int \dvol \left(-\frac{1}{4}(\chi^*)^2\right) \\
+I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
 \end{align*}
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;
-RR)$, acting on $W$ by its (Dirac) spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;\RR)$, acting on $W$ by its (Dirac) spin representation.
 

### 2020-01-29 paper.tex
(2,1) correct
merging
adding a 2d table

@@
 
-\begin{table}[!ht]
- \centering
- \begin{tabular}{c|c|c|c}
- $\mc N$ & Twist & Description & Invariant Directions \\
- \hline
- \multirow{2}*{6}
-
- \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
-When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
-When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
- \label{table_of_twists_2d}
-\end{table}
-
 \begin{table}[hbp]
@@
  \label{table_of_twists_4}
+\end{table}
+
+\begin{table}[!ht]
+ \centering
+ \begin{tabular}{c|c|c|c}
+ $\mc N$ & Twist & Description & Invariant Directions \\
+ \hline
+ \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
+ & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
+ && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
+ & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
+ \multirow{4}*{$(2,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
+ & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
+ \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
+ \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
+ \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
+ \end{tabular}
+ \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
+When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
+When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
+ \label{table_of_twists_2d}
 \end{table}
@@
 
+\begin{prop} 
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+\[
+E = E_0 \oplus \left(F \oplus F^! [-1]\right) \oplus \left(F^! \oplus F[-1] \right)
+\]
+and $\omega$ given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
+The action functional is
+\[
+S = S_0 + \int \phi^\star \psi .
+\]
+\end{prop}
+
 \begin{proof}

### 2020-01-29 paper.tex
merge

--- 2020-01-29 paper.tex
@@
 Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.
-This twist was studied by Johansen \cite{Johansen}.
+This twist was studied \chris{in the pure case?
+check} by Johansen \cite{Johansen}.
+Including the chiral multiplet, this twist was considered in \cite{ACMV}.
  \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
@@
 Its equations of motion include the Donaldson-Witten equations.
-If the supersymmetry is promoted to $\mc N=4$, then \chris{...twisting homomorphisms} \cite{Lozano, VafaWitten}
+If the supersymmetry is promoted to $\mc N=4$, then  \cite{Lozano, VafaWitten}
  \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
@@
  \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
- \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} \cite{BlauThompson1, KapustinVyas}
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} \cite{BlauThompson2, RozanskyWitten} 
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.}
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.}
 \end{itemize}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
-\end{table}
-
-\begin{table}[!ht]
- \centering
- \begin{tabular}{c|c|c|c}
- $\mc N$ & Twist & Description & Invariant Directions \\
- \hline
- \multirow{2}*{6}
-
- \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
-When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
-When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
- \label{table_of_twists_2d}
 \end{table}
@@
 Fix a volume form $\dvol_M$ on $M$.
-Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
+Suppose $(E, \omega, S)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand.
 Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$.
@@
 where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
 \label{prop:integrateoutfield}
@@
 \begin{proof}
-Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.
 Then we define the required perturbative equivalence as follows.
@@
 
-\begin{prop}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+%\begin{prop}
+%Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+%\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+%where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
 Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-\label{prop:BRSTdoublet}
+%\label{prop:BRSTdoublet}
+%\end{prop}
+
+\begin{prop} 
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+\[
+E = E_0 \oplus \left(F \oplus F^! [-1]\right) \oplus \left(F^! \oplus F[-1] \right)
+\]
+and $\omega$ given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
+Suppose further that the action functional
+\[
+S = S_0 + \int \phi^* \psi - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
+\]
+satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are local functionals. 
+Then, the classical BV theory $(E, \omega, S)$ is equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}$ and $\psi^* = I_{\phi}$ in the original action functional $S$.
 \end{prop}
@@
 \begin{proof}
-Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.
-We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining
-\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
-Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.
+Again, concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
+We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ defining 
+\[F_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]
+
+The maps $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
 Also, by construction, the $F_n$ intertwine the action functionals, since
@@
 S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
-&= S_0(e).
+&= S'(e).
 \end{align*}
-Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
+The linear term $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
 \end{proof}
@@
 \subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
-\label{sect:4d2Donaldson}
+\label{sec:4d2Donaldson}
 
@@
 Next we look at the case of the twist by a rank $(2,0)$ supercharge. 
-As in Section \ref{sect:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
+As in Section \ref{sec:4d2Donaldson}, it will be useful to consider a family of topological supercharges which degenerate to the rank $(1,0)$ supercharge we just discussed.
 
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;\RR)$, acting on $W$ by its (Dirac) spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;
+RR)$, acting on $W$ by its (Dirac) spin representation.
 

### 2020-01-29 paper.tex

@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}

### 2020-01-29 paper.tex
merging

--- 2020-01-29 paper.tex
@@
 Its equations of motion include the Donaldson-Witten equations.
-If the supersymmetry is promoted to $\mc N=4$, then \chris{...twisting homomorphisms} \cite{Lozano, VafaWitten}
- \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
- \item \emph{More general $\mc N=4$ topological twists} \cite{KapustinWitten, ElliottYoo1}
+If the supersymmetry is promoted to $\mc N=4$, then this theory is identified either with the theory studied by Vafa and Witten, \cite{VafaWitten}, or with the A-twist studied by Kapustin and Witten \cite{KapustinWitten}, depending on the twisting homomorphism one uses to make the twisted theory $\spin(4;\RR)$-invariant.
+ \item \emph{$\mc N=4$ topological B twist.} If $\mc N=4$, there are additional topological twists.
+The most important one is the Kapustin-Witten B-twist \cite{KapustinWitten}.
+This theory is obtained by dimensional reduction from the B-twist of 5d $\mc N=2$, or by twisting by a special supercharge of rank $(2,2)$.
+It is equivalent to a topological BF theory.
+This theory is $\spin(4;\RR)$-invariant using the Kapustin-Witten twisting homomorphism, and can be defined on arbitrary 4-manifolds.
+ \item \emph{More general $\mc N=4$ topological twists} In the $\mc N=4$ case, the B-twist fits into a larger family of topological twists, most of which are perturbatively trivial.
+A $\bb{CP^1}$-family of such twists, generically of rank $(2,2)$, was studied by Kapustin and Witten \cite{KapustinWitten}, which is invariant for $\spin(4;\RR)$ using the Kapustin-Witten twisting homomorphism.
+There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.
+An analysis of these twists using similar techniques to this paper, but with an aim to obtain the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
 \end{itemize}
@@
  &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d_8_minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_8_B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_8_A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
 
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
 Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
@@
 \subsubsection{Minimal Twist}
-\label{sect:3d_8_minimal_twist}
+\label{sect:3d8minimal_twist}
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
@@
 \subsubsection{Topological A Twist}
-\label{sect:3d_8_A_Twist}
+\label{sect:3d8A_Twist}
 From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
@@
 \subsubsection{Topological B Twist}
-\label{sect:3d_8_B_Twist}
+\label{sect:3d8B_Twist}
 From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.

### 2020-01-30 paper.tex
quad

--- 2020-01-29 paper.tex
@@
 \begin{definition}
-A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e.
-a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is
+% a nonlinear map of vector bundles $E\rightsquigarrow E'$, 
+a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 
-\begin{prop}
+\begin{prop}\label{prop:integrateoutfield}
 Fix a volume form $\dvol_M$ on $M$.
@@
 \[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
-where $S_0$ and $S_1$ are independent of $\phi$.
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
-\label{prop:integrateoutfield}
+where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
 \end{prop}
 
+\begin{remark}
+In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
+\[\xymatrix{
+\cdots & \ul{0} & \ul{1} & \cdots \\
+\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
+&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
+}\]
+where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
+\end{remark}
+
 \begin{proof}
 Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
-Then we define the required perturbative equivalence as follows.
-First $F_1(e) = (e, Q_1(e), 0) \in E$.
-Then, for $n > 1$, define
+The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
+The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
+For $n > 1$, define
 \begin{align*}
-F_n \colon \sym^n(E_0) &\to E \\
+\Psi_n \colon \sym^n(E_0) &\to E \\
 e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
 \end{align*}
-These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
+These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
+To see that they intertwine the action functionals, we observe that 
 \begin{align*}
-S(F(e)) &= S(e, S_1(e), 0) \\
+S(\Psi(e)) &= S(e, S_1(e), 0) \\
 &= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
@@
 \end{align*}
-Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
-\end{proof}
-
-\begin{remark}
-In terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
-\[\xymatrix{
-\cdots \ar[r] &\mc E_0^0 \ar[r]^{Q_0} \ar[dr] &\mc E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^{i}[r] \ar[ur] &\dens_M &
-}\]
-where $i$ is the canonical inclusion, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify the differential $Q_0$ and the Lie structure.
-\end{remark}
+\end{proof}
 
@@
 \begin{prop} 
+\label{prop:BRSTdoublet}
 Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
@@
 \]
-and $\omega$ given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
-Suppose further that the action functional
-\[
-S = S_0 + \int \phi^* \psi - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
-\]
-satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are local functionals. 
-Then, the classical BV theory $(E, \omega, S)$ is equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}$ and $\psi^* = I_{\phi}$ in the original action functional $S$.
+whose sections we denote by $e_0 + \varphi + \varphi^* + \psi + \psi^*$ according to the above decomposition. 
+The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
+Suppose further that the local functional
+\[
+S = S_0 + \int \phi \psi^* - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
+\]
+satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of $\phi$ and $\psi^*$.
+Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.
 \end{prop}
 
-\begin{proof}
-Again, concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
-We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ defining 
-\[F_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]
-
-The maps $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
-Also, by construction, the $F_n$ intertwine the action functionals, since
+\begin{remark}
+For the classical BV theory $(E, \omega, S)$ as in the proposition, the linearized BV differential defines the following cochain complex of fields:
+\[\xymatrix{
+\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
+\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
+&&F_\phi \ar^{~}[dr] &F^!_{\phi*} \ar[ur] && \\
+&&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
+}\]
+where the subscripts match the notation for the fields in the statement above.
+\footnote{Note that we are writing $F$ as if it is concentrated in a single cohomological degree, but the proposition applies for any graded vector bundle as in the statement of the proposition.}
+The differentials $F_\phi \to F_\psi$ and $F^!_{\psi^*} \to F^!_{\phi^*}$ are given by the identity.
+The arrows from the top line to the bottom lines represent potential $\phi^*$ and $\psi$ dependent terms in $I_\phi, I_{\psi^*}$. 
+The above proposition implies we can replace this cochain complex of fields with a quasi-isomorphic complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
+\end{remark}
+
+\begin{proof}
+Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
+The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
+The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
+\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]
+
+The maps $\Psi_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $\Psi_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
+Also, by construction, the $\Psi_n$ intertwine the action functionals, since
 \begin{align*}
-S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
+S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(I_{\psi^*}(e), I_\phi(e) - I_\phi(e)) + \omega(I_\phi (e), I_{\psi^*}(e) - I_{\psi^*}(e)) \\
 &= S'(e).
 \end{align*}
-The linear term $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
-\end{proof}
-
-\begin{remark}
-Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
-\[\xymatrix{
-\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
-&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
-}\]
-with the differentials $E_1 \to E_1$ and $E_1^!
-\to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure.
-\end{remark}
+\end{proof}
+
+There is a corollary of this proposition obtained by iterating the procedure. 
+We will only use a single iteration.
+
+\begin{cor} \label{cor: quad}
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+\[
+E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
+\]
+whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
+The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
+Suppose further that the local functional
+\[
+S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+\]
+satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
+\[
+E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
+\]
+and
+\[
+S' = S_0 + \int \phi_1 \psi_1^* - S''
+\]
+is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.\brian{finish}
+\end{cor}
+\begin{proof}
+%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
+We begin by making the following change of coordinates on the BV fields:
+\begin{align*}
+\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
+\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
+%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
+%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
+\end{align*}
+with $\phi_1, \psi_1$ left fixed. 
+This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
+Further, in the new coordinates, the action takes the form
+\[
+S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+\]
+\end{proof}
 
@@
 
+\begin{proof}
+We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
+\begin{align*}
+& (t \varphi, \rho, t \phi, A_{1,0}) \\
+& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+\end{align*}
+This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+\begin{align*}
+I^{(1)}(Q_t) &= \int \dvol\left(- \wt \chi\wt a^* - t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* \right) \\
+I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+\end{align*}
+
+\end{proof}
 \subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}

### 2020-01-30 paper.tex
3d N=4

@@
 
-This theory admits a unique twist:
-\begin{itemize}
- \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
-\end{itemize}
-
-We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
+The fields we obtain are
 \begin{itemize}
@@
  \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
+ \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
+\end{itemize}
+
+This theory admits a unique twist:
+\begin{itemize}
+ \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
+There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
 \end{itemize}
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation.
-
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
-The classification of orbits includes the rank of this map.
-\begin{itemize}
- \item Rank 1.
-In this case $Q$ is minimal, with 2 invariant directions.
-Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-Rank 2 supercharges are topological.
-A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
-The $G_R = \SO(4)$-action also corresponds to a choice of orientation, so there are two $G_R$ orbits: those determining the same orientation, and those determining the opposite orientation.
-We refer to as the $A$-twist and the $B$-twist respectively.
-When we dimensionally reduce the rank $(2,0)$ twist from 4d we obtain the A-twist.
-It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.
-The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$.
-\end{itemize}
-
-We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
+The $R$-symmetry group is $G_R = \Spin(4;\RR)$, acting on $W$ by its defining representation.
+
+\vspace{-10pt}
+\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
+The fields we obtain are
 \begin{itemize}
@@
  \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
-\end{itemize}
+ \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
+\end{itemize}
+
+In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
+An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
+The classification of orbits includes the rank of this map.
+\begin{itemize}
+ \item Rank 1.
+In this case $Q$ is minimal, with 2 invariant directions.
+Such supercharges come from the $\mc N=2$ supersymmetry algebra.
+They admit the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $A$-twist.
+Rank 2 supercharges are topological.
+A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
+The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action, which also corresponds to a choice of orientation, so there are two $G_R$ orbits: those determining the same orientation, and those determining the opposite orientation.
+We refer to as the $A$-twist and the $B$-twist respectively.
+The A-twist admits the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \iso G_R$.  This twist is only $\ZZ/2\ZZ$-graded
+\end{itemize}
+
+The claims about twisting homomorphisms and $\ZZ$-gradings follows by identifying the twists as dimensional reductions from 4d $\mc N=2$.
+
+\begin{lemma} \label{3d_4_orbits_lemma}
+A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an A-twisting supercharge in 3d $\mc N=4$.
+Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a B-twisting supercharge in 3d $\mc N=4$.
+\end{lemma}
+
+\begin{proof}
+The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\RR) \sub \spin(3;\CC)$.
+Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
+This splits the fundamental representation $W$ into the sum of two oriented Lagrangians.
+A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
+A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
+This subspace has the opposite orientation.
+\end{proof}
 
@@
 The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
-From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.
+However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
+Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
 
 \begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
+
+\begin{proof}
+The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
+This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
+
+To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
+The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
+Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
+\end{proof}
 
@@
 \begin{theorem}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 
-In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three classes: 
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+The fields we obtain are
+\begin{itemize}
+ \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
+ \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
+ \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
+\end{itemize}
+
+In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.
+That is, there are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.
+We can see this in the following way.
+\begin{lemma}
+There are two $\spin(3;\RR) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
+\end{lemma}
+
+\begin{proof}
+
+\end{proof}
+
+The classification of twists therefore takes the following form.
+We identify how the two orbits of rank 2 supercharges arise by dimensional reduction from 4d $\mc N=4$ by forgetting the supertranslation action down to 3d $\mc N=4$ (this may partially break the R-symmetry, but this is enough to distinguish the two classes of twisted theory).
 \begin{itemize}
@@
 The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso G_R$.
-\end{itemize}
-
- We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
-In addition to the ghost $c$, the fields we obtain are
-\begin{itemize}
- \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
- \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
+It admits a twisting homomorphism $\phi \colon \Spin(3;\RR) \to G_R$.
 \end{itemize}

### 2020-01-30 paper.tex
3d N=4 corrections

@@
 A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
-The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action, which also corresponds to a choice of orientation, so there are two $G_R$ orbits: those determining the same orientation, and those determining the opposite orientation.
-We refer to as the $A$-twist and the $B$-twist respectively.
+The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
+We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
 The A-twist admits the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
@@
 
-The claims about twisting homomorphisms and $\ZZ$-gradings follows by identifying the twists as dimensional reductions from 4d $\mc N=2$.
+The distinction via twisting homomorphisms and $\ZZ$-gradings follows by identifying the twists as dimensional reductions from 4d $\mc N=2$.
 
@@
 Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
-This splits the fundamental representation $W$ into the sum of two oriented Lagrangians.
+This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$.
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
+The corresponding twist can be promoted to a twisting datum using, so this is the A-twist in our classification above.
+
 A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
-This subspace has the opposite orientation.
+This subspace has the opposite orientation, so corresponds to the B-twist in our classification above.
 \end{proof}
@@
 The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
+Moreover, the equivalence is $\Spin(5; \RR)$-equivariant.
 \end{theorem}

### 2020-01-30 paper.tex
3d N=8, added Pavel's argument

@@
 
-\section{Dimension 9}
+\section{Dimension 9} \label{9d_section}
 
@@
 \begin{lemma}
-There are two $\spin(3;\RR) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
+There are two $\spin(3;\CC) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
 \end{lemma}
@@
 \begin{proof}
-
+Choose a symplectic basis $\langle s, s' \rangle$ for $S$, and let $Q = s \otimes w + s' \otimes w'$ be a square-zero rank 2 element of $S \otimes W$.
+Let $V_7$ denote the fundamental representation of $G_R$.
+As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of half-density.
+This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$, under whose action the auxiliary space $W$ decomposes as
+\[W \iso \left(\CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \right) \otimes \det(L)^{-1/2},\]
+(see also \cite[Section 4.7]{ElliottSafronov}), with $w$ lying in the last summand.  Under this decomposition, split the remaining element $w' = (v_0, v_1, v_2, v_3)$.  Then
+\begin{itemize}
+ \item $v_0 = 0$, because the square-zero condition implies, in particular, that $(w,w') = 0$ with respect to the scalar spinor pairing on $W$, here given by the wedge pairing.
+ \item Without loss of generality $v_3 = 0$, since under the action of $\spin(3;\CC)$, $s \otimes w + s' \otimes w' \sim s \otimes w + s' \otimes (w'-w)$.
+ \item If $v_1 = 0$ then $v_2 \ne 0$, and all choices of non-zero $v_2$ are in the same orbit under $\SL(L) \sub \stab(w) \sub G_R$.
+ \item If $v_1 \ne 0$ then without loss of generality $v_2 = 0$, using the action by wedge product of $L \sub \stab(w) \sub G_R$.
+Finally all choices of non-zero $v_1$ are likewise in the same orbit under $\SL(L) \sub \stab(w) \sub G_R$.
+The stabilizer of $w$ acts on the space $v_1 \ne 0$, so these latter two cases comprise two inequivalent orbits.
+\end{itemize}
 \end{proof}

### 2020-01-30 paper.tex
prop 1.7

--- 2020-01-30 paper.tex
@@
 }\]
+\[\xymatrix{
+\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
+\cdots \ar[r] & E_0^{-1}\ar[r] &E_0^0 \ar[ddr] \ar[dr]  \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
+&&F_\phi \ar^{~}[dr]  \ar[ur] &F^!_{\phi*} && \\
+&&F^!_{\psi^*} \ar^{~}[ur]  \ar[uur]  &F_\psi && \\
+}\]
 where the subscripts match the notation for the fields in the statement above.

### 2020-01-30 10draft.tex
10draft

--- 2019-07-17 10d_section_draft.tex
@@
 \input ./combined_macros.sty
+\def\hCS{\mathrm{hCS}}
 
@@
 \begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
-Let $(E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
+Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
 There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
 \end{lemma}
-\begin{proof}
-The BV complex is of the form $\left(\cO(\cE), Q + \{I,-\}\right)$.
-We have already exhibited \brian{this is a general fact that should go in the functional analysis section} a differentiable pro-cochain complex structure on the BV complex via the 
-natural decreasing filtration 
-\[
-F^k \cO (\cE) = \Sym^{\geq k} (\cE^\vee)
-\]
-which is compatible with both $Q$ and $\{I,-\}$ separately.
-The associated graded of this filtration is the differentiable cochain complex given by
-\[
-\left(\prod_{n \geq 0} \Sym^n (\cE^\vee) , Q \right) .
-\]
-This is simply the BV complex associated to the free theory based on $(E, Q, \omega)$ obtained by forgetting $I$. 
-Thus, the $E_1$ page of the corresponding spectral sequence is the BV cohomology of the underlying free theory, as desired. 
-\brian{shall we say a word about convergence? This must follow from completeness of the filtration in addition to boundedness in some direction of the cohomology of $\cE$.}
-\end{proof}
 
@@
 \end{lemma}
-\brian{I think Pavel had something to say for this lemma.}
 
@@
 
-The action functional for super Yang-Mills theory is given by
+The action functional in 10d super Yang-Mills is given by
 \[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
@@
 
-\brian{I may be optimistic, but shouldn't the lemmas below all follow from the fact that the category we are working with is a Grothendieck abelian category?
-In any case, I do like that we've stated them clearly.}
-
 \begin{lemma} \label{inclusion_and_projection_lemma}
@@
 \begin{lemma} \label{interaction_pullback_lemma}
-In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
-Suppose that all monomial summands of the interaction $I$ which depend on fields in $\mc C_2^\bullet$ also depend on fields in $\mc C_1^\bullet$.
-Then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
+In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
+If $\mc C_2^\bullet = 0$, or if $\mc C_1^\bullet$ and $\mc C_2^\bullet$ are both isotropic subspaces of $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, then the map \ref{symp_composite_eqn} is compatible with the interactions $I$ and $I'$
 \end{lemma}
-
-\begin{proof}
-We defined a quasi-isomorphism of cochain complexes in Lemma \ref{symplectic_composite_lemma} to be the composite $F$ of the inclusion $i$ of $\mc E^\bullet \oplus \mc C_2^\bullet$ with a quasi-inverse to the projection onto $\mc E^\bullet$: this composite map is a twisted inclusion $\mc E^\bullet \to \mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ of the form $F \colon \phi \mapsto (\phi, 0, f(\phi))$ for some linear map $f$.
-Because, by the hypothesis, all monomial summands of $I$ involving fields in $\mc C_2^\bullet$ also include fields in $\mc C_1^\bullet$, the pullback of $I$ under the map $F$ coincides with the pullback of $I$ under the inclusion map $\phi \mapsto (\phi, 0, 0)$ as required.
-\end{proof}
 
@@
 \begin{remark}
-From the point of view of supersymmetry, the twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-This is of course compatible with our conventions for holomorphic Chern-Simons: holomorphic Chern-Simons (with values in an ordinary Lie algebra) on an odd dimensional Calabi-Yau only defines a $\ZZ/2$-graded theory (unless $d=3$, where this can be lifted to a $\ZZ$-grading).
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $(-1)$-symplectic pairing.
+This twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
+As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $-1$-symplectic pairing.
 \end{remark}
@@
  \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-The morphism from step 1 is just given by an inclusion, so the interaction on twisted 10d Yang-Mills theory is compatible with the interaction evaluated at $\chi'=\chi'^\vee=0$.
-In order to make the same observation for the fields $\psi$ and $A_{1,0}$, we'll use Lemma \ref{interaction_pullback_lemma}, which we can apply using the observation that the antifields $A_{1,0}^\vee$ and $\psi^\vee$ only appear in the action together with the corresponding fields.
+We'll use Lemma \ref{interaction_pullback_lemma}.
 Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
@@
 The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-\brian{How do we place 10d YM on an arbitrary 5-fold? 
-Are you using something about sugra?
-}
 

### 2020-01-30 paper.tex
removing 10draft

@@
 
-%\begin{prop}
-%Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+\begin{prop}
+Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-%\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-%where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
 Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
 %\label{prop:BRSTdoublet}
-%\end{prop}
+\end{prop}
 
@@
 \begin{align*}
-S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
 &+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
-&+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
+&+ \int \dvol(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*))
 \end{align*}
@@
 We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
+Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
 \[
@@
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
+Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
 From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.

### 2020-01-30 paper.tex
3d N=8

@@
 Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
-From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
 
@@
 
+\begin{proof}
+On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
+We can then enhance this identifying the fields, as $\ZZ$-graded $\mr U(1)$ with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
+When we calculate that dimensional reduction the fields reduce according to the rule
+\begin{align*}
+\Omega^{\bullet,\bullet}(\CC^2;\gg[k]) &\mapsto \Omega^{\bullet,\bullet}(\CC; \Omega^\bullet(\RR; \gg[k] \oplus \gg[k-1])) \\
+&\iso \Omega^{0,\bullet}(\CC; \Omega^\bullet(\RR; (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]))).
+\end{align*}
+Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
+\end{proof}
+
 \subsubsection{Topological A Twist}
 \label{sect:3d8A_Twist}
-From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
+From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.
 
@@
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
-Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
+%Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
 \end{theorem}

### 2020-01-30 paper.tex
intro corrections and additions

@@
 \begin{itemize}
- \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} 
- \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} \cite{BlauThompson1, KapustinVyas}
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} \cite{BlauThompson2, RozanskyWitten} 
+ \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} There is a minimal twist in dimension 3 which can be defined with $\mc N=2$ supersymmetry, including a chiral multiplet valued in a representation $R$.
+This twist is perturbatively equivalent to a mixed form of BF theory with one real direction and one complex holomorphic direction, coupled to a mixed $\beta \gamma$-system valued in $R$.
+This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
+If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a mixed BF theory now coupled to a mixed symplectic boson.
+Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with mixed BF theory valued in $T[1](\gg/\gg)$.
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.
+The first is a perturbatively trivial theory which we refer to as the A-twist, obtained by dimensional reduction from the 4d A-twist.
+This theory fits into a non-trivial family deforming the minimal twist, which is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
+This twist was studied by Blau and Thompson \cite{BlauThompson1}, where it is referred to as a Casson invariant model, as well as Kapustin and Vyas \cite{KapustinVyas} as a dimensional reduction of Donaldson-Witten theory.
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The remaining topological twist is perturbatively equivalent to the 3d topological BF theory coupled to a symplectic boson valued in symplectic representation $U$.
+It is $\spin(3;\RR)$-invariant, and can be defined on arbitrary 3-manifolds.
+This form of twist was studied by Rozansky and Witten, \cite{RozanskyWitten} as well as by Blau and Thompson \cite{BlauThompson2}.
 \end{itemize}
@@
  \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
- &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\bun_G(\CC^4)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
@@
   && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
- &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
+ &&& $\bun_G(\CC^4)_\mr{dR}$ & \\ \hline
   \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
- &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
@@
   && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ Impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
- &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
+ &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}})_\mr{dR}$ & \\ \hline
  \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{\hyperref[sect:6d11holomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
@@
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (Casson)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
  &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (Casson)} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline

### 2020-01-30 paper.tex
merge

--- 2020-01-30 paper.tex
@@
 Its equations of motion include the Donaldson-Witten equations.
-If the supersymmetry is promoted to $\mc N=4$, then this theory is identified either with the theory studied by Vafa and Witten, \cite{VafaWitten}, or with the A-twist studied by Kapustin and Witten \cite{KapustinWitten}, depending on the twisting homomorphism one uses to make the twisted theory $\spin(4;\RR)$-invariant.
- \item \emph{$\mc N=4$ topological B twist.} If $\mc N=4$, there are additional topological twists.
-The most important one is the Kapustin-Witten B-twist \cite{KapustinWitten}.
-This theory is obtained by dimensional reduction from the B-twist of 5d $\mc N=2$, or by twisting by a special supercharge of rank $(2,2)$.
-It is equivalent to a topological BF theory.
-This theory is $\spin(4;\RR)$-invariant using the Kapustin-Witten twisting homomorphism, and can be defined on arbitrary 4-manifolds.
- \item \emph{More general $\mc N=4$ topological twists} In the $\mc N=4$ case, the B-twist fits into a larger family of topological twists, most of which are perturbatively trivial.
-A $\bb{CP^1}$-family of such twists, generically of rank $(2,2)$, was studied by Kapustin and Witten \cite{KapustinWitten}, which is invariant for $\spin(4;\RR)$ using the Kapustin-Witten twisting homomorphism.
-There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.
-An analysis of these twists using similar techniques to this paper, but with an aim to obtain the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
+If the supersymmetry is promoted to $\mc N=4$, then \chris{...twisting homomorphisms} \cite{Lozano, VafaWitten}
+ \item \emph{$\mc N=4$ topological B twist.} \cite{KapustinWitten}
+ \item \emph{More general $\mc N=4$ topological twists} \cite{KapustinWitten, ElliottYoo1}
 \end{itemize}
@@
  &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d_8_minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_8_B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_8_A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
 
-\begin{prop}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+%\begin{prop}
+%Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+%\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+%where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
 Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
 %\label{prop:BRSTdoublet}
-\end{prop}
+%\end{prop}
 
@@
 &&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
-}\]
-\[\xymatrix{
-\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
-\cdots \ar[r] & E_0^{-1}\ar[r] &E_0^0 \ar[ddr] \ar[dr]  \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-&&F_\phi \ar^{~}[dr]  \ar[ur] &F^!_{\phi*} && \\
-&&F^!_{\psi^*} \ar^{~}[ur]  \ar[uur]  &F_\psi && \\
 }\]
@@
 \begin{align*}
-S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
 &+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
-&+ \int \dvol(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*))
+&+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
 \end{align*}
@@
 
-\section{Dimension 9} \label{9d_section}
+\section{Dimension 9}
 
@@
 We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
+Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
 \[
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(- \wt \chi\wt a^* - t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* \right) \\
-I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] -[\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( + t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
+\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
 \end{align*}
@@
 
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
-The fields we obtain are
+This theory admits a unique twist:
+\begin{itemize}
+ \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
+There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
+\end{itemize}
+
+We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
 \begin{itemize}
@@
  \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
- \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
-\end{itemize}
-
-This theory admits a unique twist:
-\begin{itemize}
- \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
 \end{itemize}
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \Spin(4;\RR)$, acting on $W$ by its defining representation.
-
-\vspace{-10pt}
-\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
-The fields we obtain are
+The $R$-symmetry group is $G_R = \SO(4)$, acting on $W$ by its defining representation.
+
+In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
+An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
+The classification of orbits includes the rank of this map.
+\begin{itemize}
+ \item Rank 1.
+In this case $Q$ is minimal, with 2 invariant directions.
+Such supercharges come from the $\mc N=2$ supersymmetry algebra.
+They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $A$-twist.
+Rank 2 supercharges are topological.
+A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
+The $G_R = \SO(4)$-action also corresponds to a choice of orientation, so there are two $G_R$ orbits: those determining the same orientation, and those determining the opposite orientation.
+We refer to as the $A$-twist and the $B$-twist respectively.
+When we dimensionally reduce the rank $(2,0)$ twist from 4d we obtain the A-twist.
+It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $B$-twist.
+The other topological orbit arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
+It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso \SU(2) \to \SO(4)$.
+\end{itemize}
+
+We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
 \begin{itemize}
@@
  \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
- \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
-\end{itemize}
-
-In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.
-An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.
-The classification of orbits includes the rank of this map.
-\begin{itemize}
- \item Rank 1.
-In this case $Q$ is minimal, with 2 invariant directions.
-Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-Rank 2 supercharges are topological.
-A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
-The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
-We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
-The A-twist admits the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
-and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \iso G_R$.  This twist is only $\ZZ/2\ZZ$-graded
-\end{itemize}
-
-The distinction via twisting homomorphisms and $\ZZ$-gradings follows by identifying the twists as dimensional reductions from 4d $\mc N=2$.
-
-\begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an A-twisting supercharge in 3d $\mc N=4$.
-Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a B-twisting supercharge in 3d $\mc N=4$.
-\end{lemma}
-
-\begin{proof}
-The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\RR) \sub \spin(3;\CC)$.
-Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
-This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$.
-A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using, so this is the A-twist in our classification above.
-
-A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
-This subspace has the opposite orientation, so corresponds to the B-twist in our classification above.
-\end{proof}
+\end{itemize}
 
@@
 The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
-However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
-Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
+From Theorem \ref{3d_minimal_twist_thm} we obtain the following statement.
 
 \begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
-This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
-
-To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
-The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
-Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
-\end{proof}
 
@@
 \begin{theorem}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-Moreover, the equivalence is $\Spin(5; \RR)$-equivariant.
-\end{theorem}
-
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
+Moreover, the equivalence is $\Spin(5, \RR)$-equivariant.
+\end{theorem}
+
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
 Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
@@
 
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
-The fields we obtain are
-\begin{itemize}
- \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
- \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
- \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
-\end{itemize}
-
-In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.
-That is, there are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.
-We can see this in the following way.
-\begin{lemma}
-There are two $\spin(3;\CC) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
-\end{lemma}
-
-\begin{proof}
-Choose a symplectic basis $\langle s, s' \rangle$ for $S$, and let $Q = s \otimes w + s' \otimes w'$ be a square-zero rank 2 element of $S \otimes W$.
-Let $V_7$ denote the fundamental representation of $G_R$.
-As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of half-density.
-This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$, under whose action the auxiliary space $W$ decomposes as
-\[W \iso \left(\CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \right) \otimes \det(L)^{-1/2},\]
-(see also \cite[Section 4.7]{ElliottSafronov}), with $w$ lying in the last summand.  Under this decomposition, split the remaining element $w' = (v_0, v_1, v_2, v_3)$.  Then
-\begin{itemize}
- \item $v_0 = 0$, because the square-zero condition implies, in particular, that $(w,w') = 0$ with respect to the scalar spinor pairing on $W$, here given by the wedge pairing.
- \item Without loss of generality $v_3 = 0$, since under the action of $\spin(3;\CC)$, $s \otimes w + s' \otimes w' \sim s \otimes w + s' \otimes (w'-w)$.
- \item If $v_1 = 0$ then $v_2 \ne 0$, and all choices of non-zero $v_2$ are in the same orbit under $\SL(L) \sub \stab(w) \sub G_R$.
- \item If $v_1 \ne 0$ then without loss of generality $v_2 = 0$, using the action by wedge product of $L \sub \stab(w) \sub G_R$.
-Finally all choices of non-zero $v_1$ are likewise in the same orbit under $\SL(L) \sub \stab(w) \sub G_R$.
-The stabilizer of $w$ acts on the space $v_1 \ne 0$, so these latter two cases comprise two inequivalent orbits.
-\end{itemize}
-\end{proof}
-
-The classification of twists therefore takes the following form.
-We identify how the two orbits of rank 2 supercharges arise by dimensional reduction from 4d $\mc N=4$ by forgetting the supertranslation action down to 3d $\mc N=4$ (this may partially break the R-symmetry, but this is enough to distinguish the two classes of twisted theory).
+In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three classes: 
 \begin{itemize}
@@
 The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \Spin(3;\RR) \to G_R$.
+It admits a twisting homomorphism $\phi \colon \spin(3;\RR) \iso G_R$.
+\end{itemize}
+
+ We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+In addition to the ghost $c$, the fields we obtain are
+\begin{itemize}
+ \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
+ \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
 \end{itemize}
@@
 \subsubsection{Minimal Twist}
-\label{sect:3d8minimal_twist}
+\label{sect:3d_8_minimal_twist}
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
-Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
 From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
@@
 \subsubsection{Topological A Twist}
-\label{sect:3d8A_Twist}
+\label{sect:3d_8_A_Twist}
 From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
@@
 \subsubsection{Topological B Twist}
-\label{sect:3d8B_Twist}
+\label{sect:3d_8_B_Twist}
 From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.

### 2020-01-30 paper.tex
merge

--- 2020-01-30 paper.tex
@@
 Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-%\label{prop:BRSTdoublet}
+\label{prop:BRSTdoublet}
 \end{prop}
@@
 \[
-S = S_0 + \int \phi \psi^* - \int \phi I_\phi - \int \psi^* I_{\psi^*} 
-\]
-satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of $\phi$ and $\psi^*$.
+S = S_0 + \int \phi \psi^* - \int \phi I_\phi - \int \psi^* I_{\psi^*} - \int \phi^* I_{\phi^*} - \int \psi I_{\psi}
+\]
+satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}, I_{\phi^*}, I_{\psi}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of $\phi$ and $\psi^*$.
 Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.
@@
 For the classical BV theory $(E, \omega, S)$ as in the proposition, the linearized BV differential defines the following cochain complex of fields:
+%\[\xymatrix{
+%\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
+%\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
+%&&F_\phi \ar^{~}[dr] &F^!_{\phi*} \ar[ur] && \\
+%&&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
+%}\]
 \[\xymatrix{
 \cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
-\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-&&F_\phi \ar^{~}[dr] &F^!_{\phi*} \ar[ur] && \\
-&&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
-}\]
-\[\xymatrix{
-\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
-\cdots \ar[r] & E_0^{-1}\ar[r] &E_0^0 \ar[ddr] \ar[dr]  \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-&&F_\phi \ar^{~}[dr]  \ar[ur] &F^!_{\phi*} && \\
-&&F^!_{\psi^*} \ar^{~}[ur]  \ar[uur]  &F_\psi && \\
+\cdots \ar[r] & E_0^{-1}\ar[r] \ar@{.>}[dr] \ar@{.>}[ddr] &E_0^0 \ar@{.>}[ddr] \ar@{.>}[dr]  \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
+&&F_\phi \ar^{~}[dr]  \ar@{.>}[ur] &F^!_{\phi*}  \ar@{.>}[ur] && \\
+&&F^!_{\psi^*} \ar^{~}[ur]  \ar@{.>}[uur]  &F_\psi  \ar@{.>}[uur] && \\
 }\]
@@
 \footnote{Note that we are writing $F$ as if it is concentrated in a single cohomological degree, but the proposition applies for any graded vector bundle as in the statement of the proposition.}
-The differentials $F_\phi \to F_\psi$ and $F^!_{\psi^*} \to F^!_{\phi^*}$ are given by the identity.
-The arrows from the top line to the bottom lines represent potential $\phi^*$ and $\psi$ dependent terms in $I_\phi, I_{\psi^*}$. 
+The top line is the underlying cochain complex of the theory with fields $E_0$. 
+The arrows $F_\phi \to F_\psi$ and $F^!_{\psi^*} \to F^!_{\phi^*}$ are given by the identity.
+The dotted arrows represent terms in the differential arising from $I_\phi, I_{\psi^*}, I_{\phi^*}, I_{\psi}$. 
 The above proposition implies we can replace this cochain complex of fields with a quasi-isomorphic complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
@@
 \[
-S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
-\]
-satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}$ are polydifferential operators on fields valued in $F^!$, $F$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
+\]
+satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
 Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
@@
 \]
-is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.\brian{finish}
+where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
 \end{cor}
@@
 &+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* \right) \\
+&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* -  t \Lambda \dd_{\phi}\nu \chi^* + t [\phi, a] \varphi^* \right) \\
 I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
@@
 The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.
-Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
+From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
 
@@
 
-\begin{proof}
-On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
-We can then enhance this identifying the fields, as $\ZZ$-graded $\mr U(1)$ with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
-When we calculate that dimensional reduction the fields reduce according to the rule
-\begin{align*}
-\Omega^{\bullet,\bullet}(\CC^2;\gg[k]) &\mapsto \Omega^{\bullet,\bullet}(\CC; \Omega^\bullet(\RR; \gg[k] \oplus \gg[k-1])) \\
-&\iso \Omega^{0,\bullet}(\CC; \Omega^\bullet(\RR; (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]))).
-\end{align*}
-Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
-\end{proof}
-
 \subsubsection{Topological A Twist}
 \label{sect:3d8A_Twist}
-From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.
+From Theorem \ref{3d_4_A_twist_thm} we obtain the following statement.
 
@@
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
-%Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
+Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
 \end{theorem}

### 2020-01-30 paper.tex
starting 2d

--- 2020-01-30 paper.tex
@@
  \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
- \item  Table of the twists, and commentary on where each has appeared before in the literature.
  \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
@@
  \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
- \item  Summary of the sections of the paper.
 \end{enumerate}}
@@
 It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold.
-\chris{Maybe no reference here?
-Baulieu, Nekrasov, Losev define a kind of 9d twisted theory but it seems to be truly topological, not partially holomorphic?
-It reduces to the 8d A-twist.}
 \end{itemize}
@@
 The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
-Moreover, the equivalence is $\Spin(5; \RR)$-equivariant.
+Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.
 \end{theorem}
@@
 \section{Dimension 2}
-
+In dimension 2, the semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm 1$.
+There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
 There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
+The R-symmetry group is $\SO(2) \times \SO(2)$, with the factors acting by their fundamental representation on $W_+$ and $W_-$ repectively.
 
@@
 \paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.
-In addition to the ghost $c$, the fields we obtain are
+The fields we obtain are
 \begin{itemize}
@@
  \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus \otimes (S_+ \oplus S_-) \otimes R^*)$.
-\end{itemize}
-
-\vspace{-10pt}
-\paragraph{Supersymmetry action:} 
-\chris{todo}
-
-\vspace{-10pt}
-\paragraph{Twisting data:}
+ \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
+ \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
+\end{itemize}
+
 In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
 \begin{itemize}
- \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic
- \item Square-zero supecharges of rank $(1,1)$ are topological, and split into two classes: the B-supercharge arises by dimensional reduction from 3 dimensions, and the A-supercharge does not.
-\end{itemize}
-\chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}
+ \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.
+There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.
+ \item Square-zero supercharges of rank $(1,1)$ are topological, and split into two orbits under $\spin(2;\RR) \times G_R$: acting by $G_R$, we can \chris{...}. The B-supercharge
+ \item 
+\end{itemize}
 

### 2020-01-30 paper.tex
typo fixes

@@
 
-\begin{prop}
-Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
+% \begin{prop}
+% Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
 Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
 Suppose
-\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
+% \[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
+% where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
 Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-%\label{prop:BRSTdoublet}
-\end{prop}
+% \end{prop}
 
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(- \wt \chi\wt a^* - t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* \right) \\
-I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] -[\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( + t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
+\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
 \end{align*}
@@
 
-The R-symmetry group is $\mr O(2)$, acting on $W$ by its defining representation.
+The R-symmetry group is $\spin(2;\CC)$, acting on $W$ by its defining representation.
 
@@
  \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$, so the twisted theory carries a $U(1)$-action.
+There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
 \end{itemize}
@@
 \label{sect:3dminimaltwist}
-A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow \mr O(2)$.
+A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$.
 
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \Spin(4;\RR)$, acting on $W$ by its defining representation.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by its defining representation.
 
@@
 A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.
-The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
+The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
 We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
@@
 and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \iso G_R$.  This twist is only $\ZZ/2\ZZ$-graded
+ \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  This twist is only $\ZZ/2\ZZ$-graded
 \end{itemize}
@@
 \begin{proof}
-The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\RR) \sub \spin(3;\CC)$.
+The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.
 Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using, so this is the A-twist in our classification above.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$ -- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
 
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;\RR)$, acting on $W$ by its (Dirac) spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, acting on $W$ by its (Dirac) spin representation.
 
@@
 \begin{align*}
-\Omega^{\bullet,\bullet}(\CC^2;\gg[k]) &\mapsto \Omega^{\bullet,\bullet}(\CC; \Omega^\bullet(\RR; \gg[k] \oplus \gg[k-1])) \\
-&\iso \Omega^{0,\bullet}(\CC; \Omega^\bullet(\RR; (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]))).
+\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes \gg[k] \oplus \gg[k-1] \\
+&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR\otimes (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]).
 \end{align*}
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-The R-symmetry group is $\SO(2) \times \SO(2)$, with the factors acting by their fundamental representation on $W_+$ and $W_-$ repectively.
+The R-symmetry group is $CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
 

### 2020-01-31 paper.tex
gah

@@
  \hline
- \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
- & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
+ & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
  && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
- & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
+ & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
  && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
- \multirow{4}*{$(2,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
- & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
+  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
+ && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
+ & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
  && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
- \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
- \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
- \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
@@
 I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
+& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
+&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varphi^* \right) \\
 I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
@@
 \end{prop}
+
+%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
+%\begin{align*}
+%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+%\end{align*}
 
@@
 We are left with the action
-\[S_{BF} + \int\dvol\left(-t(b, A_{0, 1}^*) + t a c^* + \frac{t}{2} \xi^*\wedge B^* + t (\varphi, \phi^*) + \frac t4 (\psi^*, \psi^*) \right),\]
+\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
@@
 I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
 \end{align*}
@@
 \Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] -[\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( + t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
-\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
+\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
 \end{align*}
+
+The next step is to decompose the $(1,1)$ form $\psi$ as
+\[
+\psi = \omega \Lambda \psi + \psi_{\perp}
+\]
+where $\Lambda \psi_{\perp} = 0$.
 
@@
 On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
-We can then enhance this identifying the fields, as $\ZZ$-graded $\mr U(1)$ with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
-When we calculate that dimensional reduction the fields reduce according to the rule
+We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.
+The dimensionally reduced theory is a $\ZZ$-graded and $\mr U(1)$-equivariant theory, equivalent as a $\ZZ/2\ZZ$-graded theory to the one obtained from 3d $\mc N=4$ -- this promotes the description given above to a $\ZZ$-graded and $\mr U(1)$-equivariant theory.
+When we calculate that dimensional reduction, the fields reduce according to the rule
 \begin{align*}
-\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes \gg[k] \oplus \gg[k-1] \\
-&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR\otimes (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]).
+\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
+&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
 \end{align*}
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-The R-symmetry group is $CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
+The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
 
@@
 There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.
- \item Square-zero supercharges of rank $(1,1)$ are topological, and split into two orbits under $\spin(2;\RR) \times G_R$: acting by $G_R$, we can \chris{...}. The B-supercharge
- \item 
+ \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.
+Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.
+By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.
+The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
+Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
 \end{itemize}
@@
 
+\subsubsection{Minimal Twist} \label{sect:2d22minimaltwist}
+
 \begin{theorem} \label{2d_minimal_twist_thm}
@@
 
+\subsubsection{Topological A Twist} \label{sect:2d22Atwist}
+
 \begin{theorem} \label{2d_2_A_twist_thm}
@@
 
+\subsubsection{Topological B Twist} \label{sect:2d22Btwist}
+
 Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
 \begin{theorem} \label{2d_2_B_twist_thm}
-The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2, (R/\gg))$.
+The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
 \end{theorem}
@@
 
+\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
+\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
+
 \begin{theorem}
@@
 \end{theorem}
+
+\subsubsection{Topological B Twist} \label{sect:2d44Btwist}
 
@@
 We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.
+
+\subsubsection{Minimal Twist} \label{sect:2d02minimaltwist}
 
@@
 
+\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
+
 \begin{theorem}\label{2d(0,4)}
@@
 %\end{align*}
+
+\subsubsection{Minimal Twist} \label{sect:2d0Nminimaltwist}
 

### 2020-01-31 paper.tex
(1,2) attempt

@@
 Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
-We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
 We are left with the action
@@
 \end{proof}
+
+\chris{I just made the following attempt}
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$.
+Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
+Consider the supersymmetry actions
+\begin{align*}
+&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
+&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
+\end{align*}
+We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
+Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.
+We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.
+The key fact is that the part of the deformation of the action proportional to $s$, namely
+\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
+only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields)
+
+So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
+The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
+Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
+Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
+
+As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.
+This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
+\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
+The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+\begin{equation}
+\label{eq:4d_12_further_deformation}t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
+\end{equation}
+The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
+
+Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
+This deformation gives the desired theory.
+The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.
+Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
+
+\end{proof}
+
 \subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
+The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
 

### 2020-01-31 paper.tex

@@
 \begin{abstract}
-We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.
-Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory.
+We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
+We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
+For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory.
 \end{abstract}
@@
 \end{enumerate}}
+
+\subsection*{Applications to quantization and a relationship to factorization algebras}
+\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
+
+The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
+An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
+In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
 

### 2020-01-31 paper.tex
clarifying point

--- 2020-01-31 paper.tex
@@
 \[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields)
+only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
+In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
 
@@
 
-As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.
+As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.
 This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
@@
 \begin{equation}
-\label{eq:4d_12_further_deformation}t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
+\label{eq:4d_12_further_deformation}
+t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
 \end{equation}

### 2020-01-31 paper.tex
4d (1,2) correction

@@
 \begin{prop}
+\label{4d_donaldson_susy_prop}
 Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
@@
 
-As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.
+As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
 This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
-\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
-The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+\begin{equation}
+\label{eq:4d_12_general_def}
+\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
+\end{equation}
+To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.
+This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.
+
+The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
 \begin{equation}

### 2020-01-31 paper.tex
typo fixes

@@
 
-As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.

### 2020-01-31 paper.tex
merge

--- 2020-01-31 paper.tex
@@
 \begin{abstract}
-We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
-We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
-For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory.
+We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.
+Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory.
 \end{abstract}
@@
 \end{enumerate}}
-
-\subsection*{Applications to quantization and a relationship to factorization algebras}
-\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
-
-The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
-An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
-
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
-In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
 
@@
 Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}.
-We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
 We are left with the action
@@
 \end{proof}
-
-\chris{I just made the following attempt}
-\begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$.
-Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
-\end{theorem}
-
-\begin{proof}
-Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
-Consider the supersymmetry actions
-\begin{align*}
-&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
-&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
-\end{align*}
-We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
-Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.
-We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.
-The key fact is that the part of the deformation of the action proportional to $s$, namely
-\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
-More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
-In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
-
-So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
-We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
-The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
-Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
-Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
-
-As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.
-This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
-\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
-The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
-\begin{equation}
-\label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
-\end{equation}
-The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
-
-Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
-This deformation gives the desired theory.
-The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.
-Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
-
-\end{proof}
-
 \subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}

### 2020-02-03 paper.tex
Minor edits

--- 2020-01-31 paper.tex
@@
 
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $\Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
 
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
+\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.
 The fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
+\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.
 The fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
 The fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
 The fields we obtain are
@@
  \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.
-There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.
+There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.
  \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+Moreover, this equivalence is $\mr U(1)$-equivariant.
 \end{theorem}

### 2020-02-04 paper.tex
introduction

--- 2020-01-31 paper.tex
@@
 
+\setcounter{tocdepth}{2}
 \tableofcontents
@@
 
-\chris{Possible topics for the introduction
+In this paper we calculate supersymmetric twists of super Yang--Mills theories in dimension 2 through 10.
+Our main tools are the classical Batalin--Vilkovisky formalism which eliminates the need for auxiliary fields to close the on-shell supersymmetry action and a consistent use of dimensional reduction which allows us to deduce lower-dimensional statements from higher-dimensional statements.
+
+\subsection*{Classical field theories}
+
+Let us begin with an informal discussion of classical field theories.
+A classical field theory is usually taken to be the data of the space of fields $\cF$ equipped with an action functional.
+To incorporate gauge symmetries, one may either work with $\cF$ as a stack or, as in the BRST formalism, with $\cF$ as a $Q$-manifold, i.e.
+a graded manifold equipped with a square-zero vector field of cohomological degree $1$ (the BRST differential).
+In the Batalin--Vilkovisky approach one considers instead the space of BV fields $\cE$ which is equipped with a $(-1)$-shifted symplectic structure which may be modeled by a $QP$-manifold.
+Moreover, we assume that the $Q$-structure is Hamiltonian, i.e.
+it is given by a Poisson bracket $\{S, -\}$ with respect to the BV action functional.
+Here $\cE$ is supposed to be the derived critical locus of the action functional on $\cF$.
+
+In this paper we follow the approach developed in the works of Costello and Gwilliam \cite{CostelloBook,Book1}.
+As the space of BV fields $\cE$ is an infinite-dimensional manifold, it is difficult to work with it directly (for instance, to make sense of a $(-1)$-shifted symplectic structure).
+Instead, we zoom in on a neighborhood of a point where $Q$ vanishes (i.e.
+we consider a given classical solution).
+We may then consider $\cE$ as the space of sections of a graded vector bundle $E\rightarrow M$ over the spacetime manifold $M$.
+This allows us to work with finite-dimensional objects throughout.
+Namely, a $(-1)$-shifted symplectic structure on $\cE$ boils down to a $(-1)$-shifted symplectic pairing $E\cong E^![-1]$, where $E^!=E^*\otimes \Dens_M$.
+We refer to Definition \ref{def:classicalfieldtheory} for the precise definition of a classical field theory in the BV formalism that we use.
+Moreover, with this definition we may talk about weak equivalences of classical field theories (a notion inaccessible with $QP$-manifolds) which are simply maps of classical field theories inducing a quasi-isomorphism on $\cE$.
+We call these \emph{perturbative equivalences} (see Definition \ref{def:perturbativeequivalence}) to emphasize that we are working in a formal neighborhood of a given classical solution.
+For simplicity, throughout the paper we ignore issues of unitarity, so we complexify all fields.
+
+\subsection*{Supersymmetric classical field theories}
+
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant.
+Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
+A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$.
+In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.
+
+In most literature on supersymmetry one simply tries to build an action of $\fA$ on the space of ordinary fields $\cF$.
+However, one often runs into a problem that the supersymmetry action is only \emph{on-shell}: the map from $\fA$ to vector fields $\mathrm{Vect}(\cF)$ preserves Lie brackets only on the critical locus of the action functional.
+The usual solution is to enlarge the space of fields by adding auxiliary fields with no kinetic terms on which there is an honest (\emph{off-shell}) action of $\fA$.
+However, this choice may be not canonical.
+For instance, in 10d $\cN=(1, 0)$ super Yang--Mills one needs to break the Lorentz group $\SO(10)$ to $\Spin(7)\times\SO(2)$ to have an off-shell action of a subalgebra of $\fA$ where the odd part is 9-dimensional (instead of 16-dimensional) \cite{BaulieuBerkovitsBossardMartin}.
+
+We instead take another approach pioneered by Baulieu \cite{}.
+Namely, one may canonically extend the supersymmetry action from ordinary fields $\cF$ to the space of BV fields $\cE$.
+The property of the action being on-shell now means that the map $\fA\rightarrow \mathrm{Vect}(\cE)$ preserves Lie brackets up to homotopy.
+One may then try to extend it to an $L_\infty$ action.
+
+In these paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10.
+In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills.
+First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing.
+In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 thse depend on a choice of an orthogonal $\fg$-representation.
+We do not consider superpotential and mass terms in this paper.
+Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).
+
+The on-shell supersymmetry of pure super Yang--Mills theories in these dimensions can be proven by using a well-known relationship between composition algebras (e.g.
+division algebras) and supersymmetry (see Section \ref{sect:compositionalgebras}) which goes back to the works \cite{Evans,KugoTownsend}.
+For instance, we may construct the 10d $\cN=(1, 0)$ supersymmetry from octonions $\mathbb{O}$, 6d $\cN=(1, 0)$ supersymmetry from quaternions $\mathbb{H}$, 4d $\cN=1$ supersymmetry from complex numbers $\CC$ and 3d $\cN=1$ supersymmetry from real numbers $\RR$.
+Our treatment follows the work of Baez and Huerta \cite{BaezHuerta} and we show how to extend the $\fA$-action to an $L_\infty$-action using these ideas.
+As a new result, we also construct an $L_\infty$-action on matter multiplets where the language of composition algebras turns out to be indispensable (see Section \ref{sect:mattermultipletSUSY}).
+Namely, for any real associative composition algebra $A_\RR$ we simply need a complex $\fg$-representation equipped with an $A_\RR$-module structure and a symmetric bilinear pairing.
+We have the following three cases:
+\begin{itemize}
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) For $A_\RR=\mathbb{H}$ this forces $P=U\otimes W_+$, where $U$ is a symplectic $\fg$-representation and $W_+$ is a 2d complex symplectic vector space (so that $\mathbb{H}\otimes_\RR\CC\cong \eend(W_+)$).
+\item (\textbf{4d $\cN=1$ supersymmetry}) For $A_\RR=\mathbb{C}$ this forces $P=R\oplus R^*$, where $R$ is a $\fg$-representation.
+\item (\textbf{3d $\cN=1$ supersymmetry}) For $A_\RR=\mathbb{R}$ we simply have an orthogonal $\fg$-representation $P$.
+\end{itemize}
+
+In addition to dimensional reduction of these four super Yang--Mills theories, there are also certain special super Yang--Mills theories with chiral supersymmetry: namely, 2d $\cN=(1, 0)$, $\cN=(2, 0)$ and $\cN=(4, 0)$ with matter as well as pure $\cN=(\cN_+, 0)$ theories for any $\cN_+$.
+We treat these separately (see Section \ref{sect:2dchiral}), but again the language of composition algebras turns out to be convenient.
+
+\subsection*{Supersymmetric twists}
+
+The notion of supersymmetric twist of a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}.
+The definitions we use in this paper will follow our previous work \cite{ElliottSafronov}, so let us briefly recall those.
+
+Suppose $Q$ is a square-zero supercharge, i.e.
+an odd element $Q\in\fA$ such that $[Q, Q]=0$.
+Then it gives rise to a square-zero odd symplectic vector field on the space of BV fields $\cE$.
+In particular, we may modify the differential on $\cE$ as $\mathrm{d}\mapsto \mathrm{d}+Q$.
+Working up to perturbative equivalence, this turns out to drastically simplify the theory as we will shortly see.
+
+The original classical field theory carried a $\ZZ\times\ZZ/2$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2$ is the fermionic grading.
+We see that $\mathrm{d}$ has bidegree $(1, 0)$ while $Q$ has bidegree $(0, 1)$.
+So, in general the twisted theory is only $\ZZ/2$-graded (with respect to the total grading).
+To improve that, we may additionally consider a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ into the R-symmetry group under which $Q$ has weight $1$ and such that the $\alpha$-grading modulo 2 coincides with the fermionic grading.
+Then the $\alpha$-grading gives rise to a $\ZZ$-grading on the twisted theory.
+
+Finally, let us observe that the original classical field theory carried an action of $\Spin(n)$ by rotations of $\RR^n$.
+But since $Q$ is not preserved under $\Spin(n)$, this action does not survive in the twisted theory.
+To improve that, we may consider a group $G$ with a \emph{twisting homomorphism} $G\rightarrow \Spin(n)\times G_R$ under which $Q$ is a scalar.
+Given such a twisting homomorphism, the twisted theory carries a $G$-action.
+
+To summarize, supersymmetric twisting consists of the following three steps:
 \begin{enumerate}
- \item  Context and literature on twists, including in the BV formalism.
+\item Choose a square-zero supercharge $Q\in\Sigma$ and modify the differential of the theory as $\mathrm{d}\mapsto\mathrm{d}+Q$.
+
+\item Choose a group $G$ together with a twisting homomorphism $G\rightarrow \Spin(n)\times G_R$ under which $Q$ is scalar.
+To remove redundancy, we will assume $G\rightarrow \Spin(n)$ is an embedding.
+
+\item Choose a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which $Q$ has weight $1$ and such that the $\alpha$-grading modulo 2 is the fermionic grading.
+This step may not be possible in general.
+\end{enumerate}
+
+A classification of possible square-zero supercharges $Q$ was previously done in \cite{ElliottSafronov} and in this paper we use that classification to calculate the twist of super Yang--Mills theories on $\RR^n$ in all dimensions.
+
+\subsection*{Supersymmetric twists and supergravity}
+
+In this paper we only consider the case of global supersymmetry for super Yang--Mills theories on $\RR^n$.
+In certain cases one may consider coupling of super Yang--Mills to supergravity in which case the interpretation of the twist is that we consider a nontrivial supergravity background.
+Let us briefly explain this perspective.
+
+A classical solution of supergravity consists, in particular, of the following data: a spacetime manifold $M$, a $\Spin(n)$-bundle $P_\Spin\rightarrow M$ equipped with a connection (spin connection), a $G_R$-bundle $P_R\rightarrow M$ equipped with a connection and a ghost for supertranslations $\eta\in \Gamma(M, (P_\Spin\times P_R)\times^{\Spin(n)\times G_R}\Sigma)$.
+If we couple super Yang--Mills to supergravity, then the super Yang--Mills fields become sections of the associated bundles to $P_\Spin\times P_R$.
+
+We have the following supergravity analogs of the data $(Q, \phi, \alpha)$ for supersymmetric twisting:
+\begin{itemize}
+\item The supergravity analog of the choice of a square-zero supercharge $Q$ is the value of the ghost $\eta$.
+
+\item In the supergravity setting we consider a $G$-bundle $P_G\rightarrow M$ with a connection so that $P_\Spin\times P_R$ is induced via the homomorphism $G\rightarrow \Spin(n)\times G_R$.
+
+\item Given $\alpha\colon \U(1)\rightarrow G_R$, we consider a trivial $\U(1)$-subbundle in $G_R$ on which the connection restricts to zero.
+\end{itemize}
+
+%\chris{Possible topics for the introduction
+%\begin{enumerate}
+% \item  Context and literature on twists, including in the BV formalism.
 There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
 Also at least a remark on the perspective in terms of coupling to twisted sugra.
- \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
- \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
- \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
- \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
- \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
- \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
-\end{enumerate}}
-
-\subsection*{Applications to quantization and a relationship to factorization algebras}
-\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
-
-The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
-An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
-
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
-In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
-
-\subsection*{Summary of Twisted Super Yang-Mills Theories}
-\addcontentsline{toc}{subsection}{Summary of Twisted Super Yang-Mills Theories}
-In this section we'll summarize the results of Part \ref{classification_part} of the paper, in which we classify all twists of super Yang-Mills theories in dimensions 2 to 10.
-We'll give this summary in two forms.
-In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we will display all the possible twists with a short name, and a precise description in terms of the moduli space of solutions to the twisted equations of motion.
-We will also, in this subsection, give a short description of each twisted theory in more physical language, with references to where in the literature it was previously considered.
+% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
+% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
+% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
+% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
+% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
+% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
+%\end{enumerate}}
+
+\subsection*{Summary of Twisted Super Yang--Mills Theories}
+%\addcontentsline{toc}{subsection}{Summary of Twisted Super Yang-Mills Theories}
+
+In this section we will summarize the main results of the paper presented in Part \ref{classification_part}, where we calculate twists of super Yang--Mills theories in dimensions 2 through 10.
+
+Let us begin by explaining what we mean by ``calculation''.
+Recall that for a Lie algebra $\fg$ there is a $d$-dimensional topological BF theory defined on a $d$-dimensional spacetime manifold $M$ with the space of BV fields $\Omega^\bullet(M; \fg)[1]\oplus \Omega^\bullet(M; \fg^*)[d-2]$, where $\Omega^\bullet$ denotes the space of differential forms equipped with the de Rham differential $\mathrm{d}$.
+If $M$ is replaced by a complex manifold $X$, we may also consider its version with the space of fields $\Omega^{\bullet, \bullet}(X; \fg)[1]\oplus \Omega^{\bullet, \bullet}(X; \fg^*)[2\dim(X)-2]$, where $\Omega^{\bullet, \bullet}$ is the space of differential forms equipped with the Dolbeault differential.
+Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$.
+We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{}).
+We may also combine these three examples into what we call a \emph{generalized BF theory} with the spaces of fields $T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ (see Definition \ref{def:generalizedBF} for more details).
+
+Let us also recall that if $\fg$ is equipped with a symmetric bilinear nondegenerate pairing, we also have a 3-dimensional topological Chern--Simons theory.
+If we forgo $\ZZ$-gradings and work with $\ZZ/2$-gradings, we may also consider a topological Chern--Simons theory in any odd dimension (see \cite{AlekseevMnev} for a 1-dimensional version and \cite{BakGustavsson2} for a 5-dimensional version).
+Just like for the BF theory, we also have two other versions which may be combined into a generalized Chern--Simons theory.
+Another direction we can generalize in is to replace the Lie algebra $\fg$ by a dg Lie algebra in which case the BF theory itself becomes a particular example of the Chern--Simons theory.
+
+Our goal will then be to show that a particular twist of super Yang--Mills is equivalent to a given generalized Chern--Simons theory.
+We summarize our results in two forms.
+In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we summarize all the possible twists of dimensional reductions of 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills and 4d $\cN=1$ super Yang--Mills respectively.
+We will now give a short description of each twisted theory in a more physical language, with references to where in the literature it was previously considered.
 
@@
 This twist was first studied by Baulieu \cite{Baulieu}.
+As is well-known \cite{}, the theory has a one-loop anomaly and does not admit a quantization.
 \end{itemize}
@@
 
+\subsection*{Applications to quantization and a relationship to factorization algebras}
+%\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
+
+The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
+An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
+In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
+
 \subsection*{Outline of the Paper}
-\addcontentsline{toc}{subsection}{Outline of the Paper}
+%\addcontentsline{toc}{subsection}{Outline of the Paper}
 The remainder of the paper is divided into two parts.
@@
 \[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+\label{def:classicalfieldtheory}
 \end{definition}
@@
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
+\label{def:perturbativeequivalence}
 \end{definition}
@@
 
-As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.

### 2020-02-04 paper.tex
Minor edits

--- 2020-02-03 paper.tex
@@
 
-\subsection*{Applications to quantization and a relationship to factorization algebras}
+\subsection*{Applications to Quantization and a Relationship to Factorization Algebras}
 \addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
@@
 
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
 In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
@@
 
-\subsubsection{Generalized Hodge theory}
+\subsubsection{Generalized Hodge Theory}
 Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
@@
 
-\section{Supersymmetric Yang--Mills theories} \label{sect:SYM}
+\section{Supersymmetric Yang--Mills Theories} \label{sect:SYM}
 
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:10dholomorphictwist}
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal Twist}
 \label{sect:9dminimaltwist}
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:8dholomorphictwist}
@@
 
-\subsubsection{Topological twist}
+\subsubsection{Topological Twist}
 \label{sect:8dtopologicaltwist}
@@
 
-\subsubsection{Partially topological twist}
+\subsubsection{Partially Topological Twist}
 \label{sect:8dpartiallytopologicaltwist}
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal Twist}
 \label{sect:7dminimaltwist}
@@
 
-\subsubsection{Topological twist}
+\subsubsection{Topological Twist}
 \label{sect:7dtopologicaltwist}
@@
 
-\subsubsection{Partially topological twist}
+\subsubsection{Partially Topological Twist}
 \label{sect:7dpartialtwist}
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:6dholomorphictwist}
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:6d11holomorphictwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
+\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} Partially Topological Twist}
 \label{sect:6d11partialtwist}
@@
 
-\subsubsection{Topological twist}
+\subsubsection{Topological Twist}
 \label{sect:6d11topologicaltwist}
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal Twist}
 \label{sect:5d1minimaltwist}
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal Twist}
 \label{sect:5dminimaltwist}
@@
 
-\subsubsection{Rank 2 partially topological twist}
+\subsubsection{Rank 2 Partially Topological Twist}
 \label{sect:5dpartialtwist}
@@
 
-\subsubsection{Rank 2 topological twist}
+\subsubsection{Rank 2 Topological Twist}
 \label{sect:5drank2topologicaltwist}
@@
 
-\subsubsection{Rank 4 twist}
+\subsubsection{Rank 4 Twist}
 \label{sect:5drank4twist}
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:4d1holomorphictwist}
@@
 
-\subsubsection{Holomorphic twist}
+\subsubsection{Holomorphic Twist}
 \label{sect:4d_2_holomorphictwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
 \label{sect:4d2Donaldson}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} twist}
+\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} Twist}
 \label{sect:4d_2_11}
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
 \label{sect:4d4Atwist}
@@
 
-\subsubsection{Rank (1, 1) twist}
+\subsubsection{Rank (1, 1) Partially Topological Twist}
 \label{sect:4d4partialtwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} twist}
+\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}
 
@@
 
-\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
+\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Topological Twist}
 \label{sect:4dqgltwist}
@@
 
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
 First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.

### 2020-02-04 paper.tex

--- 2020-02-04 paper.tex
@@
 
-\subsection*{Classical field theories}
+\subsection*{Classical Field Theories}
 
@@
 
-\subsection*{Supersymmetric classical field theories}
+\subsection*{Supersymmetric Classical Field Theories}
 
@@
 
-\subsection*{Supersymmetric twists}
+\subsection*{Supersymmetric Twists}
 
@@
 
-\subsection*{Supersymmetric twists and supergravity}
+\subsection*{Supersymmetric Twists and Supergravity}
 
@@
 \end{itemize}
-
-%\chris{Possible topics for the introduction
-%\begin{enumerate}
-% \item  Context and literature on twists, including in the BV formalism.
-There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
-Also at least a remark on the perspective in terms of coupling to twisted sugra.
-% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
-% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
-% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
-% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
-% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
-% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
-%\end{enumerate}}
 
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang-Mills theory in 9 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory with one topological direction and four holomorphic directions.
+ \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang-Mills theory in 9 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory with one topological direction and four holomorphic directions.
 It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold.
@@
  \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in two directions and holomorphic in the remaining three complex directions.
-This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.
+This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
 It is $\SU(3) \times \Spin(2;\RR)$-invariant, and can be defined on the product of a Calabi-Yau 3-fold and a Riemann surface.
@@
  \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
-The minimal twist is equivalent to a mixed version of BF theory with one topological direction and three complex holomorphic directions.
+The minimal twist is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.
 This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
  \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.
-This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a mixed version of Chern-Simons theory.
+This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
 It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
@@
  \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
-The one by a supercharge of rank $(1,1)$ is equivalent to a mixed form of BF theory, with two topological directions and two complex holomorphic directions.
+The one by a supercharge of rank $(1,1)$ is equivalent to a generalized form of BF theory, with two topological directions and two complex holomorphic directions.
 This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
- \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a mixed form of Chern-Simons theory with four real directions and one complex holomorphic direction.
+ \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a generalized form of Chern-Simons theory with four real directions and one complex holomorphic direction.
 This theory is only $\ZZ/2\ZZ$-graded.
@@
  \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.
-This twist is equivalent to a mixed form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.
+This twist is equivalent to a generalized form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.
 It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).
 This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.
-If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a mixed form of BF theory valued in the adjoint quotient $\gg/\gg$.
+If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized form of BF theory valued in the adjoint quotient $\gg/\gg$.
  \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist, with four invariant directions.
@@
  \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
-This twist is equivalent to a mixed version of BF theory with two real directions and one complex holomorphic direction, coupled to a mixed version of a $U$-valued symplectic boson.
+This twist is equivalent to a generalized version of BF theory with two real directions and one complex holomorphic direction, coupled to a generalized version of a $U$-valued symplectic boson.
 This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.
@@
  \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} There is a minimal twist in dimension 3 which can be defined with $\mc N=2$ supersymmetry, including a chiral multiplet valued in a representation $R$.
-This twist is perturbatively equivalent to a mixed form of BF theory with one real direction and one complex holomorphic direction, coupled to a mixed $\beta \gamma$-system valued in $R$.
+This twist is perturbatively equivalent to a generalized form of BF theory with one real direction and one complex holomorphic direction, coupled to a generalized $\beta \gamma$-system valued in $R$.
 This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
-If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a mixed BF theory now coupled to a mixed symplectic boson.
-Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with mixed BF theory valued in $T[1](\gg/\gg)$.
+If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
+Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
  \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.
@@
  \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
- &&&$\bun_G(\CC^5)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
- &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
+ &&&$\mr{Map}(\CC^5, B\gg)$ &\\ \hline
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Generalized Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ &&&$\mr{Map}(\CC^4 \times \RR_{\mr{dR}}, B\gg)$ &\\ \hline
  \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:8dholomorphictwist] {Rank $(1,0)$ pure}} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
- &&& $T^*[-1]\bun_G(\CC^4)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
- &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^4, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\mr{Map}(\CC^3 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
   && \multirow{2}*{\hyperref[sect:8dtopologicaltwist]{Rank $(1,0)$ impure}} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
- &&& $\bun_G(\CC^4)_\mr{dR}$ & \\ \hline
-  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
- &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
- &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\CC^4, B\gg)_\mr{dR}$ & \\ \hline
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Generalized BF Theory & \multirow{2}*{4 (minimal)} \\
+ &&& $T^*[-1]\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
+ &&& $\mr{Map}(\CC^2 \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
   && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ Impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
- &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}})_\mr{dR}$ & \\ \hline
+ &&& $\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)_\mr{dR}$ & \\ \hline
  \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{\hyperref[sect:6d11holomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
  &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6d11partialtwist]{Rank $(1,1)$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
- &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
- &&& $\bun_G(\CC \times \RR^4_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6d11topologicaltwist]{Rank $(1,1)$ generic}} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
- &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
- \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{\hyperref[sect:5dminimaltwist]{Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
+ && \multirow{2}*{\hyperref[sect:6d11partialtwist]{Rank $(1,1)$ special}} & {Generalized BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Generalized Chern-Simons Theory} & \multirow{2}*{5} \\
+ &&& $\mr{Map}(\CC \times \RR^4_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:6d11topologicaltwist]{Rank $(1,1)$ generic}} & {Perturbatively trivial} & \multirow{2}*{6 (topological)} \\
+ &&& $\mr{Map}(\CC^2 \times \RR^2_{\mr{dR}}, B\gg)_{\mr{dR}}$ & \\ \hline
+ \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{\hyperref[sect:5dminimaltwist]{Rank $1$}} & {Generalized BF Theory} & \multirow{2}*{3 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5dpartialtwist]{Rank $2$ special}} & {Mixed BF Theory} & \multirow{2}*{4} \\
- &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:5dpartialtwist]{Rank $2$ special}} & {Generalized BF Theory} & \multirow{2}*{4} \\
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
  &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5drank2topologicaltwist] {Rank $2$ generic}} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
- &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
+ && \multirow{2}*{\hyperref[sect:5drank2topologicaltwist] {Rank $2$ generic}} & {Perturbatively trivial} & \multirow{2}*{5 (topological)} \\
+ &&& $\mr{Map}(\CC \times \RR^3_{\mr{dR}}, B\gg)_{\mr{dR}}$ & \\ \hline
  \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{\hyperref[sect:4d4holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(1,1)$}} & Mixed BF Theory & \multirow{2}*{3} \\
- &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ special}} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
- &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^2_{\mr{Dol}}, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(1,1)$}} & Generalized BF Theory & \multirow{2}*{3} \\
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ special}} & BF Theory  & \multirow{2}*{4 (topological)} \\
+ &&& $T^*[-1]\mr{Map}(\RR^4_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d4partialtwist] {Rank $(2,1)$}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
- &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d4Atwist] {Rank $(2,0)$}} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
- &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ generic}} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
- &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
-  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
+ &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg)_{\mr{dR}}$ & \\ \cline{3-5}
+ && \multirow{2}*{\hyperref[sect:4d4Atwist] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
+ &&& $\mr{Map}(\CC^2_{\mr{Dol}}, B\gg)_{\mr{dR}}$ & \\ \cline{3-5}
+  && \multirow{2}*{\hyperref[sect:4dqgltwist] {Rank $(2,2)$ generic}} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
+ &&& $\mr{Map}(\RR^4_{\mr{dR}}, B\gg)_{\mr{dR}}$ & \\ \hline
+  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Generalized BF Theory} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial (Casson)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
@@
  &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
- \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
+ \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3 (minimal)} \\
  &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
@@
  &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
+ && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
  &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
  &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
- \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
+ \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial (Casson)} & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
  &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
@@
  &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
- \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{\hyperref[sect:3dminimaltwist] {Rank $1$}} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
+ \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{\hyperref[sect:3dminimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
  &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
@@
 
-\subsection*{Applications to quantization and a relationship to factorization algebras}
+\subsection*{Applications to Quantization and a Relationship to Factorization algebras}
 %\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
@@
 \begin{theorem} \label{3d_minimal_twist_thm}
-The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
 Moreover this equivalence is $\mr U(1)$-equivariant.

### 2020-02-04 paper.tex
merge

--- 2020-02-04 paper.tex
@@
 
-\subsection*{Applications to Quantization and a Relationship to Factorization Algebras}
-\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
+\subsection*{Applications to quantization}
+\addcontentsline{toc}{subsection}{Applications to quantization}
 
@@
 
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
-In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
+This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
+In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+
+In principle, the existence of local counterterms can be used to analyze the full untwisted supersymmetric gauge theories in a mathematically rigorous way.
+In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.
+
+A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
+For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}
+
+There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
+For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
+Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
+Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.
+
+We show that while not every twist results in a topological field theory, it does result in a theory that is {\em mixed holomorphic / topological}. 
+\brian{open to a new name}
+For a translation invariant field theory, what this means is that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way.
+
+Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
+The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
+It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. 
+Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.
+
+These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. 
+In fact, in many examples not much is lost when asking for just the one-loop behavior, any gauge theory of type $BF$ results in quantization which is exact at one loop; meaning all higher order corrections vanish identically.
+While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.
+
+\subsection*{The relationship to factorization algebras}
 
@@
 
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $\Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
+\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
 
@@
 
-\subsubsection{Generalized Hodge Theory}
+\subsubsection{Generalized Hodge theory}
 Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
@@
 
-\section{Supersymmetric Yang--Mills Theories} \label{sect:SYM}
+\section{Supersymmetric Yang--Mills theories} \label{sect:SYM}
 
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:10dholomorphictwist}
@@
 
-\subsubsection{Minimal Twist}
+\subsubsection{Minimal twist}
 \label{sect:9dminimaltwist}
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:8dholomorphictwist}
@@
 
-\subsubsection{Topological Twist}
+\subsubsection{Topological twist}
 \label{sect:8dtopologicaltwist}
@@
 
-\subsubsection{Partially Topological Twist}
+\subsubsection{Partially topological twist}
 \label{sect:8dpartiallytopologicaltwist}
@@
 
-\subsubsection{Minimal Twist}
+\subsubsection{Minimal twist}
 \label{sect:7dminimaltwist}
@@
 
-\subsubsection{Topological Twist}
+\subsubsection{Topological twist}
 \label{sect:7dtopologicaltwist}
@@
 
-\subsubsection{Partially Topological Twist}
+\subsubsection{Partially topological twist}
 \label{sect:7dpartialtwist}
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:6dholomorphictwist}
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:6d11holomorphictwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} Partially Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
 \label{sect:6d11partialtwist}
@@
 
-\subsubsection{Topological Twist}
+\subsubsection{Topological twist}
 \label{sect:6d11topologicaltwist}
@@
 
-\subsubsection{Minimal Twist}
+\subsubsection{Minimal twist}
 \label{sect:5d1minimaltwist}
@@
 
-\subsubsection{Minimal Twist}
+\subsubsection{Minimal twist}
 \label{sect:5dminimaltwist}
@@
 
-\subsubsection{Rank 2 Partially Topological Twist}
+\subsubsection{Rank 2 partially topological twist}
 \label{sect:5dpartialtwist}
@@
 
-\subsubsection{Rank 2 Topological Twist}
+\subsubsection{Rank 2 topological twist}
 \label{sect:5drank2topologicaltwist}
@@
 
-\subsubsection{Rank 4 Twist}
+\subsubsection{Rank 4 twist}
 \label{sect:5drank4twist}
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:4d1holomorphictwist}
@@
 
-\subsubsection{Holomorphic Twist}
+\subsubsection{Holomorphic twist}
 \label{sect:4d_2_holomorphictwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
 \label{sect:4d2Donaldson}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} Twist}
+\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} twist}
 \label{sect:4d_2_11}
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
 \label{sect:4d4Atwist}
@@
 
-\subsubsection{Rank (1, 1) Partially Topological Twist}
+\subsubsection{Rank (1, 1) twist}
 \label{sect:4d4partialtwist}
@@
 
-\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} twist}
 
@@
 
-\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
 \label{sect:4dqgltwist}
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.
+\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(3)$.
 The fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.
+\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.
 The fields we obtain are
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.
 The fields we obtain are
@@
 
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
 First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\mr O(2)$.
 The fields we obtain are
@@
  \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.
-There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.
+There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.
  \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
-Moreover, this equivalence is $\mr U(1)$-equivariant.
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
 \end{theorem}

### 2020-02-04 paper.tex

--- 2020-02-04 paper.tex
@@
 \begin{abstract}
-We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
+We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
 We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
@@
 To summarize, supersymmetric twisting consists of the following three steps:
+
 \begin{enumerate}
@@
 \end{itemize}
+
+% \item  Context and literature on twists, including in the BV formalism.
+There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
+Also at least a remark on the perspective in terms of coupling to twisted sugra.
+% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
+% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
+% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
+% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
+% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
+% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
+%\end{enumerate}}
+
+\subsection*{Applications to quantization}
+%\addcontentsline{toc}{subsection}{Applications to quantization}
+
+The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
+An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
+This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
+In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+
+In principle, the existence of local counterterms can be used to analyze the full untwisted supersymmetric gauge theories in a mathematically rigorous way.
+In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.
+
+A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
+For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}
+
+There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
+For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
+Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
+Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.
+
+We show that while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
+For a translation invariant field theory, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way, but it is possible that more than half of the translation invariant vector fields act trivially in cohomology.
+
+Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
+The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
+It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. 
+Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.
+
+These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. 
+Furthermore, in many examples of theories obtained via twisting not much is lost when asking for the one-loop quantization.
+The twisted gauge theories of type $BF$, which are plentiful in the examples we consider,  admit quantizations which are exact at one loop; meaning all higher order corrections vanish identically. 
+While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.
+
+\subsection*{The relationship to factorization algebras}
 

### 2020-02-04 paper.tex
working on 2d

--- 2020-02-04 paper.tex
@@
 \end{theorem}
+
 \begin{proof}
@@
  \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
+ \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
  \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
@@
 \begin{proof}
-This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_to_BF_diml_red_prop} to dimensionally reduce in the real de Rham direction.
+The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_to_BF_diml_red_prop}) to Theorem \ref{3d_minimal_twist_thm} calculating the minimal twist of 3d $\mc N=2$ super Yang-Mills on $\CC \times \RR_{\mr{dR}}$.
+This equivalence is $\mr U(1)$-equivariant.
+It is also $\ZZ$-graded, using the twisting datum $\alpha = \phi_A$.
 \end{proof}
@@
 \subsubsection{Topological A Twist} \label{sect:2d22Atwist}
+
+To deform the holomorphic twist to the topological A-twist, obtaining a Hodge deformation, we use similar techniques to those of Section \ref{sect:4d2Donaldson}.
+We first analyze how the supersymmetry action decomposes.
+Consider the 1-parameter family of supercharges
+\begin{equation} \label{eq:2dHodgefamily}
+Q_t = Q_0 + tQ',
+\end{equation}
+where $Q_0 = (1,i) \in S_+$ is a holomorphic supercharge, and $Q' = (1,i) \in S_-$.
+This family of supercharges are all compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
+They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.
+Let us first decompose our fields according to the twisting homomorphism $\phi_A$.
+The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
+\begin{itemize}
+ \item $\gg$-valued bosons: $(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^4)$.
+ \item $R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
+ \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
+ \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+\end{itemize}
+
+\begin{prop}
+Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
+The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
+\begin{align*}
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(\frac 12((\rho(\dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\dd_{A_1}\chi_{-1}), \lambda_0^*)) -t(\lambda_{-2}, A^*_1) + (\lambda_0, \chi^*_{-1})) \right)  \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol  \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol  \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol .
+\end{align*}
+\end{prop}
 

### 2020-02-04 paper.tex
bib

--- 2020-02-04 paper.tex
@@
 
-We instead take another approach pioneered by Baulieu \cite{}.
+We instead take another approach pioneered by Baulieu \cite{BaulieuBV}.
 Namely, one may canonically extend the supersymmetry action from ordinary fields $\cF$ to the space of BV fields $\cE$.
@@
 This twist was first studied by Baulieu \cite{Baulieu}.
-As is well-known \cite{}, the theory has a one-loop anomaly and does not admit a quantization.
+As is well-known \cite{GSanomaly}, the theory has a one-loop anomaly and does not admit a quantization.
 \end{itemize}

### 2020-02-04 paper.tex
merging

--- 2020-02-04 paper.tex
@@
 
-\subsection*{Applications to quantization}
+\subsection*{Applications to Quantization}
 %\addcontentsline{toc}{subsection}{Applications to quantization}

### 2020-02-04 paper.tex
2d calc in progress

@@
 \begin{itemize}
- \item $\gg$-valued bosons: $(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^4)$.
+ \item $\gg$-valued bosons: $(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
  \item $R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
@@
 \begin{align*}
-I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(\frac 12((\rho(\dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\dd_{A_1}\chi_{-1}), \lambda_0^*)) -t(\lambda_{-2}, A^*_1) + (\lambda_0, \chi^*_{-1})) \right)  \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol  \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol  \\
-I_{\rm matter}^{(2)}(Q_t) &= \int \dvol .
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) + (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) + (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{2}^*) + (\rho(\dd_{A_1}\chi_{1}), \lambda_0^{'*}))   \right)  \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(\frac t4 (\lambda_{-2}^*, \lambda_0^*) - ********** - t(\chi_{-1}, c_0^*)\right)  \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*  \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\ol \dd_{A_1}  \phi_0, \psi_{1}^*  \right)\right)  \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
 \end{align*}
@@
 \begin{proof}
-
+\chris{in progress}
+We proceed by first integrating out the field $\lambda_2$ and its antifield $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.
+We can then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$.
+At $t=0$, we are left with the holomorphic twist from Theorem \ref{2d_minimal_twist_thm}, i.e, the theory $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The action functional is further deformed by the remaining $t$-linear terms, which together take the form
+\[\int \dvol t\left( \right).\]
+In terms of the classical BV complex we can identify these terms as introducing the following dotted isomorphism between two summands:
+\[\xymatrix@R=0.4cm@C=0.2cm{
+\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
+&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^*_2} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
+\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_2^*} \ar@{-->}[ur]\\
+&\Omega^0(\RR^2; R^*)_{\ol \psi_1} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
+&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
+&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
+&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{-1}}. &\\
+}\]
+This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
 \end{proof}

### 2020-02-05 paper.tex
2d A-twist

--- 2020-02-04 paper.tex
@@
 \end{itemize}
+We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
 
@@
 \begin{align*}
-I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(\frac 12((\rho(\dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\dd_{A_1}\chi_{-1}), \lambda_0^*)) -t(\lambda_{-2}, A^*_1) + (\lambda_0, \chi^*_{-1})) \right)  \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol  \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol  \\
-I_{\rm matter}^{(2)}(Q_t) &= \int \dvol .
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*  \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*  \right)\right)  \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
 \end{align*}
@@
 \begin{proof}
-
+We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$, integrating out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.
+We can then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}.
+At $t=0$, we are left with the holomorphic twist from Theorem \ref{2d_minimal_twist_thm}, i.e, the theory $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The action functional is further deformed by the remaining $t$-linear terms, which together take the form
+\[\int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right).\]
+In terms of the classical BV complex we can identify these terms as introducing the following dotted isomorphism between two summands:
+\[\xymatrix@R=0.4cm@C=0.2cm{
+\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
+&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
+\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
+&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
+&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
+&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
+&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
+}\]
+This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
 \end{proof}
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sect:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with Matter} \label{sect:2d(0,2)}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with matter}
+\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with Matter}
 

### 2020-02-05 paper.tex
cmon guys, we can't use phi and varphi to mean two different things

@@
 \]
-whose sections we denote by $e_0 + \varphi + \varphi^* + \psi + \psi^*$ according to the above decomposition. 
+whose sections we denote by $e_0 + \varsigma + \varsigma^* + \psi + \psi^*$ according to the above decomposition. 
 The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
@@
 \item Matter bosons $\nu\in\Omega^0(M; U\otimes K_M^{-1/2})[-2n]$, $\phi\in\Omega^0(M; U\otimes K_M^{1/2})[2n]$.
-\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U\otimes K_M^{1/2})[2n-1]$, $\varphi \in \Omega^{2,0} (M ; U\otimes K_M^{-1/2})[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U\otimes K_M^{-1/2})[-2n+1]$.
+\item Matter fermions $\psi \in \Omega^{0,1} (M ;  U\otimes K_M^{1/2})[2n-1]$, $\varsigma \in \Omega^{2,0} (M ; U\otimes K_M^{-1/2})[-2n+1]$, $\Tilde{\nu} \in \Omega^{0,2}(M ; U\otimes K_M^{-1/2})[-2n+1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 \rho&\rightsquigarrow \rho, \Tilde{\chi} \\
-\psi & \rightsquigarrow \psi, \varphi . \\
+\psi & \rightsquigarrow \psi, \varsigma . \\
 \end{align*}
@@
 \\
-\phi + \psi + \varphi^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
-\varphi + \psi^* + \phi^* &\in\Omega^{2, \bullet}(M; U\otimes K_M^{-1/2})[1-2n]
+\phi + \psi + \varsigma^*&\in\Omega^{0, \bullet}(M; U\otimes K_M^{1/2})[2n] \\
+\varsigma + \psi^* + \phi^* &\in\Omega^{2, \bullet}(M; U\otimes K_M^{-1/2})[1-2n]
 \end{align*}
@@
 \ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
-\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varphi^*} \\
-& & & & \Omega^{2,0}(\CC^2 ; U)_{\varphi} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
+\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varsigma^*} \\
+& & & & \Omega^{2,0}(\CC^2 ; U)_{\varsigma} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
 }
@@
 I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varphi^* \right) \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
 I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
@@
 %\begin{align*}
-%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
 %I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
@@
 We are left with the action
-\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
+\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
@@
 & & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
-& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
-& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
+& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varsigma^*} \\
+& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varsigma} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
 }
@@
 \item Matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
-\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varphi \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
+\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 c+A_{0, 1}+B&\in\Omega^{0, \bullet}(M; \fg)[1] \\
-\phi + \psi + \varphi^*&\in\Omega^{1, \bullet}(M; \fg) \\
+\phi + \psi + \varsigma^*&\in\Omega^{1, \bullet}(M; \fg) \\
 \xi + b^* + a^*&\in\Omega^{2, \bullet}(M; \fg)[-1] \\
@@
 a + b + \xi^*&\in\Omega^{0, \bullet}(M; \fg)[2] \\
-\varphi + \psi^* + \phi^* &\in\Omega^{1, \bullet}(M; \fg)[1] \\
+\varsigma + \psi^* + \phi^* &\in\Omega^{1, \bullet}(M; \fg)[1] \\
 B^*+A^*_{0, 1}+ c^*&\in\Omega^{2, \bullet}(M; \fg)
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
 I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
@@
 \begin{align*}
-& (t \varphi, \rho, t \phi, A_{1,0}) \\
+& (t \varsigma, \rho, t \phi, A_{1,0}) \\
 & (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
@@
 \begin{align*}
-\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
 &+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
+%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
 \Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
@@
 \[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
 More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
@@
 \label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
+t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
 \end{equation}

### 2020-02-05 paper.tex
Starting 2d (4,4)

@@
 The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 
-Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
+Finally, there is the 2d B-twist.
+This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
+Indeed, let $W_3$ be the 2d auxiliary space in the 3d $\mc N=2$ supertranslation algebra.
+The 3d spin representation $S \otimes W_3$ splits into $S_+ \otimes W_3 \oplus S_- \otimes W_3$ as a $\spin(2;\CC)$-module.
+Rank one square zero elements in 3d $\mc N=2$ generically become rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.
+There is a square-zero supercharge in 3d $\mc N=2$ compatible with the identity twisting homomorphism $\spin(2;\CC) \to \spin(2;\CC)$.
+This becomes the B-twisting homomorphism of $\spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ of weight $(1,-1)$ in the 2d $\mc N=(2,2)$-algebra.
+
 \begin{theorem} \label{2d_2_B_twist_thm}
 The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.
+In other words, every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group in the $\mc N=(4,4)$ case is $\spin(4;\CC) \times \spin(4;\CC)$, and in the $\mc N=(8,8)$ case it is $\spin(8;\CC)$ (acting on both $W_+$ and $W_-$ by its defining representation.
+In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.
+\chris{todo}
 
@@
 \subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
+\begin{theorem}
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
+\end{theorem}
+
 \subsubsection{Topological A Twist} \label{sect:2d44Atwist}
-
 \begin{theorem}
 The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.
-Together they are perturbatively equivalent to a holomorphic BF theory and its Hodge deformation, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
-
+This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.

### 2020-02-06 paper.tex
just in case

@@
 
-\begin{proof}
-We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
-\begin{align*}
-& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-\end{align*}
-This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-\begin{align*}
-\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-\end{align*}
-
-The next step is to decompose the $(1,1)$ form $\psi$ as
-\[
-\psi = \omega \Lambda \psi + \psi_{\perp}
-\]
-where $\Lambda \psi_{\perp} = 0$.
-
-\end{proof}
-
-\chris{I just made the following attempt}
+%\begin{proof}
+%We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
+%\begin{align*}
+%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
+%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+%\end{align*}
+%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+%\begin{align*}
+%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+%\end{align*}
+%
+%The next step is to decompose the $(1,1)$ form $\psi$ as
+%\[
+%\psi = \omega \Lambda \psi + \psi_{\perp}
+%\]
+%where $\Lambda \psi_{\perp} = 0$. 
+%
+%\end{proof}
+
 \begin{theorem}
@@
 
-This theory admits a unique twist:
+This theory admits a unique twist up to equivalence:
 \begin{itemize}
@@
  In this case $Q$ is minimal, with 2 invariant directions.  
-Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-Rank 2 supercharges are topological.
+ Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
+They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2. Such supercharges are topological.  
 A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
-The $G_R = \Spin(4;\RR)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
+The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  
 We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
-The A-twist admits the twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
-and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.  The other topological orbit admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  This twist is only $\ZZ/2\ZZ$-graded
+\begin{enumerate}
+\item
+An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$. and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+\item
+A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
+This twist is only $\ZZ/2\ZZ$-graded
+\end{enumerate}
 \end{itemize}

### 2020-02-06 paper.tex
merging

--- 2020-02-05 paper.tex
@@
 
-The original classical field theory carried a $\ZZ\times\ZZ/2$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2$ is the fermionic grading.
+The original classical field theory carried a $\ZZ\times\ZZ/2\ZZ$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2\ZZ$ is the fermionic grading.
 We see that $\mathrm{d}$ has bidegree $(1, 0)$ while $Q$ has bidegree $(0, 1)$.
-So, in general the twisted theory is only $\ZZ/2$-graded (with respect to the total grading).
+So, in general the twisted theory is only $\ZZ/2\ZZ$-graded (with respect to the total grading).
 To improve that, we may additionally consider a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ into the R-symmetry group under which $Q$ has weight $1$ and such that the $\alpha$-grading modulo 2 coincides with the fermionic grading.
@@
 
-\subsection*{The relationship to factorization algebras}
+\subsection*{The Relationship to Factorization Algebras}
 
@@
 Let us also recall that if $\fg$ is equipped with a symmetric bilinear nondegenerate pairing, we also have a 3-dimensional topological Chern--Simons theory.
-If we forgo $\ZZ$-gradings and work with $\ZZ/2$-gradings, we may also consider a topological Chern--Simons theory in any odd dimension (see \cite{AlekseevMnev} for a 1-dimensional version and \cite{BakGustavsson2} for a 5-dimensional version).
+If we forgo $\ZZ$-gradings and work with $\ZZ/2\ZZ$-gradings, we may also consider a topological Chern--Simons theory in any odd dimension (see \cite{AlekseevMnev} for a 1-dimensional version and \cite{BakGustavsson2} for a 5-dimensional version).
 Just like for the BF theory, we also have two other versions which may be combined into a generalized Chern--Simons theory.
@@
 Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge.
-The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
+The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
 \[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
@@
 
-The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
+The claim about the underlying $\ZZ/2\ZZ$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
@@
 \item Rank $(2, 2)$.
-The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory.
+The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2\ZZ$-graded theory.
 The twisting homomorphism is given by the obvious embedding $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \CC)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
@@
 
-The claim about the underlying $\ZZ/2$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
+The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
 
@@
 In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.
-\chris{todo}
+We may instead compose the inclusion $\spin(2;\CC) \to \spin(3;\CC)$ with the twisting homomorphism from Section \ref{3d8section}.
 
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
+
+For the topological B-twist, the following result follows again by substituting $R = U \oplus \gg$, but in order to obtain $\mr U(1)$-equivariance in the $\mc N=(8,8)$ case \chris{...}
 
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}

### 2020-02-06 paper.tex
2d N=(4,4) and (8,8)

@@
 When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
-When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
+When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.
+We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
  \label{table_of_twists_2d}
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
+The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
 
@@
 There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.
- \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.
+ \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.
 Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.
 By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.
-The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
+The $\ZZ/2\ZZ$-action swaps the two A supercharges and the two B supercharges, leaving two orbits under $\spin(2;\CC) \times G_R$.
+The A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
 Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
@@
 
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sect:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
-We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.
-In other words, every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
-
-The R-symmetry group in the $\mc N=(4,4)$ case is $\spin(4;\CC) \times \spin(4;\CC)$, and in the $\mc N=(8,8)$ case it is $\spin(8;\CC)$ (acting on both $W_+$ and $W_-$ by its defining representation.
-In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.
-We may instead compose the inclusion $\spin(2;\CC) \to \spin(3;\CC)$ with the twisting homomorphism from Section \ref{3d8section}.
-
-The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
+We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
+No new twists arise, i.e.
+every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e.
+by its fundamental representation on $W^6$.
+
+In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
+
+\begin{prop}
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
+The B-supercharge occurs as a degeneration of A-type supercharges.
+\end{prop}
+
+\begin{proof}
+First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$.
+A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.
+There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.
+We will refer to these as the B- and A-supercharges respectively.
+\end{proof}
+
+Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.
+Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.
+Therefore the two vectors in $W_+^6$ discussed above must be colinear.
 
 \subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
+We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
 \begin{theorem}
 The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
-If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \subsubsection{Topological A Twist} \label{sect:2d44Atwist}
+We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
 \begin{theorem}
@@
 This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
-If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-
-For the topological B-twist, the following result follows again by substituting $R = U \oplus \gg$, but in order to obtain $\mr U(1)$-equivariance in the $\mc N=(8,8)$ case \chris{...}
+Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
@@
 The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
-If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
+
+\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
+Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.
+No new twists arise, i.e.
+every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semispin representations.
+As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we say in the $\mc N=(4,4)$ case.
+Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.
+
+\begin{prop}
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
+The B-supercharge occurs as a degeneration of A-type supercharges.
+\end{prop}
+
+\begin{proof}
+Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
+Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.
+The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.
+As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
+\begin{align*}
+ W_+ &\iso (\CC \oplus \wedge^2 L \oplus \wedge^4 L) \otimes \det(L)^{-1/2} \\
+ W_- &\iso (L \oplus \wedge^3 L) \otimes \det(L)^{-1/2},
+\end{align*}
+with $w_+ \in \wedge^4 L$.
+With respect to this decomposition, say $w_- = (v_1,v_3)$.
+If $v_1 \ne 0$, then we can act by $\wedge^2 L \sub \stab(w_+)$ to make $v_3 = 0$.
+Under the action of $\SL(L)$ all such non-zero $v_1$ are in the same orbit.
+Likewise if $v_1 = 0$ then $v_3 \ne 0$ and we can act by $\SL(L)$ to see that all such non-zero $v_3$ are in the same orbit.
+There are, therefore, two orbits once again, with one degenerating to the other.
+\end{proof}
+
+Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.
+Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.
+In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.
+
+\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
+We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
+\begin{theorem}
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
+
+\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
+We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
+\begin{theorem}
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.
+This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
+
+\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
+We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
+\begin{theorem}
+The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.
 This equivalence is $\mr U(1)$-invariant.

### 2020-02-06 paper.tex
merge

--- 2020-02-06 paper.tex
@@
 
-\subsection*{Supersymmetric Classical Field Theories}
+\subsection*{Classical Supersymmetric Field Theories}
 
@@
 
-The original classical field theory carried a $\ZZ\times\ZZ/2\ZZ$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2\ZZ$ is the fermionic grading.
+The original classical field theory carried a $\ZZ\times\ZZ/2$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2$ is the fermionic grading.
 We see that $\mathrm{d}$ has bidegree $(1, 0)$ while $Q$ has bidegree $(0, 1)$.
-So, in general the twisted theory is only $\ZZ/2\ZZ$-graded (with respect to the total grading).
+So, in general the twisted theory is only $\ZZ/2$-graded (with respect to the total grading).
 To improve that, we may additionally consider a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ into the R-symmetry group under which $Q$ has weight $1$ and such that the $\alpha$-grading modulo 2 coincides with the fermionic grading.
@@
 
-\subsection*{The Relationship to Factorization Algebras}
+\subsection*{The relationship to factorization algebras}
 
@@
 Let us also recall that if $\fg$ is equipped with a symmetric bilinear nondegenerate pairing, we also have a 3-dimensional topological Chern--Simons theory.
-If we forgo $\ZZ$-gradings and work with $\ZZ/2\ZZ$-gradings, we may also consider a topological Chern--Simons theory in any odd dimension (see \cite{AlekseevMnev} for a 1-dimensional version and \cite{BakGustavsson2} for a 5-dimensional version).
+If we forgo $\ZZ$-gradings and work with $\ZZ/2$-gradings, we may also consider a topological Chern--Simons theory in any odd dimension (see \cite{AlekseevMnev} for a 1-dimensional version and \cite{BakGustavsson2} for a 5-dimensional version).
 Just like for the BF theory, we also have two other versions which may be combined into a generalized Chern--Simons theory.
@@
  \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
+Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenCDO} in relationship to the chiral algebra of chiral differential operators. 
 \end{itemize}
@@
 
+\subsection{Local formal moduli problems}
+
 \subsection{Classical BV Theories}
@@
 \end{definition}
+
+\brian{Cite Getzler \cite{GetzlerBracket}}
 
@@
 Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge.
-The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
+The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
 \[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
@@
 
-The claim about the underlying $\ZZ/2\ZZ$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
+The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}).
 We are left to check that the equivalence respects  the gradings and the $\U(4)$-action.
@@
 \item Rank $(2, 2)$.
-The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2\ZZ$-graded theory.
+The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory.
 The twisting homomorphism is given by the obvious embedding $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \CC)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
@@
 
-The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
+The claim about the underlying $\ZZ/2$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
 
@@
 The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-We fix $W = \CC^2$ equipped with a nondegenerate symmetric bililear pairing.
+We fix $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
 
@@
 In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.
-We may instead compose the inclusion $\spin(2;\CC) \to \spin(3;\CC)$ with the twisting homomorphism from Section \ref{3d8section}.
+\chris{todo}
 
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
-This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-
-For the topological B-twist, the following result follows again by substituting $R = U \oplus \gg$, but in order to obtain $\mr U(1)$-equivariance in the $\mc N=(8,8)$ case \chris{...}
 
@@
 If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
-This equivalence is $\mr U(1)$-invariant.
 \end{theorem}

### 2020-02-07 paper.tex
merge

@@
 
-\brian{Cite Getzler \cite{GetzlerBracket}}
-
 We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
@@
 This bracket is of cohomological degree $+1$. 
-We will now explain how to define the BV bracket.  First note that there is a linear map
+This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
+
+We explain how to define the BV bracket in our context.  
+First note that there is a linear map
 \[
@@
 
-There is a corollary of this proposition obtained by iterating the procedure. 
-We will only use a single iteration.
-
-\begin{cor} \label{cor: quad}
-Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
-Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
-\[
-E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
-\]
-whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
-The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
-Suppose further that the local functional
-\[
-S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
-\]
-satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
-Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
-\[
-E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
-\]
-and
-\[
-S' = S_0 + \int \phi_1 \psi_1^* - S''
-\]
-where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
-\end{cor}
-\begin{proof}
-%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
-We begin by making the following change of coordinates on the BV fields:
-\begin{align*}
-\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
-\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
-%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
-%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
-\end{align*}
-with $\phi_1, \psi_1$ left fixed. 
-This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
-Further, in the new coordinates, the action takes the form
-\[
-S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
-\]
-\end{proof}
+%There is a corollary of this proposition obtained by iterating the procedure. 
+%We will only use a single iteration. 
+%
+%\begin{cor} \label{cor: quad}
+%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+%\[
+%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
+%\]
+%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
+%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
+%Suppose further that the local functional
+%\[
+%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
+%\]
+%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
+%\[
+%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
+%\]
+%and
+%\[
+%S' = S_0 + \int \phi_1 \psi_1^* - S''
+%\]
+%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
+%\end{cor}
+%\begin{proof}
+%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
+%We begin by making the following change of coordinates on the BV fields:
+%\begin{align*}
+%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
+%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
+%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
+%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
+%\end{align*}
+%with $\phi_1, \psi_1$ left fixed. 
+%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
+%Further, in the new coordinates, the action takes the form
+%\[
+%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+%\]
+%\end{proof}
 
@@
 \begin{proof}
-Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
+Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
 Consider the supersymmetry actions

### 2020-02-07 paper.tex
working on p1

@@
 
-We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
+We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$ as vector bundles on $\RR$. 
 Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
@@
 
-We have
+We have an isomorphism of vector bundles on $V$:
 \[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
-and
+and similarly an isomorphism of bundles on $V_\RR$:
 \[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]
 
-Under the pullback map
+Under the composition
 \[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
-the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$.
-\brian{This is not defined} \chris{is compactly supported enough?
-We want to compare pairings.}
+defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ which projects onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
+This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
 \end{proof}
@@
 We begin with a description of certain pure supersymmetric Yang--Mills theories.
-Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
+Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
 Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
@@
 
-\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
-\end{itemize}
-
-We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
-Let $\cE_{\gauge}$ denote the space of BV fields.
+\item A ghost field $c\in\Omega^0(V_\RR; \fg[1])$.
+\end{itemize}
 
@@
 
-The BRST action is given by
-\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
-
-We introduce gauge transformations
-\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
-so that the BV action is given by
+\begin{definition}
+The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
+\[
+F_{\rm gauge} = \Omega^1(V_\RR; \fg) \oplus \Gamma(V_\RR; \Pi \Sigma \otimes \fg) \oplus \Omega^0(V_\RR; \fg[1])
+\]
+whose sections we denote by $(A, \lambda, c)$.  
+The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d : \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
+\[
+\begin{array}{ccccccc}
+[-,-] & : & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
+\end{array}
+\]
+defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
+The BRST action is defined by
+\[
+S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).
+\]
+\end{definition}
+
+The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
+By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
+If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
+%We introduce gauge transformations
+%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
+%so that the BV action is given by
 \begin{equation}
@@
 \end{equation}
-
+%
+%We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
+Let $\cE_{\gauge}$ denote the space of BV fields.
 To simplify the notation, the pairing on $\fg$ from now on will be implicit.

### 2020-02-07 paper.tex
working on p1

@@
 Under the composition
-\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
+\[\Omega^\bullet(V_\RR; \CC)\xto{p^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
 defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ which projects onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
@@
 \label{sect:mattermultipletSUSY}
-
-\brian{How do we see the various flavors of matter multiplets? For instance, in $2d (0,2)$ there is the Fermi multiplet and the chiral multiplet. 
-Your description only sees the chiral.
-In $2d (0,4)$ there are even more: the hypermultiplet (two $(0,2)$ chirals), the twisted hypermultiplet (the same as the hyper, different $R$-symmetry), the fermi multiplet (two $(0,2)$ fermi multiplets).
-I'm not sure which your description sees, but I have a hunch it's the $(0,4)$ hypermultiplet. 
-What is the reason for only seeing certain multiplets via this general setup?
-} \chris{Presumably pure $\mc N = (0,N)$ means a $(0,2)$ vector coupled to $N-2$ Fermi multiplets, so some of these are already covered by the classification?
-Perhaps your concern is that you want a formalism that allows Fermis that are not adjoint valued?
-I don't think the difference between this hyper and twisted hyper is germane here: the proof of supersymmetry is that there is an action of super Poincar\'e, it doesn't involve the action of R-symmetry.}
 

### 2020-02-08 paper.tex
minor edits

@@
 
-\subsection*{Applications to Quantization and a Relationship to Factorization algebras}
-%\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
-
-The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
-An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
-
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
-In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
-
 \subsection*{Outline of the Paper}
@@
 \[
-\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+\d_{\mr{dR}} \colon \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
 \]
@@
 \]
-where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
+where $D_i$ is a differential operator $D_i \colon \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
 Without loss of generality, suppose $F$ is of this form. 
@@
 \[
-\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
 \]
@@
 Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
-The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
-The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
+The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
 First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
@@
 Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
-The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
-The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
+The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
 The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
@@
 Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
-These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
+These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model.
 By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.
@@
 whose sections we denote by $(A, \lambda, c)$.  
-The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d : \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
+The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d :\colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
 \[
 \begin{array}{ccccccc}
-[-,-] & : & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
+[-,-] & \colon & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
 \end{array}
@@
 
-We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+We use the same twisting homomorphism $\phi \colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha \colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
 Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
@@
 
-\begin{theorem} 
+\begin{theorem}  \label{3d_8_minimal_twist_thm}
 The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
@@
 
-\begin{theorem} 
+\begin{theorem} \label{3d_8_A_twist_thm}
 The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
@@
 
-\begin{theorem} 
+\begin{theorem} \label{3d_8_B_twist_thm}
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
@@
 The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.
-
-\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
 

### 2020-02-10 paper.tex
Minor, and a remark on unitary structures in 10d

@@
 
+\begin{remark}
+It is important here that we are working in the complexified setting.
+While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges, since a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
+So necessarily, twists of maximal super Yang-Mills theory cannot be compatible with any unitary structure.
+\end{remark}
+
 Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as

### 2020-02-11 paper.tex
merge

--- 2020-02-07 paper.tex
@@
 
-\subsection*{Classical Supersymmetric Field Theories}
+\subsection*{Supersymmetric Classical Field Theories}
 
@@
  \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.}
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenCDO} in relationship to the chiral algebra of chiral differential operators. 
 \end{itemize}
@@
 When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
-When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.
-We can promote the supersymmetry to $\mc N=(8,8)$ when $U = T^*\gg$, but no new twists occur.}
+When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
  \label{table_of_twists_2d}
@@
 
-\subsection{Local formal moduli problems}
-
 \subsection{Classical BV Theories}
@@
 This bracket is of cohomological degree $+1$. 
-This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
-
-We explain how to define the BV bracket in our context.  
-First note that there is a linear map
+We will now explain how to define the BV bracket.  First note that there is a linear map
 \[
@@
 
-%There is a corollary of this proposition obtained by iterating the procedure. 
-%We will only use a single iteration. 
-%
-%\begin{cor} \label{cor: quad}
-%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
-%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
-%\[
-%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
-%\]
-%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
-%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
-%Suppose further that the local functional
-%\[
-%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
-%\]
-%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
-%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
-%\[
-%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
-%\]
-%and
-%\[
-%S' = S_0 + \int \phi_1 \psi_1^* - S''
-%\]
-%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
-%\end{cor}
-%\begin{proof}
-%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
-%We begin by making the following change of coordinates on the BV fields:
-%\begin{align*}
-%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
-%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
-%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
-%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
-%\end{align*}
-%with $\phi_1, \psi_1$ left fixed. 
-%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
-%Further, in the new coordinates, the action takes the form
-%\[
-%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
-%\]
-%\end{proof}
+There is a corollary of this proposition obtained by iterating the procedure. 
+We will only use a single iteration.
+
+\begin{cor} \label{cor: quad}
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+\[
+E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
+\]
+whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
+The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
+Suppose further that the local functional
+\[
+S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
+\]
+satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
+\[
+E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
+\]
+and
+\[
+S' = S_0 + \int \phi_1 \psi_1^* - S''
+\]
+where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
+\end{cor}
+\begin{proof}
+%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
+We begin by making the following change of coordinates on the BV fields:
+\begin{align*}
+\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
+\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
+%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
+%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
+\end{align*}
+with $\phi_1, \psi_1$ left fixed. 
+This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
+Further, in the new coordinates, the action takes the form
+\[
+S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+\]
+\end{proof}
 
@@
 
-We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$ as vector bundles on $\RR$. 
+We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$.
 Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
@@
 
-We have an isomorphism of vector bundles on $V$:
+We have
 \[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
-and similarly an isomorphism of bundles on $V_\RR$:
+and
 \[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]
 
-Under the composition
-\[\Omega^\bullet(V_\RR; \CC)\xto{p^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
-defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ which projects onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
-This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
+Under the pullback map
+\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
+the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$.
+\brian{This is not defined} \chris{is compactly supported enough?
+We want to compare pairings.}
 \end{proof}
@@
 We begin with a description of certain pure supersymmetric Yang--Mills theories.
-Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
+Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
 Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
@@
 
-\item A ghost field $c\in\Omega^0(V_\RR; \fg[1])$.
-\end{itemize}
+\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
+\end{itemize}
+
+We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
+Let $\cE_{\gauge}$ denote the space of BV fields.
 
@@
 
-\begin{definition}
-The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
-\[
-F_{\rm gauge} = \Omega^1(V_\RR; \fg) \oplus \Gamma(V_\RR; \Pi \Sigma \otimes \fg) \oplus \Omega^0(V_\RR; \fg[1])
-\]
-whose sections we denote by $(A, \lambda, c)$.  
-The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d : \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
-\[
-\begin{array}{ccccccc}
-[-,-] & : & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
-\end{array}
-\]
-defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
-The BRST action is defined by
-\[
-S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).
-\]
-\end{definition}
-
-The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
-By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
-If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
-%We introduce gauge transformations
-%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
-%so that the BV action is given by
+The BRST action is given by
+\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+
+We introduce gauge transformations
+\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
+so that the BV action is given by
 \begin{equation}
@@
 \end{equation}
-%
-%We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$.
-Let $\cE_{\gauge}$ denote the space of BV fields.
+
 To simplify the notation, the pairing on $\fg$ from now on will be implicit.
@@
 
+\brian{How do we see the various flavors of matter multiplets? For instance, in $2d (0,2)$ there is the Fermi multiplet and the chiral multiplet. 
+Your description only sees the chiral.
+In $2d (0,4)$ there are even more: the hypermultiplet (two $(0,2)$ chirals), the twisted hypermultiplet (the same as the hyper, different $R$-symmetry), the fermi multiplet (two $(0,2)$ fermi multiplets).
+I'm not sure which your description sees, but I have a hunch it's the $(0,4)$ hypermultiplet. 
+What is the reason for only seeing certain multiplets via this general setup?
+} \chris{Presumably pure $\mc N = (0,N)$ means a $(0,2)$ vector coupled to $N-2$ Fermi multiplets, so some of these are already covered by the classification?
+Perhaps your concern is that you want a formalism that allows Fermis that are not adjoint valued?
+I don't think the difference between this hyper and twisted hyper is germane here: the proof of supersymmetry is that there is an action of super Poincar\'e, it doesn't involve the action of R-symmetry.}
+
 In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e.
@@
 We are left with the action
-\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
+\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
@@
 
-\begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
+%\begin{theorem}
+%The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
 Moreover, this equivalence is $\U(2)$-equivariant.
-\label{thm:4d12hodge}
-\end{theorem}
-
-%\begin{proof}
-%We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
-%\begin{align*}
-%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-%\end{align*}
-%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-%\begin{align*}
-%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-%\end{align*}
-%
-%The next step is to decompose the $(1,1)$ form $\psi$ as
-%\[
-%\psi = \omega \Lambda \psi + \psi_{\perp}
-%\]
-%where $\Lambda \psi_{\perp} = 0$. 
-%
-%\end{proof}
+%\label{thm:4d12hodge}
+%\end{theorem}
+
+\begin{proof}
+We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
+\begin{align*}
+& (t \varsigma, \rho, t \phi, A_{1,0}) \\
+& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+\end{align*}
+This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+\begin{align*}
+\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+\end{align*}
+
+The next step is to decompose the $(1,1)$ form $\psi$ as
+\[
+\psi = \omega \Lambda \psi + \psi_{\perp}
+\]
+where $\Lambda \psi_{\perp} = 0$.
+
+\end{proof}
 
@@
 \begin{proof}
-Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
+Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
 Consider the supersymmetry actions
@@
 The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-We fix $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
+We fix $W = \CC^2$ equipped with a nondegenerate symmetric bililear pairing.
 
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
-The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
+The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
 
@@
 There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.
- \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.
+ \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.
 Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.
 By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.
-The $\ZZ/2\ZZ$-action swaps the two A supercharges and the two B supercharges, leaving two orbits under $\spin(2;\CC) \times G_R$.
-The A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
+The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
 Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
@@
 
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
-No new twists arise, i.e.
-every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
-
-The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e.
-by its fundamental representation on $W^6$.
-
-In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
-
-\begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
-The B-supercharge occurs as a degeneration of A-type supercharges.
-\end{prop}
-
-\begin{proof}
-First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$.
-A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.
-There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.
-We will refer to these as the B- and A-supercharges respectively.
-\end{proof}
-
-Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.
-Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.
-Therefore the two vectors in $W_+^6$ discussed above must be colinear.
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sect:2d(4,4)}
+We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.
+We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.
+In other words, every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group in the $\mc N=(4,4)$ case is $\spin(4;\CC) \times \spin(4;\CC)$, and in the $\mc N=(8,8)$ case it is $\spin(8;\CC)$ (acting on both $W_+$ and $W_-$ by its defining representation.
+In this latter case we must be somewhat careful since the $B$-twisting homomorphism $\phi_B$ does not factor through the diagonal.
+\chris{todo}
+
+The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.
 
 \subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
-We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
-
 \begin{theorem}
 The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
-This equivalence is $\mr U(1)$-invariant.
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
 \end{theorem}
@@
 \subsubsection{Topological A Twist} \label{sect:2d44Atwist}
-We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
-
 \begin{theorem}
@@
 This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
 \end{theorem}
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
@@
 The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
-Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.
-No new twists arise, i.e.
-every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
-
-The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semispin representations.
-As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we say in the $\mc N=(4,4)$ case.
-Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.
-
-\begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
-The B-supercharge occurs as a degeneration of A-type supercharges.
-\end{prop}
-
-\begin{proof}
-Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
-Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.
-The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.
-As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
-\begin{align*}
- W_+ &\iso (\CC \oplus \wedge^2 L \oplus \wedge^4 L) \otimes \det(L)^{-1/2} \\
- W_- &\iso (L \oplus \wedge^3 L) \otimes \det(L)^{-1/2},
-\end{align*}
-with $w_+ \in \wedge^4 L$.
-With respect to this decomposition, say $w_- = (v_1,v_3)$.
-If $v_1 \ne 0$, then we can act by $\wedge^2 L \sub \stab(w_+)$ to make $v_3 = 0$.
-Under the action of $\SL(L)$ all such non-zero $v_1$ are in the same orbit.
-Likewise if $v_1 = 0$ then $v_3 \ne 0$ and we can act by $\SL(L)$ to see that all such non-zero $v_3$ are in the same orbit.
-There are, therefore, two orbits once again, with one degenerating to the other.
-\end{proof}
-
-Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.
-Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.
-In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.
-
-\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
-We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
-
-\begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
-We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
-
-\begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.
-This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
-We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
-
-\begin{theorem}
-The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.
-This equivalence is $\mr U(1)$-invariant.
+If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
 \end{theorem}

### 2020-02-11 paper.tex
merge

--- 2020-02-10 paper.tex
@@
 
-Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant.
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant.
 Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
@@
 First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing.
-In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 thse depend on a choice of an orthogonal $\fg$-representation.
+In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation.
 We do not consider superpotential and mass terms in this paper.
@@
 \end{itemize}
-
-% \item  Context and literature on twists, including in the BV formalism.
-There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
-Also at least a remark on the perspective in terms of coupling to twisted sugra.
-% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
-% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
-% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
-% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
-% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
-% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
-%\end{enumerate}}
 

### 2020-02-11 paper.tex
Intro edits and references

@@
 
-The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
-An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
-
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
-This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
-In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+The quantization of gauge theories is notoriously subtle and requires a rich theory of renormalization.
+One attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization in a setting where the machinery required for renormalization is much more rigid.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
+This theory of renormalization can been used to study field theories with and without supersymmetry.
+\brian{many citations} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.
-
-A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
-For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
-The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}
-
-There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
-For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
-Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
-Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.
-
-We show that while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
-For a translation invariant field theory, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way, but it is possible that more than half of the translation invariant vector fields act trivially in cohomology.
-
-Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
-The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
+However, a significant simplification happens at the level of the {\em twisted} supersymmetric Yang-Mills theories that we study in this work.
+To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}.
+\brian{more examples}
+
+In the general setting of this paper, while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
+For a mixed holomorphic-topological translation invariant field theory of this type on $\RR^n \times \CC^d$, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way.
+
+Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiFeynman, LiVertex}, the foundations of renormalization for mixed holomorphic-topological field theories on Euclidean space has been developed in \cite{BWhol}.
+The key result is that the renormalization for mixed holomorphic-topological theories is extremely well-behaved from an analytic perspective.
 It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}.
@@
 These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory.
-Furthermore, in many examples of theories obtained via twisting not much is lost when asking for the one-loop quantization.
-The twisted gauge theories of type $BF$, which are plentiful in the examples we consider,  admit quantizations which are exact at one loop; meaning all higher order corrections vanish identically. 
-While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.
+Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
+The twisted gauge theories here are all either equivalent to $BF$-type theories, or deformations of such theories by a holomorphic differential operator.
+Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop; meaning all higher order corrections vanish identically.
+
+From this starting point, the first natural problem would be to verify whether these one-loop exact prequantizations define actual quantizations of the classical twisted field theory.
+That is, for each such theory, to compute the one-loop anomalies to the solution of the quantum master equation.
+This problem comes in two parts: first, to compute the one-loop anomaly to quantization of the theory on flat space $\RR^n \times \CC^d$, and second -- in the case where we can use a twisting homomorphism to define the twisted theory on certain structured $(n+2d)$-manifolds, to calculate the corresponding one-loop anomaly on curved space (in other words, incorporating the computation of a gravitational anomaly).
+We plan to return to this question in future work.
 
@@
  \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenCDO} in relationship to the chiral algebra of chiral differential operators. 
+Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
 \end{itemize}
@@
 %
-%\begin{cor} \label{cor: quad}
+%\begin{cor} \label{cor:quad}
 %Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
@@
 \begin{proof}
-We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
+We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
 \begin{align*}

### 2020-02-11 paper.tex
paper

--- 2020-02-11 paper.tex
@@
 
-Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant.
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant.
 Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
@@
 First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing.
-In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation.
+In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 thse depend on a choice of an orthogonal $\fg$-representation.
 We do not consider superpotential and mass terms in this paper.
@@
 \end{itemize}
+
+% \item  Context and literature on twists, including in the BV formalism.
+There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
+Also at least a remark on the perspective in terms of coupling to twisted sugra.
+% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
+% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
+% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
+% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
+% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
+% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
+%\end{enumerate}}
 
@@
 
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$.
-In the case $S_{\mr{BRST}} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.
+We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ as {\em the BV theory associated to the BRST theory} $\cF$.
+%and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. 
+In the case $S_{\mr{BRST}} = 0$ we refer to the associated BV theory as being of {\em cotangent type}, which we will denote by $T^*[-1] \cF$.
 
@@
 Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
-\[S(A,B) = \int_M \langle F_A \wedge B \rangle.\]
+\[S(A,B) = \int_M \langle B \wedge F_A \rangle.\]
 This theory is, in fact, of cotangent type, where the base of the cotangent includes $A$ and its antifield, and the fiber includes $B$ and its antifield.
@@
 Fix an $L_\infty$ algebra $\fg$.
-The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+The \defterm{generalized $BF$ theory} is the BV theory associated to the following BRST theory:
 \begin{itemize}
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix a complex vector space $V$.
-The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the BV theory associated to the following BRST theory:
 \begin{itemize}
@@
 where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}=
+\end{example}
 
@@
 \begin{prop}
-Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+Let $\fg$ be a dg Lie algebra, and consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ for Lie algebra $\fg$ with the space of BV fields
 \[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
@@
 \label{ex:CSHamiltonianreduction}
+\brian{Will $V\ham \fg$ already be defined above in the FMP section?}
 \end{example}
@@
 
-As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.
+As with generalized BF theory, generalized Chern--Simons theory carries a natural rotation action by linear automorphism groups of spacetime.
 
 \begin{prop}
-Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
+Suppose $\fg$ is a dg Lie algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
 Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
@@
 \begin{itemize}
-\item Elements $Q\in S_+\oplus S_-$ of rank $(1, 0)$ or rank $(0, 1)$.
-Such supercharges are automatically square-zero and are holomorphic.
-The embedding $\alpha \colon \U(1) \hookrightarrow G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory.
-Also, we have a compatible twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow G_R$.
+\item Elements $Q\in S_+\oplus S_-$ of rank $(1, 0)$ or rank $(0, 1)$. Such supercharges are automatically square-zero and are holomorphic. 
+We have a compatible twisting homomorphism 
+\[
+\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow G_R 
+\]
+with the second arrow the natural embedding.
+The twist is $\ZZ$-graded with homomorphism $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding.
 \end{itemize}
@@
 \item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
-\item Gauge fermions $\lambda_{1, 0}\in\Omega^{1, 0}(M; \fg)[1]$, $\lambda_0\in\Omega^0(M; \fg)[-1]$, $A_{0, 2}\in\Omega^{0, 2}(M; \fg)[-1]$.
+\item Gauge fermions $\lambda_0\in\Omega^0(M; \fg)[-1]$, $A_{0, 2}\in\Omega^{0, 2}(M; \fg)[-1]$, $\lambda_{1, 0}\in\Omega^{1, 0}(M; \fg)[1]$.
 \item Matter bosons $\phi\in\Omega^0(M; R^*)$, $\gamma_0\in\Omega^0(M; R)$.
@@
 \end{itemize}
-The corresponding antifields are given by:
-\begin{itemize}
-\item $A_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-1]$, $B_{2, 1}\in\Omega^{2, 1}(M; \fg)[-1]$.
-\item $\lambda_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-2]$, $\lambda_0^*\in\Omega^0(M; \fg)$, $B_{2, 0}\in\Omega^{2, 0}(M; \fg)$.
-\item $\phi^*\in\Omega^{2, 2}(M; R)$, $\gamma_0^*\in\Omega^0(M; R^*)$.
-\item $\psi_0^*\in\Omega^{2, 2}(M; R)[-2]$, $\gamma_{0, 2}\in\Omega^{0, 2}(M; R)[-2]$, $\beta_{2, 1}\in\Omega^{2, 1}(M; R^*)$.
-\item $B_{2, 2}\in\Omega^{2, 2}(M; \gg)[-2]$.
-\end{itemize}
+%The corresponding antifields are given by:
+%\begin{itemize}
+%\item $A_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-1]$, $B_{2, 1}\in\Omega^{2, 1}(M; \fg)[-1]$.
+%\item $\lambda_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-2]$, $\lambda_0^*\in\Omega^0(M; \fg)$, $B_{2, 0}\in\Omega^{2, 0}(M; \fg)$.
+%\item $\phi^*\in\Omega^{2, 2}(M; R)$, $\gamma_0^*\in\Omega^0(M; R^*)$.
+%\item $\psi_0^*\in\Omega^{2, 2}(M; R)[-2]$, $\gamma_{0, 2}\in\Omega^{0, 2}(M; R)[-2]$, $\beta_{2, 1}\in\Omega^{2, 1}(M; R^*)$.
+%\item $B_{2, 2}\in\Omega^{2, 2}(M; \gg)[-2]$.
+%\end{itemize}
 
@@
 Let $W$ be a two-dimensional complex symplectic vector space.
-The theory admits the $R$-symmetry group $G_R=\SL(W)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
+The theory admits the $R$-symmetry group $G_R=\SL(2)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
 
@@
 
-$\GL(1, \CC)\subset G_R$ has the following action: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.
-
-If the representation $U$ is $T^*R = R\oplus R^*$, the $R$-symmetry group is enhanced to $G_R=\SL(W)\times \GL(1, \CC)\times \GL(1, \CC)$, where the last $\GL(1, \CC)$ acts with weight $1$ on $R$ and weight $-1$ on $R^*$.
+The subgroup $\GL(1, \CC)\subset G_R$ has the following action on fields: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.
+
+If the representation $U$ is $T^*R = R\oplus R^*$, the $R$-symmetry group is enhanced to $G_R=\SL(2)\times \GL(1, \CC)\times \GL(1, \CC)$, where the last $\GL(1, \CC)$ acts with weight $1$ on $R$ and weight $-1$ on $R^*$.
 
@@
 \end{proof}
+
+When $U$ is of cotangent type $U = R \oplus R^*$ the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$.
+In this case, the twist admits twisting data homomorphism $\alpha \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components.
+%\[
+%\begin{array}{ccccc}
+%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
+%&  z & \mapsto & \left(1 , z, z \right)
+%\end{array}
+%\]
+There is a new twisting homomorphism 
+\[
+\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\alpha} G_R
+\]
+By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
+
+\begin{thm}
+\label{thm:4d_2minimaltwistgraded}
+The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
+Moreover, this equivalence is $\U(2)$-equivariant.
+\end{thm}
 
@@
 The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
-We fix $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
-
-The R-symmetry group is $\spin(2;\CC)$, acting on $W$ by its defining representation.
+In this case, $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
+
+The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by the defining representation.
+
+%The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by its defining representation.
 
@@
  \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
- \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
+ \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
+ \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
  \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
@@
  \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
+There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
+The twist is $\ZZ$-graded with $\alpha : \U(1) \hookrightarrow G_R$ given by the natural embedding. 
 \end{itemize}
@@
 \label{sect:3dminimaltwist}
-A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  There is an essentially trivial twisting homomorphism $\phi \colon \MU(1) = \U(1)\hookrightarrow G_R$.
+A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
+We use thetwisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.
 
@@
 By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\MU(1) = \mr U(1)$-equivariant.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
 \end{proof}
@@
  \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
- \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
+ \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
  \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
@@
 The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
-However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
+
+%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
 Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
@@
  \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.
-Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.
+Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors~
+
+\noindent$((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.
 By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.
 The $\ZZ/2\ZZ$-action swaps the two A supercharges and the two B supercharges, leaving two orbits under $\spin(2;\CC) \times G_R$.
-The A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.
-Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
-\end{itemize}
-
-The calculation of the twists here is similar to what we saw in 4d $\mc N=2$.
-The holomorphic twist and the B-twist arise by dimensional reduction from 3d, but the A-twist as a deformation of the holomorphic twist is not, and must be calculated directly.
+\begin{enumerate}
+\item The $A$-supercharges are compatible with the twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
+\item The $B$-supercharges are compatible with the twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  
+\end{enumerate}
+Moreover, the $A$-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the $B$-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
+\end{itemize}
+
+The calculation of the twists here is similar to what we saw in 4d $\mc N=2$ supersymmetry.  
+The minimal twist and the $B$-twist arise by dimensional reduction from twists of $3d$ $\cN=2$ supersymmetric Yang-Mills theory.
+On the contrary, the $A$-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
 
@@
 \begin{itemize}
- \item $\gg$-valued bosons: $(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item $R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
+ %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
+ \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
+ %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
  \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
@@
 I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*  \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*  \right)\right)  \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
 I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).

### 2020-02-11 paper.tex

@@
 
-% \item  Context and literature on twists, including in the BV formalism.
-There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
-Also at least a remark on the perspective in terms of coupling to twisted sugra.
-% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
-% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
-% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
-% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
-% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
-% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
-%\end{enumerate}}
-
 \subsection*{Applications to Quantization}

### 2020-02-12 paper.tex
merge
local FMPs (in progress)

--- 2020-02-11 paper.tex
@@
 
-\subsection*{Classical Supersymmetric Field Theories}
-
-Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant.
+\subsection*{Supersymmetric Classical Field Theories}
+
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant.
 Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
@@
 
+% \item  Context and literature on twists, including in the BV formalism.
+There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).
+Also at least a remark on the perspective in terms of coupling to twisted sugra.
+% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
+% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
+% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
+% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
+% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
+% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
+%\end{enumerate}}
+
 \subsection*{Applications to Quantization}
@@
 
-The quantization of gauge theories is notoriously subtle and requires a rich theory of renormalization.
-One attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization in a setting where the machinery required for renormalization is much more rigid.
-
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
-This theory of renormalization can been used to study field theories with and without supersymmetry.
-\brian{many citations} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
+An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
+This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
+In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.
-However, a significant simplification happens at the level of the {\em twisted} supersymmetric Yang-Mills theories that we study in this work.
-To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
-The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}.
-\brian{more examples}
-
-In the general setting of this paper, while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
-For a mixed holomorphic-topological translation invariant field theory of this type on $\RR^n \times \CC^d$, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way.
-
-Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiFeynman, LiVertex}, the foundations of renormalization for mixed holomorphic-topological field theories on Euclidean space has been developed in \cite{BWhol}.
-The key result is that the renormalization for mixed holomorphic-topological theories is extremely well-behaved from an analytic perspective.
+
+A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
+For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}
+
+There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
+For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
+Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
+Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.
+
+We show that while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
+For a translation invariant field theory, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way, but it is possible that more than half of the translation invariant vector fields act trivially in cohomology.
+
+Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
+The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
 It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. 
@@
 These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. 
-Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
-The twisted gauge theories here are all either equivalent to $BF$-type theories, or deformations of such theories by a holomorphic differential operator.
-Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop; meaning all higher order corrections vanish identically.
-
-From this starting point, the first natural problem would be to verify whether these one-loop exact prequantizations define actual quantizations of the classical twisted field theory.
-That is, for each such theory, to compute the one-loop anomalies to the solution of the quantum master equation.
-This problem comes in two parts: first, to compute the one-loop anomaly to quantization of the theory on flat space $\RR^n \times \CC^d$, and second -- in the case where we can use a twisting homomorphism to define the twisted theory on certain structured $(n+2d)$-manifolds, to calculate the corresponding one-loop anomaly on curved space (in other words, incorporating the computation of a gravitational anomaly).
-We plan to return to this question in future work.
+Furthermore, in many examples of theories obtained via twisting not much is lost when asking for the one-loop quantization.
+The twisted gauge theories of type $BF$, which are plentiful in the examples we consider,  admit quantizations which are exact at one loop; meaning all higher order corrections vanish identically. 
+While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.
 
@@
  \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.}
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
 \end{itemize}
@@
 
+\subsection*{Applications to Quantization and a Relationship to Factorization algebras}
+%\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}
+
+The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
+An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.
+
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
+In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re
+
 \subsection*{Outline of the Paper}
@@
 This bracket is of cohomological degree $+1$. 
-This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
-
-We explain how to define the BV bracket in our context.  
-First note that there is a linear map
-\[
-\d_{\mr{dR}} \colon \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
+We will now explain how to define the BV bracket.  First note that there is a linear map
+\[
+\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
 \]
@@
 \]
-where $D_i$ is a differential operator $D_i \colon \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
+where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
 Without loss of generality, suppose $F$ is of this form. 
@@
 \[
-\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
 \]
@@
 Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
-The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
-The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
+The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
 First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
@@
 Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
-The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
-The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
+The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
 The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
@@
 
-%There is a corollary of this proposition obtained by iterating the procedure. 
-%We will only use a single iteration. 
-%
-%\begin{cor} \label{cor:quad}
-%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
-%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
-%\[
-%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
-%\]
-%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
-%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
-%Suppose further that the local functional
-%\[
-%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
-%\]
-%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
-%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
-%\[
-%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
-%\]
-%and
-%\[
-%S' = S_0 + \int \phi_1 \psi_1^* - S''
-%\]
-%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
-%\end{cor}
-%\begin{proof}
-%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
-%We begin by making the following change of coordinates on the BV fields:
-%\begin{align*}
-%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
-%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
-%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
-%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
-%\end{align*}
-%with $\phi_1, \psi_1$ left fixed. 
-%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
-%Further, in the new coordinates, the action takes the form
-%\[
-%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
-%\]
-%\end{proof}
+There is a corollary of this proposition obtained by iterating the procedure. 
+We will only use a single iteration.
+
+\begin{cor} \label{cor: quad}
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+\[
+E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
+\]
+whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
+The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
+Suppose further that the local functional
+\[
+S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
+\]
+satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
+\[
+E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
+\]
+and
+\[
+S' = S_0 + \int \phi_1 \psi_1^* - S''
+\]
+where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
+\end{cor}
+\begin{proof}
+%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
+We begin by making the following change of coordinates on the BV fields:
+\begin{align*}
+\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
+\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
+%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
+%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
+\end{align*}
+with $\phi_1, \psi_1$ left fixed. 
+This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
+Further, in the new coordinates, the action takes the form
+\[
+S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+\]
+\end{proof}
 
@@
 
+\subsection{Local formal moduli problems}
+
+It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
+In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
+
+Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
+We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
+
+For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
+\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
+where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
+The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
+The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
+This important result will only serve as a motivation.
+
+Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
+\[L_{V, \fg}=\fg\oplus V[-1]\]
+with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
+\[V/\fg:= B L_{V, \fg}.\]
+
+\begin{example}
+If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
+\[T[n] B\fg = \fg[n+1] / \fg.\]
+\label{ex:tangentBg}
+\end{example}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
+Then $\fg^*$ is a coadjoint representation of $\fg$.
+We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
+\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
+\label{ex:cotangentBg}
+\end{example}
+
+\begin{definition}
+Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
+\end{definition}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
+Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
+For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
+\end{example}
+
+Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
+\[(B L)(U) = B L(U),\]
+i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
+
+\begin{definition}
+A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
+\end{definition}
+
+\begin{remark}
+In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
+It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
+\end{remark}
+
+\begin{example}
+Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
+Then we may define the following local formal moduli problem on $X\times Y\times M$.
+Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
+We may then consider a graded vector bundle
+\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
+on $X\times Y\times M$.
+It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
+It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
+We then define
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
+\label{ex:mappingspace}
+\end{example}
+
+\begin{remark}
+A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
+So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
+Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
+\end{remark}
+
+\begin{example}
+Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
+Moreover, assume $B\fg$ carries a $\Gm$-action.
+We then have a local $L_\infty$ algebra
+\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
+on $X\times Y\times M$. We define
+\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
+\end{example}
+
+As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
+
+\begin{lemma}
+Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
+The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
+\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
+where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
+\end{lemma}
+\begin{proof}
+The claim follows from the following isomorphisms of graded vector bundles:
+\begin{align*}
+\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
+\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
+\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
+\end{align*}
+\end{proof}
+
+Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper will only be interested in a strict notion as follows.
+
+\begin{definition}
+Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
+A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
+\begin{enumerate}
+\item It is fiberwise nondegenerate.
+
+\item It is graded skew symmetric.
+
+\item The pairing
+\begin{align*}
+\cL_c\otimes \cL_c&\rightarrow \CC \\
+\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
+\end{align*}
+is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
+\end{enumerate}
+\end{definition}
+
+\begin{definition}
+A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
+\end{definition}
+
 \subsection{Examples of Classical Field Theories}
@@
 We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
-\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(m)\otimes K_X^{n/m} [1]\]
+\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(n)\otimes K_X^{n/m} [1]\]
 and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
@@
 The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$.
-With respec to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
+With respect to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
 \[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
@@
 Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.
-These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model.
+These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.
 By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.
@@
 
-\begin{definition}
-The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
-\[
-F_{\rm gauge} = \Omega^1(V_\RR; \fg) \oplus \Gamma(V_\RR; \Pi \Sigma \otimes \fg) \oplus \Omega^0(V_\RR; \fg[1])
-\]
-whose sections we denote by $(A, \lambda, c)$.  
-The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d :\colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
-\[
-\begin{array}{ccccccc}
-[-,-] & \colon & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
-\end{array}
-\]
-defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
-The BRST action is defined by
-\[
-S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).
-\]
-\end{definition}
-
-The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
-By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
-If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
-%We introduce gauge transformations
-%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
-%so that the BV action is given by
+The BRST action is given by
+\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]
+
+We introduce gauge transformations
+\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
+so that the BV action is given by
 \begin{equation}
@@
 Moreover, we may canonically identify $\sigma(L)\cong L^*$.
-
-\begin{remark}
-It is important here that we are working in the complexified setting.
-While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges, since a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
-So necessarily, twists of maximal super Yang-Mills theory cannot be compatible with any unitary structure.
-\end{remark}
 
@@
 We are left with the action
-\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
+\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
@@
 
-We use the same twisting homomorphism $\phi \colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha \colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
 Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
@@
 
-In this case $S_+\otimes W$ and $S_-\otimes W$ have two-dimensional trivial $G$-subrepresentations.
+In this case $S_+\otimes W$ and $S_-\otimes W^*$ have two-dimensional trivial $G$-subrepresentations.
 Any scalar rank $(1, 1)$ supercharge is square-zero.
@@
 
-%\begin{theorem}
-%The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
+\begin{theorem}
+The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
 Moreover, this equivalence is $\U(2)$-equivariant.
-%\label{thm:4d12hodge}
-%\end{theorem}
-
-\begin{proof}
-We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
-\begin{align*}
-& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-\end{align*}
-This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-\begin{align*}
-\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-\end{align*}
-
-The next step is to decompose the $(1,1)$ form $\psi$ as
-\[
-\psi = \omega \Lambda \psi + \psi_{\perp}
-\]
-where $\Lambda \psi_{\perp} = 0$.
-
-\end{proof}
+\label{thm:4d12hodge}
+\end{theorem}
+
+%\begin{proof}
+%We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
+%\begin{align*}
+%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
+%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+%\end{align*}
+%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+%\begin{align*}
+%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+%\end{align*}
+%
+%The next step is to decompose the $(1,1)$ form $\psi$ as
+%\[
+%\psi = \omega \Lambda \psi + \psi_{\perp}
+%\]
+%where $\Lambda \psi_{\perp} = 0$. 
+%
+%\end{proof}
 
@@
 
-\begin{theorem}  \label{3d_8_minimal_twist_thm}
+\begin{theorem} 
 The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
@@
 
-\begin{theorem} \label{3d_8_A_twist_thm}
+\begin{theorem} 
 The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
@@
 
-\begin{theorem} \label{3d_8_B_twist_thm}
+\begin{theorem} 
 The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
@@
 The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.
+
+\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
 

### 2020-02-12 paper.tex

--- 2020-02-11 paper.tex
@@
 A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
-We use thetwisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.
+We use the twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.
 
@@
 \end{proof}
+
+\begin{remark}
+\brian{Cotangent type.}
+\end{remark}
 

### 2020-02-12 paper.tex
merge

--- 2020-02-11 paper.tex
@@
 \begin{definition}
+\label{dfn: cs}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
@@
 \begin{prop} \label{CS_to_BF_diml_red_prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
+Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the corresponding generalized Chern--Simons theory
 \[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, acting on $W$ by its (Dirac) spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, and $W$ is its $8$-dimensional (Dirac) spin representation.
 
@@
 \begin{lemma}
-There are two $\spin(3;\CC) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
+There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
 \end{lemma}
@@
 Let $V_7$ denote the fundamental representation of $G_R$.
-As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of half-density.
-This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$, under whose action the auxiliary space $W$ decomposes as
+As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of a half-density.
+This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$.
+Under the group $\ML(L)$ the auxiliary space $W$ decomposes as
 \[W \iso \left(\CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \right) \otimes \det(L)^{-1/2},\]
@@
 \end{theorem}
+
+\begin{proof}
 

### 2020-02-12 paper.tex

--- 2020-02-12 paper.tex
@@
 
-\begin{remark}
-\brian{Cotangent type.}
-\end{remark}
-
 \subsubsection{Topological A Twist}

### 2020-02-12 paper.tex
2d twists in intro

--- 2020-02-12 paper.tex
@@
 This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
-If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
+If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
 Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
@@
 \begin{itemize}
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
- \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
- \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
- \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.} There is a holomorphic twist in dimension 2 which can be defined with $\mc N=(2,2)$ supersymmetry, including a chiral multiplet valued in a representation $R$.
+This twist is perturbatively equivalent to a holomorphic BF theory coupled to a $\beta \gamma$-system valued in $R$.
+More specifically: to holomorphic BG theory valued in the tangent space $T[1]R/\gg$.
+This theory is $\mr U(1)$-equivariant, and can be defined on any Riemann surface.
+If the supersymmetry is promoted to $\mc N=(4,4)$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory can now be modelled by holomorphic BF theory coupled to a holomorphic symplectic boson.
+Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with holomorphic BF theory valued in $T[1]T^*[2](\gg/\gg))$.
+The study of twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to work of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
+The first is a perturbatively trivial theory: the A-model valued in the cotangent space to the quotient stack $R/\gg$.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological B twist.} The remaining topological twist, the B-twist, is perturbatively equivalent to a 2d topological BF theory, coupled a topological matter valued in the representation $R$.
+ \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} Chiral theories in 2-dimensions only admit a holomorphic twist.
+These twists can all be realised as holomorphic BF theory on $\CC$, coupled to a holomorphic $\beta \gamma$-system (in the case where the chiral theory includes matter), or to a holomorphic free fermion (in the case where the chiral theory is pure gauge with $\mc N=(0,N_-)$ supersymmetry).
+Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
 \end{itemize}
@@
 \begin{definition}
-\label{dfn: cs}
 Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
@@
 \begin{prop} \label{CS_to_BF_diml_red_prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
-Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the corresponding generalized Chern--Simons theory
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
 \[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
@@
 
+\begin{remark}
+\brian{Cotangent type.}
+\end{remark}
+
 \subsubsection{Topological A Twist}
@@
 This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, and $W$ is its $8$-dimensional (Dirac) spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, acting on $W$ by its (Dirac) spin representation.
 
@@
 \begin{lemma}
-There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
+There are two $\spin(3;\CC) \times G_R$-orbits of rank 2 supercharges in the 3d $\mc N=8$ supersymmetry algebra.
 \end{lemma}
@@
 Let $V_7$ denote the fundamental representation of $G_R$.
-As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of a half-density.
-This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$.
-Under the group $\ML(L)$ the auxiliary space $W$ decomposes as
+As in Section \ref{9d_section}, the element $w \in W$ is equivalent to the data of a maximal isotropic subspace $L \sub V_7$, together with a choice of half-density.
+This element $w$ is stabilized, in particular, by a copy of the metalinear group $\ML(L)$, under whose action the auxiliary space $W$ decomposes as
 \[W \iso \left(\CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \right) \otimes \det(L)^{-1/2},\]
@@
 \end{theorem}
-
-\begin{proof}
 
@@
 
+\textsc{University of Massachusetts, Amherst}\\
+\textsc{Department of Mathematics and Statistics, 710 N Pleasant St, Amherst, MA 01003}\\
+\texttt{celliott@math.umass.edu}\\
+\vspace{-5pt}
+
+\textsc{Institut f\"ur Mathematik, Universit\"at Z\"urich}\\
+\textsc{Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}\\
+\texttt{pavel.safronov@math.uzh.ch}\\
+\vspace{-5pt}
+
+\textsc{Northeastern University}\\
+\textsc{Department of Mathematics, 360 Huntington Ave, Boston, MA 02115}\\
+\texttt{brianwilliams.math@gmail.com}\\
+
 \end{document}

### 2020-02-12 paper.tex
intro draft

@@
 This theory of renormalization can been used to study field theories with and without supersymmetry.
-\brian{many citations} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+\brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
-The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}.
-\brian{more examples}
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich, AxelrodSinger}.
 
@@
 \subsection*{The Relationship to Factorization Algebras}
+In our previous paper \cite{ElliottSafronov}, we discussed supersymmetric twisting with an emphasis not on the classical fields of a supersymmetric field theory, but instead on their classical or quantum \emph{observables}.
+The factorization algebra formalism of Costello and Gwilliam \cite{Book1, Book2} provides a model for the local structure of the observables in a general quantum field theory.
+In brief, for every open subset $U \sub M$ of the spacetime manifold, one associates a (possibly $\ZZ \times \ZZ/2\ZZ$-graded) vector space $\obs(U)$ of local observables on $U$.
+For any pair $U_1, U_2 \sub V$ of disjoint open subsets of an open set $V$, one associates a morphism
+\[m_{U_1, U_2}^V \colon \obs(U_1) \otimes \obs(U_2)\to \obs(V),\]
+thought of as an \emph{operator product} for local observables.
+These products should vary smoothly as one varies the open subsets $U_1, U_2$ and $V$.
+Starting with a classical field theory on $M$, defined using the BV formalism, one can build a factorization algebra $\obs^{\mr{cl}}$ modelling the classical observables of the field theory.
+If the classical field theory carried the action of a group $G$, so would the factorization algebra.
+Furthermore, Costello and Gwilliam develop techniques for the quantization of such algebras of classical observables, using the theory of renormalization as discussed in the previous section.
+
+In \cite{ElliottSafronov} we studied the supersymmetric twisting procedure as applied to factorization algebras on $\RR^n$ with an action of a supersymmetry algebra.
+If $Q$ is a topological supercharge, then the $Q$-twist $\obs^Q$ of a supersymmetric factorization algebra automatically satisfies a strong translation invariance condition: all translations must act homotopically trivially.
+In good circumstances, we can say even more.
+An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
+\begin{theorem}[{\cite[Theorem 3]{ElliottSafronov}}]
+If $Q$ is a topological supercharge, and the operator $\obs^Q(B_r(0)) \to \obs^Q(B_R(0))$ associated to the inclusion of concentric balls is an equivalence, then the factorization algebra $\obs^Q$ has the canonical structure of an $\bb E_n$-algebra.
+\end{theorem}
+The hypothesis of the theorem is automatically satisfied, for example, for superconformal theories, and should be concretely checkable in examples.
+
+In the present work we classify twists of classical field theories, to which one can associate twisted factorization algebras of classical -- and, if the appropriate anomalies vanish, quantum -- observables in the sense of our previous work.
+In some (topological) examples, these define $\bb E_n$-algebras.
+In other examples, where the twist is not fully topological, the twisted local observables will define higher analogues of vertex algebras (as in, for instance, \cite{GwilliamWilliamsKM}).
 
@@
 Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$.
-We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{}).
+We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMP}).
 We may also combine these three examples into what we call a \emph{generalized BF theory} with the spaces of fields $T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ (see Definition \ref{def:generalizedBF} for more details).
@@
 This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}.
-\chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
  \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence} (\chris{I'm struggling to understand whether we should cite \cite{BaulieuKannoSinger, BaulieuLosevNekrasov} here or elsewhere.}; its equations of motion include the Donaldson-Thomas equations.
+This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the Donaldson-Thomas equations.
 \end{itemize}
@@
 
-\subsection{Local formal moduli problems}
-
-\subsection{Classical BV Theories}
+\subsection{Classical BV Theories} \label{sect:BV}
 
@@
 
-\subsection{Local formal moduli problems}
+\subsection{Local Formal Moduli Problems} \label{sect:FMP}
 
@@
 \item It is fiberwise nondegenerate.
-
 \item It is graded skew symmetric.
-
-\item The pairing
-\begin{align*}
-\cL_c\otimes \cL_c&\rightarrow \CC \\
-\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
-\end{align*}
+\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
+\[\alpha\otimes \beta \mapsto \int_M \omega (\alpha \otimes \beta)\]
 is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
@@
 
-\begin{definition}
-A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
-\end{definition}
+\begin{remark}
+A classical BV field theory as defined in Section \ref{sect:BV} is equivalent to the data of a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
+\end{remark}
 
@@
 \end{definition}
-
-\brian{We have not defined the notation $\Omega^{0,\bu}, \Omega^{\bu,\bu}, \Omega^\bu$.}
-\brian{Also, define the notation $T^*[-1] {\rm Map}$. }
 
@@
 \begin{proof}
-
-\begin{proof}
 On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.

### 2020-02-12 paper.tex
minor

@@
 An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
-\begin{theorem}[{\cite[Theorem 3]{ElliottSafronov}}]
+\begin{nonum}[{\cite[Theorem 3]{ElliottSafronov}}]
 If $Q$ is a topological supercharge, and the operator $\obs^Q(B_r(0)) \to \obs^Q(B_R(0))$ associated to the inclusion of concentric balls is an equivalence, then the factorization algebra $\obs^Q$ has the canonical structure of an $\bb E_n$-algebra.
-\end{theorem}
+\end{nonum}
 The hypothesis of the theorem is automatically satisfied, for example, for superconformal theories, and should be concretely checkable in examples.
@@
 It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
+This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the $G_2$-monopole equations.
 \end{itemize}
@@
 It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the Donaldson-Thomas equations.
+This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the Donaldson-Thomas equations.
 \end{itemize}

### 2020-02-12 paper.tex
small change:

--- 2020-02-12 paper.tex
@@
 This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
-If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
+If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
 Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
@@
 \begin{itemize}
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.} There is a holomorphic twist in dimension 2 which can be defined with $\mc N=(2,2)$ supersymmetry, including a chiral multiplet valued in a representation $R$.
-This twist is perturbatively equivalent to a holomorphic BF theory coupled to a $\beta \gamma$-system valued in $R$.
-More specifically: to holomorphic BG theory valued in the tangent space $T[1]R/\gg$.
-This theory is $\mr U(1)$-equivariant, and can be defined on any Riemann surface.
-If the supersymmetry is promoted to $\mc N=(4,4)$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory can now be modelled by holomorphic BF theory coupled to a holomorphic symplectic boson.
-Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with holomorphic BF theory valued in $T[1]T^*[2](\gg/\gg))$.
-The study of twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to work of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
-The first is a perturbatively trivial theory: the A-model valued in the cotangent space to the quotient stack $R/\gg$.
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological B twist.} The remaining topological twist, the B-twist, is perturbatively equivalent to a 2d topological BF theory, coupled a topological matter valued in the representation $R$.
- \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} Chiral theories in 2-dimensions only admit a holomorphic twist.
-These twists can all be realised as holomorphic BF theory on $\CC$, coupled to a holomorphic $\beta \gamma$-system (in the case where the chiral theory includes matter), or to a holomorphic free fermion (in the case where the chiral theory is pure gauge with $\mc N=(0,N_-)$ supersymmetry).
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
+ \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
+ \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
+ \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
+Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
 \end{itemize}
@@
 \end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+We denote the space of BV fields by $T^*[-1] \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg)$.
 \label{def:generalizedBF}
@@
 
-We will now concentrate on the 7-dimensional case.
+The 7-dimensional result immediately follows.
 
@@
 
-\textsc{University of Massachusetts, Amherst}\\
-\textsc{Department of Mathematics and Statistics, 710 N Pleasant St, Amherst, MA 01003}\\
-\texttt{celliott@math.umass.edu}\\
-\vspace{-5pt}
-
-\textsc{Institut f\"ur Mathematik, Universit\"at Z\"urich}\\
-\textsc{Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}\\
-\texttt{pavel.safronov@math.uzh.ch}\\
-\vspace{-5pt}
-
-\textsc{Northeastern University}\\
-\textsc{Department of Mathematics, 360 Huntington Ave, Boston, MA 02115}\\
-\texttt{brianwilliams.math@gmail.com}\\
-
 \end{document}

### 2020-02-12 paper.tex
merge to desktop

--- 2020-02-12 paper.tex
@@
 
-\subsection{Local formal moduli problems}
-
-It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
-In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
-
-Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
-We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
-
-For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
-\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
-where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
-The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
-The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
-This important result will only serve as a motivation.
-
-Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
-\[L_{V, \fg}=\fg\oplus V[-1]\]
-with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
-\[V/\fg:= B L_{V, \fg}.\]
-
-\begin{example}
-If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
-\[T[n] B\fg = \fg[n+1] / \fg.\]
-\label{ex:tangentBg}
-\end{example}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
-Then $\fg^*$ is a coadjoint representation of $\fg$.
-We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
-\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
-\label{ex:cotangentBg}
-\end{example}
-
-\begin{definition}
-Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
-\end{definition}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
-Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
-For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
-\end{example}
-
-Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
-\[(B L)(U) = B L(U),\]
-i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
-
-\begin{definition}
-A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
-\end{definition}
-
-\begin{remark}
-In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
-It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
-\end{remark}
-
-\begin{example}
-Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
-Then we may define the following local formal moduli problem on $X\times Y\times M$.
-Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
-We may then consider a graded vector bundle
-\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
-on $X\times Y\times M$.
-It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
-It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
-We then define
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
-\label{ex:mappingspace}
-\end{example}
-
-\begin{remark}
-A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
-So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
-Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
-\end{remark}
-
-\begin{example}
-Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
-Moreover, assume $B\fg$ carries a $\Gm$-action.
-We then have a local $L_\infty$ algebra
-\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
-on $X\times Y\times M$. We define
-\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
-\end{example}
-
-As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
-
-\begin{lemma}
-Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
-The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
-\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
-where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
-\end{lemma}
-\begin{proof}
-The claim follows from the following isomorphisms of graded vector bundles:
-\begin{align*}
-\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
-\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
-\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
-\end{align*}
-\end{proof}
-
-Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper will only be interested in a strict notion as follows.
-
-\begin{definition}
-Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
-A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
-\begin{enumerate}
-\item It is fiberwise nondegenerate.
-
-\item It is graded skew symmetric.
-
-\item The pairing
-\begin{align*}
-\cL_c\otimes \cL_c&\rightarrow \CC \\
-\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
-\end{align*}
-is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
-\end{enumerate}
-\end{definition}
-
-\begin{definition}
-A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
-\end{definition}
-
 \subsection{Examples of Classical Field Theories}
@@
 \end{itemize}
-We denote the space of BV fields by $T^*[-1] \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg)$.
+We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
 \label{def:generalizedBF}
@@
 We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
-\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(n)\otimes K_X^{n/m} [1]\]
+\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(m)\otimes K_X^{n/m} [1]\]
 and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
@@
 The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$.
-With respect to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
+With respec to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
 \[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
@@
 
-The 7-dimensional result immediately follows.
+We will now concentrate on the 7-dimensional case.
 
@@
 Let $W$ be a two-dimensional complex symplectic vector space.
-The theory admits the $R$-symmetry group $G_R=\SL(2)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
+The theory admits the $R$-symmetry group $G_R=\SL(2;\CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
 
@@
 
-When $U$ is of cotangent type $U = R \oplus R^*$ the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$.
-In this case, the twist admits twisting data homomorphism $\alpha \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components.
+%There is an alternative $\ZZ$-grading one can assign to the twist when $U$ is of cotangent type $U = R \oplus R^*$. 
+%In this case, the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$. 
+%The new twisting datum is $\Tilde{\alpha} \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components. 
+%%\[
+%%\begin{array}{ccccc}
+%%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
+%%&  z & \mapsto & \left(1 , z, z \right)
+%%\end{array}
+%%\]
+%There is also a new twisting homomorphism 
 %\[
-%\begin{array}{ccccc}
-%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
-%&  z & \mapsto & \left(1 , z, z \right)
-%\end{array}
+%\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\Tilde{\alpha}} G_R
 %\]
-There is a new twisting homomorphism 
-\[
-\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\alpha} G_R
-\]
-By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
-
-\begin{thm}
-\label{thm:4d_2minimaltwistgraded}
-The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
-Moreover, this equivalence is $\U(2)$-equivariant.
-\end{thm}
+%By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
+%
+%\begin{thm}
+%\label{thm:4d_2minimaltwistgraded}
+%The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
+%Moreover, this equivalence is $\U(2)$-equivariant.
+%\end{thm}
 
@@
 
-In this case $S_+\otimes W$ and $S_-\otimes W^*$ have two-dimensional trivial $G$-subrepresentations.
+In this case $S_+\otimes W$ and $S_-\otimes W$ have two-dimensional trivial $G$-subrepresentations.
 Any scalar rank $(1, 1)$ supercharge is square-zero.
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by its defining representation.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, and $W$ is its defining representation.
 
@@
 \begin{proof}
+Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
 The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.
-Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
 This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
@@
 
+There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
+
+This twist also admits the following twisting datum.
+To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
+The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
+Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
 %However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
@@
 This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
-
-To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
-The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
-Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
-\end{proof}
+\end{proof}
+
+\begin{remark}
+\brian{Cotangent type.}
+\end{remark}
 

### 2020-02-12 paper.tex

--- 2020-02-12 paper.tex
@@
 This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
-
-To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
-The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
-Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
 \end{proof}

### 2020-02-13 paper.tex
merge

@@
   \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Generalized BF Theory} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \gg/\gg)$
+ %$T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$
+ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
@@
  && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
@@
 \begin{prop}
-The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+%$\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
 
@@
 
-We will now describe dimensional reductions of the classical Chern--Simons theory.
+We will now describe dimensional reductions of some of the previously discussed BV theories.
+Throughout this section we let $X$ and $Y$ be complex manifolds and $M$ be a smooth manifold. 
+We focus on BV theories described as formal mapping spaces whose sources are formal manifolds of the form 
+\begin{equation}\label{eqn: generalized}
+X \times Y_{\rm Dol} \times M_{\rm dR} .
+\end{equation}
+
+We first consider the case in which $M$ is of the form $M' \times \RR$ and we reduce along the projection
+\[
+p_{\rm dR} : X \times Y \times (M' \times \RR) \to X \times Y \times M' .
+\]
+In this case, we will only need to know the dimensional reduction of generalized Chern-Simons theory.
 
 \begin{prop} \label{CS_to_BF_diml_red_prop}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold.
 Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the corresponding generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
+\[\map(X\times Y_{\mr{Dol}}\times (M'\times \RR)_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p_{\rm dR}$ is equivalent to the generalized BF theory
+\[
+T^*[-1] {\rm Map}(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, B\fg) .
+\]
+%\map(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
 \end{prop}
@@
 \begin{proof}
-To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
-\[\map(\pt, T^*[-1] B \fg)\]
+To simplify the proof, we assume $X,Y,M'=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+\[T^*[-1] \map(\pt, B \fg) = T^*[-1] B \fg\]
 has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
@@
 
-\begin{corollary}
-Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
-Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
-\label{cor:Hodgetopologicalreduction}
-\end{corollary}
+%\begin{corollary}
+%Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
+%\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
+%Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
+%\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
+%\label{cor:Hodgetopologicalreduction}
+%\end{corollary}
+
+Next, we consider dimensional reduction along a holomorphic direction. 
+First, we set up some notation.
 
 Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation. 
-Recall that the symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e.
-a real volume form.
+The symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e. a real volume form. 
 We denote by $V=V_\RR\otimes_{\RR}\CC$ its complexification. 
-$V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$.
-Moreover, $V$ carries a complex volume form $\Omega_V$:
+Note that $V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$. 
+Also, since
 \[\det(V)\cong \det(V_\RR)\otimes_{\RR}\CC\]
-and we use the real volume form on $V_\RR$.
-
-Functoriality of this construction gives a group homomorphism
+the real volume form on $V_\RR$ determines a complex volume form on $V$.
+
+Complexification yields a group homomorphism
 \begin{equation}
@@
 
+As in Equation (\ref{eqn: generalized}), we assume $X$ is a complex manifold of the form $X' \times V$ and consider the dimensional reduction along the map
+\[
+p_{\dbar} : (X' \times V) \times Y \times M \to X' \times Y \times (M \times V_\RR)
+\]
+induced by ${\rm Re} : V \to V_{\RR}$.
+
 \begin{prop} \label{CS_diml_red_prop}
-Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above. Consider the generalized Chern--Simons theory
-\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
-The isomorphism is moreover $\SO(V_\RR)$-equivariant.
+Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above.
+Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the generalized Chern--Simons theory
+\[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized Chern--Simons theory
+\[\map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
+The equivalence is $\SO(V_\RR)$-equivariant.
 \end{prop}
 \begin{proof}
-We may assume $X,Y,M=\pt$ as in the previous proof.
+We may assume $X',Y,M=\pt$ as in the previous proof.
 
@@
 
+As a corollary of this result we obtain the reduction of generalized Hodge theory.
+
 \begin{corollary}
-Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
-\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg).\]
-
-Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized BF theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, T^*[d] B\fg).\]
-The isomorphism is moreover $\SO(V_\RR)$-equivariant.
-\label{cor:BFholomorphicreduction}
-\end{corollary}
-
-\begin{corollary}
-Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
-\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
-
-Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Hodge theory
-\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
-The isomorphism is moreover $\SO(V_\RR)$-equivariant.
+Let $X', Y, M, V_\RR, V$ be as before. 
+Fix an $L_\infty$ algebra equipped with a non-degenerate pairing as in Definition \ref{Hodge_family_def} and consider the generalized Hodge theory
+\[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
+Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized Hodge theory
+\[\map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
+The equivalence is $\SO(V_\RR)$-equivariant.
 \label{cor:Hodgeholomorphicreduction}
 \end{corollary}
+
+By essentially the same argument as in the proof of Proposition \ref{CS_diml_red_prop}, we obtain the reduction of generalized BF theory.
+
+\begin{prop}
+Let $X', Y, M, V_\RR, V$ be as before. 
+Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
+\[T^*[-1] \map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized BF theory
+\[T^*[-1] \map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
+This equivalence is $\SO(V_\RR)$-equivariant.
+\label{prop:BFholomorphicreduction}
+\end{prop}
+
+Finally, we take $Y$ to be a complex manifold of the form $\CC^{n-k} \times V$, where $V$ is complex $k$-dimensional and consider the projection
+\[
+p_{\rm Dol} : X \times (\CC^{n-k} \times V) \times M \to X \times Y' \times (M \times V_\RR) 
+\]
+induced by ${\rm Re} : V \to V_\RR$.
+
+\begin{prop}
+\label{prop:BFdolbeaultreduction}
+Let $X, M, V_\RR, V$ be as before.
+Fix an $L_\infty$ algebra $\fg$ and consider the generalized $BF$ theory
+\[
+T^*[-1] {\rm Map}(X \times (\CC^{n-k} \times V)_{\rm Dol} \times M_{\rm dR} , B \fg) .
+\]
+Its dimensional reduction along $p_{\rm Dol}$ is equivalent to the generalized BF theory
+\[
+T^*[-1] {\rm Map} (X \times \CC^{n-k} \times (M \times V_\RR)_{\rm dR}, B \fg[\epsilon_1,\ldots,\epsilon_n])
+\]
+where $\epsilon_1,\ldots, \epsilon_n$ are formal parameters of degree $+1$.
+This equivalence is $\SO(V_\RR)$-equivariant.
+\end{prop}
+\begin{proof}
+Note that there is an isomorphism of $L_\infty$ algebras
+\[
+\Omega^{\bu, \bu} (\CC^{n-k} \times V ; \fg) = \Omega^{0,\bu}(\CC^{n-k} \times V ; \fg) \otimes {\rm Sym}(\CC^n [-1]) = \Omega^{0,\bu} (\CC^{n-k} \times V ; \fg[\epsilon_1,\ldots, \epsilon_n]) .
+\]
+The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon_1,\ldots, \epsilon_n]$. 
+\end{proof}
 
@@
 Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant.
-By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
 \end{proof}
@@
 
-The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
+The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
 
@@
 
-\begin{proof}
-We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
-\begin{align*}
-& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-\end{align*}
-This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-\begin{align*}
-\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-\end{align*}
-
-The next step is to decompose the $(1,1)$ form $\psi$ as
-\[
-\psi = \omega \Lambda \psi + \psi_{\perp}
-\]
-where $\Lambda \psi_{\perp} = 0$.
-
-\end{proof}
+%\begin{proof}
+%We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
+%\begin{align*}
+%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
+%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+%\end{align*}
+%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+%\begin{align*}
+%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+%\end{align*}
+%
+%The next step is to decompose the $(1,1)$ form $\psi$ as
+%\[
+%\psi = \omega \Lambda \psi + \psi_{\perp}
+%\]
+%where $\Lambda \psi_{\perp} = 0$. 
+%
+%\end{proof}
 
@@
 \begin{theorem}  \label{3d_8_minimal_twist_thm}
-The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*(\fg/\fg))$.
 Moreover, the equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
-On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
+By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to generalized BF theory on $\CC \times \RR_{\rm dR}$ for dg Lie algebra $\fg[\epsilon_1,\epsilon_2]$ where $\epsilon_1,\epsilon_2$ are of cohomological degree $+1$.
+The result the follows from the identification of formal moduli problems $T^*(\fg / \fg) = B \fg[\epsilon_1,\epsilon_2]$.
+\end{proof}
+
+%\begin{proof}
+%On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
 We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.
@@
 When we calculate that dimensional reduction, the fields reduce according to the rule
-\begin{align*}
-\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
-&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
-\end{align*}
-Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
-\end{proof}
+%\begin{align*}
+%\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
+%&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
+%\end{align*}
+%Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
+%\end{proof}
 
@@
 \end{theorem}
+
+\begin{corollary}
+The topological $A$-twist of 3d $\cN=8$ super Yang-Mills is perturbatively trivial.
+\end{corollary}
 

### 2020-02-13 paper.tex
3d done

@@
 
-Finally, we take $Y$ to be a complex manifold of the form $\CC^{n-k} \times V$, where $V$ is complex $k$-dimensional and consider the projection
-\[
-p_{\rm Dol} : X \times (\CC^{n-k} \times V) \times M \to X \times Y' \times (M \times V_\RR) 
-\]
-induced by ${\rm Re} : V \to V_\RR$.
+Finally, we take $Y$ to be a complex manifold of the form $Y' \times \CC$, where $V$ is complex $k$-dimensional and consider the projection
+\[
+p_{\rm Dol} : X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
+\]
+induced by ${\rm Re} : \CC \to \RR$.
 
@@
 \label{prop:BFdolbeaultreduction}
-Let $X, M, V_\RR, V$ be as before.
+Let $X, M, Y'$ be as above.
 Fix an $L_\infty$ algebra $\fg$ and consider the generalized $BF$ theory
 \[
-T^*[-1] {\rm Map}(X \times (\CC^{n-k} \times V)_{\rm Dol} \times M_{\rm dR} , B \fg) .
+T^*[-1] {\rm Map}(X \times (Y' \times \CC)_{\rm Dol} \times M_{\rm dR} , B \fg) .
 \]
@@
 \[
-T^*[-1] {\rm Map} (X \times \CC^{n-k} \times (M \times V_\RR)_{\rm dR}, B \fg[\epsilon_1,\ldots,\epsilon_n])
-\]
-where $\epsilon_1,\ldots, \epsilon_n$ are formal parameters of degree $+1$.
+T^*[-1] {\rm Map} (X \times Y'_{\rm Dol} \times (M \times \RR)_{\rm dR}, \fg / \fg)
+\]
 This equivalence is $\SO(V_\RR)$-equivariant.
@@
 \[
-\Omega^{\bu, \bu} (\CC^{n-k} \times V ; \fg) = \Omega^{0,\bu}(\CC^{n-k} \times V ; \fg) \otimes {\rm Sym}(\CC^n [-1]) = \Omega^{0,\bu} (\CC^{n-k} \times V ; \fg[\epsilon_1,\ldots, \epsilon_n]) .
-\]
-The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon_1,\ldots, \epsilon_n]$. 
+\Omega^{\bu, \bu} (Y' \times \CC ; \fg) = \Omega^{\bu,\bu}(Y') \otimes \Omega^{0,\bu}(\CC) \otimes \fg[\epsilon]
+\]
+where $\epsilon$ is a parameter of degree $+1$.
+The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon]$. 
 \end{proof}
@@
 \item
-An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$. and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item
@@
 \begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an A-twisting supercharge in 3d $\mc N=4$.
-Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a B-twisting supercharge in 3d $\mc N=4$.
+A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
+Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
 \end{lemma}
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$ -- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
+This is the $A$-twist in our classification above.
+%-- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
 
 A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
-This subspace has the opposite orientation, so corresponds to the B-twist in our classification above.
+This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.
 \end{proof}
@@
 
-\subsubsection{Topological A Twist}
+\subsubsection{Topological $A$-Twist}
 \label{sect:3d_4_A_twist}
@@
 
-\subsubsection{Topological B Twist}
+\subsubsection{Topological $B$-Twist}
 \label{sect:3d_4_B_twist}
@@
 \begin{theorem}  \label{3d_8_minimal_twist_thm}
-The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*(\fg/\fg))$.
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
 Moreover, the equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
-By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to generalized BF theory on $\CC \times \RR_{\rm dR}$ for dg Lie algebra $\fg[\epsilon_1,\epsilon_2]$ where $\epsilon_1,\epsilon_2$ are of cohomological degree $+1$.
-The result the follows from the identification of formal moduli problems $T^*(\fg / \fg) = B \fg[\epsilon_1,\epsilon_2]$.
+By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to the desired generalized BF theory.
 \end{proof}
@@
 
-\subsubsection{Topological A Twist}
+\subsubsection{Topological $A$-Twist}
 \label{sect:3d8A_Twist}
@@
 
-\subsubsection{Topological B Twist}
+\subsubsection{Topological $B$-Twist}
 \label{sect:3d8B_Twist}

### 2020-02-13 paper.tex
merge

--- 2020-02-12 paper.tex
@@
 
-In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing which should be thought of as the complexified Lie algebra of the gauge group.
+In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing, which should be thought of as the complexified Lie algebra of the gauge group.
 
@@
 Let $W$ be a two-dimensional complex symplectic vector space.
-The theory admits the $R$-symmetry group $G_R=\SL(2;\CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
+The theory admits the $R$-symmetry group $G_R=\SL(2)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
 
@@
 
-%There is an alternative $\ZZ$-grading one can assign to the twist when $U$ is of cotangent type $U = R \oplus R^*$. 
-%In this case, the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$. 
-%The new twisting datum is $\Tilde{\alpha} \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components. 
-%%\[
-%%\begin{array}{ccccc}
-%%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
-%%&  z & \mapsto & \left(1 , z, z \right)
-%%\end{array}
-%%\]
-%There is also a new twisting homomorphism 
+When $U$ is of cotangent type $U = R \oplus R^*$ the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$.
+In this case, the twist admits twisting data homomorphism $\alpha \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components.
 %\[
-%\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\Tilde{\alpha}} G_R
+%\begin{array}{ccccc}
+%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
+%&  z & \mapsto & \left(1 , z, z \right)
+%\end{array}
 %\]
-%By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
-%
-%\begin{thm}
-%\label{thm:4d_2minimaltwistgraded}
-%The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
-%Moreover, this equivalence is $\U(2)$-equivariant.
-%\end{thm}
+There is a new twisting homomorphism 
+\[
+\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\alpha} G_R
+\]
+By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
+
+\begin{thm}
+\label{thm:4d_2minimaltwistgraded}
+The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
+Moreover, this equivalence is $\U(2)$-equivariant.
+\end{thm}
 
@@
 We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, and $W$ is its defining representation.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by its defining representation.
 
@@
 \begin{proof}
-Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
 The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.
+Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
 This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$.
@@
 
-There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
-
-This twist also admits the following twisting datum.
+%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
+Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
+
+\begin{theorem} \label{3d_4_minimal_twist_thm}
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
+Moreover, the equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
+This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
+
 To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
@@
 Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
-%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
-Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
-
-\begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
-Moreover, the equivalence is $\U(1)$-equivariant.
-\end{theorem}
-
-\begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
-This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
 \end{proof}

### 2020-02-13 paper.tex
Intro copyedits

@@
 We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
-We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
-For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory.
+We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.
+For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.
+These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and $BF$ theory.
 \end{abstract}
@@
 In this paper we calculate supersymmetric twists of super Yang--Mills theories in dimension 2 through 10.
-Our main tools are the classical Batalin--Vilkovisky formalism which eliminates the need for auxiliary fields to close the on-shell supersymmetry action and a consistent use of dimensional reduction which allows us to deduce lower-dimensional statements from higher-dimensional statements.
+Our main tools are the classical Batalin--Vilkovisky formalism, which eliminates the need for auxiliary fields to close the on-shell supersymmetry action, and a consistent use of dimensional reduction which allows us to deduce lower-dimensional statements from higher-dimensional statements.
 
@@
 Let us begin with an informal discussion of classical field theories.
-A classical field theory is usually taken to be the data of the space of fields $\cF$ equipped with an action functional.
+A classical field theory is usually defined in terms of the data of the space of fields $\cF$ equipped with an action functional.
 To incorporate gauge symmetries, one may either work with $\cF$ as a stack or, as in the BRST formalism, with $\cF$ as a $Q$-manifold, i.e.
 a graded manifold equipped with a square-zero vector field of cohomological degree $1$ (the BRST differential).
-In the Batalin--Vilkovisky approach one considers instead the space of BV fields $\cE$ which is equipped with a $(-1)$-shifted symplectic structure which may be modeled by a $QP$-manifold.
+In the Batalin--Vilkovisky approach one considers instead the space of BV fields $\cE$, which is equipped with a $(-1)$-shifted symplectic structure; this may be modeled by a $QP$-manifold \cite{Schwarz}.
 Moreover, we assume that the $Q$-structure is Hamiltonian, i.e.
-it is given by a Poisson bracket $\{S, -\}$ with respect to the BV action functional.
+that it is given by a Poisson bracket $\{S, -\}$ with respect to the BV action functional.
 Here $\cE$ is supposed to be the derived critical locus of the action functional on $\cF$.
@@
 As the space of BV fields $\cE$ is an infinite-dimensional manifold, it is difficult to work with it directly (for instance, to make sense of a $(-1)$-shifted symplectic structure).
-Instead, we zoom in on a neighborhood of a point where $Q$ vanishes (i.e.
+Instead, we zoom in on the neighborhood of a point where $Q$ vanishes (i.e.
 we consider a given classical solution).
@@
 We call these \emph{perturbative equivalences} (see Definition \ref{def:perturbativeequivalence}) to emphasize that we are working in a formal neighborhood of a given classical solution.
-For simplicity, throughout the paper we ignore issues of unitarity, so we complexify all fields.
+For simplicity, throughout the paper we ignore issues of unitarity: in other words, we always consider complexified bundles of fields.
 
@@
 
-Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant.
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is moreover translation-invariant.
 Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
-A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$.
+A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action on the fields is extended to an action of the super Lie algebra $\fA$.
 In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.
@@
 
-We instead take another approach pioneered by Baulieu \cite{BaulieuBV}.
+We instead take another approach pioneered by Baulieu, Bellon, Ouvry and Wallet \cite{BaulieuBV}.
 Namely, one may canonically extend the supersymmetry action from ordinary fields $\cF$ to the space of BV fields $\cE$.
-The property of the action being on-shell now means that the map $\fA\rightarrow \mathrm{Vect}(\cE)$ preserves Lie brackets up to homotopy.
-One may then try to extend it to an $L_\infty$ action.
-
-In these paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10.
+The property of the action being on-shell now means that the map $\fA\rightarrow \mathrm{Vect}(\cE)$ preserves Lie brackets, but only up to homotopy.
+One may then try to incorporate these homotopies: to extend the Lie action to an $L_\infty$ action.
+This contrasts with the auxiliary field approach of the previous paragraph, where one instead builds a resolution of the space of BV fields on which the supersymmetry Lie algebra acts strictly.
+
+In this paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10.
 In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills.
-First of all, these theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing.
+These theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing.
 In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation.
@@
 division algebras) and supersymmetry (see Section \ref{sect:compositionalgebras}) which goes back to the works \cite{Evans,KugoTownsend}.
-For instance, we may construct the 10d $\cN=(1, 0)$ supersymmetry from octonions $\mathbb{O}$, 6d $\cN=(1, 0)$ supersymmetry from quaternions $\mathbb{H}$, 4d $\cN=1$ supersymmetry from complex numbers $\CC$ and 3d $\cN=1$ supersymmetry from real numbers $\RR$.
-Our treatment follows the work of Baez and Huerta \cite{BaezHuerta} and we show how to extend the $\fA$-action to an $L_\infty$-action using these ideas.
+For instance, we may construct the 10d $\cN=(1, 0)$ supersymmetry from the algebra of octonions $\mathbb{O}$, 6d $\cN=(1, 0)$ supersymmetry from the algebra of quaternions $\mathbb{H}$, 4d $\cN=1$ supersymmetry from the complex numbers $\CC$ and 3d $\cN=1$ supersymmetry from the real numbers $\RR$.
+Our treatment follows the work of Baez and Huerta \cite{BaezHuerta} and we show how to extend the on-shell $\fA$-action to an $L_\infty$-action using these ideas.
 As a new result, we also construct an $L_\infty$-action on matter multiplets where the language of composition algebras turns out to be indispensable (see Section \ref{sect:mattermultipletSUSY}).
@@
 
-In addition to dimensional reduction of these four super Yang--Mills theories, there are also certain special super Yang--Mills theories with chiral supersymmetry: namely, 2d $\cN=(1, 0)$, $\cN=(2, 0)$ and $\cN=(4, 0)$ with matter as well as pure $\cN=(\cN_+, 0)$ theories for any $\cN_+$.
+In addition to the dimensional reduction of these four super Yang--Mills theories, there are also certain special super Yang--Mills theories with chiral supersymmetry: namely, 2d $\cN=(1, 0)$, $\cN=(2, 0)$ and $\cN=(4, 0)$ with matter as well as pure $\cN=(\cN_+, 0)$ theories for any $\cN_+$.
 We treat these separately (see Section \ref{sect:2dchiral}), but again the language of composition algebras turns out to be convenient.
@@
 
-The notion of supersymmetric twist of a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}.
+The notion of supersymmetric twisting for a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}.
 The definitions we use in this paper will follow our previous work \cite{ElliottSafronov}, so let us briefly recall those.
@@
 Then it gives rise to a square-zero odd symplectic vector field on the space of BV fields $\cE$.
-In particular, we may modify the differential on $\cE$ as $\mathrm{d}\mapsto \mathrm{d}+Q$.
+In particular, we may modify the differential on $\cE$ by the replacement $\mathrm{d}\mapsto \mathrm{d}+Q$.
 Working up to perturbative equivalence, this turns out to drastically simplify the theory as we will shortly see.
 
-The original classical field theory carried a $\ZZ\times\ZZ/2\ZZ$-grading, where $\ZZ$ is the cohomological (ghost) grading and $\ZZ/2\ZZ$ is the fermionic grading.
+The original classical field theory carried a $\ZZ\times\ZZ/2\ZZ$-grading, where $\ZZ$ is the cohomological (in the physics literature: ghost number) grading and $\ZZ/2\ZZ$ is the fermionic grading.
 We see that $\mathrm{d}$ has bidegree $(1, 0)$ while $Q$ has bidegree $(0, 1)$.
@@
 In this paper we only consider the case of global supersymmetry for super Yang--Mills theories on $\RR^n$.
-In certain cases one may consider coupling of super Yang--Mills to supergravity in which case the interpretation of the twist is that we consider a nontrivial supergravity background.
+In certain cases one may consider coupling of super Yang--Mills to supergravity in which case there is an interpretation of the twisting procedure as performing perturbation theory in a nontrivial supergravity background.
 Let us briefly explain this perspective.
@@
 A classical solution of supergravity consists, in particular, of the following data: a spacetime manifold $M$, a $\Spin(n)$-bundle $P_\Spin\rightarrow M$ equipped with a connection (spin connection), a $G_R$-bundle $P_R\rightarrow M$ equipped with a connection and a ghost for supertranslations $\eta\in \Gamma(M, (P_\Spin\times P_R)\times^{\Spin(n)\times G_R}\Sigma)$.
+The ghost $\eta$ is bosonic: it lives in bidegree $(-1,1)$ for the $\ZZ \times \ZZ/2\ZZ$-grading, so it makes sense to give it a non-zero value.
 If we couple super Yang--Mills to supergravity, then the super Yang--Mills fields become sections of the associated bundles to $P_\Spin\times P_R$.
@@
 
-\item In the supergravity setting we consider a $G$-bundle $P_G\rightarrow M$ with a connection so that $P_\Spin\times P_R$ is induced via the homomorphism $G\rightarrow \Spin(n)\times G_R$.
-
-\item Given $\alpha\colon \U(1)\rightarrow G_R$, we consider a trivial $\U(1)$-subbundle in $G_R$ on which the connection restricts to zero.
+\item The supergravity analog of the twisting homomorphism is a choice of $G$-bundle $P_G\rightarrow M$ with connection so that $P_\Spin\times P_R$ is induced via the homomorphism $G\rightarrow \Spin(n)\times G_R$.
+
+\item The supergravity analog of $\alpha\colon \U(1)\rightarrow G_R$, if a choice of trivial $\U(1)$-subbundle in $G_R$ on which the connection restricts to zero.
 \end{itemize}
@@
 To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
+This occurs whenever the bracket $[Q,-]$ with the twisting supercharge surjects onto the space of translations.
 The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich, AxelrodSinger}.
@@
 The key result is that the renormalization for mixed holomorphic-topological theories is extremely well-behaved from an analytic perspective.
-It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}.
+It is shown in the cited work that, to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}.
 Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.
 
-These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory.
+These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory.
 Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
-The twisted gauge theories here are all either equivalent to $BF$-type theories, or deformations of such theories by a holomorphic differential operator.
-Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop; meaning all higher order corrections vanish identically.
+The twisted gauge theories here are all either equivalent to $BF$-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
+Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop, meaning all higher order corrections vanish identically.
 
@@
 Starting with a classical field theory on $M$, defined using the BV formalism, one can build a factorization algebra $\obs^{\mr{cl}}$ modelling the classical observables of the field theory.
-If the classical field theory carried the action of a group $G$, so would the factorization algebra.
+If the classical field theory carries the action of a group $G$, so does the associated factorization algebra.
 Furthermore, Costello and Gwilliam develop techniques for the quantization of such algebras of classical observables, using the theory of renormalization as discussed in the previous section.
@@
 In good circumstances, we can say even more.
-An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
+An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this can be obtained from a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
 \begin{nonum}[{\cite[Theorem 3]{ElliottSafronov}}]
@@
 If $M$ is replaced by a complex manifold $X$, we may also consider its version with the space of fields $\Omega^{\bullet, \bullet}(X; \fg)[1]\oplus \Omega^{\bullet, \bullet}(X; \fg^*)[2\dim(X)-2]$, where $\Omega^{\bullet, \bullet}$ is the space of differential forms equipped with the Dolbeault differential.
-Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$.
+Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$, again equipped with the Dolbeault differential.
 We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMP}).
@@
 Just like for the BF theory, we also have two other versions which may be combined into a generalized Chern--Simons theory.
-Another direction we can generalize in is to replace the Lie algebra $\fg$ by a dg Lie algebra in which case the BF theory itself becomes a particular example of the Chern--Simons theory.
+Another direction we can generalize in is to replace the Lie algebra $\fg$ by a dg Lie algebra, in which case the BF theory itself becomes a particular example of the Chern--Simons theory.
 
@@
 In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we summarize all the possible twists of dimensional reductions of 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills and 4d $\cN=1$ super Yang--Mills respectively.
-We will now give a short description of each twisted theory in a more physical language, with references to where in the literature it was previously considered.
+In Table \ref{table_of_twists_2d} we summarize the twists of 2d supersymmetric Yang-Mills theory.
+Before these tables, we will give a short description of each twisted theory in a more physical language, with references to where in the literature it was previously considered.
 
@@
  \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang-Mills theory in 9 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory with one topological direction and four holomorphic directions.
-It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold.
+It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold (i.e.
+$\RR$ or $\RR/\ZZ$).
 \end{itemize}
@@
  \item \emph{$\mc N=1$ holomorphic twist.} Super Yang-Mills theory in 8 dimensions admits three classes of twist.
-The minimal twist, by a holomorphic supercharge, is equivalent to a holomorphic version of BF theory.
+The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of BF theory.
 This theory is $\mr U(4)$-invariant, and can be defined on arbitrary complex 4-folds.
- \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in two directions and holomorphic in the remaining three complex directions.
+ \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist by a rank 1 impure spinor, which is topological in two directions and holomorphic in the remaining three complex directions.
 This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
@@
  \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
-The minimal twist is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.
+The minimal twist, by a pure spinor, is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.
 This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
- \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.
+ \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist, by a rank 1 impure spinor, which is topological in three directions and holomorphic in the remaining two complex directions.
 This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
@@
 This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.
-If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized form of BF theory valued in the adjoint quotient $\gg/\gg$.
- \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist, with four invariant directions.
+If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized BF theory valued in the adjoint quotient $\gg/\gg$.
+ \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist with four invariant directions.
 This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.
@@
 There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.
-An analysis of these twists using similar techniques to this paper, but with an aim to obtain the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
+An analysis of these twists using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
 \end{itemize}
@@
  &&& $\mr{Map}(\CC^4, B\gg)_\mr{dR}$ & \\ \hline
-  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ Pure}} & Generalized BF Theory & \multirow{2}*{4 (minimal)} \\
+  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{\hyperref[sect:7dminimaltwist] {Rank $1$ pure}} & Generalized BF Theory & \multirow{2}*{4 (minimal)} \\
  &&& $T^*[-1]\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $\mr{Map}(\CC^2 \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
-  && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ Impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
+  && \multirow{2}*{\hyperref[sect:7dtopologicaltwist]{Rank $1$ impure}} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
  &&& $\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)_\mr{dR}$ & \\ \hline
@@
  &&& $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \gg/\gg)$
- %$T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$
  & \\ \cline{3-5}
@@
  &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
- %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
- %&&& {} & \\ \cline{3-5}
- %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
- %&&& {} & \\ \cline{3-5}
- %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
- %&&& {} & \\ \hline
  \end{tabular}
@@
 \end{tikzpicture}
-\caption{This figure shows the orbits of square-zero supercharges in each dimension.
+\caption{This figure shows the orbits of square-zero supercharges in each dimension, and how they relate to one another under dimensional reduction.
 The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiplet orbits.
 Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.
-Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.}
+Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.
+There is an arrow whenever one twist dimensionally reduces to another twist one dimension lower.}
 \label{fig:superchargeorbits}

### 2020-02-13 paper.tex
Proofreading S1

@@
 It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.
-It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
+It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the unitary metalinear group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
 When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter.
@@
 In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.
-Most of the material in this section is not original.
+Much of the material in this section is not original.
 We refer the reader to \cite{CostelloBook, Book2} for more details on this perspective.
-We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.
+We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: mixed holomorphic-topological theories.
 We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.
@@
 
-Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
+Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and by $\cE_c$ the topological vector space of smooth compactly supported sections.
 We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
@@
 In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
-That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
+That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.
 The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
@@
 
-We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
+We call $\cE$ the \defterm{space of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}.
+The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook})
 \[
@@
 This bracket is of cohomological degree $+1$. 
-This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
+This bracket is a graded version of the so-called Soloviev bracket \cite{Soloviev} defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
 
@@
 \]
-Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+Integrating by parts, we see that for any $(n-1)$-tuple $(\phi_1, \ldots, \phi_{n-1}) \in \cE_c^{n-1}$ the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
 This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
@@
 
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
+In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $(Q_{\mr{BV}}, I)$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
 The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
 
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
+Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead of the quadruple$(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
 
@@
 
-Next, we formulate the notion of an equivalence of classical BV theories.
+Next, we formulate the notion of a morphism, and an equivalence, of classical BV theories.
 
 \begin{definition}
-A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is
-% a nonlinear map of vector bundles $E\rightsquigarrow E'$, 
-a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
+A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwine the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
 A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+\end{definition}
+
+The interpretation of this definition is that $\Phi$ is a non-linear map between the bundles of BV fields, and $\Phi_n$ is its $n^{\text{th}}$ Taylor coefficient.
+
+\begin{definition}
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. 
+We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying our descriptions of twisted theories.
 First, we consider the process of integrating out an auxiliary field.
@@
 where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
+Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where the equivalence sets $\phi = S_1$ and $\phi^* = 0$.
 \end{prop}
@@
 \begin{proof}
-Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^{(n)}$.  
 The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
@@
 \Psi_n \colon \sym^n(E_0) &\to E \\
-e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
+e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^{(n)}(e_1, \ldots, e_n), 0).
 \end{align*}
@@
 \]
-whose sections we denote by $e_0 + \varsigma + \varsigma^* + \psi + \psi^*$ according to the above decomposition. 
+whose sections we denote by $e_0 + \phi + \phi^* + \psi + \psi^*$ according to the above decomposition. 
 The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
@@
 For the classical BV theory $(E, \omega, S)$ as in the proposition, the linearized BV differential defines the following cochain complex of fields:
-%\[\xymatrix{
-%\cdots & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \cdots \\
-%\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
-%&&F_\phi \ar^{~}[dr] &F^!_{\phi*} \ar[ur] && \\
-%&&F^!_{\psi^*} \ar^{~}[ur] &F_\psi \ar[uur] && \\
-%}\]
 \[\xymatrix{
@@
 }\]
-where the subscripts match the notation for the fields in the statement above.
-\footnote{Note that we are writing $F$ as if it is concentrated in a single cohomological degree, but the proposition applies for any graded vector bundle as in the statement of the proposition.}
+where the subscripts match the notation for the fields in the statement above \footnote{Note that we are writing $F$ as if it is concentrated in a single cohomological degree, but the proposition applies for any graded vector bundle as in the statement of the proposition.}.
 The top line is the underlying cochain complex of the theory with fields $E_0$.
@@
 %
-%\begin{cor} \label{cor:quad}
+%\begin{corollary} \label{cor:quad}
 %Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
@@
 %\]
-%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
-%\end{cor}
+%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$
+
+%\end{corollary}
 %\begin{proof}
@@
 In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion).
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
+Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and let $\fg$ be a super Lie algebra.
 We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
@@
 \begin{definition}
-The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
+The \defterm{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
@@
 We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.
-These data can be packaged into what's known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
+These data can be packaged into what's known as a BRST theory, where fermionic fields (referred to as ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
 
@@
 \begin{itemize}
-\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
+\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$.
 \item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
@@
 \]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
-The differential of the free BV theory is
+The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.  The differential of the free BV theory is
 \[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
@@
 We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ as {\em the BV theory associated to the BRST theory} $\cF$.
-%and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. 
-In the case $S_{\mr{BRST}} = 0$ we refer to the associated BV theory as being of {\em cotangent type}, which we will denote by $T^*[-1] \cF$.
+In the case where $S_{\mr{BRST}} = 0$ we refer to the associated BV theory as being of {\em cotangent type}, which we will denote by $T^*[-1] \cF$.
 
@@
 
-For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
+For instance, if $\fg$ is a complex $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
 \[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
@@
 \begin{definition}
-Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
+Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \bigoplus_{m \in \ZZ} \fg(m)$ compatible with the $L_\infty$ structure.
 \end{definition}
@@
 In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
-It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
+It is only relevant for quantization which we do not consider in this paper, so for simplicity we will not require ellipticity (though in fact all examples we consider will end up being elliptic).
 \end{remark}
@@
 \begin{example}
-Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
+Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by a complex $L_\infty$ algebra $\fg$.
 Then we may define the following local formal moduli problem on $X\times Y\times M$.
@@
 \[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
-Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
+If $F = BG$ is the classifying stack of a complex algebraic group, the mapping stack $\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, BG)$ has a natural geometric interpretation: its closed points correspond to algebraic principal $G$-bundles $P$ on $X \times Y \times M$, with a Higgs field on each slice $P|_{\{x\} \times Y \times \{m\}}$ and a flat connection on each slice $P|_{\{x\} \times \{y\} \times M}$.
+Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems, and can be thought of as modelling the formal neighborhood of the trivial bundle in this moduli stack.
 \end{remark}
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
+Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth oriented manifold.
+Fix a complex $L_\infty$ algebra $\fg$.
 The \defterm{generalized $BF$ theory} is the BV theory associated to the following BRST theory:
@@
 \item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
+The shift $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
 
@@
 \end{definition}
-
-\begin{remark} \label{mapping_stack_remark}
-The mapping stack above has a precise meaning in the language of derived algebraic geometry -- see for instance \cite{PTVV}, where, if $X, Y$ and $M$ are compact, such a mapping stack is shown to carry a $-1$-shifted symplectic structure.
-For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
-The language of the mapping stack will simply be used as a compact way of referring to the theory above.
-\end{remark}
 
@@
 \[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
-where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.
+where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and where $\ell_k$ denote the $k^{\text{th}}$ component of the $L_\infty$ structure on $\fg$.
 
@@
 
-We will see many $BF$ theories as the output when we twists a supersymmetric gauge theories.
-In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as a generalized $\beta\gamma$ system, extending the usual 2d $\beta \gamma$ system.
+We will see many $BF$ theories as the output when we twist supersymmetric gauge theories.
+In fact, a special case of the definition above also arises when twisting theories of matter.
+We will refer to as this as a generalized $\beta\gamma$ system, where the definition will extend that of the usual 2d $\beta \gamma$ system.
 
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the BV theory associated to the following BRST theory:
+Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth manifold.
+Fix a complex vector space $V$.
+The \defterm{generalized $\beta\gamma$ system} valued in $V$ is the BV theory associated to the following BRST theory:
 \begin{itemize}
 \item The spacetime is the smooth manifold $X\times Y\times M$.
-
 \item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
 $F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-
 \item The BRST action is $S_{\mr{BRST}} = 0$.
@@
 with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
+The space of fields in the corresponding generalized BF theory will be denoted using the formal moduli problem notation  as
 \[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
@@
 \subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
-The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.
+The next class of examples of classical BV theories will be generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not generally of cotangent type.
 
@@
 \label{dfn: cs}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth oriented manifold.
 Fix an $L_\infty$ algebra $\fg$.
-We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+We assume that $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and that $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
 The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
@@
 
-\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
+\item $Q_{\mr{BV}} = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
 
@@
 \label{ex:CSHamiltonianreduction}
-\brian{Will $V\ham \fg$ already be defined above in the FMP section?}
 \end{example}
@@
 
-We denote the space of fields $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.
+We denote the space of fields by $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.
 
@@
 
-At $t\neq 0$ the $L_\infty$ algebra $\fg_\Hod$ becomes acyclic which proves the second claim.
+At $t\neq 0$ the $L_\infty$ algebra $\fg_\Hod$ becomes acyclic, which proves the second claim.
 \end{proof}
@@
 \begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 
-We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
+We have an obvious notion of isomorphisms of dimensional reductions: these are linear isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$.
 Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
@@
 \begin{proof} \textbf{Uniqueness}.
-We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
+We begin by showing that any two dimensional reductions are isomorphic and moreover that such an isomorphism is unique if it exists.
 Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
@@
 We first consider the case in which $M$ is of the form $M' \times \RR$ and we reduce along the projection
-\[
-p_{\rm dR} : X \times Y \times (M' \times \RR) \to X \times Y \times M' .
-\]
+\[p_{\rm dR} \colon X \times Y \times (M' \times \RR) \to X \times Y \times M' .\]
 In this case, we will only need to know the dimensional reduction of generalized Chern-Simons theory.
@@
 \begin{proof}
-To simplify the proof, we assume $X,Y,M'=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+To simplify the notation in the proof, we assume $X,Y,M'=\pt$, though the argument in the general case is identical.
+Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$.
+In particular, the generalized BF theory
 \[T^*[-1] \map(\pt, B \fg) = T^*[-1] B \fg\]
@@
 \begin{definition}
-Let $\fA$ be a supertranslation algebra.  The corresponding \emph{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
+Let $\fA$ be a supertranslation algebra.  The corresponding \defterm{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
 \end{definition}
@@
 \begin{definition}
-The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
+The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
 \[
@@
 
-\begin{cor}
+\begin{corollary}
 The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s=1$ is perturbatively equivalent to the topological BF theory $T^*[-1]\map(\RR^4_{\mathrm{dR}}, B\fg)$.
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 
-\begin{cor}
+\begin{corollary}
 The rank $(2, 2)$ twist of 4d $\cN=4$ super Yang--Mills for $s\neq 1$ is perturbatively trivial.
-\end{cor}
+\end{corollary}
 \begin{proof}

### 2020-02-13 paper.tex
local FMPs (finished)

--- 2020-02-13 paper.tex
@@
 This theory of renormalization can been used to study field theories with and without supersymmetry.
-\brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+\brian{many citations} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
-The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich, AxelrodSinger}.
+The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}.
+\brian{more examples}
 
@@
 \subsection*{The Relationship to Factorization Algebras}
-In our previous paper \cite{ElliottSafronov}, we discussed supersymmetric twisting with an emphasis not on the classical fields of a supersymmetric field theory, but instead on their classical or quantum \emph{observables}.
-The factorization algebra formalism of Costello and Gwilliam \cite{Book1, Book2} provides a model for the local structure of the observables in a general quantum field theory.
-In brief, for every open subset $U \sub M$ of the spacetime manifold, one associates a (possibly $\ZZ \times \ZZ/2\ZZ$-graded) vector space $\obs(U)$ of local observables on $U$.
-For any pair $U_1, U_2 \sub V$ of disjoint open subsets of an open set $V$, one associates a morphism
-\[m_{U_1, U_2}^V \colon \obs(U_1) \otimes \obs(U_2)\to \obs(V),\]
-thought of as an \emph{operator product} for local observables.
-These products should vary smoothly as one varies the open subsets $U_1, U_2$ and $V$.
-Starting with a classical field theory on $M$, defined using the BV formalism, one can build a factorization algebra $\obs^{\mr{cl}}$ modelling the classical observables of the field theory.
-If the classical field theory carried the action of a group $G$, so would the factorization algebra.
-Furthermore, Costello and Gwilliam develop techniques for the quantization of such algebras of classical observables, using the theory of renormalization as discussed in the previous section.
-
-In \cite{ElliottSafronov} we studied the supersymmetric twisting procedure as applied to factorization algebras on $\RR^n$ with an action of a supersymmetry algebra.
-If $Q$ is a topological supercharge, then the $Q$-twist $\obs^Q$ of a supersymmetric factorization algebra automatically satisfies a strong translation invariance condition: all translations must act homotopically trivially.
-In good circumstances, we can say even more.
-An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
-\begin{nonum}[{\cite[Theorem 3]{ElliottSafronov}}]
-If $Q$ is a topological supercharge, and the operator $\obs^Q(B_r(0)) \to \obs^Q(B_R(0))$ associated to the inclusion of concentric balls is an equivalence, then the factorization algebra $\obs^Q$ has the canonical structure of an $\bb E_n$-algebra.
-\end{nonum}
-The hypothesis of the theorem is automatically satisfied, for example, for superconformal theories, and should be concretely checkable in examples.
-
-In the present work we classify twists of classical field theories, to which one can associate twisted factorization algebras of classical -- and, if the appropriate anomalies vanish, quantum -- observables in the sense of our previous work.
-In some (topological) examples, these define $\bb E_n$-algebras.
-In other examples, where the twist is not fully topological, the twisted local observables will define higher analogues of vertex algebras (as in, for instance, \cite{GwilliamWilliamsKM}).
 
@@
 Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$.
-We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMP}).
+We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMPs}).
 We may also combine these three examples into what we call a \emph{generalized BF theory} with the spaces of fields $T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ (see Definition \ref{def:generalizedBF} for more details).
@@
 It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the $G_2$-monopole equations.
+This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
 \end{itemize}
@@
 This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}.
+\chris{something was studied by \cite{BaulieuBossard} in the pure $\mc N=(1,0)$ case, but it doesn't look the same?}
  \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the Donaldson-Thomas equations.
+This theory was also studied in \cite{AcharyaOLoughlinSpence} (\chris{I'm struggling to understand whether we should cite \cite{BaulieuKannoSinger, BaulieuLosevNekrasov} here or elsewhere.}; its equations of motion include the Donaldson-Thomas equations.
 \end{itemize}
@@
  && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
- &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
+ &&& $\map(\RR^5_{\mr{dR}}, B\fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:5drank2topologicaltwist] {Rank $2$ generic}} & {Perturbatively trivial} & \multirow{2}*{5 (topological)} \\
@@
   \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{\hyperref[sect:3d8minimal_twist] {Rank $1$}} & {Generalized BF Theory} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \gg/\gg)$
- %$T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$
- & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
@@
  && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
@@
  \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge Lie algebra $\fg$ (16 supercharges).}
  \label{table_of_twists_16}
@@
  \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
- &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^3, U \ham \fg)$ & \\ \hline
  \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3 (minimal)} \\
- &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
+ &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham \fg)$ & \\ \hline
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
- &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
+ &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
@@
  \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{\hyperref[sect:4d1holomorphictwist] {Rank $(1,0)$}} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
+ &&& $T^*[-1]\mr{Map}(\CC^2, R/\fg)$ & \\ \hline
  \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{\hyperref[sect:3dminimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
- &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
+ &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\fg)$ & \\ \hline
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
  \label{table_of_twists_4}
@@
 
-\subsection{Classical BV Theories} \label{sect:BV}
-
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
-In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
-That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
-The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
+\subsection{Formal Moduli Problems and Classical Field Theories}
+\label{sect:FMPs}
+
+It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
+In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
+
+Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
+We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
+
+For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
+\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
+where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
+The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
+The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
+This important result will only serve as a motivation.
+
+Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
+\[L_{V, \fg}=\fg\oplus V[-1]\]
+with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
+\[V/\fg:= B L_{V, \fg}.\]
+
+\begin{example}
+If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
+\[T[n] B\fg = \fg[n+1] / \fg.\]
+\label{ex:tangentBg}
+\end{example}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
+Then $\fg^*$ is a coadjoint representation of $\fg$.
+We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
+\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
+\label{ex:cotangentBg}
+\end{example}
 
 \begin{definition}
-A \defterm{free BV theory} on a manifold $M$ is the data of:
-\begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
-\[
-Q_{\mr{BV}} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
-\item a map of bundles
-\[
-\omega\colon E \otimes E \to \Dens_M [-1]
-\]
-that is
+Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
+\end{definition}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
+Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
+For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
+\end{example}
+
+\begin{example}
+Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-represntation equipped with an $n$-shifted symplectic structure $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
+\[\fh = \fg\oplus U[-1]\oplus \fg^*[n-2]\]
+with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes U\rightarrow U$ given by the $\fg$-action on $U$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon U\otimes U\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_U$.
+The dg Lie algebra $\fh$ carries nondegenerate invariant symmetric pairing of cohomological degree $n-2$ given by pairing $\fg$ and $\fg^*$ and pairing $U$ with itself.
+We denote
+\[U\ham \fg := B\fh.\]
+This formal moduli problem is equipped with a $\Gm$-action where $\fg$ has weight 0, $U[-1]$ has weight $1$ and $\fg^*[n-2]$ has weight $2$.
+This may be thought of as an infinitesimal version of the Hamiltonian reduction of $U$ by the $\fg$-action.
+\end{example}
+
+Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
+\[(B L)(U) = B L(U),\]
+i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
+
+\begin{definition}
+A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
+\end{definition}
+
+\begin{remark}
+In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
+It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
+\end{remark}
+
+Given a local formal moduli problem $\cM=B L$, we may consider the space of local functionals which is defined as
+\[\oloc(\cM) := \oloc(\cL[1]).\]
+The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg diffrential on $\oloc(\cM)$.
+
+\begin{example}
+Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
+Then we may define the following local formal moduli problem on $X\times Y\times M$.
+Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
+We may then consider a graded vector bundle
+\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
+on $X\times Y\times M$.
+It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
+It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
+We then define
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
+\label{ex:mappingspace}
+\end{example}
+
+\begin{remark}
+A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
+So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
+Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
+\end{remark}
+
+\begin{example}
+Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
+Moreover, assume $B\fg$ carries a $\Gm$-action.
+We then have a local $L_\infty$ algebra
+\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
+on $X\times Y\times M$. We define
+\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
+\end{example}
+
+As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
+
+\begin{prop}
+Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
+The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
+\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
+where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
+\end{prop}
+\begin{proof}
+The claim follows from the following isomorphisms of graded vector bundles:
+\begin{align*}
+\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
+\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
+\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
+\end{align*}
+\end{proof}
+
+\begin{cor}
+Suppose $X,Y,M,\fg$ are as in Example \ref{ex:mappingspace} and, moreover, $X$ is equipped with a holomorphic volume form and $M$ is oriented. Then
+\[T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)\cong \map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg).\]
+\label{cor:mapintocotangent}
+\end{cor}
+
+Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper we will only be interested in a strict notion as follows.
+
+\begin{definition}
+Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
+A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
 \begin{enumerate}
-\item[$(1)$] fiberwise nondegenerate,
-\item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item It is fiberwise nondegenerate.
+
+\item It is graded skew symmetric.
+
+\item The pairing
+\begin{align*}
+\cL_c\otimes \cL_c&\rightarrow \CC \\
+\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
+\end{align*}
+is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
 \end{enumerate}
-\end{itemize}
 \end{definition}
 
-We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
-\]
-This bracket is of cohomological degree $+1$. 
-This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
-
-We explain how to define the BV bracket in our context.  
-First note that there is a linear map
+Given a local formal moduli problem $\cM = BL$ equipped with a strict $n$-shifted symplectic structure, the space of local functionals $\oloc(\cM)$ is equipped with a Poisson bracket (see \cite[Chapter 5.3]{CostelloBook})
+\[
+\{-,-\}\colon \oloc(\cM) \times \oloc(\cM) \to \oloc(\cM)[-n]
+\]
+This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in \cite[Section 4]{GetzlerBracket}.
+
+We explain how to define the Poisson bracket in our context. Write $E = L[1]$ for convenience. First note that there is a linear map
 \[
@@
 
-The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
-\[
-\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
+The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [n]$ and hence an isomorphism of local functions
+\[
+\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[-n]) .
 \]
@@
 \[
-X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
+X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[-n])  .
 \]
 This is the Hamiltonian vector field corresponding to $F$. 
-Finally, the BV bracket between local functionals $F, G$ is defined by
+Finally, the Poisson bracket between local functionals $F, G$ is defined by
 \[
@@
 
-The BV bracket enjoys the graded skew symmetry property
+The Poisson bracket enjoys the graded skew symmetry property
 \[
@@
 as well as the graded Jacobi identity.
-This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
-Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.
-
-%\[
-%\{F(A, B), G(A, B)\} = \frac{\partial}{\partial A} F(A, B) \frac{\partial}{\partial B}  G(A,B) + \frac{\partial}{\partial B} F(A, B) \frac{\partial}{\partial A}  G(A,B)
-%\]
-
-Now, we will include interactions in the BV picture.
+
+The differential on a local $L_\infty$ algebra $L$ is given by a differential operator $Q_{\mathrm{BV}}\colon L\rightarrow L$.
+The structure of a cyclic $L_\infty$ algebra can be encoded into its potential.
+In the same way, the structure of a local $L_\infty$ algebra $L$ together with an $n$-shifted symplectic structure on $BL$ may be encoded into the \defterm{action functional} $S\in\oloc(BL)$ of cohomological degree $1-n$ such that
+\[S = \frac{1}{2}\int_M\omega(e, Q_{BV} e) + I,\]
+where $e\in L$ and $I\in\oloc(BL)$ is at least cubic. Moreover, the action functional satisfies the \defterm{classical master equation}
+\[\{S, S\} = 0.\]
+We refer to \cite[Proposition 5.4.0.2]{Book2} for this construction.
 
 \begin{definition}
-A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
-\[I \in \oloc^+(\cE)\]
-of cohomological degree zero satisfying the Maurer-Cartan equation
-\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
 \label{def:classicalfieldtheory}
@@
 
-Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
-the BV action of the theory.
-
-The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
-
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
-The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
-
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
-
-\begin{remark}
-We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
-\end{remark}
-
-\begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$ \cite[Chapter 5.4]{Book2}.
-\end{remark}
-
-We will also sometimes consider $\CC[t]$-families of classical field theories.  These will be defined as follows.
+Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}.
+Moreover, we call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}.
+It will be convenient to think of a classical field theory as a triple $(E, \omega, S)$ of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$ and an action functional $S$.
+
+\begin{example}
+Let $\cM=BL$ be a local formal moduli problem.
+Then the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ carries a natural $(-1)$-shifted symplectic structure.
+Indeed, $T^*[-1]\cM = B(L\oplus L^![-3])$ and we simply pair $L$ and $L^!$.
+Classical field theories arising via this construction are called of \defterm{cotangent type}.
+\end{example}
+
+%The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
+In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
+That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
+The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
+
+We will also consider $\CC[t]$-families of classical field theories.
 \begin{definition} \label{family_of_BV_theories_def}
-A $\CC[t]$-family of classical BV theories is a quadruple $(E,Q_{\mr{BV}}, \omega, I)$ as before, but where now the classical BV differential is $t$-dependent.  In other words, it is given as a map
-\[Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1],\]
-where, for each $t_0 \in \CC$, the quadruple $(E,Q^{t_0}_{\mr{BV}}, \omega, I)$
-\[Q^{t_0}_{\mr{BV}} = \mr{ev}_{t_0} \circ Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1] \to \cE[1]\]
-defines a classical field theory.
+A \defterm{$\CC[t]$-family of classical field theories} is a graded bundle of locally-free $\CC[t]$-modules $L$ on $M$ equipped with a structure of a $\CC[t]$-linear local $L_\infty$ algebra and a $\CC[t]$-linear $(-1)$-shifted symplectic structure $\omega\colon L\otimes_{\CC[t]} L\rightarrow \CC[t]\otimes \Dens_M[-3]$.
 \end{definition}
 
+We will consider $\CC[t]$-families of classical field theories where $L = \CC[t]\otimes L_0$ and the pairing
+\[\omega\colon L\otimes_{\CC[t]} L\rightarrow \CC[t]\otimes \Dens_M[-3]\]
+comes from a pairing
+\[\omega_0\colon L_0\otimes L_0\rightarrow \Dens_M[-3].\]
+In this case the local $L_\infty$ structure is encoded in a $t$-dependent action functional $S$.
+
+Besides the $\ZZ$-graded classical field theories defined above, we may consider the following variants of the above definition:
+\begin{itemize}
+\item A $\ZZ\times \ZZ/2\ZZ$-graded local $L_\infty$ algebra is a $\ZZ$-graded local $L_\infty$ algebra $L$ equipped with an extra $\ZZ/2\ZZ$-grading (the \defterm{fermionic grading}) with respect to which all operations are even.
+An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$ which is even with respect to the fermionic grading.
+
+\item A $\ZZ/2\ZZ$-graded classical field theory is defined in the same way as a $\ZZ$-graded classical field theory where we only consider the cohomological grading modulo 2.
+\end{itemize}
+
+\subsection{Perturbative equivalence of classical field theories}
+
 Next, we formulate the notion of an equivalence of classical BV theories.
@@
 \begin{definition}
-A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is
-% a nonlinear map of vector bundles $E\rightsquigarrow E'$, 
-a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
+A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwines the pairings $\omega, \omega'$ and defines an $L_\infty$ map $\cE_c[-1]\rightarrow \cE'_c[-1]$.
+A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon \cE\rightarrow \cE'$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. 
-First, we consider the process of integrating out an auxiliary field.
+First, we consider the process of eliminating an auxiliary field.
 
@@
 where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
+Then the theory $(E, \omega, S)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
 \end{prop}
-
-\begin{remark}
-In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
-\[\xymatrix{
-\cdots & \ul{0} & \ul{1} & \cdots \\
-\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
-}\]
-where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
-\end{remark}
-
 \begin{proof}
@@
 
-We may also remove a trivial BRST doublet.
+\begin{remark}
+In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
+\[\xymatrix{
+\cdots & \ul{0} & \ul{1} & \cdots \\
+\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
+&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
+}\]
+where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
+\end{remark}
+
+We may also eliminate pairs of fields as follows.
 
@@
 \end{prop}
+\begin{proof}
+Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
+The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
+The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
+The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
+\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]
+
+The maps $\Psi_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $\Psi_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
+Also, by construction, the $\Psi_n$ intertwine the action functionals, since
+\begin{align*}
+S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(I_{\psi^*}(e), I_\phi(e) - I_\phi(e)) + \omega(I_\phi (e), I_{\psi^*}(e) - I_{\psi^*}(e)) \\
+&= S'(e).
+\end{align*}
+\end{proof}
 
@@
 \end{remark}
-
-\begin{proof}
-Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
-The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
-The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
-The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
-\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]
-
-The maps $\Psi_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $\Psi_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  
-Also, by construction, the $\Psi_n$ intertwine the action functionals, since
-\begin{align*}
-S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(I_{\psi^*}(e), I_\phi(e) - I_\phi(e)) + \omega(I_\phi (e), I_{\psi^*}(e) - I_{\psi^*}(e)) \\
-&= S'(e).
-\end{align*}
-\end{proof}
+\begin{remark}
+We will call the pair $(\phi, \psi)$ satisfying the conditions of the previous proposition a \defterm{trivial BRST doublet}.
+\end{remark}
 
@@
 In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion).
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.
-We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
-We begin by defining an appropriate version of the Chevalley-Eilenberg cochain complex.
+Let $(E, \omega, S)$ be a classical field theory and $\fg$ a super Lie algebra.
+We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
+We begin by defining an appropriate version of the Chevalley--Eilenberg cochain complex.
 
 \begin{definition}
-The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
+The \defterm{Chevalley--Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, is defined as follows.  Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
@@
 
-The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-\[
-(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
-\]
-where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
-The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
-Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
+%The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+%\[
+%(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
+%\]
+%where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
+%The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
+%Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
 This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.
@@
 \label{infinitesimal_action_def}
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
-%\begin{itemize}
-%\item[(1)]
-An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
-where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $I_\fg^{(0)} = I$.
-\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
-\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
-\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
-\end{itemize}
-%\item[(2)]
-%For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
-%An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
-%\[
-%Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
-%\]
-%is elliptic as a $C^\bu(\fg)$-linear differential operator.
-%\end{itemize}
+Let $(E, \omega, S)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, \omega, S)$ is an element 
+\[\fS_\fg = \sum_{k\geq 0} \fS_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
+of cohomological degree zero, where $\fS_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $\fS_\fg^{(0)} = S$.
+\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $\fS^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
+\item[(c)] $\fS_\fg$ satisfies the Maurer--Cartan equation:
+\[\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0.\]
+\end{itemize}
 \end{definition}
@@
 \begin{remark}
-We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
-One can also formulate actions of a Lie algebra on a classical theory in these terms. 
-The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
-\[
-\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
-\]
-is satisfied.
-\end{remark}
-
-\begin{remark}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $\fS_\fg$.
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + \{\fS_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 \label{group_action_def}
-Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory, and let $G$ be a supergroup acting on spacetime $M$.
-An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
+Let $(E, \omega, S)$ be a classical field theory, and let $G$ be a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, \omega, S)$ is given by the following data:
 \begin{itemize}
@@
 
-\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$ 
+\item An action $\fS_\fg$ of its super Lie algebra $\fg$ with $\fS^{(k)}_\fg = 0$ for $k\geq 2$ 
 \end{itemize}
@@
 \begin{itemize}
-\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, the differential $Q$ and the interaction term $I$.
-
-\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
+\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$ and the action functional $S$.
+
+\item For every $x\in\fg$, the vector field $X_{{\fS^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
 \end{itemize}
@@
 \subsection{From BRST to BV}
+
 We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.
-These data can be packaged into what's known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
+These data can be packaged into what is known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
 
@@
 \begin{itemize}
-\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\item A local formal moduli problem $\cM$ represented by a local $L_\infty$ algebra $L$.
+\item A local functional $S_{\mr{BRST}} \in \oloc(\cM)$ of polynomial degree $\geq 2$.
 \end{itemize}
@@
 \[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
-where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
+where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the local $L_\infty$ structure on $L$.
 \end{definition}
 
-We call $\cF$ the \defterm{space of BRST fields}.
+We call $L[1]$ the \defterm{space of BRST fields}.
 
 \begin{remark}
-In the most typical examples, the bundle $F$ is concentrated in $\ZZ$-degrees $-1$ and 0.
+In the most typical examples, the bundle $L[1]$ is concentrated in $\ZZ$-degrees $-1$ and 0.
 In this case, sections in degree 0 are thought of as physical fields, and ghosts -- sections in degree $-1$ -- are thought of as generators of the infinitesimal gauge symmetry.
@@
 
-From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
-Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
-
-First, we define the free BV theory.
-Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
-\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
-The underlying bundle of the BV theory is
-\[
-E = F \oplus F^! [-1].
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
-The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
-\]
-
-The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
-These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
-\[
-I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
-\] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
-\]
-
-\begin{lemma}
-Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
-\end{lemma}
-
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ as {\em the BV theory associated to the BRST theory} $\cF$.
-%and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. 
-In the case $S_{\mr{BRST}} = 0$ we refer to the associated BV theory as being of {\em cotangent type}, which we will denote by $T^*[-1] \cF$.
+Given a classical BRST theory, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
+Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
+Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
+
+\begin{definition}
+Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory.
+The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_g$.
+\end{definition}
 
 \begin{remark}
-In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
-Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
+It is common to refer to coordinates on $\cM$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\cM$ as \defterm{antifields}.
+Given a field $\phi$ the corresponding antifield will be denoted by $\phi^*$.
 \end{remark}
 
-If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
-\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-\brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.} \chris{I don't think we need to say this so precisely.
-I think it's enough to say that a homogeneous splitting $F = \bigoplus_i \Phi_i$ induces a splitting $F^!
-= \bigoplus_i \Phi_i^!$, and if we denote a general element of the summand $\Phi_i$ by $\phi$ then we will denote a general element of the summand $\Phi_i^!$ by $\phi^*$.}
-
-\subsection{Local Formal Moduli Problems} \label{sect:FMP}
-
-It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
-In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
-
-Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
-We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
-
-For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
-\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
-where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
-The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
-The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
-This important result will only serve as a motivation.
-
-Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
-\[L_{V, \fg}=\fg\oplus V[-1]\]
-with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
-\[V/\fg:= B L_{V, \fg}.\]
-
-\begin{example}
-If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
-\[T[n] B\fg = \fg[n+1] / \fg.\]
-\label{ex:tangentBg}
-\end{example}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
-Then $\fg^*$ is a coadjoint representation of $\fg$.
-We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
-\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
-\label{ex:cotangentBg}
-\end{example}
-
-\begin{definition}
-Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
-\end{definition}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
-Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
-For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
-\end{example}
-
-Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
-\[(B L)(U) = B L(U),\]
-i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
-
-\begin{definition}
-A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
-\end{definition}
-
-\begin{remark}
-In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
-It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
-\end{remark}
-
-\begin{example}
-Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
-Then we may define the following local formal moduli problem on $X\times Y\times M$.
-Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
-We may then consider a graded vector bundle
-\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
-on $X\times Y\times M$.
-It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
-It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
-We then define
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
-\label{ex:mappingspace}
-\end{example}
-
-\begin{remark}
-A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
-So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
-Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
-\end{remark}
-
-\begin{example}
-Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
-Moreover, assume $B\fg$ carries a $\Gm$-action.
-We then have a local $L_\infty$ algebra
-\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
-on $X\times Y\times M$. We define
-\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
-\end{example}
-
-As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
-
-\begin{lemma}
-Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
-The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
-\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
-where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
-\end{lemma}
-\begin{proof}
-The claim follows from the following isomorphisms of graded vector bundles:
-\begin{align*}
-\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
-\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
-\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
-\end{align*}
-\end{proof}
-
-Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper will only be interested in a strict notion as follows.
-
-\begin{definition}
-Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
-A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
-\begin{enumerate}
-\item It is fiberwise nondegenerate.
-\item It is graded skew symmetric.
-\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
-\[\alpha\otimes \beta \mapsto \int_M \omega (\alpha \otimes \beta)\]
-is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
-\end{enumerate}
-\end{definition}
-
-\begin{remark}
-A classical BV field theory as defined in Section \ref{sect:BV} is equivalent to the data of a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
-\end{remark}
-
 \subsection{Examples of Classical Field Theories}
 
-In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories.
-All theories we consider in this section are $\ZZ$-graded, i.e.
-the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.
+In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories. All theories we consider in this section are $\ZZ$-graded.
 
@@
 
-Our first example will generalize the fundamental example of \emph{BF theory} to a not entirely topological context.
+Our first example will generalize the fundamental example of the \emph{BF theory} to a not entirely topological context.
 Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an $L_\infty$ algebra $\fg$.
-The \defterm{generalized $BF$ theory} is the BV theory associated to the following BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-$F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-We denote the space of BV fields by $T^*[-1] \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg)$.
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized $BF$ theory} is the classical field theory
+\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg).\]
 \label{def:generalizedBF}
 \end{definition}
-
-\begin{remark} \label{mapping_stack_remark}
-The mapping stack above has a precise meaning in the language of derived algebraic geometry -- see for instance \cite{PTVV}, where, if $X, Y$ and $M$ are compact, such a mapping stack is shown to carry a $-1$-shifted symplectic structure.
-For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.
-The language of the mapping stack will simply be used as a compact way of referring to the theory above.
-\end{remark}
 
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the BV theory associated to the following BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
-$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the classical field theory
+\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, V).\]
 \end{definition}
-
-\begin{remark}
-This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure.
-\end{remark}
-
-We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.
-
-\begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\]
-with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
-where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}
 
@@
 Let $\fg$ be a dg Lie algebra, and consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ for Lie algebra $\fg$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
-Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
+\[\cE = T^*[-1]\map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
+Then it carries an action of $\U(n_1)\times \U(n_2)\times \mathrm{O}(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
 \label{prop:BFrotationaction}
@@
 \begin{remark}
-In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
+In fact, the $\mathrm{O}(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
 \end{remark}
@@
 We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-
-\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
-
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $\Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
-
-\item The interaction term is
-\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+The \defterm{generalized Chern--Simons theory} is the classical field theory
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg),\]
+whose underlying local $L_\infty$ algebra
+\[\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg\]
+is equipped with a cyclic structure coming from the nondegenerate pairing on $\fg$ and the wedge product of forms on $X\times Y\times M$.
 \label{def:generalizedCS}
@@
 We may also consider a $\ZZ/2\ZZ$-graded version of the above theory where $\fg$ is merely $\ZZ/2\ZZ$-graded.
+If we assume that $B\fg$ carries a $\Gm$-action, we may define the generalized Chern--Simons theory without choosing a holomorphic volume form on $X$ (see also \cite{GinzburgRozenblyum}).
+
+\begin{definition}
+Let $X,Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Fix an integer $m$ and suppose $X$ is equipped with an $m$-th root $K_X^{1/m}$.
+Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\oplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $m$ with respect to the grading.
+Then the generalized Chern--Simons theory is the classical field theory
+\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} K_X^{1/m}).\]
+\label{def:sectChernSimons}
+\end{definition}
 
@@
 \begin{example}
-If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term.
-The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$.
-Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
+Using Corollary \ref{cor:mapintocotangent} we have an isomorphism
+\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)\cong \map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[d-1]B\fg),\]
+so the generalized BF theory may be considered as a particular example of the generalized Chern--Simons theory.
 \label{ex:CSBF}
@@
 Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
-Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
-Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
-with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
-The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
-The space of fields in the corresponding Chern--Simons theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
+Suppose $\fg$ is a dg Lie algebra and $U$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $U\otimes U\rightarrow  \CC[d-1]$.
+Then we may consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, U \ham \fg).\]
 \label{ex:CSHamiltonianreduction}
-\brian{Will $V\ham \fg$ already be defined above in the FMP section?}
 \end{example}
-
-We will also sometimes use the following variant of the generalized Chern--Simons theory (see also \cite{GinzburgRozenblyum}).
-
-\begin{definition}
-Let $m$ be a positive integer.
-Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$.
-We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
-\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(n)\otimes K_X^{n/m} [1]\]
-and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
-\end{definition}
-
-We denote the space of fields $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.
 
@@
 Consider the setting of Example \ref{ex:CSHamiltonianreduction}.
-The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$.
-With respect to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
-\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
+The formal moduli problem $U\ham \fg$ carries a natural $\Gm$-action which acts on $U$ with weight $1$.
+With respect to this weight grading, the $(d-1)$-shifted symplectic structure on $U\ham \fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
+\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, U\ham \fg\times_{\Gm} K_X^{1/2}).\]
+We will also use the notation
+\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg)\]
+for the same theory.
 \end{example}
@@
 \begin{prop}
-Suppose $\fg$ is a dg Lie algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
+Suppose $\fg$ is a dg Lie algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$. Consider the generalized Chern--Simons theory
 \[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
@@
 
-We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle.
-We define the unitary metalinear group to be
+We may slightly enhance the previous proposition if we are in the setting of Definition \ref{def:sectChernSimons}. Define the unitary metalinear group to be
 \[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
@@
 \begin{prop}
-Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure.
-Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
-\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, (V\otimes K_{\CC^{n_1}}^{1/2})\ham\fg).\]
+Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure. Consider the generalized Chern--Simons theory
+\[\Sect(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, (U\otimes K_{\CC^{n_1}}^{1/2})\ham\fg).\]
 Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
@@
 
-\begin{example}
-There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
+%\begin{example}
+%There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
 This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.
 If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
-\end{example}
+%\end{example}
 
@@
 The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.
-The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.
+We define $\fg_{\mathrm{dR}}$ to be the value of $\fg_{\Hod}$ at $t=1$.
+Note that the underlying complex is contractible.
+
+\begin{remark}
+The terminology comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$ and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has a contractible tangent complex.
+\end{remark}
 
@@
 We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Hodge theory} is the $\CC[t]$-family of classical BV theories, as in Definition \ref{family_of_BV_theories_def}, given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
+The \defterm{generalized Hodge theory} is the $\CC[t]$-family of classical BV theories, as in Definition \ref{family_of_BV_theories_def}, given by the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod).\]
 \end{definition}
@@
 \begin{prop}
-The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
-%$\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
+The $t=0$ specialization of the generalized Hodge theory $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
 
@@
 \begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 
-\item The diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-is commutative.
-
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_M = S_N$.
 \end{itemize}
@@
 Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.
-In fact, when dimensional reduction makes sense, this groupoid is always contractible.
 
 \begin{prop}
-Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
-Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.
+Suppose $(E_M, \omega_M, S_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence.
+Then the groupoid of dimensional reductions of $(E_M, \omega_M, S_M)$ is either contractible or empty.
 
@@
 We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists.
-Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
+Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an equivalence between the category of graded vector bundles on $N$ and on $M$.
 In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
 
-Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
+Since $\cE_N\rightarrow \cE_M$ is injective, the condition $p^* S_M = S_N$ uniquely determines $S_N$.
 
 \textbf{Existence}.
-Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
+Now suppose $(E_M, \omega_M, S_M)$ is translation-invariant along the $\RR$ direction.
 Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
-Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
-The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
+Moreover, the restriction of $S_M$ under $\cE_N\hookrightarrow \cE_M$ is independent of the $\RR$ factor by translation invariance, so $S_N=p^* S_M$ is again a local functional.
 \end{proof}
@@
 
-We will now describe dimensional reductions of some of the previously discussed BV theories.
-Throughout this section we let $X$ and $Y$ be complex manifolds and $M$ be a smooth manifold. 
-We focus on BV theories described as formal mapping spaces whose sources are formal manifolds of the form 
-\begin{equation}\label{eqn: generalized}
-X \times Y_{\rm Dol} \times M_{\rm dR} .
-\end{equation}
-
-We first consider the case in which $M$ is of the form $M' \times \RR$ and we reduce along the projection
-\[
-p_{\rm dR} : X \times Y \times (M' \times \RR) \to X \times Y \times M' .
-\]
-In this case, we will only need to know the dimensional reduction of generalized Chern-Simons theory.
+We will now describe dimensional reductions of the classical Chern--Simons theory.
 
 \begin{prop} \label{CS_to_BF_diml_red_prop}
-Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the corresponding generalized Chern--Simons theory
-\[\map(X\times Y_{\mr{Dol}}\times (M'\times \RR)_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p_{\rm dR}$ is equivalent to the generalized BF theory
-\[
-T^*[-1] {\rm Map}(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, B\fg) .
-\]
-%\map(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
 \end{prop}
@@
 \begin{proof}
-To simplify the proof, we assume $X,Y,M'=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
-\[T^*[-1] \map(\pt, B \fg) = T^*[-1] B \fg\]
+To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
+\[\map(\pt, T^*[-1] B \fg)\]
 has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.
@@
 
-%\begin{corollary}
-%Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
-%\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
-%Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
-%\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
-%\label{cor:Hodgetopologicalreduction}
-%\end{corollary}
-
-Next, we consider dimensional reduction along a holomorphic direction. 
-First, we set up some notation.
+\begin{corollary}
+Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
+Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
+\label{cor:Hodgetopologicalreduction}
+\end{corollary}
 
 Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation.
-The symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e. a real volume form. 
+Recall that the symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e.
+a real volume form.
 We denote by $V=V_\RR\otimes_{\RR}\CC$ its complexification.
-Note that $V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$. 
-Also, since
+$V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$.
+Moreover, $V$ carries a complex volume form $\Omega_V$:
 \[\det(V)\cong \det(V_\RR)\otimes_{\RR}\CC\]
-the real volume form on $V_\RR$ determines a complex volume form on $V$.
-
-Complexification yields a group homomorphism
+and we use the real volume form on $V_\RR$.
+
+Functoriality of this construction gives a group homomorphism
 \begin{equation}
@@
 
-As in Equation (\ref{eqn: generalized}), we assume $X$ is a complex manifold of the form $X' \times V$ and consider the dimensional reduction along the map
-\[
-p_{\dbar} : (X' \times V) \times Y \times M \to X' \times Y \times (M \times V_\RR)
-\]
-induced by ${\rm Re} : V \to V_{\RR}$.
-
 \begin{prop} \label{CS_diml_red_prop}
-Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above.
-Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the generalized Chern--Simons theory
-\[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized Chern--Simons theory
-\[\map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
-The equivalence is $\SO(V_\RR)$-equivariant.
+Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above. Consider the generalized Chern--Simons theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
 \end{prop}
 \begin{proof}
-We may assume $X',Y,M=\pt$ as in the previous proof.
+We may assume $X,Y,M=\pt$ as in the previous proof.
 
@@
 
-As a corollary of this result we obtain the reduction of generalized Hodge theory.
-
 \begin{corollary}
-Let $X', Y, M, V_\RR, V$ be as before. 
-Fix an $L_\infty$ algebra equipped with a non-degenerate pairing as in Definition \ref{Hodge_family_def} and consider the generalized Hodge theory
-\[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
-Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized Hodge theory
-\[\map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
-The equivalence is $\SO(V_\RR)$-equivariant.
+Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg).\]
+
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized BF theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, T^*[d] B\fg).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
+\label{cor:BFholomorphicreduction}
+\end{corollary}
+
+\begin{corollary}
+Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
+\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
+
+Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Hodge theory
+\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
+The isomorphism is moreover $\SO(V_\RR)$-equivariant.
 \label{cor:Hodgeholomorphicreduction}
 \end{corollary}
-
-By essentially the same argument as in the proof of Proposition \ref{CS_diml_red_prop}, we obtain the reduction of generalized BF theory.
-
-\begin{prop}
-Let $X', Y, M, V_\RR, V$ be as before. 
-Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
-\[T^*[-1] \map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
-Its dimensional reduction along the projection $p_{\dbar}$ is equivalent to the generalized BF theory
-\[T^*[-1] \map(X'\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
-This equivalence is $\SO(V_\RR)$-equivariant.
-\label{prop:BFholomorphicreduction}
-\end{prop}
-
-Finally, we take $Y$ to be a complex manifold of the form $Y' \times \CC$, where $V$ is complex $k$-dimensional and consider the projection
-\[
-p_{\rm Dol} : X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
-\]
-induced by ${\rm Re} : \CC \to \RR$.
-
-\begin{prop}
-\label{prop:BFdolbeaultreduction}
-Let $X, M, Y'$ be as above.
-Fix an $L_\infty$ algebra $\fg$ and consider the generalized $BF$ theory
-\[
-T^*[-1] {\rm Map}(X \times (Y' \times \CC)_{\rm Dol} \times M_{\rm dR} , B \fg) .
-\]
-Its dimensional reduction along $p_{\rm Dol}$ is equivalent to the generalized BF theory
-\[
-T^*[-1] {\rm Map} (X \times Y'_{\rm Dol} \times (M \times \RR)_{\rm dR}, \fg / \fg)
-\]
-This equivalence is $\SO(V_\RR)$-equivariant.
-\end{prop}
-\begin{proof}
-Note that there is an isomorphism of $L_\infty$ algebras
-\[
-\Omega^{\bu, \bu} (Y' \times \CC ; \fg) = \Omega^{\bu,\bu}(Y') \otimes \Omega^{0,\bu}(\CC) \otimes \fg[\epsilon]
-\]
-where $\epsilon$ is a parameter of degree $+1$.
-The result then follows from Proposition \ref{prop:BFholomorphicreduction} applied to the $L_\infty$ algebra $\fg[\epsilon]$. 
-\end{proof}
 
@@
 
-In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing, which should be thought of as the complexified Lie algebra of the gauge group.
+In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing which should be thought of as the complexified Lie algebra of the gauge group.
 
@@
 Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant.
-By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
-\end{proof}
-
-The 7-dimensional result immediately follows.
+By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
+\end{proof}
+
+We will now concentrate on the 7-dimensional case.
 
@@
 
-The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
+The claim about the underlying $\ZZ/2\ZZ$-graded $\MU(2)$-equivariant theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 5d $\cN=1$ super Yang--Mills theory (Theorem \ref{thm:5dminimaltwist}).
 
@@
 
-%\begin{proof}
-%We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
-%\begin{align*}
-%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-%\end{align*}
-%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-%\begin{align*}
-%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-%\end{align*}
-%
-%The next step is to decompose the $(1,1)$ form $\psi$ as
-%\[
-%\psi = \omega \Lambda \psi + \psi_{\perp}
-%\]
-%where $\Lambda \psi_{\perp} = 0$. 
-%
-%\end{proof}
+\begin{proof}
+We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
+\begin{align*}
+& (t \varsigma, \rho, t \phi, A_{1,0}) \\
+& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
+\end{align*}
+This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
+\begin{align*}
+\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
+\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
+\end{align*}
+
+The next step is to decompose the $(1,1)$ form $\psi$ as
+\[
+\psi = \omega \Lambda \psi + \psi_{\perp}
+\]
+where $\Lambda \psi_{\perp} = 0$.
+
+\end{proof}
 
@@
 \item
-An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$. and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item
@@
 \begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
-Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
+A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an A-twisting supercharge in 3d $\mc N=4$.
+Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a B-twisting supercharge in 3d $\mc N=4$.
 \end{lemma}
@@
 \begin{proof}
-Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
 The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.
+Here $W_4$ is the $d=4$ auxiliary space, with dimension 2.
 This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$.
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
-This is the $A$-twist in our classification above.
-%-- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$ -- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
 
 A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
-This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.
+This subspace has the opposite orientation, so corresponds to the B-twist in our classification above.
 \end{proof}
@@
 Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
-%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
-Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
-
-\begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
-Moreover, the equivalence is $\U(1)$-equivariant.
-\end{theorem}
-
-\begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
-This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
-\end{proof}
-
-\subsubsection{Topological $A$-Twist}
+\end{proof}
+
+\begin{remark}
+\brian{Cotangent type.}
+\end{remark}
+
+\subsubsection{Topological A Twist}
 \label{sect:3d_4_A_twist}
@@
 
-\subsubsection{Topological $B$-Twist}
+\subsubsection{Topological B Twist}
 \label{sect:3d_4_B_twist}
@@
 \begin{theorem}  \label{3d_8_minimal_twist_thm}
-The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$.
 Moreover, the equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
-By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to the desired generalized BF theory.
-\end{proof}
-
-%\begin{proof}
-%On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
+On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
 We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.
@@
 When we calculate that dimensional reduction, the fields reduce according to the rule
-%\begin{align*}
-%\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
-%&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
-%\end{align*}
-%Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
-%\end{proof}
-
-\subsubsection{Topological $A$-Twist}
+\begin{align*}
+\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
+&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
+\end{align*}
+Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
+\end{proof}
+
+\subsubsection{Topological A Twist}
 \label{sect:3d8A_Twist}
@@
 
-\begin{corollary}
-The topological $A$-twist of 3d $\cN=8$ super Yang-Mills is perturbatively trivial.
-\end{corollary}
-
-\subsubsection{Topological $B$-Twist}
+\subsubsection{Topological B Twist}
 \label{sect:3d8B_Twist}

### 2020-02-13 paper.tex

--- 2020-02-13 paper.tex
@@
 Finally, we have yet another version, a \emph{holomorphic BF theory}, with the space of BV fields $\Omega^{0, \bullet}(X; \fg)[1]\oplus \Omega^{\dim(X), \bullet}(X; \fg^*)[\dim(X)-2]$, again equipped with the Dolbeault differential.
-We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMP}).
+We will denote the space of fields in these three examples as $T^*[-1]\map(M_{\mathrm{dR}}, B\fg)$, $T^*[-1]\map(X_{\mathrm{Dol}}, B\fg)$ and $T^*[-1]\map(X, B\fg)$ respectively (the notation is explained in Section \ref{sect:FMPs}).
 We may also combine these three examples into what we call a \emph{generalized BF theory} with the spaces of fields $T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ (see Definition \ref{def:generalizedBF} for more details).
@@
 
-\subsection{Classical BV Theories} \label{sect:BV}
-
-The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
-In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
-That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.
-The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
+\subsection{Formal Moduli Problems and Classical Field Theories}
+\label{sect:FMPs}
+
+It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
+In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
+
+Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
+We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
+
+For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
+\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
+where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
+The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
+The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
+This important result will only serve as a motivation.
+
+Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
+\[L_{V, \fg}=\fg\oplus V[-1]\]
+with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
+\[V/\fg:= B L_{V, \fg}.\]
+
+\begin{example}
+If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
+\[T[n] B\fg = \fg[n+1] / \fg.\]
+\label{ex:tangentBg}
+\end{example}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
+Then $\fg^*$ is a coadjoint representation of $\fg$.
+We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
+\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
+\label{ex:cotangentBg}
+\end{example}
 
 \begin{definition}
-A \defterm{free BV theory} on a manifold $M$ is the data of:
-\begin{itemize}
-\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
-\[
-Q_{\mr{BV}} \colon \cE \to \cE [1] 
-\]
-such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
-\item a map of bundles
-\[
-\omega\colon E \otimes E \to \Dens_M [-1]
-\]
-that is
+Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
+\end{definition}
+
+\begin{example}
+Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
+Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
+For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
+\end{example}
+
+\begin{example}
+Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-represntation equipped with an $n$-shifted symplectic structure $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
+\[\fh = \fg\oplus U[-1]\oplus \fg^*[n-2]\]
+with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes U\rightarrow U$ given by the $\fg$-action on $U$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon U\otimes U\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_U$.
+The dg Lie algebra $\fh$ carries nondegenerate invariant symmetric pairing of cohomological degree $n-2$ given by pairing $\fg$ and $\fg^*$ and pairing $U$ with itself.
+We denote
+\[U\ham \fg := B\fh.\]
+This formal moduli problem is equipped with a $\Gm$-action where $\fg$ has weight 0, $U[-1]$ has weight $1$ and $\fg^*[n-2]$ has weight $2$.
+This may be thought of as an infinitesimal version of the Hamiltonian reduction of $U$ by the $\fg$-action.
+\end{example}
+
+Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
+\[(B L)(U) = B L(U),\]
+i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
+
+\begin{definition}
+A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
+\end{definition}
+
+\begin{remark}
+In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
+It is only relevant for quantization which we do not consider in this paper, so for simplicity we will not require ellipticity (though in fact all examples we consider will end up being elliptic).
+\end{remark}
+
+Given a local formal moduli problem $\cM=B L$, we may consider the space of local functionals which is defined as
+\[\oloc(\cM) := \oloc(\cL[1]).\]
+The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg diffrential on $\oloc(\cM)$.
+
+\begin{example}
+Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
+Then we may define the following local formal moduli problem on $X\times Y\times M$.
+Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
+We may then consider a graded vector bundle
+\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
+on $X\times Y\times M$.
+It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
+It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
+We then define
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
+\label{ex:mappingspace}
+\end{example}
+
+\begin{remark}
+A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
+So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
+Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
+\end{remark}
+
+\begin{example}
+Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
+Moreover, assume $B\fg$ carries a $\Gm$-action.
+We then have a local $L_\infty$ algebra
+\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
+on $X\times Y\times M$. We define
+\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
+\end{example}
+
+As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
+
+\begin{prop}
+Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
+The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
+\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
+where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
+\end{prop}
+\begin{proof}
+The claim follows from the following isomorphisms of graded vector bundles:
+\begin{align*}
+\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
+\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
+\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
+\end{align*}
+\end{proof}
+
+\begin{cor}
+Suppose $X,Y,M,\fg$ are as in Example \ref{ex:mappingspace} and, moreover, $X$ is equipped with a holomorphic volume form and $M$ is oriented. Then
+\[T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)\cong \map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg).\]
+\label{cor:mapintocotangent}
+\end{cor}
+
+Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper we will only be interested in a strict notion as follows.
+
+\begin{definition}
+Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
+A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
 \begin{enumerate}
-\item[$(1)$] fiberwise nondegenerate,
-\item[$(2)$] graded skew symmetric, and
-\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\item It is fiberwise nondegenerate.
+
+\item It is graded skew symmetric.
+
+\item The pairing
+\begin{align*}
+\cL_c\otimes \cL_c&\rightarrow \CC \\
+\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
+\end{align*}
+is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
 \end{enumerate}
-\end{itemize}
 \end{definition}
 
-We call $\cE$ the \defterm{space of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}.
-The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook})
-\[
-\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
-\]
-This bracket is of cohomological degree $+1$. 
-This bracket is a graded version of the so-called Soloviev bracket \cite{Soloviev} defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.
-
-We explain how to define the BV bracket in our context.  
-First note that there is a linear map
+Given a local formal moduli problem $\cM = BL$ equipped with a strict $n$-shifted symplectic structure, the space of local functionals $\oloc(\cM)$ is equipped with a Poisson bracket (see \cite[Chapter 5.3]{CostelloBook})
+\[
+\{-,-\}\colon \oloc(\cM) \times \oloc(\cM) \to \oloc(\cM)[-n]
+\]
+This bracket is a graded version to the so-called Soloviev bracket \cite{Soloviev} defined on the $\infty$-jets, as described in \cite[Section 4]{GetzlerBracket}.
+
+We explain how to define the Poisson bracket in our context. Write $E = L[1]$ for convenience. First note that there is a linear map
 \[
@@
 
-Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
-\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
-the BV action of the theory.
-
-The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]
-
-In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $(Q_{\mr{BV}}, I)$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
-The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
-
-Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead of the quadruple$(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.
-
-\begin{remark}
-We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
-\end{remark}
-
-\begin{remark}
-The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e.
-a symplectic isomorphism $L\cong L^![-3]$ \cite[Chapter 5.4]{Book2}.
-\end{remark}
-
-We will also sometimes consider $\CC[t]$-families of classical field theories.  These will be defined as follows.
+Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}.
+Moreover, we call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}.
+It will be convenient to think of a classical field theory as a triple $(E, \omega, S)$ of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$ and an action functional $S$.
+
+\begin{example}
+Let $\cM=BL$ be a local formal moduli problem.
+Then the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ carries a natural $(-1)$-shifted symplectic structure.
+Indeed, $T^*[-1]\cM = B(L\oplus L^![-3])$ and we simply pair $L$ and $L^!$.
+Classical field theories arising via this construction are called of \defterm{cotangent type}.
+\end{example}
+
+%The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
+In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
+That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
+The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
+
+We will also consider $\CC[t]$-families of classical field theories.
 \begin{definition} \label{family_of_BV_theories_def}
-A $\CC[t]$-family of classical BV theories is a quadruple $(E,Q_{\mr{BV}}, \omega, I)$ as before, but where now the classical BV differential is $t$-dependent.  In other words, it is given as a map
-\[Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1],\]
-where, for each $t_0 \in \CC$, the quadruple $(E,Q^{t_0}_{\mr{BV}}, \omega, I)$
-\[Q^{t_0}_{\mr{BV}} = \mr{ev}_{t_0} \circ Q_{\mr{BV}} \colon \cE \to \cE  \otimes \CC[t] [1] \to \cE[1]\]
-defines a classical field theory.
+A \defterm{$\CC[t]$-family of classical field theories} is a graded bundle of locally-free $\CC[t]$-modules $L$ on $M$ equipped with a structure of a $\CC[t]$-linear local $L_\infty$ algebra and a $\CC[t]$-linear $(-1)$-shifted symplectic structure $\omega\colon L\otimes_{\CC[t]} L\rightarrow \CC[t]\otimes \Dens_M[-3]$.
 \end{definition}
+
+We will consider $\CC[t]$-families of classical field theories where $L = \CC[t]\otimes L_0$ and the pairing
+\[\omega\colon L\otimes_{\CC[t]} L\rightarrow \CC[t]\otimes \Dens_M[-3]\]
+comes from a pairing
+\[\omega_0\colon L_0\otimes L_0\rightarrow \Dens_M[-3].\]
+In this case the local $L_\infty$ structure is encoded in a $t$-dependent action functional $S$.
+
+Besides the $\ZZ$-graded classical field theories defined above, we may consider the following variants of the above definition:
+\begin{itemize}
+\item A $\ZZ\times \ZZ/2\ZZ$-graded local $L_\infty$ algebra is a $\ZZ$-graded local $L_\infty$ algebra $L$ equipped with an extra $\ZZ/2\ZZ$-grading (the \defterm{fermionic grading}) with respect to which all operations are even.
+An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$ which is even with respect to the fermionic grading.
+
+\item A $\ZZ/2\ZZ$-graded classical field theory is defined in the same way as a $\ZZ$-graded classical field theory where we only consider the cohomological grading modulo 2.
+\end{itemize}
+
+\subsection{Perturbative Equivalence of Classical Field Theories}
 
@@
 \begin{definition}
+A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwines the pairings $\omega, \omega'$ and defines an $L_\infty$ map $\cE_c[-1]\rightarrow \cE'_c[-1]$.
+A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon \cE\rightarrow \cE'$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying our descriptions of twisted theories.
-First, we consider the process of integrating out an auxiliary field.
+We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. 
+First, we consider the process of eliminating an auxiliary field.
 
@@
 where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
-Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where the equivalence sets $\phi = S_1$ and $\phi^* = 0$.
+Then the theory $(E, \omega, S)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
 \end{prop}
-
-\begin{remark}
-In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
-\[\xymatrix{
-\cdots & \ul{0} & \ul{1} & \cdots \\
-\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
-}\]
-where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
-\end{remark}
-
 \begin{proof}
@@
 In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion).
-Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and let $\fg$ be a super Lie algebra.
-We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
-We begin by defining an appropriate version of the Chevalley-Eilenberg cochain complex.
+Let $(E, \omega, S)$ be a classical field theory and $\fg$ a super Lie algebra.
+We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.
+We begin by defining an appropriate version of the Chevalley--Eilenberg cochain complex.
 
 \begin{definition}
-The \defterm{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
+The \defterm{Chevalley--Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, is defined as follows.  Consider the graded vector space
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
@@
 We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.
-These data can be packaged into what's known as a BRST theory, where fermionic fields (referred to as ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
+These data can be packaged into what is known as a BRST theory, where fermionic fields (referred to as ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.
 
@@
 \begin{itemize}
-\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$.
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
+\item A local formal moduli problem $\cM$ represented by a local $L_\infty$ algebra $L$.
+\item A local functional $S_{\mr{BRST}} \in \oloc(\cM)$ of polynomial degree $\geq 2$.
 \end{itemize}
@@
 
-From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows.
-Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.
-
-First, we define the free BV theory.
-Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
-\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
-The underlying bundle of the BV theory is
-\[
-E = F \oplus F^! [-1].
-\]
-The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.  The differential of the free BV theory is
-\[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
-\]
-
-The interacting theory is constructed as follows.
-First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$.
-These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
-\[
-I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
-\] 
-which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
-\[
-I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
-\]
-
-\begin{lemma}
-Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
-\end{lemma}
-
-We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ as {\em the BV theory associated to the BRST theory} $\cF$.
-In the case where $S_{\mr{BRST}} = 0$ we refer to the associated BV theory as being of {\em cotangent type}, which we will denote by $T^*[-1] \cF$.
+Given a classical BRST theory, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
+Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
+Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
+
+\begin{definition}
+Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory.
+The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_g$.
+\end{definition}
 
 \begin{remark}
-In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
-Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
+It is common to refer to coordinates on $\cM$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\cM$ as \defterm{antifields}.
+Given a field $\phi$ the corresponding antifield will be denoted by $\phi^*$.
 \end{remark}
 
-If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
-\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
-\brian{Looks like you're using a bracket we haven't defined. 
-We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.} \chris{I don't think we need to say this so precisely.
-I think it's enough to say that a homogeneous splitting $F = \bigoplus_i \Phi_i$ induces a splitting $F^!
-= \bigoplus_i \Phi_i^!$, and if we denote a general element of the summand $\Phi_i$ by $\phi$ then we will denote a general element of the summand $\Phi_i^!$ by $\phi^*$.}
-
-\subsection{Local Formal Moduli Problems} \label{sect:FMP}
-
-It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
-In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
-
-Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition.
-We refer to \cite{DAGX,PridhamFMP,Toen} for more details.
-
-For instance, if $\fg$ is a complex $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
-\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
-where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements.
-The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems.
-The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
-This important result will only serve as a motivation.
-
-Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
-\[L_{V, \fg}=\fg\oplus V[-1]\]
-with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
-\[V/\fg:= B L_{V, \fg}.\]
-
-\begin{example}
-If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
-\[T[n] B\fg = \fg[n+1] / \fg.\]
-\label{ex:tangentBg}
-\end{example}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces.
-Then $\fg^*$ is a coadjoint representation of $\fg$.
-We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
-\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
-\label{ex:cotangentBg}
-\end{example}
-
-\begin{definition}
-Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \bigoplus_{m \in \ZZ} \fg(m)$ compatible with the $L_\infty$ structure.
-\end{definition}
-
-\begin{example}
-Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation.
-Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$.
-For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
-\end{example}
-
-Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
-\[(B L)(U) = B L(U),\]
-i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
-
-\begin{definition}
-A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
-\end{definition}
-
-\begin{remark}
-In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
-It is only relevant for quantization which we do not consider in this paper, so for simplicity we will not require ellipticity (though in fact all examples we consider will end up being elliptic).
-\end{remark}
-
-\begin{example}
-Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by a complex $L_\infty$ algebra $\fg$.
-Then we may define the following local formal moduli problem on $X\times Y\times M$.
-Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$.
-We may then consider a graded vector bundle
-\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
-on $X\times Y\times M$.
-It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$.
-It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms.
-We then define
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
-\label{ex:mappingspace}
-\end{example}
-
-\begin{remark}
-A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}.
-So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
-\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
-If $F = BG$ is the classifying stack of a complex algebraic group, the mapping stack $\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, BG)$ has a natural geometric interpretation: its closed points correspond to algebraic principal $G$-bundles $P$ on $X \times Y \times M$, with a Higgs field on each slice $P|_{\{x\} \times Y \times \{m\}}$ and a flat connection on each slice $P|_{\{x\} \times \{y\} \times M}$.
-Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems, and can be thought of as modelling the formal neighborhood of the trivial bundle in this moduli stack.
-\end{remark}
-
-\begin{example}
-Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$.
-Moreover, assume $B\fg$ carries a $\Gm$-action.
-We then have a local $L_\infty$ algebra
-\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
-on $X\times Y\times M$. We define
-\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
-\end{example}
-
-As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.
-
-\begin{lemma}
-Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}.
-The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
-\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
-where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
-\end{lemma}
-\begin{proof}
-The claim follows from the following isomorphisms of graded vector bundles:
-\begin{align*}
-\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
-\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
-\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
-\end{align*}
-\end{proof}
-
-Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper will only be interested in a strict notion as follows.
-
-\begin{definition}
-Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$.
-A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
-\begin{enumerate}
-\item It is fiberwise nondegenerate.
-\item It is graded skew symmetric.
-\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
-\[\alpha\otimes \beta \mapsto \int_M \omega (\alpha \otimes \beta)\]
-is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
-\end{enumerate}
-\end{definition}
-
-\begin{remark}
-A classical BV field theory as defined in Section \ref{sect:BV} is equivalent to the data of a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
-\end{remark}
-
 \subsection{Examples of Classical Field Theories}
 
-In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories.
-All theories we consider in this section are $\ZZ$-graded, i.e.
-the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.
+In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories. All theories we consider in this section are $\ZZ$-graded.
 
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth oriented manifold.
-Fix a complex $L_\infty$ algebra $\fg$.
-The \defterm{generalized $BF$ theory} is the BV theory associated to the following BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-The shift $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.
-
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
-We denote the space of BV fields by $T^*[-1] \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg)$.
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized $BF$ theory} is the classical field theory
+\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg).\]
 \label{def:generalizedBF}
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth manifold.
-Fix a complex vector space $V$.
-The \defterm{generalized $\beta\gamma$ system} valued in $V$ is the BV theory associated to the following BRST theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$.
-$F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.
-\item The BRST action is $S_{\mr{BRST}} = 0$.
-\end{itemize}
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the classical field theory
+\[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, V).\]
 \end{definition}
-
-\begin{remark}
-This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure.
-\end{remark}
-
-We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.
-
-\begin{example}
-Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\]
-with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$.
-The space of fields in the corresponding generalized BF theory will be denoted using the formal moduli problem notation  as
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
-where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-\end{example}
 
@@
 \begin{definition}
-\label{dfn: cs}
-Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth oriented manifold.
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
 Fix an $L_\infty$ algebra $\fg$.
-We assume that $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and that $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
-The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
-\begin{itemize}
-\item The spacetime is the smooth manifold $X\times Y\times M$.
-
-\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.
-
-\item $Q_{\mr{BV}} = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.
-
-\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $\Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.
-
-\item The interaction term is
-\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
-\end{itemize}
-We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
+We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$.
+The \defterm{generalized Chern--Simons theory} is the classical field theory
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg),\]
+whose underlying local $L_\infty$ algebra
+\[\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg\]
+is equipped with a cyclic structure coming from the nondegenerate pairing on $\fg$ and the wedge product of forms on $X\times Y\times M$.
 \label{def:generalizedCS}
@@
 Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$.
-Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$.
-Consider the dg Lie algebra
-\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
-with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$.
-The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself.
-The space of fields in the corresponding Chern--Simons theory will be denoted by
-\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
+Suppose $\fg$ is a dg Lie algebra and $U$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $U\otimes U\rightarrow  \CC[d-1]$.
+Then we may consider the generalized Chern--Simons theory
+\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, U \ham \fg).\]
 \label{ex:CSHamiltonianreduction}
@@
 
-We will also sometimes use the following variant of the generalized Chern--Simons theory (see also \cite{GinzburgRozenblyum}).
-
-\begin{definition}
-Let $m$ be a positive integer.
-Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$.
-We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
-\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(n)\otimes K_X^{n/m} [1]\]
-and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
-\end{definition}
-
-We denote the space of fields by $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.
-
 \begin{example}
 Consider the setting of Example \ref{ex:CSHamiltonianreduction}.
-The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$.
-With respect to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
-\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
+The formal moduli problem $U\ham \fg$ carries a natural $\Gm$-action which acts on $U$ with weight $1$.
+With respect to this weight grading, the $(d-1)$-shifted symplectic structure on $U\ham \fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
+\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, U\ham \fg\times_{\Gm} K_X^{1/2}).\]
+We will also use the notation
+\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg)\]
+for the same theory.
 \end{example}
@@
 \begin{prop}
-The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
-%$\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
-
+The $t=0$ specialization of the generalized Hodge theory $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory $T^*[-1]\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
 The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
@@
 \begin{definition}
-We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
+We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
 \begin{itemize}
@@
 We begin by showing that any two dimensional reductions are isomorphic and moreover that such an isomorphism is unique if it exists.
-Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$.
+Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an equivalence between the category of graded vector bundles on $N$ and on $M$.
 In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.
 
-Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
-\[
-\xymatrix{
-\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
-\cE_M \ar^{Q_M}[r] & \cE_M[1]
-}
-\]
-uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.
+Since $\cE_N\rightarrow \cE_M$ is injective, the condition $p^* S_M = S_N$ uniquely determines $S_N$.
 
 \textbf{Existence}.
-Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction.
+Now suppose $(E_M, \omega_M, S_M)$ is translation-invariant along the $\RR$ direction.
 Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$.
-Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$.
-The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
+Moreover, the restriction of $S_M$ under $\cE_N\hookrightarrow \cE_M$ is independent of the $\RR$ factor by translation invariance, so $S_N=p^* S_M$ is again a local functional.
 \end{proof}
@@
 \begin{prop} \label{CS_to_BF_diml_red_prop}
-Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the corresponding generalized Chern--Simons theory
+Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{def:generalizedCS} and consider the corresponding generalized Chern--Simons theory
 \[\map(X\times Y_{\mr{Dol}}\times (M'\times \RR)_{\mr{dR}}, B\fg).\]
@@
 \[
-p_{\dbar} : (X' \times V) \times Y \times M \to X' \times Y \times (M \times V_\RR)
-\]
-induced by ${\rm Re} : V \to V_{\RR}$.
+p_{\dbar}\colon (X' \times V) \times Y \times M \to X' \times Y \times (M \times V_\RR)
+\]
+induced by ${\rm Re}\colon V \to V_{\RR}$.
 
@@
 Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above.
-Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{dfn: cs} and consider the generalized Chern--Simons theory
+Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing as in Definition \ref{def:generalizedCS} and consider the generalized Chern--Simons theory
 \[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
@@
 \textsc{Institut f\"ur Mathematik, Universit\"at Z\"urich}\\
-\textsc{Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}\\
+\textsc{Winterthurerstrasse 190, 8057 Zurich, Switzerland}\\
 \texttt{pavel.safronov@math.uzh.ch}\\

### 2020-02-13 paper.tex
Brian's many papers
reconciling

@@
  \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge Lie algebra $\fg$ (16 supercharges).}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}
  \label{table_of_twists_16}
@@
 
-It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces.
-In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.
+The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
+In brief, the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
+That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.
+The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$ as a formal moduli problem.
 
@@
 where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
+\label{prop:mapintocotangent}
 \end{prop}
@@
 
-\item The pairing
-\begin{align*}
-\cL_c\otimes \cL_c&\rightarrow \CC \\
-\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
-\end{align*}
+\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
+\[\alpha\otimes \beta \mapsto \int_M \omega( \alpha, \beta)\]
 is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
@@
 
-Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}.
-Moreover, we call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}.
-It will be convenient to think of a classical field theory as a triple $(E, \omega, S)$ of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$ and an action functional $S$.
-
-\begin{example}
+Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}.
+We call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}.
+It will be convenient to think of a classical field theory as a quadruple $(E, \omega, Q_{\mr{BV}}, I)$ consisting of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$, a classical BV differential $Q_{\mr{BV}}$ and an interaction functional $I$.
+We characterize such data in the following way.
+
+\begin{definition}
+A \defterm{free BV theory} on a manifold $M$ is the data of:
+\begin{itemize}
+\item a finite rank graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
+\[
+Q_{\mr{BV}} \colon \cE \to \cE [1] 
+\]
+such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
+\item a map of bundles
+\[
+\omega\colon E \otimes E \to \Dens_M [-1]
+\]
+that is
+\begin{enumerate}
+\item[$(1)$] fiberwise nondegenerate,
+\item[$(2)$] graded skew symmetric, and
+\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
+\end{enumerate}
+\end{itemize}
+\end{definition}
+
+The datum of a classical BV field theory as in Definition \ref{def:classicalfieldtheory} is equivalent to the datum of a free BV theory $(E, Q, \omega)$ equipped with an even functional
+\[I \in \oloc^+(\cE)\]
+of cohomological degree zero satisfying the Maurer-Cartan equation
+\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0,\]
+under the identification of the BV action as
+\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E).\]
+
+\begin{example} \label{def:cotangent_type}
 Let $\cM=BL$ be a local formal moduli problem.
@@
 
-%The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.
-In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.
-That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.
-The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.
-
 We will also consider $\CC[t]$-families of classical field theories.
@@
 
+\begin{remark}
 Besides the $\ZZ$-graded classical field theories defined above, we may consider the following variants of the above definition:
@@
 \end{itemize}
+\end{remark}
 
@@
 We may also eliminate pairs of fields as follows.
-
-% \begin{prop}
-% Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$.
-Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$.
-Suppose
-% \[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
-% where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$.
-Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
-% \end{prop}
 
@@
 
-%The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
-%\[
-%(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
-%\]
-%where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
-%The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
-%Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
+The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
+\[
+(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
+\]
+where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
+The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$.
+Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.
 This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.
@@
 
+\begin{remark}
+We have seen that a classical BV theory can also be presented in terms of a BV differential $Q_{\mr{BV}}$ and an interaction $I$ satisfying the Maurer-Cartan equation
+\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
+One can also formulate actions of a Lie algebra on a classical theory in these terms. 
+The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local interaction functional 
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
+satisfying the Maurer-Cartan equation
+\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
+\end{remark}
+
 We may also define actions of supergroups on classical field theories.
@@
 \end{definition}
+
+In the case where $S_{\mr{BRST}} = 0$, the associated BV theory is of cotangent type, as in Example \ref{def:cotangent_type}.
+
+\begin{remark}
+In general, multiple BRST theories can give rise to the same BV theory.
+A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
+Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
+\end{remark}
 
@@
 
+\begin{example}
+There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWSuperconformal} which is the theory
+\[\Sect(\CC, (U\otimes K_\CC^{1/2})\ham\fg).\]
+For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
+\[T^*[-1] \map(\CC, R / \fg)\]
+by Proposition \ref{prop:mapintocotangent}.
+\end{example}
+
 As with generalized BF theory, generalized Chern--Simons theory carries a natural rotation action by linear automorphism groups of spacetime.
@@
 \end{prop}
-
-%\begin{example}
-%There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWchar}.
-This is the case when $n_1 = 1$, $n_2 = n_3 = 0$, so $V$ is a $\fg$ representation with an ordinary symplectic structure.
-If $V = T^*R$, we are considering the classical cotangent field theory whose classical solutions to the equations of motion model the cotangent bundle to $G$-bundles on a Riemann surface with a section of the associated bundle to $R$.
-%\end{example}
 
@@
 
-%The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by its defining representation.
-
 \vspace{-10pt}
@@
 This is the $A$-twist in our classification above.
-%-- if $G_R = \SL(2;\CC)_+ \times \SL(2;\CC)_-$ where the first factor is the 4d R-symmetry group, by a $\mr U(1)$ in the second factor -- so this is the A-twist in our classification above.
 
@@
 \end{remark}
-
-% \cN=(0,8) Super Yang-Mills with matter
 

### 2020-02-14 paper.tex
10d-6d intro edits

@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ holomorphic twist.} The unique twisted super Yang-Mills theory in 10 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to 5d holomorphic Chern-Simons theory.
-It is $\SU(5)$ invariant, and can be defined on a Calabi-Yau 5-fold.
+ \item \emph{$\mc N=(1,0)$ holomorphic twist.} The unique twisted super Yang--Mills theory in 10 dimensions is equivalent to the 5d holomorphic Chern--Simons theory defined on a Calabi--Yau 5-fold.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
 This twist was first studied by Baulieu \cite{Baulieu}.
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang-Mills theory in 9 dimensions is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory with one topological direction and four holomorphic directions.
-It is $\SU(4)$-invariant, and can be defined on the product of a Calabi-Yau 4-fold and a flat 1-manifold (i.e.
-$\RR$ or $\RR/\ZZ$).
+ \item \emph{$\mc N=1$ minimal twist.} The unique twisted super Yang--Mills theory in 9 dimensions is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 4-fold and a real 1-manifold.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
+Its classical solutions are $G$-bundles holomorphic along the Calabi--Yau manifold and flat along the 1-manifold.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ holomorphic twist.} Super Yang-Mills theory in 8 dimensions admits three classes of twist.
-The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of BF theory.
-This theory is $\mr U(4)$-invariant, and can be defined on arbitrary complex 4-folds.
- \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist by a rank 1 impure spinor, which is topological in two directions and holomorphic in the remaining three complex directions.
-This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
-It is $\SU(3) \times \Spin(2;\RR)$-invariant, and can be defined on the product of a Calabi-Yau 3-fold and a Riemann surface.
- \item \emph{$\mc N=1$ topological twist.}  There is, finally, a novel topological twist in 8-dimensions, which does not arise via dimensional reduction from the theories above.
+ \item \emph{$\mc N=1$ holomorphic twist.} Super Yang--Mills theory in 8 dimensions admits three classes of twists.
+The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
+ \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor.
+This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
+ \item \emph{$\mc N=1$ topological twist.} The holomorphic twist also admits a deformation to a topological twist defined on $\spin(7)$-manifolds.
 This theory is perturbatively trivial, in the sense that the classical BV complex is contractible.
-It can, however, be realised as the generic point in a 1-parameter degeneration of the holomorphic twist.
-This theory is $\spin(7;\RR)$-invariant, although the full one-parameter family is only $\SU(4)$-invariant.
-This theory was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}; its equations of motion include the $\spin(7)$-instanton equation.
+It was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}.
+The partition function of this theory counts $\spin(7)$-instantons modulo gauge \cite{Lewis,DonaldsonThomas,ReyesCarrion}.
+If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
+ \[F = \ast (\Omega\wedge F).\]
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
-The minimal twist, by a pure spinor, is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.
-This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
- \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist, by a rank 1 impure spinor, which is topological in three directions and holomorphic in the remaining two complex directions.
-This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.
-It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
- \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.
-This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.
-It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the $G_2$-monopole equations.
+ \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang--Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.
+The minimal twist, by a pure spinor, is equivalent to a generalized version of the BF theory defined on a product of a complex 3-fold and a real 1-manifold.
+ \item \emph{$\mc N=1$ intermediate twist.} The minimal twist admits a deformation to a twist by a rank 1 impure spinor.
+This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau surface and a real oriented 3-manifold.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
+ \item \emph{$\mc N=1$ topological twist.} The minimal twist also admits a deformation to a topological twist defined on $G_2$-manifolds.
+This theory is again perturbatively trivial.
+It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}.
+The partition function of this theory counts $G_2$-monopoles modulo gauge \cite{DonaldsonSegal}.
+If we denote by $\psi$ the calibration 4-form on a $G_2$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying
+\[d_A\sigma = \ast(F_A\wedge \psi).\] 
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.
-This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.
-It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.
-It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the unitary metalinear group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.
-When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter.
-This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}.
- \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
-The one by a supercharge of rank $(1,1)$ is equivalent to a generalized form of BF theory, with two topological directions and two complex holomorphic directions.
-This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
- \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a generalized form of Chern-Simons theory with four real directions and one complex holomorphic direction.
-This theory is only $\ZZ/2\ZZ$-graded.
-It is invariant for the action of $\spin(4;\RR)$, and can be defined on the product of a flat Riemann surface and a spin 4-manifold.
- \item \emph{$\mc N=(1,1)$ topological twist.} Finally, there is a topological twist in 6 dimensions obtained by dimensionally reducing the 7-dimensional topological twist.
-This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the holomorphic twist.
-It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.
-This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the Donaldson-Thomas equations.
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
+In general, this theory is only $\ZZ/2\ZZ$-graded.
+If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/\fg$.
+6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
+This twist is also calculated in the forthcoming work of Dylan Butson \cite{Butson}.
+ \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
+The one by a supercharge of rank $(2, 2)$ is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau curve and a real oriented 4-manifold.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
+ \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} The other intermediate twist, by a rank $(1, 1)$ supercharge, is equivalent to a generalized form of the BF theory defined on a product of a complex surface and a real surface.
+ \item \emph{$\mc N=(1,1)$ topological twist.} The special rank $(1, 1)$ twist admits a deformation to a topological twist defined on Calabi--Yau 3-folds.
+This theory is perturbatively trivial.
+It was studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}.
+The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}.
+If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
+\begin{align*}
+F_{0, 2} + \ol\dd^*_A u &= 0 \\
+\Lambda F_{1, 1}\wedge \omega^2 + [u, \bar{u}] + \lambda \omega^3 &= 0.
+\end{align*}
+\pavel{$\lambda$ to be explained.}
 \end{itemize}
@@
  \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
- &&& $\mr{Map}(\CC^3, U \ham \fg)$ & \\ \hline
+ &&& $\Sect(\CC^3, (U\otimes K_{\CC^3}^{1/2}) \ham \fg)$ & \\ \hline
  \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3 (minimal)} \\
- &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham \fg)$ & \\ \hline
+ &&& $\Sect(\CC^2 \times \RR_{\mr{dR}}, (U\otimes K_{\CC^2}^{1/2}) \ham \fg)$ & \\ \hline
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
@@
  && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
- &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
+ &&& $\Sect(\CC \times \RR^2_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
@@
 \begin{definition}
-A \defterm{morphism} $\Phi \colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$, that intertwine the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$.
-A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism.
-\end{definition}
-
-The interpretation of this definition is that $\Phi$ is a non-linear map between the bundles of BV fields, and $\Phi_n$ is its $n^{\text{th}}$ Taylor coefficient.
-
-\begin{definition}
-A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwines the pairings $\omega, \omega'$ and defines an $L_\infty$ map $\cE_c[-1]\rightarrow \cE'_c[-1]$.
-A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon \cE\rightarrow \cE'$ is a quasi-isomorphism.
+A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwines the pairings $\omega, \omega'$ and defines an $L_\infty$ map $\cE[-1]\rightarrow \cE'[-1]$.
+A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q'_{BV})$ is a quasi-isomorphism.
 A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
@@
 \end{definition}
+
+The interpretation of this definition is that $\Phi$ is a non-linear map between the bundles of BV fields, and $\Phi_n$ is its $n^{\text{th}}$ Taylor coefficient.
 

### 2020-02-14 paper.tex
Added 'many' citations

@@
 To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
-This theory of renormalization can been used to study field theories with and without supersymmetry.
-\brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}.
+In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 

### 2020-02-14 paper.tex
fixing page headers
random edits

--- 2020-02-14 paper.tex
@@
 \]
-Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
+Up to rescaling of the antifields by the rule
+\[
+\alpha^* \mapsto \Omega^{-1} e^{\omega} (\alpha^*)
+\]
+the fields and action coincide precisely with those of holomorphic Chern--Simons theory (see Section \ref{gen_CS_section}).
 \end{proof}
@@
 \item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{4, 1}(M; \gg)[1]$.
+%Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
 \end{itemize}
+\brian{I've changed where $C$ lives to fit the proof below.}
 
@@
 I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) \\
-I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right).
+&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
+I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
 \end{align*}
@@
 We are left with the action
-\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
+\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
@@
 &\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
-&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
+S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*)  +  [\xi, c] \xi^* + [\chi, c]\chi^* +[\rho, c] \rho^* + \\
+&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c] \nu^* + [\phi, c] \phi^* + [\psi, c] \psi^* + [\wt\nu, c] \wt\nu^* \bigg) + [B, c]\wedge B^* \\
 I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
@@
  S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
- &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
+ &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + ([B, c], B^*) .
 \end{align*}
@@
 S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
-S_{\mr{matter}} &= \int \dvol \left((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)\right) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
-&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )  \\
-S_{\mr{anti}} &= \int \bigg(\dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0 \wedge B_{2, 1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* + \dvol ([\lambda_{0}, A_0], \lambda_{0}^*) + [A_0, A_{0,1}]\wedge B_{2, 1} + [A_{0}, A_{1,0}]\wedge A_{1, 0}^* \\
-&\qquad + \frac{1}{2}[A_0, A_0]B_{2, 2} + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \bigg) \\
-I^{(1)}_{\mr{gauge}} &=  \int  \left( - \lambda_{1,0}\wedge A_{1,0}^* + \frac 12 F_{0,2}\wedge B_{2,0} + \frac 12 \omega\wedge F_{1,1} \lambda_0^*  \right) \\
-I^{(1)}_{\mr{matter}} &=  \int  \left( \psi_0 \phi^* + \frac 12 \ol \dd_{A_{0,1}} \gamma_{0}\wedge \beta_{2,1} \right)\\
+S_{\mr{matter}} &= \int \dvol \bigg((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi) + ([A_{0,2}, \beta_{2,0}], \phi) \bigg) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
+&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0})  ) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) \\
+S_{\mr{anti}} &= \int \dvol \bigg((\dd_{A_{1, 0}} A_0, A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) \bigg) +  \\
+& \qquad + \dvol \bigg([A_0, \lambda_0] \lambda_0^* + [A_0, A_{0,2}] A_{0,2}^* \bigg) + [\lambda_{1,0}, A_0] \wedge \lambda_{1,0}^* + \dvol \frac{1}{2}[A_0, A_0]A_0^*\\ 
+&\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
+I^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
+I^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
 I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
@@
 \begin{align*}
- S_{\mr{BV}} &= \int \bigg( (B_{2,1} \ol \dd_{A_{0,1}} A_{0})  + B_{2,0} F_{0,2} + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} + \beta_{2,1} \dbar_{A_{0,1}} \gamma_0 \\ 
-  &\qquad  + [A_{0,2}, A_0]\wedge B_{2,0} + \frac{1}{2}[A_0, A_0]B_{2,2} +  [\gamma_0, A_0]\wedge \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1}  \bigg).
+S_{\rm BV} & = \int \dvol \bigg((A_{0,1}^* \ol \dd_{A_{0,1}} A_{0}) + (\dbar_{A_{0,1}} \gamma_0, \gamma_{0,1}^*)\bigg) + F_{0,2} \wedge A_{0,2}^* + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} \\ & \qquad + \dvol \bigg([A_0, A_{0,2}] A_{0,2}^* + \frac{1}{2} [A_0,A_0] A_0^* + [A_0, \gamma_0] \gamma_0^* + [A_0, \gamma_{0,1}] \gamma_{0,1}^* + [A_0, \beta_{2,0}^*] \beta_{2,0}\bigg)
 \end{align*}
-This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{2,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{2,\bu}$ comprise the fields of the $\beta\gamma$ system.
+
+Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic $BF$ theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
 \end{proof}

### 2020-02-14 paper.tex

@@
 
+\pagestyle{intro}
 \section*{Introduction} 
@@
 
+\pagestyle{standard}
 \part{Supersymmetric Gauge Theory} \label{formalism_part}

### 2020-02-14 paper.tex
merge

--- 2020-02-14 paper.tex
@@
 \[
-p_{\rm Dol} : X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
-\]
-induced by ${\rm Re} : \CC \to \RR$.
+p_{\rm Dol} \colon X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
+\]
+induced by ${\rm Re} \colon \CC \to \RR$.
 
@@
 whose sections we denote by $(A, \lambda, c)$.  
-The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d :\colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
+The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d \colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
 \[
@@
 There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
-The twist is $\ZZ$-graded with $\alpha : \U(1) \hookrightarrow G_R$ given by the natural embedding. 
+The twist is $\ZZ$-graded with $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding. 
 \end{itemize}
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
 This is the $A$-twist in our classification above.
@@
 
-There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
+There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
 

### 2020-02-14 paper.tex
paper

--- 2020-02-14 paper.tex
@@
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Map}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Sect}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
@@
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Map}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $\mr{Sect}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
@@
 \cdots & \ul{0} & \ul{1} & \cdots \\
-\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
+\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar@{.>}[dr] & E_0^1 \ar[r] &\cdots \\
+&\cO_M \ar^-{{\rm dvol}}[r] \ar@{.>}[ur] &\dens_M &
 }\]
-where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
+The bottom map multiplies a function by the volume element.
+The dotted arrows are induced from $S_1$.
+The proposition implies that we can replace this with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
 \end{remark}
@@
 There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWSuperconformal} which is the theory
-\[\Sect(\CC, (U\otimes K_\CC^{1/2})\ham\fg).\]
-For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
-\[T^*[-1] \map(\CC, R / \fg)\]
-by Proposition \ref{prop:mapintocotangent}.
+\[\Sect(X, (U\otimes K_X^{1/2})\ham\fg) . \]
+%For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
+%\[T^*[-1] \map(\CC, R / \fg)\]
+%by Proposition \ref{prop:mapintocotangent}.
 \end{example}
@@
 \begin{theorem} \label{thm:4d_11_twist}
-The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U\ham \gg)$.
+The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
 Moreover, this equivalence is $\U(1) \times \Spin(2, \RR)$-equivariant.
@@
 \begin{theorem}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 \begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Sect}(\RR^3_{\mr{dR}}, U\ham \gg)$.
 Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.

### 2020-02-17 paper.tex
all around edits

@@
 Let $(E, \omega, S)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, \omega, S)$ is an element 
-\[\fS_\fg = \sum_{k\geq 0} \fS_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
-of cohomological degree zero, where $\fS_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $\fS_\fg^{(0)} = S$.
-\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $\fS^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
-\item[(c)] $\fS_\fg$ satisfies the Maurer--Cartan equation:
-\[\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0.\]
+\[S_\fg = \sum_{k\geq 0} S_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
+of cohomological degree zero, where $S_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $S_\fg^{(0)} = S$.
+\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $S^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
+\item[(c)] $S_\fg$ satisfies the Maurer--Cartan equation:
+\[\d_{\mr{CE}} S_\fg + \frac{1}{2} \{S_\fg, S_\fg\} = 0.\]
 \end{itemize}
@@
 \begin{remark}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $\fS_\fg$.
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $S_\fg$.
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
@@
 
-\item An action $\fS_\fg$ of its super Lie algebra $\fg$ with $\fS^{(k)}_\fg = 0$ for $k\geq 2$ 
+\item An action $S_\fg$ of its super Lie algebra $\fg$ with $S^{(k)}_\fg = 0$ for $k\geq 2$ 
 \end{itemize}
@@
 
-\item For every $x\in\fg$, the vector field $X_{{\fS^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
+\item For every $x\in\fg$, the vector field $X_{{S^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
 \end{itemize}
@@
 \[
-I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
-\]
-where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
+S_{\fA} = S + \sum_{k \geq 1} S_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
 
@@
 The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
-\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
+\[S^Q = S + \sum_{k \geq 1} S_{\fA}^{(k)}(Q, \dots, Q).\]
 \end{definition}
@@
 \begin{equation}
-I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
+S_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
 \label{eq:YMPoincareaction}
@@
 \begin{align}
-I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
-I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
+S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
+S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
 \label{eq:gaugeI2}
@@
 \begin{theorem}\label{thm:gaugemultipletSUSY}
-The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
-\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
-Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
-\end{theorem}
+The functional $S_{\gauge, \fA} = S_{\gauge} + S_{\gauge}^{(1)} + S_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
+\[\d_{\mr{CE}} \left(S_{\gauge, \fA}\right) + \frac{1}{2}\{S_{\gauge, \fA}, S_{\gauge, \fA}\} = 0.\]
+\end{theorem}
+
+This result implies that the pure gauge sector of super Yang--Mills theory carries an $L_\infty$ action by the super Lie algebra $\fA$.
+We consider coupling to matter in the next section.
 
@@
 \begin{align*}
-\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
-\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
-\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
-\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
+\{S_{\gauge}, S_{\gauge}^{(1)}\} &= 0 \\
+\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} &= 0 \\
+\d_{\mr{CE}} S_{\gauge}^{(2)} + \{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\} &= 0 \\
+\{S_{\gauge}^{(2)}, S_{\gauge}^{(2)}\} &= 0.
 \end{align*}
 
-Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
+Note that the last equation is automatically satisfied since $S_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
 The rest of the claims will be proved in a sequence of Lemmas.
@@
 \begin{lemma}
-One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
+For each $Q\in \Sigma$, one has $\{S_{\gauge}, S_{\gauge}^{(1)}(Q)\} = 0$.
 \label{lm:gaugemultiplet1}
@@
 \begin{proof}
-Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.
+Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge, i}$ into individual summands of Equation (\ref{eq:YMBVaction}).
 
@@
 \begin{align*}
-\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
+\{S_{\gauge, 1}, S_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
 &= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
@@
 \begin{align*}
-\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
+\{S_{\gauge, 2}, S_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
 &= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
@@
 
-By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
-
-Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
+By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_1 + S_2, S_{\gauge}^{(1)}(Q)\} = 0$.
+
+Finally, $\{S_{\gauge,3} + S_{\gauge,4} + S_{\gauge, 5}, S_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $S_{\gauge}^{(1)}(Q)$.
 \end{proof}
@@
 One has
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
+\[\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} = 0.\]
 \label{lm:gaugemultiplet2}
@@
 Evaluating the equation
-\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
+\[\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} = 0\]
 on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $S_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
@@
 \begin{align*}
-\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
+\frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\gauge}^{(1)}(Q_2)\} \\
 = &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
@@
 \begin{align*}
-(\d_{\mr{CE}} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+(\d_{\mr{CE}} S_{\gauge}^{(1)})(Q_1, Q_2) &= S_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
 &= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
@@
 \begin{align*}
-\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
+\{S_{\gauge}, S_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
 &+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
@@
 Evaluating the equation
-\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
+\[\d_{\mr{CE}} S_{\gauge}^{(2)} + \{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\} = 0\]
 on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $S_{\gauge}^{(2)}$.
 
 \begin{lemma}
-\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+One has
+\[\{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in\Sigma$.
@@
 \begin{align*}
-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+\{S_{\gauge}^{(1)}(Q_1), S_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
 &+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
@@
 
-$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
+$\{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
 By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
@@
 The BV action for the matter multiplet is
-\[
+\begin{equation}\label{matteraction}
 S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
-\]
+\end{equation}
 where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
@@
 \begin{equation}
-I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
+S_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
 \label{eq:matterPoincareaction}
@@
 \begin{align}
-I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
-I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
+S_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
+S_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
 \end{align}
@@
 We consider the full action of the super Yang--Mills theory
-\[S_{\BV} = S_{\gauge} + S_{\matter}\]
-together with a supersymmetry action functionals
-\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]
+\[S_{\rm SYM} = S_{\gauge} + S_{\matter}\]
+together with the $\fA$-dependent functionals
+\[S^{(1)} = S^{(1)}_{\gauge} + S^{(1)}_{\matter},\qquad S^{(2)} = S^{(2)}_{\gauge} + S^{(2)}_{\matter}.\]
 
@@
 \begin{theorem}
-The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
+The functional $S_{\fA} = S_{\rm SYM} + S^{(1)} + S^{(2)}$ satisfies the classical master equation
 \begin{equation}
 \label{CMEYM}
-\d_{\mr{CE}} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
+\d_{\mr{CE}} S_\fA + \frac{1}{2} \{S_\fA, S_\fA\} = 0 .
 \end{equation}
+Thus, according to Definition \ref{infinitesimal_action_def}, the functional $S_{\fA}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric
 \label{thm:YMSUSY}
@@
 
-The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
+The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. 
+Notice that when we take the matter to be valued in a trivial representation for the Lie algebra $\fg$, the result reduces to Theorem \ref{thm:gaugemultipletSUSY}.
+We may therefore restrict our attention to the terms in \eqref{CMEYM} which involve fields of the matter multiplet. 
+Consequently, the classical master equation \eqref{CMEYM} decomposes into the following set of equations:
 \begin{equation}
@@
 \begin{array}{rrrrrr}
-\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
-\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
-\d_{\mr{CE}} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
-\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
+\{S_{\rm SYM} , S^{(1)}\} & = & 0 \\ 
+\{S_{\matter}, S^{(2)}\} + \d_{\mr{CE}} S_{\matter}^{(1)} + \{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\} + \frac{1}{2} \{S_{\matter}^{(1)}, S_{\matter}^{(1)}\} & = & 0 \\
+\d_{\mr{CE}} S_{\matter}^{(2)} + \{S_{\matter}^{(1)}, S_{\matter}^{(2)}\} & =& 0 \\
+\{S_{\matter}^{(2)}, S_{\matter}^{(2)}\} & =& 0
 \end{array}
@@
 
-The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
+The last equation is automatically satisfied since $S^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
 
@@
 \begin{lemma} \label{lem:YM1}
-One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+One has $\{S_{\rm SYM}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
 \end{lemma}
 \begin{proof}
-Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.
+Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter, i}$ into the individual summands in Equation \eqref{matteraction}.
 
@@
 \begin{align*}
-\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
+\{S_{\matter,1}, S^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
 &= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
@@
 \begin{align*}
-\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
+\{S_{\matter,2}, S^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
 &= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
@@
 \begin{align*}
-\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
+\{S_{\matter,3}, S^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
 &= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
@@
 where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
-\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
-
-Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
+\[\{S_{\matter,1} + S_{\matter,2} + S_{\matter,3}, S^{(1)}(Q)\} = 0.\]
+
+Finally, the terms $\{S_{\matter,4} + S_{\matter,5} + S_{\gauge,3}, S^{(1)}(Q)\}$ are zero due to gauge-invariance of $S^{(1)}(Q)$, while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
 \end{proof}
@@
 \begin{equation}\label{CMEYM3}
-\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
+\{S_{\matter}, S^{(2)}\} + \d_{\mr{CE}} S_{\matter}^{(1)} + \{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\} + \frac{1}{2} \{S_{\matter}^{(1)}, S_{\matter}^{(1)}\} = 0 .
 \end{equation}
@@
 \begin{align*}
-\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
+\frac{1}{2}\{S_{\matter}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{S_{\matter}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} \\
 =&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
@@
 \begin{align*}
-\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
+\{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} - \{S_{\gauge}^{(1)}(Q_2), S_{\matter}^{(1)}(Q_1)\} \\
 =& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
@@
 \[
-(\d_{\mr{CE}}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+(\d_{\mr{CE}}S_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
 \]
@@
 \[
-\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
+\{S_{\matter}, S^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
 \]
@@
 \begin{lemma}
-\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+One has
+\[\{S_{\matter}^{(1)}, S_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in \Sigma$.
@@
 \begin{align*}
-\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\{S_{\matter}^{(1)}(Q_1), S_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
 \end{align*}
 The expression
-$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
+$\{S_{\matter}^{(1)}, S_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
 \end{proof}

### 2020-02-18 paper.tex
merge

@@
 
-\subsection{Pure Super Yang--Mills Theory}
+\subsection{Super Yang--Mills Theory: pure gauge theory}
 \label{sect:gaugemultipletSUSY}
@@
 \begin{definition}
+\label{def:sym}
 The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
@@
 \[S_{\rm SYM} = S_{\gauge} + S_{\matter}\]
-together with the $\fA$-dependent functionals
-\[S^{(1)} = S^{(1)}_{\gauge} + S^{(1)}_{\matter},\qquad S^{(2)} = S^{(2)}_{\gauge} + S^{(2)}_{\matter}.\]
-
+where $S_{\gauge}$ is the BV action of the pure gauge sector of super Yang--Mills theory defined in Equation \eqref{eq:YMBVaction}.
+
+The action by supersymmetry on the full theory is encoded by the $\fA$-dependent functionals
+\[S^{(1)} = S^{(1)}_{\gauge} + S^{(1)}_{\matter},\qquad S^{(2)} = S^{(2)}_{\gauge} + S^{(2)}_{\matter}\]
+where $S^{(1)}_\gauge, S^{(2)}_\gauge$ are as in Equations (\ref{eq:gaugeI1}), (\ref{eq:gaugeI2}).
 The following result states that these functionals encode an off-shell action of the supersymmetry algebra.
@@
 
-Let $Q\in\Sigma$ be a square-zero supercharge.
+Let $Q\in\Sigma$ be a square-zero supercharge, which we will fix for the rest of this section. 
 The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$.
@@
 
-Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
+Let $\ML(L) = \ML(5)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
 \[\Sigma = \det(L)^{1/2} \oplus \wedge^2 L^*\otimes \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2}.\]
@@
 Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
+The BV action of the twisted theory $S_{\mr{twist}}$ is then the sum of the following terms:
 \begin{align}
@@
 S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
-I^{(1)} &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
-I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+S^{(1)}(Q) &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
+S^{(2)}(Q) &= -\frac{1}{4}\int \dvol (\chi^*)^2.
 \end{align}
+The first two terms comprise the action of supersymmetric Yang--Mills theory $S_{\rm SYM} = S_{\rm gauge}$ of Definition \ref{def:sym} written with respect to the $\ML(L) = \ML(5)$ decomposition. 
+The last two terms arise from the twisting procedure.
 
@@
 First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
+So, the above theory described by $S_{\rm twist}$ is perturbatively equivalent to the theory without the fields $\chi$ and $\chi^*$ with the BV action
 \begin{align*}
@@
 
-Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e.
-$(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
-The above theory then becomes perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
+Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e. $(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it. 
+The above theory described by $S_{{\rm no } \chi}$ is perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
@@
 Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt a, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
+%\[
+%\xymatrix@R=0.5cm@C=0.5cm{
+%&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
+%&&\ar@{}^{\bigoplus}[r] &&& \\
+%\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
+%}
+%\]
 \[
@@
 \begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
 &+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
-I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
+S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
 \end{align*}
@@
 The action of the twisted 8d super Yang--Mills theory is given by
-\[S_{Q_t} = S_{\mathrm{BRST}} + S_{\mathrm{anti}} + I^{(1)}(Q_t) + I^{(2)}(Q_t),\]
+\[S_{Q_t} = S_{\rm SYM} + S^{(1)}(Q_t) + S^{(2)}(Q_t),\]
 where $S_{\mathrm{BRST}}$ and $S_{\mathrm{anti}}$ are given by \eqref{eq:10dBRST} and \eqref{eq:10danti} respectively.
@@
 which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+\brian{Need to be careful with where things live. This diagram does not match the diagram above, though we are using the same twisting homomorphism.}
 \end{proof}
@@
 
-Consider a nonzero $Q\in S_+\otimes W_+$.
+Consider a nonzero $Q\in S_+\otimes W_+$ which we fix for the remainder of this section.
 Since $\wedge^2(S_+)\cong V$, the square-zero condition is equivalent to the condition that $Q$ has rank 1, i.e.
@@
 
-Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
+Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{twist}}$ of the $Q$-twisted theory consists of the sum of the following terms:
 
@@
 &\qquad + \frac{1}{2}[c, c]c^* + [\nu, c] \nu^* + [\phi, c] \phi^* + [\psi, c] \psi^* + [\wt\nu, c] \wt\nu^* \bigg) + [B, c]\wedge B^* \\
-I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
-I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
-I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+S^{(1)}_{\gauge} (Q) &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
+S^{(1)}_{\matter} (Q) &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
+S^{(2)}_{\gauge} (Q) &= -\frac{1}{4}\int \dvol (\chi^*)^2.
 \end{align*}
@@
 In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
-The twisted theory is therefore perturbatively equivalent to the theory with the BV action
+The twisted theory $S_{\rm twist}$ is therefore perturbatively equivalent to the theory with the BV action
 \begin{align*}
- S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
- &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + ([B, c], B^*) .
+& \int \bigg(\xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \bigg) \\
+ &+ \int \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + [B, c] \wedge B^* .
 \end{align*}
-Up to rescaling of the antifields, this is the action functional of the required theory.
+Up to rescaling the antifields, this is the action functional of the required theory.
 %where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
@@
 \begin{align*}
-I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
 & + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
@@
 %&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
-I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
+S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
+S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
+S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
 \end{align*}
@@
 \begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
  \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
@@
 \end{itemize}
+
+\begin{itemize}
+\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Bar{a} \in \Omega^0(\CC ; \fg)[2]$. 
+\item $\gg$-valued fermions: $\lambda \in \Omega^{??}(\CC ; \fg)[-1]$, $\Bar{\lambda} \in \Omega^{??}(\CC ; \fg) [-1]$, $\lambda' \in \Omega^{0,1}(\CC ; \fg)[1]$, $\Bar{\lambda}' \in \Omega^{??}(\CC ; \fg)[1]$.
+ %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
+ \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
+ %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
+ \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+\end{itemize}
 We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
@@
 \begin{align*}
-I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
 &+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
-I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
-I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
-I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
+S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
+S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
+S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
 \end{align*}

### 2020-02-18 paper.tex
merging

--- 2020-02-14 paper.tex
@@
 
+\pagestyle{intro}
 \setcounter{tocdepth}{2}
@@
 
-\pagestyle{intro}
 \section*{Introduction} 
@@
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Sect}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
@@
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Sect}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
@@
 \cdots & \ul{0} & \ul{1} & \cdots \\
-\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar@{.>}[dr] & E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^-{{\rm dvol}}[r] \ar@{.>}[ur] &\dens_M &
+\cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar[dr] & E_0^1 \ar[r] &\cdots \\
+&\cO_M \ar^{{\rm dvol}}[r] \ar[ur] &\dens_M &
 }\]
-The bottom map multiplies a function by the volume element.
-The dotted arrows are induced from $S_1$.
-The proposition implies that we can replace this with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
+where the bottom map multiplies a function by the volume element, then we can replace it with a quasi-isomorphic cochain complex consisting of only the first line, provided we make a suitable modification of the classical action functional.
 \end{remark}
@@
 There is a special case of this, which one might label the ``holomorphic symplectic boson'' \cite[Definition 4.8]{SWSuperconformal} which is the theory
-\[\Sect(X, (U\otimes K_X^{1/2})\ham\fg) . \]
-%For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
-%\[T^*[-1] \map(\CC, R / \fg)\]
-%by Proposition \ref{prop:mapintocotangent}.
+\[\Sect(\CC, (U\otimes K_\CC^{1/2})\ham\fg).\]
+For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
+\[T^*[-1] \map(\CC, R / \fg)\]
+by Proposition \ref{prop:mapintocotangent}.
 \end{example}
@@
 \begin{theorem} \label{thm:4d_11_twist}
-The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
+The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U\ham \gg)$.
 Moreover, this equivalence is $\U(1) \times \Spin(2, \RR)$-equivariant.
@@
 \begin{theorem}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Map}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 \begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Sect}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.
 Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.

### 2020-02-18 paper.tex
conflict

--- 2020-02-18 paper.tex
@@
 
+First, we record the minimal twist of 2d $\cN=(2,2)$ supersymmetric Yang--Mills theory.
+
 \begin{theorem} \label{2d_minimal_twist_thm}
@@
 \begin{proof}
-We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$, integrating out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.
-We can then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}.
-At $t=0$, we are left with the holomorphic twist from Theorem \ref{2d_minimal_twist_thm}, i.e, the theory $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
-The action functional is further deformed by the remaining $t$-linear terms, which together take the form
-\[\int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right).\]
-In terms of the classical BV complex we can identify these terms as introducing the following dotted isomorphism between two summands:
+We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
+We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
+We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
+The resulting action functional is of the form
+\[
+S_{BF} + \int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right)\]
+Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
+
+We can identify the linearized BV complex with the following diagram:
 \[\xymatrix@R=0.4cm@C=0.2cm{
@@
 }\]
+Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
 This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
@@
 
-Finally, there is the 2d B-twist.
-This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
-Indeed, let $W_3$ be the 2d auxiliary space in the 3d $\mc N=2$ supertranslation algebra.
-The 3d spin representation $S \otimes W_3$ splits into $S_+ \otimes W_3 \oplus S_- \otimes W_3$ as a $\spin(2;\CC)$-module.
-Rank one square zero elements in 3d $\mc N=2$ generically become rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.
+Finally, there is the $B$-twist of 2d $\cN=(2,2)$ supersymmetry.
+This twist arises from the twist of 3d $\cN=2$ via dimensional reduction in a non-invariant direction.  
+Indeed, let $W_3$ be the two-dimensional auxiliary space in the 3d $\mc N=2$ supertranslation algebra.  
+As a $\spin(2;\CC)$-representation, the 3d $\cN=2$ spinorial representation decomposes as $S_+ \otimes W_3 \oplus S_- \otimes W_3$.
+Generically, rank one square zero elements in 3d $\mc N=2$ supersymmetry define rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.  
 There is a square-zero supercharge in 3d $\mc N=2$ compatible with the identity twisting homomorphism $\spin(2;\CC) \to \spin(2;\CC)$.

### 2020-02-18 paper.tex
merge

--- 2020-02-18 paper.tex
@@
 
-\pagestyle{intro}
 \setcounter{tocdepth}{2}
@@
 
-Given a classical BRST theory, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
+Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
+\brian{
+Why $S_g$? I suggest $S_0$, or $S_\cM$, or $S_{\rm cot}$. Also it's not clear from this sentence how $S_g$ depends on the data of the BRST theory. It doesn't use $S_{BRST}$, for instance.
+} 
 Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
@@
 \[
-p_{\rm Dol} \colon X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
-\]
-induced by ${\rm Re} \colon \CC \to \RR$.
+p_{\rm Dol} : X \times (Y' \times \CC) \times M \to X \times Y' \times (M \times \RR) 
+\]
+induced by ${\rm Re} : \CC \to \RR$.
 
@@
 whose sections we denote by $(A, \lambda, c)$.  
-The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d \colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
+The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d :\colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
 \[
@@
 \item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{4, 1}(M; \gg)[1]$.
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3,0}(M; \gg)[1]$.
 %Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
@@
 \end{itemize}
-\brian{I've changed where $C$ lives to fit the proof below.}
 
@@
 \]
+
 concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
@@
 We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}.
-Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$.
+Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$, $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$, and $a \in \Omega^0(\CC^4 ; \fg)$.
 First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.
@@
 which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
-\brian{Need to be careful with where things live. This diagram does not match the diagram above, though we are using the same twisting homomorphism.}
 \end{proof}
@@
 &\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
-I^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
-I^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
+S^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
+S^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
+S^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
 \end{align*}
@@
 There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
-The twist is $\ZZ$-graded with $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding. 
+The twist is $\ZZ$-graded with $\alpha : \U(1) \hookrightarrow G_R$ given by the natural embedding. 
 \end{itemize}
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha : \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
 This is the $A$-twist in our classification above.
@@
 
-There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
+There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
 

### 2020-02-19 paper.tex
(2,2) done

--- 2020-02-18 paper.tex
@@
 \section{Dimension 2}
-In dimension 2, the semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm 1$.
+The odd part of the $2$-dimensional supersymmetry algebra is $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$.
+The comlpex semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
 There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
+
 There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+First we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
 We additionally have gauge theories with chiral, i.e.
@@
 This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
-The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
+The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$, with the factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
+\brian{Not sure what $(a^{-1},b^{-1})$ means?
+Do you mean $(-a,-b)$?}
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
-The fields we obtain are
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
+In any case, the fields we obtain are
 \begin{itemize}
@@
 The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
-\begin{itemize}
- \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
+%\begin{itemize}
+% \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
+% %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
+% \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
+% %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+% \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
+% \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
+% \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+%\end{itemize}
+
+\begin{itemize}
+\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
+\item $\gg$-valued fermions: $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
  %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
+ \item  $R$-valued bosons: $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
  %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
- \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
- \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
-\end{itemize}
-
-\begin{itemize}
-\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Bar{a} \in \Omega^0(\CC ; \fg)[2]$. 
-\item $\gg$-valued fermions: $\lambda \in \Omega^{??}(\CC ; \fg)[-1]$, $\Bar{\lambda} \in \Omega^{??}(\CC ; \fg) [-1]$, $\lambda' \in \Omega^{0,1}(\CC ; \fg)[1]$, $\Bar{\lambda}' \in \Omega^{??}(\CC ; \fg)[1]$.
- %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
- %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
- \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+ \item $R$-valued fermions: $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
+ \item Ghost field: $c \in \Omega^0(\RR^2; \fg)[1]$.
 \end{itemize}
@@
 Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
-The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
+The $\U(1)$ decomposition of the functionals $S_{\rm gauge}^{(1)}, S^{(1)}_{\rm matter}, S^{(2)}_{\rm gauge}, S^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
 \begin{align*}
-S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
-&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
-S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
-S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
-S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
+S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{1,0}, A_{1,0}^*) - (\Tilde{\lambda}_0, \Tilde{a}^*) + \frac 12(F_{1,1} \lambda_0^* + (\ol \dd_{A_{0,1}}a, \chi_{0,1}^*)) \right)  \\
+&+  \int \dvol t \left( -(\chi_{0,1}, A_{0,1}^*) - (\lambda_0, \Tilde{a}^*) + \frac 12(F_{1,1} \Tilde{\lambda}_0^*+ (\partial_{A_{1,0}} \Tilde{a}, \lambda_{1,0}^*) )   \right)  \\
+S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t (\lambda_0^*, \Tilde{\lambda}_0^*) - \frac 14(\lambda_0^* + t \Tilde{\lambda}_0^*)^2 + t(a, c^*)\right)  \\
+S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( \psi_0 \phi^* + \frac 12 (\ol \dd_{A_{0,1}} \gamma_0, \gamma_{0,1}^*) \right) +t\left( (\Tilde{\psi}_0, \gamma_0^*) + \frac 12 (\dd_{A_{1,0}}  \phi, \beta_{1,0}^*)  \right)\right)  \\
+S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t2 \left(\beta_{1,0}^*, \gamma_{0,1}^*\right).
 \end{align*}
 \end{prop}
+
+%\begin{prop}
+%Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
+%The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
+%\begin{align*}
+%S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+%&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
+%S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t (\lambda_0^*, \Tilde{\lambda}_0^*) - \frac 14(\lambda_0^* + t \Tilde{\lambda}_0^*)^2 + t(a, c^*)\right)  \\
+%S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
+%S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
+%\end{align*}
+%\end{prop}
 
@@
 \begin{proof}
-We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
-We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
-We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
-The resulting action functional is of the form
-\[
-S_{BF} + \int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right)\]
+Observe that the quadruple of fields $\{\lambda_0^*, \lambda_0, \Tilde{\lambda}_0^*, \Tilde{\lambda}_0\}$ has the same Poisson brackets as the quadruple $\{\lambda_0^* - t \Tilde{\lambda}_0^*, \lambda_0, \lambda_0^*, \Tilde{\lambda}_0 + t \lambda_0\}$.
+Therefore, we may eliminate the fields $\lambda_0^*-t\wt\lambda_0^*, \chi$ using Proposition \ref{prop:integrateoutfield}. 
+We then have trivial BRST doublets $\{\wt\lambda_0 + t\lambda_0, \wt a\}$, $\{\lambda_{1,0}, A_{1,0}\}, \{\psi_0, \phi\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
+We are left with the action
+
+%We first perform a change of variables sending $\lambda_0$ to $\lambda_0 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
+%We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
+%We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
+%The resulting action functional is of the form
+\[
+S_{BF} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
+\]
 Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
@@
 \ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
-\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
-&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
-&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
-&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
-&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
+&\Omega^0(\CC; \gg)_{c} \ar[r] &\Omega^{0,1}(\CC; \gg)_{A_{0,1}} & & \Omega^{1,0}(\CC; \gg^*)_{\chi_{0,1}^*} \ar[r] &\Omega^{1,1}(\CC; \gg^*)_{a^*} \\
+\Omega^0(\CC; \gg)_{a} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\CC; \gg)_{\chi_{0,1}} \ar@{-->}[ur] && \Omega^{1,0}(\CC; \gg^*)_{A_{0,1}^*} \ar[r] \ar@{-->}[ur] &\Omega^{1,1}(\CC; \gg^*)_{c^*} \ar@{-->}[ur]\\
+&\Omega^0(\CC; R^*)_{\Tilde{\psi}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\CC; R^*)_{\beta_{1,0}^*} \ar@{-->}[dr] &&&\\
+&& \Omega^0(\CC; R^*)_{\gamma_0} \ar[r]  &\Omega^{0,1}(\CC; R^*)_{\gamma_{0,1}} &&\\
+&&\Omega^{1,0}(\CC; R)_{\gamma_{0,1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{1,1}(\CC;  R)_{\gamma_0^*} \ar@{-->}[dr] &&\\
+&&& \Omega^{1,0}(\CC; R)_{\beta_{1,0}} \ar[r]  &\Omega^{1,1}(\CC; R)_{\Tilde{\psi}_0^*}. &\\
 }\]
+%\[\xymatrix@R=0.4cm@C=0.2cm{
+%\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
+%&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
+%\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
+%&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
+%&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
+%&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
+%&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
+%}\]
 Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.

### 2020-02-19 paper.tex
3d 2d

@@
 In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation.
-We do not consider superpotential and mass terms in this paper.
+We do not consider superpotential, mass, or Fayet--Iliopoulos terms in this paper.
 Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).
@@
 
-Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
-\brian{
-Why $S_g$? I suggest $S_0$, or $S_\cM$, or $S_{\rm cot}$. Also it's not clear from this sentence how $S_g$ depends on the data of the BRST theory. It doesn't use $S_{BRST}$, for instance.
-} 
+Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_{\rm anti}$.
 Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
-Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
+Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
 
@@
 Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory.
-The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_g$.
+The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
 \end{definition}
@@
 \begin{lemma} \label{lem:YM1}
-One has $\{S_{\rm SYM}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+One has $\{S_{\rm SYM}, S^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
 \end{lemma}
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
-We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, and $W$ is its defining representation.
+Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
 
@@
 \label{sect:3d_4_minimal_twist}
-The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
+Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.
 
@@
 \subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
-Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
-This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, and $W$ is its $8$-dimensional (Dirac) spin representation.
+Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
+This theory is the dimensional reduction of 10d $\cN = (1,0)$ supersymmetric Yang--Mills theory.  
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional (Dirac) spin representation.
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
-The fields we obtain are
-\begin{itemize}
- \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
- \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
+The fields are:
+\begin{itemize}
+ \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
+ \item Fermions: spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
  \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
@@
 
-In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.
-That is, there are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.
-We can see this in the following way.
+In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in 3d $\mc N=4$.  
+There are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.  We can see this in the following way.
 \begin{lemma}
@@
 \label{sect:3d8minimal_twist}
-The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  
-Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
+The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.
+Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.
 
@@
 \end{theorem}
+\brian{Need to explain what happened to $\Sect$}
 
@@
 \subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
-First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  
-This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
-The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$, with the factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
+First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
+%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
+The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
 \brian{Not sure what $(a^{-1},b^{-1})$ means?
@@
 
-In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
+In the $\mc N=(2,2)$ supersymmetry algebra there are three classes of non-trivial orbits of square-zero supercharges.  
 \begin{itemize}
@@
 They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.
-Let us first decompose our fields according to the twisting homomorphism $\phi_A$.
-The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
+Let us first decompose our fields according to the twisting homomorphism $\phi_A$:
+%The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
 %\begin{itemize}
@@
 \end{itemize}
-We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
+%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
 
@@
 \begin{theorem} \label{2d_2_A_twist_thm}
-The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 
-\subsubsection{Topological B Twist} \label{sect:2d22Btwist}
+\begin{corollary}
+The topological $A$-twist of 2d $\cN=(2,2)$-supersymmetric Yang--Mills theory is perturbatively trivial.
+\end{corollary}
+
+\subsubsection{Topological $B$-Twist} \label{sect:2d22Btwist}
 
@@
 \begin{proof}
-We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.
-That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
+We dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills in a non-invariant direction.  
+Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} to turn the we obtain the desired result.
 \end{proof}
@@
 \subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
-We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
-No new twists arise, i.e.
-every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
-
-The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e.
-by its fundamental representation on $W^6$.
-
-In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
+Next, we consider $\mc N=(4,4)$ supersymmetric Yang--Mills theory.
+This theory is obtained as the dimension reduction of 3d $\mc N=4$ supersymmetric Yang--Mills theory.  
+No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
+First, $\spin(4;\CC)$ acts on $W_+$ and $W_-$ by the fundamental and anti-fundamental representations, respectively.
+The group $\SU(2)$ acts by permuting the two factors.
+
+In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  
+As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
 
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
-The B-supercharge occurs as a degeneration of A-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
+The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
 \end{prop}
@@
 \begin{proof}
-First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$.
-A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.
+Decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. 
+A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
 There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  
-We will refer to these as the B- and A-supercharges respectively.
-\end{proof}
-
-Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.
-Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.
+These are the $B$- and $A$-supercharges respectively.
+\end{proof}
+
+Upon dimensional reduction from 3d $\mc N=4$, the $B$-supercharge reduces to the 2d $\mc N=(4,4)$ $B$-supercharge.  
+Indeed, the 3d $B$-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  
 Therefore the two vectors in $W_+^6$ discussed above must be colinear.
@@
 \subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
-We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
+By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
 
@@
 \subsubsection{Topological A Twist} \label{sect:2d44Atwist}
-We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
+By Theorem \ref{3d_4_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
 
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+
+The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
+By Theorem \ref{3d_4_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
 
@@
 \subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
-Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.
-No new twists arise, i.e.
-every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
+This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
+No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
 
@@
 \subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
-We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
 
@@
 \subsubsection{Topological A Twist} \label{sect:2d88Atwist}
-We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{3d_8_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
 
@@
 \subsubsection{Topological B Twist} \label{sect:2d88Btwist}
-We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
+The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{3d_8_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
 

### 2020-02-19 paper.tex
merge

--- 2020-02-18 paper.tex
@@
 
-Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
-\brian{
-Why $S_g$? I suggest $S_0$, or $S_\cM$, or $S_{\rm cot}$. Also it's not clear from this sentence how $S_g$ depends on the data of the BRST theory. It doesn't use $S_{BRST}$, for instance.
-} 
+Given a classical BRST theory, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
 Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
@@
 \item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3,0}(M; \gg)[1]$.
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{4, 1}(M; \gg)[1]$.
 %Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
@@
 \end{itemize}
+\brian{I've changed where $C$ lives to fit the proof below.}
 
@@
 \]
-
 concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
@@
 We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}.
-Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$, $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$, and $a \in \Omega^0(\CC^4 ; \fg)$.
+Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$.
 First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.
@@
 S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
+&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
 S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
@@
 &\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
-S^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
-S^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
-S^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
+I^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
+I^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
 \end{align*}

### 2020-02-19 paper.tex
(0,2) done

--- 2020-02-19 paper.tex
@@
 \begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 Fix the twisting datum $\alpha = \alpha_n$.
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
 Moreover, the equivalence is $\MU(2)$-equivariant.
@@
 \begin{itemize}
-\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
-\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
-\item Matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
-\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
-\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
+\item gauge bosons $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$, $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
+\item gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
+\item matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
+\item matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
+\item a ghost field $c\in \Omega^0(M; \gg)[1]$.
 \end{itemize}
@@
 \begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
- \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
- \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
- \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
+ \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
+ \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
+ \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
+ \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
 \end{itemize}
@@
 \paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
-The fields we obtain are
-\begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
- \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
- \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
- \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
+The fields are:
+\begin{itemize}
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
+ \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
+ \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
+ \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
+ \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
 \end{itemize}
@@
 \begin{itemize}
- \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
- \item Fermions: spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
- \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
+ \item gauge fermions $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
+ \item a ghost field $c \in \Omega^0(\RR^3;\gg)[1]$.
 \end{itemize}
@@
 \section{Dimension 2}
-The odd part of the $2$-dimensional supersymmetry algebra is $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$.
-The comlpex semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
+The odd part of the $2$-dimensional supersymmetry algebra is 
+\[
+\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
+\]
+The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
 There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
@@
 \begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
- \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
- \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
+ \item gauge bosons $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item gauge fermions $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
+ \item matter fermions $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
+ \item a ghost field $c \in \Omega^0(\RR^2; \gg)[1]$.
 \end{itemize}
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
@@
 \begin{itemize}
-\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
-\item $\gg$-valued fermions: $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
+\item gauge fermions $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
  %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item  $R$-valued bosons: $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
+ \item matter bosons $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
  %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $R$-valued fermions: $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
- \item Ghost field: $c \in \Omega^0(\RR^2; \fg)[1]$.
+ \item matter fermions $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
+ \item a ghost field $c \in \Omega^0(\RR^2; \fg)[1]$.
 \end{itemize}
@@
 \begin{theorem} \label{2d_2_A_twist_thm}
-The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{theorem} \label{2d_2_B_twist_thm}
-The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
+The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{proof}
-We dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills in a non-invariant direction.  
-Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} to turn the we obtain the desired result.
+The theory is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=2$ supersymmetric Yang--Mills theory in a non-invariant direction.  
+Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} we obtain the desired result.
 \end{proof}
@@
 The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
-First, $\spin(4;\CC)$ acts on $W_+$ and $W_-$ by the fundamental and anti-fundamental representations, respectively.
-The group $\SU(2)$ acts by permuting the two factors.
+We can identify $W_\pm = S^4_\pm \otimes W_+^6$, where $W_+^6$ is the auxiliary space of 6d $\cN=(1,0)$ supersymmetry, and $S^4_\pm$ are the semi-spin representations of $\spin(4;\CC)$. 
+The group $\spin(4;\CC)$ acts on $S^4_\pm$ in the natural way, and $\SU(2)$ acts on $W_+^6 \cong \CC^2$ as the fundamental representation.
 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic $BF$ theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.
-This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in symplectic $\fg$-representation $U$ admits a one-parameter deformation to the A-twist.  
+This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 \begin{theorem}
-The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
+The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological $BF$ theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
-The B-supercharge occurs as a degeneration of A-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
+The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
 \end{prop}
@@
 \begin{proof}
-Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
+We classify $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
 Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.
@@
 
-Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.
-Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.
-In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.
+Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
+Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.
+In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.
 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.
 This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
@@
 
-We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
+We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
+Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
 The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$. 
+The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.
 
@@
 \begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
-\end{itemize}
-Here, $W$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
-Choose the basis $\{u,v\}$ for $W_-$ with pairing given by $\<u, v\> = 1$.
-
-We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.
+\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
+\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
+\end{itemize}
+The field $\lambda$ transforms in the defining representation of $G_R = \spin(2; \CC)$.
+The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively under $G_R \cong \CC^\times$.
+
+The theory admits a unique twist:
+\begin{itemize}
+\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
+Such supercharges are automatically square-zero and are holomorphic.
+There is a compatible twisting homomorphism
+\[
+\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+\]
+\end{itemize}
 
@@
 
-The fields decompose as
-\[
-\begin{array} {lllcccccc}
-& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
-A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
-\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
-\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
-\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
-\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
-\end{array}
-\]
-The anti-fields decompose as
-\[
-\begin{array} {lllcccccc}
-& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
-A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
-\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
-\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
-\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
-\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
-\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
-\end{array}
-\]
+Choose a complex structure $L \subset V_\RR$. 
+Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
+\]
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
+
+Further, fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
+\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
+\item matter bosons $\phi \in \Omega^0(\CC ; R^*)$, $\gamma_0 \in \Omega^0(\CC ; R)$;
+\item matter fermions $\psi \in \Omega^{0}(\CC ; R^*)[1]$, $\gamma_{0,1} \in \Omega^{0,1}(\CC ; \fg)[-1]$;
+\item a ghost field $A_0 \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
+
+%
+%\[
+%\begin{array} {lllcccccc}
+%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+%c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
+%A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+%\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
+%\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
+%\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
+%\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
+%\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
+%\end{array}
+%\]
+%The anti-fields decompose as
+%\[
+%\begin{array} {lllcccccc}
+%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+%c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
+%A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
+%\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
+%\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
+%\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
+%\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
+%\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
+%\end{array}
+%\]
 
@@
 \begin{align*}
-S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0})  \right)  \\
-S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi})) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} \wedge \partial_{A_{1,0}} \psi_{0})  + \\
-&\qquad + (([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1}) )   \bigg) \\
-S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \beta_{1,1} + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \beta_{1,0} + [\psi_0, A_0] \psi_{1,1}^* \\
-I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
-I^{(1)}_{\mr{matter}} &=  \int \left( (\psi_{1,1}^*, \Bar{\phi}) + \frac 12(\beta_{1,0} \wedge \dbar \gamma_0) \right)\\
-I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
+S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} , \dbar_{A_{0,1}} \lambda_{0}) \bigg)    \\
+S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi}) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} , \partial_{A_{1,0}} \psi_{0})  + \\
+&\qquad + ([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \\
+S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} A_0 , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) + ([\lambda_{1,0}, A_0], \lambda_{1,0}^*) +  [\lambda_{0}, A_0] \lambda_{0}^*\\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \gamma_0^* + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^* + [\psi_0, A_0] \psi_{0}^*\bigg) \\
+S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda_{1,0}, A_{1,0}^*) \bigg) \\
+S^{(1)}_{\mr{matter}} &=  \int \dvol \bigg( (\psi_{0}^*, \Bar{\phi}) + \frac 12(\dbar \gamma_0, \gamma_{0,1}^*) \bigg)\\
+S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda_0^*)^2 \bigg) .
 \end{align*}
@@
 
-\begin{theorem}[See also \cite{SWchar}] \label{2d(0,2)}
-The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
+\begin{theorem}
+The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+This equivalence is $\U(1)$-equivariant.
 \end{theorem}
@@
 The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
+First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_0^*)$.  
 Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
@@
 \begin{align*}
- S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + \beta_{1,0} \dbar_{A_{0,1}} \gamma_{0} \\ 
-  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [\gamma_0, A_0]\wedge \beta_{1,1} + [\gamma_{0,1}, A_0]\wedge \beta_{1,0}  \bigg).
+& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+  [\gamma_0, A_0] \gamma_0^*  \bigg).
 \end{align*}
-This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{1,\bu}$ comprise the fields of the $\beta\gamma$ system.
+This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic $BF$ theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
 \end{proof}

### 2020-02-19 paper.tex
5d-4d intro edits

--- 2020-02-19 paper.tex
@@
 To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
-This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}.
-In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+This theory of renormalization can been used to study field theories with and without supersymmetry.
+\brian{many citations} \chris{I'm not sure what you want to cite here.} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
- \[F = \ast (\Omega\wedge F).\]
+\begin{equation} 
+ F = \ast (\Omega\wedge F).
+ \end{equation}
 \end{itemize}
@@
 If we denote by $\psi$ the calibration 4-form on a $G_2$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying
-\[d_A\sigma = \ast(F_A\wedge \psi).\] 
+\begin{equation}
+d_A\sigma = \ast(F_A\wedge \psi).
+\end{equation}
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
 In general, this theory is only $\ZZ/2\ZZ$-graded.
-If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/\fg$.
+If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/G$.
 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
-This twist is also calculated in the forthcoming work of Dylan Butson \cite{Butson}.
+This twist is also calculated in a forthcoming work of Dylan Butson \cite{Butson}.
  \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}.
-If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
-\begin{align*}
+If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
+\begin{align}
 F_{0, 2} + \ol\dd^*_A u &= 0 \\
-\Lambda F_{1, 1}\wedge \omega^2 + [u, \bar{u}] + \lambda \omega^3 &= 0.
-\end{align*}
-\pavel{$\lambda$ to be explained.}
+F_{1, 1}\wedge \omega^2 + [u, \bar{u}] &= 0.
+\end{align}
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.
-This twist is equivalent to a generalized form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.
-It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).
-This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.
-If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized BF theory valued in the adjoint quotient $\gg/\gg$.
- \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist with four invariant directions.
-This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.
-It is invariant for the group $\spin(2;\RR) \times \spin(3;\RR)$ and can be defined on the product of a 2-manifold and a 3-manifold, each equipped with a spin structure.
-This twist was considered in \cite{ElliottPestun} on manifolds of the form $\Sigma \times C \times S^1$, where $\Sigma$ and $C$ are Riemann surfaces, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
- \item \emph{$\mc N=2$ topological A twist.} There are two topological twists in 5d $\mc N=2$.
-One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1,1)$ super Yang-Mills theory.
-It is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the intermediate twist.
-The full family is invariant for the group $\Spin(3;\RR)$.
-This theory was studied by Qiu and Zabzine, \cite{QiuZabzine}, where the equations of motion were shown to include the Haydys-Witten equations.
-Twisting homomorphisms in this situation were previously studied by Anderson \cite{Anderson}.
- \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with 5d Chern-Simons theory.
-This theory is only $\ZZ/2\ZZ$-graded, and it is invariant for the group $\spin(3;\RR)$.
-This twist was identified in work of Geyer-M\"ulsch and of Bak-Gustavsson\cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} The minimal twist of 5d $\cN=1$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to a theory defined on a product of a Calabi--Yau surface $X$ and a real 1-manifold $M$.
+The classical solutions are given by maps from $X\times M$ to the symplectic reduction of $U$ holomorphic along $X$ and locally-constant along $M$.
+In general, this theory is only $\ZZ/2\ZZ$-graded.
+It was studied by K\"all\'en and Zabzine \cite{KallenZabzine}.
+If $U=T^* R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of maps from $X\times M$ to $R/G$ holomorphic along $X$ and locally-constant along $M$.
+5d $\cN=2$ super Yang--Mills corresponds to the special case $R=\fg$.
+ \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case the minimal twist admits a deformation to an intermediate twist.
+The corresponding theory is equivalent to a generalized BF theory defined on a product of a complex curve $C$ and a real 3-manifold $M$.
+The twist was considred in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
+ \item \emph{$\mc N=2$ topological A twist.} The intermediate twist admits a deformation to two topological twists.
+One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1, 1)$ super Yang--Mills theory.
+This theory is perturbatively trivial.
+It was studied by Qiu and Zabzine, \cite{QiuZabzine} (see also \cite{Anderson} for a discussion of the twisting homomorphism).
+The partition function of this theory counts solutions to the Haydys--Witten equations \cite{Haydys,WittenFivebranes}.
+Let $M$ be a $K$-contact manifold and denote by $R$ the Reeb vector field.
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $B\in\Omega^2(M; \mathrm{ad} P)$ satisfying a self-duality equation $\iota_R \ast B = B$ which together satisfy the following equations (see \cite[equations (4) and (5)]{QiuZabzine}; we refer there for the explanation of the notation):
+\begin{align}
+\iota_R F - (d_A^* B)^H &= 0 \\
+F^+_H - \frac{1}{4}B\times B - \frac{1}{2}\iota_R d_A B &= 0.
+\end{align} 
+ \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with a 5d Chern--Simons theory defined on an oriented 5-manifold.
+Note that this theory is only $\ZZ/2\ZZ$-graded.
+This twist was identified in work of Geyer--M\"ulsch and of Bak--Gustavsson \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.
-This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.
-It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.
-In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.
-In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.
-Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.
+ \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
 This twist was studied by Johansen \cite{Johansen}.
- \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
-This twist is equivalent to a generalized version of BF theory with two real directions and one complex holomorphic direction, coupled to a generalized version of a $U$-valued symplectic boson.
-This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.
-This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
- \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.
-This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.
-Its equations of motion include the Donaldson-Witten equations.
-If the supersymmetry is promoted to $\mc N=4$, then this theory is identified either with the theory studied by Vafa and Witten, \cite{VafaWitten}, or with the A-twist studied by Kapustin and Witten \cite{KapustinWitten}, depending on the twisting homomorphism one uses to make the twisted theory $\spin(4;\RR)$-invariant.
- \item \emph{$\mc N=4$ topological B twist.} If $\mc N=4$, there are additional topological twists.
-The most important one is the Kapustin-Witten B-twist \cite{KapustinWitten}.
-This theory is obtained by dimensional reduction from the B-twist of 5d $\mc N=2$, or by twisting by a special supercharge of rank $(2,2)$.
-It is equivalent to a topological BF theory.
-This theory is $\spin(4;\RR)$-invariant using the Kapustin-Witten twisting homomorphism, and can be defined on arbitrary 4-manifolds.
- \item \emph{More general $\mc N=4$ topological twists} In the $\mc N=4$ case, the B-twist fits into a larger family of topological twists, most of which are perturbatively trivial.
-A $\bb{CP^1}$-family of such twists, generically of rank $(2,2)$, was studied by Kapustin and Witten \cite{KapustinWitten}, which is invariant for $\spin(4;\RR)$ using the Kapustin-Witten twisting homomorphism.
-There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.
-An analysis of these twists using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
+ \item \emph{$\cN=2$ and $\cN=4$ holomorphic twist.} We may also consider holomorphic twists of 4d $\cN=2$ and 4d $\cN=4$ super Yang--Mills theories.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of holomorphic maps from a Calabi--Yau surface $X$ to the Hamiltonian reduction of $U$.
+4d $\cN=4$ super Yang--Mills corresponds to the case $U=T^*\fg$ in which case the space of classical solutions is a $(-1)$-shifted cotangent bundle to the moduli stack of $G$-Higgs bundles on a complex surface $X$.
+ \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.} There is a deformation of the $\cN=2$ holomorphic twist which is equivalent to a theory of maps from a product of a Calabi--Yau curve $C$ and an oriented surface $\Sigma$ into the Hamiltonian reduction of $U$ which are holomorphic along $C$ and locally-constant along $\Sigma$.
+This twist was previously studied by Kapustin \cite{KapustinHolo}.
+ \item \emph{$\mc N=2$ topological rank (2, 0) twist.} The $\cN=2$ holomorphic twist admits a deformation to a topological twist, the \emph{Donaldson twist}.
+This theory is perturbatively trivial.
+This theory was first considered in \cite{WittenTQFT}, and the coupling to matter was studied in \cite{AnselmiFre, AlvarezLabastida, HyunParkPark}.
+The partition function counts solutions to nonabelian Seiberg--Witten equations \cite{Pidstrigach}.
+Let $G_\RR$ be a compact Lie group and $U$ a quaternionic-unitary $G_\RR$-representation.
+In particular, $U$ carries a commuting $\SU(2)$-action given by unit quaternions.
+Suppose $M$ is a spin 4-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(4)$-principal bundle.
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \SU(2)} U)$ which together satisfy
+\begin{align}
+\sd \d_A u &= 0 \label{eq:SW1} \\
+F^+ + \Phi(u) &= 0, \label{eq:SW2}
+\end{align}
+where $\Phi$ is the moment map and $\sd\d_A$ is the Dirac operator (we refer to \cite{Pidstrigach,HaydysDirac} for more details).
+
+\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for 4d $\cN=4$ super Yang--Mills, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e.
+there are three ways of interpreting the differential equations on arbitrary oriented 4-manifolds.
+First, considering 4d $\cN=4$ super Yang--Mills as a 4d $\cN=2$ super Yang--Mills with $U=\fg\otimes\mathbb{H}$, we obtain a theory which counts solutions to the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}.
+Another twisting homomorphism was studied by Vafa and Witten \cite{VafaWitten}.
+The corresponding theory counts solutions of the Vafa--Witten equations on an oriented 4-manifold $M$.
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a self-dual two-form $B\in\Omega^{2, +}(M, \mathrm{ad} P)$ and a section $C\in\Gamma(M, \mathrm{ad} P)$ which satisfy
+\begin{align}
+-\d_A C + \d_A^* B &= 0 \\
+F^+ - \frac{1}{4}B\times B - \frac{1}{2}[C, B] &= 0.
+\end{align}
+Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus} and Kapustin and Witten \cite{KapustinWitten}.
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
+\begin{align}
+(F-\phi\wedge \phi)^+ &= 0\\
+(\d_A \phi)^- &= 0 \\
+\d^*_A \phi &= 0.
+\end{align}
+
+ \item \emph{$\mc N=4$ topological B twist.} For 4d $\cN=4$ super Yang--Mills there is a single topological twist which is not perturbatively trivial.
+It is equivalent to a topological BF theory defined on a 4-manifold (this theory corresponds to the value $t=\pm i$ of the family considered in \cite{KapustinWitten}).
+
+ \item \emph{$\cN=4$ topological rank $(2, 2)$ twist.} The $\cN=4$ topological B twist admits a deformation to a perturbatively trivial theory.
+The corresponding deformation is parametrized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
+Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$.
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
+\begin{align}
+(F-\phi\wedge\phi +t \d_A \phi)^+ &= 0 \\
+(F-\phi\wedge\phi -t^{-1}\d_A \phi)^- &= 0 \\
+\d^*_A \phi &= 0.
+\end{align}
+
+\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge.
+The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow C\times \Sigma$ together with a connection $A$ and a section $\phi\in\Gamma(C\times \Sigma, \mathrm{ad} P)$ which satisfy
+\begin{align}
+(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
+(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
+\d^*_A \phi &= 0.
+\end{align}
+Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
+
+An analysis of topological twists of 4d $\cN=4$ super Yang--Mills using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
 \end{itemize}
@@
 
-\pagestyle{standard}
 \part{Supersymmetric Gauge Theory} \label{formalism_part}
@@
 Let $(E, \omega, S)$ be a classical field theory. An \defterm{action} of a super Lie algebra $\fg$ on $(E, \omega, S)$ is an element 
-\[S_\fg = \sum_{k\geq 0} S_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
-of cohomological degree zero, where $S_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
-\begin{itemize}
-\item[(a)] $S_\fg^{(0)} = S$.
-\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $S^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
-\item[(c)] $S_\fg$ satisfies the Maurer--Cartan equation:
-\[\d_{\mr{CE}} S_\fg + \frac{1}{2} \{S_\fg, S_\fg\} = 0.\]
+\[\fS_\fg = \sum_{k\geq 0} \fS_{\fg}^{(k)}\in C^\bullet(\fg, \oloc(\cE))\]
+of cohomological degree zero, where $\fS_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
+\begin{itemize}
+\item[(a)] $\fS_\fg^{(0)} = S$.
+\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $\fS^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
+\item[(c)] $\fS_\fg$ satisfies the Maurer--Cartan equation:
+\[\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0.\]
 \end{itemize}
@@
 \begin{remark}
-We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $S_\fg$.
+We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $\fS_\fg$.
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
@@
 
-\item An action $S_\fg$ of its super Lie algebra $\fg$ with $S^{(k)}_\fg = 0$ for $k\geq 2$ 
+\item An action $\fS_\fg$ of its super Lie algebra $\fg$ with $\fS^{(k)}_\fg = 0$ for $k\geq 2$ 
 \end{itemize}
@@
 
-\item For every $x\in\fg$, the vector field $X_{{S^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
+\item For every $x\in\fg$, the vector field $X_{{\fS^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
 \end{itemize}
@@
 \[
-S_{\fA} = S + \sum_{k \geq 1} S_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
-\]
-where $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
+I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
+\]
+where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.
 
@@
 The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
-\[S^Q = S + \sum_{k \geq 1} S_{\fA}^{(k)}(Q, \dots, Q).\]
+\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
 \end{definition}
@@
 
-\subsection{Super Yang--Mills Theory: pure gauge theory}
+\subsection{Pure Super Yang--Mills Theory}
 \label{sect:gaugemultipletSUSY}
@@
 \begin{definition}
-\label{def:sym}
 The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
@@
 \begin{equation}
-S_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
+I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
 \label{eq:YMPoincareaction}
@@
 \begin{align}
-S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
-S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
+I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
+I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right).
 \label{eq:gaugeI2}
@@
 \begin{theorem}\label{thm:gaugemultipletSUSY}
-The functional $S_{\gauge, \fA} = S_{\gauge} + S_{\gauge}^{(1)} + S_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
-\[\d_{\mr{CE}} \left(S_{\gauge, \fA}\right) + \frac{1}{2}\{S_{\gauge, \fA}, S_{\gauge, \fA}\} = 0.\]
-\end{theorem}
-
-This result implies that the pure gauge sector of super Yang--Mills theory carries an $L_\infty$ action by the super Lie algebra $\fA$.
-We consider coupling to matter in the next section.
+The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
+\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
+Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
+\end{theorem}
 
@@
 \begin{align*}
-\{S_{\gauge}, S_{\gauge}^{(1)}\} &= 0 \\
-\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} &= 0 \\
-\d_{\mr{CE}} S_{\gauge}^{(2)} + \{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\} &= 0 \\
-\{S_{\gauge}^{(2)}, S_{\gauge}^{(2)}\} &= 0.
+\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
+\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
+\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
+\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
 \end{align*}
 
-Note that the last equation is automatically satisfied since $S_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
+Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$.
 The rest of the claims will be proved in a sequence of Lemmas.
@@
 \begin{lemma}
-For each $Q\in \Sigma$, one has $\{S_{\gauge}, S_{\gauge}^{(1)}(Q)\} = 0$.
+One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
 \label{lm:gaugemultiplet1}
@@
 \begin{proof}
-Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge, i}$ into individual summands of Equation (\ref{eq:YMBVaction}).
+Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.
 
@@
 \begin{align*}
-\{S_{\gauge, 1}, S_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
+\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
 &= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
@@
 \begin{align*}
-\{S_{\gauge, 2}, S_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
+\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
 &= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
@@
 
-By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_1 + S_2, S_{\gauge}^{(1)}(Q)\} = 0$.
-
-Finally, $\{S_{\gauge,3} + S_{\gauge,4} + S_{\gauge, 5}, S_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $S_{\gauge}^{(1)}(Q)$.
+By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.
+
+Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
 \end{proof}
@@
 One has
-\[\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} = 0.\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
 \label{lm:gaugemultiplet2}
@@
 Evaluating the equation
-\[\{S_{\gauge}, S_{\gauge}^{(2)}\} + \d_{\mr{CE}} S_{\gauge}^{(1)} + \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\} = 0\]
+\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
 on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $S_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.
@@
 \begin{align*}
-\frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\gauge}^{(1)}(Q_2)\} \\
+\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
 = &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
@@
 \begin{align*}
-(\d_{\mr{CE}} S_{\gauge}^{(1)})(Q_1, Q_2) &= S_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
+(\d_{\mr{CE}} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
 &= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
@@
 \begin{align*}
-\{S_{\gauge}, S_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
+\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
 &+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
@@
 Evaluating the equation
-\[\d_{\mr{CE}} S_{\gauge}^{(2)} + \{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\} = 0\]
+\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
 on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero.
-Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $S_{\gauge}^{(2)}$.
+Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.
 
 \begin{lemma}
-One has
-\[\{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in\Sigma$.
@@
 \begin{align*}
-\{S_{\gauge}^{(1)}(Q_1), S_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
+\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
 &+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
@@
 
-$\{S_{\gauge}^{(1)}, S_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
+$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression.
 By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero.
@@
 The BV action for the matter multiplet is
-\begin{equation}\label{matteraction}
+\[
 S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
-\end{equation}
+\]
 where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.
@@
 \begin{equation}
-S_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
+I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
 \label{eq:matterPoincareaction}
@@
 \begin{align}
-S_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
-S_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
+I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
+I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
 \end{align}
@@
 We consider the full action of the super Yang--Mills theory
-\[S_{\rm SYM} = S_{\gauge} + S_{\matter}\]
-where $S_{\gauge}$ is the BV action of the pure gauge sector of super Yang--Mills theory defined in Equation \eqref{eq:YMBVaction}.
-
-The action by supersymmetry on the full theory is encoded by the $\fA$-dependent functionals
-\[S^{(1)} = S^{(1)}_{\gauge} + S^{(1)}_{\matter},\qquad S^{(2)} = S^{(2)}_{\gauge} + S^{(2)}_{\matter}\]
-where $S^{(1)}_\gauge, S^{(2)}_\gauge$ are as in Equations (\ref{eq:gaugeI1}), (\ref{eq:gaugeI2}).
+\[S_{\BV} = S_{\gauge} + S_{\matter}\]
+together with a supersymmetry action functionals
+\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]
+
 The following result states that these functionals encode an off-shell action of the supersymmetry algebra.
@@
 \begin{theorem}
-The functional $S_{\fA} = S_{\rm SYM} + S^{(1)} + S^{(2)}$ satisfies the classical master equation
+The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
 \begin{equation}
 \label{CMEYM}
-\d_{\mr{CE}} S_\fA + \frac{1}{2} \{S_\fA, S_\fA\} = 0 .
+\d_{\mr{CE}} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
 \end{equation}
-Thus, according to Definition \ref{infinitesimal_action_def}, the functional $S_{\fA}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric
 \label{thm:YMSUSY}
@@
 
-The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. 
-Notice that when we take the matter to be valued in a trivial representation for the Lie algebra $\fg$, the result reduces to Theorem \ref{thm:gaugemultipletSUSY}.
-We may therefore restrict our attention to the terms in \eqref{CMEYM} which involve fields of the matter multiplet. 
-Consequently, the classical master equation \eqref{CMEYM} decomposes into the following set of equations:
+The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
 \begin{equation}
@@
 \begin{array}{rrrrrr}
-\{S_{\rm SYM} , S^{(1)}\} & = & 0 \\ 
-\{S_{\matter}, S^{(2)}\} + \d_{\mr{CE}} S_{\matter}^{(1)} + \{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\} + \frac{1}{2} \{S_{\matter}^{(1)}, S_{\matter}^{(1)}\} & = & 0 \\
-\d_{\mr{CE}} S_{\matter}^{(2)} + \{S_{\matter}^{(1)}, S_{\matter}^{(2)}\} & =& 0 \\
-\{S_{\matter}^{(2)}, S_{\matter}^{(2)}\} & =& 0
+\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
+\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
+\d_{\mr{CE}} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
+\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
 \end{array}
@@
 
-The last equation is automatically satisfied since $S^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
+The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.
 
@@
 \begin{lemma} \label{lem:YM1}
-One has $\{S_{\rm SYM}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
 \end{lemma}
 \begin{proof}
-Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter, i}$ into the individual summands in Equation \eqref{matteraction}.
+Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.
 
@@
 \begin{align*}
-\{S_{\matter,1}, S^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
+\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
 &= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
@@
 \begin{align*}
-\{S_{\matter,2}, S^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
+\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
 &= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
@@
 \begin{align*}
-\{S_{\matter,3}, S^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
+\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
 &= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
@@
 where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
-\[\{S_{\matter,1} + S_{\matter,2} + S_{\matter,3}, S^{(1)}(Q)\} = 0.\]
-
-Finally, the terms $\{S_{\matter,4} + S_{\matter,5} + S_{\gauge,3}, S^{(1)}(Q)\}$ are zero due to gauge-invariance of $S^{(1)}(Q)$, while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
+\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]
+
+Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
 \end{proof}
@@
 \begin{equation}\label{CMEYM3}
-\{S_{\matter}, S^{(2)}\} + \d_{\mr{CE}} S_{\matter}^{(1)} + \{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\} + \frac{1}{2} \{S_{\matter}^{(1)}, S_{\matter}^{(1)}\} = 0 .
+\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
 \end{equation}
@@
 \begin{align*}
-\frac{1}{2}\{S_{\matter}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{S_{\matter}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} \\
+\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
 =&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
@@
 \begin{align*}
-\{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} - \{S_{\gauge}^{(1)}(Q_2), S_{\matter}^{(1)}(Q_1)\} \\
+\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
 =& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
@@
 \[
-(\d_{\mr{CE}}S_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
+(\d_{\mr{CE}}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
 \]
@@
 \[
-\{S_{\matter}, S^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
+\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
 \]
@@
 \begin{lemma}
-One has
-\[\{S_{\matter}^{(1)}, S_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
+\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
 for every $Q_1, Q_2, Q_3\in \Sigma$.
@@
 \begin{align*}
-\{S_{\matter}^{(1)}(Q_1), S_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
+\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
 \end{align*}
 The expression
-$\{S_{\matter}^{(1)}, S_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
+$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
 \end{proof}
@@
 
-Let $Q\in\Sigma$ be a square-zero supercharge, which we will fix for the rest of this section. 
+Let $Q\in\Sigma$ be a square-zero supercharge.
 The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$.
@@
 
-Let $\ML(L) = \ML(5)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
+Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
 \[\Sigma = \det(L)^{1/2} \oplus \wedge^2 L^*\otimes \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2}.\]
@@
 Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it.
-The BV action of the twisted theory $S_{\mr{twist}}$ is then the sum of the following terms:
+The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
 \begin{align}
@@
 S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
-S^{(1)}(Q) &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
-S^{(2)}(Q) &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+I^{(1)} &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
+I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
 \end{align}
-The first two terms comprise the action of supersymmetric Yang--Mills theory $S_{\rm SYM} = S_{\rm gauge}$ of Definition \ref{def:sym} written with respect to the $\ML(L) = \ML(5)$ decomposition. 
-The last two terms arise from the twisting procedure.
 
@@
 First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.
-So, the above theory described by $S_{\rm twist}$ is perturbatively equivalent to the theory without the fields $\chi$ and $\chi^*$ with the BV action
+So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
 \begin{align*}
@@
 
-Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e. $(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it. 
-The above theory described by $S_{{\rm no } \chi}$ is perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
+Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e.
+$(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it.
+The above theory then becomes perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
@@
 \]
-Up to rescaling of the antifields by the rule
-\[
-\alpha^* \mapsto \Omega^{-1} e^{\omega} (\alpha^*)
-\]
-the fields and action coincide precisely with those of holomorphic Chern--Simons theory (see Section \ref{gen_CS_section}).
+Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
 \end{proof}
@@
 \item Scalar fields $a\in\Omega^{4,0}(M; \gg)[2]$ and $\wt a\in\Omega^{0, 4}(M; \gg)[-2]$.
-\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{4, 1}(M; \gg)[1]$.
-%Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
+\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
 \end{itemize}
-\brian{I've changed where $C$ lives to fit the proof below.}
 
@@
 Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt a, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
-%\[
-%\xymatrix@R=0.5cm@C=0.5cm{
-%&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{a^*} \\
-%&&\ar@{}^{\bigoplus}[r] &&& \\
-%\Omega^{4,0}(\CC^4; \gg)_{a} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
-%}
-%\]
 \[
@@
 \begin{align*}
-S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
-S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) \\
+I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right).
 \end{align*}
@@
 The action of the twisted 8d super Yang--Mills theory is given by
-\[S_{Q_t} = S_{\rm SYM} + S^{(1)}(Q_t) + S^{(2)}(Q_t),\]
+\[S_{Q_t} = S_{\mathrm{BRST}} + S_{\mathrm{anti}} + I^{(1)}(Q_t) + I^{(2)}(Q_t),\]
 where $S_{\mathrm{BRST}}$ and $S_{\mathrm{anti}}$ are given by \eqref{eq:10dBRST} and \eqref{eq:10danti} respectively.
@@
 We are left with the action
-\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
+\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
 where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
@@
 
-Consider a nonzero $Q\in S_+\otimes W_+$ which we fix for the remainder of this section.
+Consider a nonzero $Q\in S_+\otimes W_+$.
 Since $\wedge^2(S_+)\cong V$, the square-zero condition is equivalent to the condition that $Q$ has rank 1, i.e.
@@
 
-Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{twist}}$ of the $Q$-twisted theory consists of the sum of the following terms:
+Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
 
@@
 &\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
-S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*)  +  [\xi, c] \xi^* + [\chi, c]\chi^* +[\rho, c] \rho^* + \\
-&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c] \nu^* + [\phi, c] \phi^* + [\psi, c] \psi^* + [\wt\nu, c] \wt\nu^* \bigg) + [B, c]\wedge B^* \\
-S^{(1)}_{\gauge} (Q) &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
-S^{(1)}_{\matter} (Q) &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
-S^{(2)}_{\gauge} (Q) &= -\frac{1}{4}\int \dvol (\chi^*)^2.
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
+&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
+I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
+I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
+I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
 \end{align*}
@@
 In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
-The twisted theory $S_{\rm twist}$ is therefore perturbatively equivalent to the theory with the BV action
+The twisted theory is therefore perturbatively equivalent to the theory with the BV action
 \begin{align*}
-& \int \bigg(\xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \bigg) \\
- &+ \int \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + [B, c] \wedge B^* .
+ S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
+ &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
 \end{align*}
-Up to rescaling the antifields, this is the action functional of the required theory.
+Up to rescaling of the antifields, this is the action functional of the required theory.
 %where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
@@
 S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
-S_{\mr{matter}} &= \int \dvol \bigg((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi) + ([A_{0,2}, \beta_{2,0}], \phi) \bigg) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
-&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0})  ) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) \\
-S_{\mr{anti}} &= \int \dvol \bigg((\dd_{A_{1, 0}} A_0, A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) \bigg) +  \\
-& \qquad + \dvol \bigg([A_0, \lambda_0] \lambda_0^* + [A_0, A_{0,2}] A_{0,2}^* \bigg) + [\lambda_{1,0}, A_0] \wedge \lambda_{1,0}^* + \dvol \frac{1}{2}[A_0, A_0]A_0^*\\ 
-&\qquad  + \dvol \bigg( [\phi, A_0] \phi^* + [\gamma_0, A_0] \gamma_0^*  + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \beta_{2,0}^* \bigg) + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^*\\
-I^{(1)}_{\mr{gauge}} &=  \int  \dvol - (\lambda_{1,0} A_{1,0}^*)  + \frac 12  \left(F_{0,2}\wedge A_{0,2}^*+ \omega\wedge F_{1,1} \lambda_0^*  \right) \\
-I^{(1)}_{\mr{matter}} &=  \int  \dvol \left( \psi_0 \phi^* + \frac 12 ( \ol \dd_{A_{0,1}} \gamma_{0} , \gamma_{0,1}^*) \right)\\
+S_{\mr{matter}} &= \int \dvol \left((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)\right) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
+&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )  \\
+S_{\mr{anti}} &= \int \bigg(\dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0 \wedge B_{2, 1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* + \dvol ([\lambda_{0}, A_0], \lambda_{0}^*) + [A_0, A_{0,1}]\wedge B_{2, 1} + [A_{0}, A_{1,0}]\wedge A_{1, 0}^* \\
+&\qquad + \frac{1}{2}[A_0, A_0]B_{2, 2} + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \bigg) \\
+I^{(1)}_{\mr{gauge}} &=  \int  \left( - \lambda_{1,0}\wedge A_{1,0}^* + \frac 12 F_{0,2}\wedge B_{2,0} + \frac 12 \omega\wedge F_{1,1} \lambda_0^*  \right) \\
+I^{(1)}_{\mr{matter}} &=  \int  \left( \psi_0 \phi^* + \frac 12 \ol \dd_{A_{0,1}} \gamma_{0}\wedge \beta_{2,1} \right)\\
 I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
@@
 \begin{align*}
-S_{\rm BV} & = \int \dvol \bigg((A_{0,1}^* \ol \dd_{A_{0,1}} A_{0}) + (\dbar_{A_{0,1}} \gamma_0, \gamma_{0,1}^*)\bigg) + F_{0,2} \wedge A_{0,2}^* + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} \\ & \qquad + \dvol \bigg([A_0, A_{0,2}] A_{0,2}^* + \frac{1}{2} [A_0,A_0] A_0^* + [A_0, \gamma_0] \gamma_0^* + [A_0, \gamma_{0,1}] \gamma_{0,1}^* + [A_0, \beta_{2,0}^*] \beta_{2,0}\bigg)
+ S_{\mr{BV}} &= \int \bigg( (B_{2,1} \ol \dd_{A_{0,1}} A_{0})  + B_{2,0} F_{0,2} + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} + \beta_{2,1} \dbar_{A_{0,1}} \gamma_0 \\ 
+  &\qquad  + [A_{0,2}, A_0]\wedge B_{2,0} + \frac{1}{2}[A_0, A_0]B_{2,2} +  [\gamma_0, A_0]\wedge \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1}  \bigg).
 \end{align*}
-
-Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic $BF$ theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{2,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{2,\bu}$ comprise the fields of the $\beta\gamma$ system.
 \end{proof}
@@
 \begin{align*}
-S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
 & + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
@@
 %&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
-S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
-S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
-S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
 \end{align*}
@@
 \begin{itemize}
- \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
  \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
@@
 \subsubsection{Minimal Twist} \label{sect:2d22minimaltwist}
-
-First, we record the minimal twist of 2d $\cN=(2,2)$ supersymmetric Yang--Mills theory.
 
@@
 \end{itemize}
-
-\begin{itemize}
-\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Bar{a} \in \Omega^0(\CC ; \fg)[2]$. 
-\item $\gg$-valued fermions: $\lambda \in \Omega^{??}(\CC ; \fg)[-1]$, $\Bar{\lambda} \in \Omega^{??}(\CC ; \fg) [-1]$, $\lambda' \in \Omega^{0,1}(\CC ; \fg)[1]$, $\Bar{\lambda}' \in \Omega^{??}(\CC ; \fg)[1]$.
- %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
- %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
- \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
-\end{itemize}
 We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
@@
 \begin{align*}
-S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
 &+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
-S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
-S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
-S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
+I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
+I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
+I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
 \end{align*}
@@
 \begin{proof}
-We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
-We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
-We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
-The resulting action functional is of the form
-\[
-S_{BF} + \int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right)\]
-Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
-
-We can identify the linearized BV complex with the following diagram:
+We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$, integrating out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.
+We can then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}.
+At $t=0$, we are left with the holomorphic twist from Theorem \ref{2d_minimal_twist_thm}, i.e, the theory $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The action functional is further deformed by the remaining $t$-linear terms, which together take the form
+\[\int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right).\]
+In terms of the classical BV complex we can identify these terms as introducing the following dotted isomorphism between two summands:
 \[\xymatrix@R=0.4cm@C=0.2cm{
@@
 }\]
-Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
 This is exactly the deformation to $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
@@
 
-Finally, there is the $B$-twist of 2d $\cN=(2,2)$ supersymmetry.
-This twist arises from the twist of 3d $\cN=2$ via dimensional reduction in a non-invariant direction.  
-Indeed, let $W_3$ be the two-dimensional auxiliary space in the 3d $\mc N=2$ supertranslation algebra.  
-As a $\spin(2;\CC)$-representation, the 3d $\cN=2$ spinorial representation decomposes as $S_+ \otimes W_3 \oplus S_- \otimes W_3$.
-Generically, rank one square zero elements in 3d $\mc N=2$ supersymmetry define rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.  
+Finally, there is the 2d B-twist.
+This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
+Indeed, let $W_3$ be the 2d auxiliary space in the 3d $\mc N=2$ supertranslation algebra.
+The 3d spin representation $S \otimes W_3$ splits into $S_+ \otimes W_3 \oplus S_- \otimes W_3$ as a $\spin(2;\CC)$-module.
+Rank one square zero elements in 3d $\mc N=2$ generically become rank $(1,1)$ square zero elements in the 2d $\mc N=(2,2)$ supersymmetry algebra.
 There is a square-zero supercharge in 3d $\mc N=2$ compatible with the identity twisting homomorphism $\spin(2;\CC) \to \spin(2;\CC)$.

### 2020-02-19 paper.tex
typo fixed

@@
 \item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge.
-The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow C\times \Sigma$ together with a connection $A$ and a section $\phi\in\Gamma(C\times \Sigma, \mathrm{ad} P)$ which satisfy
+The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
 \begin{align}

### 2020-02-19 paper.tex
merge

@@
 In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation.
-We do not consider superpotential, mass, or Fayet--Iliopoulos terms in this paper.
+We do not consider superpotential and mass terms in this paper.
 Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).
@@
 If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
-\begin{equation} 
- F = \ast (\Omega\wedge F).
- \end{equation}
+ \[F = \ast (\Omega\wedge F).\]
 \end{itemize}
@@
 If we denote by $\psi$ the calibration 4-form on a $G_2$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying
-\begin{equation}
-d_A\sigma = \ast(F_A\wedge \psi).
-\end{equation}
+\[d_A\sigma = \ast(F_A\wedge \psi).\] 
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
 In general, this theory is only $\ZZ/2\ZZ$-graded.
-If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/G$.
+If $U=T^*R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of holomorphic maps from a complex 3-fold to $R/\fg$.
 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
-This twist is also calculated in a forthcoming work of Dylan Butson \cite{Butson}.
+This twist is also calculated in the forthcoming work of Dylan Butson \cite{Butson}.
  \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}.
-If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
-\begin{align}
+If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
+\begin{align*}
 F_{0, 2} + \ol\dd^*_A u &= 0 \\
-F_{1, 1}\wedge \omega^2 + [u, \bar{u}] &= 0.
-\end{align}
+\Lambda F_{1, 1}\wedge \omega^2 + [u, \bar{u}] + \lambda \omega^3 &= 0.
+\end{align*}
+\pavel{$\lambda$ to be explained.}
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} The minimal twist of 5d $\cN=1$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to a theory defined on a product of a Calabi--Yau surface $X$ and a real 1-manifold $M$.
-The classical solutions are given by maps from $X\times M$ to the symplectic reduction of $U$ holomorphic along $X$ and locally-constant along $M$.
-In general, this theory is only $\ZZ/2\ZZ$-graded.
-It was studied by K\"all\'en and Zabzine \cite{KallenZabzine}.
-If $U=T^* R$, the theory is $\ZZ$-graded and is the cotangent theory to the space of maps from $X\times M$ to $R/G$ holomorphic along $X$ and locally-constant along $M$.
-5d $\cN=2$ super Yang--Mills corresponds to the special case $R=\fg$.
- \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case the minimal twist admits a deformation to an intermediate twist.
-The corresponding theory is equivalent to a generalized BF theory defined on a product of a complex curve $C$ and a real 3-manifold $M$.
-The twist was considred in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
- \item \emph{$\mc N=2$ topological A twist.} The intermediate twist admits a deformation to two topological twists.
-One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1, 1)$ super Yang--Mills theory.
-This theory is perturbatively trivial.
-It was studied by Qiu and Zabzine, \cite{QiuZabzine} (see also \cite{Anderson} for a discussion of the twisting homomorphism).
-The partition function of this theory counts solutions to the Haydys--Witten equations \cite{Haydys,WittenFivebranes}.
-Let $M$ be a $K$-contact manifold and denote by $R$ the Reeb vector field.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $B\in\Omega^2(M; \mathrm{ad} P)$ satisfying a self-duality equation $\iota_R \ast B = B$ which together satisfy the following equations (see \cite[equations (4) and (5)]{QiuZabzine}; we refer there for the explanation of the notation):
-\begin{align}
-\iota_R F - (d_A^* B)^H &= 0 \\
-F^+_H - \frac{1}{4}B\times B - \frac{1}{2}\iota_R d_A B &= 0.
-\end{align} 
- \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with a 5d Chern--Simons theory defined on an oriented 5-manifold.
-Note that this theory is only $\ZZ/2\ZZ$-graded.
-This twist was identified in work of Geyer--M\"ulsch and of Bak--Gustavsson \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.
+This twist is equivalent to a generalized form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.
+It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).
+This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.
+If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a generalized BF theory valued in the adjoint quotient $\gg/\gg$.
+ \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist with four invariant directions.
+This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.
+It is invariant for the group $\spin(2;\RR) \times \spin(3;\RR)$ and can be defined on the product of a 2-manifold and a 3-manifold, each equipped with a spin structure.
+This twist was considered in \cite{ElliottPestun} on manifolds of the form $\Sigma \times C \times S^1$, where $\Sigma$ and $C$ are Riemann surfaces, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
+ \item \emph{$\mc N=2$ topological A twist.} There are two topological twists in 5d $\mc N=2$.
+One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1,1)$ super Yang-Mills theory.
+It is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the intermediate twist.
+The full family is invariant for the group $\Spin(3;\RR)$.
+This theory was studied by Qiu and Zabzine, \cite{QiuZabzine}, where the equations of motion were shown to include the Haydys-Witten equations.
+Twisting homomorphisms in this situation were previously studied by Anderson \cite{Anderson}.
+ \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with 5d Chern-Simons theory.
+This theory is only $\ZZ/2\ZZ$-graded, and it is invariant for the group $\spin(3;\RR)$.
+This twist was identified in work of Geyer-M\"ulsch and of Bak-Gustavsson\cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
+ \item \emph{$\mc N=1$, $\mc N=2$ and $\mc N=4$ holomorphic twist.} There is a holomorphic twist in dimension 4, which makes sense with $\mc N=1$ supersymmetry, coupled to a chiral multiplet valued in a representation $R$.
+This twist is equivalent to holomorphic BF theory coupled to a $\beta \gamma$-system valued in the representation $R$.
+It is invariant for the action of $\mr U(2)$, and can be defined on arbitrary complex surfaces.
+In the case where $R = U \oplus \gg$ for a symplectic representation $U$, the $\mc N=1$ supersymmetry can be lifted to $\mc N=2$ supersymmetry, and the twisted theory is modelled by a holomorphic BF theory now coupled to a holomorphic symplectic boson.
+In general this theory is only $\mr MU(2)$-invariant, and depends on a choice of square root of the canonical bundle.
+Finally, if $U = T^*\gg$, the supersymmetry lifts further to $\mc N=4$, and the twisted theory is modelled by a Dolbeault version of holomorphic BF theory -- the moduli space of solutions to the equations of motion are represented by the shifted cotangent space to the moduli stack of $G$-Higgs bundles.
 This twist was studied by Johansen \cite{Johansen}.
- \item \emph{$\cN=2$ and $\cN=4$ holomorphic twist.} We may also consider holomorphic twists of 4d $\cN=2$ and 4d $\cN=4$ super Yang--Mills theories.
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of holomorphic maps from a Calabi--Yau surface $X$ to the Hamiltonian reduction of $U$.
-4d $\cN=4$ super Yang--Mills corresponds to the case $U=T^*\fg$ in which case the space of classical solutions is a $(-1)$-shifted cotangent bundle to the moduli stack of $G$-Higgs bundles on a complex surface $X$.
- \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.} There is a deformation of the $\cN=2$ holomorphic twist which is equivalent to a theory of maps from a product of a Calabi--Yau curve $C$ and an oriented surface $\Sigma$ into the Hamiltonian reduction of $U$ which are holomorphic along $C$ and locally-constant along $\Sigma$.
-This twist was previously studied by Kapustin \cite{KapustinHolo}.
- \item \emph{$\mc N=2$ topological rank (2, 0) twist.} The $\cN=2$ holomorphic twist admits a deformation to a topological twist, the \emph{Donaldson twist}.
-This theory is perturbatively trivial.
-This theory was first considered in \cite{WittenTQFT}, and the coupling to matter was studied in \cite{AnselmiFre, AlvarezLabastida, HyunParkPark}.
-The partition function counts solutions to nonabelian Seiberg--Witten equations \cite{Pidstrigach}.
-Let $G_\RR$ be a compact Lie group and $U$ a quaternionic-unitary $G_\RR$-representation.
-In particular, $U$ carries a commuting $\SU(2)$-action given by unit quaternions.
-Suppose $M$ is a spin 4-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(4)$-principal bundle.
-The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \SU(2)} U)$ which together satisfy
-\begin{align}
-\sd \d_A u &= 0 \label{eq:SW1} \\
-F^+ + \Phi(u) &= 0, \label{eq:SW2}
-\end{align}
-where $\Phi$ is the moment map and $\sd\d_A$ is the Dirac operator (we refer to \cite{Pidstrigach,HaydysDirac} for more details).
-
-\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for 4d $\cN=4$ super Yang--Mills, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e.
-there are three ways of interpreting the differential equations on arbitrary oriented 4-manifolds.
-First, considering 4d $\cN=4$ super Yang--Mills as a 4d $\cN=2$ super Yang--Mills with $U=\fg\otimes\mathbb{H}$, we obtain a theory which counts solutions to the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}.
-Another twisting homomorphism was studied by Vafa and Witten \cite{VafaWitten}.
-The corresponding theory counts solutions of the Vafa--Witten equations on an oriented 4-manifold $M$.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a self-dual two-form $B\in\Omega^{2, +}(M, \mathrm{ad} P)$ and a section $C\in\Gamma(M, \mathrm{ad} P)$ which satisfy
-\begin{align}
--\d_A C + \d_A^* B &= 0 \\
-F^+ - \frac{1}{4}B\times B - \frac{1}{2}[C, B] &= 0.
-\end{align}
-Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus} and Kapustin and Witten \cite{KapustinWitten}.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
-\begin{align}
-(F-\phi\wedge \phi)^+ &= 0\\
-(\d_A \phi)^- &= 0 \\
-\d^*_A \phi &= 0.
-\end{align}
-
- \item \emph{$\mc N=4$ topological B twist.} For 4d $\cN=4$ super Yang--Mills there is a single topological twist which is not perturbatively trivial.
-It is equivalent to a topological BF theory defined on a 4-manifold (this theory corresponds to the value $t=\pm i$ of the family considered in \cite{KapustinWitten}).
-
- \item \emph{$\cN=4$ topological rank $(2, 2)$ twist.} The $\cN=4$ topological B twist admits a deformation to a perturbatively trivial theory.
-The corresponding deformation is parametrized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
-Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
-\begin{align}
-(F-\phi\wedge\phi +t \d_A \phi)^+ &= 0 \\
-(F-\phi\wedge\phi -t^{-1}\d_A \phi)^- &= 0 \\
-\d^*_A \phi &= 0.
-\end{align}
-
-\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge.
-The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
-\begin{align}
-(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
-(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
-\d^*_A \phi &= 0.
-\end{align}
-Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
-
-An analysis of topological twists of 4d $\cN=4$ super Yang--Mills using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
+ \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.}  If $\mc N=2$ then there is an intermediate twist, with three invariant directions.
+This twist is equivalent to a generalized version of BF theory with two real directions and one complex holomorphic direction, coupled to a generalized version of a $U$-valued symplectic boson.
+This theory is $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and can be defined on the product of two Riemann surfaces.
+This twist is often referred to as the \emph{Kapustin twist} \cite{KapustinHolo}.
+ \item \emph{$\mc N=2$ and $\mc N=4$ topological A twist.} There is also a topological twist for $\mc N=2$, the \emph{Donaldson twist}, which is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the holomorphic twist.
+This theory was first considered in \cite{WittenTQFT}, and the coupling to a hypermultiplet of cotangent type was studied in \cite{AlvarezLabastida, HyunParkPark}.
+Its equations of motion include the Donaldson-Witten equations.
+If the supersymmetry is promoted to $\mc N=4$, then this theory is identified either with the theory studied by Vafa and Witten, \cite{VafaWitten}, or with the A-twist studied by Kapustin and Witten \cite{KapustinWitten}, depending on the twisting homomorphism one uses to make the twisted theory $\spin(4;\RR)$-invariant.
+ \item \emph{$\mc N=4$ topological B twist.} If $\mc N=4$, there are additional topological twists.
+The most important one is the Kapustin-Witten B-twist \cite{KapustinWitten}.
+This theory is obtained by dimensional reduction from the B-twist of 5d $\mc N=2$, or by twisting by a special supercharge of rank $(2,2)$.
+It is equivalent to a topological BF theory.
+This theory is $\spin(4;\RR)$-invariant using the Kapustin-Witten twisting homomorphism, and can be defined on arbitrary 4-manifolds.
+ \item \emph{More general $\mc N=4$ topological twists} In the $\mc N=4$ case, the B-twist fits into a larger family of topological twists, most of which are perturbatively trivial.
+A $\bb{CP^1}$-family of such twists, generically of rank $(2,2)$, was studied by Kapustin and Witten \cite{KapustinWitten}, which is invariant for $\spin(4;\RR)$ using the Kapustin-Witten twisting homomorphism.
+There are additional topological twists, including those of rank $(1,2)$, which are only invariant for the group $\spin(2;\RR) \times \spin(2;\RR)$.
+An analysis of these twists using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
 \end{itemize}
@@
 
-Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_{\rm anti}$.
+Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_0$.
 Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
-Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
+Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_0, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
 
@@
 Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory.
-The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
+The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_0$.
 \end{definition}
@@
 \begin{lemma} \label{lem:YM1}
-One has $\{S_{\rm SYM}, S^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
+One has $\{S_{\rm SYM}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
 \end{lemma}
@@
 S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
+&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
 S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
@@
 \begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 Fix the twisting datum $\alpha = \alpha_n$.
-The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
+The holomorphic twist of 4d $\cN=2$ super Yang--Mills is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
 Moreover, the equivalence is $\MU(2)$-equivariant.
@@
 \begin{itemize}
-\item gauge bosons $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$, $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
-\item gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
-\item matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
-\item matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
-\item a ghost field $c\in \Omega^0(M; \gg)[1]$.
+\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
+\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[-2]$ and $a \in\Omega^{0}(M; \gg)[2]$;
+\item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[-1]$.
+\item Matter bosons $\nu\in\Omega^{0, 1}(M; \fg)$, $\phi\in\Omega^{1,0}(M; \fg)$.
+\item Matter fermions $\psi \in \Omega^{1,1} (M;  \fg)[-1]$, $\varsigma \in \Omega^{1,0} (M ; \fg)[1]$, $\Tilde{\nu} \in \Omega^{0,1}(M; \fg)[1]$.
+\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
 \end{itemize}
@@
 \begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
- \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
- \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
- \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
- \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
+ \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
+ \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
+ \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
+ \item Ghost: $c \in \Omega^0(\RR^3; \gg)[1]$.
 \end{itemize}
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
-Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
+We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, and $W$ is its defining representation.
 
@@
 \paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.
-The fields are:
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
- \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
- \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
- \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
+The fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
+ \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
+ \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
+ \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
+ \item Ghost field: $c \in \Omega^0(\RR^3; \gg)[1]$.
 \end{itemize}
@@
 \label{sect:3d_4_minimal_twist}
-Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.
-
-There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
+The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.
+
+There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
 
@@
 \subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
-Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
-This theory is the dimensional reduction of 10d $\cN = (1,0)$ supersymmetric Yang--Mills theory.  
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional (Dirac) spin representation.
+Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.
+This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, and $W$ is its $8$-dimensional (Dirac) spin representation.
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
-The fields are:
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
- \item gauge fermions $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
- \item a ghost field $c \in \Omega^0(\RR^3;\gg)[1]$.
-\end{itemize}
-
-In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in 3d $\mc N=4$.  
-There are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.  We can see this in the following way.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
+The fields we obtain are
+\begin{itemize}
+ \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
+ \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
+ \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
+\end{itemize}
+
+In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.
+That is, there are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.
+We can see this in the following way.
 \begin{lemma}
@@
 \label{sect:3d8minimal_twist}
-The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.
-Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.
+The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  
+Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.
 
@@
 \end{theorem}
-\brian{Need to explain what happened to $\Sect$}
 
@@
 \end{theorem}
-\brian{Need to explain what happened to $\Sect$}
 
 \section{Dimension 2}
-The odd part of the $2$-dimensional supersymmetry algebra is 
-\[
-\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
-\]
-The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
+In dimension 2, the semispin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm 1$.
 There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
-
 There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+First we have theories with $(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
 We additionally have gauge theories with chiral, i.e.
@@
 \subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
-First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
-%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
-The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
-\brian{Not sure what $(a^{-1},b^{-1})$ means?
-Do you mean $(-a,-b)$?}
+First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.
+This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.
+The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
 
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
-In any case, the fields we obtain are
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
- \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item gauge fermions $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item matter fermions $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
- \item a ghost field $c \in \Omega^0(\RR^2; \gg)[1]$.
-\end{itemize}
-
-In the $\mc N=(2,2)$ supersymmetry algebra there are three classes of non-trivial orbits of square-zero supercharges.  
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
+The fields we obtain are
+\begin{itemize}
+ \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
+ \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
+ \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
+\end{itemize}
+
+In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
 \begin{itemize}
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
@@
 They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.
-Let us first decompose our fields according to the twisting homomorphism $\phi_A$:
-%The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
-%\begin{itemize}
-% \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
-% %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
-% \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
-% %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
-% \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
-% \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
-% \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
-%\end{itemize}
-
-\begin{itemize}
-\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
-\item gauge fermions $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
+Let us first decompose our fields according to the twisting homomorphism $\phi_A$.
+The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
+\begin{itemize}
+ \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
  %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item matter bosons $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
+ \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
  %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item matter fermions $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
- \item a ghost field $c \in \Omega^0(\RR^2; \fg)[1]$.
-\end{itemize}
-%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
+ \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
+ \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
+ \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+\end{itemize}
+
+\begin{itemize}
+\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Bar{a} \in \Omega^0(\CC ; \fg)[2]$. 
+\item $\gg$-valued fermions: $\lambda \in \Omega^{??}(\CC ; \fg)[-1]$, $\Bar{\lambda} \in \Omega^{??}(\CC ; \fg) [-1]$, $\lambda' \in \Omega^{0,1}(\CC ; \fg)[1]$, $\Bar{\lambda}' \in \Omega^{??}(\CC ; \fg)[1]$.
+ %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
+ \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
+ %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
+ \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
+\end{itemize}
+We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
 
@@
 Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
-The $\U(1)$ decomposition of the functionals $S_{\rm gauge}^{(1)}, S^{(1)}_{\rm matter}, S^{(2)}_{\rm gauge}, S^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
+The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
 \begin{align*}
-S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{1,0}, A_{1,0}^*) - (\Tilde{\lambda}_0, \Tilde{a}^*) + \frac 12(F_{1,1} \lambda_0^* + (\ol \dd_{A_{0,1}}a, \chi_{0,1}^*)) \right)  \\
-&+  \int \dvol t \left( -(\chi_{0,1}, A_{0,1}^*) - (\lambda_0, \Tilde{a}^*) + \frac 12(F_{1,1} \Tilde{\lambda}_0^*+ (\partial_{A_{1,0}} \Tilde{a}, \lambda_{1,0}^*) )   \right)  \\
-S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t (\lambda_0^*, \Tilde{\lambda}_0^*) - \frac 14(\lambda_0^* + t \Tilde{\lambda}_0^*)^2 + t(a, c^*)\right)  \\
-S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( \psi_0 \phi^* + \frac 12 (\ol \dd_{A_{0,1}} \gamma_0, \gamma_{0,1}^*) \right) +t\left( (\Tilde{\psi}_0, \gamma_0^*) + \frac 12 (\dd_{A_{1,0}}  \phi, \beta_{1,0}^*)  \right)\right)  \\
-S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t2 \left(\beta_{1,0}^*, \gamma_{0,1}^*\right).
+S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
+&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
+S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(\frac t2 (\lambda_{-2}^*, \lambda_0^{'*}) - \frac 12(\lambda_{-2}^* + t\lambda_0^{'*})^2 - t(\chi_{-1}, c_0^*)\right)  \\
+S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
+S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
 \end{align*}
@@
 
-%\begin{prop}
-%Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
-%The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
-%\begin{align*}
-%S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
-%&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
-%S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t (\lambda_0^*, \Tilde{\lambda}_0^*) - \frac 14(\lambda_0^* + t \Tilde{\lambda}_0^*)^2 + t(a, c^*)\right)  \\
-%S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
-%S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
-%\end{align*}
-%\end{prop}
-
 \begin{theorem} \label{2d_2_A_twist_thm}
-The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{proof}
-Observe that the quadruple of fields $\{\lambda_0^*, \lambda_0, \Tilde{\lambda}_0^*, \Tilde{\lambda}_0\}$ has the same Poisson brackets as the quadruple $\{\lambda_0^* - t \Tilde{\lambda}_0^*, \lambda_0, \lambda_0^*, \Tilde{\lambda}_0 + t \lambda_0\}$.
-Therefore, we may eliminate the fields $\lambda_0^*-t\wt\lambda_0^*, \chi$ using Proposition \ref{prop:integrateoutfield}. 
-We then have trivial BRST doublets $\{\wt\lambda_0 + t\lambda_0, \wt a\}$, $\{\lambda_{1,0}, A_{1,0}\}, \{\psi_0, \phi\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}.
-We are left with the action
-
-%We first perform a change of variables sending $\lambda_0$ to $\lambda_0 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
-%We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
-%We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
-%The resulting action functional is of the form
-\[
-S_{BF} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
-\]
+We first perform a change of variables sending $\lambda_2$ to $\lambda_2 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
+We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
+We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
+The resulting action functional is of the form
+\[
+S_{BF} + \int \dvol t\left( -(\lambda'_0, \chi_{1}^*) - (\chi_{-1}, c_0^*) + (\ol \psi_1, \ol \phi_0^*) + \frac 14 (\psi^*_{-1} ,\psi^*_{-1}) + \frac 14  (\psi^*_{1}, \psi^*_{1})\right)\]
 Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
@@
 \ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-&\Omega^0(\CC; \gg)_{c} \ar[r] &\Omega^{0,1}(\CC; \gg)_{A_{0,1}} & & \Omega^{1,0}(\CC; \gg^*)_{\chi_{0,1}^*} \ar[r] &\Omega^{1,1}(\CC; \gg^*)_{a^*} \\
-\Omega^0(\CC; \gg)_{a} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\CC; \gg)_{\chi_{0,1}} \ar@{-->}[ur] && \Omega^{1,0}(\CC; \gg^*)_{A_{0,1}^*} \ar[r] \ar@{-->}[ur] &\Omega^{1,1}(\CC; \gg^*)_{c^*} \ar@{-->}[ur]\\
-&\Omega^0(\CC; R^*)_{\Tilde{\psi}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\CC; R^*)_{\beta_{1,0}^*} \ar@{-->}[dr] &&&\\
-&& \Omega^0(\CC; R^*)_{\gamma_0} \ar[r]  &\Omega^{0,1}(\CC; R^*)_{\gamma_{0,1}} &&\\
-&&\Omega^{1,0}(\CC; R)_{\gamma_{0,1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{1,1}(\CC;  R)_{\gamma_0^*} \ar@{-->}[dr] &&\\
-&&& \Omega^{1,0}(\CC; R)_{\beta_{1,0}} \ar[r]  &\Omega^{1,1}(\CC; R)_{\Tilde{\psi}_0^*}. &\\
+&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
+\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
+&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
+&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
+&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
+&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
 }\]
-%\[\xymatrix@R=0.4cm@C=0.2cm{
-%\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-%&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
-%\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
-%&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
-%&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
-%&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
-%&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
-%}\]
 Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
@@
 
-\begin{corollary}
-The topological $A$-twist of 2d $\cN=(2,2)$-supersymmetric Yang--Mills theory is perturbatively trivial.
-\end{corollary}
-
-\subsubsection{Topological $B$-Twist} \label{sect:2d22Btwist}
+\subsubsection{Topological B Twist} \label{sect:2d22Btwist}
 
@@
 \begin{theorem} \label{2d_2_B_twist_thm}
-The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
+The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{proof}
-The theory is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=2$ supersymmetric Yang--Mills theory in a non-invariant direction.  
-Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} we obtain the desired result.
+We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.
+That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
 \end{proof}
@@
 \subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
-Next, we consider $\mc N=(4,4)$ supersymmetric Yang--Mills theory.
-This theory is obtained as the dimension reduction of 3d $\mc N=4$ supersymmetric Yang--Mills theory.  
-No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
-
-The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
-We can identify $W_\pm = S^4_\pm \otimes W_+^6$, where $W_+^6$ is the auxiliary space of 6d $\cN=(1,0)$ supersymmetry, and $S^4_\pm$ are the semi-spin representations of $\spin(4;\CC)$. 
-The group $\spin(4;\CC)$ acts on $S^4_\pm$ in the natural way, and $\SU(2)$ acts on $W_+^6 \cong \CC^2$ as the fundamental representation.
-
-In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  
-As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
+We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.
+No new twists arise, i.e.
+every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+
+The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e.
+by its fundamental representation on $W^6$.
+
+In addition to rank $(1,0)$ supercharges, which are holomorphic, there are square-zero rank $(1,1)$ supercharges.  As in Section \ref{sect:2d(2,2)}, these supercharges split into two orbits.
 
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
-The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
+The B-supercharge occurs as a degeneration of A-type supercharges.
 \end{prop}
@@
 \begin{proof}
-Decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. 
-A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
+First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$.
+A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.
 There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.
-These are the $B$- and $A$-supercharges respectively.
-\end{proof}
-
-Upon dimensional reduction from 3d $\mc N=4$, the $B$-supercharge reduces to the 2d $\mc N=(4,4)$ $B$-supercharge.  
-Indeed, the 3d $B$-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  
+We will refer to these as the B- and A-supercharges respectively.
+\end{proof}
+
+Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.
+Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.
 Therefore the two vectors in $W_+^6$ discussed above must be colinear.
@@
 \subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
-The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
-By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic $BF$ theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \subsubsection{Topological A Twist} \label{sect:2d44Atwist}
-The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
-By Theorem \ref{3d_4_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in symplectic $\fg$-representation $U$ admits a one-parameter deformation to the A-twist.  
-This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.
+This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-invariant.
 \end{theorem}
@@
 \subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-
-The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
-By Theorem \ref{3d_4_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
 \begin{theorem}
-The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological $BF$ theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
+The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
-Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
-This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
-No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
+Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.
+No new twists arise, i.e.
+every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
 
@@
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
-The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.
+The B-supercharge occurs as a degeneration of A-type supercharges.
 \end{prop}
@@
 \begin{proof}
-We classify $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
+Our aim is to understand the classification of $\spin(8;\CC)$-orbits in the space of pairs of non-zero null-vectors $w_+ \in W_+$ and $w_- \in W_-$.
 Since $\spin(8;\CC)$ acts transitively on the possible choices of $w_+$, it remains for us to understand the action of the stabilizer $\stab(w_+) \sub \spin(8;\CC)$ on the space of null vectors $w_-$.
@@
 
-Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
-Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.
-In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.
+Upon dimensional reduction from 3d $\mc N=8$, the B-supercharge reduces to the 2d $\mc N=(8,8)$ B-supercharge.
+Indeed, if we forget down to $\mc N=4$ supersymmetry, then the B-twist should correspond to the B-twist.
+In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of B-twists lies in the closure of the orbit of A-twists.
 
 \subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
-The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
@@
 \subsubsection{Topological A Twist} \label{sect:2d88Atwist}
-The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the A-twist.
 This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
@@
 \subsubsection{Topological B Twist} \label{sect:2d88Btwist}
-The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.
 
@@
 
-We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
-Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
 The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.
-The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.
 
@@
 \begin{itemize}
-\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
-\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
-\end{itemize}
-The field $\lambda$ transforms in the defining representation of $G_R = \spin(2; \CC)$.
-The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively under $G_R \cong \CC^\times$.
-
-The theory admits a unique twist:
-\begin{itemize}
-\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
-Such supercharges are automatically square-zero and are holomorphic.
-There is a compatible twisting homomorphism
-\[
-\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
-\]
-\end{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
+\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
+\end{itemize}
+Here, $W$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+Choose the basis $\{u,v\}$ for $W_-$ with pairing given by $\<u, v\> = 1$.
+
+We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.
 
@@
 
-Choose a complex structure $L \subset V_\RR$. 
-Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
-\[
-S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
-\]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
-
-Further, fields decompose under the twisting homomorphism as:
-\begin{itemize}
-\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
-\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
-\item matter bosons $\phi \in \Omega^0(\CC ; R^*)$, $\gamma_0 \in \Omega^0(\CC ; R)$;
-\item matter fermions $\psi \in \Omega^{0}(\CC ; R^*)[1]$, $\gamma_{0,1} \in \Omega^{0,1}(\CC ; \fg)[-1]$;
-\item a ghost field $A_0 \in \Omega^0(\CC ; \fg)[1]$.
-\end{itemize}
-
-%
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
-%A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-%\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
-%\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
-%\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
-%\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
-%\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
-%\end{array}
-%\]
-%The anti-fields decompose as
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
-%A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
-%\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
-%\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
-%\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
-%\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
-%\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
-%\end{array}
-%\]
+The fields decompose as
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
+A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
+\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
+\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
+\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
+\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
+\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
+\end{array}
+\]
+The anti-fields decompose as
+\[
+\begin{array} {lllcccccc}
+& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
+c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
+A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
+\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
+\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
+\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
+\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
+\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
+\end{array}
+\]
 
@@
 \begin{align*}
-S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} , \dbar_{A_{0,1}} \lambda_{0}) \bigg)    \\
-S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi}) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} , \partial_{A_{1,0}} \psi_{0})  + \\
-&\qquad + ([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \\
-S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} A_0 , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) + ([\lambda_{1,0}, A_0], \lambda_{1,0}^*) +  [\lambda_{0}, A_0] \lambda_{0}^*\\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \gamma_0^* + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^* + [\psi_0, A_0] \psi_{0}^*\bigg) \\
-S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda_{1,0}, A_{1,0}^*) \bigg) \\
-S^{(1)}_{\mr{matter}} &=  \int \dvol \bigg( (\psi_{0}^*, \Bar{\phi}) + \frac 12(\dbar \gamma_0, \gamma_{0,1}^*) \bigg)\\
-S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda_0^*)^2 \bigg) .
+S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0})  \right)  \\
+S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi})) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} \wedge \partial_{A_{1,0}} \psi_{0})  + \\
+&\qquad + (([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1}) )   \bigg) \\
+S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \beta_{1,1} + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \beta_{1,0} + [\psi_0, A_0] \psi_{1,1}^* \\
+I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
+I^{(1)}_{\mr{matter}} &=  \int \left( (\psi_{1,1}^*, \Bar{\phi}) + \frac 12(\beta_{1,0} \wedge \dbar \gamma_0) \right)\\
+I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
 \end{align*}
@@
 
-\begin{theorem}
-The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
-This equivalence is $\U(1)$-equivariant.
+\begin{theorem}[See also \cite{SWchar}] \label{2d(0,2)}
+The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$.
 \end{theorem}
@@
 The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_0^*)$.  
+First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
 Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
@@
 \begin{align*}
-& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+  [\gamma_0, A_0] \gamma_0^*  \bigg).
+ S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + \beta_{1,0} \dbar_{A_{0,1}} \gamma_{0} \\ 
+  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [\gamma_0, A_0]\wedge \beta_{1,1} + [\gamma_{0,1}, A_0]\wedge \beta_{1,0}  \bigg).
 \end{align*}
-This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic $BF$ theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
+This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{1,\bu}$ comprise the fields of the $\beta\gamma$ system.
 \end{proof}

### 2020-02-19 paper.tex

--- 2020-02-19 paper.tex
@@
 We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
-Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.
-We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.
-The key fact is that the part of the deformation of the action proportional to $s$, namely
+Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
+
+We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
+\begin{equation}
+\label{eq:4d_12_general_def}
+\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
+\end{equation}
+First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
+This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
+
+Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
+The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
 \[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
-More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
+is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
+To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
 In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
 
-So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
 We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
@@
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
-This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
-\begin{equation}
-\label{eq:4d_12_general_def}
-\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
-\end{equation}
-To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.
-This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.
-
-The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+That is, we extract the summand in the $Q_{st}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
+
+It is important that we check that this expression $S_1$ occuring in the $Q_{st}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
+To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
+Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.
+Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
+
+We have therefore shown that the $Q_{st}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
+The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
 \begin{equation}
 \label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
+t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
 \end{equation}
-The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
+in terms of the $\mr U(2)$-component fields, which can be further broken to $\mr U(1) \times \mr U(1)$.
 
@@
 Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
-
 \end{proof}

### 2020-02-19 paper.tex
typo fix

@@
 \end{align*}
-We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
+We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
 Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
@@
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
-That is, we extract the summand in the $Q_{st}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
-
-It is important that we check that this expression $S_1$ occuring in the $Q_{st}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
+That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
+
+It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
 To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
@@
 
-We have therefore shown that the $Q_{st}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
+We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
 The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
@@
 \end{equation}
-in terms of the $\mr U(2)$-component fields, which can be further broken to $\mr U(1) \times \mr U(1)$.
-
-Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
+in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
+
+Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
 This deformation gives the desired theory.

### 2020-02-19 paper.tex
Small changes

--- 2020-02-19 paper.tex
@@
 We summarize our results in two forms.
-In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we summarize all the possible twists of dimensional reductions of 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills and 4d $\cN=1$ super Yang--Mills respectively.
+In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we summarize all the possible twists of dimensional reductions of the 10d $\cN=(1, 0)$, 6d $\cN=(1, 0)$ and 4d $\cN=1$ super Yang--Mills theories respectively.
 In Table \ref{table_of_twists_2d} we summarize the twists of 2d supersymmetric Yang-Mills theory.
@@
 \begin{itemize}
- \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
+ \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} The holomorphic twist of the 6d $\cN=(1, 0)$ super Yang--Mills theory with matter valued in a symplectic $G$-representation $U$ is equivalent to the theory whose classical solutions are holomorphic maps from a Calabi--Yau 3-fold $X$ to the Hamiltonian reduction of $U$ (a holomorphic version of the gauged Rozansky--Witten model).
 In general, this theory is only $\ZZ/2\ZZ$-graded.
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} The minimal twist of 5d $\cN=1$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to a theory defined on a product of a Calabi--Yau surface $X$ and a real 1-manifold $M$.
+ \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} The minimal twist of the 5d $\cN=1$ super Yang--Mills theory with matter valued in a symplectic $G$-representation $U$ is equivalent to a theory defined on a product of a Calabi--Yau surface $X$ and a real 1-manifold $M$.
 The classical solutions are given by maps from $X\times M$ to the symplectic reduction of $U$ holomorphic along $X$ and locally-constant along $M$.
@@
 \begin{itemize}
- \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
+ \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of the 4d $\cN=1$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
 This twist was studied by Johansen \cite{Johansen}.
@@
 The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of holomorphic maps from a Calabi--Yau surface $X$ to the Hamiltonian reduction of $U$.
-4d $\cN=4$ super Yang--Mills corresponds to the case $U=T^*\fg$ in which case the space of classical solutions is a $(-1)$-shifted cotangent bundle to the moduli stack of $G$-Higgs bundles on a complex surface $X$.
+The d $\cN=4$ super Yang--Mills theory corresponds to the case $U=T^*\fg$ in which case the space of classical solutions is a $(-1)$-shifted cotangent bundle to the moduli stack of $G$-Higgs bundles on a complex surface $X$.
  \item \emph{$\mc N=2$ and $\mc N=4$ intermediate twist.} There is a deformation of the $\cN=2$ holomorphic twist which is equivalent to a theory of maps from a product of a Calabi--Yau curve $C$ and an oriented surface $\Sigma$ into the Hamiltonian reduction of $U$ which are holomorphic along $C$ and locally-constant along $\Sigma$.
@@
 
-\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for 4d $\cN=4$ super Yang--Mills, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e.
+\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for the 4d $\cN=4$ super Yang--Mills theory, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e.
 there are three ways of interpreting the differential equations on arbitrary oriented 4-manifolds.
-First, considering 4d $\cN=4$ super Yang--Mills as a 4d $\cN=2$ super Yang--Mills with $U=\fg\otimes\mathbb{H}$, we obtain a theory which counts solutions to the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}.
+First, considering the 4d $\cN=4$ super Yang--Mills theory as a 4d $\cN=2$ super Yang--Mills theory with $U=\fg\otimes\mathbb{H}$, we obtain a theory which counts solutions to the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}.
 Another twisting homomorphism was studied by Vafa and Witten \cite{VafaWitten}.
@@
 
- \item \emph{$\mc N=4$ topological B twist.} For 4d $\cN=4$ super Yang--Mills there is a single topological twist which is not perturbatively trivial.
+ \item \emph{$\mc N=4$ topological B twist.} For the 4d $\cN=4$ super Yang--Mills theory there is a single topological twist which is not perturbatively trivial.
 It is equivalent to a topological BF theory defined on a 4-manifold (this theory corresponds to the value $t=\pm i$ of the family considered in \cite{KapustinWitten}).
@@
 
-An analysis of topological twists of 4d $\cN=4$ super Yang--Mills using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
+An analysis of topological twists of the 4d $\cN=4$ super Yang--Mills theory using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
 \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} There is a minimal twist in dimension 3 which can be defined with $\mc N=2$ supersymmetry, including a chiral multiplet valued in a representation $R$.
-This twist is perturbatively equivalent to a generalized form of BF theory with one real direction and one complex holomorphic direction, coupled to a generalized $\beta \gamma$-system valued in $R$.
-This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
-If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.
-Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
+ \item \emph{$\cN=2$ minimal twist.} The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is defined on a product $C\times L$ of a complex curve $C$ and a real 1-manifold $L$.
+It is equivalent to the cotangent theory of the theory of maps from $C\times L$ to $R/G$ which are holomorphic along $C$ and locally-constant along $L$.
+ \item \emph{$\cN=4$ and $\cN=8$ minimal twist.} We may also consider the minimal twist of $\cN=4$ and $\cN=8$ super Yang--Mills theories.
+The minimal twist of the $\cN=4$ super Yang--Mills theory with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of maps from $C\times L$ to the Hamiltonian reduction of $U$ which are holomorphic along $C$ and locally-constant along $L$.
+The 3d $\cN=8$ theory corresponds to the case $U=T^*\fg$.
  \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.
@@
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Sect}(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $\map(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills Theory}
 
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills Theory}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills Theory}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}
+\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills Theory}
 
@@
 
-\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang--Mills}
+\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang--Mills Theory}
 \label{5d_1_section}
@@
 
-\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang--Mills} \label{5d_2_section}
+\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang--Mills Theory} \label{5d_2_section}
 
@@
 
-\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{sect:4d_1_section}
+\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills Theory} \label{sect:4d_1_section}
 The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
@@
 
-\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang--Mills} \label{4d_2_section}
+\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang--Mills Theory} \label{4d_2_section}
 
@@
 Moreover, the equivalence is $\MU(2)$-equivariant.
-\label{thm:4dholomorphictwist}
+\label{thm:4d2holomorphictwist}
 \end{theorem}
@@
 The former is given by (cf.
-the proof of Theorem \ref{thm:4dholomorphictwist})
+the proof of Theorem \ref{thm:4d2holomorphictwist})
 \[
@@
 
-\subsection{\texorpdfstring{$\cN=4$}{N=4} Super Yang-Mills} \label{4d_4_section}
+\subsection{\texorpdfstring{$\cN=4$}{N=4} Super Yang--Mills Theory} \label{4d_4_section}
 
@@
 Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}.
-From Theorem \ref{thm:4dholomorphictwist} we obtain that the twist is given by $T^*[-1] \map(\CC^2 , (T^*\fg\otimes K_{\CC^2}^{1/2})\ham \fg)$ as a $\ZZ$-graded theory.
+From Theorem \ref{thm:4d2holomorphictwist} we obtain that the twist is given by $T^*[-1] \map(\CC^2 , (T^*\fg\otimes K_{\CC^2}^{1/2})\ham \fg)$ as a $\ZZ$-graded theory.
 
@@
 We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
-Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
-
-We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
+Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.
+We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.
+The key fact is that the part of the deformation of the action proportional to $s$, namely
+\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
+only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
+In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
+
+So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
+The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
+Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
+Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
+
+As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
+This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
 \begin{equation}
@@
 \end{equation}
-First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
-This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
-
-Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
-The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
-\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
-That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
-To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
-In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
-
-So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
-We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
-The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
-Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
-Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
-
-As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
-Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
-That is, we extract the summand in the $Q_{st}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
-
-It is important that we check that this expression $S_1$ occuring in the $Q_{st}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
-To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
-Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.
-Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
-
-We have therefore shown that the $Q_{st}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
-The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.
+This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.
+
+The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
 \begin{equation}
 \label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
+t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
 \end{equation}
-in terms of the $\mr U(2)$-component fields, which can be further broken to $\mr U(1) \times \mr U(1)$.
+The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
 
@@
 Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
+
 \end{proof}
@@
 
-\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} 
+\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang--Mills Theory}
 \label{sect:3d_2_section}
@@
 
-\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
+\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
 Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
@@
 
-There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{4d_2_minimal_twist_thm} to the subgroup $\U(1) \subset \MU(2)$.
+There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
 
@@
 The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
-Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{4d_2_minimal_twist_thm} induced by $\alpha_0$.
+Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
 %However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
@@
 \begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{4d_2_minimal_twist_thm} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
+The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
 This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
@@
 \begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Sect}(\RR^3_{\mr{dR}}, U\ham \gg)$.
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\map(\RR^3_{\mr{dR}}, U\ham \gg)$.
 Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.
@@
 
-\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
+\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang--Mills Theory} \label{3d8section}
 Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
@@
 
-\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
+\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang--Mills Theory} \label{sect:2d(2,2)}
 First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
@@
 
-\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
+\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang--Mills Theory} \label{sect:2d(4,4)}
 Next, we consider $\mc N=(4,4)$ supersymmetric Yang--Mills theory.
@@
 
-\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
+\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang--Mills Theory} \label{sect:2d(8,8)}
 Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with Matter} \label{sect:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with Matter}
+\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang--Mills Theory}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang-Mills}
+\subsection{Pure \texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang--Mills Theory}
 
@@
 
-\begin{theorem}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
+\begin{theorem}[See also \cite{SWchar}]
 The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.

### 2020-02-19 paper.tex

@@
 \end{align*}
-We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.
-Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.
-We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.
-The key fact is that the part of the deformation of the action proportional to $s$, namely
+We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
+Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
+
+We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
+\begin{equation}
+\label{eq:4d_12_general_def}
+\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
+\end{equation}
+First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
+This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
+
+Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
+The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
 \[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
-More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
+is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
+To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
 In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
 
-So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
 We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
@@
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
-This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
-\begin{equation}
-\label{eq:4d_12_general_def}
-\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
-\end{equation}
-To see this, we must verify that the expression $S_1$ occuring in the $Q_{st}$-twisted action functional agrees with the corresponding expression in the $Q_0 + sQ_2$-twisted action functional.
-This follows from the fact that the only term proportional to $t(\chi^*-t\wt\chi^*)$ in the $Q_0 + tQ_1$-twisted action functional from equation \ref{4d_donaldson_susy_prop} is proportional to $\wt \chi^*$, and so vanishes after setting $\wt \chi^* = 0$.
-
-The deformation given by the first three terms in \ref{eq:4d_12_general_def} was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
+
+It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
+To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
+Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.
+Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
+
+We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
+The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
 \begin{equation}
 \label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
+t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
 \end{equation}
-The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.
-
-Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
+in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
+
+Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
 This deformation gives the desired theory.
@@
 
-There is a unique twisting homomorphism $\phi : \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
+There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
 

### 2020-02-19 paper.tex
merge

--- 2020-02-19 paper.tex
@@
 
-\begin{theorem} 
+\begin{theorem} \label{2d(0,2)}
 The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.

### 2020-02-19 paper.tex
minor

@@
 
-\subsection{Super Yang--Mills Theory: pure gauge theory}
+\subsection{Super Yang--Mills Theory: Pure Gauge Theory}
 \label{sect:gaugemultipletSUSY}
@@
 \[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
 That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
@@
 %This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
-The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$.
-\brian{Not sure what $(a^{-1},b^{-1})$ means?
-Do you mean $(-a,-b)$?}
+The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (-a, -b)$.
 

### 2020-02-19 paper.tex
3d intro edit

--- 2020-02-19 paper.tex
@@
 Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus} and Kapustin and Witten \cite{KapustinWitten}.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
 \begin{align}
@@
 Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
 \begin{align}
@@
 
-\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by a twist by a rank $(2, 1)$ supercharge.
-The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $\phi\in\Gamma(M, \mathrm{ad} P)$ which satisfy
-\begin{align}
-(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
-(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
-\d^*_A \phi &= 0.
-\end{align}
-Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
+\item \emph{$\cN=4$ topological rank $(2, 1)$ twist.} The $\cN=4$ intermediate twist also admits a deformation to a perturbatively trivial theory defined on K\"ahler surface $M$ given by twisting by a rank $(2, 1)$ supercharge.
+The corresponding equation is a deformation of the Kapustin--Witten equations using the K\"ahler form.
+
+%The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
+%\begin{align}
+%(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
+%(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
+%\d^*_A \phi &= 0.
+%\end{align}
+%Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
 
@@
 The 3d $\cN=8$ theory corresponds to the case $U=T^*\fg$.
- \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.
-The first is a perturbatively trivial theory which we refer to as the A-twist, obtained by dimensional reduction from the 4d A-twist.
-This theory fits into a non-trivial family deforming the minimal twist, which is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.
-This twist was studied by Blau and Thompson \cite{BlauThompson1}, where it is referred to as a Casson invariant model, as well as Kapustin and Vyas \cite{KapustinVyas} as a dimensional reduction of Donaldson-Witten theory.
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The remaining topological twist is perturbatively equivalent to the 3d topological BF theory coupled to a symplectic boson valued in symplectic representation $U$.
-It is $\spin(3;\RR)$-invariant, and can be defined on arbitrary 3-manifolds.
-This form of twist was studied by Rozansky and Witten, \cite{RozanskyWitten} as well as by Blau and Thompson \cite{BlauThompson2}.
+
+ \item \emph{$\mc N=4$ topological A twist.} In 3d $\cN=4$ super Yang--Mills theory we may consider a deformation of the minimal twist which gives rise to a perturbatively trivial topological theory defined on spin 3-manifolds.
+This twist was studied in \cite{BaulieuGrossman,BlauThompson1,Ohta}.
+From a mathematical point of view the space of states on a two-sphere is studied in \cite{BFN}.
+The partition function counts solutions to a 3-dimensional version of the nonabelian Seiberg--Witten equations \eqref{eq:SW1}, \eqref{eq:SW2}.
+Let $G_\RR$ be a compact Lie group and $U$ a quaternionic-unitary $G_\RR$-representation.
+Let $M$ be a spin 3-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(3)$-principal bundle.
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \Spin(3)} U)$ which together satisfy
+\begin{align}
+\sd \d_A u + [\sigma, u]  &= 0 \label{eq:3dSW1} \\
+F + \ast\d_A \sigma + \Phi(u) &= 0. \label{eq:3dSW2}
+\end{align}
+
+\item \emph{$\cN=8$ topological A twist.} We may regard the 3d $\cN=8$ super Yang--Mills theory as a 3d $\cN=4$ super Yang--Mills theory with matter valued in $U=\fg\otimes\mathbb{H}$.
+In particular, the partition function in the twisted theory counts solutions to the equations \eqref{eq:3dSW1}, \eqref{eq:3dSW2}.
+We may also consider a different twisting homomorphism obtained by dimensionally reducing the Vafa--Witten or Kapustin--Witten twisting homomorphism.
+The classical solutions in this theory are given by principal $G$-bundles $P\rightarrow M$ ($G$ is the complexification of the compact Lie group $G_\RR$) together with a connection $A$ and a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ satisfying a complexified version of the Bogomolny equation:
+\[
+F + \ast \d_A \sigma = 0.
+\]
+The corresponding field theory in the formalism of extended topological field theories is studied in \cite{BZGN}.
+
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The minimal twist of the 3d $\cN=4$ super Yang--Mills theory also admits another deformation to a gauged version of the Rozansky--Witten model valued in the Hamiltonian reduction of $U$ \cite{RozanskyWitten,BlauThompson2}.
  \end{itemize}
@@
 
-\subsubsection{Rank (1, 1) Partially Topological Twist}
+\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} Partially Topological Twist}
 \label{sect:4d4partialtwist}
@@
 
-\begin{theorem} \label{2d(0,2)}
+\begin{theorem} 
 The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.

### 2020-02-20 paper.tex
merge
2d intro edit

@@
 \begin{equation}
-d_A\sigma = \ast(F_A\wedge \psi).
+\d_A\sigma = \ast(F\wedge \psi).
 \end{equation}
@@
 The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}.
-If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
+If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a 3-form $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
 \begin{align}
@@
 Suppose $M$ is a spin 4-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(4)$-principal bundle.
-The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \SU(2)} U)$ which together satisfy
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G_\RR\times \Spin(4)} U)$ which together satisfy
 \begin{align}
@@
 Let $M$ be a spin 3-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(3)$-principal bundle.
-The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \Spin(3)} U)$ which together satisfy
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G_\RR\times \Spin(3)} U)$ which together satisfy
 \begin{align}
@@
 
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The minimal twist of the 3d $\cN=4$ super Yang--Mills theory also admits another deformation to a gauged version of the Rozansky--Witten model valued in the Hamiltonian reduction of $U$ \cite{RozanskyWitten,BlauThompson2}.
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The minimal twist of the 3d $\cN=4$ super Yang--Mills theory also admits another deformation to a gauged version of the Rozansky--Witten model valued in the Hamiltonian reduction $U\ham G$ \cite{RozanskyWitten,BlauThompson2}.
  \end{itemize}
@@
 \begin{itemize}
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.} There is a holomorphic twist in dimension 2 which can be defined with $\mc N=(2,2)$ supersymmetry, including a chiral multiplet valued in a representation $R$.
-This twist is perturbatively equivalent to a holomorphic BF theory coupled to a $\beta \gamma$-system valued in $R$.
-More specifically: to holomorphic BG theory valued in the tangent space $T[1]R/\gg$.
-This theory is $\mr U(1)$-equivariant, and can be defined on any Riemann surface.
-If the supersymmetry is promoted to $\mc N=(4,4)$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory can now be modelled by holomorphic BF theory coupled to a holomorphic symplectic boson.
-Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with holomorphic BF theory valued in $T[1]T^*[2](\gg/\gg))$.
-The study of twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to work of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
-The first is a perturbatively trivial theory: the A-model valued in the cotangent space to the quotient stack $R/\gg$.
- \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological B twist.} The remaining topological twist, the B-twist, is perturbatively equivalent to a 2d topological BF theory, coupled a topological matter valued in the representation $R$.
- \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} Chiral theories in 2-dimensions only admit a holomorphic twist.
-These twists can all be realised as holomorphic BF theory on $\CC$, coupled to a holomorphic $\beta \gamma$-system (in the case where the chiral theory includes matter), or to a holomorphic free fermion (in the case where the chiral theory is pure gauge with $\mc N=(0,N_-)$ supersymmetry).
-Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
+ \item \emph{$\mc N=(2,2), (4,4), (8,8)$ holomorphic twist.} There is a holomorphic twist in dimension 2 which is defined on complex curves $C$.
+The twist of 2d $\cN=(2, 2)$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory to the theory of holomorphic maps from $C$ to $R/G$.
+The twist of 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory to the theory of holomorphic maps from $C$ to the Hamiltonian reduction $U\ham G$.
+Finally, the case of 2d $\cN=(8, 8)$ super Yang--Mills theory corresponds to choosing $U=T^*\fg$.
+ \item \emph{$\mc N=(2,2), (4,4), (8,8)$ topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
+The first is a perturbatively trivial theory, the gauged A-model.
+We begin with a description of the twist of the 2d $\cN=(2, 2)$ super Yang--Mills theory with gauge group $G_\RR$ (a compact Lie group) and matter valued in a unitary $G_\RR$-representation $R$ equipped with a moment map $\Phi$.
+The partition function counts solutions to symplectic vortex equations \cite{CGMRS}.
+Let $\Sigma$ be an oriented surface equipped with an almost complex structure and a square root $S$ of the line bundle of densities $\Dens_\Sigma$.
+The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and a section $u\in\Gamma(M, ((P\times^{G_\RR} R)\otimes_\RR S)$ which satisfy
+\begin{align}
+\ol\dd_A u &= 0 \label{eq:symplecticvortex1} \\
+F + \Phi(u) &= 0. \label{eq:symplecticvortex2}
+\end{align}
+Next, consider the twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory with a complexified gauge group $G$ and matter valued in a complex symplectic $G$-representation $U$ equipped with a moment map $\Phi$.
+In this case the classical solutions are given by principal $G$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and a section $u\in\Gamma(\Sigma, (P\times^G U)\otimes_\RR S)$ which satisfy a complexified version of \eqref{eq:symplecticvortex1}, \eqref{eq:symplecticvortex2}:
+\begin{align}
+\ol\dd_A u &= 0 \\
+F + \Phi(u) &= 0.
+\end{align}
+Finally, consider the twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory.
+The classical solutions are given by principal $G$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and sections $u_1\in\Gamma(\Sigma, \mathrm{ad} P)$, $u_2\in\Omega^{1, 1}(\Sigma, \mathrm{coad} P)$ which satisfy
+\begin{align}
+\ol\dd_A u_1 &= 0 \\
+\ol\dd_A u_2 &= 0 \\
+F + 2(u_1, u_2) &= 0.
+\end{align}
+
+ \item \emph{$\mc N=(2,2), (4,4), (8,8)$ topological B twist.} The other topological twist gives rise to a gauged B-model.
+The twist of the 2d $\cN=(2, 2)$ super Yang--Mills theory with complexified gauge group $G$ and matter valued in a $G$-representation $R$ is equivalent to the cotangent theory to the theory of locally-constant maps from a surface $\Sigma$ to $R/G$.
+The twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory with complexified gauge group $G$ and matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of locally-constant maps from $\Sigma$ to the Hamiltonian reduction $U\ham G$.
+Finally, the case of the 2d $\cN=(8, 8)$ super Yang--Mills theory corresponds to choosing $U=T^*\fg$.
+The study of the topological twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to the works of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
+ \item \emph{$(\cN, 0)$ holomorphic twist.} Theories with chiral supersymmetry in 2 dimensions (i.e.
+with 2d $(\cN, 0)$ supersymmetry) only admit a holomorphic twist.
+The corresponding twisted theory is equivalent to a cotangent theory to the theory of holomorphic maps from a complex curve $C$ to $\fg^{\cN-2} / G$.
+Twisted 2-dimensional $(2,0)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
 \end{itemize}

### 2020-02-20 paper.tex
merge

--- 2020-02-19 paper.tex
@@
 For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.
-These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and $BF$ theory.
+These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and BF theory.
 \end{abstract}
@@
 Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is moreover translation-invariant.
-Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$.
+Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$, where $\Pi$ indicates that $\Sigma$ is placed in odd $\ZZ/2\ZZ$-degree, with the only nonvanishing Lie bracket given by $\Gamma$.
 A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action on the fields is extended to an action of the super Lie algebra $\fA$.
@@
 Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
-The twisted gauge theories here are all either equivalent to $BF$-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
+The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
 Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop, meaning all higher order corrections vanish identically.
@@
   \draw[dotted] (-6.3,-7) -- (-6.3,7);
-  \draw[dotted] (-7.3,-7) -- (-7.3,7);
+  \draw[dotted] (-7.2,-7) -- (-7.2,7);
 
@@
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
+We will write $\Pi E$ to denote $E$ placed in odd $\ZZ/2\ZZ$ degree.
 For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized $BF$ theory} is the classical field theory
+Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized BF theory} is the classical field theory
 \[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg).\]
@@
 \begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with the BV action
 \[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
@@
 
-We will see many $BF$ theories as the output when we twist supersymmetric gauge theories.
+We will see many BF theories as the output when we twist supersymmetric gauge theories.
 In fact, a special case of the definition above also arises when twisting theories of matter.
@@
 Let $X, M, Y'$ be as above.
-Fix an $L_\infty$ algebra $\fg$ and consider the generalized $BF$ theory
+Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
 \[
@@
 We are left with the action
-\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
-where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$.
+\[S_{\mr{BF}} + \int\dvol\left(-t(C, A_{0, 1}^*) + ta c^*\right) + \frac{t}{2} \Omega^{-1} B^*\wedge B^*,\]
+where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$.
 Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
@@
 \begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 
-Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic $BF$ theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
+Up to rescaling the antifields, this is the action functional of the required theory, where $A_{0,\bu}, A_{0,\bu}^*$ comprise the fields of holomorphic BF theory with $B_{2,\bu} = A_{0,\bu}^*$, and the remaining fields comprise the fields of the $\beta\gamma$ system with $\beta_{2,1} = \gamma_{0,1}^*$, $\beta_{2,2} = \gamma_0^*$, and $\gamma_{0,2} = \beta_{2,0}^*$.
 \end{proof}
@@
 We are left with the action
-\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
-where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
+\[S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
+where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
 Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
@@
 \begin{theorem} \label{3d_minimal_twist_thm}
-The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized BF theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
 Moreover this equivalence is $\mr U(1)$-equivariant.
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
@@
 \[
-S_{BF} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
-\]
-Here $S_{BF}$ is the action functional of holomorphic $BF$ theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
+S_{\mr{BF}} + \int \dvol t \bigg( -(\chi_{0,1}, A_{0,1}^*) + (a, c^*) + (\Tilde{\psi}_0, \gamma_0^*) + \frac{1}{2} (\beta_{1,0}^*, \gamma_{0,1}^*) \bigg) 
+\]
+Here $S_{\mr{BF}}$ is the action functional of holomorphic BF theory as in the result of the minimal twist of $\cN=(2,2)$, see Theorem \ref{2d_minimal_twist_thm}, obtained by setting $t = 0$.
 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic $BF$ theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{theorem}
-The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological $BF$ theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
+The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \begin{theorem} \label{2d(0,2)}
-The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \end{align*}
-This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic $BF$ theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
+This is the action functional of the required theory, where $B_{1,0} = A_{0,1}^*$, $B_{1,1} = A_{0}^* \dvol$ comprise the anti-fields of holomorphic BF theory and $\beta_{1,0} = \gamma_{0,1}^*$,  $\beta_{1,1} = \gamma_0^* \dvol$ comprise the anti-fields of the $\beta\gamma$ system.
 \end{proof}
@@
 \begin{theorem}\label{2d(0,4)}
-The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
 \end{theorem}
@@
 \begin{theorem}[See also \cite{SWchar}]
-The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
+The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
 \end{theorem}
@@
 %\end{align*}
-%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system.
+%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic BF theory and $\chi$ is the fundamental field for the free fermion system.
 \end{proof}

### 2020-02-20 paper.tex

@@
 \begin{array}{ccccl}
-\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
-& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\d_{\mr{dR}} F  \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
+& (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
 \end{array}

### 2020-02-20 paper.tex
(4,0)

--- 2020-02-20 paper.tex
@@
 \begin{equation}
-\d_A\sigma = \ast(F\wedge \psi).
+d_A\sigma = \ast(F_A\wedge \psi).
 \end{equation}
@@
 The partition function of this theory counts solutions to the Donaldson--Thomas equations \cite{Thomas}.
-If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a 3-form $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
+If we denote by $\omega$ the K\"ahler form on a Calabi--Yau 3-fold $M$, then the classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Omega^{0, 3}(M, \mathrm{ad} P\otimes_\RR \CC)$ satisfying
 \begin{align}
@@
 Suppose $M$ is a spin 4-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(4)$-principal bundle.
-The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G_\RR\times \Spin(4)} U)$ which together satisfy
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \SU(2)} U)$ which together satisfy
 \begin{align}
@@
 Let $M$ be a spin 3-manifold and let $P_{\Spin}\rightarrow M$ be the corresponding $\Spin(3)$-principal bundle.
-The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G_\RR\times \Spin(3)} U)$ which together satisfy
+The classical solutions in this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$, a section $\sigma\in\Gamma(M, \mathrm{ad} P)$ and a section $u\in\Gamma(M, (P\times P_{\Spin})\times^{G\times \Spin(3)} U)$ which together satisfy
 \begin{align}
@@
 
- \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The minimal twist of the 3d $\cN=4$ super Yang--Mills theory also admits another deformation to a gauged version of the Rozansky--Witten model valued in the Hamiltonian reduction $U\ham G$ \cite{RozanskyWitten,BlauThompson2}.
+ \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The minimal twist of the 3d $\cN=4$ super Yang--Mills theory also admits another deformation to a gauged version of the Rozansky--Witten model valued in the Hamiltonian reduction of $U$ \cite{RozanskyWitten,BlauThompson2}.
  \end{itemize}
@@
 \begin{itemize}
- \item \emph{$\mc N=(2,2), (4,4), (8,8)$ holomorphic twist.} There is a holomorphic twist in dimension 2 which is defined on complex curves $C$.
-The twist of 2d $\cN=(2, 2)$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory to the theory of holomorphic maps from $C$ to $R/G$.
-The twist of 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory to the theory of holomorphic maps from $C$ to the Hamiltonian reduction $U\ham G$.
-Finally, the case of 2d $\cN=(8, 8)$ super Yang--Mills theory corresponds to choosing $U=T^*\fg$.
- \item \emph{$\mc N=(2,2), (4,4), (8,8)$ topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
-The first is a perturbatively trivial theory, the gauged A-model.
-We begin with a description of the twist of the 2d $\cN=(2, 2)$ super Yang--Mills theory with gauge group $G_\RR$ (a compact Lie group) and matter valued in a unitary $G_\RR$-representation $R$ equipped with a moment map $\Phi$.
-The partition function counts solutions to symplectic vortex equations \cite{CGMRS}.
-Let $\Sigma$ be an oriented surface equipped with an almost complex structure and a square root $S$ of the line bundle of densities $\Dens_\Sigma$.
-The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and a section $u\in\Gamma(M, ((P\times^{G_\RR} R)\otimes_\RR S)$ which satisfy
-\begin{align}
-\ol\dd_A u &= 0 \label{eq:symplecticvortex1} \\
-F + \Phi(u) &= 0. \label{eq:symplecticvortex2}
-\end{align}
-Next, consider the twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory with a complexified gauge group $G$ and matter valued in a complex symplectic $G$-representation $U$ equipped with a moment map $\Phi$.
-In this case the classical solutions are given by principal $G$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and a section $u\in\Gamma(\Sigma, (P\times^G U)\otimes_\RR S)$ which satisfy a complexified version of \eqref{eq:symplecticvortex1}, \eqref{eq:symplecticvortex2}:
-\begin{align}
-\ol\dd_A u &= 0 \\
-F + \Phi(u) &= 0.
-\end{align}
-Finally, consider the twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory.
-The classical solutions are given by principal $G$-bundles $P\rightarrow \Sigma$ equipped with a connection $A$ and sections $u_1\in\Gamma(\Sigma, \mathrm{ad} P)$, $u_2\in\Omega^{1, 1}(\Sigma, \mathrm{coad} P)$ which satisfy
-\begin{align}
-\ol\dd_A u_1 &= 0 \\
-\ol\dd_A u_2 &= 0 \\
-F + 2(u_1, u_2) &= 0.
-\end{align}
-
- \item \emph{$\mc N=(2,2), (4,4), (8,8)$ topological B twist.} The other topological twist gives rise to a gauged B-model.
-The twist of the 2d $\cN=(2, 2)$ super Yang--Mills theory with complexified gauge group $G$ and matter valued in a $G$-representation $R$ is equivalent to the cotangent theory to the theory of locally-constant maps from a surface $\Sigma$ to $R/G$.
-The twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory with complexified gauge group $G$ and matter valued in a symplectic $G$-representation $U$ is equivalent to the cotangent theory of the theory of locally-constant maps from $\Sigma$ to the Hamiltonian reduction $U\ham G$.
-Finally, the case of the 2d $\cN=(8, 8)$ super Yang--Mills theory corresponds to choosing $U=T^*\fg$.
-The study of the topological twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to the works of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
- \item \emph{$(\cN, 0)$ holomorphic twist.} Theories with chiral supersymmetry in 2 dimensions (i.e.
-with 2d $(\cN, 0)$ supersymmetry) only admit a holomorphic twist.
-The corresponding twisted theory is equivalent to a cotangent theory to the theory of holomorphic maps from a complex curve $C$ to $\fg^{\cN-2} / G$.
-Twisted 2-dimensional $(2,0)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.} There is a holomorphic twist in dimension 2 which can be defined with $\mc N=(2,2)$ supersymmetry, including a chiral multiplet valued in a representation $R$.
+This twist is perturbatively equivalent to a holomorphic BF theory coupled to a $\beta \gamma$-system valued in $R$.
+More specifically: to holomorphic BG theory valued in the tangent space $T[1]R/\gg$.
+This theory is $\mr U(1)$-equivariant, and can be defined on any Riemann surface.
+If the supersymmetry is promoted to $\mc N=(4,4)$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory can now be modelled by holomorphic BF theory coupled to a holomorphic symplectic boson.
+Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with holomorphic BF theory valued in $T[1]T^*[2](\gg/\gg))$.
+The study of twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to work of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.
+The first is a perturbatively trivial theory: the A-model valued in the cotangent space to the quotient stack $R/\gg$.
+ \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological B twist.} The remaining topological twist, the B-twist, is perturbatively equivalent to a 2d topological BF theory, coupled a topological matter valued in the representation $R$.
+ \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} Chiral theories in 2-dimensions only admit a holomorphic twist.
+These twists can all be realised as holomorphic BF theory on $\CC$, coupled to a holomorphic $\beta \gamma$-system (in the case where the chiral theory includes matter), or to a holomorphic free fermion (in the case where the chiral theory is pure gauge with $\mc N=(0,N_-)$ supersymmetry).
+Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}.
 \end{itemize}
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2; \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
-
-We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
-Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
-The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$. 
-The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.
-
-The untwisted fields are given by:
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
+
+We turn to $\cN=(2,0)$ supersymmetric Yang-Mills theory.
+In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
+The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_+$ by the defining representation.
+
+The fields of the untwisted theory are:
 \begin{itemize}
 \item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
 \item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_- \otimes R)$.
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 \begin{itemize}
-\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
 Such supercharges are automatically square-zero and are holomorphic.
@@
 \]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det^{-1/2}$.
 
@@
 
-\begin{theorem} \label{2d(0,2)}
-The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+\begin{theorem} \label{thm: 2d(2,0)}
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 
-We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
-The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
-Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
-
-The field content is:
-\begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-\end{itemize}
-
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
+In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
+The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
+The $R$-symmetry group is $\Spin(4;\CC)$, which acts on $W_+$ as the defining representation.
+
+%The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
+%Let $W = {\rm span}_{\CC} \{u_1,u_2\}$. 
+\begin{itemize}
+\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item matter bosons $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$  
+\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
+\end{itemize}
+
+The fields $\lambda, \psi$ transform in the defining representation of $G_R = \spin(4;\CC)$.
+
+The theory admits a unique twist:
+\begin{itemize}
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
+Such supercharges are automatically square-zero, holomorphic, and lie in a $(2,0)$ supersymmetry subalgebra.
+There is a compatible twisting homomorphism
+\[
+\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
+\]
+which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
+\end{itemize}
+
+%The field content is:
+%\begin{itemize}
+%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+%\end{itemize}
+
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
 

### 2020-02-20 paper.tex

--- 2020-02-20 paper.tex
@@
 a graded manifold equipped with a square-zero vector field of cohomological degree $1$ (the BRST differential).
-In the Batalin--Vilkovisky approach one considers instead the space of BV fields $\cE$, which is equipped with a $(-1)$-shifted symplectic structure; this may be modeled by a $QP$-manifold \cite{Schwarz}.
+In the Batalin--Vilkovisky \cite{BatalinVilkovisky} approach one considers instead the space of BV fields $\cE$, which is equipped with a $(-1)$-shifted symplectic structure; this may be modeled by a $QP$-manifold \cite{Schwarz}.
 Moreover, we assume that the $Q$-structure is Hamiltonian, i.e.
 that it is given by a Poisson bracket $\{S, -\}$ with respect to the BV action functional.
-Here $\cE$ is supposed to be the derived critical locus of the action functional on $\cF$.
+Here $\cE$ is interpreted as modelling the derived critical locus of the action functional on $\cF$.
 
@@
 
-Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is moreover translation-invariant.
+Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, and where the theory is translation-invariant.
 Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$, where $\Pi$ indicates that $\Sigma$ is placed in odd $\ZZ/2\ZZ$-degree, with the only nonvanishing Lie bracket given by $\Gamma$.
 A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action on the fields is extended to an action of the super Lie algebra $\fA$.
-In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.
+In addition, we may consider an $R$-symmetry group $G_R$ that acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.
 
@@
 We instead take another approach pioneered by Baulieu, Bellon, Ouvry and Wallet \cite{BaulieuBV}.
-Namely, one may canonically extend the supersymmetry action from ordinary fields $\cF$ to the space of BV fields $\cE$.
+Namely, one may canonically extend the supersymmetry action from the space of ordinary fields $\cF$ to the space of BV fields $\cE$.
 The property of the action being on-shell now means that the map $\fA\rightarrow \mathrm{Vect}(\cE)$ preserves Lie brackets, but only up to homotopy.
@@
 As a new result, we also construct an $L_\infty$-action on matter multiplets where the language of composition algebras turns out to be indispensable (see Section \ref{sect:mattermultipletSUSY}).
-Namely, for any real associative composition algebra $A_\RR$ we simply need a complex $\fg$-representation equipped with an $A_\RR$-module structure and a symmetric bilinear pairing.
+Namely, for any real associative composition algebra $A_\RR$ we simply need a complex $\fg$-representation $P$ equipped with an $A_\RR$-module structure and a symmetric bilinear pairing.
 We have the following three cases:
 \begin{itemize}
-\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) For $A_\RR=\mathbb{H}$ this forces $P=U\otimes W_+$, where $U$ is a symplectic $\fg$-representation and $W_+$ is a 2d complex symplectic vector space (so that $\mathbb{H}\otimes_\RR\CC\cong \eend(W_+)$).
-\item (\textbf{4d $\cN=1$ supersymmetry}) For $A_\RR=\mathbb{C}$ this forces $P=R\oplus R^*$, where $R$ is a $\fg$-representation.
+\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) For $A_\RR=\mathbb{H}$ $P$ is forced to take the form $U\otimes W_+$, where $U$ is a symplectic $\fg$-representation and $W_+$ is a 2d complex symplectic vector space (so that $\mathbb{H}\otimes_\RR\CC\cong \eend(W_+)$).
+\item (\textbf{4d $\cN=1$ supersymmetry}) For $A_\RR=\mathbb{C}$ $P$ is forced to take the form $R\oplus R^*$, where $R$ is a $\fg$-representation.
 \item (\textbf{3d $\cN=1$ supersymmetry}) For $A_\RR=\mathbb{R}$ we simply have an orthogonal $\fg$-representation $P$.
@@
 
-In addition to the dimensional reduction of these four super Yang--Mills theories, there are also certain special super Yang--Mills theories with chiral supersymmetry: namely, 2d $\cN=(1, 0)$, $\cN=(2, 0)$ and $\cN=(4, 0)$ with matter as well as pure $\cN=(\cN_+, 0)$ theories for any $\cN_+$.
+In addition to the dimensional reduction of these super Yang--Mills theories, there are also certain special super Yang--Mills theories with chiral supersymmetry in dimension 2: namely, 2d $\cN=(1, 0)$, $\cN=(2, 0)$ and $\cN=(4, 0)$ with matter as well as pure $\cN=(\cN_+, 0)$ theories for any $\cN_+$.
 We treat these separately (see Section \ref{sect:2dchiral}), but again the language of composition algebras turns out to be convenient.
@@
 The notion of supersymmetric twisting for a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}.
-The definitions we use in this paper will follow our previous work \cite{ElliottSafronov}, so let us briefly recall those.
+The definitions we use in this paper will follow our previous work \cite{ElliottSafronov}, so let us briefly recall the important terminology.
 
@@
 
-\item The supergravity analog of $\alpha\colon \U(1)\rightarrow G_R$, if a choice of trivial $\U(1)$-subbundle in $G_R$ on which the connection restricts to zero.
+\item The supergravity analog of $\alpha\colon \U(1)\rightarrow G_R$ is a choice of trivial $\U(1)$-subbundle in $G_R$ on which the connection restricts to zero.
 \end{itemize}
@@
 \subsection*{Applications to Quantization}
-%\addcontentsline{toc}{subsection}{Applications to quantization}
 
@@
 This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}.
-In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+In the context of (non-supersymmetric) Yang-Mills theory for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 
-In the general setting of this paper, while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically.
+In the general setting of this paper, while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically and the remaining directions behave holomorphically.
 For a mixed holomorphic-topological translation invariant field theory of this type on $\RR^n \times \CC^d$, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way.
@@
 \subsection*{Summary of Twisted Super Yang--Mills Theories}
-%\addcontentsline{toc}{subsection}{Summary of Twisted Super Yang-Mills Theories}
 
@@
 \caption{This figure shows the orbits of square-zero supercharges in each dimension, and how they relate to one another under dimensional reduction.
-The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiplet orbits.
+The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiple orbits.
 Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.
@@
 \subsection*{Outline of the Paper}
-%\addcontentsline{toc}{subsection}{Outline of the Paper}
 The remainder of the paper is divided into two parts.
@@
 The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint.
-This important result will only serve as a motivation.
+This important result will serve as motivation for the main definition in this section (Definition \ref{def:classicalfieldtheory}).
 
@@
 \begin{definition}
-Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
+Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \bigoplus_m \fg(m)$ compatible with the $L_\infty$ structure.
 \end{definition}
@@
 \begin{example}
-Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-represntation equipped with an $n$-shifted symplectic structure $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
+Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with an $n$-shifted symplectic pairing $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
 \[\fh = \fg\oplus U[-1]\oplus \fg^*[n-2]\]
@@
 \[(B L)(U) = B L(U),\]
-i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
+i.e. $L$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.
 
@@
 In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered.
-It is only relevant for quantization which we do not consider in this paper, so for simplicity we will not require ellipticity (though in fact all examples we consider will end up being elliptic).
+It is only relevant for quantization, which we do not consider in this paper, so for simplicity we will not require ellipticity (though in fact all examples we consider will end up being elliptic).
 \end{remark}
@@
 \begin{example}
-Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
+Let $X,Y$ be complex manifolds, let $M$ be a smooth manifold and let $B\fg$ be a formal moduli problem represented by an $L_\infty$ algebra $\fg$.
 Then we may define the following local formal moduli problem on $X\times Y\times M$.
@@
 
-\begin{cor}
-Suppose $X,Y,M,\fg$ are as in Example \ref{ex:mappingspace} and, moreover, $X$ is equipped with a holomorphic volume form and $M$ is oriented. Then
+\begin{corollary}
+Suppose $X,Y,M,\fg$ are as in Example \ref{ex:mappingspace} and, moreover, that $X$ is equipped with a holomorphic volume form and $M$ is oriented. Then
 \[T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)\cong \map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg).\]
 \label{cor:mapintocotangent}
-\end{cor}
+\end{corollary}
 
@@
 
+We can now state a concise definition of a classical field theory in the BV formalism.
+
+\begin{definition}
+A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
+\label{def:classicalfieldtheory}
+\end{definition}
+
 Given a local formal moduli problem $\cM = BL$ equipped with a strict $n$-shifted symplectic structure, the space of local functionals $\oloc(\cM)$ is equipped with a Poisson bracket (see \cite[Chapter 5.3]{CostelloBook})
@@
 \]
-This bracket is a graded version to the so-called Soloviev bracket \cite{Soloviev} defined on the $\infty$-jets, as described in \cite[Section 4]{GetzlerBracket}.
+This bracket is a graded version of the so-called Soloviev bracket \cite{Soloviev} defined on the $\infty$-jets, as described in \cite[Section 4]{GetzlerBracket}.
 
@@
 Define the symmetric multilinear map
-\[
-\begin{array}{ccccl}
-\d_{\mr{dR}} F  \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
-& (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
-\end{array}
-\]
+\begin{align*}
+\d_{\mr{dR}} F  \colon  \cE_c^{\times (n-1)} & \to  \cE^\vee \\
+ (\phi_1, \ldots, \phi_{n-1}) & \mapsto  D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\end{align*}
 Integrating by parts, we see that for any $(n-1)$-tuple $(\phi_1, \ldots, \phi_{n-1}) \in \cE_c^{n-1}$ the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
@@
 \]
-This is the Hamiltonian vector field corresponding to $F$. 
-Finally, the Poisson bracket between local functionals $F, G$ is defined by
-\[
-\{F, G\} = X_F (G) .
-\]
+This is the Hamiltonian vector field corresponding to $F$.  We can now define the Poisson bracket.
+
+\begin{definition}
+The Poisson bracket between local functionals $F, G$ is defined by
+\[\{F, G\} = X_F (G).\]
+\end{definition}
 
 The Poisson bracket enjoys the graded skew symmetry property
-\[
-\{F, G\} = (-1)^{|F| |G|} \{G, F\}
-\]
+\[\{F, G\} = (-1)^{|F| |G|} \{G, F\}\]
 as well as the graded Jacobi identity.
@@
 The differential on a local $L_\infty$ algebra $L$ is given by a differential operator $Q_{\mathrm{BV}}\colon L\rightarrow L$.
-The structure of a cyclic $L_\infty$ algebra can be encoded into its potential.
+The structure of the $L_\infty$ brackets can be encoded into its potential.
 In the same way, the structure of a local $L_\infty$ algebra $L$ together with an $n$-shifted symplectic structure on $BL$ may be encoded into the \defterm{action functional} $S\in\oloc(BL)$ of cohomological degree $1-n$ such that
@@
 
-\begin{definition}
-A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
-\label{def:classicalfieldtheory}
-\end{definition}
-
-Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, we call $E=L[1]$ the \defterm{bundle of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}.
+Given a classical field theory represented by a local $L_\infty$ algebra $L$ on $M$, as in Definition \ref{def:classicalfieldtheory}, we call $E=L[1]$ the \defterm{bundle of BV fields}, and we call the complex $(E, Q_{\mr{BV}})$ the \defterm{classical BV complex}.
 We call the Poisson bracket on $\oloc(\cM)$ the \defterm{BV bracket}.
-It will be convenient to think of a classical field theory as a quadruple $(E, \omega, Q_{\mr{BV}}, I)$ consisting of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$, a classical BV differential $Q_{\mr{BV}}$ and an interaction functional $I$.
+It will sometimes be convenient to think of a classical field theory as a quadruple $(E, \omega, Q_{\mr{BV}}, I)$ consisting of the bundle of BV fields equipped with a $(-1)$-shifted symplectic pairing $\omega$, a classical BV differential $Q_{\mr{BV}}$ and an interaction functional $I$.
 We characterize such data in the following way.
@@
 Indeed, $T^*[-1]\cM = B(L\oplus L^![-3])$ and we simply pair $L$ and $L^!$.
-Classical field theories arising via this construction are called of \defterm{cotangent type}.
+Classical field theories arising via this construction are called \defterm{cotangent type} theories.
 \end{example}
@@
 \item A $\ZZ\times \ZZ/2\ZZ$-graded local $L_\infty$ algebra is a $\ZZ$-graded local $L_\infty$ algebra $L$ equipped with an extra $\ZZ/2\ZZ$-grading (the \defterm{fermionic grading}) with respect to which all operations are even.
-An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$ which is even with respect to the fermionic grading.
+An $n$-shifted symplectic structure on a $\ZZ\times\ZZ/2\ZZ$-graded local formal moduli problem $BL$ is a pairing $L\otimes L\rightarrow \Dens_M[n-2]$, which is even with respect to the fermionic grading.
 
@@
 \begin{definition}
-A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwines the pairings $\omega, \omega'$ and defines an $L_\infty$ map $\cE[-1]\rightarrow \cE'[-1]$.
+A \defterm{morphism} $\Phi\colon (E, \omega, S)\rightsquigarrow (E', \omega', S')$ of classical field theories over the same manifold $M$ is a collection $\Phi =\sum_{n\geq 1}^\infty \Phi_n$ of poly-differential operators $\Phi_n\colon \Sym^n(E)\rightarrow E'$ that intertwine the pairings $\omega, \omega'$ and define an $L_\infty$ map $\cE[-1]\rightarrow \cE'[-1]$.
 A morphism is a \defterm{perturbative equivalence} if the map $\Phi_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q'_{BV})$ is a quasi-isomorphism.
@@
 
-We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. 
+We will now describe two primitive examples of equivalences of classical field theories that will be useful in simplifying twisted theories. 
 First, we consider the process of eliminating an auxiliary field.
@@
 where $S_0$ is a local functional independent of $\phi,\phi^*$ and $S_1$ is a $\cO_M$-valued polydifferential operator which is independent of $\phi$. 
-Then the theory $(E, \omega, S)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set and $\phi = S_1$ and $\phi^* = 0$.
+Then the theory $(E, \omega, S)$ is perturbatively equivalent to the theory $(E_0, \omega_0, S')$ with the BV action $S' = S_0 - S_1^2/2$, where we set $\phi = S_1$ and $\phi^* = 0$.
 \end{prop}
 \begin{proof}
-Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^{(n)}$.  
+Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and that the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^{(n)}$.  
 The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
@@
 \end{align*}
-These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
-To see that they intertwine the action functionals, we observe that 
+These $\Psi_n$ manifestly intertwine the pairings $\omega$ and $\omega'$. To see that they intertwine the action functionals, we observe that 
 \begin{align*}
@@
 \begin{remark}
-In terms of the classical BV complex, this proposition tells us that if a classical BV complex is of the form
+In terms of the classical BV complex, this proposition has the following interpretation.  We consider theories where the classical BV complex is of the form
 \[\xymatrix{
@@
 \cdots \ar[r] & E_0^0 \ar[r]^{Q_0} \ar@{.>}[dr] & E_0^1 \ar[r] &\cdots \\
-&\cO_M \ar^-{{\rm dvol}}[r] \ar@{.>}[ur] &\dens_M &
+&\cO_M \ar^-{{\rm dvol}}[r] \ar@{.>}[ur] &\dens_M. &
 }\]
@@
 \label{prop:BRSTdoublet}
-Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+Let $(E_0, \omega_0, S_0)$ be a classical BV theory and let $F \to M$ be a graded vector bundle.
 Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
@@
 whose sections we denote by $e_0 + \phi + \phi^* + \psi + \psi^*$ according to the above decomposition. 
-The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
+The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ and the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$. 
 Suppose further that the local functional
@@
 satisfies the classical master equation, where $I_{\phi}, I_{\psi^*}, I_{\phi^*}, I_{\psi}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of $\phi$ and $\psi^*$.
-Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.
+Then the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E_0, \omega_0, S')$ where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the original action functional $S$.
 \end{prop}
@@
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
+parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ that satisfy the antisymmetry property
 \[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
@@
 Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
-By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + \{\fS_\fg, -\}$ 
+By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + \{S_\fg, -\}$ 
 defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
@@
 
-Our first example will generalize the fundamental example of the \emph{BF theory} to a not entirely topological context.
+Our first example will generalize the fundamental example of \emph{BF theory} to a not entirely topological context.
 Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
@@
 \[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
-where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and where $\ell_k$ denote the $k^{\text{th}}$ component of the $L_\infty$ structure on $\fg$.
+where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and where $\ell_k$ denotes the $k^{\text{th}}$ component of the $L_\infty$ structure on $\fg$.
 
 \begin{example}
-For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with the BV action
+For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological BF theory with BV action functional
 \[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
@@
 \begin{definition}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the classical field theory
+Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the classical field theory
 \[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, V).\]
@@
 \[\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg\]
-is equipped with a cyclic structure coming from the nondegenerate pairing on $\fg$ and the wedge product of forms on $X\times Y\times M$.
+is equipped with a shifted symplectic structure coming from the nondegenerate pairing on $\fg$ and the wedge product of forms on $X\times Y\times M$.
 \label{def:generalizedCS}
@@
 Let $X,Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an integer $m$ and suppose $X$ is equipped with an $m$-th root $K_X^{1/m}$.
-Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\oplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $m$ with respect to the grading.
+Fix an integer $m$ and suppose $X$ is equipped with an $m$-th root of the canonical bundle $K_X^{1/m}$.
+Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\bigoplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $m$ with respect to the grading.
 Then the generalized Chern--Simons theory is the classical field theory
@@
 \[T^*[-1]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)\cong \map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[d-1]B\fg),\]
-so the generalized BF theory may be considered as a particular example of the generalized Chern--Simons theory.
+so the generalized BF theory may be considered as a particular example of a generalized Chern--Simons theory.
 \label{ex:CSBF}
@@
 \[\Sect(X, (U\otimes K_X^{1/2})\ham\fg) . \]
-%For $U=T^*R$ this theory is isomorphic to the holomorphic BF theory
-%\[T^*[-1] \map(\CC, R / \fg)\]
-%by Proposition \ref{prop:mapintocotangent}.
 \end{example}
@@
 \begin{definition} \label{Hodge_family_def}
-Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold.
+Let $X$ and $Y$ be complex manifolds and let $M$ be a smooth oriented manifold.
 Fix an $L_\infty$ algebra $\fg$.
@@
 Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction.
-If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
+If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist, i.e.
+the groupoid is non-empty.
 \label{prop:dimensionalreductionunique}
@@
 \]
-%\map(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
 \end{prop}
@@
 Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$.
-The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$.
+The de Rham differential vanishes on translation-invariant forms, which shows compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$.
 Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
@@
 
-As in Equation (\ref{eqn: generalized}), we assume $X$ is a complex manifold of the form $X' \times V$ and consider the dimensional reduction along the map
+As in Equation (\ref{eqn: generalized}), we assume that $X$ is a complex manifold of the form $X' \times V$.  We now consider the dimensional reduction along the map
 \[
@@
 \[\Omega^\bullet(V_\RR; \CC)\xto{p^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
-defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ which projects onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
+defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
 This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
@@
 
-So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.
+So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ is a finite dimensional multiplicity space.
 
@@
 \begin{definition}
-Let $\fA$ be a supertranslation algebra.  The corresponding \defterm{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
+Let $\fA$ be a supertranslation algebra.  The corresponding \defterm{supersymmetry algebra} is the super Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
 \end{definition}
@@
 \item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
-Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.
+Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations of $\Spin(4;\CC)$.
 
 \item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
-Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$.
-
-\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{O}\otimes_{\RR}\CC$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
+Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ is the sum of two copies of a semi-spin representation of $\Spin(6;\CC)$.
+
+\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{O}\otimes_{\RR}\CC$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation of $\Spin(10;\CC)$.
 \end{enumerate}
@@
 \[\Sigma^* = S_-\otimes W.\]
-The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
+The Clifford action $\rho \colon V\otimes S_+\rightarrow S_-$ is defined so that
 \[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
@@
 \[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
+We now give the analogue of Theorem \ref{thm:matter3psi} in the 2d chiral setting.
 
@@
 Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge.
-The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
+The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2\ZZ$-graded classical field theory with the same bundle of $BV$ fields and symplectic pairing $\omega$, but with the BV action
 \[S^Q = S + \sum_{k \geq 1} S_{\fA}^{(k)}(Q, \dots, Q).\]
@@
 Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-grading on mod 2 on $E$ coincides with the fermionic grading.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
@@
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
-The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$.
+The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
 But it also has cohomological degree $-k$.
@@
 \begin{definition}
-Let $Q\in\Sigma$ be a square-zero supercharge and suppose $G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism.
-A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the composite $G\rightarrow \Spin(V_\RR)\times G_R$.
+Let $Q\in\Sigma$ be a square-zero supercharge and suppose $\iota \colon G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism.
+A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the product $(\iota, \phi) \colon G\rightarrow \Spin(V_\RR)\times G_R$.
 \end{definition}
@@
 
-In this section we construct supersymmetry action on super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
-\begin{itemize}
-\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.
-
-\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
-
-\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
-
-\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
+In this section we construct supersymmetry algebra action on super Yang--Mills theories. We have the following versions of super Yang--Mills theory depending on $\dim(\Sigma)$:
+\begin{itemize}
+\item (16 supercharges). This theory exists in dimensions 2 through 10 and depends on a Lie algebra $\fg$.
+
+\item (8 supercharges). This theory exists in dimensions 2 through 6 and depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.
+
+\item (4 supercharges). This theory exists in dimensions 2 through 4 and depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.
+
+\item (2 supercharges). This theory exists in dimensions 2 through 3 and depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
 \end{itemize}
@@
 We begin with a description of certain pure supersymmetric Yang--Mills theories.
-Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification.
+Let $V_\RR = \RR^n$ be a real vector space of dimension $n$ equipped with a nondegenerate symmetric bilinear pairing and let $V$ be its complexification.
 Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
@@
 
-Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The fields of the Yang--Mills theory are as follows:
+Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The BRST fields of the Yang--Mills theory are as follows:
 \begin{itemize}
@@
 The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d \colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
-\[
-\begin{array}{ccccccc}
-[-,-] & \colon & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
-\end{array}
-\]
+\begin{align*}
+[-,-]  \colon  \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to  \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
+\end{align*}
 defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
@@
 If we denote by $(A^*, \lambda^*,c^*)$ the anti-fields, the full BV action takes the form:
-%We introduce gauge transformations
-%\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
-%so that the BV action is given by
 \begin{equation}
@@
 
-We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfy the classical master equation.
 The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
@@
 The rest of the claims will be proved in a sequence of Lemmas.
-To simplify the expressions, we drop the integrals.
+To simplify the expressions, we drop the integrals from our notation.
 
@@
 \begin{remark}
-The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; this was proven by Baez and Huerta in \cite{BaezHuerta}, and our proof essentially follows the proof in loc.
+The previous Lemma expresses the fact that the pure super Yang--Mills on-shell action on BRST fields is supersymmetric; this was proven by Baez and Huerta in \cite{BaezHuerta}, and our proof essentially follows the proof in loc.
 cit.
@@
 The individual terms are
-\begin{align*}
+\begin{enumerate}
+\item\begin{align*}
 \frac{1}{2}\{S_{\gauge}^{(1)}, S_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\gauge}^{(1)}(Q_2)\} \\
@@
 \end{align*}
-\begin{align*}
+\item\begin{align*}
 (\d_{\mr{CE}} S_{\gauge}^{(1)})(Q_1, Q_2) &= S_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
-&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
+&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*,
 \end{align*}
-and
+\item 
 \begin{align*}
@@
 &+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
-&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
+&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*.
 \end{align*}
+\end{enumerate}
 The total coefficient in front of $A^*$ is
@@
 
-\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(Z)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(Z)$ where $Z$ is a 2-dimensional symplectic vector space.
+Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
 
@@
 The individual terms are:
-\begin{align*}
+\begin{enumerate}
+\item \begin{align*}
 \frac{1}{2}\{S_{\matter}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{S_{\matter}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} \\
@@
 
-\begin{align*}
+\item \begin{align*}
 \{S_{\gauge}^{(1)}, S_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{S_{\gauge}^{(1)}(Q_1), S_{\matter}^{(1)}(Q_2)\} - \{S_{\gauge}^{(1)}(Q_2), S_{\matter}^{(1)}(Q_1)\} \\
@@
 
+\item
 \[
@@
 
-and
+\item
 \[
@@
 \]
+\end{enumerate}
 
@@
 It is important here that we are working in the complexified setting.
-While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges, since a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
+While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges.
+Indeed, a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
 So necessarily, twists of maximal super Yang-Mills theory cannot be compatible with any unitary structure.
@@
 \begin{theorem}
-The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$.
+The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$.
 Moreover, the equivalence is $\SU(5)$-equivariant.
@@
 \begin{align*}
-S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
+S_{-\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
 &+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
-&+ \int \dvol(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*))
+&+ \int \dvol(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*)).
 \end{align*}
@@
 Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e. $(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it. 
-The above theory described by $S_{{\rm no } \chi}$ is perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
+The above theory described by $S_{-\chi}$ is perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
 \[
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
-
-This theory admits three twists:
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2; \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+
+This theory admits three twists by the following supercharges.
 \begin{itemize}
@@
 Moreover, we have an embedding $\alpha\colon \U(1)\subset\Spin(2, \CC)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action.
-In fact, this action will factor through $\U(4)$ by a direct observation.
+In fact, this action will manifestly factor through $\U(4)$.
 
@@
 \item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3,0}(M; \gg)[1]$.
-%Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
 \item A ghost field $c\in \Omega^0(M; \gg)[1]$.
@@
 \begin{align*}
-A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt a \\
-A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
-\rho&\rightsquigarrow \rho, \wt\chi \\
-B&\rightsquigarrow B, C.
+A_{1, 0}&\rightsquigarrow A_{1, 0}+ \wt a \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}+ a \\
+\rho&\rightsquigarrow \rho+ \wt\chi \\
+B&\rightsquigarrow B+ C.
 \end{align*}
@@
 \[(Q_t, Q_t) = t,\]
-so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.
+so at $t=0$ we have a holomorphic supercharge and $t\neq 0$ we have a topological supercharge.
 
 We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}.
-Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$, $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$, and $a \in \Omega^0(\CC^4 ; \fg)$.
+Using the Calabi--Yau structure we will regard $C$ as an element of $\Omega^{0, 1}(\CC^4;\fg)[1]$, $\wt\chi$ as an element of $\Omega^0(\CC^4;\fg)[-1]$, and $a$ as an element of $\Omega^0(\CC^4 ; \fg)$.
 First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.
@@
 \begin{align*}
-S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*) + (t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
+S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^* + (F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*)\right) 
+&+ \int\dvol\left((t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
 S^{(2)}(Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + tac^*\right) + \frac{t}{2}\Omega^{-1}B^*\wedge B^* .
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \CC)$ with $W$ the two-dimensional spin representation.
-
-This theory admits three twists:
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \CC)$ acting on $W$ by its two-dimensional spin representation.
+
+This theory admits three twists, by the following classes of supercharge.
 \begin{itemize}
@@
 These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
-We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection on the second factor, so the theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
+We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection onto the second factor, so the theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
 \end{itemize}
@@
 
-It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations.
+It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations, similarly to Theorem \ref{thm:10dCSreduction}.
 
@@
 Suppose $N_\RR=\RR^{4-\dim(L)}$ equipped with a Euclidean metric and a spin structure.
-Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density.
+Denote by $N=N_\RR\otimes_\RR\CC$ its complexification, which carries a complex half-density.
 Let $V_\RR = L\times N$ (an 8-dimensional real vector space).
@@
 Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(2, \CC)\times \Spin(N_\RR)$.
-We consider the grading $\alpha\colon \U(1)\rightarrow G_R$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
+We consider the $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
 \[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\Spin(2, \RR)\times \Spin(N_\RR).\]
@@
 
-There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(1, 1)$ supersymmetry, which we consider separately.
+There are Yang--Mills theories with $\cN=(1, 0)$ and $\cN=(1, 1)$ supersymmetry, which we consider separately.
 
@@
 \begin{align*}
-& \int \bigg(\xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \bigg) \\
- &+ \int \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + [B, c] \wedge B^* .
+& \int \bigg(\xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \bigg) + \dvol \left(  \frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*)\right) \\
+ &+ \int \dvol\left((\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right) + [B, c] \wedge B^* .
 \end{align*}
 Up to rescaling the antifields, this is the action functional of the required theory.
-%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
 \end{proof}
@@
 
-Note that the $\MU(3)$-action on the fields factors through $\U(3)$ since the square roots of $K$ have canceled out.
+Note that the $\MU(3)$-action on the fields factors through $\U(3)$ since only integer powers of $K$ occur.
 By comparing the degrees and the transformation rules of the fields in Theorem \ref{thm:6dholomorphictwist} we obtain the following statement.
@@
 \begin{theorem}
-The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $T^*[-1]\map(M, R/\fg)$.
+The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with space of fields $T^*[-1]\map(M, R/\fg)$.
 Moreover, the equivalence is $\U(3)$-equivariant.
@@
 These automatically square to zero and have 4 invariant directions.
-There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SL(2, CC)\times \SL(2, \CC)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
+There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SL(2, \CC)\times \SL(2, \CC)$ given by the diagonal embedding and a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.
 
@@
 
-A square-zero supercharge $Q$ has rank 1, i.e. $Q=q_+\otimes w_1$ for some $w_1\in W$. We also choose $w_2\in W$ such that $(w_1, w_2) = 1$. We have a twisting homomorphism
+A square-zero supercharge $Q$ has rank 1, i.e. $Q=q_+\otimes w_1$ for some $w_1\in W$. Choose a complementary element $w_2\in W$ such that $(w_1, w_2) = 1$. We have a twisting homomorphism
 \[\phi\colon\MU(2)\xrightarrow{\det^{1/2}}\U(1)\subset \SL(2, \CC)\]
@@
 The 5d $\cN=2$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
-It admits $R$-symmetry group $G_R=\Spin(5, \CC)$ under which $W$ is the 4-dimensional spin representation which carries a symplectic pairing.
+It admits $R$-symmetry group $G_R=\Spin(5, \CC)$ under which $W$ is the 4-dimensional spin representation equipped with a symplectic pairing.
 
@@
 
-This theory admits four twists:
+This theory admits twists by the following four classes of supercharge.
 \begin{itemize}
@@
 Consider the 8-dimensional spacetime $V_\RR=L\times N$.
-Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 8-dimensional square-zero supercharges given by \eqref{eq:8dHodgefamily} dimensionally reduces to a family of 5-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 4 invariant directions.
+Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 8-dimensional square-zero supercharges given by \eqref{eq:8dHodgefamily} dimensionally reduces to a family of 5-dimensional square-zero supercharges, which at $t\neq 0$ are topological at and $t=0$ have 4 invariant directions.
 Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the rank 2 partially topological twist and at $t\neq 0$ we obtain the rank 2 topological twist.
@@
 
-We consider $V_\RR=\RR^5$ equipped with a Euclidean structure and as before let $V=V_\RR\otimes_\RR\CC$ be its complexification.
+We consider $V_\RR=\RR^5$ equipped with a Euclidean structure and, as before, let $V=V_\RR\otimes_\RR\CC$ be its complexification.
 $V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sect:10dholomorphictwist} we obtain a square-zero supercharge $Q$.
@@
 \subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills Theory} \label{sect:4d_1_section}
-The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall.
+The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sect:SYM}, which we now recall.
 Let $R$ be a complex $\fg$-representation.
@@
 \end{itemize}
-%The corresponding antifields are given by:
-%\begin{itemize}
-%\item $A_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-1]$, $B_{2, 1}\in\Omega^{2, 1}(M; \fg)[-1]$.
-%\item $\lambda_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-2]$, $\lambda_0^*\in\Omega^0(M; \fg)$, $B_{2, 0}\in\Omega^{2, 0}(M; \fg)$.
-%\item $\phi^*\in\Omega^{2, 2}(M; R)$, $\gamma_0^*\in\Omega^0(M; R^*)$.
-%\item $\psi_0^*\in\Omega^{2, 2}(M; R)[-2]$, $\gamma_{0, 2}\in\Omega^{0, 2}(M; R)[-2]$, $\beta_{2, 1}\in\Omega^{2, 1}(M; R^*)$.
-%\item $B_{2, 2}\in\Omega^{2, 2}(M; \gg)[-2]$.
-%\end{itemize}
 
@@
 The 4d $\cN=2$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$.
-Let $W$ be a two-dimensional complex symplectic vector space.
+Let $W$ be a two-dimensional complex vector space.
 The theory admits the $R$-symmetry group $G_R=\SL(2;\CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts on $W$ with weight $1$.
@@
 \item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
-\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[4n-2]$ and $a \in\Omega^{0}(M; \gg)[-4n+2]$;
+\item Scalar fields $\Tilde{a} \in \Omega^{0}(M; \gg)[4n-2]$ and $a \in\Omega^{0}(M; \gg)[-4n+2]$
 \item Gauge fermions $\chi \in \Omega^0(M ; \gg)[-1]$, $\xi \in \Omega^{2,0}(M ; \gg)[4n-1]$, $B \in \Omega^{0,2}(M ; \gg)[-1]$, $b \in \Omega^{0,1}(M ; \gg)[-4n+1]$, $\rho \in \Omega^{1,0}(M ; \gg)[1]$,  $\Tilde{\chi} \in \Omega^0(M ; \gg)[4n-1]$.
@@
 \begin{align*}
-A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
-A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
-B&\rightsquigarrow B, b \\
-\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
-\psi & \rightsquigarrow \psi, \varsigma . \\
+A_{1, 0}&\rightsquigarrow A_{1, 0}+ \Tilde{a} \\
+A_{0, 1}&\rightsquigarrow A_{0, 1}+ a \\
+B&\rightsquigarrow B+ b \\
+\rho&\rightsquigarrow \rho+ \Tilde{\chi} \\
+\psi & \rightsquigarrow \psi+ \varsigma . \\
 \end{align*}
@@
 Next, we check that the equivalence respects  the gradings.
-Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates fields $A_{1, 0}, \Tilde{a}, \rho, \chi, \Tilde{\chi}$.
+Indeed, the equivalence given by Theorem \ref{thm:5dminimaltwist} eliminates the fields $A_{1, 0}, \Tilde{a}, \rho, \chi$ and $\Tilde{\chi}$.
 The rest of the fields organize into the following collections:
@@
 &+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
 S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
@@
  \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
- Since $S_+$, $S_-$ and $W$ all carry volume forms, such a square-zero supercharge is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, the space of such square-zero supercharges is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
 These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
@@
 
-We use the same twisting homomorphism $\phi \colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha \colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+We use the same twisting homomorphism $\phi \colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha \colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
 Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
@@
 The 4d $\cN=4$ super Yang--Mills theory viewed as a $\cN=2$ theory is 4d $\cN=2$ Yang--Mills theory with matter valued in $U=T^*\fg$. 
-Under this correspondence $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
+Under this identification $\alpha\colon \U(1)\rightarrow G_R$ defined above coincides with $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. 
 From Theorem \ref{thm:4dDonaldsontwist} we obtain that the twist is $\Sect\left(\CC^2, \left((T^*\fg \otimes K_{\CC^2}^{1/2})\ham \fg\right)_{\Hod}\right)$ as a $\ZZ$-graded theory.
@@
 
-We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
 Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
@@
 \]
-Further, the representation $S_- \otimes W^*$ decomposes as
+The representation $S_- \otimes W^*$ decomposes as
 \[
@@
 In this case the spinorial representation becomes
-\[\Sigma\cong S_+\otimes S_+\oplus S_+\otimes S_-\oplus S_-\otimes S_+\oplus S_-\otimes S_-.\]
+\[\Sigma\cong (S_+\otimes S_+)\oplus (S_+\otimes S_-)\oplus (S_-\otimes S_+)\oplus (S_-\otimes S_-).\]
 In particular, there are two scalar supercharges $Q_+$ and $Q_-$ given by the volume forms on $S_+$ and $S_-$ respectively. We may then consider a family of supercharges
@@
 \begin{remark}
-The family $uQ_+ + iv Q_-$ of square-zero supercharges is the same family as studied by Kapustin and Witten, see \cite[Section 3.1]{KapustinWitten}.
+The family $uQ_+ + iv Q_-$ of square-zero supercharges is the same family studied by Kapustin and Witten, see \cite[Section 3.1]{KapustinWitten}.
 \end{remark}
@@
 $S_+^8$ splits as
-\[S_+^8\cong S_+\otimes S_+\oplus S_-\otimes S_-,\]
+\[S_+^8\cong (S_+\otimes S_+)\oplus (S_-\otimes S_-),\]
 so $Q_+, Q_-\in S_+^8$. We then obtain
@@
 
-As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
+As in Section \ref{sect:9dminimaltwist}, the specification of $q$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.
 Note that in one dimension the choice of a complex half-density is equivalent to a choice of spin structure.
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
-Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
+Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory, or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
 The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
@@
 \begin{proof}
-Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
+Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supersymmetry algebra.
 The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.
@@
 First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.
-%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
 The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (-a, -b)$.
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section}, to representations of the group $\spin(2;\CC)$.
 In any case, the fields we obtain are
@@
 The calculation of the twists here is similar to what we saw in 4d $\mc N=2$ supersymmetry.  
-The minimal twist and the $B$-twist arise by dimensional reduction from twists of $3d$ $\cN=2$ supersymmetric Yang-Mills theory.
+The minimal twist and the $B$-twist arise by dimensional reduction from twists of 3d $\cN=2$ supersymmetric Yang-Mills theory.
 On the contrary, the $A$-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
@@
 Let us first decompose our fields according to the twisting homomorphism $\phi_A$:
-%The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
-%\begin{itemize}
-% \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
-% %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
-% \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
-% %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
-% \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
-% \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
-% \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
-%\end{itemize}
 
@@
 \item gauge fermions $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
- %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
- \item matter bosons $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
- %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
+ \item matter bosons $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$.
  \item matter fermions $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
@@
 \end{itemize}
-%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.
 
@@
 
-%\begin{prop}
-%Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
-%The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
-%\begin{align*}
-%S_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(-(\lambda_{-2}, A^*_1) - (\lambda_0, \chi^*_{-1})) + \frac 12((\rho(\ol \dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\ol \dd_{A_1}\chi_{-1}), \lambda_0^*)) \right)  \\
-%&+  \int \dvol t \left( -(\lambda_{2}, A^*_1) - (\lambda'_0, \chi^*_{1})) + \frac 12((\rho(\dd_{A_{-1}}A_{-1}), \lambda_{2}^*) + (\rho(\dd_{A_{-1}}\chi_{1}), \lambda_0^{'*}))   \right)  \\
-%S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t (\lambda_0^*, \Tilde{\lambda}_0^*) - \frac 14(\lambda_0^* + t \Tilde{\lambda}_0^*)^2 + t(a, c^*)\right)  \\
-%S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left(\left( (\ol \psi_{-1},\phi_0^*) + \frac 12 (\ol \dd_{A_1} \ol \phi_0, \psi_{-1}^*) \right) +t\left( (\ol \psi_{1},\ol \phi_0^*) + \frac 12 (\dd_{A_{-1}}  \phi_0, \psi_{1}^*)  \right)\right)  \\
-%S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4 \left( (\psi^*_{-1} ,\psi^*_{-1}) +  (\psi^*_{1}, \psi^*_{1}) \right).
-%\end{align*}
-%\end{prop}
-
 \begin{theorem} \label{2d_2_A_twist_thm}
@@
 
-%We first perform a change of variables sending $\lambda_0$ to $\lambda_0 + t\lambda_0'$, and its antifield $\lambda_{-2}^*$ to $\lambda_{-2}^* - t\lambda_0^{'*}$.
-%We integrate out the field $\lambda_2 + t\lambda_0'$ and its antifield using Proposition \ref{prop:integrateoutfield}.  
-%We then eliminate the trivial BRST doublets $(\lambda_{-2}, A_{-1}), (\ol \psi_{-1}, \phi_0)$ and $(\lambda_0, \chi_1)$ using Proposition \ref{prop:BRSTdoublet}. 
-%The resulting action functional is of the form
 \[
@@
 }\]
-%\[\xymatrix@R=0.4cm@C=0.2cm{
-%\ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-%&\Omega^0(\RR^2; \gg)_{c_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg)_{A_1} & & \Omega^0(\RR^2; \gg^*)_{\lambda^{'*}_0} \ar[r] &\Omega^{0,1}(\RR^2; \gg^*)_{\chi_1^*} \\
-%\Omega^0(\RR^2; \gg)_{\chi_{-1}} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg)_{\lambda'_0} \ar@{-->}[ur] && \Omega^0(\RR^2; \gg^*)_{A^*_1} \ar[r] \ar@{-->}[ur] &\Omega^{0,1}(\RR^2; \gg^*)_{c_0^*} \ar@{-->}[ur]\\
-%&\Omega^0(\RR^2; R^*)_{\ol \psi_{-1}} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2; R^*)_{\psi^*_1} \ar@{-->}[dr] &&&\\
-%&& \Omega^0(\RR^2; R^*)_{\ol \phi_0} \ar[r]  &\Omega^{0,1}(\RR^2; R^*)_{\psi_{-1}} &&\\
-%&&\Omega^0(\RR^2; R)_{\psi_{-1}^*} \ar[r] \ar@{-->}[dr] &\Omega^{0,1}(\RR^2;  R)_{\ol \phi^*_0} \ar@{-->}[dr] &&\\
-%&&& \Omega^0(\RR^2; R)_{\psi_1} \ar[r]  &\Omega^{0,1}(\RR^2; R)_{\ol \psi^*_{1}}. &\\
-%}\]
 Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
@@
 \begin{proof}
-Decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. 
+Decompose the 6d semi-spin representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. 
 A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
@@
 
-The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semispin representations.
-As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we say in the $\mc N=(4,4)$ case.
+The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.
+As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we saw in the $\mc N=(4,4)$ case.
 Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.
@@
 The element $w_+$ is equivalent to the data of a Lagrangian subspace $L \sub V_8$, along with a half-density.
-As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semispin representations decompose as
+As a representation of the subgroup $\mr{ML}(L)$ of $\stab(w_+)$, the two semi-spin representations decompose as
 \begin{align*}
@@
 
-The theory admits a unique twist:
-\begin{itemize}
-\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
+The theory admits a unique twist by the following class of supercharge.
+\begin{itemize}
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
 Such supercharges are automatically square-zero and are holomorphic.
@@
 \]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
-
-Further, fields decompose under the twisting homomorphism as:
-\begin{itemize}
-\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
-\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
-\item matter bosons $\phi \in \Omega^0(\CC ; R^*)$, $\gamma_0 \in \Omega^0(\CC ; R)$;
-\item matter fermions $\psi \in \Omega^{0}(\CC ; R^*)[1]$, $\gamma_{0,1} \in \Omega^{0,1}(\CC ; \fg)[-1]$;
+Note that under the twisting homomorphism $\phi = \det^{1/2}$ we have $W_+ = \det(L)^{1/2} \oplus \det^{-1/2}$.
+
+The fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$.
+\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$.
+\item matter bosons $\phi \in \Omega^0(\CC ; R^*)$, $\gamma_0 \in \Omega^0(\CC ; R)$.
+\item matter fermions $\psi \in \Omega^{0}(\CC ; R^*)[1]$, $\gamma_{0,1} \in \Omega^{0,1}(\CC ; \fg)[-1]$.
 \item a ghost field $A_0 \in \Omega^0(\CC ; \fg)[1]$.
@@
 
-%
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
-%A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-%\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
-%\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
-%\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
-%\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
-%\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
-%\end{array}
-%\]
-%The anti-fields decompose as
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
-%A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
-%\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
-%\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
-%\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
-%\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
-%\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
-%\end{array}
-%\]
-
-%\begin{align*}
-%c^* & \mapsto B_{1,1} \in \Omega^0(\CC ; \fg) \\
-%A^* & \mapsto A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \\
-%\lambda^* & \mapsto \lambda^*_{1,1} w_1 + \lambda^*_{0,1} w_2 \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \\
-%\phi^* & \mapsto \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) \\
-%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{1,1}(\CC ; R) \\
-%\psi^* & \mapsto \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) \\
-%\Bar{\psi}^* & \mapsto \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)  
-%\end{align*}
-
-The action functionals decompose as:
+The action functional decomposes as follows:
 \begin{align*}
@@
 \end{align*}
-%Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.
-
-\begin{theorem} \label{2d(0,2)}
-The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+
+\begin{theorem} \label{thm:2d(2,0)}
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 
-We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
-The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
-Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
-
-The field content is:
-\begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-\end{itemize}
-
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
+In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
+The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$.
+The $R$-symmetry group is $\Spin(4;\CC)$, which acts on $W_+$ as the defining representation.
+
+\begin{itemize}
+\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item matter bosons $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$  
+\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
+\end{itemize}
+
+The fields $\lambda, \psi$ transform in the defining representation of $G_R = \spin(4;\CC)$.
+
+The theory admits a unique twist:
+\begin{itemize}
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
+Such supercharges are automatically square-zero, holomorphic, and lie in a $(2,0)$ supersymmetry subalgebra.
+There is a compatible twisting homomorphism
+\[
+\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
+\]
+which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
+\end{itemize}
 
@@
 \begin{theorem}\label{2d(0,4)}
-The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-\end{theorem}
-
-\begin{proof}
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$, where $\fg$ acts by the adjoint action, plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+\end{theorem}
+
+\begin{proof}
+The supercharge $Q$ lies in an $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
+On the odd part of the supersymmetry algebra, this embedding is induced by the algebra map
 \[
@@
 The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
-The claim now follows from Theorem \ref{2d(0,2)}. 
+The claim now follows from Theorem \ref{thm:2d(2,0)}. 
 \end{proof}
@@
 
-The field content is:
-\[
-\begin{array} {lllcccccc}
-& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
-A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v + \chi \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_- \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
-\end{array}
-\]
+The field content is given as follows.
+\begin{itemize}
+ \item Bosons $(A_{0,1}, A_{1,0}) \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)$.
+ \item Fermions $(\lambda_{0} u, \lambda_{1,0} v, \chi) \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_- \otimes W_-' \otimes \fg)$.
+ \item A ghost field $A_{0} \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
 
 We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
-
-%\[
-%\begin{array} {lllcccccc}
-%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
-%c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
-%A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
-%\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
-%\end{array}
-%\]
-
-%\begin{align*}
-%S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
-%S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
-%&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
-%I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
-%I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
-%\end{align*}
 
@@
 The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The claim now follows from a special case of Theorem \ref{2d(0,2)} where we take $R = 0$. 
-%First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
-%We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
-%Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
-%which can be integrated out using Proposition \ref{prop:BRSTdoublet}.  
-%
-%The twisted theory is therefore perturbatively equivalent to the theory with BV action 
-%\begin{align*}
-% S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
-%  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
-%\end{align*}
-%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic BF theory and $\chi$ is the fundamental field for the free fermion system.
+The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
 \end{proof}

### 2020-02-21 paper.tex
3d updates

--- 2020-02-20 paper.tex
@@
  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[cor:3dN8Btwist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ && \multirow{2}*{\hyperref[cor:3dN8Atwist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
@@
 Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
+This datum generates a supersymmetry algebra, which we will denote by $\mf A$.
 We have a natural embedding
@@
 \begin{prop} \label{prop:susydimlred}
-Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
+Suppose $(E, \omega, S)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*S^{(i)}_{V_\RR} = S^{(i)}_{W_\RR}$.
 \end{prop}
@@
 \begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, \omega, S)$ to auxiliary fields generated by the representation $\Sigma$.
 \end{proof}
@@
 \begin{prop}
-Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
+Fix a square-zero supercharge $Q$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
 Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
@@
 
-We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
+We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $S_{\gauge}^{(1)}, S_{\gauge}^{(2)}, \dots$, where $S_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $S_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
 The action of supersymmetry is given by a linear and a quadratic functional
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2; \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
@@
 \begin{theorem}
-Fix the twisting datum $\alpha = \alpha_n$.
+Fix the homomorphism $\alpha = \alpha_n$.
 The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
@@
 The maximal supersymmetric gauge theory has $\mc N=8$.
-However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.
+There are $\mc N=4$ super Yang--Mills theories for every choice $U$ of a complex symplectic representation of the gauge group, and $\mc N=2$ super Yang--Mills theories for every choice $R$ of arbitrary complex representation of the gauge group.
+Finally, there are $\cN=1$ super Yang--Mills theories in 3 dimensions, but there are no square-zero supercharges with that amount of supersymmetry.
 In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
@@
 \label{sect:3d_2_section}
-We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
-So, fix a gauge group $G$, and a representation $R$.
-The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
+
+Fix a gauge group $G$ and a representation $R$.
+The 3d $\mc N=2$ super Yang--Mills theory arises by dimensional reduction from 4d $\mc N=1$ super Yang--Mills theory with an $R$-valued chiral multiplet.
 In this case, $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
-
-The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by the defining representation.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.
-The fields we obtain are
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
- \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
- \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
- \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
- \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
-\end{itemize}
+The R-symmetry group is $G_R=\CC^\times$, acting on $W$ with weights $1$ and $-1$.
 
@@
  \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
-The twist is $\ZZ$-graded with $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding. 
+There is a twisting homomorphism $\phi = \MU(1)\cong \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
+The twist is $\ZZ$-graded.
 \end{itemize}
@@
 \label{sect:3dminimaltwist}
-A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
-We use the twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.
+A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$. We use the twisting homomorphism $\phi\colon \MU(1)\xrightarrow{\det^{1/2}} \U(1)\hookrightarrow G_R$.
 
@@
 \begin{theorem} \label{3d_minimal_twist_thm}
-The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with Lie algebra $\fg$ with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
 Moreover this equivalence is $\mr U(1)$-equivariant.
@@
 \begin{proof}
-By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
+By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
+By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of the holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$.
 \end{proof}
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
-Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
-
-\vspace{-10pt}
-\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
-The fields are:
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
- \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
- \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
- \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
-\end{itemize}
+Next, consider the 3d $\mc N=4$ supersymmetric Yang--Mills theory with matter valued in a symplectic $G$-representation $U$.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the vector representation.
 
@@
  In this case $Q$ is minimal, with 2 invariant directions.  
- Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
-They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
+ Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence. They admit a twisting homomorphism and a $\ZZ$-grading.
  \item Rank 2. Such supercharges are topological.  
@@
 The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
-We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
+We refer to these as the $A$-twist and the $B$-twist, distinguished by whether they admit a $\ZZ$-grading:
 \begin{enumerate}
@@
 A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
-This twist is only $\ZZ/2\ZZ$-graded
+This twist is only $\ZZ/2\ZZ$-graded.
 \end{enumerate}
@@
 \begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
-Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
+A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
+Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
 \end{lemma}
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
+This supercharge admits a compatible homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
 This is the $A$-twist in our classification above.
 
-A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
+A rank $(1,1)$ supercharge induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
 This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.
@@
 \label{sect:3d_4_minimal_twist}
-Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.
-
-There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
-
-This twist also admits the following twisting datum.
-To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
-The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
-Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
+There is a unique twisting homomorphism $\phi \colon \MU(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\MU(1) \subset \MU(2)$.
+
+To incorporate the $\ZZ$-grading, we use the homomorphism $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
+This homomorphism coincides with the dimensional reduction of $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}.
+The corresponding $\U(1)$-action on the 3d auxiliary space $W$ under $\alpha$ coincides with the $\U(1)$-action on the 4d auxiliary space $W_4$ under the isomorphism $W\cong W_4\oplus W_4^*$.
+Indeed, both have weights $(1,1,-1,-1)$.
+Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
 %However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
@@
 \begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\Sect(\CC \times \RR_{\mr{dR}}, (U \otimes K^{1/2}_\CC) \ham \gg))$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
-This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
+\begin{proof}
+The statement follows by applying the dimensional reduction (Theorem \ref{prop:BFholomorphicreduction}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of the 4d $\mc N=2$ super Yang--Mills theory on $\CC\times\CC$, where we dimensionally reduce along the projection $\Re\colon\CC\rightarrow \RR$ in the second factor.
 \end{proof}
@@
 Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
-Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological $A$ twist.
 Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
@@
 \begin{theorem}
-The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
+The twist of the 3d $\cN=4$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(\CC \times \RR_{\mr{dR}}, ((U \otimes K^{1/2}_\CC)\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 \begin{corollary}
-The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
+The topological $A$ twist of the 3d $\cN=4$ super Yang--Mills theory is perturbatively trivial.
 \end{corollary}
@@
 \begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\map(\RR^3_{\mr{dR}}, U\ham \gg)$.
+The rank $2$ B-twist of the 3d $\mc N=4$ super Yang--Mills theory is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\RR^3_{\mr{dR}}, U\ham \gg)$.
 Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.
@@
 \subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang--Mills Theory} \label{3d8section}
-Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
+Finally, consider the maximally supersymmetric Yang--Mills theory in dimension 3.
 This theory is the dimensional reduction of 10d $\cN = (1,0)$ supersymmetric Yang--Mills theory.  
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional (Dirac) spin representation.
-
-\vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
-The fields are:
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
- \item gauge fermions $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
- \item a ghost field $c \in \Omega^0(\RR^3;\gg)[1]$.
-\end{itemize}
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional spin representation.
 
@@
 \begin{lemma}
-There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
+There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra: the generic orbit and the special orbit.
+\label{lm:3dN8twoorbits}
 \end{lemma}
@@
 The classification of twists therefore takes the following form.
-We identify how the two orbits of rank 2 supercharges arise by dimensional reduction from 4d $\mc N=4$ by forgetting the supertranslation action down to 3d $\mc N=4$ (this may partially break the R-symmetry, but this is enough to distinguish the two classes of twisted theory).
 \begin{itemize}
@@
 Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $A$-twist.
-These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
-The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
-It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
- \item Rank 2 $B$-twist.
-These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
-The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
-It admits a twisting homomorphism $\phi \colon \Spin(3;\RR) \to G_R$.
+They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading.
+ \item Rank 2 twists. These twists are topological, and come from the $\mc N=4$ supersymmetry algebra. They admit a twisting homomorphism from $\Spin(3, \RR)$ and a $\ZZ$-grading. There are two such:
+ \begin{enumerate}
+ \item $A$-twist (the generic rank 2 orbit).
+ \item $B$-twist (the special rank 2 orbit).
+ \end{enumerate}
 \end{itemize}
@@
 \label{sect:3d8minimal_twist}
-The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.
-Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.
+
+The 3d $\cN=8$ supersymmetric Yang--Mills theory is obtained by a dimensional reduction of the 4d $\mc N=4$ supersymmetric Yang--Mills theory.
+Therefore, from Theorem \ref{thm:4d4holomorphictwist} we obtain the following statement.
 
 \begin{theorem}  \label{3d_8_minimal_twist_thm}
-The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
+The minimal twist of the 3d $\cN=8$ super Yang--Mills theory on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to the desired generalized BF theory.
-\end{proof}
 
@@
 
-\subsubsection{Topological $A$-Twist}
-\label{sect:3d8A_Twist}
-From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.
-
-\begin{theorem} \label{3d_8_A_twist_thm}
-The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
-Moreover, this equivalence is $\U(1)$-equivariant.
-\end{theorem}
-\brian{Need to explain what happened to $\Sect$}
-
-\begin{corollary}
-The topological $A$-twist of 3d $\cN=8$ super Yang-Mills is perturbatively trivial.
-\end{corollary}
-
-\subsubsection{Topological $B$-Twist}
-\label{sect:3d8B_Twist}
-From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
-
-\begin{theorem} \label{3d_8_B_twist_thm}
-The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
-%Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
-\end{theorem}
-\brian{Need to explain what happened to $\Sect$}
+\subsubsection{Topological Twists}
+
+Consider the dimensional reduction of the family $Q_t$ of rank $(2, 2)$ square-zero supercharges in the 4d $\cN=4$ supersymmetry algebra from Section \ref{sect:4dqgltwist}.
+Since this is a family of topological supercharges in 4 dimensions, it dimensionally reduces to a family of topological supercharges in 3 dimensions.
+
+\begin{theorem}
+The twist of the 3d $\cN=8$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $T^*[-1]\map(\RR^3_{\mathrm{dR}}, B\fg_{\Hod})$.
+Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
+\label{thm:3d8Hodgetwist}
+\end{theorem}
+\begin{proof}
+The claim follows by dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) from the corresponding statement in 4 dimensions (Theorem \ref{thm:4d422Hodgetwist}) which calculates the twist of the 4d $\cN=4$ super Yang--Mills theory with respect to that family to be $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$.
+\end{proof}
+
+As we see from Theorem \ref{thm:3d8Hodgetwist}, at $t\neq 0$ the twist is perturbatively trivial while at $t=0$ it is not.
+By Lemma \ref{lm:3dN8twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the $A$-twist and the case $t=0$ (the special orbit) must be the $B$-twist.
+
+\begin{cor}
+The topological $A$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
+\label{cor:3dN8Atwist}
+\end{cor}
+
+\begin{cor}
+The topological $B$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$.
+Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
+\label{cor:3dN8Btwist}
+\end{cor}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
-
-We turn to $\cN=(2,0)$ supersymmetric Yang-Mills theory.
-In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
-The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
-The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_+$ by the defining representation.
-
-The fields of the untwisted theory are:
+\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
+
+We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
+Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$. 
+The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.
+
+The untwisted fields are given by:
 \begin{itemize}
 \item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
 \item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_- \otimes R)$.
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 \begin{itemize}
-\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
+\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
 Such supercharges are automatically square-zero and are holomorphic.
@@
 \]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det^{-1/2}$.
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
 
@@
 
-\begin{theorem} \label{thm: 2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+\begin{theorem} \label{2d(0,2)}
+The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 
-Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
-In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
-The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The $R$-symmetry group is $\Spin(4;\CC)$, which acts on $W_+$ as the defining representation.
-
-%The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
-%Let $W = {\rm span}_{\CC} \{u_1,u_2\}$. 
-\begin{itemize}
-\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$  
-\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
-\end{itemize}
-
-The fields $\lambda, \psi$ transform in the defining representation of $G_R = \spin(4;\CC)$.
-
-The theory admits a unique twist:
-\begin{itemize}
-\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
-Such supercharges are automatically square-zero, holomorphic, and lie in a $(2,0)$ supersymmetry subalgebra.
-There is a compatible twisting homomorphism
-\[
-\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
-\]
-which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
-\end{itemize}
-
-%The field content is:
-%\begin{itemize}
-%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-%\end{itemize}
-
-%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
+The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
+The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
+Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
+
+The field content is:
+\begin{itemize}
+\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+\end{itemize}
+
+We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
 

### 2020-02-21 paper.tex

--- 2020-02-20 paper.tex
@@
 We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfy the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $S_{\gauge}^{(1)}, S_{\gauge}^{(2)}, \dots$, where $S_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $S_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
 The action of supersymmetry is given by a linear and a quadratic functional
@@
 \begin{theorem} \label{3d_minimal_twist_thm}
-The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized BF theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
-Moreover this equivalence is $\mr U(1)$-equivariant.
-\end{theorem}
-
-\begin{proof}
-By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
-By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
+The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with Lie algebra $\fg$ with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+Moreover, this equivalence is $\mr U(1)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
+By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of the holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$.
 \end{proof}
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
-Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory, or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
-
-\vspace{-10pt}
-\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
-The fields are:
-\begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
- \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
- \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
- \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
- \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
-\end{itemize}
+Next, consider the 3d $\mc N=4$ supersymmetric Yang--Mills theory with matter valued in a symplectic $G$-representation $U$.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the vector representation.
 

### 2020-02-21 paper.tex
merge

--- 2020-02-21 paper.tex
@@
  & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[cor:3dN8Btwist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\
  &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[cor:3dN8Atwist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
+ && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
+ &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
@@
  \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
- &&& $T^*[-1]\mr{Sect}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Sect}(\CC^2, (U \otimes K_{\CC^2}^{1/2}) \ham \fg)$ & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
@@
 Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.
-This datum generates a supersymmetry algebra, which we will denote by $\mf A$.
+This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.
 We have a natural embedding
@@
 \begin{prop} \label{prop:susydimlred}
-Suppose $(E, \omega, S)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
-Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*S^{(i)}_{V_\RR} = S^{(i)}_{W_\RR}$.
+Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$.
+Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
 \end{prop}
@@
 \begin{proof}
-This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, \omega, S)$ to auxiliary fields generated by the representation $\Sigma$.
+This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
 \end{proof}
@@
 \begin{prop}
-Fix a square-zero supercharge $Q$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$.
+Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$.
 Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
@@
 
-We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
-Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $S_{\gauge}^{(1)}, S_{\gauge}^{(2)}, \dots$, where $S_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
-The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $S_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
+We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory.
+Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation.
+The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$.
 The action of supersymmetry is given by a linear and a quadratic functional
@@
 \begin{theorem}
-Fix the homomorphism $\alpha = \alpha_n$.
+Fix the twisting datum $\alpha = \alpha_n$.
 The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$.
@@
 The maximal supersymmetric gauge theory has $\mc N=8$.
-There are $\mc N=4$ super Yang--Mills theories for every choice $U$ of a complex symplectic representation of the gauge group, and $\mc N=2$ super Yang--Mills theories for every choice $R$ of arbitrary complex representation of the gauge group.
-Finally, there are $\cN=1$ super Yang--Mills theories in 3 dimensions, but there are no square-zero supercharges with that amount of supersymmetry.
+However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.
 In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
@@
 \label{sect:3d_2_section}
-
-Fix a gauge group $G$ and a representation $R$.
-The 3d $\mc N=2$ super Yang--Mills theory arises by dimensional reduction from 4d $\mc N=1$ super Yang--Mills theory with an $R$-valued chiral multiplet.
+We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).
+So, fix a gauge group $G$, and a representation $R$.
+The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.
 In this case, $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.
-The R-symmetry group is $G_R=\CC^\times$, acting on $W$ with weights $1$ and $-1$.
+
+The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by the defining representation.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.
+The fields we obtain are
+\begin{itemize}
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
+ \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
+ \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
+ \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
+ \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
+\end{itemize}
 
@@
  \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.
-There is a twisting homomorphism $\phi = \MU(1)\cong \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
-The twist is $\ZZ$-graded.
+There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
+The twist is $\ZZ$-graded with $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding. 
 \end{itemize}
@@
 \label{sect:3dminimaltwist}
-A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$. We use the twisting homomorphism $\phi\colon \MU(1)\xrightarrow{\det^{1/2}} \U(1)\hookrightarrow G_R$.
+A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
+We use the twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.
 
@@
 \begin{theorem} \label{3d_minimal_twist_thm}
-The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with Lie algebra $\fg$ with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
+The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$.
 Moreover this equivalence is $\mr U(1)$-equivariant.
@@
 \begin{proof}
-By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
-By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of the holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$.
+By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$.
+By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
 \end{proof}
@@
 \subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
-Next, consider the 3d $\mc N=4$ supersymmetric Yang--Mills theory with matter valued in a symplectic $G$-representation $U$.
-The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the vector representation.
+Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory.
+The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.
+
+\vspace{-10pt}
+\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
+The fields are:
+\begin{itemize}
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
+ \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
+ \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
+ \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
+ \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
+\end{itemize}
 
@@
  In this case $Q$ is minimal, with 2 invariant directions.  
- Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence. They admit a twisting homomorphism and a $\ZZ$-grading.
+ Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
+They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
  \item Rank 2. Such supercharges are topological.  
@@
 The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  
-We refer to these as the $A$-twist and the $B$-twist, distinguished by whether they admit a $\ZZ$-grading:
+We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
 \begin{enumerate}
@@
 A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
-This twist is only $\ZZ/2\ZZ$-graded.
+This twist is only $\ZZ/2\ZZ$-graded
 \end{enumerate}
@@
 \begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
-Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
+A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
+Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
 \end{lemma}
@@
 A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.
-This supercharge admits a compatible homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
+The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
 This is the $A$-twist in our classification above.
 
-A rank $(1,1)$ supercharge induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
+A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
 This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.
@@
 \label{sect:3d_4_minimal_twist}
-There is a unique twisting homomorphism $\phi \colon \MU(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\MU(1) \subset \MU(2)$.
-
-To incorporate the $\ZZ$-grading, we use the homomorphism $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
-This homomorphism coincides with the dimensional reduction of $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}.
-The corresponding $\U(1)$-action on the 3d auxiliary space $W$ under $\alpha$ coincides with the $\U(1)$-action on the 4d auxiliary space $W_4$ under the isomorphism $W\cong W_4\oplus W_4^*$.
-Indeed, both have weights $(1,1,-1,-1)$.
-Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
+Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.
+
+There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.
+
+This twist also admits the following twisting datum.
+To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.
+The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.
+Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
 %However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
@@
 \begin{theorem} \label{3d_4_minimal_twist_thm}
-The minimal twist of 3d $\cN=4$ super Yang--Mills on $\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\Sect(\CC \times \RR_{\mr{dR}}, (U \otimes K^{1/2}_\CC) \ham \gg))$.
+The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
-\begin{proof}
-The statement follows by applying the dimensional reduction (Theorem \ref{prop:BFholomorphicreduction}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of the 4d $\mc N=2$ super Yang--Mills theory on $\CC\times\CC$, where we dimensionally reduce along the projection $\Re\colon\CC\rightarrow \RR$ in the second factor.
+
+\begin{proof}
+The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_diml_red_prop}) to Theorem \ref{thm:4d2holomorphictwist} calculating the holomorphic twist of 4d $\mc N=2$ super Yang-Mills on $N \times L_\CC$.
+This equivalence is equivariant for the action of $\mr U(1) \iso \MU(N) \sub \MU(N \times L_\CC)$.
 \end{proof}
@@
 Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
-Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological $A$ twist.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological B twist.
 Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
@@
 \begin{theorem}
-The twist of the 3d $\cN=4$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(\CC \times \RR_{\mr{dR}}, ((U \otimes K^{1/2}_\CC)\ham \gg)_{\mr{Hod}})$.
+The twist of 3d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\mr{Sect}(N \times L_{\mr{dR}}, ((U \otimes K^{1/2}_N)\ham \gg)_{\mr{Hod}})$.
 Moreover, this equivalence is $\U(1)$-equivariant.
@@
 \begin{corollary}
-The topological $A$ twist of the 3d $\cN=4$ super Yang--Mills theory is perturbatively trivial.
+The topological $A$ twist of 3d $\cN=4$ super Yang--Mills is perturbatively trivial.
 \end{corollary}
@@
 \begin{theorem} \label{3d_4_B_twist_thm}
-The rank $2$ B-twist of the 3d $\mc N=4$ super Yang--Mills theory is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\RR^3_{\mr{dR}}, U\ham \gg)$.
+The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\map(\RR^3_{\mr{dR}}, U\ham \gg)$.
 Moreover, the equivalence is $\Spin(3; \RR)$-equivariant.
@@
 \subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang--Mills Theory} \label{3d8section}
-Finally, consider the maximally supersymmetric Yang--Mills theory in dimension 3.
+Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
 This theory is the dimensional reduction of 10d $\cN = (1,0)$ supersymmetric Yang--Mills theory.  
-The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional spin representation.
+The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional (Dirac) spin representation.
+
+\vspace{-10pt}
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.
+The fields are:
+\begin{itemize}
+ \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
+ \item gauge fermions $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
+ \item a ghost field $c \in \Omega^0(\RR^3;\gg)[1]$.
+\end{itemize}
 
@@
 \begin{lemma}
-There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra: the generic orbit and the special orbit.
-\label{lm:3dN8twoorbits}
+There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
 \end{lemma}
@@
 The classification of twists therefore takes the following form.
+We identify how the two orbits of rank 2 supercharges arise by dimensional reduction from 4d $\mc N=4$ by forgetting the supertranslation action down to 3d $\mc N=4$ (this may partially break the R-symmetry, but this is enough to distinguish the two classes of twisted theory).
 \begin{itemize}
@@
 Such supercharges come from the $\mc N=2$ supersymmetry algebra.
-They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading.
- \item Rank 2 twists. These twists are topological, and come from the $\mc N=4$ supersymmetry algebra. They admit a twisting homomorphism from $\Spin(3, \RR)$ and a $\ZZ$-grading. There are two such:
- \begin{enumerate}
- \item $A$-twist (the generic rank 2 orbit).
- \item $B$-twist (the special rank 2 orbit).
- \end{enumerate}
+They admit a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $A$-twist.
+These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
+The $A$-twist arises by dimensional reduction from the rank $(2,0)$ twist in 4d.
+It admits a twisting homomorphism from $\mr U(1)$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+ \item Rank 2 $B$-twist.
+These twists are topological, and come from the $\mc N=4$ supersymmetry algebra.
+The $B$ twist arises by dimensional reduction from the rank $(1,1)$ twist in 4d.
+It admits a twisting homomorphism $\phi \colon \Spin(3;\RR) \to G_R$.
 \end{itemize}
@@
 \label{sect:3d8minimal_twist}
-
-The 3d $\cN=8$ supersymmetric Yang--Mills theory is obtained by a dimensional reduction of the 4d $\mc N=4$ supersymmetric Yang--Mills theory.
-Therefore, from Theorem \ref{thm:4d4holomorphictwist} we obtain the following statement.
+The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.
+Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.
 
 \begin{theorem}  \label{3d_8_minimal_twist_thm}
-The minimal twist of the 3d $\cN=8$ super Yang--Mills theory on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
+The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory with space of fields $T^*[-1]\mr{Map}(\CC_{\rm Dol} \times \RR_{\mr{dR}}, \fg/\fg)$.
 Moreover, the equivalence is $\U(1)$-equivariant.
 \end{theorem}
+
+\begin{proof}
+By Proposition \ref{thm:4d4holomorphictwist} and Proposition \ref{prop:BFdolbeaultreduction} the dimensional reduction of the minimal twist of 4d $\cN=4$ super Yang-Mills along $\CC^2 \to \CC \times \RR$ is equivalent to the desired generalized BF theory.
+\end{proof}
 
@@
 
-\subsubsection{Topological Twists}
-
-Consider the dimensional reduction of the family $Q_t$ of rank $(2, 2)$ square-zero supercharges in the 4d $\cN=4$ supersymmetry algebra from Section \ref{sect:4dqgltwist}.
-Since this is a family of topological supercharges in 4 dimensions, it dimensionally reduces to a family of topological supercharges in 3 dimensions.
-
-\begin{theorem}
-The twist of the 3d $\cN=8$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $T^*[-1]\map(\RR^3_{\mathrm{dR}}, B\fg_{\Hod})$.
-Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
-\label{thm:3d8Hodgetwist}
-\end{theorem}
-\begin{proof}
-The claim follows by dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) from the corresponding statement in 4 dimensions (Theorem \ref{thm:4d422Hodgetwist}) which calculates the twist of the 4d $\cN=4$ super Yang--Mills theory with respect to that family to be $\map(\RR^4_{\mathrm{dR}}, B\fg_{\Hod})$.
-\end{proof}
-
-As we see from Theorem \ref{thm:3d8Hodgetwist}, at $t\neq 0$ the twist is perturbatively trivial while at $t=0$ it is not.
-By Lemma \ref{lm:3dN8twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the $A$-twist and the case $t=0$ (the special orbit) must be the $B$-twist.
-
-\begin{cor}
-The topological $A$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
-\label{cor:3dN8Atwist}
-\end{cor}
-
-\begin{cor}
-The topological $B$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$.
-Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
-\label{cor:3dN8Btwist}
-\end{cor}
+\subsubsection{Topological $A$-Twist}
+\label{sect:3d8A_Twist}
+From Theorem \ref{3d_4_A_twist_thm}, using the same argument, we obtain the following statement.
+
+\begin{theorem} \label{3d_8_A_twist_thm}
+The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
+Moreover, this equivalence is $\U(1)$-equivariant.
+\end{theorem}
+\brian{Need to explain what happened to $\Sect$}
+
+\begin{corollary}
+The topological $A$-twist of 3d $\cN=8$ super Yang-Mills is perturbatively trivial.
+\end{corollary}
+
+\subsubsection{Topological $B$-Twist}
+\label{sect:3d8B_Twist}
+From Theorem \ref{3d_4_B_twist_thm} we obtain the following statement.
+
+\begin{theorem} \label{3d_8_B_twist_thm}
+The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$.
+%Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
+\end{theorem}
+\brian{Need to explain what happened to $\Sect$}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
-
-We turn to $\cN=(0,2)$ supersymmetric Yang-Mills theory.
-Here, $W_+ = 0$ and $W_-$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
-The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$. 
-The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_-$ by the defining representation.
-
-The untwisted fields are given by:
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
+
+We turn to $\cN=(2,0)$ supersymmetric Yang-Mills theory.
+In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
+The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
+The $R$-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.
+
+The fields of the untwisted theory are:
 \begin{itemize}
 \item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
 \item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
+\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_- \otimes R)$.
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
 \end{itemize}
-The field $\lambda$ transforms in the defining representation of $G_R = \spin(2; \CC)$.
-The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively under $G_R \cong \CC^\times$.
+The field $\lambda$ transforms in the defining representation of $G_R = \SO(2;\CC)$.
+The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively.
 
@@
 \begin{itemize}
-\item Elements $Q \in S_- \otimes W_-$ of rank $1$. 
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
 Such supercharges are automatically square-zero and are holomorphic.
+We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
 There is a compatible twisting homomorphism
 \[
-\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
 \]
@@
 \]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_- = \det(L)^{1/2} \oplus \det^{-1/2}$.
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det(L)^{-1/2}$.
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang--Mills Theory}
-
-We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
-The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
-Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.
-
-The field content is:
-\begin{itemize}
-\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-\end{itemize}
-
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
-
-\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
-
-\begin{theorem}\label{2d(0,4)}
-The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-\end{theorem}
-
-\begin{proof}
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
-Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
-The claim now follows from Theorem \ref{2d(0,2)}. 
-\end{proof}
-
-\begin{remark}
-The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-\end{remark}
+\subsection{\texorpdfstring{$\cN=(4,0)$}{N=(4,0)} Super Yang--Mills Theory}
+
+Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
+In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
+The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
+The $R$-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
+As a $G_R$-representation, $W_+ = \Tilde{W} \oplus \Tilde{W}$ where $\Tilde{W}$ is the defining representation of $\SL(2;\CC)$ and where $\GL(1;\CC)$ acts by weight $(1,-1)$ with respect to this decomposition.
+
+%The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$.
+%Let $W = {\rm span}_{\CC} \{u_1,u_2\}$. 
+\begin{itemize}
+\item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
+\item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
+\item matter bosons $(\phi, \Bar{\phi}) \in C^\infty(\RR^2 ; (\Tilde{W} \oplus \Tilde{W}) \otimes U)$;
+\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
+%\item \brian{matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$}
+\item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
+\end{itemize}
+
+Under $\GL(1; \CC) \subset G_R$, the pairs of fields $(\lambda_-, \lambda_+)$ and $(\psi_-, \psi_+)$ have weights $(-1,+1)$ 
+The fields $\phi, \Bar{\phi}$ have weight zero.
+
+The theory admits a unique twist:
+\begin{itemize}
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
+Such supercharges are automatically square-zero and holomorphic.
+There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha : \U(1) \to G_R$. 
+%We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(0,2)}.
+%We take $\alpha : \U(1) \hookrightarrow \spin(2;\CC) \to \spin(4;\CC)$ to factor through the twisting data of Section \ref{sect:2d(0,2)}.
+%There is a compatible twisting homomorphism
+%\[
+%\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
+%\]
+%which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
+\end{itemize}
+
+\subsubsection{Minimal twist}
+
+Choose a complex structure $L \subset V_\RR$. 
+Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
+\]
+We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $W_+ = (\det(L)^{1/2} \oplus \det(L)^{-1/2})^{\oplus 2}$
+so that
+\[
+S_+ \otimes W_+ = \CC Q \oplus \CC \oplus L^{\oplus 2} .
+\]
+
+The twisting data homomorphism is the natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.
+
+Further, fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
+\item gauge fermions $\lambda^+ \in \Omega^0(\CC ; \fg)[-1]$, $\lambda^+_{1,0} \in \Omega^{1,0}(\CC ; \fg) [-1]$,  $\lambda^- \in \Omega^0(\CC ; \fg)[1]$, $\lambda^-_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
+\item matter bosons $\gamma \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\nu \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$, $\Bar{\phi} \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\Bar{\nu} \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$;
+\item matter fermions $\psi^- \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[1]$, $\psi^+ \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[-1]$;
+\item a ghost field $c \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
+
+%The field content is:
+%\begin{itemize}
+%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+%\end{itemize}
+
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+
+\begin{theorem} \label{thm: 2d(2,0)}
+The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+This equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+%\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
+%
+%\begin{theorem}\label{2d(0,4)}
+%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+%\end{theorem}
+%
+%\begin{proof}
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+%Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
+%The claim now follows from Theorem \ref{2d(0,2)}. 
+%\end{proof}
+%
+%\begin{remark}
+%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+%\end{remark}
 

### 2020-02-21 paper.tex

--- 2020-02-21 paper.tex
@@
 The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
-The $R$-symmetry group is $G_R = \spin(2;\CC)$ which acts on $W_+$ by the defining representation.
+The $R$-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.
 
@@
 \end{itemize}
-The field $\lambda$ transforms in the defining representation of $G_R = \spin(2; \CC)$.
-The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively under $G_R \cong \CC^\times$.
+The field $\lambda$ transforms in the defining representation of $G_R = \SO(2;\CC)$.
+The fields $\psi, \Bar{\psi}$ have weights $-1,+1$ respectively.
 
@@
 Such supercharges are automatically square-zero and are holomorphic.
+We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
 There is a compatible twisting homomorphism
 \[
-\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
 \]
@@
 \]
-Note that under the twisting homomorphism $\phi = \det^{1/2}$ we have $W_+ = \det(L)^{1/2} \oplus \det^{-1/2}$.
+
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det(L)^{-1/2}$.
 
@@
 
-\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(4,0)$}{N=(4,0)} Super Yang--Mills Theory}
 
@@
 The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The $R$-symmetry group is $\Spin(4;\CC)$, which acts on $W_+$ as the defining representation.
+The $R$-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
+As a $G_R$-representation, $W_+ = \Tilde{W} \oplus \Tilde{W}$ where $\Tilde{W}$ is the defining representation of $\SL(2;\CC)$ and where $\GL(1;\CC)$ acts by weight $(1,-1)$ with respect to this decomposition.
 
@@
 \item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$  
+\item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
+\item matter bosons $(\phi, \Bar{\phi}) \in C^\infty(\RR^2 ; (\Tilde{W} \oplus \Tilde{W}) \otimes U)$;
+\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
+%\item \brian{matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$}
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 
-The fields $\lambda, \psi$ transform in the defining representation of $G_R = \spin(4;\CC)$.
+Under $\GL(1; \CC) \subset G_R$, the pairs of fields $(\lambda_-, \lambda_+)$ and $(\psi_-, \psi_+)$ have weights $(-1,+1)$ 
+The fields $\phi, \Bar{\phi}$ have weight zero.
 
@@
 \item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
-Such supercharges are automatically square-zero, holomorphic, and lie in a $(2,0)$ supersymmetry subalgebra.
-There is a compatible twisting homomorphism
-\[
-\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
-\]
-which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
-\end{itemize}
-
-\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
-
-\begin{theorem}\label{2d(0,4)}
-The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$, where $\fg$ acts by the adjoint action, plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-\end{theorem}
-
-\begin{proof}
-The supercharge $Q$ lies in an $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
-On the odd part of the supersymmetry algebra, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
-Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
-The claim now follows from Theorem \ref{thm:2d(2,0)}. 
-\end{proof}
-
-\begin{remark}
-The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-\end{remark}
+Such supercharges are automatically square-zero and holomorphic.
+There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha : \U(1) \to G_R$. 
+%We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(0,2)}.
+%We take $\alpha : \U(1) \hookrightarrow \spin(2;\CC) \to \spin(4;\CC)$ to factor through the twisting data of Section \ref{sect:2d(0,2)}.
+%There is a compatible twisting homomorphism
+%\[
+%\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
+%\]
+%which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
+\end{itemize}
+
+\subsubsection{Minimal twist}
+
+Choose a complex structure $L \subset V_\RR$. 
+Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
+\]
+We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $W_+ = (\det(L)^{1/2} \oplus \det(L)^{-1/2})^{\oplus 2}$
+so that
+\[
+S_+ \otimes W_+ = \CC Q \oplus \CC \oplus L^{\oplus 2} .
+\]
+
+The twisting data homomorphism is the natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.
+
+Further, fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
+\item gauge fermions $\lambda^+ \in \Omega^0(\CC ; \fg)[-1]$, $\lambda^+_{1,0} \in \Omega^{1,0}(\CC ; \fg) [-1]$,  $\lambda^- \in \Omega^0(\CC ; \fg)[1]$, $\lambda^-_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
+\item matter bosons $\gamma \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\nu \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$, $\Bar{\phi} \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\Bar{\nu} \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$;
+\item matter fermions $\psi^- \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[1]$, $\psi^+ \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[-1]$;
+\item a ghost field $c \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
+
+%The field content is:
+%\begin{itemize}
+%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+%\end{itemize}
+
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+
+\begin{theorem} \label{thm: 2d(2,0)}
+The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+This equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+%\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
+%
+%\begin{theorem}\label{2d(0,4)}
+%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+%\end{theorem}
+%
+%\begin{proof}
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+%Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
+%The claim now follows from Theorem \ref{2d(0,2)}. 
+%\end{proof}
+%
+%\begin{remark}
+%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+%\end{remark}
 

### 2020-02-21 paper.tex
2d (4,0) done

@@
 \begin{align*}
-S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} , \dbar_{A_{0,1}} \lambda_{0}) \bigg)    \\
-S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi}) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} , \partial_{A_{1,0}} \psi_{0})  + \\
-&\qquad + ([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \\
+S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0})  \bigg)    \\
+S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi}) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \\
 S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} A_0 , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) + ([\lambda_{1,0}, A_0], \lambda_{1,0}^*) +  [\lambda_{0}, A_0] \lambda_{0}^*\\
-&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \gamma_0^* + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \gamma_{0,1}^* + [\psi_0, A_0] \psi_{0}^*\bigg) \\
+&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \gamma_0^* + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0] \gamma_{0,1}^* + [\psi_0, A_0] \psi_{0}^*\bigg) \\
 S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda_{1,0}, A_{1,0}^*) \bigg) \\
-S^{(1)}_{\mr{matter}} &=  \int \dvol \bigg( (\psi_{0}^*, \Bar{\phi}) + \frac 12(\dbar \gamma_0, \gamma_{0,1}^*) \bigg)\\
+S^{(1)}_{\mr{matter}} &=  \int \dvol \bigg( (\psi_{0}, \Bar{\phi}^*) + \frac 12(\dbar_{A_{0,1}} \gamma_0, \gamma_{0,1}^*) \bigg)\\
 S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda_0^*)^2 \bigg) .
@@
 \begin{proof}
-The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
+%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
-We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_0^*)$.  
+We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
 Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
@@
 \begin{align*}
-& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+  [\gamma_0, A_0] \gamma_0^*  \bigg).
+& \int \bigg(\dbar_{A_{0,1}} A_{0} \wedge A_{0,1}^* + (\dbar_{A_{0,1}} \gamma_{0} \wedge \gamma_{0,1}^*) \bigg) + \dvol \bigg( \frac{1}{2}[A_0, A_0]A_0^*+ [\gamma_0, A_0] \gamma_0^* + ([\gamma_{0,1}, A_0] , \gamma_{0,1}^*)  \bigg).
 \end{align*}
@@
 \item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
-\item matter bosons $(\phi, \Bar{\phi}) \in C^\infty(\RR^2 ; (\Tilde{W} \oplus \Tilde{W}) \otimes U)$;
+\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$;
 \item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
@@
 Under $\GL(1; \CC) \subset G_R$, the pairs of fields $(\lambda_-, \lambda_+)$ and $(\psi_-, \psi_+)$ have weights $(-1,+1)$ 
-The fields $\phi, \Bar{\phi}$ have weight zero.
+The field $\phi$ has weight zero.
 
@@
 \]
-We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $W_+ = (\det(L)^{1/2} \oplus \det(L)^{-1/2})^{\oplus 2}$
+We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $\Tilde{W} = \det(L)^{1/2} \oplus \det(L)^{-1/2}$
 so that
@@
 \item gauge fermions $\lambda^+ \in \Omega^0(\CC ; \fg)[-1]$, $\lambda^+_{1,0} \in \Omega^{1,0}(\CC ; \fg) [-1]$,  $\lambda^- \in \Omega^0(\CC ; \fg)[1]$, $\lambda^-_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$;
-\item matter bosons $\gamma \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\nu \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$, $\Bar{\phi} \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\Bar{\nu} \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$;
-\item matter fermions $\psi^- \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[1]$, $\psi^+ \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[-1]$;
+\item matter bosons $\gamma \in \Omega^0(\CC ; K_{\CC}^{1/2} \otimes U)$, $\nu \in \Omega^0(\CC ; K_{\CC}^{-1/2} \otimes U)$;
+\item matter fermions $\psi_- \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[1]$, $\psi_+ \in \Omega^{0}(\CC ; K_\CC^{-1/2} \otimes U)[-1]$;
 \item a ghost field $c \in \Omega^0(\CC ; \fg)[1]$.
 \end{itemize}
+
+The action functional decomposes as follows:
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 \bigg) + \lambda^+_0  \dbar_{A_{0,1}} \lambda^-_{1,0} + \lambda^-_{0} , \dbar_{A_{0,1}} \lambda^+_{1,0}    \\
+S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}} \nu , \ol \dd_{A_{0,1}} \gamma) + (\dd_{A_{1,0}}\gamma, \ol \dd_{A_{0,1}} \nu) + (\psi_- , \partial_{A_{1,0}} \gamma) + (\psi_+ , \partial_{A_{1,0}} \nu)  + \\
+%&\qquad + ([\lambda^+_{1,0}, ],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \/\
+& \qquad + \brian{Figure out Yukawa's} \\
+S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} c , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0,1}^*) \\ & \qquad + ([\lambda^+_{1,0}, c], \lambda_{1,0}^{+*}) + + ([\lambda^-_{1,0}, c], \lambda_{1,0}^{-*}) +  [\lambda^+_{0}, c] \lambda_{0}^{+*}+ [\lambda^-_{0}, c] \lambda_{0}^{-*}\\
+&\qquad + \frac{1}{2}[c, c]c^* + [\gamma, c] \gamma^* + [\nu, c] \nu^* + [\psi_-^*, c] \psi_-^* + [\psi_+, c] \psi_+^*\bigg) \\
+S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda^-_{1,0}, A_{1,0}^*) \bigg) \\
+S^{(1)}_{\mr{matter}} &=  \int \dvol \bigg( (\psi_{-}, \nu^*) + \frac 12(\dbar_{A_{0,1}} \gamma, \psi_+^*) \bigg)\\
+S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda^{-*})^2 \bigg) .
+\end{align*}
 
@@
 
-\begin{theorem} \label{thm: 2d(2,0)}
+\begin{theorem} \label{thm: 2d(4,0)}
 The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
@@
 \end{theorem}
+
+\begin{proof}
+First, we integrate out the field $\lambda^-$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the terms $\int  (\lambda^-_{1,0} , A_{1,0}^*)$ and  $\int (\psi_-, \nu^*)$.  
+Thus, the two pairs $(\lambda^-_{1,0}, A_{1,0})$ and $(\nu, \psi_-)$ form BRST doublets, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+& \int \bigg(\dbar_{A_{0,1}} c \wedge A_{0,1}^* + \lambda^+ \dbar_{A_{0,1}} \lambda^-_{1,0} + \dbar_{A_{0,1}} \gamma \wedge \psi_+^* \bigg) + \dvol \bigg( \frac{1}{2}[c, c]c^*+ ([\lambda_{1,0}^-, c] , \lambda_{1,0}^{-*}) + [\lambda^+, c] \lambda^{+*} + [\gamma, c] \gamma^* + [\psi_+, c] \psi_+^* \bigg).
+\end{align*}
+This is the action functional of the required theory.
+\end{proof}
 
@@
 
-We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
 

### 2020-02-21 paper.tex
Typo
fixed broken references

@@
 \begin{align*}
-S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^* + (F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*)\right) 
+S^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^* + (F_{0, 2}, B^*)  + (\ol\dd_{A_{0, 1}} a, C^*)\right) \\
 &+ \int\dvol\left((t\dd_{A_{1, 0}} \Tilde{a}, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*) + \frac{1}{2}[a, \wt a](\chi^*+t\wt\chi^*)\right) + t\Omega^{-1} F_{2, 0}\wedge B^* \\
@@
 
-\begin{cor}
+\begin{corollary}
 The topological $A$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
 \label{cor:3dN8Atwist}
-\end{cor}
-
-\begin{cor}
+\end{corollary}
+
+\begin{corollary}
 The topological $B$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$.
@@
 \label{cor:3dN8Btwist}
-\end{cor}
+\end{corollary}
 
@@
 The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+Combining Theorem \ref{thm:3d8Hodgetwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
 
@@
 The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+Combining Theorem \ref{cor:3dN8Btwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
 
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal twist} \label{sect:2d04minimaltwist}
 
@@
 
-\begin{theorem} \label{thm: 2d(4,0)}
+\begin{theorem} \label{thm:2d(4,0)}
 The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
@@
 
-\subsection{Pure \texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang--Mills Theory}
 
@@
 \begin{proof}
-The proof is similar to the proof of Theorem \ref{2d(0,4)}.
+The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
 The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
@@
 We may identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -\rangle)} \omega).\]
+\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
 This gives rise to an action map

### 2020-02-21 paper.tex
merge abort

--- 2020-02-21 paper.tex
@@
  && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
- \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
- \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
- \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
+ \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
+ \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
@@
 
-\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(4,0)}
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2d02minimaltwist}
+\subsubsection{Minimal Twist} \label{sect:2d20minimaltwist}
 
@@
 
-\subsubsection{Minimal twist}
+\subsubsection{Minimal twist} \label{sect:2d40minimaltwist}
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2d0Nminimaltwist}
+\subsubsection{Minimal Twist} \label{sect:2dN0minimaltwist}
 
@@
 Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
 Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 

### 2020-02-21 paper.tex

--- 2020-02-21 paper.tex
@@
 
-\subsubsection{Minimal twist} \label{sect:2d04minimaltwist}
+\subsubsection{Minimal twist} \label{sect:2d40minimaltwist}
 

### 2020-02-21 paper.tex
2d done

@@
 
-\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(4,0)}
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(2,0)}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(4,0)$}{N=(4,0)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(4,0)$}{N=(4,0)} Super Yang--Mills Theory} \label{sect:2d(4,0)}
 
@@
 %&\qquad + ([\lambda^+_{1,0}, ],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \/\
-& \qquad + \brian{Figure out Yukawa's} \\
+& \qquad + ([\lambda^+, \gamma], \psi_-) + ([\lambda_{1,0}^+, \nu], \psi_-) + ([\lambda^-, \gamma], \psi_+) + ([\lambda^-_{1,0}, \nu], \psi_-) \bigg) \\
 S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} c , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0,1}^*) \\ & \qquad + ([\lambda^+_{1,0}, c], \lambda_{1,0}^{+*}) + + ([\lambda^-_{1,0}, c], \lambda_{1,0}^{-*}) +  [\lambda^+_{0}, c] \lambda_{0}^{+*}+ [\lambda^-_{0}, c] \lambda_{0}^{-*}\\
@@
 
-\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang--Mills Theory}
-
-We consider pure $\cN=(0,\cN_-)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_- \geq 2$.
-The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_-$ is the $\cN_-$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.
+\subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N_+,0)} Super Yang--Mills Theory}
+
+We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
+The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.
 
@@
 \item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-\end{itemize}
-Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$ such that the pairing restricted to $ {\rm span}_{\CC} \{u, v\}$ is $\<u,v\> = 1$.
-
-The field content is given as follows.
-\begin{itemize}
- \item Bosons $(A_{0,1}, A_{1,0}) \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)$.
- \item Fermions $(\lambda_{0} u, \lambda_{1,0} v, \chi) \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_- \otimes W_-' \otimes \fg)$.
- \item A ghost field $A_{0} \in \Omega^0(\CC ; \fg)[1]$.
+\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
+\end{itemize}
+
+The theory admits a unique twist by the following class of supercharge.
+\begin{itemize}
+\item Elements $Q \in S_+ \otimes W_+$ of rank $1$. 
+Such supercharges are automatically square-zero, holomorphic, and lie in a $\cN = (2,0)$ subalgebra.
+We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(2,0)}.
+%We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
+%There is a compatible twisting homomorphism
+%\[
+%\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+%\]
 \end{itemize}
@@
 
-\begin{theorem}[See also \cite{SWchar}]
-The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
-\end{theorem}
-
-\begin{proof}
-The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
-Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
-Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
-\end{proof}
+Choose a complex structure $L \subset V_\RR$. 
+Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
+\]
+
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det(L)^{-1/2} \oplus \CC^{\cN_+ - 2}$.
+
+The fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
+\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$, $\Tilde{\lambda} \in \Omega^{0} (\CC ; K^{1/2}_\CC \otimes \fg)$;
+\item a ghost field $A_0 \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
+
+The action functional decomposes as follows:
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) + \frac 12 (\Tilde{\lambda}, \dbar_{A_{0,1}} \Tilde{\lambda}) \bigg)    \\
+S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} A_0 , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) + ([\lambda_{1,0}, A_0], \lambda_{1,0}^*) +  [\lambda_{0}, A_0] \lambda_{0}^*\\
+&\qquad + [\Tilde{\lambda}, A_0] \Tilde{\lambda}^* + \frac{1}{2}[A_0, A_0]A_0^* \bigg) \\
+S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda_{1,0}, A_{1,0}^*) \bigg) \\
+S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda_0^*)^2 \bigg) .
+\end{align*}
+
+\begin{theorem} \label{thm:2d(N,0)}
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+This equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
+First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
+Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+& \int \dvol \bigg((\dbar_{A_{0,1}} A_{0}, A_{0,1}^*) + (\dbar_{A_{0,1}} \Tilde{\lambda} ,  \Tilde{\lambda}) + \frac{1}{2}[A_0, A_0]A_0^*+ [ \Tilde{\lambda} , A_0]  \Tilde{\lambda}^* \bigg).
+\end{align*}
+This is the action functional of the required theory.
+\end{proof}
+
+%\begin{proof}
+%The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
+%Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
+%Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
+%\end{proof}
 

### 2020-02-21 paper.tex
2d (2, 2) and (4, 4)

--- 2020-02-21 paper.tex
@@
  \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
+ && {$T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$} & \\ \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
@@
  & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
- && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
+ && {$\mr{Map}(\RR^2_{\mathrm{dR}}, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
  \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
+ && {$T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$} & \\  \cline{2-4}
   & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
- && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
+ && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
  && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
- \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
- \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Sect}(\CC, (U \otimes K_\CC^{1/2}) \ham \gg)$} & \\  \hline
- \multirow{2}*{$(2,0)$} & \multirow{2}*{\hyperref[sect:2d20minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
+ \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
+ \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
+ && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
+ \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
  && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
@@
 Let $X', Y, M, V_\RR, V$ be as before. 
-Fix an $L_\infty$ algebra equipped with a non-degenerate pairing as in Definition \ref{Hodge_family_def} and consider the generalized Hodge theory
+Fix an $L_\infty$ algebra $\fg$ equipped with a non-degenerate pairing as in Definition \ref{Hodge_family_def} and consider the generalized Hodge theory
 \[\map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]
@@
 
-By essentially the same argument as in the proof of Proposition \ref{CS_diml_red_prop}, we obtain the reduction of generalized BF theory.
+We have the following analogs of Propositions \ref{CS_to_BF_diml_red_prop} and \ref{CS_diml_red_prop} for the generalized BF theory.
 
 \begin{prop}
-Let $X', Y, M, V_\RR, V$ be as before. 
-Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
+Let $X, Y, M', \fg$ be as in Proposition \ref{CS_to_BF_diml_red_prop}. The dimensional reduction of the generalized BF theory
+\[T^*[-1]\map(X\times Y_{\mr{Dol}}\times (M'\times \RR)_{\mr{dR}}, B\fg)\]
+along the projection $p_{\rm dR}$ is equivalent to the generalized BF theory
+\[
+T^*[-1] \map(X\times Y_{\mr{Dol}}\times M'_{\mr{dR}}, \fg/\fg).
+\]
+\label{prop:BFdeRhamreduction}
+\end{prop}
+
+\begin{prop}
+Let $X', Y, M, V_\RR, V$ be as in \ref{CS_diml_red_prop}. Fix an $L_\infty$ algebra $\fg$ and consider the generalized BF theory
 \[T^*[-1] \map((X'\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
@@
 The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.
-We refer to these as the $A$-twist and the $B$-twist, distinguished by whether they admit a $\ZZ$-grading:
+We refer to these as the A twist and the B twist, distinguished by whether they admit a $\ZZ$-grading:
 \begin{enumerate}
 \item
-An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
+An A-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
 \item
-A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
+A B-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
 This twist is only $\ZZ/2\ZZ$-graded.
@@
 \begin{lemma} \label{3d_4_orbits_lemma}
-A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.
-Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
+A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an A-twisting supercharge in 3d $\mc N=4$.
+Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a B-twisting supercharge in 3d $\mc N=4$.
 \end{lemma}
@@
 This supercharge admits a compatible homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor.
-This is the $A$-twist in our classification above.
+This is the A-twist in our classification above.
 
 A rank $(1,1)$ supercharge induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.
-This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.
+This subspace has the opposite orientation, so corresponds to the B-twist in our classification above.
 \end{proof}
@@
 
-\subsubsection{Topological $A$-Twist}
+\subsubsection{Topological A-Twist}
 \label{sect:3d_4_A_twist}
@@
 Under the projection $\Re\colon N\rightarrow N_\RR$ the family $Q_t$ of 4-dimensional square-zero supercharges given by \eqref{eq:4dHodgefamily} dimensionally reduces to a family of 3-dimensional square-zero supercharges which at $t\neq 0$ are topological at and $t=0$ have 2 invariant directions.
-Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological $A$ twist.
+Since they admit a compatible $\ZZ$-grading, at $t=0$ we obtain the holomorphic twist and at $t\neq 0$ we obtain the topological A-twist.
 Therefore, from Theorem \ref{thm:4dDonaldsontwist} we obtain the following statement.
@@
 \begin{corollary}
-The topological $A$ twist of the 3d $\cN=4$ super Yang--Mills theory is perturbatively trivial.
+The topological A-twist of the 3d $\cN=4$ super Yang--Mills theory is perturbatively trivial.
 \end{corollary}
 
-\subsubsection{Topological $B$-Twist}
+\subsubsection{Topological B-Twist}
 \label{sect:3d_4_B_twist}
@@
 $V$ carries a Hermitian structure and a half-density, so by the results of Section \ref{sect:6dholomorphictwist} we obtain a square-zero supercharge $Q$.
-Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological $B$ supercharge in 3 dimensions.
+Under the projection $\Re\colon V\rightarrow V_\RR$ the supercharge $Q$ dimensionally reduces to the topological B-supercharge in 3 dimensions.
 Therefore, from Theorem \ref{thm:6dCSreduction} we obtain the following statement.
@@
  \begin{enumerate}
- \item $A$-twist (the generic rank 2 orbit).
- \item $B$-twist (the special rank 2 orbit).
+ \item A-twist (the generic rank 2 orbit).
+ \item B-twist (the special rank 2 orbit).
  \end{enumerate}
@@
 As we see from Theorem \ref{thm:3d8Hodgetwist}, at $t\neq 0$ the twist is perturbatively trivial while at $t=0$ it is not.
-By Lemma \ref{lm:3dN8twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the $A$-twist and the case $t=0$ (the special orbit) must be the $B$-twist.
+By Lemma \ref{lm:3dN8twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the A-twist and the case $t=0$ (the special orbit) must be the B-twist.
 
 \begin{corollary}
-The topological $A$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
+The topological A-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively trivial.
 \label{cor:3dN8Atwist}
@@
 \begin{corollary}
-The topological $B$-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$.
+The topological B-twist of the 3d $\cN=8$ super Yang--Mills theory is perturbatively equivalent to $T^*[-1]\map(\RR^3_{\mathrm{dR}}, \fg/\fg)$.
 Moreover, the equivalence is $\Spin(3, \RR)$-equivariant.
@@
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
-There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
-
-There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.
-First we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+There is a pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
+
+There are two classes of twisted supersymmetric gauge theory that we will consider in two dimensions.
+First, we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+Namely, we have the 2d $\cN=(1, 1)$, 2d $\cN=(2, 2)$, 2d $\cN=(4, 4)$ and 2d $\cN=(8, 8)$ super Yang--Mills theories.
+The 2d $\cN=(1, 1)$ supersymmetry algebra does not admit square-zero supercharges, so we will not consider it.
 We additionally have gauge theories with chiral, i.e.
-$(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sect:2dchiral}.
-We'll address twists for these two classes of theory in turn.
+$(\cN, 0)$ supersymmetry, which we have constructed in Sections \ref{sect:2dchiral} and \ref{sect:SYM}.
+We will address twists for these two classes of theories in turn.
 
 \subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang--Mills Theory} \label{sect:2d(2,2)}
-First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.
-The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (-a, -b)$.
+First, consider the 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory.
+The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\Spin(2; \CC)$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (-a, -b)$.
 
@@
 \begin{itemize}
- \item gauge bosons $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Bar{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
+ \item gauge bosons $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(a, \Tilde{a}) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
  \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
- \item gauge fermions $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
- \item matter fermions $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
+ \item gauge fermions $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; \Pi(S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
+ \item matter fermions $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; \Pi(S_+ \oplus S_-) \otimes R \oplus \Pi(S_+ \oplus S_-) \otimes R^*)$.
  \item a ghost field $c \in \Omega^0(\RR^2; \gg)[1]$.
@@
 \begin{enumerate}
-\item The $A$-supercharges are compatible with the twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
-\item The $B$-supercharges are compatible with the twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  
+\item The A-twist is compatible with the twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
+\item The B-twist is compatible with the twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  
 \end{enumerate}
-Moreover, the $A$-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the $B$-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
+Moreover, the A-supercharges admit a compatible homomorphism $\alpha_A = \phi_B\colon \U(1)\rightarrow G_R$, and the B-supercharges admit a compatible homomorphism $\alpha_B = \phi_A\colon \U(1)\rightarrow G_R$.
 \end{itemize}
@@
 The calculation of the twists here is similar to what we saw in 4d $\mc N=2$ supersymmetry.  
-The minimal twist and the $B$-twist arise by dimensional reduction from twists of 3d $\cN=2$ supersymmetric Yang-Mills theory.
-On the contrary, the $A$-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
-
-\subsubsection{Minimal Twist} \label{sect:2d22minimaltwist}
-
-First, we record the minimal twist of 2d $\cN=(2,2)$ supersymmetric Yang--Mills theory.
+The holomorphic twist and the B-twist arise by a dimensional reduction from twists of the 3d $\cN=2$ supersymmetric Yang-Mills theory.
+On the contrary, the A-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
+
+\subsubsection{Holomorphic Twist} \label{sect:2d22minimaltwist}
+
+First, we record the holomorphic twist of the 2d $\cN=(2,2)$ supersymmetric Yang--Mills theory. The holomorphic twist is $\ZZ$-graded using $\alpha = \phi_A$.
 
 \begin{theorem} \label{2d_minimal_twist_thm}
-The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory for the Lie algebra $\fg$ coupled to the $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$.
+The holomorphic twist of the 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
 \end{theorem}
-
-\begin{proof}
-The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_to_BF_diml_red_prop}) to Theorem \ref{3d_minimal_twist_thm} calculating the minimal twist of 3d $\mc N=2$ super Yang-Mills on $\CC \times \RR_{\mr{dR}}$.
-This equivalence is $\mr U(1)$-equivariant.
-It is also $\ZZ$-graded, using the twisting datum $\alpha = \phi_A$.
-\end{proof}
-
-\subsubsection{Topological A Twist} \label{sect:2d22Atwist}
+\begin{proof}
+The statement follows by applying dimensional reduction (Proposition \ref{prop:BFdeRhamreduction}) to Theorem \ref{3d_minimal_twist_thm} calculating the minimal twist of 3d $\cN=2$ super Yang--Mills on $\CC\times \RR_{\mathrm{dR}}$, where we dimensionally reduce along the projection $\RR\rightarrow \pt$.
+\end{proof}
+
+\subsubsection{Topological A-Twist} \label{sect:2d22Atwist}
 
 To deform the holomorphic twist to the topological A-twist, obtaining a Hodge deformation, we use similar techniques to those of Section \ref{sect:4d2Donaldson}.
-We first analyze how the supersymmetry action decomposes.
+We first analyze the supersymmetry action.
 Consider the 1-parameter family of supercharges
@@
 where $Q_0 = (1,i) \in S_+$ is a holomorphic supercharge, and $Q' = (1,i) \in S_-$.
-This family of supercharges are all compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
-They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.
+This family of supercharges is compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.
+They admit a compatible homomorphism $\alpha=\phi_B\colon \U(1)\rightarrow G_R$ with weights $(1,-1)$.
 Let us first decompose our fields according to the twisting homomorphism $\phi_A$:
@@
 \begin{prop}
-Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
+Suppose $Q_t$ is the rank $(1,1)$ supercharge of \eqref{eq:2dHodgefamily}.
 The $\U(1)$ decomposition of the functionals $S_{\rm gauge}^{(1)}, S^{(1)}_{\rm matter}, S^{(2)}_{\rm gauge}, S^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
@@
 \begin{theorem} \label{2d_2_A_twist_thm}
-The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
+The twist of the 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with the space of fields $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-equivariant.
 \end{theorem}
@@
 \begin{corollary}
-The topological $A$-twist of 2d $\cN=(2,2)$-supersymmetric Yang--Mills theory is perturbatively trivial.
+The topological A-twist of the 2d $\cN=(2,2)$-supersymmetric Yang--Mills theory is perturbatively trivial.
 \end{corollary}
 
-\subsubsection{Topological $B$-Twist} \label{sect:2d22Btwist}
-
-Finally, there is the $B$-twist of 2d $\cN=(2,2)$ supersymmetry.
-This twist arises from the twist of 3d $\cN=2$ via dimensional reduction in a non-invariant direction.  
+\subsubsection{Topological B-Twist} \label{sect:2d22Btwist}
+
+Finally, there is the B-twist of 2d $\cN=(2,2)$ supersymmetry.
+This twist arises from the twist of 3d $\cN=2$ via dimensional reduction along the holomorphic direction.
 Indeed, let $W_3$ be the two-dimensional auxiliary space in the 3d $\mc N=2$ supertranslation algebra.  
@@
 \begin{theorem} \label{2d_2_B_twist_thm}
-The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\begin{proof}
-The theory is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=2$ supersymmetric Yang--Mills theory in a non-invariant direction.  
-Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} we obtain the desired result.
+The topological B-twist of the 2d $\mc N=(2,2)$ super Yang--Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the topological BF theory with the space of fields $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, R/\gg)$.
+This equivalence is $\SO(2)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+The theory is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=2$ supersymmetric Yang--Mills theory along the holomorphic direction.
+Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{prop:BFholomorphicreduction} we obtain the desired result.
 \end{proof}
@@
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
-The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra.
+The generic orbit consists of A-supercharges and the special orbit consists of B-supercharges.
+\label{prop:2d44twoorbits}
 \end{prop}
@@
 There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  
-These are the $B$- and $A$-supercharges respectively.
+These are the B- and A-supercharges respectively.
 \end{proof}
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 
-\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
-The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
-By Theorem \ref{3d_4_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+\subsubsection{Topological Twists}
+\label{sect:2d44Atwist}
+\label{sect:2d44Btwist}
+
+Let $V_\RR=\RR^2$ equipped with a Euclidean structure and $V=V_\RR\otimes_\RR\CC$ its complexification.
+By the results of Section \ref{sect:4d2Donaldson} we obtain a family $Q_t$ of square-zero supercharges in the 4-dimensional supersymmetry algebra.
+Dimensionally reducing this family along $\Re\colon V\rightarrow V_\RR$, we obtain a family of square-zero supercharges in the 2-dimensional supersymmetry algebra.
+It is easy to see that it is a family of topological supercharges.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in symplectic $\fg$-representation $U$ admits a one-parameter deformation to the A-twist.  
-This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.   This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsubsection{Topological B Twist} \label{sect:2d44Btwist}
-
-The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
-By Theorem \ref{3d_4_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
-
-\begin{theorem}
-The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
+The twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $\map(\RR^2_{\mathrm{dR}}, (U\ham \fg)_{\Hod})$.
+Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
+\label{thm:2d44Hodgetwist}
+\end{theorem}
+\begin{proof}
+The claim follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) from the corresponding statement in 4 dimensions (Theorem \ref{thm:4dDonaldsontwist}) which calculates the twist of the 4d $\cN=2$ super Yang--Mills theory with respect to that family to be $\Sect(\CC^2, ((U\otimes K^{1/2}_{\CC^2})\ham \fg)_{\Hod})$.
+\end{proof}
+
+As we see from Theorem \ref{thm:2d44Hodgetwist}, at $t\neq 0$ the twist is perturbatively trivial while at $t=0$ it is not.
+By Proposition \ref{prop:2d44twoorbits} there are only two orbits of topological supercharges, so the case $t\neq 0$ (the generic orbit) must be the A-twist and the case $t=0$ (the special orbit) must be the B-twist.
+
+\begin{corollary}
+The topological A-twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory is perturbatively trivial.
+\label{cor:2d44Atwist}
+\end{corollary}
+
+\begin{corollary}
+The topological B-twist of the 2d $\cN=(4, 4)$ super Yang--Mills theory is perturbatively equivalent to the theory $T^*[-1]\map(\RR^2_{\mathrm{dR}}, U\ham \fg)$.
+Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
+\label{cor:2d44Btwist}
+\end{corollary}
 
@@
 
-\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(4,0)}
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2d20minimaltwist}
+\subsubsection{Minimal Twist} \label{sect:2d02minimaltwist}
 
@@
 
-\subsubsection{Minimal twist} \label{sect:2d40minimaltwist}
+\subsubsection{Minimal twist} \label{sect:2d04minimaltwist}
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2dN0minimaltwist}
+\subsubsection{Minimal Twist} \label{sect:2d0Nminimaltwist}
 
@@
 Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
+Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
 Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 

### 2020-02-21 paper.tex

@@
 
-\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(0,2)}
+\subsection{\texorpdfstring{$\cN=(2,0)$}{N=(2,0)} Super Yang--Mills Theory} \label{sect:2d(2,0)}
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2d0Nminimaltwist}
-
-\begin{theorem}[See also \cite{SWchar}]
-The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action.
-\end{theorem}
-
-\begin{proof}
-The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
-The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
-On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-\[
-S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
-\]
-given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
-Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
-Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
-The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
-\end{proof}
+\subsubsection{Minimal Twist} \label{sect:2dN0minimaltwist}
+
+Choose a complex structure $L \subset V_\RR$. 
+Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\[
+S_+ = \det(L)^{1/2} \;\; , \;\; S_- = \det(L)^{-1/2} .
+\]
+
+Note that under the twisting homomorphism $\phi = \det^{1/2}$, we have $W_+ = \det(L)^{1/2} \oplus \det(L)^{-1/2} \oplus \CC^{\cN_+ - 2}$.
+
+The fields decompose under the twisting homomorphism as:
+\begin{itemize}
+\item gauge bosons $A_{1,0} \in \Omega^{1,0}(\CC ; \fg)$, $A_{0,1} \in \Omega^{0,1}(\CC ; \fg)$;
+\item gauge fermions $\lambda_0 \in \Omega^0(\CC ; \fg)[-1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg) [1]$, $\Tilde{\lambda} \in \Omega^{0} (\CC ; K^{1/2}_\CC \otimes \fg)$;
+\item a ghost field $A_0 \in \Omega^0(\CC ; \fg)[1]$.
+\end{itemize}
+
+The action functional decomposes as follows:
+\begin{align*}
+S_{\mr{gauge}} &= \int \dvol \bigg(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \frac 12 (\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) + \frac 12 (\Tilde{\lambda}, \dbar_{A_{0,1}} \Tilde{\lambda}) \bigg)    \\
+S_{\mr{anti}} &= \int \dvol \bigg( (\dd_{A_{1, 0}} A_0 , A_{1,0}^*) + (\ol\dd_{A_{0, 1}} A_0, A_{0,1}^*) + ([\lambda_{1,0}, A_0], \lambda_{1,0}^*) +  [\lambda_{0}, A_0] \lambda_{0}^*\\
+&\qquad + [\Tilde{\lambda}, A_0] \Tilde{\lambda}^* + \frac{1}{2}[A_0, A_0]A_0^* \bigg) \\
+S^{(1)}_{\mr{gauge}} &=  \int \dvol \bigg( - (\lambda_{1,0}, A_{1,0}^*) \bigg) \\
+S^{(2)}_{\mr{gauge}} &= \int \dvol \bigg( -\frac{1}{4} (\lambda_0^*)^2 \bigg) .
+\end{align*}
+
+\begin{theorem} \label{thm:2d(N,0)}
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+This equivalence is $\U(1)$-equivariant.
+\end{theorem}
+
+\begin{proof}
+%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
+First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
+Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
+which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+
+The twisted theory is therefore perturbatively equivalent to the theory with BV action 
+\begin{align*}
+& \int \dvol \bigg((\dbar_{A_{0,1}} A_{0}, A_{0,1}^*) + (\dbar_{A_{0,1}} \Tilde{\lambda} ,  \Tilde{\lambda}) + \frac{1}{2}[A_0, A_0]A_0^*+ [ \Tilde{\lambda} , A_0]  \Tilde{\lambda}^* \bigg).
+\end{align*}
+This is the action functional of the required theory.
+\end{proof}
+
+%\begin{proof}
+%The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
+%Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
+%Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
+%\end{proof}
 

### 2020-02-21 paper.tex
merge error

--- 2020-02-21 paper.tex
@@
  \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
+ && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
  \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
@@
 
-\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}
-
-Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
-As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.
-
-We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
-\[
-S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
-\]
-The representation $S_- \otimes W^*$ decomposes as
-\[
-S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
-\]
-where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
+\subsubsection{Rank \texorpdfstring{$(2,1)$}{(1,2)} Topological Twist}
+
+%Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
+%As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$. 
+%
+%We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+%Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
+%\[
+%S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
+%\]
+%The representation $S_- \otimes W^*$ decomposes as
+%\[
+%S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
+%\]
+%where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
 The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$.
@@
 Therefore, we may consider a family of square-zero supercharges
-\begin{equation}
-Q_t = Q_0 + tQ'
-\label{eq:4d412Hodgefamily}
-\end{equation}
-which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
-
-We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
-
-\begin{prop}
-Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
+%\begin{equation}
+%Q_t = Q_0 + tQ'
+%\label{eq:4d412Hodgefamily}
+%\end{equation}
+%which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
+%
+%We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
+%
+%\begin{prop}
+%Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
 The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
-\begin{align*}
-I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
-\end{align*}
-\end{prop}
+%\begin{align*}
+%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+%I^{(2)} (Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+%\end{align*}
+%\end{prop}
 
@@
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
-There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
+There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.
 
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.

### 2020-02-21 paper.tex

--- 2020-02-21 paper.tex
@@
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
-There is a pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
+There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.
 

### 2020-02-21 paper.tex
merge

--- 2020-02-21 paper.tex
@@
  \multirow{2}*{$(\mc N_+, 0)$} & \multirow{2}*{\hyperref[sect:2dN0minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_+ - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
+ && {$T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$} & \\  \hline
  \multirow{2}*{$(4,0)$} & \multirow{2}*{\hyperref[sect:2d40minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,1)$}{(1,2)} Topological Twist}
-
-%Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
-%As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$. 
-%
-%We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-%Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
-%\[
-%S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
-%\]
-%The representation $S_- \otimes W^*$ decomposes as
-%\[
-%S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
-%\]
-%where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
+\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}
+
+Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
+As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$.
+
+We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
+Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
+\[
+S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
+\]
+The representation $S_- \otimes W^*$ decomposes as
+\[
+S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
+\]
+where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
 The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$.
@@
 Therefore, we may consider a family of square-zero supercharges
-%\begin{equation}
-%Q_t = Q_0 + tQ'
-%\label{eq:4d412Hodgefamily}
-%\end{equation}
-%which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
-%
-%We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
-%
-%\begin{prop}
-%Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
+\begin{equation}
+Q_t = Q_0 + tQ'
+\label{eq:4d412Hodgefamily}
+\end{equation}
+which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
+
+We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
+
+\begin{prop}
+Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
 The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
-%\begin{align*}
-%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-%I^{(2)} (Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
-%\end{align*}
-%\end{prop}
+\begin{align*}
+I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+\end{align*}
+\end{prop}
 
@@
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
-There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.
+There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
 
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \begin{theorem} \label{thm:2d(4,0)}
-The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 %\begin{theorem}\label{2d(0,4)}
-%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
 %\end{theorem}
@@
 
-\subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N_+,0)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N+,0)} Super Yang--Mills Theory}
 
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic BF with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.

### 2020-02-21 paper.tex
2d (8, 8)

--- 2020-02-21 paper.tex
@@
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
-There is an independent pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality, where $\Spin(2;\CC)$ acts on $\CC_1, \CC_{-1}$ with weights $1, -1$ respectively.
+There is a pairing $\Gamma_\pm \colon S_\pm^{\otimes 2} \to V_2 \iso \CC_1 \oplus \CC_{-1}$ for each chirality.
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
-The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
+\subsubsection{Holomorphic Twist} \label{sect:2d44minimaltwist}
+The holomorphic twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
 By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
@@
 This equivalence is $\mr U(1)$-invariant.
+\label{thm:2d44holomorphictwist}
 \end{theorem}
@@
 \subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang--Mills Theory} \label{sect:2d(8,8)}
-Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
-This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
+Next we consider the $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
 No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
 
-The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.
-As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we saw in the $\mc N=(4,4)$ case.
+The R-symmetry group in the $\mc N=(8,8)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.
+The classification of square-zero supercharges is identical to the classification we saw in the $\mc N=(4,4)$ case.
 Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.
@@
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
-The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra.
+The generic orbit consists of A-supercharges and the special orbit consists of B-supercharges.
 \end{prop}
@@
 
-Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
-Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.
-In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.
-
-\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
-The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
+The 2d $\cN=(8, 8)$ super Yang--Mills theory may be considered as a 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in the symplectic $\fg$-representation $U=T^*\fg$.
+So, all the computations in this section follow from the corresponding computations in Section \ref{sect:2d(4,4)}.
+
+\subsubsection{Holomorphic Twist} \label{sect:2d88minimaltwist}
+
+From Theorem \ref{thm:2d44holomorphictwist} we obtain the following statement.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
-The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{thm:3d8Hodgetwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC, T[1] T^*(\fg/\fg))$.
+This equivalence is $\mr U(1)$-equivariant.
+\end{theorem}
+
+\subsubsection{Topological Twists}
+\label{sect:2d88Atwist}
+\label{sect:2d88Btwist}
+
+Consider the family of topological supercharges $Q_t$ from Section \ref{sect:2d44Atwist}. From Theorem \ref{thm:2d44Hodgetwist} we obtain the following statement.
 
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.
-This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
-
-\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
-The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
-Combining Theorem \ref{cor:3dN8Btwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
-
-\begin{theorem}
-The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.
-This equivalence is $\mr U(1)$-invariant.
-\end{theorem}
+The twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg)_{\Hod})$.
+Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
+\label{thm:2d88Hodgetwist}
+\end{theorem}
+
+\begin{corollary}
+The topological A-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively trivial.
+\label{cor:2d88Atwist}
+\end{corollary}
+
+\begin{corollary}
+The topological B-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively equivalent to the theory $T^*[-1]\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg))$.
+Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
+\label{cor:2d88Btwist}
+\end{corollary}
 
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.

### 2020-02-21 paper.tex

@@
 
-\subsubsection{Holomorphic Twist} \label{sect:2d44minimaltwist}
-The holomorphic twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
+\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
+The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
 By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
@@
 This equivalence is $\mr U(1)$-invariant.
-\label{thm:2d44holomorphictwist}
 \end{theorem}
@@
 \subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang--Mills Theory} \label{sect:2d(8,8)}
-Next we consider the $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
+Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
+This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
 No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.
 
-The R-symmetry group in the $\mc N=(8,8)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.
-The classification of square-zero supercharges is identical to the classification we saw in the $\mc N=(4,4)$ case.
+The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \spin(8;\CC)$, acting on $W_+$ and $W_-$ by its two semi-spin representations.
+As in the $\mc N=(4,4)$ case, the classification of square-zero supercharge is identical to the classification we saw in the $\mc N=(4,4)$ case.
 Rank $(1,0)$ square zero supercharges, and rank $(1,1)$ square zero supercharges split into two orbits in the following way.
@@
 \begin{prop}
-There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra.
-The generic orbit consists of A-supercharges and the special orbit consists of B-supercharges.
+There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(8,8)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.
+The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
 \end{prop}
@@
 
-The 2d $\cN=(8, 8)$ super Yang--Mills theory may be considered as a 2d $\cN=(4, 4)$ super Yang--Mills theory with matter valued in the symplectic $\fg$-representation $U=T^*\fg$.
-So, all the computations in this section follow from the corresponding computations in Section \ref{sect:2d(4,4)}.
-
-\subsubsection{Holomorphic Twist} \label{sect:2d88minimaltwist}
-
-From Theorem \ref{thm:2d44holomorphictwist} we obtain the following statement.
+Upon dimensional reduction from 3d $\mc N=8$, the $B$-supercharge reduces to the 2d $\mc N=(8,8)$ $B$-supercharge. 
+Indeed, if we forget down to $\mc N=4$ supersymmetry, then the $B$-twist should correspond to the $B$-twist.
+In both $\mc N=(4,4)$ and $\mc N=(8,8)$ the two orbits are distinguished, in that the orbit of $B$-twists lies in the closure of the orbit of $A$-twists.
+
+\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
+The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.
 
 \begin{theorem}
-The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC, T[1] T^*(\fg/\fg))$.
-This equivalence is $\mr U(1)$-equivariant.
-\end{theorem}
-
-\subsubsection{Topological Twists}
-\label{sect:2d88Atwist}
-\label{sect:2d88Btwist}
-
-Consider the family of topological supercharges $Q_t$ from Section \ref{sect:2d44Atwist}. From Theorem \ref{thm:2d44Hodgetwist} we obtain the following statement.
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Dol}})$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
+
+\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
+The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{thm:3d8Hodgetwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
 
 \begin{theorem}
-The twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the theory $\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg)_{\Hod})$.
-Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
-\label{thm:2d88Hodgetwist}
-\end{theorem}
-
-\begin{corollary}
-The topological A-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively trivial.
-\label{cor:2d88Atwist}
-\end{corollary}
-
-\begin{corollary}
-The topological B-twist of the 2d $\cN=(8, 8)$ super Yang--Mills theory is perturbatively equivalent to the theory $T^*[-1]\map(\RR^2_{\mathrm{dR}}, T^*(\fg/\fg))$.
-Moreover, the equivalence is $\SO(2, \RR)$-equivariant.
-\label{cor:2d88Btwist}
-\end{corollary}
+The holomorphic twist of 2d $\mc N=(8,8)$ super Yang-Mills admits a one-parameter deformation to the $A$-twist.
+This family is perturbatively equivalent to a Hodge theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
+
+\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
+The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
+Combining Theorem \ref{cor:3dN8Btwist} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
+
+\begin{theorem}
+The B-twist of 2d $\mc N=(8,8)$ super Yang-Mills is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg / \gg))$.
+This equivalence is $\mr U(1)$-invariant.
+\end{theorem}
 
@@
 \begin{proof}
-%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  

### 2020-02-21 paper.tex
intro to each section

--- 2020-02-21 paper.tex
@@
 
-The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10, \CC)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with nondegenerate symmetric bilinear pairings.
-There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries.
+The odd part of the $10$-dimensional supersymmetry algebra is 
+\[
+\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-,
+\] 
+where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10, \CC)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with nondegenerate symmetric bilinear pairings.
+
+There are supersymmetric Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetry. 
 We concentrate on the first case, the second case being identical. 
@@
 
-The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9, \CC)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
+The odd part of the $9$-dimensional supersymmetry algebra is 
+\[
+\Sigma\cong S\otimes W,
+\] 
+where $S$ is the 16-dimensional spin representation of $\Spin(9, \CC)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+
+There is a supersymmetric Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
 
@@
 
-The 8-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 8-dimensional semi-spin representations of $\Spin(8, \CC)$ and $W$ is a complex vector space.
+The odd part of the $8$-dimensional supersymmetry algebra is 
+\[
+\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*,
+\] 
+where $S_+, S_-$ are the $8$-dimensional semi-spin representations of $\Spin(8, \CC)$ and $W$ is a complex vector space. 
 The semi-spin representations carry nondegenerate symmetric bilinear pairings $S_{\pm}\otimes S_{\pm}\rightarrow \CC$.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
+
+There is a supersymmetric Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.
 
@@
 
-We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2; \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
+We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits R-symmetry group $G_R=\Spin(2; \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.
 
@@
 
-The 7-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 8-dimensional spin representation of $\Spin(7, \CC)$ and $W$ is a complex symplectic vector space.
+The odd part of the $7$-dimensional supersymmetry algebra is
+\[
+\Sigma\cong S\otimes W
+\]
+where $S$ is the 8-dimensional spin representation of $\Spin(7, \CC)$, and $W$ is a complex symplectic vector space.
 The spin representation carries a nondegenerate symmetric bilinear pairing $S\otimes S\rightarrow \CC$.
-There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC^2$.
+
+There is a supersymmetric Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC^2$.
 
@@
 
-The 6-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 4-dimensional semi-spin representations of $\Spin(6, \CC)\cong \SL(4, \CC)$ and $W_+, W_-$ are complex symplectic vector spaces.
-We have isomorphisms $S_+\cong S_-^*$.
+The odd part of the $6$-dimensional supersymmetry algebra is
+\[
+\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-
+\] 
+where $S_+, S_-$ are the 4-dimensional semi-spin representations of $\Spin(6 , \CC)\cong \SL(4, \CC)$, and $W_+, W_-$ are complex symplectic vector spaces. 
+We have $\Spin(6;\CC)$-invariant isomorphisms $S_+\cong S_-^*$.
 
@@
 
-The 5-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 4-dimensional spin representation of $\Spin(5, \CC)\cong \Sp(4, \CC)$ and $W$ is a complex symplectic vector space.
+The odd part of the $5$-dimensional supersymmetry algebra is 
+\[
+\Sigma\cong S\otimes W
+\]
+where $S$ is the 4-dimensional spin representation of $\Spin(5, \CC)\cong \Sp(4, \CC)$ and $W$ is a complex symplectic vector space. 
 The spin representation carries a symplectic paring $S\otimes S\rightarrow \CC$.
 
-There are Yang--Mills theories with $\cN=1$ or $\cN=2$ supersymmetry, which we consider separately.
+There are Yang--Mills theories with $\cN=1$ or $\cN=2$ supersymmetry, where $2 \cN = \dim(W)$, which we consider separately.
 
@@
 
-The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional semi-spin representations of $\Spin(4, \CC)\cong \SL(2, \CC) \times \SL(2, \CC)$ and $W$ is a complex vector space.
+The odd part of the $4$-dimensional supersymmetry algebra is
+\[
+\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*
+\] 
+where $S_+, S_-$ are the 2-dimensional semi-spin representations of $\Spin(4, \CC)\cong \SL(2, \CC) \times \SL(2, \CC)$ and $W$ is a complex vector space. 
 The semi-spin representations carry symplectic pairings $S_\pm\otimes S_\pm\rightarrow \CC$.
 
-There are Yang--Mills theories with $\cN=1,2,4$ supersymmetry, which we consider separately.
+There are Yang--Mills theories with $\cN= \dim(W) = 1,2,4$ supersymmetry, which we consider separately.
 
@@
 \section{Dimension 3}
-The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.
-The maximal supersymmetric gauge theory has $\mc N=8$.
+The odd part of the $3$-dimensional supersymmetry algebra is
+\[
+\Sigma \iso S \otimes W, 
+\]
+where $S$ is the two-dimensional complex spin representation of $\Spin(3;\CC)$, and where $W$ is a vector space equipped with a bilinear pairing.
+
+The maximal supersymmetric gauge theory has $\mc N= \dim(W) = 8$.  
 There are $\mc N=4$ super Yang--Mills theories for every choice $U$ of a complex symplectic representation of the gauge group, and $\mc N=2$ super Yang--Mills theories for every choice $R$ of arbitrary complex representation of the gauge group.
 Finally, there are $\cN=1$ super Yang--Mills theories in 3 dimensions, but there are no square-zero supercharges with that amount of supersymmetry.
-In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
+In dimension $3$, much like we saw in dimensions $5$ and $7$, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.
 
@@
 \[
-\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- .
-\]
+\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_- ,
+\]
+where $W_\pm$ are complex vector spaces equipped with symmetric nondegenerate bilinear pairings. 
 The complex semi-spin representations $S_\pm$ are 1-dimensional, where $\spin(2;\CC) \iso \CC^\times$ acts with weight $\pm \frac{1}{2}$. 
@@
 There are two classes of twisted supersymmetric gauge theory that we will consider in two dimensions.
-First, we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
+First, we have theories with $(\mc N, \mc N)$ supersymmetry corresponding to $\cN = \dim(W_+) = \dim(W_-)$; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.
 Namely, we have the 2d $\cN=(1, 1)$, 2d $\cN=(2, 2)$, 2d $\cN=(4, 4)$ and 2d $\cN=(8, 8)$ super Yang--Mills theories.
@@
 We additionally have gauge theories with chiral, i.e.
-$(\cN, 0)$ supersymmetry, which we have constructed in Sections \ref{sect:2dchiral} and \ref{sect:SYM}.
+$(\cN_+, 0)$ supersymmetry, which we have constructed in Sections \ref{sect:2dchiral} and \ref{sect:SYM}.
 We will address twists for these two classes of theories in turn.
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \begin{theorem} \label{thm:2d(4,0)}
-The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 %\begin{theorem}\label{2d(0,4)}
-%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
 %\end{theorem}
@@
 
-\subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N+,0)} Super Yang--Mills Theory}
+\subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N_+,0)} Super Yang--Mills Theory}
 
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic BF with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_- -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
+%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  

### 2020-02-21 paper.tex
2d chiral edits

--- 2020-02-21 paper.tex
@@
 
+\subsection{Spinors}
+\label{sect:spinors}
+
+In this paper we will extensively use the theory of spinors.
+Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
+Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
+\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
+Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$.
+Denote the Clifford action by $\rho(v)\in\eend(M)$.
+We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
+\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
+for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
+\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
+by
+\begin{equation}
+(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
+\label{eq:Gammaspinorpairing}
+\end{equation}
+
+We have a subset $\Spin(V)\subset \Cl(V)$, so $\Sigma$ and $\Sigma^*$ are representations of the spin group. Moreover, the Clifford action and the maps $\Gamma$ are $\Spin(V)$-equivariant.
+
+We may identify $\wedge^2(V)\rightarrow \so(V)$ via
+\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
+This gives rise to an action map
+\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
+of two-forms on spinors.
+
+Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
+\begin{equation}
+q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
+\label{eq:quantizationtwoforms}
+\end{equation}
+
+The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$, so that $\so(V)$-equivariance of $\Gamma$ gives the following.
+
+\begin{prop}
+For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
+\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
+\label{prop:cliffordactionproperty1}
+\end{prop}
+
+We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
+Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
+\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]
+
+From \eqref{eq:quantizationtwoforms} we get the following property.
+
+\begin{prop}
+Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
+\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
+\label{prop:cliffordactionproperty2}
+\end{prop}
+
+Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
+
+\begin{prop}
+Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
+\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
+\label{prop:cliffordactionproperty3}
+\end{prop}
+
+Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\d}$ is the corresponding twisted Dirac operator.
+
 \subsection{Supersymmetry Algebras} \label{sect:susyalgebras}
@@
 \[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
-defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.
+defined as in Section \ref{sect:spinors}. We make the following assumption on this setup.
 
@@
 
-Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).
+Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Section \ref{sect:spinors}).
 
@@
 
-We turn to $\cN=(2,0)$ supersymmetric Yang-Mills theory.
+We turn to the $\cN=(2,0)$ supersymmetric Yang-Mills theory.
 In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
-The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a representation $R$. 
-The $R$-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.
+The supersymmetric matter consists of the $\cN = (2,0)$ chiral multiplet with values in a $\fg$-representation $R$. 
+The R-symmetry group is $G_R = \SO(2;\CC)$ which acts on $W_+$ by the defining representation.
 
@@
 \item a gauge boson $A \in \Omega^1(\RR^2;\fg)$.
-\item gauge fermions $\lambda \in C^\infty(\RR^2 ; S_+ \otimes W_+ \otimes \fg)$. 
+\item gauge fermions $\lambda \in C^\infty(\RR^2 ; \Pi S_+ \otimes W_+ \otimes \fg)$. 
 \item matter bosons $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
-\item matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_- \otimes R)$.
+\item matter fermions $\psi \in C^\infty(\RR^2 ; \Pi S_- \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; \Pi S_- \otimes R)$.
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 \[
-\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
-\]
-\end{itemize}
-
-\subsubsection{Minimal Twist} \label{sect:2d20minimaltwist}
-
-Choose a complex structure $L \subset V_\RR$. 
-Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\phi \colon \MU(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+\]
+\end{itemize}
+
+\subsubsection{Holomorphic Twist} \label{sect:2d20minimaltwist}
+
+Choose a complex structure $L \subset V$. 
+Under the embedding $MU(1) \hookrightarrow \Spin(2; \CC)$, the semi-spin representations decompose as
 \[
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The holomorphic twist of the 2d $\cN=(2,0)$ super Yang--Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 %The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
 We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
 Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
 
@@
 
-Next, we consider $\cN=(4,0)$ supersymmetric Yang-Mills theory.
+Next, we consider the $\cN=(4,0)$ supersymmetric Yang--Mills theory.
 In the supersymmetry algebra, we have $W_- = 0$ and $W_+$ is a complex four-dimensional vector space equipped with a nondegenerate symmetric bilinear pairing.
-The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic representation $U$. 
-The $R$-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
+The supersymmetric matter consists of the $\cN = (4,0)$ hypermultiplet with values in a complex symplectic $\fg$-representation $U$. 
+The R-symmetry group is $G_R = \SL(2;\CC) \times \GL(1;\CC)$.
 As a $G_R$-representation, $W_+ = \Tilde{W} \oplus \Tilde{W}$ where $\Tilde{W}$ is the defining representation of $\SL(2;\CC)$ and where $\GL(1;\CC)$ acts by weight $(1,-1)$ with respect to this decomposition.
@@
 
-\subsubsection{Minimal twist} \label{sect:2d40minimaltwist}
-
-Choose a complex structure $L \subset V_\RR$. 
-Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
+\subsubsection{Holomorphic twist} \label{sect:2d40minimaltwist}
+
+Choose a complex structure $L \subset V$. 
+Under the embedding $MU(1) \hookrightarrow \Spin(2; \CC)$, the semi-spin representations decompose as
 \[
@@
 \]
-We choose a twisting homomorphism $\phi : \U(1) \to G_R$ under which $\Tilde{W} = \det(L)^{1/2} \oplus \det(L)^{-1/2}$
+We choose a twisting homomorphism $\phi\colon \U(1) \to G_R$ under which $\Tilde{W} = \det(L)^{1/2} \oplus \det(L)^{-1/2}$
 so that
@@
 
-The twisting data homomorphism is the natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.
+The $\ZZ$-grading is induced by a natural embedding $\alpha \colon \U(1) \hookrightarrow \GL(1;\CC) \to G_R$.
 
@@
 \begin{theorem} \label{thm:2d(4,0)}
-The minimal twist of 2d $\cN=(4,0)$ super Yang-Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+The holomorphic twist of the 2d $\cN=(4,0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with the space of fields $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
-First, we integrate out the field $\lambda^-$ using Proposition \ref{prop:integrateoutfield}.  
+First, we eliminate the field $\lambda^-$ using Proposition \ref{prop:integrateoutfield}.  
 We then observe that the action includes the terms $\int  (\lambda^-_{1,0} , A_{1,0}^*)$ and  $\int (\psi_-, \nu^*)$.  
 Thus, the two pairs $(\lambda^-_{1,0}, A_{1,0})$ and $(\nu, \psi_-)$ form BRST doublets, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
 
@@
 We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
-The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.
+The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary space equipped with a nondegenerate symmetric bilinear pairing.
 
@@
 
-\subsubsection{Minimal Twist} \label{sect:2dN0minimaltwist}
-
-Choose a complex structure $L \subset V_\RR$. 
+\subsubsection{Holomorphic Twist} \label{sect:2dN0minimaltwist}
+
+Choose a complex structure $L \subset V$. 
 Under the embedding $U(1) \hookrightarrow \spin(2;\CC)$, the semi-spin representations decompose as
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The minimal twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to holomorphic $BF$ with moduli space $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 %The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
 We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
 Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
-which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
+which can be eliminated using Proposition \ref{prop:BRSTdoublet}.
 
@@
 
-\appendix
-
-\section{Spinors}
-\label{sect:spinors}
-
-In this paper we will extensively use the theory of spinors.
-Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
-Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
-\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
-Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$.
-Denote the Clifford action by $\rho(v)\in\eend(M)$.
-We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
-\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
-for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
-\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
-by
-\begin{equation}
-(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
-\label{eq:Gammaspinorpairing}
-\end{equation}
-
-We have a subset $\Spin(V)\subset \Cl(V)$, so $\Sigma$ and $\Sigma^*$ are representations of the spin group. Moreover, the Clifford action and the maps $\Gamma$ are $\Spin(V)$-equivariant.
-
-We may identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
-This gives rise to an action map
-\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
-of two-forms on spinors.
-
-Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
-\begin{equation}
-q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
-\label{eq:quantizationtwoforms}
-\end{equation}
-
-The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$, so that $\so(V)$-equivariance of $\Gamma$ gives the following.
-
-\begin{prop}
-For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
-\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
-\label{prop:cliffordactionproperty1}
-\end{prop}
-
-We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
-Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
-\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]
-
-From \eqref{eq:quantizationtwoforms} we get the following property.
-
-\begin{prop}
-Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
-\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
-\label{prop:cliffordactionproperty2}
-\end{prop}
-
-Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
-
-\begin{prop}
-Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
-\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
-\label{prop:cliffordactionproperty3}
-\end{prop}
-
-Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\d}$ is the corresponding twisted Dirac operator.
-
 \pagestyle{bib}

### 2020-02-21 paper.tex
merge with p

--- 2020-02-21 paper.tex
@@
 For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. 
-We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$.
-$V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
+Let $V$ to be the complex vector space of $2\times 2$ Hermitian matrices with values in $A$.
+Note that $\dim(V) = \dim(A) + 2$. 
+The space $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. 
 Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
+Let ${\rm C}\ell_V$ be the resulting Clifford algebra.
 
@@
 
-Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.
+Consider the two isomorphic spinorial representations $\Sigma=A\oplus A$ and its dual $\Sigma^* = A\oplus A$.
+We will equip the sum $\Sigma \oplus \Sigma^*$ with an action of the Clifford algebra ${\rm C}\ell_V$.  
 The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.  
@@
 
-All four examples are alternative, while the first three examples are moreover associative.
+All four examples are alternative, while the first three examples are also associative.
 
@@
 \end{prop}
-
+\brian{Anti field in $S^{(1)}_{matter}$.}
 %The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.

### 2020-02-21 paper.tex
matter

@@
 We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow that of Baez and Huerta \cite{BaezHuerta}.
+This section provides the representation theoretic underpinning for theories with minimally supersymmetric matter in dimensions $\geq 3$.
 
@@
 
-Consider the two isomorphic spinorial representations $\Sigma=A\oplus A$ and its dual $\Sigma^* = A\oplus A$.
+Consider the left $A$-module $\Sigma=A\oplus A$ and the right $A$-module $\Sigma^* = A\oplus A$.
 We will equip the sum $\Sigma \oplus \Sigma^*$ with an action of the Clifford algebra ${\rm C}\ell_V$.  
 The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.  
-We define action maps
+Define the action maps
 \[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
-given, respectively, by
+by
 \[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
@@
 
-So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.
+As a result, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.
 
@@
 
+Note that since $\dim(V) = \dim(A) + 2$, the above constructions are only valid in dimensions $\geq 3$.
 We will be interested in the following examples:
 \begin{enumerate}
-\item (\textbf{3d $\mc N=1$ supersymmetry}) $A = \CC$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3, \CC)$.
+\item (\textbf{3d $\mc N=1$ supersymmetry}) $A = \CC$. 
+Here, $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3, \CC)$.
 
@@
 
-Explicitly, we consider the following cases:
 \begin{itemize}
@@
 
-Explicitly, we consider the following cases:
+Explicitly, we consider the following examples of theories of matter with minimal supersymmetry.
+
+The first three examples concern chiral two-dimensional supersymmetry, where $\Sigma = S^{2 \rm d}_+ \otimes A$, with $S_+^{2 \rm d}$ the one-dimensional positive complex semi-spin representation of $\Spin(2;\CC)$:
+
 \begin{itemize}
@@
 Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.
+\end{itemize}
+
+In dimensions $\geq 3$ we have the following examples, where $\Sigma = A \oplus A$:
+
+\begin{itemize}
 

### 2020-02-22 paper.tex
4d (2, 1) (in progress)

--- 2020-02-21 paper.tex
@@
 For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries.
-Let $V$ to be the complex vector space of $2\times 2$ Hermitian matrices with values in $A$.
-Note that $\dim(V) = \dim(A) + 2$. 
-The space $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. 
+We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$.
+$V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$.
 Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
-Let ${\rm C}\ell_V$ be the resulting Clifford algebra.
 
@@
 
-Consider the two isomorphic spinorial representations $\Sigma=A\oplus A$ and its dual $\Sigma^* = A\oplus A$.
-We will equip the sum $\Sigma \oplus \Sigma^*$ with an action of the Clifford algebra ${\rm C}\ell_V$.  
+Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.
 The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.
@@
 
-All four examples are alternative, while the first three examples are also associative.
+All four examples are alternative, while the first three examples are moreover associative.
 
@@
 \end{prop}
-\brian{Anti field in $S^{(1)}_{matter}$.}
+
 %The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
@@
 
-\subsubsection{Rank \texorpdfstring{$(2,1)$}{(1,2)} Topological Twist}
-
-%Next we look at the case of the twist by a rank $(1,2)$ supercharge. 
-%As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(1,2)$. 
-%
-%We use the same twisting homomorphism $\phi\colon \MU(2) \to \Spin(6;\CC)$ and twisting datum $\alpha\colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
-%Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
-%\[
-%S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \oplus \det(L)^{-1}.
-%\]
-%The representation $S_- \otimes W^*$ decomposes as
-%\[
-%S_- \otimes W^* = L \oplus L^* \oplus \CC Q'\oplus\eend_0(L),
-%\]
-%where $\eend_0(L)\subset \eend(L)$ is the subspace of traceless endomorphisms.
-The supercharge $Q_0$ has rank $(1, 0)$ and the supercharge $Q'$ has rank $(0, 2)$.
-Moreover, both are square-zero and commute with each other.
-Therefore, we may consider a family of square-zero supercharges
-%\begin{equation}
-%Q_t = Q_0 + tQ'
-%\label{eq:4d412Hodgefamily}
-%\end{equation}
-%which is of rank $(1, 0)$ at $t=0$ and of rank $(1, 2)$ at $t\neq 0$.
-%
-%We are going to use the notation of the fields from Section \ref{sect:4d4holomorphictwist}.
-%
-%\begin{prop}
-%Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}.
-The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
-%\begin{align*}
-%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-%I^{(2)} (Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
-%\end{align*}
-%\end{prop}
-
-%\begin{theorem}
-%The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$.
-Moreover, this equivalence is $\U(2)$-equivariant.
-%\label{thm:4d12hodge}
-%\end{theorem}
-
-%\begin{proof}
-%We begin by applying Corollary \ref{cor:quad} to the two $t$-dependent quadruples of fields:
-%\begin{align*}
-%& (t \varsigma, \rho, t \phi, A_{1,0}) \\
-%& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
-%\end{align*}
-%This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
-%\begin{align*}
-%\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varsigma, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varsigma^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varsigma^* - t [A_{0,1}, a]b^* \right) \\
-%\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
-%\end{align*}
-%
-%The next step is to decompose the $(1,1)$ form $\psi$ as
-%\[
-%\psi = \omega \Lambda \psi + \psi_{\perp}
-%\]
-%where $\Lambda \psi_{\perp} = 0$. 
-%
-%\end{proof}
+\subsubsection{Rank \texorpdfstring{$(2,1)$}{(2,1)} Topological Twist}
+
+Next we look at the case of the twist by a rank $(2,1)$ supercharge. 
+As in many cases so far, it will be useful to consider a family of supercharges which are generically of rank $(2,1)$.
+Consider the twisting homomorphism $\phi\colon \Spin(2; \RR)\times \Spin(2; \RR)\to G_R$ from Section \ref{sect:4d4partialtwist}.
+
+Consider a family of scalar square-zero supercharges
+\begin{equation}
+Q_{s, t} = Q_0 + t Q_1 + sQ_2,
+\label{eq:4d412Hodgefamily}
+\end{equation}
+where $Q_0,Q_1$ are rank $(1, 0)$ supercharges and $Q_2$ is a rank $(0, 1)$ supercharge, so that $Q_0 + t Q_1$ is the family of square-zero supercharges from Section \ref{sect:4d4Atwist} and $Q_0 + Q_2$ is the rank $(1, 1)$ square-zero supercharge from Section \ref{sect:4d4partialtwist}.
+We will now calculate the twist with respect to the family $Q_0 + tQ_1 + Q_2$.
 
 \begin{theorem}
-The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$.
+The twist of the 4d $\cN=4$ super Yang--Mills theory with respect to the family $Q_{1, t}$ of square-zero supercharges of Equation \eqref{eq:4d412Hodgefamily} is perturbatively equivalent to the theory $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$.
 Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
 \end{theorem}
+\begin{proof}
+The idea of the proof will be to eliminate fields as in the proof of Theorem \ref{thm:4dDonaldsontwist}, but keeping track of the $s$-dependence.
+
+Let $S(s,t)$ be the action functional of the 4d $\cN=4$ super Yang--Mills theory twisted by $Q_0 + tQ_1 + sQ_2$. Then we have
+\[S(s, t) = S(s, 0) + \left(S^{(1)}(tQ_1) + 2 S^{(2)}(Q_0, tQ_1) + S^{(2)}(tQ_1, tQ_1)\right) + 2S^{(2)}(tQ_1, sQ_2),\]
+where $S^{(1)}, S^{(2)}$ are the supersymmetry actions from Section \ref{sect:gaugemultipletSUSY}.
+Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.
+
+We will now repeat the simplifications performed in the proof of Theorem \ref{thm:4dDonaldsontwist}.
+We first perform a change of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$.
+Then we perform the following field eliminations:
+\begin{itemize}
+\item Using Proposition \ref{prop:integrateoutfield} we set $\chi = 0$ and $\chi^* - t\wt\chi^*$ to a certain value.
+
+\item Using Proposition \ref{prop:BRSTdoublet} we set $\rho^* = 0$, $A_{1, 0} = 0$ and $\rho, A_{1, 0}^*$ to certain values.
+
+\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{a} = 0$, $\tilde{\chi}^*=0$ and $\tilde{\chi}+t\chi, \tilde{a}^*$ to certain values.
+
+\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{\nu}^* = 0$, $\nu = 0$ and $\tilde{\nu},\nu^*$ to certain values.
+\end{itemize}
+\end{proof}
 
@@
 The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.
-Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
+Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
 \end{proof}
@@
 \begin{theorem} \label{thm:2d(4,0)}
-The holomorphic twist of the 2d $\cN=(4,0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system with the space of fields $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
+The holomorphic twist of the 2d $\cN=(4,0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1] \Sect(\CC , (U \otimes K^{1/2}_{\CC}) \ham \fg)$.
 This equivalence is $\U(1)$-equivariant.

### 2020-02-22 paper.tex

@@
 
-The notion of supersymmetric twisting for a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}.
+The notion of supersymmetric twisting for a supersymmetric field theory was introduced by Witten \cite{WittenTQFT}, and further developed mathematically by Costello \cite{CostelloSUSY}. 
 The definitions we use in this paper will follow our previous work \cite{ElliottSafronov}, so let us briefly recall the important terminology.
@@
 \end{itemize}
+
+%^An approach to twisting supergravity with the goal of formulating a twisted version of the AdS/CFT correspondence has been initiated in \cite{CostelloLiSUGRA}.
 
@@
 In Part \ref{formalism_part} we set up the formalism that we will use when we study supersymmetric gauge theories and their twists.
-The first main ingredient is the Batalin-Vilkovisky formalism \cite{BatalinVilkovisky} for classical field theory (Section \ref{BV_section}), as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.
-The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}), following Baez and Huerta \cite{BaezHuerta}.
+The first main ingredient is the Batalin-Vilkovisky formalism for classical field theory (Section \ref{BV_section}).
+%, as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.  
+The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}).
+%, following Baez and Huerta \cite{BaezHuerta}.  
 We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
@@
 We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.  
-We are also grateful to Dylan Butson for kind discussion of his related forthcoming work.
-The research of CE on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
+We are also grateful to Dylan Butson for kind discussion of his related forthcoming work, specifically in reference to supersymmetric theories in dimension $6$.  
+The research of C.E.
+on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
+The work of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
+\pavel{Support}
 
@@
 
-Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.
+Consider the left $A$-module $\Sigma=A\oplus A$ and the right $A$-module $\Sigma^* = A\oplus A$.
+We will equip the sum $\Sigma \oplus \Sigma^*$ with an action of the Clifford algebra ${\rm C}\ell_V$.  
 The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.  
-We define action maps
+Define the action maps
 \[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
-given, respectively, by
+by
 \[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The holomorphic twist of the 2d $\cN=(2,0)$ super Yang--Mills theory with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \begin{proof}
-%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
@@
 \begin{proof}
+First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
 %The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
-First, we eliminate the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
 We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.

### 2020-02-22 paper.tex
Acknowledgements
(2,1) done

@@
 on this project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (QUASIFT grant agreement 677368).
-The work of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
-\pavel{Support}
+The research of P.S. was supported by the NCCR SwissMAP grant of the Swiss National Science Foundation.
+The research of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
 
@@
 S^{(2)}_{\rm gauge} (Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
-S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
+S_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varsigma, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varsigma^* \right) \\
 S_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
@@
 \end{prop}
-\brian{Anti field in $S^{(1)}_{matter}$.}
+%\brian{Anti field in $S^{(1)}_{matter}$.}
 %The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
@@
 We are left with the action
-\[S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
+\begin{equation}\label{eqn:(2,0)}
+S_{\mr{BF}} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),
+\end{equation}
 where $S_{\mr{BF}}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
@@
 Let $S(s,t)$ be the action functional of the 4d $\cN=4$ super Yang--Mills theory twisted by $Q_0 + tQ_1 + sQ_2$. Then we have
-\[S(s, t) = S(s, 0) + \left(S^{(1)}(tQ_1) + 2 S^{(2)}(Q_0, tQ_1) + S^{(2)}(tQ_1, tQ_1)\right) + 2S^{(2)}(tQ_1, sQ_2),\]
-where $S^{(1)}, S^{(2)}$ are the supersymmetry actions from Section \ref{sect:gaugemultipletSUSY}.
+\begin{equation}\label{eqn:(2,1)2}
+S(s, t) = S(s, 0) + \left(S^{(1)}(tQ_1) + 2 S^{(2)}(Q_0 + tQ_1) + S^{(2)}(tQ_1)\right) + 2S^{(2)}(tQ_1 + sQ_2),
+\end{equation}
+where $S^{(1)} = S^{(1)}_{\rm gauge}, S^{(2)} = S^{(2)}_{\rm gauge}$ are the functionals from Section \ref{sect:gaugemultipletSUSY} encoding the infinitesimal actions by supersymmtery. 
 Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.
@@
 
-\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{a} = 0$, $\tilde{\chi}^*=0$ and $\tilde{\chi}+t\chi, \tilde{a}^*$ to certain values.
-
-\item Using Proposition \ref{prop:BRSTdoublet} we set $\tilde{\nu}^* = 0$, $\nu = 0$ and $\tilde{\nu},\nu^*$ to certain values.
-\end{itemize}
-\end{proof}
-
-\begin{proof}
-Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
+\item Using Proposition \ref{prop:BRSTdoublet} we set $\Tilde{a} = 0$, $\tilde{\chi}^*=0$ and $\Tilde{\chi}+t\chi, \Tilde{a}^*$ to certain values.
+
+\item Using Proposition \ref{prop:BRSTdoublet} we set $\Tilde{\nu}^* = 0$, $\nu = 0$ and $\Tilde{\nu},\nu^*$ to certain values.
+\end{itemize}
+
+The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
+Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
+Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (accept now the fields are adjoint valued). 
+We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
+\end{proof}
+
+%\begin{proof}
+%Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
 Consider the supersymmetry actions
-\begin{align*}
-&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
-&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
-\end{align*}
-We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
+%\begin{align*}
+%&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
+%&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
+%\end{align*}
+%We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
 Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
-
-We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
-\begin{equation}
-\label{eq:4d_12_general_def}
-\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
-\end{equation}
-First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
+%
+%We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
+%\begin{equation}
+%\label{eq:4d_12_general_def}
+%\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
+%\end{equation}
+%First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
 This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
-
-Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
+%
+%Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
 The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
-\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+%\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
+%is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
 That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
@@
 In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
-
-So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+%
+%So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
 We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
@@
 Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
-
-As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+%
+%As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
 Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
 That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
-
-It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
+%
+%It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
 To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
@@
 Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
-
-We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
+%
+%We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
 The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
-\begin{equation}
-\label{eq:4d_12_further_deformation}
-t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
-\end{equation}
-in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
-
-Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
+%\begin{equation}
+%\label{eq:4d_12_further_deformation}
+%t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
+%\end{equation}
+%in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
+%
+%Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
 This deformation gives the desired theory.
@@
 Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
-\end{proof}
+%\end{proof}
 

### 2020-02-22 paper.tex
typo fix

@@
 Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
-Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (accept now the fields are adjoint valued). 
+Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (where now the fields are adjoint valued). 
 We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 

### 2020-02-22 paper.tex
typo fix

@@
 \end{equation}
-where $S^{(1)} = S^{(1)}_{\rm gauge}, S^{(2)} = S^{(2)}_{\rm gauge}$ are the functionals from Section \ref{sect:gaugemultipletSUSY} encoding the infinitesimal actions by supersymmtery. 
+where $S^{(1)} = S^{(1)}_{\rm gauge}, S^{(2)} = S^{(2)}_{\rm gauge}$ are the functionals from Section \ref{sect:gaugemultipletSUSY} encoding the infinitesimal actions by supersymmetry.
 Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.

### 2020-02-22 paper.tex
removed commented out code

@@
 \end{itemize}
-
-%^An approach to twisting supergravity with the goal of formulating a twisted version of the AdS/CFT correspondence has been initiated in \cite{CostelloLiSUGRA}.
 
@@
 The corresponding equation is a deformation of the Kapustin--Witten equations using the K\"ahler form.
-
-%The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
-%\begin{align}
-%(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
-%(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
-%\d^*_A \phi &= 0.
-%\end{align}
-%Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
 
@@
 The first main ingredient is the Batalin-Vilkovisky formalism for classical field theory (Section \ref{BV_section}).
-%, as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.  
 The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}).
-%, following Baez and Huerta \cite{BaezHuerta}.  
 We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
@@
 
-%There is a corollary of this proposition obtained by iterating the procedure. 
-%We will only use a single iteration. 
-%
-%\begin{corollary} \label{cor:quad}
-%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
-%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
-%\[
-%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
-%\]
-%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
-%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
-%Suppose further that the local functional
-%\[
-%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
-%\]
-%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
-%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
-%\[
-%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
-%\]
-%and
-%\[
-%S' = S_0 + \int \phi_1 \psi_1^* - S''
-%\]
-%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$
-
-%\end{corollary}
-%\begin{proof}
-%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
-%We begin by making the following change of coordinates on the BV fields:
-%\begin{align*}
-%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
-%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
-%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
-%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
-%\end{align*}
-%with $\phi_1, \psi_1$ left fixed. 
-%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
-%Further, in the new coordinates, the action takes the form
-%\[
-%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
-%\]
-%\end{proof}
-
 \subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
@@
 \end{proof}
-
-%\begin{corollary}
-%Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
-%\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
-%Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
-%\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
-%\label{cor:Hodgetopologicalreduction}
-%\end{corollary}
 
@@
 These fields have the same degrees as in the holomorphic BF theory.
-
-\begin{comment}
-and hence the underlying local $L_\infty$ algebra after the twist becomes
-
-\[
-\xymatrix@R=0.5cm@C=0.5cm{
-\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
-\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
-  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
-  }
-\]
-
-\[
-\xymatrix@R=0.5cm@C=0.5cm{
-\ul{-4n+2} & \ul{-4n+3} & \ul{-4n+4} & \cdots & \ul{4n-1} & \ul{4n} & \ul{4n+1} \\ 
- &&&& \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
- \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
-}
-\]
-
-\[
-\xymatrix@R=0.5cm@C=0.5cm{
-\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
-\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varsigma^*} \\
-& & & & \Omega^{2,0}(\CC^2 ; U)_{\varsigma} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
-}
-\]
-\end{comment}
-\end{proof}
-
-%There is an alternative $\ZZ$-grading one can assign to the twist when $U$ is of cotangent type $U = R \oplus R^*$. 
-%In this case, the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$. 
-%The new twisting datum is $\Tilde{\alpha} \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components. 
-%%\[
-%%\begin{array}{ccccc}
-%%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
-%%&  z & \mapsto & \left(1 , z, z \right)
-%%\end{array}
-%%\]
-%There is also a new twisting homomorphism 
-%\[
-%\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\Tilde{\alpha}} G_R
-%\]
-%By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
-%
-%\begin{thm}
-%\label{thm:4d_2minimaltwistgraded}
-%The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
-%Moreover, this equivalence is $\U(2)$-equivariant.
-%\end{thm}
+\end{proof}
 
@@
 \end{prop}
-%\brian{Anti field in $S^{(1)}_{matter}$.}
-%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
-%\begin{align*}
-%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
-%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
-%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
-%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
-%\end{align*}
 
@@
 \end{proof}
-
-%\begin{proof}
-%Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
-Consider the supersymmetry actions
-%\begin{align*}
-%&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
-%&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
-%\end{align*}
-%We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
-Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
-%
-%We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
-%\begin{equation}
-%\label{eq:4d_12_general_def}
-%\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
-%\end{equation}
-%First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
-This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
-%
-%Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
-The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
-%\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
-%is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
-That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
-To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
-In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
-%
-%So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
-We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
-The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
-Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
-Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
-%
-%As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
-Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
-That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
-%
-%It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
-To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
-Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.
-Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
-%
-%We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
-The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
-%\begin{equation}
-%\label{eq:4d_12_further_deformation}
-%t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
-%\end{equation}
-%in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
-%
-%Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
-This deformation gives the desired theory.
-The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.
-Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
-%\end{proof}
 
@@
 Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
-%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
-Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
 
@@
 \end{theorem}
-
-%\begin{proof}
-%On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
-We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.
-The dimensionally reduced theory is a $\ZZ$-graded and $\mr U(1)$-equivariant theory, equivalent as a $\ZZ/2\ZZ$-graded theory to the one obtained from 3d $\mc N=4$ -- this promotes the description given above to a $\ZZ$-graded and $\mr U(1)$-equivariant theory.
-When we calculate that dimensional reduction, the fields reduce according to the rule
-%\begin{align*}
-%\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
-%&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
-%\end{align*}
-%Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
-%\end{proof}
 
@@
 \item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$;
-\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
-%\item \brian{matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$}
+\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$.
+\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$.
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha : \U(1) \to G_R$. 
-%We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(0,2)}.
-%We take $\alpha : \U(1) \hookrightarrow \spin(2;\CC) \to \spin(4;\CC)$ to factor through the twisting data of Section \ref{sect:2d(0,2)}.
-%There is a compatible twisting homomorphism
-%\[
-%\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
-%\]
-%which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
 \end{itemize}
@@
 S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}} \nu , \ol \dd_{A_{0,1}} \gamma) + (\dd_{A_{1,0}}\gamma, \ol \dd_{A_{0,1}} \nu) + (\psi_- , \partial_{A_{1,0}} \gamma) + (\psi_+ , \partial_{A_{1,0}} \nu)  + \\
-%&\qquad + ([\lambda^+_{1,0}, ],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \/\
 & \qquad + ([\lambda^+, \gamma], \psi_-) + ([\lambda_{1,0}^+, \nu], \psi_-) + ([\lambda^-, \gamma], \psi_+) + ([\lambda^-_{1,0}, \nu], \psi_-) \bigg) \\
@@
 
-%The field content is:
-%\begin{itemize}
-%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
-%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
-%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
-%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
-%\end{itemize}
-
-%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
-
 \begin{theorem} \label{thm:2d(4,0)}
@@
 
-%\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
-%
-%\begin{theorem}\label{2d(0,4)}
-%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
-%\end{theorem}
-%
-%\begin{proof}
-%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
-%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-%\[
-%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
-%\]
-%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
-%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
-%Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
-%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-%The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
-%The claim now follows from Theorem \ref{2d(0,2)}. 
-%\end{proof}
-%
-%\begin{remark}
-%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
-%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
-%\end{remark}
-
 \subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N+,0)} Super Yang--Mills Theory}
@@
 We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(2,0)}.
-%We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
-%There is a compatible twisting homomorphism
-%\[
-%\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
-%\]
-\end{itemize}
-
-%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+\end{itemize}
 
@@
 First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.   
-%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
@@
 
-%\begin{proof}
-%The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
-%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
-%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
-%\[
-%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
-%\]
-%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
-%Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
-%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
-%Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
-%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
-%The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
-%\end{proof}
-
 \pagestyle{bib}

### 2020-02-22 paper.tex
Sect

@@
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC^2, (U\otimes K_{\CC^2}^{1/2}) \ham \fg)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
@@
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
@@
  \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$} & \\ \cline{2-4}
+ && {$T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$} & \\ \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
@@
 
-The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
+The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation \eqref{eqn:(2,1)2} is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
 Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
-Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (where now the fields are adjoint valued). 
+Finally, the term in parentheses in Equation \eqref{eqn:(2,1)2} agrees with the $t$-dependent terms in Equation \eqref{eqn:(2,0)}, (where now the fields are adjoint valued). 
 We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 
-From Theorem \ref{thm:2d44holomorphictwist} we obtain the following statement.
+The 2d $\cN=(8, 8)$ super Yang--Mills theory is a dimensional reduction of the 3d $\cN=8$ super Yang--Mills theory.
+Therefore, from Theorem \ref{3d_8_minimal_twist_thm} we obtain the following statement.
 
 \begin{theorem}
-The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC, T[1] T^*(\fg/\fg))$.
+The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC_{\mathrm{Dol}}, T[1] \fg/\fg)$.
 This equivalence is $\mr U(1)$-equivariant.

### 2020-02-22 paper.tex
I -> S

@@
 \begin{proof}
-Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
+Concretely, we will write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
 The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
@@
 The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local interaction functional 
-\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
+\[I_\fg = I + \sum_{k\geq 1} S_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
 satisfying the Maurer-Cartan equation
@@
 In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
+A BV theory $(E, \omega, S)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
 Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
@@
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
-The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
+The map $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $S_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
 But it also has cohomological degree $-k$.
@@
 The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action.
-However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
-However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
+However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $S_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
+However, given a twisting homomorphism $\phi$ we see that $S_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
 
@@
 Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action.
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $S^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
@@
 \begin{prop}
-The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
+The functionals $S^{(1)}$ and $S^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
 \begin{align*}
@@
 Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
-The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
+The $\MU(2)$ decomposition of the functionals $S_{\rm gauge}^{(1)}, S^{(1)}_{\rm matter}, S^{(2)}_{\rm gauge}, S^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
 \begin{align*}

### 2020-02-22 paper.tex
spellcheck

@@
 \begin{abstract}
-We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
-We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.
+We give a complete classification of twists of supersymmetric Yang--Mills theories in dimensions~$2\leq n \leq 10$.
+We formulate supersymmetric Yang--Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.
 For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.
-These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and BF theory.
+These twists can be described in terms of mixed holomorphic-topological versions of Chern--Simons and BF theory.
 \end{abstract}
@@
 
-To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
+To rigorously study the quantization of supersymmetric Yang--Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
 This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}.
-In the context of (non-supersymmetric) Yang-Mills theory for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+In the context of (non-supersymmetric) Yang--Mills theory for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 
-These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory.
-Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
+These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang--Mills theory.
+Furthermore, in all examples of theories obtained via twisting occurring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
 The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
@@
 The corresponding theory is equivalent to a generalized BF theory defined on a product of a complex curve $C$ and a real 3-manifold $M$.
-The twist was considred in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
+The twist was considered in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
  \item \emph{$\mc N=2$ topological A twist.} The intermediate twist admits a deformation to two topological twists.
@@
  \item \emph{$\cN=4$ topological rank $(2, 2)$ twist.} The $\cN=4$ topological B twist admits a deformation to a perturbatively trivial theory.
-The corresponding deformation is parametrized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
+The corresponding deformation is parameterized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
 Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$.
@@
  \hline
- \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern--Simons Theory & \multirow{2}*{5 (holomorphic)} \\
  &&&$\mr{Map}(\CC^5, B\gg)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Generalized Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Generalized Chern--Simons Theory & \multirow{2}*{5 (minimal)} \\
  &&&$\mr{Map}(\CC^4 \times \RR_{\mr{dR}}, B\gg)$ &\\ \hline
@@
  &&& $T^*[-1]\mr{Map}(\CC^4, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Generalized Chern--Simons Theory& \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC^3 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Generalized Chern--Simons Theory& \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC^2 \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Generalized Chern-Simons Theory} & \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Generalized Chern--Simons Theory} & \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC \times \RR^4_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern--Simons Theory} & \multirow{2}*{5 (topological)} \\
  &&& $\map(\RR^5_{\mr{dR}}, B\fg)$ & \\ \cline{3-5}
@@
  \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}
+ \caption{Twists of Maximally Supersymmetric Pure Yang--Mills Theories with Lie algebra $\fg$ (16 supercharges).}
  \label{table_of_twists_16}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
+ \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
  \label{table_of_twists_4}
@@
  \end{tabular}
- \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
+ \caption{Twists of Supersymmetric Yang--Mills Theories in two dimensions with gauge group $G$.
 When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
@@
 The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}).
-We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
+We use this formalism to prove in Section \ref{sect:SYM} that super Yang--Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
 We introduce the idea of dimensional reduction (Section \ref{dim_red_section}) for classical field theories to show that supersymmetry action are well-defined in lower dimensions.
 
-In Part \ref{classification_part} of the paper, we produce the classification of supersymmetric Yang-Mills theories in dimensions 2 to 10 systematically.
+In Part \ref{classification_part} of the paper, we produce the classification of supersymmetric Yang--Mills theories in dimensions 2 to 10 systematically.
 We start with dimension 10 and work down by dimensional reduction.
@@
 \subsection{Conventions}
-Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
+Throughout the paper we will frequently study objects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
@@
 \[\oloc(\cM) := \oloc(\cL[1]).\]
-The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg diffrential on $\oloc(\cM)$.
+The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg differential on $\oloc(\cM)$.
 
@@
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ that satisfy the antisymmetry property
+parameterizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ that satisfy the antisymmetry property
 \[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
@@
 \subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
-The next class of examples of classical BV theories will be generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not generally of cotangent type.
+The next class of examples of classical BV theories will be generalizations of Chern--Simons theory.
+Unlike the example of the generalized BF theory, these theories are not generally of cotangent type.
 
@@
 \begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
 \[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.
+More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern--Simons theory.
 This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.
@@
 \[p_{\rm dR} \colon X \times Y \times (M' \times \RR) \to X \times Y \times M' .\]
-In this case, we will only need to know the dimensional reduction of generalized Chern-Simons theory.
+In this case, we will only need to know the dimensional reduction of generalized Chern--Simons theory.
 
@@
 So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
-We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sect:SYM} below.
+We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang--Mills theories in Section \ref{sect:SYM} below.
 
@@
 \label{def:sym}
-The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
+The BRST theory for classical supersymmetric Yang--Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
 \[
@@
 
-The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
+The BV theory of supersymmetric Yang--Mills is the BV theory associated to this BRST theory. 
 By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
@@
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
-Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
+Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the corresponding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
 We make the following additional assumption.
@@
 It is important here that we are working in the complexified setting.
-While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges.
+While it makes sense to study a real form of 10d supersymmetric Yang--Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges.
 Indeed, a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
-So necessarily, twists of maximal super Yang-Mills theory cannot be compatible with any unitary structure.
+So necessarily, twists of maximal super Yang--Mills theory cannot be compatible with any unitary structure.
 \end{remark}
@@
 We are going to prove that it is perturbatively trivial.
-In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and decribe the corresponding family of twisted theories.
+In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and describe the corresponding family of twisted theories.
 
@@
 \begin{theorem} \label{thm:4d_11_twist}
-The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
+The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang--Mills theory is perturbatively equivalent to the generalized Chern--Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
 Moreover, this equivalence is $\U(1) \times \Spin(2, \RR)$-equivariant.
@@
  \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
- Since $S_+$, $S_-$ and $W$ all carry volume forms, the space of such square-zero supercharges is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, the space of such square-zero supercharges is parameterized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
 These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
@@
 Comparing these volume forms under the above exact sequence gives an invariant $s\in\CC^\times$ of a rank $(2, 2)$ square-zero supercharge.
-Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parametrized by this invariant.
+Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parameterized by this invariant.
 
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section}, to representations of the group $\spin(2;\CC)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang--Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section}, to representations of the group $\spin(2;\CC)$.
 In any case, the fields we obtain are
@@
 The calculation of the twists here is similar to what we saw in 4d $\mc N=2$ supersymmetry.  
-The holomorphic twist and the B-twist arise by a dimensional reduction from twists of the 3d $\cN=2$ supersymmetric Yang-Mills theory.
+The holomorphic twist and the B-twist arise by a dimensional reduction from twists of the 3d $\cN=2$ supersymmetric Yang--Mills theory.
 On the contrary, the A-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The holomorphic twist of the 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$.
+The holomorphic twist of the 2d $\cN=(2,2)$ super Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
@@
 A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
-There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  
+There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are collinear, or they are distinct.  
 These are the B- and A-supercharges respectively.
@@
 Indeed, the 3d $B$-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  
-Therefore the two vectors in $W_+^6$ discussed above must be colinear.
+Therefore the two vectors in $W_+^6$ discussed above must be collinear.
 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 
-We turn to the $\cN=(2,0)$ supersymmetric Yang-Mills theory.
+We turn to the $\cN=(2,0)$ supersymmetric Yang--Mills theory.
 In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(2,0)$ super Yang--Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 
-We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
+We consider pure $\cN=(\cN_+,0)$ super Yang--Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
 The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary space equipped with a nondegenerate symmetric bilinear pairing.
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang--Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.

### 2020-02-23 paper.tex
References

@@
 This twist was first studied by Baulieu \cite{Baulieu}.
-As is well-known \cite{GSanomaly}, the theory has a one-loop anomaly and does not admit a quantization.
+As is well-known \cite{GSanomaly,CostelloLiAnomaly}, the theory has a one-loop anomaly and does not admit a quantization.
 \end{itemize}
@@
 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
-This twist is also calculated in a forthcoming work of Dylan Butson \cite{Butson}.
+This twist is studied in \cite{CostelloYagi,Butson}.
  \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
  \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of the 4d $\cN=1$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
-This twist was studied by Johansen \cite{Johansen}.
+This twist was studied by Johansen \cite{Johansen} (see also \cite{BaulieuTanzini,CostelloSUSY}).
  \item \emph{$\cN=2$ and $\cN=4$ holomorphic twist.} We may also consider holomorphic twists of 4d $\cN=2$ and 4d $\cN=4$ super Yang--Mills theories.
@@
 It is equivalent to the cotangent theory of the theory of maps from $C\times L$ to $R/G$ which are holomorphic along $C$ and locally-constant along $L$.
+This twist was studied in \cite{ACMV}.
  \item \emph{$\cN=4$ and $\cN=8$ minimal twist.} We may also consider the minimal twist of $\cN=4$ and $\cN=8$ super Yang--Mills theories.

### 2020-02-24 paper.tex
compile, and an added remark

@@
 Before these tables, we will give a short description of each twisted theory in a more physical language, with references to where in the literature it was previously considered.
+
+\begin{remarknonum}
+Let us briefly discuss a twisting construction that our classification will not include.
+Given a supercharge $Q$ whose square is not zero, but instead generates an $S^1$-action on spacetime, one can construct a $Q$-twisted theory on the locus of $S^1$-fixed points.
+This is Nekrasov's $\Omega$-background construction \cite{Nekrasovthesis,NekrasovSW}, see also the discussion in \cite{CostelloOmega}.
+In \cite{Nekrasovthesis}, 3d and 5d topological Chern--Simons theories, as well as a 4d mixed holomorphic-topological Chern--Simons theory are discussed as arriving in this context.
+In \cite{CostelloOmega} the 5-dimensional theory, and a non-commutative version thereof, is shown to arise from this construction.
+\end{remarknonum}
 

### 2020-02-24 paper.tex
Added Kevin to acknowledgments

@@
 \subsection*{Acknowledgements}
-We would like to thank Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.  
+We would like to thank Kevin Costello, Owen Gwilliam, Justin Hilburn and Philsang Yoo for helpful discussions during the preparation of this paper.  
 We are also grateful to Dylan Butson for kind discussion of his related forthcoming work, specifically in reference to supersymmetric theories in dimension $6$.  

### 2020-02-24 arxiv - Feb 2020/taxonomy_arxivFeb20.tex
reorganize

--- 2020-02-24 paper.tex
@@
 \title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory}
-\author{Chris Elliott\and Pavel Safronov \and Brian Williams}
+\author{Chris Elliott\and Pavel Safronov \and Brian R. Williams}
 
@@
 The research of P.S. was supported by the NCCR SwissMAP grant of the Swiss National Science Foundation.
-The research of B.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
+The research of B.R.W. was supported by Northeastern University and National Science Foundation Award DMS-1645877.
 
@@
 where $S^{(1)} = S^{(1)}_{\rm gauge}, S^{(2)} = S^{(2)}_{\rm gauge}$ are the functionals from Section \ref{sect:gaugemultipletSUSY} encoding the infinitesimal actions by supersymmetry.
-Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1, sQ_2)$ is proportional to $\tilde{\chi}^*$.
+Here the middle three terms in the parentheses are the $t$-dependent terms in Proposition \ref{4d_donaldson_susy_prop} and $S^{(2)}(tQ_1 + sQ_2)$ is proportional to $\tilde{\chi}^*$.
 

### 2020-02-24 old stuff/10d_section_draft.tex
reorganize

--- 2019-07-18 10d_section_draft.tex
@@
 \[\phi \mapsto i^*(Q(p^*(\phi))).\]
-Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}.
+Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}: there is a canonical map defined on an open set $U \sub \RR^m$ by
+\[\sym^k \mc E^\vee(U\times (\RR^m)^\perp) \to \sym^k p^*i^*\mc E^\vee(U\times (\RR^m)^\perp) \iso \sym^k i^*\mc E(U).\]
 \end{definition}

### 2020-02-24 old stuff/10d_twist_lemmas.tex
reorganize

--- 2020-01-30 10draft.tex
@@
 \input ./combined_macros.sty
-\def\hCS{\mathrm{hCS}}
 
@@
 
-\section{Background Structure}
-\chris{This section consists of material common to our twisting calculations, to be edited and perhaps inserted before the 10d section}
+\section{Structure of the 10d Twist Argument}
 
-\chris{As you pointed out, these lemmas should go with other discussion of functional analysis issues.}
-\begin{lemma}[Free to Interacting Spectral Sequence] \label{free_int_ss_lemma}
-Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
-There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
-\end{lemma}
+Based on our conversation in Edinburgh I think we had an outline like this in mind.
 
-\begin{lemma} \label{invert_quis_lemma}
-Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
-\end{lemma}
+\begin{enumerate}
+\item There is a map of abelian theories.
+\item Lemma: linear upper triangular change of coordinates is a symplectic equivalence (should take care: shearing is not symplectic, if you alter $\chi^\vee$ you must also alter $\chi$ itself dually).
+\item Lemma: If $A$ is contractible, an inclusion $B \to (A \to B)$ is an equivalence.  Likewise a projection $(B \to A) \to B$ is an equivalence.
+\item Lemma: All equivalences are invertible (by a suitable change of variables).
+\item Lemma: The composite of an inclusion and the inverse of a projection, or the opposite, where $A_1 + A_2$ is a symplectic subspace of the fields, is a symplectic map.
+\item Putting these together we can build our desired symplectic equivalence.
+\item The equivalence preserves interactions (maybe this will be clear from a general lemma).
+\item Lemma: free to interacting spectral sequence, implies the desired result (needs some functional analysis).
+\end{enumerate}
 
-\subsection{Dimensional Reduction} \label{dim_red_section}
-\chris{I'm including this with the aim to not have to prove supersymmetry invariance of non-maximal theories.  It's a pretty rough draft, so apologies there}
-The idea of the \emph{dimensional reduction} of a rotation invariant classical field theory to a linear subspace of $\RR^n$ is to restrict attention to only those fields with are constant in directions perpendicular to the subspace.
-
-\begin{definition}
-Let $i\colon \RR^m \inj \RR^n$ be the inclusion of a linear subspace, and let $p \colon \RR^n \to \RR^m$ be the corresponding orthogonal projection.
-Let $(E, \omega, Q, I)$ be a rotation invariant classical field theory on $\RR^n$.
-The \emph{dimensional reduction} of the classical field theory from $\RR^n$ to $\RR^m$ is the classical field theory whose underlying bundle of fields is the pullback bundle $i^*E$, with the following structure.
-The symplectic pairing is defined as the composite
-\[(i^*\mc E \otimes i^*\mc E)(U) \iso (p^*i^*\mc E \otimes p^*i^*\mc E)(U \times (\RR^m)^\perp) \to (\mc E \otimes \mc E)(U \times (\RR^m)^\perp) \overset \omega \to \dens(U \times (\RR^m)^\perp),\]
-with the observation that the density we obtain splits canonically into a density on $U$ and a constant density on $(\RR^m)^\perp$.
-The classical differential $Q \colon i^*\mc E(U) \to i^*\mc E(U)$ is defined by
-\[\phi \mapsto i^*(Q(p^*(\phi))).\]
-Finally, the classical interaction is defined similarly: the pullback $p^*$ defines a map from $\mc O(\mc E)$ to $\mc O(i^*\mc E)$ that preserves locality \footnote{Intuitively, given a local functional on fields on $\RR^n$, restrict to a local functional on those fields constant in directions perpendicular to $\RR^m$.}.
-\end{definition}
-
-Rotation invariance guarantees that the dimensional reduction is independent of the choice of $m$-dimensional subspace of $\RR^n$.
-
-\begin{prop} \label{dim_red_SUSY_prop}
-The dimensional reduction of a supersymmetric classical field theory on $\RR^n$ with supersymmetry algebra $\mf A = (\so(n) \oplus \gg_R) \ltimes (\RR^n \oplus \Pi \Sigma)$ is a supersymmetric classical field theory on $\RR^m$ with supersymmetry algebra $\mf A' = (\so(m) \oplus \gg_R) \ltimes (\RR^m \oplus \Pi \Sigma')$, where $\Sigma'$ is the restriction of the representation $\Sigma$ of $\so(n)$ to a representation of the subalgebra $\so(m)$ of rotations of the subspace $\RR^m \sub \RR^n$.
-\end{prop}
-
-\begin{proof}
- \chris{I think this will be straightforward.}
-\end{proof}
-
-\chris{we could alternatively write this in terms of BRST fields.}
-
-\chris{By the way, I see no obstruction to proving the following.}
-\begin{lemma}
-If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
-\end{lemma}
-
-\subsection{Supersymmetric Yang-Mills Theory}
-We'll begin with a detailed description of the maximal (complexified) supersymmetric Yang-Mills theories, which exist in dimensions 3,4, 6 and 10.
-Using the methods described in Section \ref{dim_red_section}, the construction of these theory, with the supersymmetry actions, will descend to supersymmetric theories in all lower dimensions.
-
-Let us begin with a general description of supersymmetric Yang-Mills theory on $\RR^n$, with spinorial matter.
-Fix a complex semisimple Lie group $G$ with Lie algebra $\fg$, and a spinorial representation $\Sigma$ of $\so(n;\CC)$ with symmetric equivariant pairing $\Gamma \colon \Sigma \otimes \Sigma \to \CC^n$.
-The ordinary fields of super Yang-Mills theory on $\RR^{n}$ consist of:
-\begin{itemize}
-\item A connection $A \in \Omega^1(\RR^{n} ; \fg)$ on the trivial $G$-bundle;
-\item A $\gg$-valued section $\lambda \in \Omega^0(\RR^{n}) \otimes \Pi \Sigma \otimes \fg$ of the spinor bundle associated to the representation $\Sigma$
-\footnote{If we didn't complexify we would instead consider $G_\RR$ a compact connected Lie group, and a section of a real spinor bundle, whose structure is signature dependent.
-For our purposes it's interesting enough to just consider the complexified theory and avoid signature issues.}.
-\end{itemize}
-These fields are acted upon by the group of gauge transformations -- $G$-valued functions on $\RR^{n}$. 
-Hence, there is a single ghost for the theory given by a $\gg$-valued section of the trivial $G$-bundle $c \in \Omega^0(\RR^{n} ; \fg)$.
-
-We can model the stack of fields modulo gauge transformations infinitesimally near the point $0$ by the corresponding BRST complex.  This is the local super Lie algebra
-\[
-L \;\;\; = \begin{array}{ccccc}
-& \ul{0} & & \ul{1} & \\ 
-& & & & \\
-& \Omega^0(\RR^{n}; \gg) & \to & \Omega^1(\RR^{n}; \gg) \oplus \Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) & 
-\end{array}
-\]
-with the de Rham differential, placed in cohomological degrees 0 and 1, with bracket induced from the Lie bracket on $\gg$.
-
-The action functional in 10d super Yang-Mills is given by
-\[S(A,\lambda) = \int_{\RR^{n}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
-where $\langle - \rangle_\fg$ denotes an invariant pairing on $\gg$, and where the latter term is obtained using the vector-valued pairing $\Gamma$ on $\Sigma$ to obtain a Dirac operator $\sd D_A \colon \Sigma \to \Sigma^*$.
-\chris{Brian suggested defining this notation in the section on supersymmety more broadly.
-I agree.}
-
-We can re-encode this data in terms of the classical BV complex (see also \cite[Section 3.1]{ElliottYoo1}).  
-This is the local $L_\infty$-algebra $\fL$ on $\RR^{n}$ whose underlying cochain complex takes the form
-\[
-\xymatrix{
-& & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
-\fL & = & \Omega^0(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^1(\RR^{n}; \gg) \ar[r]^{\d \ast \d} &\Omega^{n-1}(\RR^{n}; \gg) \ar[r]^{\d} &\Omega^{n}(\RR^{n}; \gg) \\
-& & &\Omega^0(\RR^{n}; \Pi \Sigma \otimes \gg) \ar[r]^{\ast \sd \d} &\Omega^{n}(\RR^{n}; \Pi \Sigma^* \otimes \gg), &
-}\]
-with degree $(-3)$ invariant pairing $\<-,-\>$ induced by the invariant pairing on $\gg$ and the evaluation pairing $(-,-)$ between $\Sigma$ and $\Sigma^*$, and with degree 2 and 3 brackets given by the action of $\Omega^0(\RR^{n}; \gg)$ on everything along with
-\begin{align*}
-\ell_2^{\mr{Bos}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
-(A \otimes B) &\mapsto [A \wedge \ast \mr d B] + [\ast \mr d  A \wedge B] + \mathrm{d} \ast[A \wedge B] \\
-\ell_2^{\mr{Fer}} \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^0(\RR^{n}; \Sigma \otimes \gg) &\to \Omega^{n}(\RR^{10}; \Sigma* \otimes \gg) \\
-(A \otimes \lambda) &\mapsto \ast \sd A \lambda
-\end{align*}
-in degree 2, and the map
-\begin{align*}
-\ell_3 \colon \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) \otimes \Omega^1(\RR^{n};\gg) &\to \Omega^{n-1}(\RR^{n};\gg) \\
-(A \otimes B \otimes C) &\mapsto [A \wedge \ast[B \wedge C]] + [B \wedge \ast[C \wedge A]] + [C \wedge \ast[A \wedge B]]
-\end{align*}
-in degree 3.
-
-We obtain the BV action by the formula
-\[
-S_{BV} (\alpha) = \frac{1}{2} \<\alpha , Q_{BV} \alpha\> + \sum_{n \geq 2} \frac{1}{n!} \<\alpha, \ell_n(\alpha,\ldots, \alpha)\> 
-\]
-where $\alpha$ is a general BV field and $Q_{BV}$ is the linear BV differential. 
-The statement that $S_{BV}$ is gauge invariant is encoded by the fact that it satisfies that classical master equation $\{S_{BV}, S_{BV}\} = 0$, which is equivalent to the statement that $S_{BV}$ determines a Mauer-Cartan element in the dg Lie algebra $\cloc^\bu(\fL)[-1]$.
-
-\subsubsection{Supersymmetry Actions} \label{SUSY_action_section}
-For minimal choices of the spinorial representation, Yang-Mills theory admits an action of the supersymmetry algebra when $n=3,4,6$ or 10, so $\Sigma$ is the 2-dimensional Dirac representation $S$, the 4-dimensional Dirac representation $S_+ \oplus S_-$, the 8-dimensional symplectic Weyl representation $S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, and the 16-dimensional Weyl representation $S_+$ respectively.
-We will now proceed to construct this supersymmetry algebra action.
-\chris{can we do it all in one go, using the fact that the 3 $\psi$ rule \cite[Theorem 11]{BaezHuerta} works exactly in these dimensions?
-If not we can just write the calculation out four times.
-We've already started to write it in the 10-dimensional case, though it's incomplete.
-How would you suggest proceeding?}
-
-\subsection{Standard Equivalences Between Classical Field Theories}
-In this section, we will collect some standard lemmas that we'll use to simplify the descriptions of twisted supersymmetric field theories below.
+So including point 7 (which needs formulating more precisely), that's 6 lemmas to state and prove.
+Cochain complexes here will be complexes of differentiable vector spaces, so we'll have to think about functional analysis.
 
@@
 \end{lemma}
+
+We'll use this where $F$ is the transformation $\chi^\vee \mapsto \chi^\vee + \Lambda F_{1,1}$, although in order to get a symplectomorphism $\chi$ will also have to transform.
+The result of this procedure will be that $\chi$ and $\chi^\vee$ form a contractible doublet only admitting maps in to the rest of the classical BV complex, and we can then integrate them out using the following lemma.
 
@@
 \end{enumerate}
+\end{lemma}
+
+\begin{lemma}
+Any quasi-isomorphism of cochain complexes admits a quasi-inverse.
 \end{lemma}
@@
 
-\begin{lemma} \label{interaction_pullback_lemma}
+Now, altogether this gives us an equivalence of free BV theories between holomorphic Chern-Simons and twisted 10d super Yang-Mills.
+To conclude we should deal with the interaction functionals.
+It's enough to check that the quasi-isomorphism we've constructed is compatible with interaction functionals using the following lemma.
+Note that I've phrased this in terms of classical observables (i.e.
+local functionals) because as I said in my e-mail I'm unsure whether the differential coming from $\{I,-\}$ on the full algebra of functionals on fields is well-defined (but if I'm wrong about this being a problem we can amend the statement).
+
+\begin{lemma}[Free to Interacting Spectral Sequence]
+Let $(\mc E^\bullet, Q, \omega, I)$ be a classical field theory with polynomial interaction.
+There is a convergent spectral sequence whose $E_1$ page is the complex of classical observables of the underlying free theory, and whose $E_\infty$ page is equivalent to the complex of classical observables of the interacting theory.
+\end{lemma}
+
+So, finally, we need a statement capturing the compatibility of the interaction functionals of our two theories.
+Assuming we can deal with the change of coordinates from Lemma \ref{symplectomorphism_lemma} explicitly, it would suffice to prove the following.
+\begin{lemma} 
 In the set-up of Lemma \ref{symplectic_composite_lemma}, suppose we're given an interaction $I$ on the graded vector space $\mc E^\bullet \oplus \mc C_1^\bullet \oplus C_2^\bullet$, which pulls back to $I'$ under the inclusion of $\mc E^\bullet$.
@@
 
-\section{Twists}
-\subsection{Dimension 10}
-We'll begin by studying the twist of 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory, with the supersymmetry action we analyzed in Section \ref{SUSY_action_section}.
-In the 10d $\mc N=(1,0)$ supersymmetry algebra there is a unique $\Spin(10)$ orbit of non-trivial square-zero supercharges given by the locus of pure spinors.
-These square-zero supercharges are holomorphic.
-
-Fix a non-trivial pure spinor $Q$, or equivalently, fix a Calabi-Yau structure on $\RR^{10}$.
-The stabilizer of $Q$ in $\Spin(10)$ is isomorphic to $\SU(5)$.
-Let us first, therefore, decompose the component fields of 10d super Yang-Mills theory into sections of the associated bundles to irreducible representations of $\SU(5)$.
-The BRST fields split as follows:
-\begin{align*}
-c &\mapsto c \in \Omega^0(\CC^5; \gg) \\
-A &\mapsto A_{0, 1} + A_{1, 0} \in \Omega^{0,1}(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg)\\
-\lambda &\mapsto \chi + \psi + B \in \Omega^0(\CC^5; \gg) \oplus \Omega^{1,0}(\CC^5; \gg) \oplus \Omega^{0,2}(\CC^5; \gg). 
-\end{align*}
-
-In terms of these component fields, the BV action functional can be written in the following way.  We'll split the action functional up into the BRST action and the antifield action.
-\begin{align*}
-S_{\mr{BRST}} &= \int \d^5z \left(\Lambda^2 \langle F_{0,2} \wedge F_{2,0}\rangle + \frac 12 |\Lambda F_{1,1}|^2 + \Lambda( \chi \wedge (\ol \dd_{A_{0,1}} \psi))  + \Lambda^2(B \wedge (\dd_{A_{1,0}} \psi))\right) \Omega + (B \wedge \ol \dd_{A_{0,1}} B) \\
-S_{\mr{anti}} &= \int \d^5z \langle \dd_{A_{1,0}}c, A_{1,0}^\vee \rangle +  \langle \ol \dd_{A_{0,1}}c, A_{0,1}^\vee \rangle + \langle [c,c], c^\vee \rangle + \langle [\chi,c], \chi^\vee \rangle + \langle [\psi,c], \psi^\vee \rangle + \langle [B,c], B^\vee \rangle,
-\end{align*}
-where $F_{i,j}$ is the $(i,j)$-form component of the curvature of the gauge field $A_{0, 1} + A_{1, 0}$, and $\Omega$ is the Calabi-Yau $(0,5)$-form.
-Similarly, we can write explicitly the $L_\infty$ interaction functional associated to the action of the square 0 supercharge $Q$.
-It has a quadratic and a cubic component given by
-\begin{align*}
-I^{(1)} &= \int \langle A_{1,0}^\vee, \psi \rangle + \langle \chi^\vee \Lambda F_{1,1} \rangle + \langle B^\vee, F_{0,2} \rangle \\
-I^{(2)} &= \frac 12 \int \d^5z \Omega |\chi^\vee|^2.
-\end{align*}
-The twisted action functional is obtained by adding these terms to the original BV action functional.
-
-We can now calculate the 10d holomorphic twist.  This calculation is originally due to Baulieu \cite{Baulieu}.
-
-\begin{theorem}
-The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
-\end{theorem}
-
-\begin{remark}
-This twisted theory is only $\ZZ/2\ZZ$-graded, because the R-symmetry group is trivial, so there is no possible R-charge with which to regrade the twisted theory to make it $\ZZ$-graded.
-As a consequence, the twisted BV-BRST complex only has an odd symplectic pairing, not a $-1$-symplectic pairing.
-\end{remark}
-
-\begin{proof}
-We'll prove this equivalence by first describing an equivalence of the underlying classical theories, as the composite of several maps, then showing that this equivalence is compatible with the two interaction functionals, and therefore defines a morphism of classical field theories, and finally observing that by Lemma \ref{free_int_ss_lemma} this morphism is automatically an equivalence.
-
-\begin{enumerate}
- \item The first part of our equivalence of classical field theories will be a simple change of variables.
-Let $\chi'^\vee = \chi^\vee + \Lambda F_{1,1}$, and dually let $\chi' = \chi + \Lambda F_{1,1}^\vee$.
-In terms of $\chi'$, the quadratic part of the twisted action functional becomes
- \begin{align*}
-  S^Q &= \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \frac 12 |\chi'^\vee|^2 + \Lambda( \chi' \wedge (\ol \dd \psi)) - \Lambda^2(\dd A_{0,1} \wedge \ol \dd \psi) + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) \\
-  &\quad + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.
- \end{align*}
- The classical BV complex associated to the theory after performing this change of variables is quasi-isomorphic to the classical BV complex of the original theory according to Lemma \ref{symplectomorphism_lemma}.
-However, after performing the change of variables, the classical BV complex takes the form $(\Omega^0(\CC^5; \gg)_{\chi'^\vee} \overset \id \to \Pi\Omega^0(\CC^5; \gg)_{\chi'}) \to \mc E^\bullet$, where $\mc E^\bullet$ is the part of the BV complex generated by all fields other than $\chi'$ and $\chi'^\vee$, and where the map into $\mc E^\bullet$ is given by the map $\ol \dd$ from $\chi$ to $\psi^\vee$.
-Therefore the inclusion of the complex $\mc E^\bullet$ is a quasi-isomorphism by Lemma \ref{inclusion_and_projection_lemma}.
-We think of this as ``integrating out'' the field $\chi'$ and its antifield.
-
- \item We'll now use a similar trick to integrate out the fields $\psi, A_{1,0}$ and their antifields.
-We've argued in step 1 that the free part of the $Q$-twisted theory is equivalent to the theory with action functional
- \[  S^Q = \int \d^5z \left(\Lambda^2 \langle \ol \dd A_{0,1} \wedge \dd A_{1,0} \rangle + \Lambda^2(B \wedge (\dd \psi))\right) \Omega + (B \wedge \ol \dd B) + \langle \dd c, A_{1,0}^\vee \rangle +  \langle \ol \dd c, A_{0,1}^\vee \rangle + \langle A_{1,0}^\vee, \psi \rangle + \langle B^\vee, \ol \dd A_{0,1} \rangle.\]
- We'll begin, as in step 1, by performing a linear change of variables, setting $A'_{1,0} = A_{1,0} - \ol{A_{0,1}}$, and performing the dual change of variables on the antifields.
-This change of variables has the effect of eliminating the term $\langle \dd c, A_{1,0}^\vee \rangle$ from the quadratic part of the action.
-\chris{This isn't quite right I think.
-We need to kill that term, however, for the below argument to work.
-Can we fix it?}
-
- Observe that the classical BV complex associated to this action functional can now be written in the following form:
- \[\xymatrix{
- &&\Omega^{1,0}(\CC^5;\gg)_\psi \ar[dl] \ar[dr] \ar[r] &\Omega^{1,0}(\CC^5;\gg)_{{A'}_{1,0}} \ar[dr]\\
- \Omega^0(\CC^5;\gg)_c \ar[r] &\Omega^{0,1}(\CC^5;\gg)_{A_{0,1}}  \ar[dl] \ar[r] &\Omega^{0,2}(\CC^5;\gg)_{B} \ar[dl]\ar[r] &\Omega^{0,3}(\CC^5;\gg)_{B^\vee} \ar[r] &\Omega^{0,4}(\CC^5;\gg)_{A_{0,1}^\vee} \ar[dlll] \ar[r] &\Omega^{0,5}(\CC^5;\gg)_{c^\vee} \\
- \Omega^{4,0}(\CC^5;\gg)_{{A'}_{1,0}^\vee} \ar[r]   &\Omega^{4,0}(\CC^5;\gg)_{\psi^\vee},
- }\]
- where the first and third rows are dual under the symplectic pairing.
-This is exactly in the form required to apply Lemma \ref{symplectic_composite_lemma}, so applying that result tells us that the underlying free theory of the twisted 10d super Yang Mills theory is equivalent to the middle row alone, i.e.
-the Dolbeault complex, which is exactly the free part of holomorphic Chern-Simons theory on $\CC^5$.
-
- \item Now, let's understand how the interaction functional behaves under this equivalence of classical field theories.
-We'll use Lemma \ref{interaction_pullback_lemma}.
-Take our original action functional after the change of variables from step 1, and set the fields $\chi, \psi, A_{1,0}$ and their antifields to zero (i.e, in the notation of Lemma \ref{interaction_pullback_lemma}, restrict the interaction to the complex $\mc E^\bullet$).
-The resulting interaction is
- \[
-  I^Q = \int \d^5z (B \wedge [A_{0,1} \wedge B]) + \langle B^\vee, [A_{0,1} \wedge A_{0,1}] \rangle + \langle [c,c], c^\vee \rangle + \langle [A_{0,1}, c], A_{0,1}^\vee \rangle + \langle [B,c], B^\vee \rangle,
- \]
- which is, indeed, the interaction functional for holomorphic Chern-Simons theory.
-The composite of the morphisms in steps 1 and 2 therefore defines a morphism of classical field theories from holomorphic Chern-Simons theory to twisted 10d super Yang-Mills theory.
-
- \item To conclude the proof, we only need to apply Lemma \ref{free_int_ss_lemma}.
-The morphism of classical field theories that we've constructed induces an equivalence of the $E_1$ pages of the free-to-interacting spectral sequences associated to holomorphically twisted 10d super Yang-Mills theory and holomorphic Chern-Simons theory.
-Because the spectral sequences are convergent, there is likewise an equivalence of the $E_\infty$ pages, i.e.
-an equivalence of classical field theories.
-\end{enumerate}
-\end{proof}
-
-The above argument can be applied identically on a general Calabi-Yau 5-fold $X$.
-
-\pagestyle{bib}
-\printbibliography
+If $\mc C_2^\bullet = 0$ so we're just considering inclusions, I think this is clear.
+For the other part, the idea here is that projection maps as in Lemma \ref{inclusion_and_projection_lemma} (2) will clearly be compatible with an interaction and its restriction to $\mc E^\bullet$, i.e.
+the pullback of the interaction on $\mc E^\bullet$ is just the interaction on $\mc E^\bullet \oplus \mc C_1^\bullet \oplus \mc C_2^\bullet$ with all fields in $\mc C_2^\bullet$ set to zero, but if the two summands of $\mc C_1^\bullet \oplus \mc C_2^\bullet$ are Lagrangian then that kills all the $\mc C_1^\bullet$ fields too, because they only appear paired together.
+Of course that's pretty vague and I haven't tried to write that idea down more precisely, so it might turn out to be nonsense under a bit more thought.
 

### 2020-02-24 old stuff/4dsusy.tex
reorganize

--- 2019-11-12 4dsusy.tex
@@
 \label{lem: oneform}
-Let $\alpha$ be any $1$-form on $V$, $\psi \in C^\infty(V, \Sigma)$,  and $Q \in \Sigma$. 
+Let $v \in V$, $\psi \in C^\infty(V, \Sigma)$, and $Q \in \Sigma$. 
 Then
 \[
-\d (Q, \psi) \wedge * \alpha = * (\rho(\alpha)Q, \sd \dd \psi) .
+(v, \d (Q, \psi))_V = (\rho(v)Q, \sd \dd \psi)_{\Sigma} .
 \]
@@
 
+\begin{lem}
+\label{lem: silly}
+For $Q_1,Q_2 \in \Sigma$ and $\psi_+ \in S_+$ we have
+\[
+\rho(\d(Q_1, \psi_+)) Q_2 = \rho(\Gamma(Q_1, \sd \dd \psi_+))Q_2
+\]
+\end{lem}
+
+\brian{I'd also  like the following  to be true.
+\begin{prop}
+Suppose $Q_+ \in S_+$, $Q_-\in S_-$, and $\psi_+ \in C^\infty(V , S_+)$. 
+Then
+\[
+\sd \dd (\rho(\Gamma(Q_+, Q_-)) \psi_+) = \rho(\d(Q_+, \psi_+)) Q_- + (Q_-, \sd \dd \psi_+)Q_+ .
+\]
+\end{prop}
+}
+
 \subsubsection{The chiral multiplet}
@@
 I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
-I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
+I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)_R) - ((Q_1, \psi_+^*),(Q_2, \psi_-^*))_R - ((Q_2, \psi_+^*),(Q_1, \psi_-^*))_R
 \end{align*}
 for $Q, Q_1, Q_2 \in S_+ \oplus S_-$
+A word on the notation used in the definition of $I^{(2)}$. 
+The $V$-valued pairing $\Gamma(\psi_+^*, \psi_-^*)_R$ denotes the image of $\psi_+^* \otimes \psi_-^*$ under the composition
+\[
+(S_+ \otimes R^*) \otimes (S_- \otimes R) \cong (S_+ \otimes S_-) \otimes (R^* \otimes R) \xto{\Gamma \otimes (-,-)_R} V .
+\]
+Additionally, we view $(Q_1, \psi_+^*)$ as a scalar valued in $R^*$ and $(Q_2, \psi_-^*)$ as a scalar valued in $R$. 
+The pairing $((Q_1, \psi_+^*),(Q_2, \psi_-^*))_R$ is the obvious one between $R$ and $R^*$.
 
@@
 \begin{align*}
-- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) 
+- \left\{(\d \phi, \d \Bar{\phi}) \; , \; I^{(1)} \right\}  (Q) & = (\d (Q, \psi_+), \d \Bar{\phi}) + (\d \phi, \d (Q_-, \psi_-))
 %\\
@@
 \begin{align*}
-\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
+\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & =( \d \phi , \Gamma(\sd \dd \psi_-, Q)) - (\d \Bar{\phi} , \Gamma(\sd \dd \psi_+, Q))
 \end{align*}
@@
 \begin{align*}
-\{S, I^{(2)}(Q_1,Q_2)\} = & 
+\{S, I^{(2)}(Q_1,Q_2)\} = \left\{(\psi_+ , \sd \dd \psi_-), I^{(2)} \right\} = & \Gamma(Q_1,Q_2) \Gamma(\psi_+^*, \sd \dd \psi_+) - (Q_1 , \psi_+^*)(Q_2, \sd \dd \psi_+) - (Q_2, \psi_+^*)(Q_1, \sd\dd \psi_+)  \\
+ + & \Gamma(Q_1, Q_2) \Gamma(\psi_-^*, \sd \dd \psi_-) - (Q_1 , \psi_-^*)(Q_2, \sd \dd \psi_-) - (Q_2, \psi_-^*)(Q_1, \sd\dd \psi_-) \\
+ = & (\psi_+^*, \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+) - (Q_1 , \psi_+^*)(Q_2, \sd \dd \psi_+) - (Q_2, \psi_+^*)(Q_1, \sd\dd \psi_+) \\ 
+ + & (\psi_-^*, \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_-) - (Q_1 , \psi_-^*)(Q_2, \sd \dd \psi_-) - (Q_2, \psi_-^*)(Q_1, \sd\dd \psi_-) .
 \end{align*}
@@
 \]
-By Proposition \ref{??}
+By the Clifford identity
 \brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term. 
@@
 \end{align*}
+By Lemma \ref{lem: silly} the first, second terms, and fourth terms are equal to 
+\[
+-\frac{1}{2}   \rho(\Gamma(Q_1, \sd \dd \psi_+))Q_2 - \frac{1}{2}   \rho(\Gamma(Q_2, \sd \dd \psi_+))Q_1 + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+
+\]
+This is zero by Proposition \brian{3-psi}.
 
+The remaining terms are
+\[
+- \Gamma(Q_1,Q_2) . \psi_+ + \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 + \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2 .
+\]
 \end{proof}
@@
 \end{proof}
+1405.99
+
+387.00
+318.99
 

### 2020-02-24 old stuff/6d_twist_notes_14_11_18.tex
reorganize

\documentclass[10pt, oneside]{article}
\input math_headers.sty

\title{6d Notes}
\author{Chris Elliott}
\date{\today}

\begin{document}

\section{Notes on the Holomorphic twist of pure $\mc N=(1,0)$ 6d gauge theory}

The fields in the 6d $\mc N=(1,0)$ theory can be written as follows, after breaking the Lorentz symmetry from $\SO(6)$ to $\SU(3)$.  Decompose the gauge field into $A + A'$: holomorphic + antiholomorphic.
Decompose the spinor into $\phi + \psi$, where $\phi$ is a $W$-valued scalar and $\psi$ is a $W$-valued $(0,2)$-form (maybe the same as a $(1,0)$-form?).  Here $W$ is a 2-dimensional symplectic vector space.
Auxiliary scalar field $h$, and a ghost $c$.

Guess the supersymmetries are as follows, where we write $Q$ for the operator on linear functionals (so really $\delta / \delta Q$).
\begin{align*}
QA &= \psi_-\\
QA'&= 0\\
Q\phi_+ &= h\\
Q\phi_- &= 0\\
Q\psi_+ &= \ol \dd_{A'} A'\\
Q\psi_- &= 0\\
Qh &= 0\\
Qc &= 0.
\end{align*}

Here $\pm$ denotes a basis for $W$, which we also take to be the R-symmetry weight for a chosen $\mr U(1)$.

The space of fields becomes cohomologous to $\Omega^0[1] \to \Omega^{0,1} \to \Omega^{0,2}[-1] \oplus \Omega^{3,0}[1]$.  Take this as the base of a twisted cotangent bundle defining the theory $T^*[-1]\bun_G(X)$.  The (usual, BRST) action functional is then $\phi_- \ol \del_{A'} \psi_+$ in this language.  It remains to show that the difference between the action functional for the full $\mc N=(1,0)$ theory and this functional is totally $Q$-exact.  Of course, terms involving $\psi_-$, $h$ or $\ol \dd A' = F^{0,2}$ are $Q$-exact.  There's a potentially problematic term involving the $A$'s, $\phi_+$ and $\phi_-$ which I hope vanishes for the following reason: terms in the action functional should be $\SU(3)$-invariant, and there seems to be no invariant such expression involving two scalars and a vector quantity like $\dd + A$.

The $\mc N=(1,0)$ hypermultiplet consists of a spinor (of the opposite helicity to the spinor in the vector multiplet) and four (real?) scalars.  The spinor splits up as $\phi' + \psi'$ where $\phi'$ is a $W$-valued scalar and $\psi'$ is a $W$-valued $(2,0)$-form (maybe the same as a $(0,1)$-form?).  The scalars $\chi_1, \ldots, \chi_4$ remain scalars (could they live in $W^{\otimes 2}$?).  Everything also takes values in a representation of $\gg$ which we'll suppress in the notation.  We want to be left with the same space of fields as we had for the vector multiplet, but shifted in degrees.  For instance, could have a $\chi_{+-} \to \psi'_+$ as the base and a $\chi_{--} \to \psi'_-$ as the fiber.  Then we'd need the $\chi_{-+}$ and $\chi_{++}$ to receive maps from $\phi'_-$ and $\phi'_+$ respectively.  That is
\begin{align*}
Q\phi'_+ &= 0 \\
Q\phi'_- &= 0 \\
Q\psi'_+ &= \ol \dd_{A'} \chi_{+-}\\
Q\psi'_- &= \ol \dd_{A'} \chi_{--}\\
Q\chi_{++} &= \phi'_+\\
Q\chi_{+-} &= 0\\
Q\chi_{-+} &= 0 \\
Q\chi_{--} &= \phi'_-.
\end{align*}
It's pretty easy to believe that the action functional will work out here -- the main thing to check is that the R-charges of the $\chi$ fields are correct in the multiplet!

\end{document}

### 2020-02-24 old stuff/Old_YM_section.tex
reorganize

\subsubsection{Yang--Mills Theory with Spinorial Matter} \label{YM_section}

Let us now give an example of a theory which is not partially holomorphic. We will give a general description of the Yang--Mills theory on a vector space $V_\RR = \RR^n$ with adjoint spinorial matter. Denote by $V=V_\RR\otimes_\RR \CC$ its complexification.

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$. We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}
for any $Q_1, Q_2\in\Sigma$ and $v\in V$.

The fields of Yang--Mills theory are as follows:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

\item A section $\lambda \in \Omega^0(V_\RR; \Pi \Sigma \otimes \fg)$.

\item The ghost field $c\in\Omega^0(V_\RR; \fg)[1]$.
\end{itemize}

Thus, the bundle of BRST fields is
\[F = (\Omega^1(V_\RR)\oplus \Omega^0(V_\RR; \Pi\Sigma)\oplus \Omega^0(V_\RR)[1])\otimes \fg.\]
The corresponding local super dg Lie algebra $L=F[-1]$ is
\[
L \;\;\; = \begin{array}{ccccc}
& \ul{0} & & \ul{1} & \\ 
& & & & \\
& \Omega^0(V_\RR; \gg) & \to & \Omega^1(V_\RR; \gg) \oplus \Omega^0(V_\RR; \Pi \Sigma \otimes \gg) & 
\end{array}
\]
whose differential is the de Rham differential $\Omega^0(V_\RR; \gg)\rightarrow \Omega^1(V_\RR; \gg)$ and the bracket is induced from the Lie bracket on $\gg$.

Denote by $F_A = \d_{\dR} A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd D_A \colon \Sigma \to \Sigma^*$ be the Dirac operator obtained from $\Gamma$ (see Section \ref{sec: susy}).

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]

We conclude this section with a discussion of the Poincar\'e invariance of classical Yang--Mills theory.

\begin{definition}
The {\bf Poincar\'e group} is $\mr{ISO}(V_\RR) = \Spin(V_\RR) \ltimes \RR^n$. The {\bf Poincar\'e algebra} is its complexified Lie algebra $\mf{iso}(V)$.
\end{definition}

The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$. Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$. The corresponding Hamiltonian is given by
\begin{equation}
I^{(1)}(v) = \int_{V_\RR} -(L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*,
\label{eq:Poincareaction}
\end{equation}
for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.

### 2020-02-24 old stuff/anomaly.tex
reorganize

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\addbibresource{Twist.bib}

\title{Twists of supersymmetric gauge theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\section{One-loop anomalies}

\subsection{Holomorphic Chern-Simons}

\begin{prop}
Let $X$ be any flat Calabi-Yau manifold of odd complex dimension $d$. 
The one-loop anomaly to quantizing holomorphic Chern-Simons theory with values in $\fg$ on $X$ is proportional to the local cocycle
\[
\int_X {\rm Tr}_{\rm ad} (\alpha \underbrace{\partial \alpha \cdots \partial \alpha}_{d}) \in \cloc^\bu \left(\sE_{\rm hCS}\right) .
\] 
where the trace is taken in the adjoint representation of $\fg$. 
\end{prop}

\begin{rmk}
If we expand $\alpha$ in components as $\alpha = c + A^{0,1} + \sum_{i \geq 2} A^{0,i}$ where $c \in C^\infty(X) \otimes \fg$ and $A^{0,i} \in \Omega^{0,i}(X) \otimes \fg$, then up to some nonzero factor we can write the anomaly cocycle as 
\[
\int_X {\rm Tr}_{\rm ad} (c \partial A^{0,1} \cdots \partial A^{0,1}) = \int {\rm Tr}_{\rm ad} \left(c (F_{A^{0,1}})^d \right) .
\]
\end{rmk}

\end{document}

### 2020-02-24 old stuff/chrisnotes.tex
reorganize

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\U}{\mathrm{U}}

\newcommand{\ham}{/\!\!/}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning, matrix}

\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{A Catalogue of Twists of Supersymmetric Gauge Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.  Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory. 
\end{abstract}

\tableofcontents

We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.  In these terms we can describe the BRST fields.

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
It will be enough for our purposes to describe only the action of a chiral supercharge.
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
\end{prop}

\vspace{-10pt}
\paragraph{Twisting data:}
There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
\begin{itemize}
 \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
 \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
 \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
\end{itemize}

We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.

\begin{theorem} \label{4d_2_holo_twist_thm}
The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
\end{theorem}

\begin{proof}
To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
\end{proof}

We'll first consider the deformation of the holomorphic twist to the topological twist corresponding to a rank $(2,0)$ supercharge.

\begin{theorem} \label{4d_Donaldson_twist_thm}
The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.  
\end{theorem}

\begin{proof}
Suppose the family of generically rank $(2,0)$ supercharge splits as a sum of two rank 1 supercharges as $Q_{\mr{hol}} + tQ$, where $t \in \CC$.  It is enough to understand the deformation of the holomorphically twisted action functional, which we wrote down in the proof of Theorem \ref{4d_minimal_twist_thm}, by $I^{(1)}(tQ) + I^{(2)}(tQ,tQ)$ using Proposition \ref{4d_2_susy_action_prop}.

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.  Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.  The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
\end{proof}

We now address the rank $(1,1)$ twist.  This is more straightforward: we can understand it by dimensional reduction from the 5d holomorphic twist, this time in a non-invariant direction.

\begin{theorem} \label{4d_11_twist_thm}
The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
We start with the 5d $\mc N=1$ holomorphic twist, as in Theorem \ref{5d_holo_twist_theorem}, and dimensionally reduce in one of the two non-invariant directions.  That is, we apply Proposition \ref{CS_diml_red_prop}.
\end{proof}

\end{document}

### 2020-02-24 old stuff/matter.tex
reorganize

--- 2019-12-10 matter.tex
@@
 
+\brian{Not sure if this is the correct formulation. The matter and fermions are treated differently in a theory of matter.}
+
 \begin{prop}
@@
 \item[(1)] Dimension $n = 4$.
-Suppose $Q_+ \oplus Q_- \in S_+ \oplus S_-$.
+Suppose $Q_+ + Q_- \in S_+ \oplus S_-$.
 Then, the following diagram commutes
@@
 \xymatrix{
-S_+ \otimes S_- \ar[dr]_-{(Q_+ + Q_-,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
+S_+ \otimes S_- \ar[dr]_-{(Q_+ + Q_-,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(-)(Q_+ + Q_-)} \\
 & S_+ \oplus S_- &  
@@
 \xymatrix{
-\wedge^2 S_\pm \ar[dr]_-{(Q,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
+\wedge^2 S_\pm \ar[dr]_-{(Q,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(-)Q} \\
 & S_\pm & 
@@
 \item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
-\begin{dfn}
+\end{itemize}
+
+\begin{definition}
 The BRST theory associated to a supersymmetric matter pair (even or odd) $(\SS, U)$ has underlying bundle of BRST fields:
-\[
+\end{definition}
 

### 2020-02-24 old stuff/old version.tex
reorganize

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\U}{\mathrm{U}}

\newcommand{\ham}{/\!\!/}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\addbibresource{Twist.bib}

\usepackage{pdflscape}
\usetikzlibrary{shapes.geometric, arrows, positioning, matrix}

\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{A Catalogue of Twists of Supersymmetric Gauge Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.  Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory. 
\end{abstract}

\tableofcontents

\section*{Introduction} 
\begin{table}[htbp]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
 &&&$\bun_G(\CC^5)$ &\\ \hline
 \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{Rank 1} & Mixed Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
 &&&$\bun_G(\CC^4 \times \RR_{\mr{dR}})$ &\\ \hline
 \multirow{6}*{8} & \multirow{6}*{1} & \multirow{2}*{Rank $(1,0)$ Pure} & Holomorphic BF Theory & \multirow{2}*{4 (holomorphic)} \\
 &&& $T^*[-1]\bun_G(\CC^4, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^3 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(1,0)$ Impure} & Perturbatively trivial ($\Spin(7)$ Instanton)& \multirow{2}*{8 (topological)} \\
 &&& $\bun_G(\CC^4, BG)_\mr{dR}$ & \\ \hline
  \multirow{6}*{7} & \multirow{6}*{1} & \multirow{2}*{Rank $1$ Pure} & Mixed BF Theory & \multirow{2}*{4 (minimal)} \\
 &&& $T^*[-1]\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$} & Mixed Chern-Simons Theory& \multirow{2}*{5} \\
 &&& $\bun_G(\CC^2 \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $1$ Impure} & Perturbatively trivial ($G_2$ Monopole)& \multirow{2}*{7 (topological)} \\
 &&& $\bun_G(\CC^3 \times \RR_{\mr{dR}}, BG)_\mr{dR}$ & \\ \hline
 \multirow{8}*{6} & \multirow{8}*{$(1,1)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{3 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC^2 \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$} & {Mixed Chern-Simons Theory} & \multirow{2}*{5} \\
 &&& $\bun_G(\CC \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$ generic} & {Perturbatively trivial (6d Hitchin system)} & \multirow{2}*{6 (topological)} \\
 &&& $\bun_G(\CC^2 \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{8}*{5} & \multirow{8}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{3 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ special} & {Mixed BF Theory} & \multirow{2}*{4} \\
 &&& $T^*[-1]\bun_G(\CC \times \RR^3_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $4$} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\RR^5_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ generic} & {Perturbatively trivial (Haydys-Witten)} & \multirow{2}*{5 (topological)} \\
 &&& $\bun_G(\CC \times \RR^3_{\mr{dR}})_{\mr{dR}}$ & \\ \hline
 \multirow{12}*{4} & \multirow{12}*{$4$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\higgs_G(\CC^2)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & Mixed BF Theory & \multirow{2}*{3} \\
 &&& $T^*[-1]\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,2)$ special} & BF Theory (Kapustin-Witten B-model) & \multirow{2}*{4 (topological)} \\
 &&& $T^*[-1]\flat_G(\RR^4)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,1)$} & {Perturbatively trivial} & \multirow{2}*{4 (topological)} \\
 &&& $\bun_G(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}})_{\mr{dR}}$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Kapustin-Witten A-Model)} & \multirow{2}*{4 (topological)} \\
 &&& $\higgs_G(\CC^2)_{\mr{dR}}$ & \\ \cline{3-5}
  && \multirow{2}*{Rank $(2,2)$ generic} & {Perturbatively trivial (Generic Kapustin-Witten)} & \multirow{2}*{4 (topological)} \\
 &&& $\flat_G(\RR^4)_{\mr{dR}}$ & \\ \hline
  \multirow{8}*{3} & \multirow{8}*{$8$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, T^*[2](\gg/\gg))$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $T^*[-1]\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline
 %\multirow{6}*{2} & \multirow{6}*{$(8,8)$} & \multirow{2}*{Rank $(1,0)$} & {} & \multirow{2}*{1 (holomorphic)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (B)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \cline{3-5}
 %&& \multirow{2}*{Rank $(1,1)$ (A)} & {} & \multirow{2}*{2 (topological)} \\
 %&&& {} & \\ \hline
 \end{tabular}
 \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with gauge group $G$ (16 supercharges).}
 \label{table_of_twists_16}
\end{table}

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\mr{Map}(\CC^3, U \ham G)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\mr{Map}(\CC^2 \times \RR_{\mr{dR}}, U \ham G)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{Rank $(1,0)$} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $(1,1)$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{3} \\
 &&& $\mr{Map}(\CC \times \RR^2_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $(2,0)$} & {Perturbatively trivial (Donaldson theory)} & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Map}(\CC^2, U \ham G)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to a mixed symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)$  & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (B)} & {BF Theory coupled to a symplectic boson (Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, U \ham G)$ & \\ \cline{3-5}
 && \multirow{2}*{Rank $2$ (A)} & {Perturbatively trivial (dual Rozansky-Witten)} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC \times \RR_{\mr{dR}}, U \ham G)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a hypermultiplet valued in symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

\begin{table}[hbp]
 \centering
 \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{4} & \multirow{2}*{$1$} & \multirow{2}{*}{Rank $(1,0)$} & Holomorphic BF Theory coupled to $R$-matter & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Map}(\CC^2, R/G)$ & \\ \hline
 \multirow{2}*{3} & \multirow{2}*{$2$} & \multirow{2}*{Rank $1$} & {Mixed BF Theory coupled to $R$-matter} & \multirow{2}*{2 (minimal)} \\
 &&&  $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/G)$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge group $G$ with a chiral multiplet valued in representation $R$ (4 supercharges).}
 \label{table_of_twists_4}
\end{table}

\clearpage
\begin{figure}[hbp]
\begin{tikzpicture}
  \matrix (mat) [nodes in empty cells, minimum width=3.5ex, minimum height=3.5ex, column sep=1.8ex,row sep=6ex]{
   \node (corner) {}; & \node (d10) {10}; & \node (d9) {9}; & \node (d8) {8}; & \node (d7) {7}; & \node (d6) {6}; & \node {$\qquad \quad \ 5$}; && \node (d5) {};& \node {$\qquad \ 4$}; && \node (d4) {}; & &\node (d3) {3}; & \node (d2) {}; &  \\
  \node {8}; &    &   & \node[s16] (88) {$(1,0)_A$};  &   &   &   &&   &&&&   &&&   \\
  \node {7}; &    &   &   & \node[s16] (77) {$1_A$};  &   &   &&   &&&&   &&&   \\
  \node {6}; &    &   &   &   & \node[s16] (66) {$(1,1)_A$};  &   &&   &&&&   &&&   \\
  \node {5}; & \node[s16] (105) {$(1,0)$};  & \node[s16] (95) {$1$};  & \node[s16] (85) {$(1,1)$};  & \node[s16] (75) {$2$}; & \node[s16]  (65){$(2,2)$};  & \node[s16] (55B) {$4$}; & \node[s16] (55A) {$2_A$};  &   &&&&   &&&   \\
  \node {4}; &    &   & \node[s16] (84) {$(1,0)_B$};  & \node[s16] (74) {$1_B$};  & \node[s16] (64) {$(1,1)_B$};  & \node[s16] (54) {$2_B$};  && \node[s16] (44B) {$(2,2)_B$}; & \node[s16] (44K) {$(2,1)$}; & \node[s8] (44A) {$(2,0)$}; & \node[s16] (44g) {$(2,2)_A$};  &   &&&   \\
  \node {3}; &    &   &   &   & \node[s8] (63) {$(1,0)$};  & \node[s8] (53) {$1$};  && \node[s8] (43) {$(1,1)$};  &&&& \node[s8] (33B) {$2_B$}; & \node[s8] (33A) {$2_A$}; &  &   \\
  \node {2}; &    &   &   &   &   &   && \node[s4](42) {$(1,0)$};  &&&& \node[s4] (32) {$1$};  &&   \\
  \node (i1) {1}; &   &  &  &  &  &   & &   &&& &   && &   \\};

  \draw[thick] (corner.south west) -- (d2.south west);
  \draw[thick] (corner.north east) -- (i1.south east);

  \draw[dotted] (0.5,-7) -- (0.5,7);
  \draw[dotted] (6.4,-7) -- (6.4,7);
  \draw[dotted] (-2,-7) -- (-2,7);
  \draw[dotted] (-3.8,-7) -- (-3.8,7);
  \draw[dotted] (-4.8,-7) -- (-4.8,7);
  \draw[dotted] (-6.3,-7) -- (-6.3,7);
  \draw[dotted] (-7.3,-7) -- (-7.3,7);

  \draw[arrow] (105) -- (95);
  \draw[arrow] (95) -- (85);
  \draw[arrow] (88) -- (77);
  \draw[arrow] (95) -- (84);
  \draw[arrow] (85) -- (75);
  \draw[arrow] (85) -- (74);
  \draw[arrow] (84) -- (74);
  \draw[arrow] (77) -- (66);
  \draw[arrow] (75) -- (65);
  \draw[arrow] (75) -- (64);
  \draw[arrow] (74) -- (64);
  \draw[arrow] (74) -- (63);
  \draw[arrow] (66) -- (55A);
  \draw[arrow] (65) -- (55B);
  \draw[arrow] (65) -- (54);
  \draw[arrow] (64) -- (54);
  \draw[arrow] (64) -- (53);
  \draw[arrow] (63) -- (53);
  \draw[arrow] (55A) -- (44g);
  \draw[arrow] (55B) -- (44B);
  \draw[arrow] (54) -- (44B);
  \draw[arrow] (54) -- (43);
  \draw[arrow] (53) -- (43);
  \draw[arrow] (53) -- (42);
  \draw[arrow] (44B) -- (33B);
  \draw[arrow] (44A) -- (33A);
  \draw[arrow] (44K) -- (33A);
  \draw[arrow] (43) -- (33B);
  \draw[arrow] (43) -- (32);
  \draw[arrow] (42) -- (32);
  \draw[arrow] (44g) -- (33A);

\end{tikzpicture}
\caption{This figure shows the orbits of square-zero supercharges in each dimension.  The labels indicate each orbit: the number refers to the rank, and the subscript indicates the situations where the supercharges of a given rank split into multiplet orbits.  Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.  Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.}
\label{fig:superchargeorbits}
\end{figure}

% \begin{figure}
% \begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
% \node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
% \node (91) [s16, below=of 101] {Rank $1$ $d=5$};
% \node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
% \node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
% \node (825) [right=of 82] {};
% \node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
% \node (71) [s16, below=of 81] {Rank $1$ $d=4$};
% \node (72) [s16, below=of 82] {Rank $2$ $d=5$};
% \node (73) [s16, below=of 83] {Rank $1$ $d=7$};
% \node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
% \node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
% \node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
% \node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
% \node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
% \node (51) [s8, below=of 61] {Rank $1$ $d=3$};
% \node (52) [s16, below=of 62] {Rank $2$ $d=4$};
% \node (53) [s16, below=of 63] {Rank $4$ $d=5$};
% \node (54) [s16, below=of 64] {Rank $2$ $d=5$};
% \node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
% \node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
% \node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
% \node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
% \node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
% \node (31) [s4, below=of 41] {Rank $1$ $d=2$};
% \node (32) [s8, below=of 42] {Rank $2$ $d=3$};
% \node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
% \node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
% 
% \draw[arrow] (101) -- (91);
% \draw[arrow] (91) -- (81);
% \draw[arrow] (91) -- (82);
% \draw[arrow] (81) -- (71);
% \draw[arrow] (82) -- (71);
% \draw[arrow] (82) -- (72);
% \draw[arrow] (83) -- (73);
% \draw[arrow] (71) -- (61);
% \draw[arrow] (71) -- (62);
% \draw[arrow] (72) -- (62);
% \draw[arrow] (72) -- (63);
% \draw[arrow] (73) -- (65);
% \draw[arrow] (61) -- (51);
% \draw[arrow] (62) -- (51);
% \draw[arrow] (62) -- (52);
% \draw[arrow] (63) -- (53);
% \draw[arrow] (64) -- (52);
% \draw[arrow] (64) -- (54);
% \draw[arrow] (65) -- (54);
% \draw[arrow] (51) -- (41);
% \draw[arrow] (51) -- (42);
% \draw[arrow] (52) -- (42);
% \draw[arrow] (52) -- (43);
% \draw[arrow] (53) -- (43);
% \draw[arrow] (54) -- (43);
% \draw[arrow] (54) -- (44);
% \draw[arrow] (54) -- (45);
% \draw[arrow] (41) -- (31);
% \draw[arrow] (42) -- (31);
% \draw[arrow] (42) -- (32);
% \draw[arrow] (43) -- (32);
% \draw[arrow] (44) -- (32);
% \draw[arrow] (45) -- (32);
% \draw[arrow] (31) -- (21);
% \draw[arrow] (31) -- (22);
% \draw[arrow] (32) -- (22);
% 
% \node (2d) [dimension, left=of 21] {2d};
% \node (3d) [dimension, above=of 2d] {3d};
% \node (4d) [dimension, above=of 3d] {4d};
% \node (5d) [dimension, above=of 4d] {5d};
% \node (6d) [dimension, above=of 5d] {6d};
% \node (7d) [dimension, above=of 6d] {7d};
% \node (8d) [dimension, above=of 7d] {8d};
% \node (9d) [dimension, above=of 8d] {9d};
% \node (10d) [dimension, above=of 9d] {10d};
% \end{tikzpicture}
% \caption{Orbits of square-zero supercharges.}
% \label{fig:superchargeorbits}
% \end{figure}

\part{Supersymmetric Gauge Theory}

\section{The BV-BRST Formalism}

In this section we will set up the homological formalism in which we study classical field theory: the BV-BRST formalism.  Most of the material in this section is not original.  We refer the reader to \cite{CostelloBook, Book2} for more details on this perspective.  We will conclude the section by describing a number of fundamental examples of classical field theories that are highly structured: partially holomorphic or topological theories.  We will also discuss the concept of \emph{dimensional reduction} of a classical field theory on $M$ along a fibration $M \to N$.  We will use the idea of dimensional reduction to construct many of the supersymmetric field theories which we will consider in the next section.

\subsection{Conventions}
Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading. \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.  For an element $x$ we denote by $|x|\in\ZZ/2\ZZ$ the total degree.

Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of symmetric functions on $\cE$ (respectively $\cE_c)$. 
We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted symbolically by an expression of the form
\[\int_M f (\phi, \phi', \dots),\]
where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
The space of local functionals can be viewed as a subspace
\[
\oloc(\cE) \subset \cO(\cE_c)
\]
where the integral symbol makes sense in earnest when applied to sections which are compactly supported.
We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.

Given two vector bundles $E, F$ on $M$ we can also make sense of the space of local functionals from $E$ to $F$.
By definition, this is 
\[
{\rm Fun}_{\rm loc}(\cE, \cF) = \prod_{n \geq 0} {\rm PolyDiff}(\cE^{\times n}, \cF)_{S_n}
\]
where ${\rm PolyDiff}(\cE^{\times n}, \cF)$ denotes the space of polydifferential operators, and we take coinvariants for the obvious symmetric group action.
When $\cF = \cE$, we refer to ${\rm Fun}_{\rm loc}(\cE, \cE)$ as the space of local vector fields on $E$. 
There is a natural Lie bracket on ${\rm Fun}_{\rm loc}(\cE, \cE)$ and a canonical action of this Lie algebra on local functionals.

\subsection{Classical BV Theories}

\pavel{We need to introduce classical field theories linear over a commutative ring (used to talk about symmetries and the Hodge family).}

The classical BV (Batalin-Vilkovisky) formalism \cite{BatalinVilkovisky} is a model for classical field theory from the Lagrangian perspective.  In brief the classical BV formalism produces a local model for the critical locus of an action functional, but considered in the derived sense.  That is, given a space $\Phi$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\Phi$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \Phi \cap^h_{T^*\Phi} \Gamma_{\d S}$ of the zero section in $T^*\Phi$ with the graph of $\d S$.  The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$.

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data of:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

The BV bracket enjoys the graded skew symmetry property
\[
\{F, G\} = (-1)^{|F| |G|} \{G, F\}
\]
as well as the graded Jacobi identity.
This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.

%\[
%\{F(A, B), G(A, B)\} = \frac{\partial}{\partial A} F(A, B) \frac{\partial}{\partial B}  G(A,B) + \frac{\partial}{\partial B} F(A, B) \frac{\partial}{\partial A}  G(A,B)
%\]

Now, we will include interactions in the BV picture.

\begin{definition}
A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[I \in \oloc^+(\cE)\]
of cohomological degree zero satisfying the Maurer-Cartan equation
\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
\end{definition}

Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
the BV action of the theory.

The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\]

In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely a pair $Q_{\mr{BV}}, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ that is at least quadratic and satisfies the classical master equation.
The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.

Because of this, we will sometimes refer to the triple $(E, S, \omega)$ instead $(E, Q_{\mr{BV}}, I, \omega)$ as the data of a classical field theory.

\begin{remark}
We will also consider \defterm{$\ZZ/2\ZZ$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2\ZZ$-grading and, correspondingly, $Q_{\mr{BV}}$ is simply an odd operator.
\end{remark}

\begin{remark}
The data of a classical BV theory can be equivalently encoded in an elliptic $L_\infty$ algebra $L=E[-1]$ equipped with a cyclic structure, i.e. a symplectic isomorphism $L\cong L^![-3]$ \cite[Chapter 5.4]{Book2}. 
\end{remark}

Next, we formulate the notion of an equivalence of classical BV theories.

\begin{definition}
A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism. A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
\end{definition}

We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. First, we consider the process of integrating out an auxiliary field.

\begin{prop}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ and $S_1$ are independent of $\phi$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I')$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
\label{prop:integrateoutfield}
\end{prop}

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $Q_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  Then we define the required perturbative equivalence as follows.  First $F_1(e) = (e, Q_1(e), 0) \in E$.  Then, for $n > 1$, define
\begin{align*}
F_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $F_n$ manifestly intertwine the pairings $\omega$ and $\omega'$.  To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(F(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
Finally, $F_1$ is a quasi-isomorphism with quasi-inverse given by the projection $(E,Q) \to (E_0,Q_0)$, therefore our specified morphism is an equivalence.
\end{proof}

\begin{remark}
In terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] &\mc E_0^0 \ar[r]^{Q_0} \ar[dr] &\mc E_0^1 \ar[r] &\cdots \\
&\cO_M \ar^{i}[r] \ar[ur] &\dens_M &
}\]
where $i$ is the canonical inclusion, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify the differential $Q_0$ and the Lie structure.
\end{remark}

We may also remove a trivial BRST doublet.

\begin{prop}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
\label{prop:BRSTdoublet}
\end{prop}

\begin{proof}
Again, concretely, we'll write $\sum_{n \ge 1} f^{(n)}_\phi$ and $\sum_{n \ge 1} f^{(n)}_{\psi}$ for the Taylor expansions of $f_\phi$ and $f_{\psi}$ respectively.  We can write out a morphism of classical BV theories $F \colon E_0 \to E$ by defining $F_1(e) = (e, f^{(1)}_{\phi}(e),0,f^{(1)}_\psi(e),0)$, and for $n > 1$ defining 
\[F_n(e_1\otimes e_n) = (0, f^{(n)}_{\phi}(e_1, \ldots, e_n), 0, f^{(n)}_{\psi}(e_1, \ldots, e_n)).\]
Again, these $F_n$ manifestly intertwine the pairings on $E_0$ and $E$, since the image of $F_n$ lands in an isotropic summand of the $E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$ part of $E$.  Also, by construction, the $F_n$ intertwine the action functionals, since
\begin{align*}
S(F(e)) &= S_0(e) + \frac{1}{2} \int_M \omega(f_\psi(e), f_\phi(e) - f_\phi(e)) + \omega(f_\phi(e), f_\psi(e) - f_\psi(e)) \\
&= S_0(e).
\end{align*}
Again, $F_1$ is a quasi-isomorphism between the classical BV complexes with quasi-inverse given by the projection onto the summand $E_0$.
\end{proof}

\begin{remark}
Again, in terms of the classical BV complex, this proposition tells us that given a classical BV complex of the form
\[\xymatrix{
\cdots \ar[r] & E_0^{-1}\ar[r] \ar[dr] \ar[ddr] &E_0^0 \ar[r]  &E_0^1 \ar[r] &E_0^2 \ar[r] &\cdots \\
&&E_1 \ar^{~}[dr] &E_1^! \ar[ur] && \\
&&E_1^! \ar^{~}[ur] &E_1 \ar[uur] && \\
}\]
with the differentials $E_1 \to E_1$ and $E_1^! \to E_1^!$ given by the identity, we can replace it with a quasi-isomorphic complex consisting of only the first line, as long as we suitably modify its differential and Lie structure. \chris{Pavel, is this, and the other remark above, what you wanted me to add?}
\end{remark}

\subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
In this section we define what it means for a (super) Lie algebra to act on a classical field theory  (see also \cite[Chapter 11]{Book2} for a related discussion). Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra.  We will define $\gg$-equivariant local observables in the classical field theory by introducing $\gg$-valued background fields into our classical field theory, and extending the action functional to a functional that involves these background fields, but still satisfies the classical master equation.  We begin by defining an appropriate version of the Chevalley-Eilenberg cochain complex.

\begin{definition}
The \emph{Chevalley-Eilenberg complex} for the Lie algebra $\gg$, with coefficients in $\oloc(\cE)$, will be defined as follows.  Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
where $x_j \in \fg$.  The Chevalley-Eilenberg differential is given, following the sign conventions of \cite{SafronovCoisoInt}, by the formula
\[(\d_{\mr{CE}} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n).\]
The complex is additionally equipped with a degree $+1$ BV bracket via the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
\end{definition}

The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
\[
(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
\]
where $f \colon \fg^{\otimes n} \to \oloc(\cE)$. 
The differentials $\d_{\mr{CE}}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{\mr{CE}} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{\mr{CE}} + Q_{\mr{BV}}$. 
Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.  This shifted cotangent complex will model equivariant local observables in our classical field theory, but to finish defining the $\gg$ action we must define the equivariant version of the classical interaction.  This is defined as follows.

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
\begin{itemize}
\item[(1)]
An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
where $I_\fg^{(k)}$ is a multilinear map $\fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $I_\fg^{(0)} = I$.
\item[(b)] For each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields.
\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
\[(\d_{\mr{CE}} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{itemize}
\item[(2)]
For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
An action $I_\fg$ is called \defterm{elliptic} if the induced linear differential operator
\[
Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
\]
is elliptic as a $C^\bu(\fg)$-linear differential operator.
\end{itemize}
\end{definition}

\begin{rmk}
\brian{Explain $C^\bu(\fg)$-linear elliptic}
\end{rmk}

\begin{rmk}
We have seen that a classical BV theory can also be presented in terms of a BV action $S \in \oloc(\cE)$ satisfying the classical master equation $\{S, S\} = 0$. 
One can also formulate actions of a Lie algebra on a classical theory in these terms. 
The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local functional $\fS_\fg = \sum_k \fS_\fg^{(k)}\in C^\bu(\fg, \oloc(\cE))$, at least quadratic in the fields, such that $\fS^{(0)}_\fg = S$ and such that the classical master equation
\[
\d_{\mr{CE}} \fS_\fg + \frac{1}{2} \{\fS_\fg, \fS_\fg\} = 0 
\]
is satisfied.
\end{rmk}

\begin{rmk}
We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
By the Maurer-Cartan equation, the operator $\d_{\mr{CE}} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
\[
\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
\]
combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
\end{rmk}

We may also define actions of supergroups on classical field theories.  The action of a supergroup $G$ is more data than the action of a super Lie algebra $\gg$: it includes the infinitesimal action of the Lie algebra $\gg$, along with an action of $G$ on the fields exponentiating this infinitesimal action.  That is, we make the following definition.

\begin{definition}
\label{group_action_def}
Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory, and let $G$ be a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
\begin{itemize}
\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.

\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$ 
\end{itemize}
These are required to satisfy the following conditions:
\begin{itemize}
\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, the differential $Q$ and the interaction term $I$.

\item For every $x\in\fg$, the vector field $X_{{I^{(1)}_\fg}(x)}$ on $\cE$ coincides with the infinitesimal action of $\gg$ on $\cE$.
\end{itemize}
\end{definition}

\begin{remark}
While we allow for $L_\infty$ actions of Lie algebras, we will only consider strict actions of Lie groups in the present work.
\end{remark}

\subsection{From BRST to BV}
We will now explain how to build classical BV theories from more traditional data: that of the \emph{usual} fields of a classical field theory, together with the usual action functional and the action of gauge transformations.  These data can be packaged into what's known as a BRST theory, where fermionic fields (ghosts) are introduced to generate the infinitesimal gauge transformations, in the following way.

\begin{definition}
A \defterm{classical BRST theory} on a manifold $M$ consists of the following data:
\begin{itemize}
\item a $\ZZ\times\ZZ/2\ZZ$-graded vector bundle $F$ together with the structure of a local $L_\infty$ algebra on the shift $F[-1]$;
\item A local functional $S_{\mr{BRST}} \in \oloc(\cF)$ of polynomial degree $\geq 2$.
\end{itemize}
Together, these data must satisfy the equation
\[Q_{\mr{BRST}} S_{\mr{BRST}} = 0,\]
where $Q_{\mr{BRST}}$ is the Chevalley--Eilenberg differential defined by the $L_\infty$ structure on $F[-1]$. 
\end{definition}

We call $\cF$ the \defterm{space of BRST fields}.

\begin{remark}
In the most typical examples, the bundle $F$ is concentrated in $\ZZ$-degrees $-1$ and 0.  In this case, sections in degree 0 are thought of as physical fields, and ghosts -- sections in degree $-1$ -- are thought of as generators of the infinitesimal gauge symmetry.  The action of gauge transformations on fields is then encoded by the Lie structure.
\end{remark}

From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows. Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.

First, we define the free BV theory. Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
The underlying bundle of the BV theory is
\[
E = F \oplus F^! [-1].
\]
The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.
The differential of the free BV theory is
\[Q_{\mr{BV}} = \ell_1 + S^{free}_{\mr{BRST}}.
\]

The interacting theory is constructed as follows. First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$. These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
\] 
which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
\]

\begin{lemma}
Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
\end{lemma}

We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. In the case $S_{\mr{BRST}} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.

\begin{remark}
In general, multiple BRST theories can give rise to the same BV theory.  A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.  Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
\end{remark}

If the fields of the classical BRST theory are denoted by $\phi$, we denote their antifields in the classical BV theory by $\phi^*$, so that
\[\{\phi(x), \phi^*(y)\} = \{\phi^*(y), \phi(x)\} = \delta(x-y).\]
\brian{Looks like you're using a bracket we haven't defined. 
We've only defined brackets on local functionals, but I think when you write $\phi(x)$ you mean a point-like observable, which is far from local.} \chris{I don't think we need to say this so precisely.  I think it's enough to say that a homogeneous splitting $F = \bigoplus_i \Phi_i$ induces a splitting $F^! = \bigoplus_i \Phi_i^!$, and if we denote a general element of the summand $\Phi_i$ by $\phi$ then we will denote a general element of the summand $\Phi_i^!$ by $\phi^*$.}

\subsection{Examples of Classical Field Theories}

In this section we give some examples of classical field theories we will use in our classification of twisted supersymmetric field theories. All theories we consider in this section are $\ZZ$-graded, i.e. the space $E$ of fields will be completely even with respect to the $\ZZ/2\ZZ$-grading.

\subsubsection{Generalized BF Theory} \label{gen_BF_section}

Our first example will generalize the fundamental example of \emph{BF theory} to a not entirely topological context.  Ordinarily, BF theory describes the classical BRST theory on a $d$-manifold $M$ with fields given by a $G$-gauge field $A$ and a $\gg$-valued $(d-2)$-form $B$, with action functional
\[S(A,B) = \int_M \langle F_A \wedge B \rangle.\]
This theory is, in fact, of cotangent type, where the base of the cotangent includes $A$ and its antifield, and the fiber includes $B$ and its antifield.  This basic setup can be generalized to a setting where $M$ need not be entirely topological, and where $\gg$ may be a more general $L_\infty$ algebra, in the following way.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. The \defterm{generalized $BF$ theory} is the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$. $F[-1]$ is equipped with a natural local $L_\infty$ algebra structure from $\fg$.

\item The BRST action is $S_{\mr{BRST}} = 0$.
\end{itemize}
We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
\label{def:generalizedBF}
\end{definition}

\begin{remark} \label{mapping_stack_remark}
The mapping stack above has a precise meaning in the language of derived algebraic geometry \chris{Let's say a few words about where the terminology comes from at least, even if for us it's just shorthand.  I can add this later.  I should also remark on the fact that we can pull the $T^*[d]$ out to a $T^*[k]$, with $k=-1$ if $X,Y,M$ are vector spaces.}  For the purposes of this paper, while we think of the derived stack as the global moduli space of solutions to the equations of motion in generalized BF theory, we will only use the perturbative datum of the classical BV complex.  The language of the mapping stack will simply be used as a compact way of referring to the theory above. 
\end{remark}

Let us unpack the definition. Let $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Then the bundle of BV fields is
\[E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]\oplus \Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*,\]
\chris{I changed a shift here which I don't think was correct, but someone should double check.} where we denote the two fields by $A$ and $B$. The BV action is
\[S = \int_{X\times Y\times M} \langle B\wedge (\dbar_X + \dbar_Y + \d_{\dR, M}) A\rangle + \sum_{k\geq 1}\frac{1}{k!} \int_{X\times Y\times M} \langle B\wedge \ell_k(A, \dots, A)\rangle,\]
where $\langle -, -\rangle$ is the natural pairing between $\fg^*$ and $\fg$ and $\ell_k$ denote the components of the $L_\infty$ structure on $\fg$.

\begin{example}
For $X=Y=\pt$ and $\fg$ an ordinary Lie algebra we recover the usual topological $BF$ theory with the BV action
\[S = \int_M \left\langle B\wedge \left(\d_\dR A+ \frac{1}{2}[A\wedge A]\right)\right\rangle.\]
\end{example}

We will see many $BF$ theories as the output when we twists a supersymmetric gauge theories.
In fact, a special case of the definition above also arises when twisting theories of matter.  We will refer to as a generalized $\beta\gamma$ system, extending the usual 2d $\beta \gamma$ system.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix a complex vector space $V$. The \defterm{generalized $\beta\gamma$ system} is the BV theory given by the $(-1)$-shifted cotangent bundle of the following classical BRST theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

\item The bundle of BRST fields is the $\ZZ$-graded bundle $F = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V$. $F[-1]$ is equipped with an $L_\infty$ structure with $\ell_{k} = 0$ for $k \geq 2$.

\item The BRST action is $S_{\mr{BRST}} = 0$.
\end{itemize}
\end{definition}

\begin{rmk}
This is indeed a special case of generalized BF theory: the generalized $\beta\gamma$ system appears as generalized $BF$ theory with the $L_\infty$ algebra given by $\fg = V[-1]$, with trivial $L_\infty$ structure. 
\end{rmk}

We may also couple a $\beta\gamma$ system to a more general generalized $BF$ theory as follows.

\begin{example}
Let $X,Y,M$ be as before. Suppose $\fg$ is a dg Lie algebra and $V$ is a dg representation of $\fg$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\]
with the only nontrivial brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$ and $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$. The space of fields in the corresponding generalized BF theory will be denoted using the mapping stack notation (as in Remark \ref{mapping_stack_remark}) as
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] (V / \fg)):=\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] \cL),\]
where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
\end{example}

The following is obvious from the definition.

\begin{prop}
Consider the generalized BF theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, T^*[d] B\fg).\]
Then it carries an action of $\U(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
\label{prop:BFrotationaction}
\end{prop}

\begin{remark}
In fact, the $\SO(n_3)$-action given by the previous proposition extends to a homotopically trivial action in the sense of \cite[Section 2.4]{ElliottSafronov}.
\end{remark}

Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.  In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.  So at $t=0$ we will recover generalized BF theory.

We will refer to these families as Hodge deformations of generalized BF theory.  The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.

\begin{definition} \label{Hodge_family_def}
Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.  The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so 
\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
\end{definition}

Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]

\subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
The next class of examples of classical BV theories we give are generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not of cotangent type.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Chern--Simons theory} is the following classical BV theory:
\begin{itemize}
\item The spacetime is the smooth manifold $X\times Y\times M$.

\item The bundle of BV fields is the $\ZZ$-graded bundle $E = \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1]$.

\item $Q = \dbar_X + \dbar_Y + \d_{\dR, M} + \ell_1$.

\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.

\item The interaction term is
\[I = \sum_{k\geq 2}\frac{1}{(k+1)!} \int_{X\times Y\times M} \Omega_X\wedge \langle A\wedge \ell_k(A, \dots, A)\rangle.\]
\end{itemize}
We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg)$.
\label{def:generalizedCS}
\end{definition}

We may also consider a $\ZZ/2\ZZ$-graded version of the above theory where $\fg$ is merely $\ZZ/2\ZZ$-graded.

\begin{example}
For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
\[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.  This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.  If $d$ is not 3 this theory is only $\ZZ/2\ZZ$-graded.
\end{example}

\begin{example}
For $Y=M=\pt$, $X$ a Calabi-Yau 3-fold and $\fg$ an ordinary Lie algebra we recover the holomorphic Chern--Simons theory with the BV action
\[S = \int_X \Omega_X\wedge \left(\frac{1}{2}\langle A\wedge \dbar A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
As in the previous example, this still makes sense if $X$ is a Calabi-Yau $d$-fold with $d$ odd, as a $\ZZ/2\ZZ$-graded theory.
\end{example}

\begin{example}
If $\fh$ is an $L_\infty$ algebra, $\fg = \fh \oplus \fh^*[d-3]$ carries a natural $L_\infty$ structure given by combining the original $L_\infty$ structure on the first term and the coadjoint action of the first term on the second term. The $L_\infty$ algebra $\fg$ carries a natural symmetric pairing of degree $d-3$ given by the obvious pairing between $\fh$ and $\fh^*$. Generalized Chern--Simons theory for $\fg$ in this case recovers the generalized BF theory from Definition \ref{def:generalizedBF}.
\label{ex:CSBF}
\end{example}

\begin{example}
Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$. The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself. The space of fields in the corresponding Chern--Simons theory will be denoted by
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]

Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
\begin{align*}
E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
\end{align*}
and the action functional as before.
\label{ex:CSHamiltonianreduction}
\end{example}

As for BF theories, the Chern--Simons theory on $\RR^n$ carries a natural rotation action.

\begin{prop}
Suppose $\fg$ is an $L_\infty$ algebra equipped with a nondegenerate invariant symmetric pairing of degree $n_1+2n_2+n_3-3$. Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, B\fg).\]
Then it carries an action of $\SU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
\end{prop}

We may slightly enhance the previous proposition if we are in the setting of Example \ref{ex:CSHamiltonianreduction} and we choose a square root of the canonical bundle. We define the unitary metalinear group to be
\[\MU(n) = \U(n)\times_{\U(1)} \U(1),\]
where $\U(n)\rightarrow \U(1)$ is the determinant map and $\U(1)\rightarrow \U(1)$ is the map $z\mapsto z^2$. We denote by $\det^{1/2}\colon \MU(n)\rightarrow \U(1)$ the projection on the second factor; this may be thought of as a square root of the determinant representation of $\U(n)$. The natural $\U(n)$-action on $\CC^n$ lifts to an $\MU(n)$-action on the bundle of half-densities $K_{\CC^n}^{1/2}\rightarrow \CC^n$.

\begin{prop}
Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure. Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
\end{prop}

\subsubsection{Generalized Hodge theory}

We will also consider deformations of the generalized BF theory to a perturbatively trivial theory. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

Given an $L_\infty$ algebra $\fg$ we denote by $\fg_{\Hod}$ the $\CC[t]$-linear $L_\infty$ algebra
\[\fg_{\Hod} = \CC[t]\otimes (\fg\oplus \fg[1])\]
with the $L_\infty$ brackets coming from the $L_\infty$ brackets on $\fg$ in the first term, where we consider $\fg[1]$ as the adjoint representation of $\fg$. The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.

If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}

\begin{prop}
The $t=0$ specialization of the generalized Hodge theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$ is isomorphic to the generalized BF theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B \fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.

The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
\label{prop:Hodgetheoryspecialization}
\end{prop}
\begin{proof}
At $t=0$ we get
\[\left.\fg_\Hod\right|_{t=0}\cong \fg\oplus \fg[1]\cong \fg\oplus \fg^*[d-1],\]
where we use the symmetric bilinear pairing on $\fg$ in the second isomorphism. The first claim then follows from Example \ref{ex:CSBF}.

At $t\neq 0$ the $L_\infty$ algebra $\fg_\Hod$ becomes acyclic which proves the second claim.
\end{proof}

\subsection{Dimensional Reduction} \label{dim_red_section}

In this section we formulate the procedure of dimensional reduction of a classical field theory. Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.  The idea is that the \emph{dimensional reduction} of a classical field theory on $M$ along the submersion $p$ is the theory obtained by restricting to those fields which are constant along the fibers of $p$.  We will begin with an abstract definition of dimensional reduction, then prove that if $M = N \times \RR^k$, and we consider field theories which are translation invariant along the fiber, then this procedure is well-defined.

\begin{definition}
We say that a classical field theory $(E_N, Q_N, \omega_N, I_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if one is given the data of an isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.

\item The diagram
\[
\xymatrix{
\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
\cE_M \ar^{Q_M}[r] & \cE_M[1]
}
\]
is commutative.

\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
\end{itemize}
\end{definition}

We have an obvious notion of isomorphisms of dimensional reductions: these are isomorphisms of classical field theories on $N$ which are compatible with the isomorphisms $p^* E_N\cong E_M$. Thus, the collection of dimensional reductions of a given classical field theory on $M$ forms a groupoid.  In fact, when dimensional reduction makes sense, this groupoid is always contractible.

\begin{prop}
Suppose $(E_M, Q_M, \omega_M, I_M)$ is a classical field theory on $M$ and $p\colon M\rightarrow N$ is a homotopy equivalence. Then the groupoid of dimensional reductions of $(E_M, Q_M, \omega_M, I_M)$ is either contractible or empty.

Suppose $M=N\times \RR$ and choose a translation-invariant density along the $\RR$ direction. If the original classical field theory is translation-invariant along the $\RR$ direction, dimensional reductions exist.
\label{prop:dimensionalreductionunique}
\end{prop}
\begin{proof} \textbf{Uniqueness}. We begin by showing that any two dimensional reductions are isomorphic and moreover such an isomorphism is unique if it exists. Since $p\colon M\rightarrow N$ is a homotopy equivalence, the functor $p^*$ establishes an isomorphism between the category of graded vector bundles on $N$ and on $M$. In a similar way, $p^*$ establishes an equivalence between the category of graded vector bundles $E_N$ on $N$ equipped with a nondegenerate pairing $E_N\otimes E_N\rightarrow \Dens_N[-1]$ and a similar category for $M$.

Since $\cE_N\rightarrow \cE_M$ is injective, the diagram
\[
\xymatrix{
\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
\cE_M \ar^{Q_M}[r] & \cE_M[1]
}
\]
uniquely determines $Q_N$ from $Q_M$. Moreover, the condition $p^* I_M = I_N$ uniquely determines $N$.

\textbf{Existence}. Now suppose $(E_M, Q_M, \omega_M, I_M)$ is translation-invariant along the $\RR$ direction. Translation invariance provides the descent datum to construct the bundle of fields $E_N$ on $N$ equipped with a nondegenerate pairing $\omega_N$. Moreover, it shows that the differential $Q_M$ preserves the subspace $\cE_N\hookrightarrow \cE_M$. The restriction of $I_M$ under the same embedding is independent of the $\RR$ factor by translation invariance, so $I_N=p^* I_M$ is again a local functional.
\end{proof}

\begin{remark}
Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
\end{remark}

We will now describe dimensional reductions of the classical Chern--Simons theory.

\begin{prop} \label{CS_to_BF_diml_red_prop}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth manifold. Fix an $L_\infty$ algebra $\fg$ equipped with a nondegenerate invariant pairing and consider the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times \RR)_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized BF theory
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg).\]
\end{prop}

\begin{proof}
To simplify the proof, we assume $X=Y=M=\pt$. Then $\fg$ carries a $(-2)$-shifted pairing $\langle-,-\rangle$. In particular, the generalized BF theory
\[\map(\pt, T^*[-1] B \fg)\]
has the bundle of BV fields $\fg[1] \oplus \fg^*[-2]$. We may identify it with $\fg[1]\oplus \fg$, where the pairing $\omega_N$ pairs the two factors using $\langle-,-\rangle$.

We may identify $p^*(\fg[1]\oplus \fg)\cong \Omega^\bullet_{\RR}\otimes \fg[1]$. Under this identification the integration pairing $\omega_M$ on differential forms reduces to the pairing $\omega_N$. The de Rham differential vanishes on translation-invariant forms which shows a compatibility of dimensional reduction with the differentials $Q_{\mr{BV}}$. Finally, in both cases the interaction term comes from the $L_\infty$ structure on $\fg$.
\end{proof}

\begin{cor}
Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
\label{cor:Hodgetopologicalreduction}
\end{cor}

Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and an orientation. Recall that the symmetric bilinear pairing trivializes $\det(V_\RR)^{\otimes 2}$ and the orientation allows us to obtain a trivialization of $\det(V_\RR)$, i.e. a real volume form. We denote by $V=V_\RR\otimes_{\RR}\CC$ its complexification. $V$ inherits a nondegenerate Hermitian form from the symmetric bilinear pairing on $V_\RR$. Moreover, $V$ carries a complex volume form $\Omega_V$:
\[\det(V)\cong \det(V_\RR)\otimes_{\RR}\CC\]
and we use the real volume form on $V_\RR$.

Functoriality of this construction gives a group homomorphism
\begin{equation}
\SO(V_\RR)\longrightarrow \SU(V)
\label{eq:SOtoSU}
\end{equation}
such that the real projection $\Re\colon V\rightarrow V_\RR$ is $\SO(V_\RR)$-equivariant.

\begin{prop} \label{CS_diml_red_prop}
Let $X,Y,M,\fg$ be as before and $V_\RR, V$ as above. Consider the generalized Chern--Simons theory
\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg).\]
Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Chern--Simons theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg).\]
The isomorphism is moreover $\SO(V_\RR)$-equivariant.
\end{prop}
\begin{proof}
We may assume $X,Y,M=\pt$ as in the previous proof.

We have
\[\Omega^{0, \bullet}_V\cong \Sym_\CC^\bullet(\underline{V}[-1])\]
and
\[\Omega^\bullet_{V_\RR}\cong \Sym_\RR^\bullet(\underline{V}_\RR[-1])\otimes_\RR\CC.\]

Under the pullback map
\[\Omega^\bullet(V_\RR; \CC)\rightarrow \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
the integration map $\int_V \Omega_V\wedge (-)\colon \Omega^{0, \bullet}(V)\rightarrow \CC$ reduces to the integration map $\int_{V_\RR} (-)\colon \Omega^{\bullet}(V_\RR;\CC)\rightarrow \CC$. \brian{This is not defined} \chris{is compactly supported enough?  We want to compare pairings.}
\end{proof}

\begin{cor}
Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized BF theory
\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg).\]

Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized BF theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, T^*[d] B\fg).\]
The isomorphism is moreover $\SO(V_\RR)$-equivariant.
\label{cor:BFholomorphicreduction}
\end{cor}

\begin{cor}
Let $X, Y, M, V_\RR, V$ be as before. Consider the generalized Hodge theory
\[\map((X\times V)\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg_\Hod).\]

Its dimensional reduction along the projection $p\colon (X\times V)\times Y\times M\rightarrow X\times Y\times (M\times V_\RR)$ induced by the projection $\Re\colon V\rightarrow V_\RR$ is isomorphic to the generalized Hodge theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times V_\RR)_{\mr{dR}}, B\fg_\Hod).\]
The isomorphism is moreover $\SO(V_\RR)$-equivariant.
\label{cor:Hodgeholomorphicreduction}
\end{cor}

\section{Supersymmetry} \label{sec: susy}
Having set up the formalism behind classical field theories in the BV and BRST formalisms, we will introduce the other main formal ingredient of this paper: the supersymmetry action.  So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.  We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sec:SYM} below.

\subsection{Supersymmetry Algebras} \label{sec:susyalgebras}
In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.

Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form. Denote by $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

\item If $n$ is even, $\so(V)$ has a pair of distinguished fundamental representations called the \defterm{semi-spin} representations $S_+$ and $S_-$.
\end{itemize}

\begin{definition}
A \defterm{spinorial representation} $\Sigma$ is a finite sum of spin or semi-spin representations of $\so(V)$.
\end{definition}

So, in odd dimensions we have $\Sigma=S\otimes W$ and in even dimensions we have $\Sigma=S_+\otimes W_+\oplus S_-\otimes W_-$, where $W$ denotes a multiplicity space.

We have an embedding $\U(n)\subset \SO(2n, \RR)$ which lifts to an embedding $\MU(n)\subset \Spin(2n, \RR)$. If we denote by $L$ the standard $n$-dimensional representation of $\U(n)$, then the semi-spin representations of $\Spin(2n, \RR)$ restrict to $\MU(n)$ as
\[S_+\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{even}} L,\qquad S_-\cong \det(L)^{-1/2}\otimes \wedge^{\mathrm{odd}} L.\]

\begin{definition}
Fix a spinorial representation $\Sigma$ and a nondegenerate $\so(V)$-equivariant pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$. The \defterm{supertranslation Lie algebra} is the $\so(V)$-equivariant super Lie algebra $\fA = \Pi\Sigma\oplus V$ whose only nontrivial bracket is given by $\Gamma$.
\end{definition}

For a given spinorial representation, the pairing $\Gamma$ is typically unique up to a scale, so a supertranslation Lie algebra is specified by fixing a spinorial representation. In turn, a spinorial representation is determined by the dimension of the multiplicity space, so we will talk about $\mc{N}$ or $(\mc{N}_+, \mc{N}_-)$ supertranslation Lie algebras, where the numbers are specified as follows.
\begin{itemize}
\item If $n\equiv 0, 1, 3, 4\pmod 8$, we let $\mc{N} = \dim(W)$.

\item If $n\equiv 2 \pmod 8$, we let $\mc{N}_{\pm}=\dim(W_{\pm})$.

\item If $n\equiv 5, 7\pmod 8$, we let $2\mc{N} = \dim(W)$.

\item If $n\equiv 6\pmod 8$, we let $2\mc{N}_{\pm} = \dim(W_{\pm})$.
\end{itemize}

Fix the following data:
\begin{itemize}
\item A spinorial representation $\Sigma$ of $\so(V)$.

\item An $\so(V)$-equivariant nondegenerate pairing $\Gamma\colon \sym^2(\Sigma)\rightarrow V$.

\item A Lie group $G_R$, the \defterm{group of $R$-symmetries}, which acts on $\Sigma$ by $\so(V)$-equivariant automorphisms preserving $\Gamma$.
\end{itemize}

Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.  We will sometimes want to refer to the infinitesimal version of this action.
\begin{definition}
Let $\fA$ be a supertranslation algebra.  The corresponding \emph{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
\end{definition}

We will now define the fundamental notion of a supersymmetric field theory.  Consider a spacetime manifold $M=V_\RR$. Let $\ISO(V_\RR) = \Spin(V_\RR)\ltimes V_\RR$ be the \defterm{Poincar\'{e} group} which acts by affine transformations on $M$.

\begin{definition}
\label{dfn: super}
A classical field theory $(E, S, \omega)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
\end{definition}

\subsection{Composition Algebras and Minimal Supersymmetry}
\label{sect:compositionalgebras}

We will now recall a relationship between certain ``minimal'' supersymmetry algebras and composition algebras. Our treatment will essentially follow that of Baez and Huerta \cite{BaezHuerta}.

Let $A$ be a unital (possibly non-associative) complex algebra equipped with an antiinvolution $\sigma\colon A\rightarrow A$. We make the following assumptions:
\begin{enumerate}
\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A$ spanned by the unit.

\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A\rightarrow \CC$. We assume that it is nondegenerate.
\end{enumerate}

In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e. $A$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.

For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. We define $V$ to be the space of $2\times 2$ Hermitian matrices with values in $A$, so that $\dim(V) = \dim(A) + 2$. $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.

Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction

\begin{lemma}
Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$. Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
\label{lm:extendpairing}
\end{lemma}

Consider two isomorphic spinorial representations $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$; we will equip the sum of these representations with an action of the Clifford algebra.  The action on the two summands $\Sigma$ and $\Sigma^*$ will be different, hence the different notation.  We define action maps
\[\rho \colon V \otimes \Sigma\rightarrow \Sigma^*,\qquad \rho \colon V\otimes \Sigma^*\rightarrow \Sigma\]
given, respectively, by
\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]

The following is proved in \cite[Proposition 6]{BaezHuerta}.

\begin{prop}
The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
\end{prop}

So, $\Sigma\oplus \Sigma^*$ forms a $\ZZ/2\ZZ$-graded Clifford module.

We have a nondegenerate scalar spinorial pairing
\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
given by
\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]

By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]

We will now state two important properties of $\Gamma$ and the spinorial pairing. The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).

\begin{thm}
Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
\label{thm:3psi}
\end{thm}

If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.

\begin{thm}
Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
\label{thm:matter3psi}
\end{thm}
\begin{proof}
The right-hand side is
\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
which by associativity can be rewritten as
\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
which is the left-hand side.
\end{proof}

We will be interested in the following examples:
\begin{enumerate}
\item (\textbf{3d $\mc N=1$ supersymmetry}) $A = \CC$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3, \CC)$.

\item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations.

\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$.

\item (\textbf{10d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{O}\otimes_{\RR}\CC$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation.
\end{enumerate}

All four examples are alternative, while the first three examples are moreover associative.

\subsection{Two-dimensional Chiral Supersymmetry} \label{sec:2dchiral}

In the previous section we have related composition algebras to minimal supersymmetry algebras in dimensions 3, 4, 6 and 10. In this section we explain a different relationship between composition algebras and supersymmetry algebras, this time in the case of 2d $\cN=(\cN_+, 0)$ supersymmetry.

Recall that in the case $\dim(V) = 2$ we have two one-dimensional semi-spin representations $S_+, S_-$. Moreover, we have an isomorphism
\[V\cong S_+^{\otimes 2}\oplus S_-^{\otimes 2}\]
and a pairing $( -, -)\colon S_+\otimes S_-\rightarrow \CC$, both of which are $\so(V)$-equivariant. We denote the embeddings $S_{\pm}^{\otimes 2}\subset V$ by $\Gamma_{\pm}$, so that
\begin{equation}
(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2.
\label{eq:2dvectorpairing}
\end{equation}

Let $W$ be a complex vector space of dimension $\cN_+$ equipped with a nondegenerate symmetric bilinear pairing. We consider the spinorial representation
\[\Sigma = S_+\otimes W\]
and its dual
\[\Sigma^* = S_-\otimes W.\]
The Clifford action $V\otimes S_+\rightarrow S_-$ is defined so that
\[\rho(\Gamma_-(f, f)) s = 2(s, f) f\]
and similarly for $V\otimes S_-\rightarrow S_+$.

\begin{prop}
For $v,w\in V$ and $s\in S_+\oplus S_-$ we have
\[\rho(v)\rho(w)s + \rho(w)\rho(v) s = 2(v, w) s.\]
\end{prop}
\begin{proof}
It is enough to prove the claim for $s\in S_+$, $w\in S_+^{\otimes 2}$ and $v\in S_-^{\otimes 2}$. Assume $w=\Gamma_+(s, s)$ and $v = \Gamma_-(f, f)$ for $f\in S_-$. Then we have
\begin{align*}
\rho(\Gamma_+(s, s)) \rho(\Gamma_-(f, f)) s &= 2(s, f) \rho(\Gamma_+(s, s)) f \\
&= 4(s, f)^2 s.
\end{align*}
But by \eqref{eq:2dvectorpairing} we have
\[(\Gamma_+(s, s), \Gamma_-(f, f)) = 2(s, f)^2\]
which proves the claim.
\end{proof}

The Clifford action $V\otimes S_{\pm}\rightarrow S_{\mp}$ extends in an obvious way to a Clifford action $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ given by the identity on the $W$ component. Thus, $\Sigma\oplus \Sigma^*$ is a $\ZZ/2\ZZ$-graded Clifford module.

The spaces $\Sigma, \Sigma^*$ are equipped with $\so(V)$-equivariant nondegenerate pairings $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ defined by
\[\Gamma(s\otimes q_1, s\otimes q_2) = \Gamma_+(s, s) (q_1, q_2)\]
and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ defined similarly.

\begin{prop}
For any $v\in V$ and $Q_1, Q_2\in\Sigma$ or $Q_1, Q_2\in\Sigma^*$ we have
\[(v, \Gamma(Q_1, Q_2)) = (\rho(v) Q_1, Q_2).\]
\end{prop}
\begin{proof}
It is enough to prove the claim with $Q_1, Q_2\in\Sigma$. Assume $v = \Gamma_-(f, f)$ for some $f\in S_-$, $Q_1 = s\otimes q_1$ and $Q_2 = s\otimes q_2$. Then the left-hand side is
\[(\Gamma_-(f, f), \Gamma_+(s, s)) (q_1, q_2) = 2(s, f)^2 (q_1, q_2).\]
The right-hand side is
\begin{align*}
(\rho(\Gamma_-(f, f) s\otimes q_1, s\otimes q_2) &= (2(s, f) f\otimes q_1, s\otimes q_2) \\
&= 2(s, f)^2 (q_1, q_2).
\end{align*}
\end{proof}

An important property of two-dimensional chiral supersymmetry is the following analog of Theorem \ref{thm:3psi}.

\begin{thm}
For $Q_1, Q_2, Q_3\in\Sigma$ we have
\[\rho(\Gamma(Q_1, Q_2))Q_3 = 0.\]
\label{thm:2d3psi}
\end{thm}
\begin{proof}
Indeed, $\Gamma(Q_1, Q_2)$ lies in $S_+^{\otimes 2}\subset V$, but the nonzero Clifford action is given by
\[S_-^{\otimes 2}\otimes (S_+\otimes W)\longrightarrow S_-\otimes W.\]
\end{proof}

We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$. The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing. Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.

Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]

\begin{thm}
For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
\label{thm:2dmatter3psi}
\end{thm}
\begin{proof}
Pick basis elements $s\in S_+$ and $f\in S_-$, so that
\[Q_1 = s\otimes q_1,\qquad Q_2 = s\otimes q_2,\qquad Q_3 = f\otimes q_3.\]
The right-hand side is
\begin{align*}
(q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
\end{align*}
We have
\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
so the left-hand side is
\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
By associativity of $A$ the two expressions are equal.
\end{proof}

\subsection{Supersymmetric Twisting}
The idea of twisting, originally developed by Witten \cite{WittenTQFT}, is to modify a classical BV theory by deforming the differential $Q_{\mr{BV}}$ by the action of a square-zero fermionic symmetry.

\begin{definition}
A \defterm{square-zero supercharge} is a nonzero element $Q\in\Sigma$ such that $\Gamma(Q, Q)=0$. Its \defterm{number of invariant directions} is the dimension of the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$.
\end{definition}

It is shown in \cite[Proposition 3.25]{ElliottSafronov} that the number $d$ of invariant directions is at least $n/2$. We will use the following adjectives for square-zero supercharges depending on $d$:
\begin{itemize}
\item A supercharge $Q$ is \defterm{topological} if $d = n$.

\item A supercharge $Q$ is \defterm{holomorphic} if $n$ is even and $d=n/2$.

\item A supercharge $Q$ is \defterm{minimal} if $n$ is odd and $d=(n+1)/2$.
\end{itemize}

In the intermediate case we refer to $Q$ as a \defterm{holomorphic-topological} (alternatively, partially topological) supercharge. The collection of all square-zero supercharges in dimensions 2 through 10 (where one restricts to supersymmetries with at most 16 supercharges) was studied in \cite{ElliottSafronov} and \cite{EagerSaberiWalcher}. In particular, the orbits of square-zero supercharges under the $R$-symmetry group, $\Spin(V)$ and the obvious scaling action of $\CC^\times$ are shown in Figure \ref{fig:superchargeorbits}.

Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
\[
I_{\fA} = \sum_{k \geq 0} I_{\fA}^{(k)} \in C^\bu(\fA, \oloc(\cE))
\]
where $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ as in Definition \ref{infinitesimal_action_def} and the classical field theory has an action of the $R$-symmetry group $G_R$.

\begin{definition} \label{def:twisting}
Suppose $(E, S, \omega)$ is a supersymmetric classical field theory and $Q$ a square-zero supercharge. The \defterm{$Q$-twisted classical field theory} is the $\ZZ/2$-graded classical field theory with the same bundle of $BV$ fields and the symplectic pairing $\omega$ and the BV action
\[S^Q = S + \sum_{k \geq 0} I_{\fA}^{(k)}(Q, \dots, Q).\]
\end{definition}

Given additional data, we may enhance the classical field theory.

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge. A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-grading on mod 2 on $E$ coincides with the fermionic grading.
\end{definition}

Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$. The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-grading $k$. But it also has cohomological degree $-k$. In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.

\begin{definition}
Let $Q\in\Sigma$ be a square-zero supercharge and suppose $G\rightarrow \Spin(V_\RR)$ is a fixed group homomorphism. A \defterm{twisting homomorphism} is a homomorphism $\phi\colon G\rightarrow G_R$ such that $Q$ is preserved under the composite $G\rightarrow \Spin(V_\RR)\times G_R$.
\end{definition}

The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action. However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$. However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.

\subsection{Dimensional Reduction of Supersymmetric Theories}

Suppose $V_\RR=\RR^n$ as before and choose a subspace $W_\RR\subset V_\RR$, so that $V_\RR = W_\RR\oplus W^\perp_\RR$. We denote $W=W_{\RR}\otimes_{\RR} \CC$.

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sec:susyalgebras}.

Recall from Proposition \ref{prop:dimensionalreductionunique} that the dimensional reduction of a classical field theory along the projection $p\colon V_\RR\rightarrow W_\RR$ exists and is unique. We have the following generalization of this statement to supersymmetric theories.

\begin{prop} \label{prop:susydimlred}
Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$. Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
\end{prop}

\begin{proof}
This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
\end{proof}

The following proposition is an immediate consequence of Proposition \ref{prop:susydimlred} and Definition \ref{def:twisting}.

\begin{prop}
Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$. Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
\label{prop:twistdimensionalreduction}
\end{prop}

\section{Supersymmetric Yang--Mills theories} \label{sec:SYM}

In this section we construct supersymmetry action on super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
\begin{itemize}
\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.

\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.

\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.

\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
\end{itemize}

There are a few additional possibilities that occur in dimension 2.

\begin{itemize}
\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.

\item (4 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$.

\item (2 supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.

\item (1 supercharge, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
\end{itemize}

In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills. So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.

\subsection{Pure Super Yang--Mills Theory}
\label{sect:gaugemultipletSUSY}

We begin with a description of certain pure supersymmetric Yang--Mills theories. Let $V_\RR$ be a real vector space equipped with a nondegenerate symmetric bilinear pairing and $V$ its complexification. Fix a $\ZZ/2\ZZ$-graded Clifford module $\Sigma\oplus \Sigma^*\rightarrow \CC$ with the associated $\Gamma$-pairings
\[\Gamma\colon \Sym^2(\Sigma)\rightarrow V,\qquad \Gamma\colon \Sym^2(\Sigma^*)\rightarrow V\]
defined as in Appendix \ref{sect:spinors}. We make the following assumption on this setup.

\begin{assumption}
For $Q_1, Q_2, Q_3\in\Sigma$ we have
\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
\label{assumption:3psi}
\end{assumption}

Explicitly, we consider the following cases:
\begin{itemize}
\item (\textbf{2d $\cN=(\cN_+, 0)$ supersymmetry}) We have $\dim(V) = 2$ and $\Sigma = S_+\otimes W$ for some complex vector space $W$ equipped with a nondegenerate symmetric bilinear pairing. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:2d3psi}.

\item (\textbf{3d $\cN=1$ supersymmetry}) We have $\dim(V) = 3$ and $\Sigma = S$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.

\item (\textbf{4d $\cN=1$ supersymmetry}) We have $\dim(V) = 4$ and $\Sigma = S_+\oplus S_-$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.

\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ for a two-dimensional complex symplectic vector space $W_+$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.

\item (\textbf{10d $\cN=(1, 0)$ supersymmetry}) We have $\dim(V) = 10$ and $\Sigma = S_+$. Assumption \ref{assumption:3psi} is satisfied by Theorem \ref{thm:3psi}.
\end{itemize}

Let $\fg$ be a Lie algebra equipped with a nondegenerate symmetric bilinear pairing. The fields of the Yang--Mills theory are as follows:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

\item A spinor $\lambda \in \Gamma(V_\RR; \Pi \Sigma \otimes \fg)$.

\item A ghost field $c\in\Gamma(V_\RR; \fg[1])$.
\end{itemize}

We also introduce their antifields $A^*\in\Omega^1(V_\RR; \fg[-1])$, $\lambda^*\in\Gamma(V_\RR; \Pi\Sigma^*\otimes \fg[-1])$ and $c^*\in\Gamma(V_\RR; \fg[-2])$. Let $\cE_{\gauge}$ denote the space of BV fields.

Denote by $F_A = \d A + \frac{1}{2}[A\wedge A]$ the curvature of $A$ and let $\sd\d_A$ be the twisted Dirac operator obtained from $\Gamma$ (see Appendix \ref{sect:spinors}).

The BRST action is given by
\[S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).\]

We introduce gauge transformations
\[\delta A = -\d_A c,\qquad \delta \lambda = [c, \lambda],\qquad \delta c = \frac{1}{2}[c, c],\]
so that the BV action is given by
\begin{equation}
S_{\gauge} = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd\d_A \lambda) + (\d_A c, A^*) + ([c, \lambda], \lambda^*) + \frac{1}{2}([c, c], c^*)\right).
\label{eq:YMBVaction}
\end{equation}

To simplify the notation, the pairing on $\fg$ from now on will be implicit.

The Poincar\'e group acts, in the sense of Definition \ref{group_action_def}, on Yang--Mills theory on $\RR^n$. Indeed, there is an obvious Poincar\'e action on fields where we use that $\Sigma$ is a representation of $\Spin(V_\RR)$. The corresponding Hamiltonian is given by
\begin{equation}
I_{\gauge}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, A^*) - (v.\lambda, \lambda^*) - (v.c)c^*\right),
\label{eq:YMPoincareaction}
\end{equation}
for $v\in\mf{iso}(V)$, where $v.\lambda$ contains both a derivative and the $\so(V)$ action on $\Sigma$.

We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
I_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
I_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

The following theorem summarizes the fact that super Yang--Mills theory is indeed supersymmetric in the sense of Definition \ref{dfn: super}.

\begin{thm}\label{thm:gaugemultipletSUSY}
The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\gauge}))$ satisfies the classical master equation
\[\d_{\mr{CE}} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang--Mills theory and so super Yang--Mills theory is supersymmetric.  
\end{thm}

The rest of the section will be devoted to the proof of the above theorem. The classical master equation decomposes into the following equations:
\begin{align*}
\{S_{\gauge}, I_{\gauge}^{(1)}\} &= 0 \\
\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} &= 0 \\
\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} &= 0 \\
\{I_{\gauge}^{(2)}, I_{\gauge}^{(2)}\} &= 0.
\end{align*}

Note that the last equation is automatically satisfied since $I_{\gauge}^{(2)}$ is independent of $\lambda$ and $c$. The rest of the claims will be proved in a sequence of Lemmas. To simplify the expressions, we drop the integrals.

\begin{lemma}
One has $\{S_{\gauge}, I_{\gauge}^{(1)}(Q)\} = 0$.
\label{lm:gaugemultiplet1}
\end{lemma}
\begin{proof}
Let us decompose $S_{\gauge} = \sum_{i=1}^5 S_{\gauge}^i$ into individual summands.

The first term gives
\begin{align*}
\{S_{\gauge}^1, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2} (\d_A \Gamma(Q, \lambda), F_A)\\
&= -\frac{1}{2}(-1)^{n-1} (\ast \d_A \ast F_A, \Gamma(Q, \lambda)).
\end{align*}

The second term gives
\begin{align*}
\{S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{\d}_A\lambda) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{\d}_A(\rho(F_A) Q)) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast \d_A\ast F_A) Q),
\end{align*}
where we have used Proposition \ref{prop:cliffordactionproperty3} and the Bianchi identity in the last line.

By \eqref{eq:Gammaspinorpairing} and Assumption \ref{assumption:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{\gauge}^1 + S_{\gauge}^2, I_{\gauge}^{(1)}(Q)\} = 0$.

Finally, $\{S_{\gauge}^3 + S_{\gauge}^4 + S_{\gauge}^5, I_{\gauge}^{(1)}(Q)\} = 0$ due to gauge-invariance of $I^{(1)}(Q)$.
\end{proof}

\begin{remark}
The previous Lemma expresses the fact that the pure super Yang--Mills action is supersymmetric; this was proven by Baez and Huerta in \cite{BaezHuerta}, and our proof essentially follows the proof in loc. cit.
\end{remark}

\begin{lemma}
One has
\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0.\]
\label{lm:gaugemultiplet2}
\end{lemma}
\begin{proof}
Evaluating the equation
\[\{S_{\gauge}, I_{\gauge}^{(2)}\} + \d_{\mr{CE}} I_{\gauge}^{(1)} + \frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\} = 0\]
on $v_1, v_2\in \mf{iso}(V)$, the claim reduces to the fact that \eqref{eq:YMPoincareaction} defines a strict Lie action. Evaluating it on $v\in\mf{iso}(V)$ and $Q\in\Sigma$, the claim reduces to the fact that $I_{\gauge}^{(1)}$ is Poincar\'{e}-invariant. So, the only nontrivial check is for $Q_1,Q_2\in\Sigma$.

The individual terms are
\begin{align*}
\frac{1}{2}\{I_{\gauge}^{(1)}, I_{\gauge}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(1)}(Q_2)\} \\
= &-\frac{1}{2}(\rho(\d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) + \frac{1}{2}(\Gamma(Q_2, \rho(F_A)Q_1), A^*) \\
&-\frac{1}{2}(\rho(\d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) + \frac{1}{2}(\Gamma(Q_1, \rho(F_A)Q_2), A^*),
\end{align*}
\begin{align*}
(\d_{\mr{CE}} I_{\gauge}^{(1)})(Q_1, Q_2) &= I_{\gauge}^{(1)}(\Gamma(Q_1, Q_2)) \\
&= (L_{\Gamma(Q_1, Q_2)}(A), A^*) -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
\end{align*}
and
\begin{align*}
\{S_{\gauge}, I_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
\end{align*}
The total coefficient in front of $A^*$ is
\[\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) + \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) + L_{\Gamma(Q_1, Q_2)} A - \d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
Using Proposition \ref{prop:cliffordactionproperty1} we get that the sum of the first two terms is $-\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.

The total coefficient in front of $c^*$ is
\[-\Gamma(Q_1, Q_2).c + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) - [\iota_{\Gamma(Q_1, Q_2)} A, c] = 0.\]

The total coefficient in front of $\lambda^*$ is
\begin{align*}
&-\frac{1}{2}\rho(\d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(\d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{\d}_A\lambda - \frac{1}{2}(Q_2, \sd{\d}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{\d}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
\end{align*}
Using Proposition \ref{prop:cliffordactionproperty2} the first, second, fifth and sixth terms combine to
\[-\frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{\d}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
which is equal to $\frac{1}{2} \sd{\d}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Assumption \ref{assumption:3psi}. Using the Clifford relation this term cancels the rest of the terms.
\end{proof}

Evaluating the equation
\[\d_{\mr{CE}} I_{\gauge}^{(2)} + \{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\} = 0\]
on $v_1, v_2, v_3\in\mf{iso}(V)$ or on $v_1, v_2\in\mf{iso}(V)$ and $Q\in\Sigma$ we automatically get zero. Evaluating it on $v\in\mf{iso}(V)$ and $Q_1, Q_2\in\Sigma$ we get Poincar\'{e}-invariance of $I_{\gauge}^{(2)}$.

\begin{lemma}
\[\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
for every $Q_1, Q_2, Q_3\in\Sigma$.
\label{lm:gaugemultiplet3}
\end{lemma}
\begin{proof}
We have
\begin{align*}
\{I_{\gauge}^{(1)}(Q_1), I_{\gauge}^{(2)}(Q_2, Q_3)\} = &-\iota_{\Gamma(Q_2, Q_3)}\Gamma(Q_1, \lambda) c^* - \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) \\
&+ \frac{1}{2}(Q_2, \rho(A^*)Q_1)(Q_3, \lambda^*) + \frac{1}{2}(Q_3, \rho(A^*) Q_1)(Q_2, \lambda^*).
\end{align*}

$\{I_{\gauge}^{(1)}, I_{\gauge}^{(2)}\}(Q_1, Q_2, Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization of the term with $c^*$ is zero. The Clifford relation implies that
\begin{align*}
\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
\end{align*}
Therefore, again using Assumption \ref{assumption:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
\end{proof}

\subsection{Coupling to Matter Multiplets}
\label{sect:mattermultipletSUSY}

\brian{How do we see the various flavors of matter multiplets? For instance, in $2d (0,2)$ there is the Fermi multiplet and the chiral multiplet. 
Your description only sees the chiral.
In $2d (0,4)$ there are even more: the hypermultiplet (two $(0,2)$ chirals), the twisted hypermultiplet (the same as the hyper, different $R$-symmetry), the fermi multiplet (two $(0,2)$ fermi multiplets). 
I'm not sure which your description sees, but I have a hunch it's the $(0,4)$ hypermultiplet. 
What is the reason for only seeing certain multiplets via this general setup?
} \chris{Presumably pure $\mc N = (0,N)$ means a $(0,2)$ vector coupled to $N-2$ Fermi multiplets, so some of these are already covered by the classification?  Perhaps your concern is that you want a formalism that allows Fermis that are not adjoint valued?  I don't think the difference between this hyper and twisted hyper is germane here: the proof of supersymmetry is that there is an action of super Poincar\'e, it doesn't involve the action of R-symmetry.}

In this section we describe the coupling of super Yang--Mills theory to matter valued in a $\fg$-representation $P$, i.e. the supersymmetric gauged linear $\sigma$-models. Our description of the supersymmetry of the matter multiplet is inspired by the presentation of the supersymmetric nonlinear $\sigma$-models by Deligne and Freed in \cite[Chapter 3]{DeligneFreed}.

Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}. In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras}. Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure. Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}. We make the following additional assumption.

\begin{assumption}
For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
\label{assumption:matter3psi}
\end{assumption}

Explicitly, we consider the following cases:
\begin{itemize}
\item (\textbf{2d $\cN=(1, 0)$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(2, 0)$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{2d $\cN=(4, 0)$ supersymmetry}) $A = \eend(Z)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:2dmatter3psi}.

\item (\textbf{3d $\cN=1$ supersymmetry}) $A = \CC$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{4d $\cN=1$ supersymmetry}) $A = \CC[x]/(x^2+1)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.

\item (\textbf{6d $\cN=(1, 0)$ supersymmetry}) $A = \eend(Z)$. Assumption \ref{assumption:matter3psi} is satisfied by Theorem \ref{thm:matter3psi}.
\end{itemize}

Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
\[(av, w) = (v, \sigma(a)w).\]
Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing. Explicitly, for $A=\CC, \CC\otimes_\RR\CC, \mathbb{H}\otimes_\RR\CC$ we get the following data:
\begin{itemize}
\item $A=\CC$. We are looking for a $\fg$-representation $P$ equipped with a nondegenerate symmetric bilinear pairing.

\item $A=\CC[x]/(x^2+1)$. A left $A$-module $P$ splits as $P=P_+\oplus P_-$, where $x$ acts as $\pm i$ on $P_{\pm}$. Note that with respect to the right $A$-action $x$ acts as $\mp i$ on $P_{\pm}$. So, the symmetric bilinear pairing identifies $P_+\cong P_-^*$. In other words, the data boils down to a $\fg$-representation $R$, so that $P = R\oplus R^*$.

\item $A=\eend(Z)$. A left $A$-module is necessarily of the form $P\cong Z\otimes U$, where $A$ just acts on $Z$. Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$. So, the data boils down a symplectic $\fg$-representation $U$.
\end{itemize}

We are going to construct a theory on $V_\RR$ describing a matter multiplet valued in $P$. The BRST fields are given as follows:
\begin{itemize}
\item a scalar $\phi\in\Gamma(V_\RR; P)$;
\item a spinor $\psi\in\Gamma(V_\RR; \Pi \Sigma^*\otimes_A P)$.
\end{itemize}
As usual, we denote the antifields by $\phi^*\in\Gamma(V_\RR; \Pi P)$ and $\psi^*\in\Gamma(V_\RR; \Sigma\otimes_A P)$.

We extend the pairings on $P$ and between $\Sigma$ and $\Sigma^*$ to a pairing between $\Sigma\otimes_A P$ and $\Sigma^*\otimes_A P$ in the following way. Given $\sum_i \tilde{s}_i\otimes v_i\in \Sigma^*\otimes_A P$ and $\sum_j s_j\otimes w_j\in\Sigma\otimes_A P$, their pairing is
\begin{equation}
\sum_{i, j} \Re((v_i, w_j)^A (s_j, \tilde{s}_i)^A),
\label{eq:spinorialmatterpairing}
\end{equation}
where we extend both pairings to $A$-valued pairings using Lemma \ref{lm:extendpairing}. We may also extend the $\Gamma$-pairing to a map
\[\Gamma\colon \Sym^2(\Sigma^*\otimes_A P)\rightarrow V\]
defined by the property
\[(v, \Gamma(\psi_1, \psi_2)) = (\psi_1, \rho(v) \psi_2),\qquad v\in V,\ \psi_i\in \Sigma^*\otimes_A P.\]

The BV action for the matter multiplet is
\[
S_{\matter} = \int_{V_\RR} \dvol \left(\frac{1}{2}  (\d_A \phi, \d_A \phi) + (\psi , \sd \d_A \psi) + 2 (\lambda\phi, \psi) + (c\psi, \psi^*) - (c\phi, \phi^*)\right),
\]
where we use the pairing \eqref{eq:spinorialmatterpairing} in the second term.

It is Poincar\'{e}-invariant with the corresponding Hamiltonian
\begin{equation}
I_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
\label{eq:matterPoincareaction}
\end{equation}
for $v\in\mf{iso}(V)$.

The action of supersymmetry is given by a linear and quadratic functional:
\begin{align}
I_{\matter}^{(1)} (Q) & = \int_{V_\RR}\dvol\left( ((Q, \psi), \phi^*) + \frac{1}{2}(\rho(\d_A \phi) Q, \psi^*)\right) \label{eq:matterI1} \\
I_{\matter}^{(2)} (Q_1 , Q_2) & = \frac{1}{4}\int_{V_\RR} \dvol(\Gamma(Q_1, Q_2) , \Gamma(\psi^*, \psi^*)) \label{eq:matterI2}
\end{align}
where $Q, Q_1,Q_2 \in \Sigma$.

We consider the full action of the super Yang--Mills theory
\[S_{\BV} = S_{\gauge} + S_{\matter}\]
together with a supersymmetry action functionals
\[I^{(1)} = I^{(1)}_{\gauge} + I^{(1)}_{\matter},\qquad I^{(2)} = I^{(2)}_{\gauge} + I^{(2)}_{\matter}.\]

The following result states that these functionals encode an off-shell action of the supersymmetry algebra.

\begin{thm}
The functional $\fS = S_{\BV} + I_{\BV}^{(1)} + I_{\BV}^{(2)}$ satisfies the classical master equation
\begin{equation}
\label{CMEYM}
\d_{\mr{CE}} \fS + \frac{1}{2} \{\fS, \fS\} = 0 .
\end{equation}
\label{thm:YMSUSY}
\end{thm}

The rest of this section is devoted to the proof of Theorem \ref{thm:YMSUSY}. The classical master equation \eqref{CMEYM} decomposes into a sequence of equations
\begin{equation}
\label{CMEYM2}
\begin{array}{rrrrrr}
\{S_{\BV} , I^{(1)}\} & = & 0 \\ 
\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} & = & 0 \\
\d_{\mr{CE}} I_{\matter}^{(2)} + \{I_{\matter}^{(1)}, I_{\matter}^{(2)}\} & =& 0 \\
\{I_{\matter}^{(2)}, I_{\matter}^{(2)}\} & =& 0
\end{array}
\end{equation}

The last equation is automatically satisfied since $I^{(2)}$ is independent of the fields $\phi, \psi, A, \lambda$.

The first equation in \eqref{CMEYM2} states that the classical action is supersymmetric.

\begin{lemma} \label{lem:YM1}
One has $\{S_{\BV}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
\end{lemma}
\begin{proof}
Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter}^i$ into individual summands.

The first term gives
\begin{align*}
\{S_{\matter}^1, I^{(1)}(Q)\} &= -(\d_A\phi, \d_A(Q, \psi)) + (\Gamma(Q, \lambda)\phi, \d_A\phi) \\
&= \d_A^* \d_A\phi (Q, \psi) + (\Gamma(Q, \lambda)\phi, \d_A\phi).
\end{align*}

The second term gives
\begin{align*}
\{S_{\matter}^2, I^{(1)}(Q)\} &= -(\psi, \sd \d_A \rho(\d_A \phi) Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi) \\
&= -(\psi, \rho(F_A) Q)\phi - \d_A^*\d_A \phi(\psi, Q) - (\psi, \rho(\Gamma(Q, \lambda))\psi),
\end{align*}
where we have used Proposition \ref{prop:cliffordactionproperty3} in the second line.

The third term gives
\begin{align*}
\{S_{\matter}^3, I^{(1)}(Q)\} &= ((\rho(F_A)Q) \phi, \psi) + 2(\lambda(Q, \psi), \psi) - (\lambda\phi, \rho(\d_A \phi) Q) \\
&= ((\rho(F_A)Q) \phi, \psi) + (\rho(\Gamma(Q, \lambda))\psi, \psi) - (\Gamma(\lambda\phi, Q), \d_A \phi),
\end{align*}
where we have used Assumption \ref{assumption:matter3psi} in the middle term and \eqref{eq:Gammaspinorpairing} in the last term. It is then obvious that
\[\{S_{\matter}^1 + S_{\matter}^2 + S_{\matter}^3, I^{(1)}(Q)\} = 0.\]

Finally, the terms $\{S_{\matter}^4 + S_{\matter}^5 + S_{\gauge}^3, I^{(1)}(Q)\}$ are zero due to gauge-invariance of $I^{(1)}(Q)$ while the rest of the terms are zero by Lemma \ref{lm:gaugemultiplet1}.
\end{proof}

Next, we move on to the second equation in \eqref{CMEYM2}.

\begin{lemma} 
One has
\begin{equation}\label{CMEYM3}
\{S_{\matter}, I^{(2)}\} + \d_{\mr{CE}} I_{\matter}^{(1)} + \{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\} + \frac{1}{2} \{I_{\matter}^{(1)}, I_{\matter}^{(1)}\} = 0 .
\end{equation}
\end{lemma}
\begin{proof}
Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action. Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant. So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.

The individual terms are:
\begin{align*}
\frac{1}{2}\{I_{\matter}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) =& -\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} \\
=&-\frac{1}{2}(Q_1, \rho(\d_A \phi) Q_2)\phi^* - \frac{1}{2}(Q_2, \rho(\d_A \phi)Q_1)\phi^* \\ &  +\frac{1}{2}(\rho(\d(Q_1,\psi))Q_2, \psi^*) +\frac{1}{2} (\rho(\d(Q_2, \psi)) Q_1, \psi^*),
\end{align*}

\begin{align*}
\{I_{\gauge}^{(1)}, I_{\matter}^{(1)}\}(Q_1, Q_2) = &-\{I_{\gauge}^{(1)}(Q_1), I_{\matter}^{(1)}(Q_2)\} - \{I_{\gauge}^{(1)}(Q_2), I_{\matter}^{(1)}(Q_1)\} \\
=& -\frac{1}{2}(\rho(\Gamma(Q_1, \lambda))(\phi Q_2), \psi^*) - \frac{1}{2}(\rho(\Gamma(Q_2, \lambda))(\phi Q_1), \psi^*),
\end{align*}

\[
(\d_{\mr{CE}}I_{\matter}^{(1)})(Q_1,Q_2) = L_{\Gamma(Q_1,Q_2)} (\phi)\phi^* - (\Gamma(Q_1,Q_2).\psi, \psi^*),
\]

and
\[
\{S_{\matter}, I^{(2)}(Q_1,Q_2)\} =  \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \d_A \psi - 2 \lambda\phi + c\psi^*) - ((\iota_{\Gamma(Q_1, Q_2)} A)\psi, \psi^*) + ((\iota_{\Gamma(Q_1, Q_2)} A)\phi, \phi^*)
\]

We first collect all terms in equation \eqref{CMEYM3} proportional to $\phi^*$:
\[
-\frac{1}{2} (Q_1, \rho(\d_A\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d_A \phi) Q_1) + L_{\Gamma(Q_1,Q_2)} \phi + (\iota_{\Gamma(Q_1, Q_2)} A)\phi.
\]

By \eqref{eq:Gammaspinorpairing} we observe that the first two terms cancel with the last two terms.

Next, we collect all terms in equation \eqref{CMEYM3} containing $\psi^*$ and $\psi$:
\begin{equation}\label{psistar}
\frac{1}{2} \sd \d_A Q_2(Q_1 \psi)^A + \frac{1}{2} \sd \d_A Q_1(Q_2, \partial_i\psi)^A - \Gamma(Q_1,Q_2) . \psi + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \d_A \psi - (\iota_{\Gamma(Q_1, Q_2)} A)\psi.
\end{equation}
Applying Assumption \ref{assumption:matter3psi} to $Q_3 = \psi$, the first two terms become $\frac{1}{2} \sd \d_A \rho(\Gamma(Q_1,Q_2) \psi)$. 
Finally, by the Clifford identity the sum of this term with the fourth term in \eqref{psistar} is precisely $\iota_{\Gamma(Q_1,Q_2)}\d_A \psi$ which cancels the remaining terms.
\end{proof}

\begin{lemma}
\[\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
for every $Q_1, Q_2, Q_3\in \Sigma$.
\end{lemma}
\begin{proof}
We have
\begin{align*}
\{I_{\matter}^{(1)}(Q_1), I_{\matter}^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
\end{align*}
The expression
$\{I_{\matter}^{(1)}, I_{\matter}^{(2)}\}(Q_1,Q_2,Q_3)$ is obtained by cyclically symmetrizing the above expression. By Assumption \ref{assumption:3psi} the cyclic symmetrization is identically zero.
\end{proof}

\part{Classification of Twists}

\section{Dimension 10}

The 10-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 16-dimensional semi-spin representations of $\Spin(10, \CC)$, and where $W_+$ and $W_-$ are complex vector spaces equipped with nondegenerate symmetric bilinear pairings. There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(0, 1)$ supersymmetries. We concentrate on the first case, the second case being identical. So, we fix $W_+=\CC$ and $W_- = 0$.

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1,0)} Super Yang--Mills}

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.

This theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory. Such a supercharge is stabilized by $G=\SU(5)\subset \Spin(10, \CC)$.
\end{itemize}

\subsubsection{Holomorphic twist}
\label{sect:10dholomorphictwist}

Let $Q\in\Sigma$ be a square-zero supercharge. The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$. Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$. Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$. In other words, $L$ defines a (linear) complex structure on $V_\RR$. Moreover, we may canonically identify $\sigma(L)\cong L^*$.

Let $\ML(L)$ be the metalinear group of $L$. Under the embedding $\ML(L)\subset \Spin(V)$, the semi-spin representation $\Sigma=S_+$ decomposes as
\[\Sigma = \det(L)^{1/2} \oplus \wedge^2 L^*\otimes \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2}.\]
$Q\in\Sigma$ lies in the first summand, so the choice of $Q$ is equivalent to the choice of a (linear) K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$. The square of this half-density defines a Calabi--Yau structure on $M$.

We will now rewrite the fields and the action in terms of the Calabi--Yau structure. Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{5, 0}(M)$ the holomorphic volume form and $\Lambda\colon \Omega^{p+1, q+1}(M)\rightarrow \Omega^{p, q}(M)$ the dual Lefschetz operator. We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^5}{5!}.\]

The vector representation decomposes as
\[\Omega^1(M)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 1}(M),\]
the semi-spin representation $S_+$ decomposes as
\[\Omega^0(M; S_+)\cong \Omega^{1, 0}(M)\oplus \Omega^{0, 2}(M)\oplus \Omega^0(M)\]
and the semi-spin representation $S_-$ decomposes as
\[\Omega^0(M; S_-)\cong \Omega^{0, 1}(M)\oplus \Omega^{2, 0}(M)\oplus \Omega^0(M).\]
Under this decomposition the scalar pairing $S_+\otimes S_-\rightarrow \CC$ corresponds to the wedge product of individual components post-composed with $\Lambda$. Under the above decompositions the Clifford multiplication of a vector $A = A_{1, 0} + A_{0, 1}$ and a spinor $\lambda = \rho + B + \chi\in S_+$ is given by
\[\rho(A)\lambda = (A_{0, 1}\chi + \Lambda(A_{1, 0}\wedge B), A_{1, 0}\wedge \rho + \ast(A_{0, 1}\wedge B\wedge\Omega), \Lambda(A_{0, 1}\wedge \rho))\in S_-.\]

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Fermions $\rho\in\Omega^{1, 0}(M; \Pi\gg)$, $B\in\Omega^{0, 2}(M; \Pi\gg)$, $\chi\in\Omega^0(M; \Pi\gg)$.
\item A ghost field $c\in\Omega^0(M; \gg)[1]$.
\end{itemize}
We denote their antifields by $A_{1, 0}^*, A_{0, 1}^*, \rho^*, B^*, \chi^*, c^*$.

The BV action of the theory is obtained from \eqref{eq:YMBVaction} by decomposing it in terms of the above fields. To write it out we will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.

\begin{prop}
Let $(M, \omega)$ be a K\"{a}hler $d$-fold and decompose
\[\Omega^2(M) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\CC\omega\oplus \Omega^{1, 1}_\perp(M)).\]
Then
\begin{enumerate}
\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\CC\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.

\item For a form $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]

\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]

\item For $\alpha\in\CC\omega$ we have
\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
\end{enumerate}
\end{prop}

\begin{corollary} \label{Kahler_YM_term_cor}
Let $M$ be a K\"{a}hler $d$-fold and $F = F_{2, 0} + F_{1, 1} + F_{0, 2}$ a two-form. Then
\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
\end{corollary}

Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it. The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
\begin{align}
S_{\mr{BRST}} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\rho) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \label{eq:10dBRST} \\
S_{\mr{anti}} &= \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + [\chi, c]\chi^* + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \label{eq:10danti} \\
I^{(1)} &= \int \dvol\left(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*) + \frac{1}{2}\Lambda F_{1, 1} \chi^*\right) \\
I^{(2)} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align}

\begin{thm}
The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$. Moreover, the equivalence is $\SU(5)$-equivariant.
\label{thm:10dholomorphictwist}
\end{thm}
\begin{proof}
First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}. So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
\begin{align*}
S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
&+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
\end{align*}

Next, we have a term $\int \dvol \rho\wedge A_{1, 0}^*$ in the action, i.e. $(\rho, A_{1, 0})$ is a trivial BRST doublet, so by Proposition \ref{prop:BRSTdoublet} we may remove it. The above theory then becomes perturbatively equivalent to the theory without fields $\rho,\rho^*,A_{1,0},A_{1,0}^*$ and with the BV action
\[
S_0 = \int \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega + \dvol\left((\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^* + (F_{0, 2}, B^*)\right)
\]
Up to rescaling of the antifields, it coincides with the BV action for holomorphic Chern--Simons (see Section \ref{gen_CS_section}).
\end{proof}

\begin{remark}
A similar claim was previously proved by Baulieu \cite{Baulieu} by adding an auxiliary field to 10d $\mc N=(1, 0)$ super Yang--Mills.
\end{remark}

\section{Dimension 9}

The 9-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 16-dimensional spin representation of $\Spin(9, \CC)$ and $W$ is a complex vector space equipped with a nondegenerate symmetric bilinear pairing. There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.

This theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 5 invariant directions and does not admit a compatible homomorphism $\alpha$. So, it gives rise to a $\ZZ/2\ZZ$-graded holomorphic theory. Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(9, \CC)$.
\end{itemize}

We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra. Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.

\subsubsection{Minimal twist}
\label{sect:9dminimaltwist}

Let $Q\in\Sigma$ be a square-zero supercharge. Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp\subset V$. Its orthogonal complement $L$ is maximal isotropic and $L^{\perp}/L$ is one-dimensional. Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$. Moreover, $N = L^{\perp}\cap \sigma(L^{\perp})\subset V$ is a $\sigma$-stable one-dimensional subspace, we let $N_\RR$ be the $\sigma$-invariants of $N$. Therefore, we get a decomposition
\[V = L\oplus \sigma(L)\oplus N,\]
where $L^{\perp} = L\oplus N$.

Under the embedding $\ML(L)\subset \Spin(V)$ the spin representation $\Sigma=S$ decomposes as
\[\Sigma = \wedge^\bullet L\otimes \det(L)^{-1/2}\]
and the supercharge $Q$ lies in the one-dimensional subspace $\det(L)^{1/2}\subset \Sigma$. Therefore, the choice of $Q$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.

It will be convenient to perform a computation of the twist in a slightly more general setting which will be useful for lower-dimensional computations.

Suppose $L$ is a complex vector space equipped with a K\"ahler structure and a complex half-density. Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR = L\times N$ (a 10-dimensional real vector space). By the results of Section \ref{sect:10dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density.

The dimensional reduction of 10d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(N_\RR)$. We consider a twisting homomorphism $\phi\colon \SU(L)\times \Spin(N_\RR)\rightarrow G_R=\Spin(N_\RR)$ given by the projection onto the second factor under which $Q$ is preserved.

\begin{thm}
The twist of $(5+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\SU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:10dCSreduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:10dholomorphictwist} the twist of 10d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory. Moreover, the equivalence is $\SU(L)\times \SU(N)$-equivariant. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, B\fg)$ and this isomorphism is $\SU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.

Therefore, we just need to establish that the $\Spin(N_\RR)$-action on the twisted $(5+\dim(L))$-dimensional super Yang--Mills obtained using the twisting homomorphism coincides with the $\Spin(N_\RR)$-action on the generalized Chern--Simons theory. The $\Spin(N_\RR)$-action on the fields of $(5+\dim(L))$-dimensional super Yang--Mills is obtained via the homomorphism
\[\Spin(N_\RR)\xrightarrow{\mathrm{diagonal}}\Spin(N_\RR)\times \Spin(N_\RR)\hookrightarrow \Spin(N_\RR\oplus N_\RR),\]
where the diagonal embedding comes from the identity map to the partial Lorentz group $\Spin(N_\RR)$ and the twisting homomorphism, i.e. the identity map, to the $R$-symmetry group $G_R=\Spin(N_\RR)$. The $\SO(N_\RR)$-action on the fields of the generalized Chern--Simons theory is given by the composite
\[\SO(N_\RR)\xrightarrow{\eqref{eq:SOtoSU}} \SU(N)\longrightarrow \SO(N_\RR\oplus N_\RR)\]

The claim then follows from the commutativity of the diagram
\[
\xymatrix@C=2cm{
\SO(N_\RR) \ar^-{\mathrm{diagonal}}[r] \ar^{\eqref{eq:SOtoSU}}[d] & \SO(N_\RR)\times \SO(N_\RR) \ar[d] \\
\SU(N) \ar[r] & \SO(N_\RR\oplus N_\RR).
}
\]
\end{proof}

We will now concentrate on the 9-dimensional case.

\begin{thm}
The minimal twist of 9d $\mc N=1$ super Yang--Mills on $M=\CC^4\times \RR$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$. Moreover, the equivalence is $\SU(4)$-equivariant.
\label{thm:9dminimaltwist}
\end{thm}
\begin{proof}
Any square-zero supercharge in the 9-dimensional supersymmetry algebra is square-zero in the 10-dimensional supersymmetry algebra. The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^4$.
\end{proof}

\section{Dimension 8}

The 8-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 8-dimensional semi-spin representations of $\Spin(8, \CC)$ and $W$ is a complex vector space. The semi-spin representations carry nondegenerate symmetric bilinear pairings $S_{\pm}\otimes S_{\pm}\rightarrow \CC$. There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC$.

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.

This theory admits three twists:
\begin{itemize}
\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm} = 0$. These are holomorphic. Moreover, we have an isomorphism $\alpha\colon \U(1)\xrightarrow{\sim} \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory. Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$. We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\cong G_R$, so the twisted theory carries an action of $\MU(4)$.

\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm}\neq 0$. These are topological. As before, we may choose a compatible homomorphism $\alpha$, so they give rise to a $\ZZ$-graded topological theory. Such a supercharge is stabilized by $\Spin(7, \RR)\subset \Spin(8, \CC)$.

\item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$. The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$. The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$. We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
\end{itemize}

\subsubsection{Holomorphic twist}
\label{sect:8dholomorphictwist}

Suppose $Q\in S_+$ such that $(Q, Q)_{S_+}=0$. As in Section \ref{sect:10dholomorphictwist}, the data of such $Q$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.

We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \RR)$ under which $Q$ becomes scalar. Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action. In fact, this action will factor through $\U(4)$ by a direct observation.

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0}\in\Omega^{1, 0}(M; \gg)$ and $A_{0, 1}\in\Omega^{0, 1}(M; \gg)$.
\item Scalar fields $\phi\in\Omega^{4,0}(M; \gg)[2]$ and $\wt \phi\in\Omega^{0, 4}(M; \gg)[-2]$.
\item Fermions $\chi\in\Omega^0(M; \gg)[-1]$, $B\in\Omega^{0, 2}(M; \gg)[-1]$, $\wt \chi\in\Omega^{0, 4}(M; \gg)[-1]$, $\rho\in\Omega^{1, 0}(M; \gg)[1]$ and $C\in\Omega^{3, 0}(M; \gg)[1]$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

\begin{thm}
The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$. Moreover, the equivalence is $\U(4)$-equivariant.
\label{thm:8dholomorphictwist}
\end{thm}
\begin{proof}
8d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 10d $\cN=1$ super Yang--Mills theory. Under dimensional reduction the 10d fields from Section \ref{sect:10dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
\rho&\rightsquigarrow \rho, \wt\chi \\
B&\rightsquigarrow B, C.
\end{align*}

The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}). We are left to check that the equivalence respects  the gradings and the $\U(4)$-action. Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
&&\ar@{}^{\bigoplus}[r] &&& \\
\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
}
\]
concentrated in cohomological degrees $-2, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory.
\end{proof}

\subsubsection{Topological twist}

Next we discuss the case of the topological twist. We are going to prove that it is perturbatively trivial. In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and decribe the corresponding family of twisted theories.

Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$. Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. Moreover, fix a complex volume form on $L$. Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$. Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in S_+
\label{eq:8dHodgefamily}
\end{equation}
for $t\in\CC$. We have
\[(Q_t, Q_t) = t,\]
so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.

We will use the notation for fields of 8d $\cN=1$ super Yang--Mills from Section \ref{sect:8dholomorphictwist}. Using the Calabi--Yau structure we will regard $C\in\Omega^{0, 1}(\CC^4;\fg)[1]$ and $\wt\chi\in\Omega^0(\CC^4;\fg)[-1]$. First, we are going to write the functionals \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2} in terms of these fields.

\begin{prop}
The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(C, A_{0, 1}^*) - (\wt \chi + t\chi)\wt \phi^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}\phi, C^*) + (t\dd_{A_{1, 0}} \phi, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}(Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2}\Omega^{-1}B^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t\phi c^*\right).
\end{align*}
\end{prop}

The action of the twisted 8d super Yang--Mills theory is given by
\[S_{Q_t} = S_{\mathrm{BRST}} + S_{\mathrm{anti}} + I^{(1)}(Q_t) + I^{(2)}(Q_t),\]
where $S_{\mathrm{BRST}}$ and $S_{\mathrm{anti}}$ are given by \eqref{eq:10dBRST} and \eqref{eq:10danti} respectively.

We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(2, \RR)$ with respect to which $Q_t$ has weight $1$, so the $Q_t$-twisted theory will have a $\ZZ$-grading.

\begin{thm}
The twist of 8d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the holomorphic Hodge theory $\map(\CC^4, B\fg_{\mr{Hod}})$. Moreover, this equivalence is $\SU(4)$-equivariant.
\label{thm:8dHodgetwist}
\end{thm}
\begin{proof}
The proof proceeds as in the proof of Theorem \ref{thm:10dholomorphictwist} with slight modifications.

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt\phi\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + \int\dvol\left(-t(C, A_{0, 1}^*) + t\phi c^* + \frac{t}{2} \Omega^{-1} B^*\wedge B^*\right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$. Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:8dholomorphictwist})
\[
\xymatrix@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
\Omega^0(\CC^4; \gg)_{\phi} \ar[r] \ar@{-->}^{t\id}[ur] & \Omega^{0,1}(\CC^4; \gg)_C \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,2}(\CC^4; \gg)_{B^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] \ar@{-->}^{t\id}[ur] &\Omega^{0,4}(\CC^4; \gg)_{c^*} \ar@{-->}^{t\id}[ur] &
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

\begin{cor}
The topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively trivial.
\label{cor:8dtopologicaltwist}
\end{cor}
\begin{proof}
The topological twist of 8d $\cN=1$ super Yang--Mills is the twist by $Q_t$ with $t\neq 0$. By Theorem \ref{thm:8dHodgetwist} it is equivalent to the $t\neq 0$ specialization of the holomorphic Hodge theory which by Proposition \ref{prop:Hodgetheoryspecialization} is perturbatively trivial.
\end{proof}

\subsubsection{Partially topological twist}

Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.

\begin{thm}
The partially topological twist of 8d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^3\times \RR^2_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\SU(3)\times \Spin(2, \RR)$-equivariant.
\label{thm:8dpartiallytopologicaltwist}
\end{thm}
\begin{proof}
Since $Q_+$ and $Q_-$ satisfy $(Q_\pm, Q_\pm)_{S_\pm} = 0$, they lift to a square-zero supercharge in the 10-dimensional supersymmetry algebra. The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^3$.
\end{proof}

\section{Dimension 7} \label{7d_section}

The 7-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 8-dimensional spin representation of $\Spin(7, \CC)$ and $W$ is a complex symplectic vector space.  The spin representation carries a nondegenerate symmetric bilinear pairing $S\otimes S\rightarrow \CC$. There is a Yang--Mills theory with $\mc N=1$ supersymmetry, so we fix $W = \CC^2$.

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills}

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.

This theory admits three twists:
\begin{itemize}
\item Rank 1 supercharges $Q=\alpha\otimes w\in S\otimes W$, where $(\alpha, \alpha)_S = 0$. These are minimal, i.e. the number of invariant directions is 4. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$. We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \RR)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.

\item Rank 1 supercharges $Q = \alpha \otimes w \in S \otimes W$, where $(\alpha, \alpha)_S\neq 0$. These are topological and stabilized by $G_2\subset \Spin(7, \CC)$. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.

\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor, so tht theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
\end{itemize}

\subsubsection{Minimal twist}

Denote the image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ by $L^\perp$, so that its orthogonal complement $L\subset V$ is a 3-dimensional isotropic subspace. As in Section \ref{sect:9dminimaltwist}, the data of a partially topological supercharge is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a half-density.

We have $Q=\alpha\otimes w\in S\otimes W$ and denote by $\alpha\colon \U(1)\hookrightarrow G_R=\Spin(3, \RR)$ the subgroup under which $w$ has weight $1$. We consider the twisting homomorphism given by the composite
\[\phi\colon \MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
As before, the $\MU(3)$-action on the theory factors through a $\U(3)$-action.

\begin{thm}
The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\RR^7$ is perturbatively equivalent to the generalized BF theory on $\CC^3\times \RR$ with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:7dminimaltwist}
\end{thm}
\begin{proof}
The minimal supercharge $Q=\alpha\otimes w$ may be obtained by dimensional reduction of the holomorphic supercharge in the 8-dimensional supersymmetry algebra. Therefore, the minimal twist of 7d $\cN=1$ super Yang--Mills on $\CC^3\times \RR$ is obtained by dimensional reduction from the holomorphic twist of 8d $\cN=1$ super Yang--Mills on $\CC^4$. The claim then follows from Theorem \ref{thm:8dholomorphictwist} and Corollary \ref{cor:BFholomorphicreduction}.
\end{proof}

\subsubsection{Topological twist}

Next we study the topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L\times \RR$. Under $\SU(L)\subset \Spin(V_\RR)$ the spin representation decomposes as
\[S\cong \wedge^\bullet L.\]
In particular, it contains two trivial summands: $\CC\alpha$ in the lowest degree and $\CC\beta$ in the top degree.

Consider a family of square-zero supercharges
\begin{equation}
Q_t = (\alpha + t\beta)\otimes w
\label{eq:7dHodgefamily}
\end{equation}
for some nonzero $w\in W$. We have $(\alpha + t\beta, \alpha + t\beta)=t$, so at $t=0$ we have a minimal supercharge and at $t\neq 0$ we have a topological supercharge.

\begin{thm}
The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:7dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions. The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$. The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
\end{proof}

\begin{cor}
The topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively trivial.
\end{cor}

\subsubsection{Partially topological twist}

Finally, we discuss the case of a partially topological twist. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor.

\begin{thm}
The partially topological twist of 7d $\cN=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC^2\times \RR^3_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\SU(2)\times \Spin(3, \RR)$-equivariant.
\label{thm:7dpartiallytopologicaltwist}
\end{thm}
\begin{proof}
Any partially topological supercharge in the 7-dimensional supersymmetry algebra lifts to a square-zero supercharge in the 10-dimensional supersymmetry algebra. The claim follows from Theorem \ref{thm:10dCSreduction} applied to $L=\CC^2$.
\end{proof}

\section{Dimension 6}

The 6-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W_+\oplus S_-\otimes W_-$, where $S_+, S_-$ are the 4-dimensional semi-spin representations of $\Spin(6, \CC)\cong \SL(4, \CC)$ and $W_+, W_-$ are complex symplectic vector spaces. We have isomorphisms $S_+\cong S_-^*$.

There are Yang--Mills theories with $\cN=(1, 0)$ or $\cN=(1, 1)$ supersymmetry, which we consider separately.

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}

The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $U$ a complex symplectic $\fg$-representation. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.

\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
\end{itemize}

This theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory. If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading. Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$. We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(3)$-action.
\end{itemize}

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item A gauge field $A \in \Omega^1(M;\fg)$.
\item Gauge fermion $\lambda \in \Omega^0(M; \Pi S_+ \otimes W_+ \otimes \fg)$. 
\item Matter boson $\phi\in\Omega^0(M; W_+\otimes U)$.
\item Matter fermion $\psi\in\Omega^0(M; \Pi S_-\otimes U)$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

\subsubsection{Holomorphic twist}

Consider a nonzero $Q\in S_+\otimes W_+$. Since $\wedge^2(S_+)\cong V$, the square-zero condition is equivalent to the condition that $Q$ has rank 1, i.e. $Q=q_+\otimes w_1\in S_+\otimes W_+$. We will also fix $w_2\in W_+$ such that $(w_1, w_2) = 1$.

As in Section \ref{sect:10dholomorphictwist}, the data of $q_+$ is equivalent to the data of a K\"ahler structure $L$ on $V_\RR$ together with a complex half-density on $L$.

Under the embedding $\MU(L)\subset \Spin(V_\RR)$, the semi-spin representations $S_+, S_-$ decompose as
\[S_+ = \det(L)^{1/2}\oplus L\otimes \det(L)^{-1/2},\qquad S_- = \det(L)^{-1/2} \oplus L^*\otimes \det(L)^{1/2},\]
where $q_+\in S_+$ lies in the first summand.

We fix an embedding $\U(1)\subset \SU(2)$ under which $w_1\in W_+$ has weight $1$. Under the composite
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.

We will now rewrite the fields using the twisting homomorphism $\phi$ from $\MU(3)$, where we denote by $K$ the canonical bundle of $L=\CC^3$.

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \Pi\fg)$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)$, $B\in\Omega^{0, 2}(M; \Pi\fg)$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)$.
\item Matter bosons $\nu\in\Omega^0(M; U\otimes K^{-1/2})$, $\phi\in\Omega^0(M; U\otimes K^{1/2})$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; \Pi U\otimes K^{1/2})$, $\wt\nu\in\Omega^0(M; \Pi U\otimes K^{-1/2})$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^3}{6}.\]

Using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory consists of the sum of the following terms:
\begin{align*}
S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a new twisting homomorphism
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

With these modifications the BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\chi\in\Omega^0(M; \fg)[-1]$, $\xi\in\Omega^{3, 0}(M; \Pi\fg)[1]$, $B\in\Omega^{0, 2}(M; \fg)[-1]$, $\rho\in\Omega^{1, 0}(M; \Pi\fg)[1]$.
\item Matter bosons $\nu\in\Omega^0(M; R^*\oplus R\otimes K^{-1}[-2])$, $\phi\in\Omega^0(M; R\oplus R^*\otimes K[2])$.
\item Matter fermions $\psi\in \Omega^{1, 0}(M; R[-1]\oplus R^*\otimes K[1])$, $\wt\nu\in\Omega^0(M; R^*[1]\oplus R\otimes K^{-1}[-1])$.
\item A ghost field $c\in \Omega^0(M; \gg)[1]$.
\end{itemize}

Note that the $\MU(3)$-action on the fields factors through $\U(3)$ since the square roots of $K$ have canceled out. By comparing the degrees and the transformation rules of the fields in Theorem \ref{thm:6dholomorphictwist} we obtain the following statement.

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U=T^*R=R\oplus R^*$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (R/\fg))$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:6dholomorphictwistgraded}
\end{thm}

\subsection{\texorpdfstring{$\cN=(1, 1)$}{N=(1, 1)} Super Yang--Mills}

The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.

Given an element $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ we denote by $W^*_{Q_\pm}\subset S_\pm$ the images of $Q$. We classify square-zero supercharges according to the ranks of these spaces:
\begin{itemize}
\item Rank $(1, 0)$ and $(0, 1)$. These automatically square to zero and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ (respectively, $\cN=(0, 1)$) supersymmetry algebra. They admit a twisting homomorphism from $\MU(3)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle = 0$. These automatically square to zero and have 4 invariant directions. There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle \neq 0$. These automatically square to zero and are topological. Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.

\item Rank $(2, 2)$. The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory. There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
\end{itemize}

\subsubsection{Holomorphic twist}

The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$. Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills. In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:6d11holomorphictwist}
\end{thm}

\subsubsection{Rank $(1, 1)$ partially topological twist}

We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]

Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$. Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.

\begin{thm}
The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$. Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
\end{thm}
\begin{proof}
The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.

To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$. In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}. The claim then follows from a direct comparison.
\end{proof}

\subsubsection{Topological twist}

Next we study the rank $(1, 1)$ topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$. Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
\[
S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
\]
Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in \Sigma.
\label{eq:6dHodgefamily}
\end{equation}
At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.

\begin{thm}
The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:6dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}. So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills. Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
\end{proof}

\begin{cor}
The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
\end{cor}

\subsubsection{Rank $(2, 2)$ twist}

We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.

\begin{thm}
The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
\label{thm:6drank22}
\end{thm}
\begin{proof}
Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.

Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e. $s_+^\pm, s_-^\pm$ are all nonzero. The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.

$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$. But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.

So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$. The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
\end{proof}

\section{Dimension 5}
The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.  The maximal supersymmetric gauge theory has $\mc N=2$.  However, there are $\mc N=1$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group.

\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang-Mills Theory with Matter}  \label{5d_1_section}
We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.  This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from Section \ref{6d_10_section} to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^0(\RR^5; \gg)$.
 \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
 \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
 \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
There is a unique class of square-zero supercharges in the 5d $\mc N=1$ supersymmetry algebra.  Twists by such supercharges are minimal: they are invariant in three directions.  The stabilizer of a minimal supercharge is isomorphic to $\SU(2) \sub \Spin(5)$.

\begin{theorem} \label{5d_holo_twist_theorem}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
\end{theorem}

\begin{proof}
This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in Theorem \ref{thm:6dholomorphictwist} above, by applying Proposition \ref{CS_diml_red_prop} to dimensionally reduce along one of the non-invariant Calabi-Yau directions.
\end{proof}

\subsection{\texorpdfstring{$\mc N = 2$}{N=2} Super Yang-Mills Theory} \label{5d_2_section}

\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the fields of maximal super Yang-Mills from 10d, or alternatively by restricting the 7d $\mc N=1$ fields from Section \ref{7d_section}, to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: A gauge field $A \in \Omega^1(\RR^5; \gg)$, and five scalars $\phi_1 ,\ldots, \phi_5 \in \Omega^1(\RR^5; \gg)$.
 \item Fermions: A pair of spinors $\lambda_1$ and $\lambda_2$ in $\Omega^0(\RR^5; S \otimes W \otimes \gg)$.
\end{itemize}
We could alternatively have obtained these fields by considering the $\mc N=1$ 5d super Yang-Mills theory, with matter valued in the symplectic representation $T^*\gg$.

\vspace{-10pt}
\paragraph{Twisting data:}
Exactly as in the case of the 6d $\mc N=(1,1)$ supersymmetry algebra, there are 4 inequivalent classes of twists (see \cite[Section 4.5]{ElliottSafronov}).  These supercharges all occur as square-zero supercharges in the 6-dimensional $\mc N=(1,1)$ supersymmetry algebra from the previous section.
\begin{enumerate}
 \item Rank $1$ spinors, $Q \otimes w$.  These automatically square to zero, and admit three invariant directions.  Twists by such supercharges were already described in the previous section.
 \item Rank $2$ square-zero spinors.  Like in dimension 6, these split into two inequivalent classes:
 \begin{enumerate}
 \item The open locus, consisting of topological supercharges.
 \item There is a special locus consisting of supercharges with 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $4$ square-zero spinors.  These supercharges are also topological.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

\begin{theorem} \label{5d_rk2_twist_thm}
The twist of 5d $\mc N=2$ super Yang-Mills theory by a rank $2$ supercharge with 4 invariant directions on the product of a Calabi-Yau curve $C$ and an oriented 3-manifold $M_3$ is equivalent to mixed BF theory on the product $C \times (M_3)_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(C \times (M_3)_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}
As we have done in higher dimensions, we start with with the 1-parameter family of twisted theories from Theorem \ref{6d_holo_twist_thm}, and dimensionally reduce along one of the Calabi-Yau directions by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 6-dimensions.
\end{proof}

Let us describe the partition function of the A-type topological twist appearing at generic points of this family.  
\begin{theorem}
\chris{Something about the Haydys-Witten equations...}
\end{theorem}

\begin{proof}

\end{proof}

\begin{theorem} \label{5d_rk4_twist_thm}
The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}((M_5)_{\mr{dR}}, B\gg)$.
\end{theorem}

\begin{proof}
We now take the twist of 6d $\mc N=(1,1)$ super Yang-Mills with 5 invariant directions, as calculated in Theorem \ref{6d_rk22_twist_thm}, and dimensionally reduce in the unique non-invariant direction.  That is, we apply Proposition \ref{CS_diml_red_prop} to the flat curve $C$ to obtain the required topological theory.
\end{proof}

\section{Dimension 4}

\subsection{\texorpdfstring{$\cN=1$}{N=1} with chiral multiplet matter} \label{4d_1_section}
We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.

%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.

The field content for the 4-dimensional $\cN=1$ super Yang-Mills theory coupled to chiral matter is given by:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
\item $R$-valued bosons: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^0(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
\item $R$-valued fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
\end{itemize}

The R-symmetry group is $U(1)$ which acts by $\pm 1$ on $\lambda_{\pm}$ and $\mp 1$ on $\psi_{\pm}$.

\subsubsection{Holomorphic twist}

There is a single non-zero equivalence class of square-zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on.
Such supercharges are necessarily of rank $1$, and for concreteness we will fix a square-zero supercharge of negative chirality $$Q = Q_+ \in S_+$$ to twist by. 
Such supercharges are minimal (i.e. have two dimensional image).  
The twisted theory by such a supercharge can always be made $\ZZ$-graded where the twisting datum is given by the identity map $\alpha = {\rm id} : U(1) \to U(1)$. 
Such a $Q$ is preserved under a twisting homomorphism
\[
\MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\MU(2) \to U(1)$ is the square root of determinant.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
The fields decompose as:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
\end{array}
\]
\brian{Is it necessary to put in the antifields?} 
and their antifields:
\begin{align*}
c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
\end{align*}

The untwisted action functionals decompose as follows.

\begin{align*}
S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
I^{(1)}_{\mr{gauge}} &=  \int  \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int  \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int  (\lambda_0^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\MU(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$. 
\end{thm}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_{1,1}^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

The twisted theory is therefore perturbatively equivalent to the theory with BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \bigg( (B_{2,1} \ol \dd_{A_{0,1}} A_{0})  + B_{2,0} F_{0,2} + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1} + \beta_{2,1} \dbar_{A_{0,1}} \gamma_0 \\ 
  &\qquad  + [A_{0,2}, A_0]\wedge B_{2,0} + \frac{1}{2}[A_0, A_0]B_{2,2} +  [\gamma_0, A_0]\wedge \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1}  \bigg).
\end{align*}
This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{2,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{2,\bu}$ comprise the fields of the $\beta\gamma$ system.
\end{proof}

%\begin{itemize}
%\item[(1)] 
%We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
%The fields of the pure Yang-Mills part decomposes as:
%\begin{align*}
%c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
%\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
%\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
%\end{align*}
%and their antifields:
%\begin{align*}
%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
%A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
%\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
%\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
%\end{align*}
%
%The matter fields decompose as
%\begin{align*}
%\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
%\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
%\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
%\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
%\end{align*}
%and their antifields:
%\begin{align*}
%\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
%\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
%\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
%\end{align*}
%
%\item[(2)] Next, we study the linear differential in the twisted theory. 
%At the linear level, the matter and gauge sectors completely decouple. 
%
%For the gauge sector, the linear differential on the twisted BV complex is the following:
%\[
%\xymatrix{
%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
%\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
%& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
%\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
%& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
%}
%\]
%The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
%The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
%This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$. 
%
%For the matter sector, the linear differential is:
%\[
%\xymatrix{
%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
%& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
%\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
%\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
%}
%\]
%This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$. 
%
%\item[(3)] 
%We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
%\end{itemize}

%There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
%\begin{itemize}
%\item The twisted theory is a shifted cotangent theory in the BV formalism. 
%This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
%\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
%\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
%\end{itemize}
%
%The first symmetry we exploit is translation invariance. 
%There is a general fact that translation invariant couplings can be described neatly in terms of the Lie algebra homology / cohomology of a certain Lie algebra. 
%Let $\fg$ and $R$ be a Lie algebra together with a representation.
%Define the following graded Lie algebra
%\[
%\sG_{\cN=1} = \left(\fg[z_1,z_2] \ltimes \d^2 z \; \fg^* [z_1,z_2] [-1]\right) \oplus \left(R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
%\]
%One can think of the Lie algebra $\sG_{\cN=1}$ as the $\infty$-jets at $0 \in \CC^2$ \brian{finish} of the Lie algebra describing at 
%Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$. 
%
%
%\begin{prop}
%The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
%\[
%\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
%\]
%\end{prop}

\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang-Mills with Matter} \label{4d_2_section}

We obtain $\mc N=2$ super Yang-Mills theory on $\RR^4$ by dimensionally reducing $\mc N=(1,0)$ super Yang-Mills from $\RR^6$, or $\mc N=1$ super Yang-Mills from $\RR^5$, with a hypermultiplet valued in a symplectic representation $U$.  In these terms we can describe the BRST fields.

\vspace{-10pt}
\paragraph{Fields:}  We can describe the BRST fields of $\mc N=2$ super Yang-Mills with matter valued in the symplectic representation $U$ by restricting the 5d $\mc N=2$ fields from Section \ref{5d_1_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and a pair of scalar fields $(\phi_1,\phi_2) \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))^2$.
 \item $U$-valued bosons: a $W$-valued scalar field $\phi \otimes v \in \Omega^0(\RR^4; W \otimes U)$.
 \item $\gg$-valued fermions: a $W$-valued Dirac spinor $\lambda = (\lambda_+ \otimes u_+, \lambda_-\otimes u_-) \in \Omega^0(\RR^4; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
 \item $U$-valued fermions: a Dirac spinor $\psi = (\psi_+,\psi_-) \in \Omega^0(\RR^4; (S_+\oplus S_-) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
It will be enough for our purposes to describe only the action of a chiral supercharge.
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
\end{prop}

\vspace{-10pt}
\paragraph{Twisting data:}
There are three classes of square-zero supercharge in the 3d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$.
\begin{itemize}
 \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  The corresponding twists are holomorphic, and coincide with the 4d $\mc N=1$ twists discussed above.
 \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. The corresponding twists are topological (the \emph{Donaldson twist}).
 \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
\end{itemize}

We will identify the latter two twists as further deformations of the minimal twist, which we can describe similarly to what we saw for $\mc N=1$.

\begin{theorem} \label{4d_2_holo_twist_thm}
The minimal twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a Calabi-Yau surface $S$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S, T^*[1](U\ham \gg))$.
\end{theorem}

\begin{proof}
To show this, we start with the 5d $\mc N=1$ minimal twist from Theorem \ref{5d_holo_twist_theorem} and dimensionally reduce in the de Rham direction $L_{\mr{dR}}$.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop} to the theorem obtained in Theorem \ref{5d_holo_twist_theorem}.
\end{proof}

We'll first consider the deformation of the holomorphic twist to the topological twist corresponding to a rank $(2,0)$ supercharge.

\begin{theorem} \label{4d_Donaldson_twist_thm}
The deformation of the holomorphic twist to the Donaldson twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent, as a 1-parameter family of theories, to the Hodge family $\mr{Map}(S, (U\ham \gg)_{\mr{Hod}})$.  
\end{theorem}

\begin{proof}
Suppose the family of generically rank $(2,0)$ supercharge splits as a sum of two rank 1 supercharges as $Q_{\mr{hol}} + tQ$, where $t \in \CC$.  It is enough to understand the deformation of the holomorphically twisted action functional, which we wrote down in the proof of Theorem \ref{4d_minimal_twist_thm}, by $I^{(1)}(tQ) + I^{(2)}(tQ,tQ)$ using Proposition \ref{4d_2_susy_action_prop}.

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.  Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.  The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
\end{proof}

We now address the rank $(1,1)$ twist.  This is more straightforward: we can understand it by dimensional reduction from the 5d holomorphic twist, this time in a non-invariant direction.

\begin{theorem} \label{4d_11_twist_thm}
The rank $(1,1)$ twist of 4d $\mc N=2$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ on a product $C_1 \times C_2$ of two Riemann surfaces, is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(C_1 \times {C_2}_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
We start with the 5d $\mc N=1$ holomorphic twist, as in Theorem \ref{5d_holo_twist_theorem}, and dimensionally reduce in one of the two non-invariant directions.  That is, we apply Proposition \ref{CS_diml_red_prop}.
\end{proof}

\subsection{\texorpdfstring{$\cN=4$}{N=4} Super Yang-Mills} \label{4d_4_section}

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 5d $\mc N=2$ fields from Section \ref{5d_2_section} to representations of the group $\mr O(4)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: a gauge field $A \in \Omega^1(\RR^4; \gg)$, and six scalars, which we'll denote by $\phi \in \Omega^1(\RR^4; \gg \otimes \wedge^2(W))$.
 \item Fermions: four spinors, which we'll denote by $(\lambda_+ \otimes u_+, \lambda_- \otimes u_u) \in \Omega^0(\RR^5; (S_+ \otimes W \oplus S_- \otimes W^*) \otimes \gg)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
The classification of orbits of square-zero supercharges in the 4d $\mc N=4$ supersymmetry algebra is the most interesting among the examples we consider in this paper.  We have the following classes. \chris{some comments claiming we'll discuss things above, to be added.  Also this is to revisit after writing the below.}
\begin{itemize}
 \item Rank $(1,0)$ (and $(0,1)$) supercharges.  Such supercharges automatically square to zero, and are holomorphic: indeed they sit inside an $\mc N=1$ subalgebra.  They are compatible with $\SU(2)_- \sub \Spin(4;\RR)$, which can be promoted to a twisting homomorphism from the group $\mr U(2)$ as we say in the 4d $\mc N=1$ section above.
 \item Rank $(2,0)$ (and $(0,2)$) supercharges.  Such supercharges automatically square to zero, and are topological: indeed they sit inside an $\mc N=2$ subalgebra.  They are compatible with any of three possible twisting homomorphisms:
 \begin{enumerate}
  \item The half twisting homomorphism $\phi_{\mr{1/2}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, 1, 1)$.
  \item The Kapustin-Witten twisting homomorphism $\phi_{\mr{KW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, B)$.
  \item The Vafa-Witten twisting homomorphism $\phi_{\mr{VW}} \colon \SU(2)_+ \oplus \SU(2)_- \to \SL(4;\CC)$ given by $(A,B) \mapsto \mr{diag}(A, A)$.
 \end{enumerate}
 \item Rank $(1,1)$ supercharges.  Such supercharges have three invariant directions, and also sit inside an $\mc N=2$ subalgebra.  Twists by such supercharges are compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$, but are only $\ZZ/2\ZZ$-graded, as we discussed in the $\mc N=2$ section above.
 \item Rank $(2,1)$ (and $(1,2)$) supercharges.  Such supercharges are topological, and compatible with a twisting homomorphism from $\Spin(2;\RR) \times \Spin(2;\RR)$.
 \item Rank $(2,2)$ square-zero supercharges are topological, and split into two classes.  Generically, such supercharges correspond to perturbatively trivial twisted theories, and are only compatible with $\Spin(2;\RR) \times \Spin(2;\RR)$.  There is a special point of this type which is compatible with Kapustin-Witten twisting homomorphism.
 \item There is also a special rank $(2,2)$ point (the \emph{B-twisting supercharge}) arising by dimensional reduction from the 5d $\mc N=2$ rank 4 supercharge, which is also compatible with the Kapustin-Witten twisting homomorphism.
\end{itemize}

We can study all the possible twists using what we say in the $\mc N=2$ subsection, as well as by dimensional reduction from 5d $\mc N=2$ super Yang-Mills theory.

\begin{theorem}
\chris{holomorphic deforming to rank $(2,0)$, proven above} $\mr{Map}(\CC^2_{\mr{Dol}}, B\gg_{\mr{Hod}})$.
\end{theorem}

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

\begin{theorem}
\chris{Special rank $(2,2)$ deforming to generic rank $(2,2)$, by dimensional reduction from 5d $2_A$ deforming to $2_B$} $\mr{Map}(\RR^4_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

% \vspace{-10pt}
% \paragraph{Supersymmetry action:} 
% \begin{prop}
% Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
% \begin{align*}
% I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
% &\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
% &\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
% \end{align*}
% and
% \begin{align*}
% I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
% &\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
% &\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
% \end{align*}
% where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
% \end{prop}

\chris{todo: $(1,0)$, $(2,0)$, $(1,1)$ as above, with $U = T^*\gg$.  Then $(2,1)$ and generic $(2,2)$ arise as deformations of $(1,1)$ by dimensional reduction from 5d.  Finally the special $(2,2)$ arises by dimensional reduction from the 5d B-twist.}

\section{Dimension 3}
The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.  The maximal supersymmetric gauge theory has $\mc N=8$.  However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.  In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.

\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang-Mills with Chiral Matter} \label{3d_2_section}
We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).  So, fix a gauge group $G$, and a representation $R$.  The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_1_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $\lambda \otimes u \in \Omega^0(\RR^3 ; S \otimes \gg \otimes W)$.
 \item $R$-valued fermions: $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus \otimes S \otimes R^*)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=2$ supersymmetry algebra there is a unique non-trivial orbit of square-zero supercharges, with rank one. \chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}

\begin{thm} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to mixed $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. 
\end{thm}

\begin{proof}
This follows by dimensionally reducing the holomorphic twist of 4d $\mc N=1$ super Yang-Mills.  That is, we start with the result from Theorem \ref{4d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn one of the complex directions into a real de Rham direction.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item $U$-valued bosons: a $W$-valued scalar field $(\phi \otimes v) \in \Omega^0(\RR^3; W \otimes U)$.
 \item $\gg$-valued fermions: a pair of $W$-valued spinors $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes \gg \otimes (W \oplus W))$.
 \item $U$-valued fermions:  a pair of spinors $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  In addition to rank one square-zero supercharges, which sit inside an $\mc N=2$ subalgebra, there are two possible classes of rank two square-zero supercharges.  The corresponding twisted theories are obtained by dimensionally reducing the 4d $\mc N=2$ theory twisted by a rank $(1,1)$, or a rank $(2,0)$ square-zero supercharge.  Let's first discuss the rank 1 twist, and its deformation to a perturbatively trivial rank 2 twist.

\begin{theorem} \label{3d_4_holo_A_twist_thm}
The minimal twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(\CC \times \RR_{\mr{dR}}, T^*[1](U\ham \gg))$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $\mr{Map}(\CC \times \RR_{\mr{dR}}, (U\ham \gg)_{\mr{Hod}})$.
\end{theorem}

\begin{proof}
To prove this, we start with the one-parameter family of 4d twisted theories which we computed Theorem \ref{4d_Donaldson_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to reduce to a one-parameter family of 3d twisted theories.
\end{proof}

\begin{theorem} \label{3d_2_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=4$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the generalized BF theory coupled to a $U$-valued higher holomorphic boson with space of fields $\mr{Map}(\RR^3_{\mr{dR}}, U\ham \gg)$.  This theory is generally only $\ZZ/2\ZZ$-graded.
\end{theorem}

\begin{proof}
Again, we prove this by dimensional reduction from a 4d $\mc N=2$ twisted theory, in this case the rank $(1,1)$ twist from Theorem \ref{4d_11_twist_thm}, by applying Proposition \ref{CS_diml_red_prop}.
\end{proof}

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d_8_section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\mr O(3)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
The classes of square-zero supercharge in the 3d $\mc N=8$ supersymmetry algebra are categorized in the same way as in the $\mc N=4$ supersymmetry algebra.  There are minimal twisting supercharges of rank 1, and two classes of topological twisting supercharges of rank 2, which we refer to as the A-twist (obtained from a rank $(2,0), (2,1)$ or generic $(2,2)$ supercharge in $4d \mc N=4$), and the B-twist (obtained from a rank $(1,1)$ or special rank $(2,2)$ supercharge in 4d $\mc N=4$).  The twisted theories can be calculated either by dimensional reduction -- by applying Proposition \ref{CS_diml_red_prop} to the theories from Section \ref{4d_4_section}, or from the 3d $\mc N=4$ twists by considering the representation $U = T^*\gg$.

\begin{theorem} 
The minimal twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. The deformation of this theory to the rank 2 A-twist corresponds to deforming this theory to the 1-parameter family $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$.
\end{theorem}

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. 
\end{theorem}

\section{Dimension 2}

There are two classes of twisted supersymmetric gauge theory that we will consider in 2d.  First we have theories with $(\mc N, \mc N)$ supersymmetry; these arise via dimensional reduction from supersymmetric gauge theories in higher dimensions.  We additionally have gauge theories with chiral, i.e. $(0,\mc N)$ supersymmetry, which we saw using the observations in Section \ref{sec:2dchiral}.  We'll address twists for these two classes of theory in turn.

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sec:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{3d_2_section}, or equivalently the 3d fields from Section \ref{4d_1_section} to representations of the group $\mr O(2)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus \otimes (S_+ \oplus S_-) \otimes R^*)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
\chris{todo}

\vspace{-10pt}
\paragraph{Twisting data:}
In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic
 \item Square-zero supecharges of rank $(1,1)$ are topological, and split into two classes: the B-supercharge arises by dimensional reduction from 3 dimensions, and the A-supercharge does not.
\end{itemize}
\chris{todo, say something about $\ZZ$-gradings and twisting homomorphisms.}

The calculation of the twists here is similar to what we saw in 4d $\mc N=2$.  The holomorphic twist and the B-twist arise by dimensional reduction from 3d, but the A-twist as a deformation of the holomorphic twist is not, and must be calculated directly.

\begin{theorem} \label{2d_minimal_twist_thm}
The minimal twist of 2d $\cN=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\cN=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the mixed $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$. 
\end{theorem}

\begin{proof}
This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.  That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_to_BF_diml_red_prop} to dimensionally reduce in the real de Rham direction.
\end{proof}

\begin{theorem} \label{2d_2_A_twist_thm}
The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.
\end{theorem}

\begin{proof}

\end{proof}

Finally, there is the 2d B-twist.  This is much easier, since it arises directly from 3d via dimensional reduction in a non-invariant direction.
\begin{theorem} \label{2d_2_B_twist_thm}
The topological B-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2, (R/\gg))$.
\end{theorem}

\begin{proof}
We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.  That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
\end{proof}

\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} and \texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with matter} \label{sec:2d(4,4)}
We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills with gauge group $G$, by dimensionally reducing 3d $\mc N=8$ super Yang-Mills.  We will address these two theories together, since in neither case are there any new classes of twist which were not visible already in the $\mc N=(2,2)$ section above.

The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.

\begin{theorem}
The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ admits a one-parameter deformation to the A-twist.  Together they are perturbatively equivalent to a holomorphic BF theory and its Hodge deformation, with moduli space given by $T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Hod}})$.

If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with  $T^*[-1]\mr{Map}(\CC, (T^*[2](\gg / \gg))_{\mr{Hod}})$.
\end{theorem}

\begin{theorem}
The B-twist of 2d $\mc N=(4,4)$ super Yang-Mills with gauge group $G$ and symplectic matter representation $U$ is perturbatively equivalent to the topological BF theory with moduli space $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$.  If $U = T^*\gg$ then the $\mc N=(4,4)$ supersymmetry is promoted to $\mc N=(8,8)$, and the twisted moduli space can be identified with $T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, T^*[2](\gg/\gg))$.
\end{theorem}

\subsection{\texorpdfstring{$\cN=(0,2)$}{N=(0,2)} Super Yang-Mills with matter} \label{sec:2d(0,2)}

We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.

\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}

The untwisted fields are given by:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
\item $R \oplus R^*$-valued scalars: $\phi \in C^\infty(\RR^2 ; R)$ and $\Bar{\phi} \in C^\infty(\RR^2 ; R^*)$;
\item a pair of $R \oplus R^*$-valued fermions: $\psi \in C^\infty(\RR^2 ; S_+ \otimes R^*)$  and $\Bar{\psi} \in C^\infty(\RR^2 ; S_+ \otimes R)$.
\end{itemize}
Here, $W$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
Choose the basis $\{u,v\}$ for $W_-$ with pairing given by $\<u, v\> = 1$.

We will twist by an element $Q = q \otimes u \in S_- \otimes W_-$.

The fields decompose as
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) & (0,0) & (1,-1) & (1,-1) \\
\phi & \mapsto &  \gamma_0 \in \Omega^0 (\CC ; R) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \Bar{\phi} \in \Omega^{0}(\CC ; R^*) & 0 & 0 & 0 \\
\psi & \mapsto &  \psi_0 \in \Omega^{0}(\CC ; R^*) & 0 & -1 & -1 \\
\Bar{\psi} & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC ; R)  & 0 & 1 & 1 
\end{array}
\]
The anti-fields decompose as
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c^* & \mapsto & B_{1,1} \in \Omega^{1,1} (\CC ; \fg) & 2 & 0 & 2 \\
A^* & \mapsto &  A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (1,1) & (0,0) & (1,1) \\
\lambda^* & \mapsto &  \lambda^*_{1,1} v + \lambda^*_{0,1} u \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg)  & (1,1) & (-1,1) & (0,2) \\
\phi^* & \mapsto &   \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) & 1 & 0 & 1 \\
\Bar{\phi}^* & \mapsto &\Bar{\phi}^* \in \Omega^{1,1}(\CC ; R)  & 1 & 0 & 1 \\
\psi & \mapsto &   \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) & 1 & 1 & 2 \\
\Bar{\psi} & \mapsto &  \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)   & 1 & -1 & 0 
\end{array}
\]

%\begin{align*}
%c^* & \mapsto B_{1,1} \in \Omega^0(\CC ; \fg) \\
%A^* & \mapsto A^*_{0,1} + B_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \\
%\lambda^* & \mapsto \lambda^*_{1,1} w_1 + \lambda^*_{0,1} w_2 \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \\
%\phi^* & \mapsto \beta_{1,1} \in \Omega^{1,1} (\CC ; R^*) \\
%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{1,1}(\CC ; R) \\
%\psi^* & \mapsto \psi^*_{1,1} \in \Omega^{1,1}(\CC ; R) \\
%\Bar{\psi}^* & \mapsto \beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)  
%\end{align*}

The action functionals decompose as:
\begin{align*}
S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0})  \right)  \\
S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\Bar{\phi} , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \Bar{\phi})) + (\psi_0 , \partial_{A_{1,0}} \gamma_{0,1}) + (\gamma_{0,1} \wedge \partial_{A_{1,0}} \psi_{0})  + \\
&\qquad + (([\lambda_{1,0},\gamma_{0,1}],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1}) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\gamma_0, A_0] \beta_{1,1} + [\Bar{\phi}, A_0] \Bar{\phi}^* + [\gamma_{0,1}, A_0]\wedge \beta_{1,0} + [\psi_0, A_0] \psi_{1,1}^* \\
I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
I^{(1)}_{\mr{matter}} &=  \int \left( (\psi_{1,1}^*, \Bar{\phi}) + \frac 12(\beta_{1,0} \wedge \dbar \gamma_0) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
\end{align*}
%Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.

\begin{thm}[See also \cite{SWchar}] \label{2d(0,2)}
The minimal twist of 2d $\cN=(0,2)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,2)$ chiral multiplet valued in a representation $R$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system on $\CC$ with values in the representation $R$. 
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

The twisted theory is therefore perturbatively equivalent to the theory with BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + \beta_{1,0} \dbar_{A_{0,1}} \gamma_{0} \\ 
  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [\gamma_0, A_0]\wedge \beta_{1,1} + [\gamma_{0,1}, A_0]\wedge \beta_{1,0}  \bigg).
\end{align*}
This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\gamma_{0,\bu}, \beta_{1,\bu}$ comprise the fields of the $\beta\gamma$ system.
\end{proof}

\subsection{\texorpdfstring{$\cN=(0,4)$}{N=(0,4)} Super Yang-Mills with matter}

We consider $\cN=(0,4)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,4)$ supersymmetric matter. 
The supersymmetric matter consists of the $\cN = (0,4)$ hypermultiplet with values in a complex symplectic representation $U$. 
The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_- = {\rm span}_{\CC} \{u_1,u_2, v_1,v_2\}$ is the four-dimensional auxiliary space equipped with the pairing $\<u_i, v_j\> = \delta_{ij}$. 
Let $W = {\rm span}_{\CC} \{u_1,u_2\}$.

The field content is:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
\end{itemize}

We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.

\begin{thm}\label{2d(0,4)}
The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$. 
\end{thm}

\begin{proof}
The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
\[
S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
\]
given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
The claim now follows from Theorem \ref{2d(0,2)}. 
\end{proof}

\begin{rmk}
The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
\end{rmk}

% \cN=(0,8) Super Yang-Mills with matter

\subsection{\texorpdfstring{$\cN=(0,\cN_-)$}{N=(0,N-)} Super Yang-Mills}

We consider pure $\cN=(0,\cN_-)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_- \geq 2$.
The spinorial representation is $\Sigma = S_- \otimes W_-$ where $W_-$ is the $\cN_-$-dimensional auxiliary equipped with a nondegenerate symmetric bilinear pairing.

\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
\end{itemize}
Choose a splitting $W_- = {\rm span}_{\CC} \{u, v\} \oplus W_-'$ where $\dim(W_-') = \cN_- - 2$ such that the pairing restricted to $ {\rm span}_{\CC} \{u, v\}$ is $\<u,v\> = 1$.

The field content is:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
\lambda & \mapsto & \lambda_{0} u + \lambda_{1,0} v + \chi \in \Omega^{0}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_- \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
\end{array}
\]

We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.

%\[
%\begin{array} {lllcccccc}
%& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
%c^* & \mapsto & B_{1,1} \in \Omega^{1,1}(\CC ; \fg) & -1 & 0 & -1 \\
%A^* & \mapsto & A^*_{0,1} + A^*_{1,0} \in \Omega^{0,1}(\CC ; \fg) \oplus \Omega^{1,0}(\CC ; \fg)  & (0,0) & (0,0) & (0,0) \\
%\lambda^* & \mapsto & \lambda^*_{1,1} v + \lambda^*_{0,1} u + \chi^* \in \Omega^{1,1}(\CC ; \fg) \oplus \Omega^{0,1}(\CC ; \fg) \oplus C^\infty(\RR^2 ; S_+ \otimes W_-' \otimes \fg) & (0,0,0) & (1,-1,0) & (1,-1, 0) \\
%\end{array}
%\]

%\begin{align*}
%S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_0 , \dbar_{A_{0,1}} \lambda_{1,0}) +(\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_{0}) + (\chi, \sd \dd_{A_{0,1}} \chi) \right)  \\
%S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{1,0} + [\lambda_{1,0}, A_0]\wedge \lambda_{0,1}^* +  [\lambda_{0}, A_0]\wedge \lambda_{1,1}^* +B_{1,0} \wedge [A_0, A_{0,1}] + A_{0,1}^* \wedge [A_{0}, A_{1,0}] \\
%&\qquad + \frac{1}{2}[A_0, A_0]B_{1,1} + [A_0, \chi] \chi^* \\
%I^{(1)}_{\mr{gauge}} &=  \int \left( - (\lambda_{1,0}, A_{0,1}^*) \right)\\
%I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int (\lambda_{1,1}^*)^2.
%\end{align*}

\begin{thm}[See also \cite{SWchar}] \label{4d_2_minimal_twist_thm}
The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action. 
\end{thm}

\begin{proof}
The proof is similar to the proof of Theorem \ref{2d(0,4)}.
The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
\[
S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
\]
given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sec:2d(0,2)}. 
Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
The claim now follows from a special case of Theorem \ref{2d(0,2)} where we take $R = 0$. 
%First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
%We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
%Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
%which can be integrated out using Proposition \ref{prop:BRSTdoublet}.  
%
%The twisted theory is therefore perturbatively equivalent to the theory with BV action 
%\begin{align*}
% S_{\mr{BV}} &= \int \bigg( (B_{1,0} \ol \dd_{A_{0,1}} A_{0})  + (\chi, \sd \dd_{A_{0,1}} \chi) \\ 
%  &\qquad  + [A_{0,1}, A_0]\wedge B_{1,0} + \frac{1}{2}[A_0, A_0]B_{1,1} +  [A_0, \chi] \chi^*  \bigg).
%\end{align*}
%This is indeed the action functional of the required theory, where $A_{0,\bu}, B_{1,\bu}$ comprise the fields of holomorphic $BF$ theory and $\chi$ is the fundamental field for the free fermion system. 
\end{proof}

\appendix

\section{Spinors}
\label{sect:spinors}

In this paper we will extensively use the theory of spinors. Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing. Recall that the Clifford algebra $\Cl(V)$ is defined to be the quotient of the tensor algebra on $V$ by the relation
\[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$. Denote the Clifford action by $\rho(v)\in\eend(M)$. We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
\[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
for any $Q_1, Q_2\in M$ and $v\in V$. From now on we denote $M^+=\Sigma$ and $M^-=\Sigma^*$. We define the $\Gamma$-pairings
\[\Gamma\colon\Sym^2(\Sigma)\longrightarrow V,\qquad \Gamma\colon\Sym^2(\Sigma^*)\longrightarrow V\]
by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}

We have a subset $\Spin(V)\subset \Cl(V)$, so $\Sigma$ and $\Sigma^*$ are representations of the spin group. Moreover, the Clifford action and the maps $\Gamma$ are $\Spin(V)$-equivariant.

We may identify $\wedge^2(V)\rightarrow \so(V)$ via
\[\omega\mapsto (w\mapsto -2\iota_{(w, -\rangle)} \omega).\]
This gives rise to an action map
\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
of two-forms on spinors.

Consider the map $q\colon \wedge^\bullet(V)\rightarrow \Cl(V)$ given by antisymmetrization, so that, for instance,
\begin{equation}
q(v_1\wedge v_2) = v_1v_2 - (v_1, v_2).
\label{eq:quantizationtwoforms}
\end{equation}

The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$, so that $\so(V)$-equivariance of $\Gamma$ gives the following.

\begin{prop}
For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
\label{prop:cliffordactionproperty1}
\end{prop}

We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$. Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
\[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]

From \eqref{eq:quantizationtwoforms} we get the following property.

\begin{prop}
Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
\label{prop:cliffordactionproperty2}
\end{prop}

Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.

\begin{prop}
Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
\label{prop:cliffordactionproperty3}
\end{prop}

Note that both Proposition \ref{prop:cliffordactionproperty2} and Proposition \ref{prop:cliffordactionproperty3} extend to the case when $\lambda$ and $X$ respectively are twisted by a vector bundle and $\sd{\d}$ is the corresponding twisted Dirac operator.

\pagestyle{bib}
\printbibliography

\end{document}

### 2020-02-24 old stuff/supermultiplets.tex
reorganize

--- 2019-04-14 supermultiplets.tex
@@
 
-Let $V$ be a complex vector space with a chosen spin structure.
-Let $\Sigma$ be a spinorial representation of $\Spin(V)$, $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ the associated vector-valued pairing and $T_\Sigma$ the supertranslation group with Lie algebra $\Pi\Sigma\oplus V$.
-The superPoincar\'{e} group is $\Spin(V)\ltimes T_\Sigma$.
+Let $V$ be a complex vector space of dimension $d$ with a chosen spin structure.
+Let $\Sigma$ be a spinorial representation of $\Spin(V)$, $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ the associated vector-valued pairing, and $T_\Sigma$ the supertranslation group with Lie algebra $\Pi\Sigma\oplus V$.
+The superPoincar\'{e} group is the semi-direct product $\Spin(V)\ltimes T_\Sigma$.
 
 Recall that massless representations of the Poincar\'{e} group are parametrized in the following way.
-Split $V = V_0\oplus \C e_+\oplus \C e_-$, where $e_+$ and $e_-$ are null vectors with $(e_+, e_-) = 1$.
+Split $V = V_0\oplus \C e_+\oplus \C e_-$, where $e_+$ and $e_-$ are null vectors satisfying $(e_+, e_-) = 1$.
 Then massless representations correspond to finite-dimensional representations of $\Spin(V_0)$.

### 2020-02-24 old stuff/twists.tex
reorganize

\documentclass[12pt]{amsart}

\usepackage[colorlinks=true]{hyperref}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}

\textwidth=16.5cm
\oddsidemargin=0cm
\evensidemargin=0cm
\textheight=22cm
\topmargin=0cm

\binoppenalty=10000
\relpenalty=10000

\newcommand{\B}{\mathrm{B}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\T}{\mathrm{T}}
\newcommand{\Z}{\mathbf{Z}}

\newcommand{\ch}{\mathrm{ch}}
\newcommand{\Dol}{\mathrm{Dol}}
\newcommand{\dR}{\mathrm{dR}}
\newcommand{\Map}{\mathrm{Map}}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Propostiion}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{example}[thm]{Example}

\begin{document}
\title{Twists}
\author{Pavel Safronov}
\maketitle

Compactification:
\begin{itemize}
\item $\Map((N\times S^1)_{\dR}, X)$ compactifies to $\Map(N_{dR}, \T[-1] X)$.

\item If $\Sigma$ is a complex curve and $L$ a 1-manifold, $\Map(\Sigma, X)$ compactifies to $\Map(L_{\dR}, X)$.
\end{itemize}

If an anomaly is not listed, the theory is not anomalous.

\section{$d=2$}

To define an $\cN=(2, 0)$ $\sigma$-model need a complex manifold $X$ with a holomorphic vector bundle $\cE$. If $\cE=\T_X$, we can enhance it to $\cN=(2, 2)$ supersymmetry. Let $E\rightarrow X$ be the total space.

\begin{itemize}
\item The rank $(1, 0)$ twist on $\Sigma$ gives $\T^*[-1]\Map(\Sigma, E[-1])$. It only has a one-loop anomaly which is given by $\chi(\Sigma) c_1(E[-1])$ and $\ch_2(E[-1])$.

\item If $\cE=\T_X$, this is
\[\T^*[-1]\Map(\Sigma, \T[-1]X)\cong \Map(\Sigma_{\Dol}, \T^*[1] X).\]
It only has a one-loop anomaly given by $\chi(\Sigma) c_1(X)$.

\item The rank $(1, 1)$ A-twist gives $\T^*[-1]\Map(\Sigma, X)_{\dR}$.

\item The rank $(1, 1)$ B-twist gives $\Map(\Sigma_{\dR}, \T^*[1] X)$. The anomaly is the same as for the holomorphic twist.
\end{itemize}

To define an $\cN=(2, 2)$ Yang--Mills theory we need a compact group $K$ and a complex $K$-representation $V$. Let $G$ be the complexification of $K$.

\begin{itemize}
\item The rank $(1, 0)$ twist on $\Sigma$ gives
\[\T^*[-1]\Map(\Sigma, \T[-1][V/G])\cong \Map(\Sigma_{\Dol}, \T^*[1][V/G]).\]
It only has a one-loop anomaly given by $\chi(\Sigma) c_1([V/G])$.

\item The rank $(1, 1)$ A-twist gives $\T^*[-1]\Map(\Sigma, [V/G])_{\dR}$.

\item The rank $(1, 1)$ B-twist gives $\Map(\Sigma_{\dR}, \T^*[1] [V/G])$. The anomaly is the same as for the holomorphic twist
\end{itemize}

\section{$d=3$}

To define an $\cN=2$ Yang--Mills theory we need a compact group $K$ and a complex $K$-representation $V$. If $V$ is the adjoint representation, the supersymmetry is enhanced to $\cN=4$.

\begin{itemize}
\item The rank $1$ twist on $\Sigma\times L$ where $\Sigma$ is a CY curve and $L$ is a 1-manifold gives $\T^*[-1]\Map(\Sigma\times L_{\dR}, [V/G])$.

\item For $V=\g$ get
\[\T^*[-1]\Map(\Sigma\times L_{\dR}, \T[-1]\B G)\cong \Map(\Sigma_{\Dol}\times L_{\dR}, \T^*[2] \B G).\]

\item The rank $2$ A-twist gives $\T^*[-1]\Map(\Sigma\times L_{\dR}, \B G)_{\dR}$.

\item The rank $2$ B-twist on a 3-manifold $M$ gives $\Map(M_{\dR}, \T^*[2] \B G)$.
\end{itemize}

We can also add $\cN=4$ matter. For this pick a complex $K$-representation $W$. If $W=\g$ we obtain $\cN=8$ supersymmetry. Then:

\begin{itemize}
\item The rank $2$ A-twist gives $\T^*[-1]\Map(\Sigma\times L_{\dR}, [W/G])_{\dR}$.

\item The rank $2$ B-twist gives $\Map(M_{\dR}, \T^*[2] [W/G])$.
\end{itemize}

\section{$d=4$}

To define an $\cN=1$ Yang--Mills theory we need a compact group $K$ and a complex $K$-representation $V$. The theta-term is zero. If $V$ is the adjoint representation, the supersymmetry is enhanced to $\cN=2$. We consider a complex surface $M^4=\Sigma_1\times \Sigma_2$.

\begin{itemize}
\item The rank $(1, 0)$ twist gives $\T^*[-1]\Map(M^4, [V/G])$. It only has a one-loop anomaly which in flat space is given by $\ch_3([V/G])$.

\item For $V=\g$ get
\[\T^*[-1]\Map(M, \T[-1]\B G)\cong \T^*[-1]\Map((\Sigma_1)_{\Dol}\times \Sigma_2, \B G).\]
It only has a one-loop anomaly given by $\chi(\Sigma_1) \ch_2(\B G)$.

\item The rank $(2, 0)$ twist gives $\T^*[-1]\Map(M^4, \B G)_{\dR}$. It compactifies to the 3d A-twist.

\item The rank $(1, 1)$ twist gives $\T^*[-1]\Map((\Sigma_1)_{\dR}\times \Sigma_2, \B G)$. It compactifies to the 3d B-twist or the 3d holomorphic twist. The anomaly is the same as in the holomorphic twist.
\end{itemize}

We can again add $\cN=2$ matter given a complex $K$-representation $W$:
\begin{itemize}
\item The rank $(2, 0)$ twist gives $\T^*[-1]\Map(M^4, [W/G])_{\dR}$.

\item The rank $(1, 1)$ twist gives $\T^*[-1]\Map((\Sigma_1)_{\dR}\times \Sigma_2, [W/G])$.
\end{itemize}

In the case $W=\g$ (i.e. we have $\cN=4$)
\begin{itemize}
\item The rank $(1, 0)$ twist gives
\[\T^*[-1]\Map((\Sigma_1)_{\Dol}\times (\Sigma_2)_{\Dol}, \B G).\]

\item The rank $(1, 1)$ twist gives
\[\T^*[-1]\Map((\Sigma_1)_{\dR}\times (\Sigma_2)_{\Dol}, \B G).\]

\item The rank $(2, 0)$ twist gives
\[\T^*[-1]\Map((\Sigma_1)_{\Dol}\times \Sigma_2, \B G)_{\dR}.\]

\item The special rank $(2, 2)$ twist gives
\[\T^*[-1]\Map((\Sigma_1)_{\dR}\times (\Sigma_2)_{\dR}, \B G).\]

\item The generic rank $(2, 2)$ twist gives
\[\T^*[-1]\Map((\Sigma_1)_{\dR}\times \Sigma_2, \B G)_{\dR}.\]
\end{itemize}

\section{$d=5$}

We consider $M^5=M^4\times L$ where $M^4=\Sigma_1\times \Sigma_2$ is a complex surface and $L$ is a 1-manifold.

\begin{itemize}
\item The rank $1$ twist gives $\T^*[-1]\Map(M^4\times L_{\dR}, [W/G])$.

\item If $W=\g$ get $\T^*[-1]\Map(M\times L_{\dR}, \T[-1]\B G)$.

\item The rank $2$ topological twist gives $\T^*[-1]\Map(M^4\times L_{\dR}, \B G)_{\dR}$.

\item The rank $2$ partially topological twist gives $\T^*[-1]\Map((\Sigma_1)_{\dR}\times \Sigma_2\times L_{\dR}, \B G)$.

\item The rank $4$ twist gives $\Map(M^5_{\dR}, \B G)$. This is $\Z/2$-graded.
\end{itemize}

\section{$d=6$}

Let $M^6=M^4\times \Sigma$ be a complex 3-fold.

$\cN=(1, 0)$ Yang--Mills:
\begin{itemize}
\item The rank $(1, 0)$ twist gives $\T^*[-1]\Map(M^6, [W/G])$. It only has a one-loop anomaly. In flat spacetime it is given by $\ch_4([W/G])$.
\end{itemize}

$\cN=(1, 1)$ Yang--Mills:
\begin{itemize}
\item The rank $(1, 1)$ topological twist gives $\T^*[-1]\Map(M^6, \B G)_{\dR}$.

\item The rank $(1, 1)$ partially topological twist gives $\T^*[-1]\Map(M^4\times \Sigma_{\dR}, \B G)$. It only has a one-loop anomaly when $\chi(\Sigma)\neq 0$ and $c_1(M)\neq 0$ in which case it is $\ch_2(\B G)$.

\item The rank $(2, 2)$ twist gives $\Map(M^2\times (M^4)_{\dR}, \B G)$. This is $\Z/2$-graded. It has a one-loop anomaly given by $\chi(M^4) \ch_2(\B G)$.
\end{itemize}

\section{$d=7$}

\begin{itemize}
\item The topological twist is $\Map(M^6\times L_{\dR}, \B G)_{\dR}$.

\item The holomorphic rank 1 twist is $\T^*[-1]\Map(M^6\times L_{\dR}, \B G)$.

\item The rank 2 twist is $\Map(M^4\times (M^3)_{\dR}, \B G)$. This is $\Z/2$-graded.
\end{itemize}

\section{$d=8$}

\begin{itemize}
\item The twist by a pure spinor rank $(1, 0)$ supercharge gives $\T^*[-1]\Map(M^8, \B G)$.

\item The twist by an impure spinor rank $(1, 0)$ supercharge gives $\Map(M^8, \B G)_{\dR}$.

\item The twist by a rank $(1, 1)$ supercharge gives $\Map((M^6)\times (M^2)_{\dR}, \B G)$. This is $\Z/2$-graded. Its one-loop anomaly vanishes for instance when $M^2$ is flat. If $M^2$ is not flat while $M^6$ is, the one-loop anomaly is given by $\ch_4(\B G)$.
\end{itemize}

\section{$d=9$}

\begin{itemize}
\item The twist by a pure spinor supercharge gives $\Map(M^8\times L_{\dR}, \B G)$. This is $\Z/2$-graded.
\end{itemize}

\section{$d=10$}

\begin{itemize}
\item The rank $1$ twist gives $\Map(M^{10}, \B G)$. This is $\Z/2$-graded. Its one-loop anomaly in flat spacetime is $\ch_6(\B G)$.
\end{itemize}

\end{document}

### 2020-03-20 paper.tex
typo

--- 2020-02-23 paper.tex
@@
 \begin{abstract}
-We give a complete classification of twists of supersymmetric Yang--Mills theories in dimensions~$2\leq n \leq 10$.
-We formulate supersymmetric Yang--Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.
+We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
+We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action of the supersymmetry algebra using the language of $L_\infty$ algebras.
 For each orbit in the space of square-zero supercharges in the supersymmetry algebra, under the action of the spin group and the group of R-symmetries, we give a description of the corresponding twisted theory.
-These twists can be described in terms of mixed holomorphic-topological versions of Chern--Simons and BF theory.
+These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and BF theory.
 \end{abstract}
@@
 
+%^An approach to twisting supergravity with the goal of formulating a twisted version of the AdS/CFT correspondence has been initiated in \cite{CostelloLiSUGRA}.
+
 \subsection*{Applications to Quantization}
@@
 
-To rigorously study the quantization of supersymmetric Yang--Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
+To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}.
 This theory of renormalization can been used to study field theories with and without supersymmetry: for example in \cite{CostelloWittengenus, LiLi, BCOV1, ChanLeungLi, GradyLiLi}.
-In the context of (non-supersymmetric) Yang--Mills theory for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
+In the context of (non-supersymmetric) Yang-Mills theory for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.
 
@@
 
-These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang--Mills theory.
-Furthermore, in all examples of theories obtained via twisting occurring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
+These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory.
+Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
 The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
@@
 This twist was first studied by Baulieu \cite{Baulieu}.
-As is well-known \cite{GSanomaly,CostelloLiAnomaly}, the theory has a one-loop anomaly and does not admit a quantization.
+As is well-known \cite{GSanomaly}, the theory has a one-loop anomaly and does not admit a quantization.
 \end{itemize}
@@
 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
-This twist is studied in \cite{CostelloYagi,Butson}.
+This twist is also calculated in a forthcoming work of Dylan Butson \cite{Butson}.
  \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 The corresponding theory is equivalent to a generalized BF theory defined on a product of a complex curve $C$ and a real 3-manifold $M$.
-The twist was considered in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
+The twist was considred in \cite{ElliottPestun} in the case $M=S^1\times \Sigma$ for a Riemann surface $\Sigma$, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
  \item \emph{$\mc N=2$ topological A twist.} The intermediate twist admits a deformation to two topological twists.
@@
  \item \emph{$\mc N=1$ holomorphic twist.} The holomorphic twist of the 4d $\cN=1$ super Yang--Mills theory with matter valued in a $G$-representation $R$ is equivalent to the cotangent theory of the theory of holomorphic maps from a complex surface $X$ to $R/G$.
-This twist was studied by Johansen \cite{Johansen} (see also \cite{BaulieuTanzini,CostelloSUSY}).
+This twist was studied by Johansen \cite{Johansen}.
  \item \emph{$\cN=2$ and $\cN=4$ holomorphic twist.} We may also consider holomorphic twists of 4d $\cN=2$ and 4d $\cN=4$ super Yang--Mills theories.
@@
  \item \emph{$\cN=4$ topological rank $(2, 2)$ twist.} The $\cN=4$ topological B twist admits a deformation to a perturbatively trivial theory.
-The corresponding deformation is parameterized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
+The corresponding deformation is parametrized by $s\in\CC^\times$, where $s=1$ is the topological B twist.
 Choosing a parameter $t\in\CC^\times$ satisfying $s=-t^2$, the theory counts solutions of the Kapustin--Witten equations on an oriented 4-manifold $M$.
@@
 
+%The classical solutions of this theory are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
+%\begin{align}
+%(F-\phi\wedge\phi +\d_A \phi)^+ + [F-\phi\wedge\phi, \omega] &= 0 \\
+%(F-\phi\wedge\phi -\d_A \phi)^- &= 0 \\
+%\d^*_A \phi &= 0.
+%\end{align}
+%Here $\omega$ is the K\"ahler form on $M$ and $[-, -]$ is the natural Lie bracket on differential forms given by identifying $\wedge^2 T^*_M\cong \mathfrak{so}(T_M)$.
+
 An analysis of topological twists of the 4d $\cN=4$ super Yang--Mills theory using similar techniques to this paper, but with the aim of obtaining the full derived stack of solutions to the equations of motion, rather than only the perturbative classical field theory, was carried out in \cite{ElliottYoo1}.
@@
 It is equivalent to the cotangent theory of the theory of maps from $C\times L$ to $R/G$ which are holomorphic along $C$ and locally-constant along $L$.
-This twist was studied in \cite{ACMV}.
  \item \emph{$\cN=4$ and $\cN=8$ minimal twist.} We may also consider the minimal twist of $\cN=4$ and $\cN=8$ super Yang--Mills theories.
@@
  \hline
- \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern--Simons Theory & \multirow{2}*{5 (holomorphic)} \\
+ \multirow{2}*{10} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:10dholomorphictwist]{Rank $(1,0)$}} & Holomorphic Chern-Simons Theory & \multirow{2}*{5 (holomorphic)} \\
  &&&$\mr{Map}(\CC^5, B\gg)$ &\\ \hline
- \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Generalized Chern--Simons Theory & \multirow{2}*{5 (minimal)} \\
+ \multirow{2}*{9} & \multirow{2}*{1} & \multirow{2}*{\hyperref[sect:9dminimaltwist]{Rank 1}} & Generalized Chern-Simons Theory & \multirow{2}*{5 (minimal)} \\
  &&&$\mr{Map}(\CC^4 \times \RR_{\mr{dR}}, B\gg)$ &\\ \hline
@@
  &&& $T^*[-1]\mr{Map}(\CC^4, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Generalized Chern--Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:8dpartiallytopologicaltwist]{Rank $(1,1)$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC^3 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC^3 \times \RR_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Generalized Chern--Simons Theory& \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:7dpartialtwist] {Rank $2$}} & Generalized Chern-Simons Theory& \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC^2 \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC^2 \times \RR^2_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Generalized Chern--Simons Theory} & \multirow{2}*{5} \\
+ && \multirow{2}*{\hyperref[sect:6drank22twist]{Rank $(2,2)$}} & {Generalized Chern-Simons Theory} & \multirow{2}*{5} \\
  &&& $\mr{Map}(\CC \times \RR^4_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
@@
  &&& $T^*[-1]\mr{Map}(\CC \times \RR^3_{\mr{dR}}, B\gg)$ & \\ \cline{3-5}
- && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern--Simons Theory} & \multirow{2}*{5 (topological)} \\
+ && \multirow{2}*{\hyperref[sect:5drank4twist]{Rank $4$}} & {5d Chern-Simons Theory} & \multirow{2}*{5 (topological)} \\
  &&& $\map(\RR^5_{\mr{dR}}, B\fg)$ & \\ \cline{3-5}
@@
  \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang--Mills Theories with Lie algebra $\fg$ (16 supercharges).}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}
  \label{table_of_twists_16}
@@
  && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
- &&& $\mr{Sect}(\CC^2, (U\otimes K_{\CC^2}^{1/2}) \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
- &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)$  & \\ \cline{3-5}
+ &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
  && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
@@
  && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
- &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)_{\mr{dR}}$ & \\ \hline
+ &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
   \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
  \label{table_of_twists_4}
@@
  \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
- && {$T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$} & \\ \cline{2-4}
+ && {$T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$} & \\ \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
@@
  \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories in two dimensions with gauge group $G$.
+ \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
 When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
@@
 The first main ingredient is the Batalin-Vilkovisky formalism for classical field theory (Section \ref{BV_section}).
+%, as developed by Costello and Gwilliam in \cite{CostelloBook, Book1, Book2}.  
 The other main ingredient is the systematic study of supersymmetry algebras and supersymmetric action functionals using normed division algebras (Section \ref{sect:susy}).
-We use this formalism to prove in Section \ref{sect:SYM} that super Yang--Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
+%, following Baez and Huerta \cite{BaezHuerta}.  
+We use this formalism to prove in Section \ref{sect:SYM} that super Yang-Mills theories with matter in dimensions 10, 6, 4 and 3 are in fact supersymmetric, meaning that there is a well-defined $L_\infty$ action of the supersymmetry algebra on the classical BV theory in question.
 We introduce the idea of dimensional reduction (Section \ref{dim_red_section}) for classical field theories to show that supersymmetry action are well-defined in lower dimensions.
 
-In Part \ref{classification_part} of the paper, we produce the classification of supersymmetric Yang--Mills theories in dimensions 2 to 10 systematically.
+In Part \ref{classification_part} of the paper, we produce the classification of supersymmetric Yang-Mills theories in dimensions 2 to 10 systematically.
 We start with dimension 10 and work down by dimensional reduction.
@@
 \subsection{Conventions}
-Throughout the paper we will frequently study objects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
+Throughout the paper we will frequently study obects, for instance vector bundles, equipped with a $\ZZ\times\ZZ/2\ZZ$-grading.
 \emph{Degree} will refer to the first (cohomological) grading and \emph{odd} or \emph{even} to the second (fermionic) grading.
@@
 \[\oloc(\cM) := \oloc(\cL[1]).\]
-The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg differential on $\oloc(\cM)$.
+The local $L_\infty$ structure on $\cL$ induces a Chevalley--Eilenberg diffrential on $\oloc(\cM)$.
 
@@
 \begin{proof}
-Concretely, we will write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
+Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
 The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
@@
 
+%There is a corollary of this proposition obtained by iterating the procedure. 
+%We will only use a single iteration. 
+%
+%\begin{corollary} \label{cor:quad}
+%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
+%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
+%\[
+%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
+%\]
+%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
+%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
+%Suppose further that the local functional
+%\[
+%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i}
+%\]
+%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
+%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
+%\[
+%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
+%\]
+%and
+%\[
+%S' = S_0 + \int \phi_1 \psi_1^* - S''
+%\]
+%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$
+
+%\end{corollary}
+%\begin{proof}
+%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
+%We begin by making the following change of coordinates on the BV fields:
+%\begin{align*}
+%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
+%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
+%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
+%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
+%\end{align*}
+%with $\phi_1, \psi_1$ left fixed. 
+%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
+%Further, in the new coordinates, the action takes the form
+%\[
+%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
+%\]
+%\end{proof}
+
 \subsection{Symmetries in the Classical BV Formalism} \label{symmetry_section}
@@
 \[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
-parameterizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ that satisfy the antisymmetry property
+parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ that satisfy the antisymmetry property
 \[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = (-1)^{|x_1||x_2|+1} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
@@
 The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local interaction functional 
-\[I_\fg = I + \sum_{k\geq 1} S_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
+\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
 satisfying the Maurer-Cartan equation
@@
 In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, \omega, S)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
+A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
 Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
@@
 \subsubsection{Generalized Chern--Simons Theory} \label{gen_CS_section}
-The next class of examples of classical BV theories will be generalizations of Chern--Simons theory.
-Unlike the example of the generalized BF theory, these theories are not generally of cotangent type.
+The next class of examples of classical BV theories will be generalizations of Chern-Simons theory. Unlike the example of the generalized BF theory, these theories are not generally of cotangent type.
 
@@
 \begin{example}
-For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern--Simons theory with the BV action
+For $X=Y=\pt$, $M$ a 3-manifold and $\fg$ an ordinary Lie algebra we recover the usual 3-dimensional Chern-Simons theory with the BV action
 \[S = \int_M \left(\frac{1}{2}\langle A\wedge \d_{\dR} A\rangle + \frac{1}{6}\langle A\wedge [A\wedge A]\rangle\right).\]
-More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern--Simons theory.
+More generally, if $X=Y=\pt$ and $M$ is any $d$-dimensional manifold where $d$ is odd, we recover $d$-dimensional Chern-Simons theory.
 This has the same BV action, where now $A$ is a (not necessarily homogeneous) differential form on $M$.
@@
 \[p_{\rm dR} \colon X \times Y \times (M' \times \RR) \to X \times Y \times M' .\]
-In this case, we will only need to know the dimensional reduction of generalized Chern--Simons theory.
+In this case, we will only need to know the dimensional reduction of generalized Chern-Simons theory.
 
@@
 \end{proof}
+
+%\begin{corollary}
+%Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
+%\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
+%Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
+%\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
+%\label{cor:Hodgetopologicalreduction}
+%\end{corollary}
 
@@
 So, we will discuss the classification of supersymmetry algebras, the notion of a supersymmetric field theory, and the idea of a \emph{twist} of a supersymmetric field theory, extending work of the first two authors in \cite{ElliottSafronov}.
-We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang--Mills theories in Section \ref{sect:SYM} below.
+We will introduce the classification of supersymmetry algebras using the division algebra perspective of Baez and Huerta \cite{BaezHuerta}, which will be useful for the classification of super Yang-Mills theories in Section \ref{sect:SYM} below.
 
@@
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
-The map $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $S_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
+The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
 But it also has cohomological degree $-k$.
@@
 The classical field theory $(E, S, \omega)$ carries a $\Spin(V_\RR)\times G_R$-action.
-However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $S_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
-However, given a twisting homomorphism $\phi$ we see that $S_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
+However, the $Q$-twisted theory $(E, S^Q, \omega)$ does not in general carry a $\Spin(V_\RR)\times G_R$-action since the elements $I_{\fA}^{(k)}(Q, \dots, Q)$ are not in general invariant under $\Spin(V_\RR)\times G_R$.
+However, given a twisting homomorphism $\phi$ we see that $I_{\fA}^{(k)}(Q, \dots, Q)$ is preserved under $G$, so $(E, S^Q, \omega)$ carries a $G$-action.
 
@@
 \label{def:sym}
-The BRST theory for classical supersymmetric Yang--Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
+The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2\ZZ$-graded bundle:
 \[
@@
 
-The BV theory of supersymmetric Yang--Mills is the BV theory associated to this BRST theory. 
+The BV theory of supersymmetric Yang-Mills is the BV theory associated to this BRST theory. 
 By definition, the fields are identified with sections of the bundle $T^*[-1] F_{\rm gauge} = F_{\rm gauge} \oplus F_{\rm gauge}^! [-1]$. 
@@
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
-Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the corresponding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
+Let $(-, -)^A\colon \Sigma\otimes \Sigma^*\rightarrow A$ be the correspoding $A$-valued pairing given by Lemma \ref{lm:extendpairing}.
 We make the following additional assumption.
@@
 Evaluating expression \eqref{CMEYM3} on $v_1,v_2 \in \mf{iso}(V)$ reduces to the claim that \eqref{eq:matterPoincareaction} defines a strict Lie action.
-Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $S^{(1)}$ is Poincar\'{e}-invariant.
+Evaluating on $v \in \mf{iso}(V)$ and $Q \in \Sigma$, the claim reduces to the fact that $I^{(1)}$ is Poincar\'{e}-invariant.
 So, the only nontrivial term to check is the evaluation on $Q_1,Q_2 \in \Sigma$.
@@
 It is important here that we are working in the complexified setting.
-While it makes sense to study a real form of 10d supersymmetric Yang--Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges.
+While it makes sense to study a real form of 10d supersymmetric Yang-Mills theory in Lorentzian signature associated to a real Lie algebra $\gg_\RR$, where the fermions are valued in the Majorana-Weyl spinor bundle, in this real supersymmetry algebra there are no square-zero supercharges.
 Indeed, a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
-So necessarily, twists of maximal super Yang--Mills theory cannot be compatible with any unitary structure.
+So necessarily, twists of maximal super Yang-Mills theory cannot be compatible with any unitary structure.
 \end{remark}
@@
 We are going to prove that it is perturbatively trivial.
-In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and describe the corresponding family of twisted theories.
+In fact, it will be useful to study a degeneration of the topological twist to a holomorphic twist and decribe the corresponding family of twisted theories.
 
@@
 \begin{prop}
-The functionals $S^{(1)}$ and $S^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
+The functionals $I^{(1)}$ and $I^{(2)}$ (see \eqref{eq:gaugeI1} and \eqref{eq:gaugeI2}) in terms of the fields of 8d $\cN=1$ super Yang--Mills are
 \begin{align*}
@@
 \begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.
@@
 These fields have the same degrees as in the holomorphic BF theory.
-\end{proof}
+
+\begin{comment}
+and hence the underlying local $L_\infty$ algebra after the twist becomes
+
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{0} & \ul{1} & \ul{2} & \ul{3} & \\ 
+\Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
+  & \Omega^{2,0}(\CC^2 ; \gg)_{B^*} \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*} \\
+  }
+\]
+
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{-4n+2} & \ul{-4n+3} & \ul{-4n+4} & \cdots & \ul{4n-1} & \ul{4n} & \ul{4n+1} \\ 
+ &&&& \Omega^0(\CC^2; \gg)_a \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*} \\
+ \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
+}
+\]
+
+\[
+\xymatrix@R=0.5cm@C=0.5cm{
+\ul{-2n+1} & \ul{-2n+2} & \ul{-2n+3} & \cdots & \ul{2n} & \ul{2n+1} & \ul{2n+2} \\ 
+\Omega^0(\CC^2 ; U)_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U)_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U)_{\varsigma^*} \\
+& & & & \Omega^{2,0}(\CC^2 ; U)_{\varsigma} \ar[r] & \Omega^{2,1}(\CC^2 ; U)_{\psi^*} \ar[r] & \Omega^{2,2}(\CC^2 ; U)_{\phi^*}
+}
+\]
+\end{comment}
+\end{proof}
+
+%There is an alternative $\ZZ$-grading one can assign to the twist when $U$ is of cotangent type $U = R \oplus R^*$. 
+%In this case, the $R$-symmetry group enhances to $G_R = \SL(2, \CC) \times \GL(1, \CC) \times \GL(1,\CC)$ where the last $\GL(1, \CC)$ acts by $+1$ on $R$ and $-1$ on $R^*$. 
+%The new twisting datum is $\Tilde{\alpha} \colon \U(1) \rightarrow \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC)$ given by the diagonal embedding into the last two components. 
+%%\[
+%%\begin{array}{ccccc}
+%%\alpha \colon & \U(1) & \rightarrow & \SL(2, \CC)\times \GL(1, \CC) \times \GL(1, \CC) \\
+%%&  z & \mapsto & \left(1 , z, z \right)
+%%\end{array}
+%%\]
+%There is also a new twisting homomorphism 
+%\[
+%\Tilde{\phi} \colon \MU(2) \xto{\det^{1/2}} \U(1) \xto{\Tilde{\alpha}} G_R
+%\]
+%By Theorem \ref{thm:5dminimaltwistgraded}, we obtain the following.
+%
+%\begin{thm}
+%\label{thm:4d_2minimaltwistgraded}
+%The minimal twist of $4d \cN=2$ super Yang-Mills on $M = \CC^2$ with matter representation $U = T^* R = R \oplus R^*$ is pertubatively equivalent to holomorphic BF theory with fields $T^*[-1] {\rm Map}(\CC^2 , R / \fg)$.
+%Moreover, this equivalence is $\U(2)$-equivariant.
+%\end{thm}
 
@@
 Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
-The $\MU(2)$ decomposition of the functionals $S_{\rm gauge}^{(1)}, S^{(1)}_{\rm matter}, S^{(2)}_{\rm gauge}, S^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
+The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
 \begin{align*}
@@
 \end{prop}
+%\brian{Anti field in $S^{(1)}_{matter}$.}
+%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
+%\begin{align*}
+%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varsigma, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
+%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varsigma^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
+%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varsigma^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
+%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
+%\end{align*}
 
@@
 \begin{theorem} \label{thm:4d_11_twist}
-The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang--Mills theory is perturbatively equivalent to the generalized Chern--Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
+The rank $(1,1)$ partially topological twist of 4d $\mc N=2$ super Yang-Mills theory is perturbatively equivalent to the generalized Chern-Simons theory with space of fields $\mr{Sect}(\CC \times \RR^2_{\mr{dR}}, (U \otimes K_\CC^{1/2}) \ham \gg)$.
 Moreover, this equivalence is $\U(1) \times \Spin(2, \RR)$-equivariant.
@@
  \[0\rightarrow S_+^*\rightarrow W\rightarrow S_-\rightarrow 0.\]
- Since $S_+$, $S_-$ and $W$ all carry volume forms, the space of such square-zero supercharges is parameterized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
+ Since $S_+$, $S_-$ and $W$ all carry volume forms, the space of such square-zero supercharges is parametrized by a continuous parameter $s\in\CC^\times$ given by the ratio of the isomorphism $\det(W)\cong \det(S_+)^*\otimes \det(S_-)$ induced by $Q$ and the isomorphism induced by the volume forms.
 These supercharges admit a $\ZZ$-grading and are compatible with the twisting homomorphism $\phi_{\mathrm{KW}}\colon \Spin(4, \RR)\rightarrow G_R$.
@@
 
-The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation \eqref{eqn:(2,1)2} is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
+The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
 Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
-Finally, the term in parentheses in Equation \eqref{eqn:(2,1)2} agrees with the $t$-dependent terms in Equation \eqref{eqn:(2,0)}, (where now the fields are adjoint valued). 
+Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (where now the fields are adjoint valued). 
 We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
 \end{proof}
+
+%\begin{proof}
+%Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.
+Consider the supersymmetry actions
+%\begin{align*}
+%&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
+%&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
+%\end{align*}
+%We will compute the corresponding $\ZZ$-graded $Q_{s,t}$-twisted theory.
+Our strategy will be to realize the twisted BV action functional as the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist} plus a correction term, which we will identify as turning on the Hodge deformation.
+%
+%We will make this identification by eliminating component fields from the correction term using the strategy of the proof of Theorem \ref{thm:4dDonaldsontwist}.  The correction in question is the sum
+%\begin{equation}
+%\label{eq:4d_12_general_def}
+%\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).
+%\end{equation}
+%First let us observe that the final term, $I^{(2)}(tQ_1, sQ_2)$, is proportional to $st \wt \chi^*$, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $st (Q_1,\lambda^*)$, which is proportional to $st \wt \chi^*$.
+This is important because in a moment we will be able to set $\wt \chi^* = 0$, so this term will vanish.
+%
+%Now, we will make the same moves as in the proof of Theorem \ref{thm:4dDonaldsontwist} to eliminate component fields.
+The key fact, which means that this procedure works, is that the part of the deformation of the action proportional to $s$, namely
+%\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
+%is a sum of terms that all involve both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi, \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).
+That is, none of the summands involve only fields from the vector multiplet, or only fields from the hypermultiplet.
+To be a little more precise we should say that the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.
+In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
+%
+%So, in the proof of Theorem \ref{thm:4dDonaldsontwist}, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.
+We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.
+The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.
+Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.
+Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.
+%
+%As a result of this argument, we are free, as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt\chi^*, \wt\chi + t\chi, \wt a, \wt a^*, \nu, \nu^*, \wt \nu, \wt \nu^* \rho, \rho^*, A_{1,0}$ and $A_{1,0}^*$ to 0 in the twisted action functional.
+Finally, we set the remaining eliminated field $\chi^*-t\wt\chi^*$ equal to the expression $S_1$, as in Proposition \ref{prop:integrateoutfield}.
+That is, we extract the summand in the $Q_{s,t}$-twisted action of the form $(\chi^* - t\wt \chi^*)S_1$.
+%
+%It is important that we check that this expression $S_1$ occuring in the $Q_{s,t}$-twisted action functional is equal to the corresponding expression in the $Q_0 + sQ_2$-twisted action functional, so that the presence of our correction term does not alter the $Q_0 + sQ_2$-twisted action.
+To see this, first recall that we argued above that there are no terms proportional to $st$ after setting $\wt \chi^* = 0$.
+Then, look at terms proportional to $t \chi^*$ in equation \ref{4d_donaldson_susy_prop}.
+Notice that all such terms are also proportional to $\wt \chi^*$, so vanish after setting $\wt \chi^* = 0$.
+%
+%We have therefore shown that the $Q_{s,t}$-twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation \ref{eq:4d_12_general_def}.
+The $st$-term vanishes, and the deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
+%\begin{equation}
+%\label{eq:4d_12_further_deformation}
+%t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varsigma, \phi^*) + \frac 14 (\psi^*, \psi^*) \right)
+%\end{equation}
+%in terms of the $\mr U(2)$-component fields, which can be further broken to $\spin(2;\RR) \times \spin(2;\RR)$.
+%
+%Therefore, the $Q_{s,t}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.
+This deformation gives the desired theory.
+The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.
+Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(2,1)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.
+%\end{proof}
 
@@
 Comparing these volume forms under the above exact sequence gives an invariant $s\in\CC^\times$ of a rank $(2, 2)$ square-zero supercharge.
-Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parameterized by this invariant.
+Moreover, $\Spin(6, \CC)$-orbits of rank $(2, 2)$ square-zero supercharges are parametrized by this invariant.
 
@@
 Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
+%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.
+Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.
 
@@
 
+%\begin{proof}
+%On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.
+We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.
+The dimensionally reduced theory is a $\ZZ$-graded and $\mr U(1)$-equivariant theory, equivalent as a $\ZZ/2\ZZ$-graded theory to the one obtained from 3d $\mc N=4$ -- this promotes the description given above to a $\ZZ$-graded and $\mr U(1)$-equivariant theory.
+When we calculate that dimensional reduction, the fields reduce according to the rule
+%\begin{align*}
+%\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
+%&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
+%\end{align*}
+%Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
+%\end{proof}
+
 \subsubsection{Topological Twists}
@@
 \vspace{-10pt}
-\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang--Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section}, to representations of the group $\spin(2;\CC)$.
+\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 4d fields from Section \ref{sect:4d_1_section}, to representations of the group $\spin(2;\CC)$.
 In any case, the fields we obtain are
@@
 The calculation of the twists here is similar to what we saw in 4d $\mc N=2$ supersymmetry.  
-The holomorphic twist and the B-twist arise by a dimensional reduction from twists of the 3d $\cN=2$ supersymmetric Yang--Mills theory.
+The holomorphic twist and the B-twist arise by a dimensional reduction from twists of the 3d $\cN=2$ supersymmetric Yang-Mills theory.
 On the contrary, the A-twist as a deformation of the holomorphic twist does not arise as a dimensional reduction.
@@
 \begin{theorem} \label{2d_minimal_twist_thm}
-The holomorphic twist of the 2d $\cN=(2,2)$ super Yang--Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$.
+The holomorphic twist of the 2d $\cN=(2,2)$ super Yang-Mills theory with matter valued in a complex $\fg$-representation $R$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\mr{Map}(\CC, T[1](R/\gg))$.
 Moreover, this equivalence is $\mr U(1)$-equivariant.
@@
 A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
-There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are collinear, or they are distinct.  
+There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  
 These are the B- and A-supercharges respectively.
@@
 Indeed, the 3d $B$-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  
-Therefore the two vectors in $W_+^6$ discussed above must be collinear.
+Therefore the two vectors in $W_+^6$ discussed above must be colinear.
 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang-Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 
-The 2d $\cN=(8, 8)$ super Yang--Mills theory is a dimensional reduction of the 3d $\cN=8$ super Yang--Mills theory.
-Therefore, from Theorem \ref{3d_8_minimal_twist_thm} we obtain the following statement.
+From Theorem \ref{thm:2d44holomorphictwist} we obtain the following statement.
 
 \begin{theorem}
-The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC_{\mathrm{Dol}}, T[1] \fg/\fg)$.
+The holomorphic twist of the 2d $\mc N=(8,8)$ super Yang--Mills theory is perturbatively equivalent to a holomorphic BF theory with the space of fields given by $T^*[-1]\mr{Map}(\CC, T[1] T^*(\fg/\fg))$.
 This equivalence is $\mr U(1)$-equivariant.
@@
 
-We turn to the $\cN=(2,0)$ supersymmetric Yang--Mills theory.
+We turn to the $\cN=(2,0)$ supersymmetric Yang-Mills theory.
 In the supersymmetry algebra, we have $W_-=0$ and $W_+$ is a complex two-dimensional vector space equipped with a symmetric pairing. 
@@
 \begin{theorem} \label{thm:2d(2,0)}
-The minimal twist of 2d $\cN=(2,0)$ super Yang--Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
+The minimal twist of 2d $\cN=(2,0)$ super Yang-Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory coupled to the holomorphic $\beta\gamma$ system with moduli space $T^*[-1] \map(\CC , R / \fg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 \item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$.
-\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$.
+\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$;
+\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
+%\item \brian{matter fermions $\psi \in C^\infty(\RR^2 ; S_- \otimes W_+ \otimes U)$}
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha : \U(1) \to G_R$. 
+%We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(0,2)}.
+%We take $\alpha : \U(1) \hookrightarrow \spin(2;\CC) \to \spin(4;\CC)$ to factor through the twisting data of Section \ref{sect:2d(0,2)}.
+%There is a compatible twisting homomorphism
+%\[
+%\phi : \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R 
+%\]
+%which factors through the twisting homomorphism of 2d $(2,0)$ supersymmetric Yang--Mills theory in Section \ref{sect:2d(0,2)}.
 \end{itemize}
@@
 S_{\mr{matter}} &= \int \dvol \bigg( (\dd_{A_{1,0}} \nu , \ol \dd_{A_{0,1}} \gamma) + (\dd_{A_{1,0}}\gamma, \ol \dd_{A_{0,1}} \nu) + (\psi_- , \partial_{A_{1,0}} \gamma) + (\psi_+ , \partial_{A_{1,0}} \nu)  + \\
+%&\qquad + ([\lambda^+_{1,0}, ],\psi_0) + ([\lambda_{1,0}, \psi_0], \gamma_{0,1})   \bigg) \/\
 & \qquad + ([\lambda^+, \gamma], \psi_-) + ([\lambda_{1,0}^+, \nu], \psi_-) + ([\lambda^-, \gamma], \psi_+) + ([\lambda^-_{1,0}, \nu], \psi_-) \bigg) \\
@@
 
+%The field content is:
+%\begin{itemize}
+%\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^2;\fg)$.
+%\item $\fg$-valued fermions: a spinor $\lambda \in C^\infty(\RR^2 ; S_- \otimes W_- \otimes \fg)$. 
+%\item $W \otimes U$-valued scalars: $\phi \in C^\infty(\RR^2 ; W \otimes U)$;
+%\item $W \otimes U$-valued fermions: $\psi \in C^\infty(\RR^2 ; W \otimes S_+ \otimes U)$ .
+%\end{itemize}
+
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
+
 \begin{theorem} \label{thm:2d(4,0)}
@@
 
+%\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}
+%
+%\begin{theorem}\label{2d(0,4)}
+%The minimal twist of 2d $\cN=(0,4)$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=(0,4)$ hypermultiplet is $U(1)$-equivariantly equivalent to holomorphic BF theory on $\CC$ for the Lie algebra $\fg$ coupled to the free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \oplus \fg$ where $\fg$ acts by the adjoint action plus the free $\beta\gamma$ system on $\CC$ valued in the $\fg$-representation $U$.
+%\end{theorem}
+%
+%\begin{proof}
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,4)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(W)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(W)$. 
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(0,2)}. 
+%Furthermore, under this embedding the $(0,4)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The $(0,4)$ hypermultiplet becomes a $(0,2)$ chiral multiplet valued in the representation $U$. 
+%The claim now follows from Theorem \ref{2d(0,2)}. 
+%\end{proof}
+%
+%\begin{remark}
+%The matter sector in the untwisted theory depends on $U$ as a complex symplectic $\fg$-representation. 
+%The matter sector in the twisted theory only depends on $U$ as a complex $\fg$-representation, the dependence on the symplectic form disappears when we twist.
+%\end{remark}
+
 \subsection{\texorpdfstring{$\cN=(\cN_+,0)$}{N=(N+,0)} Super Yang--Mills Theory}
 
-We consider pure $\cN=(\cN_+,0)$ super Yang--Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
+We consider pure $\cN=(\cN_+,0)$ super Yang-Mills for a Lie algebra $\fg$, where $\cN_+ \geq 2$.
 The spinorial representation is $\Sigma = S_+ \otimes W_+$ where $W_+$ is the $\cN_+$-dimensional auxiliary space equipped with a nondegenerate symmetric bilinear pairing.
@@
 We take the twisting datum $\alpha$ and twisting homomorphism $\phi$ to factor through those of Section \ref{sect:2d(2,0)}.
-\end{itemize}
+%We take $\alpha \colon U(1) \hookrightarrow G_R$ to be the standard embedding.
+%There is a compatible twisting homomorphism
+%\[
+%\phi \colon \U(1) \xto{\det^{1/2}} \U(1) \hookrightarrow G_R .
+%\]
+\end{itemize}
+
+%We twist by the nilpotent supercharge $Q = q \otimes u_1$ where $q \in S_-$ is any nonzero vector.
 
@@
 \begin{theorem} \label{thm:2d(N,0)}
-The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang--Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
+The holomorphic twist of 2d $\cN=(\cN_+,0)$ super Yang-Mills is perturbatively equivalent to the holomorphic $BF$ theory with the space of fields $T^*[-1]\mr{Sect}(\CC, (\fg^{\mc N_+ -2} \otimes K_{\CC}^{1/2}) / \gg)$.
 This equivalence is $\U(1)$-equivariant.
@@
 First, we integrate out the field $\lambda_{0}$ using Proposition \ref{prop:integrateoutfield}.  
+%The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
 We then observe that the action includes the term $\int  (\lambda_{1,0} , A_{1,0}^*)$.
@@
 
+%\begin{proof}
+%The proof is similar to the proof of Theorem \ref{thm:2d(4,0)}.
+%The supercharge $Q$ lies in a $\cN = (0,2)$ subalgebra of the full $\cN = (0,\cN_-)$ algebra.
+%On the odd part of the supersymmetry algebras, this embedding is induced by the algebra map
+%\[
+%S_- \otimes \CC[x] / x^2 \to S_- \otimes {\rm End}(\CC^2)
+%\]
+%given by the identity on $S_-$ and the $2 \times 2$ matrix $\begin{pmatrix} 0 &1 \\ -1 & 0 \end{pmatrix}$ on $\CC[x]/x^2 \to {\rm End}(\CC^2)$. 
+%Here, $\CC^2$ is spanned by $\{u,v\}$ in the decomposition of $W_-$ given above.
+%Under this embedding we see that the scalar supercharge $Q$ is precisely the same as the scalar supercharge we used to twist in Section \ref{sect:2d(2,0)}. 
+%Furthermore, under this embedding the $(0,\cN_-)$ vector multiplet $(A, \lambda)$ splits as a $(0,2)$ vector multiplet plus a $(0,2)$ Fermi multiplet valued in $\fg \otimes W_-'$. 
+%The $(0,2)$ supersymmetry algebra acts trivially on the Fermi multiplet. 
+%The claim now follows from a special case of Theorem \ref{thm:2d(2,0)} where we take $R = 0$. 
+%\end{proof}
+
 \pagestyle{bib}

### 2020-04-14 paper.tex
type in 6d(1,0)

@@
 &\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
-S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
+S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \partial_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
 &\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
@@
 \begin{theorem}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
-The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
+The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$-representation-representation $R$ is perturbatively equivalent to holomorphic BF theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$.
 Moreover, the equivalence is $\U(2)$-equivariant.

### 2020-04-20 paper.tex
signs

@@
 \[
-D_1(-) \cdots D_n(-) \Omega
+D_1(-) \cdots D_m(-) \Omega
 \]
@@
 \[
-\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
+\phi \mapsto \int_M D_1(\phi) \cdots D_m(\phi) \Omega
 \]
@@
 \begin{align*}
-\d_{\mr{dR}} F  \colon  \cE_c^{\times (n-1)} & \to  \cE^\vee \\
- (\phi_1, \ldots, \phi_{n-1}) & \mapsto  D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
+\d_{\mr{dR}} F  \colon  \cE_c^{\times (m-1)} & \to  \cE^\vee \\
+ (\phi_1, \ldots, \phi_{n-1}) & \mapsto  D_1(\phi_1) \cdots D_{m-1}(\phi_{m-1}) D_{m} (-) + \{{\rm symmetric\;terms}\} .
 \end{align*}
-Integrating by parts, we see that for any $(n-1)$-tuple $(\phi_1, \ldots, \phi_{n-1}) \in \cE_c^{n-1}$ the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
+Integrating by parts, we see that for any $(m-1)$-tuple $(\phi_1, \ldots, \phi_{m-1}) \in \cE_c^{m-1}$ the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{m-1})$ is an element of $\cE^!$. 
 This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.
@@
 The Poisson bracket enjoys the graded skew symmetry property
-\[\{F, G\} = (-1)^{|F| |G|} \{G, F\}\]
+\[\{F, G\} = (-1)^{|F||G|+n+1} \{G, F\}\]
 as well as the graded Jacobi identity.
@@
 The structure of the $L_\infty$ brackets can be encoded into its potential.
-In the same way, the structure of a local $L_\infty$ algebra $L$ together with an $n$-shifted symplectic structure on $BL$ may be encoded into the \defterm{action functional} $S\in\oloc(BL)$ of cohomological degree $1-n$ such that
+In the same way, the structure of a local $L_\infty$ algebra $L$ together with an $n$-shifted symplectic structure on $BL$ may be encoded into the \defterm{action functional} $S\in\oloc(BL)$ of cohomological degree $n+1$ such that
 \[S = \frac{1}{2}\int_M\omega(e, Q_{BV} e) + I,\]

### 2020-04-22 paper.tex
twisting

--- 2020-04-14 paper.tex
@@
 
-Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
+Let $(E, S, \omega)$ be a supersymmetric classical field theory. 
+Recall, this means we have a Maurer-Cartan element 
 \[
@@
 Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight $+1$ and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
 
+Recall, that before twisting the bundle $E$ is $\ZZ \times \ZZ/2$-graded.
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
@@
 In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
+
+\begin{rmk}
+There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ be such that the twisting supercharge $Q$ be weight $+1$. 
+One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
+This results in new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. 
+This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agree with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be concentrated purely even in the new $\ZZ/2$-degree.
+\end{rmk}
 

### 2020-04-22 paper.tex
typos

--- 2020-04-20 paper.tex
@@
 Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight $+1$ and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
 
+Recall that before twisting the bundle $E$ is $\ZZ \times \ZZ/2$-graded.
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
@@
 In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
+
+\begin{rmk}
+There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ is such that the twisting supercharge $Q$ is of weight $+1$. 
+One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
+This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. 
+This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be purely even in the new $\ZZ/2$-degree.
+\end{rmk}
 

### 2020-04-22 paper.tex
merge

--- 2020-04-22 paper.tex
@@
 
-\newcommand{\BV}{\mathrm{BV}}
-\newcommand{\Cl}{\mathrm{Cl}}
-\newcommand{\Dens}{\mathrm{Dens}}
-\newcommand{\gauge}{\mathrm{gauge}}
-\newcommand{\Gm}{\mathbb{G}_m}
-\newcommand{\Hod}{\mathrm{Hod}}
-\newcommand{\matter}{\mathrm{matter}}
-\newcommand{\ML}{\mathrm{ML}}
-\newcommand{\MU}{\mathrm{MU}}
 \renewcommand{\Re}{\mathrm{Re}}
@@
 
-Let $(E, S, \omega)$ be a supersymmetric classical field theory. 
-Recall, this means we have a Maurer-Cartan element 
+Let $(E, S, \omega)$ be a supersymmetric classical field theory. Recall, this means we have a Maurer-Cartan element 
 \[
@@
 Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight $+1$ and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
 
-Recall, that before twisting the bundle $E$ is $\ZZ \times \ZZ/2$-graded.
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
@@
 In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
-
-\begin{rmk}
-There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ be such that the twisting supercharge $Q$ be weight $+1$. 
-One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
-This results in new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$. 
-This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agree with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be concentrated purely even in the new $\ZZ/2$-degree.
-\end{rmk}
 

### 2020-04-22 paper.tex
edited remark

--- 2020-04-22 paper.tex
@@
 \input ./combined_macros.sty
-
-\newcommand{\BV}{\mathrm{BV}}
-\newcommand{\Cl}{\mathrm{Cl}}
-\newcommand{\Dens}{\mathrm{Dens}}
-\newcommand{\gauge}{\mathrm{gauge}}
-\newcommand{\Gm}{\mathbb{G}_m}
-\newcommand{\Hod}{\mathrm{Hod}}
-\newcommand{\matter}{\mathrm{matter}}
-\newcommand{\ML}{\mathrm{ML}}
-\newcommand{\MU}{\mathrm{MU}}
-\renewcommand{\Re}{\mathrm{Re}}
-\newcommand{\Sect}{\mathrm{Sect}}
-\renewcommand{\U}{\mathrm{U}}
-
-\newcommand{\ham}{/\!\!/}
-
-\newcommand{\defterm}[1]{\textbf{\emph{#1}}}
 
@@
 
-\begin{rmk}
-There is a slight generalization of this regrading procedure where one only requires that the homomorphism $\alpha$ is such that the twisting supercharge $Q$ is of weight $+1$. 
-One then defines a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously rotating the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$. 
+\begin{remark}
+There is a slight generalization of this regrading procedure where one only relaces the requirement that the $\alpha$-weight coincides mod 2 with the fermionic grading, only requiring that the twisting supercharge $Q$ is of weight $+1$.
+Given an action $\alpha$ of this more general class, one can define a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously shifting the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$.
 This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$.
-This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be purely even in the new $\ZZ/2$-degree.
-\end{rmk}
+This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be concentrated purely in the even $\ZZ/2$-degree part.
+\end{remark}
 

### 2020-04-29 Rough_Superconformal_CS_notes.tex
submitted version, conforming to formatting requirements

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\addbibresource{Twist.bib}

\title{Note on Superconformal Chern--Simons}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}

\section*{Rough Note on Supersymmetry in Superconformal Chern--Simons}
Choose a real semisimple Lie algebra $\gg$, a real representation $U$ of $\gg$ equipped with an inner product, and a superpotential $\mf W \colon U \to \RR$.  Let $\Sigma = S_\RR \otimes \Delta$ be a real spinorial representation of $\so(1,2)$, where $S_\RR$ is the 2-dimensional Majorana spin representation and $\Delta$ is equipped with an inner product (so we are considering $\mc N = \dim(\Delta)$ supersymmetry).  Superconformal Chern--Simons will have the following BRST fields in addition to the ghost $c$.
\begin{align*}
A &\in \Omega^0(\RR^3; \gg) \\
X &\in \Pi \Omega^0(\RR^3; U) \\
\Psi &\in \Pi \Omega^0(\RR^3; U \otimes \Sigma).
\end{align*}
Choose a supercharge $Q \in \Sigma$.  We define on-shell supersymmetry transformations by $Q$ to be
\begin{align*}
\delta_Q X &=  \langle Q, \Psi \rangle\\
\delta_Q \Psi &= -\frac 12\left(\rho(\d_A X)Q + \nabla\mf W(X)Q\right)\\
\delta_Q A &= k\, T(X, \Gamma( Q, \Psi )).
\end{align*}
Here $\langle - , - \rangle$ is the skew-symmetric scalar pairing on $\Sigma$ and $T \colon U \otimes U \to \gg$ is the skew-symmetric map obtained from the action using the inner products on $U$ and $\gg$.  Also we've included a number $k$ to be determined, which may depend on $\mc N$.

Let's sketch the anticommutation relations of the $\delta_Q$ operators.  I'm initially going to assume that $\mc N=\dim \Delta = 1$.  Start with the action on $X$.
\begin{align*}
\delta_{Q} \delta_{Q'}X &= \langle Q', \delta_{Q}\Psi \rangle \\
&= - \frac 12 \langle Q', \rho(\d_A X)Q \rangle - \frac 12 \nabla\mf W(X) \langle Q', Q \rangle \\
\text{so } [\delta_Q, \delta_{Q'}]X &= - \frac 12\langle Q', \rho(\d_A X)Q\rangle - \frac 12\langle Q, \rho(\d_A X)Q'\rangle \\
&= \frac 12\langle \rho(\d_A X)Q, Q'\rangle + \frac 12\langle \rho(\d_A X)Q', Q\rangle \\
&= \frac 12g(\rho(\d_A X), \Gamma(Q',Q) + \Gamma(Q,Q')) \\
&=  g(\rho(\d_A X), \Gamma(Q',Q)) \\
&= (\dd_i + A_i)X,
\end{align*}
where $\Gamma(Q',Q)$ is translation in the $x^i$ direction.  This looks pretty good.

Now let's do the analogous calculation for $A$.
\begin{align*}
\delta_{Q} \delta_{Q'}A &= k \left( T(\delta_Q X, \Gamma( Q, \Psi )) + T(X, \Gamma( Q', \delta_{Q}\Psi )) \right) \\
&= k \left( T(\langle Q', \Psi \rangle, \Gamma( Q, \Psi )) + \frac 12T(X, \Gamma( Q', \delta_{Q}\Psi )) \right) \\
&= k \left( T(\langle Q', \Psi \rangle, \Gamma( Q, \Psi )) + \frac 12T(X, \Gamma( Q', \rho(\d_A X)Q + \Gamma(Q',Q)\nabla \mf W(X)))\right).
\end{align*}
The first two terms are anti-symmetric in $Q$ and $Q'$ \chris{I think?  I checked it fairly easily for the second term but I'm getting confused with the first term}.  Therefore
\[[\delta_Q,\delta_{Q'}]A = k\Gamma(Q,Q')T(X, \nabla \mf W(X)).\]

The Chern--Simons gauge field $A$ is supposed to be topological so translations should act trivially on $A$.  This term is, therefore, something that should vanish on-shell.

If we compute $[\delta_Q, \delta_{Q'}]\Psi$ we get something more complicated.  
\begin{align*}
\delta_{Q} \delta_{Q'}\Psi &=-\frac 12\left( \rho(\d_A (\delta_Q X)Q' + \rho(\delta_Q(A)\cdot X)Q' + \nabla \mf W(\delta_Q X)Q' \right) \\
&= -\frac 12\left( \rho(\langle Q, \d_A(\Psi)\rangle)Q' + k \rho(T(X, \Gamma( Q, \Psi ))\cdot X)Q' + \nabla \mf W(\langle Q, \Psi\rangle)Q' \right).
\end{align*}
If we take the first term alone and symmetrize then we get
\begin{align*}
-\frac 12 \left(\rho(\d_A (\delta_Q X)Q' + \rho(\d_A (\delta_{Q'} X)Q \right) &= \frac 12\left( g(\d_A \Psi, \Gamma(Q, Q') + \Gamma(Q',Q)\right) \\
&= (\dd_i + A_i)\Psi,
\end{align*}
so this term alone gives the Lie derivative.  The other two terms should be $Q_{\mr{BV}}$-exact.  So in total we're claiming that
\begin{align*}
T(X, \nabla \mf W(X)) &\in \Omega^0(\RR^3; \gg) \\\
T(X, \Psi ))\cdot X &\in \Omega^0(\RR^3;U \otimes S) \\
\text{ and } T(X, \nabla \mf W(\Psi)) &\in \Omega^0(\RR^3; \gg \otimes S) 
\end{align*}
all vanish on-shell.  The vanishing of the first two follow from the claims in the paper that the supersymmetry closes off-shell when you insert auxiliary fields, which on-shell take the values $\chi = \frac 12 T(X,\Psi)$ and $C = \nabla \mf W(X)$ (suppressing the pairing on $U$).  I'm not immediately sure about the third.

Let's try to work it out in the BV formalism.  Let me first of all try the simplest, abelian, case where $\gg = \mf u(1)$ and $\mf W$ is quadratic.  Say $\left| \nabla \mf W(X)\right|^2 = (X, m^2(X))$, for some $m^2 \in \GL(U)$.  The classical BV complex looks like
\[\xymatrix{
\Omega^0(\RR^3)_c \ar[r]^\d &\Omega^1(\RR^3)_A \ar[r]^\d &\Omega^2(\RR^3)_{A^*} \ar[r]^d &\Omega^3(\RR^3)_{c^*} \\
&\Omega^0(\RR^3;U)_X \ar[r]^{\Delta + m^2} &\Omega^0(\RR^3; U)_{X^*} & \\
&\Pi \Omega^0(\RR^3; S_\RR)_\Psi \ar[r]^{\sd \d - m^2} &\Pi \Omega^0(\RR^3; S_\RR)_{\Psi^*}.
}\]
Even in this case the theory isn't quite free: it has a quartic interaction of the form $|T(X,\Psi)|^2$. \chris{I'm gonna keep thinking about this.}

% \begin{itemize}
%  \item There should only be an $\mc N=\dim(\Delta)$ supertranslation action given appropriate constraints on $\gg$, $U$ and $\mf W$.
%  \item Even when these constraints are satisfied, $([\delta_Q, \delta_{Q'}] - \mc L_{\Gamma(Q,Q')})\Psi$ should not equal zero, but rather something $Q_{\mr{BV}}$-exact.
% \end{itemize}

\end{document}

### 2020-04-29 paper_selecta.tex
submitted version, conforming to formatting requirements

--- 2020-04-22 paper.tex
@@
-\documentclass[10pt, oneside]{article}
-
-\input ./combined_macros.sty
+\documentclass[10pt, oneside]{amsart}
+
+\input ./combined_macros_selecta.sty
 
@@
 
-\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=red!30]
+\tikzstyle{s16} = [rectangle, rounded corners, text centered, draw=black,fill=black!90,text=white]
 \tikzstyle{s16chiral} = [s16, dashed]
-\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=orange!30]
-\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black,fill=yellow!30]
+\tikzstyle{s8} = [rectangle, rounded corners, text centered, draw=black,fill=gray!30]
+\tikzstyle{s4} = [rectangle, rounded corners, text centered, draw=black]
 \tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, text centered, draw=black,fill=green!30]
@@
 
-\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory}
+\title[A Taxonomy of Twists of SUSY Yang--Mills Theory]{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory}
 \author{Chris Elliott\and Pavel Safronov \and Brian Williams}
@@
 These twists can be described in terms of mixed holomorphic-topological versions of Chern-Simons and BF theory.
+
+\textbf{Keywords:} Supersymmetry, gauge theory, $L_\infty$ algebra, BV formalism,
+
+\textbf{AMS Subject Classification:} 81Q60, 70S15
 \end{abstract}
 
-\pagestyle{intro}
+%\pagestyle{intro}
 \setcounter{tocdepth}{2}
@@
 \label{sect:intro}
-\addcontentsline{toc}{section}{Introduction}
 
@@
  \centering
+ \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{c|c|c|c|c}
@@
  \end{tabular}
+ \end{adjustbox}
  \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}
@@
   \end{tabular}
+  \end{adjustbox}
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
@@
  \centering
+ \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{c|>{\centering}m{5ex}|c|>{\centering}m{65ex}|c}
@@
   \end{tabular}
+  \end{adjustbox}
  \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
@@
  \centering
+ \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{c|c|c|c}
@@
  \end{tabular}
+ \end{adjustbox}
  \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
@@
 \clearpage
-\begin{figure}[hbp]
+\begin{figure}[!hbp]
+\begin{adjustbox}{max width=\textwidth}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+\end{adjustbox}
 \caption{This figure shows the orbits of square-zero supercharges in each dimension, and how they relate to one another under dimensional reduction.
@@
 
-\pagestyle{standard}
+%\pagestyle{standard}
 \part{Supersymmetric Gauge Theory} \label{formalism_part}
@@
 \{S_{\gauge}, S_{\gauge}^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{\d}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{\d}_A \lambda + [c, \lambda^*]) \\
-&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* - (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) \\
-&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*.
+&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{\d}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(\d_A c) c^* + \\
+&- (\d_A\iota_{\Gamma(Q_1, Q_2)} A, A^*) + ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*.
 \end{align*}
@@
 Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory.
-The former is given by (cf.
-the proof of Theorem \ref{thm:8dholomorphictwist})
-\[
+The former is given by
+
+\begin{centering}
+\begin{adjustbox}{max width=\textwidth}
 \xymatrix@C=0.5cm{
@@
 }
-\]
-which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
+\end{adjustbox}
+\end{centering}
+
+(cf. the proof of Theorem \ref{thm:8dholomorphictwist}), which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
 \end{proof}
@@
 the proof of Theorem \ref{thm:4d2holomorphictwist})
-\[
+
+\begin{adjustbox}{max width=\textwidth}
 \xymatrix@R=0.5cm@C=0cm{
@@
 }
-\]
+\end{adjustbox}
+
 which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
@@
 We can identify the linearized BV complex with the following diagram:
-\[\xymatrix@R=0.4cm@C=0.2cm{
+
+\begin{adjustbox}{max width=\textwidth}
+\xymatrix@R=0.4cm@C=0.2cm{
 \ul{-2} & \ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} \\
@@
 &&& \Omega^{1,0}(\CC; R)_{\beta_{1,0}} \ar[r]  &\Omega^{1,1}(\CC; R)_{\Tilde{\psi}_0^*}. &\\
-}\]
+}
+\end{adjustbox}
+
 Here, the solid arrows represent the linearized BV operator of the minimal twist, and the dotted arrows represent the $t$-dependent terms.
@@
 
-\pagestyle{bib}
+%\pagestyle{bib}
 \printbibliography

### 2020-04-29 paper_selecta.tex
minor fix

@@
 Each column is labelled by a dimension, and each row by the number of invariant directions of the supercharge.
-Colours indicate the maximal supersymmetry algebra where the given supercharges live, so red indicates supercharges defined in algebras with 16 supercharges, orange those with 8 supercharges, and yellow those with 4 supercharges.
+Colours indicate the maximal supersymmetry algebra where the given supercharges live, so black indicates supercharges defined in algebras with 16 supercharges, gray those with 8 supercharges, and white those with 4 supercharges.
 There is an arrow whenever one twist dimensionally reduces to another twist one dimension lower.}

### 2020-10-17 paper.tex
typo

@@
 
-\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for the 4d $\cN=4$ super Yang--Mills theory, in which case it has three compatible twisting homomorphisms \cite{Yamron}, i.e.
+\item \emph{$\cN=4$ topological rank $(2, 0)$ twist.} The same twist may be considered for the 4d $\cN=4$ super Yang--Mills theory, in which case it has three compatible twisting homomorphisms \cite{Yamron} (see also \cite{LabastidaLozano,Lozano} for more details), i.e.
 there are three ways of interpreting the differential equations on arbitrary oriented 4-manifolds.
@@
 \end{align}
-Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus} and Kapustin and Witten \cite{KapustinWitten}.
+Finally, the third twisting homomorphism was studied by Marcus \cite{Marcus}.
 The classical solutions are given by principal $G_\RR$-bundles $P\rightarrow M$ together with a connection $A$ and a one-form $\phi\in\Omega^1(M, \mathrm{ad} P)$ which satisfy
@@
 \end{align}
+Twists of the 4d $\cN=4$ super Yang--Mills theory in the context of lattice gauge theory were also studied in \cite{Catterall,Unsal}.
 
@@
 \begin{equation}
-S_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}A, \phi^*) - (v.\psi, \psi^*)\right),
+S_{\matter}^{(1)}(v) = \int_{V_\RR}\dvol\left( (L_{v}\phi, \phi^*) - (v.\psi, \psi^*)\right),
 \label{eq:matterPoincareaction}

### 2022-02-24 twist_selecta_referee_comments.tex

\documentclass[10pt, oneside]{article}

\input ./combined_macros.sty

\addbibresource{Twist.bib}

\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory -- Comments on Referee Report}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

\date{\today}

\begin{document}
\maketitle

We are very grateful to the referee for their numerous helpful comments.  Please find below a summary of the changes we have made in response to the report.

\begin{enumerate}
 \item Page 8:
 \item Page 18:
 \item Page 20 points 1 and 2:
 \item Page 20 point 3:
 \item Page 28:
 \item Page 29
 \item Page 32:
 \item Page 34 point 1:
 \item Page 34 point 2:
 \item Page 35:
 \item Page 36:
 \item Page 37:
 \item Page 38:
 \item Page 51:
 \item Page 52:
 \item Page 54:
 \item Page 56:
\end{enumerate}

\end{document}

### 2022-03-01 paper_journal_edits.tex
Trying to incorporate arxiv corrections that weren't in this version

--- 2020-02-24 arxiv - Feb 2020/taxonomy_arxivFeb20.tex
@@
 In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.
-However, a significant simplification happens at the level of the {\em twisted} supersymmetric Yang-Mills theories that we study in this work.
+However, a significant simplification happens at the level of the {\em twisted} supersymmetric Yang--Mills theories that we study in this work.
 To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}.
@@
 These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang--Mills theory.
-Furthermore, in all examples of theories obtained via twisting occurring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
+Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
 The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
@@
 In Tables \ref{table_of_twists_16}, \ref{table_of_twists_8} and \ref{table_of_twists_4} we summarize all the possible twists of dimensional reductions of the 10d $\cN=(1, 0)$, 6d $\cN=(1, 0)$ and 4d $\cN=1$ super Yang--Mills theories respectively.
-In Table \ref{table_of_twists_2d} we summarize the twists of 2d supersymmetric Yang-Mills theory.
+In Table \ref{table_of_twists_2d} we summarize the twists of 2d supersymmetric Yang--Mills theory.
 Before these tables, we will give a short description of each twisted theory in a more physical language, with references to where in the literature it was previously considered.
@@
 This twist was first studied by Baulieu \cite{Baulieu}.
-As is well-known \cite{GSanomaly,CostelloLiAnomaly}, the theory has a one-loop anomaly and does not admit a quantization.
+As is well-known \cite{GSanomaly, CostelloLiAnomaly}, the theory has a one-loop anomaly and does not admit a quantization.
 \end{itemize}
@@
 The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
- \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor.
+ \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor \footnote{When we refer to the \emph{rank} of a supercharge we will always mean the rank as a tensor, for instance in the 8d $\mc N=8$ case supercharges live in a tensor product $S \otimes W$, where $S$ is an irreducible representation of $\spin(8)$ and $W$ is a two-dimensional auxiliary symplectic vector space.}.
 This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface.
@@
 6d $\cN=(1, 1)$ super Yang--Mills corresponds to the special case $R=\fg$.
-This twist is studied in \cite{CostelloYagi,Butson}.
+This twist is studied in work of Costello--Yagi and of Butson \cite{CostelloYagi,Butson}.
  \item \emph{$\mc N=(1,1)$ rank $(2, 2)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.
@@
 It is equivalent to the cotangent theory of the theory of maps from $C\times L$ to $R/G$ which are holomorphic along $C$ and locally-constant along $L$.
-This twist was studied in \cite{ACMV}.
+This twist was studied in \cite{ACMV}
+
  \item \emph{$\cN=4$ and $\cN=8$ minimal twist.} We may also consider the minimal twist of $\cN=4$ and $\cN=8$ super Yang--Mills theories.
@@
 One can also formulate actions of a Lie algebra on a classical theory in these terms. 
-The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, \omega, S)$ is equivalent to the choice of a local interaction functional 
-\[I_\fg = I + \sum_{k\geq 1} S_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
+The data of an action of a Lie algebra $\fg$ on a classical field theory $(E, Q_{\mr{BV}}, \omega, S)$ is equivalent to the choice of a local interaction functional 
+\[I_\fg = I + \sum_{k\geq 0} I_{\fg}^{(k)} \text{ in } C^\bullet(\fg, \oloc(\cE)),\]
 satisfying the Maurer-Cartan equation
@@
 Let $Q\in\Sigma$ be a square-zero supercharge.
-A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight 1 and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
+A homomorphism $\alpha\colon U(1)\rightarrow G_R$ is \defterm{compatible} with $Q$ if $Q$ has weight $+1$ and the $\alpha$-weight mod 2 on $E$ coincides with the fermionic grading.
 \end{definition}
 
+Recall that before twisting the bundle $E$ is $\ZZ \times \ZZ/2$-graded.
 Given such an $\alpha$ we may consider a new $\ZZ$-grading on $E$ given by the sum of the cohomological grading and the grading given by $\alpha$.
-The map $S_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $S_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
+The map $I_{\fA}^{(k)}\colon \fA^{\otimes k} \to \oloc(\cE)$ is $G_R$-equivariant, so the element $I_{\fA}^{(k)}(Q, \dots, Q)$ has $\alpha$-weight $k$.
 But it also has cohomological degree $-k$.
 In other words, the twisted action $S^Q$ has total degree zero, so $(E, S^Q, \omega)$ is a $\ZZ$-graded classical field theory.
+
+\begin{remark}
+There is a slight generalization of this regrading procedure where one only relaces the requirement that the $\alpha$-weight coincides mod 2 with the fermionic grading, only requiring that the twisting supercharge $Q$ is of weight $+1$.
+Given an action $\alpha$ of this more general class, one can define a new $\ZZ \times \ZZ/2$-grading on $E$ by simultaneously shifting the $\ZZ$ and $\ZZ/2$-gradings by $\alpha$.
+This results in a new $\ZZ \times \ZZ/2$-graded theory for which both the action $S$ and supercharge $Q$ are of bidegree $(1,0)$.
+This is a strict generalization of the situation above: the additional requirement that the $\alpha$-weight mod 2 on $E$ agrees with the fermionic grading forces this new $\ZZ \times \ZZ/2$-grading to be concentrated purely in the even $\ZZ/2$-degree part.
+\end{remark}
 
@@
 These fields have the same degrees as in the holomorphic BF theory.
+
 \end{proof}
@@
 
-The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation \eqref{eqn:(2,1)2} is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
+The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
 Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
-Finally, the term in parentheses in Equation \eqref{eqn:(2,1)2} agrees with the $t$-dependent terms in Equation \eqref{eqn:(2,0)}, (where now the fields are adjoint valued). 
+Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (where now the fields are adjoint valued). 
 We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
@@
 \begin{theorem}
-The holomorphic twist of 2d $\mc N=(4,4)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\Sect(\CC, T[1]((U\otimes K_\CC^{1/2}) \ham \gg))$.
+The holomorphic twist of 2d $\mc N=(4,4)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to a holomorphic BF theory, with moduli space given by $T^*[-1]\mr{Map}(\CC, T[1](U \ham \gg))$.
 This equivalence is $\mr U(1)$-invariant.
@@
 \item gauge fermions $(\lambda_-, \lambda_+) \in C^\infty(\RR^2 ; S_+ \otimes (\Tilde{W} \oplus \Tilde{W}) \otimes \fg)$. 
-\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$.
-\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$.
+\item matter bosons $\phi \in C^\infty(\RR^2 ; \Tilde{W} \otimes U)$;
+\item matter fermions $(\psi_-, \psi_+) \in C^\infty(\RR^2 ; S_- \otimes (U\oplus U))$;
 \item a ghost field $c \in \Omega^0(\RR^2 ; \fg)[1]$.
@@
 Such supercharges are automatically square-zero and holomorphic.
-There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha : \U(1) \to G_R$. 
+There is a twisting homomorphism $\phi : \U(1) \to G_R$ and twisting datum $\alpha \colon \U(1) \to G_R$. 
 \end{itemize}

### 2022-03-01 paper_journal_edits.tex
started responding to ref report

@@
 \left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
-\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
+\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)],
 \end{align*}
+where the superscript $!$ refers to the $\Dens_M$ valued dual space: $\mc E^! = \mc E^\vee \otimes \Dens_M$.
 \end{proof}
@@
 
-\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ defined by
+\item The pairing $\cL_c\otimes \cL_c \rightarrow \CC$ on the space of compactly supported sections of $L$ defined by
 \[\alpha\otimes \beta \mapsto \int_M \omega( \alpha, \beta)\]
@@
 \end{definition}
+
+\begin{remark}
+This definition is extremely broad, for instance the complex $\cL$ of fields can have cohomology in any degree.
+In specific applications to quantum field theory one is likely to encounter examples that are more heavily restricted by assumptions about the existence of a quantization with certain properties.
+\end{remark}
 
@@
 Let $X,Y$ be complex manifolds and $M$ a smooth oriented manifold.
-Fix an integer $m$ and suppose $X$ is equipped with an $m$-th root of the canonical bundle $K_X^{1/m}$.
-Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\bigoplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $m$ with respect to the grading.
+Fix an integer $m$ and suppose $X$ is equipped with a $j$-th root of the canonical bundle $K_X^{1/j}$.
+Let $\fg$ be an $L_\infty$ algebra equipped with a $\ZZ$-grading $\fg=\bigoplus_n \fg(n)$ and equipped with a symmetric pairing $\langle -, -\rangle$ as before, which has weight $j$ with respect to the grading.
 Then the generalized Chern--Simons theory is the classical field theory
-\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} K_X^{1/m}).\]
+\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} K_X^{1/j}).\]
 \label{def:sectChernSimons}
@@
 Under the composition
-\[\Omega^\bullet(V_\RR; \CC)\xto{p^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
-defined by pulling back forms along $p$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
+\[\Omega^\bullet(V_\RR; \CC)\xto{\mr{Re}^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
+defined by pulling back forms along $\mr{Re}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
 This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
@@
 
-We may identify $\wedge^2(V)\rightarrow \so(V)$ via
-\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
-This gives rise to an action map
+We may identify $\wedge^2(V)\rightarrow \so(V)$ via the map
+\[\omega\mapsto (v\mapsto -2\iota_{v^*} \omega),\]
+where $v$ is an element of $V$ and $\iota_{v^*}$ is the contraction with the associated element $v^* = (v,-)$ of $V^*$ induced by the bilinear pairing.  This gives rise to an action map
 \[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
@@
 We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
-Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as before we have the associated Dirac operator
+Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as described above we have the associated Dirac operator
 \[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]
@@
 \begin{prop}
-Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
+Suppose $Q_1,Q_2$ and $\lambda\in\Gamma(N, \Sigma)$. Then
 \[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
@@
 In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing, which should be thought of as the complexified Lie algebra of the gauge group.
+We will refer to the classification of twisting supercharges from \cite{ElliottSafronov} throughout.
 

### 2022-03-01 twist_selecta_referee_comments.tex
started responding to ref report

@@
 \begin{enumerate}
- \item Page 8:
+ \item Page 8: Added an explanatory comment.
  \item Page 18:
- \item Page 20 points 1 and 2:
- \item Page 20 point 3:
- \item Page 28:
- \item Page 29
+ \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
+ \item Page 20 point 3: Added a remark, thank you.
+ \item Page 27:
+ \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
  \item Page 32:
- \item Page 34 point 1:
+ \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part}
  \item Page 34 point 2:
- \item Page 35:
- \item Page 36:
+ \item Page 35: Added some clarification to the notation here.
+ \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
  \item Page 37:
  \item Page 38:
- \item Page 51:
+ \item Page 51: Thank you, reference added.
  \item Page 52:

### 2022-04-05 paper_journal_edits.tex
added some more referee responses

@@
 
-\begin{definition}
+\begin{definition} \label{classical_BV_def}
 A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
@@
 
+\begin{remark} \label{classical_BV_from_free_BV}
 The datum of a classical BV field theory as in Definition \ref{def:classicalfieldtheory} is equivalent to the datum of a free BV theory $(E, Q, \omega)$ equipped with an even functional
@@
 \[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E).\]
+\end{remark}
 
@@
 We call $L[1]$ the \defterm{space of BRST fields}.
+
+\begin{remark}
+We should note here that the formal moduli problem $\cM$ appearing in the definition is a local model for the stack of BRST fields \emph{before} imposing the classical equations of motion.
+This is in alignment with Remark \ref{classical_BV_from_free_BV} -- where we consider a classical BV theory and equip it with the additional data of a classical interaction -- but in contrast to the formal moduli problem occurring in Definition \ref{classical_BV_def}.
+\end{remark}
 
@@
 Let $Q\in\Sigma$ be a square-zero supercharge, which we will fix for the rest of this section. 
-The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian subspace $L\subset V$.
+The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex isotropic subspace $L\subset V$.
 Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$.
@@
 We may identify the odd part of the 9d $\mc N=1$ supersymmetry algebra with the odd part of the 10d $\mc N=(1, 0)$ supersymmetry algebra.
-Under this identification a supercharge $Q$ squares to zero in 9d iff it squares to zero in 10d.
+Under this identification a supercharge $Q$ squares to zero in 9d if and only if it squares to zero in 10d (we refer to the discussion in \cite[Section 4.8--4.10]{ElliottSafronov} for details on the spaces of square-zero spinors).
 
@@
 We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$.
-The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$.
-The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$.
+The supercharges $Q_+$ and $Q_-$ are each stabilized by copies of $\SU(4)\subset \Spin(8, \RR)$.
+The intersection of these copies of $\SU(4)$ is isomorphic to $\SU(3)\subset \Spin(8, \RR)$.
 We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \CC)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.

### 2022-04-05 twist_selecta_referee_comments.tex
added some more referee responses

@@
  \item Page 20 point 3: Added a remark, thank you.
- \item Page 27:
+ \item Page 27: Added an additional remark here to clarify the definition here.
  \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
@@
  \item Page 52:
- \item Page 54:
- \item Page 56:
+ \item Page 54: Added a reference for this claim to the relevant section of [ES].
+ \item Page 56: This section was written confusingly, and we have corrected it.
+Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
 \end{enumerate}

### 2022-04-06 paper_journal_edits.tex
merge

@@
 
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_M = S_N$.
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_N = S_M$.
 \end{itemize}
 \end{definition}
+
+\begin{remark}
+The last condition $p^* S_N = S_M$ should be understood as an equality as local functionals or equivalently as follows. 
+We recall that we can associate to the local functional $S_M$ an element of $\cO(\cE_{M,c}(M))$ where $\cE_{M,c}(M)$ is the space of compactly supported global sections of $E_M$ and similarly we can associate to the local functional $S_N$ an element of $\cO(\cE_{N,c}(N))$.
+Using the isomorphism $p^* E_N \cong E_M$, pulling back induces a map $p^* \colon \cO(\cE_{N,c}(N)) \to \cO(\cE_{M,c}(M))$ and we require $p^*S_N = S_M$ in $\cO(\cE_{M,c}(M))$.
+\end{remark}
 
@@
 In this paper we will extensively use the theory of spinors. 
+Throughout we work with the Euclidean signature and with complex spin representations. 
 Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
@@
 \label{dfn: super}
-A classical field theory $(E, S, \omega)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
+A (Euclidean) classical field theory $(E, S, \omega)$ is \defterm{supersymmetric} if $E\rightarrow M$ is an $\ISO(V_\RR)\times G_R$-equivariant vector bundle and the infinitesimal strict action of the translation Lie algebra $V$ on the classical theory is extended to a $\Spin(V_\RR)\times G_R$-equivariant $L_\infty$ action of the supertranslation Lie algebra $\fA$ on the classical theory.
 \end{definition}

### 2022-04-06 twist_selecta_referee_comments.tex
merge

@@
  \item Page 27: Added an additional remark here to clarify the definition here.
+ \brian{Maybe the issue is also with us calling this a BRST 'theory'? Perhaps less conflicting will be to refer to this as 'BRST data'. What do you think?}
  \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
- \item Page 32:
+ \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition.
+\brian{Todo, mobius example.
+Not sure what they want....
+Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.}
  \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part}
@@
  \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
- \item Page 37:
+ \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature. \brian{Todo: non associative stuff.}
  \item Page 38:

### 2022-04-06 twist_selecta_referee_comments.tex
added some notes to the comments file

@@
  \item Page 8: Added an explanatory comment.
- \item Page 18:
+ \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
  \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
@@
  \item Page 27: Added an additional remark here to clarify the definition here.
- \brian{Maybe the issue is also with us calling this a BRST 'theory'? Perhaps less conflicting will be to refer to this as 'BRST data'. What do you think?}
+ \brian{Maybe the issue is also with us calling this a BRST 'theory'?
+Perhaps less conflicting will be to refer to this as 'BRST data'.
+What do you think?} \chris{I don't think that's the issue, but maybe we should use a letter other than $\mathcal M$ for the formal moduli problem here.
+Like maybe $\mathcal F$ for fields?}
  \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
@@
 Not sure what they want....
-Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.}
- \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part}
- \item Page 34 point 2:
+Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.} \chris{He has an arrow pointing at the statement $p^*S_M = S_N$, so maybe the issue is with the way we think about action functionals.
+Maybe we should use different notation to indicate that the local functional really refers to a Lagrangian density, so there's no problem defining it on something noncompact (and no need to integrate).}
+ \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part.}
+ \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.
+Because this parameter has degree 1, it is formal and the issue indicated here does not arise.
  \item Page 35: Added some clarification to the notation here.
@@
  \item Page 51: Thank you, reference added.
- \item Page 52:
+ \item Page 52: \chris{I talked to Brian about this, I'm not totally sure that I understand the objection.
+Maybe the point is that the twisted theory can still admit real forms that could be thought of as twists of a real form of the supersymmetric theory, even if the corresponding real form didn't include a square-zero supercharge?}
  \item Page 54: Added a reference for this claim to the relevant section of [ES].

### 2022-04-14 paper_journal_edits.tex
A few more corrections

@@
 The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
- \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor \footnote{When we refer to the \emph{rank} of a supercharge we will always mean the rank as a tensor, for instance in the 8d $\mc N=8$ case supercharges live in a tensor product $S \otimes W$, where $S$ is an irreducible representation of $\spin(8)$ and $W$ is a two-dimensional auxiliary symplectic vector space.}.
+ \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor \footnote{When we refer to the \emph{rank} of a supercharge we will always mean the rank as a tensor, for instance in the 8d $\mc N=1$ case supercharges live in a tensor product $S \otimes W$, where $S$ is an irreducible representation of $\spin(8)$ and $W$ is a two-dimensional auxiliary symplectic vector space.}.
 This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface.
@@
 \begin{remark}
-The last condition $p^* S_N = S_M$ should be understood as an equality as local functionals or equivalently as follows. 
+The last condition $p^* S_N = S_M$ should be understood as an equality of local functionals or, equivalently, as follows. 
 We recall that we can associate to the local functional $S_M$ an element of $\cO(\cE_{M,c}(M))$ where $\cE_{M,c}(M)$ is the space of compactly supported global sections of $E_M$ and similarly we can associate to the local functional $S_N$ an element of $\cO(\cE_{N,c}(N))$.
@@
 \[\Omega^\bullet(V_\RR; \CC)\xto{\mr{Re}^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
-defined by pulling back forms along $\mr{Re}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
+defined by pulling back forms along ${\rm Re}\colon V \to V_{\RR}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component.
 This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
@@
 
-Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form.
+Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a positive-definite nondegenerate symmetric bilinear form.
 Denote by $V=V_\RR\otimes_\RR\CC$ its complexification.
@@
 
-Let $Q\in\Sigma$ be a square-zero supercharge, which we will fix for the rest of this section. 
-The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex isotropic subspace $L\subset V$.
+Let $Q\in\Sigma$ be a nonzero square-zero supercharge, which we will fix for the rest of this section. 
+The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian (i.e.
+maximal isotropic) subspace $L\subset V$.
 Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$.
@@
 The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills.
-It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive six-dimensional semi-spin representation and $W^* \cong S_-^6$.
+It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive semi-spin representation of $\Spin(6; \CC)$ and $W^* \cong S_-^6$.
 

### 2022-04-14 twist_selecta_referee_comments.tex
A few more corrections

@@
  \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
+ \pavel{Hmm.
+I would prefer not to add anything about $\infty$-categories as we are not really using them.
+Could be good to say that we use the equivalence as a black box: we \emph{define} FMPs as $L_\infty$ algebras.
+Like in Definition 1.6, how about we just give a definition ``an FMP is an $L_\infty$ algebra'' and add a remark after the definition that it is justified by the Lurie--Pridham result, but we will not be using it?}
+
  \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
+\pavel{We define cotangent bundles etc of formal moduli problems, but then work with local formal moduli problems.
+The confusion arises because we never really defined what $T^*BL$ is when $L$ is a local $L_\infty$ algebra.}
  \item Page 20 point 3: Added a remark, thank you.
- \item Page 27: Added an additional remark here to clarify the definition here.
+ \item Page 27: Added an additional remark here to clarify the definition.
  \brian{Maybe the issue is also with us calling this a BRST 'theory'?
@@
 Like maybe $\mathcal F$ for fields?}
+ \pavel{Perhaps, we should just reply to the referee rather than add a remark?
+Agree about changing the letters though to clarify matters: the FMP he writes down is associated to BV fields, while here we have an extra data.
+If we change the letters, it will be easier to address the objection.}
  \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
@@
 Maybe we should use different notation to indicate that the local functional really refers to a Lagrangian density, so there's no problem defining it on something noncompact (and no need to integrate).}
+ \pavel{A bit confused about the new Remark 1.59, need to discuss.}
  \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part.}
@@
  \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
- \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature. \brian{Todo: non associative stuff.}
+ \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature.
+\brian{Todo: non associative stuff.} \pavel{I don't think we should mention Euclidean signature in the beginning of Section 2.1 (we are talking about complex vector spaces there).}
  \item Page 38:
@@
 Maybe the point is that the twisted theory can still admit real forms that could be thought of as twists of a real form of the supersymmetric theory, even if the corresponding real form didn't include a square-zero supercharge?}
+ \pavel{I've added Lagrangian = maximal isotropic}
  \item Page 54: Added a reference for this claim to the relevant section of [ES].
@@
 Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
+ \item Page 77: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
 \end{enumerate}

### 2022-04-15 paper_journal_edits.tex
A fistful of corrections

@@
 In this section we formulate the procedure of dimensional reduction of a classical field theory.
-Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e.
+Fix a submersion $p\colon M\rightarrow N$ equipped with a fiberwise density, i.e.
 an isomorphism $p^*\Dens_N\cong \Dens_M$.
@@
 
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_N = S_M$.
+\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$.
 \end{itemize}
@@
 \begin{remark}
-The last condition $p^* S_N = S_M$ should be understood as an equality of local functionals or, equivalently, as follows. 
-We recall that we can associate to the local functional $S_M$ an element of $\cO(\cE_{M,c}(M))$ where $\cE_{M,c}(M)$ is the space of compactly supported global sections of $E_M$ and similarly we can associate to the local functional $S_N$ an element of $\cO(\cE_{N,c}(N))$.
-Using the isomorphism $p^* E_N \cong E_M$, pulling back induces a map $p^* \colon \cO(\cE_{N,c}(N)) \to \cO(\cE_{M,c}(M))$ and we require $p^*S_N = S_M$ in $\cO(\cE_{M,c}(M))$.
+The last condition involves a pullback of local functionals. Using the natural embeddings
+\[\oloc(\cE_M)\subset \cO(\cE_{M, c}),\qquad \oloc(\cE_N)\subset \cO(\cE_{N, c})\]
+we can interpret $S_N$ and $S_M$ as functionals on compactly-supported fields. Under these embeddings the pullback of local functionals corresponds to the map
+\[\cO(\cE_{N, c})\longrightarrow \cO(\cE_{M, c})\]
+which is the restriction under the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ for which we use the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$; these integrals are convergent due to the compact support condition.
 \end{remark}
@@
 In this paper we will extensively use the theory of spinors.
-Throughout we work with the Euclidean signature and with complex spin representations. 
 Let $V$ be a complex vector space equipped with a nondegenerate symmetric bilinear pairing.
@@
 \subsection{Supersymmetry Algebras} \label{sect:susyalgebras}
-In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}, we refer there for more details.
+In this section we will recall the framework for supersymmetry algebras and their classification following Deligne \cite{DeligneSpinors} and our previous work \cite{ElliottSafronov}; we refer there for more details.
 
@@
 
-Let $A$ be a unital (possibly non-associative) complex algebra equipped with an antiinvolution $\sigma\colon A\rightarrow A$. We make the following assumptions:
+Let $A$ be a unital alternative (recall that this means that $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric) complex algebra equipped with an antiinvolution $\dagger\colon A\rightarrow A$.
+We make the following assumptions:
 \begin{enumerate}
-\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A$ spanned by the unit.
-
-\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A\rightarrow \CC$. We assume that it is nondegenerate.
+\item The map $\Re(x)=x\mapsto (x + x^\dagger)/2$ defines a projector onto the subspace of $A$ spanned by the unit.
+
+\item By the previous assumption we have a quadratic form $xx^\dagger\colon A\rightarrow \CC$. We assume that it is nondegenerate.
 \end{enumerate}
 
-In fact, the data of the antiinvolution $\sigma$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto x\sigma(x)$, i.e.
+In fact, the data of the antiinvolution $\dagger$ may equivalently be encoded in the data of a non-degenerate multiplicative norm $x\mapsto xx^\dagger$, i.e.
 $A$ is a real composition algebra \cite[Chapter 1.3]{SpringerVeldkamp}.
 
-For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. 
+For a $2\times 2$-matrix $M$ with entries in $A$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\dagger$ to the entries. 
 Let $V$ to be the complex vector space of $2\times 2$ Hermitian matrices with values in $A$.
 Note that $\dim(V) = \dim(A) + 2$. 
-The space $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. 
+The space $V$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$ (even though $A$ is non-associative, the determinant is well-defined since we are talking about $2\times 2$ matrices).
 Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.
@@
 
-Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction
+If $A$ is associative, we may discuss left and right $A$-modules.
+Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\dagger\colon A\rightarrow A$.
+Since $A$ is a Frobenius algebra, we have the following basic construction.
 
 \begin{lemma}
-Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
+Suppose $A$ is associative.
+Let $M$ be a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$.
 Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
@@
 
-Consider the left $A$-module $\Sigma=A\oplus A$ and the right $A$-module $\Sigma^* = A\oplus A$.
+Consider $\Sigma=A\oplus A$ equipped with the left $A$-action and $\Sigma^* = A\oplus A$ equipped with the right $A$-action.
 We will equip the sum $\Sigma \oplus \Sigma^*$ with an action of the Clifford algebra ${\rm C}\ell_V$.  
@@
 \[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
-It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
+If $A$ is associative, it satisfies $(Q_1 a^\dagger, Q_2) = (Q_1, Q_2 a)$. Then the extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
 \[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]
@@
 We will now state two important properties of $\Gamma$ and the spinorial pairing.
-The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
+The following statement (an analog of the Fierz identity) was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).
 
 \begin{theorem}
-Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
+For $Q_1, Q_2, Q_3\in\Sigma$ we have
 \[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
@@
 
-\item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $\sigma(x) = -x$.
+\item (\textbf{4d $\mc N=1$ supersymmetry}) $A = \CC\otimes_{\RR}\CC\cong \CC[x]/(x^2+1)$ with $x^\dagger = -x$.
 Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations of $\Spin(4;\CC)$.
 
-\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator.
+\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\dagger$ given by the dual operator.
 Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$ is the sum of two copies of a semi-spin representation of $\Spin(6;\CC)$.
@@
 
-We will now fix a composition algebra $A$ with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
-The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1\sigma(a_2))$ on $A$ endows $W$ with a pairing.
-Both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
-
-Since $\Sigma$ and $\Sigma^*$ are right $A$-modules, by Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
-\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)\sigma(q_1) q_2.\]
+We will now fix a composition algebra $A$ with an antiinvolution $\dagger$ as in Section \ref{sect:compositionalgebras} and set $W = A$.
+The nondegenerate symmetric bilinear pairing $a_1, a_2\mapsto \Re(a_1 a_2^\dagger)$ on $A$ endows $W$ with a pairing.
+
+If we additionally assume that $A$ is associative, then both $\Sigma$ and $\Sigma^*$ are right $A$-modules and the Clifford actions $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ are maps of right $A$-modules.
+By Lemma \ref{lm:extendpairing} we may extend the scalar spinorial pairing to an $A$-valued pairing $\Sigma\otimes \Sigma^*\rightarrow A$ by
+\[(s_1\otimes q_1, s_2\otimes q_2)^A = (s_1, s_2)q_1^\dagger q_2.\]
 We now give the analogue of Theorem \ref{thm:matter3psi} in the 2d chiral setting.
@@
 \begin{theorem}
-For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
+Suppose the composition algebra $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
 \[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2))Q_3.\]
@@
 (q_1, q_2) \rho(\Gamma_+(s, s)) f\otimes q_3 &= 2(s, f) s\otimes (q_1, q_2) q_3 \\
-&= (s, f) s\otimes (q_1\sigma(q_2) + q_2\sigma(q_1)) q_3.
+&= (s, f) s\otimes (q_1 q_2^\dagger + q_2 q_1^\dagger) q_3.
 \end{align*}
 We have
-\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (\sigma(q_2)q_3),\]
+\[Q_1(Q_2, Q_3)^A = s\otimes q_1 (s, f) (q_2^\dagger q_3),\]
 so the left-hand side is
-\[s(s, f)\otimes (q_1(\sigma(q_2) q_3) + q_2(\sigma(q_1)q_3)).\]
+\[s(s, f)\otimes (q_1(q_2^\dagger q_3) + q_2(q_1^\dagger q_3)).\]
 By associativity of $A$ the two expressions are equal.
@@
 Consider as before $V_\RR$ and a Clifford module $\Sigma\oplus \Sigma^*$ satisfying Assumption \ref{assumption:3psi}.
-In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\sigma$ as in Section \ref{sect:compositionalgebras}.
+In addition, fix a complex associative composition algebra $A$ equipped with an antiinvolution $\dagger$ as in Section \ref{sect:compositionalgebras}.
 Suppose $\Sigma\oplus \Sigma^*$ carries a compatible right $A$-module structure.
@@
 Let $P$ be a left $A$-module equipped with a $\CC$-valued nondegenerate symmetric bilinear pairing such that
-\[(av, w) = (v, \sigma(a)w).\]
+\[(av, w) = (v, a^\dagger w).\]
 Moreover, assume $P$ carries a $\fg$-action commuting with the $A$-module structure and preserving the bilinear pairing.
@@
 Indeed, a square-zero supercharge induces a 5-dimensional isotropic subspace of $\RR^{10}$, which only exists in the split signature $5+5$ (in which case there is no real structure for the Weyl spinor representation).
-So necessarily, twists of maximal super Yang--Mills theory cannot be compatible with any unitary structure.
 \end{remark}

### 2022-04-15 twist_selecta_referee_comments.tex
A fistful of corrections

@@
  \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition.
-\brian{Todo, mobius example.
-Not sure what they want....
-Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.} \chris{He has an arrow pointing at the statement $p^*S_M = S_N$, so maybe the issue is with the way we think about action functionals.
-Maybe we should use different notation to indicate that the local functional really refers to a Lagrangian density, so there's no problem defining it on something noncompact (and no need to integrate).}
- \pavel{A bit confused about the new Remark 1.59, need to discuss.}
- \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part.}
+ \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here.
  \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.
@@
  \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
- \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature.
-\brian{Todo: non associative stuff.} \pavel{I don't think we should mention Euclidean signature in the beginning of Section 2.1 (we are talking about complex vector spaces there).}
- \item Page 38:
+ \item Page 37, point 1: We have added the clarifying adjective ``Euclidean''.
+ \item Page 37, point 2: We have clarified when we are working with merely alternative algebras and when we require associativity.
+ \item Page 38: We have mentioned that it is a version of the Fierz identity, thank you.
  \item Page 51: Thank you, reference added.
- \item Page 52: \chris{I talked to Brian about this, I'm not totally sure that I understand the objection.
-Maybe the point is that the twisted theory can still admit real forms that could be thought of as twists of a real form of the supersymmetric theory, even if the corresponding real form didn't include a square-zero supercharge?}
- \pavel{I've added Lagrangian = maximal isotropic}
+ \item Page 52: Thank you for the remark; we have removed the confusing sentence.
  \item Page 54: Added a reference for this claim to the relevant section of [ES].

### 2022-04-15 paper_journal_edits.tex
more corrections to earlier in the paper

@@
 That is, given a space $\mc F$ of fields and an action functional with derivative $\d S$, one considers not just the usual locus in $\mc F$ of fields with $\d S(\phi) = 0$, but the derived intersection $\mr{dCrit}(S) = \mc F \cap^h_{T^*\mc F} \Gamma_{\d S}$ of the zero section in $T^*\mc F$ with the graph of $\d S$.
+
 The formalism we describe below can be interpreted as an abstract formalism for modelling the tangent complex at a point to a derived critical locus $\mr{dCrit}(S)$ as a formal moduli problem.
+We will provide this motivation and interpretation from formal derived geometry in brief before proceeding to the main definitions of this section (for which an understanding of the following motivational notions is not required).
 
@@
 This important result will serve as motivation for the main definition in this section (Definition \ref{def:classicalfieldtheory}).
+
+\begin{remark}
+We would like to emphasise that, while our definitions are motivated by formal derived geometry, all of our constructions will be formulated entirely using the language of $L_\infty$-algebras.
+No knowledge of $\infty$-categories or formal derived algebraic geometry will be needed for any of the results we present in this paper, and -- indeed -- using the result of Lurie and Pridham cited above, the datum of a formal moduli problem is equivalent to the datum of an $L_\infty$ algebra.
+\end{remark}
 
@@
 
-\begin{example}
+\begin{example} \label{Hamiltonian_example}}
 Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with an $n$-shifted symplectic pairing $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
@@
 
-Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
+Now suppose $L$ is a \emph{local} $L_\infty$ algebra on a manifold $M$.
+By a local $L_\infty$ algebra, we mean an $L_\infty$ algebra whose underlying graded vector space is the sheaf of sections of a graded vector bundle, where the differential and the brackets are given by polydifferential operators (see \cite[Section 3.1.3]{Book2} for a detailed definition).
+
+\begin{remark}
+The constructions given in Examples \ref{ex:tangentBg} to \ref{Hamiltonian_example} all still make sense for local $L_\infty$ algebras, although we should take some care.
+Instead of using the \emph{linear} dual $\gg^*$ of a dg Lie algebra, we should always form the density-valued dual $\L^!
+= L^* \otimes \mr{dens}_M$ for a local $L_\infty$ algebra $L$ on a manifold $M$.
+\end{remark}
+
+For every open subset $U\subset M$ we have a formal moduli problem
 \[(B L)(U) = B L(U),\]
@@
 \begin{itemize}
-\item A local formal moduli problem $\cM$ represented by a local $L_\infty$ algebra $L$.
-\item A local functional $S_{\mr{BRST}} \in \oloc(\cM)$ of polynomial degree $\geq 2$.
+\item A local formal moduli problem $\mc F$ represented by a local $L_\infty$ algebra $L$.
+\item A local functional $S_{\mr{BRST}} \in \oloc(\mc F)$ of polynomial degree $\geq 2$.
 \end{itemize}
@@
 \begin{remark}
-We should note here that the formal moduli problem $\cM$ appearing in the definition is a local model for the stack of BRST fields \emph{before} imposing the classical equations of motion.
+We should note here that the formal moduli problem $\mc F$ appearing in the definition is a local model for the stack of BRST fields \emph{before} imposing the classical equations of motion.
 This is in alignment with Remark \ref{classical_BV_from_free_BV} -- where we consider a classical BV theory and equip it with the additional data of a classical interaction -- but in contrast to the formal moduli problem occurring in Definition \ref{classical_BV_def}.
@@
 
-Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_{\rm anti}$.
-Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter.
-Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.
+Given a classical BRST theory $\mc F$, we may consider the cotangent theory $T^*[-1]\mc F$ whose action functional we denote by $S_{\rm anti}$.
+Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\mc F\rightarrow \mc F$ by the same letter.
+Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\mc F)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\mc F)$.
 
 \begin{definition}
-Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory.
-The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
+Let $(\mc F, S_{\mr{BRST}})$ be a classical BRST theory.
+The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\mc F$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
 \end{definition}
@@
 In general, multiple BRST theories can give rise to the same BV theory.
-A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} $F$ with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
-Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on $F$.
+A BV theory $(E, Q_{\mr{BV}}, \omega, I)$ is of cotangent type as long as there is \emph{some} graded vector sub-bundle with $S_{\mr{BRST}} = 0$ producing the given theory using the construction above.
+Theories of cotangent type can still have interesting, non-trivial action functionals, encoded by the $L_\infty$ structure on the sub-bundle.
 \end{remark}
@@
 \begin{remark}
-It is common to refer to coordinates on $\cM$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\cM$ as \defterm{antifields}.
+It is common to refer to coordinates on $\mc F$ as \defterm{fields} and coordinates along the cotangent direction of $T^*[-1]\mc F$ as \defterm{antifields}.
 Given a field $\phi$ the corresponding antifield will be denoted by $\phi^*$.

### 2022-04-15 twist_selecta_referee_comments.tex
more corrections to earlier in the paper

@@
  \item Page 8: Added an explanatory comment.
- \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
- \pavel{Hmm.
-I would prefer not to add anything about $\infty$-categories as we are not really using them.
-Could be good to say that we use the equivalence as a black box: we \emph{define} FMPs as $L_\infty$ algebras.
-Like in Definition 1.6, how about we just give a definition ``an FMP is an $L_\infty$ algebra'' and add a remark after the definition that it is justified by the Lurie--Pridham result, but we will not be using it?}
+ \item Page 18: As the referee very reasonably points out, we only use the notion of a formal moduli problem to provide geometric motivation for the constructions formulated within the paper.
+In fact, by the cited result of Lurie and Pridham, the datum of a formal moduli problem is equivalent to that of an $L_\infty$ algebra, and all the results that we provide are presented in the latter language, so that knowledge of $\infty$-categories and derived geometry are not needed in order to understand the paper.
+We added a remark (Remark 1.1) to point this out to the reader, and to reassure the reader that a detailed understanding of this motivation is not needed to understand the results of the paper.
 
- \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
-\pavel{We define cotangent bundles etc of formal moduli problems, but then work with local formal moduli problems.
-The confusion arises because we never really defined what $T^*BL$ is when $L$ is a local $L_\infty$ algebra.}
+ \item Page 20 points 1 and 2: Some further explanation was added for the notation here, along with some additional orienting comments on the introduction of local $L_\infty$ algebras.
  \item Page 20 point 3: Added a remark, thank you.
  \item Page 27: Added an additional remark here to clarify the definition.
- \brian{Maybe the issue is also with us calling this a BRST 'theory'?
-Perhaps less conflicting will be to refer to this as 'BRST data'.
-What do you think?} \chris{I don't think that's the issue, but maybe we should use a letter other than $\mathcal M$ for the formal moduli problem here.
-Like maybe $\mathcal F$ for fields?}
- \pavel{Perhaps, we should just reply to the referee rather than add a remark?
-Agree about changing the letters though to clarify matters: the FMP he writes down is associated to BV fields, while here we have an extra data.
-If we change the letters, it will be easier to address the objection.}
+In addition, in order to emphasise the difference here with the notation we use for the $L_\infty$ algebra of BF fields, we altered our notation to refer to the space $\mathcal F$ of BRST fields, where $\mathcal F$ is intended to suggest ``fields'', instead of using $\mathcal M$ as in the BV context.
 \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.

### 2022-04-19 paper_journal_edits.tex
p 36

@@
 
-\begin{example} \label{Hamiltonian_example}}
+\begin{example} \label{Hamiltonian_example}
 Suppose $\fg$ is a dg Lie algebra and $U$ a $\fg$-representation equipped with an $n$-shifted symplectic pairing $U\otimes U\rightarrow \CC[n]$. Consider the dg Lie algebra
@@
 \[v_1 v_2 + v_2 v_1 = 2(v_1, v_2).\]
-Consider a $\ZZ/2\ZZ$-graded Clifford module $M=M^+\oplus M^-$.
-Denote the Clifford action by $\rho(v)\in\eend(M)$.
-We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
+Consider a $\ZZ/2\ZZ$-graded Clifford module 
+\begin{equation}\label{eqn:cliffordmod}
+M=M^+\oplus M^- .
+\end{equation}
+We note that in many examples with extended supersymmetry that $M$ is irreducible as a spin representation.
+Denote the Clifford action by $\rho(v)\in\eend(M)$. We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
 \[(\rho(v) Q_1, Q_2) = (Q_1, \rho(v) Q_2)\]
@@
 For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
-\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]
+\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X\]
 \label{prop:cliffordactionproperty1}
+where $\iota_{v} \colon \wedge^2(V) \to V$ denotes contraction by an element $v \in V$ using the nondegenerate symmetric pairing. 
 \end{prop}
@@
 We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
-Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$ as described above we have the associated Dirac operator
+Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$, as in \eqref{eqn:cliffordmod}, we have the associated Dirac operator
 \[\sd{\d}\colon \Gamma(N, \Sigma)\rightarrow \Gamma(N, \Sigma^*).\]
@@
 
-Finally, we have the following important compatibility between the Clifford action of differential forms and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
+Finally, we have the following important compatibility between the Clifford action of differential forms, see \eqref{eq:quantizationtwoforms}, and the Dirac operator proved in \cite[equation 7.6]{Snygg}.
 
@@
 Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
-\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q.\]
+\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q\]
+as sections of $\Sigma^* \to N$. 
 \label{prop:cliffordactionproperty3}

### 2022-04-19 twist_selecta_referee_comments.tex
p 36
prop 2.2

@@
  \item Page 35: Added some clarification to the notation here.
- \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
+ \item Page 36: We have clarified notations throughout section 2.1 per the referees advice. 
+ We have kept the statement of Proposition 2.2 the same.
+In the statement $Q_i \in \Sigma$ have no dependence on spacetime $N$ whereas $\lambda$ is a general section of the bundle that $\Sigma$ determines.
  \item Page 37, point 1: We have added the clarifying adjective ``Euclidean''.

### 2022-04-19 paper_journal_edits.tex
prop 2.2
typos

@@
 These results yield a practical approach to the problem of mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang--Mills theory.
-Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
+Furthermore, in all examples of theories obtained via twisting occurring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.
 The twisted gauge theories here are all either equivalent to BF-type theories (see Section \ref{gen_BF_section}) or deformations of such theories by a holomorphic differential operator.
@@
 \end{equation}
-We note that in many examples with extended supersymmetry that $M$ is irreducible as a spin representation.
+We note that in many examples with extended supersymmetry that $M$ is reducible as a spin representation.
 Denote the Clifford action by $\rho(v)\in\eend(M)$. We assume the Clifford module is equipped with a nondegenerate pairing $(-, -)\colon M^+\otimes M^-\rightarrow \CC$ such that
@@
 
-We may extend the discussion to the case of Riemannian manifolds $N$, where we replace $V$ by the vector bundle $TN$.
+We may extend the discussion to the case of a Riemannian manifold $N$, where we replace $V$ by the vector bundle $TN$. 
 Given a bundle of Clifford modules $M=\Sigma\oplus \Sigma^*$, as in \eqref{eqn:cliffordmod}, we have the associated Dirac operator
@@
 \begin{prop}
-Suppose $Q_1,Q_2$ and $\lambda\in\Gamma(N, \Sigma)$. Then
-\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
+Suppose $Q_1,Q_2 \in \Sigma$ and $\lambda\in\Gamma(N, \Sigma)$. Then
+\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2\]
 \label{prop:cliffordactionproperty2}
+as sections of $\Sigma^* \to N$. 
 \end{prop}

### 2022-04-19 paper_journal_edits.tex
2.2 and 2.3
typos
merge

--- 2022-04-19 paper_journal_edits.tex
@@
 is commutative.
-
-\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$.
+\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$ (see the remark below).
 \end{itemize}
@@
 \begin{remark}
-The last condition involves a pullback of local functionals. Using the natural embeddings
-\[\oloc(\cE_M)\subset \cO(\cE_{M, c}),\qquad \oloc(\cE_N)\subset \cO(\cE_{N, c})\]
-we can interpret $S_N$ and $S_M$ as functionals on compactly-supported fields. Under these embeddings the pullback of local functionals corresponds to the map
-\[\cO(\cE_{N, c})\longrightarrow \cO(\cE_{M, c})\]
-which is the restriction under the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ for which we use the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$; these integrals are convergent due to the compact support condition.
+The last condition involves a pullback of local functionals.
+Indeed, the isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine a map $p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)$ defined as follows. 
+First, we define a map
+\[
+p^* \colon \cO(\cE_{N,c}) \to \cO(\cE_{M,c}) 
+\]
+as the restriction of the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ which uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$---these integrals are convergent due to the compact support condition.
+Next, we use the natural embedding
+\[\oloc(\cE_M)\subset \cO(\cE_{M, c})
+\]
+to interpret any local functional $S \in \oloc(\cE_M)$ as a functional on compactly-supported fields $\cE_{M,c}$. 
+It is immediate to see that if $S$ is a local functional then so is $p^*S$ and hence we obtained the desired map.
 \end{remark}
@@
 \begin{prop}
-Suppose $Q_1,Q_2$ and $\lambda\in\Gamma(N, \Sigma)$. Then
-\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
+Suppose $Q_1,Q_2$ are covariantly constant sections of $\Sigma$ and $\lambda$ is a general smooth section of $\Sigma$.
+Then
+\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2\]
 \label{prop:cliffordactionproperty2}
+as sections of $\Sigma \to N$. 
 \end{prop}
@@
 \begin{prop}
-Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
+Suppose $Q$ is a covariantly constant section of $\Sigma$ and $X\in\Omega^p(N)$. Then
 \[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q\]
-as sections of $\Sigma^* \to N$. 
+as sections of $M = \Sigma \oplus \Sigma^* \to N$. 
 \label{prop:cliffordactionproperty3}

### 2022-04-19 paper_journal_edits.tex

@@
 \begin{prop}
-Suppose $Q_1,Q_2$ are covariantly constant sections of $\Sigma$ and $\lambda$ is a general smooth section of $\Sigma$.
-Then
+Suppose $Q_1,Q_2$ and $\lambda$ are sections of the bundle $\Sigma$ on $N$, and suppose that $Q_1$ and $Q_2$ are covariantly constant. Then
 \[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2\]

### 2022-04-19 twist_selecta_referee_comments.tex
fixed wrong page number

@@
  \item Page 36: We have clarified notations throughout section 2.1 per the referees advice.
- We have kept the statement of Proposition 2.2 the same.
-In the statement $Q_i \in \Sigma$ have no dependence on spacetime $N$ whereas $\lambda$ is a general section of the bundle that $\Sigma$ determines.
+We have also clarified the statement of Proposition 2.2 and 2.3.
+For instance, in the statement of Proposition 2.2, $\lambda$ is allowed to be any section of the bundle $\Sigma$, whereas $Q_i$ are assumed to be covariant constant sections.
  \item Page 37, point 1: We have added the clarifying adjective ``Euclidean''.
@@
 Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
- \item Page 77: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
+ \item Page 75: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
 \end{enumerate}

### 2022-04-19 paper_journal_edits.tex
fixed compilation error
rephrased remark

@@
 is commutative.
-\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$ (see the remark below).
+\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$.
 \end{itemize}
@@
 \begin{remark}
-The last condition involves a pullback of local functionals.
-Indeed, the isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine a map $p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)$ defined as follows. 
-First, we define a map
-\[
-p^* \colon \cO(\cE_{N,c}) \to \cO(\cE_{M,c}) 
-\]
-as the restriction of the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ which uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$---these integrals are convergent due to the compact support condition.
-Next, we use the natural embedding
-\[\oloc(\cE_M)\subset \cO(\cE_{M, c})
-\]
-to interpret any local functional $S \in \oloc(\cE_M)$ as a functional on compactly-supported fields $\cE_{M,c}$. 
-It is immediate to see that if $S$ is a local functional then so is $p^*S$ and hence we obtained the desired map.
+The isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine the pullback map
+\[p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)\]
+of local functionals used in the last condition.
+Recall that one also has inclusion maps $\oloc(\cE_N)\hookrightarrow \cO(\cE_{N, c})$ and $\oloc(\cE_M)\hookrightarrow \cO(\cE_{M, c})$ allowing us to interpret local functionals as functionals on compactly-supported fields.
+Then there is a commutative diagram
+\[
+\xymatrix{
+\oloc(\cE_N) \ar^{p^*}[r] \ar[d] & \oloc(\cE_M) \ar[d] \\
+\cO(\cE_{N, c}) \ar[r] & \cO(\cE_{M, c})
+}
+\]
+where the bottom map is the restriction under the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$: this uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$ and this is well-defined due to the compact support condition.
 \end{remark}

### 2022-04-19 paper_selecta_edits.tex
Selecta version

--- 2022-04-19 paper_journal_edits.tex
@@
 \begin{document}
-
-\maketitle
 
@@
 
-\pagestyle{intro}
+\maketitle
+
+%\pagestyle{intro}
 \setcounter{tocdepth}{2}
@@
  \end{tabular}
- \caption{Twists of Maximally Supersymmetric Pure Yang--Mills Theories with Lie algebra $\fg$ (16 supercharges).}
+ \end{adjustbox}
+ \caption{Twists of Maximally Supersymmetric Pure Yang-Mills Theories with Lie algebra $\fg$ (16 supercharges).}
  \label{table_of_twists_16}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
+  \end{adjustbox}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
  \label{table_of_twists_8}
@@
   \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
+  \end{adjustbox}
+ \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a chiral multiplet valued in a representation $R$ (4 supercharges).}
  \label{table_of_twists_4}
@@
  \end{tabular}
- \caption{Twists of Supersymmetric Yang--Mills Theories in two dimensions with gauge group $G$.
+ \end{adjustbox}
+ \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.
 When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$.
@@
 The constructions given in Examples \ref{ex:tangentBg} to \ref{Hamiltonian_example} all still make sense for local $L_\infty$ algebras, although we should take some care.
-Instead of using the \emph{linear} dual $\gg^*$ of a dg Lie algebra, we should always form the density-valued dual $\L^!
+Instead of using the \emph{linear} dual $\gg^*$ of a dg Lie algebra, we should always form the density-valued dual $L^!
 = L^* \otimes \mr{dens}_M$ for a local $L_\infty$ algebra $L$ on a manifold $M$.
